### 2011-12-10 vm_snapshot_sim/approach.tex
initial vm snapshot paper

\section{Approach}
\subsection{Similarity Detection}
Data locality is important to 
Bringing deduplication to a distributed environment may
break data locality because 
introduces several 
new problems. Former studies of centralized deduplication systems showed
 that spatial locality of 
data streams must be preserved. This is because the entire
 chunk hashes are too big to be loaded into memory, 
thus certain caching mechanism must be applied, and this require 
proximal chunk IDs to be stored at nearby places. 
Furthermore, if chunks are not stored on the disk
base on spatial locality, file read requests will result in entirely
 random disk access, since each data chunk is so small, that would 
become a disaster for any host file system.

\subsubsection{Granuarity}
Extreme binning uses files as the basic unit for
similarity detection, this simplifies the metadata management of
distributed storage because it only need to manage the mapping
 from files to their bins. However, this solution doesn't
consider the uncertainty of file sizes: it is possible that many similar big files
can be assigned to one container, thus some storage nodes may be overlaoded when
others are spare. For example, Amazon's S3 stores huge amount of
virtual machine images which are very similar, so those files will be assigned
to only a few nodes by the extreme binning.
Even those files can be evenly distributed to hundreds of nodes, the overall 
deduplication ratio won't be good since too much dulicates are tolerated.

We suggest that data segment at the size of several megabytes is the best unit for
similarity based deduplication. Sparse Indexing has already 
proved that content based chunking method can be also applied to break the list of
chunks into large segments, such that each segment contains a few hundred of small chunks.
Using such medium size segments as the basic unit for similarity detection could eliminate
disadvantages mentioned above, and doing so won't add  much computation cost
to the deduplication process.

\subsubsection{Signature Algorithm}
In general, we expect to generate a signature for each segments, such that if two segments
has a lot of chunks in common, there is a high probablity that their signatures are the same.
Since we represent segment as a list of chunks, the information available for generating 
signatures are the chunk hash values, chunk sizes, and offsets.

Extreme binning suggests the min-hash signature algorithm. By Broder's theorem, 
the probability that the smallest elements of two sets are identical, is equal to their Jaccard similarity coefficient.
Therefore they use the smallest chunk hash value as the signature to represent the whole file.

We propose a Size-based Similarity Detection (SSD) method, 
which is more storage specific because it uses the chunk size information. Intuitively if one segment is
only slightly modified, then most of the chunks should remain the same, thus their sizes should mostly remain the same.
Even modifications could change the chunk hash value, due to the modification resistant property of 
content based chunking algorithm, most of the time that chunk size is unchanged. Therefore if we want to 
generate a $n$ bit signature for a segment, we simply split the range of size evenly at logarithmic scale by $n$ , and count how many chunks
fall into each range. Then if that number is above average, we set the bit for that range as 1, otherwise 0, as shown
in figure.

By using the signature of segment to represent all of its chunks, Sloud clusters
segments that are highly similar into one container. Each container is the collection of 
segments that have the same signature. When a new segment arrives, it will be assigned by its signature to
the corresponding container which has chunks that are highly similar to it. Thus,  highly accurate deduplcation is achieved.
However, since every segment is only assigned to one container, if any of the its chunks do not 
exist in that container but exist elsewhere, they will be treated as new chunks, in other words, 
duplicates are allowed. Sloud trade such storage space efficiency for faster deduplication and  
fewer resources consumption such as RAM usage and disk access. In addition, we believe this is the best way to 
build distributed deduplication solution without losing data locality.

\subsection{Architecture}
We designed a distributed storage system, Sloud, to demonstrate the possibility of
providing scalibility to large scale deduplication systems. Sloud cluster similar segment into containers and store
those containers to the disk. The overall architecture is shown in .
Sloud uses a DHT service for node discovery and storage space partitioning, all nodes in Sloud are completely equal, 
there's no node that has special responsibilities.

At every storage node , we keep in memory a bloom filter and a segment index for every container, 
the rest of part of the container, including the chunk data and chunk index, are stored onto disk. When a new segment comes in, the segment index is used
for the first pass of deduplication, such that duplicate segments can be detected without looking below. The second pass is done by bloom filter,
most of new chunks are immediately identified. Otherwise, Sloud look into the chunk index for the final pass of deduplication, as shown in Figure.

Assuming all node are reliable, no failure ever happens, and there is no replication involved, 
the deduplication process can be described as following:
\begin{enumerate}
\item Firstly,  sender scan the files that to need be deduplicated, generate all information about chunks and segments.
\item For each segment, sender queries the DHT service to find out the node that is responsible to segment's container, then it will send a segment writting message with segment's signature and hash.
\item The receiver then lookup corresponding container's segment index to see if its a duplicate. If it is, there is no need for further deduplication, it will update the segment's reference count and acknowledge the sender deduplication is complete.
\item If the segment hash does not exist in segment index, receiver asks sender for the segment recipe, which is all the chunks' information except the actual data.
\item On receiving the segment recipe, receiver starts deduplicate them against existing chunks in that container. Firstly it goes to the bloom filter, most of the new chunks are identified in this step. For those chunks that are identified as 'exist' by the bloom filter, the receiver looks into chunk index to see if they are really there or not. At any step, if a chunk is identified as new, a request of chunk data is immdeiately sent out.
\item Incoming chunk data are written to a temporary disk place until all new chunks belonging to that segment are received. Upon this time, receiver merges new data into that container's disk file.
\item Finally the receiver update the segment index and chunk index, and acknowledge the sender this segment is sucessfully received and deduplicated.
\end{enumerate}

\subsection{Replication and Concistency}
Sloud uses consistent hashing ring\cite{consistent_hash97} to maintain a dynamic hash table for node discovery. 
Each node is given an unique ID and the Sha-1 checksum of their IDs are mapped onto this ring. 
Containers are also mapped onto the consistent hash ring by the Sha-1 checksum of their represented signatures.
The benefit of using consistent hash is that adding or removing nodes from the system won't introduce too much
workload of reorganization. For each container on the ring, Sloud treat the first three consequential nodes as 
the primary replicas of that container, and the next two nodes as the secondary replicas. Primary replicas hold
the real copy of container's data, the secondary replicas are only used to cache write requests when some of the 
primary replicas are temporarily unavailable.

Sloud provides a variation of eventual consistency\cite{eventually09} in its data replication. Read
requests will succeed if at least one of the three primary replicas is available, write requests requires
the majority of five primary and secondary replica nodes to be available, which means one of the primary replicas
must be available for the write request.
During a segment write, sender finds out the first available node in three of primary replicas, say node A, 
and let this node handle the rest of deduplication and replication process. Node A will first deduplicate
the new segment as described in previous sections, then it tries to acknowledge other two primary replicas
about this update. If succeed, then this segment is successfully written. Otherwise it will
try to write this update to secondary replicas in order to make sure the new data is written to three places.
Upon a successful writting to both primary and secondary replicas with three copies, node A can tell the sender
the new segment is added to storage. But if the sender can not find a available primary replica node, or node A
can not write to the other two replicas, then the write request will fail.

When secondary replicas receive a segment write request, it will only cache the data because they do not have
that container. They will try to send cached requests to primary replicas when possible.
However, if two secdonary replicas want to acknowledge a recently recovered primary replica about the lastest updates,
the recovered node will receive duplicate requests.
Furthermore, it is possible that multiple senders want to write identical segment simultaneously, so it is necessary to use an ID
to distinguish every unique segment writting process.
In Sloud this segment process ID (SPID) is composed of sender's node ID and an incremental logical clock. The SPID is used through out that segment's
deduplication process and carried by all related messages.
In order to avoid processing the same request twice, for every segment Sloud keeps
its recent SPIDs in the segment index for a short period, therefore if the SPID of incoming segment writting request is found in segment index, 
receiver could know it has already received and deduplicated this segment.

Periodically, Sloud synchronize each container among its replicas. Synchronization requires
all primary and secondary replicas to be available. During this process, 
primary replicas compare each others' recent SPIDs along with secondary replica's cache to determine which write request it has missed. 
Upon a successful synchronization, all cached segment updates are ensured
to be delivered to three primary replicas, thus the secondary replicas' cachecan be cleaned up. In addition,
recent SPIDs in segment index is also stale, they will be cleaned up so that Sloud do not need to keep too many recent SPIDs
in segment index. If any node is not available during the synchronization, this process will fail. However, the primary replicas
still try to synchronize as much data as possible, except that the cache and SPIDs will not be cleaned up.

### 2011-12-10 vm_snapshot_sim/intro.tex
initial vm snapshot paper

\section{Introduction}

1.how virtual machines work on storage
2.cow and why they are not good
3.introduce dedup

Virtualization is the engine behind many today's cloud computing platforms.
Amazon and many others have provided clusters that host 
hundreds of thousand virtual machines(VM) which are dynamically created
by users. In such a 
each instance of a guest operating system stores a
file called a virtual disk (e.g. .vhd, .vmdk) on the host system

Because those virtual machines are stored in  maVirtualization provide

Backing user data on these virtual disks is quite different from traditional file system backup.

File storage is a critical component in cloud infrastructure, because users and applications expect a  
persistent place to store and share their data. 
But there can be a significant amount of data redundancy in the storage system
 because large number of users employ such systems for backups, 
and file data between different users may overlap especially when user base is huge. 
For example, in a VM-based cloud, users usualy backup their virtual machine images along with application data 
to a cloud file storage periodically. 
Therefore, improving the space efficiency is an 
important factor in designing a file storage service for cloud.

Data deduplication technique can eliminate such redundancy,
today many D2D backup systems\cite{emc_avamar}\cite{datadomain_whitepaper}.
uses vaiable-size chunking algorithm to detect duplicates in file data.
Chunking divides a data stream into variable length chunks, it has been used to conserve bandwidth\cite{lbfs01}, 
search and index documents in large repositories\cite{bhag07}, scalable storage systems\cite{hydrastor09}, 
store and transfer large directory trees efficiently and with high reliability\cite{jumbo07}.

To chunk a file, starting from the first byte, its contents as seen through a fixed-sized (overlapping) 
sliding window are examined. At every position of the window, a fingerprint or signature of its 
contents, $f$, is computed using hashing techniques such as Rabin fingerprints\cite{rabin81}. 
When the fingerprint meets a certain criteria, such as $f mod D = r$ where $D$, the divisor, 
and $r$ are predefined values; that position of the window defines the boundary of the chunk. 
This process is repeated until the complete file has been broken down into chunks. Next, 
a cryptographic hash or chunk ID of the chunk is computed using techniques such as MD5 or SHA.
After a file is chunked, the index containing the chunk IDs of backed up chunks 
is queried to determine duplicate chunks. New chunks are written to disk and the 
index is updated with their chunk IDs. A file recipe containing all the information 
required to reconstruct the file is generated. The index also contains some metadata 
about each chunk, such as its size and disk location.
How much deduplication is obtained depends on the inherent content overlaps in the data, 
the average size of chunks and the chunking method\cite{poli04}. In general, smaller chunks yield better deduplication.

Inline deduplication is deduplication where the data is deduplicated before 
it is written to disk as opposed to post-process deduplication where backup data 
is first written to a temporary staging area and then deduplicated offline. 
One advantage of inline deduplication is that extra disk space is not required to 
hold and protect data yet to be backed up. 
However, unless some form of locality or similarity is exploited, inline, chunk-based deduplication, 
when done at a large scale faces what has been termed the disk bottleneck problem: to facilitate fast chunk ID lookup, 
a single index containing the chunk IDs of all the backed up chunks must be maintained. 
As the backed up data grows, the index overflows the amount of RAM available and must be paged to disk. 
Without locality, the index cannot be cached effectively, and it is common for nearly 
every index access to require a random disk access. This disk bottleneck severely limits deduplication throughput.

This problem has been addressed by many previous studies. Zhu\cite{bottleneck08} tackle it 
by using an in-memory Bloom Filter and prefetch groups of chunk IDs that are likely to be 
accessed together with high probability. Lillibridge\cite{sparseindex09} break list of chunks 
into large segments, the chunk IDs in each incoming segment are sampled and the segment is 
deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments. 
These are segments that share many chunk IDs with the incoming segment with high probability.
Deepavali\cite{extreme_binning09} uses Broder's theorem\cite{resemblance97} to find similar files and group them
into the same physical location (bins) to deduplicate against each other.

In cloud storage, we are solving data deduplication problem in a different context of 
data stream deduplication (the D2D case). 
We now consider the case for file synchronization service designed to service fine-grained low-locality backup workloads. 
Such a workload consists of newly modified files, instead of large data streams, that arrive in random order from many clients. 
There is generally no locality between files that arrive in a given window of time. 
In the absence of locality, deduplication approach designed for D2D backups perform poorly.

In addition, file storage with deduplication allow a data chunk to be shared by many files,
this has not been a problem in D2D backup systems because they may use costly hardware components
and RAID to reduce the risk of data loss. Unlike D2D backup systems, cloud storage prefers 
low-cost hardware at large scale to achieve both performance and reliability. Without software
replication, data is fragile in the constant presense of disk or system failure.

Our solution, Sloud, is designed for data deduplication in cloud storage systems. 
Sloud exploits file similarity and only in-file data locality.
Like Sparse Indexing, it splits large files into small chunks and coarse-grain segments.
Sloud uses segment as the basic unit for storage allocation, thus avoiding the possibility that a set of 
similar large files may overload part of the system. 
Then a stastic based signature algorithm is used to cluster similar segments into containers
which are located at fixed places by stateless routing. When new segment comes in, 
Sloud finds the container which is most likely to have similar data, then it store new segment
to that container for chunk deduplication. By doing this Sloud trade deduplication space efficiency
for performance and simplicity. In addition, Sloud provides software replication and eventual consistency
to enhance file availability and integrity.
Experiments shows our solution achieves a balance of space efficiency, data reliability and load balancing.

### 2011-12-10 vm_snapshot_sim/main.tex
initial vm snapshot paper

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}
\begin{document}
\title{foo}
\author{bar}
\date{}
\maketitle

\begin{abstract}
Virtualization has became the engine behind many cloud computing platforms.
In a virtualized computing environment, virtual machines
operate on virtual disks, so backing up user data is done by constantly 
taking snapshots of those virtual disks. Because such VM snapshots are huge in
terms of both quantity and individual sizes, snapshot storage would cost tremendous amount 
of space without deduplication.
Current snapshot deduplication is mainly done through copy-on-write 
on fixed-size disk blocks. Such solutions are fast but unable to handle the
 cross VM and inner-block data duplications. In addition, storing VM images and their snapshots
in the same storage engine reduce the underline design flexibility since these two kinds of data
have distinct access requirements.

In this paper, we first perform a large scale study in production VM clusters 
to show that cross VM data duplication is severe due to they have large amount of
common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
to address the above problem efficiently.
We eliminate the majority of cross VM data duplication by pre-select
a small set of frequently seen chunks to dedup against, and we also remove
many inner-block duplication using smaller chunking granuarity and locality.
Experiment shows our design can achieve high deduplication ratio and throughput
without incuring significant overhead to the runtime VM environment.
\end{abstract}

\input{intro}
%\input{background}
\input{approach}
%\input{results}
\input{related}
%\input{conclusion}
\bibliographystyle{abbrv}
\bibliography{dedup}
\end{document}

### 2011-12-10 vm_snapshot_sim/related.tex
initial vm snapshot paper

\section{Related Works}
Several approaches have been previously proposed to enable efficient deduplication in D2D backup.

DDFS\cite{bottleneck08} exploits chunk locality to achieve high-throughput perfect deduplication. 
It preserves locality by a Stream-Informed Segment Layout and exploits locality with Locality Preserved Cache. 
An in-memory Bloom Filter is also used to accelerate non-duplicate chunk identification.

Sparse Indexing\cite{sparseindex09} is an approximate deduplication technique designed for D2D backup. 
It divides data stream into variable-sized multiple kilobytes chunks, and construct multiple megabytes segments
using the same chunking technique, 
which are then sampled and mapped to a compact in-memory sparse index. 
Incoming segments are only deduplicated against several existing similar 
segments selected according to the sparse index.

Both DDFS and Sparse Indexing are designed for D2D backup workloads, 
and do not address the scalability issue in a distributed environment. 
A few scalable deduplication approaches have been proposed recently.

Extreme Binning\cite{extreme_binning09} is a scalable parallel deduplication approach 
that targets at non-traditional backup workloads that consist of low-locality individual files. 
It groups highly similar files into bins, and eliminates duplicate chunks inside each bin. 
Duplicate chunks are allowed to exist among different bins, resulting in approximate deduplication. 
By keeping only the primary index in memory, Extreme Binning can reduce the RAM requirement while 
maintaining a reasonably high throughput. However, their per-file based similarity detection 
is going to group all similar files into one node, which will break load balancing if some files are
huge and similar(e.g., virtual machine images).

MAD2\cite{mad210} is a scalable high-throughput exact duplication approach. 
MAD2 utilizes on-disk Hash Bucket Matrix to preserve fingerprint locality and 
integrates in-memory Dual Cache to capture and exploit locality. 
In addition, MAD2 employs Bloom Filter Array to efficiently identify unique 
incoming fingerprints and indicate where a duplicate may reside. 
By employing a DHT-based Load-Balance technique to distribute file recipes 
and chunk contents among multiple storage nodes in their backup sequences, 
MAD2 further enhances performance with a well balanced load. However, the
data locality does not exist for cloud storage because only changed chunks are expected
to be uploaded, and
the heavy usage of memory and CPU indicates such exact deduplication backup systems
need storage-exclusive servers with hardware replication support, which is not a general case 
for the cloud..

HYDRAstor\cite{hydrastor09}, a scalable secondary storage solution, 
constructs its backend using a grid of storage nodes built around a distributed hash table. 
The backend maintains large-scale variable-sized, content-addressed, immutable, 
and highly-resilient data blocks that are logically organized in a directed acyclic graph. 
Duplicate chunks are eliminated according to their hashes. 
HYDRAstor adopts an average chunk size of 64KB, among other constraints, 
to keep all the metadata in memory and avoid the duplicate-lookup disk bottleneck. 
This degrades the space efficiency of deduplication, and still requires huge amount of memory.

We believe a deduplication backend of cloud storage must have scalability and
 high availability built in mind, being able to run on low-cost non-proprietary machines.
  Unlike sloud, all above systems lack one or a few such properties. All exact deduplication approaches
are too costly, this is why we choose similarity based approach to trade deduplication
accuracy for speed.

Eariler deduplication systems mainly focus on improving storage space efficiency by eliminating 
duplicates at the file level, fixed-size block level, or variable-sized chunk level. 
EMC's Centera\cite{emc_centera} identify and eliminate duplicate data by comparing 
the hash of the whole file or fixed content. Venti\cite{venti02}, a block-level archival storage, 
removes redundant fixed-size data blocks by comparing their secure hashes. Pastiche\cite{pastiche02} 
utilizes chunk-level duplicate detection to construct a resource-saving peer-to-peer backup network. 
Deep Store\cite{deepstore05}, a large scale archival storage system, uses both variable-sized 
chunk-level deduplication and delta compression to save storage. Jumbo Store\cite{jumbo07} organizes 
variable-sized chunks into Hash-Based Directed Acyclic Graphs to save both storage and 
bandwidth while performing incremental upload and versioning for a utility rendering service.

Duplicate detection technique has also been used in bandwidth-saving synchronization protocols\cite{rsync} 
and low-bandwidth network file systems\cite{lbfs01}.

### 2011-12-10 vm_snapshot_sim/zipf.tex
initial vm snapshot paper

\section{Zipf-like Distribution}
%introduce zipf's law
%what we did, our methodology
%result graph
Zipf's law has been shown to characterize use of words in a natural language, city populations, 
popularity of website visits and other internet traffic data.

Here we present the first fully consistent empirical study showing that data duplication
pattern in very large scale storage follows Zipf-like distribution. More specifically,
we show that the duplication count of any unique data block is inversely proportional to its rank
in the frequency table, with $\{alpha}$ smaller than unity. 
As far as we know, this is the first study of large scale real user data to disclose
the Zipf-like distribution pattern in data storage area.

\subsection{The model}
Consider a general storage system that holds user's files without any deduplication. 
Let $N$ be the total number of unique data blocks after 
content-defined chunking and deduplication, 
$C_N(i)$ be the number of duplicate copies that the $i$th data block being
stored in storage, given all the unique data blocks be ranked in order of their number of duplicate copies.
Let $S_i$ be the size of $i$th block,
then the actual ranking of the $i$th block is reflected by $\sum_{1}^{i-1}S_i$.

\subsection{Methodology}
In Aliyun's elastic could service, each VM has several virtual disks: one OS disk and one or more data disks. 
During VM instance creation, the data of OS disk is copied from 
several pre-configured operating system virtual disks depends user's OS choice. 
The data disk is empty at the beginning, user may place their database, website, 
or anything on his data disk, and may attach to more data disks later.

500 users' virtual data disks were scanned using TTTD content-defined chunking, and we performed global perfect deduplication 
to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
and maximum block size, all variable-sized blocks are compared by their SHA-1 hash arther than real data.

We choose user's data disks rather than OS disks for several reasons: First, the data in OS disks are 
instinctively highly similar, because most of the VM users only make some common or tiny changes to their OSes,
so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
Second, the data disks are way more important in terms of data safty and backup because they are 
what users really care about.

\subsection{Result}
\begin{figure}
\centering
\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
\caption{# of duplicate copies vesus block ranking}
\label{figure:zipf}
\end{figure}

### 2012-01-30 vm_snapshot_sim/abstract.tex
First draft

--- 2011-12-10 vm_snapshot_sim/main.tex
@@
-\documentclass[finalversion]{usetex-v1}
-%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
-\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
-\usepackage{epsfig}
-\usepackage{breakurl}
-%% Define a new 'leo' style for the package that will use a smaller font.
-\makeatletter
-\def\url@leostyle{%
-  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
-\makeatother
-%% Now actually use the newly defined style.
-\urlstyle{leo}
-%\linespread{1.2}
-%\setlength{\parskip}{1ex}
-\begin{document}
-\title{foo}
-\author{bar}
-\date{}
-\maketitle
-
 \begin{abstract}
@@
 Current snapshot deduplication is mainly done through copy-on-write 
-on fixed-size disk blocks. Such solutions are fast but unable to handle the
- cross VM and inner-block data duplications. In addition, storing VM images and their snapshots
-in the same storage engine reduce the underline design flexibility since these two kinds of data
-have distinct access requirements.
+on fixed-size disk blocks. Such solutions cannot handle the
+ cross VM data duplication because VMs do not share any data. 
+In addition, storing VM images and their snapshots
+in the same storage engine reduce the underline design flexibility because 
+these two kinds of data have distinct access requirements.
 
@@
 We eliminate the majority of cross VM data duplication by pre-select
-a small set of frequently seen chunks to dedup against, and we also remove
-many inner-block duplication using smaller chunking granuarity and locality.
-Experiment shows our design can achieve high deduplication ratio and throughput
-without incuring significant overhead to the runtime VM environment.
+a small set of frequently seen data blocks to be shared globally, and we also remove
+many cross snapshot duplication by using smaller chunking granuarity and locality.
+Experiment shows our design can achieve high deduplication ratio with very limited 
+amount of resources in large scale VM cloud environment.
 \end{abstract}
-
-\input{intro}
-%\input{background}
-\input{approach}
-%\input{results}
-\input{related}
-%\input{conclusion}
-\bibliographystyle{abbrv}
-\bibliography{dedup}
-\end{document}

### 2012-01-30 vm_snapshot_sim/approach.tex
First draft

@@
-\section{Approach}
-\subsection{Similarity Detection}
-Data locality is important to 
-Bringing deduplication to a distributed environment may
-break data locality because 
-introduces several 
-new problems. Former studies of centralized deduplication systems showed
- that spatial locality of 
-data streams must be preserved. This is because the entire
- chunk hashes are too big to be loaded into memory, 
-thus certain caching mechanism must be applied, and this require 
-proximal chunk IDs to be stored at nearby places. 
-Furthermore, if chunks are not stored on the disk
-base on spatial locality, file read requests will result in entirely
- random disk access, since each data chunk is so small, that would 
-become a disaster for any host file system.
+\section{Our Approach}
+\subsection{Aliyun's VM Cloud}
+Aliyun provides the largest public VM cloud in China which is based on the 
+open-source Xen technology. A typical VM cluster in our cloud environment
+consists of from hundreds to thousands physical machines, each of which can
+host tens of virtual machines. A few varieties of mainstream OS are supported,
+including several editions of Windows Server, major Linux distributions, and FreeBSD.
+During the VM creation, user choose his flavor of OS distribution, our system will
+copy the corresponding pre-configured base VM image to his VM as the OS disk, 
+and an empty data disk is created and mounted onto his VM as well.
 
-\subsubsection{Granuarity}
-Extreme binning uses files as the basic unit for
-similarity detection, this simplifies the metadata management of
-distributed storage because it only need to manage the mapping
- from files to their bins. However, this solution doesn't
-consider the uncertainty of file sizes: it is possible that many similar big files
-can be assigned to one container, thus some storage nodes may be overlaoded when
-others are spare. For example, Amazon's S3 stores huge amount of
-virtual machine images which are very similar, so those files will be assigned
-to only a few nodes by the extreme binning.
-Even those files can be evenly distributed to hundreds of nodes, the overall 
-deduplication ratio won't be good since too much dulicates are tolerated.
+\begin{figure}
+  \centering
+  \epsfig{file=images/tapdisk.eps, height=2in, width=2.66in}
+  \caption{I/O channel between VM and image files}
+  \label{fig:tapdisk}
+\end{figure}
 
-We suggest that data segment at the size of several megabytes is the best unit for
-similarity based deduplication. Sparse Indexing has already 
-proved that content based chunking method can be also applied to break the list of
-chunks into large segments, such that each segment contains a few hundred of small chunks.
-Using such medium size segments as the basic unit for similarity detection could eliminate
-disadvantages mentioned above, and doing so won't add  much computation cost
-to the deduplication process.
+All these virtual disks are represented as virtual machine image files in our
+underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
+disks is tunneled by the TapDisk driver. To avoid network latency and congestion, 
+our distributed file system carefully selects the location of primary replica of VM's 
+image files such that they are located on the same physical machine of VM instance.
 
-\subsubsection{Signature Algorithm}
-In general, we expect to generate a signature for each segments, such that if two segments
-has a lot of chunks in common, there is a high probablity that their signatures are the same.
-Since we represent segment as a list of chunks, the information available for generating 
-signatures are the chunk hash values, chunk sizes, and offsets.
+Inside the TapDisk driver, we maintain an array of \emph{dirty bits} to record the dirty area
+of runtime VM image file since the last snapshot, each bit represent a 2MB fix-sized
+data segment. During a snapshot operation, we only need to look at the dirty region
+rather than scan over the whold image file, which would be extremely slow.
 
-Extreme binning suggests the min-hash signature algorithm. By Broder's theorem, 
-the probability that the smallest elements of two sets are identical, is equal to their Jaccard similarity coefficient.
-Therefore they use the smallest chunk hash value as the signature to represent the whole file.
+The snapshot storage system also resides in our distributed file system, just like the 
+runtime VM storage. But the difference is that snapshot storage do not need to be
+co-located with VM instances, in fact they can even live in a different cluster to improve the 
+data safty. When cluster A is offline, we can quickly restore its VMs from cluster B
+to reduce the impact to our users.
 
-We propose a Size-based Similarity Detection (SSD) method, 
-which is more storage specific because it uses the chunk size information. Intuitively if one segment is
-only slightly modified, then most of the chunks should remain the same, thus their sizes should mostly remain the same.
-Even modifications could change the chunk hash value, due to the modification resistant property of 
-content based chunking algorithm, most of the time that chunk size is unchanged. Therefore if we want to 
-generate a $n$ bit signature for a segment, we simply split the range of size evenly at logarithmic scale by $n$ , and count how many chunks
-fall into each range. Then if that number is above average, we set the bit for that range as 1, otherwise 0, as shown
-in figure.
+The detail design and implementation of our distributed file system and various 
+storage subsystems would be too complicated to be intorduced here, and also beyond
+the scope of this paper. In the remaining section we will brief the model and interface of 
+our snapshot storage.
 
-By using the signature of segment to represent all of its chunks, Sloud clusters
-segments that are highly similar into one container. Each container is the collection of 
-segments that have the same signature. When a new segment arrives, it will be assigned by its signature to
-the corresponding container which has chunks that are highly similar to it. Thus,  highly accurate deduplcation is achieved.
-However, since every segment is only assigned to one container, if any of the its chunks do not 
-exist in that container but exist elsewhere, they will be treated as new chunks, in other words, 
-duplicates are allowed. Sloud trade such storage space efficiency for faster deduplication and  
-fewer resources consumption such as RAM usage and disk access. In addition, we believe this is the best way to 
-build distributed deduplication solution without losing data locality.
+\subsection{Snapshot Representation}
+Each snapshot is a two-level index data structure in the form of HDAG. 
+At the bottom level is variable-sized data blocks, like many other deduplication storage systems, 
+we use 4KB as the average block size.
+In the middle is the segment layer, a segment contains hundreds of blocks, it records the list
+of block hash, data reference and some other meta information in a data structure we called
+segment recipe. Then the segment recipe itself, can be serialized into a data block, so the hash
+of segment recipes and their meta data formed the snapshot recipe. We take this two-level
+structure because in practice we observed that at each snapshot only a small fraction
+of dirty bits array are marked as set, so snapshot recipes can share the unmodified
+segment recipes to reduce the space cost of snapshot meta data.
 
-\subsection{Architecture}
-We designed a distributed storage system, Sloud, to demonstrate the possibility of
-providing scalibility to large scale deduplication systems. Sloud cluster similar segment into containers and store
-those containers to the disk. The overall architecture is shown in .
-Sloud uses a DHT service for node discovery and storage space partitioning, all nodes in Sloud are completely equal, 
-there's no node that has special responsibilities.
+Instead of using variables-sized segment like many others did, we take the simpler approach
+to let every segment being aligned to the boundary of dirty bits array. This is because
+\emph{vhd} file format will keep the allocated inner blocks at the same positions until deletion,
+which means the locality of snapshot data is almost natively aligned. Enforcing a boundary at every 2MB will
+only break 0.2\% of total data blocks which is tiny.
 
-At every storage node , we keep in memory a bloom filter and a segment index for every container, 
-the rest of part of the container, including the chunk data and chunk index, are stored onto disk. When a new segment comes in, the segment index is used
-for the first pass of deduplication, such that duplicate segments can be detected without looking below. The second pass is done by bloom filter,
-most of new chunks are immediately identified. Otherwise, Sloud look into the chunk index for the final pass of deduplication, as shown in Figure.
+\subsection{Snapshot Storage}
+The snapshot storage system sits on top of our distributed file system, 
+it can be abstracted as a block store which operates a few \emph{append-only} files
+in the underline file storage. Each virtual disk has its own data store, all data 
+blocks after deduplication will be stored into that system.
 
-Assuming all node are reliable, no failure ever happens, and there is no replication involved, 
-the deduplication process can be described as following:
-\begin{enumerate}
-\item Firstly,  sender scan the files that to need be deduplicated, generate all information about chunks and segments.
-\item For each segment, sender queries the DHT service to find out the node that is responsible to segment's container, then it will send a segment writting message with segment's signature and hash.
-\item The receiver then lookup corresponding container's segment index to see if its a duplicate.
-If it is, there is no need for further deduplication, it will update the segment's reference count and acknowledge the sender deduplication is complete.
-\item If the segment hash does not exist in segment index, receiver asks sender for the segment recipe, which is all the chunks' information except the actual data.
-\item On receiving the segment recipe, receiver starts deduplicate them against existing chunks in that container.
-Firstly it goes to the bloom filter, most of the new chunks are identified in this step.
-For those chunks that are identified as 'exist' by the bloom filter, the receiver looks into chunk index to see if they are really there or not.
-At any step, if a chunk is identified as new, a request of chunk data is immdeiately sent out.
-\item Incoming chunk data are written to a temporary disk place until all new chunks belonging to that segment are received. Upon this time, receiver merges new data into that container's disk file.
-\item Finally the receiver update the segment index and chunk index, and acknowledge the sender this segment is sucessfully received and deduplicated.
-\end{enumerate}
+\begin{figure}
+  \centering
+  \epsfig{file=images/storage_overview.eps, height=2in, width=2.66in}
+  \caption{Storage architecture}
+  \label{fig:arch}
+\end{figure}
 
-\subsection{Replication and Concistency}
-Sloud uses consistent hashing ring\cite{consistent_hash97} to maintain a dynamic hash table for node discovery. 
-Each node is given an unique ID and the Sha-1 checksum of their IDs are mapped onto this ring. 
-Containers are also mapped onto the consistent hash ring by the Sha-1 checksum of their represented signatures.
-The benefit of using consistent hash is that adding or removing nodes from the system won't introduce too much
-workload of reorganization. For each container on the ring, Sloud treat the first three consequential nodes as 
-the primary replicas of that container, and the next two nodes as the secondary replicas. Primary replicas hold
-the real copy of container's data, the secondary replicas are only used to cache write requests when some of the 
-primary replicas are temporarily unavailable.
+We let each virtual disk has its own block store rather than sharing for several reasons:
+first, all data written to block store are already being processed by deduplication
+process, thus no sharing is necessary unless we want to perform additional deduplication
+inside the block store. Second, such seperation will facilitate VM data stastics, 
+deletion and migration. Finally, this reduces the complexity of concurrent snapshot operations.
 
-Sloud provides a variation of eventual consistency\cite{eventually09} in its data replication. Read
-requests will succeed if at least one of the three primary replicas is available, write requests requires
-the majority of five primary and secondary replica nodes to be available, which means one of the primary replicas
-must be available for the write request.
-During a segment write, sender finds out the first available node in three of primary replicas, say node A, 
-and let this node handle the rest of deduplication and replication process. Node A will first deduplicate
-the new segment as described in previous sections, then it tries to acknowledge other two primary replicas
-about this update. If succeed, then this segment is successfully written. Otherwise it will
-try to write this update to secondary replicas in order to make sure the new data is written to three places.
-Upon a successful writting to both primary and secondary replicas with three copies, node A can tell the sender
-the new segment is added to storage. But if the sender can not find a available primary replica node, or node A
-can not write to the other two replicas, then the write request will fail.
+The main interface of our snapshot storage is \emph{get}, \emph{put} and \emph{delete}.
+Get interface accepts a piece of data, write it to the underline data file, and return
+a reference to the caller. This reference then can be used in the put interface to
+retrive or delete the data, thus the caller of put interface must preserve the
+data reference for future use. Since all the underline data structures is append only,
+upon a delete request, the corresponding data will only be marked rather than being deleted.
+A compaction will take place when deleted data has accumulated to certain threshold, thus 
+reclaiming the disk space .
 
-When secondary replicas receive a segment write request, it will only cache the data because they do not have
-that container. They will try to send cached requests to primary replicas when possible.
-However, if two secdonary replicas want to acknowledge a recently recovered primary replica about the lastest updates,
-the recovered node will receive duplicate requests.
-Furthermore, it is possible that multiple senders want to write identical segment simultaneously, so it is necessary to use an ID
-to distinguish every unique segment writting process.
-In Sloud this segment process ID (SPID) is composed of sender's node ID and an incremental logical clock. The SPID is used through out that segment's
-deduplication process and carried by all related messages.
-In order to avoid processing the same request twice, for every segment Sloud keeps
-its recent SPIDs in the segment index for a short period, therefore if the SPID of incoming segment writting request is found in segment index, 
-receiver could know it has already received and deduplicated this segment.
+In addition to above data access interfaces, the snapshot storage also supports
+\emph{scan} and \emph{quota} methods. Scan allows us to traverse all the data blocks
+that store in the data store, and quota is used to acknowledge user how much space he
+has actually used.
 
-Periodically, Sloud synchronize each container among its replicas. Synchronization requires
-all primary and secondary replicas to be available. During this process, 
-primary replicas compare each others' recent SPIDs along with secondary replica's cache to determine which write request it has missed. 
-Upon a successful synchronization, all cached segment updates are ensured
-to be delivered to three primary replicas, thus the secondary replicas' cachecan be cleaned up. In addition,
-recent SPIDs in segment index is also stale, they will be cleaned up so that Sloud do not need to keep too many recent SPIDs
-in segment index. If any node is not available during the synchronization, this process will fail. However, the primary replicas
-still try to synchronize as much data as possible, except that the cache and SPIDs will not be cleaned up.
+\subsection{CDS Operations}
+The CDS is divided into CDS meta and CDS data. THe structure of CDS meta is not different from the
+segment recipe we discussed above, except that it is partitioned into many small slices so that each node
+is easy to load its own slice. At the runtime, our CDS meta resides in a global shared memory cache for 
+deduplication lookups. The data of CDS is stored in a special block store, which doesn't belong to any VM disk.
+
+CDS meta assignment is done statically, each slice of CDS meta has one primary and two backup nodes.
+During the system bootup, snapshot storage controller will read the assignment, 
+load its primary portion of CDS meta from distributed file system. Loading the backup portion
+of CDS is due upon a query arrives for it. Everyday the CDS assignment and CDS data will be checked
+ for updates and reloaded if necessary.
+
+Behind the scene there is a offline map-reduce job, which will periodically scan the block stores
+in the entire cluster and perform a ``word counting''. High frequency blocks are then added to the CDS if its count 
+ is greater than threshold, which is pre-defined by the system memory restrictions.
+
+\subsection{Dedup Process}
+Our deduplication process can be summarized as four steps:
+\begin{list}{Dedup}{}
+\item {Dirty bits: Copy the unchanged portion of snapshot recipe from parent snapshot, base on dirty bits.}
+\item {Locality: Divide dirty segments into blocks, compare to the corresponding segment recipe at the same position of parent snapshot, if duplicate, copy the data reference into segment recipe.}
+\item {CDS: Check if this data exist in the CDS, if yes, copy the returned data reference. Otherwise, write data block to block store, save the returned reference into segment recipe.}
+\item {Save meta: write down the segment recipes and snapshot recipe when finish.}
+\end{list}

### 2012-01-30 vm_snapshot_sim/cds.tex
First draft

\section{Zipf-like Distribution and Common Data Set}
%OS data
%user data: zipf
%prediction
%say something about aliyun
In Aliyun's VM cloud, each VM has one OS disk, plus one or more data disks.
During VM's ceation, its OS disk is directly copied from user's choosen base image.
Through its lifetime user may change configurations, install software, or write user data into OS disk,
but most of the OS and software related data shall keep unchanged. 
Previous study has also supported this\cite{vmimage}. Therefore, we can let all OS disks share these
common data in their snapshot backups.

Furthermore, our study on user's data disks has shown that the duplication pattern of
variable-sized data blocks follows \emph{Zipf-like} distribution. As a result, the major portion of 
deduplication effect will emerge from eliminating the duplication of frequently seen data.
%define CDS
\subsection{OS CDS}
We define \emph{OS CDS} to be the unchanged data across the base VM image and the snapshots of all
OS disks which are derived from it. Such data are brought by the operating system and popular 
software installations, they are rarely modified or deleted, and can be easily extracted using 
base image data as a hint.

To see the data duplication of OS CDS, we choose 7 major OSes in our VM cloud platform, which are:
Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
distributions are 64 bits).
Then we pick 5 VMs for each OS, and 10 snapshots for each VM. These VMs have been actively used by their
owners, their OS disks are heavily modified, some users even store huge amount of user data on
their OS disks. For example, some Ubuntu OS disks have only 2GB of data while some have 50GB.

We take the following steps to evaluate the effect of OS CDS: for each OS, the base image and all OS
disk snapshots are splitted into variable-sized blocks using TTTD algorithm. Then for every data block
in base image, we check if this block appear in all 50 snapshots.

%table

The above analysis is only an estimation of OS and software related common data, 
some user installed software may not be discovered by this method because they are not included in the
base image. However, as we can see in the next section, the overall duplication of user generated data
follows the Zipf-like distribution, thus all popular data can be discovered by statistical analysis.

\subsection{Zipf-like Distribution and Data CDS}
Zipf's law has been shown to characterize use of words in a natural language, city populations, 
popularity of website visits and other internet traffic data.

Here we present the first fully consistent empirical study showing that data duplication
pattern in very large scale storage follows Zipf-like distribution. More specifically,
we show that the duplication count of any unique data block is inversely proportional to its rank
in the frequency table, with $\alpha$ smaller than unity. 
As far as we know, this is the first study of large scale real user data to disclose
the Zipf-like distribution pattern in data storage area.

\subsubsection{The model}
Consider a general storage system that holds user's files without any deduplication. 
Let $N$ be the total number of unique data blocks after 
content-defined chunking and deduplication, 
$C_N(i)$ be the number of duplicate copies that the $i$th data block being
stored in storage, given all the unique data blocks be ranked in order of their number of duplicate copies.
Let $S_i$ be the size of $i$th block,
then the actual ranking of the $i$th block is reflected by $\sum_{1}^{i-1}S_i$.

\subsubsection{Methodology}
1323 users' virtual data disks were scanned using TTTD content-defined chunking, and we performed global perfect deduplication 
to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
and maximum block size, all variable-sized blocks are compared by their SHA-1 hash arther than real data.

We choose user's data disks rather than OS disks in thie experiment for several reasons: First, the data in OS disks are 
instinctively highly similar, because most of the VM users only make some common or unique but tiny changes to their OSes,
so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
Second, the data disks are way more important in terms of data safty and backup because they are 
what users really care about.

\subsubsection{Result}
\begin{figure}
\centering
\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
\caption{Number of duplicate copies vesus block ranking}
\label{fig:zipf}
\end{figure}

Figure \ref{fig:zipf} shows the block duplication count vesus its ranking by that count. The almost straight line proves 
the block duplication in user generated data follows Zipf-like distribution, with $\alpha$ close to 0.78.
A tiny hottest fraction of data lead to majority of data duplication, as a result, we can target at this small set of commonly seen data
to design our fast and lightweight deduplication process, just like what people did in CDN and web proxy.

\subsection{Discussion}
By storing the hash index of a small set of hottest data (CDS), we expect to acheive great deduplication effect with minimal cost.
But one problem of the CDS is what we called \emph{blind spot}: the update of CDS is always behind new data's arrival,
as a result, some data must have been written to the backup store before being collected into CDS, thus such duplication may comprise the effect of
CDS. For instance, when a MySQL update is released, some users may apply it very quickly, so the new hot data bring by
this update will not be filtered by CDS. Only until later our CDS update includes those new data, then the rest of MySQL users get benefited.
We can take a few measurements to reduce the impact of blind spot. First, the data in blind spot will not accumulate, because snapshots backup
is a paid service, so over the long term, data in blind spot will be removed from backup store as VMs and old snapshots keep being deleted.
Second, for the major OS updates, we can anticipate them in advance by putting the new hot data into CDS before users widely adopt them.

Another problem associated with CDS is that some data in CDS may no longer be popular or even disappear
as time goes. For example, an MySQL software update may invalidate some data that we previously hold in 
the CDS. If some data blocks in CDS are no longer referenced, our map-reduce process is able to detect
this situation, so invalid data will be removed and new data will be added during the next CDS update. 
But if some users choose to keep their old MySQL version, then the corresponding old and new data will co-exist in the CDS.

### 2012-01-30 vm_snapshot_sim/conclusion.tex
First draft

\section{Conclusion}
In this paper we present a new parallel deduplication technique for VM cloud.
Our technique utilizes the special data characteristic in VM cloud backup system
to accommodate very limited resources for data deduplication.
By storing the commonly used OS related data, and the hottest user generated data, 
we greatly reduce the cross-VM data duplication in VM snapshot backups. Experiments show
our solution can eliminate the majority of data duplication with a tiny fraction of
block hash index store in memory. It does not only saves valuable system resouces in
the VM cloud, but also makes deduplication much faster.

### 2012-01-30 vm_snapshot_sim/intro.tex
First draft

@@
 
-1.how virtual machines work on storage
-2.cow and why they are not good
-3.introduce dedup
+%1.how virtual machines work on storage
+%2.cow and why they are not good
+%3.introduce dedup
 
-Virtualization is the engine behind many today's cloud computing platforms.
-Amazon and many others have provided clusters that host 
+Virtualization is the engine behind many popular cloud computing platforms.
+Amazon, Aliyun and many others have provided public VM clouds that host 
 hundreds of thousand virtual machines(VM) which are dynamically created
-by users. In such a 
-each instance of a guest operating system stores a
-file called a virtual disk (e.g. .vhd, .vmdk) on the host system
+by users. In such a virtualized environment,
+each instance of guest operating system operates
+on virutal disks, which are represented as
+files called virtual disk image (e.g. .vhd, .vmdk) in the host operating system.
+Because those virtual disk images are stored as files in the external storage,
+backing up VM data in virtual disks is mainly done by taking snapshots
+of virtual disk images,
+which is quite different from traditional file system backup.
 
-Because those virtual machines are stored in  maVirtualization provide
-
-Backing user data on these virtual disks is quite different from traditional file system backup.
-
-File storage is a critical component in cloud infrastructure, because users and applications expect a  
-persistent place to store and share their data. 
-But there can be a significant amount of data redundancy in the storage system
- because large number of users employ such systems for backups, 
-and file data between different users may overlap especially when user base is huge. 
-For example, in a VM-based cloud, users usualy backup their virtual machine images along with application data 
-to a cloud file storage periodically. 
-Therefore, improving the space efficiency is an 
-important factor in designing a file storage service for cloud.
+The most widely used snapshot method is copy-on-write (CoW). Upon VM image storage system receives a save snapshot request,
+it freezes the state of that image file, then all consequent write request will result in the write region being copied
+to a incremental snapshot data file. CoW method can finish a snapshot operation instantly, but it has several disadvantages:
+first, CoW may affect the general I/O performance due to defered data coping. 
+Second, CoW does not seperate backup data and runtime image data,
+which have distinct access requirements: runtime image data is directly used by the running VM, 
+thus need high throughput, and is very sensitive to latency,
+such data must be served with hig cost hardware, but backup data generally only need fair aggregate throughput, 
+is not sensitive to latency, thus can be stored in secondary storage devices.
+Finally and most important, VM snapshots contain tremendous amount of data duplication, which is nearly impossible to tackle 
+if these two kinds of data are tightly coupled together.
 
@@
 In cloud storage, we are solving data deduplication problem in a different context of 
-data stream deduplication (the D2D case). 
-We now consider the case for file synchronization service designed to service fine-grained low-locality backup workloads. 
-Such a workload consists of newly modified files, instead of large data streams, that arrive in random order from many clients. 
-There is generally no locality between files that arrive in a given window of time. 
-In the absence of locality, deduplication approach designed for D2D backups perform poorly.
-
-In addition, file storage with deduplication allow a data chunk to be shared by many files,
-this has not been a problem in D2D backup systems because they may use costly hardware components
-and RAID to reduce the risk of data loss. Unlike D2D backup systems, cloud storage prefers 
-low-cost hardware at large scale to achieve both performance and reliability. Without software
-replication, data is fragile in the constant presense of disk or system failure.
-
-Our solution, Sloud, is designed for data deduplication in cloud storage systems. 
-Sloud exploits file similarity and only in-file data locality.
-Like Sparse Indexing, it splits large files into small chunks and coarse-grain segments.
-Sloud uses segment as the basic unit for storage allocation, thus avoiding the possibility that a set of 
-similar large files may overload part of the system. 
-Then a stastic based signature algorithm is used to cluster similar segments into containers
-which are located at fixed places by stateless routing. When new segment comes in, 
-Sloud finds the container which is most likely to have similar data, then it store new segment
-to that container for chunk deduplication. By doing this Sloud trade deduplication space efficiency
-for performance and simplicity. In addition, Sloud provides software replication and eventual consistency
-to enhance file availability and integrity.
-Experiments shows our solution achieves a balance of space efficiency, data reliability and load balancing.
+data stream deduplication (the D2D case). Because our snapshot storage servive is co-located with runtim VMs,
+we have very limited amount of system resource to perform deduplication. For example,
+on our typical 8-core, 48GB memory, 12TB disk server, there lives over 20 VMs who are hungrily eating
+system resources: some are running map-reduce jobs, some are busy web servers, some are backend databases.
+Any behavior that affects user VMs performance or stability is unacceptable.

### 2012-01-30 vm_snapshot_sim/main.tex
First draft

@@
 \usepackage{epsfig}
-\usepackage{breakurl}
+%\usepackage{breakurl}
 %% Define a new 'leo' style for the package that will use a smaller font.
@@
 \begin{document}
-\title{foo}
-\author{bar}
+\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
+\author{Wei Zhang, Hong Tang, Hao Jiang, Rachael Zeng, Xiaogang Li, Tao Yang}
 \date{}
@@
 
-\begin{abstract}
-Virtualization has became the engine behind many cloud computing platforms.
-In a virtualized computing environment, virtual machines
-operate on virtual disks, so backing up user data is done by constantly 
-taking snapshots of those virtual disks. Because such VM snapshots are huge in
-terms of both quantity and individual sizes, snapshot storage would cost tremendous amount 
-of space without deduplication.
-Current snapshot deduplication is mainly done through copy-on-write 
-on fixed-size disk blocks. Such solutions are fast but unable to handle the
- cross VM and inner-block data duplications. In addition, storing VM images and their snapshots
-in the same storage engine reduce the underline design flexibility since these two kinds of data
-have distinct access requirements.
-
-In this paper, we first perform a large scale study in production VM clusters 
-to show that cross VM data duplication is severe due to they have large amount of
-common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
-Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
-to address the above problem efficiently.
-We eliminate the majority of cross VM data duplication by pre-select
-a small set of frequently seen chunks to dedup against, and we also remove
-many inner-block duplication using smaller chunking granuarity and locality.
-Experiment shows our design can achieve high deduplication ratio and throughput
-without incuring significant overhead to the runtime VM environment.
-\end{abstract}
-
-\input{intro}
-%\input{background}
-\input{approach}
-%\input{results}
-\input{related}
-%\input{conclusion}
+\input{abstract}
+\input{intro} %introduce the problem, related solutions and our requirements
+\input{cds} %data study, zipf, model of cds size and dedup efficiency
+\input{approach} %our dedup process
+\input{results}
+%\input{related}
+%\input{future}
+\input{conclusion}
 \bibliographystyle{abbrv}

### 2012-01-30 vm_snapshot_sim/results.tex
First draft

\section{Results}
In our snapshot deduplication architecture, CDS is the key to achieve greater deduplication than
incremental backup solutions. Our basic assumption of CDS us that VM disks, especially OS disks,
have huge amount of data in common, and such common data can be represented by a relatively smaller data set
because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
emerge from eliminating the duplication of such a small data set. In this section, we evaluate
the effectiveness of CDS using real user VM disks from our production VM cluster.

\subsection{Experiment Setup}
The data set we use is the same as described in previous section. 
We choose extreme binning and perfect deduplication to compare against.
In all experiments, our deduplication enforces 2MB fix-sized segment boundary, 
and uses TTTD algorithm to divide segment into 4KB variable-sized blocks.
For perfect deduplication and extreme binning, the whole snapshots are splitted
using TTTD with 4KB average size. The original extreme binning paper uses whole file
as the input unit, but that is way too big for our system. 
Thus we split image snapshot files into variable-sized segments base on the block hash list, 
using TTTD with average size of 2MB.

\subsection{OS Disk}
We extract the CDS of OS disks by counting the blocks that will appear in a VM's
block store if no CDS is involved in the deduplication process. The threshold is set to less than
1.5\%, which is quite sufficient to include the OS related data since their duplication is much
heavier than others. Then we use this CDS to run the deduplication process again.
Finally we extracted about 80GB of CDS data from 350 OS disk snapshots,
the corresponding CDS meta occupies 800MB in CDS cache.

\begin{figure}
  \centering
  \epsfig{file=images/os_cds_sim.eps, height=2in, width=2.66in}
  \caption{CDS deduplication effect on OS disks}
  \label{fig:oscds}
\end{figure}

For each block, we tag it with one of the following:
\begin{itemize}
\item {New: this block cannot be deduplicated and thus write to block store.}
\item {CDS: this block is deduplicated by CDS.}
\item {Parent: this block is not found in CDS, but is found in parent snapshot's segment recipe.}
\item {Both: this block is both found in CDS and parent snapshot.}
\end{itemize}
As we can see from \ref{fig:oscds}, locality dominates.
This is because the interval between two snapshots is quite short due to our daily snapshot strategy. 
However, locality still doesn't work well on some of the OSes. But CDS, on the contrary,
finds a lot of duplicates that locality can't find, especially in a VM's first snapshot.

Combining all the VMs, we see the overall 7.4TB of data is reduced to 512GB. Extreme bining 
reduces this data set to 542GB, which is slightly worse. As a reference, perfect deduplication achieves
364GB in this experiment.

Overall, none of locality or CDS can solely work well, but by combining them together 
we get fairly good and stable deduplication ratio to all kind of OSes. If compare to all
incremental backup solutions, CDS can save addition 50\%+ of disk space because it greatly reduces
the cross-VM duplicates.

\subsection{Data Disk}
Figure \ref{fig:pd} shows the compression ratio of perfect deduplication at different data scales. 
Basically perfect deduplication would help us save 50\% of space on user data, 
regardless of scale. If we put all these unique data into CDS, we could achieve perfect deduplication, 
which is not affordable. So we need to see how much space saving of perfect 
deduplication can be achieved through a limit size CDS.
\begin{figure}
  \centering
  \epsfig{file=images/dedup_ratio.eps, height=2in, width=2.66in}
  \caption{Perfect deduplication on data disks}
  \label{fig:pd}
\end{figure}

We rank unique data blocks by their duplication count, 
and choose the hottest blocks as CDS. 
We define \emph{space saving ratio} as the space saving of CDS divide by 
perfect deduplication saving. Figure \ref{fig:datacdssize} shows the relationship between CDS size and space saving. 
It’s clear a very small amount of CDS data provides more than 50\% saving. 
But this effect decreases when more data are added to CDS. 
The lower bound of CDS space saving ratio is 50\%, which is very easy to accomplish.

\begin{figure}
  \centering
  \epsfig{file=images/uniquedata-saving.eps, height=2in, width=2.66in}
  \caption{Size of CDS vesus space saving}
  \label{fig:datacdssize}
\end{figure}

The upper bound of CDS size is restricted by system memory resource.
Figure \ref{fig:datacds} shows how CDS space saving is affected by the system scale. 
In this experiment we first set out a goal of space saving ratio, 
then we watch how much data we need to put into CDS to achieve this goal.
From the graph we can see a 75\% saving goal lead to a stable ratio between 
CDS size and data size, which requires 0.01\% of data to be put in CDS.

Base on above data we can estimate the size of data CDS and its effect. 
Currently we prepared 500MB memory per machine to store CDS meta, then it can represent 50GB of data. 
If we assume each VM has 30GB of user data at runtime, and we host 25 VMs per machine, 
 maintain 10 snapshots per VM, each brings 10\% additional modified data. 
Thus the user data in snapshot system is 1.5TB per machine. So the upper bound of 
$CDS size/ Data size = 0.033$, which is sufficient for the 75\% saving goal.

\begin{figure}
  \centering
  \epsfig{file=images/cds_scale.0.7.eps, height=2in, width=2.66in}
  \caption{CDS deduplication effect on data disks}
  \label{fig:datacds}
\end{figure}

Unlike the CDS of OS disks which is mainly composed of OS related data thus highly predictable, 
data disks is unpredictable because we cannot control what user can put in there. But we still
suspect that highly duplicated data in existing data are very likely to be duplicated again.
So we randomly pick 50 out of 1322 data disks as the new data, and use the rest as existing data
to extract CDS. Using 1.5\% as CDS threshold, we see the total 1198GB of new data is reduced by 
755.8GB, while perfect deduplication can reduce 1017.4GB. So 74.3\% of duplicate blocks are eliminated 
by pre-trained CDS, which is quite satisfiable.

### 2012-02-29 vm_snapshot_sim/abstract.tex
Update abstract to a grammar corrected version.

@@
 \begin{abstract}
-Virtualization has became the engine behind many cloud computing platforms.
-In a virtualized computing environment, virtual machines
-operate on virtual disks, so backing up user data is done by constantly 
-taking snapshots of those virtual disks. Because such VM snapshots are huge in
-terms of both quantity and individual sizes, snapshot storage would cost tremendous amount 
-of space without deduplication.
-Current snapshot deduplication is mainly done through copy-on-write 
-on fixed-size disk blocks. Such solutions cannot handle the
- cross VM data duplication because VMs do not share any data. 
-In addition, storing VM images and their snapshots
-in the same storage engine reduce the underline design flexibility because 
-these two kinds of data have distinct access requirements.
-
-In this paper, we first perform a large scale study in production VM clusters 
-to show that cross VM data duplication is severe due to they have large amount of
-common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
-Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
-to address the above problem efficiently.
-We eliminate the majority of cross VM data duplication by pre-select
-a small set of frequently seen data blocks to be shared globally, and we also remove
-many cross snapshot duplication by using smaller chunking granuarity and locality.
-Experiment shows our design can achieve high deduplication ratio with very limited 
-amount of resources in large scale VM cloud environment.
+In a virtualized cloud computing environment,
+frequent snapshot backups of virtual disks improve hosting reliability,
+while storage demand of such operations is huge.
+While a dirtybit-based technique can identify unmodified data
+between versions, full deduplication with fingerprint comparison
+can remove more redundant content but it requires more computing resources.
+In this paper, we present a multi-level selective deduplication scheme which integrates inner-VM
+and cross-VM duplicate elimination with minimal resource impact
+to the existing cloud services. This scheme uses popular common
+data to facilitate fingerprint comparison while reducing the cost,
+and it strikes a balance between local and global deduplication to increase parallelism and improve
+reliability. Experimental results show the proposed scheme can achieve a high deduplication
+ratio while using a small amount of cloud resources.
 \end{abstract}

### 2012-02-29 vm_snapshot_sim/2012abs.tex
Tao

\begin{abstract}
%Virtualization has became the engine behind many cloud computing platforms.
In a virtualized cloud computing environment, frequent  snapshot backup of virtual disks improves
hosting  reliability while  storage demand of such operations is huge.
A dirtybit-based technique can identify unmodified data between versions 
and full deduplication with fingerprint comparison  can remove more redundant content
while it requires more computing resource.
%with  for similarity comparison and   reliability handling.
%Current snapshot deduplication is mainly done through copy-on-write 
%on fixed-size disk blocks. Such solutions cannot handle the
% cross VM data duplication because VMs do not share any data. 
%In addition, storing VM images and their snapshots
%in the same storage engine reduce the underline design flexibility because 
%these two kinds of data have distinct access requirements.
In this paper, 
%we show that there is a large amount of duplicated data shared amongy virtual machines
%through a production VM data study and thus it is expective to perform cross-machine deduplication. 
This paper presents a multi-level selective deduplication  scheme which
integrates  inner-VM and cross-VM duplicate elimination with minimal  resource impact
to the existing cloud services.  This scheme uses popular common data to facilitate 
fingerprint comparison while reducing the cost and it
strikes a balance  between local and global deduplication 
to  increase parallelism and  improve reliability. 
% first perform a large scale study in production VM clusters 
%to show that cross VM data duplication is severe due to they have large amount of
%common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
%Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
%to address the above problem efficiently.
%We eliminate the majority of cross VM data duplication by pre-select
%a small set of frequently seen data blocks to be shared globally, and we also remove
%many cross snapshot duplication by using smaller chunking granuarity and locality.
Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
a  small  amount of cloud resources. 
\end{abstract}

### 2012-02-29 vm_snapshot_sim/2012arch.tex
Tao

\section{Multi-level Selective Deduplication}
\label{sect:arch}

\subsection{Snapshot Service Architecture}
%\subsection{Aliyun's VM Cloud and 
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China 
based on Xen~\cite{Xen2003}. A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of VMs. A few varieties of mainstream OS are supported,
including several editions of Windows Server, major Linux distributions, and FreeBSD.
During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
copies the corresponding pre-configured base VM image to her VM as the OS disk, 
and an empty data disk is created and mounted onto her VM as well. 
All these virtual disks are represented as virtual machine image files in our
underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
disks is tunneled by the virtual device driver (called TapDisk at Xen). To avoid network latency and congestion, 
Aliyun's distributed file system carefully selects the location of primary replica of VM's 
image files such that they are located on the same physical machine of VM instance.

Figure~\ref{fig:arch} shows the architecture view of snapshot service with selective deduplication
at each node. The  snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
In accomplishing such a function, this broker accesses  the snapshot store managed by the underlying distributed file
system.  The inner VM  deduplication is conducted by the broker to access meta data in the snapshot data store
and we discuss this in details in Section~\ref{sect:innerVM}.
The inter-VM deduplication is conducted by the broker to access a  common data block set (CDS) across multiple VMs.
The CDS hash index is stored in the distributed memory cache.

\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
  \epsfig{file=images/arch.eps, width=3.5in}
  \caption{Snapshot backup architecture of each node.}
  \label{fig:arch}
\end{figure}

The snapshot store  residing in the distributed file system
supports data access operations  such as \emph{get}, \emph{put} and \emph{delete}.
Other operations include data block traverse  and resource usage  report.
Snapshots are stored  in our distributed file system, just like regular virtual data files. 
A key  difference is that snapshot storage does not need to be
co-located within VM instances and  in fact they can even live in a different cluster to improve the 
data reliability. When a computing cluster is not available, we are still able to  restore users' VMs from another cluster which
contains snapshot backup and run these VMs. 
%to reduce the impact to our users.
%Get interface accepts a piece of data, write it to the underline data file, and return
%a reference to the caller. This reference then can be used in the put interface to
%retrive or delete the data, thus the caller of put interface must preserve the
%data reference for future use. 
%In addition to above standand data access operations, the snapshot service also supports
%\emph{scan} and \emph{quota} methods. Scan allows us to traverse all the data blocks of each VM
%in the snapshot store, and quota is used to acknowledge user how much space he
%has actually used.

With Aliyun's distributed file system support, the snapshot store operates a few \emph{append-only} files
in the underline file storage. Each virtual disk has its own data store, all data 
blocks after deduplication will be stored into that system.
Since all the underline data structures is append only,
upon a delete request, the corresponding data will only be marked rather than being deleted.
A compaction will take place when deleted data has accumulated to a certain threshold, thus 
reclaiming the disk space .

%The detail design and implementation of our distributed file system and various 
%storage subsystems would be too complicated to be intorduced here, and also beyond
%the scope of this paper. In the remaining section we will brief the model and interface of 
%our snapshot storage.

\subsection{Inner-VM Deduplication}
\label{sect:innerVM}

The first-level deduplication is logically localized within each VM.
%There are several reasons that we let each MS have  its own block store for localized duplication rather than sharing. 
%First, all data written to block store are already being processed by deduplication
%process, thus no sharing is necessary unless we want to perform additional deduplication
%inside the block store. Second, 
Such localization increases data independence between different  VM backups,
simplifies  snapshot  management and statistics collection during VM migration and termination,
and facilitates parallel execution of snapshot operations.
%Finally, this reduces the complexity of concurrent snapshot operations.

%\begin{figure}[htbp]
%  \centering
%  %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
%  \epsfig{file=images/dedup_process.eps,  width=3.2in}
%  \caption{An example  of multi-level deduplication process.}
%  \label{fig:arch}
%\end{figure}
\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
  \epsfig{file=images/snapshot_representation.eps,  width=3.2in}
  \caption{An example  of snapshot representation.}
  \label{fig:snapshot}
\end{figure}

The inner VM deduplication contains two levels of duplicate detection efforts and the representation of
each snapshot is correspondingly designed as a two-level level index data structure in the form of a hierarchical
directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
An image file is divided into a set of segments and each  segment contains hundreds of content blocks from the bottom level.
These blocks are of variable-size, partitioned using
the standard chunking technique~\cite{similar94}.  We use 4KB as the average block size. 
The segment metadata (called segment recipe) records its  content block hashes and  data reference. 
The snapshot-level recipe contains a set of  segment recipes and other meta data information.
\begin{itemize}
\item {\em Level 1 Segment modification  detection}.
If a segment is not changed, indicated by a dirty bit, its content blocks are not changed also. In this case,
 segment-level duplicate detection is more efficient than the block level.

\item {\em Level 2  Block fingerprint comparison.}
If a segment is modified, content blocks of this segment are compared with 
the fingerprints of the existing content blocks within the same segment in
the previous version of this snapshot (called parent  snapshot). Partial duplication
within the segment can be detected and eliminated. 
\end{itemize}

We choose this two-level structure because in practice we observe that at each snapshot there are a large
number of content blocks which are not modified from one snapshot version to another.
Aggregating a large number of content blocks as one segment can significantly
reduce the space cost of snapshot meta data. 
%Namely the  snapshort metadata starts with
%the representation of segment-level meta data. Each segment receipe can be further represented by
%a set of content block receipes.

How can we choose the length of a segment?
Instead of using variables-sized segments, we take a simple approach
to let every segment being aligned to the page boundary of each virtual image file.
For Aliyun, each VM image file is represented as a virtual disk file format
(called \emph{vhd} at Xen) and we use a dirty bit to capture if a page (or segment) of a virtual snapshot file 
has been modified or not for segment-level deduplication.
%This is effective because  
%a vhd   file keeps the allocated inner blocks at the same positions until deletion,
%which means the locality of snapshot data is almost natively aligned. 
A dirty bit array is used to indicate which segments have been modified or not. 
Each page (segment) size in our implementation uses 2MB, which contains a large number of content blocks.
%Enforcing a boundary at every 2MB will 
%only break 0.2\% of total data blocks which is tiny.
% dirty bits array. This is because
%Inside the TapDisk driver, we maintain an array of \emph{dirty bits} to record the dirty area
%of runtime VM image file since the last snapshot, each bit represent a 2MB fix-sized
%data segment. During a snapshot operation, we only need to look at the dirty region
%rather than scan over the whold image file, which would be extremely slow.

%We let each virtual disk has its own block store rather than sharing for several reasons:
%first, all data written to block store are already being processed by deduplication
%process, thus no sharing is necessary unless we want to perform additional deduplication
%inside the block store. Second, such seperation will facilitate VM data stastics, 
%deletion and migration. Finally, this reduces the complexity of concurrent snapshot operations.

Once level-2 deduplication is activated for those segments that have been modified,
it requires memory to load  block fingerprints from the corresponding
parent snapshot's segment.
This scheme processes one segment at time and each segment of 2MB contains about 
500 content blocks on average given 4KB is the average block size.
That only takes a tiny amount of space to hold their fingerprints.
%Given  1-2 hours of window to backup snapshots and every VM has  on average about 40GB, there is enough
%time to search all segments sequentially~\cite{NOT-CLEAR-HERE}

\subsection{Cross-VM Deduplication with CDS}

The third-level of deduplication is to identify duplicated data blocks among multiple VMs through the index cache
of common data set (CDS).  CDS is the most popular content blocks 
among  recent snapshots across all VMs. 
Each index entry contains  the block fingerprint and a reference pointer to the location of its real content
in the snapshot content block store residing in the underlying distributed file system.
%The structure of CDS meta is not different from the segment recipe we discussed above, 
%except that it is partitioned into many small slices so that each node is easy to load its own slice.

At the runtime, the CDS index resides in a distributed  memory lookup table  
implemented using Memcached~\cite{memcached} to leverage the aggregated memory in a cluster.
Th usage of memory for each machine is small and thus  this scheme  does not
lead to  a memory resource contention with the existing cloud services.
For example, in our current implementation setting at Aliyun, we use up to  150MB memory per node during night backup
including CDS and other metadata for all levels of deduplication. Most of memory resource (48GB per node 
in our experiment) is used for existing  applications.
Each CDS content data stored  in the distributed file system
has multiple copies in different machines for the purpose of fault tolerance and 
while providing high read  throughput.  
%The data of CDS is stored in a special block store in the distribued file system.

% which doesn't belong to any VM disk.

%CDS meta assignment is done statically, each slice of CDS meta has one primary and two backup nodes.
%During the system bootup, snapshot storage controller will read the assignment, 
%load its primary portion of CDS meta from distributed file system. Loading the backup portion
%of CDS is due upon a query arrives for it. Everyday the CDS assignment and CDS data will be checked
% for updates and reloaded if necessary.

%Behind the scene there is a offline map-reduce job, which will periodically scan the block stores
%in the entire cluster and perform a ``word counting''. High frequency blocks are then added to the CDS if its count 
% is greater than threshold, which is pre-defined by the system memory restrictions.
To control the size of searchable common data in this global setting, we focus on those items that 
are most popular based on the historical snapshot data and the popular analysis is conducted periodically to ensure 
meta data freshness to match the latest data access trend.
There are two advantages to exploit this.
First, a smaller CDS reduces overall resource requirement while covering  most of data blocks in snapshots.
Second a smaller CDS makes the fault tolerance management  easier because we can replicate  more copies
to mitigate the failure.

In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus  one or more data disks.
During VM's creation, its OS disk is directly copied from user's chosen base image.
Given the separation of OS disks and data disks, we study  their characteristics separately.
We expect that the operating system and along with popular software installations  are not frequently
modified or deleted. 
%base image data as a hint.Through users may change configurations, install software, or write user data into OS disk,
%Thus most of content blocks for the OS related snapshots  shall keep unchanged.
%This is verified in  Section~\ref{sect:exper}.
We have sampled  the  popularity of common blocks in the OS and data disks from a dataset
containing over 1,000 VMs and each has 10 snapshots.
Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.

\begin{figure}[htbp]
\centering
%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
%\epsfig{file=images/log-log.disk.eps, width=3in}
\epsfig{file=images/datadisk.count_rank.eps, width=3in}
\caption{Duplicate count  of common data blocks in a log scale.}
\label{fig:zipf-data}
\end{figure}
Figure \ref{fig:OSpopular} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
$Y$ axis is the popularity of an OS block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
sorted by their duplicate rank.  For the top ranked blocks, there is a flat line in terms of duplicate counts. That
is because there are a large number of OS blocks which have appeared in all copies of such OS releases.

\begin{figure}
\centering
%\epsfig{file=images/log-log.35vmos.eps,  width=3in}
%\epsfig{file=images/35os.count_rank.eps, width=3in}
\epsfig{file=images/35vmos.count-rank.eps,width=3in}
\caption{ Duplicate count of  common OS blocks in a log scale.}
\label{fig:OSpopular}
\end{figure}

Thus our CDS selection strategy is designed as follows.
\begin{itemize}
\item First, most popular items from OS disks are selected.
Our experiment data shows that about 
100GB data ($25\times 10^6$\cite{BAD}) from 7 most popular OS releases
can cover over 70\% of OS snapshots and the index of these 100GB OS data blocks
only takes about total 800MB in the CDS index and then memory requirement per node for running the backup
on  100 nodes is tiny.
We expect in practice the OS CDS index may grow up to 2GB in order to cover large varieties  of commonly deployed
OS releases in practice.
\item Second, the degree of duplication is computed for snapshot blocks of data disks and
% and also snapshot 
%blocks of user data items stored in the OS disk (some users store data in their OS disks).
the  most popular items are selected. As discussed in Section~\ref{sect:exper}, 
about $10^7$ (???) most popular items
can cover about 37\% of content blocks appeared in various snapshots after level 1 and level deduplication.  
\end{itemize}

\subsection{Illustration  of multi-level deduplication process}

\comments{
\begin{figure*}
  \centering
  %\epsfig{file=images/dedup_flow1.eps, height=2in, width=3.5in}
  \epsfig{file=images/dedup_flow1.eps,  width=6in}
  \caption{Flow of deduplication.}
  \label{fig:tapdisk}
\end{figure*}

The 3-level deduplication process can be summarized as four steps:
\begin{list}{Dedup}{}
\item {Dirty bits: Copy the unchanged portion of snapshot recipe from parent snapshot, base on dirty bits.}
\item {Locality: Divide dirty segments into blocks, compare to the corresponding segment recipe at the same position of parent snapshot, if duplicate, copy the data reference into segment recipe.}
\item {CDS: Check if this data exist in the CDS, if yes, copy the returned data reference. Otherwise, write data block to block store, save the returned reference into segment recipe.}
\item {Save meta: write down the segment recipes and snapshot recipe when finish.}
\end{list}

}

%%Our deduplication process is divided into three levels, at each level, we eliminate the most of duplicate data with available knowledge, preventing them from going further because deduplication at deeper level is more expensive.
%
\begin{figure}
  \centering
  \epsfig{file=images/dedup_flow1.eps, height=2in, width=4in}
  \caption{Illustration of snapshot deduplication dataflow.}
  \label{fig:dedupflow}
\end{figure}

We illustrate the steps of 3-level deduplication in Figure~\ref{fig:dedupflow}, which can be summarized as 5 steps:
\begin{enumerate}
\item {\em Segment level checkup.}
As shown in Figure~\ref{fig:dedupflow} (a),
when  a snapshot of a plain virtual disk file is being created, we first check the dirty bitmap array of
this disk file  to see which segments are modified. If a segment is not modified since last snapshot, 
it's data pointer in the recipe of the  parent snapshot  can be directly copied into 
current snapshot recipe (shown as the shadow area in Figure~\ref{fig:dedupflow} (b)).

\item {\em Block level checkup.}
As shown in Figure~\ref{fig:dedupflow} (b),
for each dirty segment, we divide it into variable-sized blocks,
and compare their signatures with  the corresponding segment recipe in the previous snapshot version (called parent
snapshot). 
For any duplicated block, we copy the data pointer directly from the parent segment recipe. 
\item {\em CDS checkup.} For the remaining  content blocks whose duplicate status is unknown,
Figure~\ref{fig:dedupflow} (d)
shows  a further check to compare  them with  the cached signatures in the CDS by querying
the CDS hash index. If there is a match, the corresponding data pointer from the CDS index is
copied into the segment recipe. 
\item {\em Write new snapshot blocks :}
We continue the previous step and 
if a data block cannot be found in the CDS index, this block is considered to be a new block
and such a block is to be saved in the snapshot block store and  the returned reference  pointer is
saved in the  segment recipe.
\item {\em Save recipes.} Finally the  segment recipes are saved in the  snapshot block store also.
 After all segment recipes are saved, the snapshot recipe is complete and can be saved also.
\end{enumerate}

If there is no parent snapshot available, which happens when a VM creates its first snapshot, 
only CDS-based checkup will be conducted.
%This is important because most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
%at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.

### 2012-02-29 vm_snapshot_sim/2012background.tex
Tao

\section{Background and Related Work}
\label{sect:background}

In a VM cloud, several operations are provided for creating and managing snapshots and snapshot trees,
such as creating snapshots, reverting to any snapshot, and removing snapshots.
For VM snapshot backup, file-level semantics are normally not provided. 
Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided.
%Snapshots may be shared among VMs when a user runs the same binary image on different  VMs.
% This feature complicates the snapshot management, 
%but also require all snapshots be managed in a global namespace.

%While snapshot backup loads are heavy but computing and storage  resources available 
%can be limited to reduce the overall operation cost of a cloud. The whole VM cluster have petabytes of data and need to 
%be backed up at daily basis, if not more frequently. But at the same time snapshot tasks must not affect the normal VM operations
%in a cloud service, which means only a tiny slice of CPU and memory can be used for this purpose.

VM snapshots can be  backed up  incrementally by identifying file  blocks that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
%Even though the snapshots are saved incrementally,
%when deleting a snapshot, only the data not needed for any other snapshot is removed.
%So regardless of which prior snapshots have been deleted, all active snapshots will contain
%all the information needed to restore the virtual disk.
%One widely used snapshot strategy is copy-on-write (CoW).
%The earlier use of COW is to improve memory usage and reduce copying overhead in process 
%management~\cite{OSbook,Waldspurger2002} and it can be extended for snapshot 
%storage management~\cite{vmware_kb1015180}. 
%C. Waldspurger. Memory Resource Management in VMware ESX Server in Proceedings of the 5th Symposium 
%on Operating Systems Design and Implementation, 2002
%Upon VM image storage system receives a save snapshot request,
%it freezes the state of that image file, then all consequent write request will result in the write region being copied
%to an incremental snapshot data file. 
%Such a strategy exploits version difference between consecutive snapshots
%of the same image.
The main weakness
is that it does not reveal content redundancy among data blocks from different files or
different VMs.
%has several disadvantages:
%first, CoW may affect the general I/O performance due to defered data coping. 
%Second, CoW does not seperate backup data and runtime image data,
%which have distinct access requirements: runtime image data is directly used by the running VM, 
%thus need high throughput, and is very sensitive to latency,
%such data must be served with hig cost hardware, but backup data generally only need fair aggregate throughput, 
%is not sensitive to latency, thus can be stored in secondary storage devices.
%Finally, VM snapshots contain tremendous amount of data duplication, which is nearly impossible to tackle 
%if these two kinds of data are tightly coupled together.

Data deduplication techniques can eliminate redundancy globally among different files from different users. 
Backup systems have been developed to use content hash (finger prints) to identify duplicate 
content~\cite{venti02,Rhea2008}.
%,NGmiddleware2011}. 
Today's commercial data backup systems (e.g. from EMC and NetApp)
%\cite{emc_avamar}\cite{datadomain_whitepaper} 
use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
%Chunking divides a data stream into variable length chunks, it has been used to conserve bandwidth\cite{lbfs01}, 
%search and index documents in large repositories\cite{bhag07}, scalable storage systems\cite{hydrastor09}, 
%store and transfer large directory trees efficiently and with high reliability\cite{jumbo07}.
To chunk a file, starting from the first byte, its contents as seen through a fixed-sized (overlapping) 
sliding window are examined. At every position of the window, a fingerprint of its 
contents, $f$, is computed using hashing techniques such as Rabin fingerprints~\cite{rabin81}. 
When this fingerprint meets a certain criteria,
% such as $f mod D = r$ where $D$, the divisor, 
%and $r$ are predefined values; 
the position of the corresponding window defines the boundary of the chunk. 
This process is repeated until the entire file has been completely broken down into chunks. Next, 
a cryptographic hash or chunk ID of the chunk is computed using a technique such as MD5 or SHA.
After a file is chunked, the index containing the chunk IDs of backed up chunks 
is queried to determine duplicate chunks. New chunks are written to disk and the 
index is updated with their chunk IDs. A file recipe containing all the information 
required during reconstruction is generated. The index also contains some metadata 
about each chunk, such as its size and disk location.
%The compression rate obtained by deduplication depends on the inherent content overlapping degree in a dataset, 
%the average size of chunks, and the chunking method\cite{poli04}. 
%In general, smaller chunks yield better deduplication.

Data deduplication has been applied as  a post-processing operation for offline removal
of redundant content in the file system data management once backup data is written in a temporary stage area.
Dynamic inline deduplication is an effort to improve storage efficiency  
by detecting and removing  duplicates before data is written to the backup storage,
thus reduces extra disk space required to hold temporary data. 
This approach requires a fingerprint  comparison of the new content chunks with
previously stored fingerprints. 
As data grows to be big, content chunk lookup for fingerprint comparison from disk storage
becomes too slow to be scalable.
%and searching such disk
%However, unless some form of locality or similarity is exploited, inline, chunk-based deduplication, 
%when done at a large scale faces what has been termed the disk bottleneck problem: to facilitate fast chunk ID lookup, 
%a single index containing the chunk IDs of all the backed up chunks must be maintained. 
%As the backed up data grows, the index overflows the amount of RAM available and must be paged to disk. 
%Without locality, the index cannot be cached effectively, and it is common for nearly 
%every index access to require a random disk access. This disk bottleneck severely limits deduplication throughput.
Several techniques have been proposed to speedup searching of duplicate 
content~\cite{bottleneck08,extreme_binning09,sparseindex09}. For example,  
Zhu et al.~\cite{bottleneck08} tackle it 
by using an in-memory Bloom filter and prefetch groups of chunk IDs that are likely to be 
accessed together with high probability. It takes significant memory resource for filtering.
NG et al.~\cite{ NGmiddleware2011}  use  
a related filtering technique for integrating deduplication in Linux  file system and the memory
consumed is up to 2GB for a single machine. That is still too big in our context discussed below. 
%Lillibridge et al.~\cite{sparseindex09} break list of chunks 
%into large segments, the chunk IDs in each incoming segment are sampled and the segment is 
%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments. 
%These are segments that share many chunk IDs with the incoming segment with high probability.
%Deepavali et al.~\cite{extreme_binning09}  use signature-based file similarity  and group similar files
%into the same physical location (bins) to deduplicate against each other.

Duplicate  search approximation~\cite{extreme_binning09,sparseindex09}  has been proposed 
%in extreme bining and other sparse indexing 
to package similar content in one disk, and duplicate lookup  only searches
for chunks within files which have a similar file-level or segment-level  content fingerprints.
That leads  to a smaller amount of memory usage for storing meta data in signature
lookup with a tradeoff of the reduced recall ratio.

\section{Requirements and Design Options}
\label{sect:options}

We discuss the characteristics and 
main requirements for VM snapshot backup in a cloud environment.
which are different from a traditional data backup. 
% That arises mainly in Alibaba's Aliyun cloud service.
%concerns
%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
\begin{enumerate}
\item {\em Cost consciousness.}
There are tens of thousands of VMs running on a large-scale cloud cluster. 
The amount of VM data to backup is huge and cost of complete backup can be prohibitively high without
deduplication and compression support.  Thus cost minimization is required to deliver a deplorable solution.

On the other hand, the computing resource allocated for backup is often very small.
This is because snapshot data is not retrieved frequently by users and the allocation of  cluster resource
is typically prioritized towards active services such as online web services and map-reduce jobs.
Thus  it is not easy to accept any backup behavior that affects VMs performance or stability of active users.

%snapshot service shall not compete cpu, memory, or I/O bandwidth with VMs. Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
\item {\em Fast backup speed.}
The snapshot  backup  operations need to be completed quickly  every day (e.g. 1-2 hours ). 
Often a cloud service has  few hours of light workload each day (e.g. midnight),  which creates an opportunity  for backup.
But a  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with the existing cloud,
which is not preferred for cloud production system operation. 
%As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
%to be processed is huge. 
%For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, The aggreated amount of data 
 % the system must finish saving daily snapshots of all VMs in 2 hours. In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.

% the system must finish saving daily snapshots of all VMs in 2 hours. In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.
\item {\em Fault tolerance.}
The addition of a backup service should not decrease the degree of
fault tolerance.  If data failure in  a backup service  affects many users,  such a solution is not desirable.
%when users access snapshots in a recovery process. 
\end{enumerate}

There are multiple choices in designing a backup architecture  for VM snapshots.
We discuss the following design options with a consideration on their strengths and weakness.
\begin{enumerate}
\item  {\em An external and dedicated backup storage system.} 
In this architecture setting, a separate backup storage system using
the standard backup and deduplication techniques can be deployed~\cite{bottleneck08,extreme_binning09,sparseindex09}. 
This system is attached to the cloud network and every machine can periodically transfer snapshot data to 
the attached backup system. 
A key weakness of this approach is communication bottleneck between a large number of machines
in a cloud to this centralized  service.
Another weakness is that the cost of allocating separate resource for dedicated backup  can be expensive.
Since most of backup data is not used eventually, CPU and memory resource in such a backup cluster may not be fully utilized.
\item {\em A decentralized and co-hosted backup system with full deduplication.}
In this option, the backup system runs on an existing set of cluster machines. 
The advantage is that there is no separate and dedicated cost for backup.
% and a distributed storage architecture for backup allows a possible exploitation of  data locality between
%the source of data and storage location of backup data. 
The disadvantage is that 
%the backup service would compete CPU, memory, and disk resources with the other cloud services.
even such a  backup service may only use  a fraction of the existing disk storage, 
fingerprint-based search does require a significant amount of memory for fast lookup of identical content chunks.
This competes memory resource  with the existing applications.
%Decentralized deduplication is studied in ~\cite{Clements2009} and the focus is on
%block-level copy-on-write and compare-by-value techniques.
Even approximation~\cite{extreme_binning09,sparseindex09} can be used to reduce memory requirement,  
a  key weakness of global content fingerprint comparison is that it can affect fault isolation.
Because a content chunk is compared with a content signature collected from other users,
this artificially creates data dependence among different cloud users.
% since storage for shared identical content chunks can become a failure point.
The loss of a common chunk can affect many users whose VM images share this 
chunk. Adding replicas for this global dataset can enhance the availability,
but incurs significantly more cost.
%2) data sharing among users for accessing common signagutes causes the system less resilient to storage failures.
%any loss of one piece of  shared data content hash and actualcontent will damange many VM snapshots, which can cause massive impacts
%on reliability of many users.

%Another point is that the previous work in signature-based comparison does not address
%load balancing for a distributed environment during parallel access.  
%Some content signatures can be extremely hot, but the machines  that  handle such signatures can become
% a bottleneck. Uncoordinated signature assignment could lead to imbalanced access workload.
\end{enumerate}

%There are multiple choices of snapshot backup design for VM images and our considerations are described
%as follows. 
%Our design considerations
%\begin{enumerate}
%\item {\bf Centralized vs. decenalized} 
%
%It is desirable to have  a decentralized architecture.
%Given a large amount of snapshot data communicated from each machine to the backup storage,
%with a distributed storage architecture for backup, one could exploit  exploit data locality between
%the source of data and storage location of data to reduce cross-platform bandwidth requirement for backup.

%execute in parallel and easy to coordinate. In fact, we want to avoid cross-node dependency at scheduling VM snapshot operations, such that no global coordinator is necessary.
%\item {Load balancing in resource consumption}: the cost of snapshot service shall be evenly distributed onto every node. We don't have a super powerful
%or stable node that can accept extra responsibility.
%\item {minimization of inter-user data dependency for fault tolerance}: we want to minimize the data dependency to a controllable level. Data deduplication means sharing of data, thus one failure at a single point may affect the snapshot service of hundreds of VMs, which is absolutely unacceptable.
%\item {Resource usage modeling and control}.
%\end{enumerate}

With these considerations in mind, we propose a decentralized backup architecture with multi-level and selective 
deduplication. This 
backup service is hosted   in the existing set of cloud machines and resource usage is controlled
with a minimal impact to the existing applications.
The duplication process is first conducted among data within each VM
and then is conducted  across VMs when needed to 
utilize a common dataset.  
Given the concern that searching duplicates across  VMs  is a global feature which can affect parallel performance
and complicate failure management,
we would like to use a small common dataset while still maintaining a cost-effective deduplication ratio.
For this purpose, we exploit the data characteristics of snapshots and only store most popular data.
%
%in the  our studies show that there are a large amount of data unmodified in VM snapshots
%and shared among many users (e.g. OS data). The sharing pattern follows a zip-like distribution.
%With this characteristic, we can store a small amount of popular data items which coverage a large amount of
%snapshot data blocks. 
%We discuss our design and data analysis in the next section.

%This method is based on the observation of two facts in Aliyun's VM cloud: first, VM's OS disks contain 
%huge amount of operating system and software related data which is almost never modified during VM's life span. 
%Second, the duplication pattern of user generated data follows Zipf-like law, thus a tiny set of hottest data
%take up the majority of data duplication. As a result, if we extract these hot data as a common data set,
%then most of data duplication will emerge by searching in this very small scope.

%For example, In cloud storage, we are solving data deduplication problem in a different context of 
%data stream deduplication (the D2D case): our snapshot storage service is co-located with runtime VMs,
%thus we have very limited amount of system resource leave for data deduplication. For example,
%in Aliyun's 8-core, 48GB memory, 12TB VM server, there lives over 20 VMs who are hungrily competing for
%system resources: some may running map-reduce jobs, some may serving busy web requests, 
%some may storing backend databases, any behavior that affects user VMs performance or stability is unacceptable.

%To reduce the cost of deduplication, we must confine the scope of searching duplicates as much as possible,
%thus some hints are needed to tell us where the most likely duplicates would hide. 
%Several form of hints have been used in the past: many D2D systems exploits locality,
%which bases on the fact that duplicates are likely to appear in the same sequence as they have arrived before.
%Similarity is another popular hint, it suggests that two sets of data blocks may contain lots of
%duplicates if they are indetified as similar by certain similarity detection measurements.

%\section{Architecture design and Deduplication for Snapshot Support}
%
%\section{Popularity analysis}
% data on what data popular.
%
%Analysis: modeling: singular
%
%Compute: Cache hit ratio vs. cache cost (memory cost).

### 2012-02-29 vm_snapshot_sim/2012concl.tex
Tao

\section{Conclusion}
\label{sect:final}
In this paper we propose and present a multi-level selective deduplication scheme for VM snapshots. 
with minimal cost. Inner-VM deduplication localizes backup data dependence and exposes more parallelism  
while we use  data characteristic in VM cloud backup to identify popular common data blocks
and cover  a large percentage of snapshot content blocks wit a small amount of memory index.
Our evaluation using Aliyun's implementation has shown that 
level 1 and level 2 deduplication can reduce the storage need by 80\%. 
Level 3 with small CDS memory usage can accomplish close to 44\% of what full fingerprint-based
deduplication can do and bring additional 6\% storage reduction compared to the original data size.
Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,
this is about 600 terabytes.

%Our experiments show th
%our solution can eliminate the majority of data duplication with a tiny fraction of
%block hash index store in memory. It does not only saves valuable system resouces in
%the VM cloud, but also makes deduplication much faster.
%
%
%Using  50 user VM data out of 1322 data disks as the training data and
%with  1.5\% as CDS threshold, we see the total 1198GB of new data is reduced by
%755.8GB, while perfect deduplication can reduce 1017.4GB. So 74.3\% of duplicate blocks are eliminated
%by pre-trained CDS, which is quite satisfactory.

### 2012-02-29 vm_snapshot_sim/2012eval.tex
Tao

\section{Evaluation}
\label{sect:exper}

We have implemented a snapshot deduplication scheme on the Aliyun's cloud platform.
Our experimental evaluation has the following two objectives:
1) Analyze the commonality of content data blocks and the popularity  of hot items. We 
examine the impacts of CDS size on deduplication ratio.
2) Assess the effectiveness  of 3-level deduplication for reducing the storage requirement of snapshot 
backup.

\subsection{Experimental setup}

An Aliyun cluster we target is over 1000 nodes with 16 cores and 48GB memory
and each node hosts 25 VMs.
We are running our deduplication/backup  service on 100 nodes.
Memory usage is about 150MB space per node during backup and
the CPU usage is very small during the experiments. 
Based on the data studied,  each VM has about  40GB of storage  data usage on average
and each of OS disk and data disk takes about 50\% of storage space.
The backup of VM snapshots is completed within two hours  every day,
and that translates to a backup throughput of 139GB per second, or 500TB per hour.
For each VM, the system keeps  10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.

% the system must finish saving daily snapshots of all VMs in 2 hours. In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.

%In our snapshot deduplication architecture, CDS is the key to achieve greater deduplication than
%incremental backup solutions. Our basic assumption of CDS us that VM disks, especially OS disks,
%have huge amount of data in common, and such common data can be represented by a relatively smaller data set
%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
%the effectiveness of CDS using real user VM disks from our production VM cluster.

We have used a storage dataset of  1323 VM users collected from 100 Aliyun's cloud nodes  to evaluate the effectiveness.
In this dataset, there are 10 snapshots per each VM user and the total amount of space investigated 
is 23.5 terabytes.
Each VM file is  divided into a set of content blocks using
TTTD chunking~\cite{??} with an average size of 4KB. Each segment is of size 2MB.  
Popularity is computed by using 90\% of dataset, which reflects our setting that the system recomputes
CDS every 1-2 days to catch up the popularity trend.

%seg, and we performed global perfect deduplication 
%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
%and maximum block size
The signature for variable-sized blocks is computed using  their SHA-1 hash. 
%OS data
%user data: zipf
%prediction
%say something about aliyun

%To compare the effectiveness with a full deduplication approach with an approximation,
%we use  extreme binning and perfect deduplication~\cite{extreme_binning09}. 
%For perfect deduplication and extreme binning, each snapshot is also divided into chunk blocks
%using TTTD with an average size of 4KB. The original extreme binning work uses the whole file
%as the input unit and  this size is too big in our system. 
%Thus we split each image snapshot file into variable-sized segments base on the block hash list, 
%using TTTD with average size of 2MB.

\subsection{Effectiveness of 3-level Deduplication}

\begin{figure}
  \centering
  \epsfig{file=images/overall_effect.eps, width=3in}
  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
deduplication divided by the original data size and the unit is percentage. }

  \label{fig:overall}
\end{figure}

Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication.
The X axis shows the overall impact in (a),  impact on OS disk in (b), and impact on data disk in (c).
Each bar in the Y axis shows the data size after deduplication divided by the original data size.
Level-1 elimination can reduce the data size to 22\% of original data, namely it delivers close 80\% reduction.
Level-2 elimination applied after level 1
reduces the size further to 16\% of original size, namely it delivers additional 6\% reduction.
Level-3 elimination together with level 1 and 2
reduces the size further to 9\% of original size, namely it delivers additional 7\% reduction.
Level 2 elimination is more visible in OS disk than data disk, because data change frequency is really small
when we sample last 10 snapshots of each user in 10 days. Nevertheless, the average impact of level 2 is also significant.
A 6-7\% of reduction from the original data represents about 600-700TB of space.

\begin{figure}
  \centering
 %\epsfig{file=images/os_cds_sim.eps, width=3in}
  \epsfig{file=images/3level_os.eps, width=3in}
  \caption{Impact of 3-level deduplication for OS releases.}
  \label{fig:oscds}
\end{figure}

To see the impact of multi-level deduplication on different OS releases, we choose 7 major OSes in Aliyun's
VM cloud platform and they are: 
Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
distributions are 64 bits).
Then we examine 5 VM user disks from each OS, and 10 snapshots for each VM. These VMs have been actively used by their
owners. 
%Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
Figure~\ref{fig:oscds} shows the impact of different levels of deduplication for different OS releases.
In this experiment, we tag each block as  ``new''
if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot block store;
``CDS''  if this block can be found  in CDS;
``Parent segment'' if  this block is marked unchanged in parent's segment recipe.
``Parent block'' if  this block is marked unchanged in parent's block recipe.
With this tagging, we compute the percentage of duplication accomplished by level-1 inner VM deduplication,
level-2 inner VM deduplication and level 3 cross-VM deduplication.
As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination
this is because the time interval between two snapshots in our dataset
is quite short and the Aliyun cloud service makes a snapshot  everyday  for each VM.
On the other hand,  CDS still finds lots of duplicates that inner VM deduplication can't find,
contributing about about 10\% of reduction on average.

%Combining OS disks in all the VMs, we see the overall 7.4TB of data is reduced to 512GB. 
%The extreme binning approach can reduce this data set to 542GB, which is slightly worse. As a reference, 
%perfect deduplication achieves 364GB in this experiment.

Overall speaking, inner   VM deduplication or  CDS-based deduplication
can work well alone, but by combining them together we get a fairly good and stable deduplication ratio to 
all kind of OSes. 
Compared to a traditional dirty bit approach based on pages of
each file (e.g. segment in our scheme),
our CDS-based level 3 approach  can save additional 50\% storage space because many of level 2 block
content can be eliminated using the CDS also.

\subsection{Coverage of common data blocks}

%We study characteristics of common data blocks among snapshots of VM users
%and examine the impacts if we only store a relative small amount of common data blocks to be sored in the CDS server.
%There are two advantages to exploit this.
%First, a smaller CDS reduces overall resource requirement while covering  most of data blocks in snapshots.
%Second a smaller CDS makes the fault tolerance management  easier because we can replicate  more copies
%to mitigate the failure.

%We consider each virtual disk contains two parts: OS partition and regular user data partition
%and study their characteristics seperately.
%In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus  one or more data disks.
%During VM's creation, its OS disk is directly copied from user's choosen base image.
%Since  they dare brought by the operating system and popular 
%software installations,  they are rarely modified or deleted.
%base image data as a hint.
%Through users may change configurations, install software, or write user data into OS disk,
%but most of the OS related data shall keep unchanged.

%Previous study has also supported this\cite{vmimage}. Therefore, we can let all OS disks share these
%common data in their snapshot backups.
%We choose user's data disks rather than OS disks in thie experiment for several reasons: First, the data in OS disks are 
%instinctively highly similar, because most of the VM users only make some common or unique but tiny changes to their OSes,
%so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
%Second, the data disks are way more important in terms of data safty and backup because they are 
%what users really care about.

%Furthermore, our study on user's data disks has shown that the duplication pattern of
%variable-sized data blocks follows \emph{Zipf-like} distribution. As a result, the major portion of 
%deduplication effect will emerge from eliminating the duplication of frequently seen data.
%define CDS

\comments{
\begin{figure}[htbp]
\centering
%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
%\epsfig{file=images/log-log.disk.eps, width=3in}
\epsfig{file=images/datadisk.count_rank.eps, width=3in}
\caption{Duplicate count  of common data blocks in a log scale.}
\label{fig:zipf-data}
\end{figure}
Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.

\begin{figure}
\centering
%\epsfig{file=images/log-log.35vmos.eps,  width=3in}
%\epsfig{file=images/35os.count_rank.eps, width=3in}
\epsfig{file=images/35vmos.count-rank.eps,width=3in}
\caption{ Duplicate count of  common OS blocks in a log scale.}
\label{fig:OSpopular}
\end{figure}
Figure \ref{fig:OSpopular} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
$Y$ axis is the popularity of an OS block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
sorted by their duplicate rank.  For the top ranked blocks, there is a flat line in terms of duplicate counts. That
is because there are a large number of OS blocks which have appear in all copies of such OS releases.

}

\begin{figure}
\centering
\epsfig{file=images/ay41a_big.data_disk.cdf.eps, width=3in}
%\epsfig{file=images/cdf.disk.v4.eps, width=3in}
%\epsfig{file=images/datadisk.count_rank.eps, width=3in}
%\epsfig{file=images/35os.count_rank.eps, width=3in}

\caption{Cumulative  coverage of popular common user data blocks.}
\label{fig:userdatacoverage}
\end{figure}

We further study how CDS covers content blocks used in image files.
Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular common user data blocks. 
The $X$ axis is the rank of common user data blocks.
Let $S_i$ and $F_I$ be the size and duplicate count 
of the $i$-th block ranked by its duplicate rank.  Then $Y$ axis is the coverage of
the common dataset covering data items from rank 1 to rank $i$. Namely  
\[
\frac{ \sum_{i=1}^{i} S_i * F_i} {\mbox{Total data size}}
\]

Figure~\ref{fig:OSdatacoverage} shows the cumulative coverage  ratio of  popular common OS blocks. 
From both graphs, a small number of most popular common blocks can coverage a large percentage of 
snapshot blocks and thus the size of CDS can be chosen to be small while still having a large
coverage. 
% with $\alpha$ close to 0.78.
%A tiny hottest fraction of data lead to majority of data duplication, as a result, we can target at this small set of commonly seen data
%to design our fast and lightweight deduplication process, just like what people did in CDN and web proxy.

\begin{figure}
\centering
%\epsfig{file=images/cdf.os.v4.eps, width=3in}
%\epsfig{file=images/cdf.os.v4.eps, width=3in}
\epsfig{file=images/ay41a_small.os_incremental.cdf.eps, width=3in}
\caption{ Cumulative  coverage of popular common OS disk blocks.}
\label{fig:OSdatacoverage}
\end{figure}

%We define \emph{OS CDS} to be the unchanged data across the base VM image and the snapshots of all
%OS disks which are derived from it. Such data are brought by the operating system and popular 
%software installations, they are rarely modified or deleted, and can be easily extracted using 
%base image data as a hint.

The selection of CDS is completed by separating OS disk and data disk.
While block commonality among data disks may be affected in some degree
 when we scale up the number of total VMs  to be supported,
we expect that  the block commonality among OS disks still remains to be high and  
can be well covered by a fixed CDS because users still adopt common OS releases.
To  verify this,  we examine the percentage of common  OS blocks of the same
release in different VMs  OS releases in Figure~\ref{fig:OSunchanged}. 
%we choose 7 major OSes in Aliyun's
%VM cloud platform and they are: 
%Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
%distributions are 64 bits).
%we examine 5 VM user disks from each OS, and 10 snapshots for each VM. These VMs have been actively used by their
%owners. Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
%their OS disks. 
%For example, some Ubuntu OS disks have only 2GB of data while some have 50GB.
%For each OS, the base image and all OS
%disk snapshots are divided into variable-sized blocks. Then 
We consider the earlier snapshot for each OS disk as the base image.
For every block in the base image, 
we classify this block as ``completely common''
if  this block has appeared in all snapshots of the same OS release even they are used by different VMs.
Figure \ref{fig:OSunchanged} shows that for each
OS,  at least 70\% of OS blocks are common among all snapshots of the same OS. 
Some latest release  of OS tends to have a higher percentage of content change
while  old release tends to have more variations of content versions.
That can be interpreted as that users with very old  version of operating systems
have a lower tendency to update their OS versions and this causes a larger discrepancy
among OS snapshots of these users.

%into the unchanged category of OS data.

\begin{figure}
\centering
\epsfig{file=images/os_subset.eps, height=2in, width=2.66in}
\caption{Percentage of completely common blocks among different VMs for the same OS release.}
\label{fig:OSunchanged}
\end{figure}

????????????????????????????????????????????????
Based on the above analysis, we have selected a small set of most popular
OS blocks, which is 1.5\% of  unique OS blocks. This set
is quite sufficient to cover the OS related blocks. 
%Then we use this CDS to run the deduplication process again.
That correspond to about  80GB of OS blocks and its corresponding CDS meta occupies 800MB in the cache.
%  data from 350 OS disk snapshots,

%The above analysis is only an estimation of OS and software related common data, 
%some user installed software may not be discovered by this method because they are not 
%included in the base image. However, as we can see in the next section, 
%the overall duplication of user generated data
%follows the Zipf-like distribution, thus all popular data can be discovered by statistic analysis.

%Zipf's law has been shown to characterize use of words in a natural language, city populations, 
%popularity of website visits and other internet traffic data.

%Here we present the first fully consistent empirical study showing that data duplication
%pattern in very large scale storage follows Zipf-like distribution. More specifically,
%we show that the duplication count of any unique data block is inversely proportional to its rank
%in the frequency table, with $\alpha$ smaller than unity. 
%As far as we know, this is the first study of large scale real user data to disclose
%the Zipf-like distribution pattern in data storage area.

%\subsubsection{The model}
%Consider a general storage system that holds user's files without any deduplication. 
%Let $N$ be the total number of unique data blocks after 
%content-defined chunking and deduplication, 
%$C_N(i)$ be the number of duplicate copies that the $i$th data block being
%stored in storage, given all the unique data blocks be ranked in order of their number of duplicate copies.
%Let $S_i$ be the size of $i$th block,
%then the actual ranking of the $i$th block is reflected by $\sum_{1}^{i-1}S_i$.

%\subsubsection{Methodology}
%1323 users' virtual data disks were scanned using TTTD content-defined chunking, and we performed global perfect deduplication 
%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
%and maximum block size, all variable-sized blocks are compared by their SHA-1 hash arther than real data.
%
%We choose user's data disks rather than OS disks in thie experiment for several reasons: First, the data in OS disks are 
%instinctively highly similar, because most of the VM users only make some common or unique but tiny changes to their OSes,
%so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
%Second, the data disks are way more important in terms of data safty and backup because they are 
%what users really care about.

\comments{
\subsection{Discussion}
By storing the hash index of a small set of hottest data (CDS), we expect to achieve great 
deduplication effect with minimal cost.
But one problem of the CDS is what we called \emph{blind spot}: the update of CDS is always 
behind new data's arrival,
as a result, some data must have been written to the backup store before being collected into CDS, thus such 
duplication may comprise the effect of
CDS. For instance, when a MySQL update is released, some users may apply it very quickly, so the new hot data bring by
this update will not be filtered by CDS. Only until later our CDS update includes those new data, then the rest of MySQL users get benefited.
We can take a few measurements to reduce the impact of blind spot. First, the data in blind spot will not accumulate, because snapshots backup
is a paid service, so over the long term, data in blind spot will be removed from backup store as VMs and old snapshots keep being deleted.
Second, for the major OS updates, we can anticipate them in advance by putting the new hot data into CDS before users widely adopt them.

Another problem associated with CDS is that some data in CDS may no longer be popular or even disappear
as time goes. For example, an MySQL software update may invalidate some data that we previously hold in 
the CDS. If some data blocks in CDS are no longer referenced, our map-reduce process is able to detect
this situation, so invalid data will be removed and new data will be added during the next CDS update. 
But if some users choose to keep their old MySQL version, then the corresponding old and new data will co-exist in the CDS.
}

%In our snapshot deduplication architecture, CDS is the key to achieve greater deduplication than
%incremental backup solutions. Our basic assumption of CDS us that VM disks, especially OS disks,
%have huge amount of data in common, and such common data can be represented by a relatively smaller data set
%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
%the effectiveness of CDS using real user VM disks from our production VM cluster.

\subsection{A comparison of perfect and CDS-based deduplication }
%Figure~\ref{fig:pd} shows the compression ratio of perfect deduplication at different dataset sizes
%as we vary the data size from about 4 terabytes to about 23.5 terabytes.
After level-1 and level 2 elimination, our experiment shows that 
the full deduplication would reduce the storage  further   by  45\% to 53\% of user disk space. 
If we put all these unique data into CDS, we could achieve full deduplication,
but the CDS size is not affordable. So we evaluate how much space saving of 
deduplication can be achieved when varying the CDS size.
%\begin{figure}
%  \centering
%  \epsfig{file=images/dedup_ratio.eps, height=2in, width=2.66in}
%  \caption{Perfect deduplication on data disks}
%  \label{fig:pd}
%\end{figure}

%We rank unique data blocks by their duplication count, and choose the hottest blocks as CDS. 
Figure \ref{fig:datacdssize} shows the relationship between CDS cache size and relative space saving ratio
compared to the full deduplication.  The unit of CDS size is gigabytes.
We define \emph{space saving ratio} as the space saving of the CDS method divided by 
full deduplication saving ratio. 
With a small amount of CDS data can still  accomplish more than 50\% of what perfect deduplication can do.
%But this effect decreases when more data are added to CDS. 
%The lower bound of CDS space saving ratio is 50\%, which is very easy to accomplish.

\begin{figure}
  \centering
  \epsfig{file=images/uniquedata-saving.eps, width=3in}
  \caption{Relative ratio of space size compared to full deduplication when CDS size changes.}
  \label{fig:datacdssize}
\end{figure}

CDS size is restricted by system memory resource.
Figure \ref{fig:datacds} shows how CDS space saving is affected by the system scale in terms of
the dataset size. 
In this experiment we first set out a goal of space saving ratio, 
then watch how much data needs to be placed in CDS cache to achieve this goal.
From the graph we can see a 75\% saving goal lead to a stable ratio between 
CDS size and data size, which requires 0.01\% of data to be put in CDS.

Base on above data we can estimate the size of data CDS and its effect. 
Currently we prepared 500MB memory per machine to store CDS meta, then it can represent 50GB of data. 
If we assume each VM has 30GB of user data at runtime, and we host 25 VMs per machine, 
 maintain 10 snapshots per VM, each brings 10\% additional modified data. 
Thus the user data in snapshot system is 1.5TB per machine. So the upper bound of 
$CDS size/ Data size = 0.033$, which is sufficient for the 75\% saving goal.

\begin{figure}
  \centering
  \epsfig{file=images/cds_scale.0.7.eps, width=3in}
  \caption{The relative size ratio of  CDS over the data size. }
  \label{fig:datacds}
\end{figure}

%Unlike the CDS of OS disks which is mainly composed of OS related data thus highly predictable, 
%data disks is unpredictable because we cannot control what user can put in there. But we still
%suspect that highly duplicated data in existing data are very likely to be duplicated again.
%So we randomly pick 50 out of 1322 data disks as the new data, and use the rest as existing data
%to extract CDS. Using 1.5\% as CDS threshold, we see the total 1198GB of new data is reduced by 
%755.8GB, while perfect deduplication can reduce 1017.4GB. So 74.3\% of duplicate blocks are eliminated 
%by pre-trained CDS, which is quite satisfactory.

### 2012-02-29 vm_snapshot_sim/2012intro.tex
Tao

\section{Introduction}

%1.how virtual machines work on storage
%2.cow and why they are not good
%3.introduce dedup
%1

%Virtualization is the engine behind many popular cloud computing platforms.
%Amazon, Alibaba,  and many others have provided public VM clouds that host 
%tens of thousands of  virtual machines(VM) dynamically created
%for various active users. 
%In the  case of Alibaba cloud service, the sevice is called Aliyu, which
%provides the largest public cloud in based on the open-source Xen technology.
In a virtualized cloud environment such as ones provided by Amazon EC2 and  Alibaba Aliyun,
each instance of a guest operating system runs on a virtual machine, accessing
virtual disks represented as virtual disk image files  in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
Because these image files are stored as regular files from the external point of view,
backing up VM's data is mainly done by taking snapshots of virtual disk images.

A snapshot preserves the data of a VM's file system at a specific point in time. 
VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
%Even though the snapshots are saved incrementally, 
%when deleting a snapshot, only the data not needed for any other snapshot is removed. 
%So regardless of which prior snapshots have been deleted, all active snapshots will contain 
%all the information needed to restore the virtual disk.
%Snapshots can also be shared to instantiate multiple new virtual disks, such that user can make
%duplicate VMs with exact the same disk state. This feature is especially useful when a user wants to run
%an application on multiple VMs, for example Hadoop or MPI.

Frequent  backup of VM snapshots increases  the reliability of VM's hosted in a cloud.
For example, Aliyun, the largest cloud service provided by Alibaba in China, 
provides automatic frequent backup of VM images to strengthen the reliability of its service for all users.
The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
Using a backup service with full deduplication support~\cite{venti02,bottleneck08,extreme_binning09,sparseindex09}
can identify content duplicates among snapshots to remove redundant storage content,  but the weakness is that it
either adds the  extra cost significantly or competes computing resource with the existing cloud services.
Data dependence created by duplicate relationship among snapshots
adds the complexity in fault tolerance management, especially when  VMs can migrate around in the cloud.

Unlike the previous work dealing with general file-level backup and deduplication, our problem is focused on 
virtual disk image backup and even each virtual disk is viewed as a file logically, its size is very large.
On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud everyday. 
Thus our objective is to exploit the characteristics of VM snapshot data and
pursue a cost-effective solution with the following two aspects.
First,   VM snapshot backup should only use a minimal amount of system
resource so that most of resource is allocated for regular cloud system services or applications.
Second, VM snapshot backup should be  decentralized and localized as much as possible.
That brings the benefits for increased parallelism  and fault isolation.

With these in mind, we  have developed a decentralized multi-level solution to conduct 
segment-level  and block-level  within each VM to localize deduplication when possible.
It then makes global inter-VM deduplication efforts by using a small number of
popular common data blocks.  Our study shows that there are a larger number
of popular common content  blocks shared by many users while they only take
a small amount of resource for global deduplication. 
Leveraging popular blocks makes the fault tolerance management easier while
it can still effectively accomplish a significant percentage of inter-VM  deduplication
compared to a full deduplication algorithm. 
%Restricting the scope of global deduplication reduces
%the inter-component  data dependenc during machine failure.

%Several operations are provided for creating and managing snapshots and snapshot trees,
%such as create snapshots, revert to any snapshot, and remove snapshots.
%VM snapshots is different from traditional file system backup from a few aspects:
%\begin{enumerate}
%\item The backup loads are heavy but resources are limited. The whole VM cluster have PBs of data and need to be backuped at daily basis, if not more frequently. But at the same time snapshot tasks must not affect the normal VM operations, which means only a tiny slice of CPU and memory can be used for this purpose.
%\item No file system semantics are provided. Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided.
%\item Snapshots can be shared between users. This does not only complicates the parent-child relationship between snapshots, but also require all snapshots be managed in a global namespace.
%\end{enumerate}

%In this paper we intorduce the deduplication scheme of snapshot storage in Aliyun's VM cloud. We exploit the 
The rest of the paper is arranged as follows. 
Section ~\ref{sect:background}
discusses on some background and related work.
Section~\ref{sect:options} discusses the requirements and  design options.
Section ~\ref{sect:arch} presents our snapshot backup architecture with multi-level selective deduplication 
Section ~\ref{sect:exper} presents  our evaluation results on the effectiveness
of multi-level deduplication for snapshot backup. 
Section ~\ref{sect:final} concludes this paper.
% talks about Aliyun's VM snapshot system and deduplication process. In section 4 we present
%the snapshot deduplication results of our real user VMs.

### 2012-03-01 vm_snapshot_sim/2012intro.tex

@@
 On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud everyday. 
+One key requirement we face at Alibaba Aliyun is that VM snapshot backup should only use a minimal amount of system
+resource so that most of resource is allocated for regular cloud system services or applications.
 Thus our objective is to exploit the characteristics of VM snapshot data and
-pursue a cost-effective solution with the following two aspects.
-First,   VM snapshot backup should only use a minimal amount of system
-resource so that most of resource is allocated for regular cloud system services or applications.
-Second, VM snapshot backup should be  decentralized and localized as much as possible.
-That brings the benefits for increased parallelism  and fault isolation.
+pursue a cost-effective deduplication solution. 
+Another goal  is to decentralize VM snapshot backup and  localize  deduplication as much as possible,
+which brings the benefits for increased parallelism  and fault isolation.
 

### 2012-03-01 vm_snapshot_sim/2012arch.tex
Tao

@@
 implemented using Memcached~\cite{memcached} to leverage the aggregated memory in a cluster.
-Th usage of memory for each machine is small and thus  this scheme  does not
+Th usage of memory at each machine is small and thus  this scheme  does not
 lead to  a memory resource contention with the existing cloud services.
@@
 
-Thus our CDS selection strategy is designed as follows.
+As the number of VMs increases, the popularity of common blocks for data disks changes.
+But this increase has a small impact on OS block popularity because 
+there are a limited number of OS releases used by VMs. We let CDS cover the common OS blocks first and
+our CDS selection strategy is designed as follows.
 \begin{itemize}
@@
 Our experiment data shows that about 
-100GB data ($25\times 10^6$\cite{BAD}) from 7 most popular OS releases
-can cover over 70\% of OS snapshots and the index of these 100GB OS data blocks
-only takes about total 800MB in the CDS index and then memory requirement per node for running the backup
-on  100 nodes is tiny.
-We expect in practice the OS CDS index may grow up to 2GB in order to cover large varieties  of commonly deployed
+100GB data from 7 most popular OS releases
+can at least cover over 70\% of OS snapshots and the index of these 100GB OS blocks
+only takes about total 1GB in the CDS index and then memory requirement per node for running the backup
+on  a large cluster is tiny.
+We expect that the OS CDS index may grow up to 2GB in order to cover large varieties  of commonly deployed
 OS releases in practice.
@@
 the  most popular items are selected. As discussed in Section~\ref{sect:exper}, 
-about $10^7$ (???) most popular items
-can cover about 37\% of content blocks appeared in various snapshots after level 1 and level deduplication.  
+that about 1\% of data blocks are selected based on their duplicate counts and these popular blocks
+can cover about 38\% of data  blocks appeared in various snapshots after level 1 and level deduplication.  
+The memory size per node used for CDS is within 150MB.
 \end{itemize}
+Thus in total the CDS index size per node takes less than 160MB in a large cluster bigger than 100 nodes based on
+Aliyun's experiment data, covering over 53\% of blocks in OS and data disks after inner VM deduplication.
+This memory usage is well below the limit required by Aliyun.
 

### 2012-03-01 vm_snapshot_sim/2012background.tex
Tao

@@
 Thus  it is not easy to accept any backup behavior that affects VMs performance or stability of active users.  
+At Aliyun, it is required that while CPU and disk usage should be  small or modest during backup time,
+the memory footprint of deduplication should not exceed 1\% of memory at each node, which is about 480MB.
 
@@
 But a  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with the existing cloud,
-which is not preferred for cloud production system operation. 
+which is not preferred for cloud production system operation. Thus it is desirable that backup for all nodes
+can be conducted in parallel and any centralized or  cross-machine communication for
+deduplication should not become a bottleneck.
 %As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
@@
 %block-level copy-on-write and compare-by-value techniques.
+
 Even approximation~\cite{extreme_binning09,sparseindex09} can be used to reduce memory requirement,  

### 2012-03-01 vm_snapshot_sim/2012eval.tex
Tao

@@
 Each bar in the Y axis shows the data size after deduplication divided by the original data size.
-Level-1 elimination can reduce the data size to 22\% of original data, namely it delivers close 80\% reduction.
+Level-1 elimination can reduce the data size to about 22\% of original data, namely it delivers close 78\% reduction.
 Level-2 elimination applied after level 1
-reduces the size further to 16\% of original size, namely it delivers additional 6\% reduction.
+reduces the size further to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
 Level-3 elimination together with level 1 and 2
-reduces the size further to 9\% of original size, namely it delivers additional 7\% reduction.
+reduces the size further to 8\% of original size, namely it delivers additional 10.5\% reduction.
 Level 2 elimination is more visible in OS disk than data disk, because data change frequency is really small
-when we sample last 10 snapshots of each user in 10 days. Nevertheless, the average impact of level 2 is also significant.
-A 6-7\% of reduction from the original data represents about 600-700TB of space.
+when we sample last 10 snapshots of each user in 10 days. Nevertheless, the overall impact of level 2 is still significant.
+A 4.5\% of reduction from the original data represents about 450TB space saving for a 1000-node cluster.
 
@@
 
-Overall speaking, inner   VM deduplication or  CDS-based deduplication
-can work well alone, but by combining them together we get a fairly good and stable deduplication ratio to 
-all kind of OSes. 
-Compared to a traditional dirty bit approach based on pages of
-each file (e.g. segment in our scheme),
-our CDS-based level 3 approach  can save additional 50\% storage space because many of level 2 block
-content can be eliminated using the CDS also.
+%Overall speaking, inner   VM deduplication or  CDS-based deduplication
+%can work well alone, but by combining them together we get a fairly good and stable deduplication ratio to 
+%all kind of OSes. 
+%Compared to a traditional dirty bit approach based on pages of
+%each file (e.g. segment in our scheme),
+%our CDS-based level 3 approach  can save additional 50\% storage space because many of level 2 block
+%content can be eliminated using the CDS also.
 
@@
 
-Figure~\ref{fig:OSdatacoverage} shows the cumulative coverage  ratio of  popular common OS blocks. 
-From both graphs, a small number of most popular common blocks can coverage a large percentage of 
-snapshot blocks and thus the size of CDS can be chosen to be small while still having a large
-coverage. 
-% with $\alpha$ close to 0.78.
-%A tiny hottest fraction of data lead to majority of data duplication, as a result, we can target at this small set of commonly seen data
-%to design our fast and lightweight deduplication process, just like what people did in CDN and web proxy.
+%Figure~\ref{fig:OSdatacoverage} shows the cumulative coverage  ratio of  popular common OS blocks. 
+%From both graphs, a small number of most popular common blocks can coverage a large percentage of 
+%snapshot blocks and thus the size of CDS can be chosen to be small while still having a large
+%coverage.
 
-\begin{figure}
-\centering
-%\epsfig{file=images/cdf.os.v4.eps, width=3in}
-%\epsfig{file=images/cdf.os.v4.eps, width=3in}
-\epsfig{file=images/ay41a_small.os_incremental.cdf.eps, width=3in}
-\caption{ Cumulative  coverage of popular common OS disk blocks.}
-\label{fig:OSdatacoverage}
-\end{figure}
+%\begin{figure}
+%\centering
+%\epsfig{file=images/ay41a_small.os_incremental.cdf.eps, width=3in}
+%\caption{ Cumulative  coverage of popular common OS disk blocks.}
+%\label{fig:OSdatacoverage}
+%\end{figure}
 
@@
 
-The selection of CDS is completed by separating OS disk and data disk.
-While block commonality among data disks may be affected in some degree
- when we scale up the number of total VMs  to be supported,
-we expect that  the block commonality among OS disks still remains to be high and  
-can be well covered by a fixed CDS because users still adopt common OS releases.
-To  verify this,  we examine the percentage of common  OS blocks of the same
-release in different VMs  OS releases in Figure~\ref{fig:OSunchanged}. 
+Because there are a limited number of OS releases supported by Aliyun, we study common blocks  among
+OS disks loaded with  the same OS release. 
+%The selection of CDS is completed by separating OS disk and data disk.
+%While block commonality among data disks may be affected in some degree
+% when we scale up the number of total VMs  to be supported,
+%we expect that  the block commonality among OS disks still remains to be high and  
+%%can be well covered by a fixed CDS because users still adopt common OS releases.
 %we choose 7 major OSes in Aliyun's
@@
 %disk snapshots are divided into variable-sized blocks. Then 
-We consider the earlier snapshot for each OS disk as the base image.
-For every block in the base image, 
-we classify this block as ``completely common''
+In  Figure~\ref{fig:OSunchanged},  we list a conservative  commonality study in 7 major OS versions  supported
+in Aliyun.  We consider the earlier snapshot for each OS disk as the base image.
+For every block in the base image, we classify this block as ``completely common''
 if  this block has appeared in all snapshots of the same OS release even they are used by different VMs.
 Figure \ref{fig:OSunchanged} shows that for each
-OS,  at least 70\% of OS blocks are common among all snapshots of the same OS. 
+OS,  at least 70\% of OS blocks are completely common among all snapshots of the same OS. 
 Some latest release  of OS tends to have a higher percentage of content change
@@
 
-????????????????????????????????????????????????
 Based on the above analysis, we have selected a small set of most popular
-OS blocks, which is 1.5\% of  unique OS blocks. This set
-is quite sufficient to cover the OS related blocks. 
+OS blocks, which is about 100GB OS data and its corresponding CDS index takes about 1GB memory space in total.
+They can cover sufficiently over 70\% OS blocks.
+
 %Then we use this CDS to run the deduplication process again.
-That correspond to about  80GB of OS blocks and its corresponding CDS meta occupies 800MB in the cache.
+%That correspond to about  80GB of OS blocks and its corresponding CDS meta occupies 800MB in the cache.
 %  data from 350 OS disk snapshots,

### 2012-03-01 vm_snapshot_sim/2012arch.tex
tao

@@
 consists of from hundreds to thousands of physical machines, each of which can
-host tens of VMs. A few varieties of mainstream OS are supported,
-including several editions of Windows Server, major Linux distributions, and FreeBSD.
+host tens of VMs. A few varieties of mainstream OS are supported.
+%including several editions of Windows Server, major Linux distributions, and FreeBSD.
 During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
@@
 image files such that they are located on the same physical machine of VM instance.
+During snapshot backup, concurrent disk write is logged 
+so that each snapshot can have a   consistent version.
 
@@
 
-With Aliyun's distributed file system support, the snapshot store operates a few \emph{append-only} files
-in the underline file storage. Each virtual disk has its own data store, all data 
+With Aliyun's distributed file system support, the snapshot store operates 
+\emph{append-only} files. Each virtual disk has its own data store, all data 
 blocks after deduplication will be stored into that system.
@@
 lead to  a memory resource contention with the existing cloud services.
-For example, in our current implementation setting at Aliyun, we use up to  150MB memory per node during night backup
-including CDS and other metadata for all levels of deduplication. Most of memory resource (48GB per node 
-in our experiment) is used for existing  applications.
-Each CDS content data stored  in the distributed file system
+%For example, in our current implementation setting at Aliyun, we use up to  150MB memory per node during night backup
+%including CDS and other metadata for all levels of deduplication. Most of memory resource (48GB per node 
+%in our experiment) is used for existing  applications.
+CDS raw data stored  in the distributed file system
 has multiple copies in different machines for the purpose of fault tolerance and 
@@
 containing over 1,000 VMs and each has 10 snapshots.
-Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
+
+The left part of Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
 terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
@@
 The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.
+The right part of Figure \ref{fig:zipf-data} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
+%$Y$ axis is the popularity of an OS block in a log scale 
+%measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
+%sorted by their duplicate rank.  
+For the top ranked blocks, there is a flat line in terms of duplicate counts. That
+is because there are a large number of OS blocks which have appeared in all copies of such OS releases.
 
@@
 %\epsfig{file=images/log-log.disk.eps, width=3in}
-\epsfig{file=images/datadisk.count_rank.eps, width=3in}
-\caption{Duplicate count  of common data blocks in a log scale.}
+
+\begin{tabular}{cc}
+\epsfig{file=images/datadisk.count_rank.eps, width=1.5in} &
+\epsfig{file=images/35vmos.count-rank.eps,width=1.5in}
+\end{tabular}
+
+\caption{Duplicate count  of common data blocks in a log scale on the left. The right is for common OS blocks.}
 \label{fig:zipf-data}
 \end{figure}
-Figure \ref{fig:OSpopular} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
-$Y$ axis is the popularity of an OS block in a log scale 
-measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
-sorted by their duplicate rank.  For the top ranked blocks, there is a flat line in terms of duplicate counts. That
-is because there are a large number of OS blocks which have appeared in all copies of such OS releases.
 
-\begin{figure}
-\centering
-%\epsfig{file=images/log-log.35vmos.eps,  width=3in}
-%\epsfig{file=images/35os.count_rank.eps, width=3in}
-\epsfig{file=images/35vmos.count-rank.eps,width=3in}
-\caption{ Duplicate count of  common OS blocks in a log scale.}
-\label{fig:OSpopular}
-\end{figure}
+%\begin{figure}
+%\centering
+%\epsfig{file=images/35vmos.count-rank.eps,width=3in}
+%\caption{ Duplicate count of  common OS blocks in a log scale.}
+%\label{fig:OSpopular}
+%\end{figure}
 

### 2012-03-01 vm_snapshot_sim/main.tex
tao

@@
 %\setlength{\parskip}{1ex}
+
+\newcommand{\comments}[1]{}
+
 \begin{document}
-\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
-\author{Wei Zhang, Hong Tang, Hao Jiang, Rachael Zeng, Xiaogang Li, Tao Yang}
+%\title{Selective Deduplication for VM Snapshots in Cloud Storage}
+\title{Multi-level Selective Deduplication for VM Snapshots in Cloud Storage}
+%\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
+\author{Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
+Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
+   {\normalsize $^\star$UC Santa Barbara}\\
+   {\normalsize$^\dagger$Alibaba.com}
+}
+
 \date{}
@@
 
-\input{abstract}
-\input{intro} %introduce the problem, related solutions and our requirements
-\input{cds} %data study, zipf, model of cds size and dedup efficiency
-\input{approach} %our dedup process
-\input{results}
+%need to explain: vm cloud, vm backup, dedup fundamentals, vm dedup(2 works), distributed dedup, zipf
+%need to define: requirements, design considerations, architecture
+
+\input{2012abs}
+\input{2012intro} %introduce the vm cloud, backup problem, and our requirements
+\input{2012background} %related works, related solutions, 
+\input{2012arch} %, design considerations, architecture
+\input{2012eval} %data study, zipf, model of cds size and dedup efficiency
+%\input{results}
 %\input{related}
 %\input{future}
-\input{conclusion}
+\input{2012concl}
+
+      %\setlength{\itemsep}{ex}%
+%      \setlength{\parskip}{0ex}%
+%\setlength{\itemsep}{-3mm}
+
+	%\linespread{0.3} 
+  \let\oldthebibliography=\thebibliography
+  \let\endoldthebibliography=\endthebibliography
+  \renewenvironment{thebibliography}[1]{%
+    \begin{oldthebibliography}{#1}%
+      \setlength{\parskip}{-0.02ex}%
+      \setlength{\itemsep}{-0.02ex}%
+      \setlength{\baselineskip}{-0.02ex}%
+
+  }%
+  {%
+    \end{oldthebibliography}%
+  }
+{\small
 \bibliographystyle{abbrv}
-\bibliography{dedup}
+\bibliography{dedup,dedup1}
+}
 \end{document}

### 2012-03-01 vm_snapshot_sim/2012background.tex

@@
 %store and transfer large directory trees efficiently and with high reliability\cite{jumbo07}.
+\comments{
 To chunk a file, starting from the first byte, its contents as seen through a fixed-sized (overlapping) 
@@
 previously stored fingerprints. 
+}
 As data grows to be big, content chunk lookup for fingerprint comparison from disk storage
@@
 In this option, the backup system runs on an existing set of cluster machines.
-The advantage is that there is no separate and dedicated cost for backup.
 % and a distributed storage architecture for backup allows a possible exploitation of  data locality between
@@
 With these considerations in mind, we propose a decentralized backup architecture with multi-level and selective 
-deduplication. This 
-backup service is hosted   in the existing set of cloud machines and resource usage is controlled
+deduplication. This service is hosted   in the existing set of machines and resource usage is controlled
 with a minimal impact to the existing applications.
 The duplication process is first conducted among data within each VM
-and then is conducted  across VMs when needed to 
-utilize a common dataset.  
+and then is conducted  across VMs to utilize a common dataset.  
 Given the concern that searching duplicates across  VMs  is a global feature which can affect parallel performance

### 2012-03-01 vm_snapshot_sim/2012concl.tex

@@
 \label{sect:final}
-In this paper we propose and present a multi-level selective deduplication scheme for VM snapshots. 
-with minimal cost. Inner-VM deduplication localizes backup data dependence and exposes more parallelism  
-while we use  data characteristic in VM cloud backup to identify popular common data blocks
-and cover  a large percentage of snapshot content blocks wit a small amount of memory index.
-Our evaluation using Aliyun's implementation has shown that 
-level 1 and level 2 deduplication can reduce the storage need by 80\%. 
-Level 3 with small CDS memory usage can accomplish close to 44\% of what full fingerprint-based
-deduplication can do and bring additional 6\% storage reduction compared to the original data size.
-Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,
-this is about 600 terabytes.
+The main contribution of this paper is a multi-level selective deduplication scheme among VM snapshots. 
+Inner-VM deduplication localizes backup data dependence and exposes more parallelism  
+while global deduplication using a small common data set appeared in OS and data disks
+effectively  covers a large amount of snapshot blocks.
+Our evaluation using Aliyun's data has shown that 
+level 1 and level 2 deduplication can reduce the storage need by 78\% while level 2 inner 
+fingerprint comparsion contributes 4.5\%%. 
+Level 3 can add additional 10.5\% reduction and accomplish 75\% of what full fingerprint-based
+deduplication can do. Our scheme uses a very small amount of memory on each node, and leaves
+room for additional optimization we are further studying.
+%Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,
+%this is about 600 terabytes.
 

### 2012-03-01 vm_snapshot_sim/2012eval.tex

@@
 is 23.5 terabytes.
-Each VM file is  divided into a set of content blocks using
-TTTD chunking~\cite{??} with an average size of 4KB. Each segment is of size 2MB.  
+Each VM file is  divided into content blocks of
+variable sizes~\cite{similar94,rabin81} with an average size of 4KB. Each segment is of size 2MB.  
 Popularity is computed by using 90\% of dataset, which reflects our setting that the system recomputes
@@
   \centering
-  \epsfig{file=images/overall_effect.eps, width=3in}
+  \epsfig{file=images/overall_effect.eps, width=2.8in}
   \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
@@
 \centering
-\epsfig{file=images/ay41a_big.data_disk.cdf.eps, width=3in}
+\epsfig{file=images/ay41a_big.data_disk.cdf.eps, width=2.8in}
 %\epsfig{file=images/cdf.disk.v4.eps, width=3in}
@@
 \[
-\frac{ \sum_{i=1}^{i} S_i * F_i} {\mbox{Total data size}}
+\frac{ \sum_{i=1}^{i} S_i * F_i} {\mbox{Total data size}}.
 \]
+
+Thus with about 1\% of blocks on data disks, CDS can cover about 38\% of total data blocks
+appeared in in all data snapshots. CDS index uses about 150MB memory per machine.
 
@@
 full deduplication saving ratio. 
-With a small amount of CDS data can still  accomplish more than 50\% of what perfect deduplication can do.
+With a 100GB CDS data (namely 1GB CDS index) can still  accomplish about 75\% 
+of what perfect deduplication can do.
 %But this effect decreases when more data are added to CDS. 
@@
   \centering
-  \epsfig{file=images/uniquedata-saving.eps, width=3in}
+  \epsfig{file=images/uniquedata-saving.eps, width=2.8in}
   \caption{Relative ratio of space size compared to full deduplication when CDS size changes.}
@@
 CDS size is restricted by system memory resource.
-Figure \ref{fig:datacds} shows how CDS space saving is affected by the system scale in terms of
-the dataset size. 
-In this experiment we first set out a goal of space saving ratio, 
+Figure \ref{fig:datacds} shows how CDS space saving ratio
+compared to the full deduplication is affected by the dataset size. 
+The calculation is done after level 1 and level 2 deduplication.
+$X$ axis uses the data size collected  from up to 1190 VMs, which occupies about
+47 machines. 
+In this experiment we first set out a goal of space saving ratio completed, 
 then watch how much data needs to be placed in CDS cache to achieve this goal.
-From the graph we can see a 75\% saving goal lead to a stable ratio between 
-CDS size and data size, which requires 0.01\% of data to be put in CDS.
+From the graph we can see a 75\% saving ratio lead to a stable ratio between 
+CDS size and data size, which requires 1\% of data to be placed in CDS.
 
-Base on above data we can estimate the size of data CDS and its effect. 
-Currently we prepared 500MB memory per machine to store CDS meta, then it can represent 50GB of data. 
-If we assume each VM has 30GB of user data at runtime, and we host 25 VMs per machine, 
- maintain 10 snapshots per VM, each brings 10\% additional modified data. 
-Thus the user data in snapshot system is 1.5TB per machine. So the upper bound of 
-$CDS size/ Data size = 0.033$, which is sufficient for the 75\% saving goal.
+When we deal with a cluster of 1,000 nodes, we expect that using
+1\% of data disks as the CDS size can cover more what we have seen from this
+1190 VM dataset, assuming that the average behavior of every subcluster with 47 machines
+exhibits a similar commonality. 
+In addition to this, CDS for OS disks will become even more effective when
+there are more VMs sharing the same collection of OS releases. 
+%Base on above data we can estimate the size of data CDS and its effect. 
+%Currently we prepared 500MB memory per machine to store CDS meta, then it can represent 50GB of data. 
+%If we assume each VM has 30GB of user data at runtime, and we host 25 VMs per machine, 
+% maintain 10 snapshots per VM, each brings 10\% additional modified data. 
+%Thus the user data in snapshot system is 1.5TB per machine. So the upper bound of 
+%$CDS size/ Data size = 0.033$, which is sufficient for the 75\% saving goal.
 
@@
   \centering
-  \epsfig{file=images/cds_scale.0.7.eps, width=3in}
+  \epsfig{file=images/cds_scale.0.7.eps, width=2.8in}
   \caption{The relative size ratio of  CDS over the data size. }

### 2012-03-01 vm_snapshot_sim/2012abs.tex
tao

@@
 %these two kinds of data have distinct access requirements.
-In this paper, 
+%In this paper, 
 %we show that there is a large amount of duplicated data shared amongy virtual machines
@@
 This paper presents a multi-level selective deduplication  scheme which
-integrates  inner-VM and cross-VM duplicate elimination with minimal  resource impact
-to the existing cloud services.  This scheme uses popular common data to facilitate 
+integrates  inner-VM and cross-VM duplicate elimination under
+a stringent resource requirement.
+% minimal  resource impact to the existing cloud services.  
+This scheme uses popular common data to facilitate 
 fingerprint comparison while reducing the cost and it

### 2012-03-01 vm_snapshot_sim/2012arch.tex
tao

@@
 During snapshot backup, concurrent disk write is logged 
-so that each snapshot can have a   consistent version.
+so that a  consistent snapshot version  can be derived.
 
@@
 Given the separation of OS disks and data disks, we study  their characteristics separately.
-We expect that the operating system and along with popular software installations  are not frequently
+We expect that operating system blocks   along with popular software installations  are not frequently
 modified or deleted. 
@@
 sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
-The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.
 The right part of Figure \ref{fig:zipf-data} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
+These two curves exhibit that the popularity of common blocks partially follows a  Zipf-like distribution.
 %$Y$ axis is the popularity of an OS block in a log scale 
@@
 %sorted by their duplicate rank.  
-For the top ranked blocks, there is a flat line in terms of duplicate counts. That
-is because there are a large number of OS blocks which have appeared in all copies of such OS releases.
+%For the top ranked blocks, there is a flat line in terms of duplicate counts. That
+%is because there are a large number of OS blocks which have appeared in all copies of such OS releases.
 
@@
 can at least cover over 70\% of OS snapshots and the index of these 100GB OS blocks
-only takes about total 1GB in the CDS index and then memory requirement per node for running the backup
-on  a large cluster is tiny.
+only takes about total 1GB in the CDS index and then memory requirement per node 
+for duplicate search a large cluster is tiny.
 We expect that the OS CDS index may grow up to 2GB in order to cover large varieties  of commonly deployed

### 2012-03-01 vm_snapshot_sim/2012concl.tex
tao

@@
-\section{Conclusion}
+\section{Conclusions}
 \label{sect:final}
-The main contribution of this paper is a multi-level selective deduplication scheme among VM snapshots. 
+The main contribution of this paper is a multi-level selective deduplication scheme among VM 
+snapshots, using less than 0.5\% of memory per node to meet a stringent cloud resource requirement. 
 Inner-VM deduplication localizes backup data dependence and exposes more parallelism  
@@
 Our evaluation using Aliyun's data has shown that 
-level 1 and level 2 deduplication can reduce the storage need by 78\% while level 2 inner 
-fingerprint comparsion contributes 4.5\%%. 
+level 1 deduplication can reduce the storage need by 78\% while level 2 inner 
+fingerprint comparison contributes 4.5\%%. 
 Level 3 can add additional 10.5\% reduction and accomplish 75\% of what full fingerprint-based

### 2012-03-01 vm_snapshot_sim/2012eval.tex
tao

@@
 Each VM file is  divided into content blocks of
-variable sizes~\cite{similar94,rabin81} with an average size of 4KB. Each segment is of size 2MB.  
+variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
+The signature for variable-sized blocks is computed using  their SHA-1 hash. 
+Each segment is of size 2MB.  
 Popularity is computed by using 90\% of dataset, which reflects our setting that the system recomputes
@@
 %and maximum block size
-The signature for variable-sized blocks is computed using  their SHA-1 hash. 
 %OS data
@@
 
-We further study how CDS covers content blocks used in image files.
+We further study how CDS covers content blocks used in image files using 90\% of
+the collected dataset.
 Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular common user data blocks. 
@@
 Thus with about 1\% of blocks on data disks, CDS can cover about 38\% of total data blocks
-appeared in in all data snapshots. CDS index uses about 150MB memory per machine.
+appeared in in all data snapshots. The corresponding CDS index uses about 150MB memory per machine.
 
@@
 OS blocks, which is about 100GB OS data and its corresponding CDS index takes about 1GB memory space in total.
-They can cover sufficiently over 70\% OS blocks.
+They can cover sufficiently over 70\% of OS blocks.
 
@@
 
-CDS size is restricted by system memory resource.
+%CDS size is restricted by system memory resource.
 Figure \ref{fig:datacds} shows how CDS space saving ratio
@@
 The calculation is done after level 1 and level 2 deduplication.
-$X$ axis uses the data size collected  from up to 1190 VMs, which occupies about
-47 machines. 
+$X$ axis uses the data size collected  from up to 1323 VMs, which occupies about
+53 machines. 
 In this experiment we first set out a goal of space saving ratio completed, 
@@
 When we deal with a cluster of 1,000 nodes, we expect that using
-1\% of data disks as the CDS size can cover more what we have seen from this
-1190 VM dataset, assuming that the average behavior of every subcluster with 47 machines
+1\% of data disks can cover more what we have seen from this
+1323 VM dataset, assuming that the average behavior of every subcluster with 53 machines
 exhibits a similar commonality. 

### 2012-03-09 vm_snapshot_sim/2012abs.tex
updated.

@@
 hosting  reliability while  storage demand of such operations is huge.
-A dirtybit-based technique can identify unmodified data between versions 
-and full deduplication with fingerprint comparison  can remove more redundant content
-while it requires more computing resource.
+While dirtybit-based technique can identify unmodified data between versions, 
+full deduplication with fingerprint comparison  can remove more redundant content
+while it requires more computing resources.
 %with  for similarity comparison and   reliability handling.

### 2012-03-09 vm_snapshot_sim/2012background.tex
updated.

@@
 The main weakness
-is that it does not reveal content redundancy among data blocks from different files or
+is that it does not reveal content redundancy among data blocks from different snapshots or
 different VMs.
@@
 }
-As data grows to be big, content chunk lookup for fingerprint comparison from disk storage
+As data grows to be big, fingerprint lookup in such schemes
 becomes too slow to be scalable.
@@
 Several techniques have been proposed to speedup searching of duplicate 
-content~\cite{bottleneck08,extreme_binning09,sparseindex09}. For example,  
+content. For example,  
 Zhu et al.~\cite{bottleneck08} tackle it 
 by using an in-memory Bloom filter and prefetch groups of chunk IDs that are likely to be 
-accessed together with high probability. It takes significant memory resource for filtering.
+accessed together with high probability. It takes significant memory resource for filtering and caching.
 NG et al.~\cite{ NGmiddleware2011}  use  
@@
 %in extreme bining and other sparse indexing 
-to package similar content in one disk, and duplicate lookup  only searches
+to package similar content in one location, and duplicate lookup  only searches
 for chunks within files which have a similar file-level or segment-level  content fingerprints.
@@
 lookup with a tradeoff of the reduced recall ratio.
+
+One weakness the hasn't been addressed by previous solutions is that we want to isolate 
+each VM's snapshot backup as much as possible while still enjoy the benefit of deduplication.
+In large scale cloud, node faiures happen at daily basis, we don't want a problem at small scale
+to affect large amount of VMs due to data sharing.
 
@@
 \item {\em Cost consciousness.}
-There are tens of thousands of VMs running on a large-scale cloud cluster. 
-The amount of VM data to backup is huge and cost of complete backup can be prohibitively high without
-deduplication and compression support.  Thus cost minimization is required to deliver a deplorable solution.
-
-On the other hand, the computing resource allocated for backup is often very small.
-This is because snapshot data is not retrieved frequently by users and the allocation of  cluster resource
-is typically prioritized towards active services such as online web services and map-reduce jobs.
-Thus  it is not easy to accept any backup behavior that affects VMs performance or stability of active users.  
+There are tens of thousands of VMs running on a large-scale cluster. 
+The amount of data to backup is so huge such that 3rd-party solutions are generally not affordable.
+On the other hand, the computing resources allocated for snapshot service is very limited
+because VM performance has higher priority.  
 At Aliyun, it is required that while CPU and disk usage should be small or modest during backup time,
-the memory footprint of deduplication should not exceed 1\% of memory at each node, which is about 480MB.
+the memory footprint of snapshot service should not exceed 500MB at each node.
 
@@
 \item {\em Fast backup speed.}
-The snapshot  backup  operations need to be completed quickly  every day (e.g. 1-2 hours ). 
-Often a cloud service has  few hours of light workload each day (e.g. midnight),  which creates an opportunity  for backup.
-But a  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with the existing cloud,
-which is not preferred for cloud production system operation. Thus it is desirable that backup for all nodes
+Often a cloud has a few hours of light workload each day (e.g. midnight),  which creates an small window for automatic backup.
+%But a  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with the existing cloud,
+%which is not preferred for cloud production system operation. 
+Thus it is desirable that backup for all nodes
 can be conducted in parallel and any centralized or  cross-machine communication for
@@
 \item {\em Fault tolerance.}
-The addition of a backup service should not decrease the degree of
-fault tolerance.  If data failure in  a backup service  affects many users,  such a solution is not desirable.
+The addition of data deduplication should not decrease the degree of
+fault tolerance. It's not desirable that small scale of data failure affects the backup of many VMs.
 %when users access snapshots in a recovery process. 

### 2012-03-09 vm_snapshot_sim/2012intro.tex
updated.

@@
 each instance of a guest operating system runs on a virtual machine, accessing
-virtual disks represented as virtual disk image files  in the host operating system.
+virtual hard disks represented as virtual disk image files in the host operating system.
 %virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
@@
 Frequent  backup of VM snapshots increases  the reliability of VM's hosted in a cloud.
-For example, Aliyun, the largest cloud service provided by Alibaba in China, 
+For example, Aliyun, the largest cloud service provider by Alibaba in China, 
 provides automatic frequent backup of VM images to strengthen the reliability of its service for all users.
 The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
-Using a backup service with full deduplication support~\cite{venti02,bottleneck08,extreme_binning09,sparseindex09}
+Using a backup service with full deduplication support~\cite{venti02,bottleneck08}
 can identify content duplicates among snapshots to remove redundant storage content,  but the weakness is that it
 either adds the  extra cost significantly or competes computing resource with the existing cloud services.
-Data dependence created by duplicate relationship among snapshots
+In addition, data dependence created by duplicate relationship among snapshots
 adds the complexity in fault tolerance management, especially when  VMs can migrate around in the cloud.
@@
 Unlike the previous work dealing with general file-level backup and deduplication, our problem is focused on 
-virtual disk image backup and even each virtual disk is viewed as a file logically, its size is very large.
+virtual disk image backup. Although we treat each virtual disk  as a file logically, its size is very large.
 On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud everyday. 
 One key requirement we face at Alibaba Aliyun is that VM snapshot backup should only use a minimal amount of system
-resource so that most of resource is allocated for regular cloud system services or applications.
+resources so that most of resources is kept for regular cloud system services or applications.
 Thus our objective is to exploit the characteristics of VM snapshot data and
@@
 
+%,extreme_binning09,sparseindex09
+By observations on the VM snapshot data from production cloud, we found snapshot data duplication 
+can be easily classified into two categories: \emph{inner-VM} and \emph{cross-VM}. Inner-VM duplication
+exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
+On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries: 
+there are only two type of OSes (Linux and Windows), most users either uses MySQL or MS SQL Server as their database.
+As the result, different VMs tend to backup large amount of highly similar data.
+
 With these in mind, we  have developed a decentralized multi-level solution to conduct 
-segment-level  and block-level  within each VM to localize deduplication when possible.
-It then makes global inter-VM deduplication efforts by using a small number of
-popular common data blocks.  Our study shows that there are a larger number
-of popular common content  blocks shared by many users while they only take
-a small amount of resource for global deduplication. 
-Leveraging popular blocks makes the fault tolerance management easier while
-it can still effectively accomplish a significant percentage of inter-VM  deduplication
-compared to a full deduplication algorithm. 
+segment-level  and block-level inner-VM  deduplication to localize the deduplication effort when possible.
+It then makes cross-VM deduplication by excluding a small number of
+popular common data blocks from being backed up. Our study shows that common data blocks
+occupy significant amount of storage space while they only take
+a small amount of resources to deduplicate.
+Seperating deduplication into multi levels effectively accomplish the major space saving goal
+compare the global complete deduplication scheme, at the same time it makes
+the backup of different VMs to be indepdent for better fault tolerance.
+
 %Restricting the scope of global deduplication reduces

### 2012-03-10 vm_snapshot_sim/2012arch.tex
small change.

@@
 consists of from hundreds to thousands of physical machines, each of which can
-host tens of VMs. A few varieties of mainstream OS are supported.
-%including several editions of Windows Server, major Linux distributions, and FreeBSD.
+host tens of VMs.
+
+A GFS-like distributed file system holds the responsibility of managing physical disk storage
+in the cloud. All data needed for VM services, which include runtime VM disk images and snapshot backup data,
+reside in this distributed file system.
 During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
@@
 disks is tunneled by the virtual device driver (called TapDisk at Xen). To avoid network latency and congestion, 
-Aliyun's distributed file system carefully selects the location of primary replica of VM's 
-image files such that they are located on the same physical machine of VM instance.
+our distributed file system place the primary replica of VM's 
+image files at physical machine of VM instance.
 During snapshot backup, concurrent disk write is logged 
-so that a  consistent snapshot version  can be derived.
+to ensure a consistent snapshot version is captured.
 
-Figure~\ref{fig:arch} shows the architecture view of snapshot service with selective deduplication
+Figure~\ref{fig:arch} shows the architecture view of our snapshot service
 at each node. The snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
-In accomplishing such a function, this broker accesses  the snapshot store managed by the underlying distributed file
-system.  The inner VM  deduplication is conducted by the broker to access meta data in the snapshot data store
+The inner-VM  deduplication is conducted by the broker to access meta data in the snapshot data store
 and we discuss this in details in Section~\ref{sect:innerVM}.
-The inter-VM deduplication is conducted by the broker to access a  common data block set (CDS) across multiple VMs.
-The CDS hash index is stored in the distributed memory cache.
+The cross-VM deduplication is conducted by the broker to access 
+a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
+whose block hash index is stored in a distributed memory cache.
 
@@
 
-The snapshot store  residing in the distributed file system
+The snapshot store 
 supports data access operations such as \emph{get}, \emph{put} and \emph{delete}.
 Other operations include data block traverse and resource usage report.
-Snapshots are stored  in our distributed file system, just like regular virtual data files. 
-A key  difference is that snapshot storage does not need to be
-co-located within VM instances and  in fact they can even live in a different cluster to improve the 
-data reliability. When a computing cluster is not available, we are still able to  restore users' VMs from another cluster which
-contains snapshot backup and run these VMs. 
+The snapshot data does not need to be
+co-located with VM instances, and in fact they can even live in a different cluster to improve the 
+data reliability: when one cluster is not available, we are still able to restore its VMs from another cluster which
+holds its snapshot data. 
 %to reduce the impact to our users.
@@
 
-With Aliyun's distributed file system support, the snapshot store operates 
-\emph{append-only} files. Each virtual disk has its own data store, all data 
-blocks after deduplication will be stored into that system.
-Since all the underline data structures is append only,
-upon a delete request, the corresponding data will only be marked rather than being deleted.
-A compaction will take place when deleted data has accumulated to a certain threshold, thus 
-reclaiming the disk space .
+Under the hood of snapshot store, it organizes and operates snapshot data 
+in the distributed file system. We let each virtual disk has its own snapshot store, 
+and no data is shared between
+any two snapshot stores, thus achieve great fault isolation. For those selected popular data
+that shared by many VM snapshot stores, we could easily increase its availability by having more replications.
+%Since all the underline data structures is append only,
+%upon a delete request, the corresponding data will only be marked rather than being deleted.
+%A compaction will take place when deleted data has accumulated to a certain threshold, thus 
+%reclaiming the disk space .
 
@@
 %inside the block store. Second, 
-Such localization increases data independence between different  VM backups,
+Such localization increases data independency between different  VM backups,
 simplifies  snapshot  management and statistics collection during VM migration and termination,
@@
 These blocks are of variable-size, partitioned using
-the standard chunking technique~\cite{similar94}.  We use 4KB as the average block size. 
-The segment metadata (called segment recipe) records its  content block hashes and  data reference. 
-The snapshot-level recipe contains a set of  segment recipes and other meta data information.
+the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
+%To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
+Segment metadata (called segment recipe) records its  content block hashes and data pointers. 
+The snapshot recipe contains a list of segments and other meta data information.
 \begin{itemize}
 \item {\em Level 1 Segment modification  detection}.
-If a segment is not changed, indicated by a dirty bit, its content blocks are not changed also. In this case,
- segment-level duplicate detection is more efficient than the block level.
+If a segment is not changed, indicated by a dirty bit embedded in the virtual disk driver, its content blocks are not changed as well, thus its segment recipe can be simply reused.
+Operations at this level have almost no cost and most of unmodified data are filtered here.
 
 \item {\em Level 2  Block fingerprint comparison.}
-If a segment is modified, content blocks of this segment are compared with 
-the fingerprints of the existing content blocks within the same segment in
-the previous version of this snapshot (called parent  snapshot). Partial duplication
+If a segment is modified, we perform fine-grained deduplication using content blocks of this segment to compared with 
+the same segment in
+the previous snapshot (also called parent snapshot). Partial duplication
 within the segment can be detected and eliminated. 
@@
 
-We choose this two-level structure because in practice we observe that at each snapshot there are a large
-number of content blocks which are not modified from one snapshot version to another.
-Aggregating a large number of content blocks as one segment can significantly
+We choose this two-level structure because in practice we observe that during each backup period only a small amount
+of VM data are added or modified. As the result, even the meat data of two snapshots can be highly similar,
+thus aggregating a large number of content blocks as one segment can significantly
 reduce the space cost of snapshot meta data. 
@@
 For Aliyun, each VM image file is represented as a virtual disk file format
-(called \emph{vhd} at Xen) and we use a dirty bit to capture if a page (or segment) of a virtual snapshot file 
-has been modified or not for segment-level deduplication.
+(called \emph{vhd} at Xen) and we use a dirty bit to capture if a page (or segment) of a virtual disk file 
+has been modified or not to ease the segment-level deduplication.
 %This is effective because  
@@
 \subsection{Cross-VM Deduplication with CDS}
+\label{sect:crossVM}
 
-The third-level of deduplication is to identify duplicated data blocks among multiple VMs through the index cache
+The level-3 deduplication is to identify duplicated data blocks among multiple VMs through the index cache
 of common data set (CDS).  CDS is the most popular content blocks 
-among  recent snapshots across all VMs. 
+among snapshots across all VMs. 
 Each index entry contains  the block fingerprint and a reference pointer to the location of its real content
-in the snapshot content block store residing in the underlying distributed file system.
+in the snapshot content block store.
 %The structure of CDS meta is not different from the segment recipe we discussed above, 
@@
 There are two advantages to exploit this.
-First, a smaller CDS reduces overall resource requirement while covering  most of data blocks in snapshots.
-Second a smaller CDS makes the fault tolerance management  easier because we can replicate  more copies
-to mitigate the failure.
+First, a smaller CDS reduces overall resource requirement while covering most of data duplication.
+Second, knowing this small set of data is shared heavily makes the fault tolerance management 
+easier because we can replicate more copies to mitigate the failure.
 
@@
 \centering
-%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
+\epsfig{file=images/vector.eps, width=3.2in}
 %\epsfig{file=images/log-log.disk.eps, width=3in}
 
-\begin{tabular}{cc}
-\epsfig{file=images/datadisk.count_rank.eps, width=1.5in} &
-\epsfig{file=images/35vmos.count-rank.eps,width=1.5in}
-\end{tabular}
+%\begin{tabular}{cc}
+%\epsfig{file=images/datadisk.count_rank.eps, width=1.5in} &
+%\epsfig{file=images/35vmos.count-rank.eps,width=1.5in}
+%\end{tabular}
 
-\caption{Duplicate count  of common data blocks in a log scale on the left. The right is for common OS blocks.}
+\caption{Number of duplicates vesus ranking}
 \label{fig:zipf-data}
@@
 \begin{itemize}
-\item First, most popular items from OS disks are selected.
+\item First, most popular items from OS disks are selected as the initial CDS.
 Our experiment data shows that about 
@@
 OS releases in practice.
-\item Second, the degree of duplication is computed for snapshot blocks of data disks and
+\item Second, the degree of duplication is computed for the rest of blocks in snapshot store, and
 % and also snapshot 
@@
 Thus in total the CDS index size per node takes less than 160MB in a large cluster bigger than 100 nodes based on
-Aliyun's experiment data, covering over 53\% of blocks in OS and data disks after inner VM deduplication.
-This memory usage is well below the limit required by Aliyun.
+Aliyun's experiment data, covering over 53\% of blocks in OS and data disks after inner-VM deduplication.
+This memory usage is well below the limit required by our VM services.
 
@@
   \centering
-  \epsfig{file=images/dedup_flow1.eps, height=2in, width=4in}
+  \epsfig{file=images/dedup_flow1.eps, height=2in, width=3.5in}
   \caption{Illustration of snapshot deduplication dataflow.}
@@
 if a data block cannot be found in the CDS index, this block is considered to be a new block
-and such a block is to be saved in the snapshot block store and  the returned reference  pointer is
+and such a block is to be saved in the snapshot block store and  the returned data pointer is
 saved in the  segment recipe.
 \item {\em Save recipes.} Finally the  segment recipes are saved in the  snapshot block store also.
- After all segment recipes are saved, the snapshot recipe is complete and can be saved also.
+ After all segment recipes are saved, the snapshot recipe is complete and can be saved finally.
 \end{enumerate}
@@
 only CDS-based checkup will be conducted. 
+Most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
+at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.
 %This is important because most of the cross-VM duplication, such as OS related data and popular software data, is eliminated

### 2012-03-10 vm_snapshot_sim/2012background.tex
small change.

@@
 
-One weakness the hasn't been addressed by previous solutions is that we want to isolate 
-each VM's snapshot backup as much as possible while still enjoy the benefit of deduplication.
-In large scale cloud, node faiures happen at daily basis, we don't want a problem at small scale
-to affect large amount of VMs due to data sharing.
-
 \section{Requirements and Design Options}
@@
 There are tens of thousands of VMs running on a large-scale cluster. 
-The amount of data to backup is so huge such that 3rd-party solutions are generally not affordable.
+The amount of data is so huge such that backup cost must be controlled carefully.
 On the other hand, the computing resources allocated for snapshot service is very limited
@@
 even such a  backup service may only use  a fraction of the existing disk storage, 
-fingerprint-based search does require a significant amount of memory for fast lookup of identical content chunks.
-This competes memory resource  with the existing applications.
+fingerprint-based search does require a significant amount of memory for fingerprint lookup of searching duplicates.
+This competes memory resource  with the existing VMs.
 %Decentralized deduplication is studied in ~\cite{Clements2009} and the focus is on
@@
 Even approximation~\cite{extreme_binning09,sparseindex09} can be used to reduce memory requirement,
-a  key weakness of global content fingerprint comparison is that it can affect fault isolation.
+one key weakness the hasn't been addressed by previous solutions is that global content sharing affects
+fault isolation.
 Because a content chunk is compared with a content signature collected from other users,
-this artificially creates data dependence among different cloud users.
+this artificially creates data dependency among different VM users.
 % since storage for shared identical content chunks can become a failure point.
-The loss of a common chunk can affect many users whose VM images share this 
-chunk. Adding replicas for this global dataset can enhance the availability,
-but incurs significantly more cost.
+In large scale cloud, node faiures happen at daily basis,
+the loss of a shared block can affect many users whose snapshots share this 
+data block. 
+Without any control of such data sharing, we can only increase  
+replication for global dataset to enhance the availability,
+but this incurs significantly more cost.
+
+%we want to isolate 
+%each VM's snapshot backup as much as possible while still enjoy the benefit of deduplication.
+%In large scale cloud, node faiures happen at daily basis, we don't want a problem at small scale
+%to affect large amount of VMs due to data sharing.
+%a key weakness of global content fingerprint comparison is that it affects fault isolation.
+
 %2) data sharing among users for accessing common signagutes causes the system less resilient to storage failures.
@@
 with a minimal impact to the existing applications.
-The duplication process is first conducted among data within each VM
-and then is conducted  across VMs to utilize a common dataset.  
+The deduplication process is first conducted among snapshots within each VM
+and then is conducted across VMs.  
 Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
 and complicate failure management,
-we would like to use a small common dataset while still maintaining a cost-effective deduplication ratio.
-For this purpose, we exploit the data characteristics of snapshots and only store most popular data.
+we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
+For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
+Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance.
 %

### 2012-03-10 vm_snapshot_sim/2012arch.tex
change cds size analysis.

@@
 Given the separation of OS disks and data disks, we study  their characteristics separately.
-We expect that operating system blocks along with popular software installations  are not frequently
-modified or deleted. 
+We expect that data related to OS and popular software installations are not frequently
+modified or deleted, to facilitate analysis we call them \emph{OS-related} data, 
+and the rest of data, either from OS or data disks, are called \emph{user-related} data.
 %base image data as a hint.Through users may change configurations, install software, or write user data into OS disk,
@@
 %This is verified in  Section~\ref{sect:exper}.
-We have sampled  the  popularity of common blocks in the OS and data disks from a dataset
-containing over 1,000 VMs and each has 10 snapshots.
-
-The left part of Figure \ref{fig:zipf-data} shows the duplicate count for different data blocks sorted by their ranking in 
+We have studied the popularity of common blocks in the OS and data disks from a dataset
+containing over 1,000 VMs, taking their first snapshots to watch the cross-VM duplication pattern.
+Figure \ref{fig:zipf-data} shows the duplicate count for unique data blocks sorted by their ranking in 
 terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
@@
 sorted by their duplicate rank.  The rank number 1 is the block with the highest number of duplicates.
-The right part of Figure \ref{fig:zipf-data} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
 These two curves exhibit that the popularity of common blocks partially follows a Zipf-like distribution.
@@
 
+Base on the Zipf-like distribution pattern, many previous analysis and result on web caching may apply.
+In general this indicates a small set of popular data dominates data duplication.
+Although we already know OS-related data are heavily duplicated among OS disks, 
+it still surprises us that user-related data follow a similar pattern.
+Therefore, we collect the CDS by performing global reference counting through map-reduce for all
+blocks in snapshot store, and select the most popular ones base on the memory limitation of
+CDS hash index.
+
+The CDS collected from user-related data is generally proportional to the data size.
+As discussed in Section~\ref{sect:exper}, selecting about 1\% of data (after level 1 and level 2 deduplication)
+can cover about 38\% of data blocks. Consider we allow maximum 25 VMs per machine, each VM has
+about 30GB of user-related data, having 10 snapshots in its snapshot store and the data change ratio during
+each backup is 10\%, this translates to 15GB CDS data per machine, and the 
+memory cost by CDS hash index is about 150MB per machine.
+On the other hand, the CDS from OS-related data is only relvant to the number of OS releases.
+Our experiment on 7 major OS releases shows that about 100GB of data is never modified, and we expect
+it won't grow over 200GB in the near future. So it would cost the entire cluster 2GB of memory to
+store its hash index, or 20MB per machine on a 100 node cluster. On average each OS disk has about 10GB
+of data that can be completely eliminated in this way.
+\comments{
 As the number of VMs increases, the popularity of common blocks for data disks changes.
@@
 our CDS selection strategy is designed as follows.
+
 \begin{itemize}
@@
 The memory size per node used for CDS is within 150MB.
-\end{itemize}
-Thus in total the CDS index size per node takes less than 160MB in a large cluster bigger than 100 nodes based on
-Aliyun's experiment data, covering over 53\% of blocks in OS and data disks after inner-VM deduplication.
+\end{itemize}}
+Thus in total the CDS index size per node takes less than 170MB in a large cluster bigger than 100 nodes, 
+covering over 47\% of blocks in OS and data disks after inner-VM deduplication.
 This memory usage is well below the limit required by our VM services.

### 2012-03-10 vm_snapshot_sim/2012abs.tex
small adjustment

--- 2012-03-01 vm_snapshot_sim/2012abs.tex
@@
 In a virtualized cloud computing environment, frequent  snapshot backup of virtual disks improves
-hosting  reliability while  storage demand of such operations is huge.
-A dirtybit-based technique can identify unmodified data between versions 
-and full deduplication with fingerprint comparison  can remove more redundant content
-while it requires more computing resource.
+hosting  reliability but storage demand of such operations is huge.
+While dirtybit-based technique can identify unmodified data between versions, 
+full deduplication with fingerprint comparison  can remove more redundant content
+at the cost of computing resources.
 %with  for similarity comparison and   reliability handling.

### 2012-03-10 vm_snapshot_sim/2012arch.tex
small adjustment

@@
   %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
-  \epsfig{file=images/arch.eps, width=3.5in}
+  \epsfig{file=images/arch.eps, width=3.9in}
   \caption{Snapshot backup architecture of each node.}
@@
   %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
-  \epsfig{file=images/snapshot_representation.eps,  width=3.2in}
+  \epsfig{file=images/snapshot_representation.eps,  width=3.8in}
   \caption{An example of snapshot representation.}
@@
 We have studied the popularity of common blocks in the OS and data disks from a dataset
-containing over 1,000 VMs, taking their first snapshots to watch the cross-VM duplication pattern.
+containing over 1,000 VMs, taking their first snapshots to watch the cross-VM duplication pattern 
+(scale of OS disk sampling is smaller due to performance impact to user VMs).
 Figure \ref{fig:zipf-data} shows the duplicate count for unique data blocks sorted by their ranking in 
@@
 \centering
-\epsfig{file=images/vector.eps, width=3.2in}
+\epsfig{file=images/vector.eps, width=3.8in}
 %\epsfig{file=images/log-log.disk.eps, width=3in}
@@
   \centering
-  \epsfig{file=images/dedup_flow1.eps, height=2in, width=3.5in}
+  \epsfig{file=images/dedup_flow1.eps, width=3.8in}
   \caption{Illustration of snapshot deduplication dataflow.}
@@
 As shown in Figure~\ref{fig:dedupflow} (a),
-when  a snapshot of a plain virtual disk file is being created, we first check the dirty bitmap array of
-this disk file  to see which segments are modified. If a segment is not modified since last snapshot, 
+when  a snapshot of a plain virtual disk file is being created, we first check the dirty bitmap 
+to see which segments are modified. If a segment is not modified since last snapshot, 
 it's data pointer in the recipe of the  parent snapshot  can be directly copied into 
@@
 for each dirty segment, we divide it into variable-sized blocks,
-and compare their signatures with  the corresponding segment recipe in the previous snapshot version (called parent
+and compare their signatures with  the corresponding segment recipe in the previous snapshot (called parent
 snapshot). 
@@
 \item {\em Write new snapshot blocks :}
-We continue the previous step and 
-if a data block cannot be found in the CDS index, this block is considered to be a new block
-and such a block is to be saved in the snapshot block store and  the returned data pointer is
+If a data block cannot be found in the CDS index, this block is considered to be a new block
+and such a block is to be saved in the snapshot store, the returned data pointer is
 saved in the  segment recipe.
 \item {\em Save recipes.} Finally the  segment recipes are saved in the  snapshot block store also.
- After all segment recipes are saved, the snapshot recipe is complete and can be saved finally.
+ After all segment recipes are saved, the snapshot recipe is complete and can be saved.
 \end{enumerate}
@@
 only CDS-based checkup will be conducted. 
-Most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
-at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.
+Most of the cross-VM duplication, such as OS-related data, is eliminated
+at this stage. 
+%Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.
 %This is important because most of the cross-VM duplication, such as OS related data and popular software data, is eliminated

### 2012-03-10 vm_snapshot_sim/2012eval.tex
small adjustment

@@
 
-An Aliyun cluster we target is over 1000 nodes with 16 cores and 48GB memory
-and each node hosts 25 VMs.
+An Aliyun our target is to backup cluster with 1000 nodes
+with 25 VMs on each.
 We are running our deduplication/backup  service on 100 nodes.
@@
 the CPU usage is very small during the experiments. 
-Based on the data studied,  each VM has about  40GB of storage  data usage on average
-and each of OS disk and data disk takes about 50\% of storage space.
+Based on the data studied,  each VM has about  40GB of storage  data usage on average,
+OS disk and data disk each takes about 50\% of storage space.
 The backup of VM snapshots is completed within two hours  every day,
@@
   \centering
-  \epsfig{file=images/overall_effect.eps, width=2.8in}
+  \epsfig{file=images/overall_effect.eps, width=3.5in}
   \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
@@
  %\epsfig{file=images/os_cds_sim.eps, width=3in}
-  \epsfig{file=images/3level_os.eps, width=3in}
+  \epsfig{file=images/3level_os.eps, width=3.5in}
   \caption{Impact of 3-level deduplication for OS releases.}
@@
 %\epsfig{file=images/log-log.disk.eps, width=3in}
-\epsfig{file=images/datadisk.count_rank.eps, width=3in}
+\epsfig{file=images/datadisk.count_rank.eps, width=3.5in}
 \caption{Duplicate count  of common data blocks in a log scale.}
@@
 %\epsfig{file=images/35os.count_rank.eps, width=3in}
-\epsfig{file=images/35vmos.count-rank.eps,width=3in}
+\epsfig{file=images/35vmos.count-rank.eps,width=3.5in}
 \caption{ Duplicate count of  common OS blocks in a log scale.}
@@
 \centering
-\epsfig{file=images/ay41a_big.data_disk.cdf.eps, width=2.8in}
+\epsfig{file=images/ay41a_big.data_disk.cdf.eps, width=3.5in}
 %\epsfig{file=images/cdf.disk.v4.eps, width=3in}
@@
 \centering
-\epsfig{file=images/os_subset.eps, height=2in, width=2.66in}
+\epsfig{file=images/os_subset.eps, width=3.5in}
 \caption{Percentage of completely common blocks among different VMs for the same OS release.}
@@
   \centering
-  \epsfig{file=images/uniquedata-saving.eps, width=2.8in}
+  \epsfig{file=images/uniquedata-saving.eps, width=3.5in}
   \caption{Relative ratio of space size compared to full deduplication when CDS size changes.}
@@
   \centering
-  \epsfig{file=images/cds_scale.0.7.eps, width=2.8in}
+  \epsfig{file=images/cds_scale.0.7.eps, width=3.5in}
   \caption{The relative size ratio of  CDS over the data size. }

### 2012-03-10 vm_snapshot_sim/2012intro.tex
small adjustment

@@
 exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
-On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries: 
-there are only two type of OSes (Linux and Windows), most users either uses MySQL or MS SQL Server as their database.
+On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL.
 As the result, different VMs tend to backup large amount of highly similar data.

### 2012-03-10 vm_snapshot_sim/main.tex
small adjustment

@@
-\documentclass[finalversion]{usetex-v1}
+\documentclass[conference]{IEEEtran}
 %\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
@@
 %% Define a new 'leo' style for the package that will use a smaller font.
-\makeatletter
-\def\url@leostyle{%
-  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
-\makeatother
+%\makeatletter
+%\def\url@leostyle{%
+%  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
+%\makeatother
 %% Now actually use the newly defined style.
-\urlstyle{leo}
+%\urlstyle{leo}
 %\linespread{1.2}
@@
 %\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
-\author{Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
-Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
-   {\normalsize $^\star$UC Santa Barbara}\\
-   {\normalsize$^\dagger$Alibaba.com}
+\author{
+\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Hong Tang\IEEEauthorrefmark{2}, Hao Jiang\IEEEauthorrefmark{2}, Tao Yang\IEEEauthorrefmark{1}, Xiaogang Li\IEEEauthorrefmark{2}, Rachael Zeng\IEEEauthorrefmark{2}}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}Dept. of Computer Science, UC Santa barbara. Email: \{wei, tyang\}@cs.ucsb.edu}
+\IEEEauthorblockA{\IEEEauthorrefmark{2}Alibaba Inc. Email: \{hongtang, haojiang, xiaogang, rachael\}@alibaba-inc.com}
+%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
+%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
+%   {\normalsize $^\star$UC Santa Barbara}\\
+%   {\normalsize$^\dagger$Alibaba.com}
 }
@@
 	%\linespread{0.3} 
-  \let\oldthebibliography=\thebibliography
-  \let\endoldthebibliography=\endthebibliography
-  \renewenvironment{thebibliography}[1]{%
-    \begin{oldthebibliography}{#1}%
-      \setlength{\parskip}{-0.02ex}%
-      \setlength{\itemsep}{-0.02ex}%
-      \setlength{\baselineskip}{-0.02ex}%
+%  \let\oldthebibliography=\thebibliography
+%  \let\endoldthebibliography=\endthebibliography
+%  \renewenvironment{thebibliography}[1]{%
+%    \begin{oldthebibliography}{#1}%
+%      \setlength{\parskip}{-0.02ex}%
+%      \setlength{\itemsep}{-0.02ex}%
+%      \setlength{\baselineskip}{-0.02ex}%
 
-  }%
-  {%
-    \end{oldthebibliography}%
-  }
+%  }%
+%  {%
+%    \end{oldthebibliography}%
+%  }
 {\small

### 2012-03-10 vm_snapshot_sim/2012arch.tex
final

@@
 
-Base on the Zipf-like distribution pattern, many previous analysis and result on web caching may apply.
+Base on the Zipf-like distribution pattern, many previous analysis and results on web caching may apply.
 In general this indicates a small set of popular data dominates data duplication.
@@
 about 30GB of user-related data, having 10 snapshots in its snapshot store and the data change ratio during
-each backup is 10\%, this translates to 15GB CDS data per machine, and the 
+each backup is 10\%, this translates to 15GB CDS data per machine. 
+Consider each CDS hash index entry cost about 40 bytes and the average block size is 4KB, this leads to
+a 1:100 ratio so the 
 memory cost by CDS hash index is about 150MB per machine.

### 2012-03-10 vm_snapshot_sim/2012concl.tex
final

--- 2012-03-01 vm_snapshot_sim/2012concl.tex
@@
 \label{sect:final}
-The main contribution of this paper is a multi-level selective deduplication scheme among VM snapshots. 
-Inner-VM deduplication localizes backup data dependence and exposes more parallelism  
-while global deduplication using a small common data set appeared in OS and data disks
-effectively  covers a large amount of snapshot blocks.
-Our evaluation using Aliyun's data has shown that 
-level 1 and level 2 deduplication can reduce the storage need by 78\% while level 2 inner 
-fingerprint comparsion contributes 4.5\%%. 
-Level 3 can add additional 10.5\% reduction and accomplish 75\% of what full fingerprint-based
-deduplication can do. Our scheme uses a very small amount of memory on each node, and leaves
+In this paper we propose a multi-level selective deduplication scheme for 
+snapshot service in VM cloud. 
+Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
+while cross-VM deduplication with a small common data set
+effectively  covers a large amount of duplicated data.
+Our solution accomplishes the majority of
+potential global deduplication saving while still meets stringent cloud resources requirement. 
+Evaluation using real user's VM data shows
+our solution can accomplish 75\% of what complete global
+deduplication can do. 
+Compare to today's widely-used snapshot technique, our scheme reduces almost
+two-third of snapshot storage cost.
+Our scheme uses a very small amount of memory on each node, and leaves
 room for additional optimization we are further studying.

### 2012-03-10 vm_snapshot_sim/2012eval.tex
final

@@
 
-We have implemented a snapshot deduplication scheme on the Aliyun's cloud platform.
-Our experimental evaluation has the following two objectives:
-1) Analyze the commonality of content data blocks and the popularity  of hot items. We 
-examine the impacts of CDS size on deduplication ratio.
-2) Assess the effectiveness  of 3-level deduplication for reducing the storage requirement of snapshot 
+We have implemented the snapshot deduplication scheme on the Aliyun's cloud platform.
+Objectives of our experimental evaluation are:
+1) Analyze the commonality of content data blocks and the popularity  of hot items. 
+2) Assess the effectiveness  of 3-level deduplication for reducing the storage cost of snapshot 
 backup. 
+3) Examine the impacts of CDS size on deduplication ratio.
 
@@
 
-An Aliyun our target is to backup cluster with 1000 nodes
+At Aliyun our target is to backup cluster up to 1000 nodes
 with 25 VMs on each.
-We are running our deduplication/backup  service on 100 nodes.
-Memory usage is about 150MB space per node during backup and
-the CPU usage is very small during the experiments. 
+%We are running our deduplication/backup  service on 100 nodes.
+%Memory usage is about 150MB space per node during backup and
+%the CPU usage is very small during the experiments. 
 Based on the data studied,  each VM has about  40GB of storage  data usage on average,
@@
 
-We have used a storage dataset of  1323 VM users collected from 100 Aliyun's cloud nodes to evaluate the effectiveness.
+Since it's impossible to perform large scale analysis without affecting the VM performance,
+we sampled two data sets from real user VMs to measure the effectiveness of our deduplication scheme.
+Dataset1 is used study the detail impact of 3-level deduplication process,
+it compose of 35 VMs from 7 popular OSes: 
+Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
+5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
+The overall data size for this 700 full snapshots is 17.6 TB.
+
+Dataset2 contains the first snapshots of 1323 VMs' data disks from a small cluster with 100 nodes. 
+Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
+study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
+
+All data are divided into 2 MB fix-sized segments and each segment is divided into 
+variable-sized content blocks ~\cite{similar94,rabin81} with an average size of 4KB.
+The signature for variable-sized blocks is computed using their SHA-1 hash. 
+Popularity of data blocks are collected through global counting 
+and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.
+
+\comments{
+a storage dataset of 1323 VM users collected from 100 Aliyun's cloud nodes to evaluate the effectiveness.
 In this dataset, there are 10 snapshots per each VM user and the total amount of space investigated 
@@
 CDS every 1-2 days to catch up the popularity trend.
-
+}
 %seg, and we performed global perfect deduplication 
@@
 
-Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication.
-The X axis shows the overall impact in (a),  impact on OS disk in (b), and impact on data disk in (c).
+Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication on dataset1.
+The X axis shows the overall impact in (a),  impact on OS disks in (b), and impact on data disks in (c).
 Each bar in the Y axis shows the data size after deduplication divided by the original data size.
 Level-1 elimination can reduce the data size to about 22\% of original data, namely it delivers close 78\% reduction.
-Level-2 elimination applied after level 1
+Level-2 elimination is applied to data that could pass level-1, it
 reduces the size further to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
@@
 
-To see the impact of multi-level deduplication on different OS releases, we choose 7 major OSes in Aliyun's
-VM cloud platform and they are: 
-Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
-distributions are 64 bits).
-Then we examine 5 VM user disks from each OS, and 10 snapshots for each VM. These VMs have been actively used by their
-owners. 
+%To see the impact of multi-level deduplication on different OS releases,
 %Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
 Figure~\ref{fig:oscds} shows the impact of different levels of deduplication for different OS releases.
-In this experiment, we tag each block as  ``new''
-if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot block store;
+In this experiment, we tag each block in 350 OS disk snapshots from dataset1 as  ``new''
+if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot store;
 ``CDS''  if this block can be found  in CDS;
@@
 ``Parent block'' if  this block is marked unchanged in parent's block recipe.
-With this tagging, we compute the percentage of duplication accomplished by level-1 inner VM deduplication,
-level-2 inner VM deduplication and level 3 cross-VM deduplication.
-As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination
+With this tagging, we compute the percentage of deduplication accomplished by each level.
+As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination,
 this is because the time interval between two snapshots in our dataset
@@
 contributing about about 10\% of reduction on average.
+
+It is noticable that level-1 deduplication doesn't work well for CentOS, a significant percentage of data is not
+eliminated until they reach level-3. It shows that even user upgrade his VM system heavily and frequently
+such that data locality is totally lost, those OS-related data can still be identified at level-3.
+
+In gengral we see a stable data reduction ratio for all OS varieties, ranging from 92\% to 97\%, that means
+the storage cost of 10 full snapshots combined is still smaller than the original disk size. And compare to 
+today's widely used copy-on-write snapshot technique, which is similar to our level-1 deduplication, our
+solution cut the snapshot storage cost by 64\%.
 
@@
 Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
-terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
+terms of the duplication count. $Y$ axis is the popularity of a data block in log scale 
 measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
@@
 
-We further study how CDS covers content blocks used in image files using 90\% of
-the collected dataset.
-Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular common user data blocks. 
-The $X$ axis is the rank of common user data blocks.
+One of our biggest advantage is small memory footprint for deduplication, because we only
+eliminate a small amount of highly popular data.
+we use dataset2 to demostrate the coverage of popular data blocks on user-related data, 
+as shown in Figure \ref{fig:userdatacoverage}.
+%content blocks used in image files using 90\% of
+%the collected dataset.
+%Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular common user data blocks. 
+The $X$ axis is the rank of cmomon user data blocks, and $Y$ shows how much raw data can be covered given
+the size of CDS.
 Let $S_i$ and $F_I$ be the size and duplicate count 
@@
 Thus with about 1\% of blocks on data disks, CDS can cover about 38\% of total data blocks
-appeared in in all data snapshots. The corresponding CDS index uses about 150MB memory per machine.
+appeared in in all data snapshots. The corresponding CDS index uses no more than 150MB memory per machine,
+which can be easily co-located with other cloud services.
 
@@
 
-Because there are a limited number of OS releases supported by Aliyun, we study common blocks  among
+Because there are a limited number of OS releases, we study common blocks among
 OS disks loaded with  the same OS release. 
@@
 In  Figure~\ref{fig:OSunchanged},  we list a conservative  commonality study in 7 major OS versions  supported
-in Aliyun.  We consider the earlier snapshot for each OS disk as the base image.
-For every block in the base image, we classify this block as ``completely common''
+in Aliyun.
+%We consider the earlier snapshot for each OS disk as the base image.
+For every block in the base image, we classify this block as ``unchanged''
 if this block has appeared in all snapshots of the same OS release even they are used by different VMs.
 Figure \ref{fig:OSunchanged} shows that for each
-OS,  at least 70\% of OS blocks are completely common among all snapshots of the same OS. 
+OS,  at least 70\% of OS blocks are completely unchanged among all snapshots of the same OS. 
 Some latest release  of OS tends to have a higher percentage of content change
@@
 OS blocks, which is about 100GB OS data and its corresponding CDS index takes about 1GB memory space in total.
-They can cover sufficiently over 70\% of OS blocks.
+They can cover sufficiently over 70\% of OS-related data.
 
@@
 %as we vary the data size from about 4 terabytes to about 23.5 terabytes.
-After level-1 and level 2 elimination, our experiment shows that 
-the full deduplication would reduce the storage  further   by  45\% to 53\% of user disk space. 
-If we put all these unique data into CDS, we could achieve full deduplication,
-but the CDS size is not affordable. So we evaluate how much space saving of 
+After level-1 and level 2 elimination, we find that 
+the complete deduplication would reduce the storage cost further by 50\%. 
+If we put all these unique data into CDS, 
+we could achieve complete deduplication,
+but fingerprint lookup in such huge CDS hash index would become a bottleneck as discussed in many pervious works. 
+So we use dataset2 to evaluate how much space saving of 
 deduplication can be achieved when varying the CDS size.
@@
 compared to the full deduplication.  The unit of CDS size is gigabytes.
-We define \emph{space saving ratio} as the space saving of the CDS method divided by 
-full deduplication saving ratio. 
+We define \emph{space saving ratio} as the space saving of CDS method divided by 
+full deduplication space reduction. 
 With a 100GB CDS data (namely 1GB CDS index) can still  accomplish about 75\% 
@@
 %CDS size is restricted by system memory resource.
-Figure \ref{fig:datacds} shows how CDS space saving ratio
+With dataset2, Figure \ref{fig:datacds} shows how CDS space saving ratio
 compared to the full deduplication is affected by the dataset size. 
-The calculation is done after level 1 and level 2 deduplication.
-$X$ axis uses the data size collected  from up to 1323 VMs, which occupies about
-53 machines. 
+%The calculation is done after level 1 and level 2 deduplication.
 In this experiment we first set out a goal of space saving ratio completed, 
@@
 
-When we deal with a cluster of 1,000 nodes, we expect that using
-1\% of data disks can cover more what we have seen from this
-1323 VM dataset, assuming that the average behavior of every subcluster with 53 machines
+When we deal with a large cluster of 1,000 nodes, we expect that using
+1\% of data disks can cover more than what we have seen from this
+1323 VM dataset, assuming that the average behavior of every subcluster with 100 machines
 exhibits a similar commonality. 

### 2012-03-12 data_analysis/locality.tex
data analysis paper

\section{Impact of Locality}
Locality is widely used in many deduplication solutions, e.g., Zhu et al.~\cite{bottleneck08}
put in memory cache of block indices near the one which result in a disk index look-up and is found.
This is base on the observation that duplicates usually come in sequence rather than independently.

We check this fact in VM snapshots by monitoring the modification locations in VOSS. 
For each snapshot, we compare it to the previous snapshot, in the unit of 2MB fix-sized page,
to find out locations of dirty pages since last backup. We end up with a bitmap of
dirty pages for every snapshot, except those earliest ones who don't have a previous version
to compare against.

\begin{figure*}[htb]
  \centering
  \includegraphics[width=6.5in,height=2in]{countmodify.png}
\caption{Bitmaps of dirty pages between snapshots}
\label{fig:dirty}
\end{figure*}

In Figure~\ref{fig:dirty}, a snapshot's bitmap of dirty pages is represented as a vertical line 
composed of discontinuous segments. 
For each vertical line, the solid segments indicate changed regions since last snapshot backup,
and the rest represent the unchanged part.
All page locations (offset) is normalized with respect to the virtual disk size.
Because the earliest snapshots are excluded, 
every VM has 9 lines and there are 45 lines from each OS.
The bitmaps are first grouped by VMs and then by their OS type,
borders between OS types are shown as numbers at the xtics.

\emph{Observation 4: Each VM do has its own specific interested write regions, as a result, 
unchanged regions appear to be large and continous.} We see almost all VMs have
their write regions aligned across 9 snapshots, leaving the unchanged regions aligned as well.
So duplicates in the white area do come together during snapshot backup.
This observation strongly proves the importance of locality as the primary indication of
finding duplication.

\emph{Observation 5: Windows tends to write to more disk locations than Linux.} 
Although there are several Linux VMs write to large area of disk locations, this is very likely
because those users were more active during our samlping period.
On the other hand, all Windows VMs write to almost everywhere of the disk during every backup period.
We believe this is due to the design difference between NTFS and ext3, and we also see
the upgrade from Win2003 to Win2008 reduces such writes. However, this doesn't mean windows has more 
dirty pages, it's just more scattered.

In order to see the impact of locality further, we investigate deeper into the dirty pages.
We split those fix-sized pages into variable-sized 4KB blocks, for every block in the dirty pages,
we look into the corresponding
page (base on offset) of previous snapshot to see if a duplicate can be found.

\begin{table}[htb]
  \centering
    \begin{tabular}{|l|p{1.3in}|p{0.4in}|}
        \hline
        OS Type & After Reduction Within \newline Dirty Page (GB) & Ratio \\ \hline
        Debian & 161.11 & 6.42 \\ \hline
        Ubuntu & 145.02 & 6.82 \\ \hline
        RHEL & 185.34 & 5.43 \\ \hline
        CentOS & 479.78 & 2.03 \\ \hline
        Win2003 32Bit & 80.14 & 7.87 \\ \hline
        Win2003 64Bit & 95.07 & 8.35 \\ \hline
        Win2008 64Bit & 172.22 & 9.76 \\ \hline
        Combined & 1318.68 & 5.26 \\
        \hline
    \end{tabular}
    \caption{Data reduction via 4KB block deduplication within dirty pages}
    \label{tab:locality}
\end{table}

\emph{Observarion 6: Data reduction ratio is generally improved, but there is still lots of
improvment space compare to complete deduplication.} We see significant improvment for all OS
types, which definitely deserves adding an additional layer to dirty-page based 
data reduction. In addition, the cost of looking one page's block hash index
shall be very small compare to full hash index lookup.

However, this is probably the best of what we can get from locality. The rest of
duplication mainly lies between VMs, e.g., same or slightly different versions of OS distributions, 
similar software installations, etc. Such duplications can not be easily 
eliminated and worth further research efforts.

### 2012-03-12 data_analysis/main.tex
data analysis paper

--- 2012-01-30 vm_snapshot_sim/main.tex
@@
 \usepackage{epsfig}
-%\usepackage{breakurl}
-%% Define a new 'leo' style for the package that will use a smaller font.
-\makeatletter
-\def\url@leostyle{%
-  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
-\makeatother
-%% Now actually use the newly defined style.
-\urlstyle{leo}
-%\linespread{1.2}
-%\setlength{\parskip}{1ex}
+\usepackage{multirow}
+\ifx\pdftexversion\undefined
+\usepackage[dvips]{graphicx}
+\else
+\usepackage{graphicx}
+\fi
+
+\newcommand{\comments}[1]{}
+
 \begin{document}
-\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
-\author{Wei Zhang, Hong Tang, Hao Jiang, Rachael Zeng, Xiaogang Li, Tao Yang}
+%\title{Selective Deduplication for VM Snapshots in Cloud Storage}
+\title{Understanding the Data Duplication of VM Cloud Storage}
+%\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
+\author{
+Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
+   {\normalsize $^\star$UC Santa Barbara}\\
+   {\normalsize$^\dagger$Alibaba.com}
+}
 \date{}
@@
 
-\input{abstract}
-\input{intro} %introduce the problem, related solutions and our requirements
-\input{cds} %data study, zipf, model of cds size and dedup efficiency
-\input{approach} %our dedup process
-\input{results}
+%\input{abs}
+%\input{intro} %introduce the vm cloud, snapshot
+\input{overall} %complete dedup on both datasets 
+\input{locality} %
+\input{user.tex}
+\input{scale}
+\input{count} %data study, zipf, model of cds size and dedup efficiency
+%\input{results}
 %\input{related}
-%\input{future}
-\input{conclusion}
+%\input{conclusion}
+%\input{con}
+
+      %\setlength{\itemsep}{ex}%
+%      \setlength{\parskip}{0ex}%
+%\setlength{\itemsep}{-3mm}
+
+	%\linespread{0.3} 
+%  \let\oldthebibliography=\thebibliography
+%  \let\endoldthebibliography=\endthebibliography
+%  \renewenvironment{thebibliography}[1]{%
+%    \begin{oldthebibliography}{#1}%
+%      \setlength{\parskip}{-0.02ex}%
+%      \setlength{\itemsep}{-0.02ex}%
+%      \setlength{\baselineskip}{-0.02ex}%
+
+%  }%
+%  {%
+%    \end{oldthebibliography}%
+%  }
+{\small
 \bibliographystyle{abbrv}
-\bibliography{dedup}
+\bibliography{dedup,dedup1}
+}
 \end{document}

### 2012-03-12 data_analysis/overall.tex
data analysis paper

\section{Overall Deduplication Effect}
Our study start from examining the effect of complete deduplication over both data sets.
Each virtual disk image is divided into small variable-sized blocks using the TTTD algorithm\cite{frame05},
under the average 4KB, maximum 16KB and minimum 4KB setting. Complete deduplication is
done by caculating the SHA-1 hash of each block and identifying duplicate copies base on compare-by-hash.

Regarding to the VM snapshots storage, one popular technique is to split disk image file into fix-sized
pages, and only store the dirty pages since last backup. But unlike complete deduplication considering duplicates
across VMs, this technique is limited within each VM's backups. We also tested this data reduction method
using 2MB page size over the dataset VOSS.

Table~\ref{tab:dedup} shows the data reduction of both methods, 
the reduction ratio is defined as the original size divide by size after reduction.
In general, complete deduplication achieves great data reduction

We see that

\begin{table*}[htb]
  \centering
    \begin{tabular}{|l|l|p{0.8in}|p{1.1in}|p{0.3in}|p{0.9in}|p{0.3in}|}
        \hline
        Data Set & OS Type & Original Size \newline (GB) & After Complete \newline Deduplication (GB) & Ratio & After 2MB Page \newline Reduction (GB) & Ratio \\ \hline
        \multirow{8}{*}{VOSS} & Debian & 1034.59 & 77.10 & 13.42 & 218.29 & 4.74 \\ \cline{2-7}
         & Ubuntu & 989.32 & 81.60 & 12.12 & 178.38 & 5.55 \\ \cline{2-7}
         & RHEL & 1007.28 & 62.70 & 16.07 & 215.33 & 4.68 \\ \cline{2-7}
         & CentOS & 973.03 & 57.34 & 16.97 & 522.53 & 1.86 \\ \cline{2-7}
         & Win2003 32Bit & 630.37 & 30.12 & 20.93 & 150.31 & 4.19 \\ \cline{2-7}
         & Win2003 64Bit & 793.47 & 44.16 & 17.97 & 167.15 & 4.75 \\ \cline{2-7}
         & Win2008 64Bit & 1508.97 & 46.39 & 32.52 & 222.54 & 6.78 \\ \cline{2-7}
         & Combined & 6937.03 & 389.65 & 17.80 & 1674.53 & 4.14 \\ \hline
        DDS & ~ & 23125.2 & 10887.2 & 2.12 & ~ & ~ \\
        \hline
    \end{tabular}
    \caption{Data reduction via complete deduplication and dirty page reduction}
    \label{tab:dedup}
\end{table*}

\emph{Observation 1: Both methods reduce the data significantly, 
but there is still a big gap between the effect of dirty page method 
and what complete deduplication can acheive.} 
We believe complete deduplication can reduces 2x~5x more data than dirty page method for several resons:
First, the dirty page method doesn't resolve the duplication across VM backups. Second, the page size
is usually much bigger than actual range of modification, so many unchanged data are still backed up.

\emph{Observation 2: Locality could be ruined with system upgrade.}
We notice dirty page method works poorly on CentOS, while complete deduplication works as efficient as on
other OSes. We believe this is probably due to the user have upgraded his system heavily during our
data sampling period, thus damaged the offset-based locality. In addition, the cloud will only have
more and more variations of operating systems with different installation configurations,
All these suggest data reduction base on offset may not work across different user snapshot backups.

\emph{Observation 3: There is not much duplication on user data if without multiple backups.}
For DDS data set, because it doesn't contain snapshot backups, the overall reduction ratio is only about 2:1,
which suggests we probably should put less effort on the reduction of user generated data. These data
are changed slowly and mostly by append, so locality should work well enough.

### 2012-03-12 data_analysis/user.tex
data analysis paper

\section{Duplication V.S. Scale}
Dealing with large scale VM cloud, one of the most important questions is
whether data duplication will grow with the system scale. 
One hypothesis we have is that when the total number of block increases,
the chance that it being duplicated with another is going to be higher. Thus
we shall get better data reduction with larger scale of data.
Past study\cite{keren08} has suggested that virtual disks with 
operating systems installed should share large amount of software related data,
which indirectly supports this argument.
However, some other data study\cite{middleware11} showed the opposite.

In this experiment we test the complete deduplication under the scenario
that no snapshot backup is involved. To simulate the scale factor,
we start with partial data sets and scale them up by adding disk images.
Complete deduplication is performed at each stage to examine the reduction ratio.
Our DDS data set already contains no snapshot backup data. For VOSS, we simply pick
the earliest snapshot for each VM.

\begin{figure}
  \centering
  \epsfig{file=dedup_ratio.eps, width=3.2in}
  \caption{Reduction ratio of complete deduplication at different scale}
  \label{fig:scale}
\end{figure}

\emph{Observation 7: Reduction ratio by complete deduplication does not appear to increase with storage scale.}
In general we see almost no increment of reduction ratio along with the data scale, especially
for user generated data, shown as DDS in Figure\ref{fig:scale}, its reduction ratio is always
near 2:1. For OS disks, some Windows distributions appear to have incremental reduction, which is suspected to
because the size of Windows system is much bigger than Linux, thus it has much more redundant
data that widely exist in all VMs. We expect to perform larger scale study on OS disks in future
to obtain better conclusion on this topic.

### 2012-03-13 data_analysis/abs.tex
initial version

\begin{abstract}
Backup in VM cloud is mainly done by storing snapshots of
VM images. Since VM images are huge and backup is frequent, 
the snapshot storage
in VM cloud must deduplicate snapshot data to save cloud resources.
Thus it is very important to exploit the duplication pattern of snapshot
backup data for designing better cloud storage systems.
In this paper we present the data duplication pattern that
we observed from Aliyun's publie VM cloud services, and provide
some insights for researchers and engineers to design future
 deduplication strategies for VM cloud backup.
\end{abstract}

### 2012-03-13 data_analysis/con.tex
initial version

\section{Conclusion}
In this paper, a empirical study using Aliyun's real user VM data traces is conducted. 
We present a number of observations and insights on the data duplication
in VM snapshot backups. We describe
in detail the patterns of VM access, VM snapshot duplication, locality reduction, and
the dintinct difference between OS and user generated data.
We hope this will facilitate future designs of cloud storage for VMs.

### 2012-03-13 data_analysis/dup.tex
initial version

\section{Heavily Duplicated Data}
Knowing that locality has ruled the 
data reduction within individual VM's snapshot backups,
in this section we investigate the dominant factor
of data duplication between VMs.

Many deduplication study has mentioned that zero-filled
blocks were widely exist, so we count the
zero-filled blocks using the variable 4KB scheme to examine their weights in VM storage.
Table~\ref{tab:zero} shows the total size of zero-filled
blocks divide by data set size.

\begin{table}[htb]
  \centering
    \begin{tabular}{|l|c|}
        \hline
        Data Set & Weight of Zero-filled Blocks\\ \hline
        VOSS & 8.1\% \\ \hline
        DDS & 21.3\% \\
        \hline
    \end{tabular}
    \caption{Weight of zero-filled blocks in our data sets}
    \label{tab:zero}
\end{table}

\emph{Observation 8: User generated data are much less compact than operating system data.}
We see 21.3\% reduction from DDS by removing zero-filled blocks. Consider
that full deduplication can only reduce about 50\% on DDS, this indicates we could
achieve great reduction by simply avoid storing zero-filled blocks in storage system.

Data on OS disks seem much more compact than
user generated contents. However, their duplication may come in from another way.
Consider 99\% of our VM users run either Linux or Windows, and most of them only uses
a small selection of software (e.g., MySQL, Apache), such
operating system and software related data are very likely to be duplicated
across VMs.

We examine this by using the public VM images in Aliyun's cloud environment as a reference.
Every VM is generated from one of the public VM images by copying its data from base image,
so in order to see whether these data are changed after VM usage,
we first divide the public images into 4KB variable-sized blocks, then for each type of
OS, we check its 50 VM snapshot backups in VOSS, to see if this data block still exist in all
50 backups. This is a very strict criteria, a data block will only be marked as ``unchanged''
if it appear in all 50 snapshots.

\begin{figure}
  \centering
  %\epsfig{file=dedup_ratio.eps, width=3.2in}
  \includegraphics[width=3in,height=2in]{os_subset.png}
  \caption{}
  \label{fig:osdup}
\end{figure}

\emph{Observation 9: OS and software related data rarely change.}
This strongly indicates we should avoid storing such data in any VM's snapshot backups,
if we know they can be obtained from somewhere else. 
In addition, knowing these data are widely used by VMs shall help us developing
fast content delivery scheme for VM migration and snapshot restoration.

### 2012-03-13 data_analysis/intro.tex
initial version

\section{Introduction}
In a virtualized cloud environment such as ones provided by Amazon EC2 and Aliyun,
each instance of a guest operating system runs on a virtual machine, accessing
virtual hard disks represented as virtual disk image files in the host operating system.
Because these image files are stored as regular files from the external point of view,
backing up VM's data is mainly done by taking snapshots of virtual disk images.

Frequent  backup of VM snapshots increases  the reliability of VM's hosted in a cloud.
For example, Aliyun, the largest cloud service provider by Alibaba in China, 
provides automatic frequent backup of VM images to strengthen the reliability of its service for all users.
The cost of frequent backup of VM snapshots is  high because of the huge storage demand.

Unlike the legacy backup systems\cite{jumbo07} dealing with general file-level backup and deduplication, 
Backing up VM images is different. Although each VM image is treated as a file logically, its size is very large.
On the other hand, a cloud must support parallel backup of a large number of virtual disks everyday. 
One key requirement we face at Aliyun is that VM snapshot backup should only use a minimal amount of system
resources so that most of resources is kept for regular cloud system services or applications.
Thus our objective is to exploit the characteristics and duplication pattern of VM snapshot data and
pursue a cost-effective deduplication solution.

There are several previous studies on this topic. Jayaram\cite{Jayaram2011} and
Jin\cite{Jin2009} has investigated the data similarity between VM images using 
Rabin's fingerprinting\cite{identify00} algorithm. 
Silo\cite{xia2011} and Extreme Binning\cite{extreme_binning09} studied the problem
of deduplication in a large distributed environment which also helps solving the
problem of VM snapshot backup.

In this paper we present the data analysis of Aliyun's VM snapshot data.
Our work is different from previous studies at several aspects:
First, we are targeting at the problem of snapshot backups, 
and no previous study has studied VM image with backup data involved.
Second, we focus on observing the pattern of data duplication in VM snapshot backups,
rather than examining the effect of variable-sized chunking algorithm.
Finally, we use real user's VM data rather than hand-made VM images.

\section{Experiment Setup}
We sampled two data sets from Aliyun's public VM cluster, all VMs
are used by real external users running various applications such like
database, web server, rendering services or even Hadoop. Each VM has
two virtual disks, one is for OS and software installations, and the other one
is for storing user data contents.

Data set VOSS composes of the OS disks from 35 VMs in 7 popular OSes: 
Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
5 VMs are chosen, and every VM come with 10 full snapshots of it OS disk. So
there is 350 full snapshot backups in this data set, overall size is about 7 TB.
We use VOSS to study the backup duplication characteristics, and OS disk change patterns.

Data set DDS contains the first snapshots of 1323 VMs' data disks from a cluster with 100+ nodes. 
Since no backup duplication is involved in this data set, this data set helps us to 
study the duplication pattern of user generated data. The overall size of dataset2 is near 23 TB.

### 2012-03-13 data_analysis/main.tex
update
initial version

@@
 %\title{Selective Deduplication for VM Snapshots in Cloud Storage}
-\title{Understanding the Data Duplication of VM Cloud Storage}
+\title{Understanding the Data Duplication in VM Cloud Storage}
 %\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
 \author{
-Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
-   {\normalsize $^\star$UC Santa Barbara}\\
-   {\normalsize$^\dagger$Alibaba.com}
+Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$\\
+   {\normalsize $^\star$UC Santa Barbara, \{wei, tyang\}@cs.ucsb.edu}\\
+   {\normalsize$^\dagger$Alibaba.com, \{hongtang, haojiang\}@alibaba.com}
 }
@@
 
-%\input{abs}
-%\input{intro} %introduce the vm cloud, snapshot
+\input{abs}
+\input{intro} %introduce the vm cloud, snapshot
 \input{overall} %complete dedup on both datasets 
 \input{locality} %
-\input{user.tex}
-\input{scale}
-\input{count} %data study, zipf, model of cds size and dedup efficiency
+\input{user}
+\input{dup}
+%\input{count} %data study, zipf, model of cds size and dedup efficiency
 %\input{results}
@@
 %\input{conclusion}
-%\input{con}
+\input{con}
 
@@
 \bibliographystyle{abbrv}
-\bibliography{dedup,dedup1}
+\bibliography{dedup1,library}
 }

### 2012-03-13 data_analysis/overall.tex
initial version

@@
 done by caculating the SHA-1 hash of each block and identifying duplicate copies base on compare-by-hash.
-
-Regarding to the VM snapshots storage, one popular technique is to split disk image file into fix-sized
-pages, and only store the dirty pages since last backup. But unlike complete deduplication considering duplicates
-across VMs, this technique is limited within each VM's backups. We also tested this data reduction method
-using 2MB page size over the dataset VOSS.
-
-Table~\ref{tab:dedup} shows the data reduction of both methods, 
-the reduction ratio is defined as the original size divide by size after reduction.
-In general, complete deduplication achieves great data reduction
-
-We see that
 
@@
 
+Regarding to the VM snapshots storage, one popular technique is to split disk image file into fix-sized
+pages, and only store the dirty pages since last backup. But unlike complete deduplication considering duplicates
+across VMs, this technique is limited within each VM's backups. We also tested this data reduction method
+using 2MB page size over the dataset VOSS.
+
+Table~\ref{tab:dedup} shows the data reduction of both methods, 
+the reduction ratio is defined as the original size divide by size after reduction.
+In general, complete deduplication achieves great data reduction, except for DDS data set.
+
 \emph{Observation 1: Both methods reduce the data significantly, 
@@
 
-\emph{Observation 2: Locality could be ruined with system upgrade.}
+\emph{Observation 2: Locality could be damaged with system upgrade.}
 We notice dirty page method works poorly on CentOS, while complete deduplication works as efficient as on

### 2012-03-13 data_analysis/user.tex
initial version

@@
 we shall get better data reduction with larger scale of data.
-Past study\cite{keren08} has suggested that virtual disks with 
+Past study\cite{Jin2009} has suggested that virtual disks with 
 operating systems installed should share large amount of software related data,
 which indirectly supports this argument.
-However, some other data study\cite{middleware11} showed the opposite.
+However, some other data study\cite{Jayaram2011} showed the opposite.
 
@@
   \centering
-  \epsfig{file=dedup_ratio.eps, width=3.2in}
+  %\epsfig{file=dedup_ratio.eps, width=3.2in}
+  \includegraphics[width=3in,height=2in]{dedup_ratio.png}
   \caption{Reduction ratio of complete deduplication at different scale}
@@
 
-\emph{Observation 7: Reduction ratio by complete deduplication does not appear to increase with storage scale.}
+\emph{Observation 7: Reduction ratio by complete deduplication does not appear to increase.}
 In general we see almost no increment of reduction ratio along with the data scale, especially
-for user generated data, shown as DDS in Figure\ref{fig:scale}, its reduction ratio is always
+for user generated data, shown as DDS in Figure~\ref{fig:scale}, its reduction ratio is always
 near 2:1. For OS disks, some Windows distributions appear to have incremental reduction, which is suspected to
 because the size of Windows system is much bigger than Linux, thus it has much more redundant
-data that widely exist in all VMs. We expect to perform larger scale study on OS disks in future
-to obtain better conclusion on this topic.
+data that widely exist in all VMs. We suspect the operating system and software related data
+will occupy a significant percentage of data reduction regardless of number of VMs, will 
+be studied in the next section.
+%We expect to perform larger scale study on OS disks in future to obtain better conclusion on this topic.

### 2012-03-18 data_analysis/overall.tex
uodate

@@
 Each virtual disk image is divided into small variable-sized blocks using the TTTD algorithm\cite{frame05},
-under the average 4KB, maximum 16KB and minimum 4KB setting. Complete deduplication is
+under the average 4KB, maximum 16KB and minimum 2KB setting. Complete deduplication is
 done by caculating the SHA-1 hash of each block and identifying duplicate copies base on compare-by-hash.

### 2012-03-18 data_analysis/abs.tex
update

@@
 the snapshot storage
-in VM cloud must deduplicate snapshot data to save cloud resources.
+in VM cloud must reduce snapshot data to save cloud resources.
 Thus it is very important to exploit the duplication pattern of snapshot
-backup data for designing better cloud storage systems.
+backup data for developing better cloud storage system.
 In this paper we present the data duplication pattern that

### 2012-03-18 data_analysis/con.tex
update

@@
 In this paper, a empirical study using Aliyun's real user VM data traces is conducted. 
-We present a number of observations and insights on the data duplication
-in VM snapshot backups. We describe
-in detail the patterns of VM access, VM snapshot duplication, locality reduction, and
-the dintinct difference between OS and user generated data.
-We hope this will facilitate future designs of cloud storage for VMs.
+We present a number of observations and insights on where and how data duplication
+exist in VM snapshot backups. We describe
+in detail the patterns of VM access, the potential of deduplication, 
+important factors such as locality, similarity and popularity, and
+the dintinct difference between OS and user generated data duplication.
+We hope this study will facilitate researchers and engineers to design better
+data deduplication strategies
+for backup storage in VM Cloud.

### 2012-03-18 data_analysis/dup.tex
update

@@
 \section{Heavily Duplicated Data}
+\label{sect:dup}
 Knowing that locality has ruled the 
@@
 so in order to see whether these data are changed after VM usage,
-we first divide the public images into 4KB variable-sized blocks, then for each type of
+we first split the public images into 4KB variable-sized blocks, then for each type of
 OS, we check its 50 VM snapshot backups in VOSS, to see if this data block still exist in all
@@
   \includegraphics[width=3in,height=2in]{os_subset.png}
-  \caption{}
+  \caption{Data that almost never change in OS disks}
   \label{fig:osdup}

### 2012-03-18 data_analysis/intro.tex
update

@@
 Unlike the legacy backup systems\cite{jumbo07} dealing with general file-level backup and deduplication, 
-Backing up VM images is different. Although each VM image is treated as a file logically, its size is very large.
+Backing up VM images is different: although each VM image is treated as a file logically from
+external point of view, its size is very large.
 On the other hand, a cloud must support parallel backup of a large number of virtual disks everyday. 
-One key requirement we face at Aliyun is that VM snapshot backup should only use a minimal amount of system
-resources so that most of resources is kept for regular cloud system services or applications.
-Thus our objective is to exploit the characteristics and duplication pattern of VM snapshot data and
-pursue a cost-effective deduplication solution.
+Two key requirements we face during desinging a backup storage system for VM snapshot are: 
+\begin{enumerate}
+\item VM snapshot backup should only use a minimal amount of system
+resources so that most of resources is kept for regular cloud system services and VM themselves.
+\item The entire snapshot storage and deduplication process must be fully decentralized to acheive
+high scalibility and throughput, 
+no component shall become a bottleneck.
+\end{enumerate}
+
+It is impossible to accomplish such requirements without fully utilizing the data duplication pattern
+in VM snapshot backups
+and design the optimal data deduplication strategies.
+Thus we believe the first step towarding a cost-effective deduplication solution
+ is to exploit the characteristics and duplication pattern of VM snapshot data.
 
@@
 
-In this paper we present the data analysis of Aliyun's VM snapshot data.
-Our work is different from previous studies at several aspects:
+In this paper we present the data analysis of Aliyun's VM snapshot data,
+our focus is to find out exploitable data duplication patterns and
+correspoding factors.
+Our work differs from previous studies at several aspects:
 First, we are targeting at the problem of snapshot backups, 
@@
 
+The rest of the paper is organized as follows: Section~\ref{sect:setup} introduces
+the experiment setups, Section~\ref{sect:dedup} studies the potential of deduplication
+in VM snapshot backups, Section~\ref{sect:loc} discusses the locality factor
+in reduction of backup data,
+Section~\ref{sect:scale} analysis the change of data duplication against system scale,
+Section~\ref{sect:dup} introduces the patterns of heavily duplicated data.
+
 \section{Experiment Setup}
-We sampled two data sets from Aliyun's public VM cluster, all VMs
-are used by real external users running various applications such like
+\label{sect:setup}
+We sampled two data sets from Aliyun's public VM cluster, where all VMs
+are used by real world users running various applications such like
 database, web server, rendering services or even Hadoop. Each VM has
@@
 5 VMs are chosen, and every VM come with 10 full snapshots of it OS disk. So
-there is 350 full snapshot backups in this data set, overall size is about 7 TB.
-We use VOSS to study the backup duplication characteristics, and OS disk change patterns.
+there is 350 full snapshot backups in this data set, the overall size is about 7 TB.
+We use VOSS to study the backup duplication characteristics and OS disk change patterns.
 
@@
 Since no backup duplication is involved in this data set, this data set helps us to 
-study the duplication pattern of user generated data. The overall size of dataset2 is near 23 TB.
+study the duplication pattern of user generated data. The overall size of DDS is near 23 TB.

### 2012-03-18 data_analysis/locality.tex
update
initial version

@@
 \section{Impact of Locality}
+\label{sect:loc}
 Locality is widely used in many deduplication solutions, e.g., Zhu et al.~\cite{bottleneck08}
@@
 to compare against.
-
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=6.5in,height=2in]{countmodify.png}
-\caption{Bitmaps of dirty pages between snapshots}
-\label{fig:dirty}
-\end{figure*}
 
@@
 
+\begin{figure*}[tbhp]
+  \centering
+  \includegraphics[width=6.5in,height=2in]{countmodify.png}
+  %\epsfig{file=countmodify.eps, width=6.5in}
+\caption{Bitmaps of dirty pages between snapshots}
+\label{fig:dirty}
+\end{figure*}
+
 \begin{table}[htb]

### 2012-03-18 data_analysis/overall.tex
update

@@
 \section{Overall Deduplication Effect}
-Our study start from examining the effect of complete deduplication over both data sets.
-Each virtual disk image is divided into small variable-sized blocks using the TTTD algorithm\cite{frame05},
-under the average 4KB, maximum 16KB and minimum 2KB setting. Complete deduplication is
-done by caculating the SHA-1 hash of each block and identifying duplicate copies base on compare-by-hash.
+\label{sect:dedup}
 
-\begin{table*}[htb]
+\begin{table*}[tbh]
   \centering
@@
 
+Our study start from examining the effect of complete deduplication over both data sets.
+Each virtual disk image is divided into small variable-sized blocks using the TTTD algorithm\cite{frame05},
+under the average 4KB, maximum 16KB and minimum 2KB setting. Complete deduplication is
+done by caculating the SHA-1 hash of each block and identifying duplicate copies base on compare-by-hash.
+
 Regarding to the VM snapshots storage, one popular technique is to split disk image file into fix-sized
@@
 but there is still a big gap between the effect of dirty page method 
-and what complete deduplication can acheive.} 
+and what complete deduplication can accomplish.} 
 We believe complete deduplication can reduces 2x~5x more data than dirty page method for several resons:

### 2012-04-06 data_analysis/cds.tex
Add CDS analysis

\section{CDS Analysis}
Although locality based data reduction can remove most of the inner-VM duplications,
it's not able to solve the data duplication cross VMs. Different VMs still share large amount
of common data such that their snapshot backups would have a lot of data in common.
Our observations on Aliyun's real VM user data reveals several major sources of cross-VM data duplication:
  \begin{enumerate}
  \item \emph{System-related data}: These data are generated by public third-parties, they are copied/downloaded/installed into VM disks either automatically or manually. Once installed, operations on such data are mostly read only until software updates arrive. For example, data of operating systems, some widely-used software such as Apache and MySQL, and their documations all fall into this category.
  \item \emph{User-generated data}: These data are generated by individual user's behavior, either directly or indirectly. They are much less duplicated than the system-related data, but the zipf-like distribution indicates that a small amount of data in this category could represent most of data duplications.
  \item \emph{Zero-filled data}: Like previous studies [refs here], we've observed that zero-filled data exist pervasively at system wide. They are almost like the spaces and commas in text articles. Under content-based chunking, they were distilled as zero-filled blocks with the maximum allowed length. 
%Zero-filled blocks are mostly generated by user behavior to preserve the space for future data, thus we treat them as a special case of user-generated data.
  \end{enumerate}

Without eliminating the data duplication between VM snapshot backups, storage space is severely wasted when the number of VMs increases.
To address this problem, we developed a technique called \emph{Common Data Set (CDS)} to eliminate data duplication for all three situations above. 
CDS is a public data library that shared by all VM snapshot backups in the cluster, 
which consists of the most popular data blocks in VM snapshot backups. It is generated, 
managed and accessed in an uniform manner by all VMs such that [write some fancy system characteristic stuff here].

\subsection{CDS Size V.S. Coverage}
As a shared data library, we expect CDS to collect almost all the system related data, the most popular user-generated data and the zero-filled data block.
With CDS as a public data reference, each VM's snapshot backup has no need to store its own copies for data that can be found in CDS, instead they can just
store a reference.

The more data we put into CDS, the closer we come to complete deduplication. But in reality we are facing a list of restrictions such like [blabla].
We borrowed the idea of web caching[refs here] to analysis the size of CDS vesus its effectiveness on data reduction.

We let $M$ be the number of machines in a VM cluster, $N$ be the total number of VMs,
$D$ denotes the average size of one VM's snapshot backups, which is near 40 GB in our production clusters.
And let $C_0$, $C_s$ and $C_u$ denote the size of zero-filled block, system-related data and user-generated data in CDS,
then the total size of CDS is represented by $C=C_0+C_s+C_u$.
We let $S_0$, $S_s$ and $S_u$ denote the corresponding average space saving ratio (coverage) relative to $D$ in per VM's snapshot backups,
so the total saving ratio is $S=S_0+S_s+S_u$.

Zero-filled block at maximum length is the first item we need to put into CDS. This is the one and only special data block, 
and because CDS only stores unique data blocks, $C_0$ is almost equal to 0. In practice we found zero-filled blocks account
for near 20\% of total data, so $S_0$ is 20\%.

The rarely modified system-related data are the second to be added to CDS. We have thousands of VMs in each cluster, 
but all these VMs fall into only a few OS types, using a limited selection of software, therefore data duplication in this category
is highly noticable in a global block counting. In particular, most of such data already exist in the VM base images. 
We analyzed VMs running various services from 7 mainstream OS types in our cluster, and found close to 50GB of such data in total. 
Because system-related data don't change frequently, it's safe to expect that for 20 OS variations 
and software updates in 2 years, $C_s$ will not grow to exceed 200 GB.
For each VM, from 2 to 20 GB of data can be reduced in this way, depends on the OS and service type, so on average we estimate
$S_s$ would be no less than 20\%.

The rest of data are user-generated, the total size of such data can be written as $D_u=D-S_0-S_s$, which is 60\% of $D$. 
It follows a zipf-like distribution with $\alpha$ between 0.65 to 0.7. 
Let $T_u$ be the total size of unique data blocks in $D_u$,
in practice we notice that complete deduplication for such data always result in a 2:1 reduction ratio,
, so $T_u=D_u/2$.
Since we collect the most popular user-generated data into CDS, the coverage of CDS on user-generated data
is $(C_u/T_u)^{1-\alpha}$.

The following table lists CDS coverage on user-generated data under different $\alpha$ and $C_u/T_u$.

[a table of coverage with alpha from 0.65-0.70, ratio from 0.002 0.005 0.01 0.02 0.05]

It's obviously that at least 30\% of user-generated data can be reduced in this way, using about 0.02 of $T_u$, or 0.01 of $D_u$.
The size of user-generated data in CDS would be 0.006$D$, with coverage $S_u=0.18D$.

Thus the estimation of CDS coverage is $S=S_0+S_s+S_u=0.58$, with the size of CDS to be no more than $(200 + 0.006*D*N)$ GB.
In a VM cluster of 100 machines, with 25 VMs on each physical machine, the size of CDS is 800 GB in total, or 8 GB per machine.
The total size of CDS index would be 8 GB, which will cost 80 MB memory on each machine.

\subsection{CDS Access}

\subsection{CDS Management}

### 2012-05-06 vm_snapshot_sim/2012arch.tex
fixed some  typos

@@
   %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
-  \epsfig{file=images/snapshot_representation.eps,  width=3.8in}
+  \epsfig{file=images/snapshot_representation.eps,  width=3.7in}
   \caption{An example of snapshot representation.}
@@
 implemented using Memcached~\cite{memcached} to leverage the aggregated memory in a cluster.
-Th usage of memory at each machine is small and thus  this scheme  does not
+The usage of memory at each machine is small and thus  this scheme  does not
 lead to  a memory resource contention with the existing cloud services.
@@
 memory cost by CDS hash index is about 150MB per machine.
-On the other hand, the CDS from OS-related data is only relvant to the number of OS releases.
+On the other hand, the CDS from OS-related data is only relevant to the number of OS releases.
 Our experiment on 7 major OS releases shows that about 100GB of data is never modified, and we expect

### 2012-05-06 vm_snapshot_sim/2012concl.tex
update
fixed some  typos

@@
 two-third of snapshot storage cost.
-Our scheme uses a very small amount of memory on each node, and leaves
+Finally, our scheme uses a very small amount of memory on each node, and leaves
 room for additional optimization we are further studying.
+\section*{Acknowledgments}
+{\small
+We would like to thank Weicai Chen and Shikun Tian from Alibaba for their kind support, 
+and the anonymous referees for their comments.
+This work was completed while Wei Zhang was a intern at Alibaba.
+This work was supported in part by NSF IIS-1118106.
+Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
+do not necessarily reflect the views of the National Science Foundation.
+}
 %Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,

### 2012-05-06 vm_snapshot_sim/2012eval.tex
fixed some  typos

@@
 On the other hand,  CDS still finds lots of duplicates that inner VM deduplication can't find,
-contributing about about 10\% of reduction on average.
+contributing about 10\% of reduction on average.
 
-It is noticable that level-1 deduplication doesn't work well for CentOS, a significant percentage of data is not
+It is noticeable that level-1 deduplication doesn't work well for CentOS, a significant percentage of data is not
 eliminated until they reach level-3. It shows that even user upgrade his VM system heavily and frequently
@@
 
-In gengral we see a stable data reduction ratio for all OS varieties, ranging from 92\% to 97\%, that means
+In general we see a stable data reduction ratio for all OS varieties, ranging from 92\% to 97\%, that means
 the storage cost of 10 full snapshots combined is still smaller than the original disk size. And compare to 
@@
 eliminate a small amount of highly popular data.
-we use dataset2 to demostrate the coverage of popular data blocks on user-related data, 
+we use dataset2 to demonstrate the coverage of popular data blocks on user-related data, 
 as shown in Figure \ref{fig:userdatacoverage}.
@@
 %Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular common user data blocks. 
-The $X$ axis is the rank of cmomon user data blocks, and $Y$ shows how much raw data can be covered given
+The $X$ axis is the rank of common user data blocks, and $Y$ shows how much raw data can be covered given
 the size of CDS.
@@
 Thus with about 1\% of blocks on data disks, CDS can cover about 38\% of total data blocks
-appeared in in all data snapshots. The corresponding CDS index uses no more than 150MB memory per machine,
+appeared in all data snapshots. The corresponding CDS index uses no more than 150MB memory per machine,
 which can be easily co-located with other cloud services.

### 2012-05-06 vm_snapshot_sim/2012intro.tex
fixed some  typos

@@
 virtual disk image backup. Although we treat each virtual disk  as a file logically, its size is very large.
-On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud everyday. 
+On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud every day. 
 One key requirement we face at Alibaba Aliyun is that VM snapshot backup should only use a minimal amount of system
@@
 a small amount of resources to deduplicate.
-Seperating deduplication into multi levels effectively accomplish the major space saving goal
+Separating deduplication into multi levels effectively accomplish the major space saving goal
 compare the global complete deduplication scheme, at the same time it makes
-the backup of different VMs to be indepdent for better fault tolerance.
+the backup of different VMs to be independent for better fault tolerance.
 

### 2012-05-06 vm_snapshot_sim/main.tex
fixed some  typos

@@
 \author{
-\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Hong Tang\IEEEauthorrefmark{2}, Hao Jiang\IEEEauthorrefmark{2}, Tao Yang\IEEEauthorrefmark{1}, Xiaogang Li\IEEEauthorrefmark{2}, Rachael Zeng\IEEEauthorrefmark{2}}
-\IEEEauthorblockA{\IEEEauthorrefmark{1}Dept. of Computer Science, UC Santa barbara. Email: \{wei, tyang\}@cs.ucsb.edu}
+\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Hong Tang\IEEEauthorrefmark{2}, Hao Jiang\IEEEauthorrefmark{2}, Tao Yang\IEEEauthorrefmark{1}, Xiaogang Li\IEEEauthorrefmark{2}, Yue Zeng\IEEEauthorrefmark{2}}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}Dept. of Computer Science, UC Santa Barbara. Email: \{wei, tyang\}@cs.ucsb.edu}
 \IEEEauthorblockA{\IEEEauthorrefmark{2}Alibaba Inc. Email: \{hongtang, haojiang, xiaogang, rachael\}@alibaba-inc.com}

### 2012-05-06 data_analysis/cds.tex
camera ready pdf

@@
 
-We let $M$ be the number of machines in a VM cluster, $N$ be the total number of VMs,
-$D$ denotes the average size of one VM's snapshot backups, which is near 40 GB in our production clusters.
+We let $M$ be the number of nodes in a cluster, $N$ be the number of VMs hosted per node,
+and let $D$ denotes the average size of one VM's snapshot backups (after level 1 and 2 reduction, which is near 40 GB in our production environment).
 And let $C_0$, $C_s$ and $C_u$ denote the size of zero-filled block, system-related data and user-generated data in CDS,
 then the total size of CDS is represented by $C=C_0+C_s+C_u$.
-We let $S_0$, $S_s$ and $S_u$ denote the corresponding average space saving ratio (coverage) relative to $D$ in per VM's snapshot backups,
-so the total saving ratio is $S=S_0+S_s+S_u$.
+We let $S_0$, $S_s$ and $S_u$ denote the corresponding data coverage ratio (with respect to $D$) by $C_0$, $C_s$ and $C_u$,
+so the total space saving ratio is $S=S_0+S_s+S_u$.
 

### 2012-05-06 vm_snapshot_sim/2012concl.tex
some small updates

@@
 and the anonymous referees for their comments.
-This work was completed while Wei Zhang was a intern at Alibaba.
+Wei Zhang has received internship support from Alibaba  for VM backup system development.
 This work was supported in part by NSF IIS-1118106.
 Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
-do not necessarily reflect the views of the National Science Foundation.
+do not necessarily reflect the views of Alibaba or the National Science Foundation.
 }

### 2012-05-06 vm_snapshot_sim/main.tex
some small updates

@@
 \author{
-\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Hong Tang\IEEEauthorrefmark{2}, Hao Jiang\IEEEauthorrefmark{2}, Tao Yang\IEEEauthorrefmark{1}, Xiaogang Li\IEEEauthorrefmark{2}, Yue Zeng\IEEEauthorrefmark{2}}
+\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}, Hong Tang\IEEEauthorrefmark{2}, Hao Jiang\IEEEauthorrefmark{2}, Tao Yang\IEEEauthorrefmark{1}, Xiaogang Li\IEEEauthorrefmark{2}, Yue Zeng\IEEEauthorrefmark{2}}
 \IEEEauthorblockA{\IEEEauthorrefmark{1}Dept. of Computer Science, UC Santa Barbara. Email: \{wei, tyang\}@cs.ucsb.edu}

### 2012-05-06 vm_snapshot_sim/2012arch.tex
some small updates
two column graph

@@
 underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
-disks is tunneled by the virtual device driver (called TapDisk at Xen). To avoid network latency and congestion, 
+disks is tunneled by the virtual device driver (called TapDisk\cite{Warfield2005} at Xen). To avoid network latency and congestion, 
 our distributed file system place the primary replica of VM's 
@@
 
+\begin{figure*}[htbp]
+\centering
+\epsfig{file=images/vector.eps, width=7in}
+\caption{Number of duplicates vesus ranking}
+\label{fig:zipf-data}
+\end{figure*}
+
 We choose this two-level structure because in practice we observe that during each backup period only a small amount
@@
 %This is verified in  Section~\ref{sect:exper}.
+
 We have studied the popularity of common blocks in the OS and data disks from a dataset
@@
 
-\begin{figure}[htbp]
-\centering
-\epsfig{file=images/vector.eps, width=3.8in}
 %\epsfig{file=images/log-log.disk.eps, width=3in}
@@
 %\end{tabular}
-
-\caption{Number of duplicates vesus ranking}
-\label{fig:zipf-data}
-\end{figure}
 

### 2012-05-06 vm_snapshot_sim/2012background.tex
fixed some  typos
add keywordsand refs

@@
 
-Duplicate  search approximation~\cite{extreme_binning09,sparseindex09}  has been proposed 
+Duplicate  search approximation~\cite{extreme_binning09,sparseindex09,Xia2011}  has been proposed 
 %in extreme bining and other sparse indexing 
@@
 % since storage for shared identical content chunks can become a failure point.
-In large scale cloud, node faiures happen at daily basis,
+In large scale cloud, node failures happen at daily basis,
 the loss of a shared block can affect many users whose snapshots share this 

### 2012-05-06 vm_snapshot_sim/2012concl.tex
add keywordsand refs

@@
 \section*{Acknowledgments}
-{\small
+{
 We would like to thank Weicai Chen and Shikun Tian from Alibaba for their kind support, 

### 2012-05-06 vm_snapshot_sim/2012intro.tex
add keywordsand refs

@@
 %provides the largest public cloud in based on the open-source Xen technology.
-In a virtualized cloud environment such as ones provided by Amazon EC2 and Alibaba Aliyun,
+In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
 each instance of a guest operating system runs on a virtual machine, accessing

### 2012-05-07 vm_snapshot_sim/2012arch.tex
add keywordsand refs
small changes

@@
 
+\begin{figure*}[htbp]
+\centering
+\epsfig{file=images/vector.eps, width=7in}
+\caption{Number of duplicates vesus ranking}
+\label{fig:zipf-data}
+\end{figure*}
 The inner VM deduplication contains two levels of duplicate detection efforts and the representation of
@@
 \end{itemize}
-
-\begin{figure*}[htbp]
-\centering
-\epsfig{file=images/vector.eps, width=7in}
-\caption{Number of duplicates vesus ranking}
-\label{fig:zipf-data}
-\end{figure*}
 
@@
 
-Base on the Zipf-like distribution pattern, many previous analysis and results on web caching may apply.
+Base on the Zipf-like distribution pattern, many previous analysis and results on web caching\cite{Adamic2002,Breslau1999b} may apply.
 In general this indicates a small set of popular data dominates data duplication.
@@
   \centering
-  \epsfig{file=images/dedup_flow1.eps, width=3.8in}
+  \epsfig{file=images/dedup_flow1.eps, height=2.8in, width=3.8in}
   \caption{Illustration of snapshot deduplication dataflow.}

### 2012-05-07 vm_snapshot_sim/2012intro.tex
small changes

@@
 
-With these in mind, we  have developed a decentralized multi-level solution to conduct 
+With these in mind, we  have developed a distributed multi-level solution to conduct 
 segment-level  and block-level inner-VM  deduplication to localize the deduplication effort when possible.

### 2012-05-22 snapshot_system/design.tex
new paper started.

--- 2012-05-06 vm_snapshot_sim/2012background.tex
@@
-\section{Background and Related Work}
-\label{sect:background}
-
-In a VM cloud, several operations are provided for creating and managing snapshots and snapshot trees,
-such as creating snapshots, reverting to any snapshot, and removing snapshots.
-For VM snapshot backup, file-level semantics are normally not provided. 
-Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data.
-Only raw access information at disk block level are provided.
-%Snapshots may be shared among VMs when a user runs the same binary image on different  VMs.
-% This feature complicates the snapshot management, 
-%but also require all snapshots be managed in a global namespace.
-
-%While snapshot backup loads are heavy but computing and storage  resources available 
-%can be limited to reduce the overall operation cost of a cloud. The whole VM cluster have petabytes of data and need to 
-%be backed up at daily basis, if not more frequently. But at the same time snapshot tasks must not affect the normal VM operations
-%in a cloud service, which means only a tiny slice of CPU and memory can be used for this purpose.
-
-VM snapshots can be  backed up  incrementally by identifying file  blocks that have
-changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
-%Even though the snapshots are saved incrementally,
-%when deleting a snapshot, only the data not needed for any other snapshot is removed.
-%So regardless of which prior snapshots have been deleted, all active snapshots will contain
-%all the information needed to restore the virtual disk.
-%One widely used snapshot strategy is copy-on-write (CoW).
-%The earlier use of COW is to improve memory usage and reduce copying overhead in process 
-%management~\cite{OSbook,Waldspurger2002} and it can be extended for snapshot 
-%storage management~\cite{vmware_kb1015180}. 
-%C. Waldspurger. Memory Resource Management in VMware ESX Server in Proceedings of the 5th Symposium 
-%on Operating Systems Design and Implementation, 2002
-%Upon VM image storage system receives a save snapshot request,
-%it freezes the state of that image file, then all consequent write request will result in the write region being copied
-%to an incremental snapshot data file. 
-%Such a strategy exploits version difference between consecutive snapshots
-%of the same image.
-The main weakness
-is that it does not reveal content redundancy among data blocks from different snapshots or
-different VMs.
-%has several disadvantages:
-%first, CoW may affect the general I/O performance due to defered data coping. 
-%Second, CoW does not seperate backup data and runtime image data,
-%which have distinct access requirements: runtime image data is directly used by the running VM, 
-%thus need high throughput, and is very sensitive to latency,
-%such data must be served with hig cost hardware, but backup data generally only need fair aggregate throughput, 
-%is not sensitive to latency, thus can be stored in secondary storage devices.
-%Finally, VM snapshots contain tremendous amount of data duplication, which is nearly impossible to tackle 
-%if these two kinds of data are tightly coupled together.
-
-Data deduplication techniques can eliminate redundancy globally among different files from different users. 
-Backup systems have been developed to use content hash (finger prints) to identify duplicate 
-content~\cite{venti02,Rhea2008}.
-%,NGmiddleware2011}. 
-Today's commercial data backup systems (e.g. from EMC and NetApp)
-%\cite{emc_avamar}\cite{datadomain_whitepaper} 
-use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
-%Chunking divides a data stream into variable length chunks, it has been used to conserve bandwidth\cite{lbfs01}, 
-%search and index documents in large repositories\cite{bhag07}, scalable storage systems\cite{hydrastor09}, 
-%store and transfer large directory trees efficiently and with high reliability\cite{jumbo07}.
-\comments{
-To chunk a file, starting from the first byte, its contents as seen through a fixed-sized (overlapping) 
-sliding window are examined. At every position of the window, a fingerprint of its 
-contents, $f$, is computed using hashing techniques such as Rabin fingerprints~\cite{rabin81}. 
-When this fingerprint meets a certain criteria,
-% such as $f mod D = r$ where $D$, the divisor, 
-%and $r$ are predefined values; 
-the position of the corresponding window defines the boundary of the chunk. 
-This process is repeated until the entire file has been completely broken down into chunks. Next, 
-a cryptographic hash or chunk ID of the chunk is computed using a technique such as MD5 or SHA.
-After a file is chunked, the index containing the chunk IDs of backed up chunks 
-is queried to determine duplicate chunks. New chunks are written to disk and the 
-index is updated with their chunk IDs. A file recipe containing all the information 
-required during reconstruction is generated. The index also contains some metadata 
-about each chunk, such as its size and disk location.
-%The compression rate obtained by deduplication depends on the inherent content overlapping degree in a dataset, 
-%the average size of chunks, and the chunking method\cite{poli04}. 
-%In general, smaller chunks yield better deduplication.
-
-Data deduplication has been applied as  a post-processing operation for offline removal
-of redundant content in the file system data management once backup data is written in a temporary stage area.
-Dynamic inline deduplication is an effort to improve storage efficiency  
-by detecting and removing  duplicates before data is written to the backup storage,
-thus reduces extra disk space required to hold temporary data. 
-This approach requires a fingerprint  comparison of the new content chunks with
-previously stored fingerprints. 
-}
-As data grows to be big, fingerprint lookup in such schemes
-becomes too slow to be scalable.
-%and searching such disk
-%However, unless some form of locality or similarity is exploited, inline, chunk-based deduplication, 
-%when done at a large scale faces what has been termed the disk bottleneck problem: to facilitate fast chunk ID lookup, 
-%a single index containing the chunk IDs of all the backed up chunks must be maintained. 
-%As the backed up data grows, the index overflows the amount of RAM available and must be paged to disk. 
-%Without locality, the index cannot be cached effectively, and it is common for nearly 
-%every index access to require a random disk access. This disk bottleneck severely limits deduplication throughput.
-Several techniques have been proposed to speedup searching of duplicate 
-content. For example,  
-Zhu et al.~\cite{bottleneck08} tackle it 
-by using an in-memory Bloom filter and prefetch groups of chunk IDs that are likely to be 
-accessed together with high probability. It takes significant memory resource for filtering and caching.
-NG et al.~\cite{ NGmiddleware2011}  use  
-a related filtering technique for integrating deduplication in Linux  file system and the memory
-consumed is up to 2GB for a single machine. That is still too big in our context discussed below. 
-%Lillibridge et al.~\cite{sparseindex09} break list of chunks 
-%into large segments, the chunk IDs in each incoming segment are sampled and the segment is 
-%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments. 
-%These are segments that share many chunk IDs with the incoming segment with high probability.
-%Deepavali et al.~\cite{extreme_binning09}  use signature-based file similarity  and group similar files
-%into the same physical location (bins) to deduplicate against each other.
-
-Duplicate  search approximation~\cite{extreme_binning09,sparseindex09,Xia2011}  has been proposed 
-%in extreme bining and other sparse indexing 
-to package similar content in one location, and duplicate lookup  only searches
-for chunks within files which have a similar file-level or segment-level  content fingerprints.
-That leads  to a smaller amount of memory usage for storing meta data in signature
-lookup with a tradeoff of the reduced recall ratio.
-
-\section{Requirements and Design Options}
-\label{sect:options}
+\section{Design Overview}
+In this section we briefly describe all the static things in our system, such like architecture, each component’s data structure, data locations, relationship of data references, etc.
 
@@
 which are different from a traditional data backup.
-% That arises mainly in Alibaba's Aliyun cloud service.
-%concerns
-%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
+
 \begin{enumerate}
@@
 
-%snapshot service shall not compete cpu, memory, or I/O bandwidth with VMs. Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
 \item {\em Fast backup speed.}
@@
 
-%\section{Architecture design and Deduplication for Snapshot Support}
-%
-%\section{Popularity analysis}
-% data on what data popular.
-%
-%Analysis: modeling: singular
-%
-%Compute: Cache hit ratio vs. cache cost (memory cost).
+\subsection{Design Considerations}
+While this idea sounds conceptually simple, realizing it requires us to address three
+significant challenges:
+\begin{enumerate}
+\item {\em In-cloud backup}
+We decided to build 
+\item {\em Inline deduplication}
+Inline deduplication requires more resources and can suffer from latency issues as data is checked against metadata before being committed to disk or flagged as a duplicate.
+\item {\em Data dependency}
+
+\item {\em Backup speed}
+456
+\end{enumerate}
+\subsection{Architecture Overview}
+
+\subsection{Block Storage Device}
+\subsection{CDS}
+Although locality based data reduction can remove most of the inner-VM duplications,
+it's not able to solve the data duplication cross VMs. Different VMs still share large amount
+of common data such that their snapshot backups would have a lot of data in common.
+Our observations on Aliyun's real VM user data reveals several major sources of cross-VM data duplication:
+  \begin{enumerate}
+  \item \emph{System-related data}: These data are generated by public third-parties, they are copied/downloaded/installed into VM disks either automatically or manually.
+Once installed, operations on such data are mostly read only until software updates arrive.
+For example, data of operating systems, some widely-used software such as Apache and MySQL, and their documations all fall into this category.
+  \item \emph{User-generated data}: These data are generated by individual user's behavior, either directly or indirectly.
+They are much less duplicated than the system-related data, but the zipf-like distribution indicates that a small amount of data in this category could represent most of data duplications.
+  \item \emph{Zero-filled data}: Like previous studies [refs here], we've observed that zero-filled data exist pervasively at system wide.
+They are almost like the spaces and commas in text articles.
+Under content-based chunking, they were distilled as zero-filled blocks with the maximum allowed length.
+%Zero-filled blocks are mostly generated by user behavior to preserve the space for future data, thus we treat them as a special case of user-generated data.
+  \end{enumerate}
+
+Without eliminating the data duplication between VM snapshot backups, storage space is severely wasted when the number of VMs increases.
+To address this problem, we developed a technique called \emph{Common Data Set (CDS)} to eliminate data duplication for all three situations above. 
+CDS is a public data library that shared by all VM snapshot backups in the cluster, 
+which consists of the most popular data blocks in VM snapshot backups. It is generated, 
+managed and accessed in an uniform manner by all VMs such that [write some fancy system characteristic stuff here].
+
+\subsection{CDS Size V.S. Coverage}
+As a shared data library, we expect CDS to collect almost all the system related data, the most popular user-generated data and the zero-filled data block.
+With CDS as a public data reference, each VM's snapshot backup has no need to store its own copies for data that can be found in CDS, instead they can just
+store a reference.
+
+The more data we put into CDS, the closer we come to complete deduplication. But in reality we are facing a list of restrictions such like [blabla].
+We borrowed the idea of web caching[refs here] to analysis the size of CDS vesus its effectiveness on data reduction.
+
+We let $M$ be the number of nodes in a cluster, $N$ be the number of VMs hosted per node,
+and let $D$ denotes the average size of one VM's snapshot backups (after level 1 and 2 reduction, which is near 40 GB in our production environment).
+And let $C_0$, $C_s$ and $C_u$ denote the size of zero-filled block, system-related data and user-generated data in CDS,
+then the total size of CDS is represented by $C=C_0+C_s+C_u$.
+We let $S_0$, $S_s$ and $S_u$ denote the corresponding data coverage ratio (with respect to $D$) by $C_0$, $C_s$ and $C_u$,
+so the total space saving ratio is $S=S_0+S_s+S_u$.
+
+Zero-filled block at maximum length is the first item we need to put into CDS. This is the one and only special data block, 
+and because CDS only stores unique data blocks, $C_0$ is almost equal to 0. In practice we found zero-filled blocks account
+for near 20\% of total data, so $S_0$ is 20\%.
+
+The rarely modified system-related data are the second to be added to CDS. We have thousands of VMs in each cluster, 
+but all these VMs fall into only a few OS types, using a limited selection of software, therefore data duplication in this category
+is highly noticable in a global block counting. In particular, most of such data already exist in the VM base images. 
+We analyzed VMs running various services from 7 mainstream OS types in our cluster, and found close to 50GB of such data in total. 
+Because system-related data don't change frequently, it's safe to expect that for 20 OS variations 
+and software updates in 2 years, $C_s$ will not grow to exceed 200 GB.
+For each VM, from 2 to 20 GB of data can be reduced in this way, depends on the OS and service type, so on average we estimate
+$S_s$ would be no less than 20\%.
+
+The rest of data are user-generated, the total size of such data can be written as $D_u=D-S_0-S_s$, which is 60\% of $D$. 
+It follows a zipf-like distribution with $\alpha$ between 0.65 to 0.7. 
+Let $T_u$ be the total size of unique data blocks in $D_u$,
+in practice we notice that complete deduplication for such data always result in a 2:1 reduction ratio,
+, so $T_u=D_u/2$.
+Since we collect the most popular user-generated data into CDS, the coverage of CDS on user-generated data
+is $(C_u/T_u)^{1-\alpha}$.
+
+The following table lists CDS coverage on user-generated data under different $\alpha$ and $C_u/T_u$.
+
+[a table of coverage with alpha from 0.65-0.70, ratio from 0.002 0.005 0.01 0.02 0.05]
+
+It's obviously that at least 30\% of user-generated data can be reduced in this way, using about 0.02 of $T_u$, or 0.01 of $D_u$.
+The size of user-generated data in CDS would be 0.006$D$, with coverage $S_u=0.18D$.
+
+Thus the estimation of CDS coverage is $S=S_0+S_s+S_u=0.58$, with the size of CDS to be no more than $(200 + 0.006*D*N)$ GB.
+In a VM cluster of 100 machines, with 25 VMs on each physical machine, the size of CDS is 800 GB in total, or 8 GB per machine.
+The total size of CDS index would be 8 GB, which will cost 80 MB memory on each machine. 
+\subsection{Append Store}

### 2012-05-22 snapshot_system/main.tex
conference templates
new paper started.

--- 2012-01-30 vm_snapshot_sim/main.tex
@@
-\documentclass[finalversion]{usetex-v1}
-%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
+\documentclass{acm_proc_article-sp}
 \usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
 \usepackage{epsfig}
-%\usepackage{breakurl}
-%% Define a new 'leo' style for the package that will use a smaller font.
-\makeatletter
-\def\url@leostyle{%
-  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
-\makeatother
-%% Now actually use the newly defined style.
-\urlstyle{leo}
-%\linespread{1.2}
-%\setlength{\parskip}{1ex}
+
 \begin{document}
-\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
-\author{Wei Zhang, Hong Tang, Hao Jiang, Rachael Zeng, Xiaogang Li, Tao Yang}
-\date{}
+
+\title{An In-Cloud Backup System With Deduplication for VM Snapshot}
+
+\numberofauthors{7}
+\author{
+\alignauthor Wei Zhang\\
+       \affaddr{CS Dept.}\\
+       \affaddr{UC Santa Barbara}\\
+       \email{wei@cs.ucsb.edu}
+\alignauthor Hong Tang\\
+       \affaddr{Aliyun Inc.}\\
+       \affaddr{Alibaba Group}\\
+       \email{hongtang@alibaba-inc.com}
+\alignauthor Tao Yang\\
+       \affaddr{CS Dept.}\\
+       \affaddr{UC Santa Barbara}\\
+       \email{tyang@cs.ucsb.edu}
+}
+
 \maketitle
 
-\input{abstract}
-\input{intro} %introduce the problem, related solutions and our requirements
-\input{cds} %data study, zipf, model of cds size and dedup efficiency
-\input{approach} %our dedup process
-\input{results}
-%\input{related}
-%\input{future}
-\input{conclusion}
+\input{abs}
+
+% A category with the (minimum) three required fields
+\category{H.4}{Information Systems Applications}{Miscellaneous}
+%A category including the fourth, optional field follows...
+\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+
+\terms{Theory}
+
+\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+
+\input{intro}
+\input{design}
+\input{snapshot}
+\input{append}
+\input{cds}
+\input{failover}
+\input{result}
+\input{con}
+
 \bibliographystyle{abbrv}
-\bibliography{dedup}
+\bibliography{library}
 \end{document}

### 2012-08-25 snapshot_system/abs.tex
just test

\begin{abstract}
This paper proposes a VM snapshot storage architecture which adopts multiple-level selective deduplication to bring the benefits of fine-grained data reduction into cloud backup storage systems.
In this work, we describe our working snapshot system implementation, and provide
early performance measurements for both deduplication impact and
snapshot operations.
Thank you!
\end{abstract}

### 2012-08-25 snapshot_system/append.tex
Append store chapter

\section{Append Store}
\subsection{Introduction}
Append Store (AS) is our underlining storage engine for storing snapshot data after deduplication. 
AS is built on top of our highly scalable distributed file system (DFS), 
which is very similar to Google's file system
in a sense that it is optimized for large files and sequential read/append operations.

\subsection{Design considerations}
While scalability has been handled by the DFS, there are still several challenges in 
storing billions of var-sized small data chunks:
\begin{description}
\item[Locality perseveration] Chunk data must be placed next to each other in the order of their writing sequence,
because reading a snapshot incurs large sequential reads of chunks under their logical sequence in the snapshot.
\item[Flexible referencing] To avoid overwhelming metadata operation capbility of DFS's master, 
we have to group small chunks into large data files in DFS.
However, snapshot deletion brings chunk data deletion, and reclaiming disk space would require many chunk data being moved.
If such chunk movement incurs updates of data referencing in snapshot and segment recipes, then the cost of deleting 
a snapshot would be extremely high.
\item[Efficient chunk lookup] The translation from data reference to data location must be very efficient in two ways: 
first, a sorted index is necessary to fast locate the data location in $O(log(n)$ time; 
second, the size of index must be optimized to minimized its memory footprint and the cost of fetching index. 
\end{description}

\subsection{Architecture}
\begin{figure}[htbp]
  \centering
  \epsfig{file=images/append_store_arch.eps, width=3.5in}
  \caption{Architecture of Append Store}
  \label{fig:as_arch}
\end{figure}

Append Store supplies three interfaces: {\em get(ref)} accepts a data reference and retrives data, 
{\em put(data)} accepts data and returns a reference to be stored in metadata recipes, 
{\em delete(ref)} 
deletes the data pointed by the reference.
Under the hood, small var-sized data are grouped and stored into larger data containers. Each VM has
its snapshot data stored in its own Append Store, specified by the VM ID. 
We split every Append Store into multiple data containers so that reclaiming the disk space would not 
result in rewriting all the data at the same time.

As shown in Fig.\ref{fig:as_arch}, every data container is represented as three data files in DFS:
the data file holds all the actual data, the index file is responsible for translating data reference
into data locations, and a deletion log file remembers all the deletion requests to the container.

A data reference is composed of two parts: a container ID (2 bytes) and CID (6 bytes).
Append Store assign every piece of data a CID for its internal data referencing. 
When new data is appended, its CID is the current largest CID in that container plus one.
As a result, all the data locations are naturally indexed by this self-incremental CID, 
no extra sorting is needed.

Append Store groups multiple chunk data (i.e., 100) into larger units, called {\em CBlock}.
CBlock is the basic unit for append store's internal read/write/compression.
There is one index entry in the container index corresponding to every CBlock. It keeps the first chunk's CID
in that CBlock, and the CBlock data's size and location.

Using CBlock brings us several advantages: First, the write workload to DFS master is greatly reduced; second, grouping
small chunks gives better compression. Third, reading a CBlock (200 - 600 KB) typically cost the same amount of disk 
seek as reading a 4KB chunk. Finally, this greatly reduces the size of index. Let $m$ be the number of chunks in each
CBlock, then the overall index size is reduced to $1/m$. In our implementation, using $m=100$ reduces the index for
a 1GB container from 10 MB to 100 KB.

\subsection{Operations}
In order to read a chunk data by reference, Append Store client first loads the
container index file specified by the container ID, then search the CBlock index to find the entry that covers the chunk by CID.
After that, it reads the whole CBlock data from DFS, decompress it, seek the exact chunk data specified by CID. 
Finally, the client updates itws internal chunk data cache with the newly loaded contents to anticipate future sequential reads.

Write requests to append store are accumlated. When the number reaches $m$, the AS client forms a CBlock by assigning 
every chunk a CID, compress the CBlock data, and append it to the CBlock data file. Then a new CBlock index entry is appended
to CBlock index.

Append store adopts lazy delete strategy. The deletion requests are appended into every container's deletion log file with the CID of data to be deleted.
CIDs in deletion log are guaranteed to be referenced by nobody and can be safe deleted in future. 
Periodically, snapshot management system asks append store to compact containers in order to reclaim disk space. 
The actual compaction will only take place when the number of deleted items reached $d\%$ of container's capacity. 
During compaction, append store creates a new container (with the same container ID) to replace the 
existing one. This is done by sequentially scan the old container, copying all the chunks that are not 
found in deletion log to the new container, creating new CBlocks and indices. 
However, every chunk's CID is plainly copied rather than re-generated. This does not affect the sorted
order of CIDs in new container, but just leaving holes in CID values. As the result, all data references stored 
in upper level recipes are unaffected, and the data reading process is as efficient as before.

%hard problems

\subsection{Analysis}

Snapshot operation performance analysis:
\begin{table}
    \begin{tabular}{l p{1.5in} l}
        \hline
        Symbol & Description & Measurement \\ \hline
        $N_{seg}$ & Number of segments in the snapshot & ~ \\ [1ex] \\ [-1.5ex]
        $N_{chunk}$ & Number of chunks in one segment & ~ \\ [1ex] \\ [-1.5ex]
        $P_{dirty}$ & Probablity of a segment is dirty & ~ \\ [1ex] \\ [-1.5ex]
        $P_{new}$ & Percentage of new data & ~ \\ [1ex] \\ [-1.5ex]
        $P_{change}$ & Probablity that a chunk is not found in parent snapshot & ~ \\ [1ex] \\ [-1.5ex]
        $P_{in\_CDS}$ & Percentage of chunks in CDS & ~ \\ [1ex] \\ [-1.5ex]
        $T_{scan}$ & Time to scan segment data and caculate content hash & 74 ms \\ [1ex] \\ [-1.5ex]
        $T_{write\_AS}$ & Time of writing a chunk into append store & 0.24 ms \\ [1ex] \\ [-1.5ex]
        $T_{read\_AS}$ & Time of reading a chunk from append store & ~ \\ [1ex] \\ [-1.5ex]
        $T_{read\_chunk}$ & Time of reading a chunk & ~ \\ [1ex] \\ [-1.5ex]
        $T_{check\_CDS}$ & Time of checking CDS & ~ \\ [1ex] \\ [-1.5ex]
        $T_{read\_CDS}$ & Time of reading a chunk data from CDS data store& ~ \\
        \hline
    \end{tabular}
    \caption{List of performance factors}
    \label{tab:as_param}
\end{table}

The overall time of writing a snapshot is:

\begin{dmath}
T_{write} = P_{dirty} * N_{seg} * [max(T_{scan}, T_{read\_AS}) + P_{change} * N_{chunk} * T_{check\_CDS} + P_{new} * N_{chunk} * T_{write\_AS}]
\end{dmath}

The overall time to read a snapshot is:

\begin{dmath}
T_{read} = N_{seg} * {T_{read\_AS} + N_{chunks} * [P_{in\_CDS} * T_{read_CDS} + (1 - P_{in\_CDS}) * T_{read\_chunk}]}
\end{dmath}

Average time of reading a chunk:

\begin{dmath}
T_{read\_chunk} = P_{in\_CDS} * T_{read\_CDS} + (1 - P_{in\_CDS}) * T_{read\_AS}
\end{dmath}

Time of reading append store:

\begin{dmath}
T_{read\_AS} = 0 * P_{in\_cache} + (1 - P_{in\_cache} ) * T_{load\_CBlock}
\end{dmath}

### 2012-08-25 snapshot_system/design.tex
Append store chapter

@@
 
+Overall, our contributions are:
+\begin{enumerate}
+\item {\em CDS. parallelism, localized}
+We designed a highly efficient global deduplication scheme using common data between VMs as the primary
+deduplication target, which adopts to our resource-constrained production environment very well. We developed a fast
+approxmation algorithm to extract the commonly used data from VM snapshot backups.
+
+\item {\em Append Store.}
+We address the problem of managing billions of small variable-sized data objects by building an append store
+on top of our distributed file system (DFS). We carefully designed an efficient index data structure to 
+optimize large sequential read/write requests, while minimize the cost of key to object location conversion.
+
+\item {\em Fast Data Deletion.}
+Traditional deletion in deduplication systems involves reference counting, either online or offline. Both ways
+are costly due to the sharing of large amount of data objects.
+We avoid this cost of data deletion with an approxmation deletion method using bloom filters.
+
+\item {\em Fault-tolerant.}
+Golbal deduplication brings data sharing across different users VM snapshots, therefore a single failure
+on some data can break many VMs' snapshots. We avoid such all-to-all data dependency by restricting
+the cross VM data sharing with the CDS. By taking extra care of protecting CDS data, 
+the overall degree of fault tolerancy is guaranteed.
+
+\end{enumerate}
+
 \subsection{Design Considerations}
@@
 \item {\em Backup speed}
-456
+
 \end{enumerate}
 \subsection{Architecture Overview}
+Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China 
+based on Xen~\cite{Xen2003}. A typical VM cluster in our cloud environment
+consists of from hundreds to thousands of physical machines, each of which can
+host tens of VMs.
+
+A GFS-like distributed file system holds the responsibility of managing physical disk storage
+in the cloud. All data needed for VM services, which include runtime VM disk images and snapshot backup data,
+reside in this distributed file system.
+During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
+copies the corresponding pre-configured base VM image to her VM as the OS disk, 
+and an empty data disk is created and mounted onto her VM as well. 
+All these virtual disks are represented as virtual machine image files in our
+underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
+disks is tunneled by the virtual device driver (called TapDisk\cite{Warfield2005} at Xen). To avoid network latency and congestion, 
+our distributed file system place the primary replica of VM's 
+image files at physical machine of VM instance.
+During snapshot backup, concurrent disk write is logged 
+to ensure a consistent snapshot version is captured.
+
+Figure~\ref{fig:arch} shows the architecture view of our snapshot service
+at each node. The snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
+The inner-VM  deduplication is conducted by the broker to access meta data in the snapshot data store
+and we discuss this in details in Section~\ref{sect:innerVM}.
+The cross-VM deduplication is conducted by the broker to access 
+a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
+whose block hash index is stored in a distributed memory cache. 
+\begin{figure}[htbp]
+  \centering
+  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
+  \epsfig{file=images/arch.eps, width=3.9in}
+  \caption{Snapshot backup architecture of each node.}
+  \label{fig:arch}
+\end{figure}
+The snapshot store 
+supports data access operations such as \emph{get}, \emph{put} and \emph{delete}.
+Other operations include data block traverse and resource usage report.
+The snapshot data does not need to be
+co-located with VM instances, and in fact they can even live in a different cluster to improve the 
+data reliability: when one cluster is not available, we are still able to restore its VMs from another cluster which
+holds its snapshot data. 
+%to reduce the impact to our users.
+%Get interface accepts a piece of data, write it to the underline data file, and return
+%a reference to the caller. This reference then can be used in the put interface to
+%retrive or delete the data, thus the caller of put interface must preserve the
+%data reference for future use. 
+%In addition to above standand data access operations, the snapshot service also supports
+%\emph{scan} and \emph{quota} methods. Scan allows us to traverse all the data blocks of each VM
+%in the snapshot store, and quota is used to acknowledge user how much space he
+%has actually used.
+
+Under the hood of snapshot store, it organizes and operates snapshot data 
+in the distributed file system. We let each virtual disk has its own snapshot store, 
+and no data is shared between
+any two snapshot stores, thus achieve great fault isolation. For those selected popular data
+that shared by many VM snapshot stores, we could easily increase its availability by having more replications.
+%Since all the underline data structures is append only,
+%upon a delete request, the corresponding data will only be marked rather than being deleted.
+%A compaction will take place when deleted data has accumulated to a certain threshold, thus 
+%reclaiming the disk space .
 
@@
 The total size of CDS index would be 8 GB, which will cost 80 MB memory on each machine.
+
 \subsection{Append Store}

### 2012-08-28 snapshot_system/delete.tex
Add deletion analysis

\section{Deletion}
In a mature VM cluster, snapshot deletions are as frequent as snapshot creations.
Our system adopts lazy delete strategy so that all snapshot deletions are scheduled
in the backup time window at midnight. 
Therefore, snapshot deletions must be fast enough to fit in time window and
efficient enough to satisfy our resource constraints.
However, there is no simple solution can achieve these goals with high reliability.
In Aliyun's cloud, we use a {\em fuzzy deletion} method to trade deletion accuracy for
speed and resource usage. This method tolerates a tiny percentage of storage leakage
to make the deletion operation faster and efficient by an order of magnitude,
yet we still adopt an slow but accurate deletion method to fix such leakage in the long-term.
Our hybrid deletion strategy, using fuzzy deletion regularly and accurate deletion periodically,
accomplishs our speed, resource usage and relibility goals very well.

\subsection{Challenges}
Contrary to a traditional backup system, a dedupe system shares data among files by default. 
Reference management is necessary to keep track of chunk usage and reclaim freed space. 
In addition to scalability and speed, reliability is another challenge for reference management. 
If a chunk gets freed while it is still referenced by snapshots, data loss occurs and files cannot be restored. 
On the other hand, if a chunk is referenced when it is actually no longer in use, it causes storage leakage.

Reference counting, while being simple, suffers from low reliability especially in our distributed environment, 
because it is vulnerable to lost or repeated updates: when errors occur some chunks maybe updated and some may not. 
Complicated transaction rollback logic is required to make reference counts consistent. Moreover, 
there is almost no way to verify if the reference count is correct or not in a large dynamic system. 
In real deployments, where data integrity and recoverability directly affect product reputation, simple reference counting is unsatisfactory.

Mark-and-sweep is generally a better solution. During the mark phase, all snapshot recipes are traversed so as to mark the used chunks. 
In the sweep phase all chunks are swept and unmarked chunks are reclaimed. 
This approach is very resilient to errors: at any time the process can simply be restarted with no negative side effects. 
Scalability, however, is an issue. {\em needs to explain its resource usage}

\subsection{Accurate Deletion}
Our accurate deletion uses mark-and-sweep to find all the unused chunks in a VM's append store.
The following steps would take place during an accurate deletion:

\begin{enumerate}
\item Scan all the containers. For each container, extract full list of existing data references and allocate a bitmap. 
(Notice this list is self sorted.)
\item Scan all the snapshot recipes and segment recipes. For every data reference pointing to append store,
find it in the above lists and mark the corresponding position in bitmaps.
\item Scan the bitmaps, for every bit that are not marked, tell append store the corresponding data reference can be deleted.
\end{enumerate}

Although accurate deletion guarantees reliability and correctness, its speed and resource usage are big problems to our VM cloud.
Let $T_{scan\_AS}$ be the time to scan the VM's append store, $T_{scan\_recipes}$ be the time to scan one snapshot recipe
and its segment recipes, $T_{mark}$ be the time of finding a data reference in the list and mark bitmap, 
$N_{SS}$ be the number of snapshots and $N_c$ be the number of chunks in one snapshot.
The overall time of running an accurate deletion for one VM is:
\begin{equation}
T = T_{scan\_AS} + N_{SS} * T_{scan\_recipes} + N_{SS} * N_c * T_{mark}
\end{equation}

For a virtual disk that has 10 snapshots, 50 GB of data in the append store, $T_{scan\_AS}$ would have cost half an hour already.
In addition, scanning recipes of 10 snapshots cost another 5 minutes.
Furthermore, maintaining the full lists of data references and bitmaps costs about 100 MB of memory. Having tens of VMs
co-lived in one physical machine and deleting snapshot on a daily basis, 
it's infeasible to run accurate deletion as frequent as snapshot deletions.

\subsection{Fuzzy Deletion}
We design fuzzy deletion to fast identify unused data in the append store.
Instead of scanning the whold append store, it uses a bloom filter to check 
if a data are still referenced by living snapshots. However, there is a small false-positive probility which
would indetify unused data as in use, i.e., storage leakage.
The following steps would take place during an fuzzy deletion:

\begin{enumerate}
\item {\bf Creating bloom filter} Scan all the living snapshot recipess and their segment recipes,
for every reference pointing to append store, add it to the bloom filter.
\item {\bf Check existance} For every data reference in the deleted snapshot recipe and its segment recipes,
check the existance of that data reference in bloom filter. If not found, it is safe to delete that piece of data from append store
because no living snapshots has referenced it.
\end{enumerate}

The overall time of running a fuzzy deletion for one snapshot deletion would be scanning
all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
parallel and is much faster than loading recipes from DFS:
\begin{equation}
T = (N_{SS} + 1) * T_{scan\_recipes}
\end{equation}

Using the example and analysis in previous section, this fuzzy deletion can be done in 5 minutes. 
Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
when set $P_{bl}$ to 0.01, the memory footprint of fuzzy deletion is about 15 MB.

The design goal of fuzzy deletion is to reduce the frequency of running accurate deletion.
For one VM's snapshots, let $D_{leakage}$ be the amount of storage leakage, $D_{del}$ be the average amount of data
to be deleted in one snapshot deletion, 
then we have:
\begin{equation}
D_{leakage} = N_{fuzzy} * P_{bl} * D_{del}
\end{equation}
where $N_{fuzzy}$ is the number of runs of fuzzy deletion. 
An accurate deletion is triggered to fix the storage leakage
when $D_{leakage}/D_{del}$ is accmulated to exceed certain threshold $T$:
\begin{equation}
D_{leakage} / D_{del} = N_{fuzzy} * P_{bl} > T \Rightarrow N_{fuzzy} > T/P_{bl}
\end{equation}
Therefore, when $P_{bl} = 0.01$ and $T=1$, 
there would be a run of accurate deletion for every $T/P_{bl} = 100$ runs of fuzzy deletion.
On a machine that hosts 20 VMs and each VM deletes snapshot daily, there would be less than
one accurate deletion executed per day.

\subsection{Discussion}
When a snapshot is scheduled for deletion, we always choose fuzzy deletion.

### 2012-09-14 snapshot_system/delete.tex
add pdf
add snapshot system introduction

@@
 On a machine that hosts 20 VMs and each VM deletes snapshot daily, there would be less than
-one accurate deletion executed per day.
+one accurate deletion scheduled per day.
 
 \subsection{Discussion}
-When a snapshot is scheduled for deletion, we always choose fuzzy deletion.

### 2012-09-14 snapshot_system/design.tex
add snapshot system introduction

--- 2012-05-22 snapshot_system/design.tex
@@
 \item {\em Backup speed}
-456
+
 \end{enumerate}
-\subsection{Architecture Overview}
+% \subsection{Architecture Overview}
+% Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China 
+% based on Xen~\cite{Xen2003}. A typical VM cluster in our cloud environment
+% consists of from hundreds to thousands of physical machines, each of which can
+% host tens of VMs.
 
-\subsection{Block Storage Device}
+% A GFS-like distributed file system holds the responsibility of managing physical disk storage
+% in the cloud. All data needed for VM services, which include runtime VM disk images and snapshot backup data,
+% reside in this distributed file system.
+% During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
+% copies the corresponding pre-configured base VM image to her VM as the OS disk, 
+% and an empty data disk is created and mounted onto her VM as well. 
+% All these virtual disks are represented as virtual machine image files in our
+% underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
+% disks is tunneled by the virtual device driver (called TapDisk\cite{Warfield2005} at Xen). To avoid network latency and congestion, 
+% our distributed file system place the primary replica of VM's 
+% image files at physical machine of VM instance.
+% During snapshot backup, concurrent disk write is logged 
+% to ensure a consistent snapshot version is captured.
+
+% Figure~\ref{fig:arch} shows the architecture view of our snapshot service
+% at each node. The snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
+% The inner-VM  deduplication is conducted by the broker to access meta data in the snapshot data store
+% and we discuss this in details in Section~\ref{sect:innerVM}.
+% The cross-VM deduplication is conducted by the broker to access 
+% a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
+% whose block hash index is stored in a distributed memory cache. 
+% \begin{figure}[htbp]
+%   \centering
+%   %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
+%   \epsfig{file=images/arch.eps, width=3.9in}
+%   \caption{Snapshot backup architecture of each node.}
+%   \label{fig:arch}
+% \end{figure}
+% The snapshot store 
+% supports data access operations such as \emph{get}, \emph{put} and \emph{delete}.
+% Other operations include data block traverse and resource usage report.
+% The snapshot data does not need to be
+% co-located with VM instances, and in fact they can even live in a different cluster to improve the 
+% data reliability: when one cluster is not available, we are still able to restore its VMs from another cluster which
+% holds its snapshot data. 
+% %to reduce the impact to our users.
+% %Get interface accepts a piece of data, write it to the underline data file, and return
+% %a reference to the caller. This reference then can be used in the put interface to
+% %retrive or delete the data, thus the caller of put interface must preserve the
+% %data reference for future use. 
+% %In addition to above standand data access operations, the snapshot service also supports
+% %\emph{scan} and \emph{quota} methods. Scan allows us to traverse all the data blocks of each VM
+% %in the snapshot store, and quota is used to acknowledge user how much space he
+% %has actually used.
+
+% Under the hood of snapshot store, it organizes and operates snapshot data 
+% in the distributed file system. We let each virtual disk has its own snapshot store, 
+% and no data is shared between
+% any two snapshot stores, thus achieve great fault isolation. For those selected popular data
+% that shared by many VM snapshot stores, we could easily increase its availability by having more replications.
+% %Since all the underline data structures is append only,
+% %upon a delete request, the corresponding data will only be marked rather than being deleted.
+% %A compaction will take place when deleted data has accumulated to a certain threshold, thus 
+% %reclaiming the disk space .
+
+% \subsection{Block Storage Device}
 \subsection{CDS}

### 2012-09-14 snapshot_system/snapshot.tex
add snapshot system introduction

\section{Multi-level Snapshot Deduplication}
\label{sect:dedupe}

\subsection{Snapshot System}
%system arch
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China. 
A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of xen-based\cite{Barham2003} VMs.

Aliyun has built a hadoop-like platform, which includes
several highly scalable cloud infrastructure services to support
 runing large scale VM cloud service:
\begin{itemize}
\item \textbf{DFS}: a distributed file system that is optimized for many large and sequential reads or appends.
\item \textbf{KV}: a distributed key-value store for managing structured data.
\item \textbf{MP}: a distributed data processing framework which is similar to Map-Reduce\cite{Dean2004}.
\item \textbf{MemCache}: a distributed memory object caching system.
\end{itemize}
%GFS-like\cite{googlefs03} 
%BigTable-like\cite{Chang2008a} 
Our snapshot system and the virtual machine management service rely on these basic cloud services
to be functional:
DFS holds the responsibility of managing physical disk storage
in the cloud, all data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
In addition, our snapshot system 
places the index of CDS in MemCache for deduplication, 
stores small amount of snapshot metadata in KV, and uses FX to facilitate the offline
data processing. All the above services can easily find their open-source counterparts,
which shows the generality of our architecture and deduplication scheme.

User control VMs through the virtual machine management service.
During VM creation, a user chooses a pre-configured VM image or
a snapshot that contains an OS,
then the VM management service 
copies the corresponding VM image to her VM as the OS disk.
Data disks can be created and mounted onto the VM in the same way,
either empty or from an existing snapshot. 
All these virtual disks are represented as virtual disk image files in our
underline runtime VM storage system.  
To avoid network latency and congestion, 
our distributed file system place the primary replica of VM's 
image files at physical machine of VM instance.
When user deletes her VM, all the runtime virtual disk images and
their snapshot data are removed from DFS.

%ss operations
In each VM, 
the runtime I/O between virtual machine and its virtual
disks is tunneled by the virtual device driver (called TapDisk\cite{Warfield2005} at Xen).
This is also where our snapshot system is built in. Three major snapshot operations are supported:
\begin{itemize}
\item \textit{Write snapshot}: save the current state of virtual disk as a snapshot.
This is also where data deduplication would take place.
During snapshot backup, concurrent disk write is logged 
to ensure a consistent snapshot version is captured. 
\item \textit{Read snapshot}: restore the state of virtual disk from a snapshot.
\item \textit{Delete snapshot}: delete a snapshot and reclaim the disk space for unused data.
\end{itemize}

\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
  \epsfig{file=images/arch.eps, width=3.9in}
  \caption{Snapshot backup architecture of each node.}
  \label{fig:arch}
\end{figure}

Figure~\ref{fig:arch} shows the architecture view of our snapshot service
at each node. The snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
The inner-VM  deduplication is conducted by the broker to access meta data in the snapshot data store
and we discuss this in details in Section~\ref{sect:innerVM}.
The cross-VM deduplication is conducted by the broker to access 
a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
whose block hash index is stored in a distributed memory cache.

%snapshot representation
\subsection{Snapshot Representation}
The virtual device driver uses a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break 
segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/snapshot_representation.eps, width=3.7in}
  \caption{An example of snapshot representation.}
  \label{fig:snapshot}
\end{figure}
As a result, the representation of each snapshot is designed as a two-level index data structure 
in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
that holds the meatdata of its chunks. We choose this two-level structure because in practice we
observe that during each backup period only a small amount of VM data are added or modified. 
As the result, even the metadata of two snapshots can be highly similar, 
thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
segments which greatly ease the segment-level deduplication.

In both two kind of recipes, 
they do not include the actual data but only have
 references point to the data which are either stored in append store or CDS.
In our implementation the data reference is a 8 bytes field which is either an 
ASID (discuss in \ref{sect:append} or an offset of 
An additional flag indicates

\subsection{Multi-level Deduplication}
The multi-level deduplication scheme is designed base on the observations on the VM snapshot data from production cloud.
We found snapshot data duplication can be easily classified into two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize the cost of deduplication while maximize the its efficiency at each level,
and it is highly parallelizable since each segment is processed independently.

\subsubsection{Inner-VM Deduplication}
\label{sect:InnerVM}
The first-level deduplication is logically localized within each VM.
Such localization increases data independency between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.

The inner VM deduplication contains two levels of duplicate detection efforts:
\begin{itemize}
\item \textit{Level 1 Segment modification detection}.
If a segment is not changed, then its segment recipe can be simply reused by copying the data
reference from previous snapshot recipe. 
\item \textit{Level 2  Chunk fingerprint comparison.}
If a segment is modified, we perform fine-grained deduplication 
by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
thus eliminate partial data duplication within the segment.
\end{itemize}

In general, operations at level 1 have almost no cost and most of unmodified data are filtered here. 
To process a dirty segment at level 2, 
there requires no more than one DFS access to load the segment recipe from previous snapshot,
and a tiny amount of memory to hold it in main memory.
\textit{may need details here}

\subsubsection{Cross-VM Deduplication}
\label{sect:CrossVM}

\subsection{Common Data Set}
%arch
%analysis

### 2012-12-20 snapshot_system/challenge.tex
paper update

\section{Challenges}
\subsection{Indexing}
Most deduplication systems operate at the sub-file level:
a file or a data stream is divided into a sequence of fixed
or variable sized segments. For each segment, a cryptographic
hash (MD5, SHA-1/2, etc.) is calculated as its
fingerprint (FP), and it is used to uniquely identify that
particular segment. A fingerprint index is used as a catalog
of FPs stored in the system, allowing the detection
of duplicates: during backup, if a tuple of the form <
FP, location > exists in the index for a particular
FP, then a reference to the existing copy of the chunk
is created. Otherwise, the chunk is considered new, a
copy is stored on the server and the index is updated accordingly.
In many systems, the FP index is also crucial
for the restore process, as index entries are used to locate
the exact storage location of the chunks the backup
consists of.

The index needs to have three important properties:
1) scale to high capacities, 2) achieve good indexing
throughput, and 3) provide high duplicate detection
rate—i.e., high deduplication efficiency. Table 1 demonstrates
how these goals become very challenging for a
Petascale system. Consider a typical virtualized cloud 
in which 10,000 VMs store 1 PB data, and the
chunk size is 4 KB (for fine-granularity duplicate detection),
indexing capacity will need to be at least 10,000
GB to support all 250 billion objects in the system. Such
an index is impossible to maintain in memory. Storing it
on disk, however, would greatly reduce query throughput.
To support 1000 concurrent snapshot backup tasks, 
an aggregate throughput of 20 GB/sec, would require the
index and the whole dedupe system for that matter
to provide a query service throughput of at least 5,000
Kops/sec. Trying to scale to 1 PB by storing the index
on disk would make it impossible to achieve this level
of performance. Making the chunk size larger (e.g.,
128 KB) would make deduplication far more coarse and
severely reduce its efficiency.

Even we can distribute the index over the cloud machines,
the resources that can be allocated to system services are
limited to minimize the negative impact to user experiences. 
So it becomes obvious that efficient, scalable indexing is
a hard problem. On top of all other indexing challenges,
one must point out that chunk FPs are cryptographic
hashes, randomly distributed in the index. Adjacent index
entries share no locality and any kind of simple readahead
scheme could not amortize the cost of storing index
entries on disk.

\subsection{Deletion}
Contrary to a traditional backup system, a dedupe system
shares data among files by default. 
Since snapshots in VM cloud face constant deletion, 
reference management
is necessary to keep track of chunk usage and reclaim
freed space. In addition to scalability and speed, reliability
is another challenge for reference management.
If a chunk gets freed while it is still referenced by snapshots,
data loss occurs and files cannot be restored. On the other
hand, if a chunk is referenced when it is actually no
longer in use, it causes storage leakage.

For simplicity, many previous works only investigated simple reference
counting without considering reliability
and recoverability. Reference counting, however, suffers
from low reliability, since it is vulnerable to lost or repeated
updates: when errors occur some chunks may
be updated and some may not. Complicated transaction
rollback logic is required to make reference counts consistent.
Moreover, if a chunk becomes corrupted, it is
important to know which files are using it so as to recover
the lost segment by backing up the file again. Unfortunately,
reference counting cannot provide such information.
Finally, there is almost no way to verify if the
reference count is correct or not in a large dynamic system.
Our field feedback indicates that power outages and
data corruption are really not that rare. In real deployments,
where data integrity and recoverability directly
affect product reputation, simple reference counting is
unsatisfactory.

Maintaining a reference list is a better solution: it is
immune to repeated updates and it can identify the files
that use a particular segment. However, some kind of logging
is still necessary to ensure correctness in the case of
lost operations. More importantly, variable length reference
lists need to be stored on disk for each chunk.
Every time a reference list is updated, the whole list (and
possibly its adjacent reference lists—due to the lists’
variable length) must be rewritten. This greatly hurts the
speed of reference management.

Mark-and-sweep is generally a better solution. 
During the mark phase, all snapshot metadata are traversed 
so as to mark the used chunks. 
In the sweep phase all chunks are swept and unmarked chunks are reclaimed. 
This approach is very resilient to errors: 
at any time the process can simply be restarted with no negative side effects. 
Scalability, however, is an issue.
To deal with 1 PB snapshots data, which may be represented by 10,000 GB FP index,
If we account
for an average deduplication factor of 10 (i.e., each chunk
is referenced by 10 different snapshots),
the total size
of snapshot metadata that need to be read during the mark phase will
be 100 TB. 
This alone will take almost 2 hours on a
1000-machine cloud. Furthermore, marking the in-use
bits for 250 billion entries is no easy task. There is no
way to put the bit map in memory. One might want
to mitigate the poor performance of mark-and-sweep by
doing it less frequently. But in practice this is not a viable
option: customers always want to keep the utilization
of the system close to its capacity so that a longer
history can be stored. With daily snapshots taking place,
systems rarely have the luxury to postpone deletion operations
for a long time. In our field deployment, deletion
is done once a day. More than 2 hours in each run is too
much. In a large production-oriented dedupe system reference
management needs to be very reliable and have
good recoverability. It should tolerate errors and always
ensure correctness. Although mark-and-sweep provides
these properties, its performance is proportional to the
capacity of the system, thus limiting its scalability.

\subsection{Fault Tolerance}
Because deduplication storage system
 artificially creates data dependency among different VM users,
it increases the risk of data availability.
In large scale cloud, node failures happen at daily basis,
the loss of access to a shared chunk can affect many VMs whose snapshots share this chunk. 
Without any control of the scope of data sharing, we can only increase the level of 
replication to enhance availability, which would significantly 
balance out the benefits of deduplication.

### 2012-12-20 snapshot_system/delete.tex
paper update

@@
 
-\subsection{Challenges}
-Contrary to a traditional backup system, a dedupe system shares data among files by default. 
-Reference management is necessary to keep track of chunk usage and reclaim freed space. 
-In addition to scalability and speed, reliability is another challenge for reference management. 
-If a chunk gets freed while it is still referenced by snapshots, data loss occurs and files cannot be restored. 
-On the other hand, if a chunk is referenced when it is actually no longer in use, it causes storage leakage.
+% \subsection{Challenges}
+% Contrary to a traditional backup system, a dedupe system shares data among files by default. 
+% Reference management is necessary to keep track of chunk usage and reclaim freed space. 
+% In addition to scalability and speed, reliability is another challenge for reference management. 
+% If a chunk gets freed while it is still referenced by snapshots, data loss occurs and files cannot be restored. 
+% On the other hand, if a chunk is referenced when it is actually no longer in use, it causes storage leakage.
 
-Reference counting, while being simple, suffers from low reliability especially in our distributed environment, 
-because it is vulnerable to lost or repeated updates: when errors occur some chunks maybe updated and some may not. 
-Complicated transaction rollback logic is required to make reference counts consistent. Moreover, 
-there is almost no way to verify if the reference count is correct or not in a large dynamic system. 
-In real deployments, where data integrity and recoverability directly affect product reputation, simple reference counting is unsatisfactory.
+% Reference counting, while being simple, suffers from low reliability especially in our distributed environment, 
+% because it is vulnerable to lost or repeated updates: when errors occur some chunks maybe updated and some may not. 
+% Complicated transaction rollback logic is required to make reference counts consistent. Moreover, 
+% there is almost no way to verify if the reference count is correct or not in a large dynamic system. 
+% In real deployments, where data integrity and recoverability directly affect product reputation, simple reference counting is unsatisfactory.
 
-Mark-and-sweep is generally a better solution. During the mark phase, all snapshot recipes are traversed so as to mark the used chunks. 
-In the sweep phase all chunks are swept and unmarked chunks are reclaimed. 
-This approach is very resilient to errors: at any time the process can simply be restarted with no negative side effects. 
-Scalability, however, is an issue. {\em needs to explain its resource usage}
+% Mark-and-sweep is generally a better solution. During the mark phase, all snapshot recipes are traversed so as to mark the used chunks. 
+% In the sweep phase all chunks are swept and unmarked chunks are reclaimed. 
+% This approach is very resilient to errors: at any time the process can simply be restarted with no negative side effects. 
+% Scalability, however, is an issue. {\em needs to explain its resource usage}
+
+\subsection{Approximate Deletion}
+We design approximate deletion to fast identify unused data in the append store.
+Instead of scanning the whold append store, it uses a bloom filter to check 
+if a data are still referenced by living snapshots. However, there is a small false-positive probility which
+would indetify unused data as in use, i.e., storage leakage.
+The following steps would take place during an approximate deletion:
+
+\begin{enumerate}
+\item {\bf Creating bloom filter} Scan all the living snapshot recipess and their segment recipes,
+for every reference pointing to append store, add it to the bloom filter.
+\item {\bf Check existance} For every data reference in the deleted snapshot recipe and its segment recipes,
+check the existance of that data reference in bloom filter. If not found, it is safe to delete that piece of data from append store
+because no living snapshots has referenced it.
+\end{enumerate}
+
+The overall time of running a approximate deletion for one snapshot deletion would be scanning
+all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
+parallel and is much faster than loading recipes from DFS:
+\begin{equation}
+T = (N_{SS} + 1) * T_{scan\_recipes}
+\end{equation}
+
+Using the example and analysis in previous section, this approximate deletion can be done in 5 minutes. 
+Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
+when set $P_{bl}$ to 0.01, the memory footprint of approximate deletion is about 15 MB.
+
+The design goal of approximate deletion is to reduce the frequency of running accurate deletion.
+For one VM's snapshots, let $D_{leakage}$ be the amount of storage leakage, $D_{del}$ be the average amount of data
+to be deleted in one snapshot deletion, 
+then we have:
+\begin{equation}
+D_{leakage} = N_{approximate} * P_{bl} * D_{del}
+\end{equation}
+where $N_{approximate}$ is the number of runs of approximate deletion. 
+An accurate deletion is triggered to fix the storage leakage
+when $D_{leakage}/D_{del}$ is accmulated to exceed certain threshold $T$:
+\begin{equation}
+D_{leakage} / D_{del} = N_{approximate} * P_{bl} > T \Rightarrow N_{approximate} > T/P_{bl}
+\end{equation}
+Therefore, when $P_{bl} = 0.01$ and $T=1$, 
+there would be a run of accurate deletion for every $T/P_{bl} = 100$ runs of approximate deletion.
+On a machine that hosts 20 VMs and each VM deletes snapshot daily, there would be less than
+one accurate deletion scheduled per day.
 
@@
 
-\subsection{Fuzzy Deletion}
-We design fuzzy deletion to fast identify unused data in the append store.
-Instead of scanning the whold append store, it uses a bloom filter to check 
-if a data are still referenced by living snapshots. However, there is a small false-positive probility which
-would indetify unused data as in use, i.e., storage leakage.
-The following steps would take place during an fuzzy deletion:
-
-\begin{enumerate}
-\item {\bf Creating bloom filter} Scan all the living snapshot recipess and their segment recipes,
-for every reference pointing to append store, add it to the bloom filter.
-\item {\bf Check existance} For every data reference in the deleted snapshot recipe and its segment recipes,
-check the existance of that data reference in bloom filter. If not found, it is safe to delete that piece of data from append store
-because no living snapshots has referenced it.
-\end{enumerate}
-
-The overall time of running a fuzzy deletion for one snapshot deletion would be scanning
-all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
-parallel and is much faster than loading recipes from DFS:
-\begin{equation}
-T = (N_{SS} + 1) * T_{scan\_recipes}
-\end{equation}
-
-Using the example and analysis in previous section, this fuzzy deletion can be done in 5 minutes. 
-Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
-when set $P_{bl}$ to 0.01, the memory footprint of fuzzy deletion is about 15 MB.
-
-The design goal of fuzzy deletion is to reduce the frequency of running accurate deletion.
-For one VM's snapshots, let $D_{leakage}$ be the amount of storage leakage, $D_{del}$ be the average amount of data
-to be deleted in one snapshot deletion, 
-then we have:
-\begin{equation}
-D_{leakage} = N_{fuzzy} * P_{bl} * D_{del}
-\end{equation}
-where $N_{fuzzy}$ is the number of runs of fuzzy deletion. 
-An accurate deletion is triggered to fix the storage leakage
-when $D_{leakage}/D_{del}$ is accmulated to exceed certain threshold $T$:
-\begin{equation}
-D_{leakage} / D_{del} = N_{fuzzy} * P_{bl} > T \Rightarrow N_{fuzzy} > T/P_{bl}
-\end{equation}
-Therefore, when $P_{bl} = 0.01$ and $T=1$, 
-there would be a run of accurate deletion for every $T/P_{bl} = 100$ runs of fuzzy deletion.
-On a machine that hosts 20 VMs and each VM deletes snapshot daily, there would be less than
-one accurate deletion scheduled per day.
-
 \subsection{Discussion}

### 2012-12-20 snapshot_system/design1.tex
paper update

--- 2012-09-14 snapshot_system/snapshot.tex
@@
-\section{Multi-level Snapshot Deduplication}
-\label{sect:dedupe}
-
-\subsection{Snapshot System}
-%system arch
+\section{Prototype Design}
 Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China. 
@@
 \item \textbf{DFS}: a distributed file system that is optimized for many large and sequential reads or appends.
-\item \textbf{KV}: a distributed key-value store for managing structured data.
-\item \textbf{MP}: a distributed data processing framework which is similar to Map-Reduce\cite{Dean2004}.
+%\item \textbf{KV}: a distributed key-value store for managing structured data.
+\item \textbf{MapReduce}: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
 \item \textbf{MemCache}: a distributed memory object caching system.
 \end{itemize}
-%GFS-like\cite{googlefs03} 
-%BigTable-like\cite{Chang2008a} 
 Our snapshot system and the virtual machine management service rely on these basic cloud services
@@
 places the index of CDS in MemCache for deduplication, 
-stores small amount of snapshot metadata in KV, and uses FX to facilitate the offline
+and uses MapReduce to facilitate the offline
 data processing. All the above services can easily find their open-source counterparts,
@@
 
-%snapshot representation
-\subsection{Snapshot Representation}
-The virtual device driver uses a bitmap to track the changes 
-that have been made to virtual disk.
-Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
-is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
-file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
-Moreover, we break 
-segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
-which brings the opportunity of fine-grained deduplication by
-allowing data sharing between segments.
-
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=images/snapshot_representation.eps, width=3.7in}
-  \caption{An example of snapshot representation.}
-  \label{fig:snapshot}
-\end{figure}
-As a result, the representation of each snapshot is designed as a two-level index data structure 
-in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
-A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
-that holds the meatdata of its chunks. We choose this two-level structure because in practice we
-observe that during each backup period only a small amount of VM data are added or modified. 
-As the result, even the metadata of two snapshots can be highly similar, 
-thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
-Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
-segments which greatly ease the segment-level deduplication.
-
-In both two kind of recipes, 
-they do not include the actual data but only have
- references point to the data which are either stored in append store or CDS.
-In our implementation the data reference is a 8 bytes field which is either an 
-ASID (discuss in \ref{sect:append} or an offset of 
-An additional flag indicates
-
-\subsection{Multi-level Deduplication}
-The multi-level deduplication scheme is designed base on the observations on the VM snapshot data from production cloud.
-We found snapshot data duplication can be easily classified into two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
-Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
-On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL. 
-As the result, different VMs tend to backup large amount of highly similar data.
-Our multi-level pipeline process can minimize the cost of deduplication while maximize the its efficiency at each level,
-and it is highly parallelizable since each segment is processed independently.
-
-\subsubsection{Inner-VM Deduplication}
-\label{sect:InnerVM}
-The first-level deduplication is logically localized within each VM.
-Such localization increases data independency between different VM backups,
-simplifies snapshot management and statistics collection,
-and facilitates parallel execution of snapshot operations.
-
-The inner VM deduplication contains two levels of duplicate detection efforts:
-\begin{itemize}
-\item \textit{Level 1 Segment modification detection}.
-If a segment is not changed, then its segment recipe can be simply reused by copying the data
-reference from previous snapshot recipe. 
-\item \textit{Level 2  Chunk fingerprint comparison.}
-If a segment is modified, we perform fine-grained deduplication 
-by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
-thus eliminate partial data duplication within the segment.
-\end{itemize}
-
-In general, operations at level 1 have almost no cost and most of unmodified data are filtered here. 
-To process a dirty segment at level 2, 
-there requires no more than one DFS access to load the segment recipe from previous snapshot,
-and a tiny amount of memory to hold it in main memory.
-\textit{may need details here}
-
-\subsubsection{Cross-VM Deduplication}
-\label{sect:CrossVM}
-
-\subsection{Common Data Set}
-%arch
-%analysis
+\input{snapshot}
+\input{append}
+\input{delete}

### 2012-12-20 snapshot_system/intro.tex
paper update

--- 2012-05-07 vm_snapshot_sim/2012intro.tex
@@
 \section{Introduction}
-
-%1.how virtual machines work on storage
-%2.cow and why they are not good
-%3.introduce dedup
-%1
-
-%Virtualization is the engine behind many popular cloud computing platforms.
-%Amazon, Alibaba,  and many others have provided public VM clouds that host 
-%tens of thousands of  virtual machines(VM) dynamically created
-%for various active users. 
-%In the  case of Alibaba cloud service, the sevice is called Aliyu, which
-%provides the largest public cloud in based on the open-source Xen technology.
 In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
@@
 and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}.
-%Even though the snapshots are saved incrementally, 
-%when deleting a snapshot, only the data not needed for any other snapshot is removed. 
-%So regardless of which prior snapshots have been deleted, all active snapshots will contain 
-%all the information needed to restore the virtual disk.
-%Snapshots can also be shared to instantiate multiple new virtual disks, such that user can make
-%duplicate VMs with exact the same disk state. This feature is especially useful when a user wants to run
-%an application on multiple VMs, for example Hadoop or MPI.
 
@@
 
-%Restricting the scope of global deduplication reduces
-%the inter-component  data dependenc during machine failure.
-
-%Several operations are provided for creating and managing snapshots and snapshot trees,
-%such as create snapshots, revert to any snapshot, and remove snapshots.
-%VM snapshots is different from traditional file system backup from a few aspects:
-%\begin{enumerate}
-%\item The backup loads are heavy but resources are limited.
-The whole VM cluster have PBs of data and need to be backuped at daily basis, if not more frequently.
-But at the same time snapshot tasks must not affect the normal VM operations, which means only a tiny slice of CPU and memory can be used for this purpose.
-%\item No file system semantics are provided.
-Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data.
-Only raw access information at disk block level are provided.
-%\item Snapshots can be shared between users. This does not only complicates the parent-child relationship between snapshots, but also require all snapshots be managed in a global namespace.
-%\end{enumerate}
-
-%In this paper we intorduce the deduplication scheme of snapshot storage in Aliyun's VM cloud. We exploit the 
-The rest of the paper is arranged as follows. 
-Section ~\ref{sect:background}
-discusses on some background and related work.
-Section~\ref{sect:options} discusses the requirements and  design options.
-Section ~\ref{sect:arch} presents our snapshot backup architecture with multi-level selective deduplication 
-Section ~\ref{sect:exper} presents  our evaluation results on the effectiveness
-of multi-level deduplication for snapshot backup. 
-Section ~\ref{sect:final} concludes this paper.
-% talks about Aliyun's VM snapshot system and deduplication process. In section 4 we present
-%the snapshot deduplication results of our real user VMs.
+The following table shows the strength and weakness of some well-know deduplication systems:
+\begin{table}
+    \begin{tabular}{|l|l|l|l|}
+        \hline
+        ~           & Scalability & Low-cost & Full Dedup \\ \hline
+        DDFS        & N           & N        & Y          \\ 
+        Ex-bin      & Y           & Y        & N          \\ 
+        Guo         & Y           & N        & N          \\ 
+        iDedup      & N           & Y        & N          \\ 
+        Founadation & N           & N        & Y          \\
+        \hline
+    \end{tabular}
+\end{table}

### 2012-12-20 snapshot_system/snapshot.tex
paper update

@@
-\section{Multi-level Snapshot Deduplication}
+\subsection{Snapshot Deduplication}
 \label{sect:dedupe}
-
-\subsection{Snapshot System}
-%system arch
-Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China. 
-A typical VM cluster in our cloud environment
-consists of from hundreds to thousands of physical machines, each of which can
-host tens of xen-based\cite{Barham2003} VMs.
-
-Aliyun has built a hadoop-like platform, which includes
-several highly scalable cloud infrastructure services to support
- runing large scale VM cloud service:
-\begin{itemize}
-\item \textbf{DFS}: a distributed file system that is optimized for many large and sequential reads or appends.
-\item \textbf{KV}: a distributed key-value store for managing structured data.
-\item \textbf{MP}: a distributed data processing framework which is similar to Map-Reduce\cite{Dean2004}.
-\item \textbf{MemCache}: a distributed memory object caching system.
-\end{itemize}
-%GFS-like\cite{googlefs03} 
-%BigTable-like\cite{Chang2008a} 
-Our snapshot system and the virtual machine management service rely on these basic cloud services
-to be functional:
-DFS holds the responsibility of managing physical disk storage
-in the cloud, all data needed for VM services, such as virtual disk images used by runtime VMs,
-and snapshot data for backup purposes, reside in this distributed file system. 
-In addition, our snapshot system 
-places the index of CDS in MemCache for deduplication, 
-stores small amount of snapshot metadata in KV, and uses FX to facilitate the offline
-data processing. All the above services can easily find their open-source counterparts,
-which shows the generality of our architecture and deduplication scheme.
-
-User control VMs through the virtual machine management service.
-During VM creation, a user chooses a pre-configured VM image or
-a snapshot that contains an OS,
-then the VM management service 
-copies the corresponding VM image to her VM as the OS disk.
-Data disks can be created and mounted onto the VM in the same way,
-either empty or from an existing snapshot. 
-All these virtual disks are represented as virtual disk image files in our
-underline runtime VM storage system.  
-To avoid network latency and congestion, 
-our distributed file system place the primary replica of VM's 
-image files at physical machine of VM instance.
-When user deletes her VM, all the runtime virtual disk images and
-their snapshot data are removed from DFS.
-
-%ss operations
-In each VM, 
-the runtime I/O between virtual machine and its virtual
-disks is tunneled by the virtual device driver (called TapDisk\cite{Warfield2005} at Xen).
-This is also where our snapshot system is built in. Three major snapshot operations are supported:
-\begin{itemize}
-\item \textit{Write snapshot}: save the current state of virtual disk as a snapshot.
-This is also where data deduplication would take place.
-During snapshot backup, concurrent disk write is logged 
-to ensure a consistent snapshot version is captured. 
-\item \textit{Read snapshot}: restore the state of virtual disk from a snapshot.
-\item \textit{Delete snapshot}: delete a snapshot and reclaim the disk space for unused data.
-\end{itemize}
-
-\begin{figure}[htbp]
-  \centering
-  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
-  \epsfig{file=images/arch.eps, width=3.9in}
-  \caption{Snapshot backup architecture of each node.}
-  \label{fig:arch}
-\end{figure}
-
-Figure~\ref{fig:arch} shows the architecture view of our snapshot service
-at each node. The snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
-The inner-VM  deduplication is conducted by the broker to access meta data in the snapshot data store
-and we discuss this in details in Section~\ref{sect:innerVM}.
-The cross-VM deduplication is conducted by the broker to access 
-a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
-whose block hash index is stored in a distributed memory cache.
-
 %snapshot representation
-\subsection{Snapshot Representation}
+\subsubsection{Snapshot Representation}
 The virtual device driver uses a bitmap to track the changes 
@@
 
-\subsection{Multi-level Deduplication}
+\subsubsection{Multi-level Deduplication}
 The multi-level deduplication scheme is designed base on the observations on the VM snapshot data from production cloud.
@@
 
-\subsubsection{Inner-VM Deduplication}
-\label{sect:InnerVM}
+\textbf{Inner-VM Deduplication.}
 The first-level deduplication is logically localized within each VM.
@@
 
-The inner VM deduplication contains two levels of duplicate detection efforts:
+Inner VM deduplication contains two levels of duplicate detection efforts:
 \begin{itemize}
@@
 
-\subsubsection{Cross-VM Deduplication}
-\label{sect:CrossVM}
+\textbf{Cross-VM Deduplication.}
 
 \subsection{Common Data Set}
-%arch
-%analysis

### 2013-03-06 hotstorage13/abs.tex
hot storage 2013

--- 2012-03-10 vm_snapshot_sim/2012abs.tex
@@
 %Virtualization has became the engine behind many cloud computing platforms.
-In a virtualized cloud computing environment, frequent  snapshot backup of virtual disks improves
-hosting  reliability but storage demand of such operations is huge.
-While dirtybit-based technique can identify unmodified data between versions, 
-full deduplication with fingerprint comparison  can remove more redundant content
-at the cost of computing resources.
+In a virtualized cloud cluster, frequent  snapshot backup of virtual disks improves
+hosting  reliability; howver, it  takes significant 
+memory and CPU resource to perform data duplication in order to remove
+excessive redudancy among image snapsots.
+This paper presents a low-cost clustered deduplication soluton scalable for handling a large number 
+of virtual machines.  The key idea is to seperate duplicate detection from 
+the actual storage data backup instead of using inline deduplication.
+Global inddex and  detection requests are partitioned 
+among machines using  fingerprint values for parallel detection. 
+Each machine conducts duplicate detection partiton by partition indepdently
+with a minimal memory usage.
+%in parallel among all machines and  each machine full duplication detection is 
+Another optimization is to allocate and control
+buffer space for exchanging  detection messages and duplicate summary among machines.
+%The memory requirement and disk usage for the proposed solution is very small while the overall thoughput
+%and backup process timing is not compromised. 
+Our experiments show that  the proposed scheme 
+uses a very small amount of system resources while accomplishing a satisfactory backup throughput
+in a large cloud setting.
+%which only reqiires a very small amount of memory and CPU resource.  
+%Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
+%a  small  amount of cloud resources.
+
+%Our system compares well with Amazon Glacier, in that, both of them are low-cost archival systems, 
+%supporting lazy storage with asynchronous notification mechanisms and achieve parallelism by 
+%reading/writing from multiple storage nodes/disks simultaneously. At the same time,
+
+%While dirtybit-based technique can identify unmodified data between versions, 
+%full deduplication with fingerprint comparison  can remove more redundant content
+%at the cost of computing resources.
 %with  for similarity comparison and   reliability handling.
@@
 %through a production VM data study and thus it is expective to perform cross-machine deduplication. 
-This paper presents a multi-level selective deduplication  scheme which
-integrates  inner-VM and cross-VM duplicate elimination under
-a stringent resource requirement.
-% minimal  resource impact to the existing cloud services.  
-This scheme uses popular common data to facilitate 
-fingerprint comparison while reducing the cost and it
-strikes a balance  between local and global deduplication 
-to  increase parallelism and  improve reliability. 
 % first perform a large scale study in production VM clusters 
@@
 %many cross snapshot duplication by using smaller chunking granuarity and locality.
-Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
-a  small  amount of cloud resources. 
 \end{abstract}
+%\begin{IEEEkeywords}
+%Cloud storage backup,  Virtual machine snapshots,  Distributed data deduplication
+%\end{IEEEkeywords}

### 2013-03-06 hotstorage13/arch.tex
hot storage 2013

\section{ Key Ideas and Design Architecture}
\label{sect:arch}

%\begin{figure}[htbp]
%  \centering
  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
%  \epsfig{file=images/arch.eps, width=3.9in}
%  \caption{Snapshot backup architecture of each node.}
%  \label{fig:arch}
%\end{figure}

We consider deduplication in two levels. The first-level of data deduplication can be accomplished efficiently and 
inexpensively using a coarse-grain segment-level  dirty bit based detection in the OS level  to 
identify version difference from the previous snapshot to the current snapshot.  
Version-based detection has been used in the previous work~\cite{Clements2009,Vrable2009,TanIPDPS2011} and
we emphasize a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
Our experiment with Alibaba''s production dataset shows that over 70 percentage of 
duplicates can be detected using segment-based dirty bits while the segment size is as large as 2M bytes.  
This setting requires OS to keep the metadata for segment dirty bits and the amount of space for such segment 
dirty bits is negligible. In the second level of deduplication, remaining content blocks of each VM 
are compared with the signatures of all unique  blocks stored in the previous snapshots.

Our key ideas are summarized as follows.
\begin{itemize}

\item {\bf Seperation of duplicate detection and data backup.}
%Request accumulation and partition-based deduplication.}
The second level duplicate detection requires a global comparison of 
content fingerprints of stored chunks with the new chunks scanned during 
the backup process. Bloom filters and caching allows some of content 
fingerprints to be stored on the cheap disks~\cite{bottleneck08}. Such an optimization is good 
for inline deduplication where chunks scanned need to be determined to be duplicate or not instantly without 
waiting while  it memory consumption is still significant in competing with stand virtual 
machine activities.  Our idea is to perform duplicate detection first before actual data backup.
That requres a pre-scanning of  data  blocks of VM images and after that, real backup  for those nonduplicates
is conducted. That does incur an extra  round of I/O reading for nonduplicate blocks while avoiding inline 
deduplication and leading to a much smaller resource requirement. 
During duplicate detection phase, detection requests can be accmnulated on the disk 
for a period time  in a  partitioned manner.  Aggregated duplicate requests can be processed partition by partition. 
We also accumulate the delete requests and perform them partition by partitions. 
Since each partition corresponds to a small portion of global content index, the cost to 
process requests within a partition is significant smaller than process all the requests globally.

\item {\bf Buffered data redistrubution in parallel processing of  detection  requests}.  
We let {\em global index} be the meta data containing the fingerprint values of all unique blocks
in the entire cluster and  the reference pointers which lead to the actual location of raw data.
A dupliate detection request for a content block needs to be compared with the global index to determine if this
block is nonduplicate. If it is a duplicate, return the correspinding reference pointer.
We conduct parallel processing of detection requests in all machines in a cloud cluster.
A logical way to distribute detection requests is to parititon based on the content  hashing of data blocks
and the global index can also be partitioned accordingly in a  disjointed manner.
Initial data follows the VM distribution among machines and the detected results 
represented as  duplicate summary need to be collected following VM distribution. 
Therefore, there are two all-to-all data remapping operations involved.
One is to map detection requests from VM-based requests to the fignerprint based distribution.  
One is to map dupliate summary from fingerprint-based requests to the VM based distribution.  
The redistribued data needs to be accumulated on the disk to minimize the use of memory.
To minimize the cost of disk seek, outgoing or incoming data exchange messages need to be buffered to bundle small messages.
Given there are $p\times q$ partitions where $p$ is the number of machines and $q$ is the number of fingerprint-based partitions
at each machine, the number of buffers is big and space per each buffer  is small given the memory constraint.
Then there will be a large number of storage  IO operations involved, suffering the huge seek overhead.
We have designed an effient data exchange and disk data buffering  scheme to address this.

%As we detect and backup requests before actual backup takes place,  we need to store chunk data on 
%temporary disks and once duplicates 
%are detected, we only need to fetch and store these non-duplicates 
%in the backup storage.  To minimize the storage usage of temporary disk space, we donot save the data content 
%of accumulated requests with replication, but we store  data separately for each virtual machine. In an event 
%that the storage of temporary accumulation fails for certain virtual machines, rescanning of these virtual machine images 
%is conducted and backup of these machines is re-initiated.   Meta data such as content hash for accumulated requests 
%is stored separately since we map the meta data into a set of buckets using chunk fingerprints. 
%The benefit of separating content and meta data is to allow fast recovery of backup operations while enabling bucket-based lazy deduplication.

\end{itemize}

We assume a flat architecture in which  all $p$ machines that host VMs in a cluster can 
be used in parallel for deduplication. 
The nonduplicated snapshot blocks are stored either in a distribed file system built on
this cluster  or in another  external storage system. 
We assume that  a small amount of local disk space and memory on each machine can be used 
to store global index and request accmulation.
%Our design is to minimize the usage of local memory and storage on each machine.

%While we assume all machines can process  independent or coordinated
%deduplication and backup operations in parallel,  
%our scheme uses a single-thread procedure on each machine to minimize the use of CPU, network bandwidth, and disk bandwidth.
\subsection{Data Structure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{snapshopdata.pdf}
\caption{ Metadata strucrure of a VM snapshot.}
\label{fig:snapshot}
\end{figure}

The representation of each snapshot saved in the backup storage
has a two-level level index data structure in the form of a hierarchical
directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
An VM image is divided into a set of segments and each  segment contains hundreds of content blocks from the bottom level.
These blocks are of variable-size, partitioned using
the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
%To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.

Segment metadata (called segment recipe) records its  content block hashes and data pointers. 
The snapshot recipe contains a list of segments and other meta data information.
If a segment is not changed from one snapshot to another, indicated by a dirty bit embedded in the virtual disk driver, 
its content blocks are not changed as well, thus its segment recipe contains a reference pointer to an earlier segement.
If a block is dupliate to another block in the system,  the block recipe contains a reference pointer to an earlier block.

\subsection{Processing flow and resource usage}

The data flow of our partition-based  dupliate detectionis depicted in
Figure~\ref{fig:flow}. let $v$ be the total number of virtual machines hosted in  
a cluster,  we divide the backup into $k$  iterations. 
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{steps.pdf}
\caption{ Processing steps of dupliate detection.}
\label{fig:flow}
\end{figure}

\begin{itemize}
\item
The first step of each iteration is to read  $v/k$  virtual machine images in parallel on the cloud 
cluster and issue backup requests. For those segments that have been modified since last backup indicated by 
dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
information such as chunk fingerprints,  sends the metadata of a chunk block, and accumulate  into 
a partition bucket on the temporary disk storage. 
The partition mapping is using a hash function applied to the content fingerprint. 
Assuming all machines have a  homogenous resource configuration, each machine is evently  assigend with
$q$ partitons of content hash and accumulates corresponding requests on the disk. 
There are two options to assign buffers in each machine to buffer requests for each partition.
1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
since any content block in a VM image of this machine can be sent to any of these partitions.
2) Each machine has $p$ receive buffers correspond to $p$ machines in the cluster and $q$ receive 
buffers to temporarly accmulate messages from other machines, and then output each buffer to the local disk
when it becomes full.  Option 2 is much more efficient than Option 1 because $p+q$ is much smaller than
$p\times q$, as a result each buffer has a bigger size to accmulate data and results in 
much less disk seek overhead.

%We assume that the startup cost for network message sending is  much more less (e.g. an order of magnitude
%less) than from one machine to another 
%disk storage startup cost such as seek is much mu
%Note that we only accumulate requests with their meta data information.
\item
The second step is to perform duplicate detection for  all requests accumulated in the partitions.  
The system maintains the index of all chunk fingerprints divided in the buckets. We load the global index partition 
and accumulated correspnding requests, and compare them to  identify the duplicated blocks.  
Then we unloand them, load the global index and accumulated requests for another partition. 
This process is repeated until all buckets are processed.

As chunk blocks are detected as duplicates, the meta information on duplicates is 
remapped from fingerprinter-based distribution  to VM-based distribution. In this way, duplicate information 
for segments of each VM is collected in one place, which will be used in next step. 
In the sending side, each machine scans idenitified duplicates for one target machine,
and then scans for another machine. In this way, it sends dummary summary to the corresponding machines one by one
to minimize the startup cost for sending a message.
In the receiving side, 
%All-to-all machines data exchange is conducted  so that  
each machine allocates $q$ receive buffers corresponding to
$q$ local partitions, to hold received messages from other machines.  
When a receive buffer for a VM is  full, the data is written to the local disk storage. 
%These substeps are repeated as the stream of data is exchanged when each machine compares through all $q$ partitions.

\item The third step is to read  nonduplicate blocks from each VM and output to the final backup 
storage. In this process, if a segment is not dirty, we only need to output the segment meta data 
such as reference pointers to the original segments previously saved in the backup.  
If a segment is dirty,  we use the duplicate summary information from Step 2 for internal 
duplicate blocks of this dirty segment and output the remaining non-duplicate blocks to the backup storage.
\end{itemize}

%          In fetching non-duplicates,    it is sometime faster that we fetch a large number of consecutive chunk blocks from an accumulated  segment which contains duplicated chunks,  to avoid the random seek overhead.

The above steps can be executed by each machine
using one thread to minimize the use of CPU, network bandwidth, and disk bandwidth.
The  disk storage usage on each machine 
is fairly small for  storing part of global index and
accumulating  duplicate detection requests that contain fingerprint information.   
We impose a limit for memory allocated at each machine node to accomplish low-cost deduplication.  
Memory usage for each step of above iteration is carefully controlled as follows.
\begin{itemize}
\item For Step 1, the allocated memory for each machine is evenly divided for $p$ send buffers and $q$ receive buffers.

%1) $p$ send buffers. images, sends the fingerprint of a dirty block to a machine that is responsible for this fingerprint.
%2) Buffer requests gathered from other machines and divide those requests into $q$ buckets. Once a buffer for each bucket is full, output to the disk storage.
\item 
For Step 2,  the allocated memory serves 2 purposes. 1) Space for hosting a partition of global index and 
the corresponding partition of  deduplication requests. 2) Buffer space for $q$ receive buffers.
%%accumulating duplicate summary for each targeted VM.   Once  each machine processes a bucket of  duplicate detection requests, 
The duplicate summary sent other machines and accmumated for each VM contains
the block ID and  the reference pointer.   
%For each machine which hosts $v$  VMs, and will receive messages from many other machines, 
%the system needs to allocate buffer space for each VM ot accumulate the duplicate summary records. 
%When a buffer for a VM is full, the result is written to the disk.

\item For Step 3 to  perform the real backup for each VM, 
memory is used to hold the meta information summary of all duplicate blocks obtained  from Step 2. 
Another memory usage is to fetch a sequence of blocks from a virtual machines (most of them are nonduplicate) 
and write them to the  backup storage.

\end{itemize}
%We find the memory for step 2 is most critical for buffering duplicate summary in hiding the latency. 
%Certainly most storage system can allow many IO requests issued in parallel overlapping the IO latency.  
%Here we assume the worst case and also minimize the IO bandwidth usages by issuing 
%one request at a time to use the minimal disk bandwidth resource.

{\bf Snapshot deleteion.} Each virtual machine will keep at most $x$ snapshots of VM images and thus
expired snapshots will be deleted unless its owern explicitly asks for its retention. 
A block or the entire segment can be deleted if its reference counter is zero.
As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
We deal snapshot deletion in three steps similar to the VM snapshot backup.
Step 1 is to read  the meta data of a snapshot such as segment and block
recipes and  accumate  deletion requests in different machines  in the fingerprint based distribution.
The second step  is to process the deletion requests within each partition and detect those records with zero 
reference counters. The third step is that every VM gathers the confirmed deletion requests for its cotent and sends them
to the backup storage.
The archival data repository may log these deletion requests,  and will periodically perform a compaction operation when 
its deletion log is too big. 
Due to the paper constraint, we will not discuss the deletion operations in details.

The above method requires the counter information to be consistently maintained in the global index.
Another option to avoid maitaining its consitency is to perioidcally read all receipts of active 
snapsots and compute the counter of all blocks while still following the fingerprint-based partitioning. 
%Finally the deleteion summary. it will adjust the corresponding reference counts. At the end of bucket worker's operation, it outputs the unused blocks information to each VM data repository's deletion log.

%This compaction will make a copy of all the data in use, and remove the obsoleted blocks. However, after such a compaction, many block offsets will be changed, as a result, such changes are sent to the bucket job queue so that changes will be reflected upon the next bucket update.

%Since we maintain a single copy of each block information in the bucket index, and there is at most one bucket worker operating the bucket index at one time, it it safe to do the simple reference counting rather than mark-and-sweep.

### 2013-03-06 hotstorage13/background.tex
hot storage 2013

\section{Background and Related Work}
\label{sect:background}

In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided. 
Each physical hosts many VMs and a cloud cluster has  petabytes of data that need to be backed up at daily basis, 
if not more frequently. But at the same time snapshot tasks must not affect the normal cloud service, 
which means that ideally only a very small slice of CPU and memory can be used for the backup purpose.

The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
Backup systems have been developed to use content hash (finger prints) to identify duplicate
content~\cite{venti02,Rhea2008}.
%,NGmiddleware2011}.
Today's commercial data backup systems (e.g. from EMC and NetApp)
%\cite{emc_avamar}\cite{datadomain_whitepaper}
use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.

Several techniques have been proposed to speedup searching of duplicate
content. For example,
Zhu et al.~\cite{bottleneck08} tackle it
by using an in-memory Bloom filter and prefetch groups of chunk IDs that are likely to be
accessed together with high probability. It takes significant memory resource for filtering and caching.
NG et al.~\cite{ NGmiddleware2011}  use
a related filtering technique for integrating deduplication in Linux  file system and the memory
consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
Lillibridge et al.~\cite{sparseindex09} break list of chunks
into large segments, the chunk IDs in each incoming segment are sampled and the segment is
deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
These are segments that share many chunk IDs with the incoming segment with high probability.
Deepavali et al.~\cite{extreme_binning09}  use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
That leads  to a smaller amount of memory usage for storing meta data in fingerprint
lookup with a tradeoff of the reduced recall ratio.

Additional inline deduplications are studied in ~\cite{idedup}. All of the above appraoches have focused on
such inline duplicate detection, namely given a content chunk, how to detect if it is duplicate instantantly
to trigger the data backup of this chunk or not before the detection request for the next chunk can be launched. 
In our work, this constraint is relaxed and 
there is a waiting time for many duplicate detection requests. Our goal is to minimizing  computing  resource without
affeting the overall time of backup.

### 2013-03-06 hotstorage13/eval.tex
hot storage 2013

--- 2012-05-06 vm_snapshot_sim/2012eval.tex
@@
 
-We have implemented the snapshot deduplication scheme on the Aliyun's cloud platform.
-Objectives of our experimental evaluation are:
+We have implemented a prototype of the parititon-based deduplication scheme based on the 
+Alibaba's cloud platform.  Objectives of our experimental evaluation are:
 1) Analyze the commonality of content data blocks and the popularity  of hot items. 
@@
 
-\begin{figure}
-  \centering
-  \epsfig{file=images/overall_effect.eps, width=3.5in}
-  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
-deduplication divided by the original data size and the unit is percentage. }
-
-  \label{fig:overall}
-\end{figure}
+%\begin{figure}
+%  \centering
+%  \epsfig{file=images/overall_effect.eps, width=3.5in}
+%  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
+%deduplication divided by the original data size and the unit is percentage. }
+%
+%  \label{fig:overall}
+%\end{figure}
 
@@
 Each bar in the Y axis shows the data size after deduplication divided by the original data size.
-Level-1 elimination can reduce the data size to about 22\% of original data, namely it delivers close 78\% reduction.
+Level-1 elimination can reduce the data size to about 23\% of original data, namely it delivers close 77\% reduction.
 Level-2 elimination is applied to data that could pass level-1, it
@@
 
-\begin{figure}
-  \centering
- %\epsfig{file=images/os_cds_sim.eps, width=3in}
-  \epsfig{file=images/3level_os.eps, width=3.5in}
-  \caption{Impact of 3-level deduplication for OS releases.}
-  \label{fig:oscds}
-\end{figure}
+%\begin{figure}
+%  \centering
+
+%  \epsfig{file=images/3level_os.eps, width=3.5in}
+%  \caption{Impact of 3-level deduplication for OS releases.}
+%  \label{fig:oscds}
+%\end{figure}
 
@@
 
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.45\textwidth]{websearch.pdf}
+%\caption{ PDF-based figure.}
+%\label{fig:websearch}
+%\end{figure}
+
+%\begin{table}[hbt]
+%\caption{ Projected enrollment for the first five years.}
+%\begin{center}
+%\begin{tabular} {|c|c|c|c|c|c|}
+%\hline  & Year 1 & Year 2 &Year 3 & Year 4 & Year 5 \\
+%\hline Enrollment & 10&  15 & 20 & 25 & 30 ( $\le$ 40)\\
+%\hline
+%\end{tabular}
+%\end{center}
+%\label{tab:enrollment}
+%\end{table}
+
+\begin{verbatim}
+partition q/machine=		50	100	250	500	1000	2000
+Step 1
+Seek cost  for accumulating (option1)	0.015972222	0.031944444	0.079861111	0.159722222	0.319444444	0.638888889
+Seek for accumlation (option 2)     1.064814815	2.12962963	5.324074074	10.64814815	21.2962963	42.59259259
+
+Step 2
+Memory for index+bucket 	0.276	0.138	0.0552	0.0276	0.0138	0.0069
+Global index portion		0.23	0.115	0.046	0.023	0.0115	0.00575
+
+buffering factor 			-9.723320158	-8.537549407	-4.980237154	0.948616601	12.80632411	36.52173913
+Seek for writing dup sum per VM	-0.000357103	-0.0008134	-0.003486001	0.036603009	0.005422668	0.00380291
+\end{verbatim}
+
 %Combining OS disks in all the VMs, we see the overall 7.4TB of data is reduced to 512GB. 
@@
 %content can be eliminated using the CDS also.
-
-\subsection{Coverage of common data blocks}
-
-%We study characteristics of common data blocks among snapshots of VM users
-%and examine the impacts if we only store a relative small amount of common data blocks to be sored in the CDS server.
-%There are two advantages to exploit this.
-%First, a smaller CDS reduces overall resource requirement while covering  most of data blocks in snapshots.
-%Second a smaller CDS makes the fault tolerance management  easier because we can replicate  more copies
-%to mitigate the failure.
-
-%We consider each virtual disk contains two parts: OS partition and regular user data partition
-%and study their characteristics seperately.
-%In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus  one or more data disks.
-%During VM's creation, its OS disk is directly copied from user's choosen base image.
-%Since  they dare brought by the operating system and popular 
-%software installations,  they are rarely modified or deleted.
-%base image data as a hint.
-%Through users may change configurations, install software, or write user data into OS disk,
-%but most of the OS related data shall keep unchanged.
-
-%Previous study has also supported this\cite{vmimage}. Therefore, we can let all OS disks share these
-%common data in their snapshot backups.
-%We choose user's data disks rather than OS disks in thie experiment for several reasons: First, the data in OS disks are 
-%instinctively highly similar, because most of the VM users only make some common or unique but tiny changes to their OSes,
-%so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
-%Second, the data disks are way more important in terms of data safty and backup because they are 
-%what users really care about.
-
-%Furthermore, our study on user's data disks has shown that the duplication pattern of
-%variable-sized data blocks follows \emph{Zipf-like} distribution. As a result, the major portion of 
-%deduplication effect will emerge from eliminating the duplication of frequently seen data.
-%define CDS
-
-\comments{
-\begin{figure}[htbp]
-\centering
-%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
-%\epsfig{file=images/log-log.disk.eps, width=3in}
-\epsfig{file=images/datadisk.count_rank.eps, width=3.5in}
-\caption{Duplicate count  of common data blocks in a log scale.}
-\label{fig:zipf-data}
-\end{figure}
-Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
-terms of the duplication count. $Y$ axis is the popularity of a data block in log scale 
-measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
-sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
-The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.
-
-\begin{figure}
-\centering
-%\epsfig{file=images/log-log.35vmos.eps,  width=3in}
-%\epsfig{file=images/35os.count_rank.eps, width=3in}
-\epsfig{file=images/35vmos.count-rank.eps,width=3.5in}
-\caption{ Duplicate count of  common OS blocks in a log scale.}
-\label{fig:OSpopular}
-\end{figure}
-Figure \ref{fig:OSpopular} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
-$Y$ axis is the popularity of an OS block in a log scale 
-measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
-sorted by their duplicate rank.  For the top ranked blocks, there is a flat line in terms of duplicate counts. That
-is because there are a large number of OS blocks which have appear in all copies of such OS releases.
-
-}
-
-\begin{figure}
-\centering
-\epsfig{file=images/ay41a_big.data_disk.cdf.eps, width=3.5in}
-%\epsfig{file=images/cdf.disk.v4.eps, width=3in}
-%\epsfig{file=images/datadisk.count_rank.eps, width=3in}
-%\epsfig{file=images/35os.count_rank.eps, width=3in}
-
-\caption{Cumulative  coverage of popular common user data blocks.}
-\label{fig:userdatacoverage}
-\end{figure}
-
-One of our biggest advantage is small memory footprint for deduplication, because we only
-eliminate a small amount of highly popular data.
-we use dataset2 to demonstrate the coverage of popular data blocks on user-related data, 
-as shown in Figure \ref{fig:userdatacoverage}.
-%content blocks used in image files using 90\% of
-%the collected dataset.
-%Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular common user data blocks. 
-The $X$ axis is the rank of common user data blocks, and $Y$ shows how much raw data can be covered given
-the size of CDS.
-Let $S_i$ and $F_I$ be the size and duplicate count 
-of the $i$-th block ranked by its duplicate rank.  Then $Y$ axis is the coverage of
-the common dataset covering data items from rank 1 to rank $i$. Namely  
-\[
-\frac{ \sum_{i=1}^{i} S_i * F_i} {\mbox{Total data size}}.
-\]
-
-Thus with about 1\% of blocks on data disks, CDS can cover about 38\% of total data blocks
-appeared in all data snapshots. The corresponding CDS index uses no more than 150MB memory per machine,
-which can be easily co-located with other cloud services.
-
-%Figure~\ref{fig:OSdatacoverage} shows the cumulative coverage  ratio of  popular common OS blocks. 
-%From both graphs, a small number of most popular common blocks can coverage a large percentage of 
-%snapshot blocks and thus the size of CDS can be chosen to be small while still having a large
-%coverage.
-
-%\begin{figure}
-%\centering
-%\epsfig{file=images/ay41a_small.os_incremental.cdf.eps, width=3in}
-%\caption{ Cumulative  coverage of popular common OS disk blocks.}
-%\label{fig:OSdatacoverage}
-%\end{figure}
-
-%We define \emph{OS CDS} to be the unchanged data across the base VM image and the snapshots of all
-%OS disks which are derived from it. Such data are brought by the operating system and popular 
-%software installations, they are rarely modified or deleted, and can be easily extracted using 
-%base image data as a hint.
-
-Because there are a limited number of OS releases, we study common blocks among
-OS disks loaded with  the same OS release. 
-%The selection of CDS is completed by separating OS disk and data disk.
-%While block commonality among data disks may be affected in some degree
-% when we scale up the number of total VMs  to be supported,
-%we expect that  the block commonality among OS disks still remains to be high and  
-%%can be well covered by a fixed CDS because users still adopt common OS releases.
-%we choose 7 major OSes in Aliyun's
-%VM cloud platform and they are: 
-%Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
-%distributions are 64 bits).
-%we examine 5 VM user disks from each OS, and 10 snapshots for each VM. These VMs have been actively used by their
-%owners. Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
-%their OS disks. 
-%For example, some Ubuntu OS disks have only 2GB of data while some have 50GB.
-%For each OS, the base image and all OS
-%disk snapshots are divided into variable-sized blocks. Then 
-In  Figure~\ref{fig:OSunchanged},  we list a conservative  commonality study in 7 major OS versions  supported
-in Aliyun.
-%We consider the earlier snapshot for each OS disk as the base image.
-For every block in the base image, we classify this block as ``unchanged''
-if this block has appeared in all snapshots of the same OS release even they are used by different VMs.
-Figure \ref{fig:OSunchanged} shows that for each
-OS,  at least 70\% of OS blocks are completely unchanged among all snapshots of the same OS. 
-Some latest release  of OS tends to have a higher percentage of content change
-while  old release tends to have more variations of content versions.
-That can be interpreted as that users with very old  version of operating systems
-have a lower tendency to update their OS versions and this causes a larger discrepancy
-among OS snapshots of these users.
-
-%into the unchanged category of OS data.
-
-\begin{figure}
-\centering
-\epsfig{file=images/os_subset.eps, width=3.5in}
-\caption{Percentage of completely common blocks among different VMs for the same OS release.}
-\label{fig:OSunchanged}
-\end{figure}
-
-Based on the above analysis, we have selected a small set of most popular
-OS blocks, which is about 100GB OS data and its corresponding CDS index takes about 1GB memory space in total.
-They can cover sufficiently over 70\% of OS-related data.
-
-%Then we use this CDS to run the deduplication process again.
-%That correspond to about  80GB of OS blocks and its corresponding CDS meta occupies 800MB in the cache.
-%  data from 350 OS disk snapshots,
-
-%The above analysis is only an estimation of OS and software related common data, 
-%some user installed software may not be discovered by this method because they are not 
-%included in the base image. However, as we can see in the next section, 
-%the overall duplication of user generated data
-%follows the Zipf-like distribution, thus all popular data can be discovered by statistic analysis.
-
-%Zipf's law has been shown to characterize use of words in a natural language, city populations, 
-%popularity of website visits and other internet traffic data.
-
-%Here we present the first fully consistent empirical study showing that data duplication
-%pattern in very large scale storage follows Zipf-like distribution. More specifically,
-%we show that the duplication count of any unique data block is inversely proportional to its rank
-%in the frequency table, with $\alpha$ smaller than unity. 
-%As far as we know, this is the first study of large scale real user data to disclose
-%the Zipf-like distribution pattern in data storage area.
-
-%\subsubsection{The model}
-%Consider a general storage system that holds user's files without any deduplication. 
-%Let $N$ be the total number of unique data blocks after 
-%content-defined chunking and deduplication, 
-%$C_N(i)$ be the number of duplicate copies that the $i$th data block being
-%stored in storage, given all the unique data blocks be ranked in order of their number of duplicate copies.
-%Let $S_i$ be the size of $i$th block,
-%then the actual ranking of the $i$th block is reflected by $\sum_{1}^{i-1}S_i$.
-
-%\subsubsection{Methodology}
-%1323 users' virtual data disks were scanned using TTTD content-defined chunking, and we performed global perfect deduplication 
-%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
-%and maximum block size, all variable-sized blocks are compared by their SHA-1 hash arther than real data.
-%
-%We choose user's data disks rather than OS disks in thie experiment for several reasons: First, the data in OS disks are 
-%instinctively highly similar, because most of the VM users only make some common or unique but tiny changes to their OSes,
-%so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
-%Second, the data disks are way more important in terms of data safty and backup because they are 
-%what users really care about.
-
-\comments{
-\subsection{Discussion}
-By storing the hash index of a small set of hottest data (CDS), we expect to achieve great 
-deduplication effect with minimal cost.
-But one problem of the CDS is what we called \emph{blind spot}: the update of CDS is always 
-behind new data's arrival,
-as a result, some data must have been written to the backup store before being collected into CDS, thus such 
-duplication may comprise the effect of
-CDS. For instance, when a MySQL update is released, some users may apply it very quickly, so the new hot data bring by
-this update will not be filtered by CDS. Only until later our CDS update includes those new data, then the rest of MySQL users get benefited.
-We can take a few measurements to reduce the impact of blind spot. First, the data in blind spot will not accumulate, because snapshots backup
-is a paid service, so over the long term, data in blind spot will be removed from backup store as VMs and old snapshots keep being deleted.
-Second, for the major OS updates, we can anticipate them in advance by putting the new hot data into CDS before users widely adopt them.
-
-Another problem associated with CDS is that some data in CDS may no longer be popular or even disappear
-as time goes. For example, an MySQL software update may invalidate some data that we previously hold in 
-the CDS. If some data blocks in CDS are no longer referenced, our map-reduce process is able to detect
-this situation, so invalid data will be removed and new data will be added during the next CDS update. 
-But if some users choose to keep their old MySQL version, then the corresponding old and new data will co-exist in the CDS.
-}
-
-%In our snapshot deduplication architecture, CDS is the key to achieve greater deduplication than
-%incremental backup solutions. Our basic assumption of CDS us that VM disks, especially OS disks,
-%have huge amount of data in common, and such common data can be represented by a relatively smaller data set
-%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
-%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
-%the effectiveness of CDS using real user VM disks from our production VM cluster.
-
-\subsection{A comparison of perfect and CDS-based deduplication }
-%Figure~\ref{fig:pd} shows the compression ratio of perfect deduplication at different dataset sizes
-%as we vary the data size from about 4 terabytes to about 23.5 terabytes.
-After level-1 and level 2 elimination, we find that 
-the complete deduplication would reduce the storage cost further by 50\%. 
-If we put all these unique data into CDS, 
-we could achieve complete deduplication,
-but fingerprint lookup in such huge CDS hash index would become a bottleneck as discussed in many pervious works. 
-So we use dataset2 to evaluate how much space saving of 
-deduplication can be achieved when varying the CDS size.
-%\begin{figure}
-%  \centering
-%  \epsfig{file=images/dedup_ratio.eps, height=2in, width=2.66in}
-%  \caption{Perfect deduplication on data disks}
-%  \label{fig:pd}
-%\end{figure}
-
-%We rank unique data blocks by their duplication count, and choose the hottest blocks as CDS. 
-Figure \ref{fig:datacdssize} shows the relationship between CDS cache size and relative space saving ratio
-compared to the full deduplication.  The unit of CDS size is gigabytes.
-We define \emph{space saving ratio} as the space saving of CDS method divided by 
-full deduplication space reduction. 
-With a 100GB CDS data (namely 1GB CDS index) can still  accomplish about 75\% 
-of what perfect deduplication can do.
-%But this effect decreases when more data are added to CDS. 
-%The lower bound of CDS space saving ratio is 50\%, which is very easy to accomplish.
-
-\begin{figure}
-  \centering
-  \epsfig{file=images/uniquedata-saving.eps, width=3.5in}
-  \caption{Relative ratio of space size compared to full deduplication when CDS size changes.}
-  \label{fig:datacdssize}
-\end{figure}
-
-%CDS size is restricted by system memory resource.
-With dataset2, Figure \ref{fig:datacds} shows how CDS space saving ratio
-compared to the full deduplication is affected by the dataset size. 
-%The calculation is done after level 1 and level 2 deduplication.
-In this experiment we first set out a goal of space saving ratio completed, 
-then watch how much data needs to be placed in CDS cache to achieve this goal.
-From the graph we can see a 75\% saving ratio lead to a stable ratio between 
-CDS size and data size, which requires 1\% of data to be placed in CDS.
-
-When we deal with a large cluster of 1,000 nodes, we expect that using
-1\% of data disks can cover more than what we have seen from this
-1323 VM dataset, assuming that the average behavior of every subcluster with 100 machines
-exhibits a similar commonality. 
-In addition to this, CDS for OS disks will become even more effective when
-there are more VMs sharing the same collection of OS releases. 
-%Base on above data we can estimate the size of data CDS and its effect. 
-%Currently we prepared 500MB memory per machine to store CDS meta, then it can represent 50GB of data. 
-%If we assume each VM has 30GB of user data at runtime, and we host 25 VMs per machine, 
-% maintain 10 snapshots per VM, each brings 10\% additional modified data. 
-%Thus the user data in snapshot system is 1.5TB per machine. So the upper bound of 
-%$CDS size/ Data size = 0.033$, which is sufficient for the 75\% saving goal.
-
-\begin{figure}
-  \centering
-  \epsfig{file=images/cds_scale.0.7.eps, width=3.5in}
-  \caption{The relative size ratio of  CDS over the data size. }
-  \label{fig:datacds}
-\end{figure}
-
-%Unlike the CDS of OS disks which is mainly composed of OS related data thus highly predictable, 
-%data disks is unpredictable because we cannot control what user can put in there. But we still
-%suspect that highly duplicated data in existing data are very likely to be duplicated again.
-%So we randomly pick 50 out of 1322 data disks as the new data, and use the rest as existing data
-%to extract CDS. Using 1.5\% as CDS threshold, we see the total 1198GB of new data is reduced by 
-%755.8GB, while perfect deduplication can reduce 1017.4GB. So 74.3\% of duplicate blocks are eliminated 
-%by pre-trained CDS, which is quite satisfactory.

### 2013-03-06 hotstorage13/main.tex
hot storage 2013

--- 2012-05-06 vm_snapshot_sim/main.tex
@@
-\documentclass[conference]{IEEEtran}
+\documentclass[finalversion]{usetex-v1}
 %\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
@@
 %\title{Selective Deduplication for VM Snapshots in Cloud Storage}
-\title{Multi-level Selective Deduplication for VM Snapshots in Cloud Storage}
+\title{ Low-Cost Data Deduplication  for  Virtual Machine Backup in Cloud Storage}
 %\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
 \author{
-\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}, Hong Tang\IEEEauthorrefmark{2}, Hao Jiang\IEEEauthorrefmark{2}, Tao Yang\IEEEauthorrefmark{1}, Xiaogang Li\IEEEauthorrefmark{2}, Yue Zeng\IEEEauthorrefmark{2}}
-\IEEEauthorblockA{\IEEEauthorrefmark{1}Dept. of Computer Science, UC Santa Barbara. Email: \{wei, tyang\}@cs.ucsb.edu}
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Alibaba Inc. Email: \{hongtang, haojiang, xiaogang, rachael\}@alibaba-inc.com}
-%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
-%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
-%   {\normalsize $^\star$UC Santa Barbara}\\
-%   {\normalsize$^\dagger$Alibaba.com}
+Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$\\
+   {\normalsize $^\star$UC Santa Barbara, \{wei, tyang\}@cs.ucsb.edu}
 }
@@
 
-\input{2012abs}
-\input{2012intro} %introduce the vm cloud, backup problem, and our requirements
-\input{2012background} %related works, related solutions, 
-\input{2012arch} %, design considerations, architecture
-\input{2012eval} %data study, zipf, model of cds size and dedup efficiency
+\input{abs}
+\input{intro} %introduce the vm cloud, backup problem, and our requirements
+\input{background} %related works, related solutions, 
+\input{arch} %, design considerations, architecture
+%\input{analysis} %, design considerations, architecture
+\input{eval} %data study, zipf, model of cds size and dedup efficiency
 %\input{results}
@@
 %  }
-{\small
+{
 \bibliographystyle{abbrv}
-\bibliography{dedup,dedup1}
+\bibliography{library,dedup1}
 }

### 2013-03-08 hotstorage13/analysis.tex
new

\section{ Performance Analysis and Comparison}
\label{sect:analysis}

We assume a flat architecture that we use all machines in a cluster to host virtual machines, and also evenly host  raw data and meta data of the temporarily accumulated requests.  We call global index to be the meta data of all non-duplicate chunks such as chunk fingerprints and reference pointers.

Following parameters are used to analyze the performance of our system.
\begin{itemize}
\item
$p$ is the number of machines in a cluster. These machines can run in parallel for backup. The request buckets are evenly distributed among these machines.
\item $v$ is the number of virtual machines per machine. At Alibaba, $v=25$.
\item $x$ is the number of snapshots saved for each VM.
\item $k$ is the number of iterations to complete all virtual machine backup. Each iteration performs v/k backups.
\item $t$  is the  amount of temporary disk space used per physical machine for deduplication.
\item $m$ is the amount of memory used per each physical machine for deduplication. Our goal is to minimize 
\item $s$ is the average size of virtual machine image. At Alibaba data we have tested, $s=40GB$.
\item $d_1$  is the average  deduplication ratio using  segment-based dirtbit.  s*d1 represents the amount of data items that are duplicates and can be avoided for backup. For Alabalba dataset tested, 
$d_1$=77\%.
\item $d_2$ is the average  deduplication ratio using content chunk fingerprints after segment-based deduplication. For Alaba dataset tested,  $d_2=50$\%.
\item $b$ is the average disk bandwidth for reading from local storage at each machine. 
\item $q$ is the number of buckets to accumulate requests at each machine. Thus the total number of buckets is $p*q$.
\item $c$ is the chunk block size in bytes.  In practice $c=4KB$.
\item $u$ is the record size of detection request per block.  In practice, 
\item $u$=40. That includes block ID and fingerprint.
\item $m$ is the maximum memory allocated for deduplication purpose.  A $g$ fraction used for 
machine-machine network  request buffering and $(1-g)$ fraction used for memory-disk bucket buffering.
\item $e$ is the size of a duplicate summary record for each chunk block.
\item $\alpha_n$ is the startup cost for sending a message in a cluster. $\alpha_d$ is the startup cost 
such as seek for disk IO. $\beta$ is the time cost for in-memory duplicate comparison.
\end{itemize}
The system keeps at most  $ x$ copies of snapshots for each VM on average.  The total size of  global content fingerprints is $x*s*v/c*u *(1-d1)*(1-d2)$ where $c$ is the average chunk size and $u$ is the meta data size of each chunk fingerprint. In practice $c=4K$ and $u/c$  is about 100.  $x=10$ in the case of Alibaba cloud.

Define $r = s v (1-d_1)/(ck)$  which is the total number of duplicate detection requests issued at each machine and at each iteration.

We first discuss the memory usage and processing time  of 3 steps. 
 For Step 1,  the buffer for sending requests from one machine to another has a size of  $g*m/p$, and with such a buffering, the total number of outgoing communication messages from  each machine to other machines  can be 
\[
r u p/(g*m)
\]
The total  amount of data communicated among machines is relatively small: $r u p$ in the cluster, distributed among $p$ machines.

Once every machine receives detection requests and divide them into buckets, it writes the content to the disk once the buffer is full. The buffer for each bucket is $(1-g)m/q$ and the total number of disk write requests issued after the bucket buffer is full is:
\[
r u q/((1-g)*m)
\]
The total time for step 1  which  reads VM images and write accumulated detection requests  is:   
\[
r  ( c+  u) /b   +r u /m (\alpha_n  p/g  + \alpha_d q/(1-g)  )
\].

For Step 2,  part of memory at each machine is  to hold  a bucket of global index and accumulated requests. That is
\[
m_b= x*r *u*k(1-d_2)/q + r*u/q
\]
Thus the memory requirement for this portion can be made very small when setting a large q. On the other hand, as the system detects duplicates per hash bucket, we need to allocate buffer space for receiving  duplicate summary for each VM.  The total buffer size is $m-m_b$ which is used evenly for $v$ VMs.

The size of  the duplicate summary for each bucket is
\[
S_{sum}= sv(1-d_1)e /(k c q)
\]
We can buffer the outcome of multiple buckets. The total buffer factor is 
\[
(m-m_b)/ S_{sum}.
\]
The final bucket buffer for each VM is still fairly small, and writing such a buffer to the disk may involve two I/O requests (one to fetch the old block, and one is to update). The total seek cost involved 
\[
2*v*\alpha_d*q/ ((m-m_b)/S_{sum})= 2v r e  \alpha_d / (m-m_b)
\]
Thus the total time of Step 2 takes
\[
( x*r *k*u*(1-d_2) + r*u) / b_d  + r* \beta+   2v *r*e \alpha_d /  (m-m_b).
\]

The key cost of step 3  is to read the nonduplicate parts of each VM and output the backend storage. The time of Step 3  takes:
\[
2 r *c* (1-d_2) /b_d
\]
That assumes that when a content chunk is not a duplicate, there is a significant number of non-duplicate  chunks following that  chunk.

Thus the total time to process all $v$ virtual machines after $k$ iterations are:
\[
k [
r  ( c+  u) /b   +r u /m (\alpha_n  p/g  + \alpha_d q/(1-g)  )
+( x*r *k*u*(1-d_2) + r*u) / b_d  + r* \beta+   2v *r*e \alpha_d /  (m-m_b)
+2 r *c* (1-d_2) /b_d
]
\]
subject to conditions that
\[
m - m_b> 0
\]

The total disk requirement  per machine for hosting the global index  and meta  data of  accumulated requests is:
\[
x*r *k*u*(1-d2) + r*u.
\]
That is not so big, and is acceptable as we show later.

\subsection{A Comparison with Other Approaches}

The memory  space requirement for the data domain approach with bloomer filter is:
\[
x*r k u (1-d2)/r
\]
where $r$ is the bloom filter with about  1:10 ratio in practice.  The disk space used  is 
\[
x*r *k *u*(1-d_2).
\]

### 2013-03-08 hotstorage13/eval.tex
new

@@
 
-We have implemented a prototype of the parititon-based deduplication scheme based on the 
-Alibaba's cloud platform.  Objectives of our experimental evaluation are:
-1) Analyze the commonality of content data blocks and the popularity  of hot items. 
-2) Assess the effectiveness  of 3-level deduplication for reducing the storage cost of snapshot 
-backup. 
-3) Examine the impacts of CDS size on deduplication ratio.
+We have implemented a prototype of the parititon-based deduplication scheme on a Linux cluster
+based on Alibaba's Zene cloud platform.  Objectives of our experimental evaluation are:
+1) Analyze the processing time and througput of backup for a large cluster of virtual machines.
+2) Assess the effectiveness  of partition-based duplication detection 
+backup.  3) Examine the impacts of buffering during meta data exchange.
 
@@
 
-At Aliyun our target is to backup cluster up to 1000 nodes
-with 25 VMs on each.
+At Alibaba's Aliyun our target is to backup cluster up to 1000 nodes with 25 VMs on each machine.
 %We are running our deduplication/backup  service on 100 nodes.
@@
 %the CPU usage is very small during the experiments. 
-Based on the data studied,  each VM has about  40GB of storage  data usage on average,
-OS disk and data disk each takes about 50\% of storage space.
-The backup of VM snapshots is completed within two hours every day,
+Based on the Alibaba data studied,  each VM has about  40GB of storage  data usage on average
+including OS and user data disk.  The backup of VM snapshots is completed within a few  hours every night,
 and that translates to a backup throughput of 139GB per second, or 500TB per hour.
@@
 
-Since it's impossible to perform large scale analysis without affecting the VM performance,
-we sampled two data sets from real user VMs to measure the effectiveness of our deduplication scheme.
-Dataset1 is used study the detail impact of 3-level deduplication process,
-it compose of 35 VMs from 7 popular OSes: 
-Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
-5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
-The overall data size for this 700 full snapshots is 17.6 TB.
+%Since it's impossible to perform large scale analysis without affecting the VM performance,
+%We have sampled a data set from 1323 real user VMs from a cluster with 100 nodes 
+%to measure the effectiveness of our scheme.
+We have used a storage dataset of 1323 VM users collected from 100 Aliyun's cloud nodes to evaluate the effectiveness.
+In this dataset, there are 10 snapshots per each VM user and the total amount of space investigated is 23.5 terabytes.
+%This dataset contas compose of 35 VMs from 7 popular OSes: 
+%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
+%5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
+%The overall data size for this 700 full snapshots is 17.6 TB.
 
-Dataset2 contains the first snapshots of 1323 VMs' data disks from a small cluster with 100 nodes. 
-Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
-study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
-
+%This dataset  contains the snapshots of 1323 VMs.
+%Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
+%study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
 All data are divided into 2 MB fix-sized segments and each segment is divided into 
@@
 The signature for variable-sized blocks is computed using their SHA-1 hash. 
-Popularity of data blocks are collected through global counting 
-and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.
+%Popularity of data blocks are collected through global counting 
+%and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.
 
+We have also used a combination of level 1 duplicate detection using segement dirty bits and
+a bloom filter and prefetch cache  after level 1 basd on~\cite{Zhu}. 
+The bloomer filter settings  resutls a 1:10 ratio of index reduction for in-memory search before visiting
+the disk for the full index with 2\% false positives. The prefetching cache hit ratio is set to be 98\% based
+a number in ~\cite{Zhu}. Our actual cache hit ratio tested is close 90\%.
 \comments{
-a storage dataset of 1323 VM users collected from 100 Aliyun's cloud nodes to evaluate the effectiveness.
-In this dataset, there are 10 snapshots per each VM user and the total amount of space investigated 
-is 23.5 terabytes.
+
 Each VM file is  divided into content blocks of
@@
 
-\subsection{Effectiveness of 3-level Deduplication}
+%\subsection{Effectiveness of 3-level Deduplication}
 
@@
 
-Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication on dataset1.
-The X axis shows the overall impact in (a),  impact on OS disks in (b), and impact on data disks in (c).
-Each bar in the Y axis shows the data size after deduplication divided by the original data size.
-Level-1 elimination can reduce the data size to about 23\% of original data, namely it delivers close 77\% reduction.
-Level-2 elimination is applied to data that could pass level-1, it
-reduces the size further to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
-Level-3 elimination together with level 1 and 2
-reduces the size further to 8\% of original size, namely it delivers additional 10.5\% reduction.
-Level 2 elimination is more visible in OS disk than data disk, because data change frequency is really small
-when we sample last 10 snapshots of each user in 10 days. Nevertheless, the overall impact of level 2 is still significant.
-A 4.5\% of reduction from the original data represents about 450TB space saving for a 1000-node cluster.
+\begin{verbatim}
+q		50	100	250	275	300	450	500	750	1500	2000
+Memory meta data 0.161	0.0805	0.0322	0.029272727	0.026833333	0.017888889	0.0161	0.010733333	0.005366667	0.004025
+Global index 0.115	0.0575	0.023	0.020909091	0.019166667	0.012777778	0.0115	0.007666667	0.003833333	0.002875
+Seek (Step 1) 0.0212962960.0425 0.106 0.117 0.127777778	0.191666667	0.212962963	0.319444444	0.638888889	0.851851852
+Seek Option 6.388888889	12.77777778	31.94444444	35.13888889	38.33333333	57.5	63.88888889	95.83333333	191.6666667	255.5555556
+Total time 3.059031718	3.078670034	3.131061779	3.137163671	3.141047877	3.313871832	3.296994302	3.377385758	3.689876824	3.901831421
+throughput  per node 0.090805785	0.090226551	0.088716799	0.088544242	0.088434748	0.083822728	0.084251822	0.082246387	0.075281044	0.07119164
+
+\end{verbatim}
+
+Table~\ref{tab:overall} shows the performance of partition-based deduplication when 
+the number of partitons per machine varis from 50 to 2000.
+This is the overall time for a 100-node cluster and the throughput per machine reported  is the total 
+amount of virtual machine images divided by the processing time. The processng time includes the first scanning time
+of dirty VM segments to generate block figureprints and the second scann time for real backup.
 
@@
 %Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
-Figure~\ref{fig:oscds} shows the impact of different levels of deduplication for different OS releases.
-In this experiment, we tag each block in 350 OS disk snapshots from dataset1 as  ``new''
-if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot store;
-``CDS''  if this block can be found  in CDS;
-``Parent segment'' if  this block is marked unchanged in parent's segment recipe.
-``Parent block'' if  this block is marked unchanged in parent's block recipe.
-With this tagging, we compute the percentage of deduplication accomplished by each level.
-As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination,
-this is because the time interval between two snapshots in our dataset
-is quite short and the Aliyun cloud service makes a snapshot  everyday  for each VM.
-On the other hand,  CDS still finds lots of duplicates that inner VM deduplication can't find,
-contributing about 10\% of reduction on average.
-
-It is noticeable that level-1 deduplication doesn't work well for CentOS, a significant percentage of data is not
-eliminated until they reach level-3. It shows that even user upgrade his VM system heavily and frequently
-such that data locality is totally lost, those OS-related data can still be identified at level-3.
-
-In general we see a stable data reduction ratio for all OS varieties, ranging from 92\% to 97\%, that means
-the storage cost of 10 full snapshots combined is still smaller than the original disk size. And compare to 
-today's widely used copy-on-write snapshot technique, which is similar to our level-1 deduplication, our
-solution cut the snapshot storage cost by 64\%.
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.45\textwidth]{websearch.pdf}
-%\caption{ PDF-based figure.}
-%\label{fig:websearch}
-%\end{figure}
-
-%\begin{table}[hbt]
-%\caption{ Projected enrollment for the first five years.}
-%\begin{center}
-%\begin{tabular} {|c|c|c|c|c|c|}
-%\hline  & Year 1 & Year 2 &Year 3 & Year 4 & Year 5 \\
-%\hline Enrollment & 10&  15 & 20 & 25 & 30 ( $\le$ 40)\\
-%\hline
-%\end{tabular}
-%\end{center}
-%\label{tab:enrollment}
-%\end{table}
 
 \begin{verbatim}
-partition q/machine=		50	100	250	500	1000	2000
-Step 1
-Seek cost  for accumulating (option1)	0.015972222	0.031944444	0.079861111	0.159722222	0.319444444	0.638888889
-Seek for accumlation (option 2)     1.064814815	2.12962963	5.324074074	10.64814815	21.2962963	42.59259259
-
-Step 2
-Memory for index+bucket 	0.276	0.138	0.0552	0.0276	0.0138	0.0069
-Global index portion		0.23	0.115	0.046	0.023	0.0115	0.00575
-
-buffering factor 			-9.723320158	-8.537549407	-4.980237154	0.948616601	12.80632411	36.52173913
-Seek for writing dup sum per VM	-0.000357103	-0.0008134	-0.003486001	0.036603009	0.005422668	0.00380291
+q= is chosen between 500 or 100
+Memory limit:   20 30M   50M  75M  100M  200M
+Time:          3.2  3.11   3  2.99 2.96  2.95
+Time for two scans: 2.78 2.78 2.78 2.78 2.78
 \end{verbatim}

### 2013-03-08 hotstorage13/intro.tex
new

\section{Introduction}

%Virtualization is the engine behind many popular cloud computing platforms.
%Amazon, Alibaba,  and many others have provided public VM clouds that host
%tens of thousands of  virtual machines(VM) created for various active users.
Periodic  archiving of virtual machine (VM) snaps is important for a public cloud service provider
for long-term data  retention and fault recovery in case of machine failures.  
While VM backup  may  be mainly requested by users  in some providers,  
in the case of Alibaba which provides the largest public cloud service in China,
daily backup of VM images  is conducted automatically for all  active users 
to improve data reliability and availability.

The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
This issue has been addressed by   storage data deduplication ~\cite{venti02,bottleneck08} that
identifies redundant content duplicates among snapshots.  On the other hand, performing
deduplication adds significant  memory cost for comparison of content fingerprints. 
Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently. 
Cloud providers often wish that the backup service only consumes  the minimal resource usage without 
impacting any existing cloud service.  Another challenge for backup with deduplication is that deletion 
of old snapshot competes computing resource with noticable cost. That is because data dependence created 
by duplicate relationship among snapshots  adds processing complexity, especially when  
VMs can migrate around in the cloud.

Among the three factors - time, cost and de-deduplication efficiency, one of them has to be compromised for the other two. For instance, if we were build a deduplication system that has a high rate of duplication detection and has a very fast response time, 
it would need a lot of memory to hold fingerprint index and do fast comparison.  This leads to a compromise on cost. 
Our objective in this paper is to lower the cost incurred while sustaining the highest de-duplication ratio. 
%at the expense of processing latency.  
At the same time, we ensure the aggregate read/write throughput of the system 
is sufficiently scalable  for dealing with backup of a large number of virtual machine images. 
% This business model partially  resembles that of Amazon Glacier.

%Our solution  only uses a very small amount of memory space during backup while completing  snapshot backup and 
%deletion in a reasonable amount of time. 
The traditional approach to  deduplication for backup is an inline approach which follows
a sequence of VM block reading, duplicate detection,  and nonduplicate  block write to the 
backup storage.  
Our key idea  is to  perform parallel duplicate detection first for VM content blocks 
among all machines before performing actual data backup. Each machine
accumulates detection requests and  then performs detection   parititon by partition 
with minimal resource usage.
Fignureprint based partitioning allows highly parallel duplicate detection  and also simplifies 
reference counting management  during snapshot detection.
% as the entire process can also be divided into a
%parition-wise  deletion. 
With careful parallelism management and message buffering during cross-machine data exchange,
this partition-based  deduplication scheme can provide  a sufficient 
throughput for large-scale cloud data  backup.

%Our study shows that common data blocks
%occupy significant amount of storage space while they only take
%a small amount of resources to deduplicate.
%Separating deduplication into multi levels effectively accomplish the major space saving goal
%compare the global complete deduplication scheme, at the same time it makes
%the backup of different VMs to be independent for better fault tolerance.

%Restricting the scope of global deduplication reduces
%the inter-component  data dependenc during machine failure.

%Several operations are provided for creating and managing snapshots and snapshot trees,
%such as create snapshots, revert to any snapshot, and remove snapshots.
%VM snapshots is different from traditional file system backup from a few aspects:
%\begin{enumerate}
%\item The backup loads are heavy but resources are limited. The whole VM cluster have PBs of data and need to be backuped at daily basis, if not more frequently. But at the same time snapshot tasks must not affect the normal VM operations, which means only a tiny slice of CPU and memory can be used for this purpose.
%\item No file system semantics are provided. Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided.
%\item Snapshots can be shared between users. This does not only complicates the parent-child relationship between snapshots, but also require all snapshots be managed in a global namespace.
%\end{enumerate}

%In this paper we intorduce the deduplication scheme of snapshot storage in Aliyun's VM cloud. We exploit the 
The rest of the paper is arranged as follows. 
Section ~\ref{sect:background}
discusses on the background and related work.
Section ~\ref{sect:arch} presents our snapshot backup solution with request and index partitioning.
Section ~\ref{sect:analysis} summarizes  our analysis of the system performance.
Section ~\ref{sect:exper} presents  our evaluation results on the effectiveness.
Section ~\ref{sect:final} concludes this paper.
% talks about Aliyun's VM snapshot system and deduplication process. In section 4 we present
%the snapshot deduplication results of our real user VMs.

### 2013-03-08 hotstorage13/main.tex
new

--- 2012-05-06 vm_snapshot_sim/main.tex
@@
 %\title{Selective Deduplication for VM Snapshots in Cloud Storage}
-\title{Multi-level Selective Deduplication for VM Snapshots in Cloud Storage}
+\title{ Low-Cost Data Deduplication  for  Virtual Machine Backup in Cloud Storage}
 %\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
@@
 %\input{future}
-\input{2012concl}
+\input{concl}
 

### 2013-03-08 hotstorage13/eval.tex
t

@@
 \begin{verbatim}
+memory
 q		50	100	250	275	300	450	500	750	1500	2000
@@
 Seek (Step 1) 0.0212962960.0425 0.106 0.117 0.127777778	0.191666667	0.212962963	0.319444444	0.638888889	0.851851852
-Seek Option 6.388888889	12.77777778	31.94444444	35.13888889	38.33333333	57.5	63.88888889	95.83333333	191.6666667	255.5555556
+Seek Option 2: 6.388888889	12.77777778	31.94444444	35.13888889	38.33333333	57.5	63.88888889	95.83333333	191.6666667	255.5555556
 Total time 3.059031718	3.078670034	3.131061779	3.137163671	3.141047877	3.313871832	3.296994302	3.377385758	3.689876824	3.901831421

### 2013-03-08 hotstorage13/main.tex
t

--- 2013-03-06 hotstorage13/main.tex
@@
 %\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
+
 \author{
-Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$\\
-   {\normalsize $^\star$UC Santa Barbara, \{wei, tyang\}@cs.ucsb.edu}
+Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Tao Yang$^\star$\\
+   {\normalsize $^\star$UC Santa Barbara, \{wei, tyang\}@cs.ucsb.edu}\\
+   {\normalsize$^\dagger$Alibaba.com, \{hongtang, haojiang\}@alibaba.com}
 }

### 2013-03-08 hotstorage13/abs.tex
5 papges

@@
 memory and CPU resource to perform data duplication in order to remove
-excessive redudancy among image snapsots.
+excessive redudancy among snapsots.
 This paper presents a low-cost clustered deduplication soluton scalable for handling a large number 
 of virtual machines.  The key idea is to seperate duplicate detection from 
-the actual storage data backup instead of using inline deduplication.
-Global inddex and  detection requests are partitioned 
-among machines using  fingerprint values for parallel detection. 
-Each machine conducts duplicate detection partiton by partition indepdently
-with a minimal memory usage.
+the actual storage data backup instead of using inline deduplication, and partition
+global index and  detection requests among machines using  fingerprint values.
+Then each machine conducts duplicate detection partiton by partition indepdently with a minimal memory usage.
 %in parallel among all machines and  each machine full duplication detection is 

### 2013-03-08 hotstorage13/arch.tex
5 papges

@@
-\section{ Key Ideas and Design Architecture}
+\section{ Key Ideas and Architecture}
 \label{sect:arch}
@@
 for a period time  in a  partitioned manner.  Aggregated duplicate requests can be processed partition by partition. 
-We also accumulate the delete requests and perform them partition by partitions. 
+%We also accumulate the delete requests and perform them partition by partitions. 
 Since each partition corresponds to a small portion of global content index, the cost to 
@@
 
-\item {\bf Buffered data redistrubution in parallel processing of  detection  requests}.  
+\item {\bf Buffered data redistrubution in parallel duplicate detection}.  
 We let {\em global index} be the meta data containing the fingerprint values of all unique blocks
@@
 A block or the entire segment can be deleted if its reference counter is zero.
-As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
-We deal snapshot deletion in three steps similar to the VM snapshot backup.
-Step 1 is to read  the meta data of a snapshot such as segment and block
-recipes and  accumate  deletion requests in different machines  in the fingerprint based distribution.
-The second step  is to process the deletion requests within each partition and detect those records with zero 
-reference counters. The third step is that every VM gathers the confirmed deletion requests for its cotent and sends them
+%As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
+We perioidcally read all receipts of active 
+snapsots and compute the counter of all blocks while still following the fingerprint-based partitioning.
+That is based on the idea of mark-and-sweep~\cite{MarkSweep} while 
+we deal such snapshot deletion in three partition-based steps similar to the VM snapshot backup.
+Step 1 is to read  the meta data of snapshots such as segment and block
+recipes and  accumate  reference count requests in different machines  in the fingerprint based distribution.
+The second step  is to count references within each partition and detect those records with zero 
+reference. The third step is that every VM gathers the confirmed deletion requests for its cotent and sends them
 to the backup storage.
@@
 
-The above method requires the counter information to be consistently maintained in the global index.
-Another option to avoid maitaining its consitency is to perioidcally read all receipts of active 
-snapsots and compute the counter of all blocks while still following the fingerprint-based partitioning. 
+%The above method requires the counter information to be consistently maintained in the global index.
 %Finally the deleteion summary.

### 2013-03-08 hotstorage13/background.tex
5 papges

@@
 
-In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks represented as virtual disk image files in the host operating system.
+%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
+At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
+represented as virtual disk image files in the host operating system.
 For VM snapshot backup, file-level semantics are normally not provided.
@@
 %,NGmiddleware2011}.
-Today's commercial data backup systems (e.g. from EMC and NetApp)
+%Today's commercial data backup systems (e.g. from EMC and NetApp)
 %\cite{emc_avamar}\cite{datadomain_whitepaper}
-use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
-
+%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
 Several techniques have been proposed to speedup searching of duplicate
@@
 accessed together with high probability. It takes significant memory resource for filtering and caching.
-NG et al.~\cite{ NGmiddleware2011}  use
-a related filtering technique for integrating deduplication in Linux  file system and the memory
-consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
-Lillibridge et al.~\cite{sparseindex09} break list of chunks
-into large segments, the chunk IDs in each incoming segment are sampled and the segment is
-deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
-These are segments that share many chunk IDs with the incoming segment with high probability.
-Deepavali et al.~\cite{extreme_binning09}  use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
-That leads  to a smaller amount of memory usage for storing meta data in fingerprint
-lookup with a tradeoff of the reduced recall ratio.
+%NG et al.~\cite{ NGmiddleware2011}  use
+%a related filtering technique for integrating deduplication in Linux  file system and the memory
+%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
+%Lillibridge et al.~\cite{sparseindex09} break list of chunks
+%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
+%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
+%These are segments that share many chunk IDs with the incoming segment with high probability.
+The approximation techniques are studied in Deepavali et al.~\cite{extreme_binning09} and
+Zhang et al.~\cite{WeiZhangIEEE}  to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
+%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
+%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
+%lookup  
+In comparison, this paper focuses on  full deduplication without approximation.
 
-Additional inline deduplications are studied in ~\cite{idedup}. All of the above appraoches have focused on
-such inline duplicate detection, namely given a content chunk, how to detect if it is duplicate instantantly
-to trigger the data backup of this chunk or not before the detection request for the next chunk can be launched. 
+Additional inline deduplications are studied in ~\cite{sparseindex09,idedup}. All of the above appraoches have focused on
+such inline duplicate detection, namely given a content chunk block, how to detect if it is duplicate instantantly
+to trigger the data backup of this block or not before the detection request for the next blocks can be launched. 
 In our work, this constraint is relaxed and 

### 2013-03-08 hotstorage13/intro.tex
5 papges

@@
 %tens of thousands of  virtual machines(VM) created for various active users.
-Periodic  archiving of virtual machine (VM) snaps is important for a public cloud service provider
+Periodic  archiving of virtual machine (VM) snaps is important 
 for long-term data  retention and fault recovery in case of machine failures.  
-While VM backup  may  be mainly requested by users  in some providers,  
-in the case of Alibaba which provides the largest public cloud service in China,
-daily backup of VM images  is conducted automatically for all  active users 
-to improve data reliability and availability.
-
+For example, daily backup of VM images  is conducted automatically 
+at Alibaba which provides the largest public cloud service in China.
 The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
@@
 %In this paper we intorduce the deduplication scheme of snapshot storage in Aliyun's VM cloud. We exploit the 
+\comments{
 The rest of the paper is arranged as follows. 
@@
 Section ~\ref{sect:final} concludes this paper.
+}
 % talks about Aliyun's VM snapshot system and deduplication process. In section 4 we present

### 2013-03-08 hotstorage13/arch.tex
evaluation changes

@@
 The data flow of our partition-based  dupliate detectionis depicted in
-Figure~\ref{fig:flow}. let $v$ be the total number of virtual machines hosted in  
-a cluster,  we divide the backup into $k$  iterations. 
+Figure~\ref{fig:flow}. 
+%let $v$ be the total number of virtual machines hosted in  a cluster,  
+%we divide the backup into $k$  iterations. 
 \begin{figure}
@@
 \item
-The first step of each iteration is to read  $v/k$  virtual machine images in parallel on the cloud 
-cluster and issue backup requests. For those segments that have been modified since last backup indicated by 
+The first step is that each machine independently reads  
+%$v/k$  
+virtual machine images that need a backup
+and forms duplicate  detection requests. For those segments that have been modified since last backup indicated by 
 dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
@@
 \item The third step is to read  nonduplicate blocks from each VM and output to the final backup 
-storage. In this process, if a segment is not dirty, we only need to output the segment meta data 
+storage. Additionally, the global index on each machine is updated with the meta data of new chunk blocks added.
+In this process, if a segment is not dirty, we only need to output the segment meta data 
 such as reference pointers to the original segments previously saved in the backup.  
@@
 We impose a limit for memory allocated at each machine node to accomplish low-cost deduplication.  
-Memory usage for each step of above iteration is carefully controlled as follows.
+Memory usage for each step of above scheme is carefully controlled as follows.
 \begin{itemize}
@@
 its deletion log is too big. 
-Due to the paper constraint, we will not discuss the deletion operations in details.
+%Due to the paper constraint, we will not discuss the deletion operations in details.
 

### 2013-03-08 hotstorage13/eval.tex
evaluation changes

--- 2013-03-08 hotstorage13/eval.tex
@@
 
-We have implemented a prototype of the parititon-based deduplication scheme on a Linux cluster
-based on Alibaba's Zene cloud platform.  Objectives of our experimental evaluation are:
+We have implemented and evaluated a prototype of the parititon-based deduplication scheme on a Linux cluster
+of AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
 1) Analyze the processing time and througput of backup for a large cluster of virtual machines.
@@
 
-At Alibaba's Aliyun our target is to backup cluster up to 1000 nodes with 25 VMs on each machine.
+Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.  
+At Alibaba's Aliyun, the  target is to backup cluster of a few thousands nodes with 25 VMs on each machine.
 %We are running our deduplication/backup  service on 100 nodes.
@@
 including OS and user data disk.  The backup of VM snapshots is completed within a few  hours every night,
-and that translates to a backup throughput of 139GB per second, or 500TB per hour.
+%and that translates to an aggregated backup throughput of 139GB per second, or 500TB per hour.
+%  For 2 hours, every machine can do 139MB/second. For 3 hours, then 92MB/second
 For each VM, the system keeps 10 automatically-backed snapshots in the storage while
@@
 %to measure the effectiveness of our scheme.
-We have used a storage dataset of 1323 VM users collected from 100 Aliyun's cloud nodes to evaluate the effectiveness.
-In this dataset, there are 10 snapshots per each VM user and the total amount of space investigated is 23.5 terabytes.
+We have performed a trace-driven study using a dataset containing 10 snapsots of 35 VMs.
+That is part of a 1323 VM dataset  collected from 100 Aliyun's cloud nodes 
+in our earier work with  Alibaba Aliyun~\cite{WeiZhang}.
+%In this dataset, there are 10 snapshots per each VM user and the total amount of space 
+%investigated is 17.5 terabytes.
 %This dataset contas compose of 35 VMs from 7 popular OSes: 
@@
 %The overall data size for this 700 full snapshots is 17.6 TB.
-
 %This dataset  contains the snapshots of 1323 VMs.
@@
 
-We have also used a combination of level 1 duplicate detection using segement dirty bits and
-a bloom filter and prefetch cache  after level 1 basd on~\cite{Zhu}. 
-The bloomer filter settings  resutls a 1:10 ratio of index reduction for in-memory search before visiting
-the disk for the full index with 2\% false positives. The prefetching cache hit ratio is set to be 98\% based
-a number in ~\cite{Zhu}. Our actual cache hit ratio tested is close 90\%.
 \comments{
@@
 \begin{verbatim}
-q		50	100	250	275	300	450	500	750	1500	2000
+memory
+#partitions/node	50	100	250	275	300	450	500	750	1500	2000
 Memory meta data 0.161	0.0805	0.0322	0.029272727	0.026833333	0.017888889	0.0161	0.010733333	0.005366667	0.004025
@@
 Table~\ref{tab:overall} shows the performance of partition-based deduplication when 
-the number of partitons per machine varis from 50 to 2000.
-This is the overall time for a 100-node cluster and the throughput per machine reported  is the total 
-amount of virtual machine images divided by the processing time. The processng time includes the first scanning time
-of dirty VM segments to generate block figureprints and the second scann time for real backup.
+the number of partitons per machine ($q$) varies from 50 to 2000.
+Row 2 shows the memory usage needed to load a partition of global index and detection requests,
+varying from 161MB to 4.025MB. As we impose a constraint of 30MB, then only $q>300$ would be a viable choice.
+Row 3 shows the majority of memory usage is for global index.
+Row 4 is the total time for a 100-node cluster.
+Row 5 is  the throughput per machine reported  is the total 
+amount of virtual machine images divided by the processing time. 
+The processng time includes the first scanning time
+of dirty VM segments to generate block figureprints and the second scan time for real backup.
 
@@
 
+Table~\ref{tab:memory} shows the performance of partition-based deduplication when 
+the memory limit imposed on each node, varying from 
+The overall processing time does not have a signficant reduction as we increase memory usage  20MB to 200MB.
+As Row 2 shows, the time is mainly dominated by  the IO costs of two scans of VMs.
+Thus we conlude that using about 30MB is sufficient to have VM backup completed in parallel within about 3.11 hours.
+
 %Combining OS disks in all the VMs, we see the overall 7.4TB of data is reduced to 512GB. 
@@
 %content can be eliminated using the CDS also.
+
+We have also compared our pre-detection approach with another approach by combining
+dirtybit segement  detection and  the data domain method~\cite{Zhu}. 
+The bloomer filter setting  results a 1:10 ratio of index reduction for in-memory search before visiting
+the disk for the full index with 2\% false positives. The prefetching cache hit ratio is set to be 98.96\% based
+a number in ~\cite{Zhu}.
+We measure its  total time including one scan of VM dirty segemnts in about 1.38 hours.
+That approach takes about 3.19 hours comparable with our pre-detection scheme while its memory cost
+includes 1GB of bloom filters and additional space for cache. That is an significant amount of space,
+compeuting with other cloud service while memory cost of our setting is  insignifcant.
+
+%Our actual cache hit ratio tested is close 90\%.

### 2013-03-08 hotstorage13/intro.tex
evaluation changes

@@
 it would need a lot of memory to hold fingerprint index and do fast comparison.  This leads to a compromise on cost. 
-Our objective in this paper is to lower the cost incurred while sustaining the highest de-duplication ratio. 
+The objective of our project is to lower the cost incurred while sustaining the highest de-duplication ratio. 
 %at the expense of processing latency.  
@@
 backup storage.  
-Our key idea  is to  perform parallel duplicate detection first for VM content blocks 
+Our key idea  is to  first perform parallel duplicate pre-detection for VM content blocks 
 among all machines before performing actual data backup. Each machine
-accumulates detection requests and  then performs detection   parititon by partition 
+accumulates detection requests and  then performs pre-detection   parititon by partition 
 with minimal resource usage.
-Fignureprint based partitioning allows highly parallel duplicate detection  and also simplifies 
-reference counting management  during snapshot detection.
+Fignureprint based partitioning allows highly parallel duplicate pre-detection  and also simplifies 
+reference counting management.  
 % as the entire process can also be divided into a
@@
 With careful parallelism management and message buffering during cross-machine data exchange,
-this partition-based  deduplication scheme can provide  a sufficient 
-throughput for large-scale cloud data  backup.
+this pre-detecton scheme can provide  a sufficient throughput for large-scale cloud data  backup.
 

### 2013-03-08 hotstorage13/abs.tex
evaluation changes
ispell

@@
 In a virtualized cloud cluster, frequent  snapshot backup of virtual disks improves
-hosting  reliability; howver, it  takes significant 
+hosting  reliability; however, it  takes significant 
 memory and CPU resource to perform data duplication in order to remove
-excessive redudancy among snapsots.
-This paper presents a low-cost clustered deduplication soluton scalable for handling a large number 
-of virtual machines.  The key idea is to seperate duplicate detection from 
+excessive redundancy among snapshots.
+This paper presents a low-cost clustered deduplication solution scalable for handling a large number 
+of virtual machines.  The key idea is to separate duplicate detection from 
 the actual storage data backup instead of using inline deduplication, and partition
 global index and  detection requests among machines using  fingerprint values.
-Then each machine conducts duplicate detection partiton by partition indepdently with a minimal memory usage.
+Then each machine conducts duplicate pre-detection partition by partition independently with a minimal memory usage.
 %in parallel among all machines and  each machine full duplication detection is 
@@
 Our experiments show that  the proposed scheme 
-uses a very small amount of system resources while accomplishing a satisfactory backup throughput
-in a large cloud setting.
+uses a very small amount of system resources while delivering a satisfactory backup throughput.
+%in a large cloud setting.
 %which only reqiires a very small amount of memory and CPU resource.  

### 2013-03-08 hotstorage13/arch.tex
ispell

@@
 
-\item {\bf Seperation of duplicate detection and data backup.}
+\item {\bf Separation of duplicate detection and data backup.}
 %Request accumulation and partition-based deduplication.}
@@
 machine activities.  Our idea is to perform duplicate detection first before actual data backup.
-That requres a pre-scanning of  data  blocks of VM images and after that, real backup  for those nonduplicates
-is conducted. That does incur an extra  round of I/O reading for nonduplicate blocks while avoiding inline 
+That requires a pre-scanning of  data  blocks of VM images and after that, real backup  for those non-duplicates
+is conducted. That does incur an extra  round of I/O reading for non-duplicate blocks while avoiding inline 
 deduplication and leading to a much smaller resource requirement. 
-During duplicate detection phase, detection requests can be accmnulated on the disk 
+During duplicate detection phase, detection requests can be accumulated on the disk 
 for a period time  in a  partitioned manner.  Aggregated duplicate requests can be processed partition by partition. 
@@
 
-\item {\bf Buffered data redistrubution in parallel duplicate detection}.  
+\item {\bf Buffered data redistribution in parallel duplicate detection}.  
 We let {\em global index} be the meta data containing the fingerprint values of all unique blocks
 in the entire cluster and  the reference pointers which lead to the actual location of raw data.
-A dupliate detection request for a content block needs to be compared with the global index to determine if this
-block is nonduplicate. If it is a duplicate, return the correspinding reference pointer.
+A duplicate detection request for a content block needs to be compared with the global index to determine if this
+block is non-duplicate. If it is a duplicate, return the corresponding reference pointer.
 We conduct parallel processing of detection requests in all machines in a cloud cluster.
-A logical way to distribute detection requests is to parititon based on the content  hashing of data blocks
+A logical way to distribute detection requests is to partition based on the content  hashing of data blocks
 and the global index can also be partitioned accordingly in a  disjointed manner.
@@
 Therefore, there are two all-to-all data remapping operations involved.
-One is to map detection requests from VM-based requests to the fignerprint based distribution.  
-One is to map dupliate summary from fingerprint-based requests to the VM based distribution.  
-The redistribued data needs to be accumulated on the disk to minimize the use of memory.
+One is to map detection requests from VM-based requests to the fingerprint based distribution.  
+One is to map duplicate summary from fingerprint-based requests to the VM based distribution.  
+The redistributed data needs to be accumulated on the disk to minimize the use of memory.
 To minimize the cost of disk seek, outgoing or incoming data exchange messages need to be buffered to bundle small messages.
@@
 Then there will be a large number of storage  IO operations involved, suffering the huge seek overhead.
-We have designed an effient data exchange and disk data buffering  scheme to address this.
+We have designed an efficient data exchange and disk data buffering  scheme to address this.
 
@@
 be used in parallel for deduplication. 
-The nonduplicated snapshot blocks are stored either in a distribed file system built on
+The non-duplicate snapshot blocks are stored either in a distributed file system built on
 this cluster  or in another  external storage system. 
 We assume that  a small amount of local disk space and memory on each machine can be used 
-to store global index and request accmulation.
+to store global index and request accumulation.
 %Our design is to minimize the usage of local memory and storage on each machine.
@@
 \includegraphics[width=0.45\textwidth]{snapshopdata.pdf}
-\caption{ Metadata strucrure of a VM snapshot.}
+\caption{ Metadata structure of a VM snapshot.}
 \label{fig:snapshot}
@@
 If a segment is not changed from one snapshot to another, indicated by a dirty bit embedded in the virtual disk driver, 
-its content blocks are not changed as well, thus its segment recipe contains a reference pointer to an earlier segement.
-If a block is dupliate to another block in the system,  the block recipe contains a reference pointer to an earlier block.
+its content blocks are not changed as well, thus its segment recipe contains a reference pointer to an earlier segment.
+If a block is duplicate to another block in the system,  the block recipe contains a reference pointer to an earlier block.
 
@@
 
-The data flow of our partition-based  dupliate detectionis depicted in
+The data flow of our partition-based  duplicate detection is depicted in
 Figure~\ref{fig:flow}. 
@@
 \includegraphics[width=0.45\textwidth]{steps.pdf}
-\caption{ Processing steps of dupliate detection.}
+\caption{ Processing steps of duplicate detection.}
 \label{fig:flow}
@@
 The partition mapping is using a hash function applied to the content fingerprint. 
-Assuming all machines have a  homogenous resource configuration, each machine is evently  assigend with
-$q$ partitons of content hash and accumulates corresponding requests on the disk. 
+Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
+$q$ parititons of content hash and accumulates corresponding requests on the disk. 
 There are two options to assign buffers in each machine to buffer requests for each partition.
@@
 2) Each machine has $p$ receive buffers correspond to $p$ machines in the cluster and $q$ receive 
-buffers to temporarly accmulate messages from other machines, and then output each buffer to the local disk
+buffers to temporarily accumulate messages from other machines, and then output each buffer to the local disk
 when it becomes full.  Option 2 is much more efficient than Option 1 because $p+q$ is much smaller than
-$p\times q$, as a result each buffer has a bigger size to accmulate data and results in 
+$p\times q$, as a result each buffer has a bigger size to accumulate data and results in 
 much less disk seek overhead.
@@
 The system maintains the index of all chunk fingerprints divided in the buckets. We load the global index partition 
-and accumulated correspnding requests, and compare them to  identify the duplicated blocks.  
-Then we unloand them, load the global index and accumulated requests for another partition. 
+and accumulated corresponding requests, and compare them to  identify the duplicated blocks.  
+Then we unload them, load the global index and accumulated requests for another partition. 
 This process is repeated until all buckets are processed.
@@
 As chunk blocks are detected as duplicates, the meta information on duplicates is 
-remapped from fingerprinter-based distribution  to VM-based distribution. In this way, duplicate information 
+remapped from fingerprint-based distribution  to VM-based distribution. In this way, duplicate information 
 for segments of each VM is collected in one place, which will be used in next step. 
-In the sending side, each machine scans idenitified duplicates for one target machine,
-and then scans for another machine. In this way, it sends dummary summary to the corresponding machines one by one
+In the sending side, each machine scans identified duplicates for one target machine,
+and then scans for another machine. In this way, it sends duplicate summary to the corresponding machines one by one
 to minimize the startup cost for sending a message.
@@
 
-\item The third step is to read  nonduplicate blocks from each VM and output to the final backup 
+\item The third step is to read  non-duplicate blocks from each VM and output to the final backup 
 storage. Additionally, the global index on each machine is updated with the meta data of new chunk blocks added.
@@
 %%accumulating duplicate summary for each targeted VM.   Once  each machine processes a bucket of  duplicate detection requests, 
-The duplicate summary sent other machines and accmumated for each VM contains
+The duplicate summary sent other machines and acclimated for each VM contains
 the block ID and  the reference pointer.   
@@
 memory is used to hold the meta information summary of all duplicate blocks obtained  from Step 2. 
-Another memory usage is to fetch a sequence of blocks from a virtual machines (most of them are nonduplicate) 
+Another memory usage is to fetch a sequence of blocks from a virtual machines (most of them are non-duplicate) 
 and write them to the  backup storage.
@@
 
-{\bf Snapshot deleteion.} Each virtual machine will keep at most $x$ snapshots of VM images and thus
-expired snapshots will be deleted unless its owern explicitly asks for its retention. 
+{\bf Snapshot deletion.} Each virtual machine will keep at most $x$ snapshots of VM images and thus
+expired snapshots will be deleted unless its owner explicitly asks for its retention. 
 A block or the entire segment can be deleted if its reference counter is zero.
 %As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
-We perioidcally read all receipts of active 
-snapsots and compute the counter of all blocks while still following the fingerprint-based partitioning.
+We periodically read all receipts of active 
+snapshots and compute the counter of all blocks while still following the fingerprint-based partitioning.
 That is based on the idea of mark-and-sweep~\cite{MarkSweep} while 
@@
 Step 1 is to read  the meta data of snapshots such as segment and block
-recipes and  accumate  reference count requests in different machines  in the fingerprint based distribution.
+recipes and  accumulate  reference count requests in different machines  in the fingerprint based distribution.
 The second step  is to count references within each partition and detect those records with zero 
-reference. The third step is that every VM gathers the confirmed deletion requests for its cotent and sends them
+reference. The third step is that every VM gathers the confirmed deletion requests for its content and sends them
 to the backup storage.

### 2013-03-08 hotstorage13/background.tex
ispell

@@
 
-Additional inline deduplications are studied in ~\cite{sparseindex09,idedup}. All of the above appraoches have focused on
-such inline duplicate detection, namely given a content chunk block, how to detect if it is duplicate instantantly
+Additional inline deduplication techniques are studied in ~\cite{sparseindex09,idedup}. All of the above approaches have focused on
+such inline duplicate detection, namely given a content chunk block, how to detect if it is duplicate instantly
 to trigger the data backup of this block or not before the detection request for the next blocks can be launched. 
@@
 there is a waiting time for many duplicate detection requests. Our goal is to minimizing  computing  resource without
-affeting the overall time of backup.
+affecting the overall time of backup.

### 2013-03-08 hotstorage13/eval.tex
ispell

@@
 
-We have implemented and evaluated a prototype of the parititon-based deduplication scheme on a Linux cluster
+We have implemented and evaluated a prototype of the partition-based deduplication scheme on a Linux cluster
 of AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
-1) Analyze the processing time and througput of backup for a large cluster of virtual machines.
+1) Analyze the processing time and throughput of backup for a large cluster of virtual machines.
 2) Assess the effectiveness  of partition-based duplication detection 
@@
 %to measure the effectiveness of our scheme.
-We have performed a trace-driven study using a dataset containing 10 snapsots of 35 VMs.
+We have performed a trace-driven study using a dataset containing 10 snapshots of 35 VMs.
 That is part of a 1323 VM dataset  collected from 100 Aliyun's cloud nodes 
-in our earier work with  Alibaba Aliyun~\cite{WeiZhang}.
+in our earlier work with  Alibaba Aliyun~\cite{WeiZhangIEEE}.
 %In this dataset, there are 10 snapshots per each VM user and the total amount of space 
@@
 Table~\ref{tab:overall} shows the performance of partition-based deduplication when 
-the number of partitons per machine ($q$) varies from 50 to 2000.
+the number of parititons per machine ($q$) varies from 50 to 2000.
 Row 2 shows the memory usage needed to load a partition of global index and detection requests,
@@
 amount of virtual machine images divided by the processing time. 
-The processng time includes the first scanning time
-of dirty VM segments to generate block figureprints and the second scan time for real backup.
+The processing time includes the first scanning time
+of dirty VM segments to generate block fingerprints and the second scan time for real backup.
 
@@
 the memory limit imposed on each node, varying from 
-The overall processing time does not have a signficant reduction as we increase memory usage  20MB to 200MB.
+The overall processing time does not have a significant reduction as we increase memory usage  20MB to 200MB.
 As Row 2 shows, the time is mainly dominated by  the IO costs of two scans of VMs.
-Thus we conlude that using about 30MB is sufficient to have VM backup completed in parallel within about 3.11 hours.
+Thus we conclude that using about 30MB is sufficient to have VM backup completed in parallel within about 3.11 hours.
 
@@
 We have also compared our pre-detection approach with another approach by combining
-dirtybit segement  detection and  the data domain method~\cite{Zhu}. 
+dirtybit segment  detection and  the data domain method~\cite{Zhu}. 
 The bloomer filter setting  results a 1:10 ratio of index reduction for in-memory search before visiting
@@
 a number in ~\cite{Zhu}.
-We measure its  total time including one scan of VM dirty segemnts in about 1.38 hours.
+We measure its  total time including one scan of VM dirty segments in about 1.38 hours.
 That approach takes about 3.19 hours comparable with our pre-detection scheme while its memory cost
 includes 1GB of bloom filters and additional space for cache. That is an significant amount of space,
-compeuting with other cloud service while memory cost of our setting is  insignifcant.
+competing with other cloud service while memory cost of our setting is  insignificant.
 

### 2013-03-08 hotstorage13/intro.tex
ispell

@@
 impacting any existing cloud service.  Another challenge for backup with deduplication is that deletion 
-of old snapshot competes computing resource with noticable cost. That is because data dependence created 
+of old snapshot competes computing resource also. That is because data dependence created 
 by duplicate relationship among snapshots  adds processing complexity, especially when  
@@
 The traditional approach to  deduplication for backup is an inline approach which follows
-a sequence of VM block reading, duplicate detection,  and nonduplicate  block write to the 
+a sequence of VM block reading, duplicate detection,  and non-duplicate  block write to the 
 backup storage.  
@@
 among all machines before performing actual data backup. Each machine
-accumulates detection requests and  then performs pre-detection   parititon by partition 
+accumulates detection requests and  then performs pre-detection   partition by partition 
 with minimal resource usage.
-Fignureprint based partitioning allows highly parallel duplicate pre-detection  and also simplifies 
+Fingerprint based partitioning allows highly parallel duplicate pre-detection  and also simplifies 
 reference counting management.  
@@
 With careful parallelism management and message buffering during cross-machine data exchange,
-this pre-detecton scheme can provide  a sufficient throughput for large-scale cloud data  backup.
+this pre-detection scheme can provide  a sufficient throughput for backup.
 

### 2013-03-08 hotstorage13/main.tex
5 papges
ispell

--- 2013-03-06 hotstorage13/main.tex
@@
 %\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
+
 \author{
-Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$\\
-   {\normalsize $^\star$UC Santa Barbara, \{wei, tyang\}@cs.ucsb.edu}
+Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
+{\normalsize$^\star$Department of Computer Science, University of California at Santa Barbara}
+  {\normalsize$^\dagger$Alibaba Inc.}
 }
+
+% \{wei, tyang\}@cs.ucsb.edu
 
@@
 %  }
-{
+{\small
 \bibliographystyle{abbrv}

### 2013-03-08 hotstorage13/main.tex
fix bib refs

@@
 Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
-{\normalsize$^\star$Department of Computer Science, University of California at Santa Barbara}
+{\normalsize$^\star$ University of California at Santa Barbara} \ \ \ 
   {\normalsize$^\dagger$Alibaba Inc.}
@@
 \bibliographystyle{abbrv}
-\bibliography{library,dedup1}
+\bibliography{library}
 }

### 2013-03-09 hotstorage13/abs.tex
ad

@@
 hosting  reliability; however, it  takes significant 
-memory and CPU resource to perform data duplication in order to remove
+memory resource to perform data duplication in order to remove
 excessive redundancy among snapshots.
-This paper presents a low-cost clustered deduplication solution scalable for handling a large number 
+This paper presents a low-cost deduplication solution scalable for a large number 
 of virtual machines.  The key idea is to separate duplicate detection from 
@@
 Another optimization is to allocate and control
-buffer space for exchanging  detection messages and duplicate summary among machines.
+buffer space for exchanging  detection requests and duplicate summary among machines.
 %The memory requirement and disk usage for the proposed solution is very small while the overall thoughput

### 2013-03-09 hotstorage13/arch.tex
Add graphs
ad

@@
 This setting requires OS to keep the metadata for segment dirty bits and the amount of space for such segment 
-dirty bits is negligible. In the second level of deduplication, remaining content blocks of each VM 
-are compared with the signatures of all unique  blocks stored in the previous snapshots.
+dirty bits is negligible. In the second level of deduplication, content blocks of dirty segments at each VM 
+are compared with the fingerprints of unique  blocks from the previous snapshots.
 
@@
 content fingerprints of stored chunks with the new chunks scanned during 
-the backup process. Bloom filters and caching allows some of content 
-fingerprints to be stored on the cheap disks~\cite{bottleneck08}. Such an optimization is good 
-for inline deduplication where chunks scanned need to be determined to be duplicate or not instantly without 
-waiting while  it memory consumption is still significant in competing with stand virtual 
-machine activities.  Our idea is to perform duplicate detection first before actual data backup.
-That requires a pre-scanning of  data  blocks of VM images and after that, real backup  for those non-duplicates
-is conducted. That does incur an extra  round of I/O reading for non-duplicate blocks while avoiding inline 
+the backup process. 
+%Bloom filters and caching allows some of content 
+%fingerprints to be stored on the cheap disks~\cite{bottleneck08}. Such an optimization is good 
+%for inline deduplication where chunks scanned need to be determined to be duplicate or not instantly without 
+%waiting while  it memory consumption is still significant in competing with stand virtual 
+%machine activities.  
+Our approach is to perform duplicate detection first before actual data backup.
+That requires a pre-scanning of  data  blocks in dirty VM segments  and after that, real backup  for those non-duplicates
+is conducted. That does incur an extra  round of local VM block reading while avoiding inline 
 deduplication and leading to a much smaller resource requirement.  
@@
 Since each partition corresponds to a small portion of global content index, the cost to 
-process requests within a partition is significant smaller than process all the requests globally.
+process requests within a partition is significantly smaller than processing all the requests globally.
 
 \item {\bf Buffered data redistribution in parallel duplicate detection}.  
-We let {\em global index} be the meta data containing the fingerprint values of all unique blocks
+Let {\em global index} be the meta data containing the fingerprint values of unique blocks of snapshots
 in the entire cluster and  the reference pointers which lead to the actual location of raw data.
-A duplicate detection request for a content block needs to be compared with the global index to determine if this
-block is non-duplicate. If it is a duplicate, return the corresponding reference pointer.
-We conduct parallel processing of detection requests in all machines in a cloud cluster.
-A logical way to distribute detection requests is to partition based on the content  hashing of data blocks
-and the global index can also be partitioned accordingly in a  disjointed manner.
+%A duplicate detection request for a content block needs to be compared with the global index to determine if this
+%block is non-duplicate. If it is a duplicate, return the corresponding reference pointer.
+We conduct parallel processing of detection requests in all machines involved. 
+A logical way to distribute detection requests is to partition based on fingerprint values of content blocks
+in a  disjointed manner.
 Initial data follows the VM distribution among machines and the detected results 
 represented as  duplicate summary need to be collected following VM distribution. 
-Therefore, there are two all-to-all data remapping operations involved.
-One is to map detection requests from VM-based requests to the fingerprint based distribution.  
-One is to map duplicate summary from fingerprint-based requests to the VM based distribution.  
+Therefore, there are two all-to-all data redistribution operations involved.
+One is to map detection requests from VM-based distribution to fingerprint based distribution.  
+One is to map duplicate summary from fingerprint-based distribution to VM based distribution.  
 The redistributed data needs to be accumulated on the disk to minimize the use of memory.
-To minimize the cost of disk seek, outgoing or incoming data exchange messages need to be buffered to bundle small messages.
+To minimize the excessive disk seek cost, outgoing or incoming data exchange messages need to be buffered to bundle small messages.
 Given there are $p\times q$ partitions where $p$ is the number of machines and $q$ is the number of fingerprint-based partitions
-at each machine, the number of buffers is big and space per each buffer  is small given the memory constraint.
-Then there will be a large number of storage  IO operations involved, suffering the huge seek overhead.
+at each machine, the number of buffers is big and space per each buffer  is small given the memory constraint,
+counteracting seek cost reduction.  
+%Then there will be a large number of storage  IO operations involved, suffering the huge seek overhead.
 We have designed an efficient data exchange and disk data buffering  scheme to address this.
@@
 be used in parallel for deduplication. 
-The non-duplicate snapshot blocks are stored either in a distributed file system built on
-this cluster  or in another  external storage system. 
-We assume that  a small amount of local disk space and memory on each machine can be used 
+A small amount of local disk space and memory on each machine can be used 
 to store global index and request accumulation.
+The real backup storage can be either a distributed file system built on
+this cluster  or use another  external storage system. 
 %Our design is to minimize the usage of local memory and storage on each machine.
@@
 %our scheme uses a single-thread procedure on each machine to minimize the use of CPU, network bandwidth, and disk bandwidth.
-\subsection{Data Structure}
+\subsection{Snapshot Representation}
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{snapshopdata.pdf}
+\includegraphics[width=0.4\textwidth]{snapshotdata.pdf}
 \caption{ Metadata structure of a VM snapshot.}
@@
 directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
-An VM image is divided into a set of segments and each  segment contains hundreds of content blocks from the bottom level.
+An VM image is divided into a set of segments and each  segment contains hundreds of content blocks. 
 These blocks are of variable-size, partitioned using
@@
 %To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
-
-Segment metadata (called segment recipe) records its  content block hashes and data pointers. 
-The snapshot recipe contains a list of segments and other meta data information.
+The snapshot metadata (called snapshot recipe) contains a list of segments and other meta data information.
+Segment metadata (called segment recipe) contains its  content block fingerprints and reference pointers. 
 If a segment is not changed from one snapshot to another, indicated by a dirty bit embedded in the virtual disk driver, 
-its content blocks are not changed as well, thus its segment recipe contains a reference pointer to an earlier segment.
-If a block is duplicate to another block in the system,  the block recipe contains a reference pointer to an earlier block.
+%its content blocks are not changed as well, thus 
+its segment recipe contains a reference pointer to an earlier segment.
+For a dirty segment, if one of its blocks is duplicate to another block in the system,  
+the block recipe contains a reference pointer to the earlier block.
 
@@
 
-The data flow of our partition-based  duplicate detection is depicted in
-Figure~\ref{fig:flow}. 
+The data flow of our multi-step duplicate detection is depicted in Figure~\ref{fig:flow}. 
 %let $v$ be the total number of virtual machines hosted in  a cluster,  
@@
 dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
-information such as chunk fingerprints,  sends the metadata of a chunk block, and accumulate  into 
+information such as chunk fingerprints,  sends the metadata of a chunk block, and accumulates  into 
 a partition bucket on the temporary disk storage. 
@@
 1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
-since any content block in a VM image of this machine can be sent to any of these partitions.
-2) Each machine has $p$ receive buffers correspond to $p$ machines in the cluster and $q$ receive 
-buffers to temporarily accumulate messages from other machines, and then output each buffer to the local disk
-when it becomes full.  Option 2 is much more efficient than Option 1 because $p+q$ is much smaller than
+since a content block in a VM image of this machine can be sent to any of these partitions.
+2) Each machine allocates $p$ send buffers correspond to send requests to $p$ machines and 
+$p$ receive buffers to collect requests  from other machines.
+Then the system copies requests in each $p$ disk buffers to  $q$ local disk buffers,
+and outputs each disk buffer to one of the request partitions on the disk
+when this disk buffer becomes full.  Option 2 is much more efficient than Option 1 because $2p+q$ is much smaller than
 $p\times q$, as a result each buffer has a bigger size to accumulate data and results in 
@@
 \item
-The second step is to perform duplicate detection for  all requests accumulated in the partitions.  
-The system maintains the index of all chunk fingerprints divided in the buckets. We load the global index partition 
-and accumulated corresponding requests, and compare them to  identify the duplicated blocks.  
-Then we unload them, load the global index and accumulated requests for another partition. 
-This process is repeated until all buckets are processed.
+The second step is to load disk data and perform duplicate detection at each machine for  all accumulated 
+requests one partition at a time.
+% in the partitions.  
+%The system maintains the index of all chunk fingerprints divided in the buckets. 
+%The system loads the global index partition 
+%and accumulated corresponding requests, and compare them to  identify the duplicated blocks.  
+%Then we unload them, load the global index and accumulated requests for another partition. 
+%This process is repeated until all buckets are processed.
+At each iteration, as in-memory comparison between an index partition and request partition
+is completed,  
+duplicate information for segments of each VM is routed to  from fingerprint-based distribution  to VM-based distribution. 
+The duplicate summary contains the block ID and  the reference pointer for each detected duplicate block.   
+Each machine uses memory space of the request partition as a send buffer with no extra memory space required.
+But it needs to allocate $p$ receive buffers to collect duplicate summary from other machines.
+It also allocates $v$ disk buffers to copy duplicate summary from $p$ receive buffers and output to the local disk
+when disk buffers are full.
 
-As chunk blocks are detected as duplicates, the meta information on duplicates is 
-remapped from fingerprint-based distribution  to VM-based distribution. In this way, duplicate information 
-for segments of each VM is collected in one place, which will be used in next step. 
-In the sending side, each machine scans identified duplicates for one target machine,
-and then scans for another machine. In this way, it sends duplicate summary to the corresponding machines one by one
-to minimize the startup cost for sending a message.
-In the receiving side, 
+%. In this way, it sends duplicate summary to the corresponding machines one by one to minimize the startup cost for sending a message.
+%In the receiving side, 
 %All-to-all machines data exchange is conducted  so that  
-each machine allocates $q$ receive buffers corresponding to
-$q$ local partitions, to hold received messages from other machines.  
-When a receive buffer for a VM is  full, the data is written to the local disk storage. 
+%each machine allocates $q$ receive buffers corresponding to
+%$q$ local partitions, to hold received messages from other machines.  
+%When a receive buffer for a VM is  full, the data is written to the local disk storage. 
 %These substeps are repeated as the stream of data is exchanged when each machine compares through all $q$ partitions.
 
-\item The third step is to read  non-duplicate blocks from each VM and output to the final backup 
-storage. Additionally, the global index on each machine is updated with the meta data of new chunk blocks added.
-In this process, if a segment is not dirty, we only need to output the segment meta data 
-such as reference pointers to the original segments previously saved in the backup.  
-If a segment is dirty,  we use the duplicate summary information from Step 2 for internal 
-duplicate blocks of this dirty segment and output the remaining non-duplicate blocks to the backup storage.
+\item The third step is to perform real backup one VM at a time.
+The system loads the duplicate summary of a VM obtained from Step 2, 
+reads  dirty segments of a VM, and output non-duplicate blocks to the final backup 
+storage. Additionally, the global index on each machine is updated with the meta data of new chunk blocks. 
+In this process, if a segment is not dirty, the system only needs to output the segment meta data 
+such as reference pointers to the original segments previously saved in the backup storage.  
+%If a segment is dirty,  the system  use the duplicate summary information from Step 2 for internal 
+%duplicate blocks of this dirty segment and output the remaining non-duplicate blocks to the backup storage.
 \end{itemize}
@@
 We impose a limit for memory allocated at each machine node to accomplish low-cost deduplication.  
-Memory usage for each step of above scheme is carefully controlled as follows.
+Memory usage for each step of the above scheme is carefully controlled as follows.
 \begin{itemize}
-\item For Step 1, the allocated memory for each machine is evenly divided for $p$ send buffers and $q$ receive buffers.
+\item For Step 1, the allocated memory for each machine is divided for 
+1) a disk buffer to read dirty segments; 2) $2p$ send/receive buffers and $q$ disk buffers.
 
@@
 \item 
-For Step 2,  the allocated memory serves 2 purposes. 1) Space for hosting a partition of global index and 
-the corresponding partition of  deduplication requests. 2) Buffer space for $q$ receive buffers.
+For Step 2,  the allocated memory at each machine is divided for 1) space for hosting a global index partition and 
+the corresponding request partition; 2) $p$ receive buffers and $v$ disk buffers.
 %%accumulating duplicate summary for each targeted VM.   Once  each machine processes a bucket of  duplicate detection requests, 
-The duplicate summary sent other machines and acclimated for each VM contains
-the block ID and  the reference pointer.   
 %For each machine which hosts $v$  VMs, and will receive messages from many other machines, 
@@
 \item For Step 3 to  perform the real backup for each VM,
-memory is used to hold the meta information summary of all duplicate blocks obtained  from Step 2. 
-Another memory usage is to fetch a sequence of blocks from a virtual machines (most of them are non-duplicate) 
-and write them to the  backup storage.
-
+the allocated memory is divided for 1) a disk buffer to read dirty segments of a VM and   
+write non-duplicate raw blocks to the  backup storage.
+2) summary of duplicate blocks within dirty segments of  a VM.
 \end{itemize}
@@
 
-{\bf Snapshot deletion.} Each virtual machine will keep at most $x$ snapshots of VM images and thus
+{\bf Snapshot deletion.} Each VM will keep a limited number of  automatically-saved VM snapshots and thus
 expired snapshots will be deleted unless its owner explicitly asks for its retention.
-A block or the entire segment can be deleted if its reference counter is zero.
+We adopt the idea of mark-and-sweep~\cite{MarkSweep}. 
+A block or a segment can be deleted if its reference count is zero.
 %As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
-We periodically read all receipts of active 
-snapshots and compute the counter of all blocks while still following the fingerprint-based partitioning.
-That is based on the idea of mark-and-sweep~\cite{MarkSweep} while 
-we deal such snapshot deletion in three partition-based steps similar to the VM snapshot backup.
-Step 1 is to read  the meta data of snapshots such as segment and block
-recipes and  accumulate  reference count requests in different machines  in the fingerprint based distribution.
-The second step  is to count references within each partition and detect those records with zero 
-reference. The third step is that every VM gathers the confirmed deletion requests for its content and sends them
-to the backup storage.
-The archival data repository may log these deletion requests,  and will periodically perform a compaction operation when 
+To delete useless  blocks or segments periodically, we read the meta data  of live 
+snapshots and compute the reference count of all blocks and segments  in parallel
+while following the fingerprint-based partitioning.
+Similar to the duplicate pre-detection process, reference counting is conducted in multi-steps. 
+Step 1 is to read  the metadata of snapshots such as segment and block
+recipes and  to accumulate  reference count requests in different machines  in the fingerprint based distribution.
+Step  2 is to count references within each partition and detect those records with zero 
+reference. 
+%Step 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.
+The backup  data repository logs deletion instructions,  and will periodically perform a compaction operation when 
 its deletion log is too big. 

### 2013-03-09 hotstorage13/background.tex
ad

@@
 Only raw access information at disk block level are provided.
-Each physical hosts many VMs and a cloud cluster has  petabytes of data that need to be backed up at daily basis, 
-if not more frequently. But at the same time snapshot tasks must not affect the normal cloud service, 
-which means that ideally only a very small slice of CPU and memory can be used for the backup purpose.
+Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
+Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
+only a very small slice of cluster resource can be used for the backup purpose.
 
@@
 %These are segments that share many chunk IDs with the incoming segment with high probability.
-The approximation techniques are studied in Deepavali et al.~\cite{extreme_binning09} and
-Zhang et al.~\cite{WeiZhangIEEE}  to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
+The approximation techniques are studied in~\cite{extreme_binning09,WeiZhangIEEE}  
+%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
+to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
 %use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.

### 2013-03-09 hotstorage13/eval.tex
ad

@@
 
-We have implemented and evaluated a prototype of the partition-based deduplication scheme on a Linux cluster
-of AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
-1) Analyze the processing time and throughput of backup for a large cluster of virtual machines.
-2) Assess the effectiveness  of partition-based duplication detection 
-backup.  3) Examine the impacts of buffering during meta data exchange.
+We have implemented and evaluated a prototype of our multi-step deduplication scheme on a Linux cluster
+of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
+1) Analyze the throughput and effectiveness for a large number of virtual machines.
+Compare with the data domain approach~\cite{bottleneck08}.
+2) Examine the impacts of buffering during metadata exchange.
 
@@
 Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.  
-At Alibaba's Aliyun, the  target is to backup cluster of a few thousands nodes with 25 VMs on each machine.
+At Alibaba's Aliyun, each multi-core machine   hosts  up to 25 VMs and 
 %We are running our deduplication/backup  service on 100 nodes.
@@
 %the CPU usage is very small during the experiments. 
-Based on the Alibaba data studied,  each VM has about  40GB of storage  data usage on average
-including OS and user data disk.  The backup of VM snapshots is completed within a few  hours every night,
+based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
+including OS and user data disk.  
+For each VM, the system keeps 10 automatically-backed snapshots in the storage while
+a user may instruct extra snapshots to be saved.
+The backup of VM snapshots is completed within a few  hours every night,
 %and that translates to an aggregated backup throughput of 139GB per second, or 500TB per hour.
 %  For 2 hours, every machine can do 139MB/second. For 3 hours, then 92MB/second
-For each VM, the system keeps 10 automatically-backed snapshots in the storage while
-a user may instruct extra snapshots to be saved.
 
@@
 We have also compared our pre-detection approach with another approach by combining
-dirtybit segment  detection and  the data domain method~\cite{Zhu}. 
+dirtybit segment  detection and  the data domain method~\cite{bottleneck08}. 
 The bloomer filter setting  results a 1:10 ratio of index reduction for in-memory search before visiting
 the disk for the full index with 2\% false positives. The prefetching cache hit ratio is set to be 98.96\% based
-a number in ~\cite{Zhu}.
+a number in ~\cite{bottleneck08}.
 We measure its  total time including one scan of VM dirty segments in about 1.38 hours.

### 2013-03-09 hotstorage13/intro.tex
ad

@@
 it would need a lot of memory to hold fingerprint index and do fast comparison.  This leads to a compromise on cost. 
-The objective of our project is to lower the cost incurred while sustaining the highest de-duplication ratio. 
-%at the expense of processing latency.  
-At the same time, we ensure the aggregate read/write throughput of the system 
-is sufficiently scalable  for dealing with backup of a large number of virtual machine images. 
+The objective of our project is to lower the cost incurred while sustaining the highest de-duplication ratio
+and  the sufficient deduplication  throughput for dealing with a large number of virtual machine images. 
 % This business model partially  resembles that of Amazon Glacier.
@@
 %parition-wise  deletion. 
-With careful parallelism management and message buffering during cross-machine data exchange,
+With careful parallelism and buffer  management,
 this pre-detection scheme can provide  a sufficient throughput for backup.

### 2013-03-09 hotstorage13/arch.tex
w

@@
 %our scheme uses a single-thread procedure on each machine to minimize the use of CPU, network bandwidth, and disk bandwidth.
-\subsection{Snapshot Representation}
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{snapshotdata.pdf}
+\includegraphics[width=0.5\textwidth]{snapshotdata.pdf}
 \caption{ Metadata structure of a VM snapshot.}
@@
 \end{figure}
+\subsection{Snapshot Representation}
 
@@
 
+\begin{figure*}[tbhp]
+\centering
+\includegraphics[width=0.75\textwidth]{steps.pdf}
+\caption{Processing flow in Phase 1 (VM scan/request accumulation) and Phase  2 (fingerprint comparison and duplicate summary output)
+ for duplicate detection.}
+\label{fig:flow}
+\end{figure*}
+
 \subsection{Processing flow and resource usage}
-
-The data flow of our multi-step duplicate detection is depicted in Figure~\ref{fig:flow}. 
+The data flow of our multi-phase duplicate detection is depicted in Figure~\ref{fig:flow}. 
 %let $v$ be the total number of virtual machines hosted in  a cluster,  
 %we divide the backup into $k$  iterations. 
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{steps.pdf}
-\caption{ Processing steps of duplicate detection.}
-\label{fig:flow}
-\end{figure}
-
-\begin{itemize}
-\item
-The first step is that each machine independently reads  
+%\begin{itemize}
+%\item
+The first phase is that each machine independently reads  
 %$v/k$  
@@
 %Note that we only accumulate requests with their meta data information.
-\item
-The second step is to load disk data and perform duplicate detection at each machine for  all accumulated 
+%\item
+The second phase is to load disk data and perform duplicate detection at each machine for  all accumulated 
 requests one partition at a time.
@@
 
-\item The third step is to perform real backup one VM at a time.
-The system loads the duplicate summary of a VM obtained from Step 2, 
+%\item 
+The third phase is to perform real backup one VM at a time.
+The system loads the duplicate summary of a VM obtained from Phase 2, 
 reads  dirty segments of a VM, and output non-duplicate blocks to the final backup 
@@
 %duplicate blocks of this dirty segment and output the remaining non-duplicate blocks to the backup storage.
-\end{itemize}
+%\end{itemize}
 
@@
 We impose a limit for memory allocated at each machine node to accomplish low-cost deduplication.  
-Memory usage for each step of the above scheme is carefully controlled as follows.
+Memory usage for each phase of the above scheme is carefully controlled as follows.
 \begin{itemize}
-\item For Step 1, the allocated memory for each machine is divided for 
+\item For Phase 1, the allocated memory for each machine is divided for 
 1) a disk buffer to read dirty segments; 2) $2p$ send/receive buffers and $q$ disk buffers.
@@
 \item 
-For Step 2,  the allocated memory at each machine is divided for 1) space for hosting a global index partition and 
+For Phase 2,  the allocated memory at each machine is divided for 1) space for hosting a global index partition and 
 the corresponding request partition; 2) $p$ receive buffers and $v$ disk buffers.
@@
 
-\item For Step 3 to  perform the real backup for each VM,
+\item For Phase 3 to  perform the real backup for each VM,
 the allocated memory is divided for 1) a disk buffer to read dirty segments of a VM and   
@@
 while following the fingerprint-based partitioning.
-Similar to the duplicate pre-detection process, reference counting is conducted in multi-steps. 
-Step 1 is to read  the metadata of snapshots such as segment and block
+Similar to the multi-phase duplicate detection process, reference counting is conducted in multi-phases. 
+Phase  1 is to read  the metadata of snapshots such as segment and block
 recipes and  to accumulate  reference count requests in different machines  in the fingerprint based distribution.
-Step  2 is to count references within each partition and detect those records with zero 
+Phase   2 is to count references within each partition and detect those records with zero 
 reference. 
-%Step 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.
+%Phase 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.
 The backup  data repository logs deletion instructions,  and will periodically perform a compaction operation when 

### 2013-03-09 hotstorage13/eval.tex
w

@@
 
-We have implemented and evaluated a prototype of our multi-step deduplication scheme on a Linux cluster
+We have implemented and evaluated a prototype of our multi-phase deduplication scheme on a Linux cluster
 of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
@@
 %to measure the effectiveness of our scheme.
-We have performed a trace-driven study using a dataset containing 10 snapshots of 35 VMs.
-That is part of a 1323 VM dataset  collected from 100 Aliyun's cloud nodes 
-in our earlier work with  Alibaba Aliyun~\cite{WeiZhangIEEE}.
+
+We have performed a trace-driven study using  a 1323 VM dataset  collected from 100 Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
 %In this dataset, there are 10 snapshots per each VM user and the total amount of space 
@@
 %study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
-All data are divided into 2 MB fix-sized segments and each segment is divided into 
+%
+%using a dataset containing 10 snapshots of 35 VMs.
+A VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
 variable-sized content blocks ~\cite{similar94,rabin81} with an average size of 4KB.
 The signature for variable-sized blocks is computed using their SHA-1 hash. 
+The final snapshots are stored in a distributed file system built on the same cluster and local I/O speed is averaged
+about 50MB/second. 
+%The seek cost of each random IO request is about  10 milliseconds.
 %Popularity of data blocks are collected through global counting 
@@
 
-\begin{verbatim}
-memory
-#partitions/node	50	100	250	275	300	450	500	750	1500	2000
-Memory meta data 0.161	0.0805	0.0322	0.029272727	0.026833333	0.017888889	0.0161	0.010733333	0.005366667	0.004025
-Global index 0.115	0.0575	0.023	0.020909091	0.019166667	0.012777778	0.0115	0.007666667	0.003833333	0.002875
-Seek (Step 1) 0.0212962960.0425 0.106 0.117 0.127777778	0.191666667	0.212962963	0.319444444	0.638888889	0.851851852
-Seek Option 2: 6.388888889	12.77777778	31.94444444	35.13888889	38.33333333	57.5	63.88888889	95.83333333	191.6666667	255.5555556
-Total time 3.059031718	3.078670034	3.131061779	3.137163671	3.141047877	3.313871832	3.296994302	3.377385758	3.689876824	3.901831421
-throughput  per node 0.090805785	0.090226551	0.088716799	0.088544242	0.088434748	0.083822728	0.084251822	0.082246387	0.075281044	0.07119164
+\begin{table}[hbt]
+\caption{ Performance of multi-phase backup with deduplication.}
+\begin{center}
+\begin{tabular} {|c|c|c|c|c|c|}
+\hline \#Partitions  & 50 & 275  &450 &  750 &  1500 \\
+\hline Index+request & 161&  29 & 17.9 & 10.7 & 5.3 \\
+  (MB)           &  &   &  & &  \\
 
-\end{verbatim}
+\hline Time (hrs) & N/A&  3.27 & 3.09 & 3.18 & 3.42 \\
+%\hline Throughput/node & N/A&  85MB/s& 90M & 87 & 81 \\
+\hline Throughput GB/s& N/A&  8.5& 9 & 8.7 & 8.1 \\
+\hline Option 2 time & N/A&  8& 13.3 & 18.7 & 34 \\
+\hline
+\end{tabular}
+\end{center}
+\label{tab:overall}
+\end{table}
 
-Table~\ref{tab:overall} shows the performance of partition-based deduplication when 
-the number of parititons per machine ($q$) varies from 50 to 2000.
+%\begin{verbatim}
+%memory
+%#partitions/node	50	100	250	275	300	450	500	750	1500	2000
+%Memory meta data 0.161	0.0805	0.0322	0.029272727	0.026833333	0.017888889	0.0161	0.010733333	0.005366667	0.004025
+%Global index 0.115	0.0575	0.023	0.020909091	0.019166667	0.012777778	0.0115	0.007666667	0.003833333	0.002875
+%Seek (Step 1) 0.0212962960.0425 0.106 0.117 0.127777778	0.191666667	0.212962963	0.319444444	0.638888889	0.851851852
+%Seek Option 2: 6.388888889	12.77777778	31.94444444	35.13888889	38.33333333	57.5	63.88888889	95.83333333	191.6666667	255.5555556
+%Total time 3.059031718	3.078670034	3.131061779	3.137163671	3.141047877	3.313871832	3.296994302	3.377385758	3.689876824	3.901831421
+%throughput  per node 0.090805785	0.090226551	0.088716799	0.088544242	0.088434748	0.083822728	0.084251822	0.082246387	0.075281044	0.07119164
+%
+%\end{verbatim}
+
+The total local disk space usage for each machine is 8.05GB:  5.75GB for global index partitions and 2.3GB for accumulated requests.
+Table~\ref{tab:overall} shows memory usage and performance when 
+the number of parititons per machine ($q$) varies from 50 to 1500.
 Row 2 shows the memory usage needed to load a partition of global index and detection requests,
-varying from 161MB to 4.025MB. As we impose a constraint of 30MB, then only $q>300$ would be a viable choice.
-Row 3 shows the majority of memory usage is for global index.
-Row 4 is the total time for a 100-node cluster.
-Row 5 is  the throughput per machine reported  is the total 
-amount of virtual machine images divided by the processing time. 
-The processing time includes the first scanning time
-of dirty VM segments to generate block fingerprints and the second scan time for real backup.
+varying from 161MB to 5.35MB. As we impose a constraint of 30MB, then $q=50$ would not be a viable choice.
+%Row 3 shows the major  memory usage is for global index.
+Row 3 is the parallel time which includes the first scanning time, 
+of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
+fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
+Row 4 is  the aggregated throughput of  100 nodes, which is  
+the size of 2500 VM images divided by the parallel time. 
+Row 5 is  the aggregated throughput of  100 nodes, which is  the size of 2500 VM images divided by the parallel time. 
+The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
+with the very small resource usage.
+Row 6 is  the parallel time if  we use Option 2 with $p\times q$ send buffers described in Section~\ref{sect:arch}. 
+With the large number of buffers, the available space per buffer reduces significantly as $q$ increases, which leads to
+a big increase of IO requests and seek cost.
 
@@
 
-Table~\ref{tab:memory} shows the performance of partition-based deduplication when 
-the memory limit imposed on each node, varying from 
-The overall processing time does not have a significant reduction as we increase memory usage  20MB to 200MB.
-As Row 2 shows, the time is mainly dominated by  the IO costs of two scans of VMs.
-Thus we conclude that using about 30MB is sufficient to have VM backup completed in parallel within about 3.11 hours.
+Table~\ref{tab:memory} shows the performance data when 
+the memory limit imposed on each node varies  from 20MB to 200MB.
+The overall processing time does not have a significant reduction as we increase to 200MB.
+As Row 2 shows, the time is mainly dominated by  the two scans of dirty VM segments.
+Each scan takes about 1.4 hours.
+Thus we conclude that using about 30MB is sufficient to have VM backup completed in parallel 
+within about 3.09 hours.
 
@@
 
-We have also compared our pre-detection approach with another approach by combining
+We have also compared our multi-phase detection approach with an inline approach by combining
 dirtybit segment  detection and  the data domain method~\cite{bottleneck08}. 
@@
 We measure its  total time including one scan of VM dirty segments in about 1.38 hours.
-That approach takes about 3.19 hours comparable with our pre-detection scheme while its memory cost
-includes 1GB of bloom filters and additional space for cache. That is an significant amount of space,
+That approach takes about 3.19 hours comparable with our scheme while its memory takes
+over 1GB for bloom filters and prefetch cache. That is an significant amount of space,
 competing with other cloud service while memory cost of our setting is  insignificant.

### 2013-03-09 hotstorage13/intro.tex
w

@@
 backup storage.  
-Our key idea  is to  first perform parallel duplicate pre-detection for VM content blocks 
+Our key idea  is to  first perform parallel duplicate detection for VM content blocks 
 among all machines before performing actual data backup. Each machine
-accumulates detection requests and  then performs pre-detection   partition by partition 
+accumulates detection requests and  then performs detection   partition by partition 
 with minimal resource usage.
-Fingerprint based partitioning allows highly parallel duplicate pre-detection  and also simplifies 
+Fingerprint based partitioning allows highly parallel duplicate detection  and also simplifies 
 reference counting management.  
@@
 With careful parallelism and buffer  management,
-this pre-detection scheme can provide  a sufficient throughput for backup.
+this multi-phase detection scheme can provide  a sufficient throughput for backup.
 

### 2013-03-09 hotstorage13/eval.tex
add graph

--- 2013-03-09 hotstorage13/eval.tex
@@
 
-\begin{verbatim}
-q= is chosen between 500 or 100
-Memory limit:   20 30M   50M  75M  100M  200M
-Time:          3.2  3.11   3  2.99 2.96  2.95
-Time for two scans: 2.78 2.78 2.78 2.78 2.78
-\end{verbatim}
+\begin{figure}
+\centering
+\includegraphics[width=0.4\textwidth]{mem_time.eps}
+\caption{Performance of partition-based deduplication under different memory limits}
+\label{fig:memory}
+\end{figure}
 
-Table~\ref{tab:memory} shows the performance of partition-based deduplication when 
+% \begin{verbatim}
+% q= is chosen bteween 500 or 100
+% Memory limit:   20 30M   50M  75M  100M  200M
+% Time:          3.2  3.11   3  2.99 2.96  2.95
+% Time for two scans: 2.78 2.78 2.78 2.78 2.78
+% \end{verbatim}
+
+Figure~\ref{fig:memory} shows the performance of partition-based deduplication when 
 the memory limit imposed on each node, varying from 

### 2013-03-09 hotstorage13/eval.tex
w

--- 2013-03-09 hotstorage13/eval.tex
@@
 
-\begin{verbatim}
-q= is chosen between 500 or 100
-Memory limit:   20 30M   50M  75M  100M  200M
-Time:          3.2  3.11   3  2.99 2.96  2.95
-Time for two scans: 2.78 2.78 2.78 2.78 2.78
-\end{verbatim}
+%\begin{verbatim}
+%q= is chosen between 500 or 100
+%Memory limit:   20 30M   50M  75M  100M  200M
+%Time:          3.2  3.11   3  2.99 2.96  2.95
+%Time for two scans: 2.78 2.78 2.78 2.78 2.78
+%\end{verbatim}
 
-Table~\ref{tab:memory} shows the performance data when 
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{mem_time.pdf}
+\caption{ Parallel time when memory limit imposed varies from 20MB to 200MB.}
+\label{fig:memory}
+\end{figure}
+
+Figure~\ref{tab:memory} shows the performance data when 
 the memory limit imposed on each node varies  from 20MB to 200MB.
@@
 Each scan takes about 1.4 hours.
-Thus we conclude that using about 30MB is sufficient to have VM backup completed in parallel 
+Using about 30MB is sufficient to have VM backup completed in parallel 
 within about 3.09 hours.

### 2013-03-09 hotstorage13/arch.tex
fix mark-sweep ref
w

@@
 \end{figure}
-\subsection{Snapshot Representation}
+%\subsection{Snapshot Representation}
 
@@
 \includegraphics[width=0.75\textwidth]{steps.pdf}
-\caption{Processing flow in Phase 1 (VM scan/request accumulation) and Phase  2 (fingerprint comparison and duplicate summary output)
- for duplicate detection.}
+\caption{Processing flow of Phases 1  and 2.}
 \label{fig:flow}
@@
 
-\subsection{Processing flow and resource usage}
+%\subsection{Processing flow and resource usage}
 The data flow of our multi-phase duplicate detection is depicted in Figure~\ref{fig:flow}. 

### 2013-03-09 hotstorage13/eval.tex
w

@@
 
-\subsection{Experimental setup}
+%\subsection{Experimental setup}
 
@@
 \begin{table}[hbt]
-\caption{ Performance of multi-phase backup with deduplication.}
+\caption{ Performance of multi-phase deduplication.}
 \begin{center}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{mem_time.pdf}
-\caption{ Parallel time when memory limit imposed varies from 20MB to 200MB.}
+\includegraphics[width=0.4\textwidth]{mem_time.pdf}
+\caption{ Parallel time when memory limit varies.}
 \label{fig:memory}
@@
 
-Figure~\ref{tab:memory} shows the performance data when 
+Figure~\ref{fig:memory} shows the performance data when 
 the memory limit imposed on each node varies  from 20MB to 200MB.

### 2013-03-09 hotstorage13/abs.tex
another iteration

@@
 of virtual machines.  The key idea is to separate duplicate detection from 
-the actual storage data backup instead of using inline deduplication, and partition
+the actual storage backup instead of using inline deduplication, and partition
 global index and  detection requests among machines using  fingerprint values.
-Then each machine conducts duplicate pre-detection partition by partition independently with a minimal memory usage.
+Then each machine conducts duplicate detection partition by partition independently with a minimal memory usage.
 %in parallel among all machines and  each machine full duplication detection is 
@@
 %and backup process timing is not compromised. 
-Our experiments show that  the proposed scheme 
+Our evaluation shows that  the proposed multi-phase scheme 
 uses a very small amount of system resources while delivering a satisfactory backup throughput.

### 2013-03-09 hotstorage13/background.tex
another iteration

@@
 Only raw access information at disk block level are provided.
-Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
-Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
-only a very small slice of cluster resource can be used for the backup purpose.
+%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
+%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
+%only a very small slice of cluster resource can be used for the backup purpose.
 
-The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
-Backup systems have been developed to use content hash (finger prints) to identify duplicate
+%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
+Backup systems have been developed to use content hash (fingerprints) to identify duplicate
 content~\cite{venti02,Rhea2008}.
@@
 Zhu et al.~\cite{bottleneck08} tackle it
-by using an in-memory Bloom filter and prefetch groups of chunk IDs that are likely to be
+by using an in-memory Bloom filter and prefetching groups of chunk IDs that are likely to be
 accessed together with high probability. It takes significant memory resource for filtering and caching.
@@
 
-Additional inline deduplication techniques are studied in ~\cite{sparseindex09,idedup}. All of the above approaches have focused on
-such inline duplicate detection, namely given a content chunk block, how to detect if it is duplicate instantly
-to trigger the data backup of this block or not before the detection request for the next blocks can be launched. 
+Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. All of the above approaches have focused on
+such inline duplicate detection in which  the duplicate detection  speed of an individual block  is critical.
 In our work, this constraint is relaxed and 
-there is a waiting time for many duplicate detection requests. Our goal is to minimizing  computing  resource without
-affecting the overall time of backup.
+there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
+in our context, finishing the backup of required VM images within a reasonable time window is more
+important than optimizing individual content block backup requests.
+%affecting the overall time of backup.

### 2013-03-09 hotstorage13/intro.tex
another iteration

@@
 of old snapshot competes computing resource also. That is because data dependence created 
-by duplicate relationship among snapshots  adds processing complexity, especially when  
-VMs can migrate around in the cloud.
+by duplicate relationship among snapshots  adds processing complexity.
+% especially when  VMs can migrate around in the cloud.
 
@@
 The objective of our project is to lower the cost incurred while sustaining the highest de-duplication ratio
-and  the sufficient deduplication  throughput for dealing with a large number of virtual machine images. 
+and  the sufficient deduplication  throughput for dealing with a large number of VM images. 
 % This business model partially  resembles that of Amazon Glacier.
@@
 With careful parallelism and buffer  management,
-this multi-phase detection scheme can provide  a sufficient throughput for backup.
+this multi-phase detection scheme can provide  a sufficient throughput for VM backup.
 

### 2013-03-09 hotstorage13/arch.tex
correction

@@
-\section{ Key Ideas and Architecture}
+\section{System Design}
 \label{sect:arch}
@@
 we emphasize a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
-Our experiment with Alibaba''s production dataset shows that over 70 percentage of 
-duplicates can be detected using segment-based dirty bits while the segment size is as large as 2M bytes.  
+Our experiment with Alibaba's production dataset shows that over 70 percentage of 
+duplicates can be detected using segment-based dirty bits when the segment size is as large as 2M bytes.  
 This setting requires OS to keep the metadata for segment dirty bits and the amount of space for such segment 
@@
 
-Our key ideas are summarized as follows.
+Our key strategies are explained as follows.
 \begin{itemize}
@@
 The second level duplicate detection requires a global comparison of 
-content fingerprints of stored chunks with the new chunks scanned during 
-the backup process. 
+content fingerprints.
+% of stored chunks with the new chunks scanned during the backup process. 
 %Bloom filters and caching allows some of content 
@@
 deduplication and leading to a much smaller resource requirement.  
-During duplicate detection phase, detection requests can be accumulated on the disk 
+During VM reading, detection requests can be accumulated on the disk 
 for a period time  in a  partitioned manner.  Aggregated duplicate requests can be processed partition by partition. 
@@
 Since each partition corresponds to a small portion of global content index, the cost to 
-process requests within a partition is significantly smaller than processing all the requests globally.
+process detection requests within a partition is significantly smaller than processing all the requests globally.
 
@@
 in a  disjointed manner.
-Initial data follows the VM distribution among machines and the detected results 
-represented as  duplicate summary need to be collected following VM distribution. 
+Initial VM data reading follows the VM distribution among machines and the detected duplicate summary results 
+need to be collected following the VM distribution. 
 Therefore, there are two all-to-all data redistribution operations involved.
@@
 Given there are $p\times q$ partitions where $p$ is the number of machines and $q$ is the number of fingerprint-based partitions
-at each machine, the number of buffers is big and space per each buffer  is small given the memory constraint,
-counteracting seek cost reduction.  
+at each machine, space per each buffer  is small under the memory constraint for large $p$ or $q$ values.
+This counteracts the effort of seek cost reduction.  
 %Then there will be a large number of storage  IO operations involved, suffering the huge seek overhead.
@@
 A small amount of local disk space and memory on each machine can be used 
-to store global index and request accumulation.
+to store global index and temporary data. 
 The real backup storage can be either a distributed file system built on
@@
 %\item
-The first phase is that each machine independently reads  
+In the first phase, each machine independently reads  
 %$v/k$  
-virtual machine images that need a backup
+VM images that need a backup
 and forms duplicate  detection requests. For those segments that have been modified since last backup indicated by 
 dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
-information such as chunk fingerprints,  sends the metadata of a chunk block, and accumulates  into 
-a partition bucket on the temporary disk storage. 
+information such as chunk fingerprints,  sends a request to a proper machine, accumulates  
+received requests into a partition on the local temporary disk storage. 
 The partition mapping is using a hash function applied to the content fingerprint. 
@@
 since a content block in a VM image of this machine can be sent to any of these partitions.
-2) Each machine allocates $p$ send buffers correspond to send requests to $p$ machines and 
+2) Each machine allocates $p$ send buffers to deliver requests to $p$ machines and 
 $p$ receive buffers to collect requests  from other machines.
-Then the system copies requests in each $p$ disk buffers to  $q$ local disk buffers,
+Then the system copies requests from each of $p$ receive buffers to  $q$ local disk buffers,
 and outputs each disk buffer to one of the request partitions on the disk
 when this disk buffer becomes full.  Option 2 is much more efficient than Option 1 because $2p+q$ is much smaller than
-$p\times q$, as a result each buffer has a bigger size to accumulate data and results in 
-much less disk seek overhead.
+$p\times q$. As a result, each buffer has a bigger size to accumulate requests and that means
+less disk seek overhead.
 
@@
 %\item
-The second phase is to load disk data and perform duplicate detection at each machine for  all accumulated 
+The second phase is to load disk data and perform fingerprint comparison at each machine for  all accumulated 
 requests one partition at a time.
@@
 %This process is repeated until all buckets are processed.
-At each iteration, as in-memory comparison between an index partition and request partition
-is completed,  
-duplicate information for segments of each VM is routed to  from fingerprint-based distribution  to VM-based distribution. 
-The duplicate summary contains the block ID and  the reference pointer for each detected duplicate block.   
+At each iteration, once in-memory comparison between an index partition and request partition is completed,  
+duplicate summary information for segments of each VM is routed from the fingerprint-based distribution  to the
+VM-based distribution.  The duplicate summary contains the block ID and  the reference pointer for each detected duplicate block.   
 Each machine uses memory space of the request partition as a send buffer with no extra memory space required.
@@
 In this process, if a segment is not dirty, the system only needs to output the segment meta data 
-such as reference pointers to the original segments previously saved in the backup storage.  
+such as a reference pointer to the original segment previously saved in the backup storage.  
 %If a segment is dirty,  the system  use the duplicate summary information from Step 2 for internal 
@@
 accumulating  duplicate detection requests that contain fingerprint information.   
-We impose a limit for memory allocated at each machine node to accomplish low-cost deduplication.  
-Memory usage for each phase of the above scheme is carefully controlled as follows.
+We impose a memory limit $M$ allocated for each phase of processing at each machine.
+The usage of $M$ is controlled as follows and the detailed distribution is optimized based on the relative
+ratio between the cross-machine network  startup cost and disk access startup cost.
 \begin{itemize}
@@
 
-\item For Phase 3 to  perform the real backup for each VM,
-the allocated memory is divided for 1) a disk buffer to read dirty segments of a VM and   
-write non-duplicate raw blocks to the  backup storage.
+\item For Phase 3, the allocated memory is divided for 1) an I/O buffer to read dirty segments of a VM and   
+write non-duplicate content blocks to the  backup storage.
 2) summary of duplicate blocks within dirty segments of  a VM.
@@
 expired snapshots will be deleted unless its owner explicitly asks for its retention.
-We adopt the idea of mark-and-sweep~\cite{MarkSweep}. 
+We adopt the idea of mark-and-sweep~\cite{Guo2011}. 
 A block or a segment can be deleted if its reference count is zero.
@@
 
-%Since we maintain a single copy of each block information in the bucket index, and there is at most one bucket worker operating the bucket index at one time, it it safe to do the simple reference counting rather than mark-and-sweep.
+%Since we maintain a single copy of each block information in the bucket index, and there is at most one bucket worker operating the bucket index at one time, it it safe to do the simple referencec ounting rather than mark-and-sweep.

### 2013-03-09 hotstorage13/eval.tex

@@
 of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
-1) Analyze the throughput and effectiveness for a large number of virtual machines.
+1) Analyze the deduplication throughput and effectiveness for a large number of VMs.
 Compare with the data domain approach~\cite{bottleneck08}.
@@
 
-Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.  
-At Alibaba's Aliyun, each multi-core machine   hosts  up to 25 VMs and 
+Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}
+where each multi-core machine   hosts  up to 25 VMs. 
 %We are running our deduplication/backup  service on 100 nodes.
@@
 %the CPU usage is very small during the experiments. 
-based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
-including OS and user data disk.  
 For each VM, the system keeps 10 automatically-backed snapshots in the storage while
 a user may instruct extra snapshots to be saved.
-The backup of VM snapshots is completed within a few  hours every night,
+The backup of VM snapshots is completed within a few  hours every night.
+Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
+including OS and user data disk. 
 %and that translates to an aggregated backup throughput of 139GB per second, or 500TB per hour.
@@
 A VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
-variable-sized content blocks ~\cite{similar94,rabin81} with an average size of 4KB.
+variable-sized content blocks ~\cite{similar94} with an average size of 4KB.
 The signature for variable-sized blocks is computed using their SHA-1 hash. 
-The final snapshots are stored in a distributed file system built on the same cluster and local I/O speed is averaged
-about 50MB/second. 
-%The seek cost of each random IO request is about  10 milliseconds.
+The final snapshots are stored in a distributed file system built on the same cluster and local I/O rate
+is averaged about 50MB/second.  The seek cost of each random IO request is about  10 milliseconds.
 %Popularity of data blocks are collected through global counting 
@@
 
+The total local disk space usage for each machine is 8.05GB:  5.75GB for global index partitions with 10 snapshots per VM
+and 2.3GB for accumulated requests.
+Level 1 segment dirty bits can identify 78\% of duplicate blocks. For the remaining dirty segments,
+block-wise full cross-VM deduplication can remove about additional 70\% of duplicates.
+Thus the content finally copied to the backup storage is reduced by 93.4\% in total.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.4\textwidth]{mem_time.pdf}
+\caption{ Parallel time when memory limit varies.}
+\label{fig:memory}
+\end{figure}
+
+Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
+ a 100-node cluster a  when 
+the memory limit imposed on each node varies  from 20MB to 200MB.
+The overall processing time does not have a significant reduction as we increase to 200MB.
+The parallel time includes the first scanning time, 
+of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
+fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
+The total time is mainly dominated by  the two scans of dirty VM segments.
+The time for copying to the final backup storage is overlapped with VM scanning.
+%Each scan takes about 1.4 hours.
+The aggregated throughput is  about 8GB per second,
+which is the size of 2500 VM images divided by the parallel time. 
+The result shows the backup with multi-phase deduplication  for all VM images can be 
+completed in about 3.09 hours with the very small resource usage.
+As we vary the cluster size and the number of VMs for backup remains a constant (25),
+the processing time and throughput do not change much. Thus the aggregated throughput
+scales up linearly.
+
+Table~\ref{tab:overall} shows memory usage and performance when 30MB memory limit is imposed and
+the number of parititons per machine ($q$) varies from 50 to 1500.
+Row 2 shows the memory usage required to load a partition of global index and detection requests,
+varying from 161MB to 5.3MB. With  30MB memory limit,  $q=50$ would not be a viable choice.
+Row 3 is the total time and Row 4 is  the aggregated throughput of  100 nodes.
+%The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
+%with the very small resource usage.
+Row 5 is  the parallel time if  we use Option 1 with $p\times q$ send buffers 
+described in Section~\ref{sect:arch}. 
+With the large number of buffers, the available space per buffer reduces significantly as $q$ increases, which leads to
+a big increase of IO requests and seek cost.
+
 \begin{table}[hbt]
-\caption{ Performance of multi-phase deduplication.}
+\caption{ Performance when the number of partitions varies.}
 \begin{center}
@@
 
-\hline Time (hrs) & N/A&  3.27 & 3.09 & 3.18 & 3.42 \\
+\hline Total Time  & N/A&  3.27 & 3.09 & 3.18 & 3.42 \\
+  (Hours)           &  &   &  & &  \\
 %\hline Throughput/node & N/A&  85MB/s& 90M & 87 & 81 \\
 \hline Throughput GB/s& N/A&  8.5& 9 & 8.7 & 8.1 \\
-\hline Option 2 time & N/A&  8& 13.3 & 18.7 & 34 \\
+\hline Total time & N/A&  8& 13.3 & 18.7 & 34 \\
+  (Option 1)           &  &   &  & &  \\
 \hline
@@
 
-The total local disk space usage for each machine is 8.05GB:  5.75GB for global index partitions and 2.3GB for accumulated requests.
-Table~\ref{tab:overall} shows memory usage and performance when 
-the number of parititons per machine ($q$) varies from 50 to 1500.
-Row 2 shows the memory usage needed to load a partition of global index and detection requests,
-varying from 161MB to 5.35MB. As we impose a constraint of 30MB, then $q=50$ would not be a viable choice.
-%Row 3 shows the major  memory usage is for global index.
-Row 3 is the parallel time which includes the first scanning time, 
-of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
-fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
-Row 4 is  the aggregated throughput of  100 nodes, which is  
-the size of 2500 VM images divided by the parallel time. 
-Row 5 is  the aggregated throughput of  100 nodes, which is  the size of 2500 VM images divided by the parallel time. 
-The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
-with the very small resource usage.
-Row 6 is  the parallel time if  we use Option 2 with $p\times q$ send buffers described in Section~\ref{sect:arch}. 
-With the large number of buffers, the available space per buffer reduces significantly as $q$ increases, which leads to
-a big increase of IO requests and seek cost.
-
 %\begin{figure}
@@
 %\end{verbatim}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.4\textwidth]{mem_time.pdf}
-\caption{ Parallel time when memory limit varies.}
-\label{fig:memory}
-\end{figure}
-
-Figure~\ref{fig:memory} shows the performance data when 
-the memory limit imposed on each node varies  from 20MB to 200MB.
-The overall processing time does not have a significant reduction as we increase to 200MB.
-As Row 2 shows, the time is mainly dominated by  the two scans of dirty VM segments.
-Each scan takes about 1.4 hours.
-Using about 30MB is sufficient to have VM backup completed in parallel 
-within about 3.09 hours.
 
@@
 That approach takes about 3.19 hours comparable with our scheme while its memory takes
-over 1GB for bloom filters and prefetch cache. That is an significant amount of space,
+over 1GB with 575MB bloom filters and extra space for prefetching cache. That is an significant amount of space,
 competing with other cloud service while memory cost of our setting is  insignificant.

### 2013-03-10 hotstorage13/arch.tex
update figure 2

@@
 identify version difference from the previous snapshot to the current snapshot.  
-Version-based detection has been used in the previous work~\cite{Clements2009,Vrable2009,TanIPDPS2011} and
+Version-based detection has been used in the previous work~\cite{Clements2009,cumulus09,TanIPDPS2011} and
 we emphasize a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{steps.pdf}
+\includegraphics[width=0.95\textwidth]{steps.pdf}
 \caption{Processing flow of Phases 1  and 2.}

### 2013-03-10 hotstorage13/arch.tex
new

--- 2013-03-09 hotstorage13/arch.tex
@@
 
-We consider deduplication in two levels. The first-level of data deduplication can be accomplished efficiently and 
-inexpensively using a coarse-grain segment-level  dirty bit based detection in the OS level  to 
-identify version difference from the previous snapshot to the current snapshot.  
-Version-based detection has been used in the previous work~\cite{Clements2009,Vrable2009,TanIPDPS2011} and
-we emphasize a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
+We consider deduplication in two levels. The first level
+uses coarse-grain segment  dirty bits for version-based detection~\cite{Clements2009,Vrable2009} to 
+identify difference from the previous snapshot to the current snapshot.  
+%That  can be accomplished efficiently and inexpensively in the OS level.
+%We use a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
 Our experiment with Alibaba's production dataset shows that over 70 percentage of 
-duplicates can be detected using segment-based dirty bits when the segment size is as large as 2M bytes.  
+duplicates can be detected using segment dirty bits when the segment size is 2M bytes.  
 This setting requires OS to keep the metadata for segment dirty bits and the amount of space for such segment 
@@
 are compared with the fingerprints of unique  blocks from the previous snapshots.
-
 Our key strategies are explained as follows.
@@
 Let {\em global index} be the meta data containing the fingerprint values of unique blocks of snapshots
-in the entire cluster and  the reference pointers which lead to the actual location of raw data.
+in all VMs and  the reference pointers which lead to the location of raw data.
 %A duplicate detection request for a content block needs to be compared with the global index to determine if this
 %block is non-duplicate. If it is a duplicate, return the corresponding reference pointer.
-We conduct parallel processing of detection requests in all machines involved. 
-A logical way to distribute detection requests is to partition based on fingerprint values of content blocks
+%We conduct parallel processing of detection requests in all machines involved. 
+A logical way to distribute detection requests among machines is to partition based on fingerprint values of content blocks
 in a  disjointed manner.
@@
 
-The representation of each snapshot saved in the backup storage
-has a two-level level index data structure in the form of a hierarchical
+The representation of each snapshot in the backup storage
+has a two-level index structure in the form of a hierarchical
 directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
@@
 %To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
-The snapshot metadata (called snapshot recipe) contains a list of segments and other meta data information.
-Segment metadata (called segment recipe) contains its  content block fingerprints and reference pointers. 
+The snapshot metadata  contains a list of segments and other meta data information.
+Segment metadata  contains its  content block fingerprints and reference pointers. 
 If a segment is not changed from one snapshot to another, indicated by a dirty bit embedded in the virtual disk driver, 
 %its content blocks are not changed as well, thus 
-its segment recipe contains a reference pointer to an earlier segment.
+its segment metadata contains a reference pointer to an earlier segment.
 For a dirty segment, if one of its blocks is duplicate to another block in the system,  
-the block recipe contains a reference pointer to the earlier block.
+the block metadata contains a reference pointer to the earlier block.
 
@@
 \includegraphics[width=0.75\textwidth]{steps.pdf}
-\caption{Processing flow of Phases 1  and 2.}
+\caption{Processing flow of Stages  1,  2 and 3.}
 \label{fig:flow}
@@
 %\subsection{Processing flow and resource usage}
-The data flow of our multi-phase duplicate detection is depicted in Figure~\ref{fig:flow}. 
+The data flow of our multi-stage duplicate detection is depicted in Figure~\ref{fig:flow}. 
 %let $v$ be the total number of virtual machines hosted in  a cluster,  
@@
 %\item
-In the first phase, each machine independently reads  
+In Stage 1, each machine independently reads  
 %$v/k$  
@@
 $p$ receive buffers to collect requests  from other machines.
-Then the system copies requests from each of $p$ receive buffers to  $q$ local disk buffers,
-and outputs each disk buffer to one of the request partitions on the disk
-when this disk buffer becomes full.  Option 2 is much more efficient than Option 1 because $2p+q$ is much smaller than
+Then the system copies requests from each of $p$ receive buffers to  $q$ local request buffers,
+and outputs each request buffer to one of the request partitions on the disk
+when this request buffer becomes full.  Option 2 is much more efficient than Option 1 because $2p+q$ is much smaller than
 $p\times q$. As a result, each buffer has a bigger size to accumulate requests and that means
@@
 %\item
-The second phase is to load disk data and perform fingerprint comparison at each machine for  all accumulated 
-requests one partition at a time.
+Stage  2 is to load disk data and perform fingerprint comparison at each machine one request partition at a time.
 % in the partitions.  
@@
 duplicate summary information for segments of each VM is routed from the fingerprint-based distribution  to the
-VM-based distribution.  The duplicate summary contains the block ID and  the reference pointer for each detected duplicate block.   
-Each machine uses memory space of the request partition as a send buffer with no extra memory space required.
+VM-based distribution.  The summary contains the block ID and  the reference pointer for each detected duplicate block.   
+Each machine uses memory space of the request partition as a send buffer with no extra memory requirement.
 But it needs to allocate $p$ receive buffers to collect duplicate summary from other machines.
-It also allocates $v$ disk buffers to copy duplicate summary from $p$ receive buffers and output to the local disk
-when disk buffers are full.
+It also allocates $v$ request buffers to copy duplicate summary from $p$ receive buffers and output to the local disk
+when request buffers are full.
 
@@
 %\item 
-The third phase is to perform real backup one VM at a time.
-The system loads the duplicate summary of a VM obtained from Phase 2, 
+Stage 3 is to perform real backup one VM at a time.
+The system loads the duplicate summary of a VM, 
 reads  dirty segments of a VM, and output non-duplicate blocks to the final backup 
 storage. Additionally, the global index on each machine is updated with the meta data of new chunk blocks. 
-In this process, if a segment is not dirty, the system only needs to output the segment meta data 
-such as a reference pointer to the original segment previously saved in the backup storage.  
+When a segment is not dirty, the system only needs to output the segment meta data such as a reference pointer. 
+There is an option to directly read dirty blocks instead of fetching a dirty segment which can include duplicate
+blocks. Our experiment shows that it is faster to read dirty segments in the tested workload.
+Another issue is that during global index update, the system  may find some  blocks with the same fingerprint may be 
+created redundantly. For example, two different VM blocks have the same content block fingerprint while the  global 
+index does not have such a fingerprint. The redundancy is discovered and logged during the index update and can be repaired
+periodically when necessary.  Our experience is that there is a redundancy during the initial snapshot backup and once 
+that is repaired, the percentage of redundant blocks due to concurrent processing  is insignificant.
+
 %If a segment is dirty,  the system  use the duplicate summary information from Step 2 for internal 
@@
 accumulating  duplicate detection requests that contain fingerprint information.   
-We impose a memory limit $M$ allocated for each phase of processing at each machine.
-The usage of $M$ is controlled as follows and the detailed distribution is optimized based on the relative
-ratio between the cross-machine network  startup cost and disk access startup cost.
+We impose a memory limit $M$ allocated for each stage of processing at each machine.
+The usage of $M$ is controlled as follows and the distribution among buffers is optimized based on the relative
+ratio between the cross-machine network  startup cost and disk access startup cost such as seek time.
+Slower start cost requires more buffer space.
 \begin{itemize}
-\item For Phase 1, the allocated memory for each machine is divided for 
-1) a disk buffer to read dirty segments; 2) $2p$ send/receive buffers and $q$ disk buffers.
+\item For Stage 1, $M$  is divided for 
+1) an I/O buffer to read dirty segments; 2) $2p$ send/receive buffers and $q$ request  buffers.
 
@@
 \item 
-For Phase 2,  the allocated memory at each machine is divided for 1) space for hosting a global index partition and 
-the corresponding request partition; 2) $p$ receive buffers and $v$ disk buffers.
+For Stage 2,  $M$  is divided for 1) space for hosting a global index partition and 
+the corresponding request partition; 2) $p$ receive buffers and $v$ summary buffers.
 %%accumulating duplicate summary for each targeted VM.   Once  each machine processes a bucket of  duplicate detection requests, 
@@
 
-\item For Phase 3, the allocated memory is divided for 1) an I/O buffer to read dirty segments of a VM and   
+\item For Stage 3, $M$  is divided for 1) an I/O buffer to read dirty segments of a VM and   
 write non-duplicate content blocks to the  backup storage.
@@
 while following the fingerprint-based partitioning.
-Similar to the multi-phase duplicate detection process, reference counting is conducted in multi-phases. 
-Phase  1 is to read  the metadata of snapshots such as segment and block
-recipes and  to accumulate  reference count requests in different machines  in the fingerprint based distribution.
-Phase   2 is to count references within each partition and detect those records with zero 
+Similar to the multi-stage duplicate detection process, reference counting is conducted in multi-stages. 
+Stage  1 is to read  the segment and block  metadata of snapshots 
+to accumulate  reference count requests in different machines  in the fingerprint based distribution.
+Stage   2 is to count references within each partition and detect those records with zero 
 reference. 
-%Phase 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.
+%Stage 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.
 The backup  data repository logs deletion instructions,  and will periodically perform a compaction operation when 

### 2013-03-10 hotstorage13/background.tex
new

@@
 content~\cite{venti02,Rhea2008}.
+Offline deduplication is used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
 %,NGmiddleware2011}.
@@
 content. For example,
-Zhu et al.~\cite{bottleneck08} tackle it
-by using an in-memory Bloom filter and prefetching groups of chunk IDs that are likely to be
-accessed together with high probability. It takes significant memory resource for filtering and caching.
+The data domain method ~\cite{bottleneck08} 
+uses  in-memory Bloom filter and maintains a prefetch cache for data blocks  which may be
+accessed with high probability.  An improvement to this work with parallelization is in ~\cite{DEBAR}.
+Still such methods use  a significant amount of memory resource for filtering and caching.
 %NG et al.~\cite{ NGmiddleware2011}  use
@@
 
-Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. All of the above approaches have focused on
-such inline duplicate detection in which  the duplicate detection  speed of an individual block  is critical.
+Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
+All of the above approaches have focused on
+such inline duplicate detection in which  deduplication of an individual block  is on the critical write path.
 In our work, this constraint is relaxed and 
@@
 in our context, finishing the backup of required VM images within a reasonable time window is more
-important than optimizing individual content block backup requests.
+important than optimizing individual VM block  backup requests.
+
+%It should be emphasized that our approach does not  accumulate raw backup data temporarily for deduplication
+%and does not require a significant amount of extra storage capacity.
+%Our strategy is to perform a drity  scan to collect
+% a small amount of disk space  to accumulate
+%deduplicate requests along with necessary meta data, and perform actual backup after deduplicate detection completes.
+
 %affecting the overall time of backup.

### 2013-03-10 hotstorage13/eval.tex
new

@@
 
-We have implemented and evaluated a prototype of our multi-phase deduplication scheme on a Linux cluster
+We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a Linux cluster
 of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
 1) Analyze the deduplication throughput and effectiveness for a large number of VMs.
-Compare with the data domain approach~\cite{bottleneck08}.
+%Compare with the data domain approach~\cite{bottleneck08}.
 2) Examine the impacts of buffering during metadata exchange.
@@
 and 2.3GB for accumulated requests.
-Level 1 segment dirty bits can identify 78\% of duplicate blocks. For the remaining dirty segments,
-block-wise full cross-VM deduplication can remove about additional 70\% of duplicates.
-Thus the content finally copied to the backup storage is reduced by 93.4\% in total.
+Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
+block-wise full deduplication removes about additional 74.5\% of duplicates.
+The final content copied to the backup storage is reduced by 94.4\% in total.
 
@@
 which is the size of 2500 VM images divided by the parallel time. 
-The result shows the backup with multi-phase deduplication  for all VM images can be 
+The result shows the backup with multi-stage deduplication  for all VM images can be 
 completed in about 3.09 hours with the very small resource usage.
@@
 \hline \#Partitions  & 50 & 275  &450 &  750 &  1500 \\
-\hline Index+request & 161&  29 & 17.9 & 10.7 & 5.3 \\
+\hline Index+request & 156&  28.4 & 17.4 & 10.7 & 5.2 \\
   (MB)           &  &   &  & &  \\
 
-\hline Total Time  & N/A&  3.27 & 3.09 & 3.18 & 3.42 \\
+\hline Total Time  & N/A&  2.9 & 2.91 & 3 & 3.1 \\
   (Hours)           &  &   &  & &  \\
 %\hline Throughput/node & N/A&  85MB/s& 90M & 87 & 81 \\
-\hline Throughput GB/s& N/A&  8.5& 9 & 8.7 & 8.1 \\
+\hline Throughput GB/s& N/A&  9.6& 9.5 & 9.3 & 8.9 \\
 \hline Total time & N/A&  8& 13.3 & 18.7 & 34 \\
@@
 %q= is chosen between 500 or 100
-%Memory limit:   20 30M   50M  75M  100M  200M
-%Time:          3.2  3.11   3  2.99 2.96  2.95
-%Time for two scans: 2.78 2.78 2.78 2.78 2.78
+%Memory limit:   20 35M   50M  75M  100M  200M
+%req buf	    30M   40M  60   90M     180M
+%q:          450     275    275   275 275   
+%Time:          3.06  2.9  2.86  2.84 2.834  2.823
+%Time for two scans: 2.63  2.63
 %\end{verbatim}
@@
 
-We have also compared our multi-phase detection approach with an inline approach by combining
+\comments{
+We have also compared our multi-stage detection approach with an inline approach by combining
 dirtybit segment  detection and  the data domain method~\cite{bottleneck08}. 
@@
 competing with other cloud service while memory cost of our setting is  insignificant.
-
+} 
 %Our actual cache hit ratio tested is close 90\%.

### 2013-03-10 hotstorage13/eval.tex
new dat

@@
 
-The total local disk space usage for each machine is 8.05GB:  5.75GB for global index partitions with 10 snapshots per VM
-and 2.3GB for accumulated requests.
+The total local disk usage on
+each machine is about 8GB for duplicate detection purpose and most of them for global index. 
 Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
@@
 %Each scan takes about 1.4 hours.
-The aggregated throughput is  about 8GB per second,
+The aggregated throughput is  about 9.6GB per second,
 which is the size of 2500 VM images divided by the parallel time. 
 The result shows the backup with multi-stage deduplication  for all VM images can be 
-completed in about 3.09 hours with the very small resource usage.
+completed in about 2.9 hours with the very small resource usage.
 As we vary the cluster size and the number of VMs for backup remains a constant (25),
@@
 
-Table~\ref{tab:overall} shows memory usage and performance when 30MB memory limit is imposed and
+Table~\ref{tab:overall} shows memory usage and performance when 35MB memory limit is imposed and
 the number of parititons per machine ($q$) varies from 50 to 1500.
 Row 2 shows the memory usage required to load a partition of global index and detection requests,
-varying from 161MB to 5.3MB. With  30MB memory limit,  $q=50$ would not be a viable choice.
+varying from 156MB to 5.2MB. With  35MB memory limit,  $q=50$ would not be a viable choice.
 Row 3 is the total time and Row 4 is  the aggregated throughput of  100 nodes.

### 2013-03-10 hotstorage13/abs.tex

@@
 %and backup process timing is not compromised. 
-Our evaluation shows that  the proposed multi-phase scheme 
+Our evaluation shows that  the proposed multi-stage scheme 
 uses a very small amount of system resources while delivering a satisfactory backup throughput.

### 2013-03-10 hotstorage13/arch.tex
revision

@@
 deduplication and leading to a much smaller resource requirement.  
-During VM reading, detection requests can be accumulated on the disk 
+During VM reading, detection requests are accumulated on the disk 
 for a period time  in a  partitioned manner.  Aggregated duplicate requests can be processed partition by partition. 
@@
 One is to map detection requests from VM-based distribution to fingerprint based distribution.  
-One is to map duplicate summary from fingerprint-based distribution to VM based distribution.  
+Another one  is to map duplicate summary from fingerprint-based distribution to VM based distribution.  
 The redistributed data needs to be accumulated on the disk to minimize the use of memory.
@@
 \centering
-\includegraphics[width=0.75\textwidth]{steps.pdf}
-\caption{Processing flow of Stages  1,  2 and 3.}
+
+\includegraphics[width=0.95\textwidth]{steps.pdf}
+\caption{Processing flow of Stage  1 (dirty segment scan and request accumulation), Stage 2 
+(fingerprint comparison and summary output),  and Stage 3 (non-duplicate block backup).}
 \label{fig:flow}
@@
 Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
-$q$ parititons of content hash and accumulates corresponding requests on the disk. 
-There are two options to assign buffers in each machine to buffer requests for each partition.
+$q$ parititons of global index and accumulates corresponding requests on the disk. 
+There are two options to allocate buffers at each machine. 
 1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
 since a content block in a VM image of this machine can be sent to any of these partitions.
-2) Each machine allocates $p$ send buffers to deliver requests to $p$ machines and 
+2) Each machine allocates $p$ send buffers to deliver requests to $p$ machines; it allocates 
 $p$ receive buffers to collect requests  from other machines.
@@
 and outputs each request buffer to one of the request partitions on the disk
-when this request buffer becomes full.  Option 2 is much more efficient than Option 1 because $2p+q$ is much smaller than
-$p\times q$. As a result, each buffer has a bigger size to accumulate requests and that means
+when this request buffer becomes full.  Option 2 depicted in Figure~\ref{fig:flow}
+is much more efficient than Option 1 because $2p+q$ is much smaller than
+$p\times q$. As a result, each buffer in Option 2 has a bigger size to accumulate requests and that means
 less disk seek overhead.
@@
 The system loads the duplicate summary of a VM, 
-reads  dirty segments of a VM, and output non-duplicate blocks to the final backup 
+reads  dirty segments of a VM, and outputs non-duplicate blocks to the final backup 
 storage. Additionally, the global index on each machine is updated with the meta data of new chunk blocks. 
@@
 blocks. Our experiment shows that it is faster to read dirty segments in the tested workload.
-Another issue is that during global index update, the system  may find some  blocks with the same fingerprint may be 
-created redundantly. For example, two different VM blocks have the same content block fingerprint while the  global 
-index does not have such a fingerprint. The redundancy is discovered and logged during the index update and can be repaired
+Another issue is that during global index update after new block creation in the backup storage,
+the system  may find some  blocks with the same fingerprint may be 
+created redundantly. For example, two different VM blocks that have the same  fingerprint are not detected
+because  the  global index has not contained such a fingerprint yet. 
+The redundancy is discovered and logged during the index update and can be repaired
 periodically when necessary.  Our experience is that there is a redundancy during the initial snapshot backup and once 

### 2013-03-10 hotstorage13/eval.tex
revision

@@
 We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a Linux cluster
-of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
+of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  
+Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
+
+Objectives of our evaluation are:
 1) Analyze the deduplication throughput and effectiveness for a large number of VMs.
@@
 
-Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}
-where each multi-core machine   hosts  up to 25 VMs. 
 %We are running our deduplication/backup  service on 100 nodes.
@@
 %the CPU usage is very small during the experiments. 
+We have performed a trace-driven study using  a 1323 VM dataset  collected from 100 
+Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
+Each multi-core machine   hosts  up to 25 VMs. 
 For each VM, the system keeps 10 automatically-backed snapshots in the storage while
@@
 including OS and user data disk.
+Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
+variable-sized content blocks ~\cite{similar94} with an average size of 4KB.
+The signature for variable-sized blocks is computed using their SHA-1 hash. 
+The final snapshots are stored in a distributed file system built on the same cluster and the average I/O bandwidth
+of local storage is about 50MB/second.  The seek cost of each random IO request is about  10 milliseconds.
 %and that translates to an aggregated backup throughput of 139GB per second, or 500TB per hour.
@@
 
-We have performed a trace-driven study using  a 1323 VM dataset  collected from 100 Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
 %In this dataset, there are 10 snapshots per each VM user and the total amount of space 
@@
 %using a dataset containing 10 snapshots of 35 VMs.
-A VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
-variable-sized content blocks ~\cite{similar94} with an average size of 4KB.
-The signature for variable-sized blocks is computed using their SHA-1 hash. 
-The final snapshots are stored in a distributed file system built on the same cluster and local I/O rate
-is averaged about 50MB/second.  The seek cost of each random IO request is about  10 milliseconds.
 %Popularity of data blocks are collected through global counting 
@@
  a 100-node cluster a  when 
-the memory limit imposed on each node varies  from 20MB to 200MB.
-The overall processing time does not have a significant reduction as we increase to 200MB.
+the memory limit $M$ imposed on each node varies  from 20MB to 200MB.
+The overall processing time does not have a significant reduction as $M$ increases to 200MB.
 The parallel time includes the first scanning time, 
@@
 The result shows the backup with multi-stage deduplication  for all VM images can be 
-completed in about 2.9 hours with the very small resource usage.
-As we vary the cluster size and the number of VMs for backup remains a constant (25),
-the processing time and throughput do not change much. Thus the aggregated throughput
-scales up linearly.
+completed in about 2.9 hours with 35MB memory and 8GB disk overhead.
+As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
+scales up linearly since the number of VMs is  $25p$.
 
-Table~\ref{tab:overall} shows memory usage and performance when 35MB memory limit is imposed and
+Table~\ref{tab:overall} shows performance change when memory limit $M$=35MB is imposed and
 the number of parititons per machine ($q$) varies from 50 to 1500.
-Row 2 shows the memory usage required to load a partition of global index and detection requests,
-varying from 156MB to 5.2MB. With  35MB memory limit,  $q=50$ would not be a viable choice.
-Row 3 is the total time and Row 4 is  the aggregated throughput of  100 nodes.
+Row 2 is the memory space required to load a partition of global index and detection requests.
+When $q=50$, the required memory is 156MB, which  is  not  a viable choice  under  constraint $M=$35MB.  
+Row 3 is the parallel time and Row 4 is  the aggregated throughput of  100 nodes.
 %The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
@@
 \begin{table}[hbt]
-\caption{ Performance when the number of partitions varies.}
+\caption{ Performance when the number of partitions per machine node varies and $M$=35MB is imposed.}
 \begin{center}
@@
 \hline Throughput GB/s& N/A&  9.6& 9.5 & 9.3 & 8.9 \\
-\hline Total time & N/A&  8& 13.3 & 18.7 & 34 \\
+\hline Total time & N/A&  7.8& 11.7 & 14.8 & 26 \\
   (Option 1)           &  &   &  & &  \\

### 2013-03-10 hotstorage13/intro.tex
revision

@@
 Among the three factors - time, cost and de-deduplication efficiency, one of them has to be compromised for the other two.
-For instance, if we were build a deduplication system that has a high rate of duplication detection and has a very fast response time,
-it would need a lot of memory to hold fingerprint index and do fast comparison.  This leads to a compromise on cost. 
+For instance, if we were building a deduplication system that has a high rate of duplication detection and has a very fast response time,
+it would need a lot of memory to hold fingerprint index and cache.  This leads to a compromise on cost. 
 The objective of our project is to lower the cost incurred while sustaining the highest de-duplication ratio
@@
 The traditional approach to  deduplication for backup is an inline approach which follows
-a sequence of VM block reading, duplicate detection,  and non-duplicate  block write to the 
+a sequence of block reading, duplicate detection,  and non-duplicate  block write to the 
 backup storage.  
@@
 With careful parallelism and buffer  management,
-this multi-phase detection scheme can provide  a sufficient throughput for VM backup.
+this multi-stage detection scheme can provide  a sufficient throughput for VM backup.
 

### 2013-03-11 hotstorage13/eval.tex
fix typos

@@
 Table~\ref{tab:overall} shows performance change when memory limit $M$=35MB is imposed and
-the number of parititons per machine ($q$) varies from 50 to 1500.
+the number of partitions per machine ($q$) varies from 50 to 1500.
 Row 2 is the memory space required to load a partition of global index and detection requests.

### 2013-03-11 hotstorage13/arch.tex
fix typos

@@
 directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
-An VM image is divided into a set of segments and each  segment contains hundreds of content blocks. 
+A VM image is divided into a set of segments and each  segment contains hundreds of content blocks. 
 These blocks are of variable-size, partitioned using
@@
 Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
-$q$ parititons of global index and accumulates corresponding requests on the disk. 
+$q$ partitions of global index and accumulates corresponding requests on the disk. 
 There are two options to allocate buffers at each machine. 

### 2013-03-11 hotstorage13/background.tex

@@
 The data domain method ~\cite{bottleneck08} 
-uses  in-memory Bloom filter and maintains a prefetch cache for data blocks  which may be
+uses  in-memory Bloom filter and maintains a prefetching cache for data blocks  which may be
 accessed with high probability.  An improvement to this work with parallelization is in ~\cite{DEBAR}.

### 2013-03-11 hotstorage13/eval.tex
revised conclusions
figure/conclusions

@@
 
-The total local disk usage on
-each machine is about 8GB for duplicate detection purpose and most of them for global index. 
+The total local disk usage on each machine is about 8GB for the duplicate detection purpose,
+mainly for global index. 
 Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
@@
 the memory limit $M$ imposed on each node varies  from 20MB to 200MB.
+This figure also depicts the time breakdown for Stages 1, 2, and 3. 
+%The parallel time includes the first scanning time, 
+%of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
+%fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
+The time in Stages 1 and 2  is  dominated by  the two scans of dirty VM segments
+and the time for copying to the final backup storage is overlapped with VM scanning.
+During dirty VM segment reading, the average number of consecutive dirty segments is 2.92. 
+%Each scan takes about 1.4 hours.
 The overall processing time does not have a significant reduction as $M$ increases to 200MB.
-The parallel time includes the first scanning time, 
-of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
-fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
-The total time is mainly dominated by  the two scans of dirty VM segments.
-The time for copying to the final backup storage is overlapped with VM scanning.
-%Each scan takes about 1.4 hours.
-The aggregated throughput is  about 9.6GB per second,
+The aggregated deduplication throughput is  about 9.6GB per second,
 which is the size of 2500 VM images divided by the parallel time. 
+The system runs with  a single thread and  its CPU resource usage is upto 10\% of one core. 
 The result shows the backup with multi-stage deduplication  for all VM images can be 
-completed in about 2.9 hours with 35MB memory and 8GB disk overhead.
+completed in about 2.9 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
 As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
@@
 
+\comments{
 %\begin{verbatim}
 %q= is chosen between 500 or 100
-%Memory limit:   20 35M   50M  75M  100M  200M
-%req buf	    30M   40M  60   90M     180M
-%q:          450     275    275   275 275   
-%Time:          3.06  2.9  2.86  2.84 2.834  2.823
-%Time for two scans: 2.63  2.63
+Memory limit:   20 35M   50M  75M  100M  200M
+req buf	        15M 30M   40M  60   90M     180M
+q:           450     275    275   275 275   
+Time:         3.1  2.9  2.86  2.84 2.834  2.823
+stage 1      1.53    1.4   1.38  1.37 1.36 1.35
+stage 2	     0.23    0.17 0.15   0.15 0.15  0.15
+stage 3	     1.33    1.328  1.33  1.33 1.33  1.33
+
+Time for two scans: 2.63  2.63
 %\end{verbatim}
+}
 

### 2013-03-11 hotstorage13/eval.tex

@@
 %fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
-The time in Stages 1 and 2  is  dominated by  the two scans of dirty VM segments
+The time in Stages 1 and 3  is  dominated by  the two scans of dirty VM segments
 and the time for copying to the final backup storage is overlapped with VM scanning.

### 2013-03-11 hotstorage13/eval.tex
sharing

@@
 The signature for variable-sized blocks is computed using their SHA-1 hash. 
-The final snapshots are stored in a distributed file system built on the same cluster and the average I/O bandwidth
-of local storage is about 50MB/second.  The seek cost of each random IO request is about  10 milliseconds.
+The average I/O bandwidth of local storage is about 50MB/second 
+in the presence of other I/O jobs.
+The seek cost of each random IO request is about  10 milliseconds.
+The final snapshots are stored in a distributed file system built on the same 
+cluster. 
 %and that translates to an aggregated backup throughput of 139GB per second, or 500TB per hour.
@@
 which is the size of 2500 VM images divided by the parallel time. 
-The system runs with  a single thread and  its CPU resource usage is upto 10\% of one core. 
+The system runs with  a single thread and  its CPU resource usage is 10-13\% of one core. 
 The result shows the backup with multi-stage deduplication  for all VM images can be 

### 2013-03-12 hotstorage13/abs.tex
resource...

@@
 Our evaluation shows that  the proposed multi-stage scheme 
-uses a very small amount of system resources while delivering a satisfactory backup throughput.
+uses a small or modest amount of system resources while delivering a satisfactory backup throughput.
 %in a large cloud setting.

### 2013-03-12 hotstorage13/intro.tex
fix typos
resource...

@@
 Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently. 
-Cloud providers often wish that the backup service only consumes  the minimal resource usage without 
-impacting any existing cloud service.  Another challenge for backup with deduplication is that deletion 
+Cloud providers often wish that the backup service only consumes  a small or modest resource usage 
+with a minimal impact to the existing cloud services.  Another challenge for backup with deduplication is that deletion 
 of old snapshot competes computing resource also. That is because data dependence created 
@@
 
-Among the three factors - time, cost and de-deduplication efficiency, one of them has to be compromised for the other two.
+Among the three factors - time, cost and deduplication efficiency, one of them has to be compromised for the other two.
 For instance, if we were building a deduplication system that has a high rate of duplication detection and has a very fast response time,
 it would need a lot of memory to hold fingerprint index and cache.  This leads to a compromise on cost. 
-The objective of our project is to lower the cost incurred while sustaining the highest de-duplication ratio
-and  the sufficient deduplication  throughput for dealing with a large number of VM images. 
+Our objective is to lower the cost incurred while sustaining the highest de-duplication ratio
+and  a sufficient throughput in dealing with a large number of VM images. 
 % This business model partially  resembles that of Amazon Glacier.

### 2013-03-12 hotstorage13/abs.tex
update abstract

--- 2013-03-10 hotstorage13/abs.tex
@@
 Our evaluation shows that  the proposed multi-stage scheme 
-uses a very small amount of system resources while delivering a satisfactory backup throughput.
+uses a small amount of system resources while delivering a satisfactory backup throughput.
 %in a large cloud setting.

### 2013-03-12 hotstorage13/eval.tex
resource...
w

@@
 We have performed a trace-driven study using  a 1323 VM dataset  collected from 100 
-Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
-Each multi-core machine   hosts  up to 25 VMs. 
+Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE} and each
+of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
 For each VM, the system keeps 10 automatically-backed snapshots in the storage while
@@
 The signature for variable-sized blocks is computed using their SHA-1 hash. 
+The seek cost of each random IO request in our test machines is about  10 milliseconds.
 The average I/O bandwidth of local storage is about 50MB/second 
-in the presence of other I/O jobs.
-The seek cost of each random IO request is about  10 milliseconds.
+in the presence of other I/O jobs. Noted that a RAID 0 configuration can deliver
+over 300MB/second with 4 drives or more and our setting uses
+16.7\% or less of local storage bandwidth. 
 The final snapshots are stored in a distributed file system built on the same 

### 2013-03-12 hotstorage13/background.tex

--- 2013-03-10 hotstorage13/background.tex
@@
 %The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
-Backup systems have been developed to use content hash (fingerprints) to identify duplicate
+Backup systems have been developed to use content fingerprints to identify duplicate
 content~\cite{venti02,Rhea2008}.
@@
 Several techniques have been proposed to speedup searching of duplicate
-content. For example,
-The data domain method ~\cite{bottleneck08} 
-uses  in-memory Bloom filter and maintains a prefetch cache for data blocks  which may be
-accessed with high probability.  An improvement to this work with parallelization is in ~\cite{DEBAR}.
+fingerprints. For example, the data domain method ~\cite{bottleneck08} 
+uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
+accessed.  An improvement to this work with parallelization is in ~\cite{DEBAR}.
 Still such methods use  a significant amount of memory resource for filtering and caching.

### 2013-03-12 hotstorage13/eval.tex
w

@@
 Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
-
 Objectives of our evaluation are:
@@
 Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
-variable-sized content blocks ~\cite{similar94} with an average size of 4KB.
+variable-sized content blocks  with an average size of 4KB.
+%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
 The signature for variable-sized blocks is computed using their SHA-1 hash.
+
 The seek cost of each random IO request in our test machines is about  10 milliseconds.

### 2013-03-12 hotstorage13/main.tex
ad

--- 2013-03-08 hotstorage13/main.tex
@@
 Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
-{\normalsize$^\star$Department of Computer Science, University of California at Santa Barbara}
-  {\normalsize$^\dagger$Alibaba Inc.}
+{\normalsize$^\star$ University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
 }

### 2013-03-12 hotstorage13/arch.tex
w
update deletion

@@
 These blocks are of variable-size, partitioned using
-the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
+the standard content-based chunking technique with 4KB as the average block size. 
+%the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
 %To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
@@
 %As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
-To delete useless  blocks or segments periodically, we read the meta data  of live 
+To delete useless  blocks or segments periodically, we read the meta data  of all
 snapshots and compute the reference count of all blocks and segments  in parallel

### 2013-05-01 hotstorage13/arch.tex
revise

@@
 dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
-information such as chunk fingerprints,  sends a request to a proper machine, accumulates  
+information such as chunk fingerprints,  sends a request to a proper machine, and accumulates  
 received requests into a partition on the local temporary disk storage. 
@@
 and outputs each request buffer to one of the request partitions on the disk
-when this request buffer becomes full.  Option 2 depicted in Figure~\ref{fig:flow}
+when this request buffer becomes full.  Option 2, which is  depicted in Figure~\ref{fig:flow},
 is much more efficient than Option 1 because $2p+q$ is much smaller than
-$p\times q$. As a result, each buffer in Option 2 has a bigger size to accumulate requests and that means
+$p\times q$, except for the very small  values. 
+As a result, each buffer in Option 2 has a bigger size to accumulate requests and that means
 less disk seek overhead.

### 2013-05-01 hotstorage13/background.tex
revise

@@
 uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
-accessed.  An improvement to this work with parallelization is in ~\cite{DEBAR}.
+accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
 Still such methods use  a significant amount of memory resource for filtering and caching.
@@
 
+Noted that this paper optimizes the cost of backup when such a service runs on the existing
+cluster resource for the cloud. Another option is to attach  a separate backup storage system with deduplication
+support  the cloud cluster and every machine can periodically transfer snapshot data to
+the attached backup system.
+%One  weakness of this approach is communication bottleneck between a large number of machines
+%in a cloud to this centralized  service.
+The cost of allocating the above dedicated backup  resource can be expensive.
+Since most of backup data is not used eventually, CPU and memory resource in such a backup service may 
+not be fully utilized. This paper seeks for on a low-cost architecture option.
+
 %It should be emphasized that our approach does not  accumulate raw backup data temporarily for deduplication

### 2013-05-01 hotstorage13/intro.tex
re
revise

@@
 %tens of thousands of  virtual machines(VM) created for various active users.
-Periodic  archiving of virtual machine (VM) snaps is important 
+Periodic  archiving of virtual machine (VM) snapshots is important 
 for long-term data  retention and fault recovery in case of machine failures.  
@@
 Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently. 
-Cloud providers often wish that the backup service only consumes  a small or modest resource usage 
-with a minimal impact to the existing cloud services.  Another challenge for backup with deduplication is that deletion 
-of old snapshot competes computing resource also. That is because data dependence created 
+Cloud providers often wish that the backup service only consumes  small or modest resources 
+with a minimal impact to the existing cloud services.  Another challenge for backup with deduplication is 
+that deletion of old snapshot competes for computing resource as well. That is because data dependence created 
 by duplicate relationship among snapshots  adds processing complexity.
@@
 %parition-wise  deletion. 
+The tradeoff is that every machine has to read dirty segments twice
+and that some deduplication requests are delayed for staged parallel processing.
 With careful parallelism and buffer  management,

### 2013-05-02 hotstorage13/eval.tex
new experiment data

@@
 We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a Linux cluster
-of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  
+of Intel Nehalem E5530 machines.  
 Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
@@
 cluster.
-%and that translates to an aggregated backup throughput of 139GB per second, or 500TB per hour.
-%  For 2 hours, every machine can do 139MB/second. For 3 hours, then 92MB/second
-
-% the system must finish saving daily snapshots of all VMs in 2 hours.
-In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.
-
-%In our snapshot deduplication architecture, CDS is the key to achieve greater deduplication than
-%incremental backup solutions. Our basic assumption of CDS us that VM disks, especially OS disks,
-%have huge amount of data in common, and such common data can be represented by a relatively smaller data set
-%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
-%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
-%the effectiveness of CDS using real user VM disks from our production VM cluster.
-
-%Since it's impossible to perform large scale analysis without affecting the VM performance,
-%We have sampled a data set from 1323 real user VMs from a cluster with 100 nodes 
-%to measure the effectiveness of our scheme.
-
-%In this dataset, there are 10 snapshots per each VM user and the total amount of space 
-%investigated is 17.5 terabytes.
-%This dataset contas compose of 35 VMs from 7 popular OSes: 
-%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
-%5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
-%The overall data size for this 700 full snapshots is 17.6 TB.
-%This dataset  contains the snapshots of 1323 VMs.
-%Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
-%study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
-%
-%using a dataset containing 10 snapshots of 35 VMs.
-%Popularity of data blocks are collected through global counting 
-%and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.
-
-\comments{
-
-Each VM file is  divided into content blocks of
-variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
-The signature for variable-sized blocks is computed using  their SHA-1 hash. 
-Each segment is of size 2MB.  
-Popularity is computed by using 90\% of dataset, which reflects our setting that the system recomputes
-CDS every 1-2 days to catch up the popularity trend.
-}
-%seg, and we performed global perfect deduplication 
-%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
-%and maximum block size
-%OS data
-%user data: zipf
-%prediction
-%say something about aliyun
-
-%To compare the effectiveness with a full deduplication approach with an approximation,
-%we use  extreme binning and perfect deduplication~\cite{extreme_binning09}. 
-%For perfect deduplication and extreme binning, each snapshot is also divided into chunk blocks
-%using TTTD with an average size of 4KB. The original extreme binning work uses the whole file
-%as the input unit and  this size is too big in our system. 
-%Thus we split each image snapshot file into variable-sized segments base on the block hash list, 
-%using TTTD with average size of 2MB.
-
-%\subsection{Effectiveness of 3-level Deduplication}
-
-%\begin{figure}
-%  \centering
-%  \epsfig{file=images/overall_effect.eps, width=3.5in}
-%  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
-%deduplication divided by the original data size and the unit is percentage. }
-%
-%  \label{fig:overall}
-%\end{figure}
 
@@
 \begin{tabular} {|c|c|c|c|c|c|}
-\hline \#Partitions  & 50 & 275  &450 &  750 &  1500 \\
-\hline Index+request & 156&  28.4 & 17.4 & 10.7 & 5.2 \\
+\hline \#Partitions  & 100 & 250  & 500 &  750 &  1000 \\
+\hline Index+request & 100.1 &  40.1 & 20.1 & 13.4 & 10.1 \\
   (MB)           &  &   &  & &  \\

### 2013-05-02 hotstorage13/eval.tex
update storage desc

@@
 The seek cost of each random IO request in our test machines is about  10 milliseconds.
-The average I/O bandwidth of local storage is about 50MB/second 
-in the presence of other I/O jobs. Noted that a RAID 0 configuration can deliver
-over 300MB/second with 4 drives or more and our setting uses
-16.7\% or less of local storage bandwidth. 
+The average I/O usage of local storage is controlled about 50MB/second for our backup task
+in the presence of other I/O jobs. Noted that a typical 1U server can host
+6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less of local storage bandwidth.
 The final snapshots are stored in a distributed file system built on the same

### 2013-05-03 hotstorage13/abs.tex
shorten to 5 pages

@@
 hosting  reliability; however, it  takes significant 
-memory resource to perform data duplication in order to remove
-excessive redundancy among snapshots.
+memory resource to detect and remove duplicated content blocks among snapshots.
 This paper presents a low-cost deduplication solution scalable for a large number 
@@
 Our evaluation shows that  the proposed multi-stage scheme 
-uses a small amount of system resources while delivering a satisfactory backup throughput.
+uses a small amount of memory  while delivering a satisfactory backup throughput.
 %in a large cloud setting.

### 2013-05-03 hotstorage13/arch.tex
shorten to 5 pages

@@
 We consider deduplication in two levels. The first level
-uses coarse-grain segment  dirty bits for version-based detection~\cite{Clements2009,Vrable2009} to 
-identify difference from the previous snapshot to the current snapshot.  
+uses coarse-grain segment  dirty bits for version-based detection~\cite{Clements2009,Vrable2009}.
+% to identify difference from the previous snapshot to the current snapshot.  
 %That  can be accomplished efficiently and inexpensively in the OS level.
@@
 duplicates can be detected using segment dirty bits when the segment size is 2M bytes.  
-This setting requires OS to keep the metadata for segment dirty bits and the amount of space for such segment 
-dirty bits is negligible. In the second level of deduplication, content blocks of dirty segments at each VM 
+This setting requires OS to keep segment dirty bits and the amount of space for this purpose
+is negligible. In the second level of deduplication, content blocks of dirty segments 
 are compared with the fingerprints of unique  blocks from the previous snapshots.
@@
 %Request accumulation and partition-based deduplication.}
-The second level duplicate detection requires a global comparison of 
-content fingerprints.
+The second level detection requires a global comparison of fingerprints.
 % of stored chunks with the new chunks scanned during the backup process. 
@@
 Our approach is to perform duplicate detection first before actual data backup.
-That requires a pre-scanning of  data  blocks in dirty VM segments  and after that, real backup  for those non-duplicates
-is conducted. That does incur an extra  round of local VM block reading while avoiding inline 
-deduplication and leading to a much smaller resource requirement.  
-During VM reading, detection requests are accumulated on the disk 
-for a period time  in a  partitioned manner.  Aggregated duplicate requests can be processed partition by partition. 
+That requires a prescanning of  data  blocks in dirty VM segments, which
+%  and after that, real backup  for those non-duplicates is conducted. 
+does incur an extra  round of VM reading.
+% while avoiding inline deduplication and leading to a much smaller resource requirement.  
+During VM prescanning, detection requests are accumulated.
+Aggregated duplicate requests can be processed partition by partition. 
 %We also accumulate the delete requests and perform them partition by partitions. 
-Since each partition corresponds to a small portion of global content index, the cost to 
-process detection requests within a partition is significantly smaller than processing all the requests globally.
+Since each partition corresponds to a small portion of global content index, 
+memory cost to process detection requests within a partition is small.
+%the cost to process detection requests within a partition is significantly smaller than processing all 
+%the requests globally.
 
@@
 Let {\em global index} be the meta data containing the fingerprint values of unique blocks of snapshots
-in all VMs and  the reference pointers which lead to the location of raw data.
+in all VMs and  the reference pointers to the location of raw data.
 %A duplicate detection request for a content block needs to be compared with the global index to determine if this
@@
 %We conduct parallel processing of detection requests in all machines involved. 
-A logical way to distribute detection requests among machines is to partition based on fingerprint values of content blocks
-in a  disjointed manner.
-Initial VM data reading follows the VM distribution among machines and the detected duplicate summary results 
-need to be collected following the VM distribution. 
+A logical way to distribute detection requests among machines is to partition based on 
+fingerprint values of content blocks.
+% in a  disjointed manner.
+Initial data  blocks follows the VM distribution among machines and the detected duplicate summary 
+should be collected following the same distribution.
 Therefore, there are two all-to-all data redistribution operations involved.
@@
 Another one  is to map duplicate summary from fingerprint-based distribution to VM based distribution.  
-The redistributed data needs to be accumulated on the disk to minimize the use of memory.
-To minimize the excessive disk seek cost, outgoing or incoming data exchange messages need to be buffered to bundle small messages.
+The redistributed data needs to be accumulated on the disk to reduce the use of memory.
+To minimize the disk seek cost, outgoing or incoming data exchange messages are buffered to 
+bundle small messages.
 Given there are $p\times q$ partitions where $p$ is the number of machines and $q$ is the number of fingerprint-based partitions
@@
 directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
-A VM image is divided into a set of segments and each  segment contains hundreds of content blocks. 
-These blocks are of variable-size, partitioned using
-the standard content-based chunking technique with 4KB as the average block size. 
+A VM image is divided into a set of segments and each  segment contains 
+content blocks of variable-size, partitioned using
+the standard chunking technique with 4KB as the average block size. 
 %the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
@@
 VM images that need a backup
-and forms duplicate  detection requests. For those segments that have been modified since last backup indicated by 
-dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
+and forms duplicate  detection requests. 
+%For those dirty segments,
+%segments that have been modified since last backup indicated by dirty bits,  
+The system divides  each dirty segment into a sequence of chunk blocks,  computes the meta 
 information such as chunk fingerprints,  sends a request to a proper machine, and accumulates  
@@
 \item For Stage 3, $M$  is divided for 1) an I/O buffer to read dirty segments of a VM and   
-write non-duplicate content blocks to the  backup storage.
-2) summary of duplicate blocks within dirty segments of  a VM.
+write non-duplicate blocks to the  backup storage;
+2) summary of duplicate blocks within dirty segments. 
 \end{itemize}
@@
 
-{\bf Snapshot deletion.} Each VM will keep a limited number of  automatically-saved VM snapshots and thus
-expired snapshots will be deleted unless its owner explicitly asks for its retention.
+{\bf Snapshot deletion.} Each VM will keep a limited number of  automatically-saved snapshots and 
+expired snapshots are normally deleted.
+% unless its owner explicitly asks for its retention.
 We adopt the idea of mark-and-sweep~\cite{Guo2011}. 
@@
 To delete useless  blocks or segments periodically, we read the meta data  of all
-snapshots and compute the reference count of all blocks and segments  in parallel
-while following the fingerprint-based partitioning.
+snapshots and compute the reference count of all blocks and segments  in parallel.
+%while following the fingerprint-based partitioning.
 Similar to the multi-stage duplicate detection process, reference counting is conducted in multi-stages. 
-Stage  1 is to read  the segment and block  metadata of snapshots 
+Stage  1 is to read  the segment and block  metadata 
 to accumulate  reference count requests in different machines  in the fingerprint based distribution.

### 2013-05-03 hotstorage13/background.tex
shorten to 5 pages

@@
 
-Noted that this paper optimizes the cost of backup when such a service runs on the existing
-cluster resource for the cloud. Another option is to attach  a separate backup storage system with deduplication
-support  the cloud cluster and every machine can periodically transfer snapshot data to
+This paper considers a backup service uses the existing cluster computing resource. 
+Another option is to attach  a separate backup system with deduplication
+support the cluster, and  every machine can periodically transfer snapshots to
 the attached backup system.

### 2013-05-03 hotstorage13/eval.tex
shorten to 5 pages

@@
 
-We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a Linux cluster
-of Intel Nehalem E5530 machines.  
+We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a cluster
+of dual quad-core Intel Nehalem 2.4GHz E5530 machines with 24GB memory.  
 Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
@@
 The seek cost of each random IO request in our test machines is about  10 milliseconds.
-The average I/O usage of local storage is controlled about 50MB/second for our backup task
+The average I/O usage of local storage is controlled about 50MB/second for backup. 
 in the presence of other I/O jobs. Noted that a typical 1U server can host
-6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less of local storage bandwidth.
+6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
+of local storage bandwidth. 
 The final snapshots are stored in a distributed file system built on the same 
@@
  a 100-node cluster a  when 
-the memory limit $M$ imposed on each node varies  from 20MB to 200MB.
+limit $M$ imposed on each node varies.
+%  from 20MB to 200MB.
 This figure also depicts the time breakdown for Stages 1, 2, and 3. 
@@
 %fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
-The time in Stages 1 and 3  is  dominated by  the two scans of dirty VM segments
-and the time for copying to the final backup storage is overlapped with VM scanning.
-During dirty VM segment reading, the average number of consecutive dirty segments is 2.92. 
+The time in Stages 1 and 3  is  dominated by  the two scans of dirty segments,
+and final data copying to the backup storage is overlapped with VM scanning.
+During dirty segment reading, the average number of consecutive dirty segments is 2.92. 
 %Each scan takes about 1.4 hours.
@@
 
-Table~\ref{tab:overall} shows performance change when memory limit $M$=35MB is imposed and
-the number of partitions per machine ($q$) varies from 50 to 1500.
-Row 2 is the memory space required to load a partition of global index and detection requests.
-When $q=50$, the required memory is 156MB, which  is  not  a viable choice  under  constraint $M=$35MB.  
+Table~\ref{tab:overall} shows performance change when limit $M$=35MB is imposed and
+the number of partitions per machine ($q$) varies.
+% varies from 100 to 1000.
+Row 2 is memory space required to load a partition of global index and detection requests.
+When $q=100$, the required memory is 100.1 MB and this exceeds the limit $M=$35MB.  
 Row 3 is the parallel time and Row 4 is  the aggregated throughput of  100 nodes.
@@
 %with the very small resource usage.
-Row 5 is  the parallel time if  we use Option 1 with $p\times q$ send buffers 
+Row 5 is  the parallel time for using Option 1 with $p\times q$ send buffers 
 described in Section~\ref{sect:arch}. 
-With the large number of buffers, the available space per buffer reduces significantly as $q$ increases, which leads to
-a big increase of IO requests and seek cost.
+When $q$ increases, the available space per buffer reduces and there is a big increase of seek cost.  
+The main network usage before performing the final data write is for request accumulation and
+summary output. It lasts about 20 minutes and each machine exchanges 
+about   8MB of metadata per second with others during that period, which is 6.25\% of the network bandwidth.
 
 \begin{table}[hbt]
-\caption{ Performance when the number of partitions per machine node varies and $M$=35MB is imposed.}
+\caption{ Performance when $M$=35MB and $q$ varies.}
 \begin{center}
 \begin{tabular} {|c|c|c|c|c|c|}
-\hline \#Partitions  & 100 & 250  & 500 &  750 &  1000 \\
+\hline \#Partitions ($q$)  & 100 & 250  & 500 &  750 &  1000 \\
 \hline Index+request & 100.1 &  40.1 & 20.1 & 13.4 & 10.1 \\

### 2013-05-03 hotstorage13/intro.tex
shorten to 5 pages

@@
 Periodic  archiving of virtual machine (VM) snapshots is important 
-for long-term data  retention and fault recovery in case of machine failures.  
+for long-term data  retention and fault recovery. 
+%in case of machine failures.  
 For example, daily backup of VM images  is conducted automatically 
@@
 %deletion in a reasonable amount of time. 
-The traditional approach to  deduplication for backup is an inline approach which follows
+The traditional approach to  deduplication is an inline approach which follows
 a sequence of block reading, duplicate detection,  and non-duplicate  block write to the 

### 2013-05-03 hotstorage13/main.tex
shorten to 5 pages

@@
 
+{\bf Acknowledgment.} We thank the anonymous referees for their valuable comments.
+This work is supported in part by NSF IIS-1118106. 
+Any opinions, findings, conclusions or recommendations expressed in this material
+are those of the authors and
+do not necessarily reflect the views of the National Science Foundation.
+
       %\setlength{\itemsep}{ex}%

### 2013-05-03 hotstorage13/arch.tex
correction

@@
 received requests into a partition on the local temporary disk storage. 
-The partition mapping is using a hash function applied to the content fingerprint. 
+The partition mapping uses a hash function applied to the content fingerprint. 
 Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
-$q$ partitions of global index and accumulates corresponding requests on the disk. 
+$q$ partitions of global index and it accumulates corresponding requests on the disk. 
 There are two options to allocate buffers at each machine. 
@@
 Another issue is that during global index update after new block creation in the backup storage,
-the system  may find some  blocks with the same fingerprint may be 
+the system  may find some  blocks with the same fingerprint are 
 created redundantly. For example, two different VM blocks that have the same  fingerprint are not detected
@@
 
-The above steps can be executed by each machine
-using one thread to minimize the use of CPU, network bandwidth, and disk bandwidth.
+The above steps can be executed by each machine using one thread to minimize the use of computing resource.
 The  disk storage usage on each machine 
@@
 We impose a memory limit $M$ allocated for each stage of processing at each machine.
-The usage of $M$ is controlled as follows and the distribution among buffers is optimized based on the relative
+The usage of $M$ is controlled as follows and space distribution among buffers is optimized based on the relative
 ratio between the cross-machine network  startup cost and disk access startup cost such as seek time.

### 2013-05-03 hotstorage13/intro.tex
correction

@@
 This issue has been addressed by   storage data deduplication ~\cite{venti02,bottleneck08} that
-identifies redundant content duplicates among snapshots.  On the other hand, performing
+identifies redundant content duplicates among snapshots.
+
+This paper considers a backup service uses the existing cluster computing resource.
+Another option is to attach  a separate backup system with deduplication
+support the cluster, and  every machine can periodically transfer snapshots to
+the attached backup system.
+The cost of allocating the above dedicated backup  resource can be expensive.
+Since most of backup data is not used eventually, CPU and memory resource in such a backup service may
+not be fully utilized. This paper seeks for a low-cost architecture option.
+Performing
 deduplication adds significant  memory cost for comparison of content fingerprints. 

### 2013-05-03 hotstorage13/arch.tex
grammar fixed

@@
 Another issue is that during global index update after new block creation in the backup storage,
-the system  may find some  blocks with the same fingerprint are 
+the system  may find some  blocks with the same fingerprints have been 
 created redundantly. For example, two different VM blocks that have the same  fingerprint are not detected

### 2013-05-03 hotstorage13/arch.tex
change

--- 2013-05-03 hotstorage13/arch.tex
@@
 We impose a memory limit $M$ allocated for each stage of processing at each machine.
-The usage of $M$ is controlled as follows and space distribution among buffers is optimized based on the relative
+The usage of $M$ is controlled as follows and space allocation among buffers is optimized based on the relative
 ratio between the cross-machine network  startup cost and disk access startup cost such as seek time.
-Slower start cost requires more buffer space.
+Using a bigger buffer  can mitigate the impact of slower start cost. 
 \begin{itemize}

### 2013-05-03 hotstorage13/background.tex
correction

@@
 For VM snapshot backup, file-level semantics are normally not provided.
-Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data.
+Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data.
 Only raw access information at disk block level are provided.
@@
 
+\comments{
 This paper considers a backup service uses the existing cluster computing resource. 
@@
 Since most of backup data is not used eventually, CPU and memory resource in such a backup service may 
-not be fully utilized. This paper seeks for on a low-cost architecture option.
-
+not be fully utilized. This paper seeks for a low-cost architecture option.
+}
 %It should be emphasized that our approach does not  accumulate raw backup data temporarily for deduplication

### 2013-05-03 hotstorage13/intro.tex
revised

--- 2013-05-03 hotstorage13/intro.tex
@@
 This issue has been addressed by   storage data deduplication ~\cite{venti02,bottleneck08} that
-identifies redundant content duplicates among snapshots.  On the other hand, performing
-deduplication adds significant  memory cost for comparison of content fingerprints. 
+identifies redundant content duplicates among snapshots.
+
+This paper considers a backup service uses the existing cloud computing resource.
+Another option is to attach  a separate backup system with deduplication
+support to the cloud cluster, and  every machine periodically transfers snapshots to
+the attached backup system.
+The cost of allocating a dedicated backup  system can be expensive.
+%Since most of backup data is not used in practice, system resource in such a service is not fully utilized. 
+This paper seeks for a low-cost architecture option.
+Performing deduplication adds significant  memory cost for comparison of content fingerprints. 
 Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently. 
@@
 with a minimal impact to the existing cloud services.  Another challenge for backup with deduplication is 
-that deletion of old snapshot competes for computing resource as well. That is because data dependence created 
+that deletion of old snapshots compete for computing resource as well. That is because data dependence created 
 by duplicate relationship among snapshots  adds processing complexity.

### 2013-05-03 hotstorage13/arch.tex

@@
 duplicates can be detected using segment dirty bits when the segment size is 2M bytes.  
-This setting requires OS to keep segment dirty bits and the amount of space for this purpose
-is negligible. In the second level of deduplication, content blocks of dirty segments 
+This setting requires OS to maintain segment dirty bits and 
+the amount of space for this purpose is negligible. In the second level of deduplication, content blocks of dirty segments 
 are compared with the fingerprints of unique  blocks from the previous snapshots.
@@
 ratio between the cross-machine network  startup cost and disk access startup cost such as seek time.
-Using a bigger buffer  can mitigate the impact of slower start cost. 
+Using a bigger buffer  can mitigate the impact of slower startup cost. 
 \begin{itemize}

### 2013-05-04 hotstorage13/intro.tex
revised

@@
 identifies redundant content duplicates among snapshots.  
+One architectural approach is to attach  a separate backup system with deduplication
+support to the cloud cluster, and  every machine periodically transfers snapshots to
+the attached backup system.  The cost of allocating such a dedicated backup  system can be expensive.
 
-This paper considers a backup service uses the existing cloud computing resource.
-Another option is to attach  a separate backup system with deduplication
-support to the cloud cluster, and  every machine periodically transfers snapshots to
-the attached backup system.
-The cost of allocating a dedicated backup  system can be expensive.
+This paper seeks for a low-cost architecture option and considers that
+a backup service uses the existing cloud computing resource.
 %Since most of backup data is not used in practice, system resource in such a service is not fully utilized. 
-This paper seeks for a low-cost architecture option.
 Performing deduplication adds significant  memory cost for comparison of content fingerprints. 

### 2013-05-04 hotstorage13/eval.tex
correction
fix some numbers

@@
 The seek cost of each random IO request in our test machines is about  10 milliseconds.
-The average I/O usage of local storage is controlled about 50MB/second for backup. 
+The average I/O usage of local storage is controlled about 50MB/second for backup 
 in the presence of other I/O jobs. Noted that a typical 1U server can host
@@
 %Each scan takes about 1.4 hours.
-The overall processing time does not have a significant reduction as $M$ increases to 200MB.
-The aggregated deduplication throughput is  about 9.6GB per second,
+The overall processing time does not have a significant reduction as $M$ increases to 95MB.
+The aggregated deduplication throughput is  about 8.76GB per second,
 which is the size of 2500 VM images divided by the parallel time. 
@@
 The result shows the backup with multi-stage deduplication  for all VM images can be 
-completed in about 2.9 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
+completed in about 3.1 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
 As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
@@
 Row 2 is memory space required to load a partition of global index and detection requests.
-When $q=100$, the required memory is 100.1 MB and this exceeds the limit $M=$35MB.  
+When $q=100$, the required memory is 83.6 MB and this exceeds the limit $M=$35MB.  
 Row 3 is the parallel time and Row 4 is  the aggregated throughput of  100 nodes.
@@
 \hline \#Partitions ($q$)  & 100 & 250  & 500 &  750 &  1000 \\
-\hline Index+request & 100.1 &  40.1 & 20.1 & 13.4 & 10.1 \\
+\hline Index+request & 83.6 &  33.5 & 16.8 & 11.2 & 8.45 \\
   (MB)           &  &   &  & &  \\
 
-\hline Total Time  & N/A&  2.9 & 2.91 & 3 & 3.1 \\
+\hline Total Time  & N/A&  3.12 & 3.15 & 3.22 & 3.29 \\
   (Hours)           &  &   &  & &  \\
 %\hline Throughput/node & N/A&  85MB/s& 90M & 87 & 81 \\
-\hline Throughput GB/s& N/A&  9.6& 9.5 & 9.3 & 8.9 \\
+\hline Throughput GB/s& N/A&  8.76 & 8.67 & 8.48 & 8.30 \\
 \hline Total time & N/A&  7.8& 11.7 & 14.8 & 26 \\

### 2013-05-07 hotstorage13/main.tex

@@
 \author{
-Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
+Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, and Hong Tang$^\dagger$ \\
 {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
+%Wei Zhang, Tao Yang, Gautham Narayanasamy\\
+%University of California at Santa Barbara
+%\and
+%Hong Tang\\
+%Alibaba Inc.
 }

### 2013-05-13 hotstorage13/background.tex
revised
give reasoning on why we want to avoid dedicated dedup nodes

@@
 Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. 
-Only raw access information at disk block level are provided.
+%Only raw access information at disk block level are provided. 
 %Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
@@
 accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-Still such methods use  a significant amount of memory resource for filtering and caching.
+%Still such methods use a significant amount of memory resource for filtering and caching.
+Such methods use dedicated nodes for deduplication, which add cost to cloud infrastructure and is less scalable.
 %NG et al.~\cite{ NGmiddleware2011}  use
@@
 %These are segments that share many chunk IDs with the incoming segment with high probability.
-The approximation techniques are studied in~\cite{extreme_binning09,WeiZhangIEEE}  
+The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
 %Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  

### 2013-05-14 hotstorage13/arch.tex
re

@@
 Our approach is to perform duplicate detection first before actual data backup.
-That requires a prescanning of  data  blocks in dirty VM segments, which
+That requires a prescanning of  dirty VM segments, which
 %  and after that, real backup  for those non-duplicates is conducted. 
@@
 \item {\bf Buffered data redistribution in parallel duplicate detection}.  
-Let {\em global index} be the meta data containing the fingerprint values of unique blocks of snapshots
+Let {\em global index} be the meta data containing the fingerprint values of unique snapshot blocks 
 in all VMs and  the reference pointers to the location of raw data.
@@
 %We conduct parallel processing of detection requests in all machines involved. 
-A logical way to distribute detection requests among machines is to partition based on 
+A logical way to distribute detection requests among machines is based on 
 fingerprint values of content blocks.
 % in a  disjointed manner.
-Initial data  blocks follows the VM distribution among machines and the detected duplicate summary 
+Initial data  blocks follows the VM distribution 
+among machines 
+and the detected duplicate summary 
 should be collected following the same distribution.
@@
 %\item 
-Stage 3 is to perform real backup one VM at a time.
+Stage 3 is to perform real backup.
+% one VM at a time.
 The system loads the duplicate summary of a VM, 

### 2013-05-14 hotstorage13/background.tex
re

@@
 content~\cite{venti02,Rhea2008}.
-Offline deduplication is used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
+Offline deduplication is 
+used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
 %,NGmiddleware2011}.
@@
 accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-%Still such methods use a significant amount of memory resource for filtering and caching.
-Such methods use dedicated nodes for deduplication, which add cost to cloud infrastructure and is less scalable.
+Still such methods use  a significant amount of memory resource for filtering and caching.
+As discussed in Section~\ref{sect:intro}, 
+there is no dedicated resource for deduplication in our targeted setting and low memory usage 
+is required so that the resource impact to other cloud services is minimized.
+
 %NG et al.~\cite{ NGmiddleware2011}  use
@@
 In comparison, this paper focuses on  full deduplication without approximation.
+%We also take advantages of the fact that in a VM cloud environment,
+%the virtual device driver can easily keep track if  large data
+%segments have been modified using dirty bits and such information can avoid sending
+%unmodified data segments for deduplication, which significantly saves cost.
 

### 2013-05-14 hotstorage13/arch.tex
save some lines

--- 2013-05-03 hotstorage13/arch.tex
@@
 During VM prescanning, detection requests are accumulated.
-Aggregated duplicate requests can be processed partition by partition. 
+Aggregated deduplicate requests can be processed partition by partition. 
 %We also accumulate the delete requests and perform them partition by partitions. 
-Since each partition corresponds to a small portion of global content index, 
+Since each partition corresponds to a small portion of global index, 
 memory cost to process detection requests within a partition is small.
@@
 Stage 3 is to perform real backup one VM at a time.
-The system loads the duplicate summary of a VM, 
+The system loads duplicate summary of a VM, 
 reads  dirty segments of a VM, and outputs non-duplicate blocks to the final backup 
@@
 blocks. Our experiment shows that it is faster to read dirty segments in the tested workload.
-Another issue is that during global index update after new block creation in the backup storage,
+Another issue is that during global index update after new block creation,
+% in the backup storage,
 the system  may find some  blocks with the same fingerprints have been 

### 2013-05-14 hotstorage13/background.tex
save some lines

--- 2013-05-13 hotstorage13/background.tex
@@
 %Still such methods use a significant amount of memory resource for filtering and caching.
-Such methods use dedicated nodes for deduplication, which add cost to cloud infrastructure and is less scalable.
+%Such methods use dedicated nodes for deduplication, which add cost to cloud infrastructure and are less scalable.
+As discussed in Section~\ref{sect:intro},
+there is no dedicated resource for deduplication in our targeted setting and low memory usage
+ is required so that the resource impact to other cloud services is minimized.
 %NG et al.~\cite{ NGmiddleware2011}  use

### 2013-05-14 hotstorage13/intro.tex
re
save some lines

@@
 \section{Introduction}
+\label{sect:intro}
 
@@
 support to the cloud cluster, and  every machine periodically transfers snapshots to
-the attached backup system.  The cost of allocating such a dedicated backup  system can be expensive.
+the attached backup system.  Such a dedicated backup  configuration can be expensive, 
+considering that significant networking  and computing resource  is required to transfer 
+raw data and conduct signature comparison.
 
@@
 Cloud providers often wish that the backup service only consumes  small or modest resources 
-with a minimal impact to the existing cloud services.  Another challenge for backup with deduplication is 
-that deletion of old snapshots compete for computing resource as well. That is because data dependence created 
+%with a minimal impact to the existing cloud services.  Another challenge for backup with deduplication is 
+with a minimal impact to the existing cloud services.  Another challenge is 
+%that deletion of old snapshots compete for computing resource as well. That is because data dependence created 
+that deletion of old snapshots compete for computing resource as well, because data dependence created 
 by duplicate relationship among snapshots  adds processing complexity.

### 2013-05-14 hotstorage13/main.tex
save some lines
update acknowledgement

@@
 
-{\bf Acknowledgment.} We thank the anonymous referees for their valuable comments.
+{\bf Acknowledgment.} 
+We wish to thank the following people for their contributions to the paper.
+Renu Tewari (our shepherd) and the anonymous referees for their valuable comments. Michael Agun 
+commented on the earlier drafts of the paper.
 This work is supported in part by NSF IIS-1118106. 

### 2013-05-24 snapshot_system/abs.tex
Append store chapter
chnge

@@
 \begin{abstract}
-This paper proposes a VM snapshot storage architecture which adopts multiple-level selective deduplication to bring the benefits of fine-grained data reduction into cloud backup storage systems.
-In this work, we describe our working snapshot system implementation, and provide
-early performance measurements for both deduplication impact and
-snapshot operations.
-Thank you!
+A cloud environment that  hosts a large number of  virtual machines has
+a high storage demand for frequent backup of system image snapshots.
+Deduplication of data blocks can lead a big reduction of redundant blocks when
+their signatures are identical. However it is expensive and less fault-resilient to perform a global comparison
+of all data block signatures and let a data block share by many virtual machines. 
+This paper studies a cluster-based design which collocates a lightweight
+backup service with the cloud service and integrates multiple duplicate detection strategies that  
+localize the deduplication as much as possible within each virtual machine.
+The optimized design only requires a small amount of memory resource to conduct duplicate detection
+and an analysis illustrates this design with deduplication localization  provides  better fault tolerance.
+This  paper  provides an evaluation that shows this  proposed scheme can accomplish a high deduplication 
+efficiency while sustaining a good backup throughput.
+
+%This paper studies the      a VM snapshot storage architecture which adopts multiple-level selective deduplication to bring the benefits of fine-grained data reduction into cloud backup storage systems.
+%In this work, we describe our working snapshot system implementation, and provide
+%early performance measurements for both deduplication impact and
+%snapshot operations.
 \end{abstract}

### 2013-05-24 snapshot_system/intro.tex
chnge

@@
 \section{Introduction}
-In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
-each instance of a guest operating system runs on a virtual machine, accessing
-virtual hard disks represented as virtual disk image files in the host operating system.
+In a cluster-based cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} 
+and Alibaba Aliyun\cite{Aliyun},
+each physical machine runs a number  of virtual machines as  instances of a guest operating system 
+and their  virtual hard disks are represented as virtual disk image files in the host operating system.
 %virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
-Because these image files are stored as regular files from the external point of view,
-backing up VM's data is mainly done by taking snapshots of virtual disk images.
+%Backup  of virtual disks is relatively straightforward since
+%these image files are stored as regular files from the external point of view,
+%backing up VM's data is mainly done by taking snapshots of virtual disk images.
 
-A snapshot preserves the data of a VM's file system at a specific point in time. 
-VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
-and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}.
+%A snapshot preserves the data of a VM's file system at a specific point in time. 
+%VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
+%and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
+Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
+For example, the Aliyun cloud , which is  the largest cloud service provider by Alibaba in China, 
+automatically conducts  the backup of virtual disk images to all active users every day.
+The cost of supporting a large number of concurrent backup streams is high
+because of the huge storage demand and  
+Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
+can effectively identify content duplicates among snapshots and  remove 
+redundant storage content,  but the solution can be expensive and there is a large amount of 
+network traffic to transfer  data from the host machines to the backup facility
+before duplicates are removed.
 
-Frequent  backup of VM snapshots increases  the reliability of VM's hosted in a cloud.
-For example, Aliyun, the largest cloud service provider by Alibaba in China, 
-provides automatic frequent backup of VM images to strengthen the reliability of its service for all users.
-The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
-Using a backup service with full deduplication support~\cite{venti02,bottleneck08}
-can identify content duplicates among snapshots to remove redundant storage content,  but the weakness is that it
-either adds the  extra cost significantly or competes computing resource with the existing cloud services.
-In addition, data dependence created by duplicate relationship among snapshots
-adds the complexity in fault tolerance management, especially when  VMs can migrate around in the cloud.
+This paper seeks for a low-cost architecture option and considers that
+a backup service collocates  on  the cloud cluster with a minimum resource usage. 
+%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
+The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
+duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
+On the other hand, comparing fingerprints  adds significant  memory cost. 
+Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
+Cloud providers often wish that the backup service only consumes  small or modest resources
+with a minimal impact to the existing cloud services.  A 
+recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
+Another issue is that after deduplication, the most of data blocks are shared by many virtual machines.
+Failure of such blocks would  have a catastrophic effect and many snapshots of virtual machines would be affected.
+Furthermore, 
+%that deletion of old snapshots compete for computing resource as well. That is because data dependence created
+deletion of old snapshots compete for computing resource as well and that  needs
+to be considered. That is  because data dependence created
+by duplicate relationship among snapshots  adds processing complexity.
+% especially when  VMs can migrate around in the cloud.
 
-Unlike the previous work dealing with general file-level backup and deduplication, our problem is focused on 
-virtual disk image backup. Although we treat each virtual disk  as a file logically, its size is very large.
-On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud every day. 
-One key requirement we face at Alibaba Aliyun is that VM snapshot backup should only use a minimal amount of system
-resources so that most of resources is kept for regular cloud system services or applications.
-Thus our objective is to exploit the characteristics of VM snapshot data and
-pursue a cost-effective deduplication solution. 
-Another goal  is to decentralize VM snapshot backup and  localize  deduplication as much as possible,
-which brings the benefits for increased parallelism  and fault isolation.
+The paper proposes an integrated approach which uses  multiple duplicate detection strategies
+integrating  version  detection, small-scope inner VM duplicate comparison
+and controlled cross-VM comparison. 
+The key idea of this approach is to localize duplicate detection within each virtual machine as much as possible
+and minimize memory usage while delivering a decent deduplication efficiency. 
+That brings the benefits for parallelism  utilization and fault isolation.
+Our deletion strategy uses a double Boomer filer strategy for periodic mark-and-sweeping of expired data blocks.
+We have developed a prototype system that runs a cluster of Linux machines running Zen.
+The backup storage uses a standard distributed file system  with data replication and
+we allocate more  replicas for the commonly-shared  data blocks among VM snapshots to enhance fault tolerance.
+
+%************** Paper sections summary
+%THIS NEEDS MODIFICATION
+The rest of this paper is organized as follows.
+Section~\ref{review} reviews background and related work.
+Section~\ref{sec:framework}  discusses the  design framework and system architecture.
+Section~\ref{sec:model}  analyzes the benefit of our approach for fault isolation. 
+Section~\ref{exper} is our experimental evaluation that compare with the other approach.
+Section~\ref{conc}  concludes this paper.
+
+%We are seeking Unlike the previous work dealing with general file-level backup and deduplication, our problem is focused on 
+%virtual disk image backup. Although we treat each virtual disk  as a file logically, its size is very large.
+%On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud every day. 
+%One key requirement we face at Alibaba Aliyun is that VM snapshot backup should only use a minimal amount of system
+%resources so that most of resources is kept for regular cloud system services or applications.
+%Thus our objective is to exploit the characteristics of VM snapshot data and
+%pursue a cost-effective deduplication solution. 
+%Another goal  is to decentralize VM snapshot backup and  localize  deduplication as much as possible,
 
 %,extreme_binning09,sparseindex09
+\comments{
 By observations on the VM snapshot data from production cloud, we found snapshot data duplication 
@@
 \end{table}
+}

### 2013-05-24 snapshot_system/cds.tex
Add cds analysiswq

\section{CDS Analysis}
[Purpose of using CDS]
CDS is a small percentage of the global data index that we into DHT as a shared index. 
With CDS as as a public data resource, each VM's snapshot backup has no need to 
store its own copies for data that already exist in CDS, instead they can just
store a reference. 
We expect CDS to contain most of the data related to operating system, software and libraries.

[What's the benifits]
Using CDS as a common data source brings us several benefits: 
First, the data we collect into CDS are commonly used in many VMs, 
thus the CDS index, a special subset of global index, has very high deduplication efficency.
Second, in our architecture the CDS data are the only data that can be shared between different VMs,
by carefully control the replication degree of CDS data, we could improve the fault-tolerancy
in such a data sharing environment. Finally, the CDS index is small enough to be put into a 
in-memory DHT, thus it avoids the excess memory usage of global index 
while brings us the majority of deduplication efficiency of it.

[Describe how CDS is generated]

[Explain why CDS scales effectively as data grow]
Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the 
frequency of data duplication follows Zipf-like distribution\cite{zipf}, 
with the exponent $\alpha$ between 0.65 ~ 0.70. 
As a result, it can be proved that deduplication efficiency of CDS index is scalable:

[Describe the dedup efficiency model in detail]
Let $S_c$ be the total number of FPs in CDS, $S_g$ be the total number of FPs in global index, $F$ be the size of a FP, $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size. The deduplication efficiency will be:
\begin{equation}
  E = (S_c / S_g)^{1-\alpha}
\end{equation}
The $S_c$ and $S_g$ can be expressed as:
\begin{equation}
S_c = N*m/F, S_g = N*D/B
\end{equation}
By replacing $S_c$ and $S_g$ in the first formula, we have:
\begin{equation}
  E = (\frac{m*B}{F*D})^{1-\alpha}
\end{equation}

Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.

### 2013-05-28 snapshot_system/background.tex
rev

--- 2013-05-14 hotstorage13/background.tex
@@
 
-%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
+The previous work for storage backup has extensively studied  data deduplication techniques can eliminate redundancy 
+globally among different files from different users.
 Backup systems have been developed to use content fingerprints to identify duplicate
-content~\cite{venti02,Rhea2008}.
-Offline deduplication is 
+content~\cite{venti02,Rhea2008}.  Offline deduplication is 
 used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
@@
 accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-Still such methods use  a significant amount of memory resource for filtering and caching.
 As discussed in Section~\ref{sect:intro},
@@
  is required so that the resource impact to other cloud services is minimized.
-
 %NG et al.~\cite{ NGmiddleware2011}  use
@@
 %lookup  
-In comparison, this paper focuses on  full deduplication without approximation.
+%In comparison, this paper focuses on  full deduplication without approximation.
 %We also take advantages of the fact that in a VM cloud environment,

### 2013-05-28 snapshot_system/challenge.tex
rev

@@
+\section{Design Consideration and Options}
+\label{sect:options}
+
+As we discuss earlier, collocating the backup service on the existing
+cloud cluster avoids the extra cost to acquire a dedicated backup facility
+and reduces the network bandwidth consumption in transferring the un-deduplicated
+raw data for backup. The running of such a service is subject to
+the resource availability of the system and we discuss the design considerations
+as follows.
+
+% That arises mainly in Alibaba's Aliyun cloud service.
+%concerns
+%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
+\begin{itemize}
+\item {\em Backup storage.}
+We use a distributed file system to cluster
+the storage  and store the backup with multiple replicas in the clustered storage.
+There can be a concern that storing many versions  of snapshots would
+require	a large amount of storage.
+The previous research shows the deduplication can compress the backup copies 
+effectively in a 10:1 or even 15:1 rage. Assume on the average the compression
+ratio is $c$:1.  When the number of versions
+saved in the backup storage is $b$  on the average, 
+the amount of storage space in the cluster allocated  for the backup would be $\frac{b}{b+c}$.
+For example, when $b=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
+When $b=9$ and $c=13$, storage usage is 40\%. 
+That is acceptable given today's cheap cost for disk storage.
+In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data
+while each machine typically can provide over 10TB storage.
+Thus the normal disk usage  is about 1TB per machine, and adding 30\% to 100\% 
+extra space for the backup is not a practical concern.
+
+\item {\em Backup throughput and computing resource}.
+As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
+to be processed can be huge. 
+On the other hand, the computing resources allocated for a snapshot service is limited
+because VM performance has higher priority.  
+The key usage of resource for backup is memory for storing and comparing the fingerprints. 
+We will consider the approximation techniques with less memory consumption
+studied in~\cite{extreme_binning09,Guo2011} along with the fault isolation consideration discussed below. 
+%A snapshot backup service shall not compete cpu, memory, or I/O bandwidth with VMs. 
+%Fingerprint-based search does require a significant amount of memory for fingerprint lookup
+%and comparison.  This competes memory resource  with the existing VMs.
+%Our design is to identify a low-cost and low-profile scheme for deduplication.
+%Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
+
+A  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with 
+the existing cloud, which is not preferred for cloud production system operation. 
+Thus it is desirable that backup for all nodes
+can be conducted in parallel and in a short period of time,
+and any centralized or  cross-machine communication for
+deduplication should not become a bottleneck.
+For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, The aggreated amount of data 
+the system must finish saving daily snapshots of all VMs in 2 hours.
+In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or
+500TB/hour.  The system must finish saving daily snapshots of all VMs in few hours. 
+Often a cloud has a few hours of light workload each day (e.g. midnight),  
+which creates an small window for automatic backup.
+
+%At Aliyun, it is required that while CPU and disk usage should be small or modest during backup time,
+%the memory footprint of snapshot service should not exceed 500MB at each node.
+
+Another consideration is backup data cleaning to delete useless blocks.
+Keeping reference counters for shared data blocks is challenging and less reliable.
+The previous work has advocated the mark-and-sweep approach  which periodically
+scans all data (or modified latest version of data)~\cite{?, Guo2011}. It first marks
+all used blocks and then sweep all chunks to reclaim unmarked blocks. 
+This approach is resilient to errors: at any time the process can simply be restarted with no 
+negative side effects.  Scalability, however, is an issue.
+To deal with 1 PB snapshots data, which may be represented by 10,000 GB FP index,
+If we account for an average deduplication factor of 10 (i.e., each chunk
+is referenced by 10 different snapshots), the total size
+of snapshot metadata that need to be read during the mark phase will
+be 100 TB.  This alone will take almost 2 hours on a
+1000-machine cloud. Furthermore, marking the in-use
+bits for 250 billion entries is no easy task. There is no
+way to put the bit map in memory. One might want
+to mitigate the poor performance of mark-and-sweep by
+doing it less frequently. But in practice this is not a viable
+option: customers always want to keep the utilization
+of the system close to its capacity so that a longer
+history can be stored. With daily snapshots taking place,
+systems rarely have the luxury to postpone deletion operations
+for a long time. In our field deployment, deletion
+is done once a day. More than 2 hours in each run is too
+much. In a large production-oriented dedupe system reference
+management needs to be very reliable and have
+good recover-ability. It should tolerate errors and always
+ensure correctness. Although mark-and-sweep provides
+these properties, its performance is proportional to the
+capacity of the system, thus limiting its scalability.
+
+\item {\em Fault tolerance and isolation.}
+The distributed file system~\cite{GoogleFS,Hadoop} provides the replication support
+and we can use the open-source software to implement such a layer.
+When the number of machines failed exceeds the replication degree, there will be
+ some data loss.  Storage deduplication worsens the impact of such faults
+because  the majority of data snapshots (e.g. over 90\%) is deduplicated
+and the corresponding data blocks are shared among VMs.
+
+The previous work in deduplication~\cite{extreme_binning09,sparseindex09} has
+studied the solutions  to reduce memory requirement.
+They have not considered content sharing affects
+fault isolation.
+Because a content chunk is compared with a content signature collected from other users,
+this artificially creates data dependency among different VM users.
+% since storage for shared identical content chunks can become a failure point.
+In large scale cloud, node failures happen at daily basis,
+the loss of a shared block can affect many users whose snapshots share this 
+data block. 
+Without any control of such data sharing, we can only increase  
+replication for global dataset to enhance the availability,
+but this incurs significantly more cost.
+Loss of a small number of  shared data blocks can 
+cause the unavailability of snapshots for a large number of virtual machines.
+Thus a key goal  in our design
+is restricting the impact of  data loss to a limited number of VMs. 
+It is not desirable that small scale of data failure affects the backup of many VMs.
+%when users access snapshots in a recovery process. 
+\end{itemize}
+
+%we want to isolate 
+%each VM's snapshot backup as much as possible while still enjoy the benefit of deduplication.
+%In large scale cloud, node faiures happen at daily basis, we don't want a problem at small scale
+%to affect large amount of VMs due to data sharing.
+%a key weakness of global content fingerprint comparison is that it affects fault isolation.
+
+%2) data sharing among users for accessing common signagutes causes the system less resilient to storage failures.
+%any loss of one piece of  shared data content hash and actualcontent will damange many VM snapshots, which can cause massive impacts
+%on reliability of many users.
+
+%Another point is that the previous work in signature-based comparison does not address
+%load balancing for a distributed environment during parallel access.  
+%Some content signatures can be extremely hot, but the machines  that  handle such signatures can become
+% a bottleneck. Uncoordinated signature assignment could lead to imbalanced access workload.
+
+%There are multiple choices of snapshot backup design for VM images and our considerations are described
+%as follows. 
+%Our design considerations
+%\begin{enumerate}
+%\item {\bf Centralized vs. decenalized} 
+%
+%It is desirable to have  a decentralized architecture.
+%Given a large amount of snapshot data communicated from each machine to the backup storage,
+%with a distributed storage architecture for backup, one could exploit  exploit data locality between
+%the source of data and storage location of data to reduce cross-platform bandwidth requirement for backup.
+
+%execute in parallel and easy to coordinate. In fact, we want to avoid cross-node dependency at scheduling VM snapshot operations, such that no global coordinator is necessary.
+%\item {Load balancing in resource consumption}: the cost of snapshot service shall be evenly distributed onto every node. We don't have a super powerful
+%or stable node that can accept extra responsibility.
+%\item {minimization of inter-user data dependency for fault tolerance}: we want to minimize the data dependency to a controllable level.
+Data deduplication means sharing of data, thus one failure at a single point may affect the snapshot service of hundreds of VMs, which is absolutely unacceptable.
+%\item {Resource usage modeling and control}.
+%\end{enumerate}
+
+With these considerations in mind, we propose a decentralized backup architecture with multi-level and selective 
+deduplication. This service is hosted   in the existing set of machines and resource usage is controlled
+with a minimal impact to the existing applications.
+The deduplication process is first conducted among snapshots within each VM
+and then is conducted across VMs.  
+Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
+and complicate failure management,
+we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
+For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
+Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance.
+%
+%in the  our studies show that there are a large amount of data unmodified in VM snapshots
+%and shared among many users (e.g. OS data). The sharing pattern follows a zip-like distribution.
+%With this characteristic, we can store a small amount of popular data items which coverage a large amount of
+%snapshot data blocks. 
+%We discuss our design and data analysis in the next section.
+
+%This method is based on the observation of two facts in Aliyun's VM cloud: first, VM's OS disks contain 
+%huge amount of operating system and software related data which is almost never modified during VM's life span. 
+%Second, the duplication pattern of user generated data follows Zipf-like law, thus a tiny set of hottest data
+%take up the majority of data duplication. As a result, if we extract these hot data as a common data set,
+%then most of data duplication will emerge by searching in this very small scope.
+
+%For example, In cloud storage, we are solving data deduplication problem in a different context of 
+%data stream deduplication (the D2D case): our snapshot storage service is co-located with runtime VMs,
+%thus we have very limited amount of system resource leave for data deduplication. For example,
+%in Aliyun's 8-core, 48GB memory, 12TB VM server, there lives over 20 VMs who are hungrily competing for
+%system resources: some may running map-reduce jobs, some may serving busy web requests, 
+%some may storing backend databases, any behavior that affects user VMs performance or stability is unacceptable.
+
+%To reduce the cost of deduplication, we must confine the scope of searching duplicates as much as possible,
+%thus some hints are needed to tell us where the most likely duplicates would hide. 
+%Several form of hints have been used in the past: many D2D systems exploits locality,
+%which bases on the fact that duplicates are likely to appear in the same sequence as they have arrived before.
+%Similarity is another popular hint, it suggests that two sets of data blocks may contain lots of
+%duplicates if they are indetified as similar by certain similarity detection measurements.
+
+%\section{Architecture design and Deduplication for Snapshot Support}
+%
+%\section{Popularity analysis}
+% data on what data popular.
+%
+%Analysis: modeling: singular
+%
+%Compute: Cache hit ratio vs. cache cost (memory cost).
+
+\comments{
 \section{Challenges}
@@
 balance out the benefits of deduplication.
+
+}

### 2013-05-28 snapshot_system/design1.tex
rev

@@
 \section{Prototype Design}
+
+The architecture of our snapshot backup service contains the following components:
+\begin{itemize}
+
+\item  The backup storage layer. 
+That stores snapshots on a distribued file system. 
+Our prototype implementtion uses the QFS.
+Since the distributed file system such as Hadoop and GFS takes the large block size such as 64MB,
+and the data blcok size for dueduplication is nonuniform with 4KB on average,
+we have added a layer to accmulate  data blocks from the deduplicated stream, and 
+package them as 64MB, and apply data compression when applicable.
+
+\item The deduplication layer.
+
+\end{itemize}
+
 Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China. 
@@
 
-\input{snapshot}
+%\input{snapshot}
 \input{append}

### 2013-05-28 snapshot_system/snapshot.tex
rev

@@
-\subsection{Snapshot Deduplication}
+\subsection{Snapshot Deduplication and Fault Isolation}
 \label{sect:dedupe}
 %snapshot representation
-\subsubsection{Snapshot Representation}
+
+\subsection{Inner and corss VM deduplication}
+
+Our  deduplication scheme compares the fingerprints of the current snapshot
+with its parent snapshot and also other snapshots in the entire cloud.
+This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
+Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
+Such localization increases data independency between different VM backups,
+simplifies snapshot management and statistics collection,
+and facilitates parallel execution of snapshot operations.
+On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
+As the result, different VMs tend to backup large amount of highly similar data.
+Our multi-level pipeline process can minimize 
+the cost of deduplication while maximize the its efficiency at each level,
+and it is parallel since each segment is processed independently.
+
+\begin{itemize}
+\item \textbf{Dirty-based corase-grain inner-VM deduplication.}
+The first-level deduplication is to follow the standand dirty bit approach, but is conducted
+in the coarse grain segment level.
+We use the  Xen virtual device driver which supports dirty bits for thestorage device
+and the dirty bit setting is maintained in a corase grain level we call it a segment.
+In our implementation, the segment size is 2MB. 
+Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
+and cannot affort a small segment  size.
+
+\item \textbf{Chunk-level fine-grain nearby duplicate detection.}
+
+The best deduplication uses a nonuniform chunk size 
+in the average of 4K or 8K~\cite{??}.
+Thus the second-level inner-VM deduplication is to assess in this
+level, but only for those dirty  segments. 
+We load the fingerprints of block chunks of the corresponding segment from the
+parent for a comparisons and compare near-by fingerprint matching within this segement.
+The amount of memory for maintaining those fingerprints  is small.
+For example, with a 2MB segment, there are about 500 fingerprints to compare.
+
+%If we use 4KB in level-1, then such a level-1 should have similar dedup efficiency 
+%as the current level-1 and level-2 combined, because finally they equal to comparing  
+%parent snapshot at 4KB granularity.
+%
+%However, at level-3 things are different.
+If we use 4KB fix-size block uniformly, it would be harder for different VM to share data through CDS, because there is no guarantee that the location of duplicate data on different VM disks are always aligned at 4KB boundary.
+For example, if two VMs each has a copy of duplicate data, but they are not aligned, then we won't be able to detect them.
+Our study at the current small data set has shown that using 4KB fix-size block will make CDS method less efficient by nearly 10%.
+Over the long time, more and more OS variations will co-exist in the cluster, making this 4KB fix-size approach inefficient in reducing duplicate data across VMs.
+
+%\item \textit{Level 2  Chunk fingerprint comparison.}
+%If a segment is modified, we perform fine-grained deduplication 
+%by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
+%thus eliminate partial data duplication within the segment.
+%\end{itemize}
+%
+%In general, operations at level 1 have almost no cost and most of unmodified data are filtered here. 
+%To process a dirty segment at level 2, 
+%there requires no more than one DFS access to load the segment recipe from previous snapshot,
+%and a tiny amount of memory to hold it in main memory.
+
+\item \textbf{Cross-VM deduplication.}
+This step accomplishes the standand global fingerprint  comparison as conducted
+in the previous work~\cite{??}.
+One key observation is that the inner deduplication has removed many of duplicates.
+There are not lot of deduplication opportunities cross VMs while the memory
+consumption for global comparison is expensive.
+Thus our approximation is that duplicate sharing patterns among  VM follows
+a zip-like distribution, and the global fingerprint  comparison  only searches
+for the most popular items. 
+\end{itemize}
+
+\subsection{Popular Chunk Management and VM-oriented Fault Isolation}
+
+Our objective for fault isolation is to minimize the number of VMs affected when there are failures
+in the cluster.  The inner-VM deduplication does not depend on any global service and the comparison
+for each VM is localized within the parent and the current snapshot.
+Thus there is no data dependence between VMs.
+For cross-VM deduplication, there is a data dependence among VMs and we would minimize the faiulre impact
+of shared blocks by adding extra replcas of those shared blocks.
+
+{\bf Snapshot Representation}.
 The virtual device driver uses a bitmap to track the changes 
@@
 An additional flag indicates
-
-\subsubsection{Multi-level Deduplication}
-The multi-level deduplication scheme is designed base on the observations on the VM snapshot data from production cloud.
-We found snapshot data duplication can be easily classified into two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
-Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
-On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL. 
-As the result, different VMs tend to backup large amount of highly similar data.
-Our multi-level pipeline process can minimize the cost of deduplication while maximize the its efficiency at each level,
-and it is highly parallelizable since each segment is processed independently.
-
-\textbf{Inner-VM Deduplication.}
-The first-level deduplication is logically localized within each VM.
-Such localization increases data independency between different VM backups,
-simplifies snapshot management and statistics collection,
-and facilitates parallel execution of snapshot operations.
-
-Inner VM deduplication contains two levels of duplicate detection efforts:
-\begin{itemize}
-\item \textit{Level 1 Segment modification detection}.
-If a segment is not changed, then its segment recipe can be simply reused by copying the data
-reference from previous snapshot recipe. 
-\item \textit{Level 2  Chunk fingerprint comparison.}
-If a segment is modified, we perform fine-grained deduplication 
-by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
-thus eliminate partial data duplication within the segment.
-\end{itemize}
-
-In general, operations at level 1 have almost no cost and most of unmodified data are filtered here. 
-To process a dirty segment at level 2, 
-there requires no more than one DFS access to load the segment recipe from previous snapshot,
-and a tiny amount of memory to hold it in main memory.
-\textit{may need details here}
-
-\textbf{Cross-VM Deduplication.}
-
-\subsection{Common Data Set}

### 2013-05-28 snapshot_system/design1.tex
ew

@@
 \section{Prototype Design}
+
+{\bf Snapshot Representation}.
+The virtual device driver uses a bitmap to track the changes 
+that have been made to virtual disk.
+Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
+is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
+file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
+Moreover, we break 
+segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
+which brings the opportunity of fine-grained deduplication by
+allowing data sharing between segments.
+
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=images/snapshot_representation.eps, width=3.7in}
+  \caption{An example of snapshot representation.}
+  \label{fig:snapshot}
+\end{figure}
+As a result, the representation of each snapshot is designed as a two-level index data structure 
+in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
+A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
+that holds the meatdata of its chunks. We choose this two-level structure because in practice we
+observe that during each backup period only a small amount of VM data are added or modified. 
+As the result, even the metadata of two snapshots can be highly similar, 
+thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
+Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
+segments which greatly ease the segment-level deduplication.
+
+In both two kind of recipes, 
+they do not include the actual data but only have
+ references point to the data which are either stored in append store or CDS.
+In our implementation the data reference is a 8 bytes field which is either an 
+ASID (discuss in \ref{sect:append} or an offset of 
+An additional flag indicates
 

### 2013-05-28 snapshot_system/snapshot.tex
ew

@@
 
-{\bf Snapshot Representation}.
-The virtual device driver uses a bitmap to track the changes 
-that have been made to virtual disk.
-Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
-is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
-file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
-Moreover, we break 
-segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
-which brings the opportunity of fine-grained deduplication by
-allowing data sharing between segments.
+This section analyzes the choice of popular blocks and its impact on the deduplication efficiency.
+It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
+global deduplication.
 
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=images/snapshot_representation.eps, width=3.7in}
-  \caption{An example of snapshot representation.}
-  \label{fig:snapshot}
-\end{figure}
-As a result, the representation of each snapshot is designed as a two-level index data structure 
-in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
-A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
-that holds the meatdata of its chunks. We choose this two-level structure because in practice we
-observe that during each backup period only a small amount of VM data are added or modified. 
-As the result, even the metadata of two snapshots can be highly similar, 
-thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
-Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
-segments which greatly ease the segment-level deduplication.
+{\bf Impact of CDS deduplication.}
+Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the
+frequency of data duplication follows Zipf-like distribution\cite{zipf},
+with the exponent $\alpha$ between 0.65 ~ 0.70.
+As a result, it can be proved that deduplication efficiency of CDS index is scalable:
 
-In both two kind of recipes, 
-they do not include the actual data but only have
- references point to the data which are either stored in append store or CDS.
-In our implementation the data reference is a 8 bytes field which is either an 
-ASID (discuss in \ref{sect:append} or an offset of 
-An additional flag indicates
+[Describe the dedup efficiency model in detail]
+Let $S_c$ be the total number of FPs in CDS, $S_g$ be the total number of FPs in global index, $F$ be the size of a FP, $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size.
+The deduplication efficiency will be:
+\begin{equation}
+  E = (S_c / S_g)^{1-\alpha}
+\end{equation}
+The $S_c$ and $S_g$ can be expressed as:
+\begin{equation}
+S_c = N*m/F, S_g = N*D/B
+\end{equation}
+By replacing $S_c$ and $S_g$ in the first formula, we have:
+\begin{equation}
+  E = (\frac{m*B}{F*D})^{1-\alpha}
+\end{equation}
+
+Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.
+
+{\bf Fault resilence.}

### 2013-05-28 snapshot_system/failover.tex
analysis

\subsection{Fault Analysis }

We  compare the impact of losing $d$ machines using the following two approaches:
\begin{itemize}
\item The VM-centric approach (VC).  The replication degree of the backup storage 
is $r$ for regular content blocks and $r_c$ for CDS blocks where $r_c>r$. 
\item The VM-oblivious (VO) approach.
All chunk  blocks are treated uniformly and global comparison is conducted.
\end{itemize}

When $d<r$, there is no loss of data in the snapshot storage.
When $d \ge r$, some of data blocks in the storage are loss, and we compute the number of VMs that could
suffer the loss of their snapshots.
We use the following parameters  during the analysis
\begin{itemize}
\item 	$V$ is the number of VMs. $m$ is the number of physical machines hosting the bakcup storage.
$d$ is the number of machines failed.
\item In the VC approach, $s_c$  of them in the backup storage
are shared by others with a zipf distribution. $(1-s_c)$ 
of them  is unique (nobody shares with them).
$L_c$ is the average number of VMs sharing a block (if it is in CDS for the VC approach.
$b_c$ is the number of shared blocks in VC.
\item In the VO approach, $s_o$ is the number of blocks shared.
$L_o$ is the average number of VMs sharing a block. 
\item $b$ is the  number of blocks stored in the storage after deduplication.
 \end{itemize}

The distribution of data blocks shared among VMs in VC follows a zipf distribution.
Given a VM block, the probability of being rank $x$ block is $P(x) = P(1) * x^{-\alpha}$
where $P(1)$ is the probability of being rank 1 most popular block.
Since $\sum P(x)= 1$, $P(1)= \frac{1}{\sum_1^{b_c} x^{-\alpha} }$.
Let $y$ be the number of VMs sharing rank $x$ block in VC, and  then  $y= V* P(x)$.

Thus the average number of VMs sharing a data block in the VC backup storage is:
\begin{equation}
%\begin{align}
\begin{split}
L_c& =  (1-s_c)*1 + s_c \sum_1^{b_c} P(x) * y \\
& =  (1-s_c)*1 + s_c \sum P(1)^2 *  x^{-2\alpha} *  V.
\end{split}
%\end{align}
\end{equation}

We can build a bipartite graph representing the association from unique data blocks
to their corresponding VMs. An association edge is  drawn  from a data block  to a VM 
if this block is used by this VM, 
The average incoming degree of VM nodes is equal to
the average outgoing degree of data blocks, which is $L_c$.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{shared.pdf}
\caption{Assoication of data blocks to VMs.}
\label{fig:shared}
\end{figure}

Under $d$ failed machines, the  expected number of VMs 
which suffer from data loss in VC is
\begin{multline}
%\begin{split}
 \sum_{1}^{V}  ( Probability (\mbox{ a VM fails)}) \\
= \sum_{1}^{V}  ( 1- Probability (\mbox{ a VM has no data loss)}) \\
= V ( 1-  Probability(\mbox{ A block has no data loss} )^{L_c} ).
%\end{split}
\end{multline}

\comments{
Prob(i-th block shared by (V-i+1) machines = X/i.
b
Sum (X/i) =1.      Thus       X= 1/ ln (V).
Length of sharing=  Probality(this block is shared with 1 VM) 1 + Probablity(this block shared by 2 VM) 2+..] =  X *V +X*(V-1)/2+ X*(V-2)/3 +..
=  X * sum (V-i+1)/I   for I from 1 to V.
=  (V+1) sum (X/i) . Sum(X) =  (V+1) -  X*V= V(1- 1/lnV) +1.
}

%Thus the number of VMs using a block =    $(1-s_c)  + s_c *L$.

When there are $d$ machines failed and the probability of
a block failure depends on if all replicas of this block reside in the failed machines.
When $r< d <r_c$,  only unshared data blocks can fail in VC. Then
%Probablity(\mbox { no loss for this  block}) = 1 - Probability (\mbox{ this block in d failed machiens})
\begin{multline}
%\begin{split}
Probability(\mbox{ A block has data loss})\\
= (1-s_c) (1- Probability (\mbox{ this block in d failed machines}))\\
= (1-s_c) (1- \frac{ \binom{d}{r}} { \binom{m}{r} }).
%\end{split}
\end{multline}
When $r_c \leq d$, shared data blocks in VC can have a loss. 
\[
Probability(\mbox{A block has data loss})
= 
(1-s_c) (1- \frac{ \binom{d}{r}} { \binom{m}{r} })
+ s_c (1- \frac{ \binom{r_c}{d}} { \binom{m}{r_c} }).
\]

By comparison, under $d$ failed machines, the  expected number of VMs 
which suffer from data loss in VO is
\[
V ( 1-  (1- \frac{ \binom{d}{r}} { \binom{m}{r} })^{L_o} ).
\]
where
\[
L_o = (1-s_o) + s_o \sum_1^b  P(1)^2 *  (x')^{-2\alpha'} *V.  
\]

\comments{
	=  sum _for_all_block(   Probablity (a block fails) *number of VM sharing this block ))
               = Probability(a block fails) * sum_for_all_blocks (numb of VM shared)
	= Probablity (a block fails) *b *aveageLengthVM
	= [ 1-  C(r, k) /C(n,r)] * b* [ 1+ s *V(1-1/ln V)]

----------------------------------------------------------------------

For CDS model, 85% blocks are using the data from the same VM while upto 10% data is for CDS (we actually only use 5% perhaps).  Thus the overall speaking, at most 10% of data are shared.
Thus  for CDS approach,   the # VM failure caused by k machines is at most  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.10 *V(1-1/ln V)].
For original approach,  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.90 *V(1-1/ln V)].
For large V, the reliability improves by 9 times.
}

### 2013-05-28 snapshot_system/snapshot.tex
analysis

@@
 \subsection{Popular Chunk Management and VM-oriented Fault Isolation}
-
 Our objective for fault isolation is to minimize the number of VMs affected when there are failures
@@
 Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.
-
-{\bf Fault resilence.}

### 2013-05-28 snapshot_system/arch.tex
add architecture

\section{Design Overview}
%[describe what is going to be presented in this section]
We start by analyzing the main features in the design of our system.
We first present its architecture,
then introduce the two major contributions: the colocated deduplication 
scheme and the snapshot deletion strategy.
\subsection{Architecture}
%[describe the cloud environment]
Our architecture, as shown in figure.\ref{fig:arch}, is built on top of 
Alibaba's platform which is the largest cloud service provider in China. 
A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of xen-based\cite{Barham2003} VMs.
Alibaba's cloud platform provides a hadoop-like infrastructure, 
which includes several highly scalable distributed service:
\begin{description}
\item[Distributed file system] This is a scalable distributed file system (DFS) being optimized for many large and sequential reads or appends. DFS holds the responsibility of managing physical disk storage
in the cloud. All data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
%\item[KV]: a distributed key-value store for managing structured data.
%\item[MapReduce]: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
\item[Distributed memory cache]: A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inqueries. 
\end{description}
In addition, our implementation also uses MapReduce to facilitate the offline
data processing, and stores a small amount of snapshot metadata in a 
BigTable-like persistent key-value store.

%[describe the benefits of using mature cloud technologies]
In general, our snapshot system and the virtual machine management service 
rely on these fundamental cloud services
to be functional. Such a colocated deduplication architecture allow us 
to enjoy the benefits from these mature technologies 
such as load balancing, scalability, and fault tolerancy.
Moreover, all the above cloud services can easily find their open-source counterparts,
which improves the generality of our architecture and deduplication scheme.

{\bf Snapshot Representation}
The virtual device driver uses a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit 
in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break 
segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/snapshot_representation.pdf, width=3.7in}
  \caption{An example of snapshot representation.}
  \label{fig:snapshot_rep}
\end{figure}
As a result, the representation of each snapshot is designed as a two-level index data structure 
in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot_rep}.
A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
that holds the meatdata of its chunks. We choose this two-level structure because in practice we
observe that during each backup period only a small amount of VM data are added or modified. 
As the result, even the metadata of two snapshots can be highly similar, 
thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
segments which greatly ease the segment-level deduplication.

In both two kind of recipes, 
they do not include the actual data but only have
 references point to the data which are either stored in append store or CDS.
In our implementation the data reference is a 8 bytes field which is either an 
ASID (discuss in \ref{sect:append}) or an offset of an additional flag indicates
the location of CDS data.

\begin{figure}
    \centering
    \subfigure[Node architecture from VM point of view]
    {
        \includegraphics[width=3in]{images/socc_arch_vm.pdf}
        \label{fig:arch_vm}
    }
    \\
    \subfigure[Cluster architecture]
    {
        \includegraphics[width=3in]{images/socc_arch_cluster.pdf}
        \label{fig:arch_cluster}
    }
    \caption{System architecture}
    \label{fig:arch}
\end{figure}

%[describe the architecture frm node side]
{\bf Node Architecuture} 
Our node-side architecture, depicted in figure.\ref{fig:arch_vm}, consists of
two main entities: a virtual block device driver, and a snapshot deduplication component.

%[brief the virtual device driver]
One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
This driver maintains a map of dirty-bits to record
the change status of every fix-size segment of the virtual disk. 
When the VM issue a disk write, the bits coresponding to the segments that covers 
the modified disk region are set, thus letting snapshot deduplication component knows these
segments must be checked during snapshot backup. After the snapshot backup is finished, 
snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
a clean state.

%[brief the snapshot deduplication]
The snapshot deduplication component consists of the chunking and deduplication 
logic of our snapshot storage system. We choose

It contains an append store client which provides facilities to manage stored snapshot data, and a CDS client to support CDS index access. We will further discuss our deduplication scheme in section\ref{sec:dedup}.

%[describe the arch from cluster side]
{\bf Cluster Architecture}

%[describe the data structure in underlying storage]
{\bf Append Store}
Append Store (AS) is our underlining storage engine for storing snapshot data after deduplication. 
AS is built on top of our highly scalable distributed file system (DFS), 
which is very similar to Google's file system
in a sense that it is optimized for large files and sequential read/append operations.

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/append_store_arch.pdf, width=3.5in}
  \caption{Architecture of Append Store}
  \label{fig:as_arch}
\end{figure}

Append Store supplies three interfaces: {\em get(ref)} accepts a data reference and retrives data, 
{\em put(data)} accepts data and returns a reference to be stored in metadata recipes, 
{\em delete(ref)} 
deletes the data pointed by the reference.
Under the hood, small var-sized data are grouped and stored into larger data containers. Each VM has
its snapshot data stored in its own Append Store, specified by the VM ID. 
We split every Append Store into multiple data containers so that reclaiming the disk space would not 
result in rewriting all the data at the same time.

As shown in Fig.\ref{fig:as_arch}, every data container is represented as three data files in DFS:
the data file holds all the actual data, the index file is responsible for translating data reference
into data locations, and a deletion log file remembers all the deletion requests to the container.

A data reference is composed of two parts: a container ID (2 bytes) and CID (6 bytes).
Append Store assign every piece of data a CID for its internal data referencing. 
When new data is appended, its CID is the current largest CID in that container plus one.
As a result, all the data locations are naturally indexed by this self-incremental CID, 
no extra sorting is needed.

Append Store groups multiple chunk data (i.e., 100) into larger units, called {\em CBlock}.
CBlock is the basic unit for append store's internal read/write/compression.
There is one index entry in the container index corresponding to every CBlock. It keeps the first chunk's CID
in that CBlock, and the CBlock data's size and location.

Using CBlock brings us several advantages: First, the write workload to DFS master is greatly reduced; second, grouping
small chunks gives better compression. Third, reading a CBlock (200 - 600 KB) typically cost the same amount of disk 
seek as reading a 4KB chunk. Finally, this greatly reduces the size of index. Let $m$ be the number of chunks in each
CBlock, then the overall index size is reduced to $1/m$. In our implementation, using $m=100$ reduces the index for
a 1GB container from 10 MB to 100 KB.

In order to read a chunk data by reference, Append Store client first loads the
container index file specified by the container ID, then search the CBlock index to find the entry that covers the chunk by CID.
After that, it reads the whole CBlock data from DFS, decompress it, seek the exact chunk data specified by CID. 
Finally, the client updates itws internal chunk data cache with the newly loaded contents to anticipate future sequential reads.

Write requests to append store are accumlated. When the number reaches $m$, the AS client forms a CBlock by assigning 
every chunk a CID, compress the CBlock data, and append it to the CBlock data file. Then a new CBlock index entry is appended
to CBlock index.

Append store adopts lazy delete strategy. The deletion requests are appended into every container's deletion log file with the CID of data to be deleted.
CIDs in deletion log are guaranteed to be referenced by nobody and can be safe deleted in future. 
Periodically, snapshot management system asks append store to compact containers in order to reclaim disk space. 
The actual compaction will only take place when the number of deleted items reached $d\%$ of container's capacity. 
During compaction, append store creates a new container (with the same container ID) to replace the 
existing one. This is done by sequentially scan the old container, copying all the chunks that are not 
found in deletion log to the new container, creating new CBlocks and indices. 
However, every chunk's CID is plainly copied rather than re-generated. This does not affect the sorted
order of CIDs in new container, but just leaving holes in CID values. As the result, all data references stored 
in upper level recipes are unaffected, and the data reading process is as efficient as before.

\subsection{Snapshot Deduplication and Fault Isolation}
\label{sect:dedupe}
%snapshot representation
%\subsection{Inner and corss VM deduplication}
Our  deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
Such localization increases data independency between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize 
the cost of deduplication while maximize the its efficiency at each level,
and it is parallel since each segment is processed independently.

\begin{itemize}
\item \textbf{Dirty-based corase-grain inner-VM deduplication.}
The first-level deduplication is to follow the standand dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports dirty bits for thestorage device
and the dirty bit setting is maintained in a corase grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
and cannot affort a small segment  size.

\item \textbf{Chunk-level fine-grain nearby duplicate detection.}

The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}.
Thus the second-level inner-VM deduplication is to assess in this
level, but only for those dirty  segments. 
We load the fingerprints of block chunks of the corresponding segment from the
parent for a comparisons and compare near-by fingerprint matching within this segement.
The amount of memory for maintaining those fingerprints  is small.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

%If we use 4KB in level-1, then such a level-1 should have similar dedup efficiency 
%as the current level-1 and level-2 combined, because finally they equal to comparing  
%parent snapshot at 4KB granularity.
%
%However, at level-3 things are different. If we use 4KB fix-size block uniformly, it would be harder for different VM to share data through CDS, because there is no guarantee that the location of duplicate data on different VM disks are always aligned at 4KB boundary. For example, if two VMs each has a copy of duplicate data, but they are not aligned, then we won't be able to detect them. Our study at the current small data set has shown that using 4KB fix-size block will make CDS method less efficient by nearly 10%. Over the long time, more and more OS variations will co-exist in the cluster, making this 4KB fix-size approach inefficient in reducing duplicate data across VMs.

%\item \textit{Level 2  Chunk fingerprint comparison.}
%If a segment is modified, we perform fine-grained deduplication 
%by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
%thus eliminate partial data duplication within the segment.
%\end{itemize}
%
%In general, operations at level 1 have almost no cost and most of unmodified data are filtered here. 
%To process a dirty segment at level 2, 
%there requires no more than one DFS access to load the segment recipe from previous snapshot,
%and a tiny amount of memory to hold it in main memory.

\item \textbf{Cross-VM deduplication.}
This step accomplishes the standand global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of duplicates.
There are not lot of deduplication opportunities cross VMs while the memory
consumption for global comparison is expensive.
Thus our approximation is that duplicate sharing patterns among  VM follows
a zip-like distribution, and the global fingerprint  comparison  only searches
for the most popular items. 
\end{itemize}

{\bf Popular Chunk Management and VM-oriented Fault Isolation}
Our objective for fault isolation is to minimize the number of VMs affected when there are failures
in the cluster.  The inner-VM deduplication does not depend on any global service and the comparison
for each VM is localized within the parent and the current snapshot.
Thus there is no data dependence between VMs.
For cross-VM deduplication, there is a data dependence among VMs and we would minimize the faiulre impact
of shared blocks by adding extra replcas of those shared blocks.

This section analyzes the choice of popular blocks and its impact on the deduplication efficiency.
It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
global deduplication.

{\bf Impact of CDS deduplication.}
Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the
frequency of data duplication follows Zipf-like distribution\cite{zipf},
with the exponent $\alpha$ between 0.65 ~ 0.70.
As a result, it can be proved that deduplication efficiency of CDS index is scalable:

For the Zipf-like distribution, an approximation to the sum of the first $n$ 
elements of the distribution can be derived as follows:
\begin{equation}
\sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
\end{equation}

So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
of global index with size $S_g$ is:

\begin{equation}
  E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
\end{equation}

%[Describe the dedup efficiency model in detail]
Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size. Then $S_c$ and $S_g$ can be expressed as:
\begin{equation}
S_c = N*m/F, S_g = N*D/B
\end{equation}

By replacing $S_c$ and $S_g$ in the first formula, the deduplication efficiency becomes:
\begin{equation}
  E = (\frac{m*B}{F*D})^{1-\alpha}
\end{equation}

Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.

\subsection{Snapshot Summaries for Deletion}

### 2013-05-28 snapshot_system/impl.tex
add architecture

--- 2012-12-20 snapshot_system/delete.tex
@@
-\section{Deletion}
+\section{Implementation}
+\subsection{Snapshot Backup}
+\subsection{Snapshot Read}
+\subsection{Snapshot Deletion}
 In a mature VM cluster, snapshot deletions are as frequent as snapshot creations.
@@
 
-% \subsection{Challenges}
-% Contrary to a traditional backup system, a dedupe system shares data among files by default. 
-% Reference management is necessary to keep track of chunk usage and reclaim freed space. 
-% In addition to scalability and speed, reliability is another challenge for reference management. 
-% If a chunk gets freed while it is still referenced by snapshots, data loss occurs and files cannot be restored. 
-% On the other hand, if a chunk is referenced when it is actually no longer in use, it causes storage leakage.
-
-% Reference counting, while being simple, suffers from low reliability especially in our distributed environment, 
-% because it is vulnerable to lost or repeated updates: when errors occur some chunks maybe updated and some may not. 
-% Complicated transaction rollback logic is required to make reference counts consistent. Moreover, 
-% there is almost no way to verify if the reference count is correct or not in a large dynamic system. 
-% In real deployments, where data integrity and recoverability directly affect product reputation, simple reference counting is unsatisfactory.
-
-% Mark-and-sweep is generally a better solution. During the mark phase, all snapshot recipes are traversed so as to mark the used chunks. 
-% In the sweep phase all chunks are swept and unmarked chunks are reclaimed. 
-% This approach is very resilient to errors: at any time the process can simply be restarted with no negative side effects. 
-% Scalability, however, is an issue. {\em needs to explain its resource usage}
-
-\subsection{Approximate Deletion}
+{\bf Approximate Deletion}
 We design approximate deletion to fast identify unused data in the append store.
@@
 
-\subsection{Accurate Deletion}
+{\bf Append Store Cleanup}
 Our accurate deletion uses mark-and-sweep to find all the unused chunks in a VM's append store.
@@
 it's infeasible to run accurate deletion as frequent as snapshot deletions.
-
-\subsection{Discussion}

### 2013-05-28 snapshot_system/design1.tex
add architecture
change

--- 2013-05-28 snapshot_system/design1.tex
@@
-\section{Prototype Design}
+\section{Architecture Design}
+
+%\subsection{ Snapshot management}
+The virtual device driver uses a bitmap to track the changes that have been made to virtual disk.
+Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
+is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
+file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
+Moreover, we break segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
+which brings the opportunity of fine-grained deduplication by
+allowing data sharing between segments.
+The representation of each snapshot has  a two-level index data structure. 
+%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
+The snapshot meta data (called snapshot receipe) contains a list of segments, each of which contains segment 
+meatdata of its chunks (called segment receipe).
+
+%\begin{figure}[htbp]
+%  \centering
+%  \epsfig{file=images/snapshot_representation.eps, width=3.7in}
+%  \caption{An example of snapshot representation.}
+%  \label{fig:snapshot}
+%\end{figure}
+%We choose this two-level structure because in practice we
+%observe that during each backup period only a small amount of VM data are added or modified. 
+%As the result, even the metadata of two snapshots can be highly similar, 
+%thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
+%Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
+%segments which greatly ease the segment-level deduplication.
+
+In both two kind of recipes, 
+they do not include the actual data but only have
+ references pointers to the data which are either stored in backup storage or CDS.
+In our implementation the data reference is a 8 bytes field which is either an 
+ASID (discuss in \ref{sect:append} or an offset of 
+An additional flag indicates
 

### 2013-05-28 snapshot_system/intro.tex
change

@@
 
-The paper proposes an integrated approach which uses  multiple duplicate detection strategies
-integrating  version  detection, small-scope inner VM duplicate comparison
+The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
+based on  version  detection, small-scope inner VM duplicate comparison
 and controlled cross-VM comparison. 
-The key idea of this approach is to localize duplicate detection within each virtual machine as much as possible
+This approach is VM centric by localizing duplicate detection within each VM  as much as possible
 and minimize memory usage while delivering a decent deduplication efficiency. 
@@
 Our deletion strategy uses a double Boomer filer strategy for periodic mark-and-sweeping of expired data blocks.
-We have developed a prototype system that runs a cluster of Linux machines running Zen.
-The backup storage uses a standard distributed file system  with data replication and
-we allocate more  replicas for the commonly-shared  data blocks among VM snapshots to enhance fault tolerance.
+We have developed a prototype system that runs a cluster of Linux machines with Xen.
+The backup storage uses a standard distributed file system  with data replication and block packaging,
+and we allocate more  replicas for the commonly-shared  data blocks among VM snapshots to enhance fault tolerance.
 

### 2013-05-28 snapshot_system/main.tex
Append store chapter
add pdf
paper update
chnge
Add cds analysiswq
some changes
rev
analysis
add architecture
change

@@
 \usepackage{epsfig}
+\usepackage{breqn}
+
+\newcommand{\comments}[1]{}
 
@@
 
-\title{An In-Cloud Backup System With Deduplication for VM Snapshot}
+%\title{Deduplication Localization for Virtual Machine Snapshot Backup}
+\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup}
+%\title{BigArchive: Low-cost and Scalable Deduplication Storage for VM Snapshot}
 
-\numberofauthors{7}
 \author{
-\alignauthor Wei Zhang\\
-       \affaddr{CS Dept.}\\
-       \affaddr{UC Santa Barbara}\\
-       \email{wei@cs.ucsb.edu}
-\alignauthor Hong Tang\\
-       \affaddr{Aliyun Inc.}\\
-       \affaddr{Alibaba Group}\\
-       \email{hongtang@alibaba-inc.com}
-\alignauthor Tao Yang\\
-       \affaddr{CS Dept.}\\
-       \affaddr{UC Santa Barbara}\\
-       \email{tyang@cs.ucsb.edu}
+Wei Zhang, Michael Agun,  Tao Yang \\
+%Wei Zhang$^{\star}$, Michael Agun,  Tao Yang$^\star$
+%{\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
+%Wei Zhang, Tao Yang, Gautham Narayanasamy\\
+Department of Computer Science\\
+University of California,  Santa Barbara, CA 93106
+%\and
+%Hong Tang\\
+%Alibaba Inc.
 }
+%, Gautham Narayanasamy$^\star$, and Hong Tang$^\dagger$ \\
 
@@
 % A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
+%\category{H.4}{Information Systems Applications}{Miscellaneous}
 %A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
 
-\terms{Theory}
+%\terms{Theory}
 
-\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+%\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
 
 \input{intro}
-\input{design}
+%\input{design}
+\input{background}
+\input{challenge}
 \input{snapshot}
-\input{append}
+\input{failover}
+\input{design1}
+%\input{snapshot}
+%\input{append}\
 \input{cds}
-\input{failover}
+%\input{delete}
+%\input{failover}
 \input{result}

### 2013-05-28 snapshot_system/snapshot.tex
change

@@
-\subsection{Snapshot Deduplication and Fault Isolation}
+\section{Snapshot Deduplication and Fault Isolation}
 \label{sect:dedupe}
@@
 
-\subsection{Inner and corss VM deduplication}
+%We use the The deduplication process is first conducted among snapshots within each VM
+%and then is conducted across VMs.
+%Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
+%and complicate failure management,
+%we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
+%For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
+%Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance
 
@@
 This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
-Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
-Such localization increases data independency between different VM backups,
+We discuss the integration of several strategies as follows and analyze its effectiveness.
+
+\subsection{Inner and corss VM deduplication}
+
+Inner-VM duplication can be effecive within  VM's snapshots because the majority of data are unchanged during each backup period. 
+Localizing the snapshot data deduplication witin  a VM first
+increases data independency between different VM backups,
 simplifies snapshot management and statistics collection,
 and facilitates parallel execution of snapshot operations.
-On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
+On the other hand, cross-VM duplication can also be desirable mainly due to widely-used software and libraries. 
 As the result, different VMs tend to backup large amount of highly similar data.
-Our multi-level pipeline process can minimize 
-the cost of deduplication while maximize the its efficiency at each level,
-and it is parallel since each segment is processed independently.
+We integrate those strategies together as follows.
+%Our multi-level pipeline process can minimize 
+%the cost of deduplication while maximize the its efficiency at each level,
+%and it is parallel since each segment is processed independently.
 
 \begin{itemize}
-\item \textbf{Dirty-based corase-grain inner-VM deduplication.}
+\item \textbf{Dirtybit-based corase-grain inner-VM deduplication.}
 The first-level deduplication is to follow the standand dirty bit approach, but is conducted
@@
 consumption for global comparison is expensive.
-Thus our approximation is that duplicate sharing patterns among  VM follows
-a zip-like distribution, and the global fingerprint  comparison  only searches
-for the most popular items. 
+Thus our approximation is that the global fingerprint  comparison  only searches for the most popular items. 
+%Since duplicate sharing patterns among  VM follows a zip-like distribution,  
 \end{itemize}
@@
 
-{\bf Impact of CDS deduplication.}
+\subsubsection{Impact of CDS deduplication}
 Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the

### 2013-05-29 snapshot_system/arch.tex
update arch

@@
 \section{Design Overview}
+\label{sect:design}
 %[describe what is going to be presented in this section]
@@
 scheme and the snapshot deletion strategy.
+
+\begin{figure}
+    \centering
+    \subfigure[Cluster architecture]
+    {
+        \includegraphics[width=3in]{images/socc_arch_cluster.pdf}
+        \label{fig:arch_cluster}
+    }
+    \\
+    \subfigure[Node architecture from VM point of view]
+    {
+        \includegraphics[width=3in]{images/socc_arch_vm.pdf}
+        \label{fig:arch_vm}
+    }
+    \caption{System architecture}
+    \label{fig:arch}
+\end{figure}
+
 \subsection{Architecture}
+\label{sect:arch}
 %[describe the cloud environment]
@@
 Alibaba's platform which is the largest cloud service provider in China.
+
+%[describe the arch from cluster side]
+{\bf Cluster Architecture}
 A typical VM cluster in our cloud environment
@@
 which includes several highly scalable distributed service:
-\begin{description}
-\item[Distributed file system] This is a scalable distributed file system (DFS) being optimized for many large and sequential reads or appends.
+\begin{enumerate}
+\item {\bf Distributed file system} This is a scalable distributed file system (DFS) being optimized for many large and sequential reads or appends.
 DFS holds the responsibility of managing physical disk storage
@@
 %\item[MapReduce]: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
-\item[Distributed memory cache]: A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inqueries. 
-\end{description}
+\item {\bf Distributed memory cache} A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inqueries. 
+\end{enumerate}
 In addition, our implementation also uses MapReduce to facilitate the offline
@@
 which improves the generality of our architecture and deduplication scheme.
+
+%[describe the architecture frm node side]
+{\bf Node Architecuture} 
+Our node-side architecture, depicted in figure.\ref{fig:arch_vm}, consists of
+two main entities: a virtual block device driver, and snapshot deduplication component.
+
+%[brief the virtual device driver]
+In Alibaba's VM cloud, every VM access its virtual machine disk image through the
+virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
+This driver maintains a map of dirty-bits to record
+the change status of every fix-size segment of the virtual disk. 
+When the VM issue a disk write, the bits coresponding to the segments that covers 
+the modified disk region are set, thus letting snapshot deduplication component knows these
+segments must be checked during snapshot backup. After the snapshot backup is finished, 
+snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
+a clean state.
+
+%[brief the snapshot deduplication]
+The snapshot deduplication component consists of the chunking and deduplication 
+logic of our snapshot storage system. We choose
+
+It contains an append store client which provides facilities to manage stored snapshot data, and a CDS client to support CDS index access.
+We will further discuss our deduplication scheme in section\ref{sect:dedupe}.
 
@@
   \centering
-  \epsfig{file=images/snapshot_representation.pdf, width=3.7in}
+  \epsfig{file=images/snapshot_representation.pdf, width=3in}
   \caption{An example of snapshot representation.}
@@
 
-\begin{figure}
-    \centering
-    \subfigure[Node architecture from VM point of view]
-    {
-        \includegraphics[width=3in]{images/socc_arch_vm.pdf}
-        \label{fig:arch_vm}
-    }
-    \\
-    \subfigure[Cluster architecture]
-    {
-        \includegraphics[width=3in]{images/socc_arch_cluster.pdf}
-        \label{fig:arch_cluster}
-    }
-    \caption{System architecture}
-    \label{fig:arch}
-\end{figure}
-
-%[describe the architecture frm node side]
-{\bf Node Architecuture} 
-Our node-side architecture, depicted in figure.\ref{fig:arch_vm}, consists of
-two main entities: a virtual block device driver, and a snapshot deduplication component.
-
-%[brief the virtual device driver]
-One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
-virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
-This driver maintains a map of dirty-bits to record
-the change status of every fix-size segment of the virtual disk. 
-When the VM issue a disk write, the bits coresponding to the segments that covers 
-the modified disk region are set, thus letting snapshot deduplication component knows these
-segments must be checked during snapshot backup. After the snapshot backup is finished, 
-snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
-a clean state.
-
-%[brief the snapshot deduplication]
-The snapshot deduplication component consists of the chunking and deduplication 
-logic of our snapshot storage system. We choose
-
-It contains an append store client which provides facilities to manage stored snapshot data, and a CDS client to support CDS index access.
-We will further discuss our deduplication scheme in section\ref{sec:dedup}.
-
-%[describe the arch from cluster side]
-{\bf Cluster Architecture}
-
 %[describe the data structure in underlying storage]
@@
   \centering
-  \epsfig{file=images/append_store_arch.pdf, width=3.5in}
+  \epsfig{file=images/append_store_arch.pdf, width=3in}
   \caption{Architecture of Append Store}
@@
 \end{equation}
-
 So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
 of global index with size $S_g$ is:
-
 \begin{equation}
@@
 \end{equation}
-
 %[Describe the dedup efficiency model in detail]
@@
 \end{equation}
-
 By replacing $S_c$ and $S_g$ in the first formula, the deduplication efficiency becomes:
@@
 \end{equation}
-
 Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.
 
-\subsection{Snapshot Summaries for Deletion}
+\subsection{Snapshot Summaries for Approximate Deletion}
+In a mature VM cluster, snapshot deletions are as frequent as snapshot creations.
+Our system adopts lazy delete strategy so that all snapshot deletions are scheduled
+in the backup time window at midnight. 
+Therefore, snapshot deletions must be fast enough to fit in time window and
+efficient enough to satisfy our resource constraints.
+However, there is no simple solution can achieve these goals with high reliability.
+Hence we designed a two-phase {\em approximate deletion} strategy to trade deletion accuracy for
+speed and resource usage. Our method sacrifaces a tiny percentage of storage leakage
+to effectively identify unused blocks in $O(n)$ speed, with $n$ being the logical amount of blocks 
+to be deleted.
+%Our hybrid deletion strategy, using fuzzy deletion regularly and accurate deletion periodically,
+%accomplishs our speed, resource usage and relibility goals very well.
+
+{\bf Snapshot Summaries}
+
+{\bf Approximate Deletion Phase-1}
+The goal of approximate deletion phase-1 to fast identify unused blocks 
+which are no longer referenced by other snapshots after a snapshot deletion.
+Instead of scanning the entire append store indices, we merge the type-1 summaries of all
+valid snapshots. Since each VM has uniform bloom filter parameters to create snapshot summaries, 
+such merged summeries give us a compact representation of
+all block fingerprints that are still in use.
+Thus by the property of bloom filter, if a fingerprint is not found in merged summaries, 
+we are certain that block is no longer used by any valid snapshot, it would be then added
+to append store's deletion log.
+However, there is a small false-positive probility which
+would indetify unused data as in use, resulting in temporary storage leakage.
+
+{\bf Approximate Deletion Phase-2}
+%[exlpain why second bloom filter, why scan append store]
+We designed the second phase of approxmite deletion to solve the 
+temporary storage leakage problem mentioned above.
+In this phase we scan the entire append store indices, using the merged type-2 snapshot summaries.
+Still, if a block fingerprint can be found in
+
+We cannot simply repeat the phase 1 multiple times to reduce temporary storage leakage, because:
+\begin{enumerate} 
+\item After several runs of phase-1, it is proven that the merged type-1 summaries cannot sieve remaining unused blocks, due to the false-positive property of bloom filter.
+\item The recipes of deleted snapshots have been removed from the system, thus we are not able to obtain the deleted block fingerprints from any metadata, the only way to discover them is to scan the append store indices.
+\end{enumerate}
+
+%uses the logical a bloom filter to check if a data are still referenced by living snapshots. 
+{\bf Discussion}
+For one VM's snapshots, let $D_{leak}$ be the amount of storage leakage, 
+$D_{del}$ be the average amount of data that should be physically deleted in one snapshot deletion,
+$P_{1}$ be the false-positive rate of merged bloom filter type-1,
+$N_1$ be the number of runs of approximate deletion phase-1, then we have:
+\begin{equation}
+D_{leak} = N_1 * P_b * D_{del}
+\end{equation}
+
+We let approxmite deletion phase-2 be triggered  
+when $D_{leak}/D_{del}$ is accmulated to exceed certain threshold $t$:
+\begin{equation}
+\frac{D_{leak}}{D_{del}} = N_1 * P_1 > t \Rightarrow N_{1} > \frac{t}{P_1}
+\end{equation}
+For example, letting $P_1 = 0.01$ and $t=1.0$, 
+we would expect deletion phase-2 be triggered once for 
+every $T/P_{bl} = 100$ runs of deletion phase-1.
+On a node that hosts 20 VMs and each VM deletes one snapshot per day, there would be 
+only 1 deletion phase-2 scheduled for every 5 days, which is sufficiently small to prevent the 
+heavy I/O workload of deletion phase-2 from disturbing normal VM opeations.

### 2013-05-29 snapshot_system/design1.tex

@@
 allowing data sharing between segments.
+
 The representation of each snapshot has  a two-level index data structure. 
@@
 %segments which greatly ease the segment-level deduplication.
+
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=images/snapshot_representation.pdf, width=3.7in}
+  \caption{An example of snapshot representation.}
+  \label{fig:snapshot}
+\end{figure}
+As a result, the representation of each snapshot is designed as a two-level index data structure 
+in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
+A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
+that holds the meatdata of its chunks. We choose this two-level structure because in practice we
+observe that during each backup period only a small amount of VM data are added or modified. 
+As the result, even the metadata of two snapshots can be highly similar, 
+thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
+Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
+segments which greatly ease the segment-level deduplication.
 
@@
   \centering
-  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
-  \epsfig{file=images/arch.eps, width=3.9in}
+  \epsfig{file=images/arch.pdf, width=3.9in}
   \caption{Snapshot backup architecture of each node.}

### 2013-05-29 snapshot_system/snapshot.tex

@@
 \item \textbf{Chunk-level fine-grain nearby duplicate detection.}
-
 The best deduplication uses a nonuniform chunk size 
@@
 \end{equation}
+{\bf How this is derived?} 
 The $S_c$ and $S_g$ can be expressed as:

### 2013-05-29 snapshot_system/arch.tex
w

--- 2013-05-28 snapshot_system/arch.tex
@@
-\section{Design Overview}
+\section{Architecture and Implementation Details}
 %[describe what is going to be presented in this section]
-We start by analyzing the main features in the design of our system.
-We first present its architecture,
-then introduce the two major contributions: the colocated deduplication 
-scheme and the snapshot deletion strategy.
-\subsection{Architecture}
+%We start by analyzing the main features in the design of our system.
+%We first present its architecture,
+%then introduce the two major contributions: the colocated deduplication 
+%scheme and the snapshot deletion strategy.
+%\subsection{Architecture}
 %[describe the cloud environment]
-Our architecture, as shown in figure.\ref{fig:arch}, is built on top of 
-Alibaba's platform which is the largest cloud service provider in China. 
-A typical VM cluster in our cloud environment
-consists of from hundreds to thousands of physical machines, each of which can
-host tens of xen-based\cite{Barham2003} VMs.
-Alibaba's cloud platform provides a hadoop-like infrastructure, 
-which includes several highly scalable distributed service:
+
+%Our architecture, as shown in figure.\ref{fig:arch}, is built on top of 
+%Alibaba's platform which is the largest cloud service provider in China. 
+%A typical VM cluster in our cloud environment
+%consists of from hundreds to thousands of physical machines, each of which can
+%host tens of xen-based\cite{Barham2003} VMs.
+%Alibaba's cloud platform provides a hadoop-like infrastructure, 
+%which includes several highly scalable distributed service:
+
+Our system runs on a cluster of Linux machines with Xen-based VMs.
+A distributed file system (DFS) manages  the physical disk storage and we use 
+QFS~\cite{QFS}. 
+All data needed for VM services, such as virtual disk images used by runtime VMs,
+and snapshot data for backup purposes, reside in this distributed file system. 
+One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
+virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
+
+\comments{
 \begin{description}
@@
 DFS holds the responsibility of managing physical disk storage
-in the cloud. All data needed for VM services, such as virtual disk images used by runtime VMs,
+in the cloud. 
+All data needed for VM services, such as virtual disk images used by runtime VMs,
 and snapshot data for backup purposes, reside in this distributed file system. 
@@
 %\item[MapReduce]: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
-\item[Distributed memory cache]: A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inqueries. 
+\item[Distributed memory cache]: A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inquiries. 
 \end{description}
@@
 rely on these fundamental cloud services
-to be functional. Such a colocated deduplication architecture allow us 
+to be functional. Such a co-located deduplication architecture allow us 
 to enjoy the benefits from these mature technologies 
-such as load balancing, scalability, and fault tolerancy.
+such as load balancing, scalability, and fault tolerance.
 Moreover, all the above cloud services can easily find their open-source counterparts,
@@
 file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
-Moreover, we break 
-segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
+Moreover, we break segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
 which brings the opportunity of fine-grained deduplication by
 allowing data sharing between segments.
+}
 
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=images/snapshot_representation.pdf, width=3.7in}
-  \caption{An example of snapshot representation.}
-  \label{fig:snapshot_rep}
-\end{figure}
-As a result, the representation of each snapshot is designed as a two-level index data structure 
-in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot_rep}.
-A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
-that holds the meatdata of its chunks. We choose this two-level structure because in practice we
-observe that during each backup period only a small amount of VM data are added or modified. 
-As the result, even the metadata of two snapshots can be highly similar, 
-thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
-Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
-segments which greatly ease the segment-level deduplication.
+\subsection{ Components of a cluster node }
 
-In both two kind of recipes, 
-they do not include the actual data but only have
- references point to the data which are either stored in append store or CDS.
-In our implementation the data reference is a 8 bytes field which is either an 
-ASID (discuss in \ref{sect:append}) or an offset of an additional flag indicates
-the location of CDS data.
+As  depicted in Figure~\ref{fig:arch_vm}, 
+there are four key service components running on each cluster
+node  for supporting backup and deduplication: 
+1) a virtual block device driver, 2) a snapshot deduplication component,
+3) an append store client which provides facilities to store  and access snapshot data,
+and 4)  a CDS client to support CDS index access. We will further discuss our deduplication scheme 
+in Section~\ref{sec:dedup}.
+
+We use the virtual device driver in Xen that employs a bitmap to track the changes 
+that have been made to virtual disk.
+%This driver maintains a map of dirty bits to record the change status of every fix-size segment of the virtual disk. 
+When the VM issue a disk write, the bits corresponding to the segments that covers 
+the modified disk region are set, thus letting snapshot deduplication component knows these
+segments must be checked during snapshot backup. After the snapshot backup is finished, 
+snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
+a clean state.
+Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
+is modified since last backup. Hence we could treat segment as the basic unit 
+in snapshot backup similar to
+file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
+As a standard practice, segments are further divided into variable-sized chunks (average 4KB) 
+using content-based chunking algorithm, which brings the opportunity of fine-grained deduplication by
+allowing data sharing between segments.
+
+The representation of each snapshot has  a two-level index data structure.
+%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
+The snapshot meta data (called snapshot recipe) contains a list of segments, each of which contains segment
+metadata of its chunks (called segment recipe).
+%\begin{figure}[htbp]
+%  \centering
+%  \epsfig{file=images/snapshot_representation.pdf, width=3in}
+%  \caption{An example of snapshot representation.}
+%  \label{fig:snapshot_rep}
+%\end{figure}
+%As a result, the representation of each snapshot is designed as a two-level index data structure 
+%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot_rep}.
+%A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
+%that holds the meatdata of its chunks. We choose this two-level structure because in practice we
+%observe that during each backup period only a small amount of VM data are added or modified. 
+%As the result, even the metadata of two snapshots can be highly similar, 
+%thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
+%Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
+%segments which greatly ease the segment-level deduplication.
+In a snapshot recipes or a segment recipe, 
+the data structures  includes reference pointers to the actual data location.
+%In our implementation the data reference is a 8 bytes field which is either an 
+%ASID (discuss in Section \ref{sect:append}) or an offset of an additional flag indicates
+%the location of CDS data.
+
+%\subsection{ Snapshot management}
 
@@
     }
-    \caption{System architecture}
+    \caption{System architecture.}
     \label{fig:arch}
@@
 %[describe the architecture frm node side]
-{\bf Node Architecuture} 
-Our node-side architecture, depicted in figure.\ref{fig:arch_vm}, consists of
-two main entities: a virtual block device driver, and a snapshot deduplication component.
-
 %[brief the virtual device driver]
-One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
-virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
-This driver maintains a map of dirty-bits to record
-the change status of every fix-size segment of the virtual disk. 
-When the VM issue a disk write, the bits coresponding to the segments that covers 
-the modified disk region are set, thus letting snapshot deduplication component knows these
-segments must be checked during snapshot backup. After the snapshot backup is finished, 
-snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
-a clean state.
+%One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
+%virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
+%This driver maintains a map of dirty-bits to record
+%the change status of every fix-size segment of the virtual disk. 
+%When the VM issue a disk write, the bits coresponding to the segments that covers 
+%the modified disk region are set, thus letting snapshot deduplication component knows these
+%segments must be checked during snapshot backup. After the snapshot backup is finished, 
+%snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
+%a clean state.
 
 %[brief the snapshot deduplication]
-The snapshot deduplication component consists of the chunking and deduplication 
-logic of our snapshot storage system. We choose
-
-It contains an append store client which provides facilities to manage stored snapshot data, and a CDS client to support CDS index access.
-We will further discuss our deduplication scheme in section\ref{sec:dedup}.
+%The snapshot deduplication component consists of the chunking and deduplication 
+%logic of our snapshot storage system. We choose
 
 %[describe the arch from cluster side]
-{\bf Cluster Architecture}
 
 %[describe the data structure in underlying storage]
-{\bf Append Store}
-Append Store (AS) is our underlining storage engine for storing snapshot data after deduplication. 
-AS is built on top of our highly scalable distributed file system (DFS), 
-which is very similar to Google's file system
-in a sense that it is optimized for large files and sequential read/append operations.
+\subsection{Append store for backup data}
+The Append Store (AS) is our underlining storage engine for storing snapshot data in the distributed file system
+after deduplication.
+%AS is built on top of our highly scalable distributed file system (DFS), 
+%which is very similar to Google's file system
+%in a sense that it is optimized for large files and sequential read/append operations.
 
@@
 
-Append Store supplies three interfaces: {\em get(ref)} accepts a data reference and retrives data, 
+AS supplies three interfaces: {\em get(ref)} accepts a data reference and retrieves data, 
 {\em put(data)} accepts data and returns a reference to be stored in metadata recipes, 
@@
 
-Write requests to append store are accumlated. When the number reaches $m$, the AS client forms a CBlock by assigning 
+Write requests to append store are accumulated. When the number reaches $m$, the AS client forms a CBlock by assigning 
 every chunk a CID, compress the CBlock data, and append it to the CBlock data file. Then a new CBlock index entry is appended
@@
 
+\comments{
 \subsection{Snapshot Deduplication and Fault Isolation}
@@
 Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
-Such localization increases data independency between different VM backups,
+Such localization increases data independence between different VM backups,
 simplifies snapshot management and statistics collection,
@@
 \begin{itemize}
-\item \textbf{Dirty-based corase-grain inner-VM deduplication.}
-The first-level deduplication is to follow the standand dirty bit approach, but is conducted
+\item \textbf{Dirty-based coarse-grain inner-VM deduplication.}
+The first-level deduplication is to follow the standard dirty bit approach, but is conducted
 in the coarse grain segment level.
-We use the  Xen virtual device driver which supports dirty bits for thestorage device
-and the dirty bit setting is maintained in a corase grain level we call it a segment.
+We use the  Xen virtual device driver which supports dirty bits for the storage device
+and the dirty bit setting is maintained in a coarse grain level we call it a segment.
 In our implementation, the segment size is 2MB. 
-Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
-and cannot affort a small segment  size.
+Since every write for a block will touch a dirty bit, the device driver maintains dirty bits in memory
+and cannot afford a small segment  size.
 
@@
 We load the fingerprints of block chunks of the corresponding segment from the
-parent for a comparisons and compare near-by fingerprint matching within this segement.
+parent for a comparisons and compare near-by fingerprint matching within this segment.
 The amount of memory for maintaining those fingerprints  is small.
@@
 \item \textbf{Cross-VM deduplication.}
-This step accomplishes the standand global fingerprint  comparison as conducted
+This step accomplishes the standard global fingerprint  comparison as conducted
 in the previous work~\cite{??}.
@@
 Thus there is no data dependence between VMs.
-For cross-VM deduplication, there is a data dependence among VMs and we would minimize the faiulre impact
-of shared blocks by adding extra replcas of those shared blocks.
+For cross-VM deduplication, there is a data dependence among VMs and we would minimize the failure impact
+of shared blocks by adding extra replicas of those shared blocks.
 
 This section analyzes the choice of popular blocks and its impact on the deduplication efficiency.
-It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
+It also  compares the  fault resilience of our VM-centric deduplication approach with a standard approach using 
 global deduplication.
@@
 \subsection{Snapshot Summaries for Deletion}
+}

### 2013-05-29 snapshot_system/intro.tex
w

@@
 \section{Introduction}
-In a cluster-based cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} 
-and Alibaba Aliyun\cite{Aliyun},
+In a cluster-based cloud environment,
+% such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
 each physical machine runs a number  of virtual machines as  instances of a guest operating system 
@@
 %backing up VM's data is mainly done by taking snapshots of virtual disk images.
-
 %A snapshot preserves the data of a VM's file system at a specific point in time. 
@@
 Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
-For example, the Aliyun cloud , which is  the largest cloud service provider by Alibaba in China, 
+For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
 automatically conducts  the backup of virtual disk images to all active users every day.
@@
 %Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
-The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
-duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
-On the other hand, comparing fingerprints  adds significant  memory cost. 
-Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
+%The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
+%duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
+%On the other hand, comparing fingerprints  adds significant  memory cost. 
+%Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
 Cloud providers often wish that the backup service only consumes  small or modest resources
-with a minimal impact to the existing cloud services.  A 
-recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
-Another issue is that after deduplication, the most of data blocks are shared by many virtual machines.
+with a minimal impact to the existing cloud services.  
+We study and evaluate the integration of several deduplication strategies to meet
+the low-cost collocation requirement. In parallel, we identify deduplication options that yield
+better fault isolation.
+%A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
+This is because  after deduplication, the most of data blocks are shared by many virtual machines.
 Failure of such blocks would  have a catastrophic effect and many snapshots of virtual machines would be affected.
-Furthermore, 
+The previous work in deduplication focuses on the efficiency and approximation of
+finger print comparison, and has not addressed the  fault tolerance along with a low-cost solution.
+Another issue considered is that
 %that deletion of old snapshots compete for computing resource as well. That is because data dependence created

### 2013-05-30 snapshot_system/arch.tex
add deletion

--- 2013-05-29 snapshot_system/arch.tex
@@
 \begin{equation}
-S_c = N*m/F, S_g = N*D/B
+S_c = N*m/F, \; S_g = N*D/B
 \end{equation}
@@
 {\bf Discussion}
-For one VM's snapshots, let $D_{leak}$ be the amount of storage leakage, 
+For one VM's snapshots, let $L_{temp}$ be the amount of temporary storage leakage, 
 $D_{del}$ be the average amount of data that should be physically deleted in one snapshot deletion,
 $P_{1}$ be the false-positive rate of merged bloom filter type-1,
-$N_1$ be the number of runs of approximate deletion phase-1, then we have:
+$N_1$ be the number of runs of deletion phase-1 during the gap of two deletion phase-2 operations, then we have:
 \begin{equation}
-D_{leak} = N_1 * P_b * D_{del}
+L_{temp} = N_1 * P_b * D_{del}
 \end{equation}
 
-We let approxmite deletion phase-2 be triggered  
-when $D_{leak}/D_{del}$ is accmulated to exceed certain threshold $t$:
+If we let approxmite deletion phase-2 be triggered  
+when $L_{temp}/D_{del}$ is accmulated to exceed certain threshold $t$, then:
 \begin{equation}
-\frac{D_{leak}}{D_{del}} = N_1 * P_1 > t \Rightarrow N_{1} > \frac{t}{P_1}
+\frac{L_{temp}}{D_{del}} = N_1 * P_1 > t \Rightarrow N_{1} > \frac{t}{P_1}
 \end{equation}
+
+Let $P_{2}$ be the false-positive rate of merged snapshot summaries type-2,
+$L_{perm}$ be the permanent storage leakage resulting from the approxmite deletion phase-2,
+it can be calculated as follows: 
+\begin{equation}
+L_{perm} = 
+\end{equation}
+
 For example, letting $P_1 = 0.01$ and $t=1.0$, 

### 2013-05-30 snapshot_system/impl.tex
add deletion

@@
 \subsection{Snapshot Deletion}
-In a mature VM cluster, snapshot deletions are as frequent as snapshot creations.
-Our system adopts lazy delete strategy so that all snapshot deletions are scheduled
-in the backup time window at midnight. 
-Therefore, snapshot deletions must be fast enough to fit in time window and
-efficient enough to satisfy our resource constraints.
-However, there is no simple solution can achieve these goals with high reliability.
-In Aliyun's cloud, we use a {\em fuzzy deletion} method to trade deletion accuracy for
-speed and resource usage. This method tolerates a tiny percentage of storage leakage
-to make the deletion operation faster and efficient by an order of magnitude,
-yet we still adopt an slow but accurate deletion method to fix such leakage in the long-term.
-Our hybrid deletion strategy, using fuzzy deletion regularly and accurate deletion periodically,
-accomplishs our speed, resource usage and relibility goals very well.
-
-{\bf Approximate Deletion}
-We design approximate deletion to fast identify unused data in the append store.
-Instead of scanning the whold append store, it uses a bloom filter to check 
-if a data are still referenced by living snapshots. However, there is a small false-positive probility which
-would indetify unused data as in use, i.e., storage leakage.
 The following steps would take place during an approximate deletion:
@@
 when set $P_{bl}$ to 0.01, the memory footprint of approximate deletion is about 15 MB.
-
-The design goal of approximate deletion is to reduce the frequency of running accurate deletion.
-For one VM's snapshots, let $D_{leakage}$ be the amount of storage leakage, $D_{del}$ be the average amount of data
-to be deleted in one snapshot deletion, 
-then we have:
-\begin{equation}
-D_{leakage} = N_{approximate} * P_{bl} * D_{del}
-\end{equation}
-where $N_{approximate}$ is the number of runs of approximate deletion. 
-An accurate deletion is triggered to fix the storage leakage
-when $D_{leakage}/D_{del}$ is accmulated to exceed certain threshold $T$:
-\begin{equation}
-D_{leakage} / D_{del} = N_{approximate} * P_{bl} > T \Rightarrow N_{approximate} > T/P_{bl}
-\end{equation}
-Therefore, when $P_{bl} = 0.01$ and $T=1$, 
-there would be a run of accurate deletion for every $T/P_{bl} = 100$ runs of approximate deletion.
-On a machine that hosts 20 VMs and each VM deletes snapshot daily, there would be less than
-one accurate deletion scheduled per day.
-
-{\bf Append Store Cleanup}
-Our accurate deletion uses mark-and-sweep to find all the unused chunks in a VM's append store.
-The following steps would take place during an accurate deletion:
-
-\begin{enumerate}
-\item Scan all the containers. For each container, extract full list of existing data references and allocate a bitmap. 
-(Notice this list is self sorted.)
-\item Scan all the snapshot recipes and segment recipes. For every data reference pointing to append store,
-find it in the above lists and mark the corresponding position in bitmaps.
-\item Scan the bitmaps, for every bit that are not marked, tell append store the corresponding data reference can be deleted.
-\end{enumerate}
-
-Although accurate deletion guarantees reliability and correctness, its speed and resource usage are big problems to our VM cloud.
-Let $T_{scan\_AS}$ be the time to scan the VM's append store, $T_{scan\_recipes}$ be the time to scan one snapshot recipe
-and its segment recipes, $T_{mark}$ be the time of finding a data reference in the list and mark bitmap, 
-$N_{SS}$ be the number of snapshots and $N_c$ be the number of chunks in one snapshot.
-The overall time of running an accurate deletion for one VM is:
-\begin{equation}
-T = T_{scan\_AS} + N_{SS} * T_{scan\_recipes} + N_{SS} * N_c * T_{mark}
-\end{equation}
-
-For a virtual disk that has 10 snapshots, 50 GB of data in the append store, $T_{scan\_AS}$ would have cost half an hour already.
-In addition, scanning recipes of 10 snapshots cost another 5 minutes.
-Furthermore, maintaining the full lists of data references and bitmaps costs about 100 MB of memory. Having tens of VMs
-co-lived in one physical machine and deleting snapshot on a daily basis, 
-it's infeasible to run accurate deletion as frequent as snapshot deletions.

### 2013-06-04 snapshot_system/abs.tex

@@
 localize the deduplication as much as possible within each virtual machine.
-The optimized design only requires a small amount of memory resource to conduct duplicate detection
-and an analysis illustrates this design with deduplication localization  provides  better fault tolerance.
-This  paper  provides an evaluation that shows this  proposed scheme can accomplish a high deduplication 
+Our analysis shows that  this virtual machine centric scheme uses a small amount of memory resource to conduct duplicate detection
+and can  provide  better fault tolerance through deduplication localization.  
+This  paper  provides a comparative evaluation of this scheme in  accomplishing a high deduplication 
 efficiency while sustaining a good backup throughput.

### 2013-06-04 snapshot_system/arch.tex

--- 2013-05-29 snapshot_system/arch.tex
@@
+\comments{
+\section{Design Overview}
+\label{sect:design}
+%[describe what is going to be presented in this section]
+We start by analyzing the main features in the design of our system.
+We first present its architecture,
+then introduce the two major contributions: the colocated deduplication 
+scheme and the snapshot deletion strategy.
+
+\begin{figure}
+    \centering
+    \subfigure[Cluster architecture]
+    {
+        \includegraphics[width=3in]{images/socc_arch_cluster.pdf}
+        \label{fig:arch_cluster}
+    }
+    \\
+    \subfigure[Node architecture from VM point of view]
+    {
+        \includegraphics[width=3in]{images/socc_arch_vm.pdf}
+        \label{fig:arch_vm}
+    }
+    \caption{System architecture}
+    \label{fig:arch}
+\end{figure}
+
+\subsection{Architecture}
+\label{sect:arch}
+%[describe the cloud environment]
+Our architecture, as shown in figure.\ref{fig:arch}, is built on top of 
+Alibaba's platform which is the largest cloud service provider in China.
+
+%[describe the arch from cluster side]
+{\bf Cluster Architecture}
+A typical VM cluster in our cloud environment
+consists of from hundreds to thousands of physical machines, each of which can
+host tens of xen-based\cite{Barham2003} VMs.
+Alibaba's cloud platform provides a hadoop-like infrastructure, 
+which includes several highly scalable distributed service:
+\begin{enumerate}
+\item {\bf Distributed file system} This is a scalable distributed file system (DFS) being optimized for many large and sequential reads or appends.
+DFS holds the responsibility of managing physical disk storage
+in the cloud. All data needed for VM services, such as virtual disk images used by runtime VMs,
+and snapshot data for backup purposes, reside in this distributed file system. 
+%\item[KV]: a distributed key-value store for managing structured data.
+%\item[MapReduce]: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
+\item {\bf Distributed memory cache} A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inqueries. 
+\end{enumerate}
+}
+
 \section{Architecture and Implementation Details}
@@
 \end{description}
+
 In addition, our implementation also uses MapReduce to facilitate the offline
@@
 
-%\subsection{ Snapshot management}
+%\subsection{Snapshot management}
 
@@
 
-\comments{
 \subsection{Snapshot Deduplication and Fault Isolation}
@@
 \begin{equation}
-S_c = N*m/F, S_g = N*D/B
+S_c = N*m/F, \; S_g = N*D/B
 \end{equation}
-
 By replacing $S_c$ and $S_g$ in the first formula, the deduplication efficiency becomes:
@@
 \end{equation}
-
 Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.
 
-\subsection{Snapshot Summaries for Deletion}
-}
+\begin{table}
+    \begin{tabular}{llll}
+    Data size (GB) & 1\%    & 2\%    & 4\%    \\
+    14.6           & 18.6\% & 22.1\% & 31.4\% \\
+    28.1           & 19.5\% & 26.2\% & 38.8\% \\
+    44.2           & 21.7\% & 26.5\% & 36\%   \\
+    61.6           & 23.2\% & 32.9\% & 35\%   \\
+    74.2           & 23.6\% & 33.6\% & 37.5\% \\
+    \end{tabular}
+    \caption{Deduplication effectiveness of top k\% of global index}
+    \label{tab:cds}
+\end{table}
+
+\subsection{Snapshot Summaries for Approximate Deletion}
+In a busy VM cluster, snapshot deletions are as frequent as snapshot creations.
+Our system adopts lazy delete strategy so that all snapshot deletions are scheduled
+in the backup time window at midnight. 
+Therefore, snapshot deletions must be fast enough to fit in time window and
+efficient enough to satisfy our resource constraints.
+However, there is no simple solution can achieve these goals with high reliability.
+Hence we designed a two-phase {\em approximate deletion} strategy to trade deletion accuracy for
+speed and resource usage. Our method sacrifaces a tiny percentage of storage leakage
+to effectively identify unused blocks in $O(n)$ speed, with $n$ being the logical amount of blocks 
+to be deleted.
+%Our hybrid deletion strategy, using fuzzy deletion regularly and accurate deletion periodically,
+%accomplishs our speed, resource usage and relibility goals very well.
+
+{\bf Snapshot Summaries}
+
+{\bf Approximate Deletion Phase-1}
+The goal of approximate deletion phase-1 to fast identify unused blocks 
+which are no longer referenced by other snapshots after a snapshot deletion.
+Instead of scanning the entire append store indices, we merge the type-1 summaries of all
+valid snapshots. Since each VM has uniform bloom filter parameters to create snapshot summaries, 
+such merged summeries give us a compact representation of
+all block fingerprints that are still in use.
+Thus by the property of bloom filter, if a fingerprint is not found in merged summaries, 
+we are certain that block is no longer used by any valid snapshot, it would be then added
+to append store's deletion log.
+However, there is a small false-positive probility which
+would indetify unused data as in use, resulting in temporary storage leakage.
+
+{\bf Approximate Deletion Phase-2}
+%[exlpain why second bloom filter, why scan append store]
+We designed the second phase of approxmite deletion to solve the 
+temporary storage leakage problem mentioned above.
+In this phase we scan the entire append store indices, 
+using the merged type-2 snapshot summaries to check if any of them are not
+referenced by existing snapshots.
+We cannot simply repeat the phase 1 multiple times to reduce temporary storage leakage, because:
+\begin{enumerate} 
+\item After several runs of phase-1, it is proven that the merged type-1 summaries cannot sieve remaining unused blocks, due to the false-positive property of bloom filter.
+\item The recipes of deleted snapshots have been removed from the system, thus we are not able to obtain the deleted block fingerprints from any metadata, the only way to discover them is to scan the append store indices.
+\end{enumerate}
+
+{\bf Discussion}
+For one VM's snapshots, let $L_{temp}$ be the amount of temporary storage leakage, 
+$D_{del}$ be the average amount of data that should be physically deleted in one snapshot deletion,
+$P_{1}$ be the false-positive rate of merged bloom filter type-1,
+$N_1$ be the number of runs of deletion phase-1 during the gap of two deletion phase-2 operations, then we have:
+\begin{equation}
+L_{temp} = N_1 * P_1 * D_{del}
+\end{equation}
+
+If we let approxmite deletion phase-2 be triggered  
+when $L_{temp}/D_{del}$ is accmulated to exceed certain threshold $t$, then:
+\begin{equation}
+\frac{L_{temp}}{D_{del}} = N_1 * P_1 > t \Rightarrow N_{1} > \frac{t}{P_1}
+\end{equation}
+
+Let $P_2$ be the false-positive rate of merged snapshot type-2 summaries,
+$N_2$ be the number of runs of deletion phase-2,
+$L_{perm}$ be the permanent storage leakage resulting from the approxmite deletion phase-2,
+it can be calculated as follows: 
+\begin{equation}
+L_{perm} = N_2 * P_1 * P_2 * D_{del}
+\end{equation}
+
+For example, letting $P_1 = 0.01$ and $t=1.0$, 
+we would expect deletion phase-2 be triggered once for 
+every $T/P_{bl} = 100$ runs of deletion phase-1.
+On a node that hosts 20 VMs and each VM deletes one snapshot per day, there would be 
+only 1 deletion phase-2 scheduled for every 5 days, which is sufficiently small to prevent the 
+heavy I/O workload of deletion phase-2 from disturbing normal VM opeations.

### 2013-06-04 snapshot_system/challenge.tex

@@
 and reduces the network bandwidth consumption in transferring the un-deduplicated
-raw data for backup. The running of such a service is subject to
-the resource availability of the system and we discuss the design considerations
-as follows.
+raw data for backup. 
+%The running of such a service is subject to the resource availability of the system and 
+We discuss the design considerations as follows.
 
@@
 \begin{itemize}
-\item {\em Backup storage.}
-We use a distributed file system to cluster
+\item {\em Cluster-based backup storage.}
+We use a distributed file system~\cite{GFS2004,Hadoop}  to cluster
 the storage  and store the backup with multiple replicas in the clustered storage.
@@
 ratio is $c$:1.  When the number of versions
-saved in the backup storage is $b$  on the average, 
-the amount of storage space in the cluster allocated  for the backup would be $\frac{b}{b+c}$.
-For example, when $b=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
-When $b=9$ and $c=13$, storage usage is 40\%. 
+saved in the backup storage is $l$  on the average, 
+the amount of storage space in the cluster allocated  for the backup would be $\frac{l}{l+c}$.
+For example, when $l=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
+When $l=9$ and $c=13$, storage usage is 40\%. 
 That is acceptable given today's cheap cost for disk storage.
@@
 
-\item {\em Backup throughput and computing resource}.
+Since the block size in the Hadoop and GFS is uniform and large with 64MB as a default setting,
+the content block in a deduplication system is of nonuniform size with 4KB or 8KB on average.
+We need to build an intermediate layer that supports large snapshot writing with append operations
+and infrequent snapshot access.
+
+\item {\em Requirement for backup throughput and low computing resource usage}.
 As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
@@
 
-With these considerations in mind, we propose a decentralized backup architecture with multi-level and selective 
-deduplication. This service is hosted   in the existing set of machines and resource usage is controlled
-with a minimal impact to the existing applications.
-The deduplication process is first conducted among snapshots within each VM
-and then is conducted across VMs.  
-Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
-and complicate failure management,
-we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
-For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
-Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance.
+With these considerations in mind, we study a cluster-based backup service 
+VM-centric deduplication. This service is co-hosted   in the existing set of machines and resource usage is friendly
+to the existing applications.  
+We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, and then present
+an architecture and implementation design with deletion support.
+
+%The deduplication process is first conducted among snapshots within each VM
+%and then is conducted across VMs.  
+%Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
+%and complicate failure management,
+%we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
+%For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
+%Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance.
 %

### 2013-06-04 snapshot_system/snapshot.tex

@@
-\section{Snapshot Deduplication and Fault Isolation}
+\section{Snapshot Deduplication}
 \label{sect:dedupe}
@@
 \subsubsection{Impact of CDS deduplication}
+
 Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the
@@
 
-[Describe the dedup efficiency model in detail]
-Let $S_c$ be the total number of FPs in CDS, $S_g$ be the total number of FPs in global index, $F$ be the size of a FP, $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size.
-The deduplication efficiency will be:
+For the Zipf-like distribution, an approximation to the sum of the first $n$ 
+elements of the distribution can be derived as follows:
 \begin{equation}
-  E = (S_c / S_g)^{1-\alpha}
+\sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
 \end{equation}
-{\bf How this is derived?} 
-The $S_c$ and $S_g$ can be expressed as:
+
+So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
+of global index with size $S_g$ is:
+
+\begin{equation}
+  E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
+\end{equation}
+
+%[Describe the dedup efficiency model in detail]
+Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size.
+Then $S_c$ and $S_g$ can be expressed as:
 \begin{equation}
@@
 \end{equation}
-By replacing $S_c$ and $S_g$ in the first formula, we have:
+
+By replacing $S_c$ and $S_g$ in the first formula, the deduplication efficiency becomes:
 \begin{equation}

### 2013-06-11 snapshot_system/snapshot.tex
modif

@@
 in the coarse grain segment level.
-We use the  Xen virtual device driver which supports dirty bits for thestorage device
+We use the  Xen virtual device driver which supports changed block tracking
+for the storage device
 and the dirty bit setting is maintained in a corase grain level we call it a segment.
@@
 and cannot affort a small segment  size.
+
+It should be noted that changed block tracking is supported or can be easily implemented in several 
+major virtualization solution vendors. 
+%(VMware, Xen, Microsoft).  
+VMware support it directly. Their hypervisor has API to let external backup application know 
+the changed areas since last backup.  Xen doesn't directly support it. However, their open-source 
+architecture allows anyone to extend the device driver, thus enabling changed block tracking. 
+We implements this way in the Alibaba's platform.  
+Microsoft SDK provides an API that allows external application monitor 
+the VM's I/O traffic.  Therefore changed block tracking can be implemented externally.
 

### 2013-06-13 snapshot_system/failover.tex
merge
Added some initial data files for block<-snapshot links, and a couple paragraphs to failover.tex on how the empirical results support the model.

@@
-\subsection{Fault Analysis }
+\subsubsection{Fault Analysis }
 
@@
 
+\comments{
 \begin{figure}[htbp]
@@
 \end{figure}
+}
 
@@
 
+\subsection{Empirical Validation}
+To validate our theoritical model for the probability of data loss, we computed
+the number of VMs using each block in a global index for the 350 VM traces.
+As you can see in Fig.~\ref{??}, The average number of VMs sharing a block
+%TODO: insert figure generated from data/links_no_cds.dat
+increases linearly with the number of snapshots. For 350 snapshots there are an
+average of 13.1 links to a given block in the global index.
+%What else do we need from the simulation to validate the model?
+
+\subsubsection{CDS and Fault Tolerance}
+%all numbers in this paragraph need to be corrected after I re-run the tests
+%using the actual cds generator code
+As part of our emprirical validation of our model, we also computed the effects
+of the CDS on fault tolerance. If we exclude the top 5\% most popular blocks
+and set aside those in the CDS, the average number of links to a non-CDS block
+%TODO: insert figure generated from data/links_cds.dat and data/links_wo_cds.dat
+drops to 10.3 for 350 snapshots. This means that on average, \~3 fewer
+snapshots will be affected by a lost data block in the general data store.
+The average number of links to a CDS block however, for 350 snapshots, is
+65.7. This suggests that a much higher replication factor is warranted for
+the CDS, as on average, a CDS block appears in 19\% of all the snapshots.
+
+The CDS gives a clear boundary for setting different replication factors,
+And our tests suggest that by separating the replication factor for the CDS
+and non-CDS blocks, greater fault tolerance can be acheived.
+
+----------------------------------------------------------------------
+
 For CDS model, 85% blocks are using the data from the same VM while upto 10% data is for CDS (we actually only use 5% perhaps).  Thus the overall speaking, at most 10% of data are shared.

### 2013-06-14 snapshot_system/snapshot.tex
Added some initial data files for block<-snapshot links, and a couple paragraphs to failover.tex on how the empirical results support the model.
update cds analysis

@@
 
-\subsection{Inner and corss VM deduplication}
+\subsection{Inner and cross VM deduplication}
 
@@
 
-For the Zipf-like distribution, an approximation to the sum of the first $n$ 
-elements of the distribution can be derived as follows:
+Let $b$ be the total amount of data blocks after localized deduplication, $b_u$ be the total amount of fingerprints 
+in the global index after complete deduplication, $C_i$ be the frequency for the $i$th most popular fingerprint. 
+By Zipf-like distribution we know an fingerprint's frequency is inversely proportional to its rank:
+\begin{equation*}
+C_i = X\frac{1}{i^\alpha},\; \sum_{i=1}^{b_u}C_i = X\sum_{i=1}^{b_u}\frac{1}{i^\alpha} = b
+\end{equation*}
+
+Thus $C_i$ can be expressed as:
 \begin{equation}
-\sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
+C_i=\frac{b(1-\alpha)}{b_u^{1-\alpha}i^\alpha}
 \end{equation}
 
-So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
-of global index with size $S_g$ is:
-
+We define deduplication efficiency $e$ to be the proportion of raw data that can be deduplicated,
+In complete deduplication scenario, it deduplication efficiency $e_c$ is:
 \begin{equation}
-  E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
+e_c = \frac{b-b_u}{b} = 1 - \frac{b_u}{b}
 \end{equation}
 
-%[Describe the dedup efficiency model in detail]
-Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size.
-Then $S_c$ and $S_g$ can be expressed as:
+If we only select the top $k$ most popular fingerprints from global index and remove only their duplicates,
+the deduplication efficiency will be:
 \begin{equation}
-S_c = N*m/F, S_g = N*D/B
+\begin{split}
+e_k &= (\sum_{i=1}^{k}C_i - k)/{b} = (b * \frac{1-\alpha}{b_u^{1-\alpha}} * \sum_{i=1}^{k}\frac{1}{i^\alpha} - k)/b \\
+%&\approx \frac{b*\frac{1-\alpha}{b_u^{1-\alpha}}*\frac{k^{1-alpha}}{1-\alpha} - k}{b}
+&\approx (\frac{k}{b_u})^{1-\alpha} - \frac{k}{b} \approx (\frac{k}{b_u})^{1-\alpha},\; (since\; k \ll b)
+\end{split}
 \end{equation}
 
-By replacing $S_c$ and $S_g$ in the first formula, the deduplication efficiency becomes:
+% For the Zipf-like distribution, an approximation to the sum of the first $n$ 
+% elements of the distribution can be derived as follows:
+% \begin{equation}
+% \sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
+% \end{equation}
+
+% So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
+% of global index with size $S_g$ is:
+
+% \begin{equation}
+%   E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
+% \end{equation}
+
+%[Describe the dedup efficiency model in detail]
+Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node used by CDS, 
+$F$ be the size of an CDS index entry,
+$D$ be the amount of unique data on each node, and $B$ be the average block size. Then $k$ and $b_u$ can be expressed as:
+\begin{equation*}
+k = N*m/F,\; b_u = N*D/B
+\end{equation*}
+
+Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
 \begin{equation}
-  E = (\frac{m*B}{F*D})^{1-\alpha}
+  e_k = (\frac{m*B}{F*D})^{1-\alpha}
 \end{equation}
 
-Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.
+Since $B$, $D$ and $F$ are environment constants, the deduplication efficiency of CDS is mainly affected by the its memory usage,
+and the Zipf-like distribution parameter $\alpha$.
+From the memory usage perspective, the more memory we give to CDS index, the more duplicates it can found.
+From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
+$\alpha$ would be small and thus CDS approach would not be effective. But in a VM cluster all VMs
+have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
+the better deduplication efficiency our CDS deduplication approach will have.

### 2013-06-14 snapshot_system/failover.tex
Added some to failover.text (added numbers for block<-VM links)

@@
 
+%the above model assumes uniform distribution of blocks and doesn't provide compelling numbers
+%with 3 replicas, 100 machines, and only 3 failures the chance of a single 10GB VM surviving is 9.11*10^-8
+%if we wanted to include it we probably want a model that includes containers, but that might be too complex
+%to be useful.
+
 \comments{
@@
 \subsection{Empirical Validation}
-To validate our theoritical model for the probability of data loss, we computed
-the number of VMs using each block in a global index for the 350 VM traces.
-As you can see in Fig.~\ref{??}, The average number of VMs sharing a block
-%TODO: insert figure generated from data/links_no_cds.dat
-increases linearly with the number of snapshots. For 350 snapshots there are an
-average of 13.1 links to a given block in the global index.
+%To validate our theoritical model for the probability of data loss, we computed
+%the number of snapshots using each block in a global index for the 350 snapshot
+%traces. As you can see in Fig.~\ref{??}, The average number of VMs sharing a block
+%%TODO: insert figure generated from data/links_no_cds.dat
+%increases linearly with the number of snapshots. For 350 snapshots there are an
+%average of 13.1 links to a given block in the global index.
+To validate our theoretical model for the probability of data loss, we measured
+the number of snapshots and VMs sharing data blocks for our 350 snapshot
+dataset. As you can see in Fig.~\ref{??}, the average number of snapshots sharing
+a block increases linearly with the number of snapshots. For 350 snapshots
+there are an average of 13.1 incoming links to a given data block in the global
+index. If we look at the number of VMs sharing a data block rather than
+snapshots, in the full dataset on average 1.47 VMs point to a data block in the
+index.
 %What else do we need from the simulation to validate the model?
@@
 65.7. This suggests that a much higher replication factor is warranted for
-the CDS, as on average, a CDS block appears in 19\% of all the snapshots.
+the CDS, as on average, a CDS block appears in \~20\% of all the snapshots.
+These measured numbers are different from our theoritical model due to the fact
+that duplicate data blocks are not uniformly distributed across all VMs.
+With uniform distribution of duplicates (and a zipf distribution on the number
+of duplicates), there should be on average 2.55 incoming VM links to each
+block. Since we show the average number of links to be 1.47 in our actual
+traces, the duplicates are
+more tighly grouped than the uniform model would predict. This supports
+the benefits of using a CDS plus more localized deduplication.
 

### 2013-06-15 snapshot_system/snapshot.tex
uodate cds analysis

@@
 
-Since $B$, $D$ and $F$ are environment constants, the deduplication efficiency of CDS is mainly affected by the its memory usage,
+Since $B$, $D$ and $F$ are environment constants, the deduplication efficiency of CDS is mainly affected by its memory usage,
 and the Zipf-like distribution parameter $\alpha$.

### 2013-06-15 snapshot_system/background.tex
modify the analysi

@@
 All of the above approaches have focused on
-such inline duplicate detection in which  deduplication of an individual block  is on the critical write path.
-In our work, this constraint is relaxed and 
-there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
-in our context, finishing the backup of required VM images within a reasonable time window is more
-important than optimizing individual VM block  backup requests.
+optimization of deduplication efficiency, and none of them have considered the impact
+of deduplication for the fault tolerance in the cluster-based environment that we have considered
+in this paper.
+We will describe the motivation of using the cluster-based   approach
+for running the backup service and then present our solution  with fault isolation.
+%In our work, the foucs 
+%there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
+%in our context, finishing the backup of required VM images within a reasonable time window is more
+%important than optimizing individual VM block  backup requests.
 

### 2013-06-15 snapshot_system/challenge.tex
modify the analysi

@@
 
-\item {\em Requirement for backup throughput and low computing resource usage}.
-As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
-to be processed can be huge. 
-On the other hand, the computing resources allocated for a snapshot service is limited
-because VM performance has higher priority.  
-The key usage of resource for backup is memory for storing and comparing the fingerprints. 
-We will consider the approximation techniques with less memory consumption
-studied in~\cite{extreme_binning09,Guo2011} along with the fault isolation consideration discussed below. 
-%A snapshot backup service shall not compete cpu, memory, or I/O bandwidth with VMs. 
-%Fingerprint-based search does require a significant amount of memory for fingerprint lookup
-%and comparison.  This competes memory resource  with the existing VMs.
-%Our design is to identify a low-cost and low-profile scheme for deduplication.
-%Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
-
-A  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with 
-the existing cloud, which is not preferred for cloud production system operation. 
-Thus it is desirable that backup for all nodes
-can be conducted in parallel and in a short period of time,
-and any centralized or  cross-machine communication for
-deduplication should not become a bottleneck.
-For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, The aggreated amount of data 
-the system must finish saving daily snapshots of all VMs in 2 hours.
-In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or
-500TB/hour.  The system must finish saving daily snapshots of all VMs in few hours. 
-Often a cloud has a few hours of light workload each day (e.g. midnight),  
-which creates an small window for automatic backup.
-
-%At Aliyun, it is required that while CPU and disk usage should be small or modest during backup time,
-%the memory footprint of snapshot service should not exceed 500MB at each node.
-
-Another consideration is backup data cleaning to delete useless blocks.
-Keeping reference counters for shared data blocks is challenging and less reliable.
-The previous work has advocated the mark-and-sweep approach  which periodically
-scans all data (or modified latest version of data)~\cite{?, Guo2011}. It first marks
-all used blocks and then sweep all chunks to reclaim unmarked blocks. 
-This approach is resilient to errors: at any time the process can simply be restarted with no 
-negative side effects.  Scalability, however, is an issue.
-To deal with 1 PB snapshots data, which may be represented by 10,000 GB FP index,
-If we account for an average deduplication factor of 10 (i.e., each chunk
-is referenced by 10 different snapshots), the total size
-of snapshot metadata that need to be read during the mark phase will
-be 100 TB.  This alone will take almost 2 hours on a
-1000-machine cloud. Furthermore, marking the in-use
-bits for 250 billion entries is no easy task. There is no
-way to put the bit map in memory. One might want
-to mitigate the poor performance of mark-and-sweep by
-doing it less frequently. But in practice this is not a viable
-option: customers always want to keep the utilization
-of the system close to its capacity so that a longer
-history can be stored. With daily snapshots taking place,
-systems rarely have the luxury to postpone deletion operations
-for a long time. In our field deployment, deletion
-is done once a day. More than 2 hours in each run is too
-much. In a large production-oriented dedupe system reference
-management needs to be very reliable and have
-good recover-ability. It should tolerate errors and always
-ensure correctness. Although mark-and-sweep provides
-these properties, its performance is proportional to the
-capacity of the system, thus limiting its scalability.
-
 \item {\em Fault tolerance and isolation.}
@@
 %when users access snapshots in a recovery process.
+
 \end{itemize}
+
+%\item {\em Requirement for backup throughput and low computing resource usage}.
+Because of collocation of this snapshot service with other existing cloud services, 
+%As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
+%to be processed can be huge. 
+the computing resources allocated for a snapshot service is limited
+because of its lower priority.  
+The key usage of resource for backup is memory for storing and comparing the fingerprints. 
+We will consider the approximation techniques with less memory consumption
+studied in~\cite{extreme_binning09,Guo2011} along with the fault isolation consideration discussed below. 
+%A snapshot backup service shall not compete cpu, memory, or I/O bandwidth with VMs. 
+%Fingerprint-based search does require a significant amount of memory for fingerprint lookup
+%and comparison.  This competes memory resource  with the existing VMs.
+%Our design is to identify a low-cost and low-profile scheme for deduplication.
+%Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
+
+A  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with 
+the existing cloud, which is not preferred for cloud production system operation. 
+Thus it is desirable that backup for all nodes
+can be conducted in parallel and in a short period of time,
+and any centralized or  cross-machine communication for
+deduplication should not become a bottleneck.
+For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, 
+the system must finish saving daily snapshots of all VMs in a few hours. 
+Often a cloud has a few hours of light workload each day (e.g. midnight),  
+which creates an small window for automatic backup.
+The backup service can generate hundreds of terabytes of data in such a time window
+without optimization and thus the resource content is considered carefully as we design
+a fault-resilient cluster-based solution. 
+%In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 
+%500TB/hour.  The system must finish saving daily snapshots of all VMs in few hours.
+
+%At Aliyun, it is required that while CPU and disk usage should be small or modest during backup time,
+%the memory footprint of snapshot service should not exceed 500MB at each node.
+
+\comments{
+Another consideration is backup data cleaning to delete useless blocks.
+Keeping reference counters for shared data blocks is challenging and less reliable.
+The previous work has advocated the mark-and-sweep approach  which periodically
+scans all data (or modified latest version of data)~\cite{?, Guo2011}. It first marks
+all used blocks and then sweep all chunks to reclaim unmarked blocks. 
+This approach is resilient to errors: at any time the process can simply be restarted with no 
+negative side effects.  Scalability, however, is an issue.
+To deal with 1 PB snapshots data, which may be represented by 10,000 GB FP index,
+If we account for an average deduplication factor of 10 (i.e., each chunk
+is referenced by 10 different snapshots), the total size
+of snapshot metadata that need to be read during the mark phase will
+be 100 TB.  This alone will take almost 2 hours on a
+1000-machine cloud. Furthermore, marking the in-use
+bits for 250 billion entries is no easy task. There is no
+way to put the bit map in memory. One might want
+to mitigate the poor performance of mark-and-sweep by
+doing it less frequently. But in practice this is not a viable
+option: customers always want to keep the utilization
+of the system close to its capacity so that a longer
+history can be stored. With daily snapshots taking place,
+systems rarely have the luxury to postpone deletion operations
+for a long time. In our field deployment, deletion
+is done once a day. More than 2 hours in each run is too
+much. In a large production-oriented deduplication system reference
+management needs to be very reliable and have
+good recover-ability. It should tolerate errors and always
+ensure correctness. Although mark-and-sweep provides
+these properties, its performance is proportional to the
+capacity of the system, thus limiting its scalability.
+
+}
 
@@
 particular segment. A fingerprint index is used as a catalog
-of FPs stored in the system, allowing the detection
+of fingerprints stored in the system, allowing the detection
 of duplicates: during backup, if a tuple of the form <
@@
 an aggregate throughput of 20 GB/sec, would require the
-index and the whole dedupe system for that matter
+index and the whole deduplication system for that matter
 to provide a query service throughput of at least 5,000

### 2013-06-15 snapshot_system/failover.tex
modify the analysi

--- 2013-06-13 snapshot_system/failover.tex
@@
-\subsubsection{Fault Analysis }
+\subsection{Fault Analysis }
 
-We  compare the impact of losing $d$ machines using the following two approaches:
-\begin{itemize}
-\item The VM-centric approach (VC).  The replication degree of the backup storage 
-is $r$ for regular content blocks and $r_c$ for CDS blocks where $r_c>r$. 
-\item The VM-oblivious (VO) approach.
-All chunk  blocks are treated uniformly and global comparison is conducted.
-\end{itemize}
+We  compare the impact of losing $d$ machines 
+to the the VC and VO approaches.  
+The replication degree of the backup storage 
+is $r$ for regular content blocks and $r=3$ is a typical setting in the distributed
+file system~\cite{Hadoop,GFS}.
+in The VC approach, a special replica degree $r_c$ used for CDS blocks where $r_c>r$. 
+Noted that the storage cost for VO with full deduplication is $b_u *r$
+while it is
+\[ r*b*s(1 -   (\frac{k}{b_u})^{1-\alpha}) +k*(r-r_c).
+\]
 
 When $d<r$, there is no loss of data in the snapshot storage.
-When $d \ge r$, some of data blocks in the storage are loss, and we compute the number of VMs that could
+When $d \ge r$, some of data blocks in the storage are lost, and we compute the number of VMs that could
 suffer the loss of their snapshots.

### 2013-06-15 snapshot_system/intro.tex
modify the analysi

@@
 Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
-can effectively identify content duplicates among snapshots and  remove 
-redundant storage content,  but the solution can be expensive and there is a large amount of 
+can effectively identify and remove content duplicates among snapshots, 
+but the solution can be expensive and there is a large amount of 
 network traffic to transfer  data from the host machines to the backup facility
@@
 The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
-based on  version  detection, small-scope inner VM duplicate comparison
+based on  version  detection, inner VM duplicate search,
 and controlled cross-VM comparison. 

### 2013-06-15 snapshot_system/snapshot.tex
modify the analysi

--- 2013-06-11 snapshot_system/snapshot.tex
@@
-\section{Snapshot Deduplication}
+\section{VM-centric Snapshot Deduplication}
 \label{sect:dedupe}
@@
 
-Our  deduplication scheme compares the fingerprints of the current snapshot
+A deduplication scheme compares the fingerprints of the current snapshot
 with its parent snapshot and also other snapshots in the entire cloud.
-This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
-We discuss the integration of several strategies as follows and analyze its effectiveness.
+The tradition approach compares all fingerprints and 
+reserve one copy for all of its deduplicates.
+We call this as  the VM-oblivious (VO) approach.
+In comparison, we analyze the design of
+a VM-centric approach (VC) which differenates duplicates within a VM and cross VMs,
+and conducts \textit{Inner-VM} and \textit{cross-VM} detection.
 
-\subsection{Inner and corss VM deduplication}
+\subsection{Inner and cross VM deduplication}
 
-Inner-VM duplication can be effecive within  VM's snapshots because the majority of data are unchanged during each backup period. 
-Localizing the snapshot data deduplication witin  a VM first
+Inner-VM duplication can be effecive within  VM's snapshots there
+are a large amount of duplicates existing among the snapshots within
+each VM.  Localizing the snapshot data deduplication witin  a VM first
 increases data independency between different VM backups,
@@
 
-\subsection{Popular Chunk Management and VM-oriented Fault Isolation}
-Our objective for fault isolation is to minimize the number of VMs affected when there are failures
-in the cluster.  The inner-VM deduplication does not depend on any global service and the comparison
-for each VM is localized within the parent and the current snapshot.
-Thus there is no data dependence between VMs.
-For cross-VM deduplication, there is a data dependence among VMs and we would minimize the faiulre impact
-of shared blocks by adding extra replcas of those shared blocks.
+\subsection{Popular Chunk Management}
+%VM-oriented Fault Isolation}
+%Our objective for fault isolation is to minimize the number of VMs affected when there are failures
+%in the cluster.  
+%The inner-VM deduplication does not depend on any global service and the comparison
+%for each VM is localized within the parent and the current snapshot.
+%Lack of data dependence between VMs brings 
+With cross-VM deduplication, shared data blocks
+create an artifical dependence  among VMs and failure of one shared block
+affects many VMs. Thus we only maintain the index for a small set of popular chunks.
+The mnagement for popular data chunks contains two aspects.
+\begin{itemize}
+\item Compute and select top-$k$ most popular chunks.
+The popularity of a chunk is the number  of data blocks from different VMs
+that are duplicates of this block after the inner VM deduplication.
+This number can be computed perioidically in a weekly basis.
+Once the popularity of all data blocks is collected, the system only maintains the top $k$
+most popular blocks.
+\item  Top $k$ number is chosen to be small while 
+our analysis belows will show that the algorithm can still deliver competitive deduplication effiency.
+Since $k$ is small and these top $k$ blocks are shared among multiple VMs, 
+we can afford to provide extra replicas for these popular blocks to enhanace the fault resilence.
+We will provide an alaysis in the next subsection.
+\end{itemize}
 
-This section analyzes the choice of popular blocks and its impact on the deduplication efficiency.
-It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
-global deduplication.
+This section analyzes how value   $k$ impacts on the deduplication efficiency.
+%It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
+%global deduplication.
+%\subsubsection{Impact of CDS deduplication}
+The analysis is based on the our study 
+using Alibaba's production user data~\cite{ieeecloud} 
+which shows that the popularity of data blocks after inner VM deduplication follows 
+a Zipf-like distribution\cite{zipf} and its
+exponent $\alpha$ is ranged between 0.65  and  0.70.
+%As a result, it can be proved that deduplication efficiency of CDS index is scalable:
 
-\subsubsection{Impact of CDS deduplication}
+\begin{table}[ht]
+\centering
+\begin{tabular}{|p{1.25cm}|p{6.5cm}|}
+\hline
+$b$ &  the total amount of data blocks\\ 
+\hline
+$b_u$ &  the total amount of unique fingerprints after inner VM  deduplication\\
+\hline
+$C_i$ &  the frequency for the $i$th most popular fingerprint\\
+\hline
+$s$ &  the percentage of duplicates detected in inner VM deduplication\\
+\hline
+$s$ &  the percentage of duplicates detected in inner VM deduplication\\
+\hline
+$p$ & the number of nodes in the cluster\\
+\hline
+$D$ & the amount of unique data on each node\\
+\hline
+$B$ & the average block size\\
+\hline
+$m$ & memory size on each node used by VC\\ 
+\hline
+$F$ & the size of an polular data index entry\\
+\hline
+\end{tabular}
+\caption{Modeling  symbols.}
+\label{tab:symbol}
+\end{table}
 
-Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the
-frequency of data duplication follows Zipf-like distribution\cite{zipf},
-with the exponent $\alpha$ between 0.65 ~ 0.70.
-As a result, it can be proved that deduplication efficiency of CDS index is scalable:
-
-For the Zipf-like distribution, an approximation to the sum of the first $n$ 
-elements of the distribution can be derived as follows:
+Let $b$ be the total amount of data blocks after localized deduplication, 
+$b_u$ be the total amount of fingerprints 
+in the global index after complete deduplication, 
+$C_i$ be the frequency for the $i$th most popular fingerprint. 
+By Zipf-like distribution, $C_i = \frac{C_1}{i^\alpha}.$
+Since $ \sum_{i=1}^{b_u}C_i = b$,
+\[
+C_1 \sum_{i=1}^{b_u}\frac{1}{i^\alpha} = b
+\]
+Given $\alpha <1$, $C_1$ can be approximated with integration:
 \begin{equation}
-\sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
+C_1=\frac{b(1-\alpha)}{b_u^{1-\alpha}}.
 \end{equation}
 
-So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
-of global index with size $S_g$ is:
+%We define deduplication efficiency $e$ to be the proportion of raw data that can be deduplicated,
+%In complete deduplication scenario, it deduplication efficiency $e_c$ is:
+%\begin{equation}
+%e_c = \frac{b-b_u}{b} = 1 - \frac{b_u}{b}
+%\end{equation}
 
+The  $k$ most popular fingerprints can cover the following number of blocks.
+\[
+C_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
+C_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  C_1\frac{  k^{1-\alpha}} {1-\alpha}.
+\]
+
+Deduplication efficiency of VC using top $k$ popular blocks
+is the percentage of duplicates that can be detected:  
 \begin{equation}
-  E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
+\begin{split}
+e_k &= 
+\frac{ b(1-s) + C_1\frac{  k^{1-\alpha}} {1-\alpha}} 
+{b(1-s)  + sb - b_u }\\
+&= 
+\frac{ (1-s) + s (\frac{k}{b_u})^{1-\alpha}}
+{ 1- \frac{b_u}{b} }.
+\end{split}
 \end{equation}
 
+%\begin{equation}
+%\begin{split}
+%e_k &= (\sum_{i=1}^{k}C_i - k)/{b} = (b * \frac{1-\alpha}{b_u^{1-\alpha}} * \sum_{i=1}^{k}\frac{1}{i^\alpha} - k)/b \\
+%&\approx \frac{b*\frac{1-\alpha}{b_u^{1-\alpha}}*\frac{k^{1-alpha}}{1-\alpha} - k}{b}
+%&\approx (\frac{k}{b_u})^{1-\alpha} - \frac{k}{b} \approx (\frac{k}{b_u})^{1-\alpha},\; (since\; k \ll b)
+%\end{split}
+%\end{equation}
+
+% For the Zipf-like distribution, an approximation to the sum of the first $n$ 
+% elements of the distribution can be derived as follows:
+% \begin{equation}
+% \sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
+% \end{equation}
+
+% So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
+% of global index with size $S_g$ is:
+
+% \begin{equation}
+%   E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
+% \end{equation}
+
 %[Describe the dedup efficiency model in detail]
-Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size.
-Then $S_c$ and $S_g$ can be expressed as:
-\begin{equation}
-S_c = N*m/F, S_g = N*D/B
-\end{equation}
+Let $p$ be the number of physical machines in the cluster, $m$ be the memory on each node used by the popular
+index, $F$ be the size of an index entry,
+$D$ be the amount of unique data on each phyiscal machine, and 
+$B$ be the average block size. We store the popular index using a distribued shared memory hashtable
+such as MemCacheD.  Then $k$ and $b_u$ can be expressed as:
+$
+k = p*m/F$, and $b_u = p*D/B.
+$
 
-By replacing $S_c$ and $S_g$ in the first formula, the deduplication efficiency becomes:
-\begin{equation}
-  E = (\frac{m*B}{F*D})^{1-\alpha}
-\end{equation}
+The overall deduplication effiency is
+\[
+\frac{ (1-s) + s (\frac{m*B}{D*F})^{1-\alpha}}
+{ 1- \frac{b_u}{b} }.
+\]
+where $(\frac{m*B}{D*F})^{1-\alpha}$ represents the percentage of the remaining blocks detected as duplicates
+after inner VM deduplication. 
+%Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
+%\begin{equation}
+%  e_k = (\frac{m*B}{F*D})^{1-\alpha}
+%\end{equation}
 
-Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.
+When the number of machines at each cluster increases, the number of total VMs increases.
+Then $k$ increases since more memory is available to host the popular block index.
+But for each physical machine, the number of VMs remains the same, and thus
+$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
+a constant.
+
+% is mainly affected by the its memory usage,
+%and the Zipf-like distribution parameter $\alpha$.
+%From the memory usage perspective, the more memory we give to CDS index, the more duplicates it can found.
+%From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
+%$\alpha$ would be small and thus CDS approach would not be effective. But in a VM cluster all VMs
+%have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
+%the better deduplication efficiency our CDS deduplication approach will have.
+
+\begin{table}
+    \begin{tabular}{llll}
+    Data size (GB) & 1\%    & 2\%    & 4\%    \\
+    14.6           & 18.6\% & 22.1\% & 31.4\% \\
+    28.1           & 19.5\% & 26.2\% & 38.8\% \\
+    44.2           & 21.7\% & 26.5\% & 36\%   \\
+    61.6           & 23.2\% & 32.9\% & 35\%   \\
+    74.2           & 23.6\% & 33.6\% & 37.5\% \\
+    \end{tabular}
+    \caption{Deduplication effectiveness of top k\% of global index}
+    \label{tab:cds}
+\end{table}

### 2013-06-15 snapshot_system/snapshot.tex

@@
 
+\comments{
+Since $B$, $D$ and $F$ are environment constants, the deduplication efficiency of CDS is mainly affected by its memory usage,
+and the Zipf-like distribution parameter $\alpha$.
+From the memory usage perspective, the more memory we give to CDS index, the more duplicates it can found.
+From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
+$\alpha$ would be small and thus CDS approach would not be effective. But in a VM cluster all VMs
+have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
+the better deduplication efficiency our CDS deduplication approach will have.
+}
+
 \begin{table}

### 2013-06-17 snapshot_system/failover.tex
modify analysis

@@
 while it is
-\[ r*b*s(1 -   (\frac{k}{b_u})^{1-\alpha}) +k*(r-r_c).
+\[ r*b*\delta(1 -   (\frac{k}{b_u})^{1-\alpha}) +k*(r-r_c).
 \]
 
+For each rank $i$ block which appears $C_i$ times  among $V$ virtual machines.
+Assigning this block to virtual machines can be viewed as a classical ball-bin assignment
+approximated by a Poisson distribution. Namely the virtual machines that share this block
+is approximated as $1 -  e^{C_i/V}$.
+Thus the average number of VMs that share a block is:
+\[
+(1-\delta) + \delta \sum_1^{u_b} \frac{1 -  e^{C_i/V}}{u_b}.
+\]
+Any failure of a block would impact the above number of virtual machines.
+In VO, the number of VMs that share a block is:
+\[
+\sum_1^{u_b'} \frac{1 -  e^{C_i'/V}}{u_b'}.
+\]
+
+Next we discuss how a failure of $d$ machines impacts the VM snapshots in VC.
 When $d<r$, there is no loss of data in the snapshot storage.
-When $d \ge r$, some of data blocks in the storage are lost, and we compute the number of VMs that could
+When $r_c> d \ge r$, some of data blocks in the storage are lost, and we compute the number of VMs that could
 suffer the loss of their snapshots.
+When $d \ge r_c$, some of CDS blocks are affected.
+In VC, the blocks in CDS are stored in a container manner (superblock), and they are shared by many VMs.
+The number of data containers stored with replication degree $r$ for
+referenced by each VM is:
+\[
+N_1= \frac{b}{v*s} (1-\delta) +b/(v*s)\delta (1 -  (\frac{k}{b_u})^{1-\alpha})
+\]
+The number of CDS data containers stored with replication degree $r_c$ for
+referenced by each VM is:
+\[
+N_2= \frac{b}{v*s}\delta (\frac{k}{b_u})^{1-\alpha}.
+\]
+
+%Thus the number of VMs using a block =    $(1-s_c)  + s_c *L$.
+
+When there are $r \le d<r_c$ machines failed and the probability of
+a container failure depends on if all replicas of this container reside in the failed machines.
+\begin{multline}
+Probability (\mbox{ a VM fails in VC})\\
+= 1- Probability (\mbox{ a VM has no data container loss}) \\
+= 1-  Probability(\mbox{ A container has no data loss})^{N_1}
+%\end{split}
+\end{multline}
+
+%Probablity(\mbox { no loss for this  block}) = 1 - Probability (\mbox{ this block in d failed machiens})
+\begin{multline}
+%\begin{split}
+Probability(\mbox{A container no data loss})\\
+= 1- Probability (\mbox{ this container is in d failed machines})\\
+=  1- \frac{\binom{d}{r}} { \binom{p}{r} }.
+%\end{split}
+\end{multline}
+
+When $r_c \leq d$, the CDS data containers in VC can also have a loss. 
+\begin{multline}
+Probability (\mbox{ a VM fails in VC})\\
+= 1-  Probability(\mbox{ A container has no data loss})^{N_1}* \\
+Probability(\mbox{ A CDS container has no data loss})^{N_2}\\
+= 1 - 
+(\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
+*
+(\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2} 
+%\end{split}
+\end{multline}
+
+By comparison, the probability that a VM has data loss is close to
+1 once  there are  $d \ge r$ failed machines. That is because there are more data blocks
+shared among VMs. Any failure of these blocks causes many more VMs to fail.
+
+\comments{
 We use the following parameters  during the analysis
 \begin{itemize}
-\item 	$V$ is the number of VMs. $m$ is the number of physical machines hosting the bakcup storage.
+\item 	$V$ is the number of VMs. $m$ is the number of physical machines hosting the backup storage.
 $d$ is the number of machines failed.
@@
 
-\comments{
 \begin{figure}[htbp]
@@
 \end{figure}
-}
 
@@
 \end{multline}
-
-\comments{
-Prob(i-th block shared by (V-i+1) machines = X/i.
-b
-Sum (X/i) =1.      Thus       X= 1/ ln (V).
-Length of sharing=  Probality(this block is shared with 1 VM) 1 + Probablity(this block shared by 2 VM) 2+..] =  X *V +X*(V-1)/2+ X*(V-2)/3 +..
-=  X * sum (V-i+1)/I   for I from 1 to V.
-=  (V+1) sum (X/i) . Sum(X) =  (V+1) -  X*V= V(1- 1/lnV) +1.
-}
 
@@
 %to be useful.
-
+}
 \comments{

### 2013-06-19 snapshot_system/result.tex
Started comparison section with sampling and data routing methods

\section{Experiments}

\subsection{Sampled Index}
One alternative approach to avoiding a single global index is to use a sampled
index. This is the approach taken by Guo and Efstathopoulos\cite{Guo2011}. We
compare their solution to ours by running their algorithm on our 350 traces
using a sampling rate of 1 out of 101 blocks, and always including the first
block in a container (which we fix at 16MB in size). The results of running this
test are shown in Table~\ref{??}, and the memory usage comparison can be found
Sec.~\ref{??}. Our results show that using a sampled index achieves a very high
rate of deduplication, and so a sampled index might be a good way to do dedup
in a single node setup.

The problems for sampling are in distributing the
algorithm and in deduplicating extremely large bodies of data. The algorithm
stores the entire (sampled) index in memory, which is required for high
throughput to avoid the disk-bottleneck problem - since the index itself has no
locality information, lookups are essentially random, so the index must be
somehow optimized to prevent excessive disk seeking (the sampling algorithm does
this by storing the index in memory). To distribute this index, each node would
either require a complete copy of the index which would have a prohibitive cost in
memory, or something like memcached must be used, which leaves the same problem
as the disk bottleneck with every index check potentially using the network.
The difficulty in storing extremely large bodies of data
is related, as once 1PB is stored in the system, assuming a sampling rate of 
1/101 with 22 byte index entires, 55GB of (in memory) index are required.

Our solution uses more total memory (??how much??), but is more scalable both in
terms of capactity and distributing the deduplication. The only part of our
algorithm which requires significant network traffic is the CDS deduplication,
but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
so is only done for a small percent of blocks (?? 5-10\% ??).

\subsection{Scalable Data Routing}
Another approach to avoiding a global index is to use a content-based hash
partitioning algorithm to break up the deduplication work. This approach is
taken by Dong et al. in their Scalable Data Routing paper, and is similar to
Exreme Binning\cite{??}\cite{extreme_binning09}. We compared our solution to
content-based hash partitioning by running the algorithm on our set of 
traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
the minhashes of the superchunks for routing. The results of this are shown in
Table~\ref{??}. Routing each chunk to a bin provides good deduplication
efficiency, and only requires each storage node to keep an index of local data
and the bin mapping, but misses significant opportunities in our indended use
case.

The problem with the Data Routing algorithm is in the very high network traffic.
Our intended use case is a backup system which runs alongside a number of VMs,
in order to save costs. Data Routing makes no use of the inherent locality in
such a system, and therefore puts a much higher network burden on machines which
are also running 35 VMs each. This will reduce the available network bandwidth
to users of the VMs, and/or reduce the possible deduplication throughput.

### 2013-06-19 snapshot_system/challenge.tex
revise intro/background/challenge

@@
 \begin{itemize}
-\item {\em Cluster-based backup storage.}
-We use a distributed file system~\cite{GFS2004,Hadoop}  to cluster
-the storage  and store the backup with multiple replicas in the clustered storage.
+\item {\em Collocating with cluster-based cloud services.}
+We collocate the backup service with other cloud serices in a cluster
+and  use a distributed file system~\cite{GFS2004,Hadoop}  to 
+store the backup with multiple replicas. 
 There can be a concern that storing many versions  of snapshots would
@@
 %Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
-
 A  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with 

### 2013-06-19 snapshot_system/snapshot.tex
modify analysis
revise intro/background/challenge

@@
 a VM-centric approach (VC) which differenates duplicates within a VM and cross VMs,
-and conducts \textit{Inner-VM} and \textit{cross-VM} detection.
+and conducts \textit{Inner-VM} and \textit{cross-VM} detection seperately.
 
@@
 
-\item \textbf{Chunk-level fine-grain nearby duplicate detection.}
+\item \textbf{Chunk-level fine-grain inner-VM detection.}
 The best deduplication uses a nonuniform chunk size 
@@
 
+When a block is not detected as a duplicate to any existing block, this block will be written
+to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
+accumnulate small local blocks. We manage  this accmulation process using an apendstore  scheme
+and discuss this in details in Section~\ref{sect:arch}.
+
  \subsection{Popular Chunk Management}
@@
 Once the popularity of all data blocks is collected, the system only maintains the top $k$
-most popular blocks.
-\item  Top $k$ number is chosen to be small while 
+most popular blocks.  For cross-VM comparison,
+we only store  top $k$ items and $k$ is  chosen to be small while 
 our analysis belows will show that the algorithm can still deliver competitive deduplication effiency.
-Since $k$ is small and these top $k$ blocks are shared among multiple VMs, 
+\item  Since $k$ is small and these top $k$ blocks are shared among multiple VMs, 
 we can afford to provide extra replicas for these popular blocks to enhanace the fault resilence.
@@
 \hline
-$s$ &  the percentage of duplicates detected in inner VM deduplication\\
-\hline
-$s$ &  the percentage of duplicates detected in inner VM deduplication\\
+$\delta$ &  the percentage of duplicates detected in inner VM deduplication\\
 \hline
@@
 \hline
-$B$ & the average block size\\
+$B$ & the average block size. Our setting is  4K.\\
+\hline
+$s$ & the average size of data containers stored in the distributed file system . Our setting is  64MB.\\
 \hline
@@
 e_k &= 
-\frac{ b(1-s) + C_1\frac{  k^{1-\alpha}} {1-\alpha}} 
-{b(1-s)  + sb - b_u }\\
+\frac{ b(1-\delta) + C_1\frac{  k^{1-\alpha}} {1-\alpha}} 
+{b(1-\delta)  + sb - b_u }\\
 &= 
-\frac{ (1-s) + s (\frac{k}{b_u})^{1-\alpha}}
+\frac{ (1-\delta) + s (\frac{k}{b_u})^{1-\alpha}}
 { 1- \frac{b_u}{b} }.
@@
 \[
-\frac{ (1-s) + s (\frac{m*B}{D*F})^{1-\alpha}}
+\frac{ (1-\delta) + \delta (\frac{m*B}{D*F})^{1-\alpha}}
 { 1- \frac{b_u}{b} }.

### 2013-06-19 snapshot_system/failover.tex
added plot for VO block links. still has some issue though.

@@
 }
+\begin{figure}[ht]
+  \centering
+  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
+	\begin{tikzpicture}
+		\begin{axis}[
+		title={VO Block links},
+		xlabel={Number of VMs added},
+		ylabel={Avg. Block Links},
+		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
+		legend pos=south east
+		]
+		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
+		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
+		\legend{Measured,Theoretical};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Average number of VMs sharing a block in the global index}
+  \label{fig-vo-links}
+\end{figure}
 \comments{

### 2013-06-19 snapshot_system/intro.tex
Minor changes to intro.

@@
 The cost of supporting a large number of concurrent backup streams is high
-because of the huge storage demand and  
+because of the huge storage demand. 
 Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
 can effectively identify and remove content duplicates among snapshots, 
-but the solution can be expensive and there is a large amount of 
+but the solution can be expensive. There is also a large amount of 
 network traffic to transfer  data from the host machines to the backup facility
@@
 
-This paper seeks for a low-cost architecture option and considers that
-a backup service collocates  on  the cloud cluster with a minimum resource usage. 
+This paper seeks for a low-cost architecture option and takes advantage of the
+fact that the
+backup service collocates on the cloud cluster with a minimum resource usage. 
 %Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
@@
 %A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
-This is because  after deduplication, the most of data blocks are shared by many virtual machines.
-Failure of such blocks would  have a catastrophic effect and many snapshots of virtual machines would be affected.
-The previous work in deduplication focuses on the efficiency and approximation of
-finger print comparison, and has not addressed the  fault tolerance along with a low-cost solution.
+We achieve improved fault isolation by accounting for the fact that after
+deduplication most data blocks are shared by several to many virtual machines.
+Failure of such popluar blocks would have a catastrophic effect and many
+snapshots of virtual machines would be affected.
+The previous work in deduplication focuses mainly on the efficiency and approximation of
+finger print comparison, and has not addressed fault tolerance along with a low-cost solution.
 Another issue considered is that
 %that deletion of old snapshots compete for computing resource as well. That is because data dependence created
-deletion of old snapshots compete for computing resource as well and that  needs
-to be considered. That is  because data dependence created
-by duplicate relationship among snapshots  adds processing complexity.
+deletion of old snapshots compete for computing resources as well so deletion needs
+to be considered in system design. The additional complexity for deletions
+come from the dependencies created by multiple links to the same problem, so
+some solution is needed to determine blocks with no dependent snapshots after deletion.
 % especially when  VMs can migrate around in the cloud.
@@
 and minimize memory usage while delivering a decent deduplication efficiency. 
-That brings the benefits for parallelism  utilization and fault isolation.
-Our deletion strategy uses a double Boomer filer strategy for periodic mark-and-sweeping of expired data blocks.
+Our partially localized solution also brings the benefits of parallelism, utilization, and fault isolation.
+Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data blocks.
 We have developed a prototype system that runs a cluster of Linux machines with Xen.

### 2013-06-19 snapshot_system/challenge.tex
wording changes

@@
 
-As we discuss earlier, collocating the backup service on the existing
+As discussed earlier, collocating the backup service on the existing
 cloud cluster avoids the extra cost to acquire a dedicated backup facility
@@
 store the backup with multiple replicas. 
-There can be a concern that storing many versions  of snapshots would
-require	a large amount of storage.
+There might be a concern that storing many versions of snapshots would
+go against the purpose of deduplication.
 The previous research shows the deduplication can compress the backup copies 
@@
 That is acceptable given today's cheap cost for disk storage.
-In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data
-while each machine typically can provide over 10TB storage.
+In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data.
+Each machine however can typically provide over 10TB storage.
 Thus the normal disk usage  is about 1TB per machine, and adding 30\% to 100\% 
-extra space for the backup is not a practical concern.
+extra space for the backup is not a practical concern, especially with the
+added benefits of cheaper running costs and lower network bandwidth requirements.
 
@@
 The distributed file system~\cite{GoogleFS,Hadoop} provides the replication support
-and we can use the open-source software to implement such a layer.
-When the number of machines failed exceeds the replication degree, there will be
+and we can leverage existing open-source software to implement such a layer.
+When the number of machines failed exceeds the replication degree, there may be
  some data loss.  Storage deduplication worsens the impact of such faults
-because  the majority of data snapshots (e.g. over 90\%) is deduplicated
+because  the majority of each snapshot (e.g. over 90\%) is deduplicated
 and the corresponding data blocks are shared among VMs.
 
-The previous work in deduplication~\cite{extreme_binning09,sparseindex09} has
-studied the solutions  to reduce memory requirement.
-They have not considered content sharing affects
+Previous work in deduplication~\cite{extreme_binning09,sparseindex09} has
+studied the solutions to reduce memory requirements.
+One important issue not considered in the previous work is how content sharing affects
 fault isolation.
@@
 Without any control of such data sharing, we can only increase  
-replication for global dataset to enhance the availability,
-but this incurs significantly more cost.
+replication for global datasets to enhance the availability,
+but this incurs significantly higher costs.
 Loss of a small number of shared data blocks can 
@@
 %to be processed can be huge. 
-the computing resources allocated for a snapshot service is limited
+the computing resources allocated for the snapshot service is limited, especially
 because of its lower priority.
@@
 %Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
-A  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with 
-the existing cloud, which is not preferred for cloud production system operation. 
+Excessive use of bandwidth and computing resource for backup can create
+noticeable contention for resources with the existing cloud, which is not
+preferred and may not not be acceptible for production system operation. 
 Thus it is desirable that backup for all nodes
@@
 With these considerations in mind, we study a cluster-based backup service 
-VM-centric deduplication. This service is co-hosted   in the existing set of machines and resource usage is friendly
+with VM-centric deduplication. This service is co-hosted   in the existing set of machines and resource usage is friendly
 to the existing applications.  

### 2013-06-20 snapshot_system/result.tex
Iadd experiment results

@@
 \section{Experiments}
+Our main test-bed is an cluster of 6 machines,
+each of which is equiped with a 8-core AMD FX-8120 at 3.1 GHz
+with 16 GB RAM, running Linux. 
+A distributed file system (QFS) runs
 
-\subsection{Sampled Index}
-One alternative approach to avoiding a single global index is to use a sampled
-index. This is the approach taken by Guo and Efstathopoulos\cite{Guo2011}. We
-compare their solution to ours by running their algorithm on our 350 traces
-using a sampling rate of 1 out of 101 blocks, and always including the first
-block in a container (which we fix at 16MB in size). The results of running this
-test are shown in Table~\ref{??}, and the memory usage comparison can be found
-Sec.~\ref{??}. Our results show that using a sampled index achieves a very high
-rate of deduplication, and so a sampled index might be a good way to do dedup
-in a single node setup.
-
-The problems for sampling are in distributing the
-algorithm and in deduplicating extremely large bodies of data. The algorithm
-stores the entire (sampled) index in memory, which is required for high
-throughput to avoid the disk-bottleneck problem - since the index itself has no
-locality information, lookups are essentially random, so the index must be
-somehow optimized to prevent excessive disk seeking (the sampling algorithm does
-this by storing the index in memory). To distribute this index, each node would
-either require a complete copy of the index which would have a prohibitive cost in
-memory, or something like memcached must be used, which leaves the same problem
-as the disk bottleneck with every index check potentially using the network.
-The difficulty in storing extremely large bodies of data
-is related, as once 1PB is stored in the system, assuming a sampling rate of 
-1/101 with 22 byte index entires, 55GB of (in memory) index are required.
-
-Our solution uses more total memory (??how much??), but is more scalable both in
-terms of capactity and distributing the deduplication. The only part of our
-algorithm which requires significant network traffic is the CDS deduplication,
-but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
-so is only done for a small percent of blocks (?? 5-10\% ??).
-
-\subsection{Scalable Data Routing}
-Another approach to avoiding a global index is to use a content-based hash
-partitioning algorithm to break up the deduplication work. This approach is
-taken by Dong et al. in their Scalable Data Routing paper, and is similar to
-Exreme Binning\cite{??}\cite{extreme_binning09}. We compared our solution to
-content-based hash partitioning by running the algorithm on our set of 
-traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
-the minhashes of the superchunks for routing. The results of this are shown in
-Table~\ref{??}. Routing each chunk to a bin provides good deduplication
-efficiency, and only requires each storage node to keep an index of local data
-and the bin mapping, but misses significant opportunities in our indended use
-case.
-
-The problem with the Data Routing algorithm is in the very high network traffic.
-Our intended use case is a backup system which runs alongside a number of VMs,
-in order to save costs. Data Routing makes no use of the inherent locality in
-such a system, and therefore puts a much higher network burden on machines which
-are also running 35 VMs each. This will reduce the available network bandwidth
-to users of the VMs, and/or reduce the possible deduplication throughput.
+We used two main data sets for testing. Our synthetic
+data set consists of multiple 3 GB files, each with globally
+unique data segments. Our second data set consists
+of virtual machine images, which are a very common
+real-world enterprise use-case, that takes advantage
+of deduplication. We use a VMware “gold” disk image
+(VM0), hosting a Microsoft Windows XP installation,
+and created three additional versions of it (VM1, VM2,
+and VM3), each with incremental changes: VM1 is VM0
+with all Microsoft updates and service packs, VM2 is

### 2013-06-20 snapshot_system/intro.tex
Added traditional arch and colocated arch figures

@@
 Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
+(see Figure~\ref{fig:traditional-arch})
 can effectively identify and remove content duplicates among snapshots, 
@@
 
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=3in]{images/traditional-arch.pdf}
+    \label{fig:traditional-arch}
+    \caption{Traditional VM Backup System}
+\end{figure}
+
 This paper seeks for a low-cost architecture option and takes advantage of the
 fact that the
-backup service collocates on the cloud cluster with a minimum resource usage. 
+backup service collocates on the cloud cluster with a minimum resource usage (see Figure~\ref{fig:colocated-arch})
 %Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
@@
 % especially when  VMs can migrate around in the cloud.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=3in]{images/colocated-arch.pdf}
+    \label{fig:colocated-arch}
+    \caption{Colocated VM Backup System}
+\end{figure}
 

### 2013-06-20 snapshot_system/failover.tex
Added VM failure

@@
 shared among VMs. Any failure of these blocks causes many more VMs to fail.
+
+The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failue}.
+The graph assumes 10X40GB snapshots per VM with 20\% unique data after local
+dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
+VM).
+
+\begin{figure}[ht]
+  \centering
+  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
+	\begin{tikzpicture}
+		\begin{axis}[
+		title={Node failure affect on VMs},
+		xlabel={Number of nodes failed},
+		ylabel={chance that a VM is affected (\%)},
+		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
+		]
+		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Percent chance that a VM is affected as storage nodes fail}
+  \label{fig-vm-failure}
+\end{figure}
 

### 2013-06-20 snapshot_system/snapshot.tex
Added CDS coverage graph with measured vs predicted. Not sure the predicted is helpful to the graph though.

@@
 with its parent snapshot and also other snapshots in the entire cloud.
-The tradition approach compares all fingerprints and 
-reserve one copy for all of its deduplicates.
+The traditional approach compares all fingerprints and 
+stores one copy for all of a block's duplicates.
 We call this as  the VM-oblivious (VO) approach.
@@
 
-Inner-VM duplication can be effecive within  VM's snapshots there
-are a large amount of duplicates existing among the snapshots within
-each VM.  Localizing the snapshot data deduplication witin  a VM first
-increases data independency between different VM backups,
-simplifies snapshot management and statistics collection,
-and facilitates parallel execution of snapshot operations.
+Inner-VM duplication can be very effecive within VM's snapshots. There
+are typically a large number of duplicates existing among the snapshots
+for a single VM.  Localizing the snapshot data deduplication witin a VM
+improves the system by:
+increasing data independency between different VM backups,
+simplifying snapshot management and statistics collection,
+and facilitating parallel execution of snapshot operations.
 On the other hand, cross-VM duplication can also be desirable mainly due to widely-used software and libraries. 
@@
 
-It should be noted that changed block tracking is supported or can be easily implemented in several 
+It should be noted that changed block tracking is supported or can be easily implemented in many 
 major virtualization solution vendors. 
 %(VMware, Xen, Microsoft).  
-VMware support it directly. Their hypervisor has API to let external backup application know 
-the changed areas since last backup.  Xen doesn't directly support it. However, their open-source 
+VMware support it directly; the VMWare hypervisor has an API to let external backup application know 
+the changed areas since last backup. Xen doesn't directly support it, However, their open-source 
 architecture allows anyone to extend the device driver, thus enabling changed block tracking. 
-We implements this way in the Alibaba's platform.  
-Microsoft SDK provides an API that allows external application monitor 
-the VM's I/O traffic.  Therefore changed block tracking can be implemented externally.
+We implement dirty bit tracking this way in Alibaba's platform.  
+The Microsoft SDK provides an API that allows external applications to monitor 
+the VM's I/O traffic, therefore changed block tracking can be implemented externally.
 
@@
 The best deduplication uses a nonuniform chunk size 
-in the average of 4K or 8K~\cite{??}.
-Thus the second-level inner-VM deduplication is to assess in this
-level, but only for those dirty  segments. 
+in the average of 4K or 8K~\cite{??}. This allows the system to
+achieve deduplication even when there are insertions/deletions which would
+affect many fixed-size blocks.
+Thus the second-level inner-VM deduplication is to perform this chunking for
+dirty segments, and to compare the snapshot with its parent. 
 We load the fingerprints of block chunks of the corresponding segment from the
-parent for a comparisons and compare near-by fingerprint matching within this segement.
-The amount of memory for maintaining those fingerprints  is small.
+parent and perform fingerprint matching for further inner-VM deduplication.
+The amount of memory for maintaining those fingerprints  is small, as we only
+load one segment at a time.
 For example, with a 2MB segment, there are about 500 fingerprints to compare.
@@
 in the previous work~\cite{??}.
-One key observation is that the inner deduplication has removed many of duplicates.
-There are not lot of deduplication opportunities cross VMs while the memory
-consumption for global comparison is expensive.
+One key observation is that the inner deduplication has removed many of the duplicates.
+There are fewer deduplication opportunities across VMs while the memory and network
+consumption for global comparison is more expensive.
 Thus our approximation is that the global fingerprint comparison only searches for the most popular items. 
@@
 to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
-accumnulate small local blocks. We manage  this accmulation process using an apendstore  scheme
+accululate small local blocks. We manage this accumulation process using an apendstore  scheme
 and discuss this in details in Section~\ref{sect:arch}.
@@
 affects many VMs. Thus we only maintain the index for a small set of popular chunks.
-The mnagement for popular data chunks contains two aspects.
+The management for popular data chunks contains two aspects.
 \begin{itemize}
@@
 most popular blocks.  For cross-VM comparison,
-we only store  top $k$ items and $k$ is  chosen to be small while 
-our analysis belows will show that the algorithm can still deliver competitive deduplication effiency.
+we only store  top $k$ items and $k$ is chosen to be relatively small.
+Our analysis below will show that the algorithm can still deliver competitive
+deduplication effiency after making these approximations.
 \item  Since $k$ is small and these top $k$ blocks are shared among multiple VMs, 
 we can afford to provide extra replicas for these popular blocks to enhanace the fault resilence.
-We will provide an alaysis in the next subsection.
+We will provide an analysis of the fault tolerance in the next subsection.
 \end{itemize}
 
-This section analyzes how value   $k$ impacts on the deduplication efficiency.
+This section analyzes how value   $k$ impacts the deduplication efficiency.
 %It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
@@
 %\subsubsection{Impact of CDS deduplication}
-The analysis is based on the our study 
+The analysis is based on VM traces collected
 using Alibaba's production user data~\cite{ieeecloud} 
@@
 
-Let $b$ be the total amount of data blocks after localized deduplication, 
-$b_u$ be the total amount of fingerprints 
-in the global index after complete deduplication, 
+Let $b$ be the total number of data blocks after localized deduplication, 
+$b_u$ be the total number of fingerprints 
+in the global index after complete deduplication, and
 $C_i$ be the frequency for the $i$th most popular fingerprint. 
@@
 \end{table}
+
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={CDS Coverage},
+            xlabel={Total Data Stored (GB)},
+            ylabel={CDS Coverage (\%)},
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            %legend pos=outer north east,
+            legend columns=2,
+            legend style={
+                at={(0.5,-0.2)},
+            anchor=north}
+            ]
+            \addplot[color=blue,mark=*] table[x=InputSize,y=A1] {figures/cds_coverage.txt};
+            \addplot[color=blue,mark=square*] table[x=InputSize,y=A2] {figures/cds_coverage.txt};
+            \addplot[color=blue,mark=triangle*] table[x=InputSize,y=A4] {figures/cds_coverage.txt};
+            \addplot[densely dashed,color=red,mark=*] table[x=InputSize,y=T1] {figures/cds_coverage.txt};
+            \addplot[densely dashed,color=red,mark=square*] table[x=InputSize,y=T2] {figures/cds_coverage.txt};
+            \addplot[densely dashed,color=red,mark=triangle*] table[x=InputSize,y=T4] {figures/cds_coverage.txt};
+            \legend{Measured (1\%CDS),Measured (2\%CDS),Measured (4\%CDS),Predicted (1\%CDS),Predicted (2\%CDS),Predicted (4\%CDS)};
+            \end{axis}
+    \end{tikzpicture}
+  \caption{fixed-alpha predicted vs. actual CDS coverage as data size increases.}
+  \label{fig-vo-links}
+\end{figure}

### 2013-06-21 snapshot_system/append.tex
add snapshot system introduction
add architecture
mwording changes

@@
 \section{Append Store}
+\label{sect:append}
 \subsection{Introduction}
@@
 While scalability has been handled by the DFS, there are still several challenges in 
-storing billions of var-sized small data chunks:
+storing billions of variable-sized small data chunks:
 \begin{description}
@@
 we have to group small chunks into large data files in DFS.
-However, snapshot deletion brings chunk data deletion, and reclaiming disk space would require many chunk data being moved.
+However, snapshot deletion brings chunk data deletion, and reclaiming disk space would require many chunks being moved.
 If such chunk movement incurs updates of data referencing in snapshot and segment recipes, then the cost of deleting 
@@
 \item[Efficient chunk lookup] The translation from data reference to data location must be very efficient in two ways: 
-first, a sorted index is necessary to fast locate the data location in $O(log(n)$ time; 
-second, the size of index must be optimized to minimized its memory footprint and the cost of fetching index. 
+first, a sorted index is necessary to quickly find the data location in $O(log(n)$ time; 
+second, the size of the index must be optimized to minimize its memory footprint and the cost of fetching index. 
 \end{description}
@@
   \centering
-  \epsfig{file=images/append_store_arch.eps, width=3.5in}
+  \epsfig{file=images/append_store_arch.pdf, width=3.5in}
   \caption{Architecture of Append Store}

### 2013-06-21 snapshot_system/failover.tex
mwording changes

--- 2013-06-19 snapshot_system/failover.tex
@@
 shared among VMs. Any failure of these blocks causes many more VMs to fail.
+
+The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failure}
+(for a 100 node cluster).
+The graph assumes 10X40GB snapshots per VM with 18\% unique data after local
+dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
+VM). We assume 18\% unique data after local dedup because that is what our
+snapshots have shown.
+
+\begin{figure}[ht]
+  \centering
+  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Node failure affect on VMs},
+		xlabel={Number of nodes failed},
+		ylabel={chance that a VM is affected (\%)},
+		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
+		]
+		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Percent chance that a VM is affected as storage nodes fail}
+  \label{fig-vm-failure}
+\end{figure}
 
@@
 }
+
+Figure~\ref{fig-vo-links} shows the average number of links to a given block in the global index as more VMs are added.
+The first 15 VMs are all windows machines, so that explains the initial higher values, but for the most part the average number of links is between 1.5 and 2.
+
 \begin{figure}[ht]
@@
 		\begin{axis}[
-		title={VO Block links},
+		%title={VO Block links},
 		xlabel={Number of VMs added},
-		ylabel={Avg. Block Links},
+		ylabel={Avg. Links to a Block},
 		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7

### 2013-06-21 snapshot_system/failover.tex
Added VM failure figures for two different models

@@
 
+\comments{\begin{figure}[ht]
+  \centering
+  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Node failure affect on VMs},
+		xlabel={Number of nodes failed},
+		ylabel={chance that a VM is affected (\%) in VO},
+		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
+		]
+		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Percent chance that a VM is affected as storage nodes fail}
+  \label{fig-vm-failure}
+\end{figure}}
+
 \begin{figure}[ht]
@@
 		%title={Node failure affect on VMs},
-		xlabel={Number of nodes failed},
-		ylabel={chance that a VM is affected (\%)},
-		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
+		xlabel={Failed storage nodes},
+		ylabel={Chance VM is affected (\%)},
+		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
+                mark options=solid,
+                legend pos=north west
 		]
-		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
+                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO]{figures/vm_failure_1.txt};
+                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_1.txt};
+                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_1.txt};
+                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_1.txt};
+                \legend{$VO$,$VC_{C_R=3}$,$VC_{C_R=4}$,$VC_{C_R=5}$,$VC_{C_R=6}$,$VC_{C_R=7}$}
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Percent chance that a VM is affected as storage nodes fail}
+  \label{fig-vm-failure}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Node failure affect on VMs},
+		xlabel={Failed storage nodes},
+		ylabel={Chance VM is affected (\%)},
+		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
+                mark options=solid,
+                legend pos=north west
+		]
+                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
+                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
+                \addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
+                \addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
+                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
+                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
+                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
+                \addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
+                \legend{$VO_{C=5}$,$VO_{C=10}$,$VO_{C=20}$,$VO_{C=40}$,$VC_{C=100}$,$VC_{C=200}$,$VC_{C=400}$,$VC_{C=800}$}
 		\end{axis}

### 2013-06-21 snapshot_system/failover.tex
Added several figures (VM Availability, CDS Replication, container links

@@
 
-The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failure}
-(for a 100 node cluster).
-The graph assumes 10X40GB snapshots per VM with 18\% unique data after local
-dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
-VM). We assume 18\% unique data after local dedup because that is what our
-snapshots have shown.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%OLD MODEL START%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failure}
+%(for a 100 node cluster).
+%The graph assumes 10X40GB snapshots per VM with 18\% unique data after local
+%dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
+%VM). We assume 18\% unique data after local dedup because that is what our
+%snapshots have shown.
 
@@
 
-\begin{figure}[ht]
+\comments{\begin{figure}[ht]
   \centering
@@
   \label{fig-vm-failure}
-\end{figure}
+\end{figure}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%OLD MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL START%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 		xlabel={Failed storage nodes},
-		ylabel={Chance VM is affected (\%)},
+		ylabel={VM Availability (\%)},
 		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                 mark options=solid,
-                legend pos=north west
+                legend style={
+                    cells={anchor=west}, %legend entry alignment
+                    legend pos=south west %legend position
+                }
 		]
+                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                 \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
-                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
-                \addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
-                \addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
+                %\addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
+                %\addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
+                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                 \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
-                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
-                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
-                \addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
-                \legend{$VO_{C=5}$,$VO_{C=10}$,$VO_{C=20}$,$VO_{C=40}$,$VC_{C=100}$,$VC_{C=200}$,$VC_{C=400}$,$VC_{C=800}$}
+                %\addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
+                %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
+            \legend{$VO\,10$,$VO\,5$,$VC\,1000$,$VC\,11$}
 		\end{axis}
 	\end{tikzpicture}
-  \caption{Percent chance that a VM is affected as storage nodes fail}
-  \label{fig-vm-failure}
+  \caption{Availability of VM backups as nodes fail for VO and VC models for varying average block link counts (i.e. average number of VMs that use a block)}
+  \label{fig-vm-availability}
 \end{figure}
+
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={CDS Replication affect on availability},
+		xlabel={Failed storage nodes},
+		ylabel={VM Availability (\%)},
+		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
+                mark options=solid,
+                legend style={
+                    cells={anchor=west}, %legend entry alignment
+                    legend pos=south west %legend position
+                }
+		]
+                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
+                \addplot[color=blue,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
+                \addplot[color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
+                \addplot[color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
+            \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Availability of VM backups as nodes fail in the VC model for different CDS Replication factors (Non-CDS replication fixed at 3, and average CDS block links set to 1000)}
+  \label{fig-cds-replication}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{figure}
+
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={VO Container links},
+		xlabel={Number of VMs},
+		ylabel={Avgerage Container links},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		]
+		\addplot[color=blue,mark=*] table[x=VMs,y=ContainerLinks] {figures/vo_container_links.txt};
+		%\legend{Measured,Theoretical};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Measured Average number of VMs sharing a container in the global index (for VO)}
+  \label{fig-vo-container-links}
+\end{figure}
+
 \comments{

### 2013-06-21 snapshot_system/background.tex

@@
 For VM snapshot backup, file-level semantics are normally not provided.
-Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. 
+Snapshot operations take place at the virtual device driver level, which
+means no fine-grained file system metadata can be used to determine the changed data. 
 %Only raw access information at disk block level are provided. 
@@
 %Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
-to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
+to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
 %use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
@@
 Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
-All of the above approaches have focused on
-optimization of deduplication efficiency, and none of them have considered the impact
-of deduplication for the fault tolerance in the cluster-based environment that we have considered
+All of the above approaches have focused on optimization of deduplication
+efficiency, and none of them have considered the impact
+of deduplication on fault tolerance in the cluster-based environment that we have considered
 in this paper.

### 2013-06-21 snapshot_system/result.tex

--- 2013-06-19 snapshot_system/result.tex
@@
 \section{Experiments}
+Our main test-bed is an cluster of 6 machines,
+each of which is equiped with a 8-core AMD FX-8120 at 3.1 GHz
+with 16 GB RAM, running Linux.
+A distributed file system (QFS) runs in the cluster manages six 3TB disks
+ with default replication degree set to 3.
+Our data set consists of 350 virtual machine image snapshots taken from Alibaba.com's
+public VM cloud in China. We select 35 VMs from the most popular 7 OSes: 
+Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
+For each OS, 5 VMs are chosen, and every VM come with 10 full snapshots.
 
-\subsection{Sampled Index}
+\subsection{Comparison with Other Approaches}
+\subsubsection{Sampled Index}
 One alternative approach to avoiding a single global index is to use a sampled
@@
 
-\subsection{Scalable Data Routing}
+\subsubsection{Scalable Data Routing}
 Another approach to avoiding a global index is to use a content-based hash

### 2013-06-21 snapshot_system/snapshot.tex

@@
 \end{table}
-
-\begin{figure}[ht]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={CDS Coverage},
-            xlabel={Total Data Stored (GB)},
-            ylabel={CDS Coverage (\%)},
-            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
-            %legend pos=outer north east,
-            legend columns=2,
-            legend style={
-                at={(0.5,-0.2)},
-            anchor=north}
-            ]
-            \addplot[color=blue,mark=*] table[x=InputSize,y=A1] {figures/cds_coverage.txt};
-            \addplot[color=blue,mark=square*] table[x=InputSize,y=A2] {figures/cds_coverage.txt};
-            \addplot[color=blue,mark=triangle*] table[x=InputSize,y=A4] {figures/cds_coverage.txt};
-            \addplot[densely dashed,color=red,mark=*] table[x=InputSize,y=T1] {figures/cds_coverage.txt};
-            \addplot[densely dashed,color=red,mark=square*] table[x=InputSize,y=T2] {figures/cds_coverage.txt};
-            \addplot[densely dashed,color=red,mark=triangle*] table[x=InputSize,y=T4] {figures/cds_coverage.txt};
-            \legend{Measured (1\%CDS),Measured (2\%CDS),Measured (4\%CDS),Predicted (1\%CDS),Predicted (2\%CDS),Predicted (4\%CDS)};
-            \end{axis}
-    \end{tikzpicture}
-  \caption{fixed-alpha predicted vs. actual CDS coverage as data size increases.}
-  \label{fig-vo-links}
-\end{figure}

### 2013-06-21 snapshot_system/intro.tex

@@
 Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
-(see Figure~\ref{fig:traditional-arch})
+(Figure~\ref{fig-traditional-arch})
 can effectively identify and remove content duplicates among snapshots, 
@@
     \includegraphics[width=3in]{images/traditional-arch.pdf}
-    \label{fig:traditional-arch}
+    \label{fig-traditional-arch}
     \caption{Traditional VM Backup System}
@@
 fact that the
-backup service collocates on the cloud cluster with a minimum resource usage (see Figure~\ref{fig:colocated-arch})
+backup service collocates on the cloud cluster with a minimum resource usage
+(Figure~\ref{fig-colocated-arch})
 %Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
@@
     \includegraphics[width=3in]{images/colocated-arch.pdf}
-    \label{fig:colocated-arch}
+    \label{fig-colocated-arch}
     \caption{Colocated VM Backup System}

### 2013-06-21 snapshot_system/failover.tex
Added to reliability section to start to tie together the graphs

@@
 
+To consider the reliability of VM backups in our model, we can consider the likely hood that a data chunk will fail,
+given some number of storage node failures. Every time a filesystem chunk fails,
+we say that we have lost data for that virtual machine, so it is no longer
+available. (in reality it may be only one snapshot that is affected, but it is the user
+who must decide which snapshots are important, so we consider the worst case). We use
+filesystem chunks rather than data blocks as our unit of failure because the DFS keeps
+filesystem chunks as its base unit of storage (in our case there are 16384 blocks in a
+filesytem chunk, with 4KB block size and a 64MB chunk size).
+
+We take the likelyhood of VM failure to be the same as the likelyhood of chunk failure,
+so
+\[
+    P_{VMfailure}=\frac{\binom{d}{r}}{\binom{p}{r}}
+\]
+
+Since both in the CDS and in the VO approach a single filesystem chunk may be used by many VMs,
+we must multiply the block failure ratio by the number of outgoing links for the block to get
+the expected impact on the system.
+\[
+    E_{VMfailure}=L\frac{\binom{d}{r}}{\binom{p}{r}}
+\]
+
+in our current testbed we have measured the average number of links
+per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{vo-container-links})
+in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
+was 11 using a 5\% CDS. From Figure~\ref{vo-container-links} you can see that as you add VMs, the average
+number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
+should continue to increase at a slower rate. For the VC model, we have to consider both CDS chunks and 
+Non-CDS chunks. In the VO model all data is shared, but in VC only the CDS data is shared, but at a much
+higher rate. This gives a strong advantage to VC, in that for a large percent of the data (95-99\%), there
+is only one VM pointing to each Non-CDS chunk. You can see the increase in reliability in Figure~\ref{fig-vm-availability}.
+The figure shows that even as the number of links to a CDS chunk increase by 100 times, the availability only decreases
+slightly, while in VO even small increases in $L$ causes a large decrease in availability. Figure~\ref{fig-cds-replication}
+shows the advantages of increasing the replication factor for CDS blocks. These figures together show
+the advantages of the VM-centric model, and the advantages that separating the replication factor for popular blocks
+can have on reliability.
+
 \begin{figure}[ht]
@@
 		xlabel={Failed storage nodes},
-		ylabel={VM Availability (\%)},
-		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
+		ylabel={VM Snapshot Availability (\%)},
+		extra y ticks={99.9}, %if important numbers are missing
                 mark options=solid,
@@
                 \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
-                \addplot[color=blue,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
-                \addplot[color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
-                \addplot[color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
+                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
+                \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
+                \addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
             \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}

### 2013-06-23 snapshot_system/failover.tex
revised analysis

@@
 file system~\cite{Hadoop,GFS}.
-in The VC approach, a special replica degree $r_c$ used for CDS blocks where $r_c>r$. 
-Noted that the storage cost for VO with full deduplication is $b_u *r$
-while it is
-\[ r*b*\delta(1 -   (\frac{k}{b_u})^{1-\alpha}) +k*(r-r_c).
+In the VC approach, a special replica degree $r_c$ used for CDS blocks where $r_c>r$. 
+Notice that the ratio of non CSD data size vs CDS data size for each VM is
+\[
+\sigma=  \frac{b*\delta(1 -   (\frac{k}{b_u})^{1-\alpha})} {k}.
 \]
 
+Thus  storage cost for VO with full deduplication is $b_u *r$ and for VC, it is
+\[ k*r_c  + k*\sigma *r
+\]
+
+In our experiment with Alibaba data, the ratio $\sigma$ 
+is 162. Thus allocation of extra replicas for CDS only introduces a small amount of extra space
+cost.  Figure~\ref{fig:storageCDS} shows the storage cost ratio of VC and VO when 
+$r$=3, and $r_c$ varies from 3 to 10.
+The result shows that the storage cost for adding extra replication for CDS
+is insignificant.
+Now we compare the fault resilience of VC and VO.
+
+\comments{
 For each rank $i$ block which appears $C_i$ times  among $V$ virtual machines.
@@
 \]
+}
 
 %Thus the number of VMs using a block =    $(1-s_c)  + s_c *L$.
+In characterizing the reliability of VM backups in our model, 
+we consider the likely hood that a file system block fails,
+given some number of storage node failures. 
+Every time a filesystem block fails,
+we say that we have lost data for that virtual machine, so it is no longer
+available. 
+(in reality it may be only one snapshot that is affected, but it is the user
+who must decide which snapshots are important, so we consider the worst case). 
+We use filesystem blocks rather than a deduplication
+data chunk as our unit of failure because the DFS keeps
+filesystem blocks as its base unit of storage (in our case there are 
+16384 blocks in a filesytem block on average, with 4KB block size and 
+a 64MB block size).
 
-When there are $r \le d<r_c$ machines failed and the probability of
-a container failure depends on if all replicas of this container reside in the failed machines.
-\begin{multline}
-Probability (\mbox{ a VM fails in VC})\\
-= 1- Probability (\mbox{ a VM has no data container loss}) \\
-= 1-  Probability(\mbox{ A container has no data loss})^{N_1}
+To  compute the probablity of losing a virtual machine, 
+we estimate the number of file system blocks per VM in each apporach.
+We can build a bipartite graph representing the association from unique file system blocks
+to their corresponding VMs. An association edge is  drawn  from a file block  to a VM 
+if this file is used by this VM. 
+For VC, let $N_1$ be the averge number of file system blocks for non-CDS data for each VM
+and  $N_2$ be the averge number of file system blocks for CDS data for each VM.
+For VO, let $N_o$ be the averge number of file system blocks for each VM
+and  let $V_o$ be the averge number of VMs shared by each file system block.
+Figure~\ref{fig:shared} illustates the bipartite association.
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.45\textwidth]{shared.pdf}
+\caption{Assoication of data blocks to VMs.}
+\label{fig:shared}
+\end{figure}
+
+Each non-CDS file system block is associated with one VM while CDS file system blocks are
+shared among VMs. 
+\[
+V *N_1 *s  = pD  \frac{\delta} {\delta +1}
+\]
+For CDS file blocks, there are at most $V$ VMs sharing, thus
+\[
+V *N_2 *s  \leq pD  \frac{1} {\delta +1} *V
+\]
+For the VO approach, 
+\[
+V *N_o *s  = pD  V_o.
+\]
+Then
+\[
+N_1= \frac{pD \delta} {V s (\delta +1)},\; 
+N_2 \leq \frac{pD } {s (\delta +1)}, \; 
+\mbox{and} N_o = \frac{pD V_o } {s V}.
+\]
+Since each file block (with default size $s=64MB$) contains many chunks (on average 4KB),
+each file block contains the hot low-level chunks shared by many VMs, and it also contains
+rare chunks which are not shared.
+Figure~\ref{fig:VOshared} shows the number of VMs shared by each file block.
+In our experiment, we find that $V_o \approx 0.2 V$ when backuping up VMs one by one.
+We can observe that $N_1 +N_2 << N_o$.
+If  the backup for multiple VMs is conducted concurrently, there would be more
+VMs sharing for each file block on average.
+
+Figure~\ref{fig-vo-links} shows the average number of links to 
+a given block in the global index as more VMs are added. 
+The first 15 VMs are all windows machines, so that explains the initial 
+higher values, but for the most part the average number of 
+links is between 1.5 and 2.
+
+\begin{figure}[ht]
+  \centering
+  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={VO Block links},
+		xlabel={Number of VMs added},
+		ylabel={Avg. Links to a Block},
+		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
+		legend pos=south east
+		]
+		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
+		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
+		\legend{Measured,Theoretical};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Average number of VMs sharing a block in the global index}
+  \label{fig-vo-links}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={VO Container links},
+		xlabel={Number of VMs},
+		ylabel={Avgerage Container links},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		]
+		\addplot[color=blue,mark=*] table[x=VMs,y=ContainerLinks] {figures/vo_container_links.txt};
+		%\legend{Measured,Theoretical};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Measured Average number of VMs sharing a container in the global index (for VO)}
+  \label{fig-vo-container-links}
+\end{figure}
+
+The availability of is a VM is the likelyhood that
+there is no  data loss for all its file blocks.
+With replication degree $r$, the likelyhood of
+a file block block is the probability that  
+all of its replicas appear in $d$ failed machines. 
+Namely, $\binom{d}{r}/ \binom{p}{r}$.
+
+When there are $r \le d<r_c$ machines failed, 
+%a file block failure depends on if all replicas of this container reside in the failed machines.
+the avaiability of a VM in the VC approach is
+\[
+(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
+\]
+%\begin{multline}
+%= Probability (\mbox{ There is no file block loss in this VM}) \\
+%= Probability(\mbox{ A file block has file data loss})^{N_1}\\
+%= (1- Probability (\mbox{all replicas of its block fail}))^{N_1}\\
+%\end{multline}
 %\end{split}
-\end{multline}
 
-%Probablity(\mbox { no loss for this  block}) = 1 - Probability (\mbox{ this block in d failed machiens})
-\begin{multline}
-%\begin{split}
-Probability(\mbox{A container no data loss})\\
-= 1- Probability (\mbox{ this container is in d failed machines})\\
-=  1- \frac{\binom{d}{r}} { \binom{p}{r} }.
+When $r_c \leq d$, the CDS file block in VC can also have a loss.
+The availability of  a VM in the VC approach is
+\[
+(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
+*
+(1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
+\]
+%= Probability(\mbox{ No non-CDS file block loss})^{N_1}
+%Probability(\mbox{ No CDS file block loss})^{N_2}\\
+%\begin{multline}
 %\end{split}
-\end{multline}
+%\end{multline}
 
-When $r_c \leq d$, the CDS data containers in VC can also have a loss. 
-\begin{multline}
-Probability (\mbox{ a VM fails in VC})\\
-= 1-  Probability(\mbox{ A container has no data loss})^{N_1}* \\
-Probability(\mbox{ A CDS container has no data loss})^{N_2}\\
-= 1 - 
-(\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
-*
-(\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2} 
-%\end{split}
-\end{multline}
+The availability of its VM  mbox in the VO approach is
+\[ 
+(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
+\]
 
-By comparison, the probability that a VM has data loss is close to
-1 once  there are  $d \ge r$ failed machines. That is because there are more data blocks
-shared among VMs. Any failure of these blocks causes many more VMs to fail.
+%By comparison, the probability that a VM has data loss is close to
+%1 once  there are  $d \ge r$ failed machines. That is because there are more data blocks
+%shared among VMs. Any failure of these blocks causes many more VMs to fail.
 
@@
 
-To consider the reliability of VM backups in our model, we can consider the likely hood that a data chunk will fail,
-given some number of storage node failures. Every time a filesystem chunk fails,
-we say that we have lost data for that virtual machine, so it is no longer
-available. (in reality it may be only one snapshot that is affected, but it is the user
-who must decide which snapshots are important, so we consider the worst case). We use
-filesystem chunks rather than data blocks as our unit of failure because the DFS keeps
-filesystem chunks as its base unit of storage (in our case there are 16384 blocks in a
-filesytem chunk, with 4KB block size and a 64MB chunk size).
-
+\comments{
 We take the likelyhood of VM failure to be the same as the likelyhood of chunk failure,
@@
 number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
-should continue to increase at a slower rate. For the VC model, we have to consider both CDS chunks and 
+should continue to increase at a slower rate. 
+For the VC model, we have to consider both CDS chunks and 
 Non-CDS chunks. In the VO model all data is shared, but in VC only the CDS data is shared, but at a much
@@
 is only one VM pointing to each Non-CDS chunk. You can see the increase in reliability in Figure~\ref{fig-vm-availability}.
-The figure shows that even as the number of links to a CDS chunk increase by 100 times, the availability only decreases
-slightly, while in VO even small increases in $L$ causes a large decrease in availability. Figure~\ref{fig-cds-replication}
+}
+
+The figure shows that even as the number of VMs sharing a CDS file block 
+increase by 100 times, the availability only decreases
+slightly.
+The key factor placed is that  $N_1 +N_2 << N_o$.
+The VM-centric approach packs  data blocks under one VM as much as possible
+and performs deduplication mainly within the same VM. The sharing part in CDS is replicated
+with a higher degree, which also signficantly increses the availability even a CDS file blcok
+is shared by every VM.
+
+% while in VO even small increases in $L$ causes a large decrease in availability. 
+Figure~\ref{fig-cds-replication}
 shows the advantages of increasing the replication factor for CDS blocks. These figures together show
@@
 
-We can build a bipartite graph representing the association from unique data blocks
-to their corresponding VMs. An association edge is  drawn  from a data block  to a VM 
-if this block is used by this VM, 
-The average incoming degree of VM nodes is equal to
-the average outgoing degree of data blocks, which is $L_c$.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.45\textwidth]{shared.pdf}
-\caption{Assoication of data blocks to VMs.}
-\label{fig:shared}
-\end{figure}
-
 Under $d$ failed machines, the  expected number of VMs 
@@
 }
-
-Figure~\ref{fig-vo-links} shows the average number of links to a given block in the global index as more VMs are added.
-The first 15 VMs are all windows machines, so that explains the initial higher values, but for the most part the average number of links is between 1.5 and 2.
-
-\begin{figure}[ht]
-  \centering
-  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={VO Block links},
-		xlabel={Number of VMs added},
-		ylabel={Avg. Links to a Block},
-		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
-		legend pos=south east
-		]
-		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
-		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
-		\legend{Measured,Theoretical};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Average number of VMs sharing a block in the global index}
-  \label{fig-vo-links}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={VO Container links},
-		xlabel={Number of VMs},
-		ylabel={Avgerage Container links},
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		]
-		\addplot[color=blue,mark=*] table[x=VMs,y=ContainerLinks] {figures/vo_container_links.txt};
-		%\legend{Measured,Theoretical};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Measured Average number of VMs sharing a container in the global index (for VO)}
-  \label{fig-vo-container-links}
-\end{figure}
 

### 2013-06-23 snapshot_system/snapshot.tex
revised analysis

--- 2013-06-20 snapshot_system/snapshot.tex
@@
 \hline
-$p$ & the number of nodes in the cluster\\
+$\sigma$ &  the percentage of $b_u$ unique items  stored in CDS.\\
 \hline
-$D$ & the amount of unique data on each node\\
+$p$ & the number of machines in the cluster\\
+\hline
+$D$ & the amount of unique data on each machine\\
 \hline
@@
 
-The  $k$ most popular fingerprints can cover the following number of blocks.
+The  $k$ most popular fingerprints can cover the following number of blocks after inner VM 
+deduplication.
 \[
@@
 \frac{ b(1-\delta) + C_1\frac{  k^{1-\alpha}} {1-\alpha}} 
-{b(1-\delta)  + sb - b_u }\\
+{b(1-\delta)  + \delta b - b_u }\\
 &= 
-\frac{ (1-\delta) + s (\frac{k}{b_u})^{1-\alpha}}
+\frac{ (1-\delta) + \delta  (\frac{k}{b_u})^{1-\alpha}}
 { 1- \frac{b_u}{b} }.
@@
 
-The overall deduplication effiency is
+The overall deduplication effiency of VC is
 \[
@@
             %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            mark options=solid,
             %legend pos=outer north east,
@@
             \addplot[color=blue,mark=square*] table[x=InputSize,y=A2] {figures/cds_coverage.txt};
-            \addplot[color=blue,mark=triangle*] table[x=InputSize,y=A4] {figures/cds_coverage.txt};
+            \addplot[color=blue,mark=triangle*,mark size=3] table[x=InputSize,y=A4] {figures/cds_coverage.txt};
             \addplot[densely dashed,color=red,mark=*] table[x=InputSize,y=T1] {figures/cds_coverage.txt};

### 2013-06-23 snapshot_system/snapshot.tex
change

@@
 \hline
-$\sigma$ &  the percentage of $b_u$ unique items  stored in CDS.\\
+$\sigma$ &  the number of uniqie non-CDS chunks over  the number of the CDS chunks.\\
 \hline
@@
 \hline
-$B$ & the average block size. Our setting is  4K.\\
+$B$ & the average data chunk size. Our setting is  4K.\\
 \hline
-$s$ & the average size of data containers stored in the distributed file system . Our setting is  64MB.\\
+$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
 \hline
@@
 $F$ & the size of an polular data index entry\\
+$N_1$ & the average number  of non-CDS file system blocks  in a VM\\
+$N_2$ & the average number  of CDS file system blocks  in a VM\\
+$N_o$ & the average number  of file system blocks  in a VM for VO\\
 \hline

### 2013-06-24 snapshot_system/eval1.tex
adding exper.

--- 2012-05-06 vm_snapshot_sim/2012eval.tex
@@
 
-We have implemented the snapshot deduplication scheme on the Aliyun's cloud platform.
-Objectives of our experimental evaluation are:
-1) Analyze the commonality of content data blocks and the popularity  of hot items. 
-2) Assess the effectiveness  of 3-level deduplication for reducing the storage cost of snapshot 
-backup. 
-3) Examine the impacts of CDS size on deduplication ratio.
+We have implemented and evaluated a prototype of our VO scheme on a Linux cluster
+of 8-core AMD FX-8120 at 3.1 GHz with 16 GB RAM. 
+Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
+Each machine  is equiped with a 
+a distributed file system (QFS) running in the cluster manages six 3TB disks
+with default replication degree set to 3. The CDS replication is set to 5.
+Objectives of our evaluation are:
+1) Study the deduplication efficiency of the VC approach and compare with an alternative
+design.
+2) Evaluate the backup throughput performance VC  for a large number of VMs.
+%Compare with the data domain approach~\cite{bottleneck08}.
+3) Examine the impacts of VC for fault isolation.
 
-\subsection{Experimental setup}
+%\section{Experiments}
+%Our main test-bed is an cluster of 6 machines,
+%Our data set consists of 350 virtual machine image snapshots taken from Alibaba.com's
+%public VM cloud in China. 
+%We select 35 VMs from the most popular 7 OSes: 
+%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
+%For each OS, 5 VMs are chosen, and every VM come with 10 full snapshots.
+%\subsection{Experimental setup}
 
-At Aliyun our target is to backup cluster up to 1000 nodes
-with 25 VMs on each.
+\comments{
 %We are running our deduplication/backup  service on 100 nodes.
@@
 %the CPU usage is very small during the experiments. 
-Based on the data studied,  each VM has about  40GB of storage  data usage on average,
-OS disk and data disk each takes about 50\% of storage space.
-The backup of VM snapshots is completed within two hours every day,
-and that translates to a backup throughput of 139GB per second, or 500TB per hour.
+We have performed a trace-driven study using  a 1323 VM dataset  collected from 
+%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
+a cloud cluster at Alibaba's Aliyun.
+ ~\cite{WeiZhangIEEE}.
+% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
 For each VM, the system keeps 10 automatically-backed snapshots in the storage while
 a user may instruct extra snapshots to be saved.
+Each VMs uses   one of the most popular 7 OSes: 
+Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
+The backup of VM snapshots is completed within a few  hours every night.
+Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
+including OS and user data disk.
+Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
+variable-sized content blocks  with an average size of 4KB.
+%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
+The signature for variable-sized blocks is computed using their SHA-1 hash.
+
+The seek cost of each random IO request in our test machines is about  10 milliseconds.
+The average I/O usage of local storage is controlled about 50MB/second for backup 
+in the presence of other I/O jobs. Noted that a typical 1U server can host
+6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
+of local storage bandwidth. 
+The final snapshots are stored in a distributed file system built on the same 
+cluster.
+
+The total local disk usage on each machine is about 8GB for the duplicate detection purpose,
+mainly for global index. 
+Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
+block-wise full deduplication removes about additional 74.5\% of duplicates.
+The final content copied to the backup storage is reduced by 94.4\% in total.
+}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.4\textwidth]{mem_time.pdf}
+%\caption{ Parallel time when memory limit varies.}
+%\label{fig:memory}
+%%\end{figure}
+%
+%Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
+% a 100-node cluster a  when
+
+\subsection{Settings}
+We have performed a trace-driven study using  a 1323 VM dataset  collected from 
+100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
+The production environment tested has  about 1000 machines with 25 VMs on each machine.
+%We are running our deduplication/backup  service on 100 nodes.
+%Memory usage is about 150MB space per node during backup and
+%the CPU usage is very small during the experiments. 
+% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
+For each VM, the system keeps 10 automatically-backed snapshots in the storage while
+a user may instruct extra snapshots to be saved.
+%Each VM uses   one of the most popular 7 OSes: 
+%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
+The backup of VM snapshots is completed within a few  hours every night.
+Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
+including OS and user data disk.
+All data are divided into 2 MB fix-sized segments and each segment is divided into 
+variable-sized content chunks ~\cite{similar94,rabin81} with an average size of 4KB.
+The signature for variable-sized blocks is computed using their SHA-1 hash. 
+Popularity of data blocks are collected through global counting 
+and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.
+%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
+%The signature for variable-sized blocks is computed using their SHA-1 hash.
+
+%The seek cost of each random IO request in our test machines is about  10 milliseconds.
+%The average I/O usage of local storage is controlled about 50MB/second for backup 
+%in the presence of other I/O jobs. Noted that a typical 1U server can host
+%6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
+%of local storage bandwidth. 
+%The final snapshots are stored in a distributed file system built on the same 
+%cluster.
+
+%Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
+%block-wise full deduplication removes about additional 74.5\% of duplicates.
+%The final content copied to the backup storage is reduced by 94.4\% in total.
+%Based on the data studied,  each VM has about  40GB of storage  data usage on average,
+%OS disk and data disk each takes about 50\% of storage space.
+%The backup of VM snapshots is completed within two hours every day,
+%and that translates to a backup throughput of 139GB per second, or 500TB per hour.
+%For each VM, the system keeps 10 automatically-backed snapshots in the storage while
+%a user may instruct extra snapshots to be saved.
 
@@
 
-All data are divided into 2 MB fix-sized segments and each segment is divided into 
-variable-sized content blocks ~\cite{similar94,rabin81} with an average size of 4KB.
-The signature for variable-sized blocks is computed using their SHA-1 hash. 
-Popularity of data blocks are collected through global counting 
-and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.
+\subsection{Deduplication Efficiency}
 
-\comments{
-a storage dataset of 1323 VM users collected from 100 Aliyun's cloud nodes to evaluate the effectiveness.
-In this dataset, there are 10 snapshots per each VM user and the total amount of space investigated 
-is 23.5 terabytes.
-Each VM file is  divided into content blocks of
-variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
-The signature for variable-sized blocks is computed using  their SHA-1 hash. 
-Each segment is of size 2MB.  
-Popularity is computed by using 90\% of dataset, which reflects our setting that the system recomputes
-CDS every 1-2 days to catch up the popularity trend.
-}
-%seg, and we performed global perfect deduplication 
-%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
-%and maximum block size
-%OS data
-%user data: zipf
-%prediction
-%say something about aliyun
-
-%To compare the effectiveness with a full deduplication approach with an approximation,
-%we use  extreme binning and perfect deduplication~\cite{extreme_binning09}. 
-%For perfect deduplication and extreme binning, each snapshot is also divided into chunk blocks
-%using TTTD with an average size of 4KB. The original extreme binning work uses the whole file
-%as the input unit and  this size is too big in our system. 
-%Thus we split each image snapshot file into variable-sized segments base on the block hash list, 
-%using TTTD with average size of 2MB.
-
-\subsection{Effectiveness of 3-level Deduplication}
-
-\begin{figure}
-  \centering
-  \epsfig{file=images/overall_effect.eps, width=3.5in}
-  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
-deduplication divided by the original data size and the unit is percentage. }
-
-  \label{fig:overall}
-\end{figure}
+%\begin{figure}
+%  \centering
+%  \epsfig{file=images/overall_effect.eps, width=3.5in}
+%  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
+%deduplication divided by the original data size and the unit is percentage. }
+%  \label{fig:overall}
+%\end{figure}
 
@@
 
-\begin{figure}
-  \centering
+%\begin{figure}
+%  \centering
  %\epsfig{file=images/os_cds_sim.eps, width=3in}
-  \epsfig{file=images/3level_os.eps, width=3.5in}
-  \caption{Impact of 3-level deduplication for OS releases.}
-  \label{fig:oscds}
-\end{figure}
+%  \epsfig{file=images/3level_os.eps, width=3.5in}
+%  \caption{Impact of 3-level deduplication for OS releases.}
+%  \label{fig:oscds}
+%\end{figure}
 
@@
 
-\subsection{Coverage of common data blocks}
+\subsection{Comparison with Other Approaches}
+\subsubsection{Sampled Index}
+One alternative approach to avoiding a single global index is to use a sampled
+index. This is the approach taken by Guo and Efstathopoulos\cite{Guo2011}. We
+compare their solution to ours by running their algorithm on our 350 traces
+using a sampling rate of 1 out of 101 blocks, and always including the first
+block in a container (which we fix at 16MB in size). The results of running this
+test are shown in Table~\ref{??}, and the memory usage comparison can be found
+Sec.~\ref{??}. Our results show that using a sampled index achieves a very high
+rate of deduplication, and so a sampled index might be a good way to do dedup
+in a single node setup.
 
-%We study characteristics of common data blocks among snapshots of VM users
-%and examine the impacts if we only store a relative small amount of common data blocks to be sored in the CDS server.
-%There are two advantages to exploit this.
-%First, a smaller CDS reduces overall resource requirement while covering  most of data blocks in snapshots.
-%Second a smaller CDS makes the fault tolerance management  easier because we can replicate  more copies
-%to mitigate the failure.
+The problems for sampling are in distributing the
+algorithm and in deduplicating extremely large bodies of data. The algorithm
+stores the entire (sampled) index in memory, which is required for high
+throughput to avoid the disk-bottleneck problem - since the index itself has no
+locality information, lookups are essentially random, so the index must be
+somehow optimized to prevent excessive disk seeking (the sampling algorithm does
+this by storing the index in memory). To distribute this index, each node would
+either require a complete copy of the index which would have a prohibitive cost in
+memory, or something like memcached must be used, which leaves the same problem
+as the disk bottleneck with every index check potentially using the network.
+The difficulty in storing extremely large bodies of data
+is related, as once 1PB is stored in the system, assuming a sampling rate of 
+1/101 with 22 byte index entires, 55GB of (in memory) index are required.
 
-%We consider each virtual disk contains two parts: OS partition and regular user data partition
-%and study their characteristics seperately.
-%In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus  one or more data disks.
-%During VM's creation, its OS disk is directly copied from user's choosen base image.
-%Since  they dare brought by the operating system and popular 
-%software installations,  they are rarely modified or deleted.
-%base image data as a hint.
-%Through users may change configurations, install software, or write user data into OS disk,
-%but most of the OS related data shall keep unchanged.
+Our solution uses more total memory (??how much??), but is more scalable both in
+terms of capactity and distributing the deduplication. The only part of our
+algorithm which requires significant network traffic is the CDS deduplication,
+but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
+so is only done for a small percent of blocks (?? 5-10\% ??).
 
-%Previous study has also supported this\cite{vmimage}. Therefore, we can let all OS disks share these
-%common data in their snapshot backups.
-%We choose user's data disks rather than OS disks in thie experiment for several reasons: First, the data in OS disks are 
-%instinctively highly similar, because most of the VM users only make some common or unique but tiny changes to their OSes,
-%so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
-%Second, the data disks are way more important in terms of data safty and backup because they are 
-%what users really care about.
+\subsubsection{Scalable Data Routing}
+Another approach to avoiding a global index is to use a content-based hash
+partitioning algorithm to break up the deduplication work. This approach is
+taken by Dong et al. in their Scalable Data Routing paper, and is similar to
+Exreme Binning\cite{??}\cite{extreme_binning09}. We compared our solution to
+content-based hash partitioning by running the algorithm on our set of 
+traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
+the minhashes of the superchunks for routing. The results of this are shown in
+Table~\ref{??}. Routing each chunk to a bin provides good deduplication
+efficiency, and only requires each storage node to keep an index of local data
+and the bin mapping, but misses significant opportunities in our indended use
+case.
 
-%Furthermore, our study on user's data disks has shown that the duplication pattern of
-%variable-sized data blocks follows \emph{Zipf-like} distribution. As a result, the major portion of 
-%deduplication effect will emerge from eliminating the duplication of frequently seen data.
-%define CDS
-
-\comments{
-\begin{figure}[htbp]
-\centering
-%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
-%\epsfig{file=images/log-log.disk.eps, width=3in}
-\epsfig{file=images/datadisk.count_rank.eps, width=3.5in}
-\caption{Duplicate count  of common data blocks in a log scale.}
-\label{fig:zipf-data}
-\end{figure}
-Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
-terms of the duplication count. $Y$ axis is the popularity of a data block in log scale 
-measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
-sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
-The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.
-
-\begin{figure}
-\centering
-%\epsfig{file=images/log-log.35vmos.eps,  width=3in}
-%\epsfig{file=images/35os.count_rank.eps, width=3in}
-\epsfig{file=images/35vmos.count-rank.eps,width=3.5in}
-\caption{ Duplicate count of  common OS blocks in a log scale.}
-\label{fig:OSpopular}
-\end{figure}
-Figure \ref{fig:OSpopular} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
-$Y$ axis is the popularity of an OS block in a log scale 
-measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
-sorted by their duplicate rank.  For the top ranked blocks, there is a flat line in terms of duplicate counts. That
-is because there are a large number of OS blocks which have appear in all copies of such OS releases.
-
-}
-
-\begin{figure}
-\centering
-\epsfig{file=images/ay41a_big.data_disk.cdf.eps, width=3.5in}
-%\epsfig{file=images/cdf.disk.v4.eps, width=3in}
-%\epsfig{file=images/datadisk.count_rank.eps, width=3in}
-%\epsfig{file=images/35os.count_rank.eps, width=3in}
-
-\caption{Cumulative  coverage of popular common user data blocks.}
-\label{fig:userdatacoverage}
-\end{figure}
-
-One of our biggest advantage is small memory footprint for deduplication, because we only
-eliminate a small amount of highly popular data.
-we use dataset2 to demonstrate the coverage of popular data blocks on user-related data, 
-as shown in Figure \ref{fig:userdatacoverage}.
-%content blocks used in image files using 90\% of
-%the collected dataset.
-%Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular common user data blocks. 
-The $X$ axis is the rank of common user data blocks, and $Y$ shows how much raw data can be covered given
-the size of CDS.
-Let $S_i$ and $F_I$ be the size and duplicate count 
-of the $i$-th block ranked by its duplicate rank.  Then $Y$ axis is the coverage of
-the common dataset covering data items from rank 1 to rank $i$. Namely  
-\[
-\frac{ \sum_{i=1}^{i} S_i * F_i} {\mbox{Total data size}}.
-\]
-
-Thus with about 1\% of blocks on data disks, CDS can cover about 38\% of total data blocks
-appeared in all data snapshots. The corresponding CDS index uses no more than 150MB memory per machine,
-which can be easily co-located with other cloud services.
-
-%Figure~\ref{fig:OSdatacoverage} shows the cumulative coverage  ratio of  popular common OS blocks. 
-%From both graphs, a small number of most popular common blocks can coverage a large percentage of 
-%snapshot blocks and thus the size of CDS can be chosen to be small while still having a large
-%coverage.
-
-%\begin{figure}
-%\centering
-%\epsfig{file=images/ay41a_small.os_incremental.cdf.eps, width=3in}
-%\caption{ Cumulative  coverage of popular common OS disk blocks.}
-%\label{fig:OSdatacoverage}
-%\end{figure}
-
-%We define \emph{OS CDS} to be the unchanged data across the base VM image and the snapshots of all
-%OS disks which are derived from it. Such data are brought by the operating system and popular 
-%software installations, they are rarely modified or deleted, and can be easily extracted using 
-%base image data as a hint.
-
-Because there are a limited number of OS releases, we study common blocks among
-OS disks loaded with  the same OS release. 
-%The selection of CDS is completed by separating OS disk and data disk.
-%While block commonality among data disks may be affected in some degree
-% when we scale up the number of total VMs  to be supported,
-%we expect that  the block commonality among OS disks still remains to be high and  
-%%can be well covered by a fixed CDS because users still adopt common OS releases.
-%we choose 7 major OSes in Aliyun's
-%VM cloud platform and they are: 
-%Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
-%distributions are 64 bits).
-%we examine 5 VM user disks from each OS, and 10 snapshots for each VM. These VMs have been actively used by their
-%owners. Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
-%their OS disks. 
-%For example, some Ubuntu OS disks have only 2GB of data while some have 50GB.
-%For each OS, the base image and all OS
-%disk snapshots are divided into variable-sized blocks. Then 
-In  Figure~\ref{fig:OSunchanged},  we list a conservative  commonality study in 7 major OS versions  supported
-in Aliyun.
-%We consider the earlier snapshot for each OS disk as the base image.
-For every block in the base image, we classify this block as ``unchanged''
-if this block has appeared in all snapshots of the same OS release even they are used by different VMs.
-Figure \ref{fig:OSunchanged} shows that for each
-OS,  at least 70\% of OS blocks are completely unchanged among all snapshots of the same OS. 
-Some latest release  of OS tends to have a higher percentage of content change
-while  old release tends to have more variations of content versions.
-That can be interpreted as that users with very old  version of operating systems
-have a lower tendency to update their OS versions and this causes a larger discrepancy
-among OS snapshots of these users.
-
-%into the unchanged category of OS data.
-
-\begin{figure}
-\centering
-\epsfig{file=images/os_subset.eps, width=3.5in}
-\caption{Percentage of completely common blocks among different VMs for the same OS release.}
-\label{fig:OSunchanged}
-\end{figure}
-
-Based on the above analysis, we have selected a small set of most popular
-OS blocks, which is about 100GB OS data and its corresponding CDS index takes about 1GB memory space in total.
-They can cover sufficiently over 70\% of OS-related data.
-
-%Then we use this CDS to run the deduplication process again.
-%That correspond to about  80GB of OS blocks and its corresponding CDS meta occupies 800MB in the cache.
-%  data from 350 OS disk snapshots,
-
-%The above analysis is only an estimation of OS and software related common data, 
-%some user installed software may not be discovered by this method because they are not 
-%included in the base image. However, as we can see in the next section, 
-%the overall duplication of user generated data
-%follows the Zipf-like distribution, thus all popular data can be discovered by statistic analysis.
-
-%Zipf's law has been shown to characterize use of words in a natural language, city populations, 
-%popularity of website visits and other internet traffic data.
-
-%Here we present the first fully consistent empirical study showing that data duplication
-%pattern in very large scale storage follows Zipf-like distribution. More specifically,
-%we show that the duplication count of any unique data block is inversely proportional to its rank
-%in the frequency table, with $\alpha$ smaller than unity. 
-%As far as we know, this is the first study of large scale real user data to disclose
-%the Zipf-like distribution pattern in data storage area.
-
-%\subsubsection{The model}
-%Consider a general storage system that holds user's files without any deduplication. 
-%Let $N$ be the total number of unique data blocks after 
-%content-defined chunking and deduplication, 
-%$C_N(i)$ be the number of duplicate copies that the $i$th data block being
-%stored in storage, given all the unique data blocks be ranked in order of their number of duplicate copies.
-%Let $S_i$ be the size of $i$th block,
-%then the actual ranking of the $i$th block is reflected by $\sum_{1}^{i-1}S_i$.
-
-%\subsubsection{Methodology}
-%1323 users' virtual data disks were scanned using TTTD content-defined chunking, and we performed global perfect deduplication 
-%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
-%and maximum block size, all variable-sized blocks are compared by their SHA-1 hash arther than real data.
-%
-%We choose user's data disks rather than OS disks in thie experiment for several reasons: First, the data in OS disks are 
-%instinctively highly similar, because most of the VM users only make some common or unique but tiny changes to their OSes,
-%so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
-%Second, the data disks are way more important in terms of data safty and backup because they are 
-%what users really care about.
-
-\comments{
-\subsection{Discussion}
-By storing the hash index of a small set of hottest data (CDS), we expect to achieve great 
-deduplication effect with minimal cost.
-But one problem of the CDS is what we called \emph{blind spot}: the update of CDS is always 
-behind new data's arrival,
-as a result, some data must have been written to the backup store before being collected into CDS, thus such 
-duplication may comprise the effect of
-CDS. For instance, when a MySQL update is released, some users may apply it very quickly, so the new hot data bring by
-this update will not be filtered by CDS. Only until later our CDS update includes those new data, then the rest of MySQL users get benefited.
-We can take a few measurements to reduce the impact of blind spot. First, the data in blind spot will not accumulate, because snapshots backup
-is a paid service, so over the long term, data in blind spot will be removed from backup store as VMs and old snapshots keep being deleted.
-Second, for the major OS updates, we can anticipate them in advance by putting the new hot data into CDS before users widely adopt them.
-
-Another problem associated with CDS is that some data in CDS may no longer be popular or even disappear
-as time goes. For example, an MySQL software update may invalidate some data that we previously hold in 
-the CDS. If some data blocks in CDS are no longer referenced, our map-reduce process is able to detect
-this situation, so invalid data will be removed and new data will be added during the next CDS update. 
-But if some users choose to keep their old MySQL version, then the corresponding old and new data will co-exist in the CDS.
-}
-
-%In our snapshot deduplication architecture, CDS is the key to achieve greater deduplication than
-%incremental backup solutions. Our basic assumption of CDS us that VM disks, especially OS disks,
-%have huge amount of data in common, and such common data can be represented by a relatively smaller data set
-%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
-%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
-%the effectiveness of CDS using real user VM disks from our production VM cluster.
-
-\subsection{A comparison of perfect and CDS-based deduplication }
-%Figure~\ref{fig:pd} shows the compression ratio of perfect deduplication at different dataset sizes
-%as we vary the data size from about 4 terabytes to about 23.5 terabytes.
-After level-1 and level 2 elimination, we find that 
-the complete deduplication would reduce the storage cost further by 50\%. 
-If we put all these unique data into CDS, 
-we could achieve complete deduplication,
-but fingerprint lookup in such huge CDS hash index would become a bottleneck as discussed in many pervious works. 
-So we use dataset2 to evaluate how much space saving of 
-deduplication can be achieved when varying the CDS size.
-%\begin{figure}
-%  \centering
-%  \epsfig{file=images/dedup_ratio.eps, height=2in, width=2.66in}
-%  \caption{Perfect deduplication on data disks}
-%  \label{fig:pd}
-%\end{figure}
-
-%We rank unique data blocks by their duplication count, and choose the hottest blocks as CDS. 
-Figure \ref{fig:datacdssize} shows the relationship between CDS cache size and relative space saving ratio
-compared to the full deduplication.  The unit of CDS size is gigabytes.
-We define \emph{space saving ratio} as the space saving of CDS method divided by 
-full deduplication space reduction. 
-With a 100GB CDS data (namely 1GB CDS index) can still  accomplish about 75\% 
-of what perfect deduplication can do.
-%But this effect decreases when more data are added to CDS. 
-%The lower bound of CDS space saving ratio is 50\%, which is very easy to accomplish.
-
-\begin{figure}
-  \centering
-  \epsfig{file=images/uniquedata-saving.eps, width=3.5in}
-  \caption{Relative ratio of space size compared to full deduplication when CDS size changes.}
-  \label{fig:datacdssize}
-\end{figure}
-
-%CDS size is restricted by system memory resource.
-With dataset2, Figure \ref{fig:datacds} shows how CDS space saving ratio
-compared to the full deduplication is affected by the dataset size. 
-%The calculation is done after level 1 and level 2 deduplication.
-In this experiment we first set out a goal of space saving ratio completed, 
-then watch how much data needs to be placed in CDS cache to achieve this goal.
-From the graph we can see a 75\% saving ratio lead to a stable ratio between 
-CDS size and data size, which requires 1\% of data to be placed in CDS.
-
-When we deal with a large cluster of 1,000 nodes, we expect that using
-1\% of data disks can cover more than what we have seen from this
-1323 VM dataset, assuming that the average behavior of every subcluster with 100 machines
-exhibits a similar commonality. 
-In addition to this, CDS for OS disks will become even more effective when
-there are more VMs sharing the same collection of OS releases. 
-%Base on above data we can estimate the size of data CDS and its effect. 
-%Currently we prepared 500MB memory per machine to store CDS meta, then it can represent 50GB of data. 
-%If we assume each VM has 30GB of user data at runtime, and we host 25 VMs per machine, 
-% maintain 10 snapshots per VM, each brings 10\% additional modified data. 
-%Thus the user data in snapshot system is 1.5TB per machine. So the upper bound of 
-%$CDS size/ Data size = 0.033$, which is sufficient for the 75\% saving goal.
-
-\begin{figure}
-  \centering
-  \epsfig{file=images/cds_scale.0.7.eps, width=3.5in}
-  \caption{The relative size ratio of  CDS over the data size. }
-  \label{fig:datacds}
-\end{figure}
-
-%Unlike the CDS of OS disks which is mainly composed of OS related data thus highly predictable, 
-%data disks is unpredictable because we cannot control what user can put in there. But we still
-%suspect that highly duplicated data in existing data are very likely to be duplicated again.
-%So we randomly pick 50 out of 1322 data disks as the new data, and use the rest as existing data
-%to extract CDS. Using 1.5\% as CDS threshold, we see the total 1198GB of new data is reduced by 
-%755.8GB, while perfect deduplication can reduce 1017.4GB. So 74.3\% of duplicate blocks are eliminated 
-%by pre-trained CDS, which is quite satisfactory.
+The problem with the Data Routing algorithm is in the very high network traffic.
+Our intended use case is a backup system which runs alongside a number of VMs,
+in order to save costs. Data Routing makes no use of the inherent locality in
+such a system, and therefore puts a much higher network burden on machines which
+are also running 35 VMs each. This will reduce the available network bandwidth
+to users of the VMs, and/or reduce the possible deduplication throughput.

### 2013-06-24 snapshot_system/abs.tex
modify all sections

@@
 \begin{abstract}
-A cloud environment that  hosts a large number of  virtual machines has
+A cloud environment that  hosts a large number of  virtual machines (VMs) has
 a high storage demand for frequent backup of system image snapshots.
 Deduplication of data blocks can lead a big reduction of redundant blocks when
-their signatures are identical. However it is expensive and less fault-resilient to perform a global comparison
-of all data block signatures and let a data block share by many virtual machines. 
-This paper studies a cluster-based design which collocates a lightweight
-backup service with the cloud service and integrates multiple duplicate detection strategies that  
+their signatures are identical. However it is expensive and less fault-resilient to perform a global deduplication
+using signatures and let a data block share by many virtual machines. 
+This paper studies a cluster-based VM-centric scheme which collocates a lightweight
+backup service with the cloud service and it integrates multiple duplicate detection strategies that  
 localize the deduplication as much as possible within each virtual machine.
-Our analysis shows that  this virtual machine centric scheme uses a small amount of memory resource to conduct duplicate detection
-and can  provide  better fault tolerance through deduplication localization.  
+It also organizes the write of small data chunks into large file system blocks so
+that each underlying file block is associated with one VM for most of cases.
+Our analysis shows that  this VM centric scheme 
+can  provide  better fault tolerance while using a small amount of computing and storage resource. 
 This  paper  provides a comparative evaluation of this scheme in  accomplishing a high deduplication 

### 2013-06-24 snapshot_system/background.tex
modify all sections

@@
 content~\cite{venti02,Rhea2008}.  Offline deduplication is 
-used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
+used in ~\cite{EMC,NetAppOffline} to remove previously written duplicates during idle time.
 %,NGmiddleware2011}.
@@
 fingerprints. For example, the data domain method ~\cite{bottleneck08} 
-uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
+uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
 accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.

### 2013-06-24 snapshot_system/challenge.tex
modify all sections

@@
 %Base on Aliyun's production environment, the snapshot backup job has to satisfy
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=3in]{images/colocated-arch.pdf}
+    \label{fig-colocated-arch}
+    \caption{Collocated VM Backup System}
+\end{figure}
+
 \begin{itemize}
 \item {\em Collocating with cluster-based cloud services.}
-We collocate the backup service with other cloud serices in a cluster
+We collocate the backup service with other cloud services in a cluster
 and use a distributed file system~\cite{GFS2004,Hadoop} to 
@@
 
-Since the block size in the Hadoop and GFS is uniform and large with 64MB as a default setting,
-the content block in a deduplication system is of nonuniform size with 4KB or 8KB on average.
+Since the file block size in the Hadoop and GFS is uniform and large with 64MB as a default setting,
+the content chunk in a deduplication system is of nonuniform size with 4KB or 8KB on average.
 We need to build an intermediate layer that supports large snapshot writing with append operations
@@
 and we can leverage existing open-source software to implement such a layer.
-When the number of machines failed exceeds the replication degree, there may be
+When the number of machines failed exceeds the replication degree, there could be
  some data loss.  Storage deduplication worsens the impact of such faults
 because  the majority of each snapshot (e.g. over 90\%) is deduplicated
-and the corresponding data blocks are shared among VMs.
+and the corresponding data chunks stored in the underlying file blocks
+are shared by many VMs. 
+%The failure of one data chunk or block can impact many sharing VMs. 
+In large scale cloud, machine failures happen at daily basis,
+the loss of a shared chunks can affect many VM users whose snapshots share this 
+data block.
 
@@
 % since storage for shared identical content chunks can become a failure point.
-In large scale cloud, node failures happen at daily basis,
-the loss of a shared block can affect many users whose snapshots share this 
-data block. 
 Without any control of such data sharing, we can only increase  
@@
 but this incurs significantly higher costs.
-Loss of a small number of shared data blocks can 
+Loss of a small number of shared data chunks can 
 cause the unavailability of snapshots for a large number of virtual machines.
@@
 noticeable contention for resources with the existing cloud, which is not
-preferred and may not not be acceptible for production system operation. 
+preferred and may not not be acceptable for production system operation. 
 Thus it is desirable that backup for all nodes

### 2013-06-24 snapshot_system/compare.tex
modify all sections

--- 2013-06-24 snapshot_system/eval1.tex
@@
-\section{Evaluation}
-\label{sect:exper}
+\section{A Comparison  with Other Approaches}
 
-We have implemented and evaluated a prototype of our VO scheme on a Linux cluster
-of 8-core AMD FX-8120 at 3.1 GHz with 16 GB RAM. 
-Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
-Each machine  is equiped with a 
-a distributed file system (QFS) running in the cluster manages six 3TB disks
-with default replication degree set to 3. The CDS replication is set to 5.
-Objectives of our evaluation are:
-1) Study the deduplication efficiency of the VC approach and compare with an alternative
-design.
-2) Evaluate the backup throughput performance VC  for a large number of VMs.
-%Compare with the data domain approach~\cite{bottleneck08}.
-3) Examine the impacts of VC for fault isolation.
-
-%\section{Experiments}
-%Our main test-bed is an cluster of 6 machines,
-%Our data set consists of 350 virtual machine image snapshots taken from Alibaba.com's
-%public VM cloud in China. 
-%We select 35 VMs from the most popular 7 OSes: 
-%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
-%For each OS, 5 VMs are chosen, and every VM come with 10 full snapshots.
-%\subsection{Experimental setup}
-
-\comments{
-%We are running our deduplication/backup  service on 100 nodes.
-%Memory usage is about 150MB space per node during backup and
-%the CPU usage is very small during the experiments. 
-We have performed a trace-driven study using  a 1323 VM dataset  collected from 
-%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
-a cloud cluster at Alibaba's Aliyun.
- ~\cite{WeiZhangIEEE}.
-% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
-For each VM, the system keeps 10 automatically-backed snapshots in the storage while
-a user may instruct extra snapshots to be saved.
-Each VMs uses   one of the most popular 7 OSes: 
-Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
-The backup of VM snapshots is completed within a few  hours every night.
-Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
-including OS and user data disk.
-Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
-variable-sized content blocks  with an average size of 4KB.
-%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
-The signature for variable-sized blocks is computed using their SHA-1 hash.
-
-The seek cost of each random IO request in our test machines is about  10 milliseconds.
-The average I/O usage of local storage is controlled about 50MB/second for backup 
-in the presence of other I/O jobs. Noted that a typical 1U server can host
-6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
-of local storage bandwidth. 
-The final snapshots are stored in a distributed file system built on the same 
-cluster.
-
-The total local disk usage on each machine is about 8GB for the duplicate detection purpose,
-mainly for global index. 
-Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
-block-wise full deduplication removes about additional 74.5\% of duplicates.
-The final content copied to the backup storage is reduced by 94.4\% in total.
-}
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.4\textwidth]{mem_time.pdf}
-%\caption{ Parallel time when memory limit varies.}
-%\label{fig:memory}
-%%\end{figure}
-%
-%Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
-% a 100-node cluster a  when
-
-\subsection{Settings}
-We have performed a trace-driven study using  a 1323 VM dataset  collected from 
-100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
-The production environment tested has  about 1000 machines with 25 VMs on each machine.
-%We are running our deduplication/backup  service on 100 nodes.
-%Memory usage is about 150MB space per node during backup and
-%the CPU usage is very small during the experiments. 
-% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
-For each VM, the system keeps 10 automatically-backed snapshots in the storage while
-a user may instruct extra snapshots to be saved.
-%Each VM uses   one of the most popular 7 OSes: 
-%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
-The backup of VM snapshots is completed within a few  hours every night.
-Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
-including OS and user data disk.
-All data are divided into 2 MB fix-sized segments and each segment is divided into 
-variable-sized content chunks ~\cite{similar94,rabin81} with an average size of 4KB.
-The signature for variable-sized blocks is computed using their SHA-1 hash. 
-Popularity of data blocks are collected through global counting 
-and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.
-%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
-%The signature for variable-sized blocks is computed using their SHA-1 hash.
-
-%The seek cost of each random IO request in our test machines is about  10 milliseconds.
-%The average I/O usage of local storage is controlled about 50MB/second for backup 
-%in the presence of other I/O jobs. Noted that a typical 1U server can host
-%6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
-%of local storage bandwidth. 
-%The final snapshots are stored in a distributed file system built on the same 
-%cluster.
-
-%Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
-%block-wise full deduplication removes about additional 74.5\% of duplicates.
-%The final content copied to the backup storage is reduced by 94.4\% in total.
-%Based on the data studied,  each VM has about  40GB of storage  data usage on average,
-%OS disk and data disk each takes about 50\% of storage space.
-%The backup of VM snapshots is completed within two hours every day,
-%and that translates to a backup throughput of 139GB per second, or 500TB per hour.
-%For each VM, the system keeps 10 automatically-backed snapshots in the storage while
-%a user may instruct extra snapshots to be saved.
-
-% the system must finish saving daily snapshots of all VMs in 2 hours.
-In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.
-
-%In our snapshot deduplication architecture, CDS is the key to achieve greater deduplication than
-%incremental backup solutions. Our basic assumption of CDS us that VM disks, especially OS disks,
-%have huge amount of data in common, and such common data can be represented by a relatively smaller data set
-%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
-%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
-%the effectiveness of CDS using real user VM disks from our production VM cluster.
-
-Since it's impossible to perform large scale analysis without affecting the VM performance,
-we sampled two data sets from real user VMs to measure the effectiveness of our deduplication scheme.
-Dataset1 is used study the detail impact of 3-level deduplication process,
-it compose of 35 VMs from 7 popular OSes: 
-Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
-5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
-The overall data size for this 700 full snapshots is 17.6 TB.
-
-Dataset2 contains the first snapshots of 1323 VMs' data disks from a small cluster with 100 nodes. 
-Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
-study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
-
-\subsection{Deduplication Efficiency}
-
-%\begin{figure}
-%  \centering
-%  \epsfig{file=images/overall_effect.eps, width=3.5in}
-%  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
-%deduplication divided by the original data size and the unit is percentage. }
-%  \label{fig:overall}
-%\end{figure}
-
-Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication on dataset1.
-The X axis shows the overall impact in (a),  impact on OS disks in (b), and impact on data disks in (c).
-Each bar in the Y axis shows the data size after deduplication divided by the original data size.
-Level-1 elimination can reduce the data size to about 23\% of original data, namely it delivers close 77\% reduction.
-Level-2 elimination is applied to data that could pass level-1, it
-reduces the size further to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
-Level-3 elimination together with level 1 and 2
-reduces the size further to 8\% of original size, namely it delivers additional 10.5\% reduction.
-Level 2 elimination is more visible in OS disk than data disk, because data change frequency is really small
-when we sample last 10 snapshots of each user in 10 days. Nevertheless, the overall impact of level 2 is still significant.
-A 4.5\% of reduction from the original data represents about 450TB space saving for a 1000-node cluster.
-
-%\begin{figure}
-%  \centering
- %\epsfig{file=images/os_cds_sim.eps, width=3in}
-%  \epsfig{file=images/3level_os.eps, width=3.5in}
-%  \caption{Impact of 3-level deduplication for OS releases.}
-%  \label{fig:oscds}
-%\end{figure}
-
-%To see the impact of multi-level deduplication on different OS releases,
-%Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
-Figure~\ref{fig:oscds} shows the impact of different levels of deduplication for different OS releases.
-In this experiment, we tag each block in 350 OS disk snapshots from dataset1 as  ``new''
-if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot store;
-``CDS''  if this block can be found  in CDS;
-``Parent segment'' if  this block is marked unchanged in parent's segment recipe.
-``Parent block'' if  this block is marked unchanged in parent's block recipe.
-With this tagging, we compute the percentage of deduplication accomplished by each level.
-As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination,
-this is because the time interval between two snapshots in our dataset
-is quite short and the Aliyun cloud service makes a snapshot  everyday  for each VM.
-On the other hand,  CDS still finds lots of duplicates that inner VM deduplication can't find,
-contributing about 10\% of reduction on average.
-
-It is noticeable that level-1 deduplication doesn't work well for CentOS, a significant percentage of data is not
-eliminated until they reach level-3. It shows that even user upgrade his VM system heavily and frequently
-such that data locality is totally lost, those OS-related data can still be identified at level-3.
-
-In general we see a stable data reduction ratio for all OS varieties, ranging from 92\% to 97\%, that means
-the storage cost of 10 full snapshots combined is still smaller than the original disk size. And compare to 
-today's widely used copy-on-write snapshot technique, which is similar to our level-1 deduplication, our
-solution cut the snapshot storage cost by 64\%.
-
-%Combining OS disks in all the VMs, we see the overall 7.4TB of data is reduced to 512GB. 
-%The extreme binning approach can reduce this data set to 542GB, which is slightly worse. As a reference, 
-%perfect deduplication achieves 364GB in this experiment.
-
-%Overall speaking, inner   VM deduplication or  CDS-based deduplication
-%can work well alone, but by combining them together we get a fairly good and stable deduplication ratio to 
-%all kind of OSes. 
-%Compared to a traditional dirty bit approach based on pages of
-%each file (e.g. segment in our scheme),
-%our CDS-based level 3 approach  can save additional 50\% storage space because many of level 2 block
-%content can be eliminated using the CDS also.
-
-\subsection{Comparison with Other Approaches}
-\subsubsection{Sampled Index}
+{\bf Sampled Index}.
 One alternative approach to avoiding a single global index is to use a sampled
@@
 
-\subsubsection{Scalable Data Routing}
+{\bf Scalable Data Routing}.
 Another approach to avoiding a global index is to use a content-based hash

### 2013-06-24 snapshot_system/con.tex
modify all sections

--- 2012-05-06 vm_snapshot_sim/2012concl.tex
@@
 \label{sect:final}
-In this paper we propose a multi-level selective deduplication scheme for 
-snapshot service in VM cloud. 
+In this paper we propose a VM-centric deduplication scheme for 
+snapshot backup in VM cloud for maximizing fault isolation and tolerance. 
 Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
@@
 effectively  covers a large amount of duplicated data.
+The scheme organizes the write of small data chunks into large file system blocks so
+that each underlying file block is associated with one VM for most of cases.
 Our solution accomplishes the majority of
 potential global deduplication saving while still meets stringent cloud resources requirement. 
+Our analysis shows that  this VM centric scheme 
+can  provide  better fault tolerance while using a small amount of computing and storage resource.
+
+[Talk about more what we learn from Evaluation]
 Evaluation using real user's VM data shows
@@
 room for additional optimization we are further studying.
+
+%This paper studies a cluster-based VM-centric scheme which collocates a lightweight
+%backup service with the cloud service and it integrates multiple duplicate detection strategies that  
+%localize the deduplication as much as possible within each virtual machine.
+%This  paper  provides a comparative evaluation of this scheme in  accomplishing a high deduplication 
+%efficiency while sustaining a good backup throughput.
+
+%This paper studies the      a VM snapshot storage architecture which adopts multiple-level selective deduplication to bring the benefits of fine-grained data reduction into cloud backup storage systems.
+%In this work, we describe our working snapshot system implementation, and provide
+%early performance measurements for both deduplication impact and
+%snapshot operations.
+
+\comments{
 \section*{Acknowledgments}
@@
 do not necessarily reflect the views of Alibaba or the National Science Foundation.
+}
 }

### 2013-06-24 snapshot_system/eval1.tex
modify all sections

@@
 %content can be eliminated using the CDS also.
-
-\subsection{Comparison with Other Approaches}
-\subsubsection{Sampled Index}
-One alternative approach to avoiding a single global index is to use a sampled
-index. This is the approach taken by Guo and Efstathopoulos\cite{Guo2011}. We
-compare their solution to ours by running their algorithm on our 350 traces
-using a sampling rate of 1 out of 101 blocks, and always including the first
-block in a container (which we fix at 16MB in size). The results of running this
-test are shown in Table~\ref{??}, and the memory usage comparison can be found
-Sec.~\ref{??}. Our results show that using a sampled index achieves a very high
-rate of deduplication, and so a sampled index might be a good way to do dedup
-in a single node setup.
-
-The problems for sampling are in distributing the
-algorithm and in deduplicating extremely large bodies of data. The algorithm
-stores the entire (sampled) index in memory, which is required for high
-throughput to avoid the disk-bottleneck problem - since the index itself has no
-locality information, lookups are essentially random, so the index must be
-somehow optimized to prevent excessive disk seeking (the sampling algorithm does
-this by storing the index in memory). To distribute this index, each node would
-either require a complete copy of the index which would have a prohibitive cost in
-memory, or something like memcached must be used, which leaves the same problem
-as the disk bottleneck with every index check potentially using the network.
-The difficulty in storing extremely large bodies of data
-is related, as once 1PB is stored in the system, assuming a sampling rate of 
-1/101 with 22 byte index entires, 55GB of (in memory) index are required.
-
-Our solution uses more total memory (??how much??), but is more scalable both in
-terms of capactity and distributing the deduplication. The only part of our
-algorithm which requires significant network traffic is the CDS deduplication,
-but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
-so is only done for a small percent of blocks (?? 5-10\% ??).
-
-\subsubsection{Scalable Data Routing}
-Another approach to avoiding a global index is to use a content-based hash
-partitioning algorithm to break up the deduplication work. This approach is
-taken by Dong et al. in their Scalable Data Routing paper, and is similar to
-Exreme Binning\cite{??}\cite{extreme_binning09}. We compared our solution to
-content-based hash partitioning by running the algorithm on our set of 
-traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
-the minhashes of the superchunks for routing. The results of this are shown in
-Table~\ref{??}. Routing each chunk to a bin provides good deduplication
-efficiency, and only requires each storage node to keep an index of local data
-and the bin mapping, but misses significant opportunities in our indended use
-case.
-
-The problem with the Data Routing algorithm is in the very high network traffic.
-Our intended use case is a backup system which runs alongside a number of VMs,
-in order to save costs. Data Routing makes no use of the inherent locality in
-such a system, and therefore puts a much higher network burden on machines which
-are also running 35 VMs each. This will reduce the available network bandwidth
-to users of the VMs, and/or reduce the possible deduplication throughput.

### 2013-06-24 snapshot_system/failover.tex
modify all sections

@@
 The replication degree of the backup storage 
-is $r$ for regular content blocks and $r=3$ is a typical setting in the distributed
+is $r$ for regular file blocks and $r=3$ is a typical setting in the distributed
 file system~\cite{Hadoop,GFS}.
@@
 
-Figure~\ref{fig-vo-links} shows the average number of links to 
-a given block in the global index as more VMs are added. 
+Figure~\ref{fig-vo-links} shows the average number of VMs shared by 
+a block in the global index as more VMs are added. 
 The first 15 VMs are all windows machines, so that explains the initial 

### 2013-06-24 snapshot_system/intro.tex
adding exper.
modify all sections

@@
 
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=3in]{images/traditional-arch.pdf}
-    \label{fig-traditional-arch}
-    \caption{Traditional VM Backup System}
-\end{figure}
+%\begin{figure}[htb]
+%    \centering
+%    \includegraphics[width=3in]{images/traditional-arch.pdf}
+%    \label{fig-traditional-arch}
+%    \caption{Traditional VM Backup System}
+%\end{figure}
 
@@
 We achieve improved fault isolation by accounting for the fact that after
-deduplication most data blocks are shared by several to many virtual machines.
-Failure of such popluar blocks would have a catastrophic effect and many
+deduplication most data chunks are shared by several to many virtual machines.
+Failure of such popular data chunks would have a catastrophic effect and many
 snapshots of virtual machines would be affected.
-The previous work in deduplication focuses mainly on the efficiency and approximation of
-finger print comparison, and has not addressed fault tolerance along with a low-cost solution.
-Another issue considered is that
+The previous work in deduplication focuses on the efficiency and approximation of
+finger print comparison, and has not addressed fault tolerance together with deduplication.
+% along with a low-cost solution.
+%Another issue considered is that
 %that deletion of old snapshots compete for computing resource as well. That is because data dependence created
-deletion of old snapshots compete for computing resources as well so deletion needs
-to be considered in system design. The additional complexity for deletions
-come from the dependencies created by multiple links to the same problem, so
-some solution is needed to determine blocks with no dependent snapshots after deletion.
+%deletion of old snapshots compete for computing resources as well so deletion needs
+%to be considered in system design. The additional complexity for deletions
+%come from the dependencies created by multiple links to the same problem, so
+%some solution is needed to determine blocks with no dependent snapshots after deletion.
 % especially when  VMs can migrate around in the cloud.
 
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=3in]{images/colocated-arch.pdf}
-    \label{fig-colocated-arch}
-    \caption{Colocated VM Backup System}
-\end{figure}
+%\begin{figure}[htb]
+%    \centering
+%    \includegraphics[width=3in]{images/colocated-arch.pdf}
+%    \label{fig-colocated-arch}
+%    \caption{Collocated VM Backup System}
+%\end{figure}
 
@@
 and controlled cross-VM comparison. 
-This approach is VM centric by localizing duplicate detection within each VM  as much as possible
-and minimize memory usage while delivering a decent deduplication efficiency. 
-Our partially localized solution also brings the benefits of parallelism, utilization, and fault isolation.
-Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data blocks.
+This approach is VM centric by localizing duplicate detection within each VM  
+and by packaging data chunks from the same VM into a file system block as much as possible.
+The solution uses  a small amount of  memory while delivering a decent deduplication efficiency. 
+Our localization solution also brings the benefits of parallelism, resource utilization, and fault isolation.
+Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data.
 We have developed a prototype system that runs a cluster of Linux machines with Xen.
@@
 Section~\ref{review} reviews background and related work.
-Section~\ref{sec:framework}  discusses the  design framework and system architecture.
+Section~\ref{sec:framework}  discusses the  design options for snapshot backup with a VM-centric approach. 
 Section~\ref{sec:model}  analyzes the benefit of our approach for fault isolation. 
-Section~\ref{exper} is our experimental evaluation that compare with the other approach.
+Section~\ref{sec:arch}  describes our system architecture and implementation details.
+%   the benefit of our approach for fault isolation. 
+Section~\ref{exper} is our experimental evaluation that compare with the other approaches.
 Section~\ref{conc}  concludes this paper.

### 2013-06-24 snapshot_system/snapshot.tex
adding exper.
modify all sections

@@
 The traditional approach compares all fingerprints and 
-stores one copy for all of a block's duplicates.
+stores one copy for all of a chunk's duplicates.
 We call this as  the VM-oblivious (VO) approach.
 In comparison, we analyze the design of
-a VM-centric approach (VC) which differenates duplicates within a VM and cross VMs,
-and conducts \textit{Inner-VM} and \textit{cross-VM} detection seperately.
+a VM-centric approach (VC) which differentiates duplicates within a VM and cross VMs,
+and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.
 
@@
 
-Inner-VM duplication can be very effecive within VM's snapshots. There
+Inner-VM duplication can be very effective within VM's snapshots. There
 are typically a large number of duplicates existing among the snapshots
-for a single VM.  Localizing the snapshot data deduplication witin a VM
+for a single VM.  Localizing the snapshot data deduplication within a VM
 improves the system by:
-increasing data independency between different VM backups,
+increasing data independence between different VM backups,
 simplifying snapshot management and statistics collection,
@@
 \begin{itemize}
-\item \textbf{Dirtybit-based corase-grain inner-VM deduplication.}
-The first-level deduplication is to follow the standand dirty bit approach, but is conducted
+\item \textbf{Dirtybit-based coarse-grain inner-VM deduplication.}
+The first-level deduplication is to follow the standard dirty bit approach, but is conducted
 in the coarse grain segment level.
-We use the  Xen virtual device driver which supports changed block tracking
+We use the  Xen virtual device driver which supports a feature called "changed block tracking''
 for the storage device
-and the dirty bit setting is maintained in a corase grain level we call it a segment.
+and the dirty bit setting is maintained in a coarse grain level we call it a segment.
 In our implementation, the segment size is 2MB. 
-Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
-and cannot affort a small segment  size.
+Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
+and cannot afford a small segment  size.
 
-It should be noted that changed block tracking is supported or can be easily implemented in many 
+It should be noted that dirtybit tracking is supported or can be easily implemented in many 
 major virtualization solution vendors. 
@@
 achieve deduplication even when there are insertions/deletions which would
-affect many fixed-size blocks.
+affect many fixed-size chunks.
 Thus the second-level inner-VM deduplication is to perform this chunking for
 dirty segments, and to compare the snapshot with its parent. 
-We load the fingerprints of block chunks of the corresponding segment from the
+We load the chunk fingerprints in the corresponding segment from the
 parent and perform fingerprint matching for further inner-VM deduplication.
@@
 
-When a block is not detected as a duplicate to any existing block, this block will be written
+When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
 to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
-accululate small local blocks. We manage this accumulation process using an apendstore  scheme
+accumulate small local chunk. We manage this accumulation process using an append-store  scheme
 and discuss this in details in Section~\ref{sect:arch}.
+The system allows all machines conduct the backup in parallel in different machines, and each machine
+conducts the backup of one VM at a time, and thus only requires a write  buffer for one VM.
+
+It should be noted that CDS chunks are computed periodically and all CDS chunks are stored in a separate
+append-store instance. In this way, each file block for non-CDS chunks is associated with one VM
+and does not contain any CDS chunk.
 
@@
 %Lack of data dependence between VMs brings 
-With cross-VM deduplication, shared data blocks
-create an artifical dependence  among VMs and failure of one shared block
-affects many VMs. Thus we only maintain the index for a small set of popular chunks.
+With cross-VM deduplication, shared data chunks
+create an artificial dependence  among VMs. 
+Thus we only maintain the index for the most popular chunks to reduce the inter-VM dependence
+while still accomplishing competitive deduplication efficiency.
+
 The management for popular data chunks contains two aspects.
@@
 \item Compute and select top-$k$ most popular chunks.
-The popularity of a chunk is the number  of data blocks from different VMs
-that are duplicates of this block after the inner VM deduplication.
-This number can be computed perioidically in a weekly basis.
-Once the popularity of all data blocks is collected, the system only maintains the top $k$
-most popular blocks.  For cross-VM comparison,
+The popularity of a chunk is the number  of data chunks  from different VMs
+that are duplicates of this chunk after the inner VM deduplication.
+This number can be computed periodically in a weekly basis.
+Once the popularity of all data chunks is collected, the system only maintains the top $k$
+most popular chunks.  For cross-VM comparison,
 we only store  top $k$ items and $k$ is chosen to be relatively small.
 Our analysis below will show that the algorithm can still deliver competitive
-deduplication effiency after making these approximations.
-\item  Since $k$ is small and these top $k$ blocks are shared among multiple VMs, 
-we can afford to provide extra replicas for these popular blocks to enhanace the fault resilence.
-We will provide an analysis of the fault tolerance in the next subsection.
+deduplication efficiency after making these approximations.
+\item  Since $k$ is small and these top $k$ chunks are shared among multiple VMs, 
+we can afford to provide extra replicas for these popular chunks to enhance the fault resilience.
+We will provide an analysis of the space need and fault tolerance in the next subsection.
 \end{itemize}
@@
 using Alibaba's production user data~\cite{ieeecloud} 
-which shows that the popularity of data blocks after inner VM deduplication follows 
+which shows that the popularity of data chunks after inner VM deduplication follows 
 a Zipf-like distribution\cite{zipf} and its
@@
 %As a result, it can be proved that deduplication efficiency of CDS index is scalable:
+
+\begin{figure}
+\centering
+%\epsfig{file=log-log.disk.pdf,width=3in}
+%source ../vm_snapshot_sim/images/log-log.disk.eps
+ \includegraphics[width=3in]{log-log-disk.pdf}
+\caption{Duplicate frequency versus  chunk ranking in a log scale.}
+\label{fig:Datazipf}
+\end{figure}
 
@@
 \hline
-$b$ &  the total amount of data blocks\\ 
+$b$ &  the total amount of data chunks\\ 
 \hline
@@
 \hline
-$\sigma$ &  the number of uniqie non-CDS chunks over  the number of the CDS chunks.\\
+$\sigma$ &  the number of unique non-CDS chunks over  the number of the CDS chunks.\\
 \hline
@@
 \hline
-$F$ & the size of an polular data index entry\\
+$F$ & the size of an popular data index entry\\
 $N_1$ & the average number  of non-CDS file system blocks  in a VM\\
@@
 
-Let $b$ be the total number of data blocks after localized deduplication, 
+Let $b$ be the total number of data chunks after localized deduplication, 
 $b_u$ be the total number of fingerprints 
@@
 
-The  $k$ most popular fingerprints can cover the following number of blocks after inner VM 
+The  $k$ most popular fingerprints can cover the following number of chunks after inner VM 
 deduplication.
@@
 
-Deduplication efficiency of VC using top $k$ popular blocks
+Deduplication efficiency of VC using top $k$ popular chunks
 is the percentage of duplicates that can be detected:  
@@
 index, $F$ be the size of an index entry,
-$D$ be the amount of unique data on each phyiscal machine, and 
-$B$ be the average block size. We store the popular index using a distribued shared memory hashtable
+$D$ be the amount of unique data on each physical machine, and 
+$B$ be the average chunks size. We store the popular index using a distributed shared memory hashtable
 such as MemCacheD.  Then $k$ and $b_u$ can be expressed as:
@@
 
-The overall deduplication effiency of VC is
+The overall deduplication efficiency of VC is
 \[
@@
 \]
-where $(\frac{m*B}{D*F})^{1-\alpha}$ represents the percentage of the remaining blocks detected as duplicates
+where $(\frac{m*B}{D*F})^{1-\alpha}$ represents the percentage of the remaining chunks detected as duplicates
 after inner VM deduplication. 
@@
 When the number of machines at each cluster increases, the number of total VMs increases.
-Then $k$ increases since more memory is available to host the popular block index.
+Then $k$ increases since more memory is available to host the popular chunks index.
 But for each physical machine, the number of VMs remains the same, and thus

### 2013-06-24 snapshot_system/result.tex
Add performance analysis

@@
 For each OS, 5 VMs are chosen, and every VM come with 10 full snapshots.
+
+\subsection{System Performance}
+{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
+backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
+scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
+evaulate the system performance on the second snapshot backup. We repeat such procedure
+under different CDS memory usage settings, the results of backup time break down are shown in
+firure~\ref{fig:single_vm_backup}.
+
+It's easy to see that the time of I/O dominates the backup process, our deduplication
+procedure only takes a tiny fraction of the total backup time. Larger memory permits us to
+use larger CDS index to cover more of global index, as a result the amount of data to be writen
+is reduced and so do the writing time.
+Inside the deduplication procedure, the time costs of level-1
+is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
+because the number of fingerprints to process are just the same.
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=figures/single_backup_time.pdf, width=3.5in}
+  \caption{Time to backup a 40GB VM snapshot under different CDS memory usage settings}
+  \label{fig:single_vm_backup}
+\end{figure}
+
+{\bf Parallel VM Backup} We then evaluate the performance of writing snapshots in parallel.
+To begin, on each node we let 4 VMs writing snapshot concurrently, and gradually 
+increase number of VMs to 12 to saturate our system capability. We observed 
+the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
+which is far beyond our QFS file system capability. The reason behind it is our efficient
+deduplication architecture and compression greatly reduce the amount of data that need to be writen to
+the file system. The main bottleneck here is our QFS only manages one disk per node, 
+making it inefficient to utilize the benefits of parallel disk access. We expect our achitecture can
+perform even better in production cluster which normally has more than ten disks on each node.
+
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
+  \caption{Throughput per-node with concurrent snapshot backup tasks}
+  \label{fig:parallel_backup}
+\end{figure}
+
+\subsection{Read Snapshot}
 

### 2013-06-25 snapshot_system/background.tex
revise

@@
 
-The previous work for storage backup has extensively studied  data deduplication techniques can eliminate redundancy 
+The previous work for storage backup has extensively studied  data deduplication techniques that
+can eliminate redundancy 
 globally among different files from different users.
@@
 accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-As discussed in Section~\ref{sect:intro},
-there is no dedicated resource for deduplication in our targeted setting and low memory usage
- is required so that the resource impact to other cloud services is minimized.
+%As discussed in Section~\ref{sect:intro},
+%there is no dedicated resource for deduplication in our targeted setting and low memory usage
+% is required so that the resource impact to other cloud services is minimized.
 %NG et al.~\cite{ NGmiddleware2011}  use

### 2013-06-25 snapshot_system/intro.tex
revise

@@
 Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
-(Figure~\ref{fig-traditional-arch})
+%(Figure~\ref{fig-traditional-arch})
 can effectively identify and remove content duplicates among snapshots, 
-but the solution can be expensive. There is also a large amount of 
+but such a solution can be expensive. There is also a large amount of 
 network traffic to transfer  data from the host machines to the backup facility
@@
 
-This paper seeks for a low-cost architecture option and takes advantage of the
-fact that the
-backup service collocates on the cloud cluster with a minimum resource usage
-(Figure~\ref{fig-colocated-arch})
+This paper seeks for a low-cost architecture option  that collocates
+a backup service with other cloud services and  uses a minimum amount of resources. 
 %Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
@@
 %Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
-Cloud providers often wish that the backup service only consumes  small or modest resources
-with a minimal impact to the existing cloud services.  
-We study and evaluate the integration of several deduplication strategies to meet
-the low-cost collocation requirement. In parallel, we identify deduplication options that yield
-better fault isolation.
+%Cloud providers often wish that the backup service only consumes  small or modest resources
+%with a minimal impact to the existing cloud services.  
+%We study and evaluate the integration of several deduplication strategies to meet
+%the low-cost collocation requirement. 
 %A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
-We achieve improved fault isolation by accounting for the fact that after
+We also consider the fact that after
 deduplication most data chunks are shared by several to many virtual machines.
-Failure of such popular data chunks would have a catastrophic effect and many
+Failure of shared data chunks can have a catastrophic effect and many
 snapshots of virtual machines would be affected.
@@
 finger print comparison, and has not addressed fault tolerance together with deduplication.
+Thus we also seek deduplication options that yield better fault isolation.
 % along with a low-cost solution.
@@
 and by packaging data chunks from the same VM into a file system block as much as possible.
-The solution uses  a small amount of  memory while delivering a decent deduplication efficiency. 
-Our localization solution also brings the benefits of parallelism, resource utilization, and fault isolation.
-Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data.
+By narrowing duplicate sharing within a small amount of data chunks,
+this scheme can afford to allocate extra replicas of these shared chunks for better
+fault resilience.
+Localization also brings the benefits of parallelism exploitation so
+backup operations can run simultaneously without a central  bottleneck.
+This  VM-centric solution uses  a small amount of  memory while delivering a decent deduplication efficiency. 
+%Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data.
 We have developed a prototype system that runs a cluster of Linux machines with Xen.
-The backup storage uses a standard distributed file system with data replication and block packaging,
-and we allocate more  replicas for the commonly-shared  data blocks among VM snapshots to enhance fault tolerance.
+The backup storage uses a standard distributed file system with data replication and block packaging.
+%and we allocate more  replicas for the commonly-shared  data 
+%blocks among VM snapshots to enhance fault tolerance.
 

### 2013-06-25 snapshot_system/abs.tex

@@
 using signatures and let a data block share by many virtual machines. 
-This paper studies a cluster-based VM-centric scheme which collocates a lightweight
-backup service with the cloud service and it integrates multiple duplicate detection strategies that  
-localize the deduplication as much as possible within each virtual machine.
+This paper studies a VM-centric scheme which collocates a lightweight
+backup service with other cloud services in a cluster and it integrates multiple duplicate detection strategies 
+that  localize deduplication as much as possible within each virtual machine.
 It also organizes the write of small data chunks into large file system blocks so

### 2013-06-25 snapshot_system/challenge.tex

@@
 raw data for backup. 
+Figure~\ref{fig:collocated} illustrates the cluster architeture where
+each physical runs a backup service and a distribued file system (DFS)~\cite{GFS2004,Hadoop} 
+serves a backup store  for the snapshopts.
+The previous study shows that 
+ deduplication can compress the backup copies 
+effectively in a 10:1 or even 15:1 rage. 
+Therefore  the portion of space in a cluster
+allocated for snapshots of data should not dominate
+the cluster storage usage.
+
 %The running of such a service is subject to the resource availability of the system and
-We discuss the design considerations as follows.
 
@@
     \includegraphics[width=3in]{images/colocated-arch.pdf}
-    \label{fig-colocated-arch}
-    \caption{Collocated VM Backup System}
+    \label{fig:collocated}
+    \caption{Collocated VM Backup System.}
 \end{figure}
 
+%{\em Collocating with cluster-based cloud services.}
+%We collocate the backup service with other cloud services in a cluster
+%and use a distributed file system
+%store the backup with multiple replicas. 
+%There might be a concern that storing many versions of snapshots would
+%go against the purpose of deduplication.
+
+%Assume on the average the compression
+%ratio is $c$:1.  When the number of versions
+%saved in the backup storage is $l$  on the average, 
+%the amount of storage space in the cluster allocated  for the backup would be $\frac{l}{l+c}$.
+%For example, when $l=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
+%When $l=9$ and $c=13$, storage usage is 40\%. 
+%That is acceptable given today's cheap cost for disk storage.
+%In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data.
+%Each machine however can typically provide over 10TB storage.
+%Thus the normal disk usage  is about 1TB per machine, and adding 30\% to 100\% 
+%extra space for the backup is not a practical concern, especially with the
+%added benefits of cheaper running costs and lower network bandwidth requirements.
+
+We discuss the design considerations as follows. 
 \begin{itemize}
-\item {\em Collocating with cluster-based cloud services.}
-We collocate the backup service with other cloud services in a cluster
-and use a distributed file system~\cite{GFS2004,Hadoop} to 
-store the backup with multiple replicas. 
-There might be a concern that storing many versions of snapshots would
-go against the purpose of deduplication.
-The previous research shows the deduplication can compress the backup copies 
-effectively in a 10:1 or even 15:1 rage. Assume on the average the compression
-ratio is $c$:1.  When the number of versions
-saved in the backup storage is $l$  on the average, 
-the amount of storage space in the cluster allocated  for the backup would be $\frac{l}{l+c}$.
-For example, when $l=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
-When $l=9$ and $c=13$, storage usage is 40\%. 
-That is acceptable given today's cheap cost for disk storage.
-In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data.
-Each machine however can typically provide over 10TB storage.
-Thus the normal disk usage  is about 1TB per machine, and adding 30\% to 100\% 
-extra space for the backup is not a practical concern, especially with the
-added benefits of cheaper running costs and lower network bandwidth requirements.
+\item {\em Deduplication localization, sharing minmization, and fault tolerance.}
 
+%Previous work in deduplication~\cite{extreme_binning09,sparseindex09} has
+%studied the solutions to reduce memory requirements.
+%One important issue not considered in the previous work is how 
+Because a data chunk is compared with signatures collected from other VMs during
+the deduplication process, only one copy of duplicates is stored in the backup storage
+and this artificially creates data dependency among different VM users. 
+Content sharing via deduplication affects fault isolation since machine failures happen at daily 
+basis in a large-scale cloud and
+%failure of a shared block affects many VMs.
+%the loss of a shared chunks can affect many VM users whose snapshots share this 
+%data block. 
+loss of a small number of shared data chunks can 
+cause the unavailability of snapshots for a large number of virtual machines.
+Localizing the impact of deduplication can incrase fault isolation and resilience.
+Thus from the fault tolerance point of view,  duplicate sharing among mutiple VMs is 
+discourage. On the other hand, we need to seek for a tradeoff since there are
+a significant number of duplicates cross VMs.
+
+% since storage for shared identical content chunks can become a failure point.
+%Without any control of such data sharing, we can only increase  
+%replication for global datasets to enhance the availability,
+%but this incurs significantly higher costs.
+%Thus a key goal  in our design
+%is restricting the impact of  data loss to a limited number of VMs. 
+%It is not desirable that small scale of data failure affects the backup of many VMs.
+%when users access snapshots in a recovery process. 
+\item{\bf Packaging  data chunks as file system blocks.}
 Since the file block size in the Hadoop and GFS is uniform and large with 64MB as a default setting,
@@
 and infrequent snapshot access.
-
-\item {\em Fault tolerance and isolation.}
-The distributed file system~\cite{GoogleFS,Hadoop} provides the replication support
-and we can leverage existing open-source software to implement such a layer.
-When the number of machines failed exceeds the replication degree, there could be
- some data loss.  Storage deduplication worsens the impact of such faults
-because  the majority of each snapshot (e.g. over 90\%) is deduplicated
-and the corresponding data chunks stored in the underlying file blocks
-are shared by many VMs. 
+Packaging that maps data chunks to file system blocks can create data dependence among VMs
+since a file block can be shared even more VMs.
+Thus we need to consider a minimum assoocation of a fie system block to VMs in the packaging process.
+%The distributed file system~\cite{GoogleFS,Hadoop} provides the replication support
+%and we can leverage existing open-source software to implement such a layer.
+%When the number of machines failed exceeds the replication degree, there could be
+% some data loss.  
+%Storage deduplication worsens the impact of such faults
+%because  the majority of each snapshot (e.g. over 90\%) is deduplicated
+%and the corresponding data chunks stored in the underlying file blocks
+%are shared by many VMs. 
 %The failure of one data chunk or block can impact many sharing VMs. 
-In large scale cloud, machine failures happen at daily basis,
-the loss of a shared chunks can affect many VM users whose snapshots share this 
-data block.
-
-Previous work in deduplication~\cite{extreme_binning09,sparseindex09} has
-studied the solutions to reduce memory requirements.
-One important issue not considered in the previous work is how content sharing affects
-fault isolation.
-Because a content chunk is compared with a content signature collected from other users,
-this artificially creates data dependency among different VM users.
-% since storage for shared identical content chunks can become a failure point.
-Without any control of such data sharing, we can only increase  
-replication for global datasets to enhance the availability,
-but this incurs significantly higher costs.
-Loss of a small number of shared data chunks can 
-cause the unavailability of snapshots for a large number of virtual machines.
-Thus a key goal  in our design
-is restricting the impact of  data loss to a limited number of VMs. 
-It is not desirable that small scale of data failure affects the backup of many VMs.
-%when users access snapshots in a recovery process.
-
 \end{itemize}
@@
 %to be processed can be huge. 
-the computing resources allocated for the snapshot service is limited, especially
-because of its lower priority.
+cloud providers wish that the backup service only consumes  small resources
+with a minimal impact to the existing cloud services.
+%the computing resources allocated for the snapshot service is limited, especially
+%because of its lower priority.
 The key usage of resource for backup is memory for storing and comparing the fingerprints. 
@@
 %Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
-Excessive use of bandwidth and computing resource for backup can create
-noticeable contention for resources with the existing cloud, which is not
-preferred and may not not be acceptable for production system operation. 
-Thus it is desirable that backup for all nodes
-can be conducted in parallel and in a short period of time,
-and any centralized or cross-machine communication for
-deduplication should not become a bottleneck.
-For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, 
-the system must finish saving daily snapshots of all VMs in a few hours. 
-Often a cloud has a few hours of light workload each day (e.g. midnight),  
-which creates an small window for automatic backup.
-The backup service can generate hundreds of terabytes of data in such a time window
-without optimization and thus the resource content is considered carefully as we design
-a fault-resilient cluster-based solution. 
+%Excessive use of bandwidth and computing resource for backup can create
+%noticeable contention for resources with the existing cloud, which is not
+%preferred and may not not be acceptable for production system operation. 
+%Thus it is desirable that backup for all nodes
+%can be conducted in parallel and in a short period of time,
+%and any centralized or cross-machine communication for
+%deduplication should not become a bottleneck.
+%For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, 
+%the system must finish saving daily snapshots of all VMs in a few hours. 
+%Often a cloud has a few hours of light workload each day (e.g. midnight),  
+%which creates an small window for automatic backup.
+%The backup service can generate hundreds of terabytes of data in such a time window
+%without optimization and thus the resource content is considered carefully as we design
+%a fault-resilient cluster-based solution. 
 %In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 

### 2013-06-25 snapshot_system/failover.tex
replace the data sharing grpah

@@
 \subsection{Fault Analysis }
+\begin{figure}
+    \centering
+    \subfigure[Sharing of data under VM-oblivious dedup model]
+    {
+        \includegraphics[width=3in]{images/share_model_vc.pdf}
+        \label{fig:share_vc}
+    }
+    \\
+    \subfigure[Sharing of data under VM-centric dedup model]
+    {
+        \includegraphics[width=3in]{images/share_model_vo.pdf}
+        \label{fig:share_vo}
+    }
+    \caption{Difference of sharing data under VO and VC approaches}
+    \label{fig:share}
+\end{figure}
 
@@
 Figure~\ref{fig:shared} illustates the bipartite association.
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.45\textwidth]{shared.pdf}
-\caption{Assoication of data blocks to VMs.}
-\label{fig:shared}
-\end{figure}
 

### 2013-06-25 snapshot_system/snapshot.tex
inserted b bu numbers

@@
 
+{\it [Need to find a place to put these numbers in: Total number of chunks in 350 snapshots: 1,546,635,485.
+Total number of chunks after localized dedup: 283,121,924.
+Total number of unique chunks: 87,692,682.]}
 Let $b$ be the total number of data chunks after localized deduplication, 

### 2013-06-26 snapshot_system/challenge.tex
revise

@@
 
-With these considerations in mind, we study a cluster-based backup service 
-with VM-centric deduplication. This service is co-hosted   in the existing set of machines and resource usage is friendly
+A deduplication scheme compares the fingerprints of the current snapshot
+with its parent snapshot and also other snapshots in the entire cloud without consideration of .
+%The traditional approach compares all fingerprints and
+%stores one copy for all of a chunk's duplicates.
+We call this as  the VM-oblivious (VO) approach.
+In designing and selecting a duplication algorithm, we have considered the following options.
+\begin{itemize}
+\item {\bf Version-based change detection}.
+VM snapshots can be  backed up  incrementally by identifying file  blocks that have
+changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
+Active snapshots will contain all the information needed to restore the virtual disk
+and when deleting a snapshot, data referenced by other snapshots are removed.
+While full signature comparison can deliver additional reduction~\cite{Guo2011,Dong,ExtremeBining},
+content change detection falls into a VM-centric approach since deduplication is localizable. 
+We are seeking for additional optimzations to improve duplication efficency and design the 
+assoication of data chunks with the underlying file blocks so that
+file block sharing among VMs is minimized.
+\item {\bf sampled Index}.
+One alternative approach to reducing the use of memory space is 
+to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
+An evaluation with our test data shows that using a sampled index can achieve a high
+deduplication effiency with a single machine setup.  
+One key problem is that the algorithm is VM oblivious and not easy to be adopted for VM-centric.
+Another problem is  to design a distributed version 
+in deduplicating large bodies of data. 
+%The algorithm stores the sampled index in memory, which is required for high
+%throughput to avoid the disk-bottleneck problem - since the index itself has no
+%locality information, lookups are essentially random, so the index must be
+%somehow optimized to prevent excessive disk seeking (the sampling algorithm does
+%this by storing the index in memory). 
+To use a distributed memory version of the sampled index, every deduplicate request
+may access a remote machine for index lookup,  which  incurs a significant overhead.
+
+Another possibiliy is to use this approach partially  in our VM centric solution by indexing
+the most popular data chunks. For a small set of popular data chunks, the prefetching strategy
+used in the sampled index will not work well because the spatial locality is limited among popular 
+data chunks. In our test data,  on average the number of consecutive data chunks is 7, which is too small
+to be effective for index sampling.
+
+%To distribute this sampled index, every  each machine would
+%either require a complete copy of the index which would have a prohibitive cost in
+%memory, or something like memcached must be used, which leaves the same problem
+%as the disk bottleneck with every index check potentially using the network.
+%The difficulty in storing extremely large bodies of data
+%is related, as once 1PB is stored in the system, assuming a sampling rate of 
+%1/101 with 22 byte index entires, 55GB of (in memory) index are required.
+
+%Our solution uses more total memory (??how much??), but is more scalable both in
+%terms of capactity and distributing the deduplication. The only part of our
+%algorithm which requires significant network traffic is the CDS deduplication,
+%but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
+%so is only done for a small percent of blocks (?? 5-10\% ??).
+
+\item {\bf Stateless  Data Routing}.
+Another approach for duplicate comparison  is to use a content-based hash
+partitioning algorithm called stateless data routing~\cite{Dong20??}
+that divides the deduplication work with an approximation, which 
+is similar to Exreme Binning\cite{extreme_binning09}. 
+Again such an approach is VM-oblivious while each request does incur a network routing latency, and then
+additional overhead for a bloomer filter based  disk lookup~\cite{Dong20??} or 
+a disk index access~\cite{extreme_binning09}.
+
+%We compared our solution to
+%content-based hash partitioning by running the algorithm on our set of 
+%traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
+%the minhashes of the superchunks for routing. The results of this are shown in
+%Table~\ref{??}. Routing each chunk to a bin provides good deduplication
+%efficiency, and only requires each storage node to keep an index of local data
+%and the bin mapping, but misses significant opportunities in our indended use
+%case.
+
+%The problem with the Data Routing algorithm is in the very high network traffic.
+%Our intended use case is a backup system which runs alongside a number of VMs,
+%in order to save costs. Data Routing makes no use of the inherent locality in
+%such a system, and therefore puts a much higher network burden on machines which
+%are also running 35 VMs each. This will reduce the available network bandwidth
+%to users of the VMs, and/or reduce the possible deduplication throughput.
+\end{itemize}
+
+With these considerations in mind, we study a 
+VM-centric appraoch (called VC)
+for a backup service co-hosted   in the existing set of machines and resource usage is friendly
 to the existing applications.  

### 2013-06-26 snapshot_system/snapshot.tex
revise

--- 2013-06-24 snapshot_system/snapshot.tex
@@
 
-A deduplication scheme compares the fingerprints of the current snapshot
-with its parent snapshot and also other snapshots in the entire cloud.
-The traditional approach compares all fingerprints and 
-stores one copy for all of a chunk's duplicates.
-We call this as  the VM-oblivious (VO) approach.
-In comparison, we analyze the design of
-a VM-centric approach (VC) which differentiates duplicates within a VM and cross VMs,
-and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.
+%A deduplication scheme compares the fingerprints of the current snapshot
+%with its parent snapshot and also other snapshots in the entire cloud.
+%The traditional approach compares all fingerprints and 
+%stores one copy for all of a chunk's duplicates.
+%We call this as  the VM-oblivious (VO) approach.
+Our VC design has the following objectives:
+\begin{itemize}
 
-\subsection{Inner and cross VM deduplication}
-
-Inner-VM duplication can be very effective within VM's snapshots. There
-are typically a large number of duplicates existing among the snapshots
-for a single VM.  Localizing the snapshot data deduplication within a VM
-improves the system by:
-increasing data independence between different VM backups,
+\item
+1) Localize the deduplication and data blocking within each VM as much as possible so 
+that any failure of a file system block mainly affects the associated VM.
+Localizing the snapshot data deduplication within a VM
+improves the system by increasing data independence between different VM backups,
 simplifying snapshot management and statistics collection,
 and facilitating parallel execution of snapshot operations.
-On the other hand, cross-VM duplication can also be desirable mainly due to widely-used software and libraries. 
+\item
+2) Maintain a competitive deduplication effiency while being resource-friendly to other
+existing cloud services.
+Cross-VM duplication can be desirable since  there are many cloud images
+use widely-used software and libraries and their data blocks are duplicate. 
 As the result, different VMs tend to backup large amount of highly similar data.
-We integrate those strategies together as follows.
+\item
+3)  Mininimize the number of data chunks shared among VMs and add extra replicas to incrase
+fault resilience for such data chunks.
+\end{itemize}
+
+\subsection{Key VC Strategies}
+
+%Inner-VM duplication can be very effective within VM's snapshots. There
+%are typically a large number of duplicates existing among the snapshots
+%for a single VM.
+
 %Our multi-level pipeline process can minimize 
@@
 
+%Our VC differentiates duplicates within a VM and cross VMs,
+%and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.
+
 \begin{itemize}
-\item \textbf{Dirtybit-based coarse-grain inner-VM deduplication.}
-The first-level deduplication is to follow the standard dirty bit approach, but is conducted
-in the coarse grain segment level.
-We use the  Xen virtual device driver which supports a feature called "changed block tracking''
-for the storage device
-and the dirty bit setting is maintained in a coarse grain level we call it a segment.
+\item \textbf{Local duplicate search.}
+We start with the standard dirty bit approach in a coarse grain segment level
+and use the  Xen virtual device driver to implement a feature called ``changed block tracking''
+for the storage device and the dirty bit setting is maintained in a coarse grain level we call it a segment.
 In our implementation, the segment size is 2MB. 
@@
 %(VMware, Xen, Microsoft).  
-VMware support it directly; the VMWare hypervisor has an API to let external backup application know 
+%VMware support it directly; 
+The VMWare hypervisor has an API to let external backup application know 
 the changed areas since last backup. Xen doesn't directly support it, However, their open-source 
@@
 
-\item \textbf{Chunk-level fine-grain inner-VM detection.}
-The best deduplication uses a nonuniform chunk size 
-in the average of 4K or 8K~\cite{??}. This allows the system to
-achieve deduplication even when there are insertions/deletions which would
-affect many fixed-size chunks.
-Thus the second-level inner-VM deduplication is to perform this chunking for
-dirty segments, and to compare the snapshot with its parent. 
+Since the best deduplication uses a nonuniform chunk size 
+in the average of 4K or 8K~\cite{??},  
+%This allows the system to achieve deduplication even when there are insertions/deletions which would
+%affect many fixed-size chunks.
+we conduct additional local inner-VM deduplication by comparing
+chunk signatures within a dirty segment from its parent snapshot. 
 We load the chunk fingerprints in the corresponding segment from the
@@
 
-\item \textbf{Cross-VM deduplication.}
+\item \textbf{Cross-VM deduplication with top $k$ popular chunks}
 This step accomplishes the standard global fingerprint  comparison as conducted

### 2013-06-26 snapshot_system/failover.tex
revise

@@
-\subsection{Fault Analysis }
+\subsection{Storage Space and Impact on Fault Tolerance}
+
 \begin{figure}
@@
 
-We  compare the impact of losing $d$ machines 
-to the the VC and VO approaches.  
 The replication degree of the backup storage 
@@
 \[
-\sigma=  \frac{b*\delta(1 -   (\frac{k}{b_u})^{1-\alpha})} {k}.
+\sigma=  \frac{c*\delta(1 -   (\frac{k}{c_u})^{1-\alpha})} {k}.
 \]
 
-Thus  storage cost for VO with full deduplication is $b_u *r$ and for VC, it is
-\[ k*r_c  + k*\sigma *r
+Thus  storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
+\[ k*r_c  + k*\sigma *r.
 \]
@@
 is insignificant.
-Now we compare the fault resilience of VC and VO.
+
+Next we  compare the impact of losing $d$ machines 
+to the the VC and VO approaches.
 
@@
 \[
-N_1= \frac{b}{v*s} (1-\delta) +b/(v*s)\delta (1 -  (\frac{k}{b_u})^{1-\alpha})
+N_1= \frac{b}{v*s} (1-\delta) +b/(v*s)\delta (1 -  (\frac{k}{b_u})^{1-\alpha}).
 \]
@@
 we consider the likely hood that a file system block fails,
-given some number of storage node failures. 
+given some number of storage machine failures. 
 Every time a filesystem block fails,
@@
 available. 
-(in reality it may be only one snapshot that is affected, but it is the user
-who must decide which snapshots are important, so we consider the worst case). 
+In reality it may be only one snapshot that is affected, but it is the user
+who must decide which snapshots are important, so we consider the worst case. 
 We use filesystem blocks rather than a deduplication
 data chunk as our unit of failure because the DFS keeps
-filesystem blocks as its base unit of storage (in our case there are 
-16384 blocks in a filesytem block on average, with 4KB block size and 
-a 64MB block size).
+filesystem blocks as its base unit of storage.
+% (in our case there are 
+%16384 blocks in a filesytem block on average, with 4KB block size and 
+%a 64MB block size).
 
-To  compute the probablity of losing a virtual machine, 
+To  compute the probablity of losing snapshots of a virtual machine, 
 we estimate the number of file system blocks per VM in each apporach.
@@
 if this file is used by this VM. 
-For VC, let $N_1$ be the averge number of file system blocks for non-CDS data for each VM
-and  $N_2$ be the averge number of file system blocks for CDS data for each VM.
-For VO, let $N_o$ be the averge number of file system blocks for each VM
+For VC, each VM has an 
+averge number of $N_1$ file system blocks for non-CDS data. 
+It also refers  an average of   $N_2$ file system blocks for CDS data 
+For VO, each VM has an average  of  $N_o$ file system blocks
 and let $V_o$ be the averge number of VMs shared by each file system block.
@@
 
-Each non-CDS file system block is associated with one VM while CDS file system blocks are
-shared among VMs. 
+In VC, each non-CDS file system block is associated with one VM while CDS file system blocks are
+shared among VMs  (at most $V$ VMs). Thus, 
 \[
-V *N_1 *s  = pD  \frac{\delta} {\delta +1}
-\]
-For CDS file blocks, there are at most $V$ VMs sharing, thus
-\[
-V *N_2 *s  \leq pD  \frac{1} {\delta +1} *V
+V *N_1 *s  = pD  \frac{\delta} {\delta +1} \; \mbox{ and } \; 
+V *N_2 *s  \leq pD  \frac{1} {\delta +1} *V.
 \]
@@
 N_2 \leq \frac{pD } {s (\delta +1)}, \; 
-\mbox{and} N_o = \frac{pD V_o } {s V}.
+\mbox{and} \; N_o = \frac{pD V_o } {s V}.
 \]
@@
 Figure~\ref{fig:VOshared} shows the number of VMs shared by each file block.
-In our experiment, we find that $V_o \approx 0.2 V$ when backuping up VMs one by one.
+In our experiment, we find that $V_o \approx 0.2 V$ when backing up VMs one by one.
 We can observe that $N_1 +N_2 << N_o$.
 If  the backup for multiple VMs is conducted concurrently, there would be more
-VMs sharing for each file block on average.
+VMs shared  by each file block on average.
 
 Figure~\ref{fig-vo-links} shows the average number of VMs shared by 
-a block in the global index as more VMs are added. 
+a block in the global index as more VMs are added in VO. 
 The first 15 VMs are all windows machines, so that explains the initial 
@@
 
-The availability of is a VM is the likelyhood that
+The snapshot availability of is a VM is the likelyhood that
 there is no  data loss for all its file blocks.
@@
 
-When there are $r \le d<r_c$ machines failed, 
+When there are $r \le d<r_c$ machines failed and then there is no CDS data loss,  
 %a file block failure depends on if all replicas of this container reside in the failed machines.
-the avaiability of a VM in the VC approach is
+the snapshot avaiability of a VM in the VC approach is 
+and is
 \[
@@
 
-When $r_c \leq d$, the CDS file block in VC can also have a loss.
-The availability of  a VM in the VC approach is
+When $r_c \leq d$, both non-CDS and CDS file blocks in VC can have a loss.
+The snapshot availability of  a VM in the VC approach is
 \[
@@
 
-The availability of its VM  mbox in the VO approach is
+The snapshot availability of a VM  in the VO approach is
 \[ 
@@
 slightly.
-The key factor placed is that  $N_1 +N_2 << N_o$.
-The VM-centric approach packs  data blocks under one VM as much as possible
-and performs deduplication mainly within the same VM. The sharing part in CDS is replicated
-with a higher degree, which also signficantly increses the availability even a CDS file blcok
+The key factor placed is that  $N_1 +N_2 << N_o$, caused by the fact that
+the VM-centric approach localizes deduplication and
+packs  data blocks for one VM as much as possible.
+The extra replicaton for CDS blocks 
+also signficantly increses the snapshot availability even a CDS file block
 is shared by every VM.

### 2013-06-26 snapshot_system/snapshot.tex
revise

@@
 
-\item \textbf{Cross-VM deduplication with top $k$ popular chunks}
+\item \textbf{Cross-VM deduplication with popular chunks and replication support}
 This step accomplishes the standard global fingerprint  comparison as conducted
@@
 consumption for global comparison is more expensive.
-Thus our approximation is that the global fingerprint comparison only searches for the most popular items. 
+Thus our approximation is that the global fingerprint comparison only searches for the top $k$
+most popular items. This dataset is called CDS (common data set). 
 %Since duplicate sharing patterns among  VM follows a zip-like distribution,  
-\end{itemize}
+The popularity of a chunk is the number  of data chunks  from different VMs
+that are duplicates of this chunk after the inner VM deduplication.
+This number can be computed periodically on a weekly basis.
+Once the popularity of all data chunks is collected, the system only maintains the top $k$
+most popular chunk signatures in a distribued shared memory.  
+%For cross-VM comparison, we only store  top $k$ items and $k$ is chosen to be relatively small.
 
+Since $k$ is relatively small and these top $k$ chunks are shared among multiple VMs, 
+we can afford to provide extra replicas for these popular chunks to enhance the fault resilience.
+%We will provide an analysis of the space need and fault tolerance in the next subsection.
+
+\item \textbf{VM-centric file system block management.}
 When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
 to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
-accumulate small local chunk. We manage this accumulation process using an append-store  scheme
+accumulate small local chunks. We manage this accumulation process using an append-store  scheme
 and discuss this in details in Section~\ref{sect:arch}.
@@
 
-It should be noted that CDS chunks are computed periodically and all CDS chunks are stored in a separate
+CDS chunks are stored in a separate
 append-store instance. In this way, each file block for non-CDS chunks is associated with one VM
 and does not contain any CDS chunk. 
+\end{itemize}
 
- \subsection{Popular Chunk Management}
+ \subsection{Impact on deduplication efficiency}
 %VM-oriented Fault Isolation}
@@
 %Lack of data dependence between VMs brings 
-With cross-VM deduplication, shared data chunks
-create an artificial dependence  among VMs. 
-Thus we only maintain the index for the most popular chunks to reduce the inter-VM dependence
-while still accomplishing competitive deduplication efficiency.
+%Our analysis below will show that the algorithm can still deliver competitive
+%deduplication efficiency after making these approximations.
+%With cross-VM deduplication, shared data chunks
+%create an artificial dependence  among VMs. 
+%Thus we only maintain the index for the most popular chunks to reduce the inter-VM dependence
+%while still accomplishing competitive deduplication efficiency.
 
-The management for popular data chunks contains two aspects.
-\begin{itemize}
-\item Compute and select top-$k$ most popular chunks.
-The popularity of a chunk is the number  of data chunks  from different VMs
-that are duplicates of this chunk after the inner VM deduplication.
-This number can be computed periodically in a weekly basis.
-Once the popularity of all data chunks is collected, the system only maintains the top $k$
-most popular chunks.  For cross-VM comparison,
-we only store  top $k$ items and $k$ is chosen to be relatively small.
-Our analysis below will show that the algorithm can still deliver competitive
-deduplication efficiency after making these approximations.
-\item  Since $k$ is small and these top $k$ chunks are shared among multiple VMs, 
-we can afford to provide extra replicas for these popular chunks to enhance the fault resilience.
-We will provide an analysis of the space need and fault tolerance in the next subsection.
-\end{itemize}
+%The management for popular data chunks contains two aspects.
 
-This section analyzes how value   $k$ impacts the deduplication efficiency.
+We analyze how the choice of value  $k$ impacts the deduplication efficiency.
 %It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
@@
 %\subsubsection{Impact of CDS deduplication}
-The analysis is based on VM traces collected
-using Alibaba's production user data~\cite{ieeecloud} 
-which shows that the popularity of data chunks after inner VM deduplication follows 
+The analysis is based on the charactristics  of the VM snapshot traces
+studied from  Alibaba's production user data.
+Our previous study shows that the popularity of data chunks after inner VM deduplication follows 
 a Zipf-like distribution\cite{zipf} and its
-exponent $\alpha$ is ranged between 0.65  and  0.70.
+exponent $\alpha$ is ranged between 0.65  and  0.7.~\cite{ieeecloud}. 
 %As a result, it can be proved that deduplication efficiency of CDS index is scalable:
+Table~\ref{tab:symbol} lists parameters used in this analysis.
 
@@
 \hline
-$b$ &  the total amount of data chunks\\ 
+$c$ &  the total amount of data chunks\\ 
 \hline
-$b_u$ &  the total amount of unique fingerprints after inner VM  deduplication\\
+$c_u$ &  the total amount of unique fingerprints after inner VM  deduplication\\
 \hline
-$C_i$ &  the frequency for the $i$th most popular fingerprint\\
+$f_i$ &  the frequency for the $i$th most popular fingerprint\\
 \hline
@@
 \hline
-$B$ & the average data chunk size. Our setting is  4K.\\
+$C$ & the average data chunk size. Our setting is  4K.\\
 \hline
@@
 \hline
-$F$ & the size of an popular data index entry\\
+$E$ & the size of an popular data index entry\\
+\hline
 $N_1$ & the average number  of non-CDS file system blocks  in a VM\\
+\hline
 $N_2$ & the average number  of CDS file system blocks  in a VM\\
+\hline
 $N_o$ & the average number  of file system blocks  in a VM for VO\\
@@
 \end{tabular}
-\caption{Modeling  symbols.}
+\caption{Modeling  parameters and symbols.}
 \label{tab:symbol}
@@
 
-{\it [Need to find a place to put these numbers in: Total number of chunks in 350 snapshots: 1,546,635,485.
-Total number of chunks after localized dedup: 283,121,924.
-Total number of unique chunks: 87,692,682.]}
-Let $b$ be the total number of data chunks after localized deduplication, 
-$b_u$ be the total number of fingerprints 
+{\it [Need to find a place to put these numbers in: Total number of chunks 
+in 350 snapshots: 1,546,635,485. 
+Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
+
+As summarized in Table~\ref{tab:symbol},
+let $c$ be the total number of data chunks. 
+$c_u$ be the total number of fingerprints 
 in the global index after complete deduplication, and
-$C_i$ be the frequency for the $i$th most popular fingerprint. 
-By Zipf-like distribution, $C_i = \frac{C_1}{i^\alpha}.$
-Since $ \sum_{i=1}^{b_u}C_i = b$,
+$f_i$ be the frequency for the $i$th most popular fingerprint. 
+By Zipf-like distribution, $f_i = \frac{f_1}{i^\alpha}.$
+Since $ \sum_{i=1}^{c_u}f_i = c$,
 \[
-C_1 \sum_{i=1}^{b_u}\frac{1}{i^\alpha} = b
+f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c.
 \]
-Given $\alpha <1$, $C_1$ can be approximated with integration:
+Given $\alpha <1$, $f_1$ can be approximated with integration:
 \begin{equation}
-C_1=\frac{b(1-\alpha)}{b_u^{1-\alpha}}.
+f_1=\frac{c(1-\alpha)}{c_u^{1-\alpha}}.
 \end{equation}
@@
 The  $k$ most popular fingerprints can cover the following number of chunks after inner VM 
-deduplication.
+deduplication:
 \[
-C_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
-C_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  C_1\frac{  k^{1-\alpha}} {1-\alpha}.
+f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
+f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}.
 \]
@@
 \begin{equation}
-\begin{split}
-e_k &= 
-\frac{ b(1-\delta) + C_1\frac{  k^{1-\alpha}} {1-\alpha}} 
-{b(1-\delta)  + \delta b - b_u }\\
-&= 
-\frac{ (1-\delta) + \delta  (\frac{k}{b_u})^{1-\alpha}}
-{ 1- \frac{b_u}{b} }.
-\end{split}
+%\begin{split}
+%e_k &= 
+\frac{ c(1-\delta) + f_1\frac{  k^{1-\alpha}} {1-\alpha}} 
+{c(1-\delta)  + \delta c - c_u }\\
+= 
+\frac{ (1-\delta) + \delta  (\frac{k}{c_u})^{1-\alpha}}
+{ 1- \frac{c_u}{c} }.
+%\end{split}
 \end{equation}
@@
 Let $p$ be the number of physical machines in the cluster, $m$ be the memory on each node used by the popular
-index, $F$ be the size of an index entry,
+index, $E$ be the size of an index entry,
 $D$ be the amount of unique data on each physical machine, and 
-$B$ be the average chunks size. We store the popular index using a distributed shared memory hashtable
-such as MemCacheD.  Then $k$ and $b_u$ can be expressed as:
+$C$ be the average chunks size. We store the popular index using a distributed shared memory hashtable
+such as MemCacheD.  Then $k$ and $c_u$ can be expressed as:
 $
-k = p*m/F$, and $b_u = p*D/B.
+k = p*m/E$, and $c_u = p*D/E.
 $
@@
 \[
-\frac{ (1-\delta) + \delta (\frac{m*B}{D*F})^{1-\alpha}}
-{ 1- \frac{b_u}{b} }.
+\frac{ (1-\delta) + \delta (\frac{m*C}{D*E})^{1-\alpha}}
+{ 1- \frac{c_u}{c} }.
 \]
-where $(\frac{m*B}{D*F})^{1-\alpha}$ represents the percentage of the remaining chunks detected as duplicates
+where $(\frac{m*C}{D*E})^{1-\alpha}$ represents the percentage of the remaining chunks detected as duplicates
 after inner VM deduplication. 
@@
 %\end{equation}
-
-When the number of machines at each cluster increases, the number of total VMs increases.
-Then $k$ increases since more memory is available to host the popular chunks index.
-But for each physical machine, the number of VMs remains the same, and thus
-$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
-a constant.
 
@@
 \end{figure}
+
+As illiustrated in Figure~\ref{fig-vo-links},
+when the number of machines at each cluster increases, the number of total VMs increases.
+Then $k$ increases since more memory is available to host the popular chunks index.
+But for each physical machine, the number of VMs remains the same, and thus
+$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
+a constant.

### 2013-06-26 snapshot_system/snapshot.tex
update graphs

--- 2013-06-26 snapshot_system/snapshot.tex
@@
 
-%A deduplication scheme compares the fingerprints of the current snapshot
-%with its parent snapshot and also other snapshots in the entire cloud.
-%The traditional approach compares all fingerprints and 
-%stores one copy for all of a chunk's duplicates.
-%We call this as  the VM-oblivious (VO) approach.
-Our VC design has the following objectives:
-\begin{itemize}
+A deduplication scheme compares the fingerprints of the current snapshot
+with its parent snapshot and also other snapshots in the entire cloud.
+The traditional approach compares all fingerprints and 
+stores one copy for all of a chunk's duplicates.
+We call this as  the VM-oblivious (VO) approach.
+In comparison, we analyze the design of
+a VM-centric approach (VC) which differentiates duplicates within a VM and cross VMs,
+and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.
 
-\item
-1) Localize the deduplication and data blocking within each VM as much as possible so 
-that any failure of a file system block mainly affects the associated VM.
-Localizing the snapshot data deduplication within a VM
-improves the system by increasing data independence between different VM backups,
+\subsection{Inner and cross VM deduplication}
+
+Inner-VM duplication can be very effective within VM's snapshots. There
+are typically a large number of duplicates existing among the snapshots
+for a single VM.  Localizing the snapshot data deduplication within a VM
+improves the system by:
+increasing data independence between different VM backups,
 simplifying snapshot management and statistics collection,
 and facilitating parallel execution of snapshot operations.
-\item
-2) Maintain a competitive deduplication effiency while being resource-friendly to other
-existing cloud services.
-Cross-VM duplication can be desirable since  there are many cloud images
-use widely-used software and libraries and their data blocks are duplicate. 
+On the other hand, cross-VM duplication can also be desirable mainly due to widely-used software and libraries. 
 As the result, different VMs tend to backup large amount of highly similar data.
-\item
-3)  Mininimize the number of data chunks shared among VMs and add extra replicas to incrase
-fault resilience for such data chunks.
-\end{itemize}
-
-\subsection{Key VC Strategies}
-
-%Inner-VM duplication can be very effective within VM's snapshots. There
-%are typically a large number of duplicates existing among the snapshots
-%for a single VM.
-
+We integrate those strategies together as follows.
 %Our multi-level pipeline process can minimize 
@@
 
-%Our VC differentiates duplicates within a VM and cross VMs,
-%and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.
-
 \begin{itemize}
-\item \textbf{Local duplicate search.}
-We start with the standard dirty bit approach in a coarse grain segment level
-and use the  Xen virtual device driver to implement a feature called ``changed block tracking''
-for the storage device and the dirty bit setting is maintained in a coarse grain level we call it a segment.
+\item \textbf{Dirtybit-based coarse-grain inner-VM deduplication.}
+The first-level deduplication is to follow the standard dirty bit approach, but is conducted
+in the coarse grain segment level.
+We use the  Xen virtual device driver which supports a feature called "changed block tracking''
+for the storage device
+and the dirty bit setting is maintained in a coarse grain level we call it a segment.
 In our implementation, the segment size is 2MB. 
@@
 %(VMware, Xen, Microsoft).  
-%VMware support it directly; 
-The VMWare hypervisor has an API to let external backup application know 
+VMware support it directly; the VMWare hypervisor has an API to let external backup application know 
 the changed areas since last backup. Xen doesn't directly support it, However, their open-source 
@@
 
-Since the best deduplication uses a nonuniform chunk size 
-in the average of 4K or 8K~\cite{??},  
-%This allows the system to achieve deduplication even when there are insertions/deletions which would
-%affect many fixed-size chunks.
-we conduct additional local inner-VM deduplication by comparing
-chunk signatures within a dirty segment from its parent snapshot. 
+\item \textbf{Chunk-level fine-grain inner-VM detection.}
+The best deduplication uses a nonuniform chunk size 
+in the average of 4K or 8K~\cite{??}. This allows the system to
+achieve deduplication even when there are insertions/deletions which would
+affect many fixed-size chunks.
+Thus the second-level inner-VM deduplication is to perform this chunking for
+dirty segments, and to compare the snapshot with its parent. 
 We load the chunk fingerprints in the corresponding segment from the
@@
 
-\item \textbf{Cross-VM deduplication with top $k$ popular chunks}
+\item \textbf{Cross-VM deduplication.}
 This step accomplishes the standard global fingerprint  comparison as conducted
@@
             %title={CDS Coverage},
-            xlabel={Total Data Stored (GB)},
+            xlabel={Total number of chunks stored},
             ylabel={CDS Coverage (\%)},
@@
             ]
-            \addplot[color=blue,mark=*] table[x=InputSize,y=A1] {figures/cds_coverage.txt};
-            \addplot[color=blue,mark=square*] table[x=InputSize,y=A2] {figures/cds_coverage.txt};
-            \addplot[color=blue,mark=triangle*,mark size=3] table[x=InputSize,y=A4] {figures/cds_coverage.txt};
-            \addplot[densely dashed,color=red,mark=*] table[x=InputSize,y=T1] {figures/cds_coverage.txt};
-            \addplot[densely dashed,color=red,mark=square*] table[x=InputSize,y=T2] {figures/cds_coverage.txt};
-            \addplot[densely dashed,color=red,mark=triangle*] table[x=InputSize,y=T4] {figures/cds_coverage.txt};
+            \addplot[color=blue,mark=*] table[x=InputChunks,y=A1] {figures/cds_coverage.txt};
+            \addplot[color=blue,mark=square*] table[x=InputChunks,y=A2] {figures/cds_coverage.txt};
+            \addplot[color=blue,mark=triangle*,mark size=3] table[x=InputChunks,y=A4] {figures/cds_coverage.txt};
+            \addplot[densely dashed,color=red,mark=*] table[x=InputChunks,y=T1] {figures/cds_coverage.txt};
+            \addplot[densely dashed,color=red,mark=square*] table[x=InputChunks,y=T2] {figures/cds_coverage.txt};
+            \addplot[densely dashed,color=red,mark=triangle*] table[x=InputChunks,y=T4] {figures/cds_coverage.txt};
             \legend{Measured (1\%CDS),Measured (2\%CDS),Measured (4\%CDS),Predicted (1\%CDS),Predicted (2\%CDS),Predicted (4\%CDS)};

### 2013-06-26 snapshot_system/arch.tex
modify all sections

@@
 1) a virtual block device driver, 2) a snapshot deduplication component,
-3) an append store client which provides facilities to store  and access snapshot data,
+3) an append store client to store  and access snapshot data,
 and 4)  a CDS client to support CDS index access. We will further discuss our deduplication scheme 
@@
 
+}
+
 \subsection{Snapshot Summaries for Approximate Deletion}
@@
 
+\comments{
+
 {\bf Discussion}
@@
 heavy I/O workload of deletion phase-2 from disturbing normal VM opeations.
+}

### 2013-06-29 snapshot_system/result.tex
revise
update graphs
Added two different versions of the extreme-binning efficiency comparison graph (still missing the CDS alg. efficiency). One is vertical and the other horizontal, not sure which is better.

@@
 
-\begin{figure}[htbp]
+\begin{figure}
     \centering
-  \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
+    \subfigure[Real VM backup performance]
+    {
+        \includegraphics[width=3in]{figures/parallel_backup_with_read.pdf}
+        \label{fig:withread}
+    }
+    \\
+    \subfigure[Deduplication and storage system performance]
+    {
+        \includegraphics[width=3in]{figures/parallel_backup_no_read.pdf}
+        \label{fig:noread}
+    }
     \caption{Throughput per-node with concurrent snapshot backup tasks}
@@
 \end{figure}
+
+% \begin{figure}[htbp]
+%   \centering
+%   \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
+%   \caption{Throughput per-node with concurrent snapshot backup tasks}
+%   \label{fig:parallel_backup}
+% \end{figure}
+
+\subsection{Comparison with Other Approaches}
+\subsubsection{Extreme Binning}
+%\comments{
+    %this version of the figure is vertical
+    \begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Extreme-Binning Efficiency},
+            ybar,
+            bar width=1.00cm,
+            symbolic x coords={Ex-Bin,CDS},
+            xlabel={Algorithm},
+            ylabel={Dedup. Efficiency (\%)},
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            xtick=data, %without this the symbolic coords may be repeated as filler
+            enlarge x limits=0.6, %used to push plots towards center
+            ymax=100,
+            nodes near coords,
+            nodes near coords align={vertical},
+            ]
+            \addplot coordinates {(Ex-Bin,90.16) (CDS,0)};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Deduplication Efficiency
+        ($efficiency=\frac{d-du}{d-du_{complete}}$)}
+  \label{fig-exbin-efficiecy}
+\end{figure}
+%}
+%same figure as above but horizontal (better for only two data points)
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Extreme-Binning Efficiency},
+            xbar,
+            width=7cm,
+            height=3.5cm,
+            %bar width=0.75cm,
+            symbolic y coords={Ex-Bin,CDS},
+            xlabel={Dedup. Efficiency (\%)},
+            %ylabel={Algorithm},
+            %extra x ticks={4.5,5.5,6.5} %to add extra ticks
+            ytick=data, %without this the symbolic coords may be repeated as filler
+            enlarge y limits=0.5,
+            xmax=115, %otherwise label overlaps with right border
+            nodes near coords,
+            nodes near coords align={horizontal},
+            ]
+            \addplot coordinates {(90.16,Ex-Bin) (0,CDS)};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Deduplication Efficiency
+        ($efficiency=\frac{d-du}{d-du_{complete}}$)}
+  \label{fig-exbin-efficiecy}
+\end{figure}
+
+\comments{
 
@@
 to users of the VMs, and/or reduce the possible deduplication throughput.
+
+}

### 2013-06-30 snapshot_system/result.tex
updated ex-bin efficiency bar charts. added ex-bin efficiency vs VC comparison graph.

@@
             bar width=1.00cm,
-            symbolic x coords={Ex-Bin,CDS},
+            symbolic x coords={SRB,VC},
             xlabel={Algorithm},
@@
             enlarge x limits=0.6, %used to push plots towards center
-            ymax=100,
+            ymin=85,
+            %ymax=100,
             nodes near coords,
@@
             ]
-            \addplot coordinates {(Ex-Bin,90.16) (CDS,0)};
+            \addplot coordinates {(SRB,89.99) (VC,90.51)};
             \end{axis}
@@
     \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$)}
-  \label{fig-exbin-efficiecy}
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
+  \label{fig-exbin-efficiency}
 \end{figure}
@@
             %bar width=0.75cm,
-            symbolic y coords={Ex-Bin,CDS},
+            symbolic y coords={SRB,VC},
             xlabel={Dedup. Efficiency (\%)},
@@
             enlarge y limits=0.5,
-            xmax=115, %otherwise label overlaps with right border
+            xmin=85,
+            xmax=92, %otherwise label overlaps with right border
             nodes near coords,
@@
             ]
-            \addplot coordinates {(90.16,Ex-Bin) (0,CDS)};
+            \addplot coordinates {(89.99,SRB) (90.51,VC)};
             \end{axis}
@@
     \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$)}
-  \label{fig-exbin-efficiecy}
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
+  \label{fig-exbin-efficiency}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Ex-Binning Efficiency},
+            xlabel={Number of VMs added},
+            ylabel={Dedup. Efficiency (\%)},
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            mark options=solid,
+            legend pos=south west,
+            %legend columns=2,
+            %legend style={
+            %    at={(0.5,-0.2)},
+            %anchor=north}
+            ]
+            \addplot[color=blue,mark=none] table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
+            \addplot[densely dotted, color=red,mark=none] table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
+            \addplot[loosely dotted, color=brown,mark=none] table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
+            \addplot[densely dashed,color=black,mark=none] table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
+            \legend{SRB,VC (1\%CDS),VC (2\%CDS),VC (4\%CDS)};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Deduplication Efficiency
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
+    Stateless Routing with Binning and VC.}
+  \label{fig-exbin-efficiency-graph}
 \end{figure}

### 2013-07-01 snapshot_system/result.tex
my local changes

--- 2013-06-24 snapshot_system/result.tex
@@
 because the number of fingerprints to process are just the same.
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=figures/single_backup_time.pdf, width=3.5in}
-  \caption{Time to backup a 40GB VM snapshot under different CDS memory usage settings}
-  \label{fig:single_vm_backup}
-\end{figure}
 
@@
 
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
+  \caption{Time to backup a dirty segment under SRB and VC approach}
+  \label{fig:srb_vs_vc}
+\end{figure}
+
+% \begin{figure}[htbp]
+%   \centering
+%   \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
+%   \caption{Throughput per-node with concurrent snapshot backup tasks}
+%   \label{fig:parallel_backup}
+% \end{figure}
+
+% \begin{table}
+% \begin{tabular}{ |p{1.5cm}|p{1.8cm}|p{1.2cm}|p{1.4cm}| }
+% \hline
+%  & Costs & Stateless routing with binning (s) & VM-centric approach (s) \\ \hline
+% \multirow{4}{*}{\vbox{I/O related}} & Read data & 0.05 & 0.05 \\ \cline{2-4}
+%  & Transfer data  & 0.017 & 0.017 \\ \cline{2-4}
+%  & Write data & 0.03 & 0.025 \\ \cline{2-4}
+%  & Subtotal & 0.097 & 0.092 \\ \hline
+% \multirow{5}{*}{\vbox{Dedupe related}} & Read index/recipe & 0.01 & 0.00045 \\ \cline{2-4}
+%  & Write index/recipe & 0.01 & 0.0051 \\ \cline{2-4}
+%  & Transfer fingerprints & 0.00058 & 0.00013 \\ \cline{2-4}
+%  & CDS lookup & N/A & 0.00034 \\ \cline{2-4}
+%  & Subtotal & 0.021 & 0.0064 \\ \hline
+% \multicolumn{2}{ |c| }{Total} & 0.12 & 0.098 \\
+% \hline
+% \end{tabular}
+% \caption{Time of backup a segment break down}
+% \label{tab:compare}
+% \end{table}
+
+\comments{
 \subsection{Read Snapshot}

### 2013-07-01 snapshot_system/result.tex

--- 2013-06-30 snapshot_system/result.tex
@@
 For each OS, 5 VMs are chosen, and every VM come with 10 full snapshots.
+
+\subsection{Replication cost}
+\begin{table}
+    \begin{tabular}{|c|c|}
+    \hline
+    PDS replication degree & Total space (GB) \\ \hline
+    3                      & 3065             \\ \hline
+    4                      & 3072             \\ \hline
+    5                      & 3079             \\ \hline
+    6                      & 3086             \\ \hline
+    7                      & 3093             \\ \hline
+    \end{tabular}
+\caption{Storage space cost under different PDS replication degree}
+\label{tab:replcation_cost}
+\end{table}
 
@@
 
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
+  \caption{Time to backup a dirty segment under SRB and VC approach}
+  \label{fig:srb_vs_vc}
+\end{figure}
+
 % \begin{figure}[htbp]
@@
 % \end{figure}
+
+% \begin{table}
+% \begin{tabular}{ |p{1.5cm}|p{1.8cm}|p{1.2cm}|p{1.4cm}| }
+% \hline
+%  & Costs & Stateless routing with binning (s) & VM-centric approach (s) \\ \hline
+% \multirow{4}{*}{\vbox{I/O related}} & Read data & 0.05 & 0.05 \\ \cline{2-4}
+%  & Transfer data  & 0.017 & 0.017 \\ \cline{2-4}
+%  & Write data & 0.03 & 0.025 \\ \cline{2-4}
+%  & Subtotal & 0.097 & 0.092 \\ \hline
+% \multirow{5}{*}{\vbox{Dedupe related}} & Read index/recipe & 0.01 & 0.00045 \\ \cline{2-4}
+%  & Write index/recipe & 0.01 & 0.0051 \\ \cline{2-4}
+%  & Transfer fingerprints & 0.00058 & 0.00013 \\ \cline{2-4}
+%  & CDS lookup & N/A & 0.00034 \\ \cline{2-4}
+%  & Subtotal & 0.021 & 0.0064 \\ \hline
+% \multicolumn{2}{ |c| }{Total} & 0.12 & 0.098 \\
+% \hline
+% \end{tabular}
+% \caption{Time of backup a segment break down}
+% \label{tab:compare}
+% \end{table}
 
@@
 \comments{
-
 \subsection{Read Snapshot}

### 2013-07-01 snapshot_system/failover.tex
Updated terminology in plots.

@@
 		xlabel={Number of VMs added},
-		ylabel={Avg. Links to a Block},
+		ylabel={Avg. links to a chunk},
 		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
@@
 	\end{tikzpicture}
-  \caption{Average number of VMs sharing a block in the global index}
+  \caption{Average number of VMs sharing a data chunk in the global index}
   \label{fig-vo-links}
@@
 		xlabel={Number of VMs},
-		ylabel={Avgerage Container links},
+		ylabel={Avg. links to an FSB},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
 		]
-		\addplot[color=blue,mark=*] table[x=VMs,y=ContainerLinks] {figures/vo_container_links.txt};
+		\addplot[color=blue,mark=*] table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
 		%\legend{Measured,Theoretical};
@@
 	\end{tikzpicture}
-  \caption{Measured Average number of VMs sharing a container in the global index (for VO)}
-  \label{fig-vo-container-links}
+  \caption{Measured Average number of VMs sharing a 64MB Filesystem Block in the global index (for VO)}
+  \label{fig-vo-fsb-links}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Avg CDS Container Links},
+		xlabel={Number of VMs},
+		ylabel={Avg. links to CDS FSB},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		]
+		\addplot[color=blue,mark=*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
+		%\legend{Measured,Theoretical};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Measured Average number of VMs sharing a 64MB CDS Filesystem Block for (VC with 5\% CDS)}
+  \label{fig-cds-fsb-links}
 \end{figure}
@@
 in our current testbed we have measured the average number of links
-per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{vo-container-links})
+per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{vo-fsb-links})
 in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
-was 11 using a 5\% CDS. From Figure~\ref{vo-container-links} you can see that as you add VMs, the average
+was 11 using a 5\% CDS. From Figure~\ref{vo-fsb-links} you can see that as you add VMs, the average
 number of links to a chunk increases. We expect that this trend will level out with larger datasets, but

### 2013-07-01 snapshot_system/result.tex
Updated terminology in plots.
cleaned up the paper directory (moved all pdf figures to the images dir) and corrected references.
added srb comparison text, updated references throughout paper.

@@
 under different CDS memory usage settings, the results of backup time break down are shown in
-firure~\ref{fig:single_vm_backup}.
+Figure~\ref{fig:single_vm_backup}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3in]{figures/single_backup_time.pdf}
+    \caption{Backup times for varying CDS sizes}
+    \label{fig:single_vm_backup}
+\end{figure}
 
@@
 
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
-  \caption{Time to backup a dirty segment under SRB and VC approach}
-  \label{fig:srb_vs_vc}
-\end{figure}
-
 % \begin{figure}[htbp]
@@
 \subsection{Comparison with Other Approaches}
-\subsubsection{Extreme Binning}
+\subsubsection{Stateless Routing with Binning}
+We compare our system with Stateless Routing with Binning (SRB) in terms of
+both backup time and deduplication efficiency. SRB is the same as the stateless
+routing algorithm given in the Extreme Binning\cite{??} paper. the
+deduplication efficiency is compared in
+Figure~\ref{fig-exbin-efficiency-graph}, showing the deduplication efficiency
+(percent of duplicate chunks which are deduped) of SRB and VC with several
+different CDS sizes. From the graph you can see that VC provides similar or
+better deduplication efficiency in all cases. In Figure~\ref{fig:srb_vs_vc} you
+can see simulated backup times using actual throughput numbers from our test
+backup cluster, and VC outperforms SRB mainly due to significantly fewer index
+lookups (since SRB uses hash-partitioning, all lookups are essentially random
+and caching will be largely innefective).  \emph{Should we use one of the two
+bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
+charts in the paper until we decide? If we use the bar charts some tex will
+have to be changed. We could also add each of the CDS sizes to the bar chart
+and have 4 bars instead of 2.}
 %\comments{
@@
         ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
-  \label{fig-exbin-efficiency}
+  \label{fig-exbin-efficiency1}
 \end{figure}
@@
         ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
-  \label{fig-exbin-efficiency}
+  \label{fig-exbin-efficiency2}
 \end{figure}
 
+%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
 \begin{figure}[ht]
@@
   \label{fig-exbin-efficiency-graph}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
+  \caption{Time to backup a dirty segment under SRB and VC approach}
+  \label{fig:srb_vs_vc}
 \end{figure}

### 2013-07-01 snapshot_system/snapshot.tex
update grpah
Updated terminology in plots.
cleaned up the paper directory (moved all pdf figures to the images dir) and corrected references.
added srb comparison text, updated references throughout paper.

@@
 accumulate small local chunks. We manage this accumulation process using an append-store  scheme
-and discuss this in details in Section~\ref{sect:arch}.
+and discuss this in details in Section~\ref{sec:arch}.
 The system allows all machines conduct the backup in parallel in different machines, and each machine
@@
 
-CDS chunks are stored in a separate
-append-store instance. In this way, each file block for non-CDS chunks is associated with one VM
-and does not contain any CDS chunk. 
+CDS chunks are stored in a separate append-store instance. In this way, each
+file block for non-CDS chunks is associated with one VM and does not contain
+any CDS chunks. 
 \end{itemize}
@@
 %source ../vm_snapshot_sim/images/log-log.disk.eps
- \includegraphics[width=3in]{log-log-disk.pdf}
+ \includegraphics[width=3in]{figures/log-log-disk.pdf}
 \caption{Duplicate frequency versus  chunk ranking in a log scale.}
@@
 
+\comments{ %this table is superceded by the graph below it
 \begin{table}
@@
 \end{table}
+}
 
@@
   \caption{fixed-alpha predicted vs. actual CDS coverage as data size increases.}
-  \label{fig-vo-links}
+  \label{fig-cds-coverage}
 \end{figure}

### 2013-07-01 snapshot_system/snapshot.tex
updated references and added content linking text to figures.

@@
 \]
-where $(\frac{m*C}{D*E})^{1-\alpha}$ represents the percentage of the remaining chunks detected as duplicates
-after inner VM deduplication. 
+where $(\frac{m*C}{D*E})^{1-\alpha}$ represents the percentage of the remaining
+chunks detected as duplicates after inner VM deduplication.
+Figure~\ref{fig-cds-coverage} shows measured CDS coverage in our 35 VM dataset.
+You can see from the graph that the coverage actually increases as the datasize
+increases, which indicates that $\alpha$ increases with the datasize (a
+fixed-$\alpha$ model would predict constant coverage). This makes the CDS even
+more effective, as the coverage of the CDS increases as more data is added.
 %Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
@@
 
-As illiustrated in Figure~\ref{fig-vo-links},
+As illustrated in Figure~\ref{fig-vo-links}\emph{I am not sure where this reference should point, but I don't think it is pointing to the right figure},
 when the number of machines at each cluster increases, the number of total VMs increases.

### 2013-07-02 snapshot_system/arch.tex
added srb comparison text, updated references throughout paper.
update

@@
 %[describe the data structure in underlying storage]
-\subsection{Append store for backup data}
-The Append Store (AS) is our underlining storage engine for storing snapshot data in the distributed file system
-after deduplication.
+\subsection{A VM-centric snapshot store for backup data}
+
+We build a snapshot storage on the top of a distribued file system.
+Following the VM-centric idea for the purpose of fault isolation,
+each VM has its own snapshot store, contaning new data chunks which are considered
+to be non-duplicates.
+There is also a special store containing all PDS chunks shared amony different VMs.
+The replication degree of file blocks of snapshot stores in the underlying file system
+Extra replication of this store is added as discussed in Section~\ref{sect:analysis}.
+As shown in Fig.\ref{fig:as_arch}, we explain the data structure of snapshot stores as follows.
+
+\begin{itemize}
+\item The PDS snapshot contains a set of commonly used data chunks and is accessed by its offset and size
+in the corresponding DSF file.
+The PDS index uses the offset and size as a reference in its index structure.
+
+\item Each non-PDS snapshot store is divided into a set of containers and each of them is approximately 
+1G bytes. The reason we dividie the snapshot into containers is to simplify the compact process
+conducted perioidcally.  There are chunks deleted without any reference from other snapshots
+and to reclaim the space of these useless chunks, a compaction  routine can work on one container at a time
+and copy used data chunks to another container.
+	\begin{itemize}
+	\item Each container is divided into a set of chunk data groups. Each group is composed of
+	a set of data chunks and is the basic unit for the snapshot in data access and retrieval. 
+	In writing a chunk group, data chunks in this group are compressed together and then stored. 
+	When accessing a particular chunk, its chunk group is retrieved from the disk storage
+	and uncompressed. Given the high spatial locality 
+in snapshot data accessing~\cite{Sampling,FoundationPaper},
+	retrieval of  data chunks by group naturally fits in the prefetching scheme  to speedup
+	snapshot access. A  typical chunk group contains 100 to 1000 chunks, with an average size of 
+200-600KB.
+Chunk groupping also reduces the  container index size as we discuss below. 
+Given  the average chunk size  4KB,  the index size for a 1GB container reduces from 10MB to 100KB when
+the chunk group size is 100.
+%%CBlock, then the overall index size is reduced to $1/m$. 
+%n our implementation, using $m=100$ reduces the index for
+%a 1GB container from 10 MB to 100 KB.
+	\item 
+Each data container is represented by three data files in the DFS:
+1) the container data file holds the actual content of data chunks, 
+2) the container index file is responsible for translating a data reference
+into its location within a container, and 
+3) a chunk deletion log file saviing all the deletion requests within  the container.
+A VM snapshot store typically has a small number of containers because each container is fairly large with an average size of 1GB bytes, it 
+maintains a limited number of snapshots (e.g. 10 in the Alaibaba case),
+and new snapshot data chunks can be effectively compressed in chunk groups in additon to  deduplciation.
+
+\item We maintain  a chunk counter and assign the current number 
+as a chunk ID (called CID) within this container as a reference of a new chunk added to a container. 
+Since data chunks are always appended to the snapshot store, 
+ a CID is monotoically increasing.
+A data chunk reference stored in the index of snapshot reeipts
+is composed of two parts: a container ID (2 bytes) and CID (6 bytes).
+Once a snapshop is to be accessed access, the receipt in this snapshot will point to either a data chunk
+in the PDS or a reference number with a container ID and CID.
+With a container ID, the corresponding container index file is accessed and 
+the chunk group is identified using this CID.
+Once this chunk group is loaded to memory, its header contains the exact offset of the corresponding chunk and the content is then accessed from the memory buffer.
+
+%Every container  Store assign every piece of data a CID for its internal data referencing. 
+%When new data is appended, its CID is the current largest CID in that container plus one.
+%As a result, all the data locations are naturally indexed by this self-incremental CID, 
+%no extra sorting is needed.
+	\end{itemize}
+\end{itemize}
+
+%acceretrieved  and ret
+%Using CBlock brings us several advantages: First, the write workload to DFS master is greatly reduced; second, grouping
+%small chunks gives better compression. Third, reading a CBlock (200 - 600 KB) typically cost the same amount of disk 
+%seek as reading a 4KB chunk. Finally, this greatly reduces the size of index. Let $m$ be the number of chunks in each
+%CBlock, then the overall index size is reduced to $1/m$. In our implementation, using $m=100$ reduces the index for
+%a 1GB container from 10 MB to 100 KB.
+
+% of  divided into a set of data containers.
+%Each container has 3 parts.
+%Each chunk in the snapshot is referenced by the following data format
+
+%The Append Store (AS) is our underlining storage engine for storing snapshot data in the distributed file system
+%after deduplication.
 %AS is built on top of our highly scalable distributed file system (DFS), 
@@
   \epsfig{file=images/append_store_arch.pdf, width=3in}
-  \caption{Architecture of Append Store}
+  \caption{Data structure of VM snapshot stores.}
   \label{fig:as_arch}
@@
 
-AS supplies three interfaces: {\em get(ref)} accepts a data reference and retrieves data, 
-{\em put(data)} accepts data and returns a reference to be stored in metadata recipes, 
-{\em delete(ref)} 
-deletes the data pointed by the reference.
-Under the hood, small var-sized data are grouped and stored into larger data containers. Each VM has
-its snapshot data stored in its own Append Store, specified by the VM ID. 
-We split every Append Store into multiple data containers so that reclaiming the disk space would not 
-result in rewriting all the data at the same time.
+The snapshot  store supports three API calls.
+\begin{itemize}
 
-As shown in Fig.\ref{fig:as_arch}, every data container is represented as three data files in DFS:
-the data file holds all the actual data, the index file is responsible for translating data reference
-into data locations, and a deletion log file remembers all the deletion requests to the container.
+%AS supplies three interfaces: {\em get(ref)} accepts a data reference and retrieves data, 
+\item {\em Put(data)} places data chunk into the snapshot store and returns a reference to be stored in 
+the recipe metadata of a snapshot.
 
-A data reference is composed of two parts: a container ID (2 bytes) and CID (6 bytes).
-Append Store assign every piece of data a CID for its internal data referencing. 
-When new data is appended, its CID is the current largest CID in that container plus one.
-As a result, all the data locations are naturally indexed by this self-incremental CID, 
-no extra sorting is needed.
+The write requests to append a data chunk to a VM store are accumulated in the client side. 
+When the number reaches the group size $g$, the snapshot store client compresses
+the accmnulated   chunk group, adds a chunk group index  in the begining, and then
+append the header and data  to the corresponding VM file,
+Then a new container  index entry is also created and is written the corresponding
+container index file.
 
-Append Store groups multiple chunk data (i.e., 100) into larger units, called {\em CBlock}.
-CBlock is the basic unit for append store's internal read/write/compression.
-There is one index entry in the container index corresponding to every CBlock. It keeps the first chunk's CID
-in that CBlock, and the CBlock data's size and location.
+The writing of PDS data chunks is conducted periodically when there is a new PDS caclulation.
+Since the PDS dataset is small, a new PDS file is created during the periodical update.
+\item{\em Get(reference)}.
+The fetch operation for the PDS data chunk is straightforward since each referecence contains 
+the offset and size within the PDS  underlying  file.
+We also maintain a small data cache for the PDS data service to speedup the process.
 
-Using CBlock brings us several advantages: First, the write workload to DFS master is greatly reduced; second, grouping
-small chunks gives better compression. Third, reading a CBlock (200 - 600 KB) typically cost the same amount of disk 
-seek as reading a 4KB chunk. Finally, this greatly reduces the size of index. Let $m$ be the number of chunks in each
-CBlock, then the overall index size is reduced to $1/m$. In our implementation, using $m=100$ reduces the index for
-a 1GB container from 10 MB to 100 KB.
-
-In order to read a chunk data by reference, Append Store client first loads the
-container index file specified by the container ID, then search the CBlock index to find the entry that covers the chunk by CID.
-After that, it reads the whole CBlock data from DFS, decompress it, seek the exact chunk data specified by CID. 
-Finally, the client updates itws internal chunk data cache with the newly loaded contents to anticipate future sequential reads.
-
-Write requests to append store are accumulated. When the number reaches $m$, the AS client forms a CBlock by assigning 
-every chunk a CID, compress the CBlock data, and append it to the CBlock data file. Then a new CBlock index entry is appended
-to CBlock index.
-
-Append store adopts lazy delete strategy. The deletion requests are appended into every container's deletion log file with the CID of data to be deleted.
-CIDs in deletion log are guaranteed to be referenced by nobody and can be safe deleted in future. 
-Periodically, snapshot management system asks append store to compact containers in order to reclaim disk space. 
-The actual compaction will only take place when the number of deleted items reached $d\%$ of container's capacity. 
-During compaction, append store creates a new container (with the same container ID) to replace the 
+To read a non-PDS chunk data by a reference,  the snapshot store client first loads the
+corresponding VM's container index file specified by the container ID, then searches the chunk
+group  that  covers the chunk by the group  CID range.
+After that, it reads the whole chunk group from DFS, decompresses it, seeks the exact chunk data 
+specified by the CID. 
+Finally, the client updates its internal chunk data cache with the newly loaded content to 
+anticipate future sequential reads.
+\item {\em Delete(reference)}.
+A data chunk can be deleted when a snapshot expires or gets deleted explictly by a user.
+We will discuss the snapshot deletion shortly in the following subsection.
+%deletes the data pointed by the reference.
+%Under the hood, small var-sized data are grouped and stored into larger data containers. Each VM has
+%its snapshot data stored in its own Append Store, specified by the VM ID. 
+%We split every Append Store into multiple data containers so that reclaiming the disk space would not 
+%result in rewriting all the data at the same time.
+When deletion requests issued for a specific container,
+those requests are logged into the  container's deletion log file initially and thus  a lazy
+delection strategy is exercised.
+Once CIDs appear in
+the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
+Periodically, the sanpshot  store picks those containers with an excessive
+number of deletion requests to  compact and  reclaim the corrwsponding disk space. 
+%The actual compaction will only take place when the number of deleted items 
+%reached $d\%$ of container's capacity. 
+During compaction, the snapshot store creates a new container (with the same container ID) to replace the 
 existing one. This is done by sequentially scan the old container, copying all the chunks that are not 
-found in deletion log to the new container, creating new CBlocks and indices. 
+found in the deletion log to the new container, creating new chunk groups and indices. 
 However, every chunk's CID is plainly copied rather than re-generated. This does not affect the sorted
@@
 in upper level recipes are unaffected, and the data reading process is as efficient as before.
+\end{itemize}
+
+%As shown in Fig.\ref{fig:as_arch}, every data container is represented as three data files in DFS:
+%the data file holds all the actual data, the index file is responsible for translating data reference
+%into data locations, and a deletion log file remembers all the deletion requests to the container.
+%
+%A data reference is composed of two parts: a container ID (2 bytes) and CID (6 bytes).
+%Append Store assign every piece of data a CID for its internal data referencing. 
+%When new data is appended, its CID is the current largest CID in that container plus one.
+%As a result, all the data locations are naturally indexed by this self-incremental CID, 
+%no extra sorting is needed.
+
+%Append Store groups multiple chunk data (i.e., 100) into larger units, called {\em CBlock}.
+%CBlock is the basic unit for append store's internal read/write/compression.
+%There is one index entry in the container index corresponding to every CBlock. It keeps the first chunk's CID
+%in that CBlock, and the CBlock data's size and location.
+%
+%Using CBlock brings us several advantages: First, the write workload to DFS master is greatly reduced; second, grouping
+%small chunks gives better compression. Third, reading a CBlock (200 - 600 KB) typically cost the same amount of disk
 
@@
 
-\subsection{Snapshot Summaries for Approximate Deletion}
+\subsection{Fast VM-centric Snapshot Deletion with a Two-Phase  Apprxoimation}
+
 In a busy VM cluster, snapshot deletions are as frequent as snapshot creations.
-Our system adopts lazy delete strategy so that all snapshot deletions are scheduled
-in the backup time window at midnight. 
-Therefore, snapshot deletions must be fast enough to fit in time window and
-efficient enough to satisfy our resource constraints.
-However, there is no simple solution can achieve these goals with high reliability.
-Hence we designed a two-phase {\em approximate deletion} strategy to trade deletion accuracy for
+The VM-centric snapshot storage design simplifies the deletion process since we need to look
+for the useless chunks within each VM when deleting a snapshot.
+The PDS data chunks are commonly shared all VMs and we donot consider their referene
+counting  during snapshot deletion.
+The selection of PDS data chunks   is updated periodically independent of snapshot deletion process.
+
+While we can use the standand mark-sweep technique~\cite{mark-sweep}, 
+it takes time to conduct this process everytime there is a snapshot deletion request.
+In the case of Alibaba, snapshot backup is conducted automatically and there are 
+about 10 snapshot stored for  every user. Then when there is
+a new snapshort created every day,  there will be  a snapshort expired everyday to maintain
+a balanced storage use. Given a large number of snapshot deletion requests, we are seeking
+a fast solution with a very low resource usage to delete snapshorts with an approximation.
+
+With this in mind, we develop a two-phase {\em approximated} deletion strategy to trade deletion accuracy for
 speed and resource usage. Our method sacrifaces a tiny percentage of storage leakage
-to effectively identify unused blocks in $O(n)$ speed, with $n$ being the logical amount of blocks 
+to effectively identify unused blocks in $O(n)$ speed, with $n$ being the logical amount of chunks 
 to be deleted.
+
+%Our system adopts VM-centric snapshot  lazy delete strategy so that all snapshot deletions are scheduled
+%in the backup time window at midnight. 
+%Therefore, snapshot deletions must be fast enough to fit in time window and
+%efficient enough to satisfy our resource constraints.
+%However, there is no simple solution can achieve these goals with high reliability.
 %Our hybrid deletion strategy, using fuzzy deletion regularly and accurate deletion periodically,
@@
 
-{\bf Snapshot Summaries}
+{\bf Snapshot Summaries.}
+with this in mind, we compute a bloom-filter fingerprint summary for all non-PDS chunks used 
+by a snapshot during  its creation time.
 
@@
 \end{enumerate}
-
-\comments{
 
@@
 heavy I/O workload of deletion phase-2 from disturbing normal VM opeations.
-}

### 2013-07-02 snapshot_system/failover.tex

@@
 
-Figure~\ref{fig-vo-links} shows the average number of VMs shared by 
-a block in the global index as more VMs are added in VO. 
-The first 15 VMs are all windows machines, so that explains the initial 
-higher values, but for the most part the average number of 
-links is between 1.5 and 2.
+Figure~\ref{fig-vo-links} shows the average number of VMs sharing a block in
+the global index as more VMs are added in VO.  The first 15 VMs are all windows
+machines, so that explains the initial higher values, but for the most part the
+average number of links is between 1.5 and 2. Figure~\ref{fig-vo-fsb-links}
+shows the average number of VMs sharing a filesystem block (FSB) in the global
+index, but only for the 15 windows machines (the last machine has a much larger
+hard-drive, and therefore more unique data, which explains the drop-off in the
+last datapoint).  This is a reasonable assumption, that a cluster will have one
+OS dominating, and for our small dataset the number of links to an FSB
+increases as more VMs of the same OS are added. You can see in the plot however
+that even though a FSB contains 16K chunks, the average number of links to an
+FSB is only several times the number of average links to a chunk. This is
+because even in the VO global deduplication model, as long as writes are
+batched a single FSB will tend to contain chunks from only a small number of
+VMs. Below we show the significant impact the number of links has on VM backup
+reliability.
 
@@
 in our current testbed we have measured the average number of links
-per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{vo-fsb-links})
+per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{fig-vo-fsb-links})
 in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
-was 11 using a 5\% CDS. From Figure~\ref{vo-fsb-links} you can see that as you add VMs, the average
+was 11 using a 5\% CDS. From Figure~\ref{fig-vo-fsb-links} you can see that as you add VMs, the average
 number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
@@
 
-The figure shows that even as the number of VMs sharing a CDS file block 
-increase by 100 times, the availability only decreases
-slightly.
-The key factor placed is that  $N_1 +N_2 << N_o$, caused by the fact that
-the VM-centric approach localizes deduplication and
-packs  data blocks for one VM as much as possible.
-The extra replicaton for CDS blocks 
-also signficantly increses the snapshot availability even a CDS file block
+Figure~\ref{fig-vm-availability} shows the reliability of VM backups as storage
+nodes fail for different numbers of links to average blocks in the index. We
+chose 5 and 11 for the VO and VC block links counts because those are what we
+measured in our dataset, and chose higher numbers to account for much larger
+datasets. As you can see from the graph, even small changes in the number of
+links to VO blocks has a significant impact on reliability, while even a 100
+times increase in the VC block link counts only slightly affects VC
+reliability.  The key factor placed is that  $N_1 +N_2 << N_o$, caused by the
+fact that the VM-centric approach localizes deduplication and packs  data
+blocks for one VM as much as possible.  The extra replicaton for CDS blocks
+also signficantly increaes the snapshot availability even when a CDS file block
 is shared by every VM.
@@
 Figure~\ref{fig-cds-replication}
-shows the advantages of increasing the replication factor for CDS blocks. These figures together show
-the advantages of the VM-centric model, and the advantages that separating the replication factor for popular blocks
-can have on reliability.
+shows the advantages of increasing the replication factor for CDS blocks. the
+numbers in the graph are only meant to be relative, as we assume higher CDS
+block links than we have measured in our dataset (to account for a much larger
+body of data). It is easy to see though that increasing the replication of just
+the CDS blocks (which are the most popular blocks) can have a positive impact
+on the overall reliablity of the VM backups. These figures together show the
+advantages of the VM-centric model, and the advantages that separating the
+replication factor for popular blocks can have on reliability.
 

### 2013-07-02 snapshot_system/arch.tex
Updated graphs to the new versions.

@@
 \section{Architecture and Implementation Details}
+\label{sec:arch}
 %[describe what is going to be presented in this section]
@@
 
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=6in]{images/socc_arch_cluster.pdf}
+    \caption{System Architecture}
+    \label{fig:arch_cluster}
+\end{figure*}
+
+\comments{%socc_arch_cluster now includes the entire arch instead of having 2 figures
 \begin{figure}
@@
   \centering
-  \epsfig{file=images/append_store_arch.pdf, width=3in}
+  \epsfig{file=images/sstore_arch.pdf, width=3in}
   \caption{Data structure of VM snapshot stores.}
+  \label{fig:as_arch}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=images/pds_arch.pdf, width=3in}
+  \caption{System architecture for PDS data store.}
   \label{fig:as_arch}

### 2013-07-02 snapshot_system/arch.tex
update

@@
 speed and resource usage. Our method sacrifaces a tiny percentage of storage leakage
-to effectively identify unused blocks in $O(n)$ speed, with $n$ being the logical amount of chunks 
-to be deleted.
+to effectively identify unused chunks in $O(n)$ speed, with $n$ being the logical number of non-PDS chunks 
+to be deleted from a VM snapshort store.
 
@@
 %accomplishs our speed, resource usage and relibility goals very well.
+\begin{itemize}
+\item {\bf Computation for snapshot fingerprint summary.}
+Every time there is a new snapshot created,
+we compute a bloom-filter fingerprint summary for all non-PDS chunks used 
+in this snapshot.
+%{\bf Creating bloom filter} Scan all the living snapshot recipess and their segment recipes,
+%for every reference pointing to append store, add it to the bloom filter.
 
-{\bf Snapshot Summaries.}
-with this in mind, we compute a bloom-filter fingerprint summary for all non-PDS chunks used 
-by a snapshot during  its creation time.
-
-{\bf Approximate Deletion Phase-1}
-The goal of approximate deletion phase-1 to fast identify unused blocks 
-which are no longer referenced by other snapshots after a snapshot deletion.
-Instead of scanning the entire append store indices, we merge the type-1 summaries of all
-valid snapshots. Since each VM has uniform bloom filter parameters to create snapshot summaries, 
-such merged summeries give us a compact representation of
-all block fingerprints that are still in use.
-Thus by the property of bloom filter, if a fingerprint is not found in merged summaries, 
-we are certain that block is no longer used by any valid snapshot, it would be then added
-to append store's deletion log.
+\item {\bf Phase 1: Fast approximate deletion.}
+Then when there is a snapshot deletion, 
+we use  the snapshot fingerprint summary to identify if  chunks to be deleted from one snapshot
+are still used by other snapshots. 
+This is done approximately and quickly by compariing the fingerprints of deleted chunks with
+the fingerrinter bloomerfilter summary of other live snapshots.
+Since the number of live snapshots is limited for each VM (e.g. 10 in the Alibaba's production system), 
+the complexity of comparison is acceptable.
+%Instead of scanning the entire append store indices, we merge the type-1 summaries of all
+%valid snapshots. 
+%Since each VM has uniform bloom filter parameters to create snapshot summaries, 
+%such merged summeries give us a compact representation of
+%all block fingerprints that are still in use.
+%Thus by the property of bloom filter, if a fingerprint is not found in merged summaries, 
+%we are certain that block is no longer used by any valid snapshot, it would be then added
+%to append store's deletion log.
 However, there is a small false-positive probility which
@@
 
-{\bf Approximate Deletion Phase-2}
+\item {\bf Phase 2: Perodic repair of leakage}
 %[exlpain why second bloom filter, why scan append store]
-We designed the second phase of approxmite deletion to solve the 
-temporary storage leakage problem mentioned above.
-In this phase we scan the entire append store indices, 
+Since there are certain unused chunks which are not deleted during
+the approximated deletion, the leakge repair is conducted periodically.
+In this phase we scan the entire snapshot store indices of a VM, 
 using the merged type-2 snapshot summaries to check if any of them are not
@@
 \end{enumerate}
+\end{itemize}
+
+%\item {\bf Check existance} For every data reference in the deleted snapshot recipe and its segment recipes,
+%check the existance of that data reference in bloom filter. If not found, it is safe to delete that piece of data from append store
+%because no living snapshots has referenced it.
+
+The overall time of running a approximate deletion for one snapshot deletion would be scanning
+all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
+parallel and is much faster than loading recipes from DFS:
+\begin{equation}
+T = (N_{SS} + 1) * T_{scan\_recipes}
+\end{equation}
+
+Using the example and analysis in previous section, this approximate deletion can be done in 5 minutes.
+Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
+when set $P_{bl}$ to 0.01, the memory footprint of approximate deletion is about 15 MB.
+~
 

### 2013-07-02 snapshot_system/failover.tex
Updated graphs to the new versions.

@@
     {
-        \includegraphics[width=3in]{images/share_model_vc.pdf}
+        \includegraphics[width=3in]{images/share_vc.pdf}
         \label{fig:share_vc}
@@
     {
-        \includegraphics[width=3in]{images/share_model_vo.pdf}
+        \includegraphics[width=3in]{images/share_vo.pdf}
         \label{fig:share_vo}
@@
 shows the average number of VMs sharing a filesystem block (FSB) in the global
-index, but only for the 15 windows machines (the last machine has a much larger
-hard-drive, and therefore more unique data, which explains the drop-off in the
-last datapoint).  This is a reasonable assumption, that a cluster will have one
-OS dominating, and for our small dataset the number of links to an FSB
-increases as more VMs of the same OS are added. You can see in the plot however
+The first 15 VMs added are all windows (though the last one has a much larger
+hard drive which explains the drop after 14), which is why the number of block
+links goes up quickly for the first half of the graph. You can see in the plot
 that even though a FSB contains 16K chunks, the average number of links to an

### 2013-07-02 snapshot_system/arch.tex
update

@@
 We first present its architecture,
-then introduce the two major contributions: the colocated deduplication 
+then introduce the two major contributions: the collocated deduplication 
 scheme and the snapshot deletion strategy.
@@
 consists of from hundreds to thousands of physical machines, each of which can
-host tens of xen-based\cite{Barham2003} VMs.
+host tens of Xen-based\cite{Barham2003} VMs.
 Alibaba's cloud platform provides a hadoop-like infrastructure, 
@@
 %\item[MapReduce]: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
-\item {\bf Distributed memory cache} A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inqueries. 
+\item {\bf Distributed memory cache} A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inquiries. 
 \end{enumerate}
@@
 %[describe the architecture frm node side]
-{\bf Node Architecuture} 
+{\bf Node Architecture} 
 Our node-side architecture, depicted in figure.\ref{fig:arch_vm}, consists of
@@
 the change status of every fix-size segment of the virtual disk. 
-When the VM issue a disk write, the bits coresponding to the segments that covers 
+When the VM issue a disk write, the bits corresponding to the segments that covers 
 the modified disk region are set, thus letting snapshot deduplication component knows these
@@
 
-We build a snapshot storage on the top of a distribued file system.
+We build a snapshot storage on the top of a distributed file system.
 Following the VM-centric idea for the purpose of fault isolation,
-each VM has its own snapshot store, contaning new data chunks which are considered
+each VM has its own snapshot store, containing new data chunks which are considered
 to be non-duplicates.
-There is also a special store containing all PDS chunks shared amony different VMs.
+There is also a special store containing all PDS chunks shared among different VMs.
 The replication degree of file blocks of snapshot stores in the underlying file system
@@
 \item Each non-PDS snapshot store is divided into a set of containers and each of them is approximately 
-1G bytes. The reason we dividie the snapshot into containers is to simplify the compact process
-conducted perioidcally.  There are chunks deleted without any reference from other snapshots
+1G bytes. The reason we divide the snapshot into containers is to simplify the compact process
+conducted periodically.  There are chunks deleted without any reference from other snapshots
 and to reclaim the space of these useless chunks, a compaction  routine can work on one container at a time
@@
 200-600KB.
-Chunk groupping also reduces the  container index size as we discuss below. 
+Chunk grouping also reduces the  container index size as we discuss below. 
 Given  the average chunk size  4KB,  the index size for a 1GB container reduces from 10MB to 100KB when
@@
 into its location within a container, and 
-3) a chunk deletion log file saviing all the deletion requests within  the container.
+3) a chunk deletion log file saving all the deletion requests within  the container.
 A VM snapshot store typically has a small number of containers because each container is fairly large with an average size of 1GB bytes, it 
-maintains a limited number of snapshots (e.g. 10 in the Alaibaba case),
-and new snapshot data chunks can be effectively compressed in chunk groups in additon to  deduplciation.
+maintains a limited number of snapshots (e.g. 10 in the Alibaba case),
+and new snapshot data chunks can be effectively compressed in chunk groups in addition to  deduplication.
 
@@
 Since data chunks are always appended to the snapshot store, 
- a CID is monotoically increasing.
-A data chunk reference stored in the index of snapshot reeipts
+ a CID is monotonically increasing.
+A data chunk reference stored in the index of snapshot recipes
 is composed of two parts: a container ID (2 bytes) and CID (6 bytes).
-Once a snapshop is to be accessed access, the receipt in this snapshot will point to either a data chunk
+Once a snapshot is to be accessed access, the receipt in this snapshot will point to either a data chunk
 in the PDS or a reference number with a container ID and CID.
@@
 When the number reaches the group size $g$, the snapshot store client compresses
-the accmnulated   chunk group, adds a chunk group index  in the begining, and then
+the accumulated   chunk group, adds a chunk group index  in the beginning, and then
 append the header and data  to the corresponding VM file,
@@
 
-The writing of PDS data chunks is conducted periodically when there is a new PDS caclulation.
+The writing of PDS data chunks is conducted periodically when there is a new PDS calculation.
 Since the PDS dataset is small, a new PDS file is created during the periodical update.
 \item{\em Get(reference)}.
-The fetch operation for the PDS data chunk is straightforward since each referecence contains 
+The fetch operation for the PDS data chunk is straightforward since each reference contains 
 the offset and size within the PDS  underlying  file.
@@
 \item {\em Delete(reference)}.
-A data chunk can be deleted when a snapshot expires or gets deleted explictly by a user.
+A data chunk can be deleted when a snapshot expires or gets deleted explicitly by a user.
 We will discuss the snapshot deletion shortly in the following subsection.
@@
 those requests are logged into the  container's deletion log file initially and thus  a lazy
-delection strategy is exercised.
+deletion strategy is exercised.
 Once CIDs appear in
 the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
-Periodically, the sanpshot  store picks those containers with an excessive
-number of deletion requests to  compact and  reclaim the corrwsponding disk space. 
+Periodically, the snapshot  store picks those containers with an excessive
+number of deletion requests to  compact and  reclaim the corresponding disk space. 
 %The actual compaction will only take place when the number of deleted items 
@@
 
-\subsection{Fast VM-centric Snapshot Deletion with a Two-Phase  Apprxoimation}
+\subsection{ VM-centric Approximate Snapshot Deletion with Leak Repair}
 
@@
 for the useless chunks within each VM when deleting a snapshot.
-The PDS data chunks are commonly shared all VMs and we donot consider their referene
+The PDS data chunks are commonly shared all VMs and we donot consider their reference
 counting  during snapshot deletion.
@@
 
-While we can use the standand mark-sweep technique~\cite{mark-sweep}, 
-it takes time to conduct this process everytime there is a snapshot deletion request.
+While we can use the standard mark-sweep technique~\cite{mark-sweep}, 
+it takes time to conduct this process every time there is a snapshot deletion request.
 In the case of Alibaba, snapshot backup is conducted automatically and there are 
 about 10 snapshot stored for  every user. Then when there is
-a new snapshort created every day,  there will be  a snapshort expired everyday to maintain
+a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
 a balanced storage use. Given a large number of snapshot deletion requests, we are seeking
-a fast solution with a very low resource usage to delete snapshorts with an approximation.
+a fast solution with a very low resource usage to delete snapshots with an approximation.
 
-With this in mind, we develop a two-phase {\em approximated} deletion strategy to trade deletion accuracy for
-speed and resource usage. Our method sacrifaces a tiny percentage of storage leakage
+With this in mind, we develop an {\em approximate} deletion strategy to trade deletion accuracy for
+speed and resource usage. Our method sacrifices a tiny percentage of storage leakage
 to effectively identify unused chunks in $O(n)$ speed, with $n$ being the logical number of non-PDS chunks 
-to be deleted from a VM snapshort store.
+to be deleted from a VM snapshot store.
+The algorithm contains three aspects.
 
@@
 
-\item {\bf Phase 1: Fast approximate deletion.}
+\item {\bf Approximate deletion with fast summary comparison.}
 Then when there is a snapshot deletion, 
@@
 are still used by other snapshots. 
-This is done approximately and quickly by compariing the fingerprints of deleted chunks with
-the fingerrinter bloomerfilter summary of other live snapshots.
+This is done approximately and quickly by comparing the fingerprints of deleted chunks with
+the fingerprint bloomer-filter summary of other live snapshots.
 Since the number of live snapshots is limited for each VM (e.g. 10 in the Alibaba's production system), 
@@
 %to append store's deletion log.
-However, there is a small false-positive probility which
-would indetify unused data as in use, resulting in temporary storage leakage.
+However, there is a small false-positive ratio which
+would identify unused data as in use, resulting in temporary storage leakage.
 
-\item {\bf Phase 2: Perodic repair of leakage}
+\item {\bf Periodic repair of leakage}
 %[exlpain why second bloom filter, why scan append store]
 Since there are certain unused chunks which are not deleted during
-the approximated deletion, the leakge repair is conducted periodically.
-In this phase we scan the entire snapshot store indices of a VM, 
-using the merged type-2 snapshot summaries to check if any of them are not
-referenced by existing snapshots.
-We cannot simply repeat the phase 1 multiple times to reduce temporary storage leakage, because:
-\begin{enumerate} 
-\item After several runs of phase-1, it is proven that the merged type-1 summaries cannot sieve remaining unused blocks, due to the false-positive property of bloom filter.
-\item The recipes of deleted snapshots have been removed from the system, thus we are not able to obtain the deleted block fingerprints from any metadata, the only way to discover them is to scan the append store indices.
-\end{enumerate}
+the approximated deletion, the leakage repair is conducted periodically.
+In this phase we load the metadata of all containers from a VM snapshot store,
+mark if any chunk is used.  For unused chunks within this VM, such chunks are to be deleted.
+This process is identical to the previously-developed mark-and-sweep techniques except that
+we only need to conduct a VM-specific mark-and-sweep  operation.
+%We cannot simply repeat the phase 1 multiple times to reduce temporary storage leakage, because:
+%\begin{enumerate} 
+%\item After several runs of phase-1, it is proven that the merged type-1 summaries cannot sieve remaining unused blocks, due to the false-positive property of bloom filter.
+%\item The recipes of deleted snapshots have been removed from the system, thus we are not able to obtain the deleted block fingerprints from any metadata, the only way to discover them is to scan the append store indices.
+%\end{enumerate}
 \end{itemize}
@@
 
-The overall time of running a approximate deletion for one snapshot deletion would be scanning
-all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
-parallel and is much faster than loading recipes from DFS:
-\begin{equation}
-T = (N_{SS} + 1) * T_{scan\_recipes}
-\end{equation}
+%The overall time of running a approximate deletion for one snapshot deletion would be scanning
+%all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
+%parallel and is much faster than loading recipes from DFS:
+%\begin{equation}
+%T = (N_{SS} + 1) * T_{scan\_recipes}
+%\end{equation}
+%
+%Using the example and analysis in previous section, this approximate deletion can be done in 5 minutes.
+%Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
+%when set $P_{bl}$ to 0.01, the memory footprint of approximate deletion is about 15 MB.
+%~
 
-Using the example and analysis in previous section, this approximate deletion can be done in 5 minutes.
-Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
-when set $P_{bl}$ to 0.01, the memory footprint of approximate deletion is about 15 MB.
-~
+%{\bf Discussion}
+We estimate how often the leak repair needs to be conducted.
+Let $L$ be the amount of temporary storage leakage caused by our approximate snapshot deletion, 
+$H$ be the average size of non-PDS snapshot data that should be deleted. 
+$\epsilon$ be the false-positive rate of the merged bloom filter. 
+$R$ be the number of runs using the approximate deletion before a full leak repair is conducted.
+Then $ L= R * \epsilon * H.  $
 
-{\bf Discussion}
-For one VM's snapshots, let $L_{temp}$ be the amount of temporary storage leakage, 
-$D_{del}$ be the average amount of data that should be physically deleted in one snapshot deletion,
-$P_{1}$ be the false-positive rate of merged bloom filter type-1,
-$N_1$ be the number of runs of deletion phase-1 during the gap of two deletion phase-2 operations, then we have:
-\begin{equation}
-L_{temp} = N_1 * P_1 * D_{del}
-\end{equation}
+When ratio $L/H$ exceed a threshold $\tau$, then:
+\[
+\frac{L}{H} = R * \epsilon > \tau \Rightarrow R > \frac{\tau}{\epsilon}.
+\]
 
-If we let approxmite deletion phase-2 be triggered  
-when $L_{temp}/D_{del}$ is accmulated to exceed certain threshold $t$, then:
-\begin{equation}
-\frac{L_{temp}}{D_{del}} = N_1 * P_1 > t \Rightarrow N_{1} > \frac{t}{P_1}
-\end{equation}
-
-Let $P_2$ be the false-positive rate of merged snapshot type-2 summaries,
-$N_2$ be the number of runs of deletion phase-2,
-$L_{perm}$ be the permanent storage leakage resulting from the approxmite deletion phase-2,
-it can be calculated as follows: 
-\begin{equation}
-L_{perm} = N_2 * P_1 * P_2 * D_{del}
-\end{equation}
-
-For example, letting $P_1 = 0.01$ and $t=1.0$, 
+For example, when $\epsilon = 0.01$ and $\tau=3$, 
 we would expect deletion phase-2 be triggered once for 
-every $T/P_{bl} = 100$ runs of deletion phase-1.
-On a node that hosts 20 VMs and each VM deletes one snapshot per day, there would be 
-only 1 deletion phase-2 scheduled for every 5 days, which is sufficiently small to prevent the 
-heavy I/O workload of deletion phase-2 from disturbing normal VM opeations.
+every $T/P_{bl} = 300$ runs of fast deletion. 
+When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
+only one full leak repair scheduled for every 12 days, which is sufficiently small to prevent the 
+heavy I/O workload of the mark-sweep process.

### 2013-07-02 snapshot_system/intro.tex
update

@@
 % along with a low-cost solution.
-%Another issue considered is that
-%that deletion of old snapshots compete for computing resource as well. That is because data dependence created
-%deletion of old snapshots compete for computing resources as well so deletion needs
-%to be considered in system design. The additional complexity for deletions
-%come from the dependencies created by multiple links to the same problem, so
-%some solution is needed to determine blocks with no dependent snapshots after deletion.
-% especially when  VMs can migrate around in the cloud.
+Another issue considered is that
+that deletion of old snapshots compete for computing resource as well. That is because data dependence created
+deletion of old snapshots compete for computing resources as well so deletion needs
+to be considered in system design. The additional complexity for deletions
+come from the dependencies created by multiple links to the same problem, so
+some solution is needed to determine blocks with no dependent snapshots after deletion.
+especially when  VMs can migrate around in the cloud.
 

### 2013-07-02 snapshot_system/failover.tex
Updated vo-fsb-links figure to use shuffled vm list.
revisions

@@
 the global index as more VMs are added in VO. The first 15 VMs are all windows
-machines, so that explains the initial higher values, but for the most part the
-average number of links is between 1.5 and 2. Figure~\ref{fig-vo-fsb-links}
-shows the average number of VMs sharing a filesystem block (FSB) in the global
-The first 15 VMs added are all windows (though the last one has a much larger
-hard drive which explains the drop after 14), which is why the number of block
-links goes up quickly for the first half of the graph. You can see in the plot
-that even though a FSB contains 16K chunks, the average number of links to an
-FSB is only several times the number of average links to a chunk. This is
-because even in the VO global deduplication model, as long as writes are
-batched a single FSB will tend to contain chunks from only a small number of
-VMs. Below we show the significant impact the number of links has on VM backup
-reliability.
+machines in that plot, so that explains the initial higher values, but for the
+most part the average number of links is between 1.5 and 2.
+Figure~\ref{fig-vo-fsb-links} shows the average number of VMs sharing a
+filesystem block (FSB) in the global index as VMs are added. Two of the VMs had
+much larger hard drives (\~300GB), which explains the 2 drops, as those two VMs
+added much more unique data than normal. You can see in the plot that even
+though a FSB contains 16K chunks, the average number of links to an FSB is only
+several times the number of average links to a chunk. This is because even in
+the VO global deduplication model, as long as writes are batched a single FSB
+will tend to contain chunks from only a small number of VMs. Below we show the
+significant impact the number of links has on VM backup reliability.
 
@@
 
-in our current testbed we have measured the average number of links
-per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{fig-vo-fsb-links})
-in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
-was 11 using a 5\% CDS. From Figure~\ref{fig-vo-fsb-links} you can see that as you add VMs, the average
-number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
-should continue to increase at a slower rate. 
-For the VC model, we have to consider both CDS chunks and 
-Non-CDS chunks. In the VO model all data is shared, but in VC only the CDS data is shared, but at a much
-higher rate. This gives a strong advantage to VC, in that for a large percent of the data (95-99\%), there
-is only one VM pointing to each Non-CDS chunk. You can see the increase in reliability in Figure~\ref{fig-vm-availability}.
+in our current testbed we have measured the average number of links per block
+(Figure~\ref{vo-links}) and number of links per chunk
+(Figure~\ref{fig-vo-fsb-links}) in our dataset. For the complete dataset, we
+also found the average number of links to CDS chunks, which was 11 using a 5\%
+CDS. From Figure~\ref{fig-vo-fsb-links} you can see that as you add VMs, the
+average number of links to a chunk increases linearly for our dataset. We
+expect that this trend will level out with larger datasets, but should continue
+to increase at a slower rate.  For the VC model, we have to consider both CDS
+chunks and Non-CDS chunks. In the VO model all data is shared, but in VC only
+the CDS data is shared, but at a much higher rate. This gives a strong
+advantage to VC, in that for a large percent of the data (95-99\%), there is
+only one VM pointing to each Non-CDS chunk. You can see the increase in
+reliability in Figure~\ref{fig-vm-availability}.
 }

### 2013-07-02 snapshot_system/intro.tex
revisions

@@
 that deletion of old snapshots compete for computing resource as well. That is because data dependence created
-deletion of old snapshots compete for computing resources as well so deletion needs
+deletion of old snapshots competes for computing resources as well so deletion needs
 to be considered in system design. The additional complexity for deletions
@@
 and by packaging data chunks from the same VM into a file system block as much as possible.
-By narrowing duplicate sharing within a small amount of data chunks,
+By narrowing duplicate sharing within a small percent of data chunks,
 this scheme can afford to allocate extra replicas of these shared chunks for better
 fault resilience.
-Localization also brings the benefits of parallelism exploitation so
+Localization also brings the benefits of greater ability to exploit parallelism so
 backup operations can run simultaneously without a central  bottleneck.
-This  VM-centric solution uses  a small amount of  memory while delivering a decent deduplication efficiency. 
+This  VM-centric solution uses  a small amount of  memory while delivering a reasonable deduplication efficiency. 
 %Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data.

### 2013-07-03 snapshot_system/arch.tex
CDS->PDS for failover, updated figures

@@
 \item Each non-PDS snapshot store is divided into a set of containers and each of them is approximately 
-1G bytes. The reason we divide the snapshot into containers is to simplify the compact process
+1GB. The reason we divide the snapshot into containers is to simplify the compact process
 conducted periodically.  There are chunks deleted without any reference from other snapshots
@@
 3) a chunk deletion log file saving all the deletion requests within  the container.
-A VM snapshot store typically has a small number of containers because each container is fairly large with an average size of 1GB bytes, it 
+A VM snapshot store typically has a small number of containers because each container is fairly large with an average size of 1GB, it 
 maintains a limited number of snapshots (e.g. 10 in the Alibaba case),

### 2013-07-03 snapshot_system/failover.tex
CDS->PDS for failover, updated figures

@@
 file system~\cite{Hadoop,GFS}.
-In the VC approach, a special replica degree $r_c$ used for CDS blocks where $r_c>r$. 
-Notice that the ratio of non CSD data size vs CDS data size for each VM is
+In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
+Notice that the ratio of non-PDS data size vs PDS data size for each VM is
 \[
@@
 In our experiment with Alibaba data, the ratio $\sigma$ 
-is 162. Thus allocation of extra replicas for CDS only introduces a small amount of extra space
+is 162. Thus allocation of extra replicas for PDS only introduces a small amount of extra space
 cost.  Figure~\ref{fig:storageCDS} shows the storage cost ratio of VC and VO when 
 $r$=3, and $r_c$ varies from 3 to 10.
-The result shows that the storage cost for adding extra replication for CDS
+The result shows that the storage cost for adding extra replication for PDS
 is insignificant.
@@
 suffer the loss of their snapshots.
-When $d \ge r_c$, some of CDS blocks are affected.
-In VC, the blocks in CDS are stored in a container manner (superblock), and they are shared by many VMs.
+When $d \ge r_c$, some of PDS blocks are affected.
+In VC, the blocks in PDS are stored in a container manner (superblock), and they are shared by many VMs.
 The number of data containers stored with replication degree $r$ for
@@
 \]
-The number of CDS data containers stored with replication degree $r_c$ for
+The number of PDS data containers stored with replication degree $r_c$ for
 referenced by each VM is:
@@
 For VC, each VM has an 
-averge number of $N_1$ file system blocks for non-CDS data. 
-It also refers  an average of   $N_2$ file system blocks for CDS data 
+averge number of $N_1$ file system blocks for non-PDS data. 
+It also refers  an average of   $N_2$ file system blocks for PDS data 
 For VO, each VM has an average  of  $N_o$ file system blocks
@@
 
-In VC, each non-CDS file system block is associated with one VM while CDS file system blocks are
+In VC, each non-PDS file system block is associated with one VM while PDS file system blocks are
 shared among VMs  (at most $V$ VMs). Thus, 
@@
 
-Figure~\ref{fig-vo-links} shows the average number of VMs sharing a block in
-the global index as more VMs are added in VO. The first 15 VMs are all windows
-machines in that plot, so that explains the initial higher values, but for the
-most part the average number of links is between 1.5 and 2.
-Figure~\ref{fig-vo-fsb-links} shows the average number of VMs sharing a
+Figure~\ref{fig-fsb-links} shows the average number of VMs sharing a
 filesystem block (FSB) in the global index as VMs are added. Two of the VMs had
 much larger hard drives (\~300GB), which explains the 2 drops, as those two VMs
-added much more unique data than normal. You can see in the plot that even
-though a FSB contains 16K chunks, the average number of links to an FSB is only
-several times the number of average links to a chunk. This is because even in
-the VO global deduplication model, as long as writes are batched a single FSB
-will tend to contain chunks from only a small number of VMs. Below we show the
+added much more unique data than normal. Though we expect the graph to level out some for
+much larger datasets, it should continue to increase, which has important implications
+on VM backup availability in the precense of failures. Below we show the
 significant impact the number of links has on VM backup reliability.
 
+\comments{%dropping block links bec. we don't use it elsewhere
 \begin{figure}[ht]
@@
 		xlabel={Number of VMs},
-		ylabel={Avg. links to an FSB},
+		ylabel={Avg. Num. VMs sharing FSB},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		legend pos=south east
 		]
                 \addplot[color=blue,mark=*] table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
-                %\legend{Measured,Theoretical};
+		\addplot[color=red,mark=square*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
+                \legend{Global Dedup (VO), PDS FSB (VC)};
 		\end{axis}
 	\end{tikzpicture}
-  \caption{Measured Average number of VMs sharing a 64MB Filesystem Block in the global index (for VO)}
-  \label{fig-vo-fsb-links}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={Avg CDS Container Links},
-		xlabel={Number of VMs},
-		ylabel={Avg. links to CDS FSB},
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		]
-		\addplot[color=blue,mark=*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
-		%\legend{Measured,Theoretical};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Measured Average number of VMs sharing a 64MB CDS Filesystem Block for (VC with 5\% CDS)}
-  \label{fig-cds-fsb-links}
+  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in the PDS for VC.}
+  \label{fig-fsb-links}
 \end{figure}
@@
 
-When there are $r \le d<r_c$ machines failed and then there is no CDS data loss,  
+When there are $r \le d<r_c$ machines failed and then there is no PDS data loss,  
 %a file block failure depends on if all replicas of this container reside in the failed machines.
@@
 
-When $r_c \leq d$, both non-CDS and CDS file blocks in VC can have a loss.
+When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
 The snapshot availability of  a VM in the VC approach is
@@
 \]
-%= Probability(\mbox{ No non-CDS file block loss})^{N_1}
-%Probability(\mbox{ No CDS file block loss})^{N_2}\\
+%= Probability(\mbox{ No non-PDS file block loss})^{N_1}
+%Probability(\mbox{ No PDS file block loss})^{N_2}\\
 %\begin{multline}
@@
 
-Since both in the CDS and in the VO approach a single filesystem chunk may be used by many VMs,
+Since both in the PDS and in the VO approach a single filesystem chunk may be used by many VMs,
 we must multiply the block failure ratio by the number of outgoing links for the block to get
@@
 
-in our current testbed we have measured the average number of links per block
-(Figure~\ref{vo-links}) and number of links per chunk
-(Figure~\ref{fig-vo-fsb-links}) in our dataset. For the complete dataset, we
-also found the average number of links to CDS chunks, which was 11 using a 5\%
-CDS. From Figure~\ref{fig-vo-fsb-links} you can see that as you add VMs, the
+in our current testbed we have measured the average number of links per chunk
+(Figure~\ref{vo-links}) and number of links per Filesystem Block (FSB)
+(Figure~\ref{fig-fsb-links}) in our dataset. For the complete dataset, we
+also found the average number of links to PDS chunks, which was 11 using a 5\%
+PDS. From Figure~\ref{fig-fsb-links} you can see that as you add VMs, the
 average number of links to a chunk increases linearly for our dataset. We
 expect that this trend will level out with larger datasets, but should continue
-to increase at a slower rate.  For the VC model, we have to consider both CDS
-chunks and Non-CDS chunks. In the VO model all data is shared, but in VC only
-the CDS data is shared, but at a much higher rate. This gives a strong
+to increase at a slower rate.  For the VC model, we have to consider both PDS
+chunks and non-PDS chunks. In the VO model all data is shared, but in VC only
+the PDS data is shared, but at a much higher rate. This gives a strong
 advantage to VC, in that for a large percent of the data (95-99\%), there is
-only one VM pointing to each Non-CDS chunk. You can see the increase in
+only one VM pointing to each non-PDS chunk. You can see the increase in
 reliability in Figure~\ref{fig-vm-availability}.
@@
 measured in our dataset, and chose higher numbers to account for much larger
-datasets. As you can see from the graph, even small changes in the number of
-links to VO blocks has a significant impact on reliability, while even a 100
-times increase in the VC block link counts only slightly affects VC
-reliability.  The key factor placed is that  $N_1 +N_2 << N_o$, caused by the
-fact that the VM-centric approach localizes deduplication and packs  data
-blocks for one VM as much as possible.  The extra replicaton for CDS blocks
-also signficantly increaes the snapshot availability even when a CDS file block
-is shared by every VM.
+datasets. We chose to use a very optimistic setting for VO (10), and an extreme
+amount of sharing for VC (1000) to better show the significant improvement in
+data reliability for the VC model. As you can see from the graph, even small
+changes in the number of links to VO blocks has a significant impact on
+reliability, while even a 100 times increase in the VC block link counts only
+slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <<
+N_o$, caused by the fact that the VM-centric approach localizes deduplication
+and packs  data blocks for one VM as much as possible.  The extra replicaton
+for PDS blocks also signficantly increases the snapshot availability even when
+a PDS file block is shared by every VM.
 
 % while in VO even small increases in $L$ causes a large decrease in availability. 
-Figure~\ref{fig-cds-replication}
-shows the advantages of increasing the replication factor for CDS blocks. the
-numbers in the graph are only meant to be relative, as we assume higher CDS
+Figure~\ref{fig-pds-replication}
+shows the advantages of increasing the replication factor for PDS blocks. the
+numbers in the graph are only meant to be relative, as we assume higher PDS
 block links than we have measured in our dataset (to account for a much larger
 body of data). It is easy to see though that increasing the replication of just
-the CDS blocks (which are the most popular blocks) can have a positive impact
+the PDS blocks (which are the most popular blocks) can have a positive impact
 on the overall reliablity of the VM backups. These figures together show the
@@
                 %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
-            \legend{$VO\,10$,$VO\,5$,$VC\,1000$,$VC\,11$}
+            \legend{$VO\,10$ (optimistic),$VO\,5$ (measured),$VC\,1000$ (extreme),$VC\,11$ (measured)}
 		\end{axis}
 	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail for VO and VC models for varying average block link counts (i.e. average number of VMs that use a block)}
+  \caption{Availability of VM backups as nodes fail for VO and VC models for varying average block link counts (i.e.
+average number of VMs that use a block).
+Non-PDS replication fixed at 3 and PDS replication increased to 4.}
   \label{fig-vm-availability}
@@
 		\begin{axis}[
-		%title={CDS Replication affect on availability},
+		%title={PDS Replication affect on availability},
 		xlabel={Failed storage nodes},
@@
 	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail in the VC model for different CDS Replication factors (Non-CDS replication fixed at 3, and average CDS block links set to 1000)}
-  \label{fig-cds-replication}
+  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
+  \label{fig-pds-replication}
 \end{figure}
@@
 of them  is unique (nobody shares with them).
-$L_c$ is the average number of VMs sharing a block (if it is in CDS for the VC approach.
+$L_c$ is the average number of VMs sharing a block (if it is in PDS for the VC approach.
 $b_c$ is the number of shared blocks in VC.
@@
 
-\subsubsection{CDS and Fault Tolerance}
+\subsubsection{PDS and Fault Tolerance}
 %all numbers in this paragraph need to be corrected after I re-run the tests
@@
 As part of our emprirical validation of our model, we also computed the effects
-of the CDS on fault tolerance. If we exclude the top 5\% most popular blocks
-and set aside those in the CDS, the average number of links to a non-CDS block
+of the PDS on fault tolerance. If we exclude the top 5\% most popular blocks
+and set aside those in the PDS, the average number of links to a non-PDS block
 %TODO: insert figure generated from data/links_cds.dat and data/links_wo_cds.dat
@@
 snapshots will be affected by a lost data block in the general data store.
-The average number of links to a CDS block however, for 350 snapshots, is
+The average number of links to a PDS block however, for 350 snapshots, is
 65.7. This suggests that a much higher replication factor is warranted for
-the CDS, as on average, a CDS block appears in \~20\% of all the snapshots.
+the PDS, as on average, a PDS block appears in \~20\% of all the snapshots.
 These measured numbers are different from our theoritical model due to the fact
@@
 more tighly grouped than the uniform model would predict. This supports
-the benefits of using a CDS plus more localized deduplication.
+the benefits of using a PDS plus more localized deduplication.
 
-The CDS gives a clear boundary for setting different replication factors,
-And our tests suggest that by separating the replication factor for the CDS
-and non-CDS blocks, greater fault tolerance can be acheived.
+The PDS gives a clear boundary for setting different replication factors,
+And our tests suggest that by separating the replication factor for the PDS
+and non-PDS blocks, greater fault tolerance can be acheived.
 
@@
 
-For CDS model, 85% blocks are using the data from the same VM while upto 10% data is for CDS (we actually only use 5% perhaps).  Thus the overall speaking, at most 10% of data are shared.
-Thus  for CDS approach,   the # VM failure caused by k machines is at most  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.10 *V(1-1/ln V)].
+For PDS model, 85\% blocks are using the data from the same VM while upto 10\% data is for PDS (we actually only use 5% perhaps).  Thus the overall speaking, at most 10% of data are shared.
+Thus  for PDS approach,   the # VM failure caused by k machines is at most  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.10 *V(1-1/ln V)].
 For original approach,  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.90 *V(1-1/ln V)].

### 2013-07-04 snapshot_system/failover.tex
updated cds links figure, changed lower cds links from 11 to 20 for availability graph

@@
 	\end{tikzpicture}
-  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in the PDS for VC.}
+  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
   \label{fig-fsb-links}
@@
 (Figure~\ref{vo-links}) and number of links per Filesystem Block (FSB)
-(Figure~\ref{fig-fsb-links}) in our dataset. For the complete dataset, we
-also found the average number of links to PDS chunks, which was 11 using a 5\%
+(Figure~\ref{fig-fsb-links}) in our dataset. For the complete dataset, we also
+found the average number of links to PDS chunks, which was \~19 using a 2\%
 PDS. From Figure~\ref{fig-fsb-links} you can see that as you add VMs, the
@@
 nodes fail for different numbers of links to average blocks in the index. We
-chose 5 and 11 for the VO and VC block links counts because those are what we
+chose 5 and 20 for the VO and VC block links counts because those are what we
 measured in our dataset, and chose higher numbers to account for much larger
@@
 changes in the number of links to VO blocks has a significant impact on
-reliability, while even a 100 times increase in the VC block link counts only
+reliability, while even a 50 times increase in the VC block link counts only
 slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <<
@@
                 %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
-            \legend{$VO\,10$ (optimistic),$VO\,5$ (measured),$VC\,1000$ (extreme),$VC\,11$ (measured)}
+            \legend{$VO\,10$ (optimistic),$VO\,5$ (measured),$VC\,1000$ (extreme),$VC\,20$ (measured)}
 		\end{axis}

### 2013-07-05 snapshot_system/challenge.tex
added srb comparison text, updated references throughout paper.
chagne

@@
 raw data for backup. 
-Figure~\ref{fig:collocated} illustrates the cluster architeture where
-each physical runs a backup service and a distribued file system (DFS)~\cite{GFS2004,Hadoop} 
-serves a backup store  for the snapshopts.
+Figure~\ref{fig:collocated} illustrates the cluster architecture where
+each physical runs a backup service and a distributed file system (DFS)~\cite{GFS2004,Hadoop} 
+serves a backup store  for the snapshots.
 The previous study shows that 
@@
     \includegraphics[width=3in]{images/colocated-arch.pdf}
+    \caption{Collocated VM Backup System.}
     \label{fig:collocated}
-    \caption{Collocated VM Backup System.}
 \end{figure}
@@
 \begin{itemize}
-\item {\em Deduplication localization, sharing minmization, and fault tolerance.}
+\item {\em Deduplication localization, sharing minimization, and fault tolerance.}
 
@@
 cause the unavailability of snapshots for a large number of virtual machines.
-Localizing the impact of deduplication can incrase fault isolation and resilience.
-Thus from the fault tolerance point of view,  duplicate sharing among mutiple VMs is 
-discourage. On the other hand, we need to seek for a tradeoff since there are
-a significant number of duplicates cross VMs.
+Localizing the impact of deduplication can increase fault isolation and resilience.
+Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
+discourage. 
+Another disadvantage of sharing is that it complicates snapshot deletion.
+The mark-sweep approach~\cite{mark-sweep} is effective for deletion, and its main cost
+is to count if a data chunk is still shared by other snapshots.
+Thus our goal is to localize deduplication and minimize sharing, while we seek for 
+a tradeoff since there are a significant number of duplicates cross VMs.
 
@@
 since a file block can be shared even more VMs.
-Thus we need to consider a minimum assoocation of a fie system block to VMs in the packaging process.
+Thus we need to consider a minimum association of a fie system block to VMs in the packaging process.
 %The distributed file system~\cite{GoogleFS,Hadoop} provides the replication support
@@
 content change detection falls into a VM-centric approach since deduplication is localizable. 
-We are seeking for additional optimzations to improve duplication efficency and design the 
-assoication of data chunks with the underlying file blocks so that
+We are seeking for additional optimization to improve duplication efficiency and design the 
+association of data chunks with the underlying file blocks so that
 file block sharing among VMs is minimized.
@@
 An evaluation with our test data shows that using a sampled index can achieve a high
-deduplication effiency with a single machine setup.  
+deduplication efficiency with a single machine setup.  
 One key problem is that the algorithm is VM oblivious and not easy to be adopted for VM-centric.
@@
 
-Another possibiliy is to use this approach partially  in our VM centric solution by indexing
+Another possibility is to use this approach partially  in our VM centric solution by indexing
 the most popular data chunks. For a small set of popular data chunks, the prefetching strategy
@@
 With these considerations in mind, we study a 
-VM-centric appraoch (called VC)
+VM-centric approach (called VC)
 for a backup service co-hosted   in the existing set of machines and resource usage is friendly

### 2013-07-08 snapshot_system/eval1.tex
update

--- 2013-06-24 snapshot_system/eval1.tex
@@
 Objectives of our evaluation are:
-1) Study the deduplication efficiency of the VC approach and compare with an alternative
+1) Study the deduplicate detection and removal effectiveness of the VC approach and compare with an alternative VO
 design.
-2) Evaluate the backup throughput performance VC  for a large number of VMs.
+2) Examine the impacts of VC for fault isolation and tolerance. 
+3) Evaluate the backup throughput performance VC  for a large number of VMs.
+4) Assess the resource usage  of VC in terms of memory, storage, and network bandwidth.
+% the backup throughput performance VC  for a large number of VMs.
 %Compare with the data domain approach~\cite{bottleneck08}.
-3) Examine the impacts of VC for fault isolation.
 
@@
 
+{\bf Stateless Routing with Binning.}
+We compare our system with Stateless Routing with Binning (SRB) in terms of
+both backup time and deduplication efficiency. SRB is the same as the stateless
+routing algorithm given in the Extreme Binning\cite{??} paper. the
+deduplication efficiency is compared in
+Figure~\ref{fig-exbin-efficiency-graph}, showing the deduplication efficiency
+(percent of duplicate chunks which are deduped) of SRB and VC with several
+different CDS sizes. From the graph you can see that VC provides similar or
+better deduplication efficiency in all cases. In Figure~\ref{fig:srb_vs_vc} you
+can see simulated backup times using actual throughput numbers from our test
+backup cluster, and VC outperforms SRB mainly due to significantly fewer index
+lookups (since SRB uses hash-partitioning, all lookups are essentially random
+and caching will be largely innefective).  \emph{Should we use one of the two
+bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
+charts in the paper until we decide? If we use the bar charts some text will
+have to be changed. We could also add each of the CDS sizes to the bar chart
+and have 4 bars instead of 2.}
+
+\comments{%both of the bar charts are superceded by the graph below
+%\comments{
+    %this version of the figure is vertical
+    \begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Extreme-Binning Efficiency},
+            ybar,
+            bar width=1.00cm,
+            symbolic x coords={SRB,VC},
+            xlabel={Algorithm},
+            ylabel={Dedup. Efficiency (\%)},
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            xtick=data, %without this the symbolic coords may be repeated as filler
+            enlarge x limits=0.6, %used to push plots towards center
+            ymin=85,
+            %ymax=100,
+            nodes near coords,
+            nodes near coords align={vertical},
+            ]
+            \addplot coordinates {(SRB,89.99) (VC,90.51)};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Deduplication Efficiency
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
+  \label{fig-exbin-efficiency1}
+\end{figure}
+%}
+%same figure as above but horizontal (better for only two data points)
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Extreme-Binning Efficiency},
+            xbar,
+            width=7cm,
+            height=3.5cm,
+            %bar width=0.75cm,
+            symbolic y coords={SRB,VC},
+            xlabel={Dedup. Efficiency (\%)},
+            %ylabel={Algorithm},
+            %extra x ticks={4.5,5.5,6.5} %to add extra ticks
+            ytick=data, %without this the symbolic coords may be repeated as filler
+            enlarge y limits=0.5,
+            xmin=85,
+            xmax=92, %otherwise label overlaps with right border
+            nodes near coords,
+            nodes near coords align={horizontal},
+            ]
+            \addplot coordinates {(89.99,SRB) (90.51,VC)};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Deduplication Efficiency
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
+  \label{fig-exbin-efficiency2}
+\end{figure}
+}
+
+%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Ex-Binning Efficiency},
+            xlabel={Number of VMs added},
+            ylabel={Dedup. Efficiency (\%)},
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            mark options=solid,
+            legend pos=south west,
+            %legend columns=2,
+            %legend style={
+            %    at={(0.5,-0.2)},
+            %anchor=north}
+            ]
+            \addplot[color=blue,mark=none] table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
+            \addplot[densely dotted, color=red,mark=none] table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
+            \addplot[loosely dotted, color=brown,mark=none] table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
+            \addplot[densely dashed,color=black,mark=none] table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
+            \legend{SRB,VC (1\%CDS),VC (2\%CDS),VC (4\%CDS)};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Deduplication Efficiency
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
+    Stateless Routing with Binning and VC.}
+  \label{fig-exbin-efficiency-graph}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
+  \caption{Time to backup a dirty segment under SRB and VC approach}
+  \label{fig:srb_vs_vc}
+\end{figure}
+
 Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication on dataset1.
@@
 
+\subsection{Resource Usage}
+{\bf Storage cost of replication.}
+\begin{table}
+    \begin{tabular}{|c|c|}
+    \hline
+    PDS replication degree & Total space (GB) \\ \hline
+    3                      & 3065             \\ \hline
+    4                      & 3072             \\ \hline
+    5                      & 3079             \\ \hline
+    6                      & 3086             \\ \hline
+    7                      & 3093             \\ \hline
+    \end{tabular}
+\caption{Storage space cost under different PDS replication degree}
+\label{tab:replcation_cost}
+\end{table}
+
+\subsection{System Performance}
+{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
+backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
+scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
+evaulate the system performance on the second snapshot backup. We repeat such procedure
+under different CDS memory usage settings, the results of backup time break down are shown in
+Figure~\ref{fig:single_vm_backup}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3in]{figures/single_backup_time.pdf}
+    \caption{Backup times for varying CDS sizes}
+    \label{fig:single_vm_backup}
+\end{figure}
+
+It's easy to see that the time of I/O dominates the backup process, our deduplication
+procedure only takes a tiny fraction of the total backup time. Larger memory permits us to
+use larger CDS index to cover more of global index, as a result the amount of data to be writen
+is reduced and so do the writing time.
+Inside the deduplication procedure, the time costs of level-1
+is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
+because the number of fingerprints to process are just the same.
+
+{\bf Parallel VM Backup} We then evaluate the performance of writing snapshots in parallel.
+To begin, on each node we let 4 VMs writing snapshot concurrently, and gradually 
+increase number of VMs to 12 to saturate our system capability. We observed 
+the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
+which is far beyond our QFS file system capability. The reason behind it is our efficient
+deduplication architecture and compression greatly reduce the amount of data that need to be writen to
+the file system. The main bottleneck here is our QFS only manages one disk per node, 
+making it inefficient to utilize the benefits of parallel disk access. We expect our achitecture can
+perform even better in production cluster which normally has more than ten disks on each node.
+
+\begin{figure}
+    \centering
+    \subfigure[Real VM backup performance]
+    {
+        \includegraphics[width=3in]{figures/parallel_backup_with_read.pdf}
+        \label{fig:withread}
+    }
+    \\
+    \subfigure[Deduplication and storage system performance]
+    {
+        \includegraphics[width=3in]{figures/parallel_backup_no_read.pdf}
+        \label{fig:noread}
+    }
+    \caption{Throughput per-node with concurrent snapshot backup tasks}
+    \label{fig:parallel_backup}
+\end{figure}
+
+% \begin{figure}[htbp]
+%   \centering
+%   \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
+%   \caption{Throughput per-node with concurrent snapshot backup tasks}
+%   \label{fig:parallel_backup}
+% \end{figure}
+
+% \begin{table}
+% \begin{tabular}{ |p{1.5cm}|p{1.8cm}|p{1.2cm}|p{1.4cm}| }
+% \hline
+%  & Costs & Stateless routing with binning (s) & VM-centric approach (s) \\ \hline
+% \multirow{4}{*}{\vbox{I/O related}} & Read data & 0.05 & 0.05 \\ \cline{2-4}
+%  & Transfer data  & 0.017 & 0.017 \\ \cline{2-4}
+%  & Write data & 0.03 & 0.025 \\ \cline{2-4}
+%  & Subtotal & 0.097 & 0.092 \\ \hline
+% \multirow{5}{*}{\vbox{Dedupe related}} & Read index/recipe & 0.01 & 0.00045 \\ \cline{2-4}
+%  & Write index/recipe & 0.01 & 0.0051 \\ \cline{2-4}
+%  & Transfer fingerprints & 0.00058 & 0.00013 \\ \cline{2-4}
+%  & CDS lookup & N/A & 0.00034 \\ \cline{2-4}
+%  & Subtotal & 0.021 & 0.0064 \\ \hline
+% \multicolumn{2}{ |c| }{Total} & 0.12 & 0.098 \\
+% \hline
+% \end{tabular}
+% \caption{Time of backup a segment break down}
+% \label{tab:compare}
+% \end{table}
+
+\comments{
+\subsection{Read Snapshot}
+
 \subsection{Comparison with Other Approaches}

### 2013-07-08 snapshot_system/failover.tex

@@
 amount of sharing for VC (1000) to better show the significant improvement in
-data reliability for the VC model. As you can see from the graph, even small
-changes in the number of links to VO blocks has a significant impact on
-reliability, while even a 50 times increase in the VC block link counts only
-slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <<
-N_o$, caused by the fact that the VM-centric approach localizes deduplication
-and packs  data blocks for one VM as much as possible.  The extra replicaton
-for PDS blocks also signficantly increases the snapshot availability even when
-a PDS file block is shared by every VM.
+data reliability for the VC model (showing VO best case is still worse than VC
+worst case). As you can see from the graph, even small changes in the number of
+links to VO blocks has a significant impact on reliability, while even a 50
+times increase in the VC block link counts only slightly affects VC
+reliability.  The key factor placed is that  $N_1 +N_2 << N_o$, caused by the
+fact that the VM-centric approach localizes deduplication and packs  data
+blocks for one VM as much as possible.  The extra replicaton for PDS blocks
+also signficantly increases the snapshot availability even when a PDS file
+block is shared by every VM.
 
@@
 	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail for VO and VC models for varying average block link counts (i.e.
+  \caption{Availability of VM backups as nodes fail for VO and VC models for varying degrees of block sharing (i.e.
 average number of VMs that use a block).
@@
 \end{figure}
+
+\begin{table}
+    \begin{tabular}{ll}
+    Nodes Failed & Availability (\%) \\
+    1           &  100\\
+    2           & 100\\
+    3          & 99.999\\
+    5          & 99.993\\
+    10          & 99.926\\
+    20          & 99.295\\
+    \end{tabular}
+    \caption{Availability of a single block in the global data store}
+    \label{tab:block-availability}
+\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-07-09 snapshot_system/failover.tex

@@
 		\begin{axis}[
-		%title={VO Container links},
+		%title={VO FSB links},
 		xlabel={Number of VMs},
@@
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		legend pos=south east
+		legend pos=north west
 		]
@@
   \label{fig-fsb-links}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={VO VM links},
+		xlabel={Number of VMs},
+		ylabel={Avg. Num. FSBs used by VM},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		legend pos=north west
+		]
+                \addplot[color=blue,mark=*] table[x=VMs,y=VMLinks] {figures/vo_vm_links.txt};
+		\addplot[color=red,mark=square*] table[x=VMs,y=VMNonCDSLinks] {figures/vc_vm_links.txt};
+		\addplot[color=red,densely dashed,mark=triangle*,mark size=3] table[x=VMs,y=VMCDSLinks] {figures/vc_vm_links.txt};
+                \legend{VO FSB, Non-PDS FSB (VC), PDS FSB (VC)};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
+  \label{fig-vm-links}
 \end{figure}
@@
 
+\begin{table}
+    \begin{tabular}{|l|ll|}
+    \hline
+    \multirow{2}{*}{Nodes Failed}   & \multicolumn{2}{c|}{Availability(\%)}\\
+                                    & $R=3$ & $R=4$\\
+    \hline
+    1           &  100      & 100\\
+    2           & 100       & 100\\
+    3          & 99.999     & 100\\
+    5          & 99.993     & 99.9999\\
+    10          & 99.926    & 99.995\\
+    20          & 99.295    & 99.876\\
+    \hline
+    \end{tabular}
+    \caption{Availability of a single FSB in the global data store with different relplication factors}
+    \label{tab:fsb-availability}
+\end{table}
+
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={FSB Availability},
+            xlabel={Number of Machines Failed},
+            ylabel={Availability of Single FSB (\%)},
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            mark options=solid,
+            legend pos=south west,
+            %legend columns=2,
+            %legend style={
+            %    at={(0.5,-0.2)},
+            %anchor=north}
+            ]
+            \addplot[color=blue,mark=none] table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
+            \addplot[densely dashed, color=red,mark=none] table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
+            \legend{$R=3$,$R=4$};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
+  \label{fig-fsb-availability}
+\end{figure}
+
 \begin{figure}[ht]
@@
 
-\begin{table}
-    \begin{tabular}{ll}
-    Nodes Failed & Availability (\%) \\
-    1           &  100\\
-    2           & 100\\
-    3          & 99.999\\
-    5          & 99.993\\
-    10          & 99.926\\
-    20          & 99.295\\
-    \end{tabular}
-    \caption{Availability of a single block in the global data store}
-    \label{tab:block-availability}
-\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-07-09 snapshot_system/failover.tex
Added second CDS replication graph using 20 VMs per FSB

@@
 
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={PDS Replication affect on availability},
+		xlabel={Failed storage nodes},
+		ylabel={VM Snapshot Availability (\%)},
+		extra y ticks={99.9}, %if important numbers are missing
+                mark options=solid,
+                legend style={
+                    cells={anchor=west}, %legend entry alignment
+                    legend pos=south west %legend position
+                }
+		]
+                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
+                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
+                \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
+                \addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
+            \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
+  \label{fig-pds-replication2}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-07-09 snapshot_system/eval1.tex

@@
 Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
-Each machine  is equiped with a 
+Each machine  is equipped with a 
 a distributed file system (QFS) running in the cluster manages six 3TB disks
@@
 %\subsection{Experimental setup}
+
+We will also compare our VC approach with  with
+a VO approach  using stateless routing with binning (SRB).
+SRB executes a distributed deduplication by routeing a data chunk to a machine~\cite{ParallelDataDomain}
+using  the chunk hashing function discussed in \cite{??}. Within such a machine, the data chunk is compared with
+a local index.
 
@@
 
-{\bf Stateless Routing with Binning.}
-We compare our system with Stateless Routing with Binning (SRB) in terms of
-both backup time and deduplication efficiency. SRB is the same as the stateless
-routing algorithm given in the Extreme Binning\cite{??} paper. the
-deduplication efficiency is compared in
-Figure~\ref{fig-exbin-efficiency-graph}, showing the deduplication efficiency
-(percent of duplicate chunks which are deduped) of SRB and VC with several
-different CDS sizes. From the graph you can see that VC provides similar or
-better deduplication efficiency in all cases. In Figure~\ref{fig:srb_vs_vc} you
-can see simulated backup times using actual throughput numbers from our test
-backup cluster, and VC outperforms SRB mainly due to significantly fewer index
-lookups (since SRB uses hash-partitioning, all lookups are essentially random
-and caching will be largely innefective).  \emph{Should we use one of the two
-bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
-charts in the paper until we decide? If we use the bar charts some text will
-have to be changed. We could also add each of the CDS sizes to the bar chart
-and have 4 bars instead of 2.}
+%We assess the deduplication efficiency of VC and compare with
+%that of an VO approach  using stateless routing with binning (SRB).
+%SRB routes a data chunk to a machine~\cite{ParallelDataDomain}
+%using  the chunk hashing function disussed in \cite{??}.
+
+Figure~\ref{fig-exbin-efficiency-graph} shows the deduplication efficiency which is
+the percent of deduped duplicate chunks by SRB and VC.
+It also lists several PDS sizes chosen for VC. ``2\% PDS" means that
+we allocate the space of distributed shared memory  to accommodate $\delta=2\%$
+of data chunks shared among VMs. Namely 
+With $\delta=2\%$, the deduplication efficiency can reach over 90\% 
+while $\delta=4\%$, the deduplication efficiency can reach over 92\%. 
+The loss of efficiency in VC is caused by the restriction of the total physical memory available
+in the cluster to support PDS.  
+The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
+for global comparison.
+In all cases, VC provides similar or better deduplication efficiency than SRB.
 
@@
   \label{fig-exbin-efficiency-graph}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
-  \caption{Time to backup a dirty segment under SRB and VC approach}
-  \label{fig:srb_vs_vc}
 \end{figure}
@@
 
+In Figure~\ref{fig:srb_vs_vc} you
+can see simulated backup times using actual throughput numbers from our test
+backup cluster, and VC outperforms SRB mainly due to significantly fewer index
+lookups (since SRB uses hash-partitioning, all lookups are essentially random
+and caching will be largely innefective).  \emph{Should we use one of the two
+bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
+charts in the paper until we decide? If we use the bar charts some text will
+have to be changed. We could also add each of the CDS sizes to the bar chart
+and have 4 bars instead of 2.}
+
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
+  \caption{Time to backup a dirty segment under SRB and VC approach}
+  \label{fig:srb_vs_vc}
+\end{figure}
+
 \begin{figure}

### 2013-07-09 snapshot_system/eval1.tex
update exper

@@
 for global comparison.
-In all cases, VC provides similar or better deduplication efficiency than SRB.
+In all cases, VC provides similar or better deduplication efficiency than SRB
+
+This shows VC can remove  a competitive amount of duplicates.
+In general, our experiment shows that
+dirty-bit detection in the segment level  can reduce the data size to about 23\% of original data, 
+which leads  about 77\% reduction.
+Local search within a segment can   further reduce the data size
+to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
+The PDS-based cross-VM detection with $\delta=2\% $
+can reduce the  size further to 8\% of original size, namely it 
+delivers additional 10.5\% reduction.
 
@@
     \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
+         of SRB  and VC with $\delta=2\%$.}
+        %($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
   \label{fig-exbin-efficiency1}
@@
         ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
-    Stateless Routing with Binning and VC.}
+    SRB and  VC.}
   \label{fig-exbin-efficiency-graph}
 \end{figure}
-
-Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication on dataset1.
-The X axis shows the overall impact in (a),  impact on OS disks in (b), and impact on data disks in (c).
-Each bar in the Y axis shows the data size after deduplication divided by the original data size.
-Level-1 elimination can reduce the data size to about 23\% of original data, namely it delivers close 77\% reduction.
-Level-2 elimination is applied to data that could pass level-1, it
-reduces the size further to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
-Level-3 elimination together with level 1 and 2
-reduces the size further to 8\% of original size, namely it delivers additional 10.5\% reduction.
-Level 2 elimination is more visible in OS disk than data disk, because data change frequency is really small
-when we sample last 10 snapshots of each user in 10 days. Nevertheless, the overall impact of level 2 is still significant.
-A 4.5\% of reduction from the original data represents about 450TB space saving for a 1000-node cluster.
 
@@
 %Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
-Figure~\ref{fig:oscds} shows the impact of different levels of deduplication for different OS releases.
-In this experiment, we tag each block in 350 OS disk snapshots from dataset1 as  ``new''
-if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot store;
-``CDS''  if this block can be found  in CDS;
-``Parent segment'' if  this block is marked unchanged in parent's segment recipe.
-``Parent block'' if  this block is marked unchanged in parent's block recipe.
-With this tagging, we compute the percentage of deduplication accomplished by each level.
-As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination,
-this is because the time interval between two snapshots in our dataset
-is quite short and the Aliyun cloud service makes a snapshot  everyday  for each VM.
-On the other hand,  CDS still finds lots of duplicates that inner VM deduplication can't find,
-contributing about 10\% of reduction on average.
-
-It is noticeable that level-1 deduplication doesn't work well for CentOS, a significant percentage of data is not
-eliminated until they reach level-3. It shows that even user upgrade his VM system heavily and frequently
-such that data locality is totally lost, those OS-related data can still be identified at level-3.
-
-In general we see a stable data reduction ratio for all OS varieties, ranging from 92\% to 97\%, that means
-the storage cost of 10 full snapshots combined is still smaller than the original disk size. And compare to 
-today's widely used copy-on-write snapshot technique, which is similar to our level-1 deduplication, our
-solution cut the snapshot storage cost by 64\%.
 
@@
 
-\subsection{System Performance}
-{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
-backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
-scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
-evaulate the system performance on the second snapshot backup. We repeat such procedure
-under different CDS memory usage settings, the results of backup time break down are shown in
-Figure~\ref{fig:single_vm_backup}.
+\subsection{Processing Time and Throughput}
+%{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
+%backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
+%scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
+%evaulate the system performance on the second snapshot backup. We repeat such procedure
+%under different CDS memory usage settings, the results of backup time break down are shown in
+
+Figure~\ref{fig:srb_vs_vc} shows
+the  average  processing  time of  each segment using VC and SRM in handling our dataset.
+It has a breakdown of time for reading data and updating the metadata, network latency to visit
+a remote machine, and index access for finger printer comparison.
+SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
+it relies on this local machine to access its index (often on the disk) and perform comparison.
+VC is faster for index access because it conducts in-memory local search first and then
+accesses  the PDS which is on distributed shared memory.  
+SRB spends  slighter more time in  reading data and update because it also updates the on-disk
+local meta data index.
+Overall speaking,  VC is faster than SRB while data reading dominates the processing time. 
+%all lookups are essentially random and caching will be largely innefective).
+
+%\emph{Should we use one of the two
+%bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
+%charts in the paper until we decide? If we use the bar charts some text will
+%have to be changed. We could also add each of the CDS sizes to the bar chart
+%and have 4 bars instead of 2.}
+
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
+  \caption{Time to backup a dirty segment under SRB and VC approach}
+  \label{fig:srb_vs_vc}
+\end{figure}
+
+Figure~\ref{fig:single_vm_backup} reports the average bacup time for a VM with VC with a varying number
+of PDS size.
+Again it shows that data reading dominates the backup process, our deduplication
+procedure only takes a small fraction of the total backup time. 
+The change of $\delta$ does not significantly affects the overall time and
+PDS lookup takes a small amount of time.
+%Larger memory permits us to
+%use larger CDS index to cover more of global index, as a result the amount of data to be writen
+%is reduced and so do the writing time.
+%Inside the deduplication procedure, the time costs of level-1
+%is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
+%because the number of fingerprints to process are just the same.
 
@@
 
-It's easy to see that the time of I/O dominates the backup process, our deduplication
-procedure only takes a tiny fraction of the total backup time. Larger memory permits us to
-use larger CDS index to cover more of global index, as a result the amount of data to be writen
-is reduced and so do the writing time.
-Inside the deduplication procedure, the time costs of level-1
-is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
-because the number of fingerprints to process are just the same.
-
-{\bf Parallel VM Backup} We then evaluate the performance of writing snapshots in parallel.
+    Figure~\ref{fig:parallel_backup} shows the node throughput when all machine nodes run
+the backup procedure in parallel.
 To begin, on each node we let 4 VMs writing snapshot concurrently, and gradually 
@@
 which is far beyond our QFS file system capability. The reason behind it is our efficient
-deduplication architecture and compression greatly reduce the amount of data that need to be writen to
+deduplication architecture and compression greatly reduce the amount of data that need to be written to
 the file system. The main bottleneck here is our QFS only manages one disk per node, 
-making it inefficient to utilize the benefits of parallel disk access. We expect our achitecture can
+making it inefficient to utilize the benefits of parallel disk access. We expect our architecture can
 perform even better in production cluster which normally has more than ten disks on each node.
-
-In Figure~\ref{fig:srb_vs_vc} you
-can see simulated backup times using actual throughput numbers from our test
-backup cluster, and VC outperforms SRB mainly due to significantly fewer index
-lookups (since SRB uses hash-partitioning, all lookups are essentially random
-and caching will be largely innefective).  \emph{Should we use one of the two
-bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
-charts in the paper until we decide? If we use the bar charts some text will
-have to be changed. We could also add each of the CDS sizes to the bar chart
-and have 4 bars instead of 2.}
-
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
-  \caption{Time to backup a dirty segment under SRB and VC approach}
-  \label{fig:srb_vs_vc}
-\end{figure}
 

### 2013-07-10 snapshot_system/arch.tex
merge two architecture graphs
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.

@@
     {
-        \includegraphics[width=3in]{images/socc_arch_cluster.pdf}
+        \includegraphics[width=3in]{images/socc_arch_cluster}
         \label{fig:arch_cluster}
@@
     {
-        \includegraphics[width=3in]{images/socc_arch_vm.pdf}
+        \includegraphics[width=3in]{images/socc_arch_vm}
         \label{fig:arch_vm}
@@
 %  \centering
-%  \epsfig{file=images/snapshot_representation.pdf, width=3in}
+%  \epsfig{file=images/snapshot_representation, width=3in}
 %  \caption{An example of snapshot representation.}
@@
     \centering
-    \includegraphics[width=6in]{images/socc_arch_cluster.pdf}
+    \includegraphics[width=6in]{images/socc_arch_cluster}
     \caption{System Architecture}
@@
   \centering
-  \epsfig{file=images/sstore_arch.pdf, width=3in}
+  \epsfig{file=images/sstore_arch, width=3in}
   \caption{Data structure of VM snapshot stores.}
@@
 
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=images/pds_arch.pdf, width=3in}
-  \caption{System architecture for PDS data store.}
-  \label{fig:as_arch}
-\end{figure}
+%\begin{figure}[htbp]
+%  \centering
+%  \epsfig{file=images/pds_arch, width=3in}
+%  \caption{System architecture for PDS data store.}
+%  \label{fig:as_arch}
+%\end{figure}
 

### 2013-07-10 snapshot_system/eval1.tex
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.

@@
 %\centering
-%\includegraphics[width=0.4\textwidth]{mem_time.pdf}
+%\includegraphics[width=0.4\textwidth]{mem_time}
 %\caption{ Parallel time when memory limit varies.}
@@
   \centering
-  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
+  \epsfig{file=figures/srb_vs_vc, width=3.5in}
   \caption{Time to backup a dirty segment under SRB and VC approach}
@@
     \centering
-    \includegraphics[width=3in]{figures/single_backup_time.pdf}
+    \includegraphics[width=3in]{figures/single_backup_time}
     \caption{Backup times for varying CDS sizes}
@@
     {
-        \includegraphics[width=3in]{figures/parallel_backup_with_read.pdf}
+        \includegraphics[width=3in]{figures/parallel_backup_with_read}
         \label{fig:withread}
@@
     {
-        \includegraphics[width=3in]{figures/parallel_backup_no_read.pdf}
+        \includegraphics[width=3in]{figures/parallel_backup_no_read}
         \label{fig:noread}
@@
 %   \centering
-%   \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
+%   \epsfig{file=figures/parallel_backup, width=3.5in}
 %   \caption{Throughput per-node with concurrent snapshot backup tasks}

### 2013-07-10 snapshot_system/result.tex
Updated graphs to the new versions.
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.

@@
 bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
-charts in the paper until we decide? If we use the bar charts some tex will
+charts in the paper until we decide? If we use the bar charts some text will
 have to be changed. We could also add each of the CDS sizes to the bar chart
 and have 4 bars instead of 2.}
+\comments{%both of the bar charts are superceded by the graph below
 %\comments{

### 2013-07-11 snapshot_system/failover.tex
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.
revisions and figure changes

@@
     {
-        \includegraphics[width=3in]{images/share_vc.pdf}
+        \includegraphics[width=3in]{images/share_vc}
         \label{fig:share_vc}
@@
     {
-        \includegraphics[width=3in]{images/share_vo.pdf}
+        \includegraphics[width=3in]{images/share_vo}
         \label{fig:share_vo}
@@
 		xlabel={Number of VMs},
-		ylabel={Avg. Num. VMs sharing FSB},
+		ylabel={\small Avg. Num. VMs sharing FSB},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		\addplot[color=red,mark=square*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
-                \legend{Global Dedup (VO), PDS FSB (VC)};
+                \legend{VO, PDS in VC};
 		\end{axis}
@@
 		xlabel={Number of VMs},
-		ylabel={Avg. Num. FSBs used by VM},
+		ylabel={\small Avg. Num. FSBs used by VM},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		\addplot[color=red,densely dashed,mark=triangle*,mark size=3] table[x=VMs,y=VMCDSLinks] {figures/vc_vm_links.txt};
-                \legend{VO FSB, Non-PDS FSB (VC), PDS FSB (VC)};
+                \legend{$N_0$, $N_1$, $N_2$};
 		\end{axis}
@@
 		xlabel={Number of nodes failed},
-		ylabel={chance that a VM is affected (\%) in VO},
+		ylabel={\small chance that a VM is affected (\%) in VO},
 		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
@@
 		xlabel={Failed storage nodes},
-		ylabel={Chance VM is affected (\%)},
+		ylabel={\small Chance VM is affected (\%)},
 		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
@@
 \begin{table}
-    \begin{tabular}{|l|ll|}
+    \begin{tabular}{|l|lll|}
     \hline
-    \multirow{2}{*}{Nodes Failed}   & \multicolumn{2}{c|}{Availability(\%)}\\
-                                    & $R=3$ & $R=4$\\
+    \multirow{2}{*}{Nodes Failed}   & \multicolumn{3}{c|}{Availability(\%)}\\
+                                    & $R=3$ & $R=4$ & $R=5$\\
     \hline
-    1           &  100      & 100\\
-    2           & 100       & 100\\
-    3          & 99.999     & 100\\
-    5          & 99.993     & 99.9999\\
-    10          & 99.926    & 99.995\\
-    20          & 99.295    & 99.876\\
+    1           &  100      & 100       & 100\\
+    2           & 100       & 100       & 100\\
+    3          & 99.999     & 100       & 100\\
+    5          & 99.993     & 99.9999   & 99.999998\\
+    10          & 99.926    & 99.995    & 99.999\\
+    20          & 99.295    & 99.876    & 99.979\\
     \hline
     \end{tabular}
-    \caption{Availability of a single FSB in the global data store with different relplication factors}
+    \caption{Availability in a 100 machine cluster of a single FSB in the global data store with different relplication factors}
     \label{tab:fsb-availability}
@@
             xlabel={Number of Machines Failed},
-            ylabel={Availability of Single FSB (\%)},
+            ylabel={\small Availability of Single FSB (\%)},
             %extra y ticks={4.5,5.5,6.5} %to add extra ticks
@@
             ]
-            \addplot[color=blue,mark=none] table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
+            \addplot[color=blue,mark=none] table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
             \addplot[densely dashed, color=red,mark=none] table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
-            \legend{$R=3$,$R=4$};
+            \addplot[densely dotted,color=brown,mark=none] table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
+            \legend{$R=5$,$R=4$,$R=3$};
             \end{axis}
@@
                 \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
-                \addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
-            \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}
+                %\addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
+                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
 		\end{axis}
@@
                 \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
-                \addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
-            \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}
+                %\addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
+                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
 		\end{axis}

### 2013-07-11 snapshot_system/snapshot.tex
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.
revisions and figure changes

@@
 \centering
-%\epsfig{file=log-log.disk.pdf,width=3in}
+%\epsfig{file=log-log.disk,width=3in}
 %source ../vm_snapshot_sim/images/log-log.disk.eps
- \includegraphics[width=3in]{figures/log-log-disk.pdf}
+ \includegraphics[width=3in]{figures/log-log-disk}
 \caption{Duplicate frequency versus  chunk ranking in a log scale.}
@@
             xlabel={Total number of chunks stored},
-            ylabel={CDS Coverage (\%)},
+            ylabel={PDS Coverage (\%)},
             %extra y ticks={4.5,5.5,6.5} %to add extra ticks
@@
             \addplot[densely dashed,color=red,mark=triangle*] table[x=InputChunks,y=T4] {figures/cds_coverage.txt};
-            \legend{Measured (1\%CDS),Measured (2\%CDS),Measured (4\%CDS),Predicted (1\%CDS),Predicted (2\%CDS),Predicted (4\%CDS)};
+            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
             \end{axis}

### 2013-07-11 snapshot_system/eval1.tex
cleaned up graph code, removed several obsolete figures

@@
             %title={Ex-Binning Efficiency},
+            cycle list name=mline,
             xlabel={Number of VMs added},
@@
             %    at={(0.5,-0.2)},
-            %anchor=north}
+            %anchor=north},
             ]
-            \addplot[color=blue,mark=none] table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
-            \addplot[densely dotted, color=red,mark=none] table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
-            \addplot[loosely dotted, color=brown,mark=none] table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
-            \addplot[densely dashed,color=black,mark=none] table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
-            \legend{SRB,VC (1\%CDS),VC (2\%CDS),VC (4\%CDS)};
+            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
+            \addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
+            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
+            \addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
+            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$)};
             \end{axis}

### 2013-07-11 snapshot_system/failover.tex
cleaned up graph code, removed several obsolete figures

@@
 		]
-		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
-		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
+		\addplot table[x=VMs,y=Measured] {figures/vo_links.txt};
+		\addplot table[x=VMs,y=Theoretical] {figures/vo_links.txt};
 		\legend{Measured,Theoretical};
@@
 		]
-                \addplot[color=blue,mark=*] table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
-		\addplot[color=red,mark=square*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
+                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
+		\addplot table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                 \legend{VO, PDS in VC};
@@
 		ylabel={\small Avg. Num. FSBs used by VM},
+                ymin=0,
+                mark options=solid,
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		\addplot[color=red,mark=square*] table[x=VMs,y=VMNonCDSLinks] {figures/vc_vm_links.txt};
-		\addplot[color=red,densely dashed,mark=triangle*,mark size=3] table[x=VMs,y=VMCDSLinks] {figures/vc_vm_links.txt};
+		\addplot[color=red,densely dashed,mark=triangle*,mark size=2.7] table[x=VMs,y=VMCDSLinks] {figures/vc_vm_links.txt};
                 \legend{$N_0$, $N_1$, $N_2$};
@@
 %shared among VMs. Any failure of these blocks causes many more VMs to fail.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%OLD MODEL START%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failure}
-%(for a 100 node cluster).
-%The graph assumes 10X40GB snapshots per VM with 18\% unique data after local
-%dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
-%VM). We assume 18\% unique data after local dedup because that is what our
-%snapshots have shown.
-
-\comments{\begin{figure}[ht]
-  \centering
-  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={Node failure affect on VMs},
-		xlabel={Number of nodes failed},
-		ylabel={\small chance that a VM is affected (\%) in VO},
-		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
-		]
-		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Percent chance that a VM is affected as storage nodes fail}
-  \label{fig-vm-failure}
-\end{figure}}
-
-\comments{\begin{figure}[ht]
-  \centering
-  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={Node failure affect on VMs},
-		xlabel={Failed storage nodes},
-		ylabel={\small Chance VM is affected (\%)},
-		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
-                mark options=solid,
-                legend pos=north west
-		]
-                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO]{figures/vm_failure_1.txt};
-                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_1.txt};
-                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_1.txt};
-                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_1.txt};
-                \legend{$VO$,$VC_{C_R=3}$,$VC_{C_R=4}$,$VC_{C_R=5}$,$VC_{C_R=6}$,$VC_{C_R=7}$}
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Percent chance that a VM is affected as storage nodes fail}
-  \label{fig-vm-failure}
-\end{figure}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%OLD MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL START%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
             %title={FSB Availability},
+            cycle list name=mline,
             xlabel={Number of Machines Failed},
@@
             ]
-            \addplot[color=blue,mark=none] table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
-            \addplot[densely dashed, color=red,mark=none] table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
-            \addplot[densely dotted,color=brown,mark=none] table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
+            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
+            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
+            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
             \legend{$R=5$,$R=4$,$R=3$};
@@
 		%title={Node failure affect on VMs},
+                cycle multi list={
+                    mline\nextlist
+                    [2 of]mmark*\nextlist
+                },
 		xlabel={Failed storage nodes},
@@
                     legend pos=south west %legend position
-                }
+                },
+                %reverse legend,
 		]
-                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
-                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
-                %\addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
-                %\addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
-                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
-                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
-                %\addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
-                %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
-            \legend{$VO\,10$ (optimistic),$VO\,5$ (measured),$VC\,1000$ (extreme),$VC\,20$ (measured)}
+                \addplot table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
+                \addlegendentry{$VC\,20$ (measured)}
+                \addplot table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
+                \addlegendentry{$VC\,1000$ (extreme)}
+                %\addplot table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
+                %\addplot table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
+                \addplot table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
+                \addlegendentry{$VO\,5$ (measured)}
+                \addplot table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
+                \addlegendentry{$VO\,10$ (optimistic)}
+                %\addplot table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
+                %\addplot table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
 		\end{axis}
@@
                     legend pos=south west %legend position
-                }
+                },
+                reverse legend,
 		]
-                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
-                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
-                \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
-                %\addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
+                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
+                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
+                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
+                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
                 \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
@@
                     legend pos=south west %legend position
-                }
+                },
+                reverse legend,
 		]
-                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
-                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
-                \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
-                %\addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
+                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
+                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
+                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
+                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
                 \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2013-07-11 snapshot_system/main.tex
change
w
modif
added plot for VO block links. still has some issue though.
Added CDS coverage graph with measured vs predicted. Not sure the predicted is helpful to the graph though.
Added VM failure figures for two different models
adding exper.
modify all sections
revise
update graphs
my local changes
update
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.
cleaned up graph code, removed several obsolete figures

@@
-\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate-10pt}
+\usepackage{mathptmx}
 \usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
+\usepackage{subfigure}
 \usepackage{epsfig}
+\usepackage{multirow}
+\usepackage{array}
 \usepackage{breqn}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.7}
+\DeclareGraphicsExtensions{.pdf}
 
 \newcommand{\comments}[1]{}
+%pgfplots setup
+\pgfplotsset{every axis/.append style={
+	very thick,
+	tick style={thick}}}
+\pgfplotsset{
+        every mark/.append style={solid}
+}
+\pgfplotscreateplotcyclelist{mcolor}{%
+    {blue,every mark/.append style={fill=blue},mark=*},
+    {red,every mark/.append style={fill=red},mark=square*},
+    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=3},
+    {black,every mark/.append style={fill=black},mark=diamond*,mark size=3},
+    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
+    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3},
+    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
+    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
+    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=2.7},
+    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=2.7},
+    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
+    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3}}
+
+\pgfplotscreateplotcyclelist{mmark*}{
+    {mark=*},
+    {mark=square*},
+    {mark=triangle*,mark size=2.7},
+    {mark=diamond*,mark size=2.7},
+    {mark=pentagon*,mark size=2.5},
+    {mark=star,mark size=3},
+    {mark=asterisk,mark size=3},
+    {mark=+,mark size=3},
+    {mark=Mercedes star,mark size=3}}
+
+\pgfplotscreateplotcyclelist{mline}{
+    {solid,blue,every mark/.append style={fill=blue}},
+    {densely dashed,red,every mark/.append style={fill=red}},
+    {densely dotted,brown,every mark/.append style={fill=brown}},
+    {loosely dotted,black,every mark/.append style={fill=black}},
+    {loosely dashed,green!60!black,every mark/.append style={fill=green!60!black}},
+    {densely dashdotted,magenta!90!black,every mark/.append style={fill=magenta!90!black}},
+    {densely dashdotdotted,teal,every mark/.append style={fill=teal}},
+    {loosely dashdotted,orange,every mark/.append style={fill=orange}},
+    {loosely dashdotdotted,violet,every mark/.append style={fill=violet}}}
+
+    \pgfplotsset{cycle list name=mcolor}
 
@@
 \input{failover}
-\input{design1}
-%\input{snapshot}
-%\input{append}\
-\input{cds}
+%\input{compare}
+%\input{design1}
+\input{arch}
+%\input{impl}
+%\input{sampling-comparison.txt}
+\input{eval1}
+%\input{cds}
 %\input{delete}
 %\input{failover}
-\input{result}
+%\input{result}
 \input{con}

### 2013-07-11 snapshot_system/snapshot.tex
CDS->PDS fix
cleaned up graph code, removed several obsolete figures

@@
             \begin{axis}[
-            %title={CDS Coverage},
-            xlabel={Total number of chunks stored},
+            %title={PDS Coverage},
+            %width=\columnwidth,
+            cycle multi list={
+                mline\nextlist
+                [3 of]mmark*\nextlist
+            },
+            %cycle list name=mcolor,
+            xlabel={Total num. chunks stored (in billions)},
             ylabel={PDS Coverage (\%)},
@@
                 at={(0.5,-0.2)},
-            anchor=north}
+            anchor=north},
             ]
-            \addplot[color=blue,mark=*] table[x=InputChunks,y=A1] {figures/cds_coverage.txt};
-            \addplot[color=blue,mark=square*] table[x=InputChunks,y=A2] {figures/cds_coverage.txt};
-            \addplot[color=blue,mark=triangle*,mark size=3] table[x=InputChunks,y=A4] {figures/cds_coverage.txt};
-            \addplot[densely dashed,color=red,mark=*] table[x=InputChunks,y=T1] {figures/cds_coverage.txt};
-            \addplot[densely dashed,color=red,mark=square*] table[x=InputChunks,y=T2] {figures/cds_coverage.txt};
-            \addplot[densely dashed,color=red,mark=triangle*] table[x=InputChunks,y=T4] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
             \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
@@
     \end{tikzpicture}
-  \caption{fixed-alpha predicted vs. actual CDS coverage as data size increases.}
+  \caption{fixed-alpha predicted vs. actual PDS coverage as data size increases.}
   \label{fig-cds-coverage}

### 2013-07-11 snapshot_system/failover.tex
Revisions. More CDS->PDS. Added N1+N2 line to fig-vm-links

@@
 rare chunks which are not shared.
-Figure~\ref{fig:VOshared} shows the number of VMs shared by each file block.
+Figure~\ref{fig-fsb-links} shows the number of VMs sharing by each file block.
 In our experiment, we find that $V_o \approx 0.2 V$ when backing up VMs one by one.
-We can observe that $N_1 +N_2 << N_o$.
+We can observe in Figure~\ref{fig-vm-links} that $N_1 +N_2 < N_o$.
+This is likely because the PDS FSBs tightly pack data used by many VMs, which decreases the overall number of FSBs required to backup a VM.
 If  the backup for multiple VMs is conducted concurrently, there would be more
@@
 Figure~\ref{fig-fsb-links} shows the average number of VMs sharing a
-filesystem block (FSB) in the global index as VMs are added. Two of the VMs had
-much larger hard drives (\~300GB), which explains the 2 drops, as those two VMs
-added much more unique data than normal. Though we expect the graph to level out some for
+filesystem block (FSB) as VMs are added. Though we don't expect the linear trend to continue indefinitely for
 much larger datasets, it should continue to increase, which has important implications
@@
 		]
-                \addplot[color=blue,mark=*] table[x=VMs,y=VMLinks] {figures/vo_vm_links.txt};
-		\addplot[color=red,mark=square*] table[x=VMs,y=VMNonCDSLinks] {figures/vc_vm_links.txt};
-		\addplot[color=red,densely dashed,mark=triangle*,mark size=2.7] table[x=VMs,y=VMCDSLinks] {figures/vc_vm_links.txt};
-                \legend{$N_0$, $N_1$, $N_2$};
+                \addplot table[x=VMs,y=No] {figures/vo_vm_links.txt};
+		\addplot table[x=VMs,y=N1] {figures/vc_vm_links.txt};
+                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links.txt};
+                \addplot+[dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links.txt};
+                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
 		\end{axis}
@@
 all of its replicas appear in $d$ failed machines. 
-Namely, $\binom{d}{r}/ \binom{p}{r}$.
+Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig-fsb-availability} for a 100 machine cluster for 3 different replication factors.
 
@@
 Figure~\ref{fig-vm-availability} shows the reliability of VM backups as storage
-nodes fail for different numbers of links to average blocks in the index. We
-chose 5 and 20 for the VO and VC block links counts because those are what we
-measured in our dataset, and chose higher numbers to account for much larger
-datasets. We chose to use a very optimistic setting for VO (10), and an extreme
-amount of sharing for VC (1000) to better show the significant improvement in
-data reliability for the VC model (showing VO best case is still worse than VC
-worst case). As you can see from the graph, even small changes in the number of
-links to VO blocks has a significant impact on reliability, while even a 50
-times increase in the VC block link counts only slightly affects VC
-reliability.  The key factor placed is that  $N_1 +N_2 << N_o$, caused by the
-fact that the VM-centric approach localizes deduplication and packs  data
-blocks for one VM as much as possible.  The extra replicaton for PDS blocks
-also signficantly increases the snapshot availability even when a PDS file
-block is shared by every VM.
+nodes fail for different amounts of sharing of filesystem blocks in the index. We
+show 5 and 20 for the VO and VC block links counts because those are what we
+measured in our small dataset, and chose higher numbers to account for much
+larger datasets. We chose to use a very optimistic setting for VO (20), and the
+absolute worst case amount of sharing for VC in a 100 machine cluster with 25
+VMs per machine (2500). Our results show that even the VC worst case provides
+better VM reliability that VO. As you can see from the graph, even small
+changes in the number of links to VO blocks has a significant impact on
+reliability, while even a 50 times increase in the VC block link counts only
+slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <
+N_o$, caused by the fact that the VM-centric approach localizes deduplication
+and packs  data blocks for one VM as much as possible.  The extra replicaton
+for PDS blocks also signficantly increases the snapshot availability even when
+a PDS file block is shared by every VM.
 
@@
     \end{tabular}
-    \caption{Availability in a 100 machine cluster of a single FSB in the global data store with different relplication factors}
+    \caption{Availability in a 100 machine cluster of a single FSB in the global data store with different replication factors}
     \label{tab:fsb-availability}
@@
             ylabel={\small Availability of Single FSB (\%)},
-            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            extra y ticks={99.9}, %to add extra ticks
             mark options=solid,
@@
 		]
-                \addplot table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
+                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                 \addlegendentry{$VC\,20$ (measured)}
-                \addplot table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
-                \addlegendentry{$VC\,1000$ (extreme)}
-                %\addplot table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
-                %\addplot table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
-                \addplot table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
+                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
+                \addlegendentry{$VC\,2500$ (worst-case)}
+                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                 \addlegendentry{$VO\,5$ (measured)}
-                \addplot table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
-                \addlegendentry{$VO\,10$ (optimistic)}
-                %\addplot table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
-                %\addplot table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
+                \addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
+                \addlegendentry{$VO\,20$ (optimistic)}
 		\end{axis}
 	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail for VO and VC models for varying degrees of block sharing (i.e.
-average number of VMs that use a block).
-Non-PDS replication fixed at 3 and PDS replication increased to 4.}
+  \caption{Availability of VM backups as nodes fail for VO and VC models for
+  varying degrees of block sharing (i.e. average number of VMs that use a
+  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
+  Graph shown for 100 machine cluster.
+  }
   \label{fig-vm-availability}

### 2013-07-11 snapshot_system/snapshot.tex
Revisions. More CDS->PDS. Added N1+N2 line to fig-vm-links

@@
 %However, at level-3 things are different.
-If we use 4KB fix-size block uniformly, it would be harder for different VM to share data through CDS, because there is no guarantee that the location of duplicate data on different VM disks are always aligned at 4KB boundary.
+If we use 4KB fix-size block uniformly, it would be harder for different VM to share data through PDS, because there is no guarantee that the location of duplicate data on different VM disks are always aligned at 4KB boundary.
 For example, if two VMs each has a copy of duplicate data, but they are not aligned, then we won't be able to detect them.
-Our study at the current small data set has shown that using 4KB fix-size block will make CDS method less efficient by nearly 10%.
+Our study at the current small data set has shown that using 4KB fix-size block will make PDS method less efficient by nearly 10%.
 Over the long time, more and more OS variations will co-exist in the cluster, making this 4KB fix-size approach inefficient in reducing duplicate data across VMs.
@@
 Thus our approximation is that the global fingerprint comparison only searches for the top $k$
-most popular items. This dataset is called CDS (common data set). 
+most popular items. This dataset is called PDS (common data set). 
 %Since duplicate sharing patterns among  VM follows a zip-like distribution,  
@@
 
-CDS chunks are stored in a separate append-store instance. In this way, each
-file block for non-CDS chunks is associated with one VM and does not contain
-any CDS chunks. 
+PDS chunks are stored in a separate append-store instance. In this way, each
+file block for non-PDS chunks is associated with one VM and does not contain
+any PDS chunks. 
 \end{itemize}
@@
 %global deduplication.
-%\subsubsection{Impact of CDS deduplication}
+%\subsubsection{Impact of PDS deduplication}
 The analysis is based on the charactristics  of the VM snapshot traces
@@
 exponent $\alpha$ is ranged between 0.65  and  0.7.~\cite{ieeecloud}. 
-%As a result, it can be proved that deduplication efficiency of CDS index is scalable:
+%As a result, it can be proved that deduplication efficiency of PDS index is scalable:
 Table~\ref{tab:symbol} lists parameters used in this analysis.
@@
 \hline
-$\sigma$ &  the number of unique non-CDS chunks over  the number of the CDS chunks.\\
+$\sigma$ &  the number of unique non-PDS chunks over  the number of the PDS chunks.\\
 \hline
@@
 \hline
-$N_1$ & the average number  of non-CDS file system blocks  in a VM\\
+$N_1$ & the average number  of non-PDS file system blocks  in a VM\\
 \hline
-$N_2$ & the average number  of CDS file system blocks  in a VM\\
+$N_2$ & the average number  of PDS file system blocks  in a VM\\
 \hline
@@
 
-% So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
+% So the cumulative distribution function for a PDS holding top $S_c$ fingerprints
 % of global index with size $S_g$ is:
@@
 chunks detected as duplicates after inner VM deduplication.
-Figure~\ref{fig-cds-coverage} shows measured CDS coverage in our 35 VM dataset.
+Figure~\ref{fig-cds-coverage} shows measured PDS coverage in our 35 VM dataset.
 You can see from the graph that the coverage actually increases as the datasize
 increases, which indicates that $\alpha$ increases with the datasize (a
-fixed-$\alpha$ model would predict constant coverage). This makes the CDS even
-more effective, as the coverage of the CDS increases as more data is added.
-%Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
+fixed-$\alpha$ model would predict constant coverage). This makes the PDS even
+more effective, as the coverage of the PDS increases as more data is added.
+%Then the deduplication efficiency of PDS approach using top k most popular fingerprints is:
 %\begin{equation}
@@
 %and the Zipf-like distribution parameter $\alpha$.
-%From the memory usage perspective, the more memory we give to CDS index, the more duplicates it can found.
+%From the memory usage perspective, the more memory we give to PDS index, the more duplicates it can found.
 %From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
-%$\alpha$ would be small and thus CDS approach would not be effective. But in a VM cluster all VMs
+%$\alpha$ would be small and thus PDS approach would not be effective. But in a VM cluster all VMs
 %have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
-%the better deduplication efficiency our CDS deduplication approach will have.
+%the better deduplication efficiency our PDS deduplication approach will have.
 
 \comments{
-Since $B$, $D$ and $F$ are environment constants, the deduplication efficiency of CDS is mainly affected by its memory usage,
+Since $B$, $D$ and $F$ are environment constants, the deduplication efficiency of PDS is mainly affected by its memory usage,
 and the Zipf-like distribution parameter $\alpha$.
-From the memory usage perspective, the more memory we give to CDS index, the more duplicates it can found.
+From the memory usage perspective, the more memory we give to PDS index, the more duplicates it can found.
 From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
-$\alpha$ would be small and thus CDS approach would not be effective. But in a VM cluster all VMs
+$\alpha$ would be small and thus PDS approach would not be effective. But in a VM cluster all VMs
 have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
-the better deduplication efficiency our CDS deduplication approach will have.
+the better deduplication efficiency our PDS deduplication approach will have.
 }

### 2013-07-11 snapshot_system/eval1.tex
Revisions

@@
 \caption{Storage space cost under different PDS replication degree}
-\label{tab:replcation_cost}
+\label{tab:replication_cost}
 \end{table}
+
+Table~\ref{tab:replication_cost} shows the total storage space required by VC as the PDS replication degree is changed.
+The increase in storage cost is minimal because the PDS makes up a very small percent of the total storage space, but the increase in reliability can be much more significant (see Figure~\ref{fig-pds-replication}).
 

### 2013-07-11 snapshot_system/eval1.tex
minor revisions.

@@
 The final snapshots are stored in a distributed file system built on the same 
-cluster.
-
-The total local disk usage on each machine is about 8GB for the duplicate detection purpose,
+cluster. total local disk usage on each machine is about 8GB for the duplicate detection purpose,
 mainly for global index. 
@@
 
-Figure~\ref{fig-exbin-efficiency-graph} shows the deduplication efficiency which is
-the percent of deduped duplicate chunks by SRB and VC.
-It also lists several PDS sizes chosen for VC. ``2\% PDS" means that
-we allocate the space of distributed shared memory  to accommodate $\delta=2\%$
-of data chunks shared among VMs. Namely 
-With $\delta=2\%$, the deduplication efficiency can reach over 90\% 
-while $\delta=4\%$, the deduplication efficiency can reach over 92\%. 
+Figure~\ref{fig-exbin-efficiency-graph} shows the deduplication efficiency for SRB and VC.
+We define deduplication efficiency to be the percent of duplicate chunks
+which are detected and deduplicated.
+The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' means that
+we allocate the space of distributed shared memory  to accommodate 2\%
+of data chunks shared among VMs, as defined in Table~\ref{tab:symbol}. Namely 
+With $\sigma=2\%$, the deduplication efficiency can reach over 90\% 
+while with $\sigma=4\%$, the deduplication efficiency can reach over 92\%. 
 The loss of efficiency in VC is caused by the restriction of the total physical memory available
-in the cluster to support PDS.  
+in the cluster to support the PDS.  
 The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
 for global comparison.
-In all cases, VC provides similar or better deduplication efficiency than SRB
+In all cases, VC provides similar or better deduplication efficiency than SRB.
 
-This shows VC can remove  a competitive amount of duplicates.
-In general, our experiment shows that
-dirty-bit detection in the segment level  can reduce the data size to about 23\% of original data, 
+This result shows VC can remove  a competitive amount of duplicates.
+In general, our experiments show that
+dirty-bit detection at the segment level  can reduce the data size to about 23\% of original data, 
 which leads  about 77\% reduction.
@@
 to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
-The PDS-based cross-VM detection with $\delta=2\% $
+The PDS-based cross-VM detection with $\sigma=2\% $
 can reduce the  size further to 8\% of original size, namely it 

### 2013-07-11 snapshot_system/con.tex
Reference fixes and revisions

@@
 In this paper we propose a VM-centric deduplication scheme for 
-snapshot backup in VM cloud for maximizing fault isolation and tolerance. 
+VM snapshot backup in the cloud for maximizing fault isolation and tolerance. 
 Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
 while cross-VM deduplication with a small common data set
-effectively  covers a large amount of duplicated data.
+effectively  covers a large percent of duplicate data.
 The scheme organizes the write of small data chunks into large file system blocks so
-that each underlying file block is associated with one VM for most of cases.
-Our solution accomplishes the majority of
-potential global deduplication saving while still meets stringent cloud resources requirement. 
+that each underlying file block is associated with one VM for most cases.
+by keeping most of the VM-FSB mappings 1:1 we isolate faults and improve overal fault tolerance.
+Our solution accomplishes reasonable and competitive deduplication efficiency while
+still meeting stringent cloud resource usage requirements. 
 Our analysis shows that  this VM centric scheme 
-can  provide  better fault tolerance while using a small amount of computing and storage resource.
+can  provide  better fault tolerance that VM-oblivious global deduplication schemes
+while using a small amount of computing and storage resource.
 
@@
 Evaluation using real user's VM data shows
-our solution can accomplish 75\% of what complete global
+our solution can accomplish 92\% of what complete global
 deduplication can do. 

### 2013-07-11 snapshot_system/eval1.tex
Reference fixes and revisions

@@
 a distributed file system (QFS) running in the cluster manages six 3TB disks
-with default replication degree set to 3. The CDS replication is set to 5.
+with default replication degree set to 3. The PDS replication is set to 5.
 Objectives of our evaluation are:
@@
 The backup of VM snapshots is completed within a few  hours every night.
-Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
+Based on our study of production  data,  each VM has about  40GB of storage  data on average
 including OS and user data disk.
@@
 The backup of VM snapshots is completed within a few  hours every night.
-Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
+Based on our study of production  data,  each VM has about  40GB of storage  data  on average
 including OS and user data disk.
@@
 Popularity of data blocks are collected through global counting 
-and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.
+and the top 1\% will fall into PDS, as discussed in Section~\ref{sect:crossVM}.
 %variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
@@
 
-%In our snapshot deduplication architecture, CDS is the key to achieve greater deduplication than
-%incremental backup solutions. Our basic assumption of CDS us that VM disks, especially OS disks,
+%In our snapshot deduplication architecture, PDS is the key to achieve greater deduplication than
+%incremental backup solutions. Our basic assumption of PDS us that VM disks, especially OS disks,
 %have huge amount of data in common, and such common data can be represented by a relatively smaller data set
@@
 %emerge from eliminating the duplication of such a small data set. In this section, we evaluate
-%the effectiveness of CDS using real user VM disks from our production VM cluster.
+%the effectiveness of PDS using real user VM disks from our production VM cluster.
 
@@
 Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
-study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
+study the PDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
 
@@
 
-Figure~\ref{fig-exbin-efficiency-graph} shows the deduplication efficiency for SRB and VC.
+Figure~\ref{fig:exbin-efficiency-graph} shows the deduplication efficiency for SRB and VC.
 We define deduplication efficiency to be the percent of duplicate chunks
@@
          of SRB  and VC with $\delta=2\%$.}
-        %($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
-  \label{fig-exbin-efficiency1}
+        %($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% PDS.}
+  \label{fig:exbin-efficiency1}
 \end{figure}
@@
     \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
-  \label{fig-exbin-efficiency2}
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% PDS.}
+  \label{fig:exbin-efficiency2}
 \end{figure}
@@
 
-%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
+%graph comparing extreme binning (SRB) with PDS model (VC) for different cds percentages
 \begin{figure}[ht]
@@
     SRB and  VC.}
-  \label{fig-exbin-efficiency-graph}
+  \label{fig:exbin-efficiency-graph}
 \end{figure}
@@
 
-%Overall speaking, inner   VM deduplication or  CDS-based deduplication
+%Overall speaking, inner   VM deduplication or  PDS-based deduplication
 %can work well alone, but by combining them together we get a fairly good and stable deduplication ratio to 
@@
 %each file (e.g. segment in our scheme),
-%our CDS-based level 3 approach  can save additional 50\% storage space because many of level 2 block
-%content can be eliminated using the CDS also.
+%our PDS-based level 3 approach  can save additional 50\% storage space because many of level 2 block
+%content can be eliminated using the PDS also.
 
@@
 Table~\ref{tab:replication_cost} shows the total storage space required by VC as the PDS replication degree is changed.
-The increase in storage cost is minimal because the PDS makes up a very small percent of the total storage space, but the increase in reliability can be much more significant (see Figure~\ref{fig-pds-replication}).
+The increase in storage cost is minimal because the PDS makes up a very small percent of the total storage space, but the increase in reliability can be much more significant (see Figure~\ref{fig:pds-replication}).
 
@@
 %evaulate the system performance on the second snapshot backup. We repeat such procedure
-%under different CDS memory usage settings, the results of backup time break down are shown in
+%under different PDS memory usage settings, the results of backup time break down are shown in
 
@@
 %charts in the paper until we decide? If we use the bar charts some text will
-%have to be changed. We could also add each of the CDS sizes to the bar chart
+%have to be changed. We could also add each of the PDS sizes to the bar chart
 %and have 4 bars instead of 2.}
@@
 %Larger memory permits us to
-%use larger CDS index to cover more of global index, as a result the amount of data to be writen
+%use larger PDS index to cover more of global index, as a result the amount of data to be writen
 %is reduced and so do the writing time.
@@
     \includegraphics[width=3in]{figures/single_backup_time}
-    \caption{Backup times for varying CDS sizes}
+    \caption{Backup times for varying PDS sizes}
     \label{fig:single_vm_backup}
@@
 making it inefficient to utilize the benefits of parallel disk access. We expect our architecture can
-perform even better in production cluster which normally has more than ten disks on each node.
+perform even better in production clusters which often have more than ten disks on each node.
 
@@
 %  & Transfer fingerprints & 0.00058 & 0.00013 \\ \cline{2-4}
-%  & CDS lookup & N/A & 0.00034 \\ \cline{2-4}
+%  & PDS lookup & N/A & 0.00034 \\ \cline{2-4}
 %  & Subtotal & 0.021 & 0.0064 \\ \hline
@@
 terms of capactity and distributing the deduplication. The only part of our
-algorithm which requires significant network traffic is the CDS deduplication,
+algorithm which requires significant network traffic is the PDS deduplication,
 but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and

### 2013-07-11 snapshot_system/failover.tex
Revisions
Reference fixes and revisions

@@
 rare chunks which are not shared.
-Figure~\ref{fig-fsb-links} shows the number of VMs sharing by each file block.
+Figure~\ref{fig:fsb-links} shows the number of VMs sharing by each file block.
 In our experiment, we find that $V_o \approx 0.2 V$ when backing up VMs one by one.
-We can observe in Figure~\ref{fig-vm-links} that $N_1 +N_2 < N_o$.
+We can observe in Figure~\ref{fig:vm-links} that $N_1 +N_2 < N_o$.
 This is likely because the PDS FSBs tightly pack data used by many VMs, which decreases the overall number of FSBs required to backup a VM.
@@
 
-Figure~\ref{fig-fsb-links} shows the average number of VMs sharing a
+Figure~\ref{fig:fsb-links} shows the average number of VMs sharing a
 filesystem block (FSB) as VMs are added. Though we don't expect the linear trend to continue indefinitely for
@@
   \caption{Average number of VMs sharing a data chunk in the global index}
-  \label{fig-vo-links}
+  \label{fig:vo-links}
 \end{figure}
@@
   \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
-  \label{fig-fsb-links}
+  \label{fig:fsb-links}
 \end{figure}
@@
                 \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links.txt};
-                \addplot+[dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links.txt};
+                \addplot+[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links.txt};
                 \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
@@
   \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
-  \label{fig-vm-links}
+  \label{fig:vm-links}
 \end{figure}
@@
 all of its replicas appear in $d$ failed machines. 
-Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig-fsb-availability} for a 100 machine cluster for 3 different replication factors.
+Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.
 
@@
 (Figure~\ref{vo-links}) and number of links per Filesystem Block (FSB)
-(Figure~\ref{fig-fsb-links}) in our dataset. For the complete dataset, we also
+(Figure~\ref{fig:fsb-links}) in our dataset. For the complete dataset, we also
 found the average number of links to PDS chunks, which was \~19 using a 2\%
-PDS. From Figure~\ref{fig-fsb-links} you can see that as you add VMs, the
+PDS. From Figure~\ref{fig:fsb-links} you can see that as you add VMs, the
 average number of links to a chunk increases linearly for our dataset. We
@@
 only one VM pointing to each non-PDS chunk. You can see the increase in
-reliability in Figure~\ref{fig-vm-availability}.
+reliability in Figure~\ref{fig:vm-availability}.
 }
 
-Figure~\ref{fig-vm-availability} shows the reliability of VM backups as storage
+Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
 nodes fail for different amounts of sharing of filesystem blocks in the index. We
@@
 % while in VO even small increases in $L$ causes a large decrease in availability. 
-Figure~\ref{fig-pds-replication}
+Figure~\ref{fig:pds-replication}
 shows the advantages of increasing the replication factor for PDS blocks. the
@@
     \end{tabular}
-    \caption{Availability in a 100 machine cluster of a single FSB in the global data store with different replication factors}
+    \caption{Availability in a 100 machine cluster of a single FSB with different replication factors}
     \label{tab:fsb-availability}
@@
     \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
-  \label{fig-fsb-availability}
+  \label{fig:fsb-availability}
 \end{figure}
@@
   }
-  \label{fig-vm-availability}
+  \label{fig:vm-availability}
 \end{figure}
@@
   \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
-  \label{fig-pds-replication}
+  \label{fig:pds-replication}
 \end{figure}
@@
 		ylabel={VM Snapshot Availability (\%)},
-		extra y ticks={99.9}, %if important numbers are missing
+		%extra y ticks={99.99}, %if important numbers are missing
                 mark options=solid,
@@
   \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
-  \label{fig-pds-replication2}
+  \label{fig:pds-replication2}
 \end{figure}

### 2013-07-11 snapshot_system/intro.tex
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.
Reference fixes and revisions

@@
 Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
-%(Figure~\ref{fig-traditional-arch})
+%(Figure~\ref{fig:traditional-arch})
 can effectively identify and remove content duplicates among snapshots, 
@@
 %    \centering
-%    \includegraphics[width=3in]{images/traditional-arch.pdf}
-%    \label{fig-traditional-arch}
+%    \includegraphics[width=3in]{images/traditional-arch}
+%    \label{fig:traditional-arch}
 %    \caption{Traditional VM Backup System}
@@
 %    \centering
-%    \includegraphics[width=3in]{images/colocated-arch.pdf}
-%    \label{fig-colocated-arch}
+%    \includegraphics[width=3in]{images/colocated-arch}
+%    \label{fig:colocated-arch}
 %    \caption{Collocated VM Backup System}
@@
 Section~\ref{review} reviews background and related work.
-Section~\ref{sec:framework}  discusses the  design options for snapshot backup with a VM-centric approach. 
-Section~\ref{sec:model}  analyzes the benefit of our approach for fault isolation. 
-Section~\ref{sec:arch}  describes our system architecture and implementation details.
+Section~\ref{sect:framework}  discusses the  design options for snapshot backup with a VM-centric approach. 
+Section~\ref{sect:model}  analyzes the benefit of our approach for fault isolation. 
+Section~\ref{sect:arch}  describes our system architecture and implementation details.
 %   the benefit of our approach for fault isolation. 

### 2013-07-11 snapshot_system/snapshot.tex
Reference fixes and revisions

@@
 \subsection{Key VC Strategies}
+\label{sect:vc-strategies}
 
@@
 accumulate small local chunks. We manage this accumulation process using an append-store  scheme
-and discuss this in details in Section~\ref{sec:arch}.
+and discuss this in details in Section~\ref{sect:arch}.
 The system allows all machines conduct the backup in parallel in different machines, and each machine
@@
 chunks detected as duplicates after inner VM deduplication.
-Figure~\ref{fig-cds-coverage} shows measured PDS coverage in our 35 VM dataset.
+Figure~\ref{fig:cds-coverage} shows measured PDS coverage in our 35 VM dataset.
 You can see from the graph that the coverage actually increases as the datasize
@@
   \caption{fixed-alpha predicted vs. actual PDS coverage as data size increases.}
-  \label{fig-cds-coverage}
+  \label{fig:cds-coverage}
 \end{figure}
 
-As illustrated in Figure~\ref{fig-vo-links}\emph{I am not sure where this reference should point, but I don't think it is pointing to the right figure},
+As illustrated in Figure~\ref{??},
 when the number of machines at each cluster increases, the number of total VMs increases.

### 2013-07-12 snapshot_system/arch.tex
Reference fixes and revisions
Revisions to architecture section

@@
 \section{Architecture and Implementation Details}
-\label{sec:arch}
+\label{sect:arch}
 %[describe what is going to be presented in this section]
@@
 and 4)  a CDS client to support CDS index access. We will further discuss our deduplication scheme 
-in Section~\ref{sec:dedup}.
+in Section~\ref{sect:dedupe}.
 
@@
     \caption{System Architecture}
-    \label{fig:arch_cluster}
+    \label{fig:arch_vm}
 \end{figure*}
@@
 
-The write requests to append a data chunk to a VM store are accumulated in the client side. 
-When the number reaches the group size $g$, the snapshot store client compresses
-the accumulated   chunk group, adds a chunk group index  in the beginning, and then
-append the header and data  to the corresponding VM file,
-Then a new container  index entry is also created and is written the corresponding
+The write requests to append data chunks to a VM store are accumulated in the client side. 
+When the number of write requests reaches the group size $g$, the snapshot store client compresses
+the accumulated   chunk group, adds a chunk group index  to the beginning of the group, and then
+appends the header and data  to the corresponding VM file.
+A new container  index entry is also created for each chunk group and is written the corresponding
 container index file.
@@
 
-To read a non-PDS chunk data by a reference,  the snapshot store client first loads the
+To read a non-PDS chunk using a reference,  the snapshot store client first loads the
 corresponding VM's container index file specified by the container ID, then searches the chunk
@@
 %result in rewriting all the data at the same time.
-When deletion requests issued for a specific container,
-those requests are logged into the  container's deletion log file initially and thus  a lazy
+When deletion requests are issued for a specific container,
+those requests are simply logged into the  container's deletion log initially and thus  a lazy
 deletion strategy is exercised.
@@
 found in the deletion log to the new container, creating new chunk groups and indices. 
-However, every chunk's CID is plainly copied rather than re-generated. This does not affect the sorted
-order of CIDs in new container, but just leaving holes in CID values. As the result, all data references stored 
-in upper level recipes are unaffected, and the data reading process is as efficient as before.
+However, every chunk's CID is directly copied rather than re-generated. This
+process leaves holes in the CID values, but does not affect the sorted order.
+As a result, all data references stored 
+in upper level recipes are permanent and stable, and the data reading process
+is as efficient as before. This CID stability also ensures that recipes do not
+depend directly on physical storage locations.
 \end{itemize}
@@
 In a busy VM cluster, snapshot deletions are as frequent as snapshot creations.
-The VM-centric snapshot storage design simplifies the deletion process since we need to look
-for the useless chunks within each VM when deleting a snapshot.
-The PDS data chunks are commonly shared all VMs and we donot consider their reference
+The VM-centric snapshot storage design simplifies the deletion process since we need to locate unreferenced chunks within each VM to free up space when deleting a snapshot.
+The PDS data chunks are commonly shared all VMs and we do not consider their reference
 counting  during snapshot deletion.
@@
 While we can use the standard mark-sweep technique~\cite{mark-sweep}, 
-it takes time to conduct this process every time there is a snapshot deletion request.
+it takes significant time to conduct this process every time there is a snapshot deletion.
 In the case of Alibaba, snapshot backup is conducted automatically and there are 
@@
 a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
-a balanced storage use. Given a large number of snapshot deletion requests, we are seeking
-a fast solution with a very low resource usage to delete snapshots with an approximation.
+a balanced storage use. Given the large number of snapshot deletion requests, we seek
+a fast solution with a very low resource usage to delete snapshots.
 
 With this in mind, we develop an {\em approximate} deletion strategy to trade deletion accuracy for
-speed and resource usage. Our method sacrifices a tiny percentage of storage leakage
+speed and resource usage. Our method sacrifices a small percent of storage leakage
 to effectively identify unused chunks in $O(n)$ speed, with $n$ being the logical number of non-PDS chunks 
@@
 are still used by other snapshots. 
-This is done approximately and quickly by comparing the fingerprints of deleted chunks with
-the fingerprint bloomer-filter summary of other live snapshots.
+This is done approximately and quickly by comparing the fingerprints of deleted snapshots with
+the fingerprint bloom-filter summary of other live snapshots.
 Since the number of live snapshots is limited for each VM (e.g. 10 in the Alibaba's production system), 
@@
 Since there are certain unused chunks which are not deleted during
-the approximated deletion, the leakage repair is conducted periodically.
+the approximate deletion, leakage repair is conducted periodically.
 In this phase we load the metadata of all containers from a VM snapshot store,
-mark if any chunk is used.  For unused chunks within this VM, such chunks are to be deleted.
+and mark all used chunks. Unmarked (and therefore unused) chunks within this VM can be safely deleted.
 This process is identical to the previously-developed mark-and-sweep techniques except that
-we only need to conduct a VM-specific mark-and-sweep  operation.
+we only need to conduct a VM-specific mark-and-sweep  operation, and only do that periodically.
 %We cannot simply repeat the phase 1 multiple times to reduce temporary storage leakage, because:
@@
 $\epsilon$ be the false-positive rate of the merged bloom filter. 
-$R$ be the number of runs using the approximate deletion before a full leak repair is conducted.
+$R$ be the number of runs using approximate deletion before a full leak repair is conducted.
 Then $ L= R * \epsilon * H.  $
@@
 When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
-only one full leak repair scheduled for every 12 days, which is sufficiently small to prevent the 
+only one full leak repair scheduled for every 12 days, which is sufficiently small to offset the 
 heavy I/O workload of the mark-sweep process.

### 2013-07-12 snapshot_system/con.tex
Revisions to evaluation section

@@
 that each underlying file block is associated with one VM for most cases.
-by keeping most of the VM-FSB mappings 1:1 we isolate faults and improve overal fault tolerance.
+by keeping most of the FSBs only referenced by 1 VM, we isolate faults and improve overal fault tolerance.
 Our solution accomplishes reasonable and competitive deduplication efficiency while
@@
 Our analysis shows that  this VM centric scheme 
-can  provide  better fault tolerance that VM-oblivious global deduplication schemes
-while using a small amount of computing and storage resource.
+can  provide  better fault tolerance than VM-oblivious global deduplication schemes
+while using a small amount of computing and storage resources.
 

### 2013-07-12 snapshot_system/eval1.tex
Revisions to evaluation section

@@
 
-We have implemented and evaluated a prototype of our VO scheme on a Linux cluster
-of 8-core AMD FX-8120 at 3.1 GHz with 16 GB RAM. 
+We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
+8-core AMD FX-8120 at 3.1 GHz with 16 GB RAM. 
 Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
 Each machine  is equipped with a 
-a distributed file system (QFS) running in the cluster manages six 3TB disks
+a distributed file system (QFS) and overall the cluster manages six 3TB disks
 with default replication degree set to 3. The PDS replication is set to 5.
 Objectives of our evaluation are:
-1) Study the deduplicate detection and removal effectiveness of the VC approach and compare with an alternative VO
+1) Study the duplicate detection and removal effectiveness of the VC approach and compare with an alternative VO
 design.
@@
 a VO approach  using stateless routing with binning (SRB).
-SRB executes a distributed deduplication by routeing a data chunk to a machine~\cite{ParallelDataDomain}
-using  the chunk hashing function discussed in \cite{??}. Within such a machine, the data chunk is compared with
-a local index.
+SRB executes a distributed deduplication by routing a data chunk to a machine~\cite{ParallelDataDomain}
+using  the chunk hashing function discussed in \cite{??}. Within such a machine,
+the data chunk is compared with a local index. This minHash paritioning
+algorithm helps provide a greater degree of parallelism, but ignores the
+significant amount of parallelism within a single VM.
 
@@
 including OS and user data disk.
-Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
+For our system each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
 variable-sized content blocks  with an average size of 4KB.
@@
 The seek cost of each random IO request in our test machines is about  10 milliseconds.
-The average I/O usage of local storage is controlled about 50MB/second for backup 
+The average I/O usage of local storage is controlled to about 50MB/second for backup 
 in the presence of other I/O jobs. Noted that a typical 1U server can host
@@
 block-wise full deduplication removes about additional 74.5\% of duplicates.
-The final content copied to the backup storage is reduced by 94.4\% in total.
+The final content copied to the backup storage is reduced by 94.4\%
+\emph{Is this correct? Elsewhere we have used 92\% based on results from
+our srb-vc comparison graph} in total.
 }
@@
 Popularity of data blocks are collected through global counting 
-and the top 1\% will fall into PDS, as discussed in Section~\ref{sect:crossVM}.
+and the top 1-2\% will fall into the PDS, as discussed in Section~\ref{sect:crossVM}.
 %variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
@@
 
-Since it's impossible to perform large scale analysis without affecting the VM performance,
+Since it's impossible to perform large scale analysis without affecting production VM performance,
 we sampled two data sets from real user VMs to measure the effectiveness of our deduplication scheme.
@@
 5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
-The overall data size for this 700 full snapshots is 17.6 TB.
+The overall data size for these 700 full snapshots is 17.6 TB.
 
@@
 With $\sigma=2\%$, the deduplication efficiency can reach over 90\% 
-while with $\sigma=4\%$, the deduplication efficiency can reach over 92\%. 
+while with $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
 The loss of efficiency in VC is caused by the restriction of the total physical memory available
@@
 accesses  the PDS which is on distributed shared memory.  
-SRB spends  slighter more time in  reading data and update because it also updates the on-disk
+SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
 local meta data index.
-Overall speaking,  VC is faster than SRB while data reading dominates the processing time. 
+Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.
 %all lookups are essentially random and caching will be largely innefective).
@@
 
-Figure~\ref{fig:single_vm_backup} reports the average bacup time for a VM with VC with a varying number
-of PDS size.
-Again it shows that data reading dominates the backup process, our deduplication
+Figure~\ref{fig:single_vm_backup} reports the average bacup time for a VM in VC with a varying PDS size.
+Again it shows that data reading dominates the backup process; our deduplication
 procedure only takes a small fraction of the total backup time. 
-The change of $\delta$ does not significantly affects the overall time and
-PDS lookup takes a small amount of time.
+The change of $\sigma$ does not significantly affect the overall backup speed as
+PDS lookup takes only a small amount of time.
 %Larger memory permits us to
@@
 the backup procedure in parallel.
-To begin, on each node we let 4 VMs writing snapshot concurrently, and gradually 
+To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
 increase number of VMs to 12 to saturate our system capability. We observed 
@@
 which is far beyond our QFS file system capability. The reason behind it is our efficient
-deduplication architecture and compression greatly reduce the amount of data that need to be written to
-the file system. The main bottleneck here is our QFS only manages one disk per node, 
-making it inefficient to utilize the benefits of parallel disk access. We expect our architecture can
-perform even better in production clusters which often have more than ten disks on each node.
+deduplication architecture and compression which greatly reduce the amount of data that needs to be written to
+the file system. The main bottleneck here is that our QFS installation only
+manages one disk per node, which prevents it from fully utilizing the the
+benefits of parallel disk access. We expect our architecture can
+perform even better in production clusters, which often have ten or more disks on each node.
 

### 2013-07-16 snapshot_system/arch.tex
change CDS to PDs

@@
 
-It contains an append store client which provides facilities to manage stored snapshot data, and a CDS client to support CDS index access.
+It contains an append store client which provides facilities to manage stored snapshot data, and a PDS client to support PDS index access.
 We will further discuss our deduplication scheme in section\ref{sect:dedupe}.
@@
 3) an append store client to store  and access snapshot data,
-and 4)  a CDS client to support CDS index access. We will further discuss our deduplication scheme 
+and 4)  a PDS client to support PDS index access. We will further discuss our deduplication scheme 
 in Section~\ref{sect:dedupe}.
@@
 %ASID (discuss in Section \ref{sect:append}) or an offset of an additional flag indicates
-%the location of CDS data.
+%the location of PDS data.
 
@@
 
-{\bf Impact of CDS deduplication.}
+{\bf Impact of PDS deduplication.}
 Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the
@@
 with the exponent $\alpha$ between 0.65 ~ 0.70.
-As a result, it can be proved that deduplication efficiency of CDS index is scalable:
+As a result, it can be proved that deduplication efficiency of PDS index is scalable:
 
@@
 \end{equation}
-So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
+So the cumulative distribution function for a PDS holding top $S_c$ fingerprints
 of global index with size $S_g$ is:
@@
 %[Describe the dedup efficiency model in detail]
-Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size.
+Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by PDS, $D$ be the amount of data on each node, and $B$ be the average block size.
 Then $S_c$ and $S_g$ can be expressed as:
@@
 \end{equation}
-Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.
+Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of PDS is only controlled by the its memory usage.
 

### 2013-07-16 snapshot_system/result.tex
change CDS to PDs

@@
 evaulate the system performance on the second snapshot backup. We repeat such procedure
-under different CDS memory usage settings, the results of backup time break down are shown in
+under different PDS memory usage settings, the results of backup time break down are shown in
 Figure~\ref{fig:single_vm_backup}.
@@
 procedure only takes a tiny fraction of the total backup time. Larger memory permits us to
-use larger CDS index to cover more of global index, as a result the amount of data to be writen
+use larger PDS index to cover more of global index, as a result the amount of data to be writen
 is reduced and so do the writing time.
@@
 (percent of duplicate chunks which are deduped) of SRB and VC with several
-different CDS sizes. From the graph you can see that VC provides similar or
+different PDS sizes. From the graph you can see that VC provides similar or
 better deduplication efficiency in all cases. In Figure~\ref{fig:srb_vs_vc} you
@@
 charts in the paper until we decide? If we use the bar charts some text will
-have to be changed. We could also add each of the CDS sizes to the bar chart
+have to be changed. We could also add each of the PDS sizes to the bar chart
 and have 4 bars instead of 2.}
@@
     \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% PDS.}
   \label{fig-exbin-efficiency1}
@@
     \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% PDS.}
   \label{fig-exbin-efficiency2}

### 2013-07-16 snapshot_system/result.tex
Added graph for modified vc with minhash efficiency.

--- 2013-07-11 snapshot_system/result.tex
@@
 
+%version of above graph using minhash algorithm
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Ex-Binning Efficiency},
+            cycle list name=mline,
+            xlabel={Number of VMs added},
+            ylabel={Dedup. Efficiency (\%)},
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            mark options=solid,
+            legend pos=south west,
+            %legend columns=2,
+            %legend style={
+            %    at={(0.5,-0.2)},
+            %anchor=north},
+            ]
+            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
+            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$),VC (No PDS)};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Deduplication Efficiency
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
+    Stateless Routing with Binning and VC. VC uses the minhash algorithm for Level-2.}
+  \label{fig-exbin-efficiency-graph2}
+\end{figure}
+
 \begin{figure}[htbp]

### 2013-07-16 snapshot_system/cds.tex

@@
-\section{CDS Analysis}
-[Purpose of using CDS]
-CDS is a small percentage of the global data index that we into DHT as a shared index. 
-With CDS as as a public data resource, each VM's snapshot backup has no need to 
-store its own copies for data that already exist in CDS, instead they can just
+\section{PDS Analysis}
+[Purpose of using PDS]
+PDS is a small percentage of the global data index that we into DHT as a shared index. 
+With PDS as as a public data resource, each VM's snapshot backup has no need to 
+store its own copies for data that already exist in PDS, instead they can just
 store a reference. 
-We expect CDS to contain most of the data related to operating system, software and libraries.
+We expect PDS to contain most of the data related to operating system, software and libraries.
 
 [What's the benifits]
-Using CDS as a common data source brings us several benefits: 
-First, the data we collect into CDS are commonly used in many VMs, 
-thus the CDS index, a special subset of global index, has very high deduplication efficency.
-Second, in our architecture the CDS data are the only data that can be shared between different VMs,
-by carefully control the replication degree of CDS data, we could improve the fault-tolerancy
-in such a data sharing environment. Finally, the CDS index is small enough to be put into a 
+Using PDS as a common data source brings us several benefits: 
+First, the data we collect into PDS are commonly used in many VMs, 
+thus the PDS index, a special subset of global index, has very high deduplication efficency.
+Second, in our architecture the PDS data are the only data that can be shared between different VMs,
+by carefully control the replication degree of PDS data, we could improve the fault-tolerancy
+in such a data sharing environment. Finally, the PDS index is small enough to be put into a 
 in-memory DHT, thus it avoids the excess memory usage of global index 
@@
 
-[Describe how CDS is generated]
+[Describe how PDS is generated]
 
-[Explain why CDS scales effectively as data grow]
+[Explain why PDS scales effectively as data grow]
 Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the 
@@
 with the exponent $\alpha$ between 0.65 ~ 0.70. 
-As a result, it can be proved that deduplication efficiency of CDS index is scalable:
+As a result, it can be proved that deduplication efficiency of PDS index is scalable:
 
 [Describe the dedup efficiency model in detail]
-Let $S_c$ be the total number of FPs in CDS, $S_g$ be the total number of FPs in global index, $F$ be the size of a FP, $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size.
+Let $S_c$ be the total number of FPs in PDS, $S_g$ be the total number of FPs in global index, $F$ be the size of a FP, $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by PDS, $D$ be the amount of data on each node, and $B$ be the average block size.
 The deduplication efficiency will be:
@@
 
-Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.
+Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of PDS is only controlled by the its memory usage.

### 2013-07-16 snapshot_system/design.tex

@@
 \begin{enumerate}
-\item {\em CDS. parallelism, localized}
+\item {\em PDS. parallelism, localized}
 We designed a highly efficient global deduplication scheme using common data between VMs as the primary
@@
 on some data can break many VMs' snapshots. We avoid such all-to-all data dependency by restricting
-the cross VM data sharing with the CDS. By taking extra care of protecting CDS data, 
+the cross VM data sharing with the PDS. By taking extra care of protecting PDS data, 
 the overall degree of fault tolerancy is guaranteed.
@@
 % The cross-VM deduplication is conducted by the broker to access 
-% a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
+% a common data set (PDS) (will discuss in Section~\ref{sect:crossVM},
 % whose block hash index is stored in a distributed memory cache. 
@@
 % \subsection{Block Storage Device}
-\subsection{CDS}
+\subsection{PDS}
 Although locality based data reduction can remove most of the inner-VM duplications,
@@
 Without eliminating the data duplication between VM snapshot backups, storage space is severely wasted when the number of VMs increases.
-To address this problem, we developed a technique called \emph{Common Data Set (CDS)} to eliminate data duplication for all three situations above. 
-CDS is a public data library that shared by all VM snapshot backups in the cluster, 
+To address this problem, we developed a technique called \emph{Common Data Set (PDS)} to eliminate data duplication for all three situations above. 
+PDS is a public data library that shared by all VM snapshot backups in the cluster, 
 which consists of the most popular data blocks in VM snapshot backups. It is generated, 
@@
 
-\subsection{CDS Size V.S. Coverage}
-As a shared data library, we expect CDS to collect almost all the system related data, the most popular user-generated data and the zero-filled data block.
-With CDS as a public data reference, each VM's snapshot backup has no need to store its own copies for data that can be found in CDS, instead they can just
+\subsection{PDS Size V.S. Coverage}
+As a shared data library, we expect PDS to collect almost all the system related data, the most popular user-generated data and the zero-filled data block.
+With PDS as a public data reference, each VM's snapshot backup has no need to store its own copies for data that can be found in PDS, instead they can just
 store a reference.
 
-The more data we put into CDS, the closer we come to complete deduplication. But in reality we are facing a list of restrictions such like [blabla].
-We borrowed the idea of web caching[refs here] to analysis the size of CDS vesus its effectiveness on data reduction.
+The more data we put into PDS, the closer we come to complete deduplication. But in reality we are facing a list of restrictions such like [blabla].
+We borrowed the idea of web caching[refs here] to analysis the size of PDS vesus its effectiveness on data reduction.
 
@@
 and let $D$ denotes the average size of one VM's snapshot backups (after level 1 and 2 reduction, which is near 40 GB in our production environment).
-And let $C_0$, $C_s$ and $C_u$ denote the size of zero-filled block, system-related data and user-generated data in CDS,
-then the total size of CDS is represented by $C=C_0+C_s+C_u$.
+And let $C_0$, $C_s$ and $C_u$ denote the size of zero-filled block, system-related data and user-generated data in PDS,
+then the total size of PDS is represented by $C=C_0+C_s+C_u$.
 We let $S_0$, $S_s$ and $S_u$ denote the corresponding data coverage ratio (with respect to $D$) by $C_0$, $C_s$ and $C_u$,
@@
 
-Zero-filled block at maximum length is the first item we need to put into CDS. This is the one and only special data block, 
-and because CDS only stores unique data blocks, $C_0$ is almost equal to 0. In practice we found zero-filled blocks account
+Zero-filled block at maximum length is the first item we need to put into PDS. This is the one and only special data block, 
+and because PDS only stores unique data blocks, $C_0$ is almost equal to 0. In practice we found zero-filled blocks account
 for near 20\% of total data, so $S_0$ is 20\%.
 
-The rarely modified system-related data are the second to be added to CDS. We have thousands of VMs in each cluster, 
+The rarely modified system-related data are the second to be added to PDS. We have thousands of VMs in each cluster, 
 but all these VMs fall into only a few OS types, using a limited selection of software, therefore data duplication in this category
@@
 , so $T_u=D_u/2$.
-Since we collect the most popular user-generated data into CDS, the coverage of CDS on user-generated data
+Since we collect the most popular user-generated data into PDS, the coverage of PDS on user-generated data
 is $(C_u/T_u)^{1-\alpha}$.
 
-The following table lists CDS coverage on user-generated data under different $\alpha$ and $C_u/T_u$.
+The following table lists PDS coverage on user-generated data under different $\alpha$ and $C_u/T_u$.
 
@@
 It's obviously that at least 30\% of user-generated data can be reduced in this way, using about 0.02 of $T_u$, or 0.01 of $D_u$.
-The size of user-generated data in CDS would be 0.006$D$, with coverage $S_u=0.18D$.
+The size of user-generated data in PDS would be 0.006$D$, with coverage $S_u=0.18D$.
 
-Thus the estimation of CDS coverage is $S=S_0+S_s+S_u=0.58$, with the size of CDS to be no more than $(200 + 0.006*D*N)$ GB.
-In a VM cluster of 100 machines, with 25 VMs on each physical machine, the size of CDS is 800 GB in total, or 8 GB per machine.
-The total size of CDS index would be 8 GB, which will cost 80 MB memory on each machine.
+Thus the estimation of PDS coverage is $S=S_0+S_s+S_u=0.58$, with the size of PDS to be no more than $(200 + 0.006*D*N)$ GB.
+In a VM cluster of 100 machines, with 25 VMs on each physical machine, the size of PDS is 800 GB in total, or 8 GB per machine.
+The total size of PDS index would be 8 GB, which will cost 80 MB memory on each machine.
 

### 2013-07-17 snapshot_system/eval1.tex

@@
 
+%version of above graph using minhash algorithm
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Ex-Binning Efficiency},
+            cycle list name=mline,
+            xlabel={Number of VMs added},
+            ylabel={Dedup. Efficiency (\%)},
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            mark options=solid,
+            legend pos=south west,
+            %legend columns=2,
+            %legend style={
+            %    at={(0.5,-0.2)},
+            %anchor=north},
+            ]
+            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
+            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$),VC (No PDS)};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Deduplication Efficiency
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
+    Stateless Routing with Binning and VC. VC uses the minhash algorithm for Level-2.}
+  \label{fig-exbin-efficiency-graph2}
+\end{figure}
+
 %\begin{figure}

### 2013-07-24 snapshot_system/eval1.tex
update experiments

@@
 
+\begin{table}
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Tasks & CPU & Mem (MB) & Disk (MB/s) & Network \\ \hline
+    4                      & 63\% & 164 & 84     &    \\ \hline
+    6                      & 77\% & 201  & 88.5   &     \\ \hline
+    8                      & 82\% & 237   & 89.2   &    \\ \hline
+    10                      & 85\% & 273   & 90.4   &    \\ \hline
+    12                      & 91\% & 312    & 91.5   &   \\ \hline
+    \end{tabular}
+\caption{Resource usage under concurrent backup tasks}
+\label{tab:resource_usage}
+\end{table}
+
 \subsection{Processing Time and Throughput}
@@
 % \end{table}
+\subsection{Approximate Deletion}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3in]{figures/leakage}
+    \caption{Accumulated storage leakage by approximate snapshot deletions}
+    \label{fig:leakage}
+\end{figure}
+
+Figure\ref{fig:leakage} shows the average accumulated storage leakage resulted by daily
+approximate deletions among all VMs. We see the storage leakage ratio is satisfactory: 
+after 9 snapshot approximate deletions, there is only 1MB space leaked over every 10GB
+of stored data. In addition, the leakage ratio grows linearly with the number of approximate deletions
+as our analysis, which gives us a reliable prediction of when to trigger a accurate mark-and-sweep delete operation.
 

### 2013-07-25 snapshot_system/challenge.tex
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.
change CDS to PDs
reorgnaize

@@
-\section{Design Consideration and Options}
-\label{sect:options}
+%\section{Design Consideration and Options}
+%\label{sect:options}
 
-As discussed earlier, collocating the backup service on the existing
+\section{Background and Design Considerations}
+\label{sect:option}
+
+%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
+At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
+represented as virtual disk image files in the host operating system.
+For VM snapshot backup, file-level semantics are normally not provided.
+Snapshot operations take place at the virtual device driver level, which
+means no fine-grained file system metadata can be used to determine the changed data. 
+Backup systems have been developed to use content fingerprints to identify duplicate
+content~\cite{venti02,Rhea2008}.  
+As discussed earlier, collocating a backup service on the existing
 cloud cluster avoids the extra cost to acquire a dedicated backup facility
@@
     \centering
-    \includegraphics[width=3in]{images/colocated-arch.pdf}
+    \includegraphics[width=3in]{images/colocated-arch}
     \caption{Collocated VM Backup System.}
@@
 \end{figure}
+
+%Only raw access information at disk block level are provided. 
+%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
+%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
+%only a very small slice of cluster resource can be used for the backup purpose.
+
+%The previous work for storage backup has extensively studied  data deduplication techniques that
+%can eliminate redundancy globally among different files from different users.
+%Offline deduplication is 
+%used in ~\cite{EMC,NetAppOffline} to remove previously written duplicates during idle time.
+%,NGmiddleware2011}.
+%Today's commercial data backup systems (e.g. from EMC and NetApp)
+%\cite{emc_avamar}\cite{datadomain_whitepaper}
+%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
+Since it is expensive to compares a large number of chunk signatures for deduplication,
+several techniques have been proposed to speedup searching of duplicate
+fingerprints. For example, the data domain method ~\cite{bottleneck08} 
+uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
+accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
+%As discussed in Section~\ref{sect:intro},
+%there is no dedicated resource for deduplication in our targeted setting and low memory usage
+% is required so that the resource impact to other cloud services is minimized.
+%NG et al.~\cite{ NGmiddleware2011}  use
+%a related filtering technique for integrating deduplication in Linux  file system and the memory
+%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
+%Lillibridge et al.~\cite{sparseindex09} break list of chunks
+%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
+%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
+%These are segments that share many chunk IDs with the incoming segment with high probability.
+The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
+%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
+to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
+%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
+%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
+%lookup  
+%In comparison, this paper focuses on  full deduplication without approximation.
+%We also take advantages of the fact that in a VM cloud environment,
+%the virtual device driver can easily keep track if  large data
+%segments have been modified using dirty bits and such information can avoid sending
+%unmodified data segments for deduplication, which significantly saves cost.
+
+Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
+All of the above approaches have focused on optimization of deduplication
+efficiency, and none of them have considered the impact
+of deduplication on fault tolerance in the cluster-based environment that we have considered
+in this paper.
+%We will describe the motivation of using the cluster-based   approach
+%for running the backup service and then present our solution  with fault isolation.
+%In our work, the foucs 
+%there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
+%in our context, finishing the backup of required VM images within a reasonable time window is more
+%important than optimizing individual VM block  backup requests.
 
@@
 
-We discuss the design considerations as follows. 
+Our key design consideration is VM dependence minimization during deduplication and file block management.
 \begin{itemize}
-\item {\em Deduplication localization, sharing minimization, and fault tolerance.}
-
+\item {\em Deduplication localization.}
 %Previous work in deduplication~\cite{extreme_binning09,sparseindex09} has
@@
 %One important issue not considered in the previous work is how 
-Because a data chunk is compared with signatures collected from other VMs during
-the deduplication process, only one copy of duplicates is stored in the backup storage
-and this artificially creates data dependency among different VM users. 
-Content sharing via deduplication affects fault isolation since machine failures happen at daily 
-basis in a large-scale cloud and
+Because a data chunk is compared with signatures collected from all VMs during
+the deduplication process, only one copy of duplicates is stored in the storage,
+this artificially creates data dependency among different VM users. 
+Content sharing via deduplication affects fault isolation since machine failures happen periodically 
+in a large-scale cloud and
 %failure of a shared block affects many VMs.
@@
 Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
-discourage. 
-Another disadvantage of sharing is that it complicates snapshot deletion.
+discouraged. 
+Another disadvantage of sharing is that it complicates snapshot deletion, 
+which  occurs frequently when snapshots expire regularly and leads a cost concern. 
 The mark-sweep approach~\cite{mark-sweep} is effective for deletion, and its main cost
 is to count if a data chunk is still shared by other snapshots.
-Thus our goal is to localize deduplication and minimize sharing, while we seek for 
-a tradeoff since there are a significant number of duplicates cross VMs.
+Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
+deduplication efficiency, and  can faciltate parallel execition of snaptshot operations.
+Thus we seek for a tradeoff.
 
@@
 %when users access snapshots in a recovery process. 
-\item{\bf Packaging  data chunks as file system blocks.}
-Since the file block size in the Hadoop and GFS is uniform and large with 64MB as a default setting,
-the content chunk in a deduplication system is of nonuniform size with 4KB or 8KB on average.
-We need to build an intermediate layer that supports large snapshot writing with append operations
-and infrequent snapshot access.
-Packaging that maps data chunks to file system blocks can create data dependence among VMs
-since a file block can be shared even more VMs.
+\item{\bf Management of file system blocks.}
+The file block size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
+ a data chunk in a deduplication service is of a nonuniform size with 4KB or 8KB on average.
+%We need to build an intermediate layer that supports large snapshot writing with append operations
+%and infrequent snapshot access.
+Packaging data chunks to a file system block can create more data dependence among VMs
+since a file block can be shared with even more VMs.
 Thus we need to consider a minimum association of a fie system block to VMs in the packaging process.
@@
 %\item {\em Requirement for backup throughput and low computing resource usage}.
+Another consideration is the computing cost of deduplication.
 Because of collocation of this snapshot service with other existing cloud services, 
@@
 %because of its lower priority.
-The key usage of resource for backup is memory for storing and comparing the fingerprints. 
-We will consider the approximation techniques with less memory consumption
-studied in~\cite{extreme_binning09,Guo2011} along with the fault isolation consideration discussed below. 
+The key resource for signature comparison  is memory for storing the fingerprints. 
+We will consider the approximation techniques with less memory consumption along 
+with the fault isolation consideration discussed below. 
 %A snapshot backup service shall not compete cpu, memory, or I/O bandwidth with VMs. 
@@
 
-A deduplication scheme compares the fingerprints of the current snapshot
-with its parent snapshot and also other snapshots in the entire cloud without consideration of .
+We call the classical deduplication approach as   VM-oblivious (VO)
+because they compare fingerprints of snapshots without consideration of VM.
+With the above  considerations in mind, we study a 
+VM-centric approach (called VC)
+for a collocated backup service with resource usage friendly
+to the existing applications.  
+%We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, and then present
+%an architecture and implementation design with deletion support.
 %The traditional approach compares all fingerprints and
 %stores one copy for all of a chunk's duplicates.
-We call this as  the VM-oblivious (VO) approach.
-In designing and selecting a duplication algorithm, we have considered the following options.
+In designing a VC duplication algorithm, we have considered and adopted some of
+the following previously-developed techniques.
 \begin{itemize}
@@
 changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
-Active snapshots will contain all the information needed to restore the virtual disk
-and when deleting a snapshot, data referenced by other snapshots are removed.
-While full signature comparison can deliver additional reduction~\cite{Guo2011,Dong,ExtremeBining},
-content change detection falls into a VM-centric approach since deduplication is localizable. 
-We are seeking for additional optimization to improve duplication efficiency and design the 
-association of data chunks with the underlying file blocks so that
-file block sharing among VMs is minimized.
-\item {\bf sampled Index}.
-One alternative approach to reducing the use of memory space is 
-to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
-An evaluation with our test data shows that using a sampled index can achieve a high
-deduplication efficiency with a single machine setup.  
-One key problem is that the algorithm is VM oblivious and not easy to be adopted for VM-centric.
-Another problem is  to design a distributed version 
-in deduplicating large bodies of data. 
-%The algorithm stores the sampled index in memory, which is required for high
-%throughput to avoid the disk-bottleneck problem - since the index itself has no
-%locality information, lookups are essentially random, so the index must be
-%somehow optimized to prevent excessive disk seeking (the sampling algorithm does
-%this by storing the index in memory). 
-To use a distributed memory version of the sampled index, every deduplicate request
-may access a remote machine for index lookup,  which  incurs a significant overhead.
-
-Another possibility is to use this approach partially  in our VM centric solution by indexing
-the most popular data chunks. For a small set of popular data chunks, the prefetching strategy
-used in the sampled index will not work well because the spatial locality is limited among popular 
-data chunks. In our test data,  on average the number of consecutive data chunks is 7, which is too small
-to be effective for index sampling.
-
-%To distribute this sampled index, every  each machine would
-%either require a complete copy of the index which would have a prohibitive cost in
-%memory, or something like memcached must be used, which leaves the same problem
-%as the disk bottleneck with every index check potentially using the network.
-%The difficulty in storing extremely large bodies of data
-%is related, as once 1PB is stored in the system, assuming a sampling rate of 
-%1/101 with 22 byte index entires, 55GB of (in memory) index are required.
-
-%Our solution uses more total memory (??how much??), but is more scalable both in
-%terms of capactity and distributing the deduplication. The only part of our
-%algorithm which requires significant network traffic is the CDS deduplication,
-%but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
-%so is only done for a small percent of blocks (?? 5-10\% ??).
-
+Such a scheme  is  VM-centric since deduplication is localized. 
+%Active snapshots will contain all the information needed to restore the virtual disk
+%and when deleting a snapshot, data referenced by other snapshots are removed.
+We are seeking for a tradeoff since 
+cross-VM  signature comparison can deliver additional reduction~\cite{Guo2011,Dong,ExtremeBining}.
+%We are seeking for additional optimization to improve duplication efficiency and design the 
+%association of data chunks with the underlying file blocks so that
+%file block sharing among VMs is minimized.
 \item {\bf Stateless  Data Routing}.
-Another approach for duplicate comparison  is to use a content-based hash
+One approach for scalable duplicate comparison is to use a content-based hash
 partitioning algorithm called stateless data routing~\cite{Dong20??}
-that divides the deduplication work with an approximation, which 
-is similar to Exreme Binning\cite{extreme_binning09}. 
-Again such an approach is VM-oblivious while each request does incur a network routing latency, and then
-additional overhead for a bloomer filter based  disk lookup~\cite{Dong20??} or 
-a disk index access~\cite{extreme_binning09}.
+that divides the deduplication work with an approximation. This work 
+is similar to Exreme Binning\cite{extreme_binning09} and 
+each request is routed  to a machine which holds
+a bloomer filter  or can fetch on-disk index for additional comparison.
+While this approach is VM-oblivious, we can have adopted some of ideas to build
+bins in a VM to faciliate VM-specific local search.
 
@@
 %to users of the VMs, and/or reduce the possible deduplication throughput.
+\item {\bf Sampled Index}.
+One effective approach that reduces memory usage is 
+to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
+%An evaluation with our test data shows that using a sampled index can achieve a high
+%deduplication efficiency with a single machine setup.  
+The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
+%The algorithm stores the sampled index in memory, which is required for high
+%throughput to avoid the disk-bottleneck problem - since the index itself has no
+%locality information, lookups are essentially random, so the index must be
+%somehow optimized to prevent excessive disk seeking (the sampling algorithm does
+%this by storing the index in memory). 
+To use a distributed memory version of the sampled index, every deduplicate request
+may access a remote machine for index lookup and the overall overhead of latency latency for all requests
+can be significant.
+
+%Another possibility is to use this approach partially  in our VM centric solution by indexing
+%the most popular data chunks. For a small set of popular data chunks, the prefetching strategy
+%used in the sampled index will not work well because the spatial locality is limited among popular 
+%data chunks. In our test data,  on average the number of consecutive data chunks is 7, which is too small
+%to be effective for index sampling.
+
+%To distribute this sampled index, every  each machine would
+%either require a complete copy of the index which would have a prohibitive cost in
+%memory, or something like memcached must be used, which leaves the same problem
+%as the disk bottleneck with every index check potentially using the network.
+%The difficulty in storing extremely large bodies of data
+%is related, as once 1PB is stored in the system, assuming a sampling rate of 
+%1/101 with 22 byte index entires, 55GB of (in memory) index are required.
+
+%Our solution uses more total memory (??how much??), but is more scalable both in
+%terms of capactity and distributing the deduplication. The only part of our
+%algorithm which requires significant network traffic is the PDS deduplication,
+%but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
+%so is only done for a small percent of blocks (?? 5-10\% ??).
 \end{itemize}
 
-With these considerations in mind, we study a 
-VM-centric approach (called VC)
-for a backup service co-hosted   in the existing set of machines and resource usage is friendly
-to the existing applications.  
-We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, and then present
+%With these considerations in mind, we study a 
+%VM-centric approach (called VC)
+%for a backup service co-hosted   in the existing set of machines and resource usage is friendly
+%to the existing applications.  
+We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, 
+and then present
 an architecture and implementation design with deletion support.

### 2013-07-25 snapshot_system/snapshot.tex
reorgnaize

@@
 %We call this as  the VM-oblivious (VO) approach.
-Our VC design has the following objectives:
+Our VC design has the following  objectives: 1)  localizing deduplication while identifying a decent amount of
+duplicates among VMs to maintain a competitive deduplication efficiency and simplify snapshot management;
+2) Minimizing the number of file system blocks shared among VMs and adding extra replicas for shared blocks.
+
+\comments{
 \begin{itemize}
-
 \item
@@
 \item
-2) Maintain a competitive deduplication effiency while being resource-friendly to other
+2) Maintain a competitive deduplication efficiency while being resource-friendly to other
 existing cloud services.
@@
 \item
-3)  Mininimize the number of data chunks shared among VMs and add extra replicas to incrase
-fault resilience for such data chunks.
 \end{itemize}
-
-\subsection{Key VC Strategies}
+}
+\subsection{Key VM-centric  Strategies}
 \label{sect:vc-strategies}
@@
 \begin{itemize}
-\item \textbf{Local duplicate search.}
-We start with the standard dirty bit approach in a coarse grain segment level
-and use the  Xen virtual device driver to implement a feature called ``changed block tracking''
-for the storage device and the dirty bit setting is maintained in a coarse grain level we call it a segment.
-In our implementation, the segment size is 2MB. 
+\item \textbf{Local duplicate search with VM-specific bining.}
+We start with the standard dirty bit approach in a coarse grain segment level.
+In our implementation with Xen at an Alibaba platform, the segment size is 2MB
+and  the device driver is extended to support  changed block tracking. 
 Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
 and cannot afford a small segment  size.
-
-It should be noted that dirtybit tracking is supported or can be easily implemented in many 
-major virtualization solution vendors. 
+%Xen doesn't directly support it, However, their open-source 
+%architecture allows anyone to extend 
+%and use the  Xen virtual device driver to implement a feature called ``changed block tracking''
+%for the storage device and the dirty bit setting is maintained in a coarse grain level we call it a segment.
+It should be noted that dirtybit tracking is supported or can be easily implemented in 
+major virtualization solution vendors. For example,
 %(VMware, Xen, Microsoft).  
 %VMware support it directly; 
-The VMWare hypervisor has an API to let external backup application know 
-the changed areas since last backup. Xen doesn't directly support it, However, their open-source 
-architecture allows anyone to extend the device driver, thus enabling changed block tracking. 
-We implement dirty bit tracking this way in Alibaba's platform.  
+the VMWare hypervisor has an API to let external backup applications know 
+the changed areas since last backup. 
+%We implement dirty bit tracking this way in Alibaba's platform.  
 The Microsoft SDK provides an API that allows external applications to monitor 
-the VM's I/O traffic, therefore changed block tracking can be implemented externally.
+the VM's I/O traffic and implement  the changed block tracking feature.
 
@@
 Once the popularity of all data chunks is collected, the system only maintains the top $k$
-most popular chunk signatures in a distribued shared memory.  
+most popular chunk signatures in a distributed shared memory.  
 %For cross-VM comparison, we only store  top $k$ items and $k$ is chosen to be relatively small.
@@
 \end{itemize}
+
+We have not  adopted the  sampled index~\cite{Guo2011} 
+for  popular data chunks and  this is because sampling requires the use of prefetching to be effective.
+%For a small set of popular data chunks, the prefetching strategy
+%used In the sampled index will not work well because 
+For the data sets we have tested, the spatial locality is limited among popular
+data chunks and  on average the number of consecutive data chunks is 7 among popular chinks, which is not sufficient.
+%to be effective for index sampling.
 
@@
 %\subsubsection{Impact of PDS deduplication}
-The analysis is based on the charactristics  of the VM snapshot traces
+The analysis is based on the characteristics  of the VM snapshot traces
 studied from  Alibaba's production user data.
@@
 Figure~\ref{fig:cds-coverage} shows measured PDS coverage in our 35 VM dataset.
-You can see from the graph that the coverage actually increases as the datasize
-increases, which indicates that $\alpha$ increases with the datasize (a
+You can see from the graph that the coverage actually increases as the data size
+increases, which indicates that $\alpha$ increases with the data size (a
 fixed-$\alpha$ model would predict constant coverage). This makes the PDS even

### 2013-07-26 snapshot_system/arch.tex
update deletion

@@
 In a busy VM cluster, snapshot deletions are as frequent as snapshot creations.
-The VM-centric snapshot storage design simplifies the deletion process since we need to locate unreferenced chunks within each VM to free up space when deleting a snapshot.
+However, data deduplication complicates the deletion process because space saving relies on the sharing of data,
+thus making it difficult to decide which chunks are safe to delete.
+In a traditional deduplication system, deletion often require looking at global scope to
+resolve the data dependency between logical backup entities and physical data chunks.
+Our VM-centric snapshot storage design simplifies the deletion process since 
+we only need to locate unreferenced chunks within each VM's snapshot store to free up space when deleting a snapshot.
 The PDS data chunks are commonly shared all VMs and we do not consider their reference
 counting during snapshot deletion.
-The selection of PDS data chunks   is updated periodically independent of snapshot deletion process.
+%The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
 
-While we can use the standard mark-sweep technique~\cite{mark-sweep}, 
-it takes significant time to conduct this process every time there is a snapshot deletion.
+While we can use the standard mark-and-sweep technique~\cite{mark-sweep}, 
+it still takes significant time to conduct this process every time there is a snapshot deletion.
 In the case of Alibaba, snapshot backup is conducted automatically and there are 
-about 10 snapshot stored for  every user. Then when there is
+about 10 snapshot stored for every user. When there is
 a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
@@
 Every time there is a new snapshot created,
-we compute a bloom-filter fingerprint summary for all non-PDS chunks used 
+we compute a bloom-filter as the summary of reference pointers for all non-PDS chunks used 
 in this snapshot.
@@
 the approximate deletion, leakage repair is conducted periodically.
-In this phase we load the metadata of all containers from a VM snapshot store,
-and mark all used chunks. Unmarked (and therefore unused) chunks within this VM can be safely deleted.
-This process is identical to the previously-developed mark-and-sweep techniques except that
-we only need to conduct a VM-specific mark-and-sweep  operation, and only do that periodically.
+In this phase we load the reference pointers of all chunks from a VM snapshot store as a table in memory,
+then scan through all the snapshots' segment recipes. For each reference pointer that is in use by a snapshot,
+we mark the corresponding entry in the table as in use. Finally those unmarked (and therefore unused) reference pointers in the
+table represent chunks that can be safely deleted.
+
+The cost of leak repair mainly come from holding a table of reference pointers and scan of all snapshots metadata.
+Consider each reference pointer consumes 8 bytes plus 1 byte as mark field, a VM that has 40GB backup data will
+need 90MB of memory to construct such a table. Also, scanning all snapshots metadata is many times slower comparing
+to the approximate deletion which only scans single snapshot's metadata.
+It's worth to mention that compare to previously-developed mark-and-sweep techniques, 
+our leak repair still has advantage because the scope of repair is restricted within single VM's snapshot 
+store due to our VM-specific design, and we only do it periodically.
 %We cannot simply repeat the phase 1 multiple times to reduce temporary storage leakage, because:
@@
 %{\bf Discussion}
-We estimate how often the leak repair needs to be conducted.
-Let $L$ be the amount of temporary storage leakage caused by our approximate snapshot deletion, 
-$H$ be the average size of non-PDS snapshot data that should be deleted. 
-$\epsilon$ be the false-positive rate of the merged bloom filter. 
-$R$ be the number of runs using approximate deletion before a full leak repair is conducted.
-Then $ L= R * \epsilon * H.  $
-
-When ratio $L/H$ exceed a threshold $\tau$, then:
+We now give a model to estimate the storage leakage and how often leak repair needs to be conducted.
+Assuming a VM always maintain $B$ snapshots in the backup, and it creates and deletes one snapshot
+everyday. Let $c$ be the total number of chunks brought by the initial backup, $c^'$ be the average
+number of chunks brought by a consequancial backup, then the total number of chunks in use $C$ is:
 \[
-\frac{L}{H} = R * \epsilon > \tau \Rightarrow R > \frac{\tau}{\epsilon}.
+C = c + (B-1)c^'
 \]
 
-For example, when $\epsilon = 0.01$ and $\tau=3$, 
-we would expect deletion phase-2 be triggered once for 
-every $T/P_{bl} = 300$ runs of fast deletion. 
+Let $m$ be the bloom filter size in bits, $k$ be the number of hash functions used by bloom filter,
+then bloom filter's false-positive rate $\epsilon$ is:
+\[
+\epsilon = (1-e^{\frac{kC}{m}})^k
+\]
+
+For each snapshot deletion, the amount of chunks need to be deleted is nearly identical to the number of
+newly add chunks $c^'$. However, some of chunks among them are not detected as unused in our approximation
+algorithm, thus forms the storage leakage. Let $R$ be the total number of runs of approximate deletion since
+last repair, the total leakage $L$ can be estimated as:
+\[
+L = Rc^'\epsilon
+\]
+
+When leakage ratio $L/C$ exceeds a pre-defined threshold $\tau$, we need to execute a repare:
+\[
+\frac{L}{C} = \frac{Rc^'\epsilon}{c+(B-1)c^'} > \tau \rightarrow R > \frac{\tau}{\epsilon}\frac{c + (B-1)c^'}{c^'}
+\]
+For example, when $\epsilon = 0.01$ and $\tau=0.1$, when the VM keeps 10 snapshots and each snapshot contains
+about 5\% of new data, then
+we would expect leak repair be triggered once for 
+every 290 runs of approximate deletion. 
 When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 

### 2013-07-26 snapshot_system/snapshot.tex
update deletion

--- 2013-07-11 snapshot_system/snapshot.tex
@@
 we conduct additional local inner-VM deduplication by comparing
-chunk signatures within a dirty segment from its parent snapshot. 
-We load the chunk fingerprints in the corresponding segment from the
-parent and perform fingerprint matching for further inner-VM deduplication.
+dirty segment's chunk fingerprints to similar segments from its parent snapshot. 
+For every segment, the minimum value of all its chunk fingerprints is computed during backup
+and is recorded in the snapshot recipe.
+So when we are processing a dirty segment,
+we can easily find similar segments from the
+parent snapshot recipe and load their segment recipes. Then we can perform fingerprint matching 
+against them
+for further inner-VM deduplication.
 The amount of memory for maintaining those fingerprints is small, as we only

### 2013-07-26 snapshot_system/intro.tex

@@
 We also consider the fact that after
-deduplication most data chunks are shared by several to many virtual machines.
+deduplication, most data chunks are shared by several to many virtual machines.
 Failure of shared data chunks can have a catastrophic effect and many
@@
 Another issue considered is that
-that deletion of old snapshots compete for computing resource as well. That is because data dependence created
-deletion of old snapshots competes for computing resources as well so deletion needs
-to be considered in system design. The additional complexity for deletions
-come from the dependencies created by multiple links to the same problem, so
-some solution is needed to determine blocks with no dependent snapshots after deletion.
-especially when  VMs can migrate around in the cloud.
+that deletion of old snapshots compete for computing resource as well. 
+%That is because data dependence created deletion of old snapshots competes for computing resources.
+% as well so deletion needs to be considered in system design. 
+sharing of data chunks among oby multiple VMs and their snapshots needs to be detected during
+snapshot   deletion and such dependenec complicates deletion operations. 
+%The additional complexity for deletions
+%come from the dependencies created by multiple links to the same problem, so
+%some solution is needed to determine blocks with no dependent snapshots after deletion.
+%especially when  VMs can migrate around in the cloud.
 
@@
 %Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data.
-We have developed a prototype system that runs a cluster of Linux machines with Xen.
-The backup storage uses a standard distributed file system with data replication and block packaging.
+We have developed a prototype system that runs a cluster of Linux machines with Xen and uses 
+a standard distributed file system for the backup storage. 
+% with data replication and block packaging.
 %and we allocate more  replicas for the commonly-shared  data 
@@
 The rest of this paper is organized as follows.
-Section~\ref{review} reviews background and related work.
-Section~\ref{sect:framework}  discusses the  design options for snapshot backup with a VM-centric approach. 
-Section~\ref{sect:model}  analyzes the benefit of our approach for fault isolation. 
+Section~\ref{option} reviews the background and discusses the  design options for snapshot backup 
+with a VM-centric approach. 
+Section~\ref{sect:model}  analyzes the tradeoff and benefit of our approach. 
 Section~\ref{sect:arch}  describes our system architecture and implementation details.

### 2013-07-26 batchdedup/eval.tex
Added initial memory comparison figures

--- 2013-05-04 hotstorage13/eval.tex
@@
 %the CPU usage is very small during the experiments. 
-We have performed a trace-driven study using  a 1323 VM dataset  collected from 100 
-Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE} and each
-of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
+We have performed a trace-driven study using  a 1323 VM dataset  collected from 
+%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
+a cloud cluster at Alibaba's Aliyun.
+% ~\cite{WeiZhangIEEE}.
+% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
 For each VM, the system keeps 10 automatically-backed snapshots in the storage while
@@
 
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Network Buffer Size},
+		xlabel={Total Network Memory Buffer (MB)},
+		ylabel={Backup Time},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		%legend pos=north west
+		]
+                \addplot table[x=mpibufmem,y=totaltime] {figures/mpibufmem.txt};
+                %\legend{Total Backup Time};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, write buffer 6.25MB, Read Buffer 128KB}
+  \label{fig:mpibuf-mem}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Read Buffer Size},
+		xlabel={Read Buffer Size (MB)},
+		ylabel={Backup Time},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		%legend pos=north west
+		]
+                \addplot table[x=rbufmem,y=totaltime] {figures/rbufmem.txt};
+                %\legend{Total Backup Time};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Backup time for verying amounts of memory allocated to disk read buffering. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffers 2.5MB, write buffer 6.25MB}
+  \label{fig:mpibuf-mem}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Write Buffer Size},
+		xlabel={Total Write Buffer Memory (MB)},
+		ylabel={Backup Time},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		%legend pos=north west
+		]
+                \addplot table[x=wbufmem,y=totaltime] {figures/wbufmem.txt};
+                %\legend{Total Backup Time};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffer memory 2.5MB, Read Buffer 128KB}
+  \label{fig:mpibuf-mem}
+\end{figure}
+
 Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
@@
 %Each scan takes about 1.4 hours.
-The overall processing time does not have a significant reduction as $M$ increases to 95MB.
+The overall processing time does not have a significant reduction as $M$ increases to 190MB.
 The aggregated deduplication throughput is  about 8.76GB per second,

### 2013-07-26 batchdedup/main.tex
Added initial memory comparison figures

--- 2013-05-07 hotstorage13/main.tex
@@
 %\setlength{\parskip}{1ex}
+
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.7}
+\DeclareGraphicsExtensions{.pdf}
+
+%pgfplots setup
+\pgfplotsset{every axis/.append style={
+	very thick,
+	tick style={thick}}}
+\pgfplotsset{
+        every mark/.append style={solid}
+}
+\pgfplotscreateplotcyclelist{mcolor}{%
+    {blue,every mark/.append style={fill=blue},mark=*},
+    {red,every mark/.append style={fill=red},mark=square*},
+    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=3},
+    {black,every mark/.append style={fill=black},mark=diamond*,mark size=3},
+    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
+    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3},
+    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
+    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
+    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=2.7},
+    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=2.7},
+    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
+    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3}}
+
+\pgfplotscreateplotcyclelist{mmark*}{
+    {mark=*},
+    {mark=square*},
+    {mark=triangle*,mark size=2.7},
+    {mark=diamond*,mark size=2.7},
+    {mark=pentagon*,mark size=2.5},
+    {mark=star,mark size=3},
+    {mark=asterisk,mark size=3},
+    {mark=+,mark size=3},
+    {mark=Mercedes star,mark size=3}}
+
+\pgfplotscreateplotcyclelist{mline}{
+    {solid,blue,every mark/.append style={fill=blue}},
+    {densely dashed,red,every mark/.append style={fill=red}},
+    {densely dotted,brown,every mark/.append style={fill=brown}},
+    {loosely dotted,black,every mark/.append style={fill=black}},
+    {loosely dashed,green!60!black,every mark/.append style={fill=green!60!black}},
+    {densely dashdotted,magenta!90!black,every mark/.append style={fill=magenta!90!black}},
+    {densely dashdotdotted,teal,every mark/.append style={fill=teal}},
+    {loosely dashdotted,orange,every mark/.append style={fill=orange}},
+    {loosely dashdotdotted,violet,every mark/.append style={fill=violet}}}
+
+    \pgfplotsset{cycle list name=mcolor}
 
@@
 
-{\bf Acknowledgment.} We thank the anonymous referees for their valuable comments.
+{\bf Acknowledgment.} We thank Michael Agun, Renu Tewari, and
+the anonymous referees for their valuable comments.
 This work is supported in part by NSF IIS-1118106. 

### 2013-07-26 snapshot_system/abs.tex

@@
 A cloud environment that  hosts a large number of  virtual machines (VMs) has
-a high storage demand for frequent backup of system image snapshots.
-Deduplication of data blocks can lead a big reduction of redundant blocks when
-their signatures are identical. However it is expensive and less fault-resilient to perform a global deduplication
-using signatures and let a data block share by many virtual machines. 
-This paper studies a VM-centric scheme which collocates a lightweight
-backup service with other cloud services in a cluster and it integrates multiple duplicate detection strategies 
-that  localize deduplication as much as possible within each virtual machine.
-It also organizes the write of small data chunks into large file system blocks so
-that each underlying file block is associated with one VM for most of cases.
+a high storage demand for frequent backup of system image snapshots and
+signature-based deduplication of data blocks is necessary to eliminate excessive 
+redundant blocks.  Collocating a cluster-based duplicate service with other cloud services
+reduces network traffic;
+% when their signatures are identical. 
+however it is resource expensive and less fault-resilient to perform a global deduplication
+and let a data block share by many virtual machines. 
+This paper proposes a VM-centric collocated backup service that  
+localizes deduplication as much as possible within each virtual machine
+and associates  underlying file blocks with one VM for most of cases.
 Our analysis shows that  this VM centric scheme 
 can  provide  better fault tolerance while using a small amount of computing and storage resource. 
-This  paper  provides a comparative evaluation of this scheme in  accomplishing a high deduplication 
+This  paper  describes a comparative evaluation of this scheme in  accomplishing a high deduplication 
 efficiency while sustaining a good backup throughput.

### 2013-07-26 snapshot_system/eval1.tex

@@
 study the PDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
+
+\subsection{Impact on Fault Tolerance}
+
+Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
+nodes fail for different amounts of sharing of filesystem blocks in the index. We
+show 5 and 20 for the VO and VC block links counts because those are what we
+measured in our small dataset, and chose higher numbers to account for much
+larger datasets. We chose to use a very optimistic setting for VO (20), and the
+absolute worst case amount of sharing for VC in a 100 machine cluster with 25
+VMs per machine (2500). Our results show that even the VC worst case provides
+better VM reliability that VO. As you can see from the graph, even small
+changes in the number of links to VO blocks has a significant impact on
+reliability, while even a 50 times increase in the VC block link counts only
+slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <
+N_o$, caused by the fact that the VM-centric approach localizes deduplication
+and packs  data blocks for one VM as much as possible.  The extra replicaton
+for PDS blocks also signficantly increases the snapshot availability even when
+a PDS file block is shared by every VM.
+
+% while in VO even small increases in $L$ causes a large decrease in availability. 
+Figure~\ref{fig:pds-replication}
+shows the advantages of increasing the replication factor for PDS blocks. the
+numbers in the graph are only meant to be relative, as we assume higher PDS
+block links than we have measured in our dataset (to account for a much larger
+body of data). It is easy to see though that increasing the replication of just
+the PDS blocks (which are the most popular blocks) can have a positive impact
+on the overall reliablity of the VM backups. These figures together show the
+advantages of the VM-centric model, and the advantages that separating the
+replication factor for popular blocks can have on reliability.
+
+\begin{figure}[htbp]
+  \centering
+  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Node failure affect on VMs},
+                cycle multi list={
+                    mline\nextlist
+                    [2 of]mmark*\nextlist
+                },
+		xlabel={Failed storage nodes},
+		ylabel={VM Snapshot Availability (\%)},
+		extra y ticks={99.9}, %if important numbers are missing
+                mark options=solid,
+                legend style={
+                    cells={anchor=west}, %legend entry alignment
+                    legend pos=south west %legend position
+                },
+                %reverse legend,
+		]
+                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
+                \addlegendentry{$VC\,20$ (measured)}
+                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
+                \addlegendentry{$VC\,2500$ (worst-case)}
+                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
+                \addlegendentry{$VO\,5$ (measured)}
+                \addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
+                \addlegendentry{$VO\,20$ (optimistic)}
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Availability of VM backups as nodes fail for VO and VC models for
+  varying degrees of block sharing (i.e. average number of VMs that use a
+  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
+  Graph shown for 100 machine cluster.
+  }
+  \label{fig:vm-availability}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={PDS Replication affect on availability},
+		xlabel={Failed storage nodes},
+		ylabel={VM Snapshot Availability (\%)},
+		extra y ticks={99.9}, %if important numbers are missing
+                mark options=solid,
+                legend style={
+                    cells={anchor=west}, %legend entry alignment
+                    legend pos=south west %legend position
+                },
+                reverse legend,
+		]
+                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
+                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
+                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
+                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
+                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
+  \label{fig:pds-replication}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={PDS Replication affect on availability},
+		xlabel={Failed storage nodes},
+		ylabel={VM Snapshot Availability (\%)},
+		%extra y ticks={99.99}, %if important numbers are missing
+                mark options=solid,
+                legend style={
+                    cells={anchor=west}, %legend entry alignment
+                    legend pos=south west %legend position
+                },
+                reverse legend,
+		]
+                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
+                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
+                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
+                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
+                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
+  \label{fig:pds-replication2}
+\end{figure}
 

### 2013-07-26 snapshot_system/arch.tex
revised

@@
 Every time there is a new snapshot created,
-we compute a bloom-filter as the summary of reference pointers for all non-PDS chunks used 
+we compute a bloom-filter with $z$ bits as the summary of reference pointers for all non-PDS chunks used 
 in this snapshot.
+
+%To control the false positive ratio $\epislon$ under $0.01$, an average snapshot of size 40 $GB$ with 
+%$u \approx 10$ million chunks, $z$ has 10 million bits.
+
 %{\bf Creating bloom filter} Scan all the living snapshot recipess and their segment recipes,
@@
 Then when there is a snapshot deletion,  
-we use  the snapshot fingerprint summary to identify if  chunks to be deleted from one snapshot
+we need to identify if  chunks to be deleted from one snapshot
 are still used by other snapshots. 
-This is done approximately and quickly by comparing the fingerprints of deleted snapshots with
-the fingerprint bloom-filter summary of other live snapshots.
+This is done approximately and quickly by comparing the reference pointers of deleted snapshots with
+the merged reference bloom-filter summary of other live snapshots.
+The merging of live snapshot bloom-filter bits uses the logical OR operator and the merged vector still takes $z$ bits.
 Since the number of live snapshots is limited for each VM (e.g. 10 in the Alibaba's production system), 
-the complexity of comparison is acceptable.
+the time cost of this comparison is small.
 %Instead of scanning the entire append store indices, we merge the type-1 summaries of all
@@
 The cost of leak repair mainly come from holding a table of reference pointers and scan of all snapshots metadata.
-Consider each reference pointer consumes 8 bytes plus 1 byte as mark field, a VM that has 40GB backup data will
-need 90MB of memory to construct such a table. Also, scanning all snapshots metadata is many times slower comparing
+Consider each reference pointer consumes 8 bytes plus 1 byte as mark field, a VM that has 40GB backup data with about
+10 million chunks will need 90MB of memory to construct such a table. 
+Also, scanning all snapshots metadata is many times slower comparing
 to the approximate deletion which only scans single snapshot's metadata.
@@
 %{\bf Discussion}
-We now give a model to estimate the storage leakage and how often leak repair needs to be conducted.
-Assuming a VM always maintain $B$ snapshots in the backup, and it creates and deletes one snapshot
-everyday. Let $c$ be the total number of chunks brought by the initial backup, $c^'$ be the average
-number of chunks brought by a consequancial backup, then the total number of chunks in use $C$ is:
+We now estimate the storage leakage and how often leak repair needs to be conducted.
+Assuming a VM always maintain $h$ snapshots in the backup, and it creates and deletes one snapshot
+everyday. Let $u$ be the total number of chunks brought by the initial backup, $\Delta u$ be the average
+number of additional unique chunks added from one snapshot to the next snapshot. Then the total number of unique
+chunks used is about:
 \[
-C = c + (B-1)c^'
+U = u + (h-1)\Delta u.
 \]
 
-Let $m$ be the bloom filter size in bits, $k$ be the number of hash functions used by bloom filter,
-then bloom filter's false-positive rate $\epsilon$ is:
+Each bloom filter vector has  $z$ bits for each snapshot and let $j$ be the number of hash functions used by the
+bloom filter. The probablity that a particular bit is still in all $h$ summary vectors is still 0 is 
+$(1- \frac{1}{z}) ^{j U}$. Notice that when a chunk appears multiple times in these summary vectors, it does not 
+increase the probability of a particular bit being 0 in all $h$ vectors.
+Then the false-positive rate $\epsilon$ is: 
 \[
-\epsilon = (1-e^{\frac{kC}{m}})^k
+\epsilon = (1-(1-\frac{z})^{jU})^j.
 \]
@@
 For each snapshot deletion, the amount of chunks need to be deleted is nearly identical to the number of
-newly add chunks $c^'$. However, some of chunks among them are not detected as unused in our approximation
+newly add chunks $\Delta u$. However, some of chunks among them are not detected as unused in our approximation
 algorithm, thus forms the storage leakage. Let $R$ be the total number of runs of approximate deletion since
-last repair, the total leakage $L$ can be estimated as:
+last repair. we estimate  the total leakage $L$ after $R$ runs as:
 \[
-L = Rc^'\epsilon
+L = R \Delta u \epsilon
 \]
 
-When leakage ratio $L/C$ exceeds a pre-defined threshold $\tau$, we need to execute a repare:
+When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we need to execute a leak repair:
 \[
-\frac{L}{C} = \frac{Rc^'\epsilon}{c+(B-1)c^'} > \tau \rightarrow R > \frac{\tau}{\epsilon}\frac{c + (B-1)c^'}{c^'}
+\frac{L}{U} = \frac{R \Delta u \epsilon}{u+(h-1)\Delta u } > \tau 
+\Longrightarrow R > \frac{\tau}{\epsilon}\frac{u + (h-1)\Delta u}{\Delta u}
 \]
-For example, when $\epsilon = 0.01$ and $\tau=0.1$, when the VM keeps 10 snapshots and each snapshot contains
-about 5\% of new data, then
-we would expect leak repair be triggered once for 
+For example in our tested dataset,  
+each VM keeps $h=10$ snapshots and each snapshot has
+about 1-5\% of new data. Thus $\frac{\Delta u}{u}=0.05$ at most. With 40GB snapshot size, $u\approx = 10$ millions.
+Then $U=10.45$ millions.
+We choose  $\epsilon = 0.01$ and $\tau=0.1$. Then from the bloom filter  false positive formula, 
+$z=10U=100.45$ million bits. $R=290$.
+Then we would expect leak repair be triggered once for 
 every 290 runs of approximate deletion. 
 When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
-only one full leak repair scheduled for every 12 days, which is sufficiently small to offset the 
-heavy I/O workload of the mark-sweep process.
+only one full leak repair for one VM scheduled for every 12 days. Each repairs uses about 90MB memory on average
+as discussed and takes a few minutes.
+% which is sufficiently small to offset the heavy I/O workload of the mark-sweep process.

### 2013-07-26 snapshot_system/snapshot.tex
revised

@@
 \begin{itemize}
-\item \textbf{Local duplicate search with VM-specific bining.}
+\item \textbf{VM-specific local duplicate search within similar segments.}
 We start with the standard dirty bit approach in a coarse grain segment level.
@@
 and is recorded in the snapshot recipe.
-So when we are processing a dirty segment,
+When we are processing a dirty segment,
 we can easily find similar segments from the
-parent snapshot recipe and load their segment recipes. Then we can perform fingerprint matching 
-against them
-for further inner-VM deduplication.
-The amount of memory for maintaining those fingerprints is small, as we only
-load one segment at a time.
+parent snapshot recipe and load their segment recipes. Then 
+given a set of data chunks within a dirty segement,  we compare  these chunk fingerprints
+with those in similar segments.  
 For example, with a 2MB segment, there are about 500 fingerprints to compare.
+The amount of memory for maintaining those fingerprints in similar segment s is small, as we only
+load one dirty segment at a time.
 

### 2013-07-29 snapshot_system/failover.tex
revised
Added new 105VM figure.

@@
 is 162. Thus allocation of extra replicas for PDS only introduces a small amount of extra space
-cost.  Figure~\ref{fig:storageCDS} shows the storage cost ratio of VC and VO when 
+cost.  Figure~\ref{fig:storagePDS} shows the storage cost ratio of VC and VO when 
 $r$=3, and $r_c$ varies from 3 to 10.
@@
 \comments{%dropping block links bec. we don't use it elsewhere
-\begin{figure}[ht]
+\begin{figure}[htbp]
   \centering
@@
 
-\begin{figure}[ht]
+\begin{figure}[htbp]
   \centering
@@
 
+\begin{figure}[htbp]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={VO VM links},
+		xlabel={Number of VMs},
+		ylabel={\small Avg. Num. FSBs used by VM},
+                ymin=0,
+                mark options=solid,
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		legend pos=north west
+		]
+                \addplot table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
+		\addplot table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
+                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
+                \addplot+[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
+                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
+  \label{fig:vm-links}
+\end{figure}
 The snapshot availability of is a VM is the likelyhood that
@@
 reliability in Figure~\ref{fig:vm-availability}.
+\begin{table}
+    \begin{tabular}{|l|lll|}
+    \hline
+    \multirow{2}{*}{Nodes Failed}   & \multicolumn{3}{c|}{Availability(\%)}\\
+                                    & $R=3$ & $R=4$ & $R=5$\\
+    \hline
+    1           &  100      & 100       & 100\\
+    2           & 100       & 100       & 100\\
+    3          & 99.999     & 100       & 100\\
+    5          & 99.993     & 99.9999   & 99.999998\\
+    10          & 99.926    & 99.995    & 99.999\\
+    20          & 99.295    & 99.876    & 99.979\\
+    \hline
+    \end{tabular}
+    \caption{Availability in a 100 machine cluster of a single FSB with different replication factors}
+    \label{tab:fsb-availability}
+\end{table}
+
 }
+\begin{figure}[htbp]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={FSB Availability},
+            cycle list name=mline,
+            xlabel={Number of Machines Failed},
+            ylabel={\small Availability of Single FSB (\%)},
+            extra y ticks={99.9}, %to add extra ticks
+            mark options=solid,
+            legend pos=south west,
+            %legend columns=2,
+            %legend style={
+            %    at={(0.5,-0.2)},
+            %anchor=north}
+            ]
+            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
+            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
+            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
+            \legend{$R=5$,$R=4$,$R=3$};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
+  \label{fig:fsb-availability}
+\end{figure}
+
+\comments{
 
@@
 replication factor for popular blocks can have on reliability.
-
-\begin{table}
-    \begin{tabular}{|l|lll|}
-    \hline
-    \multirow{2}{*}{Nodes Failed}   & \multicolumn{3}{c|}{Availability(\%)}\\
-                                    & $R=3$ & $R=4$ & $R=5$\\
-    \hline
-    1           &  100      & 100       & 100\\
-    2           & 100       & 100       & 100\\
-    3          & 99.999     & 100       & 100\\
-    5          & 99.993     & 99.9999   & 99.999998\\
-    10          & 99.926    & 99.995    & 99.999\\
-    20          & 99.295    & 99.876    & 99.979\\
-    \hline
-    \end{tabular}
-    \caption{Availability in a 100 machine cluster of a single FSB with different replication factors}
-    \label{tab:fsb-availability}
-\end{table}
-
-\begin{figure}[ht]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={FSB Availability},
-            cycle list name=mline,
-            xlabel={Number of Machines Failed},
-            ylabel={\small Availability of Single FSB (\%)},
-            extra y ticks={99.9}, %to add extra ticks
-            mark options=solid,
-            legend pos=south west,
-            %legend columns=2,
-            %legend style={
-            %    at={(0.5,-0.2)},
-            %anchor=north}
-            ]
-            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
-            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
-            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
-            \legend{$R=5$,$R=4$,$R=3$};
-            \end{axis}
-    \end{tikzpicture}
-    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
-  \label{fig:fsb-availability}
-\end{figure}
 
@@
 \end{figure}
+
+}
 

### 2013-08-01 snapshot_system/failover.tex
updated graphs
updates

@@
 		\begin{axis}[
+		%title={VO FSB links},
+		xlabel={Number of VMs},
+		ylabel={\small Avg. Num. VMs sharing FSB},
+                cycle list name=mline,
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		legend pos=north west
+		]
+                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
+		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
+                \legend{VO, PDS in VC};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
+  \label{fig:fsb-links}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
 		%title={VO VM links},
@@
                 ymin=0,
-                mark options=solid,
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		]
-                \addplot table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
-		\addplot table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
-                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
-                \addplot+[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
+                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
+                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
+                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
+                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                 \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
@@
                 \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
-                \addlegendentry{$VC\,20$ (measured)}
+                \addlegendentry{$VC\,1250$ (estimated)}
                 \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
@@
                 \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
-                \addlegendentry{$VO\,5$ (measured)}
-                \addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
-                \addlegendentry{$VO\,20$ (optimistic)}
+                \addlegendentry{$VO\,6.3$ (optimistic)}
+                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
+                %\addlegendentry{$VO\,20$ (optimistic)}
 		\end{axis}

### 2013-08-01 snapshot_system/failover.tex
updated cds replication graph, other graphs. updated text.

@@
                 cycle list name=mline,
+                xmin=0,
+                ymin=0,
+                xmax=106,
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		ylabel={\small Avg. Num. FSBs used by VM},
+                xmin=0,
                 ymin=0,
+                xmax=106,
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		legend pos=north west
+		legend pos=south west
 		]
                 \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
+                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
+                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                 \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
-                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
-                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
-                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
+                \legend{$N_o$, $N_1+N_2$, $N_2$, $N_1$};
 		\end{axis}
@@
 Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
-nodes fail for different amounts of sharing of filesystem blocks in the index. We
-show 5 and 20 for the VO and VC block links counts because those are what we
-measured in our small dataset, and chose higher numbers to account for much
-larger datasets. We chose to use a very optimistic setting for VO (20), and the
-absolute worst case amount of sharing for VC in a 100 machine cluster with 25
-VMs per machine (2500). Our results show that even the VC worst case provides
-better VM reliability that VO. As you can see from the graph, even small
-changes in the number of links to VO blocks has a significant impact on
-reliability, while even a 50 times increase in the VC block link counts only
-slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <
+nodes fail for different amounts of sharing of filesystem blocks in the index.
+We show 6.3 for the VO sharing because that is what we measured in our dataset,
+and while we expect it to continue to grow (thereby decreasing fault
+tolerance), it should do so slowly. for VC we use 1250, because that is what we
+estimate at 2500 VMs based on the linear growth up to 105 VMs. We also show
+2500 VMs sharing each PDS FSB because that is the absolute worst case for 2500
+VMs. Our results show that even the VC worst case provides better VM
+reliability than our optimistic amount of sharing in VO. 
+The key factor placed is that  $N_1 +N_2 <
 N_o$, caused by the fact that the VM-centric approach localizes deduplication
@@
 Figure~\ref{fig:pds-replication}
-shows the advantages of increasing the replication factor for PDS blocks. the
-numbers in the graph are only meant to be relative, as we assume higher PDS
-block links than we have measured in our dataset (to account for a much larger
-body of data). It is easy to see though that increasing the replication of just
+shows the advantages of increasing the replication factor for PDS blocks. We
+use our estimate of 1250 VMs sharing each PDS block, which is what we expect
+for 2500 VMs, given the growth up to 105 VMs. It is easy to see though thatr
+increasing the replication of just
 the PDS blocks (which are the most popular blocks) can have a positive impact
-on the overall reliablity of the VM backups. These figures together show the
+on the overall reliablity of the VM backups. Increasing the
+PDS replication is cheap because is makes up a very small percent of the
+stored data, but the impact is significant. These figures together show the
 advantages of the VM-centric model, and the advantages that separating the
@@
 	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
+  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1250)}
   \label{fig:pds-replication}

### 2013-08-02 snapshot_system/arch.tex
revise the formula for deletion
revisions

@@
 segments must be checked during snapshot backup. After the snapshot backup is finished, 
-snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
+snapshot deduplication component acknowledges the driver to reset the dirty-bits map to
 a clean state.
@@
 that have been made to virtual disk.
-Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
-is modified since last backup. Hence we could treat segment as the basic unit 
-in snapshot backup similar to
-file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
-Moreover, we break segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
+Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, which indicates whether the segment
+has been modified since the last backup. Hence we could treat segment as the basic unit 
+in snapshot backup similar to a
+file in filesystem backup: a snapshot could share a segment with previous snapshot it has not been changed. 
+Moreover, we break segments into variable-sized chunks (average 4KB) using a content-based chunking algorithm,
 which brings the opportunity of fine-grained deduplication by
@@
 segments must be checked during snapshot backup. After the snapshot backup is finished, 
-snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
+snapshot deduplication component acknowledges the driver to reset the dirty-bits map to
 a clean state.
-Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
-is modified since last backup. Hence we could treat segment as the basic unit 
+Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicates whether the segment
+is modified since last backup. Hence we think of segment as the basic unit 
 in snapshot backup similar to
-file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
+file in normal filesystem backup: a snapshot could share a segment with previous snapshot it is not changed. 
 As a standard practice, segments are further divided into variable-sized chunks (average 4KB) 
-using content-based chunking algorithm, which brings the opportunity of fine-grained deduplication by
+using a content-based chunking algorithm, which brings the opportunity of fine-grained deduplication by
 allowing data sharing between segments.
@@
 %segments which greatly ease the segment-level deduplication.
-In a snapshot recipes or a segment recipe, 
-the data structures  includes reference pointers to the actual data location.
+In snapshot and segment recipes, 
+the data structures  includes reference pointers to the actual data location to eliminate the need for additional indirection.
 %In our implementation the data reference is a 8 bytes field which is either an 
@@
 
-We build a snapshot storage on the top of a distributed file system.
+We build the snapshot storage on the top of a distributed file system.
 Following the VM-centric idea for the purpose of fault isolation,
@@
 There is also a special store containing all PDS chunks shared among different VMs.
-The replication degree of file blocks of snapshot stores in the underlying file system
-Extra replication of this store is added as discussed in Section~\ref{sect:analysis}.
+This separation of PDS chunks allows us to change the replication degree of of those popular file blocks in the underlying file system
+Extra replication of this store is added and analyzed in Section~\ref{sect:analysis}.
 As shown in Fig.\ref{fig:as_arch}, we explain the data structure of snapshot stores as follows.
@@
 \item The PDS snapshot contains a set of commonly used data chunks and is accessed by its offset and size
-in the corresponding DSF file.
+in the corresponding DFS file.
 The PDS index uses the offset and size as a reference in its index structure.
 
-\item Each non-PDS snapshot store is divided into a set of containers and each of them is approximately 
-1GB. The reason we divide the snapshot into containers is to simplify the compact process
-conducted periodically.  There are chunks deleted without any reference from other snapshots
-and to reclaim the space of these useless chunks, a compaction  routine can work on one container at a time
-and copy used data chunks to another container.
+\item Each non-PDS snapshot store is divided into a set of containers and each container is approximately 
+1GB. The reason we divide the snapshot into containers is to simplify the compaction process
+conducted periodically. Chunks without any reference from other snapshots can be removed by this process, and the compaction  routine can work on one container at a time
+and copy used data chunks to another container. By limiting the size of a container, we limit the cost of the compaction process.
 	\begin{itemize}
@@
 in snapshot data accessing~\cite{Sampling,FoundationPaper},
-	retrieval of  data chunks by group naturally fits in the prefetching scheme  to speedup
+	retrieval of  data chunks by group naturally works well with prefetching to speedup
 	snapshot access. A  typical chunk group contains 100 to 1000 chunks, with an average size of 
-200-600KB.
+200-600 chunks.
 Chunk grouping also reduces the  container index size as we discuss below. 
-Given  the average chunk size  4KB,  the index size for a 1GB container reduces from 10MB to 100KB when
+Given  the average chunk size of 4KB,  the index size for a 1GB container reduces from 10MB to 100KB when
 the chunk group size is 100.
@@
 3) a chunk deletion log file saving all the deletion requests within  the container.
-A VM snapshot store typically has a small number of containers because each container is fairly large with an average size of 1GB, it 
-maintains a limited number of snapshots (e.g. 10 in the Alibaba case),
-and new snapshot data chunks can be effectively compressed in chunk groups in addition to  deduplication.
+A VM snapshot store typically has a small number of containers because each container is fairly large, with an average size of 1GB, and 
+maintains a limited number of snapshots (e.g. 10 in the Alibaba case).
+New snapshot data chunks can be effectively compressed in chunk groups in addition to  deduplication.
 
@@
 is composed of two parts: a container ID (2 bytes) and CID (6 bytes).
-Once a snapshot is to be accessed access, the receipt in this snapshot will point to either a data chunk
+When a snapshot chunk is to be accessed, the recipe for the snapshot will point to either a data chunk
 in the PDS or a reference number with a container ID and CID.
@@
 the chunk group is identified using this CID.
-Once this chunk group is loaded to memory, its header contains the exact offset of the corresponding chunk and the content is then accessed from the memory buffer.
+Once the chunk group is loaded to memory, its header contains the exact offset of the corresponding chunk and the content is then accessed from the memory buffer.
 
@@
 group  that  covers the chunk by the group  CID range.
-After that, it reads the whole chunk group from DFS, decompresses it, seeks the exact chunk data 
+After that, it reads the whole chunk group from DFS, decompresses it, and seeks to the exact chunk data 
 specified by the CID. 
@@
 A data chunk can be deleted when a snapshot expires or gets deleted explicitly by a user.
-We will discuss the snapshot deletion shortly in the following subsection.
+We will discuss the snapshot deletion in the following subsection.
 %deletes the data pointed by the reference.
@@
 During compaction, the snapshot store creates a new container (with the same container ID) to replace the 
-existing one. This is done by sequentially scan the old container, copying all the chunks that are not 
-found in the deletion log to the new container, creating new chunk groups and indices. 
-However, every chunk's CID is directly copied rather than re-generated. This
-process leaves holes in the CID values, but does not affect the sorted order.
+existing one. This is done by sequentially scanning the old container, copying all the chunks that are not 
+found in the deletion log to the new container, and creating new chunk groups and indices. 
+Every chunk's CID however is directly copied rather than re-generated. This
+process leaves holes in the CID values, but preserves the sorted order.
 As a result, all data references stored 
@@
 This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
-Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
-Such localization increases data independence between different VM backups,
+Inner-VM duplication exists between a VM's snapshots, because the majority of data is unchanged during each backup period. 
+Such localization decreases data dependencies between different VM backups,
 simplifies snapshot management and statistics collection,
@@
 On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
-As the result, different VMs tend to backup large amount of highly similar data.
+As the result, different VMs tend to backup a large amount of highly similar data.
 Our multi-level pipeline process can minimize 
 the cost of deduplication while maximize the its efficiency at each level,
-and it is parallel since each segment is processed independently.
+and is parallel since each segment is processed independently.
 
@@
 level, but only for those dirty  segments. 
-We load the fingerprints of block chunks of the corresponding segment from the
+We load the fingerprints of chunks in the corresponding segment from the
 parent for a comparisons and compare near-by fingerprint matching within this segment.
@@
 speed and resource usage. Our method sacrifices a small percent of storage leakage
-to effectively identify unused chunks in $O(n)$ speed, with $n$ being the logical number of non-PDS chunks 
+to effectively identify unused chunks in $O(n)$ time, with $n$ being the logical number of non-PDS chunks 
 to be deleted from a VM snapshot store.
@@
 
-The cost of leak repair mainly come from holding a table of reference pointers and scan of all snapshots metadata.
+The cost of leak repair mainly come from holding a table of reference pointers and the scan of all snapshots' metadata.
 Consider each reference pointer consumes 8 bytes plus 1 byte as mark field, a VM that has 40GB backup data with about
 10 million chunks will need 90MB of memory to construct such a table. 
-Also, scanning all snapshots metadata is many times slower comparing
+Also, scanning all snapshots metadata is many times slower when compared
 to the approximate deletion which only scans single snapshot's metadata.
-It's worth to mention that compare to previously-developed mark-and-sweep techniques, 
-our leak repair still has advantage because the scope of repair is restricted within single VM's snapshot 
-store due to our VM-specific design, and we only do it periodically.
+It's worth mention that compared to previously-developed mark-and-sweep techniques, 
+our leak repair still has advantages because the scope of repair is restricted within a single VM's snapshot 
+store due to our VM-centric design, and we perform leakage repair periodically.
 %We cannot simply repeat the phase 1 multiple times to reduce temporary storage leakage, because:
@@
 \[
-\epsilon = (1-(1-\frac{z})^{jU})^j.
+\epsilon = (1-(1-\frac{1}{z})^{jU})^j.
 \]
@@
 only one full leak repair for one VM scheduled for every 12 days. Each repairs uses about 90MB memory on average
-as discussed and takes a few minutes.
+as discussed earlier and takes a short period of time.
 % which is sufficiently small to offset the heavy I/O workload of the mark-sweep process.

### 2013-08-02 snapshot_system/eval1.tex
updates
update graph

@@
     \hline
-    Tasks & CPU & Mem (MB) & Disk (MB/s) & Network \\ \hline
-    4                      & 63\% & 164 & 84     &    \\ \hline
-    6                      & 77\% & 201  & 88.5   &     \\ \hline
-    8                      & 82\% & 237   & 89.2   &    \\ \hline
-    10                      & 85\% & 273   & 90.4   &    \\ \hline
-    12                      & 91\% & 312    & 91.5   &   \\ \hline
+    Tasks & CPU & Mem (MB) & Disk W (MB/s) & Network \\ \hline
+    1                      & 19\% & 18.1 & 32.1     &    \\ \hline
+    2                      & 35\% & 31.8 & 53     &    \\ \hline
+    4                      & 63\% & 54.1 & 84     &    \\ \hline
+    6                      & 77\% & 71.9  & 88.5   &     \\ \hline
+    8                      & 82\% & 90.5   & 89.2   &    \\ \hline
+    10                      & 85\% & 97.2   & 90.4   &    \\ \hline
+    12                      & 91\% & 95.6    & 91.5   &   \\ \hline
     \end{tabular}

### 2013-08-02 snapshot_system/eval1.tex
added figure for p=100000 under vm availability

--- 2013-07-26 snapshot_system/eval1.tex
@@
 
-\begin{figure}[htbp]
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}%{.5\textwidth}
+      \centering
+      %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
+            \begin{tikzpicture}
+                %\pgfplotsset{every axis legend/.append style={font={\tiny}}}
+                    \begin{axis}[
+                    %font={\tiny},
+                    tick label style={font=\scriptsize},
+                    tick style=thin,
+                    width=0.5\linewidth,
+                    title={\small $p=100$},
+                    cycle list={
+                        {blue,thin,solid,mark=none},
+                        {red,thin,densely dashed,mark=none},
+                        {red,thin,densely dotted,mark=none}
+                    },
+                    xlabel={\tiny Failed nodes},
+                    ylabel={\tiny VM Availability (\%)},
+                    extra y ticks={99.9}, %if important numbers are missing
+                    mark options=solid,
+                    legend columns=-1,
+                    legend style={
+                        font=\small,
+                        cells={anchor=west}, %legend entry alignment
+                        legend pos=south west %legend position
+                    },
+                    legend to name=legend:vm-availability,
+                    %reverse legend,
+                    ]
+                    \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
+                    \addlegendentry{$VO\,6.3$ (optimistic)}
+                    \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
+                    \addlegendentry{$VC$ (expected)}
+                    \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
+                    \addlegendentry{$VC$ (worst-case)}
+                    %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
+                    %\addlegendentry{$VO\,20$ (optimistic)}
+                    \end{axis}
+            \end{tikzpicture}
+      %\caption{100 machine cluster.}
+      \label{fig:vm-availability-100}
+    \end{subfigure}%
+    \begin{subfigure}%{.5\textwidth}
   \centering
@@
 		\begin{axis}[
-		%title={Node failure affect on VMs},
-                cycle multi list={
-                    mline\nextlist
-                    [2 of]mmark*\nextlist
+                    width=0.5\linewidth,
+                    tick label style={font=\scriptsize},
+                    tick style=thin,
+		title={\small $p=100000$},
+                cycle list={
+                    {blue,thin,solid,mark=none},
+                    {red,thin,densely dashed,mark=none},
+                    {red,thin,densely dotted,mark=none}
                 },
-		xlabel={Failed storage nodes},
-		ylabel={VM Snapshot Availability (\%)},
-		extra y ticks={99.9}, %if important numbers are missing
+		xlabel={\tiny Failed nodes},
+		ylabel={\tiny VM Availability (\%)},
+		extra y ticks={99.99}, %if important numbers are missing
                 mark options=solid,
@@
 		]
-                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
-                \addlegendentry{$VC\,20$ (measured)}
-                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
-                \addlegendentry{$VC\,2500$ (worst-case)}
-                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
-                \addlegendentry{$VO\,5$ (measured)}
-                \addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
-                \addlegendentry{$VO\,20$ (optimistic)}
+                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_100000.txt};
+                %\addlegendentry{$VO\,6.3$ (optimistic)}
+                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_100000.txt};
+                %\addlegendentry{$VC\,1250$ (estimated)}
+                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_100000.txt};
+                %\addlegendentry{$VC\,2500000$ (worst-case)}
+                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
+                %\addlegendentry{$VO\,20$ (optimistic)}
 		\end{axis}
 	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail for VO and VC models for
-  varying degrees of block sharing (i.e. average number of VMs that use a
-  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
-  Graph shown for 100 machine cluster.
+        %\caption{100000 machine cluster.}
+  \label{fig:vm-availability-100000}
+\end{subfigure}
+    \pgfplotslegendfromname{legend:vm-availability}
+      \caption{Availability of VM backups for VO and VC models for
+          varying degrees of block sharing. Non-PDS replication fixed
+          at 3 and PDS replication increased to 4. VC worst-case
+          is $V=25*p$, and expected-case is $\frac{V}{2}$
       }
       \label{fig:vm-availability}
+
 \end{figure}

### 2013-08-02 snapshot_system/failover.tex
added figure for p=100000 under vm availability

@@
 		ylabel={\small Avg. Num. VMs sharing FSB},
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		legend pos=north west
-		]
-                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
-		\addplot table[x=VMs,y=cdslinks] {figures/cds_links.txt};
-                \legend{VO, PDS in VC};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
-  \label{fig:fsb-links}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={VO FSB links},
-		xlabel={Number of VMs},
-		ylabel={\small Avg. Num. VMs sharing FSB},
                 cycle list name=mline,
@@
   \label{fig:fsb-links}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={VO VM links},
-		xlabel={Number of VMs},
-		ylabel={\small Avg. Num. FSBs used by VM},
-                ymin=0,
-                mark options=solid,
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		legend pos=north west
-		]
-                \addplot table[x=VMs,y=No] {figures/vo_vm_links.txt};
-		\addplot table[x=VMs,y=N1] {figures/vc_vm_links.txt};
-                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links.txt};
-                \addplot+[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links.txt};
-                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
-  \label{fig:vm-links}
 \end{figure}
@@
 
+\end{figure}
+
 \begin{figure}[ht]

### 2013-08-02 snapshot_system/failover.tex
normalized axis label and legend fonts, switched to sans-serif for plots

@@
 		xlabel={Number of VMs},
-		ylabel={\small Avg. Num. VMs sharing FSB},
+		ylabel={Avg. Num. VMs sharing FSB},
                 cycle list name=mline,
@@
 		xlabel={Number of VMs},
-		ylabel={\small Avg. Num. FSBs used by VM},
+		ylabel={Avg. Num. FSBs used by VM},
                 xmin=0,
@@
             xlabel={Number of Machines Failed},
-            ylabel={\small Availability of Single FSB (\%)},
+            ylabel={Availability of Single FSB (\%)},
             extra y ticks={99.9}, %to add extra ticks

### 2013-08-02 snapshot_system/eval1.tex
updated plots

@@
 Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
-nodes fail for different amounts of sharing of filesystem blocks in the index. We
-show 5 and 20 for the VO and VC block links counts because those are what we
-measured in our small dataset, and chose higher numbers to account for much
-larger datasets. We chose to use a very optimistic setting for VO (20), and the
-absolute worst case amount of sharing for VC in a 100 machine cluster with 25
-VMs per machine (2500). Our results show that even the VC worst case provides
-better VM reliability that VO. As you can see from the graph, even small
-changes in the number of links to VO blocks has a significant impact on
-reliability, while even a 50 times increase in the VC block link counts only
-slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <
+nodes fail for different amounts of sharing of filesystem blocks in the index.
+We show 6.3 for the VO sharing because that is what we measured in our dataset,
+and while we expect it to continue to grow (thereby decreasing fault
+tolerance), it should do so slowly, so we treated VO FSB sharing as a
+contstant factor of 6.3, as it doesn't change our results. for VC we use 1250, because that is what we
+estimate at 2500 VMs based on the linear growth up to 105 VMs. We also show
+2500 VMs sharing each PDS FSB because that is the absolute worst case for 2500
+VMs. Our results show that even the VC worst case provides better VM
+reliability than our optimistic amount of sharing in VO. 
+The key factor placed is that  $N_1 +N_2 <
 N_o$, caused by the fact that the VM-centric approach localizes deduplication
@@
 	\begin{tikzpicture}
+            \pgfplotsset{/pgf/number format/.cd,
+                fixed,precision=4}
 		\begin{axis}[
@@
                     tick style=thin,
-		title={\small $p=100000$},
+		title={\small $p=1000$},
                 cycle list={
@@
 		ylabel={\tiny VM Availability (\%)},
-		extra y ticks={99.99}, %if important numbers are missing
+		%extra y ticks={99.99}, %if important numbers are missing
                 mark options=solid,
@@
 		]
-                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_100000.txt};
+                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
                 %\addlegendentry{$VO\,6.3$ (optimistic)}
-                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_100000.txt};
+                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
                 %\addlegendentry{$VC\,1250$ (estimated)}
-                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_100000.txt};
+                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
                 %\addlegendentry{$VC\,2500000$ (worst-case)}
@@
 		\begin{axis}[
+                        width=\linewidth,
+                        height=0.7\linewidth,
 		%title={PDS Replication affect on availability},
@@
 
+\comments{%superceded by minhash algorithm (below)
 %graph comparing extreme binning (SRB) with PDS model (VC) for different cds percentages
@@
             %title={Ex-Binning Efficiency},
+            width=\linewidth,
+            height=0.7\linewidth,
             cycle list name=mline,
@@
             ylabel={Dedup. Efficiency (\%)},
+            xmin=0,
+            ymin=88.5,
+            ymax=100,
             %extra y ticks={4.5,5.5,6.5} %to add extra ticks
@@
             legend pos=south west,
-            %legend columns=2,
-            %legend style={
-            %    at={(0.5,-0.2)},
-            %anchor=north},
+            legend columns=2,
+            legend style={
+                font={\tiny},
+                %at={(0.5,-0.2)},
+                %anchor=north
+            },
             ]

### 2013-08-02 snapshot_system/failover.tex
updated plots

@@
 		\begin{axis}[
+                width=\linewidth,
+                height=0.7\linewidth,
 		%title={VO FSB links},
@@
 		%title={VO VM links},
+                width=\linewidth,
+                height=0.7\linewidth,
 		xlabel={Number of VMs},
@@
             \begin{axis}[
+                width=\linewidth,
+                height=0.7\linewidth,
             %title={FSB Availability},
@@
 \end{figure}
-
-\comments{
-
-Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
-nodes fail for different amounts of sharing of filesystem blocks in the index.
-We show 6.3 for the VO sharing because that is what we measured in our dataset,
-and while we expect it to continue to grow (thereby decreasing fault
-tolerance), it should do so slowly. for VC we use 1250, because that is what we
-estimate at 2500 VMs based on the linear growth up to 105 VMs. We also show
-2500 VMs sharing each PDS FSB because that is the absolute worst case for 2500
-VMs. Our results show that even the VC worst case provides better VM
-reliability than our optimistic amount of sharing in VO. 
-The key factor placed is that  $N_1 +N_2 <
-N_o$, caused by the fact that the VM-centric approach localizes deduplication
-and packs  data blocks for one VM as much as possible.  The extra replicaton
-for PDS blocks also signficantly increases the snapshot availability even when
-a PDS file block is shared by every VM.
-
-% while in VO even small increases in $L$ causes a large decrease in availability. 
-Figure~\ref{fig:pds-replication}
-shows the advantages of increasing the replication factor for PDS blocks. We
-use our estimate of 1250 VMs sharing each PDS block, which is what we expect
-for 2500 VMs, given the growth up to 105 VMs. It is easy to see though thatr
-increasing the replication of just
-the PDS blocks (which are the most popular blocks) can have a positive impact
-on the overall reliablity of the VM backups. Increasing the
-PDS replication is cheap because is makes up a very small percent of the
-stored data, but the impact is significant. These figures together show the
-advantages of the VM-centric model, and the advantages that separating the
-replication factor for popular blocks can have on reliability.
-
-\begin{figure}[ht]
-  \centering
-  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={Node failure affect on VMs},
-                cycle multi list={
-                    mline\nextlist
-                    [2 of]mmark*\nextlist
-                },
-		xlabel={Failed storage nodes},
-		ylabel={VM Snapshot Availability (\%)},
-		extra y ticks={99.9}, %if important numbers are missing
-                mark options=solid,
-                legend style={
-                    cells={anchor=west}, %legend entry alignment
-                    legend pos=south west %legend position
-                },
-                %reverse legend,
-		]
-                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
-                \addlegendentry{$VC\,1250$ (estimated)}
-                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
-                \addlegendentry{$VC\,2500$ (worst-case)}
-                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
-                \addlegendentry{$VO\,6.3$ (optimistic)}
-                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
-                %\addlegendentry{$VO\,20$ (optimistic)}
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail for VO and VC models for
-  varying degrees of block sharing (i.e. average number of VMs that use a
-  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
-  Graph shown for 100 machine cluster.
-  }
-  \label{fig:vm-availability}
-\end{figure}
-
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={PDS Replication affect on availability},
-		xlabel={Failed storage nodes},
-		ylabel={VM Snapshot Availability (\%)},
-		extra y ticks={99.9}, %if important numbers are missing
-                mark options=solid,
-                legend style={
-                    cells={anchor=west}, %legend entry alignment
-                    legend pos=south west %legend position
-                },
-                reverse legend,
-		]
-                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
-                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
-                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
-                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
-                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1250)}
-  \label{fig:pds-replication}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={PDS Replication affect on availability},
-		xlabel={Failed storage nodes},
-		ylabel={VM Snapshot Availability (\%)},
-		%extra y ticks={99.99}, %if important numbers are missing
-                mark options=solid,
-                legend style={
-                    cells={anchor=west}, %legend entry alignment
-                    legend pos=south west %legend position
-                },
-                reverse legend,
-		]
-                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
-                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
-                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
-                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
-                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
-  \label{fig:pds-replication2}
-\end{figure}
-
-}
 

### 2013-08-05 snapshot_system/eval1.tex
Graph updates

@@
             \begin{tikzpicture}
-                %\pgfplotsset{every axis legend/.append style={font={\tiny}}}
                     \begin{axis}[
-                    %font={\tiny},
                     tick label style={font=\scriptsize},
@@
                     legend style={
-                        font=\small,
+                        font=\small\sffamily,
                         cells={anchor=west}, %legend entry alignment
@@
                     \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
-                    \addlegendentry{$VO\,6.3$ (optimistic)}
+                    \addlegendentry{VO\,$6.3$ (optimistic)}
                     \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
-                    \addlegendentry{$VC$ (expected)}
+                    \addlegendentry{VC (expected)}
                     \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
-                    \addlegendentry{$VC$ (worst-case)}
+                    \addlegendentry{VC (worst-case)}
                     %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
-                    %\addlegendentry{$VO\,20$ (optimistic)}
+                    %\addlegendentry{VO\,$20$ (optimistic)}
                     \end{axis}
@@
                         width=\linewidth,
-                        height=0.7\linewidth,
+                        height=0.6\linewidth,
 		%title={PDS Replication affect on availability},
@@
 
-%version of above graph using minhash algorithm
+\comments{%version of above graph using minhash algorithm
 \begin{figure}[ht]
@@
     Stateless Routing with Binning and VC. VC uses the minhash algorithm for Level-2.}
+  \label{fig-exbin-efficiency-graph2}
+\end{figure}
+}
+
+%this version combines the old and the minhash alg. to compare against srb
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Ex-Binning Efficiency},
+            width=\linewidth,
+            height=0.75\linewidth,
+            cycle list={%
+                {blue,solid,mark=square*},
+                {blue,solid,mark=triangle*,mark size=1.5},
+                {blue,solid,mark=diamond*,mark size=1.5},
+                {blue,solid,mark=pentagon*,mark size=1.4},
+                {red,draw=red,densely dotted,mark=square},
+                {red,densely dotted,mark=triangle,mark size=1.5},
+                {red,densely dotted,mark=diamond,mark size=1.5},
+                {brown,densely dashed,mark=*},
+                %{red,densely dotted,mark=o},
+                %{red,densely dotted,mark=pentagon,mark size=1.4},
+            },
+            mark repeat={5},
+            xlabel={Number of VMs added},
+            ylabel={Dedup. Efficiency (\%)},
+            xmin=0,
+            ymin=88.5,
+            ymax=100,
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            mark options=solid,
+            legend pos=south west,
+            legend columns=2,
+            legend style={
+                font={\tiny\sffamily},
+                %at={(0.5,-0.2)},
+                %anchor=north
+            },
+            ]
+            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
+            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
+            \addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
+            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
+            \legend{VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$),VC (No PDS),VC(MH\,$\sigma=4\%$),VC(MH\,$\sigma=2\%$),VC(MH\,$\sigma=1\%$),SRB};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Deduplication Efficiency
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
+    Stateless Routing with Binning and VC. Also compares old VC algorithm to new VC with Minhash for Level-2.}
   \label{fig-exbin-efficiency-graph2}

### 2013-08-05 snapshot_system/main.tex
rename con to concl
update
normalized axis label and legend fonts, switched to sans-serif for plots
shrunk tick label size on plots
updated plots
Graph updates

--- 2013-05-28 snapshot_system/main.tex
@@
-\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate-10pt}
+\usepackage{mathptmx}
 \usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
+\usepackage{subfigure}
 \usepackage{epsfig}
+\usepackage{multirow}
+\usepackage{array}
 \usepackage{breqn}
+\usepackage{pgfplots}
+\usepackage{sansmath}
+\pgfplotsset{compat=1.7}
+\DeclareGraphicsExtensions{.pdf}
 
 \newcommand{\comments}[1]{}
+%pgfplots setup
+
+\pgfplotsset{
+    %You are supposed to use append style rather than just setting
+    %parameters globally so they are easier to override to special cases
+    %thickness options:thin,ultra thin,very thin,semithick,thick,very thick
+    every axis/.append style={
+        thick,
+        tick style={thick},
+        tick label style={font=\small\mathversion{sans}\sffamily},
+        label style={font=\small\sffamily},
+        font={\small\sffamily},
+        mark size=1.0
+    },
+    every legend/.append style={font={\small\mathversion{sans}\sffamily}}
+}
+\pgfplotsset{
+    every mark/.append style={solid}
+}
+\pgfplotscreateplotcyclelist{mcolor}{%
+    {blue,every mark/.append style={fill=blue},mark=*},
+    {red,every mark/.append style={fill=red},mark=square*},
+    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=1.5},
+    {black,every mark/.append style={fill=black},mark=diamond*,mark size=1.5},
+    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=1.4},
+    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=1.5},
+    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
+    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
+    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=1.5},
+    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=1.5},
+    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=1.4},
+    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=1.5}}
+
+\pgfplotscreateplotcyclelist{mmark*}{
+    {mark=*},
+    {mark=square*},
+    {mark=triangle*,mark size=1.5},
+    {mark=diamond*,mark size=1.5},
+    {mark=pentagon*,mark size=1.4},
+    {mark=star,mark size=1.5},
+    {mark=asterisk,mark size=1.5},
+    {mark=+,mark size=1.5},
+    {mark=Mercedes star,mark size=1.5}}
+
+\pgfplotscreateplotcyclelist{mline}{
+    {solid,blue,every mark/.append style={fill=blue}},
+    {densely dashed,red,every mark/.append style={fill=red}},
+    {densely dotted,brown,every mark/.append style={fill=brown}},
+    {loosely dotted,black,every mark/.append style={fill=black}},
+    {loosely dashed,green!60!black,every mark/.append style={fill=green!60!black}},
+    {densely dashdotted,magenta!90!black,every mark/.append style={fill=magenta!90!black}},
+    {densely dashdotdotted,teal,every mark/.append style={fill=teal}},
+    {loosely dashdotted,orange,every mark/.append style={fill=orange}},
+    {loosely dashdotdotted,violet,every mark/.append style={fill=violet}}}
+
+    \pgfplotsset{cycle list name=mcolor}
 
@@
 %\input{design}
-\input{background}
+%\input{background}
 \input{challenge}
@@
 \input{failover}
-\input{design1}
-%\input{snapshot}
-%\input{append}\
-\input{cds}
+%\input{compare}
+%\input{design1}
+\input{arch}
+%\input{impl}
+%\input{sampling-comparison.txt}
+\input{eval1}
+%\input{cds}
 %\input{delete}
 %\input{failover}
-\input{result}
-\input{con}
+%\input{result}
+\input{concl}
 
 \bibliographystyle{abbrv}
-\bibliography{library}
+\bibliography{library,dedup1}
 \end{document}

### 2013-08-05 snapshot_system/eval1.tex
graph updates
update experiments

--- 2013-08-02 snapshot_system/eval1.tex
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}%{.5\textwidth}
-      \centering
-      %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
-            \begin{tikzpicture}
-                %\pgfplotsset{every axis legend/.append style={font={\tiny}}}
-                    \begin{axis}[
-                    %font={\tiny},
-                    tick label style={font=\scriptsize},
-                    tick style=thin,
-                    width=0.5\linewidth,
-                    title={\small $p=100$},
-                    cycle list={
-                        {blue,thin,solid,mark=none},
-                        {red,thin,densely dashed,mark=none},
-                        {red,thin,densely dotted,mark=none}
-                    },
-                    xlabel={\tiny Failed nodes},
-                    ylabel={\tiny VM Availability (\%)},
-                    extra y ticks={99.9}, %if important numbers are missing
-                    mark options=solid,
-                    legend columns=-1,
-                    legend style={
-                        font=\small,
-                        cells={anchor=west}, %legend entry alignment
-                        legend pos=south west %legend position
-                    },
-                    legend to name=legend:vm-availability,
-                    %reverse legend,
-                    ]
-                    \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
-                    \addlegendentry{$VO\,6.3$ (optimistic)}
-                    \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
-                    \addlegendentry{$VC$ (expected)}
-                    \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
-                    \addlegendentry{$VC$ (worst-case)}
-                    %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
-                    %\addlegendentry{$VO\,20$ (optimistic)}
-                    \end{axis}
-            \end{tikzpicture}
-      %\caption{100 machine cluster.}
-      \label{fig:vm-availability-100}
-    \end{subfigure}%
-    \begin{subfigure}%{.5\textwidth}
+\begin{figure}[htbp]
   \centering
@@
 		\begin{axis}[
-                    width=0.5\linewidth,
-                    tick label style={font=\scriptsize},
-                    tick style=thin,
-		title={\small $p=100000$},
-                cycle list={
-                    {blue,thin,solid,mark=none},
-                    {red,thin,densely dashed,mark=none},
-                    {red,thin,densely dotted,mark=none}
+		%title={Node failure affect on VMs},
+                cycle multi list={
+                    mline\nextlist
+                    [2 of]mmark*\nextlist
                 },
-		xlabel={\tiny Failed nodes},
-		ylabel={\tiny VM Availability (\%)},
-		extra y ticks={99.99}, %if important numbers are missing
+		xlabel={Failed storage nodes},
+		ylabel={VM Snapshot Availability (\%)},
+		extra y ticks={99.9}, %if important numbers are missing
                 mark options=solid,
@@
 		]
-                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_100000.txt};
-                %\addlegendentry{$VO\,6.3$ (optimistic)}
-                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_100000.txt};
-                %\addlegendentry{$VC\,1250$ (estimated)}
-                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_100000.txt};
-                %\addlegendentry{$VC\,2500000$ (worst-case)}
+                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
+                \addlegendentry{$VC\,1250$ (estimated)}
+                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
+                \addlegendentry{$VC\,2500$ (worst-case)}
+                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
+                \addlegendentry{$VO\,6.3$ (optimistic)}
                 %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
@@
 	\end{tikzpicture}
-        %\caption{100000 machine cluster.}
-  \label{fig:vm-availability-100000}
-\end{subfigure}
-    \pgfplotslegendfromname{legend:vm-availability}
-      \caption{Availability of VM backups for VO and VC models for
-          varying degrees of block sharing. Non-PDS replication fixed
-          at 3 and PDS replication increased to 4. VC worst-case
-          is $V=25*p$, and expected-case is $\frac{V}{2}$
+  \caption{Availability of VM backups as nodes fail for VO and VC models for
+  varying degrees of block sharing (i.e. average number of VMs that use a
+  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
+  Graph shown for 100 machine cluster.
   }
   \label{fig:vm-availability}
-
 \end{figure}
@@
 
-Figure\ref{fig:leakage} shows the average accumulated storage leakage resulted by daily
+Figure \ref{fig:leakage} shows the average accumulated storage leakage resulted by daily
 approximate deletions among all VMs. We see the storage leakage ratio is satisfactory: 

### 2013-08-05 snapshot_system/eval1.tex

--- 2013-08-05 snapshot_system/eval1.tex
@@
             \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
-            \legend{VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$),VC (No PDS),VC(MH\,$\sigma=4\%$),VC(MH\,$\sigma=2\%$),VC(MH\,$\sigma=1\%$),SRB};
+            \legend{VC MH( $\sigma=4\%$),VC MH($\sigma=2\%$),VC MH($\sigma=1\%$),VC MH(No PDS),VC($\sigma=4\%$),VC($\sigma=2\%$),VC($\sigma=1\%$),SRB};
             \end{axis}

### 2013-08-05 snapshot_system/snapshot.tex
revise the formula for deletion
update
updated plots

@@
 \hline
+$k$ &  the number of top most popular chunks\\ 
+\hline
 $c$ &  the total amount of data chunks\\ 
@@
 $p$ & the number of machines in the cluster\\
+\hline
+$V$ & the number of VMs on each machine\\
 \hline
@@
             %title={PDS Coverage},
-            %width=\columnwidth,
+            width=\linewidth,
+            height=0.6\linewidth,
             cycle multi list={
@@
             legend style={
-                at={(0.5,-0.2)},
+                at={(0.5,-0.25)},
             anchor=north},

### 2013-08-13 batchdedup/analysis.tex

--- 2013-03-08 hotstorage13/analysis.tex
@@
-\section{ Performance Analysis and Comparison}
-\label{sect:analysis}
+\section{ Old Performance Analysis and Comparison}
+\label{sect:analysis-old}
 
@@
 r  ( c+  u) /b   +r u /m (\alpha_n  p/g  + \alpha_d q/(1-g)  )
-+( x*r *k*u*(1-d_2) + r*u) / b_d  + r* \beta+   2v *r*e \alpha_d /  (m-m_b)
+\]
+\[
++( x*r *k*u*(1-d_2) + r*u) / b_d  + r* \beta+   
+\]
+\[
+2v *r*e \alpha_d /  (m-m_b)
 +2 r *c* (1-d_2) /b_d
@@
 
+\section{New Performance Analysis and Comparison}
+\label{sect:analysis}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{|p{1.25cm}|p{6.5cm}|}
+\hline
+$p$ &  the number of machines in the cluster\\ 
+\hline
+$v$ & the number of VMs per machine. At Alibaba, $v=25$\\
+\hline
+$x$ & is the number of snapshots saved for each VM. At Alibaba, $x=10$\\
+\hline
+%$k$ & the number of iterations to complete all virtual machine backup. Each iteration performs v/k backups.\\
+%\hline
+$t$ & the amount of temporary disk space used per machine for deduplication\\
+\hline
+$m$ & the amount of memory used per machine for deduplication. Our goal is to minimize this\\
+\hline
+$s$ & the average size of virtual machine image. At Alibaba, from our collected data, $s=40GB$\\
+\hline
+$d_1$ & the average  deduplication ratio using segment-based dirty-bit. $d_1=77\%$\\
+\hline
+$d_2$ & the average  deduplication ratio using content chunk fingerprints after segment-based deduplication. For Alaba dataset tested,  $d_2=50$\%\\
+\hline
+$d_3$ & the average number of dup-with-new blocks, as a fraction of $r$ (defined below)\\
+\hline
+$b_r$ & the average disk bandwidth for reading from local storage at each machine\\
+\hline
+$b_w$ & the average disk bandwidth for writing to local storage at each machine\\
+\hline
+$b_b$ & average write bandwidth to back-end storage (block store)\\
+\hline
+$q$ & the number of buckets to accumulate requests at each machine. (total number of buckets is $p*q$)\\
+\hline
+$c$ & the chunk block size in bytes.  In practice $c=4KB$\\
+\hline
+$u$ & the record size of detection request per block.  In practice, $u$=40. That includes block ID and fingerprint\\
+\hline
+$e$ & the size of a duplicate summary record for each chunk block\\
+\hline
+$m_n$ & the memory allocated to network send \& receive buffering. Total network memory is $2m_n$, wich each buffer of size $m_n/p$\\
+\hline
+%$m$ & the maximum memory allocated for deduplication purpose.  A $g$ fraction used for machine-machine network  request buffering and $(1-g)$ fraction used for memory-disk bucket buffering\\
+%\hline
+$\alpha_n$ & the latency for sending a message in a cluster\\
+\hline
+%$\alpha_d$ disk latency\\
+%\hline
+$\beta$ & time cost for in-memory duplicate comparison\\
+\hline
+\end{tabular}
+\caption{Modeling  parameters and symbols.}
+\label{tab:symbol}
+\end{table}
+
+The system keeps at most  $ x$ copies of snapshots for each VM on average.
+The total size of  global content fingerprints is $x*s*v/c*u *(1-d1)*(1-d2)$ where $c$ is the average chunk size and $u$ is the meta data size of each chunk fingerprint.
+In practice $c=4K$ and $u/c$  is about 100.
+$x=10$ in the case of Alibaba cloud.
+
+Define $r = s v (1-d_1)/(ck)$  which is the total number of duplicate detection requests issued at each machine and at each iteration.
+
+We first analyze the time cost of 5 stages assuming an evenly distributed load
+across the machines. Later we analyze the additional costs associated with an
+imbalanced load.
+
+In Stage 1, the dirty segments are read from the virtual disk, the hash of each
+block is computed, and dedup requests are sent to the machine hosting the
+blocks' respective partitions. Since we must read $r$ blocks from disk, send
+$r$ dedup requests, and then save the requests to temporary files (one for each
+parition), the time for the first stage can be expressed as:
+\[
+    b_r r c + \alpha_n\frac{u r}{m_n} + b_w r u
+\]
+
+In Stage 2, each partition index is read from disk, then the dedup requests for
+that paritition are processed and the results are written back out to disk to
+be sent in Stage 3. The results are broken into 3 groups: duplicate blocks, new
+blocks, and dup-with-new blocks, which are duplicates of blocks that are new to
+this batch.
+
+Let $n$ be the total number of index entries in the system.
+$n=(p v x)(1-d_1)(1-d_2)\frac{e}{c}$,
+which represents the index cost for all the deduped data in the system.
+Since each machine holds a constant number $q$ paritions, and the paritions
+should be uniform in size as they are from the hash of the block,
+the total number of index entries at each machine should be $n/p$
+
+The cost of Stage 2 is:
+\[
+    b_r r u + b_r\frac{n e}{p} + r \beta + b_w r e
+\]
+
+In Stage 3 the new block results from Stage 2 are sent to the requesters, and
+in Stage 3b the new blocks are written out to the storage system. We will now
+mostly be dealing with the $r(1-d_2)$ blocks that are new to the system. In 3b
+the dedup results must be read and the actual disk blocks for each new block
+must be re-read before they can be sent to the block store.
+
+The cost of Stage 3 is:
+\[
+    b_r r(1-d_2)e + \alpha_n\frac{e r(1-d2)}{m_n} + b_w r(1-d_2)e
+\]
+and the cost of Stage 3b is:
+\[
+    b_r r(1-d_2)(e+c) + b_b r(1-d_2)c
+\]
+
+After the new blocks have been written to the block store, and references to
+them have been obtained, those references must be returned to the parition
+index holder so that those blocks may be deduped in the future. This Stage 4 (read the new index entries, return them to the parition master, and save the received references) costs:
+\[
+    b_r r (1-d_2)e + \alpha_n\frac{e r(1-d_2)}{m_n} + b_w r(1-d_2)e
+\]
+
+Stage 4b consists of updating the partition index with the new block references
+from Stage 4, and costs:
+\[
+    b_r r (1-d_2)e + b_w r(1-d_2)e
+\]
+
+In the final stage (Stage 5), dup-with-new references are returned to the
+requesters, so that the snapshot recipes may be updated with references to
+those blocks. This process costs:
+\[
+    b_r r d_3 e + \alpha_n\frac{e r d_3}{m_n} + b_w r e
+\]
+
+Memory Requirments:\\
+In every stage we need 1 disk read buffer, And then additionally we need the following:
+\begin{description}
+    \item[Stage 1] network buffers, and $q$ disk write buffers
+    \item[Stage 2] $n/q$ partition index space, and $p$ disk write buffers (for dedup responses)
+    \item[Stage 3] network buffers, $v$ disk write buffers (for dedup responses)
+    \item[Stage 3b] 1 disk write buffer (to write out new blocks)
+    \item[Stage 4] network buffers, $q$ disk write buffers (to write out new refs)
+    \item[Stage 4b] 1 disk write buffer (to update patition index with new blocks)
+    \item[Stage 5] network buffers
+\end{description}
+
 \subsection{A Comparison with Other Approaches}
 
-The memory  space requirement for the data domain approach with bloomer filter is:
+The memory  space requirement for the data domain approach with bloom filter is:
 \[

### 2013-08-14 snapshot_system/snapshot.tex
revise

@@
 %We call this as  the VM-oblivious (VO) approach.
-Our VC design has the following  objectives: 1)  localizing deduplication while identifying a decent amount of
-duplicates among VMs to maintain a competitive deduplication efficiency and simplify snapshot management;
-2) Minimizing the number of file system blocks shared among VMs and adding extra replicas for shared blocks.
+
+%Our VC design has the following  objectives: 1)  localizing deduplication while identifying a decent amount of
+%duplicates among VMs to maintain a competitive deduplication efficiency and simplify snapshot management;
+%2) Minimizing the number of file system blocks shared among VMs and adding extra replicas for shared blocks.
 
@@
 we conduct additional local inner-VM deduplication by comparing
-dirty segment's chunk fingerprints to similar segments from its parent snapshot. 
-For every segment, the minimum value of all its chunk fingerprints is computed during backup
-and is recorded in the snapshot recipe.
+dirty segment's chunk fingerprints within  {\em similar} segments from its parent snapshot. 
+We define two segments are similar if their approximated content signature is the same.
+This segment signature value is defined as the minimum value of all its chunk fingerprints 
+computed during backup and is recorded in the snapshot recipe.
 When we are processing a dirty segment,
 we can easily find similar segments from the
-parent snapshot recipe and load their segment recipes. Then 
-given a set of data chunks within a dirty segement,  we compare  these chunk fingerprints
+parent snapshot recipe and load their segment recipes and also set a limit on the 
+the number of  similar segments to be  searched. 
+ Then 
+given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
 with those in similar segments.  
-For example, with a 2MB segment, there are about 500 fingerprints to compare.
-The amount of memory for maintaining those fingerprints in similar segment s is small, as we only
-load one dirty segment at a time.
+For example, with a 2MB segment, there are about 500 fingerprints to compare. By limiting at most 10 similar
+segments to search,
+the amount of memory for maintaining those fingerprints in similar segment s is small.
+% as we only load one dirty segment at a time.
 

### 2013-08-14 snapshot_system/arch.tex
update graph
update eval

@@
 
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=images/deletion.png, width=3.5in}
+  \caption{Approximate deletion}
+  \label{fig:deletion_flow}
+\end{figure}
+
 In a busy VM cluster, snapshot deletions are as frequent as snapshot creations.
@@
 
-While we can use the standard mark-and-sweep technique~\cite{mark-sweep}, 
+While we can use the mark-and-sweep technique~\cite{Guo2011}, 
 it still takes significant time to conduct this process every time there is a snapshot deletion.
@@
 \item {\bf Approximate deletion with fast summary comparison.}
-Then when there is a snapshot deletion,  
-we need to identify if  chunks to be deleted from one snapshot
+When there is a snapshot deletion,  
+we need to identify if  chunks to be deleted from that snapshot
 are still used by other snapshots. 
-This is done approximately and quickly by comparing the reference pointers of deleted snapshots with
+This is done approximately and quickly by comparing the 
+reference pointers of deleted snapshot with
 the merged reference bloom-filter summary of other live snapshots.
-The merging of live snapshot bloom-filter bits uses the logical OR operator and the merged vector still takes $z$ bits.
-Since the number of live snapshots is limited for each VM (e.g. 10 in the Alibaba's production system), 
+The merging of live snapshot bloom-filter bits uses the logical OR operator 
+and the merged vector still takes $z$ bits.
+Since the number of live snapshots is limited for 
+each VM (e.g. 10 in the Alibaba's production system), 
 the time cost of this comparison is small.
@@
 %to append store's deletion log.
-However, there is a small false-positive ratio which
-would identify unused data as in use, resulting in temporary storage leakage.
+
+If a chunk's reference pointer is not found in the merged summary vector, we are sure that
+this chunk is not used by any live snapshots, thus it's safe delete it. 
+However, among all the chunks that suppose to be deleted, 
+there is a small false-positive ratio which
+would identify unused chunks as in use, resulting in temporary storage leakage.
 
@@
 \frac{L}{U} = \frac{R \Delta u \epsilon}{u+(h-1)\Delta u } > \tau 
-\Longrightarrow R > \frac{\tau}{\epsilon}\frac{u + (h-1)\Delta u}{\Delta u}
+\Longrightarrow R > \frac{\tau}{\epsilon}\times\frac{u + (h-1)\Delta u}{\Delta u}
 \]

### 2013-08-14 snapshot_system/eval1.tex
update eval

@@
 \subsection{Resource Usage}
-{\bf Storage cost of replication.}
 \begin{table}
@@
 
-Table~\ref{tab:replication_cost} shows the total storage space required by VC as the PDS replication degree is changed.
+{\bf Storage cost of replication.} Table ~\ref{tab:replication_cost} shows the total storage space required by VC as the PDS replication degree is changed.
 The increase in storage cost is minimal because the PDS makes up a very small percent of the total storage space, but the increase in reliability can be much more significant (see Figure~\ref{fig:pds-replication}).
@@
 \begin{table}
-    \begin{tabular}{|c|c|c|c|c|}
+    \begin{tabular}{|c|c|c|c|}
     \hline
-    Tasks & CPU & Mem (MB) & Disk W (MB/s) & Network \\ \hline
-    1                      & 19\% & 18.1 & 32.1     &    \\ \hline
-    2                      & 35\% & 31.8 & 53     &    \\ \hline
-    4                      & 63\% & 54.1 & 84     &    \\ \hline
-    6                      & 77\% & 71.9  & 88.5   &     \\ \hline
-    8                      & 82\% & 90.5   & 89.2   &    \\ \hline
-    10                      & 85\% & 97.2   & 90.4   &    \\ \hline
-    12                      & 91\% & 95.6    & 91.5   &   \\ \hline
+    Tasks & CPU & Mem (MB) & Disk W (MB/s) \\ \hline
+    1     & 19\% & 18.1 & 32.1 \\ \hline
+    2     & 35\% & 31.8 & 53 \\ \hline
+    4     & 63\% & 54.1 & 84 \\ \hline
+    6     & 77\% & 71.9 & 88.5 \\ \hline
+    8     & 82\% & 90.5 & 89.2 \\ \hline
+%    10                      & 85\% & 97.2   & 90.4 \\ \hline
+%    12                      & 91\% & 95.6    & 91.5 \\ \hline
     \end{tabular}
-\caption{Resource usage under concurrent backup tasks}
+\caption{Resource usage of concurrent backup tasks in each node}
 \label{tab:resource_usage}
 \end{table}
+
+{\bf Resource usage and its impact to cluster} We further studied the resource usage when running concurrent snapshot backup tasks on each node. 
+Table ~\ref{tab:resource_usage} gives the CPU, memory and disk write workload of running different number of backup tasks at the same time. 
+Notice that memory and CPU used by PDS index and QFS are not included since they belong to the cloud infrastructure services and are shared among many applications.
+We see our hybrid deduplication scheme only occupies small amount of system resources in general, the memory usage is especially small because
+our efficient localized deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in memory for duplicate detection.
 
@@
 perform even better in production clusters, which often have ten or more disks on each node.
+
+Base on the observed performance numbers, even with a single backup task per node and enforcing the disk read speed to
+50 MB/s,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
+ at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.
 

### 2013-08-14 snapshot_system/abs.tex

@@
 can  provide  better fault tolerance while using a small amount of computing and storage resource. 
-This  paper  describes a comparative evaluation of this scheme in  accomplishing a high deduplication 
+This  paper  describes a comparative evaluation of this scheme in  accomplishing a competitive deduplication 
 efficiency while sustaining a good backup throughput.

### 2013-08-14 snapshot_system/challenge.tex
revised

@@
 serves a backup store  for the snapshots.
-The previous study shows that 
- deduplication can compress the backup copies 
-effectively in a 10:1 or even 15:1 rage. 
-Therefore  the portion of space in a cluster
-allocated for snapshots of data should not dominate
-the cluster storage usage.
+%The previous study shows that 
+% deduplication can compress the backup copies 
+%effectively in a 10:1 or even 15:1 rage. 
+%Therefore  the portion of space in a cluster
+%allocated for snapshots of data should not dominate
+%the cluster storage usage.
+%perhaps briefly discuss compression is high, incremental change is small from versions..???
 
@@
 %unmodified data segments for deduplication, which significantly saves cost.
-
 Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
@@
 Another disadvantage of sharing is that it complicates snapshot deletion, 
-which  occurs frequently when snapshots expire regularly and leads a cost concern. 
+which  occurs frequently when snapshots expire regularly. 
 The mark-sweep approach~\cite{mark-sweep} is effective for deletion, and its main cost
@@
 deduplication efficiency, and  can faciltate parallel execition of snaptshot operations.
-Thus we seek for a tradeoff.
+%Thus we seek for a tradeoff.
 
@@
 %when users access snapshots in a recovery process. 
-\item{\bf Management of file system blocks.}
+\item{\em  Management of file system blocks.}
 The file block size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
- a data chunk in a deduplication service is of a nonuniform size with 4KB or 8KB on average.
+ a data chunk in a typical deduplication system is of a nonuniform size with 4KB or 8KB on average.
 %We need to build an intermediate layer that supports large snapshot writing with append operations
@@
 
-We call the classical deduplication approach as   VM-oblivious (VO)
+We call the traditional deduplication approach as   VM-oblivious (VO)
 because they compare fingerprints of snapshots without consideration of VM.
@@
 We are seeking for a tradeoff since 
-cross-VM  signature comparison can deliver additional reduction~\cite{Guo2011,Dong,ExtremeBining}.
+cross-VM  signature comparison can deliver additional compression~\cite{Guo2011,Dong,ExtremeBining}.
 %We are seeking for additional optimization to improve duplication efficiency and design the 
@@
 a bloomer filter  or can fetch on-disk index for additional comparison.
-While this approach is VM-oblivious, we can have adopted some of ideas to build
-bins in a VM to faciliate VM-specific local search.
+While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
+VM-specific local search.
 

### 2013-08-14 snapshot_system/intro.tex

@@
 deduplication, most data chunks are shared by several to many virtual machines.
-Failure of shared data chunks can have a catastrophic effect and many
+Failure of few shared data chunks can have a 
+%catastrophic 
+broad effect and many
 snapshots of virtual machines would be affected.
 The previous work in deduplication focuses on the efficiency and approximation of
-finger print comparison, and has not addressed fault tolerance together with deduplication.
+finger print comparison, and has not addressed fault handling issues  together with deduplication.
 Thus we also seek deduplication options that yield better fault isolation.
@@
 % as well so deletion needs to be considered in system design. 
-sharing of data chunks among oby multiple VMs and their snapshots needs to be detected during
-snapshot   deletion and such dependenec complicates deletion operations. 
+Sharing of data chunks among by multiple VMs needs to be detected during
+snapshot   deletion and such dependence complicates deletion operations. 
 %The additional complexity for deletions
@@
 and by packaging data chunks from the same VM into a file system block as much as possible.
-By narrowing duplicate sharing within a small percent of data chunks,
+By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
 this scheme can afford to allocate extra replicas of these shared chunks for better
-fault resilience.
+fault resilience while sustaining competitive deduplication efficiency.
 Localization also brings the benefits of greater ability to exploit parallelism so

### 2013-08-15 batchdedup/analysis.tex
updates to performance model

@@
 
-The system keeps at most  $ x$ copies of snapshots for each VM on average.
-The total size of  global content fingerprints is $x*s*v/c*u *(1-d1)*(1-d2)$ where $c$ is the average chunk size and $u$ is the meta data size of each chunk fingerprint.
-In practice $c=4K$ and $u/c$  is about 100.
-$x=10$ in the case of Alibaba cloud.
+The system keeps at most  $ x$ copies of snapshots for each VM on average.  The
+total size of  global content fingerprints is $x*s*v/c*u *(1-d1)*(1-d2)$ where
+$c$ is the average chunk size and $u$ is the meta data size of each chunk
+fingerprint. In practice $c=4K$ and $u/c$  is about 100.  $x=10$ in the case of
+Alibaba cloud.
 
-Define $r = s v (1-d_1)/(ck)$  which is the total number of duplicate detection requests issued at each machine and at each iteration.
+Define $r = s v (1-d_1)/(ck)$  which is the average number of detection
+requests made by each machine, and the number of detection requests each
+machine must handle.  We assume the load, i.e., amount of data to backup at
+each machine, is not balanced, so there is also $r_max$, which is the number of
+requests at the most heavily loaded machine. This is the case in the Alibaba
+cluster, with some machines being terabytes while the average machine is 40GB.
 
-We first analyze the time cost of 5 stages assuming an evenly distributed load
-across the machines. Later we analyze the additional costs associated with an
-imbalanced load.
+Here we develop a model for the total backup time, which becomes important in
+trying to minimize the CoW cost during backup \emph{CoW should be explained and
+justified before this point in the paper}.  The backup process can be broken
+into 4 stages, where each stage has two parts, first an all-to-all exchange of
+data, then local processing to prepare for the next stage.
 
-In Stage 1, the dirty segments are read from the virtual disk, the hash of each
-block is computed, and dedup requests are sent to the machine hosting the
-blocks' respective partitions. Since we must read $r$ blocks from disk, send
-$r$ dedup requests, and then save the requests to temporary files (one for each
-parition), the time for the first stage can be expressed as:
+In Stage 1a, the dirty segments are read from the virtual disk, the hash of
+each block is computed, and dedup requests are sent to the machine hosting the
+blocks' respective partitions. Due to the synchronization in each stage, Stage
+1a needs to wait for the most heavily loaded machine to read all it's data - so
+the read stage depends on $r_{max}$, while the write stage, which is balanced
+by the hash partitioning, depends on $r$. We first read $r$ blocks from disk,
+send $r$ dedup requests, and then save the received requests to temporary files
+(one for each parition). The time for the first stage can be expressed as:
 \[
-    b_r r c + \alpha_n\frac{u r}{m_n} + b_w r u
+    r_{max} c + \alpha_n\frac{u r_{max}}{m_n} / b_r + r u / b_w
 \]
 
-In Stage 2, each partition index is read from disk, then the dedup requests for
-that paritition are processed and the results are written back out to disk to
-be sent in Stage 3. The results are broken into 3 groups: duplicate blocks, new
+In Stage 1b, each partition index is read from disk, then the dedup requests
+(from Stage 1a) for that paritition are processed and the results are written
+back out to disk. The results are broken into 3 groups: duplicate blocks, new
 blocks, and dup-with-new blocks, which are duplicates of blocks that are new to
@@
 
-Let $n$ be the total number of index entries in the system.
-$n=(p v x)(1-d_1)(1-d_2)\frac{e}{c}$,
-which represents the index cost for all the deduped data in the system.
-Since each machine holds a constant number $q$ paritions, and the paritions
-should be uniform in size as they are from the hash of the block,
-the total number of index entries at each machine should be $n/p$
+Let $n$ be the total number of index entries at each machine before the backup
+was started.  $n=(v x)(1-d_1)(1-d_2)\frac{e}{c}$. Since each machine holds a
+constant number $q$ paritions, and the paritions are uniform in size as they
+are from the hash of the block, $n$ is very even across the machines, even when
+the vm load is imbalanced.
 
-The cost of Stage 2 is:
+The cost of Stage 1b is:
 \[
-    b_r r u + b_r\frac{n e}{p} + r \beta + b_w r e
+    r u / b_r + (n e)b_r + r \beta + r e / b_w
 \]
 
-In Stage 3 the new block results from Stage 2 are sent to the requesters, and
-in Stage 3b the new blocks are written out to the storage system. We will now
-mostly be dealing with the $r(1-d_2)$ blocks that are new to the system. In 3b
+In Stage 2a the new block results from Stage 1 are sent to the requesters, and
+in Stage 2b the new blocks are written out to the storage system. We will now
+mostly be dealing with the $r(1-d_2)$ blocks that are new to the system (or
+$r_{max}(1-d_2)$ when we must wait for the most heavily loaded machine). In 2b
 the dedup results must be read and the actual disk blocks for each new block
-must be re-read before they can be sent to the block store.
+must be re-read before they can be sent to the block store. The CoW locking on
+the filesystem cannot end until after the dirty data is re-read in Stage 2b.
 
-The cost of Stage 3 is:
+The cost of Stage 2a is:
 \[
-    b_r r(1-d_2)e + \alpha_n\frac{e r(1-d2)}{m_n} + b_w r(1-d_2)e
+    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2)}{m_n} + r_{max}(1-d_2)e / b_w
 \]
-and the cost of Stage 3b is:
+and the cost of Stage 2b is:
 \[
-    b_r r(1-d_2)(e+c) + b_b r(1-d_2)c
+    r_{max}(1-d_2)(e+c) / b_r + r(1-d_2)c / b_b
 \]
@@
 them have been obtained, those references must be returned to the parition
-index holder so that those blocks may be deduped in the future. This Stage 4 (read the new index entries, return them to the parition master, and save the received references) costs:
+index holder so that those blocks may be deduped in the future (and also so
+dup-with-new requests can be handled in this run). This Stage 3a, to read the
+new index entries, return them to the parition index holder, and save the
+received references, costs:
 \[
-    b_r r (1-d_2)e + \alpha_n\frac{e r(1-d_2)}{m_n} + b_w r(1-d_2)e
+    r (1-d_2)e / b_r + \alpha_n\frac{e r(1-d_2)}{m_n} + r(1-d_2)e / b_w
 \]
 
-Stage 4b consists of updating the partition index with the new block references
-from Stage 4, and costs:
+Stage 3b consists of updating the partition index with the new block references
+from Stage 3a, and also updating the dup-with-new results from Stage 1. First
+we load the new references from Stage 2b into memory, and then dedup the
+dup-with-new requests against the new block references and save the dup-with
+new requests back to disk. We then add the new references to the corresponding
+partition index to handle future dedup requests. Stage 3b costs:
 \[
-    b_r r (1-d_2)e + b_w r(1-d_2)e
+    r (1-d_2)e / b_r + r(1-d_2)e / b_w
 \]
 
-In the final stage (Stage 5), dup-with-new references are returned to the
+In the final stage (Stage 4), dup-with-new references are returned to the
 requesters, so that the snapshot recipes may be updated with references to
@@
 \[
-    b_r r d_3 e + \alpha_n\frac{e r d_3}{m_n} + b_w r e
+    r d_3 e / b_r + \alpha_n\frac{e r d_3}{m_n} + r e / b_w
 \]
@@
 \begin{description}
-    \item[Stage 1] network buffers, and $q$ disk write buffers
-    \item[Stage 2] $n/q$ partition index space, and $p$ disk write buffers (for dedup responses)
-    \item[Stage 3] network buffers, $v$ disk write buffers (for dedup responses)
-    \item[Stage 3b] 1 disk write buffer (to write out new blocks)
-    \item[Stage 4] network buffers, $q$ disk write buffers (to write out new refs)
-    \item[Stage 4b] 1 disk write buffer (to update patition index with new blocks)
-    \item[Stage 5] network buffers
+    \item[Stage 1a] network buffers, and $q$ disk write buffers
+    \item[Stage 1b] $n/q$ partition index space, and $p$ disk write buffers (for dedup responses)
+    \item[Stage 2a] network buffers, $v$ disk write buffers (for dedup responses)
+    \item[Stage 2b] 1 disk write buffer (to write out new blocks)
+    \item[Stage 3a] network buffers, $q$ disk write buffers (to write out new refs)
+    \item[Stage 3b] 1 disk write buffer (to update patition index with new blocks)
+    \item[Stage 4] network buffers, $v$ disk write buffers
 \end{description}

### 2013-08-15 batchdedup/analysis.tex
Updated performance model

@@
 \[
-    r_{max} c + \alpha_n\frac{u r_{max}}{m_n} / b_r + r u / b_w
+    r_{max} c / b_d + \alpha_n\frac{p u r_{max}}{m_n} + r u / b_w
 \]
@@
 \[
-    r u / b_r + (n e)b_r + r \beta + r e / b_w
+    r u / b_r + n e / b_r + r \beta + r e / b_w
 \]
@@
 \[
-    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2)}{m_n} + r_{max}(1-d_2)e / b_w
+    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2) p}{m_n} + r_{max}(1-d_2)e / b_w
 \]
@@
 \[
-    r (1-d_2)e / b_r + \alpha_n\frac{e r(1-d_2)}{m_n} + r(1-d_2)e / b_w
+    r_{max} (1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d_2) p}{m_n} + r(1-d_2)e / b_w
 \]
@@
 we load the new references from Stage 2b into memory, and then dedup the
-dup-with-new requests against the new block references and save the dup-with
-new requests back to disk. We then add the new references to the corresponding
+dup-with-new requests against the new block references. Once the dup-with-new
+results have chunk references, we can add the dup-with-new results to the
+duplicate result files. We then add the new references to the corresponding
 partition index to handle future dedup requests. Stage 3b costs:
 \[
-    r (1-d_2)e / b_r + r(1-d_2)e / b_w
+    r ((1-d_2) + d_3)e/b_r + r (1-d_2)\beta + r((1-d_2) + d_3)e / b_w
 \]
 
-In the final stage (Stage 4), dup-with-new references are returned to the
-requesters, so that the snapshot recipes may be updated with references to
-those blocks. This process costs:
+In the final stage (Stage 4), all duplicate references (including the
+dup-with-new references from 3b) are returned to the requesters, so that the
+snapshot recipes may be updated with references to those blocks. This process
+costs:
 \[
-    r d_3 e / b_r + \alpha_n\frac{e r d_3}{m_n} + r e / b_w
+    r d_3 e / b_r + \alpha_n\frac{e r_{max} d_3 p}{m_n} + r e / b_w
 \]
 
-Memory Requirments:\\
-In every stage we need 1 disk read buffer, And then additionally we need the following:
-\begin{description}
-    \item[Stage 1a] network buffers, and $q$ disk write buffers
-    \item[Stage 1b] $n/q$ partition index space, and $p$ disk write buffers (for dedup responses)
-    \item[Stage 2a] network buffers, $v$ disk write buffers (for dedup responses)
-    \item[Stage 2b] 1 disk write buffer (to write out new blocks)
-    \item[Stage 3a] network buffers, $q$ disk write buffers (to write out new refs)
-    \item[Stage 3b] 1 disk write buffer (to update patition index with new blocks)
-    \item[Stage 4] network buffers, $v$ disk write buffers
-\end{description}
+%Memory Requirments:\\
+%In every stage we need 1 disk read buffer, And then additionally we need the following:
+%\begin{description}
+%    \item[Stage 1a] network buffers, and $q$ disk write buffers
+%    \item[Stage 1b] $n/q$ partition index space, and $p$ disk write buffers (for dedup responses)
+%    \item[Stage 2a] network buffers, $v$ disk write buffers (for dedup responses)
+%    \item[Stage 2b] 1 disk write buffer (to write out new blocks)
+%    \item[Stage 3a] network buffers, $q$ disk write buffers (to write out new refs)
+%    \item[Stage 3b] 1 disk write buffer (to update patition index with new blocks)
+%    \item[Stage 4] network buffers, $v$ disk write buffers
+%\end{description}
 

### 2013-08-16 batchdedup/analysis.tex
Updated performance model
Updated batchdedup model

@@
 
-Define $r = s v (1-d_1)/(ck)$  which is the average number of detection
+Define $r = s v (1-d_1)/c$  which is the average number of detection
 requests made by each machine, and the number of detection requests each
@@
 \[
-    r_{max} c / b_d + \alpha_n\frac{p u r_{max}}{m_n} + r u / b_w
+    r_{max} c / b_r + \alpha_n\frac{p u r_{max}}{m_n} + r u / b_w
 \]
@@
 the dedup results must be read and the actual disk blocks for each new block
-must be re-read before they can be sent to the block store. The CoW locking on
-the filesystem cannot end until after the dirty data is re-read in Stage 2b.
+must be re-read before they can be sent to the block store. To avoid seeking
+we have found it faster to simply re-read all the dirty data and ignore the
+duplicate blocks rather than find only the new blocks on disk. The CoW locking
+on the filesystem cannot end until after the dirty data is re-read in Stage 2b.
 
@@
 \[
-    r_{max}(1-d_2)(e+c) / b_r + r(1-d_2)c / b_b
+    r_{max}c / b_r + r_{max}(1-d_2)e / b_r + r(1-d_2)c / b_b
 \]
@@
 \[
-    r d_3 e / b_r + \alpha_n\frac{e r_{max} d_3 p}{m_n} + r e / b_w
+    r d_2 e / b_r + \alpha_n\frac{e r_{max} d_2 p}{m_n} + r e / b_w
 \]

### 2013-08-25 snapshot_system/abs.tex
revise the analysis

@@
 This paper proposes a VM-centric collocated backup service that  
-localizes deduplication as much as possible within each virtual machine
-and associates  underlying file blocks with one VM for most of cases.
+localizes deduplication as much as possible within each virtual machine using similarity-guided
+search and associates  underlying file blocks with one VM for most of cases.
+It restricts cross-VM deduplication under common blocks with extra replication support.
 Our analysis shows that  this VM centric scheme 

### 2013-08-25 snapshot_system/failover.tex
Fixed figure showing FSBs per VM
revise the analysis

@@
     \centering
-    \subfigure[Sharing of data under VM-oblivious dedup model]
+    \subfigure[Sharing of data under VM-centric dedup model]
     {
@@
     \\
-    \subfigure[Sharing of data under VM-centric dedup model]
+    \subfigure[Sharing of data under VM-oblivious dedup model]
     {
@@
     }
-    \caption{Difference of sharing data under VO and VC approaches}
+    \caption{Bipartite association of VMs and file blocks under VO and VC approaches}
     \label{fig:share}
@@
 In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
-Notice that the ratio of non-PDS data size vs PDS data size for each VM is
+The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
+$ k*r_c  + (c_u-k)*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
 \[
-\sigma=  \frac{c*\delta(1 -   (\frac{k}{c_u})^{1-\alpha})} {k}.
+\sigma \frac{r_c}{r} + 1-\sigma
 \]
+Since $sigma$ is small,  term $\sigma \frac{r_c}{r}$ is small in the above expression.  
+Thus the impact on storage increase is very small when we choose a large $\frac{r_c}{r}$ ratio. 
+For example, $\frac{r_c}{r}=2$.
 
-Thus  storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
-\[ k*r_c  + k*\sigma *r.
-\]
+%In our experiment with Alibaba data, the ratio $\sigma$ 
+%is 162. Thus allocation of extra replicas for PDS only introduces a small amount of extra space
+%cost.  Figure~\ref{fig:storagePDS} shows the storage cost ratio of VC and VO when 
+%$r$=3, and $r_c$ varies from 3 to 10.
+%The result shows that the storage cost for adding extra replication for PDS
+%is insignificant.
 
-In our experiment with Alibaba data, the ratio $\sigma$ 
-is 162. Thus allocation of extra replicas for PDS only introduces a small amount of extra space
-cost.  Figure~\ref{fig:storagePDS} shows the storage cost ratio of VC and VO when 
-$r$=3, and $r_c$ varies from 3 to 10.
-The result shows that the storage cost for adding extra replication for PDS
-is insignificant.
-
-Next we  compare the impact of losing $d$ machines 
+Next we  assess  the impact of losing $d$ machines 
 to the the VC and VO approaches.  
+A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of snapshot blocks.
 
@@
 %Thus the number of VMs using a block =    $(1-s_c)  + s_c *L$.
-In characterizing the reliability of VM backups in our model, 
-we consider the likely hood that a file system block fails,
-given some number of storage machine failures. 
-Every time a filesystem block fails,
-we say that we have lost data for that virtual machine, so it is no longer
-available. 
-In reality it may be only one snapshot that is affected, but it is the user
-who must decide which snapshots are important, so we consider the worst case. 
+%In characterizing the reliability of VM backups in our model, 
+%we consider the likely hood that a file system block fails,
+%given some number of storage machine failures. 
+%Every time a filesystem block fails,
+%we say that we have lost data for that virtual machine, so it is no longer
+%available. 
+%In reality it may be only one snapshot that is affected, but it is the user
+%who must decide which snapshots are important, so we consider the worst case. 
 We use filesystem blocks rather than a deduplication
@@
 %a 64MB block size).
+To  compute the full availability of all snapshots of a VM, we derive
+the probablity of losing a snapshot file block of a VM by
+estimating the number of file system blocks per VM in each approach.
+As illustrated in Figure~\ref{fig:share},
+we build a bipartite graph representing the association from unique file system blocks
+to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
+if this block is used by this VM. 
+For VC, each VM has an 
+average number of $N_1$ file system blocks for non-PDS data. 
+It also refers  an average of   $N_2$ file system blocks for PDS data. 
+For VO, each VM has an average  of  $N_o$ file system blocks
+and let $V_o$ be the average number of VMs shared by each file system block.
+%Figure~\ref{fig:shared} illustates the bipartite association.
 
-To  compute the probablity of losing snapshots of a virtual machine, 
-we estimate the number of file system blocks per VM in each apporach.
-We can build a bipartite graph representing the association from unique file system blocks
-to their corresponding VMs. An association edge is  drawn  from a file block  to a VM 
-if this file is used by this VM. 
-For VC, each VM has an 
-averge number of $N_1$ file system blocks for non-PDS data. 
-It also refers  an average of   $N_2$ file system blocks for PDS data 
-For VO, each VM has an average  of  $N_o$ file system blocks
-and let $V_o$ be the averge number of VMs shared by each file system block.
-Figure~\ref{fig:shared} illustates the bipartite association.
-
-In VC, each non-PDS file system block is associated with one VM while PDS file system blocks are
-shared among VMs  (at most $V$ VMs). Thus, 
+In VC, each non-PDS file system block is associated with one VM
+ and  PDS file system blocks are
+shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block. Thus, 
 \[
-V *N_1 *s  = pD  \frac{\delta} {\delta +1} \; \mbox{ and } \; 
-V *N_2 *s  \leq pD  \frac{1} {\delta +1} *V.
+V *p*N_1 *s  = C_u (1-\sigma)\; \mbox{ and } \; 
+V *p*N_2 *s  = C_u \sigma *V_c
 \]
@@
 \[
-V *N_o *s  = pD  V_o.
+V *p*N_o *s  = C_u  V_o.
 \]
-Then
+
+Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
+each file block contains the hot low-level chunks shared by many VMs, and it also contains
+rare chunks which are not shared.  From the about equations.
 \[
-N_1= \frac{pD \delta} {V s (\delta +1)},\; 
-N_2 \leq \frac{pD } {s (\delta +1)}, \; 
-\mbox{and} \; N_o = \frac{pD V_o } {s V}.
+\frac{N_1}{N_o}=  \frac{1-\sigma}{V_o}<1.
 \] 
-Since each file block (with default size $s=64MB$) contains many chunks (on average 4KB),
-each file block contains the hot low-level chunks shared by many VMs, and it also contains
-rare chunks which are not shared.
+Thus when there is a failure in file blocks with replication degree $r$
+and there is no failure for PDS data with more replicas,   a VM in
+the VC approach has a lower chance to lose a snapshot than the VO approach because
+$N_1<N_o$. 
 Figure~\ref{fig:fsb-links} shows the number of VMs sharing by each file block.
-In our experiment, we find that $V_o \approx 0.2 V$ when backing up VMs one by one.
-We can observe in Figure~\ref{fig:vm-links} that $N_1 +N_2 < N_o$.
-This is likely because the PDS FSBs tightly pack data used by many VMs, which decreases the overall number of FSBs required to backup a VM.
+%In our experiment, we find that $V_o \approx 0.2 V$ when backing up VMs one by one.
+We can observe that $N_1 +N_2 < N_o$. 
+This is likely because the PDS FSBs tightly pack data used by many VMs, 
+which decreases the overall number of FSBs required to backup a VM.
 If  the backup for multiple VMs is conducted concurrently, there would be more
-VMs shared  by each file block on average.
+VMs shared  by each file block on average. Therefore,
+even when there is a loss of a PDS block, the VC approach tolerates the fault better.
 
-Figure~\ref{fig:fsb-links} shows the average number of VMs sharing a
-filesystem block (FSB) as VMs are added. Though we don't expect the linear trend to continue indefinitely for
-much larger datasets, it should continue to increase, which has important implications
-on VM backup availability in the precense of failures. Below we show the
-significant impact the number of links has on VM backup reliability.
+%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing a
+%filesystem block (FSB) as VMs are added. Though we don't expect the linear trend to continue indefinitely for
+%much larger datasets, it should continue to increase, which has important implications
+%on VM backup availability in the precense of failures. Below we show the
+%significant impact the number of links has on VM backup reliability.
 
@@
                 width=\linewidth,
-                height=0.7\linewidth,
+                height=0.6\linewidth,
 		%title={VO FSB links},
@@
                 width=\linewidth,
-                height=0.7\linewidth,
+                height=0.6\linewidth,
 		xlabel={Number of VMs},
@@
 \end{figure}
-The snapshot availability of is a VM is the likelyhood that
-there is no  data loss for all its file blocks.
-With replication degree $r$, the likelyhood of
-a file block block is the probability that  
-all of its replicas appear in $d$ failed machines. 
-Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.
 
-When there are $r \le d<r_c$ machines failed and then there is no PDS data loss,  
+ The full snapshot availability of a VM is estimated as follows with parameters $N_1$, $N_2$, and $N_o$.
+%the likelyhood that there is no  data loss for all its file blocks.  
+With replication degree $r$, the availability of a file block is the probability that  
+all of its replicas do not appear in any group of $d$ failed machines. 
+Namely, $1-\binom{d}{r}/ \binom{p}{r}$. 
+The snapshot availability of a VM  in the VO approach is
+\[ 
+(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
+\]
+%This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.
+When there are $r \le d<r_c$ machines failed,  there is no PDS data loss and  
 %a file block failure depends on if all replicas of this container reside in the failed machines.
-the snapshot avaiability of a VM in the VC approach is 
+the full snapshot availability of a VM in the VC approach is 
 and is
@@
 %\end{split}
+Since $N_1 <N_o$, the VC approach has a higher availability of VM snapshots than VO.
 
 When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
-The snapshot availability of  a VM in the VC approach is
+The full snapshot availability of  a VM in the VC approach is
 \[
@@
 \]
+Both conditions $N_1+N_2 <N_o$ 
+and  $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
+< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
+support the higher availability of VC.
 %= Probability(\mbox{ No non-PDS file block loss})^{N_1}
@@
 %\end{multline}
-
-The snapshot availability of a VM  in the VO approach is
-\[ 
-(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
-\]
 
@@
 }
+\comments{
 \begin{figure}[htbp]
@@
                 width=\linewidth,
-                height=0.7\linewidth,
+                height=0.6\linewidth,
             %title={FSB Availability},
@@
 \end{figure}
-
-\comments{
-We use the following parameters  during the analysis
-\begin{itemize}
-\item 	$V$ is the number of VMs. $m$ is the number of physical machines hosting the backup storage.
-$d$ is the number of machines failed.
-\item In the VC approach, $s_c$  of them in the backup storage
-are shared by others with a zipf distribution. $(1-s_c)$ 
-of them  is unique (nobody shares with them).
-$L_c$ is the average number of VMs sharing a block (if it is in PDS for the VC approach.
-$b_c$ is the number of shared blocks in VC.
-\item In the VO approach, $s_o$ is the number of blocks shared.
-$L_o$ is the average number of VMs sharing a block. 
-\item $b$ is the  number of blocks stored in the storage after deduplication.
- \end{itemize}
-
-The distribution of data blocks shared among VMs in VC follows a zipf distribution.
-Given a VM block, the probability of being rank $x$ block is $P(x) = P(1) * x^{-\alpha}$
-where $P(1)$ is the probability of being rank 1 most popular block.
-Since $\sum P(x)= 1$, $P(1)= \frac{1}{\sum_1^{b_c} x^{-\alpha} }$.
-Let $y$ be the number of VMs sharing rank $x$ block in VC, and  then  $y= V* P(x)$.
-
-Thus the average number of VMs sharing a data block in the VC backup storage is:
-\begin{equation}
-%\begin{align}
-\begin{split}
-L_c& =  (1-s_c)*1 + s_c \sum_1^{b_c} P(x) * y \\
-& =  (1-s_c)*1 + s_c \sum P(1)^2 *  x^{-2\alpha} *  V.
-\end{split}
-%\end{align}
-\end{equation}
-
-Under $d$ failed machines, the  expected number of VMs 
-which suffer from data loss in VC is
-\begin{multline}
-%\begin{split}
- \sum_{1}^{V}  ( Probability (\mbox{ a VM fails)}) \\
-= \sum_{1}^{V}  ( 1- Probability (\mbox{ a VM has no data loss)}) \\
-= V ( 1-  Probability(\mbox{ A block has no data loss} )^{L_c} ).
-%\end{split}
-\end{multline}
-
-%Thus the number of VMs using a block =    $(1-s_c)  + s_c *L$.
-
-When there are $d$ machines failed and the probability of
-a block failure depends on if all replicas of this block reside in the failed machines.
-When $r< d <r_c$,  only unshared data blocks can fail in VC. Then
-%Probablity(\mbox { no loss for this  block}) = 1 - Probability (\mbox{ this block in d failed machiens})
-\begin{multline}
-%\begin{split}
-Probability(\mbox{ A block has data loss})\\
-= (1-s_c) (1- Probability (\mbox{ this block in d failed machines}))\\
-= (1-s_c) (1- \frac{ \binom{d}{r}} { \binom{m}{r} }).
-%\end{split}
-\end{multline}
-When $r_c \leq d$, shared data blocks in VC can have a loss. 
-\[
-Probability(\mbox{A block has data loss})
-= 
-(1-s_c) (1- \frac{ \binom{d}{r}} { \binom{m}{r} })
-+ s_c (1- \frac{ \binom{r_c}{d}} { \binom{m}{r_c} }).
-\]
-
-By comparison, under $d$ failed machines, the  expected number of VMs 
-which suffer from data loss in VO is
-\[
-V ( 1-  (1- \frac{ \binom{d}{r}} { \binom{m}{r} })^{L_o} ).
-\]
-where
-\[
-L_o = (1-s_o) + s_o \sum_1^b  P(1)^2 *  (x')^{-2\alpha'} *V.  
-\]
-
-%the above model assumes uniform distribution of blocks and doesn't provide compelling numbers
-%with 3 replicas, 100 machines, and only 3 failures the chance of a single 10GB VM surviving is 9.11*10^-8
-%if we wanted to include it we probably want a model that includes containers, but that might be too complex
-%to be useful.
 }
-
-\comments{
-	=  sum _for_all_block(   Probablity (a block fails) *number of VM sharing this block ))
-               = Probability(a block fails) * sum_for_all_blocks (numb of VM shared)
-	= Probablity (a block fails) *b *aveageLengthVM
-	= [ 1-  C(r, k) /C(n,r)] * b* [ 1+ s *V(1-1/ln V)]
-
-----------------------------------------------------------------------
-
-\subsection{Empirical Validation}
-%To validate our theoritical model for the probability of data loss, we computed
-%the number of snapshots using each block in a global index for the 350 snapshot
-%traces. As you can see in Fig.~\ref{??}, The average number of VMs sharing a block
-%%TODO: insert figure generated from data/links_no_cds.dat
-%increases linearly with the number of snapshots. For 350 snapshots there are an
-%average of 13.1 links to a given block in the global index.
-To validate our theoretical model for the probability of data loss, we measured
-the number of snapshots and VMs sharing data blocks for our 350 snapshot
-dataset. As you can see in Fig.~\ref{??}, the average number of snapshots sharing
-a block increases linearly with the number of snapshots. For 350 snapshots
-there are an average of 13.1 incoming links to a given data block in the global
-index. If we look at the number of VMs sharing a data block rather than
-snapshots, in the full dataset on average 1.47 VMs point to a data block in the
-index.
-%What else do we need from the simulation to validate the model?
-
-\subsubsection{PDS and Fault Tolerance}
-%all numbers in this paragraph need to be corrected after I re-run the tests
-%using the actual cds generator code
-As part of our emprirical validation of our model, we also computed the effects
-of the PDS on fault tolerance. If we exclude the top 5\% most popular blocks
-and set aside those in the PDS, the average number of links to a non-PDS block
-%TODO: insert figure generated from data/links_cds.dat and data/links_wo_cds.dat
-drops to 10.3 for 350 snapshots. This means that on average, \~3 fewer
-snapshots will be affected by a lost data block in the general data store.
-The average number of links to a PDS block however, for 350 snapshots, is
-65.7. This suggests that a much higher replication factor is warranted for
-the PDS, as on average, a PDS block appears in \~20\% of all the snapshots.
-These measured numbers are different from our theoritical model due to the fact
-that duplicate data blocks are not uniformly distributed across all VMs.
-With uniform distribution of duplicates (and a zipf distribution on the number
-of duplicates), there should be on average 2.55 incoming VM links to each
-block. Since we show the average number of links to be 1.47 in our actual
-traces, the duplicates are
-more tighly grouped than the uniform model would predict. This supports
-the benefits of using a PDS plus more localized deduplication.
-
-The PDS gives a clear boundary for setting different replication factors,
-And our tests suggest that by separating the replication factor for the PDS
-and non-PDS blocks, greater fault tolerance can be acheived.
-
-----------------------------------------------------------------------
-
-For PDS model, 85\% blocks are using the data from the same VM while upto 10\% data is for PDS (we actually only use 5% perhaps).  Thus the overall speaking, at most 10% of data are shared.
-Thus  for PDS approach,   the # VM failure caused by k machines is at most  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.10 *V(1-1/ln V)].
-For original approach,  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.90 *V(1-1/ln V)].
-For large V, the reliability improves by 9 times.
-}

### 2013-08-25 snapshot_system/snapshot.tex
revise the analysis

@@
 
-We analyze how the choice of value  $k$ impacts the deduplication efficiency.
+Choosing the value  $k$ for the most popular chunks affects the deduplication efficiency.
 %It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
@@
 %\subsubsection{Impact of PDS deduplication}
-The analysis is based on the characteristics  of the VM snapshot traces
-studied from  Alibaba's production user data.
+We analyze this impact based on the characteristics  of the VM snapshot traces
+studied from  application datasets.
 Our previous study shows that the popularity of data chunks after inner VM deduplication follows 
@@
  \includegraphics[width=3in]{figures/log-log-disk}
-\caption{Duplicate frequency versus  chunk ranking in a log scale.}
+\caption{Duplicate frequency versus  chunk ranking in a log scale after inner-VM deduplication.}
 \label{fig:Datazipf}
@@
 \hline
-$k$ &  the number of top most popular chunks\\ 
+$k$ &  the number of top most popular chunks selected for deduplication\\ 
 \hline
@@
 \hline
-$\sigma$ &  the number of unique non-PDS chunks over  the number of the PDS chunks.\\
+$\sigma$ & =$\frac{k}{c_u}$.  The percentage of unique data  belong to  PDS.\\
 \hline
@@
 \hline
-$V$ & the number of VMs on each machine\\
-\hline
-$D$ & the amount of unique data on each machine\\
-\hline
-$C$ & the average data chunk size. Our setting is  4K.\\
-\hline
-$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
-\hline
-$m$ & memory size on each node used by VC\\ 
-\hline
-$E$ & the size of an popular data index entry\\
+$V$ & the average number of VMs hosted on each machine\\
+%\hline
+%$D$ & the amount of unique data on each machine\\
+%\hline
+%$C$ & the average data chunk size. Our setting is  4K.\\
+%\hline
+%$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
+%\hline
+%$m$ & memory size on each node used by VC\\ 
+%\hline
+%$E$ & the size of an popular data index entry\\
 \hline
@@
 By Zipf-like distribution, $f_i = \frac{f_1}{i^\alpha}.$
-Since $ \sum_{i=1}^{c_u}f_i = c$,
+Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
 \[
@@
 f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
-f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}.
+f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}
+=c(1-\delta) \sigma^{1-\alpha}.
 \]
@@
 \begin{equation}
+\label{eq:dedupeff}
 %\begin{split}
 %e_k &= 
-\frac{ c(1-\delta) + f_1\frac{  k^{1-\alpha}} {1-\alpha}} 
-{c(1-\delta)  + \delta c - c_u }\\
-= 
-\frac{ (1-\delta) + \delta  (\frac{k}{c_u})^{1-\alpha}}
-{ 1- \frac{c_u}{c} }.
+\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
+{c  - c_u }\\
 %\end{split}
@@
 %[Describe the dedup efficiency model in detail]
-Let $p$ be the number of physical machines in the cluster, $m$ be the memory on each node used by the popular
-index, $E$ be the size of an index entry,
-$D$ be the amount of unique data on each physical machine, and 
-$C$ be the average chunks size. We store the popular index using a distributed shared memory hashtable
-such as MemCacheD.  Then $k$ and $c_u$ can be expressed as:
-$
-k = p*m/E$, and $c_u = p*D/E.
-$
+%Let $p$ be the number of physical machines in the cluster, $m$ be the memory on each node used by the popular
+%index, $E$ be the size of an index entry,
+%$D$ be the amount of unique data on each physical machine, and 
+%$C$ be the average chunks size. 
+%Then $k$ and $c_u$ can be expressed as:
+%$ k = p*m/E$, and $c_u = p*D/E.  $
+We store the popular index using a distributed shared memory hashtable such as MemCacheD
+and allocate a fixed percentage of memory space   per physical machine for top $k$ popular items.
+As the number of physical machines ($p$) increases,
+the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
+a constant because each physical machine on average still hosts a fixed constant number of 
+VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
+remains to be a constant.
+Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.
 
-The overall deduplication efficiency of VC is
-\[
-\frac{ (1-\delta) + \delta (\frac{m*C}{D*E})^{1-\alpha}}
-{ 1- \frac{c_u}{c} }.
-\]
-where $(\frac{m*C}{D*E})^{1-\alpha}$ represents the percentage of the remaining
-chunks detected as duplicates after inner VM deduplication.
-Figure~\ref{fig:cds-coverage} shows measured PDS coverage in our 35 VM dataset.
-You can see from the graph that the coverage actually increases as the data size
-increases, which indicates that $\alpha$ increases with the data size (a
-fixed-$\alpha$ model would predict constant coverage). This makes the PDS even
-more effective, as the coverage of the PDS increases as more data is added.
+%where $(\frac{m*C}{D*E})^{1-\alpha}$ represents 
+Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
+chunks detected as duplicates in global cross-VM deduplication due to PDS.
+We call it PDS coverage.
+Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed as
+0.65 and measured PDS coverage in our test dataset.
+$\sigma=2\%$ represents that 100MB memory is used per machine for top $k$ PDS.
+While the predicted value remains flat, the  real coverage actually increases as the data size
+increases, which indicates that $\alpha$ increases with the data size. 
+Thus in practice, the coverage of the PDS increases as more VMs are involved.
 %Then the deduplication efficiency of PDS approach using top k most popular fingerprints is:
@@
     \end{tikzpicture}
-  \caption{fixed-alpha predicted vs. actual PDS coverage as data size increases.}
+  \caption{Predicted vs. actual PDS coverage as data size increases.}
   \label{fig:cds-coverage}
@@
 
-As illustrated in Figure~\ref{??},
-when the number of machines at each cluster increases, the number of total VMs increases.
-Then $k$ increases since more memory is available to host the popular chunks index.
-But for each physical machine, the number of VMs remains the same, and thus
-$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
-a constant.
+%As illustrated in Figure~\ref{??},
+%when the number of machines at each cluster increases, the number of total VMs increases.
+%Then $k$ increases since more memory is available to host the popular chunks index.
+%But for each physical machine, the number of VMs remains the same, and thus
+%$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
+%p constant.

### 2013-08-25 batchdedup/scheduling.tex

\section{Round Scheduling}
\label{sect:scheduling}
The simplest way to take advantage of the efficiency of batch processing is to
schedule all the work to be done in one round.  This works well if all of the
data being backed up is just copies (e.g. a separate backup system which data
is sent to over the network), however in our case we are backing up the
original virtual disk, which may still be in use during the snapshot. This adds
extra complexity to our cost analysis, because we must now also consider the
cost of maintaining a constistent view during the snapshot process. We use the
Copy on Write (CoW) provided by the virtual disk manager. With CoW, the
duration of the backup affects how much data must be copied. Other studies have
shown that as much as 8\% or even more of total capacity must be reserved for
Cow \cite{EMCIncrementalDataChanges}. The actual cost of CoW is a factor of the
data size, the write rate, and duration CoW is taking place. The data size
isn't something we can change, nor the write rate, but we can minimize the
duration that a given VM is undergoing CoW. We assume a poisson distribution of
writes (which closely fits the meaured results from
\cite{EMCIncrementalDataChanges}), and then try to minimize the CoW cost using
our performance and CoW model. Although the single batch schedule completes the
backup in the smallest amount of time, it also has the greatest CoW cost
because the most processing must be done before any VM can release the CoW
lock.

The way to decrease the CoW cost is to break up the backup into multiple
rounds, where in each round the CoW cost is minimized. The more rounds there
are the shorter each round can be and therefore the smaller the CoW cost. The
more rounds there are however the greater the backup overheads and some of the
efficiency gained from batch processing is lessened. We balance these costs by
setting a time limit on the whole backup job, and then develop an algorithm to
schedule VMs into rounds.

With these goals a model that closely fits our goals is the dual version of the
bin packing problem. In standard bin packing the goal is to fit all of the
items into as few bins as possible, without overfilling any bins. In the dual
version of the problem however as many bins as possible are to filled to at
least some minimum level. In our problem the constraint is to keep the total
cost of the schedule under a time limit rather than a minimum bin level. We
adapt an algorithm for dual bin packing\cite{DualBinPacking} to fit our VM
scheduling problem. The algorithm adapted is called iterated A and works by
iteratively callng a bin packing heuristic A with the VMs to be scheduled and
the number of rounds, using binary search to arrive at the best number of
rounds. A(I,N) is defined to return the optimality of packing set I into N bins
using A. We take this basic idea and look at several VM packing heuristics to
arrive at an efficient packing algorithm. More formally, our adaptation of the
iterated A algorithm can be defined as:

\begin{lstlisting}
Set UB=min(n,2*v)
Set LB=1
while UB>LB
    set N = (UB+LB+1)/2
    if A(machines,N) > T, set UB=N-1
    else set LB=N
Halt
\end{lstlisting}
where A(I,N) returns the total backup time of the schedule\\
return packing generated by A(machines,UB) after loop finishes

This general algorithm relies on a good choice of A to arrive at an efficent
packing. Our first VM packing heuristic, A0, is very close to the algorithm for
the dual bin packing paper.

A0:
\begin{lstlisting}
sort VMs in descending order by size
while there is an unscheduled VM
    pick the first unscheduled VM a
    pick the round with the current
        lowest runtime b
        tie-breaker:left-most round
    schedule VM a to round b
Halt
\end{lstlisting}

A0 decreases CoW cost (see Table~\ref{tab:schedule-costs}), but has room for
improvement. The first issue is that the round with the current lowest runtime
is chosen.  Because backup time is dependent on a combination of the highest
machine load and average machine load, if we add a VM to the currently most
loaded machine in a round it will increase runtime much more than if we add the
VM to a currently empty machine on an equally heavily loaded round
\textit{(maybe a figure to show this?)}. Therefore a better scheduling would be
obtained if we pick the round with the lowest runtime after we simulate adding
the new VM to that round. This new round picking heuristic takes into account
that the same VM might have different affects on different rounds.

Another improvement we can make is to the VM picking heuristic.

### 2013-08-26 snapshot_system/arch.tex
revise arch.tex

@@
 A distributed file system (DFS) manages  the physical disk storage and we use 
-QFS~\cite{QFS}. 
+an open source DFS called QFS~\cite{QFS}. 
 All data needed for VM services, such as virtual disk images used by runtime VMs,
 and snapshot data for backup purposes, reside in this distributed file system. 
-One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
+One physical node hosts tens of VMs, each of which accesses its virtual machine disk image through the
 virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
-
-\comments{
-\begin{description}
-\item[Distributed file system] This is a scalable distributed file system (DFS) being optimized for many large and sequential reads or appends.
-DFS holds the responsibility of managing physical disk storage
-in the cloud. 
-All data needed for VM services, such as virtual disk images used by runtime VMs,
-and snapshot data for backup purposes, reside in this distributed file system. 
-%\item[KV]: a distributed key-value store for managing structured data.
-%\item[MapReduce]: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
-\item[Distributed memory cache]: A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inquiries. 
-\end{description}
-
-In addition, our implementation also uses MapReduce to facilitate the offline
-data processing, and stores a small amount of snapshot metadata in a 
-BigTable-like persistent key-value store.
-
-%[describe the benefits of using mature cloud technologies]
-In general, our snapshot system and the virtual machine management service 
-rely on these fundamental cloud services
-to be functional. Such a co-located deduplication architecture allow us 
-to enjoy the benefits from these mature technologies 
-such as load balancing, scalability, and fault tolerance.
-Moreover, all the above cloud services can easily find their open-source counterparts,
-which improves the generality of our architecture and deduplication scheme.
-
-%[describe the architecture frm node side]
-{\bf Node Architecture} 
-Our node-side architecture, depicted in figure.\ref{fig:arch_vm}, consists of
-two main entities: a virtual block device driver, and snapshot deduplication component.
-
-%[brief the virtual device driver]
-In Alibaba's VM cloud, every VM access its virtual machine disk image through the
-virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
-This driver maintains a map of dirty-bits to record
-the change status of every fix-size segment of the virtual disk. 
-When the VM issue a disk write, the bits corresponding to the segments that covers 
-the modified disk region are set, thus letting snapshot deduplication component knows these
-segments must be checked during snapshot backup. After the snapshot backup is finished, 
-snapshot deduplication component acknowledges the driver to reset the dirty-bits map to
-a clean state.
-
-%[brief the snapshot deduplication]
-The snapshot deduplication component consists of the chunking and deduplication 
-logic of our snapshot storage system. We choose
-
-It contains an append store client which provides facilities to manage stored snapshot data, and a PDS client to support PDS index access.
-We will further discuss our deduplication scheme in section\ref{sect:dedupe}.
-
-{\bf Snapshot Representation}
-The virtual device driver uses a bitmap to track the changes 
-that have been made to virtual disk.
-Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, which indicates whether the segment
-has been modified since the last backup. Hence we could treat segment as the basic unit 
-in snapshot backup similar to a
-file in filesystem backup: a snapshot could share a segment with previous snapshot it has not been changed. 
-Moreover, we break segments into variable-sized chunks (average 4KB) using a content-based chunking algorithm,
-which brings the opportunity of fine-grained deduplication by
-allowing data sharing between segments.
-}
 
@@
 3) an append store client to store  and access snapshot data,
-and 4)  a PDS client to support PDS index access. We will further discuss our deduplication scheme 
-in Section~\ref{sect:dedupe}.
+and 4)  a PDS client to support PDS index access. 
+%We will further discuss our deduplication scheme in Section~\ref{sect:dedupe}.
 
@@
 that have been made to virtual disk.
+Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicating whether the segment
+is modified since last backup. 
+%Hence we think of segment as the basic unit in snapshot backup similar to
+%file in normal filesystem backup: a snapshot could share a segment with previous snapshot it is not changed. 
+Segments are further divided into variable-sized chunks (average 4KB) 
+using a content-based chunking algorithm~\cite{?}, 
+which brings the opportunity of fine-grained deduplication.
+% by allowing data sharing between segments.
 %This driver maintains a map of dirty bits to record the change status of every fix-size segment of the virtual disk. 
-When the VM issue a disk write, the bits corresponding to the segments that covers 
-the modified disk region are set, thus letting snapshot deduplication component knows these
-segments must be checked during snapshot backup. After the snapshot backup is finished, 
-snapshot deduplication component acknowledges the driver to reset the dirty-bits map to
-a clean state.
-Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicates whether the segment
-is modified since last backup. Hence we think of segment as the basic unit 
-in snapshot backup similar to
-file in normal filesystem backup: a snapshot could share a segment with previous snapshot it is not changed. 
-As a standard practice, segments are further divided into variable-sized chunks (average 4KB) 
-using a content-based chunking algorithm, which brings the opportunity of fine-grained deduplication by
-allowing data sharing between segments.
+When the VM issues a disk write, the dirty bit for the corresponding segment is set
+and this indicates such a segments needs to be checked during snapshot backup. 
+After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
+[What happens with modification during snapshot backup stage.]
 
@@
 There is also a special store containing all PDS chunks shared among different VMs.
-This separation of PDS chunks allows us to change the replication degree of of those popular file blocks in the underlying file system
-Extra replication of this store is added and analyzed in Section~\ref{sect:analysis}.
+% with a higher replication degree.
+%This separation of PDS chunks allows us to change the replication degree of of those popular file blocks in the 
+%underlying file system
+%Extra replication of this store is added and analyzed in Section~\ref{sect:analysis}.
 As shown in Fig.\ref{fig:as_arch}, we explain the data structure of snapshot stores as follows.
@@
 \begin{itemize}
-\item The PDS snapshot contains a set of commonly used data chunks and is accessed by its offset and size
-in the corresponding DFS file.
-The PDS index uses the offset and size as a reference in its index structure.
 
-\item Each non-PDS snapshot store is divided into a set of containers and each container is approximately 
-1GB. The reason we divide the snapshot into containers is to simplify the compaction process
-conducted periodically. Chunks without any reference from other snapshots can be removed by this process, and the compaction  routine can work on one container at a time
-and copy used data chunks to another container. By limiting the size of a container, we limit the cost of the compaction process.
-	\begin{itemize}
-	\item Each container is divided into a set of chunk data groups. Each group is composed of
-	a set of data chunks and is the basic unit for the snapshot in data access and retrieval. 
-	In writing a chunk group, data chunks in this group are compressed together and then stored. 
-	When accessing a particular chunk, its chunk group is retrieved from the disk storage
-	and uncompressed. Given the high spatial locality 
-in snapshot data accessing~\cite{Sampling,FoundationPaper},
-	retrieval of  data chunks by group naturally works well with prefetching to speedup
-	snapshot access. A  typical chunk group contains 100 to 1000 chunks, with an average size of 
+%The reference to each PDS cunk  contains  a container ID as explained ,
+
+%The PDS index uses the offset and size as a reference in its index structure.
+
+\item Data of each VM snapshot store excluding PDS is divided into a set of containers and 
+each container is approximately 1GB. 
+The reason for dividing the snapshot into containers is to simplify the compaction process
+conducted periodically. As discussed later, data chunks are deleted from old snapshots
+and chunks without any reference from other snapshots can be removed by this compaction process.
+By limiting the size of a container, we can effectively control the length of each compaction process.
+The compaction  routine can work on one container at a time and copy used data chunks to another container.
+
+Each container is further divided into a set of chunk data groups. Each chunk group is composed of
+a set of data chunks and is the basic unit in data access and retrieval. 
+In writing a chunk during backup, the system accumulates data chunks and store the entire
+group as a unit after a compression.
+When accessing a particular chunk, its chunk group is retrieved from the storage
+and uncompressed. Given the high spatial locality and usefulness of prefetching  in 
+snapshot chunk accessing~\cite{Sampling,FoundationPaper},
+retrieval of  a data chunk  group naturally works well with prefetching. 
+A  typical chunk group contains 100 to 1000 chunks, with an average size of 
 200-600 chunks.
-Chunk grouping also reduces the  container index size as we discuss below. 
-Given  the average chunk size of 4KB,  the index size for a 1GB container reduces from 10MB to 100KB when
-the chunk group size is 100.
+%Given  the average chunk size of 4KB,  the index size for a 1GB container reduces from 10MB to 100KB when
+%the chunk group size is 100.
 %%CBlock, then the overall index size is reduced to $1/m$. 
@@
 %a 1GB container from 10 MB to 100 KB.
-	\item 
-Each data container is represented by three data files in the DFS:
-1) the container data file holds the actual content of data chunks, 
+\item Each data container is represented by three files in the DFS:
+1) the container data file holds the actual content, 
 2) the container index file is responsible for translating a data reference
 into its location within a container, and 
-3) a chunk deletion log file saving all the deletion requests within  the container.
-A VM snapshot store typically has a small number of containers because each container is fairly large, with an average size of 1GB, and 
-maintains a limited number of snapshots (e.g. 10 in the Alibaba case).
-New snapshot data chunks can be effectively compressed in chunk groups in addition to  deduplication.
+3) a chunk deletion log file records all the deletion requests within  the container.
 
-\item We maintain  a chunk counter and assign the current number 
-as a chunk ID (called CID) within this container as a reference of a new chunk added to a container. 
-Since data chunks are always appended to the snapshot store, 
- a CID is monotonically increasing.
-A data chunk reference stored in the index of snapshot recipes
-is composed of two parts: a container ID (2 bytes) and CID (6 bytes).
-When a snapshot chunk is to be accessed, the recipe for the snapshot will point to either a data chunk
-in the PDS or a reference number with a container ID and CID.
-With a container ID, the corresponding container index file is accessed and 
-the chunk group is identified using this CID.
-Once the chunk group is loaded to memory, its header contains the exact offset of the corresponding chunk and the content is then accessed from the memory buffer.
+%A VM snapshot store typically has a small number of containers because each container is 
+%fairly large, with an average size of 1GB, and 
+%maintains a limited number of snapshots (e.g. 10 in the Alibaba case).
+%New snapshot data chunks can be effectively compressed in chunk groups in addition to  deduplication.
+
+\item A data chunk reference stored in the index of snapshot recipes
+is composed of two parts: a container ID with 2 bytes and a local chunk ID with 6 bytes.
+Each container maintains a local  chunk counter and assigns the current number 
+as a chunk ID  when  a new chunk is added to this  container. 
+Since data chunks are always appended to a snapshot store during backup, 
+a local chunk ID is monotonically increasing.
+When a snapshot chunk is to be accessed, the recipe for the snapshot will point a data chunk
+in the PDS store or in a non-PDS VM snapshot  store. 
+Using  a container ID, the corresponding container index file of this VM is accessed and 
+the chunk group is identified using a simple chunk ID range search. Once the chunk group is loaded to memory, 
+its header contains the exact offset of the corresponding chunk ID and the content is then accessed from the memory buffer.
 
@@
 %no extra sorting is needed.
-	\end{itemize}
+\item The PDS chunks are a set of commonly used data and they are stored in one PDS file.
+Since the total file size is relatively small, and
+PDS data is re-calculated periodically, the PDS data file and its index are rebuilt completely. 
+Each reference to a PDS data chunk in the PDS index is the offset within the PDS file, and the chunk size.
+
 \end{itemize}
@@
   \epsfig{file=images/sstore_arch, width=3in}
-  \caption{Data structure of VM snapshot stores.}
+  \caption{Data structure of a VM snapshot store.}
   \label{fig:as_arch}
@@
 
-The snapshot  store supports three API calls.
+A snapshot  store supports three API calls.
 \begin{itemize}
@@
 %AS supplies three interfaces: {\em get(ref)} accepts a data reference and retrieves data, 
-\item {\em Put(data)} places data chunk into the snapshot store and returns a reference to be stored in 
+\item {\em Put(data)}. This places data chunk into the snapshot store and returns a reference to be stored in 
 the recipe metadata of a snapshot. 
-
-The write requests to append data chunks to a VM store are accumulated in the client side. 
-When the number of write requests reaches the group size $g$, the snapshot store client compresses
+The write requests to append data chunks to a VM store are accumulated at the client side. 
+When the number of write requests reaches a fixed group size, the snapshot store client compresses
 the accumulated   chunk group, adds a chunk group index  to the beginning of the group, and then
@@
 container index file.
-
 The writing of PDS data chunks is conducted periodically when there is a new PDS calculation.
-Since the PDS dataset is small, a new PDS file is created during the periodical update.
+%Since the PDS dataset is small, a new PDS file is created during the periodical update.
 \item{\em Get(reference)}.
@@
 the offset and size within the PDS  underlying  file.
-We also maintain a small data cache for the PDS data service to speedup the process.
+We also maintain a small data cache for the PDS data service to speedup common data fetching.
 
-To read a non-PDS chunk using a reference,  the snapshot store client first loads the
+To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client first loads the
 corresponding VM's container index file specified by the container ID, then searches the chunk
-group  that  covers the chunk by the group  CID range.
-After that, it reads the whole chunk group from DFS, decompresses it, and seeks to the exact chunk data 
-specified by the CID. 
+groups  using their  chunk ID coverage.
+After that, it reads the identified chunk group from DFS, decompresses it, and seeks to the exact chunk data 
+specified by the chunk ID. 
 Finally, the client updates its internal chunk data cache with the newly loaded content to 
@@
 \item {\em Delete(reference)}.
-A data chunk can be deleted when a snapshot expires or gets deleted explicitly by a user.
-We will discuss the snapshot deletion in the following subsection.
+Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user
+and we will discuss the snapshot deletion in detail in the following subsection.
 %deletes the data pointed by the reference.
@@
 When deletion requests are issued for a specific container,
-those requests are simply logged into the  container's deletion log initially and thus  a lazy
+those requests are simply recorded into the  container's deletion log initially and thus  a lazy
 deletion strategy is exercised.
-Once CIDs appear in
+Once local chunk IDs appear in
 the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
@@
 found in the deletion log to the new container, and creating new chunk groups and indices. 
-Every chunk's CID however is directly copied rather than re-generated. This
+Every local chunk ID however is directly copied rather than re-generated. This
 process leaves holes in the CID values, but preserves the sorted order.
@@
 in upper level recipes are permanent and stable, and the data reading process
-is as efficient as before. This CID stability also ensures that recipes do not
+is as efficient as before. Maintaining the stability of chunk IDs also ensures that recipes do not
 depend directly on physical storage locations.
@@
 %small chunks gives better compression. Third, reading a CBlock (200 - 600 KB) typically cost the same amount of disk
-
-\comments{
-\subsection{Snapshot Deduplication and Fault Isolation}
-\label{sect:dedupe}
-%snapshot representation
-%\subsection{Inner and corss VM deduplication}
-Our  deduplication scheme compares the fingerprints of the current snapshot
-with its parent snapshot and also other snapshots in the entire cloud.
-This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
-Inner-VM duplication exists between a VM's snapshots, because the majority of data is unchanged during each backup period. 
-Such localization decreases data dependencies between different VM backups,
-simplifies snapshot management and statistics collection,
-and facilitates parallel execution of snapshot operations.
-On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
-As the result, different VMs tend to backup a large amount of highly similar data.
-Our multi-level pipeline process can minimize 
-the cost of deduplication while maximize the its efficiency at each level,
-and is parallel since each segment is processed independently.
-
-\begin{itemize}
-\item \textbf{Dirty-based coarse-grain inner-VM deduplication.}
-The first-level deduplication is to follow the standard dirty bit approach, but is conducted
-in the coarse grain segment level.
-We use the  Xen virtual device driver which supports dirty bits for the storage device
-and the dirty bit setting is maintained in a coarse grain level we call it a segment.
-In our implementation, the segment size is 2MB. 
-Since every write for a block will touch a dirty bit, the device driver maintains dirty bits in memory
-and cannot afford a small segment  size.
-
-\item \textbf{Chunk-level fine-grain nearby duplicate detection.}
-
-The best deduplication uses a nonuniform chunk size 
-in the average of 4K or 8K~\cite{??}.
-Thus the second-level inner-VM deduplication is to assess in this
-level, but only for those dirty  segments. 
-We load the fingerprints of chunks in the corresponding segment from the
-parent for a comparisons and compare near-by fingerprint matching within this segment.
-The amount of memory for maintaining those fingerprints  is small.
-For example, with a 2MB segment, there are about 500 fingerprints to compare.
-
-%If we use 4KB in level-1, then such a level-1 should have similar dedup efficiency 
-%as the current level-1 and level-2 combined, because finally they equal to comparing  
-%parent snapshot at 4KB granularity.
-%
-%However, at level-3 things are different.
-If we use 4KB fix-size block uniformly, it would be harder for different VM to share data through PDS, because there is no guarantee that the location of duplicate data on different VM disks are always aligned at 4KB boundary.
-For example, if two VMs each has a copy of duplicate data, but they are not aligned, then we won't be able to detect them.
-Our study at the current small data set has shown that using 4KB fix-size block will make PDS method less efficient by nearly 10%.
-Over the long time, more and more OS variations will co-exist in the cluster, making this 4KB fix-size approach inefficient in reducing duplicate data across VMs.
-
-%\item \textit{Level 2  Chunk fingerprint comparison.}
-%If a segment is modified, we perform fine-grained deduplication 
-%by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
-%thus eliminate partial data duplication within the segment.
-%\end{itemize}
-%
-%In general, operations at level 1 have almost no cost and most of unmodified data are filtered here. 
-%To process a dirty segment at level 2, 
-%there requires no more than one DFS access to load the segment recipe from previous snapshot,
-%and a tiny amount of memory to hold it in main memory.
-
-\item \textbf{Cross-VM deduplication.}
-This step accomplishes the standard global fingerprint  comparison as conducted
-in the previous work~\cite{??}.
-One key observation is that the inner deduplication has removed many of duplicates.
-There are not lot of deduplication opportunities cross VMs while the memory
-consumption for global comparison is expensive.
-Thus our approximation is that duplicate sharing patterns among  VM follows
-a zip-like distribution, and the global fingerprint  comparison  only searches
-for the most popular items. 
-\end{itemize}
-
-{\bf Popular Chunk Management and VM-oriented Fault Isolation}
-Our objective for fault isolation is to minimize the number of VMs affected when there are failures
-in the cluster.  The inner-VM deduplication does not depend on any global service and the comparison
-for each VM is localized within the parent and the current snapshot.
-Thus there is no data dependence between VMs.
-For cross-VM deduplication, there is a data dependence among VMs and we would minimize the failure impact
-of shared blocks by adding extra replicas of those shared blocks.
-
-This section analyzes the choice of popular blocks and its impact on the deduplication efficiency.
-It also  compares the  fault resilience of our VM-centric deduplication approach with a standard approach using 
-global deduplication.
-
-{\bf Impact of PDS deduplication.}
-Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the
-frequency of data duplication follows Zipf-like distribution\cite{zipf},
-with the exponent $\alpha$ between 0.65 ~ 0.70.
-As a result, it can be proved that deduplication efficiency of PDS index is scalable:
-
-For the Zipf-like distribution, an approximation to the sum of the first $n$ 
-elements of the distribution can be derived as follows:
-\begin{equation}
-\sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
-\end{equation}
-So the cumulative distribution function for a PDS holding top $S_c$ fingerprints
-of global index with size $S_g$ is:
-\begin{equation}
-  E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
-\end{equation}
-%[Describe the dedup efficiency model in detail]
-Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by PDS, $D$ be the amount of data on each node, and $B$ be the average block size.
-Then $S_c$ and $S_g$ can be expressed as:
-\begin{equation}
-S_c = N*m/F, \; S_g = N*D/B
-\end{equation}
-By replacing $S_c$ and $S_g$ in the first formula, the deduplication efficiency becomes:
-\begin{equation}
-  E = (\frac{m*B}{F*D})^{1-\alpha}
-\end{equation}
-Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of PDS is only controlled by the its memory usage.
-
-\begin{table}
-    \begin{tabular}{llll}
-    Data size (GB) & 1\%    & 2\%    & 4\%    \\
-    14.6           & 18.6\% & 22.1\% & 31.4\% \\
-    28.1           & 19.5\% & 26.2\% & 38.8\% \\
-    44.2           & 21.7\% & 26.5\% & 36\%   \\
-    61.6           & 23.2\% & 32.9\% & 35\%   \\
-    74.2           & 23.6\% & 33.6\% & 37.5\% \\
-    \end{tabular}
-    \caption{Deduplication effectiveness of top k\% of global index}
-    \label{tab:cds}
-\end{table}
-
-}
 

### 2013-08-26 snapshot_system/arch.tex
revise

@@
 
-In a busy VM cluster, snapshot deletions are as frequent as snapshot creations.
-However, data deduplication complicates the deletion process because space saving relies on the sharing of data,
-thus making it difficult to decide which chunks are safe to delete.
-In a traditional deduplication system, deletion often require looking at global scope to
-resolve the data dependency between logical backup entities and physical data chunks.
-Our VM-centric snapshot storage design simplifies the deletion process since 
-we only need to locate unreferenced chunks within each VM's snapshot store to free up space when deleting a snapshot.
-The PDS data chunks are commonly shared all VMs and we do not consider their reference
-counting during snapshot deletion.
-%The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
-
+In a busy VM cluster, snapshot deletions can occur frequently.
+Deduplication complicates the deletion process because space saving relies on the sharing of data
+and it requires the global reference of deldted chunks to be identified before  they can be safely removed.
 While we can use the mark-and-sweep technique~\cite{Guo2011}, 
-it still takes significant time to conduct this process every time there is a snapshot deletion.
+it still takes significant resource to conduct this process every time there is a snapshot deletion.
 In the case of Alibaba, snapshot backup is conducted automatically and there are 
@@
 a fast solution with a very low resource usage to delete snapshots.
-
-With this in mind, we develop an {\em approximate} deletion strategy to trade deletion accuracy for
+%In a traditional deduplication system, deletion often require looking at global scope to
+%resolve the data dependency between logical backup entities and physical data chunks.
+Our VM-centric snapshot storage design simplifies the deletion process since 
+we can focus on  unreferenced chunks within each VM.
+The PDS data chunks are commonly shared all VMs and we do not consider them
+during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
+Another resource-saving strategy we propose is
+an {\em approximate} deletion strategy to trade deletion accuracy for
 speed and resource usage. Our method sacrifices a small percent of storage leakage
-to effectively identify unused chunks in $O(n)$ time, with $n$ being the logical number of non-PDS chunks 
-to be deleted from a VM snapshot store.
-The algorithm contains three aspects.
+to efficiently identify unused chunks in $O(n)$ time, with $n$ being the logical number of non-PDS chunks 
+to be deleted from a VM snapshot store.  The algorithm contains three aspects.
 

### 2013-08-26 batchdedup/scheduling.tex
Updated round scheduling

@@
 original virtual disk, which may still be in use during the snapshot. This adds
-extra complexity to our cost analysis, because we must now also consider the
+extra complexity to the cost analysis, because we must now also consider the
 cost of maintaining a constistent view during the snapshot process. We use the
@@
 shown that as much as 8\% or even more of total capacity must be reserved for
-Cow \cite{EMCIncrementalDataChanges}. The actual cost of CoW is a factor of the
+CoW \cite{EMCIncrementalDataChanges}. The actual cost of CoW is a factor of the
 data size, the write rate, and duration CoW is taking place. The data size
@@
 lock.
+
+Our basic CoW cost model is:
+\[
+    CoW=n(1-e^{-m/n})
+\]
+    where \[ m=tw(1-d_1)c \]
+$n$ is the number of dirty segments, $t$ is the time under CoW, $w$ is the
+write rate during CoW, $d_1$ is the \% of clean data (which doesn't go under
+CoW), and $c$ is a constant determining how likely writes are to touch dirty
+segments which haven't yet been copied vs. dirty segments which have already
+been copied during the current backup. With this CoW cost model and the earlier
+performance model, we can estimate the CoW cost of a given backup schedule.
+Note that CoW ends in Stage 2b, so only the time up to the end of 2b counts
+towards CoW. \todo{we still need to pick a value for $c$}
 
@@
 
+%lstset{basicstyle=\ttfamily\tiny
+%}
+\todo{justify choice of initial UB (right now it is mostly arbitrary)}
 \begin{lstlisting}
@@
 where A(I,N) returns the total backup time of the schedule\\
-return packing generated by A(machines,UB) after loop finishes
+This algorithm returns the packing generated by A(machines,UB) after loop finishes
 
-This general algorithm relies on a good choice of A to arrive at an efficent
-packing. Our first VM packing heuristic, A0, is very close to the algorithm for
-the dual bin packing paper.
+The general algorithm relies on a good choice of A to arrive at an efficent
+packing. Our first VM packing heuristic, A0, is a nai\"\i{}ve approach very
+close to the un-adapted algorithm from the dual bin packing paper. For both
+algorithms we develop, in case of ties, choose the left-most item.
 
@@
     lowest runtime b
-        tie-breaker:left-most round
   schedule VM a to round b
@@
 VM to a currently empty machine on an equally heavily loaded round
-\textit{(maybe a figure to show this?)}. Therefore a better scheduling would be
-obtained if we pick the round with the lowest runtime after we simulate adding
-the new VM to that round. This new round picking heuristic takes into account
-that the same VM might have different affects on different rounds.
+\todo{(insert figure to show how this happens)}. Therefore a better scheduling
+would be obtained if we pick the round with the lowest runtime after we
+simulate adding the new VM to that round. This new round picking heuristic
+takes into account that the same VM might have different affects on different
+rounds. This aspect of must be considered because we assume a VM must be backed
+up by the machine that hosts it. If the VMs are located on a DFS and can be
+backed up by any machine in the cluster then the problem of load balancing
+becomes a simpler but much different problem, and isn't considered here. We
+also pick the most heavily loaded (i.e. most data remaing) machine in case of
+ties so we can make the most backup progress in a round.
 
-Another improvement we can make is to the VM picking heuristic.
+Another improvement we can make to A0 is to the VM picking heuristic. For the
+same reason as given above, the largest VM may not always have the greatest
+impact on time (e.g. picking a slightly smaller VM on the most heavily loaded
+machine has a greater impact than selecting the largest VM on a lightly loaded
+machine). A better way to pick VMs than just by size is to simulate removing
+VM's, then model the new single round time, and pick the VM whose removal most
+decreases the single round time. By picking VMs this way we take into account
+the machine load in picking which VM to remove, and minimize the time the
+remaining VMs will take to backup
+
+After making the two above changes we arrive at VM packing heuristic A1.
+
+A1:
+\begin{lstlisting}
+while there is an unscheduled VM
+  pick the VM a whose removal will
+    most decrease single round time
+    tie-breaker:VM on most heavily
+    loaded round
+  pick the round b whose runtime will
+    be lowest after adding VM a
+  schedule VM a to round b
+Halt
+\end{lstlisting}
+
+A1 significantly improves our simulated results, bringing our CoW costs much
+closer to the best case than the worst case, as can be seen in
+Figure~\ref{tab:schedule-costs}.  Our current implementation of the algorithm
+focuses on the deduplication and so doesn't make use of CoW, but we can see
+that our simulated times closely match measured runtimes (hopefully). \todo{I
+haven't actually implemented the schedulers into the dedup yet to test this}

### 2013-08-27 batchdedup/scheduling.tex
batchdedup revision

@@
 loaded machine in a round it will increase runtime much more than if we add the
-VM to a currently empty machine on an equally heavily loaded round
+VM to a currently empty machine on the same round
 \todo{(insert figure to show how this happens)}. Therefore a better scheduling

### 2013-08-27 snapshot_system/arch.tex
revise deletion

@@
 Deduplication complicates the deletion process because space saving relies on the sharing of data
-and it requires the global reference of deldted chunks to be identified before  they can be safely removed.
+and it requires the global reference of deleted chunks to be identified before  they can be safely removed.
 While we can use the mark-and-sweep technique~\cite{Guo2011}, 
@@
 a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
-a balanced storage use. Given the large number of snapshot deletion requests, we seek
-a fast solution with a very low resource usage to delete snapshots.
+a balanced storage use.
+
+%Given the large number of snapshot deletion requests, 
+We seek a fast solution with a low resource usage to delete snapshots.
 %In a traditional deduplication system, deletion often require looking at global scope to
@@
 speed and resource usage. Our method sacrifices a small percent of storage leakage
-to efficiently identify unused chunks in $O(n)$ time, with $n$ being the logical number of non-PDS chunks 
-to be deleted from a VM snapshot store.  The algorithm contains three aspects.
+to efficiently identify unused chunks.
+% in $O(n)$ time where $n$ is the total number of non-PDS chunks to be deleted from a VM snapshot store.  
+The algorithm contains three aspects.
 
@@
 we compute a bloom-filter with $z$ bits as the summary of reference pointers for all non-PDS chunks used 
-in this snapshot.
+in this snapshot. Given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
 
@@
 and the merged vector still takes $z$ bits.
-Since the number of live snapshots is limited for 
-each VM (e.g. 10 in the Alibaba's production system), 
-the time cost of this comparison is small.
+Since the number of live snapshots $h$ is limited for
+each VM, 
+the time and memory cost of this comparison is small, linear to the number of chunks to be deleted.
 %Instead of scanning the entire append store indices, we merge the type-1 summaries of all
@@
 this chunk is not used by any live snapshots, thus it's safe delete it. 
-However, among all the chunks that suppose to be deleted, 
-there is a small false-positive ratio which
-would identify unused chunks as in use, resulting in temporary storage leakage.
+However, among all the chunks to be deleted, 
+there is a small percentage of unused chunks  which
+are misjudged as  being in use, resulting in a storage leakage.
 
-\item {\bf Periodic repair of leakage}
+\item {\bf Periodic repair of leakage}.
 %[exlpain why second bloom filter, why scan append store]
-Since there are certain unused chunks which are not deleted during
-the approximate deletion, leakage repair is conducted periodically.
-In this phase we load the reference pointers of all chunks from a VM snapshot store as a table in memory,
-then scan through all the snapshots' segment recipes. For each reference pointer that is in use by a snapshot,
-we mark the corresponding entry in the table as in use. Finally those unmarked (and therefore unused) reference pointers in the
-table represent chunks that can be safely deleted.
-
-The cost of leak repair mainly come from holding a table of reference pointers and the scan of all snapshots' metadata.
-Consider each reference pointer consumes 8 bytes plus 1 byte as mark field, a VM that has 40GB backup data with about
-10 million chunks will need 90MB of memory to construct such a table. 
-Also, scanning all snapshots metadata is many times slower when compared
-to the approximate deletion which only scans single snapshot's metadata.
-It's worth mention that compared to previously-developed mark-and-sweep techniques, 
-our leak repair still has advantages because the scope of repair is restricted within a single VM's snapshot 
-store due to our VM-centric design, and we perform leakage repair periodically.
+%Since there are certain unused chunks which are not deleted during the approximate deletion, 
+Leakage repair is conducted periodically to fix the above approximation error.
+This procedure compares the live chunks for each VM with what are truly used through the VM snapshot metadata recipe.
+That requires a scanning of all chunks in a VM; however it is a VM-specific procedure and thus
+the cost is relatively small compared to the traditional mark-sweep procedure~\cite{?} which scans snapshot 
+chunks from all VMs.
+For example,
+% are live used   we load the reference pointers of all chunks from a VM snapshot store as a table in memory,
+%then scan through all the snapshots' segment recipes. For each reference pointer that is in use by a snapshot,
+%we mark the corresponding entry in the table as in use. Finally those unmarked (and therefore unused) reference pointers in the
+%table represent chunks that can be safely deleted.
+%The cost of leak repair mainly come from holding a table of reference pointers and the scan of all snapshots' metadata.
+consider each reference pointer consumes 8 bytes plus  1 mark bit, a VM that has 40GB backup data with about
+10 million chunks will need less than 90MB of memory to complete a VM-specific mark-sweep process.
+%, scanning all snapshots metadata is many times slower when compared
+%to the approximate deletion which only scans single snapshot's metadata.
+%It's worth mention that compared to previously-developed mark-and-sweep techniques, 
+%our leak repair still has advantages because the scope of repair is restricted within a single VM's snapshot 
+%store due to our VM-centric design, and we perform leakage repair periodically.
 %We cannot simply repeat the phase 1 multiple times to reduce temporary storage leakage, because:
@@
 %{\bf Discussion}
-We now estimate the storage leakage and how often leak repair needs to be conducted.
-Assuming a VM always maintain $h$ snapshots in the backup, and it creates and deletes one snapshot
+We now estimate the size of storage leakage and how often leak repair needs to be conducted,
+given  a VM which keeps $h$ snapshots in the backup storage, and it creates and deletes one snapshot
 everyday. Let $u$ be the total number of chunks brought by the initial backup, $\Delta u$ be the average
-number of additional unique chunks added from one snapshot to the next snapshot. Then the total number of unique
-chunks used is about:
+number of additional unique chunks added from one snapshot to the next snapshot version. Then the total number of unique
+chunks used in a VM is about:
 \[
@@
 Each bloom filter vector has  $z$ bits for each snapshot and let $j$ be the number of hash functions used by the
-bloom filter. The probablity that a particular bit is still in all $h$ summary vectors is still 0 is 
-$(1- \frac{1}{z}) ^{j U}$. Notice that when a chunk appears multiple times in these summary vectors, it does not 
-increase the probability of a particular bit being 0 in all $h$ vectors.
-Then the false-positive rate $\epsilon$ is: 
-\[
+bloom filter. The probablity that a particular bit is 0  in all $h$ summary vectors is  
+$(1- \frac{1}{z}) ^{j U}$. Notice that a chunk may appear multiple times in these summary vectors; however, this should not 
+increase the probability of being a 0 bit in all $h$ summary vectors.
+Then the misjudgment rate of being in use $\epsilon$ is: 
+\begin{equation}
+\label{eq:falserate}
 \epsilon = (1-(1-\frac{1}{z})^{jU})^j.
-\]
+\end{equation}
 
 For each snapshot deletion, the amount of chunks need to be deleted is nearly identical to the number of
-newly add chunks $\Delta u$. However, some of chunks among them are not detected as unused in our approximation
-algorithm, thus forms the storage leakage. Let $R$ be the total number of runs of approximate deletion since
-last repair. we estimate  the total leakage $L$ after $R$ runs as:
+newly add chunks $\Delta u$. 
+%However, some of chunks among them are not detected as unused in our approximation
+%algorithm, thus forms the storage leakage. 
+Let $R$ be the total number of runs of approximate deletion between two consecutive 
+repairs. we estimate  the total leakage $L$ after $R$ runs as:
 \[
@@
 When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we need to execute a leak repair:
-\[
+
+\begin{equation}
+\label{eq:leakrepair}
 \frac{L}{U} = \frac{R \Delta u \epsilon}{u+(h-1)\Delta u } > \tau 
 \Longrightarrow R > \frac{\tau}{\epsilon}\times\frac{u + (h-1)\Delta u}{\Delta u}
-\]
+\end{equation}
+
 For example in our tested dataset,  
 each VM keeps $h=10$ snapshots and each snapshot has
-about 1-5\% of new data. Thus $\frac{\Delta u}{u}=0.05$ at most. With 40GB snapshot size, $u\approx = 10$ millions.
+about 1-5\% of new data. Thus $\frac{\Delta u}{u} \leq 0.05$. For a 40GB snapshot, $u\approx  10$ millions.
 Then $U=10.45$ millions.
-We choose  $\epsilon = 0.01$ and $\tau=0.1$. Then from the bloom filter  false positive formula, 
-$z=10U=100.45$ million bits. $R=290$.
-Then we would expect leak repair be triggered once for 
-every 290 runs of approximate deletion. 
+We choose  $\epsilon = 0.01$ and $\tau=0.1$.  From Equation~\ref{eq:falserate}, 
+$z=10U=100.45$ million bits. From Equation~\ref{eq:leakrepair}, 
+leak repair should be triggered once for every R=290 runs of approximate deletion. 
 When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
-only one full leak repair for one VM scheduled for every 12 days. Each repairs uses about 90MB memory on average
+only one full leak repair for one VM scheduled for every 12 days. Each repairs uses at most  90MB memory on average
 as discussed earlier and takes a short period of time.

### 2013-08-27 batchdedup/scheduling.tex
batchdedup paper revisions

@@
 schedule all the work to be done in one round.  This works well if all of the
-data being backed up is just copies (e.g. a separate backup system which data
-is sent to over the network), however in our case we are backing up the
+data being backed up are only copies, e.g. a separate backup system which data
+is sent to over the network. However, in our case we are backing up the
 original virtual disk, which may still be in use during the snapshot. This adds
@@
 cost of maintaining a constistent view during the snapshot process. We use the
-Copy on Write (CoW) provided by the virtual disk manager. With CoW, the
+Copy on Write (CoW) provided by the virtual disk manager to maintain a
+consistent view. With CoW, the
 duration of the backup affects how much data must be copied. Other studies have
@@
 \]
-    where \[ m=tw(1-d_1)c \]
-$n$ is the number of dirty segments, $t$ is the time under CoW, $w$ is the
+    where
+\[
+    m=tw(1-d_1)c
+\]
+
+In the above model, $n$ is the number of dirty segments, $t$ is the time under
+CoW, $w$ is the
 write rate during CoW, $d_1$ is the \% of clean data (which doesn't go under
@@
 
-The way to decrease the CoW cost is to break up the backup into multiple
+We can see above that the way to decrease the CoW cost is to decrease t, the
+time the virtual disk is under CoW. We do that by breakng up the backup into
+multiple
 rounds, where in each round the CoW cost is minimized. The more rounds there
@@
 setting a time limit on the whole backup job, and then develop an algorithm to
-schedule VMs into rounds.
+schedule VMs into rounds and pick the number of rounds to use.
 
-With these goals a model that closely fits our goals is the dual version of the
+With these parameters a model that closely fits our goals is the dual version
+of the
 bin packing problem. In standard bin packing the goal is to fit all of the
@@
 version of the problem however as many bins as possible are to filled to at
-least some minimum level. In our problem the constraint is to keep the total
-cost of the schedule under a time limit rather than a minimum bin level. We
+least some minimum level. This fits our purpose because we want to maximize the
+number of rounds, with some constraint to keep the efficiency benefits of batch
+processing. In our dual-bin-packing solution the constraint is to keep the total
+cost of the schedule under a time limit rather than mandating a minimum bin
+level. We
 adapt an algorithm for dual bin packing\cite{DualBinPacking} to fit our VM
 scheduling problem. The algorithm adapted is called iterated A and works by
-iteratively callng a bin packing heuristic A with the VMs to be scheduled and
-the number of rounds, using binary search to arrive at the best number of
-rounds. A(I,N) is defined to return the optimality of packing set I into N bins
+iteratively callng a bin packing heuristic A with the items to be scheduled and
+the number of bins, using binary search to arrive at the best number of
+bins. A(I,N) is defined to return the optimality of packing set I into N bins
 using A. We take this basic idea and look at several VM packing heuristics to
 arrive at an efficient packing algorithm. More formally, our adaptation of the
-iterated A algorithm can be defined as:
+iterated A algorithm is defined as:
 
@@
 \end{lstlisting}
-where A(I,N) returns the total backup time of the schedule\\
+where A(machines,N) returns the total backup time of the schedule for N rounds\\
 This algorithm returns the packing generated by A(machines,UB) after loop finishes
@@
 loaded machine in a round it will increase runtime much more than if we add the
-VM to a currently empty machine on the same round
+VM to a different round where that machine is currently empty
 \todo{(insert figure to show how this happens)}. Therefore a better scheduling
@@
 takes into account that the same VM might have different affects on different
-rounds. This aspect of must be considered because we assume a VM must be backed
-up by the machine that hosts it. If the VMs are located on a DFS and can be
+rounds. This aspect of round picking must be considered because we assume a VM
+must be backed
+up by the machine that hosts it. If the VMs are located on a DFS such that they
+can be
 backed up by any machine in the cluster then the problem of load balancing
@@
 VM's, then model the new single round time, and pick the VM whose removal most
-decreases the single round time. By picking VMs this way we take into account
-the machine load in picking which VM to remove, and minimize the time the
-remaining VMs will take to backup
+decreases the single round time (i.e. the VM that has the greatest impact on
+overall backup time). By picking VMs this way we take into account
+the machine load in picking which VM to schedule next, and minimize the time
+the remaining VMs will take to backup
 

### 2013-08-28 snapshot_system/eval1.tex
re

@@
 We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
-8-core AMD FX-8120 at 3.1 GHz with 16 GB RAM. 
-Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
-Each machine  is equipped with a 
-a distributed file system (QFS) and overall the cluster manages six 3TB disks
-with default replication degree set to 3. The PDS replication is set to 5.
-Objectives of our evaluation are:
-1) Study the duplicate detection and removal effectiveness of the VC approach and compare with an alternative VO
-design.
-2) Examine the impacts of VC for fault isolation and tolerance. 
-3) Evaluate the backup throughput performance VC  for a large number of VMs.
-4) Assess the resource usage  of VC in terms of memory, storage, and network bandwidth.
+8-core 3.1Ghz AMD FX-8120 and 16 GB RAM. 
+Our implementation is based on Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
+and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 5.
+Our evaluation objective is to
+study the benefit of fault tolerance and   deduplication efficiency  the VC approach and compare it
+with an alternative VO design, and assess backup throughput and  resource usage for a large number of VMs.
 % the backup throughput performance VC  for a large number of VMs.
@@
 
-We will also compare our VC approach with  with
-a VO approach  using stateless routing with binning (SRB).
+We will compare our VC approach with
+a VO approach  using stateless routing with binning (call it SRB) 
+based on~\cite{ParallelDataDomain,Extremebining}
 SRB executes a distributed deduplication by routing a data chunk to a machine~\cite{ParallelDataDomain}
-using  the chunk hashing function discussed in \cite{??}. Within such a machine,
-the data chunk is compared with a local index. This minHash paritioning
-algorithm helps provide a greater degree of parallelism, but ignores the
-significant amount of parallelism within a single VM.
+using  a min-hash function discussed in \cite{Extremebining}. Once a data chunk is routed to
+a machine, this chunk is compared with the fingerprint index of this machine locally. 
+%algorithm helps provide a greater degree of parallelism, but ignores the
+%significant amount of parallelism within a single VM.
 

### 2013-08-28 snapshot_system/failover.tex
re

@@
                 \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
+                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                 \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
-                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
-                \legend{$N_o$, $N_1+N_2$, $N_2$, $N_1$};
+                \legend{$N_o$, $N_1+N_2$, $N_1$, $N_2$};
 		\end{axis}
@@
 The snapshot availability of a VM  in the VO approach is
-\[ 
+\begin{equation}
+\label{eq:VO}
 (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
-\]
+\end{equation}
+
 %This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.
+For VC, there are two cases.
+\begin{itemize}
+\item
 When there are $r \le d<r_c$ machines failed,  there is no PDS data loss and  
@@
 
+\item
 When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
@@
 \]
-Both conditions $N_1+N_2 <N_o$ 
-and  $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
-< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
-support the higher availability of VC.
+Figure~\ref{fig:fsb-availability} illustrates that the availability of an individual file system block
+with different replication degree. This demonstrates inequality $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
+< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$. As we have also observed
+$N_1+N_2 <N_o$ in our dataset, these two conditions support that VC has a  higher availability. 
+%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
+\end{itemize}
+
 %= Probability(\mbox{ No non-PDS file block loss})^{N_1}
@@
 }
-\comments{
+
 \begin{figure}[htbp]
@@
     \end{tikzpicture}
-    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
+    \caption{Availability of individual file system blocks in a 100 machine cluster with different replication degrees.}
   \label{fig:fsb-availability}
 \end{figure}
-}

### 2013-08-28 snapshot_system/concl.tex
update eval
revise eval1.tex

--- 2013-06-24 snapshot_system/con.tex
@@
 \label{sect:final}
-In this paper we propose a VM-centric deduplication scheme for 
-snapshot backup in VM cloud for maximizing fault isolation and tolerance. 
+In this paper we propose a collocated backup service built on
+the top of a cloud cluster to reduce network traffic and infrastructure.
+The key contribution is a VM-centric deduplication scheme to 
+maximize fault isolation while delivering competitive deduplication efficiency.
 Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
-while cross-VM deduplication with a small common data set
-effectively  covers a large amount of duplicated data.
-The scheme organizes the write of small data chunks into large file system blocks so
-that each underlying file block is associated with one VM for most of cases.
-Our solution accomplishes the majority of
-potential global deduplication saving while still meets stringent cloud resources requirement. 
-Our analysis shows that  this VM centric scheme 
-can  provide  better fault tolerance while using a small amount of computing and storage resource.
+while cross-VM deduplication with a small common data set.
+VM-specific file block packing also reduces inter-VM dependence and enhances fault tolerance.
+The design places a special consideration for low-resource usages as a collocated cloud service.
+Evaluation using  VM backup data shows that
+our solution can accomplish 92\% of what complete global
+deduplication can do while the availability of snapshots increases substantially with this VM-centric
+and a small replication overhead for popular inter-VM chunks.
 
-[Talk about more what we learn from Evaluation]
-Evaluation using real user's VM data shows
-our solution can accomplish 75\% of what complete global
-deduplication can do. 
-Compare to today's widely-used snapshot technique, our scheme reduces almost
-two-third of snapshot storage cost.
-Finally, our scheme uses a very small amount of memory on each node, and leaves
-room for additional optimization we are further studying.
+% effectively  covers a large percent of duplicate data.
+%The scheme organizes the write of small data chunks into large file system blocks so
+%that each underlying file block is associated with one VM for most cases.
+%by keeping most of the FSBs only referenced by 1 VM, we isolate faults and improve overal fault tolerance.
+%Our solution accomplishes reasonable and competitive deduplication efficiency while
+%still meeting stringent cloud resource usage requirements. 
+%Our analysis shows that  this VM centric scheme 
+%can  provide  better fault tolerance than VM-oblivious global deduplication schemes
+%while using a small amount of computing and storage resources.
+
+%[Talk about more what we learn from Evaluation]
+%Compare to today's widely-used snapshot technique, our scheme reduces almost
+%two-third of snapshot storage cost.
+%Finally, our scheme uses a very small amount of memory on each node, and leaves
+%room for additional optimization we are further studying.
 
@@
 %Using  50 user VM data out of 1322 data disks as the training data and
-%with  1.5\% as CDS threshold, we see the total 1198GB of new data is reduced by
+%with  1.5\% as PDS threshold, we see the total 1198GB of new data is reduced by
 %755.8GB, while perfect deduplication can reduce 1017.4GB. So 74.3\% of duplicate blocks are eliminated
-%by pre-trained CDS, which is quite satisfactory.
+%by pre-trained PDS, which is quite satisfactory.

### 2013-08-28 snapshot_system/eval1.tex
revise eval1.tex

@@
 \subsection{Settings}
-We have performed a trace-driven study using  a 1323 VM dataset  collected from 
-100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
-The production environment tested has  about 1000 machines with 25 VMs on each machine.
+We have performed a trace-driven study using a production dataset~\cite{WeiZhangIEEE} from 
+Alibaba Aliyun's cloud platform with about 100 machines. 
+The VMs  of the sampled  data set   use popular operating systems such as 
+Debian, Ubuntu, Redhat, CentOS, and win2008. 
 %We are running our deduplication/backup  service on 100 nodes.
@@
 % and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
-For each VM, the system keeps 10 automatically-backed snapshots in the storage while
+Each machine hosts upto 25 VMs and each VM keeps 10 automatically-backed snapshots in the storage while
 a user may instruct extra snapshots to be saved.
@@
 The signature for variable-sized blocks is computed using their SHA-1 hash. 
-Popularity of data blocks are collected through global counting 
-and the top 1-2\% will fall into the PDS, as discussed in Section~\ref{sect:crossVM}.
+Popularity of data blocks are collected through global counting and 
+and top popular ones ($\delta=1-2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:crossVM}.
 %variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
@@
 
-Since it's impossible to perform large scale analysis without affecting production VM performance,
-we sampled two data sets from real user VMs to measure the effectiveness of our deduplication scheme.
-Dataset1 is used study the detail impact of 3-level deduplication process,
-it compose of 35 VMs from 7 popular OSes: 
-Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
-5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
-The overall data size for these 700 full snapshots is 17.6 TB.
+%Since it's impossible to perform large scale analysis without affecting production VM performance,
+%For each OS, 5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
+%The overall data size for these 700 full snapshots is 17.6 TB.
 
-Dataset2 contains the first snapshots of 1323 VMs' data disks from a small cluster with 100 nodes. 
-Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
-study the PDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
+%Dataset2 contains the first snapshots of 1323 VMs' data disks from a small cluster with 100 nodes. 
+%Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
+%study the PDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
 
@@
 
-Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
-nodes fail for different amounts of sharing of filesystem blocks in the index.
-We show 6.3 for the VO sharing because that is what we measured in our dataset,
-and while we expect it to continue to grow (thereby decreasing fault
-tolerance), it should do so slowly, so we treated VO FSB sharing as a
-contstant factor of 6.3, as it doesn't change our results. for VC we use 1250, because that is what we
-estimate at 2500 VMs based on the linear growth up to 105 VMs. We also show
-2500 VMs sharing each PDS FSB because that is the absolute worst case for 2500
-VMs. Our results show that even the VC worst case provides better VM
-reliability than our optimistic amount of sharing in VO. 
-The key factor placed is that  $N_1 +N_2 <
-N_o$, caused by the fact that the VM-centric approach localizes deduplication
-and packs  data blocks for one VM as much as possible.  The extra replicaton
-for PDS blocks also signficantly increases the snapshot availability even when
+Figure~\ref{fig:vm-availability} shows the availability of VM snapshots when 
+there are up to 10 storage nodes failed in a 100-node cluster. 
+Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
+$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
+A  VO curve has  $V_o=150$ which is  the average number of VMs that share a file system block. 
+%We show 6.3 for the VO sharing because that is what we measured in our dataset,
+%and while we expect it to continue to grow (thereby decreasing fault
+%tolerance), it should do so slowly, so we treated VO FSB sharing as a
+%contstant factor of 6.3, as it doesn't change our results. for VC we use 1250, because that is what we
+%estimate at 2500 VMs based on the linear growth up to 105 VMs. We also show
+Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
+For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
+while VC with 99.9\% loses snapshots of 2.5 VMs.
+The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
+and packs  data blocks for one VM as much as possible.  The extra replication
+for PDS blocks also significantly increases the snapshot availability even when
 a PDS file block is shared by every VM.
@@
 Figure~\ref{fig:pds-replication}
-shows the advantages of increasing the replication factor for PDS blocks. We
-use our estimate of 1250 VMs sharing each PDS block, which is what we expect
-for 2500 VMs, given the growth up to 105 VMs. It is easy to see though thatr
-increasing the replication of just
-the PDS blocks (which are the most popular blocks) can have a positive impact
-on the overall reliablity of the VM backups. Increasing the
-PDS replication is cheap because is makes up a very small percent of the
-stored data, but the impact is significant. These figures together show the
-advantages of the VM-centric model, and the advantages that separating the
-replication factor for popular blocks can have on reliability.
+shows the snapshot availability when increasing the replication degree for PDS blocks. 
+%We use our estimate of 1250 VMs sharing each PDS block, which is what we expect
+%for 2500 VMs, given the growth up to 105 VMs. 
+It can be seen that increasing the replication of 
+the PDS blocks can have a good impact on the overall availability of the VM backups. 
+%Increasing the PDS replication is cheap because 
+PDS with more replication  makes up a small percent of the
+stored data; however, the benefit to the snapshot availability is significant. 
+%These figures together show the advantages of the VM-centric model, and the advantages that separating the
+%replication factor for popular blocks can have on reliability.
 
@@
     \pgfplotslegendfromname{legend:vm-availability}
-      \caption{Availability of VM backups for VO and VC models for
-          varying degrees of block sharing. Non-PDS replication fixed
-          at 3 and PDS replication increased to 4. VC worst-case
-          is $V=25*p$, and expected-case is $\frac{V}{2}$
+      \caption{Availability of VM backup snapshots for VO and VC when failed machines vary
+from 1 to 10.  Non-PDS replication is fixed
+          at 3 and PDS replication is 4. 
       }
@@
 	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
+  \caption{Availability of VM backup snapshots as nodes fail in VC with different PDS Replication degree
+ (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
   \label{fig:pds-replication}
@@
 	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
+  \caption{Availability of VM backups as nodes fail in VC for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
   \label{fig:pds-replication2}
 \end{figure}
-
+}
 \subsection{Deduplication Efficiency}
@@
 Figure~\ref{fig:exbin-efficiency-graph} shows the deduplication efficiency for SRB and VC.
-We define deduplication efficiency to be the percent of duplicate chunks
+Deduplication efficiency is defined as the percent of duplicate chunks
 which are detected and deduplicated.
-The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' means that
-we allocate the space of distributed shared memory  to accommodate 2\%
-of data chunks shared among VMs, as defined in Table~\ref{tab:symbol}. Namely 
-With $\sigma=2\%$, the deduplication efficiency can reach over 90\% 
-while with $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
+The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
+is defined in Table~\ref{tab:symbol}. 
+%we allocate the space of distributed shared memory  to accommodate 2\%
+%of data chunks shared among VMs, as defined in 
+With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
+and  the deduplication efficiency can reach over 90\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
 The loss of efficiency in VC is caused by the restriction of the total physical memory available
-in the cluster to support the PDS.  
+in the cluster to support PDS index.  
 The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
@@
     \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% PDS.}
+        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC 
+with $\sigma=2\%$.}
   \label{fig:exbin-efficiency2}
@@
     \end{tikzpicture}
-    \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
-    Stateless Routing with Binning and VC. Also compares old VC algorithm to new VC with Minhash for Level-2.}
+    \caption{Deduplication efficiency of VC and SRB.}
   \label{fig-exbin-efficiency-graph2}
@@
 
-\subsection{Resource Usage}
+\subsection{Resource Usage and Processing Time}
 \begin{table}
@@
     \hline
-    PDS replication degree & Total space (GB) \\ \hline
-    3                      & 3065             \\ \hline
-    4                      & 3072             \\ \hline
-    5                      & 3079             \\ \hline
-    6                      & 3086             \\ \hline
-    7                      & 3093             \\ \hline
+    PDS replication degree & Disk usage per machine  \\ \hline
+    3                      & 3065GB             \\ \hline
+    4                      & 3072GB             \\ \hline
+    5                      & 3079GB             \\ \hline
+    6                      & 3086GB             \\ \hline
+    7                      & 3093GB             \\ \hline
     \end{tabular}
-\caption{Storage space cost under different PDS replication degree}
+\caption{Storage space cost per machine for DFS under different PDS replication degree}
 \label{tab:replication_cost}
@@
 
-{\bf Storage cost of replication.} Table ~\ref{tab:replication_cost} shows the total storage space required by VC as the PDS replication degree is changed.
-The increase in storage cost is minimal because the PDS makes up a very small percent of the total storage space, but the increase in reliability can be much more significant (see Figure~\ref{fig:pds-replication}).
+{\bf Storage cost of replication.} Table ~\ref{tab:replication_cost} shows the total storage space required by 
+VC as the PDS replication degree changes. The increase in storage cost is minimal because the PDS makes up a 
+small percent of the total storage space, while increasing replication degree has a  more significant benefit for
+availability as shown in Figure~\ref{fig:pds-replication}.
 
@@
 
-{\bf Resource usage and its impact to cluster} We further studied the resource usage when running concurrent snapshot backup tasks on each node. 
-Table ~\ref{tab:resource_usage} gives the CPU, memory and disk write workload of running different number of backup tasks at the same time. 
-Notice that memory and CPU used by PDS index and QFS are not included since they belong to the cloud infrastructure services and are shared among many applications.
-We see our hybrid deduplication scheme only occupies small amount of system resources in general, the memory usage is especially small because
-our efficient localized deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in memory for duplicate detection.
+{\bf Memory and disk bandwidth usage with multi-VM processing}. 
+We have further studied the memory and disk bandwidth usage 
+when running concurrent VM snapshot backup on each node. 
+Table ~\ref{tab:resource_usage} gives the CPU, memory and disk write workload of backing up multiple VMs 
+at the same time on each physical machine. 
+[ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
+the cloud infrastructure services and are shared among many applications.]
+We see our hybrid deduplication scheme only occupies a small amount of system resources. 
+The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
+memory during duplicate detection.
 
-\subsection{Processing Time and Throughput}
+Base on the observed performance numbers, even with a single backup task per node and enforcing the disk read speed to
+50 MB/s,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
+ at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.
+
 %{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
@@
 
+{\bf Processing Time breakdown}.
 Figure~\ref{fig:srb_vs_vc} shows
-the  average  processing  time of  each segment using VC and SRM in handling our dataset.
-It has a breakdown of time for reading data and updating the metadata, network latency to visit
-a remote machine, and index access for finger printer comparison.
+the  average  processing  time of  a VM segment under VC and SRB. 
+It has a breakdown of time for reading data, updating the metadata, network latency to visit
+a remote machine, and index access for fingerprint comparison.
 SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
-it relies on this local machine to access its index (often on the disk) and perform comparison.
+it relies on this local machine to access its index (often on the disk, supported by a bloomer filter) 
+and perform comparison.
 VC is faster for index access because it conducts in-memory local search first and then
-accesses  the PDS which is on distributed shared memory.  
+accesses  the PDS on distributed shared memory.  
 SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
@@
   \epsfig{file=figures/srb_vs_vc, width=3.5in}
-  \caption{Time to backup a dirty segment under SRB and VC approach}
+  \caption{Time to backup a dirty VM segment under SRB and VC}
   \label{fig:srb_vs_vc}
@@
 
-Figure~\ref{fig:single_vm_backup} reports the average bacup time for a VM in VC with a varying PDS size.
-Again it shows that data reading dominates the backup process; our deduplication
-procedure only takes a small fraction of the total backup time. 
+Figure~\ref{fig:single_vm_backup} reports the average backup time for a VM in VC when
+varying the PDS size.  It lists the time distribution for data reading,
+similarity-guided local search, cross-VM PDS lookup, and non-duplicate data writing. 
+While data reading dominates the backup process, PDS lookup spends about a similar amount
+of time as local search.
+%procedure takes a small fraction of the total backup time. 
 The change of $\sigma$ does not significantly affect the overall backup speed as
@@
     \includegraphics[width=3in]{figures/single_backup_time}
-    \caption{Backup times for varying PDS sizes}
+    \caption{Average time to backup a VM in VC with varying PDS sizes}
     \label{fig:single_vm_backup}
@@
 
-Figure~\ref{fig:parallel_backup} shows the node throughput when all machine nodes run
-the backup procedure in parallel.
+{\bf Throughput.}
+Figure~\ref{fig:parallel_backup} shows the  backup throughput per each machine when all machine nodes 
+handle  several VMs in parallel.
 To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
@@
 
-Base on the observed performance numbers, even with a single backup task per node and enforcing the disk read speed to
-50 MB/s,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
- at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.
-
 \begin{figure}
     \centering
-    \subfigure[Real VM backup performance]
+    \subfigure[Backup throughput per node under controlled I/O bandwidth usage]
     {
@@
 % \end{table}
-\subsection{Approximate Deletion}
+\subsection{Effectiveness of Approximate Deletion}
 
@@
 
-Figure \ref{fig:leakage} shows the average accumulated storage leakage resulted by daily
-approximate deletions among all VMs. We see the storage leakage ratio is satisfactory: 
-after 9 snapshot approximate deletions, there is only 1MB space leaked over every 10GB
-of stored data. In addition, the leakage ratio grows linearly with the number of approximate deletions
-as our analysis, which gives us a reliable prediction of when to trigger a accurate mark-and-sweep delete operation.
+Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
+snapshot space per VM caused  by approximate deletions.
+The slot line is the predicted leakage using Formula~\ref{eq:leak} from Section~\ref{sect:delete}
+while the dashed line is the actual leakage measured during the experiment.
+[OTHER PARAMETERS USED]
+After 9 snapshot deletions, the actual leakage reaches 0.01\% and this means that
+there is only 1MB space leaked for every 10GB of stored data. 
+%In addition, the leakage ratio grows linearly with the number of approximate deletions
+%as our analysis, which gives us a reliable prediction of when to trigger a accurate mark-and-sweep delete operation.
 
@@
 is related, as once 1PB is stored in the system, assuming a sampling rate of 
-1/101 with 22 byte index entires, 55GB of (in memory) index are required.
+1/101 with 22 byte index entries, 55GB of (in memory) index are required.
 
 Our solution uses more total memory (??how much??), but is more scalable both in
-terms of capactity and distributing the deduplication. The only part of our
+terms of capacity and distributing the deduplication. The only part of our
 algorithm which requires significant network traffic is the PDS deduplication,
@@
 taken by Dong et al. in their Scalable Data Routing paper, and is similar to
-Exreme Binning\cite{??}\cite{extreme_binning09}. We compared our solution to
+Extreme Binning\cite{??}\cite{extreme_binning09}. We compared our solution to
 content-based hash partitioning by running the algorithm on our set of 

### 2013-08-28 snapshot_system/abs.tex
revisions

@@
 localizes deduplication as much as possible within each virtual machine using similarity-guided
-search and associates  underlying file blocks with one VM for most of cases.
+search and associates  underlying file blocks with one VM for most cases.
 It restricts cross-VM deduplication under common blocks with extra replication support.
 Our analysis shows that  this VM centric scheme 
-can  provide  better fault tolerance while using a small amount of computing and storage resource. 
+can  provide  better fault tolerance while using a small amount of computing and storage resources. 
 This  paper  describes a comparative evaluation of this scheme in  accomplishing a competitive deduplication 

### 2013-08-28 snapshot_system/arch.tex
revise eval1.tex
revisions

@@
 Every time there is a new snapshot created,
-we compute a bloom-filter with $z$ bits as the summary of reference pointers for all non-PDS chunks used 
+we compute a Bloom-filter with $z$ bits as the summary of reference pointers for all non-PDS chunks used 
 in this snapshot. Given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
@@
 
-%{\bf Creating bloom filter} Scan all the living snapshot recipess and their segment recipes,
-%for every reference pointing to append store, add it to the bloom filter.
+%{\bf Creating Bloom filter} Scan all the living snapshot recipess and their segment recipes,
+%for every reference pointing to append store, add it to the Bloom filter.
 
@@
 reference pointers of deleted snapshot with
-the merged reference bloom-filter summary of other live snapshots.
-The merging of live snapshot bloom-filter bits uses the logical OR operator 
+the merged reference Bloom-filter summary of other live snapshots.
+The merging of live snapshot Bloom-filter bits uses the logical OR operator 
 and the merged vector still takes $z$ bits.
@@
 %valid snapshots. 
-%Since each VM has uniform bloom filter parameters to create snapshot summaries, 
+%Since each VM has uniform Bloom filter parameters to create snapshot summaries, 
 %such merged summeries give us a compact representation of
 %all block fingerprints that are still in use.
-%Thus by the property of bloom filter, if a fingerprint is not found in merged summaries, 
+%Thus by the property of Bloom filter, if a fingerprint is not found in merged summaries, 
 %we are certain that block is no longer used by any valid snapshot, it would be then added
@@
 \item {\bf Periodic repair of leakage}.
-%[exlpain why second bloom filter, why scan append store]
+%[exlpain why second Bloom filter, why scan append store]
 %Since there are certain unused chunks which are not deleted during the approximate deletion, 
@@
 %\begin{enumerate} 
-%\item After several runs of phase-1, it is proven that the merged type-1 summaries cannot sieve remaining unused blocks, due to the false-positive property of bloom filter.
+%\item After several runs of phase-1, it is proven that the merged type-1 summaries cannot sieve remaining unused blocks, due to the false-positive property of Bloom filter.
 %\item The recipes of deleted snapshots have been removed from the system, thus we are not able to obtain the deleted block fingerprints from any metadata, the only way to discover them is to scan the append store indices.
@@
 %\item {\bf Check existance} For every data reference in the deleted snapshot recipe and its segment recipes,
-%check the existance of that data reference in bloom filter. If not found, it is safe to delete that piece of data from append store
+%check the existance of that data reference in Bloom filter. If not found, it is safe to delete that piece of data from append store
 %because no living snapshots has referenced it.
@@
 %The overall time of running a approximate deletion for one snapshot deletion would be scanning
-%all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
+%all the living snapshots and deleted snapshots, since operations on the in-memory Bloom filter can be done in
 %parallel and is much faster than loading recipes from DFS:
@@
 %Using the example and analysis in previous section, this approximate deletion can be done in 5 minutes.
-%Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
+%Memory usage of the Bloom filter depends on its false-positive probility $P_{bl}$,
 %when set $P_{bl}$ to 0.01, the memory footprint of approximate deletion is about 15 MB.
@@
 
-Each bloom filter vector has  $z$ bits for each snapshot and let $j$ be the number of hash functions used by the
-bloom filter. The probablity that a particular bit is 0  in all $h$ summary vectors is  
+Each Bloom filter vector has  $z$ bits for each snapshot and let $j$ be the number of hash functions used by the
+Bloom filter. The probablity that a particular bit is 0  in all $h$ summary vectors is  
 $(1- \frac{1}{z}) ^{j U}$. Notice that a chunk may appear multiple times in these summary vectors; however, this should not 

### 2013-08-28 snapshot_system/intro.tex
revisions

@@
 broad effect and many
-snapshots of virtual machines would be affected.
+snapshots of virtual machines could be affected.
 The previous work in deduplication focuses on the efficiency and approximation of
-finger print comparison, and has not addressed fault handling issues  together with deduplication.
+fingerprint comparison, and has not addressed fault tolerance issues  together with deduplication.
 Thus we also seek deduplication options that yield better fault isolation.
@@
 Another issue considered is that
-that deletion of old snapshots compete for computing resource as well. 
+that deletion of old snapshots competes for computing resource as well. 
 %That is because data dependence created deletion of old snapshots competes for computing resources.
@@
 Sharing of data chunks among by multiple VMs needs to be detected during
-snapshot   deletion and such dependence complicates deletion operations. 
+snapshot   deletion and such dependencies complicate deletion operations. 
 %The additional complexity for deletions
@@
 This approach is VM centric by localizing duplicate detection within each VM  
-and by packaging data chunks from the same VM into a file system block as much as possible.
+and by packaging only data chunks from the same VM into a file system block as much as possible.
 By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
@@
 with a VM-centric approach. 
-Section~\ref{sect:model}  analyzes the tradeoff and benefit of our approach. 
+Section~\ref{sect:model}  analyzes the tradeoffs and benefits of our approach. 
 Section~\ref{sect:arch}  describes our system architecture and implementation details.
 %   the benefit of our approach for fault isolation. 
-Section~\ref{exper} is our experimental evaluation that compare with the other approaches.
+Section~\ref{exper} is our experimental evaluation that compares with other approaches.
 Section~\ref{conc}  concludes this paper.
@@
 \comments{
-By observations on the VM snapshot data from production cloud, we found snapshot data duplication 
+By observations of the VM snapshot data from production cloud, we found snapshot data duplication 
 can be easily classified into two categories: \emph{inner-VM} and \emph{cross-VM}. Inner-VM duplication
@@
 a small amount of resources to deduplicate.
-Separating deduplication into multi levels effectively accomplish the major space saving goal
-compare the global complete deduplication scheme, at the same time it makes
-the backup of different VMs to be independent for better fault tolerance.
+Separating deduplication into multiple levels effectively accomplishes the major space saving goal
+compared the global complete deduplication scheme, but at the same time makes
+the backup of different VMs independent for better fault tolerance.
 

### 2013-08-28 snapshot_system/background.tex
reorgnaize
update background

@@
 \label{sect:background}
-
-%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
 At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
@@
 means no fine-grained file system metadata can be used to determine the changed data.
-%Only raw access information at disk block level are provided. 
-%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
-%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
-%only a very small slice of cluster resource can be used for the backup purpose.
 
@@
 used in ~\cite{EMC,NetAppOffline} to remove previously written duplicates during idle time.
-%,NGmiddleware2011}.
-%Today's commercial data backup systems (e.g. from EMC and NetApp)
-%\cite{emc_avamar}\cite{datadomain_whitepaper}
-%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
 Several techniques have been proposed to speedup searching of duplicate
@@
 accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-%As discussed in Section~\ref{sect:intro},
-%there is no dedicated resource for deduplication in our targeted setting and low memory usage
-% is required so that the resource impact to other cloud services is minimized.
-%NG et al.~\cite{ NGmiddleware2011}  use
-%a related filtering technique for integrating deduplication in Linux  file system and the memory
-%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
-%Lillibridge et al.~\cite{sparseindex09} break list of chunks
-%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
-%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
-%These are segments that share many chunk IDs with the incoming segment with high probability.
 The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
-%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
 to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
-%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
-%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
-%lookup  
-%In comparison, this paper focuses on  full deduplication without approximation.
-%We also take advantages of the fact that in a VM cloud environment,
-%the virtual device driver can easily keep track if  large data
-%segments have been modified using dirty bits and such information can avoid sending
-%unmodified data segments for deduplication, which significantly saves cost.
 
@@
 for running the backup service and then present our solution  with fault isolation.
-%In our work, the foucs 
-%there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
-%in our context, finishing the backup of required VM images within a reasonable time window is more
-%important than optimizing individual VM block  backup requests.
-
-\comments{
-This paper considers a backup service uses the existing cluster computing resource. 
-Another option is to attach  a separate backup system with deduplication
-support the cluster, and  every machine can periodically transfer snapshots to
-the attached backup system.
-%One  weakness of this approach is communication bottleneck between a large number of machines
-%in a cloud to this centralized  service.
-The cost of allocating the above dedicated backup  resource can be expensive.
-Since most of backup data is not used eventually, CPU and memory resource in such a backup service may 
-not be fully utilized. This paper seeks for a low-cost architecture option.
-}
-%It should be emphasized that our approach does not  accumulate raw backup data temporarily for deduplication
-%and does not require a significant amount of extra storage capacity.
-%Our strategy is to perform a drity  scan to collect
-% a small amount of disk space  to accumulate
-%deduplicate requests along with necessary meta data, and perform actual backup after deduplicate detection completes.
-
-%affecting the overall time of backup.

### 2013-08-28 snapshot_system/fast14_architecture.tex
change to usenix format

--- 2013-08-28 snapshot_system/arch.tex
@@
-\comments{
-\section{Design Overview}
-\label{sect:design}
-%[describe what is going to be presented in this section]
-We start by analyzing the main features in the design of our system.
-We first present its architecture,
-then introduce the two major contributions: the collocated deduplication 
-scheme and the snapshot deletion strategy.
-
-\begin{figure}
-    \centering
-    \subfigure[Cluster architecture]
-    {
-        \includegraphics[width=3in]{images/socc_arch_cluster}
-        \label{fig:arch_cluster}
-    }
-    \\
-    \subfigure[Node architecture from VM point of view]
-    {
-        \includegraphics[width=3in]{images/socc_arch_vm}
-        \label{fig:arch_vm}
-    }
-    \caption{System architecture}
-    \label{fig:arch}
-\end{figure}
-
-\subsection{Architecture}
-\label{sect:arch}
-%[describe the cloud environment]
-Our architecture, as shown in figure.\ref{fig:arch}, is built on top of 
-Alibaba's platform which is the largest cloud service provider in China.
-
-%[describe the arch from cluster side]
-{\bf Cluster Architecture}
-A typical VM cluster in our cloud environment
-consists of from hundreds to thousands of physical machines, each of which can
-host tens of Xen-based\cite{Barham2003} VMs.
-Alibaba's cloud platform provides a hadoop-like infrastructure, 
-which includes several highly scalable distributed service:
-\begin{enumerate}
-\item {\bf Distributed file system} This is a scalable distributed file system (DFS) being optimized for many large and sequential reads or appends.
-DFS holds the responsibility of managing physical disk storage
-in the cloud. All data needed for VM services, such as virtual disk images used by runtime VMs,
-and snapshot data for backup purposes, reside in this distributed file system. 
-%\item[KV]: a distributed key-value store for managing structured data.
-%\item[MapReduce]: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
-\item {\bf Distributed memory cache} A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inquiries. 
-\end{enumerate}
-}
-
 \section{Architecture and Implementation Details}
 \label{sect:arch}
-%[describe what is going to be presented in this section]
-%We start by analyzing the main features in the design of our system.
-%We first present its architecture,
-%then introduce the two major contributions: the colocated deduplication 
-%scheme and the snapshot deletion strategy.
-%\subsection{Architecture}
-%[describe the cloud environment]
-
-%Our architecture, as shown in figure.\ref{fig:arch}, is built on top of 
-%Alibaba's platform which is the largest cloud service provider in China. 
-%A typical VM cluster in our cloud environment
-%consists of from hundreds to thousands of physical machines, each of which can
-%host tens of xen-based\cite{Barham2003} VMs.
-%Alibaba's cloud platform provides a hadoop-like infrastructure, 
-%which includes several highly scalable distributed service:
-
 Our system runs on a cluster of Linux machines with Xen-based VMs.
@@
 \subsection{ Components of a cluster node } 
-
 As  depicted in Figure~\ref{fig:arch_vm}, 
@@
 and 4)  a PDS client to support PDS index access.
-%We will further discuss our deduplication scheme in Section~\ref{sect:dedupe}.
 
@@
 is modified since last backup. 
-%Hence we think of segment as the basic unit in snapshot backup similar to
-%file in normal filesystem backup: a snapshot could share a segment with previous snapshot it is not changed. 
 Segments are further divided into variable-sized chunks (average 4KB) 
@@
 which brings the opportunity of fine-grained deduplication.
-% by allowing data sharing between segments.
-%This driver maintains a map of dirty bits to record the change status of every fix-size segment of the virtual disk. 
 When the VM issues a disk write, the dirty bit for the corresponding segment is set
@@
 The representation of each snapshot has  a two-level index data structure.
-%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
 The snapshot meta data (called snapshot recipe) contains a list of segments, each of which contains segment
 metadata of its chunks (called segment recipe).
-%\begin{figure}[htbp]
-%  \centering
-%  \epsfig{file=images/snapshot_representation, width=3in}
-%  \caption{An example of snapshot representation.}
-%  \label{fig:snapshot_rep}
-%\end{figure}
-%As a result, the representation of each snapshot is designed as a two-level index data structure 
-%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot_rep}.
-%A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
-%that holds the meatdata of its chunks. We choose this two-level structure because in practice we
-%observe that during each backup period only a small amount of VM data are added or modified. 
-%As the result, even the metadata of two snapshots can be highly similar, 
-%thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
-%Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
-%segments which greatly ease the segment-level deduplication.
 In snapshot and segment recipes, 
 the data structures  includes reference pointers to the actual data location to eliminate the need for additional indirection.
-%In our implementation the data reference is a 8 bytes field which is either an 
-%ASID (discuss in Section \ref{sect:append}) or an offset of an additional flag indicates
-%the location of PDS data.
-
-%\subsection{Snapshot management}
 
@@
 
-\comments{%socc_arch_cluster now includes the entire arch instead of having 2 figures
-\begin{figure}
-    \centering
-    \subfigure[Node architecture from VM point of view]
-    {
-        \includegraphics[width=3in]{images/socc_arch_vm}
-        \label{fig:arch_vm}
-    }
-    \\
-    \subfigure[Cluster architecture]
-    {
-        \includegraphics[width=3in]{images/socc_arch_cluster}
-        \label{fig:arch_cluster}
-    }
-    \caption{System architecture.}
-    \label{fig:arch}
-\end{figure}
-}
-
-%[describe the architecture frm node side]
-%[brief the virtual device driver]
-%One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
-%virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
-%This driver maintains a map of dirty-bits to record
-%the change status of every fix-size segment of the virtual disk. 
-%When the VM issue a disk write, the bits coresponding to the segments that covers 
-%the modified disk region are set, thus letting snapshot deduplication component knows these
-%segments must be checked during snapshot backup. After the snapshot backup is finished, 
-%snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
-%a clean state.
-
-%[brief the snapshot deduplication]
-%The snapshot deduplication component consists of the chunking and deduplication 
-%logic of our snapshot storage system. We choose
-
-%[describe the arch from cluster side]
-
-%[describe the data structure in underlying storage]
 \subsection{A VM-centric snapshot store for backup data}
-
 We build the snapshot storage on the top of a distributed file system.
@@
 There is also a special store containing all PDS chunks shared among different VMs.
-% with a higher replication degree.
-%This separation of PDS chunks allows us to change the replication degree of of those popular file blocks in the 
-%underlying file system
-%Extra replication of this store is added and analyzed in Section~\ref{sect:analysis}.
 As shown in Fig.\ref{fig:as_arch}, we explain the data structure of snapshot stores as follows.
@@
 \begin{itemize}
-
-%The reference to each PDS cunk  contains  a container ID as explained ,
-
-%The PDS index uses the offset and size as a reference in its index structure.
-
 \item Data of each VM snapshot store excluding PDS is divided into a set of containers and 
@@
 200-600 chunks.
-%Given  the average chunk size of 4KB,  the index size for a 1GB container reduces from 10MB to 100KB when
-%the chunk group size is 100.
-%%CBlock, then the overall index size is reduced to $1/m$. 
-%n our implementation, using $m=100$ reduces the index for
-%a 1GB container from 10 MB to 100 KB.
+
 \item Each data container is represented by three files in the DFS:
@@
 3) a chunk deletion log file records all the deletion requests within  the container.
-
-%A VM snapshot store typically has a small number of containers because each container is 
-%fairly large, with an average size of 1GB, and 
-%maintains a limited number of snapshots (e.g. 10 in the Alibaba case).
-%New snapshot data chunks can be effectively compressed in chunk groups in addition to  deduplication.
 
@@
 
-%Every container  Store assign every piece of data a CID for its internal data referencing. 
-%When new data is appended, its CID is the current largest CID in that container plus one.
-%As a result, all the data locations are naturally indexed by this self-incremental CID, 
-%no extra sorting is needed.
 \item The PDS chunks are a set of commonly used data and they are stored in one PDS file.
@@
 \end{itemize}
-
-%acceretrieved  and ret
-%Using CBlock brings us several advantages: First, the write workload to DFS master is greatly reduced; second, grouping
-%small chunks gives better compression. Third, reading a CBlock (200 - 600 KB) typically cost the same amount of disk 
-%seek as reading a 4KB chunk. Finally, this greatly reduces the size of index. Let $m$ be the number of chunks in each
-%CBlock, then the overall index size is reduced to $1/m$. In our implementation, using $m=100$ reduces the index for
-%a 1GB container from 10 MB to 100 KB.
-
-% of  divided into a set of data containers.
-%Each container has 3 parts.
-%Each chunk in the snapshot is referenced by the following data format
-
-%The Append Store (AS) is our underlining storage engine for storing snapshot data in the distributed file system
-%after deduplication.
-%AS is built on top of our highly scalable distributed file system (DFS), 
-%which is very similar to Google's file system
-%in a sense that it is optimized for large files and sequential read/append operations.
 
@@
 
-%\begin{figure}[htbp]
-%  \centering
-%  \epsfig{file=images/pds_arch, width=3in}
-%  \caption{System architecture for PDS data store.}
-%  \label{fig:as_arch}
-%\end{figure}
-
 A snapshot  store supports three API calls.
 \begin{itemize}
-
-%AS supplies three interfaces: {\em get(ref)} accepts a data reference and retrieves data, 
 \item {\em Put(data)}. This places data chunk into the snapshot store and returns a reference to be stored in 
@@
 The writing of PDS data chunks is conducted periodically when there is a new PDS calculation.
-%Since the PDS dataset is small, a new PDS file is created during the periodical update.
 \item{\em Get(reference)}.
@@
 and we will discuss the snapshot deletion in detail in the following subsection.
-%deletes the data pointed by the reference.
-%Under the hood, small var-sized data are grouped and stored into larger data containers. Each VM has
-%its snapshot data stored in its own Append Store, specified by the VM ID. 
-%We split every Append Store into multiple data containers so that reclaiming the disk space would not 
-%result in rewriting all the data at the same time.
 When deletion requests are issued for a specific container,
@@
 number of deletion requests to  compact and  reclaim the corresponding disk space. 
-%The actual compaction will only take place when the number of deleted items 
-%reached $d\%$ of container's capacity. 
 During compaction, the snapshot store creates a new container (with the same container ID) to replace the 
@@
 
-%As shown in Fig.\ref{fig:as_arch}, every data container is represented as three data files in DFS:
-%the data file holds all the actual data, the index file is responsible for translating data reference
-%into data locations, and a deletion log file remembers all the deletion requests to the container.
-%
-%A data reference is composed of two parts: a container ID (2 bytes) and CID (6 bytes).
-%Append Store assign every piece of data a CID for its internal data referencing. 
-%When new data is appended, its CID is the current largest CID in that container plus one.
-%As a result, all the data locations are naturally indexed by this self-incremental CID, 
-%no extra sorting is needed.
-
-%Append Store groups multiple chunk data (i.e., 100) into larger units, called {\em CBlock}.
-%CBlock is the basic unit for append store's internal read/write/compression.
-%There is one index entry in the container index corresponding to every CBlock. It keeps the first chunk's CID
-%in that CBlock, and the CBlock data's size and location.
-%
-%Using CBlock brings us several advantages: First, the write workload to DFS master is greatly reduced; second, grouping
-%small chunks gives better compression. Third, reading a CBlock (200 - 600 KB) typically cost the same amount of disk
-
 \subsection{ VM-centric Approximate Snapshot Deletion with Leak Repair}
+\label{sect:delete}
 
@@
 
-%Given the large number of snapshot deletion requests, 
 We seek a fast solution with a low resource usage to delete snapshots.
-%In a traditional deduplication system, deletion often require looking at global scope to
-%resolve the data dependency between logical backup entities and physical data chunks.
 Our VM-centric snapshot storage design simplifies the deletion process since 
@@
 to efficiently identify unused chunks.
-% in $O(n)$ time where $n$ is the total number of non-PDS chunks to be deleted from a VM snapshot store.  
+
 The algorithm contains three aspects.
 
-%Our system adopts VM-centric snapshot  lazy delete strategy so that all snapshot deletions are scheduled
-%in the backup time window at midnight. 
-%Therefore, snapshot deletions must be fast enough to fit in time window and
-%efficient enough to satisfy our resource constraints.
-%However, there is no simple solution can achieve these goals with high reliability.
-%Our hybrid deletion strategy, using fuzzy deletion regularly and accurate deletion periodically,
-%accomplishs our speed, resource usage and relibility goals very well.
 \begin{itemize}
@@
 in this snapshot. Given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
-
-%To control the false positive ratio $\epislon$ under $0.01$, an average snapshot of size 40 $GB$ with 
-%$u \approx 10$ million chunks, $z$ has 10 million bits.
-
-%{\bf Creating Bloom filter} Scan all the living snapshot recipess and their segment recipes,
-%for every reference pointing to append store, add it to the Bloom filter.
 
@@
 the time and memory cost of this comparison is small, linear to the number of chunks to be deleted.
-%Instead of scanning the entire append store indices, we merge the type-1 summaries of all
-%valid snapshots. 
-%Since each VM has uniform Bloom filter parameters to create snapshot summaries, 
-%such merged summeries give us a compact representation of
-%all block fingerprints that are still in use.
-%Thus by the property of Bloom filter, if a fingerprint is not found in merged summaries, 
-%we are certain that block is no longer used by any valid snapshot, it would be then added
-%to append store's deletion log.
 
@@
 %[exlpain why second Bloom filter, why scan append store]
-%Since there are certain unused chunks which are not deleted during the approximate deletion, 
 Leakage repair is conducted periodically to fix the above approximation error.
@@
 For example,
-% are live used   we load the reference pointers of all chunks from a VM snapshot store as a table in memory,
-%then scan through all the snapshots' segment recipes. For each reference pointer that is in use by a snapshot,
-%we mark the corresponding entry in the table as in use. Finally those unmarked (and therefore unused) reference pointers in the
-%table represent chunks that can be safely deleted.
-%The cost of leak repair mainly come from holding a table of reference pointers and the scan of all snapshots' metadata.
 consider each reference pointer consumes 8 bytes plus  1 mark bit, a VM that has 40GB backup data with about
 10 million chunks will need less than 90MB of memory to complete a VM-specific mark-sweep process.
-%, scanning all snapshots metadata is many times slower when compared
-%to the approximate deletion which only scans single snapshot's metadata.
-%It's worth mention that compared to previously-developed mark-and-sweep techniques, 
-%our leak repair still has advantages because the scope of repair is restricted within a single VM's snapshot 
-%store due to our VM-centric design, and we perform leakage repair periodically.
-%We cannot simply repeat the phase 1 multiple times to reduce temporary storage leakage, because:
-%\begin{enumerate} 
-%\item After several runs of phase-1, it is proven that the merged type-1 summaries cannot sieve remaining unused blocks, due to the false-positive property of Bloom filter.
-%\item The recipes of deleted snapshots have been removed from the system, thus we are not able to obtain the deleted block fingerprints from any metadata, the only way to discover them is to scan the append store indices.
-%\end{enumerate}
 \end{itemize}
-
-%\item {\bf Check existance} For every data reference in the deleted snapshot recipe and its segment recipes,
-%check the existance of that data reference in Bloom filter. If not found, it is safe to delete that piece of data from append store
-%because no living snapshots has referenced it.
-
-%The overall time of running a approximate deletion for one snapshot deletion would be scanning
-%all the living snapshots and deleted snapshots, since operations on the in-memory Bloom filter can be done in
-%parallel and is much faster than loading recipes from DFS:
-%\begin{equation}
-%T = (N_{SS} + 1) * T_{scan\_recipes}
-%\end{equation}
-%
-%Using the example and analysis in previous section, this approximate deletion can be done in 5 minutes.
-%Memory usage of the Bloom filter depends on its false-positive probility $P_{bl}$,
-%when set $P_{bl}$ to 0.01, the memory footprint of approximate deletion is about 15 MB.
-%~
 
@@
 newly add chunks $\Delta u$. 
-%However, some of chunks among them are not detected as unused in our approximation
-%algorithm, thus forms the storage leakage. 
 Let $R$ be the total number of runs of approximate deletion between two consecutive 
@@
 as discussed earlier and takes a short period of time.
-% which is sufficiently small to offset the heavy I/O workload of the mark-sweep process.

### 2013-08-28 snapshot_system/fast14_background.tex
change to usenix format

--- 2013-08-14 snapshot_system/challenge.tex
@@
-%\section{Design Consideration and Options}
-%\label{sect:options}
-
 \section{Background and Design Considerations}
 \label{sect:option}
-
-%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
 At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
@@
 cloud cluster avoids the extra cost to acquire a dedicated backup facility
-and reduces the network bandwidth consumption in transferring the un-deduplicated
+and reduces the network bandwidth consumption in transferring the
 raw data for backup. 
 Figure~\ref{fig:collocated} illustrates the cluster architecture where
-each physical runs a backup service and a distributed file system (DFS)~\cite{GFS2004,Hadoop} 
+each physical machine runs a backup service and a distributed file system (DFS)~\cite{GFS2004,Hadoop} 
 serves a backup store  for the snapshots.
-%The previous study shows that 
-% deduplication can compress the backup copies 
-%effectively in a 10:1 or even 15:1 rage. 
-%Therefore  the portion of space in a cluster
-%allocated for snapshots of data should not dominate
-%the cluster storage usage.
-%perhaps briefly discuss compression is high, incremental change is small from versions..???
-
-%The running of such a service is subject to the resource availability of the system and
-
-% That arises mainly in Alibaba's Aliyun cloud service.
-%concerns
-%Base on Aliyun's production environment, the snapshot backup job has to satisfy
 
@@
 
-%Only raw access information at disk block level are provided. 
-%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
-%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
-%only a very small slice of cluster resource can be used for the backup purpose.
-
-%The previous work for storage backup has extensively studied  data deduplication techniques that
-%can eliminate redundancy globally among different files from different users.
-%Offline deduplication is 
-%used in ~\cite{EMC,NetAppOffline} to remove previously written duplicates during idle time.
-%,NGmiddleware2011}.
-%Today's commercial data backup systems (e.g. from EMC and NetApp)
-%\cite{emc_avamar}\cite{datadomain_whitepaper}
-%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
-Since it is expensive to compares a large number of chunk signatures for deduplication,
+Since it is expensive to compare a large number of chunk signatures for deduplication,
 several techniques have been proposed to speedup searching of duplicate
@@
 accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-%As discussed in Section~\ref{sect:intro},
-%there is no dedicated resource for deduplication in our targeted setting and low memory usage
-% is required so that the resource impact to other cloud services is minimized.
-%NG et al.~\cite{ NGmiddleware2011}  use
-%a related filtering technique for integrating deduplication in Linux  file system and the memory
-%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
-%Lillibridge et al.~\cite{sparseindex09} break list of chunks
-%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
-%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
-%These are segments that share many chunk IDs with the incoming segment with high probability.
 The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
-%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
 to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
-%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
-%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
-%lookup  
-%In comparison, this paper focuses on  full deduplication without approximation.
-%We also take advantages of the fact that in a VM cloud environment,
-%the virtual device driver can easily keep track if  large data
-%segments have been modified using dirty bits and such information can avoid sending
-%unmodified data segments for deduplication, which significantly saves cost.
 Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
@@
 in this paper.
-%We will describe the motivation of using the cluster-based   approach
-%for running the backup service and then present our solution  with fault isolation.
-%In our work, the foucs 
-%there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
-%in our context, finishing the backup of required VM images within a reasonable time window is more
-%important than optimizing individual VM block  backup requests.
-
-%{\em Collocating with cluster-based cloud services.}
-%We collocate the backup service with other cloud services in a cluster
-%and use a distributed file system
-%store the backup with multiple replicas. 
-%There might be a concern that storing many versions of snapshots would
-%go against the purpose of deduplication.
-
-%Assume on the average the compression
-%ratio is $c$:1.  When the number of versions
-%saved in the backup storage is $l$  on the average, 
-%the amount of storage space in the cluster allocated  for the backup would be $\frac{l}{l+c}$.
-%For example, when $l=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
-%When $l=9$ and $c=13$, storage usage is 40\%. 
-%That is acceptable given today's cheap cost for disk storage.
-%In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data.
-%Each machine however can typically provide over 10TB storage.
-%Thus the normal disk usage  is about 1TB per machine, and adding 30\% to 100\% 
-%extra space for the backup is not a practical concern, especially with the
-%added benefits of cheaper running costs and lower network bandwidth requirements.
 
@@
 \item {\em Deduplication localization.}
-%Previous work in deduplication~\cite{extreme_binning09,sparseindex09} has
-%studied the solutions to reduce memory requirements.
-%One important issue not considered in the previous work is how 
 Because a data chunk is compared with signatures collected from all VMs during
 the deduplication process, only one copy of duplicates is stored in the storage,
-this artificially creates data dependency among different VM users. 
+this artificially creates data dependencies among different VM users. 
 Content sharing via deduplication affects fault isolation since machine failures happen periodically 
 in a large-scale cloud and
-%failure of a shared block affects many VMs.
-%the loss of a shared chunks can affect many VM users whose snapshots share this 
-%data block. 
 loss of a small number of shared data chunks can 
@@
 deduplication efficiency, and  can faciltate parallel execition of snaptshot operations.
-%Thus we seek for a tradeoff.
-
-% since storage for shared identical content chunks can become a failure point.
-%Without any control of such data sharing, we can only increase  
-%replication for global datasets to enhance the availability,
-%but this incurs significantly higher costs.
-%Thus a key goal  in our design
-%is restricting the impact of  data loss to a limited number of VMs. 
-%It is not desirable that small scale of data failure affects the backup of many VMs.
-%when users access snapshots in a recovery process. 
 \item{\em  Management of file system blocks.}
@@
  a data chunk in a typical deduplication system is of a nonuniform size with 4KB or 8KB on average.
-%We need to build an intermediate layer that supports large snapshot writing with append operations
-%and infrequent snapshot access.
 Packaging data chunks to a file system block can create more data dependence among VMs
@@
 Thus we need to consider a minimum association of a fie system block to VMs in the packaging process.
-%The distributed file system~\cite{GoogleFS,Hadoop} provides the replication support
-%and we can leverage existing open-source software to implement such a layer.
-%When the number of machines failed exceeds the replication degree, there could be
-% some data loss.  
-%Storage deduplication worsens the impact of such faults
-%because  the majority of each snapshot (e.g. over 90\%) is deduplicated
-%and the corresponding data chunks stored in the underlying file blocks
-%are shared by many VMs. 
-%The failure of one data chunk or block can impact many sharing VMs. 
 \end{itemize}
 
-%\item {\em Requirement for backup throughput and low computing resource usage}.
 Another consideration is the computing cost of deduplication.
 Because of collocation of this snapshot service with other existing cloud services, 
-%As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
-%to be processed can be huge. 
 cloud providers wish that the backup service only consumes  small resources
 with a minimal impact to the existing cloud services.
-%the computing resources allocated for the snapshot service is limited, especially
-%because of its lower priority.
 The key resource for signature comparison  is memory for storing the fingerprints. 
@@
 with the fault isolation consideration discussed below.
-%A snapshot backup service shall not compete cpu, memory, or I/O bandwidth with VMs. 
-%Fingerprint-based search does require a significant amount of memory for fingerprint lookup
-%and comparison.  This competes memory resource  with the existing VMs.
-%Our design is to identify a low-cost and low-profile scheme for deduplication.
-%Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
-%Excessive use of bandwidth and computing resource for backup can create
-%noticeable contention for resources with the existing cloud, which is not
-%preferred and may not not be acceptable for production system operation. 
-%Thus it is desirable that backup for all nodes
-%can be conducted in parallel and in a short period of time,
-%and any centralized or cross-machine communication for
-%deduplication should not become a bottleneck.
-%For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, 
-%the system must finish saving daily snapshots of all VMs in a few hours. 
-%Often a cloud has a few hours of light workload each day (e.g. midnight),  
-%which creates an small window for automatic backup.
-%The backup service can generate hundreds of terabytes of data in such a time window
-%without optimization and thus the resource content is considered carefully as we design
-%a fault-resilient cluster-based solution. 
-%In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 
-%500TB/hour.  The system must finish saving daily snapshots of all VMs in few hours.
-
-%At Aliyun, it is required that while CPU and disk usage should be small or modest during backup time,
-%the memory footprint of snapshot service should not exceed 500MB at each node.
-
-\comments{
-Another consideration is backup data cleaning to delete useless blocks.
-Keeping reference counters for shared data blocks is challenging and less reliable.
-The previous work has advocated the mark-and-sweep approach  which periodically
-scans all data (or modified latest version of data)~\cite{?, Guo2011}. It first marks
-all used blocks and then sweep all chunks to reclaim unmarked blocks. 
-This approach is resilient to errors: at any time the process can simply be restarted with no 
-negative side effects.  Scalability, however, is an issue.
-To deal with 1 PB snapshots data, which may be represented by 10,000 GB FP index,
-If we account for an average deduplication factor of 10 (i.e., each chunk
-is referenced by 10 different snapshots), the total size
-of snapshot metadata that need to be read during the mark phase will
-be 100 TB.  This alone will take almost 2 hours on a
-1000-machine cloud. Furthermore, marking the in-use
-bits for 250 billion entries is no easy task. There is no
-way to put the bit map in memory. One might want
-to mitigate the poor performance of mark-and-sweep by
-doing it less frequently. But in practice this is not a viable
-option: customers always want to keep the utilization
-of the system close to its capacity so that a longer
-history can be stored. With daily snapshots taking place,
-systems rarely have the luxury to postpone deletion operations
-for a long time. In our field deployment, deletion
-is done once a day. More than 2 hours in each run is too
-much. In a large production-oriented deduplication system reference
-management needs to be very reliable and have
-good recover-ability. It should tolerate errors and always
-ensure correctness. Although mark-and-sweep provides
-these properties, its performance is proportional to the
-capacity of the system, thus limiting its scalability.
-
-}
-
-%we want to isolate 
-%each VM's snapshot backup as much as possible while still enjoy the benefit of deduplication.
-%In large scale cloud, node faiures happen at daily basis, we don't want a problem at small scale
-%to affect large amount of VMs due to data sharing.
-%a key weakness of global content fingerprint comparison is that it affects fault isolation.
-
-%2) data sharing among users for accessing common signagutes causes the system less resilient to storage failures.
-%any loss of one piece of  shared data content hash and actualcontent will damange many VM snapshots, which can cause massive impacts
-%on reliability of many users.
-
-%Another point is that the previous work in signature-based comparison does not address
-%load balancing for a distributed environment during parallel access.  
-%Some content signatures can be extremely hot, but the machines  that  handle such signatures can become
-% a bottleneck. Uncoordinated signature assignment could lead to imbalanced access workload.
-
-%There are multiple choices of snapshot backup design for VM images and our considerations are described
-%as follows. 
-%Our design considerations
-%\begin{enumerate}
-%\item {\bf Centralized vs. decenalized} 
-%
-%It is desirable to have  a decentralized architecture.
-%Given a large amount of snapshot data communicated from each machine to the backup storage,
-%with a distributed storage architecture for backup, one could exploit  exploit data locality between
-%the source of data and storage location of data to reduce cross-platform bandwidth requirement for backup.
-
-%execute in parallel and easy to coordinate. In fact, we want to avoid cross-node dependency at scheduling VM snapshot operations, such that no global coordinator is necessary.
-%\item {Load balancing in resource consumption}: the cost of snapshot service shall be evenly distributed onto every node. We don't have a super powerful
-%or stable node that can accept extra responsibility.
-%\item {minimization of inter-user data dependency for fault tolerance}: we want to minimize the data dependency to a controllable level.
-Data deduplication means sharing of data, thus one failure at a single point may affect the snapshot service of hundreds of VMs, which is absolutely unacceptable.
-%\item {Resource usage modeling and control}.
-%\end{enumerate}
 
@@
 to the existing applications.  
-%We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, and then present
-%an architecture and implementation design with deletion support.
-%The traditional approach compares all fingerprints and
-%stores one copy for all of a chunk's duplicates.
 In designing a VC duplication algorithm, we have considered and adopted some of
@@
 Such a scheme  is  VM-centric since deduplication is localized. 
-%Active snapshots will contain all the information needed to restore the virtual disk
-%and when deleting a snapshot, data referenced by other snapshots are removed.
 We are seeking for a tradeoff since 
 cross-VM  signature comparison can deliver additional compression~\cite{Guo2011,Dong,ExtremeBining}.
-%We are seeking for additional optimization to improve duplication efficiency and design the 
-%association of data chunks with the underlying file blocks so that
-%file block sharing among VMs is minimized.
 \item {\bf Stateless  Data Routing}.
@@
 each request is routed  to a machine which holds
-a bloomer filter  or can fetch on-disk index for additional comparison.
+a Bloom filter  or can fetch on-disk index for additional comparison.
 While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
 VM-specific local search.
-
-%We compared our solution to
-%content-based hash partitioning by running the algorithm on our set of 
-%traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
-%the minhashes of the superchunks for routing. The results of this are shown in
-%Table~\ref{??}. Routing each chunk to a bin provides good deduplication
-%efficiency, and only requires each storage node to keep an index of local data
-%and the bin mapping, but misses significant opportunities in our indended use
-%case.
-
-%The problem with the Data Routing algorithm is in the very high network traffic.
-%Our intended use case is a backup system which runs alongside a number of VMs,
-%in order to save costs. Data Routing makes no use of the inherent locality in
-%such a system, and therefore puts a much higher network burden on machines which
-%are also running 35 VMs each. This will reduce the available network bandwidth
-%to users of the VMs, and/or reduce the possible deduplication throughput.
 \item {\bf Sampled Index}.
@@
 to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
-%An evaluation with our test data shows that using a sampled index can achieve a high
-%deduplication efficiency with a single machine setup.  
 The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
-%The algorithm stores the sampled index in memory, which is required for high
-%throughput to avoid the disk-bottleneck problem - since the index itself has no
-%locality information, lookups are essentially random, so the index must be
-%somehow optimized to prevent excessive disk seeking (the sampling algorithm does
-%this by storing the index in memory). 
 To use a distributed memory version of the sampled index, every deduplicate request
@@
 can be significant.  
-
-%Another possibility is to use this approach partially  in our VM centric solution by indexing
-%the most popular data chunks. For a small set of popular data chunks, the prefetching strategy
-%used in the sampled index will not work well because the spatial locality is limited among popular 
-%data chunks. In our test data,  on average the number of consecutive data chunks is 7, which is too small
-%to be effective for index sampling.
-
-%To distribute this sampled index, every  each machine would
-%either require a complete copy of the index which would have a prohibitive cost in
-%memory, or something like memcached must be used, which leaves the same problem
-%as the disk bottleneck with every index check potentially using the network.
-%The difficulty in storing extremely large bodies of data
-%is related, as once 1PB is stored in the system, assuming a sampling rate of 
-%1/101 with 22 byte index entires, 55GB of (in memory) index are required.
-
-%Our solution uses more total memory (??how much??), but is more scalable both in
-%terms of capactity and distributing the deduplication. The only part of our
-%algorithm which requires significant network traffic is the PDS deduplication,
-%but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
-%so is only done for a small percent of blocks (?? 5-10\% ??).
 \end{itemize}
 
-%With these considerations in mind, we study a 
-%VM-centric approach (called VC)
-%for a backup service co-hosted   in the existing set of machines and resource usage is friendly
-%to the existing applications.  
 We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, 
@@
 an architecture and implementation design with deletion support.
-
-%The deduplication process is first conducted among snapshots within each VM
-%and then is conducted across VMs.  
-%Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
-%and complicate failure management,
-%we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
-%For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
-%Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance.
-%
-%in the  our studies show that there are a large amount of data unmodified in VM snapshots
-%and shared among many users (e.g. OS data). The sharing pattern follows a zip-like distribution.
-%With this characteristic, we can store a small amount of popular data items which coverage a large amount of
-%snapshot data blocks. 
-%We discuss our design and data analysis in the next section.
-
-%This method is based on the observation of two facts in Aliyun's VM cloud: first, VM's OS disks contain 
-%huge amount of operating system and software related data which is almost never modified during VM's life span. 
-%Second, the duplication pattern of user generated data follows Zipf-like law, thus a tiny set of hottest data
-%take up the majority of data duplication. As a result, if we extract these hot data as a common data set,
-%then most of data duplication will emerge by searching in this very small scope.
-
-%For example, In cloud storage, we are solving data deduplication problem in a different context of 
-%data stream deduplication (the D2D case): our snapshot storage service is co-located with runtime VMs,
-%thus we have very limited amount of system resource leave for data deduplication. For example,
-%in Aliyun's 8-core, 48GB memory, 12TB VM server, there lives over 20 VMs who are hungrily competing for
-%system resources: some may running map-reduce jobs, some may serving busy web requests, 
-%some may storing backend databases, any behavior that affects user VMs performance or stability is unacceptable.
-
-%To reduce the cost of deduplication, we must confine the scope of searching duplicates as much as possible,
-%thus some hints are needed to tell us where the most likely duplicates would hide. 
-%Several form of hints have been used in the past: many D2D systems exploits locality,
-%which bases on the fact that duplicates are likely to appear in the same sequence as they have arrived before.
-%Similarity is another popular hint, it suggests that two sets of data blocks may contain lots of
-%duplicates if they are indetified as similar by certain similarity detection measurements.
-
-%\section{Architecture design and Deduplication for Snapshot Support}
-%
-%\section{Popularity analysis}
-% data on what data popular.
-%
-%Analysis: modeling: singular
-%
-%Compute: Cache hit ratio vs. cache cost (memory cost).
-
-\comments{
-\section{Challenges}
-\subsection{Indexing}
-Most deduplication systems operate at the sub-file level:
-a file or a data stream is divided into a sequence of fixed
-or variable sized segments. For each segment, a cryptographic
-hash (MD5, SHA-1/2, etc.) is calculated as its
-fingerprint (FP), and it is used to uniquely identify that
-particular segment. A fingerprint index is used as a catalog
-of fingerprints stored in the system, allowing the detection
-of duplicates: during backup, if a tuple of the form <
-FP, location > exists in the index for a particular
-FP, then a reference to the existing copy of the chunk
-is created. Otherwise, the chunk is considered new, a
-copy is stored on the server and the index is updated accordingly.
-In many systems, the FP index is also crucial
-for the restore process, as index entries are used to locate
-the exact storage location of the chunks the backup
-consists of.
-
-The index needs to have three important properties:
-1) scale to high capacities, 2) achieve good indexing
-throughput, and 3) provide high duplicate detection
-rate—i.e., high deduplication efficiency. Table 1 demonstrates
-how these goals become very challenging for a
-Petascale system. Consider a typical virtualized cloud 
-in which 10,000 VMs store 1 PB data, and the
-chunk size is 4 KB (for fine-granularity duplicate detection),
-indexing capacity will need to be at least 10,000
-GB to support all 250 billion objects in the system. Such
-an index is impossible to maintain in memory. Storing it
-on disk, however, would greatly reduce query throughput.
-To support 1000 concurrent snapshot backup tasks, 
-an aggregate throughput of 20 GB/sec, would require the
-index and the whole deduplication system for that matter
-to provide a query service throughput of at least 5,000
-Kops/sec. Trying to scale to 1 PB by storing the index
-on disk would make it impossible to achieve this level
-of performance. Making the chunk size larger (e.g.,
-128 KB) would make deduplication far more coarse and
-severely reduce its efficiency.
-
-Even we can distribute the index over the cloud machines,
-the resources that can be allocated to system services are
-limited to minimize the negative impact to user experiences. 
-So it becomes obvious that efficient, scalable indexing is
-a hard problem. On top of all other indexing challenges,
-one must point out that chunk FPs are cryptographic
-hashes, randomly distributed in the index. Adjacent index
-entries share no locality and any kind of simple readahead
-scheme could not amortize the cost of storing index
-entries on disk.
-
-\subsection{Deletion}
-Contrary to a traditional backup system, a dedupe system
-shares data among files by default. 
-Since snapshots in VM cloud face constant deletion, 
-reference management
-is necessary to keep track of chunk usage and reclaim
-freed space. In addition to scalability and speed, reliability
-is another challenge for reference management.
-If a chunk gets freed while it is still referenced by snapshots,
-data loss occurs and files cannot be restored. On the other
-hand, if a chunk is referenced when it is actually no
-longer in use, it causes storage leakage.
-
-For simplicity, many previous works only investigated simple reference
-counting without considering reliability
-and recoverability. Reference counting, however, suffers
-from low reliability, since it is vulnerable to lost or repeated
-updates: when errors occur some chunks may
-be updated and some may not. Complicated transaction
-rollback logic is required to make reference counts consistent.
-Moreover, if a chunk becomes corrupted, it is
-important to know which files are using it so as to recover
-the lost segment by backing up the file again. Unfortunately,
-reference counting cannot provide such information.
-Finally, there is almost no way to verify if the
-reference count is correct or not in a large dynamic system.
-Our field feedback indicates that power outages and
-data corruption are really not that rare. In real deployments,
-where data integrity and recoverability directly
-affect product reputation, simple reference counting is
-unsatisfactory.
-
-Maintaining a reference list is a better solution: it is
-immune to repeated updates and it can identify the files
-that use a particular segment. However, some kind of logging
-is still necessary to ensure correctness in the case of
-lost operations. More importantly, variable length reference
-lists need to be stored on disk for each chunk.
-Every time a reference list is updated, the whole list (and
-possibly its adjacent reference lists—due to the lists’
-variable length) must be rewritten. This greatly hurts the
-speed of reference management.
-
-Mark-and-sweep is generally a better solution. 
-During the mark phase, all snapshot metadata are traversed 
-so as to mark the used chunks. 
-In the sweep phase all chunks are swept and unmarked chunks are reclaimed. 
-This approach is very resilient to errors: 
-at any time the process can simply be restarted with no negative side effects. 
-Scalability, however, is an issue.
-To deal with 1 PB snapshots data, which may be represented by 10,000 GB FP index,
-If we account
-for an average deduplication factor of 10 (i.e., each chunk
-is referenced by 10 different snapshots),
-the total size
-of snapshot metadata that need to be read during the mark phase will
-be 100 TB. 
-This alone will take almost 2 hours on a
-1000-machine cloud. Furthermore, marking the in-use
-bits for 250 billion entries is no easy task. There is no
-way to put the bit map in memory. One might want
-to mitigate the poor performance of mark-and-sweep by
-doing it less frequently. But in practice this is not a viable
-option: customers always want to keep the utilization
-of the system close to its capacity so that a longer
-history can be stored. With daily snapshots taking place,
-systems rarely have the luxury to postpone deletion operations
-for a long time. In our field deployment, deletion
-is done once a day. More than 2 hours in each run is too
-much. In a large production-oriented dedupe system reference
-management needs to be very reliable and have
-good recoverability. It should tolerate errors and always
-ensure correctness. Although mark-and-sweep provides
-these properties, its performance is proportional to the
-capacity of the system, thus limiting its scalability.
-
-\subsection{Fault Tolerance}
-Because deduplication storage system
- artificially creates data dependency among different VM users,
-it increases the risk of data availability.
-In large scale cloud, node failures happen at daily basis,
-the loss of access to a shared chunk can affect many VMs whose snapshots share this chunk. 
-Without any control of the scope of data sharing, we can only increase the level of 
-replication to enhance availability, which would significantly 
-balance out the benefits of deduplication.
-
-}

### 2013-08-28 snapshot_system/fast14_conclusion.tex
change to usenix format

--- 2013-08-28 snapshot_system/concl.tex
@@
 and a small replication overhead for popular inter-VM chunks.
-
-% effectively  covers a large percent of duplicate data.
-%The scheme organizes the write of small data chunks into large file system blocks so
-%that each underlying file block is associated with one VM for most cases.
-%by keeping most of the FSBs only referenced by 1 VM, we isolate faults and improve overal fault tolerance.
-%Our solution accomplishes reasonable and competitive deduplication efficiency while
-%still meeting stringent cloud resource usage requirements. 
-%Our analysis shows that  this VM centric scheme 
-%can  provide  better fault tolerance than VM-oblivious global deduplication schemes
-%while using a small amount of computing and storage resources.
-
-%[Talk about more what we learn from Evaluation]
-%Compare to today's widely-used snapshot technique, our scheme reduces almost
-%two-third of snapshot storage cost.
-%Finally, our scheme uses a very small amount of memory on each node, and leaves
-%room for additional optimization we are further studying.
-
-%This paper studies a cluster-based VM-centric scheme which collocates a lightweight
-%backup service with the cloud service and it integrates multiple duplicate detection strategies that  
-%localize the deduplication as much as possible within each virtual machine.
-%This  paper  provides a comparative evaluation of this scheme in  accomplishing a high deduplication 
-%efficiency while sustaining a good backup throughput.
-
-%This paper studies the      a VM snapshot storage architecture which adopts multiple-level selective deduplication to bring the benefits of fine-grained data reduction into cloud backup storage systems.
-%In this work, we describe our working snapshot system implementation, and provide
-%early performance measurements for both deduplication impact and
-%snapshot operations.
-
-\comments{
-\section*{Acknowledgments}
-{
-We would like to thank Weicai Chen and Shikun Tian from Alibaba for their kind support, 
-and the anonymous referees for their comments.
-Wei Zhang has received internship support from Alibaba  for VM backup system development.
-This work was supported in part by NSF IIS-1118106.
-Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
-do not necessarily reflect the views of Alibaba or the National Science Foundation.
-}
-}
-%Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,
-%this is about 600 terabytes.
-
-%Our experiments show th
-%our solution can eliminate the majority of data duplication with a tiny fraction of
-%block hash index store in memory. It does not only saves valuable system resouces in
-%the VM cloud, but also makes deduplication much faster.
-%
-%
-%Using  50 user VM data out of 1322 data disks as the training data and
-%with  1.5\% as PDS threshold, we see the total 1198GB of new data is reduced by
-%755.8GB, while perfect deduplication can reduce 1017.4GB. So 74.3\% of duplicate blocks are eliminated
-%by pre-trained PDS, which is quite satisfactory.

### 2013-08-28 snapshot_system/fast14_deduplication.tex
change to usenix format

--- 2013-08-25 snapshot_system/snapshot.tex
@@
 \label{sect:dedupe}
-%snapshot representation
 
-%We use the The deduplication process is first conducted among snapshots within each VM
-%and then is conducted across VMs.
-%Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
-%and complicate failure management,
-%we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
-%For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
-%Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance
-
-%A deduplication scheme compares the fingerprints of the current snapshot
-%with its parent snapshot and also other snapshots in the entire cloud.
-%The traditional approach compares all fingerprints and 
-%stores one copy for all of a chunk's duplicates.
-%We call this as  the VM-oblivious (VO) approach.
-
-%Our VC design has the following  objectives: 1)  localizing deduplication while identifying a decent amount of
-%duplicates among VMs to maintain a competitive deduplication efficiency and simplify snapshot management;
-%2) Minimizing the number of file system blocks shared among VMs and adding extra replicas for shared blocks.
-
-\comments{
-\begin{itemize}
-\item
-1) Localize the deduplication and data blocking within each VM as much as possible so 
-that any failure of a file system block mainly affects the associated VM.
-Localizing the snapshot data deduplication within a VM
-improves the system by increasing data independence between different VM backups,
-simplifying snapshot management and statistics collection,
-and facilitating parallel execution of snapshot operations.
-\item
-2) Maintain a competitive deduplication efficiency while being resource-friendly to other
-existing cloud services.
-Cross-VM duplication can be desirable since  there are many cloud images
-use widely-used software and libraries and their data blocks are duplicate. 
-As the result, different VMs tend to backup large amount of highly similar data.
-\item
-\end{itemize}
-}
 \subsection{Key VM-centric  Strategies}
 \label{sect:vc-strategies}
-
-%Inner-VM duplication can be very effective within VM's snapshots. There
-%are typically a large number of duplicates existing among the snapshots
-%for a single VM.
-
-%Our multi-level pipeline process can minimize 
-%the cost of deduplication while maximize the its efficiency at each level,
-%and it is parallel since each segment is processed independently.
-
-%Our VC differentiates duplicates within a VM and cross VMs,
-%and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.
-
 \begin{itemize}
@@
 and cannot afford a small segment  size.
-%Xen doesn't directly support it, However, their open-source 
-%architecture allows anyone to extend 
-%and use the  Xen virtual device driver to implement a feature called ``changed block tracking''
-%for the storage device and the dirty bit setting is maintained in a coarse grain level we call it a segment.
 It should be noted that dirtybit tracking is supported or can be easily implemented in 
 major virtualization solution vendors. For example,
-%(VMware, Xen, Microsoft).  
-%VMware support it directly; 
 the VMWare hypervisor has an API to let external backup applications know 
 the changed areas since last backup. 
-%We implement dirty bit tracking this way in Alibaba's platform.  
 The Microsoft SDK provides an API that allows external applications to monitor 
@@
 in the average of 4K or 8K~\cite{??},  
-%This allows the system to achieve deduplication even when there are insertions/deletions which would
-%affect many fixed-size chunks.
 we conduct additional local inner-VM deduplication by comparing
@@
 the amount of memory for maintaining those fingerprints in similar segment s is small.
-% as we only load one dirty segment at a time.
-
-%If we use 4KB in level-1, then such a level-1 should have similar dedup efficiency 
-%as the current level-1 and level-2 combined, because finally they equal to comparing  
-%parent snapshot at 4KB granularity.
-%
-%However, at level-3 things are different.
-If we use 4KB fix-size block uniformly, it would be harder for different VM to share data through PDS, because there is no guarantee that the location of duplicate data on different VM disks are always aligned at 4KB boundary.
-For example, if two VMs each has a copy of duplicate data, but they are not aligned, then we won't be able to detect them.
-Our study at the current small data set has shown that using 4KB fix-size block will make PDS method less efficient by nearly 10%.
-Over the long time, more and more OS variations will co-exist in the cluster, making this 4KB fix-size approach inefficient in reducing duplicate data across VMs.
-
-%\item \textit{Level 2  Chunk fingerprint comparison.}
-%If a segment is modified, we perform fine-grained deduplication 
-%by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
-%thus eliminate partial data duplication within the segment.
-%\end{itemize}
-%
-%In general, operations at level 1 have almost no cost and most of unmodified data are filtered here. 
-%To process a dirty segment at level 2, 
-%there requires no more than one DFS access to load the segment recipe from previous snapshot,
-%and a tiny amount of memory to hold it in main memory.
 
@@
 most popular items. This dataset is called PDS (common data set). 
-%Since duplicate sharing patterns among  VM follows a zip-like distribution,  
 The popularity of a chunk is the number  of data chunks  from different VMs
@@
 most popular chunk signatures in a distributed shared memory.
-%For cross-VM comparison, we only store  top $k$ items and $k$ is chosen to be relatively small.
 
@@
 we can afford to provide extra replicas for these popular chunks to enhance the fault resilience.
-%We will provide an analysis of the space need and fault tolerance in the next subsection.
 
@@
 for  popular data chunks and  this is because sampling requires the use of prefetching to be effective.
-%For a small set of popular data chunks, the prefetching strategy
-%used In the sampled index will not work well because 
 For the data sets we have tested, the spatial locality is limited among popular
 data chunks and  on average the number of consecutive data chunks is 7 among popular chinks, which is not sufficient.
-%to be effective for index sampling.
 
 \subsection{Impact on deduplication efficiency}
-%VM-oriented Fault Isolation}
-%Our objective for fault isolation is to minimize the number of VMs affected when there are failures
-%in the cluster.  
-%The inner-VM deduplication does not depend on any global service and the comparison
-%for each VM is localized within the parent and the current snapshot.
-%Lack of data dependence between VMs brings 
-%Our analysis below will show that the algorithm can still deliver competitive
-%deduplication efficiency after making these approximations.
-%With cross-VM deduplication, shared data chunks
-%create an artificial dependence  among VMs. 
-%Thus we only maintain the index for the most popular chunks to reduce the inter-VM dependence
-%while still accomplishing competitive deduplication efficiency.
-
-%The management for popular data chunks contains two aspects.
-
 Choosing the value  $k$ for the most popular chunks affects the deduplication efficiency.
-%It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
-%global deduplication.
-%\subsubsection{Impact of PDS deduplication}
 We analyze this impact based on the characteristics  of the VM snapshot traces
@@
 exponent $\alpha$ is ranged between 0.65  and  0.7.~\cite{ieeecloud}. 
-%As a result, it can be proved that deduplication efficiency of PDS index is scalable:
 Table~\ref{tab:symbol} lists parameters used in this analysis.
@@
 
-%We define deduplication efficiency $e$ to be the proportion of raw data that can be deduplicated,
-%In complete deduplication scenario, it deduplication efficiency $e_c$ is:
-%\begin{equation}
-%e_c = \frac{b-b_u}{b} = 1 - \frac{b_u}{b}
-%\end{equation}
-
 The  $k$ most popular fingerprints can cover the following number of chunks after inner VM 
@@
 
-%\begin{equation}
-%\begin{split}
-%e_k &= (\sum_{i=1}^{k}C_i - k)/{b} = (b * \frac{1-\alpha}{b_u^{1-\alpha}} * \sum_{i=1}^{k}\frac{1}{i^\alpha} - k)/b \\
-%&\approx \frac{b*\frac{1-\alpha}{b_u^{1-\alpha}}*\frac{k^{1-alpha}}{1-\alpha} - k}{b}
-%&\approx (\frac{k}{b_u})^{1-\alpha} - \frac{k}{b} \approx (\frac{k}{b_u})^{1-\alpha},\; (since\; k \ll b)
-%\end{split}
-%\end{equation}
-
-% For the Zipf-like distribution, an approximation to the sum of the first $n$ 
-% elements of the distribution can be derived as follows:
-% \begin{equation}
-% \sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
-% \end{equation}
-
-% So the cumulative distribution function for a PDS holding top $S_c$ fingerprints
-% of global index with size $S_g$ is:
-
-% \begin{equation}
-%   E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
-% \end{equation}
-
-%[Describe the dedup efficiency model in detail]
-%Let $p$ be the number of physical machines in the cluster, $m$ be the memory on each node used by the popular
-%index, $E$ be the size of an index entry,
-%$D$ be the amount of unique data on each physical machine, and 
-%$C$ be the average chunks size. 
-%Then $k$ and $c_u$ can be expressed as:
-%$ k = p*m/E$, and $c_u = p*D/E.  $
 We store the popular index using a distributed shared memory hashtable such as MemCacheD
@@
 
-%where $(\frac{m*C}{D*E})^{1-\alpha}$ represents 
 Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
@@
 Thus in practice, the coverage of the PDS increases as more VMs are involved.
-%Then the deduplication efficiency of PDS approach using top k most popular fingerprints is:
-%\begin{equation}
-%  e_k = (\frac{m*B}{F*D})^{1-\alpha}
-%\end{equation}
-
-% is mainly affected by the its memory usage,
-%and the Zipf-like distribution parameter $\alpha$.
-%From the memory usage perspective, the more memory we give to PDS index, the more duplicates it can found.
-%From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
-%$\alpha$ would be small and thus PDS approach would not be effective. But in a VM cluster all VMs
-%have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
-%the better deduplication efficiency our PDS deduplication approach will have.
-
-\comments{
-Since $B$, $D$ and $F$ are environment constants, the deduplication efficiency of PDS is mainly affected by its memory usage,
-and the Zipf-like distribution parameter $\alpha$.
-From the memory usage perspective, the more memory we give to PDS index, the more duplicates it can found.
-From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
-$\alpha$ would be small and thus PDS approach would not be effective. But in a VM cluster all VMs
-have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
-the better deduplication efficiency our PDS deduplication approach will have.
-}
-
-\comments{ %this table is superceded by the graph below it
-\begin{table}
-    \begin{tabular}{llll}
-    Data size (GB) & 1\%    & 2\%    & 4\%    \\
-    14.6           & 18.6\% & 22.1\% & 31.4\% \\
-    28.1           & 19.5\% & 26.2\% & 38.8\% \\
-    44.2           & 21.7\% & 26.5\% & 36\%   \\
-    61.6           & 23.2\% & 32.9\% & 35\%   \\
-    74.2           & 23.6\% & 33.6\% & 37.5\% \\
-    \end{tabular}
-    \caption{Deduplication effectiveness of top k\% of global index}
-    \label{tab:cds}
-\end{table}
-}
 
@@
 
-%As illustrated in Figure~\ref{??},
-%when the number of machines at each cluster increases, the number of total VMs increases.
-%Then $k$ increases since more memory is available to host the popular chunks index.
-%But for each physical machine, the number of VMs remains the same, and thus
-%$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
-%p constant.
+\subsection{Storage Space and Impact on Fault Tolerance}
+
+\begin{figure}
+    \centering
+    \subfigure[Sharing of data under VM-centric dedup model]
+    {
+        \includegraphics[width=3in]{images/share_vc}
+        \label{fig:share_vc}
+    }
+    \\
+    \subfigure[Sharing of data under VM-oblivious dedup model]
+    {
+        \includegraphics[width=3in]{images/share_vo}
+        \label{fig:share_vo}
+    }
+    \caption{Bipartite association of VMs and file blocks under VO and VC approaches}
+    \label{fig:share}
+\end{figure}
+
+The replication degree of the backup storage 
+is $r$ for regular file blocks and $r=3$ is a typical setting in the distributed
+file system~\cite{Hadoop,GFS}.
+In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
+The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
+$ k*r_c  + (c_u-k)*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
+\[
+\sigma \frac{r_c}{r} + 1-\sigma
+\]
+Since $sigma$ is small,  term $\sigma \frac{r_c}{r}$ is small in the above expression.  
+Thus the impact on storage increase is very small when we choose a large $\frac{r_c}{r}$ ratio. 
+For example, $\frac{r_c}{r}=2$.
+
+Next we  assess  the impact of losing $d$ machines 
+to the the VC and VO approaches.  
+A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of snapshot blocks.
+
+We use filesystem blocks rather than a deduplication
+data chunk as our unit of failure because the DFS keeps
+filesystem blocks as its base unit of storage.
+To  compute the full availability of all snapshots of a VM, we derive
+the probablity of losing a snapshot file block of a VM by
+estimating the number of file system blocks per VM in each approach.
+As illustrated in Figure~\ref{fig:share},
+we build a bipartite graph representing the association from unique file system blocks
+to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
+if this block is used by this VM. 
+For VC, each VM has an 
+average number of $N_1$ file system blocks for non-PDS data. 
+It also refers  an average of   $N_2$ file system blocks for PDS data. 
+For VO, each VM has an average  of  $N_o$ file system blocks
+and let $V_o$ be the average number of VMs shared by each file system block.
+
+In VC, each non-PDS file system block is associated with one VM
+ and  PDS file system blocks are
+shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block. Thus, 
+\[
+V *p*N_1 *s  = C_u (1-\sigma)\; \mbox{ and } \; 
+V *p*N_2 *s  = C_u \sigma *V_c
+\]
+For the VO approach, 
+\[
+V *p*N_o *s  = C_u  V_o.
+\]
+
+Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
+each file block contains the hot low-level chunks shared by many VMs, and it also contains
+rare chunks which are not shared.  From the about equations.
+\[
+\frac{N_1}{N_o}=  \frac{1-\sigma}{V_o}<1.
+\] 
+Thus when there is a failure in file blocks with replication degree $r$
+and there is no failure for PDS data with more replicas,   a VM in
+the VC approach has a lower chance to lose a snapshot than the VO approach because
+$N_1<N_o$. 
+Figure~\ref{fig:fsb-links} shows the number of VMs sharing by each file block.
+We can observe that $N_1 +N_2 < N_o$. 
+This is likely because the PDS FSBs tightly pack data used by many VMs, 
+which decreases the overall number of FSBs required to backup a VM.
+If  the backup for multiple VMs is conducted concurrently, there would be more
+VMs shared  by each file block on average. Therefore,
+even when there is a loss of a PDS block, the VC approach tolerates the fault better.
+
+\begin{figure}[htbp]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+                width=\linewidth,
+                height=0.6\linewidth,
+		%title={VO FSB links},
+		xlabel={Number of VMs},
+		ylabel={Avg. Num. VMs sharing FSB},
+                cycle list name=mline,
+                xmin=0,
+                ymin=0,
+                xmax=106,
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		legend pos=north west
+		]
+                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
+		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
+                \legend{VO, PDS in VC};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
+  \label{fig:fsb-links}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={VO VM links},
+                width=\linewidth,
+                height=0.6\linewidth,
+		xlabel={Number of VMs},
+		ylabel={Avg. Num. FSBs used by VM},
+                xmin=0,
+                ymin=0,
+                xmax=106,
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		legend pos=south west
+		]
+                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
+                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
+                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
+                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
+                \legend{$N_o$, $N_1+N_2$, $N_1$, $N_2$};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
+  \label{fig:vm-links}
+\end{figure}
+
+The full snapshot availability of a VM is estimated as follows with parameters $N_1$, $N_2$, and $N_o$.
+With replication degree $r$, the availability of a file block is the probability that  
+all of its replicas do not appear in any group of $d$ failed machines. 
+Namely, $1-\binom{d}{r}/ \binom{p}{r}$. 
+The snapshot availability of a VM  in the VO approach is
+\begin{equation}
+\label{eq:VO}
+(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
+\end{equation}
+
+For VC, there are two cases.
+\begin{itemize}
+\item
+When there are $r \le d<r_c$ machines failed,  there is no PDS data loss and  
+the full snapshot availability of a VM in the VC approach is 
+and is
+\[
+(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
+\]
+Since $N_1 <N_o$, the VC approach has a higher availability of VM snapshots than VO.
+
+\item
+When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
+The full snapshot availability of  a VM in the VC approach is
+\[
+(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
+*
+(1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
+\]
+Figure~\ref{fig:fsb-availability} illustrates that the availability of an individual file system block
+with different replication degree. This demonstrates inequality $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
+< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$. As we have also observed
+$N_1+N_2 <N_o$ in our dataset, these two conditions support that VC has a  higher availability. 
+%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
+\end{itemize}
+
+\begin{figure}[htbp]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+                width=\linewidth,
+                height=0.6\linewidth,
+            %title={FSB Availability},
+            cycle list name=mline,
+            xlabel={Number of Machines Failed},
+            ylabel={Availability of Single FSB (\%)},
+            extra y ticks={99.9}, %to add extra ticks
+            mark options=solid,
+            legend pos=south west,
+            %legend columns=2,
+            %legend style={
+            %    at={(0.5,-0.2)},
+            %anchor=north}
+            ]
+            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
+            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
+            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
+            \legend{$R=5$,$R=4$,$R=3$};
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Availability of individual file system blocks in a 100 machine cluster with different replication degrees.}
+  \label{fig:fsb-availability}
+\end{figure}

### 2013-08-28 snapshot_system/fast14_evaluation.tex
change to usenix format

--- 2013-08-28 snapshot_system/eval1.tex
@@
 \label{sect:exper}
-
 We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
@@
 with an alternative VO design, and assess backup throughput and  resource usage for a large number of VMs.
-% the backup throughput performance VC  for a large number of VMs.
-%Compare with the data domain approach~\cite{bottleneck08}.
-
-%\section{Experiments}
-%Our main test-bed is an cluster of 6 machines,
-%Our data set consists of 350 virtual machine image snapshots taken from Alibaba.com's
-%public VM cloud in China. 
-%We select 35 VMs from the most popular 7 OSes: 
-%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
-%For each OS, 5 VMs are chosen, and every VM come with 10 full snapshots.
-%\subsection{Experimental setup}
 
@@
 a machine, this chunk is compared with the fingerprint index of this machine locally.
-%algorithm helps provide a greater degree of parallelism, but ignores the
-%significant amount of parallelism within a single VM.
-
-\comments{
-%We are running our deduplication/backup  service on 100 nodes.
-%Memory usage is about 150MB space per node during backup and
-%the CPU usage is very small during the experiments. 
-We have performed a trace-driven study using  a 1323 VM dataset  collected from 
-%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
-a cloud cluster at Alibaba's Aliyun.
- ~\cite{WeiZhangIEEE}.
-% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
-For each VM, the system keeps 10 automatically-backed snapshots in the storage while
-a user may instruct extra snapshots to be saved.
-Each VMs uses   one of the most popular 7 OSes: 
-Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
-The backup of VM snapshots is completed within a few  hours every night.
-Based on our study of production  data,  each VM has about  40GB of storage  data on average
-including OS and user data disk.
-For our system each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
-variable-sized content blocks  with an average size of 4KB.
-%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
-The signature for variable-sized blocks is computed using their SHA-1 hash.
-
-The seek cost of each random IO request in our test machines is about  10 milliseconds.
-The average I/O usage of local storage is controlled to about 50MB/second for backup 
-in the presence of other I/O jobs. Noted that a typical 1U server can host
-6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
-of local storage bandwidth. 
-The final snapshots are stored in a distributed file system built on the same 
-cluster. total local disk usage on each machine is about 8GB for the duplicate detection purpose,
-mainly for global index. 
-Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
-block-wise full deduplication removes about additional 74.5\% of duplicates.
-The final content copied to the backup storage is reduced by 94.4\%
-\emph{Is this correct? Elsewhere we have used 92\% based on results from
-our srb-vc comparison graph} in total.
-}
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.4\textwidth]{mem_time}
-%\caption{ Parallel time when memory limit varies.}
-%\label{fig:memory}
-%%\end{figure}
-%
-%Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
-% a 100-node cluster a  when
 
@@
 Debian, Ubuntu, Redhat, CentOS, and win2008. 
-%We are running our deduplication/backup  service on 100 nodes.
-%Memory usage is about 150MB space per node during backup and
-%the CPU usage is very small during the experiments. 
-% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
 Each machine hosts upto 25 VMs and each VM keeps 10 automatically-backed snapshots in the storage while
 a user may instruct extra snapshots to be saved.
-%Each VM uses   one of the most popular 7 OSes: 
-%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
 The backup of VM snapshots is completed within a few  hours every night.
@@
 and top popular ones ($\delta=1-2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:crossVM}.
-%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
-%The signature for variable-sized blocks is computed using their SHA-1 hash.
-
-%The seek cost of each random IO request in our test machines is about  10 milliseconds.
-%The average I/O usage of local storage is controlled about 50MB/second for backup 
-%in the presence of other I/O jobs. Noted that a typical 1U server can host
-%6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
-%of local storage bandwidth. 
-%The final snapshots are stored in a distributed file system built on the same 
-%cluster.
-
-%Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
-%block-wise full deduplication removes about additional 74.5\% of duplicates.
-%The final content copied to the backup storage is reduced by 94.4\% in total.
-%Based on the data studied,  each VM has about  40GB of storage  data usage on average,
-%OS disk and data disk each takes about 50\% of storage space.
-%The backup of VM snapshots is completed within two hours every day,
-%and that translates to a backup throughput of 139GB per second, or 500TB per hour.
-%For each VM, the system keeps 10 automatically-backed snapshots in the storage while
-%a user may instruct extra snapshots to be saved.
-
-% the system must finish saving daily snapshots of all VMs in 2 hours.
-In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.
-
-%In our snapshot deduplication architecture, PDS is the key to achieve greater deduplication than
-%incremental backup solutions. Our basic assumption of PDS us that VM disks, especially OS disks,
-%have huge amount of data in common, and such common data can be represented by a relatively smaller data set
-%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
-%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
-%the effectiveness of PDS using real user VM disks from our production VM cluster.
-
-%Since it's impossible to perform large scale analysis without affecting production VM performance,
-%For each OS, 5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
-%The overall data size for these 700 full snapshots is 17.6 TB.
-
-%Dataset2 contains the first snapshots of 1323 VMs' data disks from a small cluster with 100 nodes. 
-%Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
-%study the PDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
 
 \subsection{Impact on Fault Tolerance}
-
 Figure~\ref{fig:vm-availability} shows the availability of VM snapshots when 
@@
 A  VO curve has  $V_o=150$ which is  the average number of VMs that share a file system block. 
-%We show 6.3 for the VO sharing because that is what we measured in our dataset,
-%and while we expect it to continue to grow (thereby decreasing fault
-%tolerance), it should do so slowly, so we treated VO FSB sharing as a
-%contstant factor of 6.3, as it doesn't change our results. for VC we use 1250, because that is what we
-%estimate at 2500 VMs based on the linear growth up to 105 VMs. We also show
 Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
@@
 
-% while in VO even small increases in $L$ causes a large decrease in availability. 
 Figure~\ref{fig:pds-replication}
 shows the snapshot availability when increasing the replication degree for PDS blocks. 
-%We use our estimate of 1250 VMs sharing each PDS block, which is what we expect
-%for 2500 VMs, given the growth up to 105 VMs. 
 It can be seen that increasing the replication of 
 the PDS blocks can have a good impact on the overall availability of the VM backups. 
-%Increasing the PDS replication is cheap because 
 PDS with more replication  makes up a small percent of the
 stored data; however, the benefit to the snapshot availability is significant.
-%These figures together show the advantages of the VM-centric model, and the advantages that separating the
-%replication factor for popular blocks can have on reliability.
 
@@
 
-\comments{
-\begin{figure}[htbp]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-                        width=\linewidth,
-                        height=0.6\linewidth,
-		%title={PDS Replication affect on availability},
-		xlabel={Failed storage nodes},
-		ylabel={VM Snapshot Availability (\%)},
-		%extra y ticks={99.99}, %if important numbers are missing
-                mark options=solid,
-                legend style={
-                    cells={anchor=west}, %legend entry alignment
-                    legend pos=south west %legend position
-                },
-                reverse legend,
-		]
-                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
-                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
-                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
-                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
-                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Availability of VM backups as nodes fail in VC for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
-  \label{fig:pds-replication2}
-\end{figure}
-}
 \subsection{Deduplication Efficiency}
-
-%\begin{figure}
-%  \centering
-%  \epsfig{file=images/overall_effect.eps, width=3.5in}
-%  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
-%deduplication divided by the original data size and the unit is percentage. }
-%  \label{fig:overall}
-%\end{figure}
-
-%We assess the deduplication efficiency of VC and compare with
-%that of an VO approach  using stateless routing with binning (SRB).
-%SRB routes a data chunk to a machine~\cite{ParallelDataDomain}
-%using  the chunk hashing function disussed in \cite{??}.
-
 Figure~\ref{fig:exbin-efficiency-graph} shows the deduplication efficiency for SRB and VC.
@@
 delivers additional 10.5\% reduction.
-
-\comments{%both of the bar charts are superceded by the graph below
-%\comments{
-    %this version of the figure is vertical
-    \begin{figure}[ht]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={Extreme-Binning Efficiency},
-            ybar,
-            bar width=1.00cm,
-            symbolic x coords={SRB,VC},
-            xlabel={Algorithm},
-            ylabel={Dedup. Efficiency (\%)},
-            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
-            xtick=data, %without this the symbolic coords may be repeated as filler
-            enlarge x limits=0.6, %used to push plots towards center
-            ymin=85,
-            %ymax=100,
-            nodes near coords,
-            nodes near coords align={vertical},
-            ]
-            \addplot coordinates {(SRB,89.99) (VC,90.51)};
-            \end{axis}
-    \end{tikzpicture}
-    \caption{Deduplication Efficiency
-         of SRB  and VC with $\delta=2\%$.}
-        %($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% PDS.}
-  \label{fig:exbin-efficiency1}
-\end{figure}
-%}
-%same figure as above but horizontal (better for only two data points)
-\begin{figure}[ht]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={Extreme-Binning Efficiency},
-            xbar,
-            width=7cm,
-            height=3.5cm,
-            %bar width=0.75cm,
-            symbolic y coords={SRB,VC},
-            xlabel={Dedup. Efficiency (\%)},
-            %ylabel={Algorithm},
-            %extra x ticks={4.5,5.5,6.5} %to add extra ticks
-            ytick=data, %without this the symbolic coords may be repeated as filler
-            enlarge y limits=0.5,
-            xmin=85,
-            xmax=92, %otherwise label overlaps with right border
-            nodes near coords,
-            nodes near coords align={horizontal},
-            ]
-            \addplot coordinates {(89.99,SRB) (90.51,VC)};
-            \end{axis}
-    \end{tikzpicture}
-    \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC 
-with $\sigma=2\%$.}
-  \label{fig:exbin-efficiency2}
-\end{figure}
-}
-
-\comments{%superceded by minhash algorithm (below)
-%graph comparing extreme binning (SRB) with PDS model (VC) for different cds percentages
-\begin{figure}[ht]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={Ex-Binning Efficiency},
-            cycle list name=mline,
-            xlabel={Number of VMs added},
-            ylabel={Dedup. Efficiency (\%)},
-            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
-            mark options=solid,
-            legend pos=south west,
-            %legend columns=2,
-            %legend style={
-            %    at={(0.5,-0.2)},
-            %anchor=north},
-            ]
-            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
-            \addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
-            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
-            \addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
-            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$)};
-            \end{axis}
-    \end{tikzpicture}
-    \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
-    SRB and  VC.}
-  \label{fig:exbin-efficiency-graph}
-\end{figure}
-}
-
-\comments{%version of above graph using minhash algorithm
-\begin{figure}[ht]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={Ex-Binning Efficiency},
-            width=\linewidth,
-            height=0.7\linewidth,
-            cycle list name=mline,
-            xlabel={Number of VMs added},
-            ylabel={Dedup. Efficiency (\%)},
-            xmin=0,
-            ymin=88.5,
-            ymax=100,
-            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
-            mark options=solid,
-            legend pos=south west,
-            legend columns=2,
-            legend style={
-                font={\tiny},
-                %at={(0.5,-0.2)},
-                %anchor=north
-            },
-            ]
-            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
-            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$),VC (No PDS)};
-            \end{axis}
-    \end{tikzpicture}
-    \caption{Deduplication Efficiency
-        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
-    Stateless Routing with Binning and VC. VC uses the minhash algorithm for Level-2.}
-  \label{fig-exbin-efficiency-graph2}
-\end{figure}
-}
 
@@
 
-%\begin{figure}
-%  \centering
- %\epsfig{file=images/os_cds_sim.eps, width=3in}
-%  \epsfig{file=images/3level_os.eps, width=3.5in}
-%  \caption{Impact of 3-level deduplication for OS releases.}
-%  \label{fig:oscds}
-%\end{figure}
-
-%To see the impact of multi-level deduplication on different OS releases,
-%Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
-
-%Combining OS disks in all the VMs, we see the overall 7.4TB of data is reduced to 512GB. 
-%The extreme binning approach can reduce this data set to 542GB, which is slightly worse. As a reference, 
-%perfect deduplication achieves 364GB in this experiment.
-
-%Overall speaking, inner   VM deduplication or  PDS-based deduplication
-%can work well alone, but by combining them together we get a fairly good and stable deduplication ratio to 
-%all kind of OSes. 
-%Compared to a traditional dirty bit approach based on pages of
-%each file (e.g. segment in our scheme),
-%our PDS-based level 3 approach  can save additional 50\% storage space because many of level 2 block
-%content can be eliminated using the PDS also.
-
 \subsection{Resource Usage and Processing Time}
@@
 
-%{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
-%backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
-%scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
-%evaulate the system performance on the second snapshot backup. We repeat such procedure
-%under different PDS memory usage settings, the results of backup time break down are shown in
-
 {\bf Processing Time breakdown}.
@@
 Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.
-%all lookups are essentially random and caching will be largely innefective).
-
-%\emph{Should we use one of the two
-%bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
-%charts in the paper until we decide? If we use the bar charts some text will
-%have to be changed. We could also add each of the PDS sizes to the bar chart
-%and have 4 bars instead of 2.}
 
@@
 of time as local search.
-%procedure takes a small fraction of the total backup time. 
 The change of $\sigma$ does not significantly affect the overall backup speed as
 PDS lookup takes only a small amount of time.
-%Larger memory permits us to
-%use larger PDS index to cover more of global index, as a result the amount of data to be writen
-%is reduced and so do the writing time.
-%Inside the deduplication procedure, the time costs of level-1
-%is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
-%because the number of fingerprints to process are just the same.
 
@@
 
-% \begin{figure}[htbp]
-%   \centering
-%   \epsfig{file=figures/parallel_backup, width=3.5in}
-%   \caption{Throughput per-node with concurrent snapshot backup tasks}
-%   \label{fig:parallel_backup}
-% \end{figure}
-
-% \begin{table}
-% \begin{tabular}{ |p{1.5cm}|p{1.8cm}|p{1.2cm}|p{1.4cm}| }
-% \hline
-%  & Costs & Stateless routing with binning (s) & VM-centric approach (s) \\ \hline
-% \multirow{4}{*}{\vbox{I/O related}} & Read data & 0.05 & 0.05 \\ \cline{2-4}
-%  & Transfer data  & 0.017 & 0.017 \\ \cline{2-4}
-%  & Write data & 0.03 & 0.025 \\ \cline{2-4}
-%  & Subtotal & 0.097 & 0.092 \\ \hline
-% \multirow{5}{*}{\vbox{Dedupe related}} & Read index/recipe & 0.01 & 0.00045 \\ \cline{2-4}
-%  & Write index/recipe & 0.01 & 0.0051 \\ \cline{2-4}
-%  & Transfer fingerprints & 0.00058 & 0.00013 \\ \cline{2-4}
-%  & PDS lookup & N/A & 0.00034 \\ \cline{2-4}
-%  & Subtotal & 0.021 & 0.0064 \\ \hline
-% \multicolumn{2}{ |c| }{Total} & 0.12 & 0.098 \\
-% \hline
-% \end{tabular}
-% \caption{Time of backup a segment break down}
-% \label{tab:compare}
-% \end{table}
 \subsection{Effectiveness of Approximate Deletion}
-
 \begin{figure}
@@
 there is only 1MB space leaked for every 10GB of stored data.
-%In addition, the leakage ratio grows linearly with the number of approximate deletions
-%as our analysis, which gives us a reliable prediction of when to trigger a accurate mark-and-sweep delete operation.
-
-\comments{
-\subsection{Read Snapshot}
-
-\subsection{Comparison with Other Approaches}
-\subsubsection{Sampled Index}
-One alternative approach to avoiding a single global index is to use a sampled
-index. This is the approach taken by Guo and Efstathopoulos\cite{Guo2011}. We
-compare their solution to ours by running their algorithm on our 350 traces
-using a sampling rate of 1 out of 101 blocks, and always including the first
-block in a container (which we fix at 16MB in size). The results of running this
-test are shown in Table~\ref{??}, and the memory usage comparison can be found
-Sec.~\ref{??}. Our results show that using a sampled index achieves a very high
-rate of deduplication, and so a sampled index might be a good way to do dedup
-in a single node setup.
-
-The problems for sampling are in distributing the
-algorithm and in deduplicating extremely large bodies of data. The algorithm
-stores the entire (sampled) index in memory, which is required for high
-throughput to avoid the disk-bottleneck problem - since the index itself has no
-locality information, lookups are essentially random, so the index must be
-somehow optimized to prevent excessive disk seeking (the sampling algorithm does
-this by storing the index in memory). To distribute this index, each node would
-either require a complete copy of the index which would have a prohibitive cost in
-memory, or something like memcached must be used, which leaves the same problem
-as the disk bottleneck with every index check potentially using the network.
-The difficulty in storing extremely large bodies of data
-is related, as once 1PB is stored in the system, assuming a sampling rate of 
-1/101 with 22 byte index entries, 55GB of (in memory) index are required.
-
-Our solution uses more total memory (??how much??), but is more scalable both in
-terms of capacity and distributing the deduplication. The only part of our
-algorithm which requires significant network traffic is the PDS deduplication,
-but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
-so is only done for a small percent of blocks (?? 5-10\% ??).
-
-\subsubsection{Scalable Data Routing}
-Another approach to avoiding a global index is to use a content-based hash
-partitioning algorithm to break up the deduplication work. This approach is
-taken by Dong et al. in their Scalable Data Routing paper, and is similar to
-Extreme Binning\cite{??}\cite{extreme_binning09}. We compared our solution to
-content-based hash partitioning by running the algorithm on our set of 
-traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
-the minhashes of the superchunks for routing. The results of this are shown in
-Table~\ref{??}. Routing each chunk to a bin provides good deduplication
-efficiency, and only requires each storage node to keep an index of local data
-and the bin mapping, but misses significant opportunities in our indended use
-case.
-
-The problem with the Data Routing algorithm is in the very high network traffic.
-Our intended use case is a backup system which runs alongside a number of VMs,
-in order to save costs. Data Routing makes no use of the inherent locality in
-such a system, and therefore puts a much higher network burden on machines which
-are also running 35 VMs each. This will reduce the available network bandwidth
-to users of the VMs, and/or reduce the possible deduplication throughput.
-
-}

### 2013-08-28 snapshot_system/fast14_introduction.tex
change to usenix format

--- 2013-08-28 snapshot_system/intro.tex
@@
 In a cluster-based cloud environment,
-% such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
 each physical machine runs a number  of virtual machines as  instances of a guest operating system 
 and their  virtual hard disks are represented as virtual disk image files in the host operating system.
-%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
-%Backup  of virtual disks is relatively straightforward since
-%these image files are stored as regular files from the external point of view,
-%backing up VM's data is mainly done by taking snapshots of virtual disk images.
-%A snapshot preserves the data of a VM's file system at a specific point in time. 
-%VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
-%and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
 Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
@@
 Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
-%(Figure~\ref{fig:traditional-arch})
 can effectively identify and remove content duplicates among snapshots, 
@@
 
-%\begin{figure}[htb]
-%    \centering
-%    \includegraphics[width=3in]{images/traditional-arch}
-%    \label{fig:traditional-arch}
-%    \caption{Traditional VM Backup System}
-%\end{figure}
-
 This paper seeks for a low-cost architecture option  that collocates
 a backup service with other cloud services and  uses a minimum amount of resources. 
-%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
-%The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
-%duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
-%On the other hand, comparing fingerprints  adds significant  memory cost. 
-%Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
-%Cloud providers often wish that the backup service only consumes  small or modest resources
-%with a minimal impact to the existing cloud services.  
-%We study and evaluate the integration of several deduplication strategies to meet
-%the low-cost collocation requirement. 
-%A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
 We also consider the fact that after
@@
 Failure of few shared data chunks can have a 
-%catastrophic 
 broad effect and many
@@
 Thus we also seek deduplication options that yield better fault isolation.
-% along with a low-cost solution.
 Another issue considered is that
 that deletion of old snapshots competes for computing resource as well. 
-%That is because data dependence created deletion of old snapshots competes for computing resources.
-% as well so deletion needs to be considered in system design. 
 Sharing of data chunks among by multiple VMs needs to be detected during
 snapshot   deletion and such dependencies complicate deletion operations.
-%The additional complexity for deletions
-%come from the dependencies created by multiple links to the same problem, so
-%some solution is needed to determine blocks with no dependent snapshots after deletion.
-%especially when  VMs can migrate around in the cloud.
-
-%\begin{figure}[htb]
-%    \centering
-%    \includegraphics[width=3in]{images/colocated-arch}
-%    \label{fig:colocated-arch}
-%    \caption{Collocated VM Backup System}
-%\end{figure}
 
@@
 This  VM-centric solution uses  a small amount of  memory while delivering a reasonable deduplication efficiency.
-%Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data.
+
 We have developed a prototype system that runs a cluster of Linux machines with Xen and uses 
 a standard distributed file system for the backup storage.
-% with data replication and block packaging.
-%and we allocate more  replicas for the commonly-shared  data 
-%blocks among VM snapshots to enhance fault tolerance.
 
@@
 Section~\ref{conc}  concludes this paper.
-
-%We are seeking Unlike the previous work dealing with general file-level backup and deduplication, our problem is focused on 
-%virtual disk image backup. Although we treat each virtual disk  as a file logically, its size is very large.
-%On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud every day. 
-%One key requirement we face at Alibaba Aliyun is that VM snapshot backup should only use a minimal amount of system
-%resources so that most of resources is kept for regular cloud system services or applications.
-%Thus our objective is to exploit the characteristics of VM snapshot data and
-%pursue a cost-effective deduplication solution. 
-%Another goal  is to decentralize VM snapshot backup and  localize  deduplication as much as possible,
-
-%,extreme_binning09,sparseindex09
-\comments{
-By observations of the VM snapshot data from production cloud, we found snapshot data duplication 
-can be easily classified into two categories: \emph{inner-VM} and \emph{cross-VM}. Inner-VM duplication
-exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
-On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL.
-As the result, different VMs tend to backup large amount of highly similar data.
-
-With these in mind, we  have developed a distributed multi-level solution to conduct 
-segment-level  and block-level inner-VM  deduplication to localize the deduplication effort when possible.
-It then makes cross-VM deduplication by excluding a small number of
-popular common data blocks from being backed up. Our study shows that common data blocks
-occupy significant amount of storage space while they only take
-a small amount of resources to deduplicate.
-Separating deduplication into multiple levels effectively accomplishes the major space saving goal
-compared the global complete deduplication scheme, but at the same time makes
-the backup of different VMs independent for better fault tolerance.
-
-The following table shows the strength and weakness of some well-know deduplication systems:
-\begin{table}
-    \begin{tabular}{|l|l|l|l|}
-        \hline
-        ~           & Scalability & Low-cost & Full Dedup \\ \hline
-        DDFS        & N           & N        & Y          \\ 
-        Ex-bin      & Y           & Y        & N          \\ 
-        Guo         & Y           & N        & N          \\ 
-        iDedup      & N           & Y        & N          \\ 
-        Founadation & N           & N        & Y          \\
-        \hline
-    \end{tabular}
-\end{table}
-}

### 2013-08-28 snapshot_system/fast14_main.tex
change to usenix format

--- 2013-08-05 snapshot_system/main.tex
@@
-\documentclass{sig-alternate-10pt}
+\documentclass[letterpaper,twocolumn,10pt]{article}
+\usepackage{usenix}
 \usepackage{mathptmx}
@@
 \newcommand{\comments}[1]{}
+
 %pgfplots setup
-
 \pgfplotsset{
@@
 
-%\title{Deduplication Localization for Virtual Machine Snapshot Backup}
 \title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup}
-%\title{BigArchive: Low-cost and Scalable Deduplication Storage for VM Snapshot}
 
 \author{
-Wei Zhang, Michael Agun,  Tao Yang \\
-%Wei Zhang$^{\star}$, Michael Agun,  Tao Yang$^\star$
-%{\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
-%Wei Zhang, Tao Yang, Gautham Narayanasamy\\
-Department of Computer Science\\
-University of California,  Santa Barbara, CA 93106
-%\and
-%Hong Tang\\
-%Alibaba Inc.
+  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, and Hong Tang$^\dagger$ \\
+  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
+  {wei, tyang, dagun}@cs.ucsb.edu, hongtang@alibaba-inc.com
 }
-%, Gautham Narayanasamy$^\star$, and Hong Tang$^\dagger$ \\
 
@@
 
-\input{abs}
-
-% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
-
-%\terms{Theory}
-
-%\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
-
-\input{intro}
-%\input{design}
-%\input{background}
-\input{challenge}
-\input{snapshot}
-\input{failover}
-%\input{compare}
-%\input{design1}
-\input{arch}
-%\input{impl}
-%\input{sampling-comparison.txt}
-\input{eval1}
-%\input{cds}
-%\input{delete}
-%\input{failover}
-%\input{result}
-\input{concl}
+\input{fast14_abstract}
+\input{fast14_introduction}
+\input{fast14_background}
+\input{fast14_deduplication}
+\input{fast14_architecture}
+\input{fast14_evaluation}
+\input{fast14_conclusion}
 

### 2013-08-28 snapshot_system/eval1.tex
figure revisions

@@
                     \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
-                    \addlegendentry{VO\,$6.3$ (optimistic)}
+                    \addlegendentry{VO}
                     \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
-                    \addlegendentry{VC (expected)}
+                    \addlegendentry{VC}
                     \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
@@
   \caption{Availability of VM backup snapshots as nodes fail in VC with different PDS Replication degree
- (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
+ (Non-PDS replication fixed at 3, and average PDS block links set to 1250)}
   \label{fig:pds-replication}
@@
                 {blue,solid,mark=diamond*,mark size=1.5},
-                {blue,solid,mark=pentagon*,mark size=1.4},
+                %{blue,solid,mark=pentagon*,mark size=1.4},
                 {red,draw=red,densely dotted,mark=square},
-                {red,densely dotted,mark=triangle,mark size=1.5},
-                {red,densely dotted,mark=diamond,mark size=1.5},
+                %{red,densely dotted,mark=triangle,mark size=1.5},
+                %{red,densely dotted,mark=diamond,mark size=1.5},
                 {brown,densely dashed,mark=*},
@@
             \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
+            %\addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
             \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
+            %\addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
             \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
-            \addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
+            %\addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
             \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
-            \legend{VC MH( $\sigma=4\%$),VC MH($\sigma=2\%$),VC MH($\sigma=1\%$),VC MH(No PDS),VC($\sigma=4\%$),VC($\sigma=2\%$),VC($\sigma=1\%$),SRB};
+            \legend{VC MH( $\sigma=4\%$),
+                VC MH($\sigma=2\%$),
+                %VC MH($\sigma=1\%$),
+                VC MH(No PDS),
+                %VC($\sigma=4\%$),
+                VC($\sigma=2\%$),
+                %VC($\sigma=1\%$),
+                SRB
+            };
             \end{axis}

### 2013-08-29 snapshot_system/fast14_evaluation.tex
figure updates, make now builds fast14_main

@@
 		title={\small $p=1000$},
+                ymin=099.9991,
+                ymax=100.0002,
+                %ytick=data,
+                %yticklabels from table={figures/vm_availability_1000.txt}{[index]1},
                 cycle list={
@@
                 \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
+                %\addplot table[x=NodesFailed,y expr=(\thisrow{VO1}-99.999)*1000]{figures/vm_availability_1000.txt};
                 %\addlegendentry{$VO\,6.3$ (optimistic)}
                 \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
+                %\addplot table[x=NodesFailed,y expr=(\thisrow{VC1}-99.999)*1000]{figures/vm_availability_1000.txt};
                 %\addlegendentry{$VC\,1250$ (estimated)}
                 \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
+                %\addplot table[x=NodesFailed,y expr=(\thisrow{VC2}-99.999)*1000]{figures/vm_availability_1000.txt};
                 %\addlegendentry{$VC\,2500000$ (worst-case)}

### 2013-08-29 snapshot_system/fast14_evaluation.tex
figure revisions

@@
 	\begin{tikzpicture}
+            %the expressions in this plot are simply to trick pgfplots into not expanding the y range, and don't actually change the data
+            % expression used: (99.999+((y-99.999)*1000)/1000)
             \pgfplotsset{/pgf/number format/.cd,
@@
 		title={\small $p=1000$},
-                ymin=099.9991,
-                ymax=100.0002,
+                %ymin=099.9991,
+                %ymax=100.0002,
                 %ytick=data,
                 %yticklabels from table={figures/vm_availability_1000.txt}{[index]1},
+                yticklabel={%this is a hack to get around the small yrange
+                    \pgfmathfloatparse{99.999+\tick/1000}
+                    \pgfmathprintnumber{\pgfmathresult}
+                },
                 cycle list={
@@
 		]
-                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
-                %\addplot table[x=NodesFailed,y expr=(\thisrow{VO1}-99.999)*1000]{figures/vm_availability_1000.txt};
+                %\addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
+                \addplot table[x=NodesFailed,y expr=(\thisrow{VO1}-99.999)*1000]{figures/vm_availability_1000.txt};
                 %\addlegendentry{$VO\,6.3$ (optimistic)}
-                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
-                %\addplot table[x=NodesFailed,y expr=(\thisrow{VC1}-99.999)*1000]{figures/vm_availability_1000.txt};
+                %\addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
+                \addplot table[x=NodesFailed,y expr=(\thisrow{VC1}-99.999)*1000]{figures/vm_availability_1000.txt};
                 %\addlegendentry{$VC\,1250$ (estimated)}
-                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
-                %\addplot table[x=NodesFailed,y expr=(\thisrow{VC2}-99.999)*1000]{figures/vm_availability_1000.txt};
+                %\addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
+                \addplot table[x=NodesFailed,y expr=(\thisrow{VC2}-99.999)*1000]{figures/vm_availability_1000.txt};
                 %\addlegendentry{$VC\,2500000$ (worst-case)}
@@
 	\end{tikzpicture}
-        %\caption{100000 machine cluster.}
-  \label{fig:vm-availability-100000}
+        %\caption{1000 machine cluster.}
+  \label{fig:vm-availability-1000}
 \end{subfigure}

### 2013-09-03 snapshot_system/fast14_architecture.tex
fix citations

@@
 \section{Architecture and Implementation Details}
-\label{sect:arch}
+\label{sect:architecture}
 Our system runs on a cluster of Linux machines with Xen-based VMs.
@@
 Segments are further divided into variable-sized chunks (average 4KB) 
-using a content-based chunking algorithm~\cite{?}, 
+using a content-based chunking algorithm~\cite{frame05}, 
 which brings the opportunity of fine-grained deduplication.
@@
 \subsection{A VM-centric snapshot store for backup data}
+\label{sect:store}
 We build the snapshot storage on the top of a distributed file system.
@@
 and uncompressed. Given the high spatial locality and usefulness of prefetching  in 
-snapshot chunk accessing~\cite{Sampling,FoundationPaper},
+snapshot chunk accessing~\cite{Guo2011,foundation08},
 retrieval of  a data chunk  group naturally works well with prefetching. 
@@
 That requires a scanning of all chunks in a VM; however it is a VM-specific procedure and thus
-the cost is relatively small compared to the traditional mark-sweep procedure~\cite{?} which scans snapshot 
+the cost is relatively small compared to the traditional mark-sweep procedure~\cite{Guo2011} which scans snapshot 
 chunks from all VMs.

### 2013-09-03 snapshot_system/fast14_conclusion.tex
fix citations

@@
 \section{Conclusion}
-\label{sect:final}
+\label{sect:conclusion}
 In this paper we propose a collocated backup service built on

### 2013-09-03 snapshot_system/fast14_deduplication.tex
figure revisions
fix citations

@@
 \section{VM-centric Snapshot Deduplication}
-\label{sect:dedupe}
+\label{sect:deduplication}
 
@@
 
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=images/mh_local_dedup.png, width=3in}
+  \caption{Min-hash based local deduplication}
+  \label{fig:local_dedup}
+\end{figure}
+
 Since the best deduplication uses a nonuniform chunk size 
-in the average of 4K or 8K~\cite{??},  
+in the average of 4K or 8K~\cite{Jin2009},
 we conduct additional local inner-VM deduplication by comparing
@@
 This step accomplishes the standard global fingerprint comparison as conducted
-in the previous work~\cite{??}.
+in the previous work~\cite{WeiZhangIEEE}.
 One key observation is that the inner deduplication has removed many of the duplicates.
@@
 accumulate small local chunks. We manage this accumulation process using an append-store  scheme
-and discuss this in details in Section~\ref{sect:arch}.
+and discuss this in details in Section~\ref{sect:architecture}.
 The system allows all machines conduct the backup in parallel in different machines, and each machine
@@
 Our previous study shows that the popularity of data chunks after inner VM deduplication follows 
-a Zipf-like distribution\cite{zipf} and its
-exponent $\alpha$ is ranged between 0.65  and  0.7.~\cite{ieeecloud}. 
+a Zipf-like distribution\cite{Breslau1999a} and its
+exponent $\alpha$ is ranged between 0.65  and  0.7.~\cite{WeiZhangIEEE}. 
 Table~\ref{tab:symbol} lists parameters used in this analysis.
@@
             legend style={
-                at={(0.5,-0.25)},
+                at={(0.5,-0.30)},
             anchor=north},
@@
 is $r$ for regular file blocks and $r=3$ is a typical setting in the distributed
-file system~\cite{Hadoop,GFS}.
+file system~\cite{googlefs03,hdfs10}.
 In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 

### 2013-09-03 snapshot_system/fast14_evaluation.tex
fix citations

@@
 \section{Evaluation}
-\label{sect:exper}
+\label{sect:evaluation}
 We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
@@
 a VO approach  using stateless routing with binning (call it SRB) 
-based on~\cite{ParallelDataDomain,Extremebining}
-SRB executes a distributed deduplication by routing a data chunk to a machine~\cite{ParallelDataDomain}
-using  a min-hash function discussed in \cite{Extremebining}. Once a data chunk is routed to
+based on~\cite{Dong2011,extreme_binning09}
+SRB executes a distributed deduplication by routing a data chunk to a machine~\cite{Dong2011}
+using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
 a machine, this chunk is compared with the fingerprint index of this machine locally.
@@
 Popularity of data blocks are collected through global counting and 
-and top popular ones ($\delta=1-2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:crossVM}.
+and top popular ones ($\delta=1-2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.
 
@@
 \subsection{Deduplication Efficiency}
-Figure~\ref{fig:exbin-efficiency-graph} shows the deduplication efficiency for SRB and VC.
+Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
 Deduplication efficiency is defined as the percent of duplicate chunks

### 2013-09-04 snapshot_system/fast14_evaluation.tex
improve formatting

@@
 \subsection{Deduplication Efficiency}
-Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
-Deduplication efficiency is defined as the percent of duplicate chunks
-which are detected and deduplicated.
-The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
-is defined in Table~\ref{tab:symbol}. 
-%we allocate the space of distributed shared memory  to accommodate 2\%
-%of data chunks shared among VMs, as defined in 
-With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
-and  the deduplication efficiency can reach over 90\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
-The loss of efficiency in VC is caused by the restriction of the total physical memory available
-in the cluster to support PDS index.  
-The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
-for global comparison.
-In all cases, VC provides similar or better deduplication efficiency than SRB.
-
-This result shows VC can remove  a competitive amount of duplicates.
-In general, our experiments show that
-dirty-bit detection at the segment level  can reduce the data size to about 23\% of original data, 
-which leads  about 77\% reduction.
-Local search within a segment can   further reduce the data size
-to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
-The PDS-based cross-VM detection with $\sigma=2\% $
-can reduce the  size further to 8\% of original size, namely it 
-delivers additional 10.5\% reduction.
-
 %this version combines the old and the minhash alg. to compare against srb
@@
     \caption{Deduplication efficiency of VC and SRB.}
-  \label{fig-exbin-efficiency-graph2}
+  \label{fig:exbin-efficiency-graph2}
 \end{figure}
+
+Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
+Deduplication efficiency is defined as the percent of duplicate chunks
+which are detected and deduplicated.
+The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
+is defined in Table~\ref{tab:symbol}. 
+%we allocate the space of distributed shared memory  to accommodate 2\%
+%of data chunks shared among VMs, as defined in 
+With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
+and  the deduplication efficiency can reach over 90\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
+The loss of efficiency in VC is caused by the restriction of the total physical memory available
+in the cluster to support PDS index.  
+The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
+for global comparison.
+In all cases, VC provides similar or better deduplication efficiency than SRB.
+
+This result shows VC can remove  a competitive amount of duplicates.
+In general, our experiments show that
+dirty-bit detection at the segment level  can reduce the data size to about 23\% of original data, 
+which leads  about 77\% reduction.
+Local search within a segment can   further reduce the data size
+to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
+The PDS-based cross-VM detection with $\sigma=2\% $
+can reduce the  size further to 8\% of original size, namely it 
+delivers additional 10.5\% reduction.
 
@@
   \centering
-  \epsfig{file=figures/srb_vs_vc, width=3.5in}
+  \epsfig{file=figures/srb_vs_vc, width=3in}
   \caption{Time to backup a dirty VM segment under SRB and VC}

### 2013-09-04 batchdedup/arch.tex
updated architecture section

@@
 duplicates can be detected using segment dirty bits when the segment size is 2M bytes.  
-This setting requires OS to maintain segment dirty bits and 
-the amount of space for this purpose is negligible. In the second level of deduplication, content blocks of dirty segments 
-are compared with the fingerprints of unique  blocks from the previous snapshots.
+This setting requires the virtual disk driver to maintain segment dirty bits,
+which has a negligible space cost (1 bit per 2 MB). In the second level of deduplication, content blocks of dirty segments 
+are compared with the fingerprints of unique  blocks from previous snapshots.
 Our key strategies are explained as follows.
@@
 % in a  disjointed manner.
-Initial data  blocks follows the VM distribution 
+Initial data  blocks follow the VM distribution 
 among machines 
@@
 should be collected following the same distribution.
-Therefore, there are two all-to-all data redistribution operations involved.
-One is to map detection requests from VM-based distribution to fingerprint based distribution.  
-Another one  is to map duplicate summary from fingerprint-based distribution to VM based distribution.  
+Therefore, there are four all-to-all data redistribution operations involved.
+One is to map detection requests from VM-based distribution to fingerprint based distribution, and
+another one  is to map duplicate summary from fingerprint-based distribution to VM based distribution.
+Two additional rounds are required to ensure no duplicate blocks are missed
+and that both the partition index holder and VM owning machines have correct
+data references.
 The redistributed data needs to be accumulated on the disk to reduce the use of memory.
@@
 We have designed an efficient data exchange and disk data buffering  scheme to address this.
+\item {\bf Round Scheduling}.
+When all data is scheduled to be deduplicated in one round, the cost of Copy
+on Write (CoW) can be significant, as explored in other papers\cite{EMCIncrementalDataChanges}.
+We therefore develop an algorithm to break up the data into multiple rounds to
+make the best use of the efficiency of batch processing, while minimizing
+the cost of CoW.
 
@@
 %\item
-In Stage 1, each machine independently reads  
+In Stage 1a, each machine independently reads  
 %$v/k$  
@@
 %\item
-Stage  2 is to load disk data and perform fingerprint comparison at each machine one request partition at a time.
+Stage 1b is to load disk data and perform fingerprint comparison at each machine one request partition at a time.
 % in the partitions.  
@@
 It also allocates $v$ request buffers to copy duplicate summary from $p$ receive buffers and output to the local disk
-when request buffers are full.
+when request buffers are full. One potential issue is that there may be
+multiple copies of a new block added to the system during the same round.
+We call these dup-with-new blocks and the redundandy is discovered and
+logged during the index lookup.
+Our experience is that there is significant redundancy during the initial snapshot backup and after
+that, the percentage of redundant blocks due to concurrent processing  is small.
+
+In stage 2a the deduplication results corresponding to unique (new) data blocks
+are exchanged using $p$ send and receive buffers to route the responses to the
+deduplication requesters. Dup-with-new blocks are not exchanged, as they are
+treated as duplicate blocks, only without data references (the data references
+to these blocks are added in Stage 3).
 
@@
 %\item 
-Stage 3 is to perform real backup.
+Stage 2b is to perform the real backup.
 % one VM at a time.
@@
 reads  dirty segments of a VM, and outputs non-duplicate blocks to the final backup 
-storage. Additionally, the global index on each machine is updated with the meta data of new chunk blocks. 
+storage. Additionally, references to each new data block are saved so that the
+global index may be updated.%the global index on each machine is updated with the meta data of new chunk blocks. 
 When a segment is not dirty, the system only needs to output the segment meta data such as a reference pointer. 
@@
 blocks. Our experiment shows that it is faster to read dirty segments in the tested workload.
-Another issue is that during global index update after new block creation,
+%Another issue is that during global index update after new block creation,
 % in the backup storage,
-the system  may find some  blocks with the same fingerprints have been 
-created redundantly. For example, two different VM blocks that have the same  fingerprint are not detected
-because  the  global index has not contained such a fingerprint yet. 
-The redundancy is discovered and logged during the index update and can be repaired
-periodically when necessary.  Our experience is that there is a redundancy during the initial snapshot backup and once 
-that is repaired, the percentage of redundant blocks due to concurrent processing  is insignificant.
+%the system  may find some  blocks with the same fingerprints have been 
+%created redundantly. For example, two different VM blocks that have the same  fingerprint are not detected
+%because  the  global index has not contained such a fingerprint yet.
 
@@
 
-The above steps can be executed by each machine using one thread to minimize the use of computing resource.
+In Stage 3a the machines exchange references to new blocks. This is required
+because it is the VM holder that backs up the data, but the partition index
+holder that must perform index lookups. Each machine reads the references
+obtained for all new blocks written, and then sends those references to the
+partition index holder, and the received references are saved to disk during 3a.
+
+Stage 3b is where the index update occurs; new blocks are added to each
+partition index, and additionally dup-with-new blocks are re-read to obtain
+references. The dup-with-new blocks, now with references, are added to the
+duplicate result lists to be returned in Stage 4.
+
+In the final Stage of our algorithm, Stage 4, All duplicate references,
+including dup-with-new blocks, are returned to the requesters and the snapshot
+recipes are updated with those pointers.
+
+The above steps can be executed by each machine using one thread to minimize
+the use of computing resources.
 The  disk storage usage on each machine 
-is fairly small for  storing part of global index and
+is fairly small for  storing part of the global index and
 accumulating  duplicate detection requests that contain fingerprint information.   

### 2013-09-04 batchdedup/background.tex
create batch dedup paper directory
updated architecture section

--- 2013-05-14 hotstorage13/background.tex
@@
 in our context, finishing the backup of required VM images within a reasonable time window is more
-important than optimizing individual VM block  backup requests.
+important than optimizing individual VM block  backup requests, and by batch
+processing the deduplication requests we can decrease resource usage.
 

### 2013-09-09 snapshot_system/fast14_evaluation.tex
updated dedup efficiency
update evaluation

@@
 at the same time on each physical machine. 
-[ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
-the cloud infrastructure services and are shared among many applications.]
+% [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
+% the cloud infrastructure services and are shared among many applications.]
 We see our hybrid deduplication scheme only occupies a small amount of system resources. 
@@
 Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
-snapshot space per VM caused  by approximate deletions.
+storage space per VM caused  by approximate deletions.
 The slot line is the predicted leakage using Formula~\ref{eq:leak} from Section~\ref{sect:delete}
 while the dashed line is the actual leakage measured during the experiment.
-[OTHER PARAMETERS USED]
+% [OTHER PARAMETERS USED]
 After 9 snapshot deletions, the actual leakage reaches 0.01\% and this means that

### 2013-09-09 batchdedup/intro.tex

--- 2013-05-14 hotstorage13/intro.tex
@@
 
-This paper seeks for a low-cost architecture option and considers that
-a backup service uses the existing cloud computing resource.
+This paper seeks for a low-cost architecture option and considers a backup
+service that uses the existing cloud computing resource.
 %Since most of backup data is not used in practice, system resource in such a service is not fully utilized. 
@@
 and that some deduplication requests are delayed for staged parallel processing.
+Another tradeoff of our efficient batched approach, related to reading each
+segment twice, is that we must maintain a consistent view of the disk between
+the first and second read. We use Copy on Write (CoW) to acheive this, at the
+cost of additional disk space.
 With careful parallelism and buffer  management,
-this multi-stage detection scheme can provide  a sufficient throughput for VM backup.
+this multi-stage detection scheme can provide  a sufficient throughput for VM
+backup, and by adopting a multiple-batch approach we can minimize the cost
+of maintaining a consistent view.
 

### 2013-09-09 batchdedup/scheduling.tex
revisions
updated architecture and scheduling. updated and split data flow figure into stages.

@@
 is sent to over the network. However, in our case we are backing up the
-original virtual disk, which may still be in use during the snapshot. This adds
-extra complexity to the cost analysis, because we must now also consider the
-cost of maintaining a constistent view during the snapshot process. We use the
-Copy on Write (CoW) provided by the virtual disk manager to maintain a
-consistent view. With CoW, the
-duration of the backup affects how much data must be copied. Other studies have
+original virtual disk, so a single round backup presents several problems.
+The first is that the average turnaround time for a VM is the time it takes to
+backup all the VMs. The second, which is related to the first, is that a single
+round backup has the highest cost to maintain a consistent view of the virtual
+disks. We use Copy on Write (CoW) for this, and the consistent view must be
+maintained between stage 1a and stage 2b, which can have sisgnificant cost if
+the system must wait for every single VM before unlocking any of the VMs.
+Other studies have
 shown that as much as 8\% or even more of total capacity must be reserved for
@@
 isn't something we can change, nor the write rate, but we can minimize the
-duration that a given VM is undergoing CoW. We assume a poisson distribution of
+duration that a given VM is undergoing CoW. By minimizing the backup time for
+individual VMs we also improve CoW cost. To evaulate our
+CoW cost improvement, we assume a poisson distribution of
 writes (which closely fits the meaured results from
-\cite{EMCIncrementalDataChanges}), and then try to minimize the CoW cost using
-our performance and CoW model. Although the single batch schedule completes the
-backup in the smallest amount of time, it also has the greatest CoW cost
-because the most processing must be done before any VM can release the CoW
-lock.
+\cite{EMCIncrementalDataChanges}).
 
@@
 
-We can see above that the way to decrease the CoW cost is to decrease t, the
-time the virtual disk is under CoW. We do that by breakng up the backup into
-multiple
-rounds, where in each round the CoW cost is minimized. The more rounds there
-are the shorter each round can be and therefore the smaller the CoW cost. The
-more rounds there are however the greater the backup overheads and some of the
+In addition to backup time for individual VMs, another cost consideration is
+total backup time for the system. It is generally preferred to run backups
+during low demand hours to make use of otherwise unused time and minimize the
+impact on users. This leaves a window of several hours (e.g. from 1am to 4am)
+to complete the backup. The more rounds there
+are the shorter each round can be and therefore the smaller the VM backup times
+and the total CoW costs. The
+more rounds there are however the greater the overheads and some of the
 efficiency gained from batch processing is lessened. We balance these costs by
-setting a time limit on the whole backup job, and then develop an algorithm to
-schedule VMs into rounds and pick the number of rounds to use.
+developing an algorithm to schedule VMs into rounds.
 
-With these parameters a model that closely fits our goals is the dual version
+From our requirements a model that closely fits our goals is the dual version
 of the
@@
 least some minimum level. This fits our purpose because we want to maximize the
-number of rounds, with some constraint to keep the efficiency benefits of batch
-processing. In our dual-bin-packing solution the constraint is to keep the total
+number of rounds to minimize VM backup times, with some constraint to keep the
+efficiency benefits of batch processing and keep the total backup time low.
+In our dual-bin-packing solution the constraint is to keep the total
 cost of the schedule under a time limit rather than mandating a minimum bin
-level. We
-adapt an algorithm for dual bin packing\cite{DualBinPacking} to fit our VM
+level. We have adapted
+an algorithm for dual bin packing\cite{DualBinPacking} to fit our VM
 scheduling problem. The algorithm adapted is called iterated A and works by
@@
 \todo{justify choice of initial UB (right now it is mostly arbitrary)}
-\begin{lstlisting}
+\begin{figure}
+\begin{lstlisting}[frame=single]
+Iterated A:
 Set UB=min(n,2*v)
@@
 \end{lstlisting}
+\caption{Iterated A scheduling algorithm, requires good choice of A to be effective}
+\end{figure}
+
 where A(machines,N) returns the total backup time of the schedule for N rounds\\
@@
 The general algorithm relies on a good choice of A to arrive at an efficent
-packing. Our first VM packing heuristic, A0, is a nai\"\i{}ve approach very
+packing. Our first VM packing heuristic, A0, is a na\"\i{}ve approach very
 close to the un-adapted algorithm from the dual bin packing paper. For both
@@
 
+\begin{figure}
+\begin{lstlisting}[frame=single]
 A0:
-\begin{lstlisting}
 sort VMs in descending order by size
@@
 \end{lstlisting}
+\caption{Na\"{\i}ve round packing heuristic based on VM size and current round runtime}
+\end{figure}
 
-A0 decreases CoW cost (see Table~\ref{tab:schedule-costs}), but has room for
-improvement. The first issue is that the round with the current lowest runtime
+A0 does provide for shorter rounds (see Table~\ref{tab:schedule-costs}), but
+the efficiency of the packing is poor due to several issues
+The first issue is that the round with the current lowest runtime
 is chosen. Because backup time is dependent on a combination of the highest
@@
 
+\begin{figure}
+\begin{lstlisting}[frame=single]
 A1:
-\begin{lstlisting}
 while there is an unscheduled VM
@@
 \end{lstlisting}
+\caption{More effective round packing heuristic based on minimizing remaining work and predicted round time}
+\end{figure}
 

### 2013-09-10 batchdedup/scheduling.tex
updated scheduling with explanatory figures

@@
 
+\begin{figure}[thb]
+\centering
+\includegraphics[width=0.5\textwidth]{images/VMRound.pdf}
+\caption{Choosing a round to schedule a VM to. Though the rounds look
+identical in terms of total/average load, Round 1 is a much better choice.}
+\label{fig:VMRound}
+\end{figure}
+
 A0 does provide for shorter rounds (see Table~\ref{tab:schedule-costs}), but
@@
 loaded machine in a round it will increase runtime much more than if we add the
-VM to a different round where that machine is currently empty
-\todo{(insert figure to show how this happens)}. Therefore a better scheduling
-would be obtained if we pick the round with the lowest runtime after we
-simulate adding the new VM to that round. This new round picking heuristic
+VM to a different round where that machine is currently empty. You can see this
+in Figure~\ref{fig:VMRound}, where VM1D must be scheduled to one of two rounds
+which currently have the same average/total load. The effect of VM1D on round 1
+would be much less than the effect on round 2 because we wouldn't be increasing
+the maximum machine load of the round, so we should schedule to round 1.
+Therefore a better
+scheduling heuristic is one based on predicted runtime after adding the VM, and
+picking the round with the lowest runtime after adding the VM to that round.
+This new round picking heuristic
 takes into account that the same VM might have different affects on different
@@
 backed up by any machine in the cluster then the problem of load balancing
-becomes a simpler but much different problem, and isn't considered here. We
+becomes a simpler but much different problem, but isn't considered here. We
 also pick the most heavily loaded (i.e. most data remaing) machine in case of
-ties so we can make the most backup progress in a round.
+ties so we can make the most backup progress in a round, given equivalent
+equivalent options.
 
@@
 machine has a greater impact than selecting the largest VM on a lightly loaded
-machine). A better way to pick VMs than just by size is to simulate removing
-VM's, then model the new single round time, and pick the VM whose removal most
+machine). Our improved hueristic to pick VMs is to predict the one-round
+runtime after removing that VM, and pick the VM whose removal most
 decreases the single round time (i.e. the VM that has the greatest impact on
@@
 
-A1 significantly improves our simulated results, bringing our CoW costs much
-closer to the best case than the worst case, as can be seen in
+A1 significantly improves our simulated results, also bringing our CoW costs
+much closer to the best case than the worst case, as can be seen in
 Figure~\ref{tab:schedule-costs}.  Our current implementation of the algorithm

### 2013-09-13 sim_src/lru_cache.cpp
add makefile

@@ -156,7 +156,6 @@ void CdsLruCache::BatchAddItem(const std::vector<Block> &blklist)
 
 void CdsLruCache::RemoveItems(size_t n)
 {
-    cout << "need to remove: " << n << std::endl;
     std::priority_queue<CacheIterator, std::vector<CacheIterator>, TimeComparison> myheap;
     for (CacheIterator it = cache_.begin(); it != cache_.end(); it ++)
     {
@@ -176,7 +175,43 @@ void CdsLruCache::RemoveItems(size_t n)
     myvector = reinterpret_cast<std::vector<CacheIterator> *>(&myheap);
     for (std::vector<CacheIterator>::iterator it = myvector->begin(); it != myvector->end(); it ++)
     {
-        cout << "remove: " << (*it)->first.size_ << std::endl;
         cache_.erase(*it);
     }
 }
+
+void CdsLruCache::Save(std::ostream &os)
+{
+    for (CacheIterator it = cache_.begin(); it != cache_.end(); it++)
+        it->first.Save(os);
+}
+
+void CdsLruCache::Load(std::istream &is)
+{
+    struct timeval tv;
+    struct timezone tz;
+    gettimeofday(&tv, &tz);
+
+    Block blk;
+    while (blk.Load(is))
+        cache_[blk] = tv;
+}
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2013-09-13 sim_src/lru_cache.hpp

@@ -72,6 +72,14 @@ public:
 
     bool SearchItem(const Block& blk);
 
+    /*
+     * save and load cache contents
+     * timestamp is ignored
+     */
+    void Save(std::ostream& os);
+
+    void Load(std::istream& is);
+
 private:
     void RemoveItems(size_t n);
     

### 2013-09-13 sim_src/dedup_types.hpp
add makefile

@@ -36,6 +36,7 @@ using namespace std;
 #define IN_PARENT 0x01		// 001
 #define IN_CDS 0x02			// 010
 #define IN_DIRTY_SEG 0x05	// 101
+#define IN_CDS_CACHE 0x0a	// 1010
 
 typedef uint8_t Checksum[CKSUM_LEN];	// checksum type
 
@@ -113,14 +114,16 @@ public:
         return size_;
     }
 
-	void Save(ostream& os) {
+	void Save(ostream& os) const
+    {
 		os.write((char *)cksum_, CKSUM_LEN);
 		os.write((char *)&file_id_, sizeof(Block::file_id_));
 		os.write((char *)&size_, sizeof(Block::size_));
 		os.write((char *)&offset_, sizeof(Block::offset_));
 	}
 
-	bool Load(istream& is) {
+	bool Load(istream& is)
+    {
 		is.read((char *)cksum_, CKSUM_LEN);
 		if (is.gcount() != CKSUM_LEN)
 			return false;
@@ -233,7 +236,7 @@ public:
         return std::binary_search(blocklist_.begin(), blocklist_.end(), blk);
     }
 
-    void Save(ostream& os) 
+    void Save(ostream& os) const
     {
         uint32_t num_blocks = blocklist_.size();
         os.write((char *)&num_blocks, sizeof(uint32_t));

### 2013-09-13 batchdedup/2012concl.tex

--- 2012-05-06 vm_snapshot_sim/2012concl.tex
@@
 room for additional optimization we are further studying.
-\section*{Acknowledgments}
-{\small
-We would like to thank Weicai Chen and Shikun Tian from Alibaba for their kind support, 
-and the anonymous referees for their comments.
-This work was completed while Wei Zhang was a intern at Alibaba.
-This work was supported in part by NSF IIS-1118106.
-Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
-do not necessarily reflect the views of the National Science Foundation.
-}
+%\section*{Acknowledgments}
+%{
+%We would like to thank Weicai Chen and Shikun Tian from Alibaba for their kind support, 
+%and the anonymous referees for their comments.
+%Wei Zhang has received internship support from Alibaba  for VM backup system development.
+%This work was supported in part by NSF IIS-1118106.
+%Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
+%do not necessarily reflect the views of Alibaba or the National Science Foundation.
+%}
 %Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,

### 2013-09-13 batchdedup/analysis.tex
updated performance model
Started round scheduling section

@@
+\comments{
 \section{ Old Performance Analysis and Comparison}
@@
 That is not so big, and is acceptable as we show later.
+}
 
-\section{New Performance Analysis and Comparison}
+\section{Performance Analysis and Comparison}
 \label{sect:analysis}
@@
 \centering
-\begin{tabular}{|p{1.25cm}|p{6.5cm}|}
+\begin{tabular}{|p{0.50cm}|p{7cm}|}
 \hline
@@
 
+Here we develop a model for the total backup time, which becomes important in
+trying to minimize the CoW cost during backup \emph{CoW should be explained and
+justified before this point in the paper}.  The backup process can be broken
+into 4 stages, where the first 3 stages each have two parts, first an
+all-to-all exchange of
+data, then local processing to prepare for the next stage.
+
 The system keeps at most  $ x$ copies of snapshots for each VM on average.  The
@@
 
-Here we develop a model for the total backup time, which becomes important in
-trying to minimize the CoW cost during backup \emph{CoW should be explained and
-justified before this point in the paper}.  The backup process can be broken
-into 4 stages, where each stage has two parts, first an all-to-all exchange of
-data, then local processing to prepare for the next stage.
-
 In Stage 1a, the dirty segments are read from the virtual disk, the hash of
@@
 \[
-    r_{max} c / b_r + \alpha_n\frac{p u r_{max}}{m_n} + r u / b_w
+    r_{max} c / b_r + \alpha_n\frac{u r_{max}}{m_n} + r u / b_w
 \]
@@
 In Stage 1b, each partition index is read from disk, then the dedup requests
-(from Stage 1a) for that paritition are processed and the results are written
-back out to disk. The results are broken into 3 groups: duplicate blocks, new
+(from Stage 1a) for that paritition are processed and the dedup results are
+written
+back out to disk. The results are broken into 3 groups for each partition:
+duplicate blocks, new
 blocks, and dup-with-new blocks, which are duplicates of blocks that are new to
@@
 $r_{max}(1-d_2)$ when we must wait for the most heavily loaded machine). In 2b
-the dedup results must be read and the actual disk blocks for each new block
+the dedup new block results must be read and the actual disk blocks for each
+new block
 must be re-read before they can be sent to the block store. To avoid seeking
@@
 \[
-    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2) p}{m_n} + r_{max}(1-d_2)e / b_w
+    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2)}{m_n} + r_{max}(1-d_2)e / b_w
 \]
@@
 \[
-    r_{max}c / b_r + r_{max}(1-d_2)e / b_r + r(1-d_2)c / b_b
+    r_{max}c / b_r + r_{max}(1-d_2)e / b_r% + r_{max}(1-d_2)c / b_b
 \]
@@
 index holder so that those blocks may be deduped in the future (and also so
-dup-with-new requests can be handled in this run). This Stage 3a, to read the
+dup-with-new requests can be handled in this round). This Stage 3a, to read the
 new index entries, return them to the parition index holder, and save the
@@
 \[
-    r_{max} (1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d_2) p}{m_n} + r(1-d_2)e / b_w
+    r_{max} (1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d_2)}{m_n} + r(1-d_2)e / b_w
 \]
@@
 results have chunk references, we can add the dup-with-new results to the
-duplicate result files. We then add the new references to the corresponding
-partition index to handle future dedup requests. Stage 3b costs:
+duplicate result files initially created in 1b. We then add the new references
+to the corresponding
+partition indices to handle future dedup requests. Stage 3b costs:
 \[
-    r ((1-d_2) + d_3)e/b_r + r (1-d_2)\beta + r((1-d_2) + d_3)e / b_w
+    r ((1-d_2) + d_3)e/b_r + r d_3\beta + r((1-d_2) + d_3)e / b_w
 \]
@@
 \[
-    r d_2 e / b_r + \alpha_n\frac{e r_{max} d_2 p}{m_n} + r e / b_w
+    r d_2 e / b_r + \alpha_n\frac{e r_{max} d_2}{m_n} + r e / b_w
 \]
@@
 \subsection{A Comparison with Other Approaches}
-
+\comments{
 The memory  space requirement for the data domain approach with bloom filter is:
@@
 \]
+}

### 2013-09-13 batchdedup/arch.tex
updated architecture
updated architecture and scheduling. updated and split data flow figure into stages.

@@
 
-\begin{figure*}[tbhp]
+%\begin{figure*}[tbhp]
+%\centering
+%\includegraphics[width=0.95\textwidth]{images/DataFlow.pdf}
+%\caption{Processing flow of Stage  1 (dirty segment scan and request accumulation), Stage 2 
+%(fingerprint comparison and summary output),  and Stage 3 (non-duplicate block backup).}
+%\label{fig:flow}
+%\end{figure*}
+
+\begin{figure}[th]
 \centering
-
-\includegraphics[width=0.95\textwidth]{steps.pdf}
-\caption{Processing flow of Stage  1 (dirty segment scan and request accumulation), Stage 2 
-(fingerprint comparison and summary output),  and Stage 3 (non-duplicate block backup).}
-\label{fig:flow}
-\end{figure*}
+\includegraphics[width=0.5\textwidth]{images/Stage1.pdf}
+\caption{Processing flow of Stage 1.}
+\label{fig:stage1}
+\end{figure}
 
 %\subsection{Processing flow and resource usage}
-The data flow of our multi-stage duplicate detection is depicted in Figure~\ref{fig:flow}. 
-%let $v$ be the total number of virtual machines hosted in  a cluster,  
-%we divide the backup into $k$  iterations. 
+%The data flow of our multi-stage duplicate detection is depicted in Figure~\ref{fig:flow}. 
 %\begin{itemize}
@@
 
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.5\textwidth]{images/Stage2.pdf}
+\caption{Processing flow of Stage 2.}
+\label{fig:stage2}
+\end{figure}
+
 In stage 2a the deduplication results corresponding to unique (new) data blocks
@@
 
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.5\textwidth]{images/Stage3.pdf}
+\caption{Processing flow of Stage 3.}
+\label{fig:stage3}
+\end{figure}
+
 In Stage 3a the machines exchange references to new blocks. This is required
@@
 
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.5\textwidth]{images/Stage4.pdf}
+\caption{Processing flow of Stage 4.}
+\label{fig:stage4}
+\end{figure}
+
 In the final Stage of our algorithm, Stage 4, All duplicate references,
-including dup-with-new blocks, are returned to the requesters and the snapshot
+including dup-with-new blocks, are returned to the requesters from the index
+holders and the snapshot
 recipes are updated with those pointers.
@@
 We impose a memory limit $M$ allocated for each stage of processing at each machine.
-The usage of $M$ is controlled as follows and space allocation among buffers is optimized based on the relative
-ratio between the cross-machine network  startup cost and disk access startup cost such as seek time.
-Using a bigger buffer  can mitigate the impact of slower startup cost. 
+%The usage of $M$ is controlled as follows and space allocation among buffers is optimized based on the relative
+%ratio between the cross-machine network  startup cost and disk access startup cost such as seek time.
+%Using a bigger buffer  can mitigate the impact of slower startup cost. 
+$M$ includes space for network communications and buffering data which is being
+sent to disk. We have found that as long as the write/read buffers are not
+unreasonably small (e.g. 4KB), the size of the disk buffers does not have a
+great impact on backup time, so we allocate small disk buffers (e.g. 128KB read
+and 2.5MB shared across all write buffers), and then allocate the remaining
+memory to index space or network buffers, depending on the stage.
 \begin{itemize}
 \item For Stage 1, $M$ is divided for 
-1) an I/O buffer to read dirty segments; 2) $2p$ send/receive buffers and $q$ request  buffers.
+1) an I/O buffer to read dirty segments; 2) $2p$ send/receive buffers and $q$
+disk buffers for deduplication requests.
 

### 2013-09-13 batchdedup/background.tex

--- 2013-05-14 hotstorage13/background.tex
@@
 
-%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
-At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
-represented as virtual disk image files in the host operating system.
-For VM snapshot backup, file-level semantics are normally not provided.
-Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. 
-%Only raw access information at disk block level are provided. 
-%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
-%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
-%only a very small slice of cluster resource can be used for the backup purpose.
+At a cloud cluster node providing access to multiple virtual machines, each
+instance of a guest operating system runs on a virtual machine (VM), accessing
+virtual hard disks represented as virtual disk image files in the host
+operating system. For VM snapshot backups, file-level semantics are normally
+not provided, and snapshot operations take place at the virtual device driver
+level.  This meands no fine-grained file system metadata can be used to
+determine the changed data.
 
-%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
-Backup systems have been developed to use content fingerprints to identify duplicate
-content~\cite{venti02,Rhea2008}.
-Offline deduplication is used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
-%,NGmiddleware2011}.
-%Today's commercial data backup systems (e.g. from EMC and NetApp)
-%\cite{emc_avamar}\cite{datadomain_whitepaper}
-%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
-Several techniques have been proposed to speedup searching of duplicate
-fingerprints. For example, the data domain method ~\cite{bottleneck08} 
-uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
-accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-%Still such methods use a significant amount of memory resource for filtering and caching.
-%Such methods use dedicated nodes for deduplication, which add cost to cloud infrastructure and are less scalable.
-As discussed in Section~\ref{sect:intro},
-there is no dedicated resource for deduplication in our targeted setting and low memory usage
- is required so that the resource impact to other cloud services is minimized.
-%NG et al.~\cite{ NGmiddleware2011}  use
-%a related filtering technique for integrating deduplication in Linux  file system and the memory
-%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
-%Lillibridge et al.~\cite{sparseindex09} break list of chunks
-%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
-%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
-%These are segments that share many chunk IDs with the incoming segment with high probability.
-The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
-%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
-to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
-%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
-%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
-%lookup  
-In comparison, this paper focuses on  full deduplication without approximation.
+Another issue is the sheer size of the backups. to maintain mutiple daily
+uncompressed snapshots of each VM would be very expensive, even though
+most of the data remains the same from day to day, and even between VMs common
+software packages and operating systems mean that the amount of unique data is
+much smaller. Backup systems have been developed to use content fingerprints to
+identify duplicate content~\cite{venti02,Rhea2008}. Offline deduplication is
+used in~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks
+during idle time.  Several techniques have been proposed to speedup searching
+of duplicate fingerprints. For example, the data domain method
+~\cite{bottleneck08} uses  an in-memory Bloom filter and a prefetching cache
+for data blocks  which may be accessed.  An improvement to this work with
+parallelization is in ~\cite{MAD210,DEBAR}.  As discussed in
+Section~\ref{sect:intro}, there is no dedicated resource for deduplication in
+our targeted setting and low memory usage is required so that the resource
+impact to other cloud services is minimized. Approximation techniques which
+reduce the memory requirement at the expense of deduplication efficiency are
+studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}.  In comparison, this
+paper focuses on full deduplication without approximation
+
+%%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
+%At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
+%represented as virtual disk image files in the host operating system.
+%For VM snapshot backup, file-level semantics are normally not provided.
+%Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. 
+%%Only raw access information at disk block level are provided. 
+%%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
+%%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
+%%only a very small slice of cluster resource can be used for the backup purpose.
+
+%%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
+%Backup systems have been developed to use content fingerprints to identify duplicate
+%content~\cite{venti02,Rhea2008}.
+%Offline deduplication is 
+%used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
+%%,NGmiddleware2011}.
+%%Today's commercial data backup systems (e.g. from EMC and NetApp)
+%%\cite{emc_avamar}\cite{datadomain_whitepaper}
+%%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
+%Several techniques have been proposed to speedup searching of duplicate
+%fingerprints. For example, the data domain method ~\cite{bottleneck08} 
+%uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
+%accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
+%As discussed in Section~\ref{sect:intro},
+%there is no dedicated resource for deduplication in our targeted setting and low memory usage
+% is required so that the resource impact to other cloud services is minimized.
+%%NG et al.~\cite{ NGmiddleware2011}  use
+%%a related filtering technique for integrating deduplication in Linux  file system and the memory
+%%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
+%%Lillibridge et al.~\cite{sparseindex09} break list of chunks
+%%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
+%%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
+%%These are segments that share many chunk IDs with the incoming segment with high probability.
+%The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
+%%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
+%to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
+%%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
+%%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
+%%lookup  
+%In comparison, this paper focuses on  full deduplication without approximation.
+%%We also take advantages of the fact that in a VM cloud environment,
+%%the virtual device driver can easily keep track if  large data
+%%segments have been modified using dirty bits and such information can avoid sending
+%%unmodified data segments for deduplication, which significantly saves cost.
 
@@
 there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
-in our context, finishing the backup of required VM images within a reasonable time window is more
-important than optimizing individual VM block  backup requests.
+in our context, efficiently finishing the backup of VM images within a reasonable time window is more
+important than optimizing individual VM block  backup requests, and by batch
+processing the deduplication requests we can decrease resource usage.
 

### 2013-09-13 snapshot_system/append.tex
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.

@@
   \centering
-  \epsfig{file=images/append_store_arch.pdf, width=3.5in}
+  \epsfig{file=images/append_store_arch, width=3.5in}
   \caption{Architecture of Append Store}
@@
         $P_{change}$ & Probablity that a chunk is not found in parent snapshot & ~ \\ [1ex] \\ [-1.5ex]
-        $P_{in\_CDS}$ & Percentage of chunks in CDS & ~ \\ [1ex] \\ [-1.5ex]
+        $P_{in\_PDS}$ & Percentage of chunks in PDS & ~ \\ [1ex] \\ [-1.5ex]
         $T_{scan}$ & Time to scan segment data and caculate content hash & 74 ms \\ [1ex] \\ [-1.5ex]
@@
         $T_{read\_chunk}$ & Time of reading a chunk & ~ \\ [1ex] \\ [-1.5ex]
-        $T_{check\_CDS}$ & Time of checking CDS & ~ \\ [1ex] \\ [-1.5ex]
-        $T_{read\_CDS}$ & Time of reading a chunk data from CDS data store& ~ \\
+        $T_{check\_PDS}$ & Time of checking PDS & ~ \\ [1ex] \\ [-1.5ex]
+        $T_{read\_PDS}$ & Time of reading a chunk data from PDS data store& ~ \\
         \hline
@@
 \begin{dmath}
-T_{write} = P_{dirty} * N_{seg} * [max(T_{scan}, T_{read\_AS}) + P_{change} * N_{chunk} * T_{check\_CDS} + P_{new} * N_{chunk} * T_{write\_AS}]
+T_{write} = P_{dirty} * N_{seg} * [max(T_{scan}, T_{read\_AS}) + P_{change} * N_{chunk} * T_{check\_PDS} + P_{new} * N_{chunk} * T_{write\_AS}]
 \end{dmath}
@@
 \begin{dmath}
-T_{read} = N_{seg} * {T_{read\_AS} + N_{chunks} * [P_{in\_CDS} * T_{read_CDS} + (1 - P_{in\_CDS}) * T_{read\_chunk}]}
+T_{read} = N_{seg} * {T_{read\_AS} + N_{chunks} * [P_{in\_PDS} * T_{read_PDS} + (1 - P_{in\_PDS}) * T_{read\_chunk}]}
 \end{dmath}
@@
 \begin{dmath}
-T_{read\_chunk} = P_{in\_CDS} * T_{read\_CDS} + (1 - P_{in\_CDS}) * T_{read\_AS}
+T_{read\_chunk} = P_{in\_PDS} * T_{read\_PDS} + (1 - P_{in\_PDS}) * T_{read\_AS}
 \end{dmath}

### 2013-09-13 snapshot_system/challenge.tex

@@
 cloud cluster avoids the extra cost to acquire a dedicated backup facility
-and reduces the network bandwidth consumption in transferring the un-deduplicated
+and reduces the network bandwidth consumption in transferring the
 raw data for backup. 
 Figure~\ref{fig:collocated} illustrates the cluster architecture where
-each physical runs a backup service and a distributed file system (DFS)~\cite{GFS2004,Hadoop} 
+each physical machine runs a backup service and a distributed file system (DFS)~\cite{GFS2004,Hadoop} 
 serves a backup store  for the snapshots.
@@
 %use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
-Since it is expensive to compares a large number of chunk signatures for deduplication,
+Since it is expensive to compare a large number of chunk signatures for deduplication,
 several techniques have been proposed to speedup searching of duplicate
@@
 the deduplication process, only one copy of duplicates is stored in the storage,
-this artificially creates data dependency among different VM users. 
+this artificially creates data dependencies among different VM users. 
 Content sharing via deduplication affects fault isolation since machine failures happen periodically 
@@
 each request is routed  to a machine which holds
-a bloomer filter  or can fetch on-disk index for additional comparison.
+a Bloom filter  or can fetch on-disk index for additional comparison.
 While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow

### 2013-09-13 snapshot_system/delete.tex

@@
 \subsection{Approximate Deletion}
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=images/deletion.png, width=3.5in}
+  \caption{Approximate deletion}
+  \label{fig:deletion_flow}
+\end{figure}
+
 We design approximate deletion to fast identify unused data in the append store.
-Instead of scanning the whold append store, it uses a bloom filter to check 
+Instead of scanning the whold append store, it uses a Bloom filter to check 
 if a data are still referenced by living snapshots. However, there is a small false-positive probility which
@@
 \begin{enumerate}
-\item {\bf Creating bloom filter} Scan all the living snapshot recipess and their segment recipes,
-for every reference pointing to append store, add it to the bloom filter.
+\item {\bf Creating Bloom filter} Scan all the living snapshot recipess and their segment recipes,
+for every reference pointing to append store, add it to the Bloom filter.
 \item {\bf Check existance} For every data reference in the deleted snapshot recipe and its segment recipes,
-check the existance of that data reference in bloom filter. If not found, it is safe to delete that piece of data from append store
+check the existance of that data reference in Bloom filter. If not found, it is safe to delete that piece of data from append store
 because no living snapshots has referenced it.
@@
 The overall time of running a approximate deletion for one snapshot deletion would be scanning
-all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
+all the living snapshots and deleted snapshots, since operations on the in-memory Bloom filter can be done in
 parallel and is much faster than loading recipes from DFS:
@@
 Using the example and analysis in previous section, this approximate deletion can be done in 5 minutes. 
-Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
+Memory usage of the Bloom filter depends on its false-positive probility $P_{bl}$,
 when set $P_{bl}$ to 0.01, the memory footprint of approximate deletion is about 15 MB.

### 2013-09-13 snapshot_system/design1.tex
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.

@@
   \centering
-  \epsfig{file=images/snapshot_representation.pdf, width=3.7in}
+  \epsfig{file=images/snapshot_representation, width=3.7in}
   \caption{An example of snapshot representation.}
@@
 they do not include the actual data but only have
- references pointers to the data which are either stored in backup storage or CDS.
+ references pointers to the data which are either stored in backup storage or PDS.
 In our implementation the data reference is a 8 bytes field which is either an 
@@
 In addition, our snapshot system 
-places the index of CDS in MemCache for deduplication, 
+places the index of PDS in MemCache for deduplication, 
 and uses MapReduce to facilitate the offline
@@
   \centering
-  \epsfig{file=images/arch.pdf, width=3.9in}
+  \epsfig{file=images/arch, width=3.9in}
   \caption{Snapshot backup architecture of each node.}
@@
 The cross-VM deduplication is conducted by the broker to access 
-a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
+a common data set (PDS) (will discuss in Section~\ref{sect:crossVM},
 whose block hash index is stored in a distributed memory cache.

### 2013-09-13 snapshot_system/fast14_abstract.tex
change to usenix format

--- 2013-08-28 snapshot_system/abs.tex
@@
 reduces network traffic;
-% when their signatures are identical. 
 however it is resource expensive and less fault-resilient to perform a global deduplication
@@
 efficiency while sustaining a good backup throughput. 
-
-%This paper studies the      a VM snapshot storage architecture which adopts multiple-level selective deduplication to bring the benefits of fine-grained data reduction into cloud backup storage systems.
-%In this work, we describe our working snapshot system implementation, and provide
-%early performance measurements for both deduplication impact and
-%snapshot operations.
 \end{abstract}

### 2013-09-13 snapshot_system/fast14_background.tex

@@
 \section{Background and Design Considerations}
-\label{sect:option}
+\label{sect:background}
 At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
@@
 Figure~\ref{fig:collocated} illustrates the cluster architecture where
-each physical machine runs a backup service and a distributed file system (DFS)~\cite{GFS2004,Hadoop} 
+each physical machine runs a backup service and a distributed file system (DFS)~\cite{googlefs03,hdfs10} 
 serves a backup store  for the snapshots.
@@
 which  occurs frequently when snapshots expire regularly. 
-The mark-sweep approach~\cite{mark-sweep} is effective for deletion, and its main cost
+The mark-sweep approach~\cite{Guo2011} is effective for deletion, and its main cost
 is to count if a data chunk is still shared by other snapshots.
@@
 We are seeking for a tradeoff since 
-cross-VM  signature comparison can deliver additional compression~\cite{Guo2011,Dong,ExtremeBining}.
+cross-VM  signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
 \item {\bf Stateless  Data Routing}.
 One approach for scalable duplicate comparison is to use a content-based hash
-partitioning algorithm called stateless data routing~\cite{Dong20??}
+partitioning algorithm called stateless data routing~\cite{Dong2011}
 that divides the deduplication work with an approximation. This work 

### 2013-09-13 snapshot_system/fast14_introduction.tex

@@
 The rest of this paper is organized as follows.
-Section~\ref{option} reviews the background and discusses the  design options for snapshot backup 
+Section~\ref{sect:background} reviews the background and discusses the  design options for snapshot backup 
 with a VM-centric approach. 
-Section~\ref{sect:model}  analyzes the tradeoffs and benefits of our approach. 
-Section~\ref{sect:arch}  describes our system architecture and implementation details.
+Section~\ref{sect:deduplication}  analyzes the tradeoffs and benefits of our approach. 
+Section~\ref{sect:architecture}  describes our system architecture and implementation details.
 %   the benefit of our approach for fault isolation. 
-Section~\ref{exper} is our experimental evaluation that compares with other approaches.
-Section~\ref{conc}  concludes this paper.
+Section~\ref{sect:evaluation} is our experimental evaluation that compares with other approaches.
+Section~\ref{sect:conclusion}  concludes this paper.

### 2013-09-13 sim_src/dedup_types.hpp
fix compiling errors

@@ -114,24 +114,24 @@ public:
         return size_;
     }
 
-<<<<<<< HEAD
+
 	void Save(ostream& os) const
     {
-=======
-	void Save(ofstream& os) {
->>>>>>> 7834a15b90088558f0705350af4f8fe970eae28b
+
+
+
 		os.write((char *)cksum_, CKSUM_LEN);
 		os.write((char *)&file_id_, sizeof(Block::file_id_));
 		os.write((char *)&size_, sizeof(Block::size_));
 		os.write((char *)&offset_, sizeof(Block::offset_));
 	}
 
-<<<<<<< HEAD
+
 	bool Load(istream& is)
     {
-=======
-	bool Load(ifstream& is) {
->>>>>>> 7834a15b90088558f0705350af4f8fe970eae28b
+
+
+
 		is.read((char *)cksum_, CKSUM_LEN);
 		if (is.gcount() != CKSUM_LEN)
 			return false;
@@ -244,11 +244,11 @@ public:
         return std::binary_search(blocklist_.begin(), blocklist_.end(), blk);
     }
 
-<<<<<<< HEAD
+
     void Save(ostream& os) const
-=======
-    void Save(ofstream& os) 
->>>>>>> 7834a15b90088558f0705350af4f8fe970eae28b
+
+
+
     {
         uint32_t num_blocks = blocklist_.size();
         os.write((char *)&num_blocks, sizeof(uint32_t));

### 2013-09-13 sim_src/lru_cache.hpp

@@ -2,6 +2,7 @@
 #define _LRU_CACHE_H_
 
 #include <vector>
+#include <map>
 #include <sys/time.h>
 #include "dedup_types.hpp"
 
@@ -35,20 +36,20 @@ public:
     /*
      * add all the blocks into cache, discard old entries by timestamp
      */
-    void AddSegment(const Segment& seg);
+    void AddItems(const Segment& seg);
 
-    bool SearchEntry(const Block& blk);
+    bool SearchItem(const Block& blk);
 
 private:
     /*
      * discard the n oldest entries from cache
      */
-    void RemoveEntries(int n);
+    void RemoveItems(int n);
     std::vector<LruCacheEntry> cache_;
     uint32_t capacity_;
 };
 
-<<<<<<< HEAD
+
 typedef std::map<Block, struct timeval>::iterator CacheIterator;
 
 class TimeComparison
@@ -88,6 +89,6 @@ private:
     uint32_t capacity_;
 };
 
-=======
->>>>>>> 7834a15b90088558f0705350af4f8fe970eae28b
+
+
 #endif

### 2013-09-13 sim_src/cds_hit_analysis.cpp
some extra analysis code

@@ -1,0 +1,105 @@
+/*
+ * Read a snapshot recipe, dedup it against its parent snapshot and CDS
+ * This simulation uses lru strategy at level 2
+ */
+#include <iostream>
+#include <fstream>
+#include <string>
+#include "dedup_types.hpp"
+
+using namespace std;
+
+#define IN_PARENT 0x01		// 001
+#define IN_CDS 0x02			// 010
+#define IN_DIRTY_SEG 0x05	// 101
+
+void usage(char *progname)
+{
+	pr_msg("This program read a snapshot recipe, dedup it against CDS only.\n"
+	       "Usage: %s snapshot CDS", progname);
+}
+
+/*
+ * Load a 2MB segment from trace
+ */
+
+bool load_segment(Segment& seg, ifstream& is)
+{
+    Block blk;
+    seg.Init();
+    while (blk.Load(is)) {
+        if (blk.GetSize() == 0) {	// fix the zero-sized block bug in scanner
+            pr_msg("ignore zero-sized block");
+            continue;
+        }
+        seg.AddBlock(blk);
+        if (seg.GetSize() >= 2*1024*1024)
+            break;
+    }
+    seg.Final();
+    if (seg.GetSize() == 0) 
+        return false;
+    else
+        return true;
+}
+
+int main(int argc, char** argv)
+{
+    std::vector<Block> cds;
+    std::vector<Block>::iterator it;
+    Segment current_seg;
+    ifstream current_input, cds_input;
+    ofstream output;
+    uint32_t i;
+    Block blk;
+
+    if (argc != 3) {
+        usage(argv[0]);
+        return 0;
+    }
+
+    current_input.open(argv[1], std::ios_base::in | std::ios_base::binary);
+    if (!current_input.is_open()) {
+        pr_msg("unable to open %s", argv[1]);
+        exit(1);
+    }
+    cds_input.open(argv[2], std::ios_base::in | std::ios_base::binary);
+    if (!cds_input.is_open()) {
+        pr_msg("unable to open %s", argv[2]);
+        exit(1);
+    }
+
+    string outputname = argv[1];
+    outputname += ".cdshit";
+    output.open(outputname.c_str(), std::ios_base::out | std::ios_base::trunc);
+
+    // prepare CDS, assume it was sorted
+    while (blk.Load(cds_input)) {
+        cds.push_back(blk);
+    }
+    //        sort(cds.begin(), cds.end());
+
+    int hit_len = 0;
[…]

### 2013-09-13 sim_src/dedup_sim.cpp
add some extra analysis code

@@ -1,0 +1,133 @@
+/*
+ * Read a snapshot recipe, dedup it against its parent snapshot and CDS
+ * This simulation uses lru strategy at level 2
+ */
+#include <iostream>
+#include <fstream>
+#include <string>
+#include "dedup_types.hpp"
+
+using namespace std;
+
+#define IN_PARENT 0x01		// 001
+#define IN_CDS 0x02			// 010
+#define IN_DIRTY_SEG 0x05	// 101
+
+void usage(char *progname)
+{
+	pr_msg("This program read a snapshot recipe, dedup it against its parent snapshot and CDS.\n"
+           "CDS option is mandatory but can accept an empty file, parent snapshot is optinal.\n"
+           "This simulation uses LRU strategy at level 2\n"
+	       "Usage: %s snapshot CDS [parent]", progname);
+}
+
+/*
+ * Load a 2MB segment from trace
+ */
+
+bool load_segment(Segment& seg, ifstream& is)
+{
+    Block blk;
+    seg.Init();
+    while (blk.Load(is)) {
+        if (blk.GetSize() == 0) {	// fix the zero-sized block bug in scanner
+            pr_msg("ignore zero-sized block");
+            continue;
+        }
+        seg.AddBlock(blk);
+        if (seg.GetSize() >= 2*1024*1024)
+            break;
+    }
+    seg.Final();
+    if (seg.GetSize() == 0) 
+        return false;
+    else
+        return true;
+}
+
+int main(int argc, char** argv)
+{
+    std::vector<Block> cds;
+    std::vector<Block>::iterator it;
+    Segment current_seg, parent_seg;
+    ifstream current_input, parent_input, cds_input;
+    ofstream output;
+    bool has_parent = false;
+    uint32_t i;
+    Block blk;
+    //uint64_t new_size = 0;
+
+    if (argc < 3 || argc > 4) {
+        usage(argv[0]);
+        return 0;
+    }
+
+    current_input.open(argv[1], std::ios_base::in | std::ios_base::binary);
+    if (!current_input.is_open()) {
+        pr_msg("unable to open %s", argv[1]);
+        exit(1);
+    }
+    cds_input.open(argv[2], std::ios_base::in | std::ios_base::binary);
+    if (!cds_input.is_open()) {
+        pr_msg("unable to open %s", argv[2]);
+        exit(1);
+    }
+
+    if (argc == 4) {
+        has_parent = true;
+        parent_input.open(argv[3], std::ios_base::in | std::ios_base::binary);
[…]

### 2013-09-13 batchdedup/intro.tex

@@
 Our objective is to lower the cost incurred while sustaining the highest de-duplication ratio
-and  a sufficient throughput in dealing with a large number of VM images. 
-% This business model partially  resembles that of Amazon Glacier.
+and  a sufficient throughput in dealing with a large number of VM images.% This business model partially  resembles that of Amazon Glacier.
 
@@
 this multi-stage detection scheme can provide  a sufficient throughput for VM
-backup, and by adopting a multiple-batch approach we can minimize the cost
-of maintaining a consistent view.
+backup. To minimize the CoW cost and adjust the balance between total backup
+time and the backup times for individual VMs, we adopt a multiple-batch
+approach based on the dual bin packing problem.
 
@@
 Section ~\ref{sect:analysis} summarizes  our analysis of the system performance.
-Section ~\ref{sect:exper} presents  our evaluation results on the effectiveness.
+Section ~\ref{sect:scheduling} presents our round scheduling algorithm based on our performance model.
+Section ~\ref{sect:exper} presents  our evaluation results on the effectiveness of our system.
 Section ~\ref{sect:final} concludes this paper.

### 2013-09-13 snapshot_system/fast14_evaluation.tex
update graphs

@@
             },
-            mark repeat={5},
+            mark repeat={2},
             xlabel={Number of VMs added},
@@
             xmin=0,
-            ymin=88.5,
+            ymin=85,
             ymax=100,
@@
             \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
-            %\addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
-            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
-            %\addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
+            %\addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison2.txt};
+            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison2.txt};
+            %\addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison2.txt};
             \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
@@
 \begin{table}
-    \begin{tabular}{|c|c|c|c|}
+    \begin{tabular}{|c|c|c|c|c|}
     \hline
-    Tasks & CPU & Mem (MB) & Disk W (MB/s) \\ \hline
-    1     & 19\% & 18.1 & 32.1 \\ \hline
-    2     & 35\% & 31.8 & 53 \\ \hline
-    4     & 63\% & 54.1 & 84 \\ \hline
-    6     & 77\% & 71.9 & 88.5 \\ \hline
-    8     & 82\% & 90.5 & 89.2 \\ \hline
+    Tasks & CPU & Mem (MB) & Write (MB/s) & Time (hrs) \\ \hline
+    1     & 19\% & 18.1 & 8.37 & 1.314\\ \hline
+    2     & 35\% & 31.8 & 8.97 & 1.226\\ \hline
+    4     & 63\% & 54.1 & 9.33 & 1.179\\ \hline
+    6     & 77\% & 71.9 & 9.46 & 1.162\\ \hline
+%    8     & 82\% & 90.5 & 89.2 & \\ \hline
 %    10                      & 85\% & 97.2   & 90.4 \\ \hline
@@
 {\bf Processing Time breakdown}.
-Figure~\ref{fig:srb_vs_vc} shows
+Figure~\ref{fig:vc_srb_combined} shows
 the  average  processing  time of  a VM segment under VC and SRB. 
@@
   \centering
-  \epsfig{file=figures/srb_vs_vc, width=3in}
-  \caption{Time to backup a dirty VM segment under SRB and VC}
-  \label{fig:srb_vs_vc}
+  \epsfig{file=figures/vc_srb_combined, width=3in}
+  \caption{Time to backup a dirty VM segment under SRB and VC appraoches}
+  \label{fig:vc_srb_combined}
 \end{figure}
 
-Figure~\ref{fig:single_vm_backup} reports the average backup time for a VM in VC when
+% \begin{figure}[htbp]
+%   \centering
+%   \epsfig{file=figures/srb_vs_vc, width=3in}
+%   \caption{Time to backup a dirty VM segment under SRB and VC}
+%   \label{fig:srb_vs_vc}
+% \end{figure}
+
+Figure~\ref{fig:vc_srb_combined} also reports the average backup time for a VM in VC when
 varying the PDS size.  It lists the time distribution for data reading,
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=3in]{figures/single_backup_time}
-    \caption{Average time to backup a VM in VC with varying PDS sizes}
-    \label{fig:single_vm_backup}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=3in]{figures/single_backup_time}
+%     \caption{Average time to backup a VM in VC with varying PDS sizes}
+%     \label{fig:single_vm_backup}
+% \end{figure}
 

### 2013-09-13 snapshot_system/fast14_main.tex
update graphs

@@
 \usepackage{sansmath}
-\pgfplotsset{compat=1.7}
+\pgfplotsset{compat=1.5}
 \DeclareGraphicsExtensions{.pdf}
@@
 
-\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup}
+\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]}
 
@@
   {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
-  {wei, tyang, dagun}@cs.ucsb.edu, hongtang@alibaba-inc.com
+  \{wei, tyang, dagun\}@cs.ucsb.edu, hongtang@alibaba-inc.com
 }

### 2013-09-16 sim_src/dedup_types.hpp
code updates for fixed size segments

@@ -16,6 +16,7 @@
 #include <errno.h>
 #include <stdio.h>
 #include <string.h>
+#include "trace_types.h"
 
 #ifdef USE_PANGU
 #include "apsara/pangu.h"
@@ -37,8 +38,9 @@ using namespace std;
 #define IN_CDS 0x02			// 010
 #define IN_DIRTY_SEG 0x05	// 101
 #define IN_CDS_CACHE 0x0a	// 1010
+//#define FIX_SEGMENT_SIZE (2 * 1024 * 1024)	// size of a segment
 
-typedef uint8_t Checksum[CKSUM_LEN];	// checksum type
+//typedef uint8_t Checksum[CKSUM_LEN];	// checksum type
 
 enum FileSystemType {LOCAL = 0, PANGU = 1, KVFILE = 2};	// file system type
 
@@ -75,211 +77,250 @@ static void pr_msg(const char *fmt, ...)
 	va_end(ap);
 }
 
-/*
- * store the information of a variable size block data
- */
-class Block {
-public:
-	uint32_t size_;
-	uint32_t file_id_;
-	uint64_t offset_;
-	Checksum cksum_;
-
-	Block() {};
-
-    Block(const Block& blk) {
-        SetValue(blk);
-    }
-
-	Block(int sz, const Checksum& ck) {
-		Set(sz, ck);
-	};
-
-	~Block() {};
-
-    void SetValue(const Block& blk) {
-        size_ = blk.size_;
-        file_id_ = blk.file_id_;
-        offset_ = blk.offset_;
-		memcpy(cksum_, blk.cksum_, CKSUM_LEN * sizeof(uint8_t));
-    }
-
-	void Set(int sz, const Checksum& ck) {
-		size_ = sz;
-		memcpy(cksum_, ck, CKSUM_LEN * sizeof(uint8_t));
-	}
-
-    uint32_t GetSize()
-    {
-        return size_;
-    }
-
-
-	void Save(ostream& os) const
-    {
-
-
-
-		os.write((char *)cksum_, CKSUM_LEN);
-		os.write((char *)&file_id_, sizeof(Block::file_id_));
-		os.write((char *)&size_, sizeof(Block::size_));
-		os.write((char *)&offset_, sizeof(Block::offset_));
-	}
-
-
-	bool Load(istream& is)
-    {
-
-
-
-		is.read((char *)cksum_, CKSUM_LEN);
-		if (is.gcount() != CKSUM_LEN)
[…]

### 2013-09-16 sim_src/eb_dedup.cpp

@@ -9,7 +9,8 @@
 #include <map>
 #include <sstream>
 
-#include "dedup_types.h"
+#include "trace_types.h"
+#include "dedup_types.hpp"
 
 using namespace std;
 
@@ -39,8 +40,8 @@ int main(int argc, char **argv)
     map<string, Bin> binmap;
     map<string, Bin>::iterator it;
     Segment seg;
-    while (seg.Load(is)) {
-        binmap[seg.GetMinHashString()].AddSegment(seg);
+    while (seg.LoadFixSize(is)) {
+        binmap[seg.GetMinHash().ToString()].AddSegment(seg);
     }
 
     /*

### 2013-09-16 sim_src/trace_types.cpp

@@ -1,0 +1,232 @@
+#include "trace_types.h"
+#include <string.h>
+#include <sstream>
+#include <cstdio>
+
+Checksum::Checksum()
+{
+    memset(data_, '\0', CKSUM_LEN);
+}
+
+Checksum& Checksum::operator=(const Checksum& other)
+{
+    if (this == &other)
+        return *this;
+    memcpy(data_, other.data_, CKSUM_LEN);
+    return *this;
+}
+
+bool Checksum::operator==(const Checksum& other) const
+{
+    return memcmp(data_, other.data_, CKSUM_LEN) == 0;
+}
+
+bool Checksum::operator!=(Checksum const &other) const
+{
+    return memcmp(data_, other.data_, CKSUM_LEN) != 0;
+}
+
+bool Checksum::operator<(const Checksum& other) const
+{
+    return memcmp(data_, other.data_, CKSUM_LEN) < 0;
+}
+
+void Checksum::ToStream(ostream& os) const
+{
+    os.write((char*)data_, CKSUM_LEN);
+}
+
+bool Checksum::FromStream(istream& is)
+{
+    is.read((char*)data_, CKSUM_LEN);
+    if (is.gcount() != CKSUM_LEN)
+        return false;
+    return true;
+}
+
+string Checksum::ToString()
+{
+    string s(2 * CKSUM_LEN, '0');
+    for (int i = 0; i < CKSUM_LEN; i++) {
+		sprintf(&s[2 * i], "%02x", (unsigned char)data_[i]);
+	}
+	return s;
+}
+
+uint32_t Checksum::First4Bytes() const
+{
+    uint32_t tmp;
+    memcpy((char*)&tmp, data_, 4);
+    return tmp;
+}
+
+uint32_t Checksum::Last4Bytes() const
+{
+    uint32_t tmp;
+    memcpy((char*)&tmp, &data_[CKSUM_LEN - 4], 4);
+    return tmp;
+}
+
+uint32_t Checksum::Middle4Bytes() const
+{
+    uint32_t tmp;
+    memcpy((char*)&tmp, &data_[CKSUM_LEN - 12], 4);
+    return tmp;
+}
+
+Block::Block(int size, const Checksum& ck) 
+{
+    size_ = size;
+    cksum_ = ck;
+}
+
+void Block::ToStream(ostream& os) const
+{
+    cksum_.ToStream(os);
+    os.write((char *)&file_id_, sizeof(Block::file_id_));
+    os.write((char *)&size_, sizeof(Block::size_));
[…]

### 2013-09-16 snapshot_system/fast14_architecture.tex
improve formatting
revisions

@@
 Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicating whether the segment
-is modified since last backup. 
+has been modified since last backup. 
 Segments are further divided into variable-sized chunks (average 4KB) 
@@
 and chunks without any reference from other snapshots can be removed by this compaction process.
-By limiting the size of a container, we can effectively control the length of each compaction process.
+By limiting the size of a container, we can effectively control the length of each round of compaction.
 The compaction  routine can work on one container at a time and copy used data chunks to another container.
@@
 Since data chunks are always appended to a snapshot store during backup, 
-a local chunk ID is monotonically increasing.
+local chunk IDs are monotonically increasing.
 When a snapshot chunk is to be accessed, the recipe for the snapshot will point a data chunk
@@
 
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=images/sstore_arch, width=3in}
-  \caption{Data structure of a VM snapshot store.}
-  \label{fig:as_arch}
-\end{figure}
-
-A snapshot  store supports three API calls.
+The snapshot  store supports three API calls.
 \begin{itemize}
@@
 appends the header and data  to the corresponding VM file.
-A new container  index entry is also created for each chunk group and is written the corresponding
+A new container  index entry is also created for each chunk group and is written to the corresponding
 container index file.
@@
 Every local chunk ID however is directly copied rather than re-generated. This
-process leaves holes in the CID values, but preserves the sorted order.
+process leaves holes in the CID values, but preserves the order and IDs of chunks.
 As a result, all data references stored 
@@
 
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=images/sstore_arch, width=3in}
+  \caption{Data structure of a VM snapshot store.}
+  \label{fig:as_arch}
+\end{figure}
+
 \subsection{ VM-centric Approximate Snapshot Deletion with Leak Repair}
@@
   \centering
-  \epsfig{file=images/deletion.png, width=3.5in}
+  \epsfig{file=images/deletion.png, width=3in}
   \caption{Approximate deletion}
@@
 While we can use the mark-and-sweep technique~\cite{Guo2011}, 
-it still takes significant resource to conduct this process every time there is a snapshot deletion.
+it still takes significant resources to conduct this process every time there is a snapshot deletion.
 In the case of Alibaba, snapshot backup is conducted automatically and there are 
@@
 
-We seek a fast solution with a low resource usage to delete snapshots.
+We seek a fast solution with low resource usage to delete snapshots.
 Our VM-centric snapshot storage design simplifies the deletion process since 
 we can focus on  unreferenced chunks within each VM.
-The PDS data chunks are commonly shared all VMs and we do not consider them
+The PDS data chunks are commonly shared among all VMs and we do not consider them
 during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
@@
 
-For each snapshot deletion, the amount of chunks need to be deleted is nearly identical to the number of
+For each snapshot deletion, the number of chunks to be deleted is nearly identical to the number of
 newly add chunks $\Delta u$. 

### 2013-09-16 snapshot_system/fast14_background.tex
revisions

@@
 Because of collocation of this snapshot service with other existing cloud services, 
-cloud providers wish that the backup service only consumes  small resources
+cloud providers will want the backup service to only consume small resources
 with a minimal impact to the existing cloud services.
@@
 partitioning algorithm called stateless data routing~\cite{Dong2011}
-that divides the deduplication work with an approximation. This work 
-is similar to Exreme Binning\cite{extreme_binning09} and 
+that divides the deduplication work with a similarity approximation. This work 
+is similar to Extreme Binning\cite{extreme_binning09} and 
 each request is routed  to a machine which holds
@@
 The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
-To use a distributed memory version of the sampled index, every deduplicate request
-may access a remote machine for index lookup and the overall overhead of latency latency for all requests
+To use a distributed memory version of the sampled index, every deduplication request
+may access a remote machine for index lookup and the overall overhead of latency for all requests
 can be significant.  

### 2013-09-16 snapshot_system/fast14_evaluation.tex
revisions

@@
 Our evaluation objective is to
-study the benefit of fault tolerance and   deduplication efficiency  the VC approach and compare it
-with an alternative VO design, and assess backup throughput and  resource usage for a large number of VMs.
+study the benefit in fault tolerance and   deduplication efficiency of the VC approach and compare it
+with an alternative VO design. We also and assess backup throughput and  resource usage for a large number of VMs.
 
 We will compare our VC approach with
-a VO approach  using stateless routing with binning (call it SRB) 
+a VO approach  using stateless routing with binning (SRB) 
 based on~\cite{Dong2011,extreme_binning09}
@@
 Debian, Ubuntu, Redhat, CentOS, and win2008. 
-Each machine hosts upto 25 VMs and each VM keeps 10 automatically-backed snapshots in the storage while
+Each machine hosts upto 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage system while
 a user may instruct extra snapshots to be saved.
@@
 $V_c=2500$ represents  the absolute worst case for 2500 VMs. 
-A  VO curve has  $V_o=150$ which is  the average number of VMs that share a file system block. 
+The VO curve has  $V_o=6.3$ which is  the average number of VMs that share a file system block in our smaller dataset. 
 Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
@@
 
-Base on the observed performance numbers, even with a single backup task per node and enforcing the disk read speed to
+Based on the observed performance numbers, even with a single backup task per node and enforcing the disk read speed to
 50 MB/s,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
@@
 SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
-it relies on this local machine to access its index (often on the disk, supported by a bloomer filter) 
+it relies on this local machine to access its index (often on the disk, supported by a Bloom filter) 
 and perform comparison.

### 2013-09-17 sim_src/dedup_types.hpp
more logging to old extreme binning code

@@ -328,8 +328,10 @@ private:
     uint32_t num_segments_;
     string min_hash_;
     uint32_t num_blocks_;
+    uint32_t num_blocks_1_;
     uint32_t num_dedup_blocks_;
     uint32_t size_;
+    uint32_t size_1_;
     uint32_t dedup_size_;
 
 public:
@@ -337,8 +339,10 @@ public:
     {
         num_segments_ = 0;
         num_blocks_ = 0;
+        num_blocks_1_ = 0;
         num_dedup_blocks_ = 0;
         size_ = 0;
+        size_1_ = 0;
         dedup_size_ = 0;
         blocklist_.reserve(200);
     }
@@ -346,12 +350,20 @@ public:
     void AddSegment(Segment& seg)
     {
         blocklist_.insert(blocklist_.end(), seg.blocklist_.begin(), seg.blocklist_.end());
+        for (uint32_t i = 0; i < seg.blocklist_.size(); i++) {
+            size_1_ += seg.blocklist_[i].size_;
+            num_blocks_1_++;
+        }
         num_segments_ ++;
         min_hash_ = seg.GetMinHash().ToString();
     }
 
     void Deduplication()
     {
+        num_blocks_ = 0;
+        size_ = 0;
+        dedup_size_ = 0;
+        num_dedup_blocks_ = 0;
         sort(blocklist_.begin(), blocklist_.end());
         for (uint32_t i = 0; i < blocklist_.size(); i++) {
             num_blocks_ ++;
@@ -371,7 +383,8 @@ public:
         stringstream ss;
         ss << "raw: " << num_segments_ << " segments, " << num_blocks_ << " blocks, "
            << size_ << " bytes. " << "dedup: " << num_dedup_blocks_ << " blocks, "
-           << dedup_size_ << " bytes.";
+           << dedup_size_ << " bytes." << "addseg: " << num_blocks_1_ << " blocks, " 
+           << size_1_ << " bytes.";
         return ss.str();
     }
 };

### 2013-09-17 sim_src/eb_dedup.cpp

@@ -40,9 +40,14 @@ int main(int argc, char **argv)
     map<string, Bin> binmap;
     map<string, Bin>::iterator it;
     Segment seg;
-    while (seg.LoadFixSize(is)) {
+    uint64_t blocks = 0;
+    uint64_t bytes = 0;
+    while (seg.FromStream(is)) {
         binmap[seg.GetMinHash().ToString()].AddSegment(seg);
+        blocks += seg.blocklist_.size();
+        bytes += seg.size_;
     }
+    cout << "Partition summary: blocks: " << blocks << " bytes: " << bytes << endl;
 
     /*
      * step 2: eliminate duplicates inside the bin

### 2013-09-17 sim_src/eb_segment.cpp

@@ -42,8 +42,12 @@ int main(int argc, char **argv)
         os[i].open(output_file.str().c_str(), std::ios_base::out | std::ios_base::binary | std::ios_base::app);
     }
 
+    uint64_t blocks = 0;
+    uint64_t bytes = 0;
     //seg.Init();
     while (seg.LoadFixSize(is)) {//(blk.Load(is)) {
+        blocks += seg.blocklist_.size();
+        bytes += seg.size_;
         //seg.AddBlock(blk);
         //nblocks ++;
 
@@ -64,10 +68,11 @@ int main(int argc, char **argv)
         //    continue;
 
         //seg.Final();	// too big, enforce a break
-        seg.SaveRaw(os[seg.GetMinHash().Middle4Bytes() % 256]);
+        seg.ToStream(os[seg.GetMinHash().Middle4Bytes() % 256]);
         //seg.Init();
         //nblocks = 0;
     }
+    cout << "Trace summary: blocks: " << blocks << " bytes: " << bytes << endl;
 
     //if (nblocks != 0) {	// the tail
     //    seg.Final();

### 2013-09-18 snapshot_system/fast14_evaluation.tex
updates to paper

@@
 storage space per VM caused  by approximate deletions.
-The slot line is the predicted leakage using Formula~\ref{eq:leak} from Section~\ref{sect:delete}
+The solid line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
 while the dashed line is the actual leakage measured during the experiment.

### 2013-09-18 snapshot_system/fast14_evaluation.tex
change to table

--- 2013-09-13 snapshot_system/fast14_evaluation.tex
@@
 
-\begin{figure}
-    \centering
-    \subfigure[Backup throughput per node under controlled I/O bandwidth usage]
-    {
-        \includegraphics[width=3in]{figures/parallel_backup_with_read}
-        \label{fig:withread}
-    }
-    \\
-    \subfigure[Deduplication and storage system performance]
-    {
-        \includegraphics[width=3in]{figures/parallel_backup_no_read}
-        \label{fig:noread}
-    }
-    \caption{Throughput per-node with concurrent snapshot backup tasks}
-    \label{fig:parallel_backup}
-\end{figure}
+\begin{table}
+    \begin{tabular}{l|lll|lll}
+    Num. of concurrent      & \multicolumn{2}{l}{Throughput without I/O throttling (MB/s)} & \multicolumn{2}{l}{Throughput with I/O throttling (MB/s)} \\
+    backup streams per node & Raw                                       & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\
+    1                       & 1369.6                                    & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
+    2                       & 2408.5                                    & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
+    4                       & 4101.8                                    & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
+    6                       & 5456.5                                    & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
+    \end{tabular}
+\end{table}
 
-\subsection{Effectiveness of Approximate Deletion}
-\begin{figure}
-    \centering
-    \includegraphics[width=3in]{figures/leakage}
-    \caption{Accumulated storage leakage by approximate snapshot deletions}
-    \label{fig:leakage}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \subfigure[Backup throughput per node under controlled I/O bandwidth usage]
+%     {
+%         \includegraphics[width=3in]{figures/parallel_backup_with_read}
+%         \label{fig:withread}
+%     }
+%     \\
+%     \subfigure[Deduplication and storage system performance]
+%     {
+%         \includegraphics[width=3in]{figures/parallel_backup_no_read}
+%         \label{fig:noread}
+%     }
+%     \caption{Throughput per-node with concurrent snapshot backup tasks}
+%     \label{fig:parallel_backup}
+% \end{figure}
+
+% \subsection{Effectiveness of Approximate Deletion}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=3in]{figures/leakage}
+%     \caption{Accumulated storage leakage by approximate snapshot deletions}
+%     \label{fig:leakage}
+% \end{figure}
 

### 2013-09-18 snapshot_system/fast14_deduplication.tex
improve formatting
update graphs

@@
 We start with the standard dirty bit approach in a coarse grain segment level.
-In our implementation with Xen at an Alibaba platform, the segment size is 2MB
+In our implementation with Xen on an Alibaba platform, the segment size is 2MB
 and  the device driver is extended to support  changed block tracking. 
@@
 in the average of 4K or 8K~\cite{Jin2009},
-we conduct additional local inner-VM deduplication by comparing
-dirty segment's chunk fingerprints within  {\em similar} segments from its parent snapshot. 
+we conduct additional local inner-VM deduplication on a snapshot by comparing
+dirty segments' chunk fingerprints within  {\em similar} segments from its parent snapshot. 
 We define two segments are similar if their approximated content signature is the same.
@@
 the number of  similar segments to be  searched. 
- Then 
+ Then,
 given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
@@
 in the previous work~\cite{WeiZhangIEEE}.
-One key observation is that the inner deduplication has removed many of the duplicates.
+One key observation is that the inner-VM deduplication has removed many of the duplicates.
 There are fewer deduplication opportunities across VMs while the memory and network
@@
 Thus our approximation is that the global fingerprint comparison only searches for the top $k$
-most popular items. This dataset is called PDS (common data set). 
+most popular items. This dataset is called the PDS (popular data set). 
 The popularity of a chunk is the number  of data chunks  from different VMs
 that are duplicates of this chunk after the inner VM deduplication.
-This number can be computed periodically on a weekly basis.
+This number can be computed periodically (e.g., on a weekly basis).
 Once the popularity of all data chunks is collected, the system only maintains the top $k$
@@
 accumulate small local chunks. We manage this accumulation process using an append-store  scheme
-and discuss this in details in Section~\ref{sect:architecture}.
-The system allows all machines conduct the backup in parallel in different machines, and each machine
+and discuss this in detail in Section~\ref{sect:architecture}.
+The system allows all machines conduct the backup in parallel, and each machine
 conducts the backup of one VM at a time, and thus only requires a write  buffer for one VM.
@@
 file block for non-PDS chunks is associated with one VM and does not contain
-any PDS chunks. 
+any PDS chunks, to maintain our goal of fault isolation.
 \end{itemize}
@@
 We have not  adopted the  sampled index~\cite{Guo2011} 
-for  popular data chunks and  this is because sampling requires the use of prefetching to be effective.
+for  popular data chunks because sampling requires the use of prefetching to be effective.
 For the data sets we have tested, the spatial locality is limited among popular
-data chunks and  on average the number of consecutive data chunks is 7 among popular chinks, which is not sufficient.
+data chunks and  on average the number of consecutive data chunks is 7 among popular chunks,
+which is not sufficient.
 
@@
 \centering
-\begin{tabular}{|p{1.25cm}|p{6.5cm}|}
+\begin{tabular}{|p{1.25cm}|p{5.5cm}|}
 \hline
@@
 
-{\it [Need to find a place to put these numbers in: Total number of chunks 
-in 350 snapshots: 1,546,635,485. 
-Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
+% {\it [Need to find a place to put these numbers in: Total number of chunks 
+% in 350 snapshots: 1,546,635,485. 
+% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
 
@@
 VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
-remains to be a constant.
+remains constant.
 Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.
@@
 chunks detected as duplicates in global cross-VM deduplication due to PDS.
-We call it PDS coverage.
-Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed as
+We call this PDS coverage.
+Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
 0.65 and measured PDS coverage in our test dataset.
-$\sigma=2\%$ represents that 100MB memory is used per machine for top $k$ PDS.
+$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for top $k$ PDS.
 While the predicted value remains flat, the  real coverage actually increases as the data size
@@
 The replication degree of the backup storage 
-is $r$ for regular file blocks and $r=3$ is a typical setting in the distributed
-file system~\cite{googlefs03,hdfs10}.
+is $r$ for regular file blocks and $r=3$ is a typical setting in distributed
+file systems~\cite{googlefs03,hdfs10}.
 In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
@@
 Since $sigma$ is small,  term $\sigma \frac{r_c}{r}$ is small in the above expression.  
-Thus the impact on storage increase is very small when we choose a large $\frac{r_c}{r}$ ratio. 
+Thus the impact on storage increase is very small even when we choose a large $\frac{r_c}{r}$ ratio. 
 For example, $\frac{r_c}{r}=2$.
@@
 to the the VC and VO approaches.  
-A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of snapshot blocks.
+A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of VM snapshot blocks.
 
@@
 each file block contains the hot low-level chunks shared by many VMs, and it also contains
-rare chunks which are not shared.  From the about equations.
+rare chunks which are not shared.  From the above equations:
 \[
@@
 $N_1<N_o$. 
-Figure~\ref{fig:fsb-links} shows the number of VMs sharing by each file block.
-We can observe that $N_1 +N_2 < N_o$. 
+Figure~\ref{fig:fsb-links} shows the number of VMs sharing each file block,
+which shows how many VMs the failure of a single block can affect. We only show
+links to PDS blocks for VC because Non-PDS blocks in VC are always pointed to
+by exactly one VM.
+We can also observe that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
 This is likely because the PDS FSBs tightly pack data used by many VMs, 

### 2013-09-18 snapshot_system/fast14_evaluation.tex
change to table

@@
 {\bf Throughput.}
-Figure~\ref{fig:parallel_backup} shows the  backup throughput per each machine when all machine nodes 
+Table~\ref{tab:throughput} shows the  backup throughput per each machine when all machine nodes 
 handle  several VMs in parallel.
@@
 
-\begin{table}
+\begin{table*}[t]
     \begin{tabular}{l|lll|lll}
-    Num. of concurrent      & \multicolumn{2}{l}{Throughput without I/O throttling (MB/s)} & \multicolumn{2}{l}{Throughput with I/O throttling (MB/s)} \\
-    backup streams per node & Raw                                       & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\
+    Num. of concurrent      & \multicolumn{3}{l}{Throughput without}   & \multicolumn{3}{l}{Throughput with} \\
+    backup tasks per node & \multicolumn{3}{l}{I/O throttling (MB/s)} & \multicolumn{3}{l}{I/O throttling (MB/s)} \\ \hline
+                            & Raw                                       & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\
     1                       & 1369.6                                    & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
@@
     \end{tabular}
-\end{table}
+\caption{Backup throughput under different concurrency}
+\label{tab:throughput}
+\end{table*}
 

### 2013-09-19 snapshot_system/fast14_evaluation.tex
update table

@@
 
+\begin{table*}[t]
+    \centering
+    \begin{tabular}{c|ccc|ccc}
+    Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
+    backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
+    per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
+    1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
+    2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
+    4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
+    6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
+    \end{tabular}
+\caption{Backup throughput under different concurrency}
+\label{tab:throughput}
+\end{table*}
 {\bf Throughput.}
@@
 perform even better in production clusters, which often have ten or more disks on each node.
-
-\begin{table*}[t]
-    \begin{tabular}{l|lll|lll}
-    Num. of concurrent      & \multicolumn{3}{l}{Throughput without}   & \multicolumn{3}{l}{Throughput with} \\
-    backup tasks per node & \multicolumn{3}{l}{I/O throttling (MB/s)} & \multicolumn{3}{l}{I/O throttling (MB/s)} \\ \hline
-                            & Raw                                       & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\
-    1                       & 1369.6                                    & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
-    2                       & 2408.5                                    & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
-    4                       & 4101.8                                    & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
-    6                       & 5456.5                                    & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
-    \end{tabular}
-\caption{Backup throughput under different concurrency}
-\label{tab:throughput}
-\end{table*}
 

### 2013-09-19 snapshot_system/fast14_abstract.tex

@@
 reduces network traffic;
-however it is resource expensive and less fault-resilient to perform a global deduplication
-and let a data block share by many virtual machines. 
+however it is resource expensive and less fault-resilient to perform global deduplication
+and let a data block be shared by many virtual machines. 
 This paper proposes a VM-centric collocated backup service that  
@@
 search and associates  underlying file blocks with one VM for most cases.
-It restricts cross-VM deduplication under common blocks with extra replication support.
+It restricts cross-VM deduplication to popular blocks with extra replication support.
 Our analysis shows that  this VM centric scheme 

### 2013-09-19 snapshot_system/fast14_background.tex

@@
 to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
-Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
+Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}
+and a parallel batch solution for cluster-based deduplication is 
+studied in ~\cite{WeiZhangHotStorage13}. 
 All of the above approaches have focused on optimization of deduplication
@@
 One approach for scalable duplicate comparison is to use a content-based hash
-partitioning algorithm called stateless data routing~\cite{Dong2011}
+partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011} 
 that divides the deduplication work with a similarity approximation. This work 
-is similar to Extreme Binning\cite{extreme_binning09} and 
+is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 
 each request is routed  to a machine which holds
@@
 To use a distributed memory version of the sampled index, every deduplication request
-may access a remote machine for index lookup and the overall overhead of latency for all requests
+may access a remote machine for index lookup and the overall overhead of access latency for all requests
 can be significant.  

### 2013-09-19 snapshot_system/fast14_deduplication.tex

@@
   \epsfig{file=images/mh_local_dedup.png, width=3in}
-  \caption{Min-hash based local deduplication}
+  \caption{Similarity-guided local duplicate detection}
   \label{fig:local_dedup}
@@
 we conduct additional local inner-VM deduplication on a snapshot by comparing
-dirty segments' chunk fingerprints within  {\em similar} segments from its parent snapshot. 
-We define two segments are similar if their approximated content signature is the same.
-This segment signature value is defined as the minimum value of all its chunk fingerprints 
-computed during backup and is recorded in the snapshot recipe.
-When we are processing a dirty segment,
-we can easily find similar segments from the
-parent snapshot recipe and load their segment recipes and also set a limit on the 
-the number of  similar segments to be  searched. 
- Then,
-given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
-with those in similar segments.  
-For example, with a 2MB segment, there are about 500 fingerprints to compare. By limiting at most 10 similar
-segments to search,
-the amount of memory for maintaining those fingerprints in similar segment s is small.
+chunk fingerprints of a dirty segment 
+with those in  {\em similar} segments from its parent snapshot. 
+We define two segments are similar if their content signature is the same.
+This segment content signature value is defined as the minimum value of all its chunk fingerprints 
+computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
+content similarity is  an approximation~\cite{AdnriBroader}.  When processing a dirty segment,
+its  similar segments can be found easily from the
+parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
+which contain chunk fingerpints which can  potentially be duplicates.
+To limit the search scope, we set a limit on the the number of  similar segments to be  searched. 
+% Then,
+%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
+%with those in similar segments.  
+For example, a 2MB segment contains about 500 fingerprints and by limiting at most 10 similar
+segments to search, the amount of memory for maintaining those fingerprints in similar segments is small.
 
@@
 to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
-accumulate small local chunks. We manage this accumulation process using an append-store  scheme
-and discuss this in detail in Section~\ref{sect:architecture}.
+accumulate small local chunks. We manage this accumulation process using an append-store  scheme built
+on a distributed file system discussed  in Section~\ref{sect:architecture}.
+%Non-PDS chunks from the same VM are stored in one append store. 
+Each file system block is either dedicated to non-PDS chunks, or PDS-chunks.
+A file system block for non-PDS chunks is associated with one VM and does not contain
+any PDS chunks, to maintain our goal of fault isolation.
+PDS chunks are stored in a separate append-store instance with special replication handling. 
 The system allows all machines conduct the backup in parallel, and each machine
 conducts the backup of one VM at a time, and thus only requires a write  buffer for one VM.
-
-PDS chunks are stored in a separate append-store instance. In this way, each
-file block for non-PDS chunks is associated with one VM and does not contain
-any PDS chunks, to maintain our goal of fault isolation.
 \end{itemize}
-
-We have not  adopted the  sampled index~\cite{Guo2011} 
-for  popular data chunks because sampling requires the use of prefetching to be effective.
-For the data sets we have tested, the spatial locality is limited among popular
-data chunks and  on average the number of consecutive data chunks is 7 among popular chunks,
-which is not sufficient.
-
-\subsection{Impact on deduplication efficiency}
-Choosing the value  $k$ for the most popular chunks affects the deduplication efficiency.
-We analyze this impact based on the characteristics  of the VM snapshot traces
-studied from  application datasets.
-Our previous study shows that the popularity of data chunks after inner VM deduplication follows 
-a Zipf-like distribution\cite{Breslau1999a} and its
-exponent $\alpha$ is ranged between 0.65  and  0.7.~\cite{WeiZhangIEEE}. 
-Table~\ref{tab:symbol} lists parameters used in this analysis.
 
@@
 \end{figure}
+We have not  adopted the  sampled index~\cite{Guo2011} 
+for  detecting duplicates from popular chunks.
+For the data sets we have tested, the spatial locality 
+among popular
+data chunks is limited and  on average the number of consecutive data chunks is 7 among popular chunks.
+This is not sufficient to enable prefetching which is required  for index sampling.
 
-\begin{table}[ht]
+\begin{table}[htbp]
 \centering
@@
 \hline
-$c$ &  the total amount of data chunks\\ 
+$c$ &  the total amount of data chunks in a cluster of VMs\\ 
 \hline
-$c_u$ &  the total amount of unique fingerprints after inner VM  deduplication\\
+$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
 \hline
@@
 \hline
-$\sigma$ & =$\frac{k}{c_u}$.  The percentage of unique data  belong to  PDS.\\
+$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belong to  PDS\\
 \hline
@@
 \hline
-$N_1$ & the average number  of non-PDS file system blocks  in a VM\\
+$N_1$ & the average number  of non-PDS file system blocks  in a VM for VC\\
 \hline
-$N_2$ & the average number  of PDS file system blocks  in a VM\\
+$N_2$ & the average number  of PDS file system blocks  in a VM for VC\\
 \hline
@@
 \end{tabular}
-\caption{Modeling  parameters and symbols.}
+\caption{Modeling  parameters}
 \label{tab:symbol}
@@
 % Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
+\subsection{Impact on deduplication efficiency}
+Choosing the value  $k$ for the most popular chunks affects the deduplication efficiency.
+We analyze this impact based on the characteristics  of the VM snapshot traces
+studied from  application datasets.
+Our previous study shows that the popularity of data chunks after inner VM deduplication follows 
+a Zipf-like distribution\cite{Breslau1999a} and its
+exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
+Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
+We will use a number of parameters in our analysis below and they are defined in
+Table~\ref{tab:symbol}.
 
-As summarized in Table~\ref{tab:symbol},
-let $c$ be the total number of data chunks. 
-$c_u$ be the total number of fingerprints 
-in the global index after complete deduplication, and
-$f_i$ be the frequency for the $i$th most popular fingerprint. 
+%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
+%let $c$ be the total number of data chunks. 
+%$c_u$ be the total number of fingerprints 
+%in the global index after complete deduplication, and
+%$f_i$ be the frequency for the $i$th most popular fingerprint. 
 By Zipf-like distribution, $f_i = \frac{f_1}{i^\alpha}.$
@@
 \[
-f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c.
+f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
 \]
@@
 \begin{equation}
-f_1=\frac{c(1-\alpha)}{c_u^{1-\alpha}}.
+f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
 \end{equation}
@@
 
-Deduplication efficiency of VC using top $k$ popular chunks
+Deduplication efficiency of the VC approach using top $k$ popular chunks
 is the percentage of duplicates that can be detected:  
@@
 \frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
-{c  - c_u }\\
+{c  - c_u }.\\
 %\end{split}
@@
 Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.
-
-Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
-chunks detected as duplicates in global cross-VM deduplication due to PDS.
-We call this PDS coverage.
-Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
-0.65 and measured PDS coverage in our test dataset.
-$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for top $k$ PDS.
-While the predicted value remains flat, the  real coverage actually increases as the data size
-increases, which indicates that $\alpha$ increases with the data size. 
-Thus in practice, the coverage of the PDS increases as more VMs are involved.
 
@@
 \end{figure}
+Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
+chunks detected as duplicates in global cross-VM deduplication due to PDS.
+We call this PDS coverage.
+Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
+0.65 and measured PDS coverage in our test dataset.
+$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for top $k$ PDS.
+While the predicted value remains flat, the  real coverage actually increases as the data size
+increases, which indicates that $\alpha$ increases with the data size. 
+Thus in practice, the coverage of the PDS increases as more VMs are involved.
 
@@
     \centering
-    \subfigure[Sharing of data under VM-centric dedup model]
+    \subfigure[Sharing of file blocks under VC]
     {
@@
     \\
-    \subfigure[Sharing of data under VM-oblivious dedup model]
+    \subfigure[Sharing of file blocks under VO]
     {
@@
     }
-    \caption{Bipartite association of VMs and file blocks under VO and VC approaches}
+    \caption{Bipartite association of VMs and file blocks under (a) VC and (b) VO. }
     \label{fig:share}
@@
 \]
-Since $sigma$ is small,  term $\sigma \frac{r_c}{r}$ is small in the above expression.  
+Since $\sigma$ is small (it is 2\% in our experiments),  
+term $\sigma \frac{r_c}{r}$ is small in the above expression.  
 Thus the impact on storage increase is very small even when we choose a large $\frac{r_c}{r}$ ratio. 
-For example, $\frac{r_c}{r}=2$.
+For example, $\frac{r_c}{r}=2$ or 3.
 
@@
 if this block is used by this VM.
-For VC, each VM has an 
-average number of $N_1$ file system blocks for non-PDS data. 
-It also refers  an average of   $N_2$ file system blocks for PDS data. 
+
+For VC, each VM has an average number of $N_1$ non-PDS file system blocks
+and  has  an average of  $N_2$ PDS file system blocks. 
+Each non-PDS file system block is associated with one VM
+ and  we denote that PDS file system blocks are
+shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block. Then, 
+\[
+V *p*N_1 *s  \approx c_u (1-\sigma)\; \mbox{ and } \; 
+V *p*N_2 *s  \approx c_u \sigma *V_c
+\]
+For the VO approach, 
 For VO, each VM has an average  of  $N_o$ file system blocks
 and let $V_o$ be the average number of VMs shared by each file system block.
-
-In VC, each non-PDS file system block is associated with one VM
- and  PDS file system blocks are
-shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block. Thus, 
 \[
-V *p*N_1 *s  = C_u (1-\sigma)\; \mbox{ and } \; 
-V *p*N_2 *s  = C_u \sigma *V_c
-\]
-For the VO approach, 
-\[
-V *p*N_o *s  = C_u  V_o.
+V *p*N_o *s  \approx c_u  V_o.
 \]
@@
 $N_1<N_o$. 
-Figure~\ref{fig:fsb-links} shows the number of VMs sharing each file block,
-which shows how many VMs the failure of a single block can affect. We only show
-links to PDS blocks for VC because Non-PDS blocks in VC are always pointed to
-by exactly one VM.
-We can also observe that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
-This is likely because the PDS FSBs tightly pack data used by many VMs, 
-which decreases the overall number of FSBs required to backup a VM.
-If  the backup for multiple VMs is conducted concurrently, there would be more
-VMs shared  by each file block on average. Therefore,
-even when there is a loss of a PDS block, the VC approach tolerates the fault better.
+Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
+our test dataset.
+%which shows how many VMs the failure of a single block can affect. 
+For VC, we only show
+the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
+one VM.
+%We can also observe that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
+%This is likely because the PDS FSBs tightly pack data used by many VMs, 
+%which decreases the overall number of FSBs required to backup a VM.
+%If  the backup for multiple VMs is conducted concurrently, there would be more
+%VMs shared  by each file block on average. Therefore,
+%even when there is a loss of a PDS block, the VC approach tolerates the fault better.
 
@@
 	\end{tikzpicture}
-  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
+  \caption{Measured average number of VMs sharing a 64MB FSB in VO and in VC.}
   \label{fig:fsb-links}
@@
 
-The full snapshot availability of a VM is estimated as follows with parameters $N_1$, $N_2$, and $N_o$.
+The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
+ $N_2$ for VC and $N_o$ for VO.
 With replication degree $r$, the availability of a file block is the probability that  
@@
 
-For VC, there are two cases.
+For VC, there are two cases for $d$ failed machines.
 \begin{itemize}
 \item
-When there are $r \le d<r_c$ machines failed,  there is no PDS data loss and  
+When $r \le d<r_c$,  there is no PDS data loss and  
 the full snapshot availability of a VM in the VC approach is 
-and is
 \[

### 2013-09-19 snapshot_system/fast14_deduplication.tex

@@
 one VM.
-%We can also observe that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
-%This is likely because the PDS FSBs tightly pack data used by many VMs, 
-%which decreases the overall number of FSBs required to backup a VM.
-%If  the backup for multiple VMs is conducted concurrently, there would be more
-%VMs shared  by each file block on average. Therefore,
-%even when there is a loss of a PDS block, the VC approach tolerates the fault better.
+From data, 
+we have observed that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
+This is likely because the PDS FSBs tightly pack data used by many VMs, 
+which decreases the overall number of FSBs required to backup a VM.
+Also if  the backup for multiple VMs were conducted concurrently, there would be more
+VMs shared  by each file block on average in VO. 
+%Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.
 
@@
 	\end{tikzpicture}
-  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
+  \caption{Measured average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
   \label{fig:vm-links}
@@
 with different replication degree. This demonstrates inequality $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
-< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$. As we have also observed
-$N_1+N_2 <N_o$ in our dataset, these two conditions support that VC has a  higher availability. 
+< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
+these two conditions support that VC has a  higher availability. 
 %comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
@@
     \end{tikzpicture}
-    \caption{Availability of individual file system blocks in a 100 machine cluster with different replication degrees.}
+    \caption{Availability of a file system block in a 100 machine cluster with different replication 
+and failure settings.}
   \label{fig:fsb-availability}

### 2013-09-19 snapshot_system/fast14_evaluation.tex
figure updates

@@
                 %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
-                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
+                \legend{$R_C=4$,$R_C=5$,$R_C=6$}%,$R_C=7$}
 		\end{axis}
 	\end{tikzpicture}
-  \caption{Availability of VM backup snapshots as nodes fail in VC with different PDS Replication degree
- (Non-PDS replication fixed at 3, and average PDS block links set to 1250)}
+  \caption{Theoretical Availability of VM backup snapshots as nodes fail in VC
+ (Non-PDS replication fixed at 3, and average PDS block links set to 1250, 1000 node cluster)}
   \label{fig:pds-replication}
@@
             },
-            mark repeat={2},
+            mark repeat={10},
             xlabel={Number of VMs added},

### 2013-09-19 snapshot_system/fast14_architecture.tex
update formula

@@
 an open source DFS called QFS~\cite{QFS}. 
-All data needed for VM services, such as virtual disk images used by runtime VMs,
-and snapshot data for backup purposes, reside in this distributed file system. 
+% All data needed for VM services, such as virtual disk images used by runtime VMs,
+% and snapshot data for backup purposes, reside in this distributed file system. 
+All data needed for VM snapshot services, such as snapshot and segment recipes,
+chunk data and PDS data are reside in this distributed file system. 
 One physical node hosts tens of VMs, each of which accesses its virtual machine disk image through the

### 2013-09-19 snapshot_system/fast14_deduplication.tex
update formula

@@
 
-We use filesystem blocks rather than a deduplication
+We use file system blocks rather than a deduplication
 data chunk as our unit of failure because the DFS keeps
@@
 \[
-V *p*N_o *s  \approx c_u  V_o.
+V *p*N_o *s  = c_u  V_o.
 \]
@@
  $N_2$ for VC and $N_o$ for VO.
-With replication degree $r$, the availability of a file block is the probability that  
-all of its replicas do not appear in any group of $d$ failed machines. 
-Namely, $1-\binom{d}{r}/ \binom{p}{r}$. 
-The snapshot availability of a VM  in the VO approach is
+Given normal data replication degree $r$, PDS data replication degree $r_c$, 
+the availability of a file system block is the probability that  
+all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
+Namely, we define it as
+\[
+A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
+\]
+Then the availability of one VM's snapshot data under VO approach is the probability that
+ all its file system blocks are unaffected during the system failure:
 \begin{equation}
 \label{eq:VO}
-(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
+%(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
+A(r)^{N_o}. 
 \end{equation}
@@
 the full snapshot availability of a VM in the VC approach is 
-\[
-(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
-\]
-Since $N_1 <N_o$, the VC approach has a higher availability of VM snapshots than VO.
+\begin{equation}
+\label{eq:VC1}
+%(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
+A(r)^{N_1}.
+\end{equation}
+Since $N_1$ is typically much smaller than $N_o$, 
+the VC approach has a higher availability of VM snapshots than VO.
 
@@
 The full snapshot availability of  a VM in the VC approach is
-\[
-(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
-*
-(1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
-\]
+\begin{equation}
+\label{eq:VC2}
+% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
+% *
+% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
+A(r)^{N_1} * A(r_c)^{N_2}
+\end{equation}
 Figure~\ref{fig:fsb-availability} illustrates that the availability of an individual file system block
-with different replication degree. This demonstrates inequality $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
-< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
+with different replication degree. This demonstrates inequality 
+% $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
+$A(r) < A(r_c)$
+.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
 these two conditions support that VC has a  higher availability. 

### 2013-09-19 snapshot_system/fast14_evaluation.tex
update description

@@
 Our implementation is based on Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
-and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 5.
+and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 6.
 Our evaluation objective is to
@@
 Alibaba Aliyun's cloud platform with about 100 machines. 
-The VMs  of the sampled  data set   use popular operating systems such as 
-Debian, Ubuntu, Redhat, CentOS, and win2008. 
 Each machine hosts upto 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage system while
 a user may instruct extra snapshots to be saved.
+The VMs of the sampled data set use popular operating systems such as 
+Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
 The backup of VM snapshots is completed within a few  hours every night.
@@
 The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
+To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
+count the number of dependencies from a file system block to VM.
+In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
+case for VO approach. 
 Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.

### 2013-09-19 snapshot_system/fast14_deduplication.tex
figure updates

@@
             ylabel={Availability of Single FSB (\%)},
-            extra y ticks={99.9}, %to add extra ticks
+            %extra y ticks={99.9}, %to add extra ticks
             mark options=solid,
@@
     \caption{Availability of a file system block in a 100 machine cluster with different replication 
-and failure settings.}
+and failure settings.THIS PLOT WILL BE REPLACED BY TABLE}
   \label{fig:fsb-availability}

### 2013-09-19 snapshot_system/fast14_evaluation.tex
figure updates

--- 2013-09-19 snapshot_system/fast14_evaluation.tex
@@
 Figure~\ref{fig:vm-availability} shows the availability of VM snapshots when 
-there are up to 10 storage nodes failed in a 100-node cluster. 
+there are up to 25 storage nodes failed in a 1000-node cluster. 
 Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
@@
                     ylabel={\tiny VM Availability (\%)},
-                    extra y ticks={99.9}, %if important numbers are missing
+                    %extra y ticks={99.9}, %if important numbers are missing
                     mark options=solid,
@@
                     ]
-                    \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
+                    \addplot table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                     \addlegendentry{VO}
-                    \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
+                    \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                     \addlegendentry{VC}
-                    \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
+                    \addplot table[x=NodesFailed,y=VCWC1]{figures/node_failures_100.txt};
                     \addlegendentry{VC (worst-case)}
-                    %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
-                    %\addlegendentry{VO\,$20$ (optimistic)}
                     \end{axis}
@@
                 %\addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
-                \addplot table[x=NodesFailed,y expr=(\thisrow{VO1}-99.999)*1000]{figures/vm_availability_1000.txt};
+                \addplot table[x=NodesFailed,y expr=(\thisrow{VO}-99.999)*1000]{figures/node_failures_1000.txt};
                 %\addlegendentry{$VO\,6.3$ (optimistic)}
                 %\addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
-                \addplot table[x=NodesFailed,y expr=(\thisrow{VC1}-99.999)*1000]{figures/vm_availability_1000.txt};
+                \addplot table[x=NodesFailed,y expr=(\thisrow{VC3}-99.999)*1000]{figures/node_failures_1000.txt};
                 %\addlegendentry{$VC\,1250$ (estimated)}
                 %\addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
-                \addplot table[x=NodesFailed,y expr=(\thisrow{VC2}-99.999)*1000]{figures/vm_availability_1000.txt};
+                \addplot table[x=NodesFailed,y expr=(\thisrow{VCWC1}-99.999)*1000]{figures/node_failures_1000.txt};
                 %\addlegendentry{$VC\,2500000$ (worst-case)}
@@
       \caption{Availability of VM backup snapshots for VO and VC when failed machines vary
-from 1 to 10.  Non-PDS replication is fixed
-          at 3 and PDS replication is 4. 
+from 1 to 40.  Non-PDS replication is fixed
+at 3 and PDS replication is 6 \emph{THIS PLOT IS BEING REPLACED BY A TABLE} 
       }
@@
 		ylabel={VM Snapshot Availability (\%)},
-		extra y ticks={99.9}, %if important numbers are missing
+                xmin=0,
+                xmax=10,
+		%extra y ticks={99.9}, %if important numbers are missing
                 mark options=solid,
@@
 		]
-                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
-                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
-                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
-                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
-                \legend{$R_C=4$,$R_C=5$,$R_C=6$}%,$R_C=7$}
+                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
+                \legend{$R_C=4$,$R_C=5$,$R_C=6$, $R_C=9$}
 		\end{axis}
@@
   \caption{Theoretical Availability of VM backup snapshots as nodes fail in VC
- (Non-PDS replication fixed at 3, and average PDS block links set to 1250, 1000 node cluster)}
+ (Non-PDS replication fixed at 3, and average PDS block links set to 1250 for 100 node cluster)}
   \label{fig:pds-replication}
@@
             \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
-            \legend{VC MH( $\sigma=4\%$),
-                VC MH($\sigma=2\%$),
+            \legend{VC( $\sigma=4\%$),
+                VC($\sigma=2\%$),
                 %VC MH($\sigma=1\%$),
-                VC MH(No PDS),
+                VC(No PDS),
                 %VC($\sigma=4\%$),
-                VC($\sigma=2\%$),
+                VC(No MH\,$\sigma=2\%$),
                 %VC($\sigma=1\%$),
@@
 Deduplication efficiency is defined as the percent of duplicate chunks
-which are detected and deduplicated.
-The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
-is defined in Table~\ref{tab:symbol}. 
+which are detected and deduplicated. We also compare several PDS sizes chosen for VC
+(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
 %we allocate the space of distributed shared memory  to accommodate 2\%

### 2013-09-19 snapshot_system/fast14_evaluation.tex
update efficiency results

--- 2013-09-19 snapshot_system/fast14_evaluation.tex
@@
 Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
-Deduplication efficiency is defined as the percent of duplicate chunks
-which are detected and deduplicated.
+Our deduplication efficiency is defined as the percent of duplicate chunks
+which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
 The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
@@
 With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
-and  the deduplication efficiency can reach over 90\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
+and  the deduplication efficiency can reach over 96\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 97\%. 
 The loss of efficiency in VC is caused by the restriction of the total physical memory available
 in the cluster to support PDS index. 
+In the extreme case if we put all the fingerprint into PDS 
+index ($\sigma=100\%$) then VC will have 100\% efficiency.
 The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
-for global comparison.
-In all cases, VC provides similar or better deduplication efficiency than SRB.
+of duplicate detection.
+Our VC approach delivers slightly worse deduplication efficiency compare to SRB, which is totally acceptable
+because we are rewarded by architecture-wise benefits such as fault-tolerant and fast approximate deletion.
 
@@
 In general, our experiments show that
-dirty-bit detection at the segment level  can reduce the data size to about 23\% of original data, 
-which leads  about 77\% reduction.
-Local search within a segment can   further reduce the data size
-to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
+dirty-bit detection at the segment level can reduce the data size to about 24\% of original data, 
+which leads  about 76\% reduction.
+Similarity-guided local search can further reduce the data size
+to about 12\% of original size, namely it delivers additional 12\% reduction.
 The PDS-based cross-VM detection with $\sigma=2\% $
-can reduce the  size further to 8\% of original size, namely it 
-delivers additional 10.5\% reduction.
+can reduce the  size further to 5.6\% of original size, namely it 
+delivers additional 6.4\% reduction.
 

### 2013-09-19 snapshot_system/fast14_evaluation.tex

--- 2013-09-19 snapshot_system/fast14_evaluation.tex
@@
 Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
+% <<<<<<< HEAD
+% Our deduplication efficiency is defined as the percent of duplicate chunks
+% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
+% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
+% is defined in Table~\ref{tab:symbol}. 
+% =======
 Deduplication efficiency is defined as the percent of duplicate chunks
-which are detected and deduplicated. We also compare several PDS sizes chosen for VC
+which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
+ We also compare several PDS sizes chosen for VC
 (see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')

### 2013-09-19 snapshot_system/fast14_architecture.tex
modify

--- 2013-09-16 snapshot_system/fast14_architecture.tex
@@
 \label{sect:architecture}
-Our system runs on a cluster of Linux machines with Xen-based VMs.
-A distributed file system (DFS) manages  the physical disk storage and we use 
-an open source DFS called QFS~\cite{QFS}. 
+Our system runs on a cluster of Linux machines with Xen-based VMs and
+an open-source package for the distributed file system  called QFS~\cite{QFS} to 
+manages  the physical disk storage. 
 All data needed for VM services, such as virtual disk images used by runtime VMs,
@@
 3) an append store client to store  and access snapshot data,
-and 4)  a PDS client to support PDS index access.
+and 4)  a PDS client to support PDS metadata access.
 
@@
 After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
-[What happens with modification during snapshot backup stage.]
+For data modification during snapshot backup stage, a copy-on-write scheme is set so that backup
+still copies a frozen version while the modification can still carry on.
 
@@
 In snapshot and segment recipes, 
-the data structures  includes reference pointers to the actual data location to eliminate the need for additional indirection.
+the data structures  includes reference to the actual data location to eliminate the need for additional indirection.
 

### 2013-09-19 snapshot_system/fast14_deduplication.tex
modify

--- 2013-09-19 snapshot_system/fast14_deduplication.tex
@@
 \[
-\frac{N_1}{N_o}=  \frac{1-\sigma}{V_o}<1.
+\frac{N_1}{N_o} \approx  \frac{1-\sigma}{V_o}.
 \]
-Thus when there is a failure in file blocks with replication degree $r$
+
+Thus $N_1$ is much smaller than $N_o$. 
+When there is a failure in file blocks with replication degree $r$
 and there is no failure for PDS data with more replicas,   a VM in
-the VC approach has a lower chance to lose a snapshot than the VO approach because
-$N_1<N_o$. 
+the VC approach has a much lower chance to lose a snapshot than VO. 
 Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from

### 2013-09-19 snapshot_system/fast14_architecture.tex

@@
 \label{sect:architecture}
+
 Our system runs on a cluster of Linux machines with Xen-based VMs and

### 2013-09-19 snapshot_system/fast14_deduplication.tex
updates to paper

--- 2013-09-19 snapshot_system/fast14_deduplication.tex
@@
 		]
-                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
-                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
-                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
-                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
+                \addplot[blue,mark=none] table[x=VMs,y=N_O] {figures/vm_links_all.txt};
+                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
+                \addplot[red,dashdotted] table[x=VMs,y=N_1] {figures/vm_links_all.txt};
+                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N_2] {figures/vm_links_all.txt};
                 \legend{$N_o$, $N_1+N_2$, $N_1$, $N_2$};

### 2013-09-19 snapshot_system/fast14_architecture.tex
revise

@@
 After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
-For data modification during snapshot backup stage, a copy-on-write scheme is set so that backup
-still copies a frozen version while the modification can still carry on.
+For data modification during backup, a copy-on-write protection is set so that backup can continue to
+copy  a specific version while new changes are still recorded.
+%copies a frozen version while the modification can still carry on.
 
@@
 There is also a special store containing all PDS chunks shared among different VMs.
-As shown in Fig.\ref{fig:as_arch}, we explain the data structure of snapshot stores as follows.
+As shown in Figure~\ref{fig:as_arch}, we explain the data structure of snapshot stores as follows.
+\end{itemize}
+\begin{figure}[htbp]
+  \centering
+  \epsfig{file=images/sstore_arch, width=3in}
+  \caption{Data structure of a VM snapshot store.}
+  \label{fig:as_arch}
+\end{figure}
 
@@
 By limiting the size of a container, we can effectively control the length of each round of compaction.
-The compaction  routine can work on one container at a time and copy used data chunks to another container.
+The compaction  routine can work on one container at a time and move used data chunks to another container.
 
@@
 a set of data chunks and is the basic unit in data access and retrieval. 
-In writing a chunk during backup, the system accumulates data chunks and store the entire
+In writing a chunk during backup, the system accumulates data chunks and stores the entire
 group as a unit after a compression.
@@
 local chunk IDs are monotonically increasing.
-When a snapshot chunk is to be accessed, the recipe for the snapshot will point a data chunk
+When a snapshot chunk is to be accessed, the snapshot recipe contains a reference pointing to  a data chunk
 in the PDS store or in a non-PDS VM snapshot  store. 
@@
 
-\item The PDS chunks are a set of commonly used data and they are stored in one PDS file.
-Since the total file size is relatively small, and
-PDS data is re-calculated periodically, the PDS data file and its index are rebuilt completely. 
-Each reference to a PDS data chunk in the PDS index is the offset within the PDS file, and the chunk size.
+\item The PDS chunks are  stored in one PDS file. 
+Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
+There is an option to use the data structure similar to the non-PDS store. We opt to this simple format because
+PDS chunks have less spatial locality in data access and it is not so effective to group a large number of chunks
+as a compression and data fetch unit.
 
-\end{itemize}
+PDS data is re-calculated periodically, but 
+the total data size is small.  When
+a new PDS data  set is computed, in-memory PDS index is replaced, but 
+the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
+The old data is not removed because they can still be referenced by the existing snapshots. 
+A periodic cleanup is conducted  to remove unused PDS chunks (e.g. in every few months).
 
@@
 \begin{itemize}
-\item {\em Put(data)}. This places data chunk into the snapshot store and returns a reference to be stored in 
+\item {\em Append()}. For non-PDS data, this call places a chunk into 
+the snapshot store and returns a reference to be stored in 
 the recipe metadata of a snapshot. 
@@
 container index file.
-The writing of PDS data chunks is conducted periodically when there is a new PDS calculation.
-\item{\em Get(reference)}.
+
+For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
+\item{\em Get()}.
 The fetch operation for the PDS data chunk is straightforward since each reference contains 
-the offset and size within the PDS  underlying  file.
+the file offset and the size of a PDS chunk is available from a segment receipt.
 We also maintain a small data cache for the PDS data service to speedup common data fetching.
@@
 anticipate future sequential reads.
-\item {\em Delete(reference)}.
+\item {\em Delete()}.
 Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user
@@
 As a result, all data references stored 
-in upper level recipes are permanent and stable, and the data reading process
+in recipes are permanent and stable, and the data reading process
 is as efficient as before. Maintaining the stability of chunk IDs also ensures that recipes do not
-depend directly on physical storage locations.
+depend directly on physical storage locations and thus simplifies data migration.
 \end{itemize}
-
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=images/sstore_arch, width=3in}
-  \caption{Data structure of a VM snapshot store.}
-  \label{fig:as_arch}
-\end{figure}
 
@@
 In the case of Alibaba, snapshot backup is conducted automatically and there are 
-about 10 snapshot stored for every user. When there is
+about 10 snapshot stored for every VM customer. When there is
 a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
@@
 
-We seek a fast solution with low resource usage to delete snapshots.
-Our VM-centric snapshot storage design simplifies the deletion process since 
-we can focus on  unreferenced chunks within each VM.
-The PDS data chunks are commonly shared among all VMs and we do not consider them
-during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
+We seek a fast solution with low resource usage to delete snapshots and
+the VM-centric design simplifies the deletion process. 
+Since PDS is small and separated, we can focus on  unreferenced non-PDS chunks within each VM. 
+%The PDS data chunks are commonly shared among all VMs and we do not consider them
+%during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
 Another resource-saving strategy we propose is
@@
 Every time there is a new snapshot created,
-we compute a Bloom-filter with $z$ bits as the summary of reference pointers for all non-PDS chunks used 
+we compute a Bloom-filter with $z$ bits as the reference summary for all non-PDS chunks used 
 in this snapshot. Given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
@@
 This is done approximately and quickly by comparing the 
-reference pointers of deleted snapshot with
-the merged reference Bloom-filter summary of other live snapshots.
+reference of deleted chunks  with
+the merged Bloom-filter reference summary in other live snapshots.
 The merging of live snapshot Bloom-filter bits uses the logical OR operator 
@@
 
-If a chunk's reference pointer is not found in the merged summary vector, we are sure that
+If a chunk's reference is not found in the merged summary vector, we are sure that
 this chunk is not used by any live snapshots, thus it's safe delete it. 
@@
 Leakage repair is conducted periodically to fix the above approximation error.
-This procedure compares the live chunks for each VM with what are truly used through the VM snapshot metadata recipe.
-That requires a scanning of all chunks in a VM; however it is a VM-specific procedure and thus
-the cost is relatively small compared to the traditional mark-sweep procedure~\cite{Guo2011} which scans snapshot 
+This procedure compares the live chunks for each VM with what are truly used in the VM snapshot metadata recipe.
+That requires a scanning of all chunks in a VM. Since it is a VM-specific procedure 
+the space and time cost is relatively small compared to the traditional mark-sweep procedure~\cite{Guo2011} which scans snapshot 
 chunks from all VMs.
 For example,
-consider each reference pointer consumes 8 bytes plus  1 mark bit, a VM that has 40GB backup data with about
+consider each reference consumes 8 bytes plus  1 mark bit, a VM that has 40GB backup data with about
 10 million chunks will need less than 90MB of memory to complete a VM-specific mark-sweep process.
@@
 %{\bf Discussion}
-We now estimate the size of storage leakage and how often leak repair needs to be conducted,
-given  a VM which keeps $h$ snapshots in the backup storage, and it creates and deletes one snapshot
-everyday. Let $u$ be the total number of chunks brought by the initial backup, $\Delta u$ be the average
+We now estimate the size of storage leakage and how often leak repair needs to be conducted.
+Assume that  a VM keeps $h$ snapshots in the backup storage, creates and deletes one snapshot
+everyday. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
 number of additional unique chunks added from one snapshot to the next snapshot version. Then the total number of unique
@@
 Each Bloom filter vector has  $z$ bits for each snapshot and let $j$ be the number of hash functions used by the
-Bloom filter. The probablity that a particular bit is 0  in all $h$ summary vectors is  
-$(1- \frac{1}{z}) ^{j U}$. Notice that a chunk may appear multiple times in these summary vectors; however, this should not 
+Bloom filter.  Notice that a chunk may appear multiple times in these summary vectors; however, this should not 
 increase the probability of being a 0 bit in all $h$ summary vectors.
+Thus the probablity that a particular bit is 0  in all $h$ summary vectors is  
+$(1- \frac{1}{z}) ^{j U}$. 
 Then the misjudgment rate of being in use $\epsilon$ is: 
@@
 For each snapshot deletion, the number of chunks to be deleted is nearly identical to the number of
-newly add chunks $\Delta u$. 
+newly added chunks $\Delta u$. 
 Let $R$ be the total number of runs of approximate deletion between two consecutive 
-repairs. we estimate  the total leakage $L$ after $R$ runs as:
+repairs. We estimate  the total leakage $L$ after $R$ runs as:
 \[
-L = R \Delta u \epsilon
+L = R \Delta u \epsilon.
 \]
 
-When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we need to execute a leak repair:
+When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we derive the condition to execute a leak repair as:
 
@@
 \frac{L}{U} = \frac{R \Delta u \epsilon}{u+(h-1)\Delta u } > \tau 
-\Longrightarrow R > \frac{\tau}{\epsilon}\times\frac{u + (h-1)\Delta u}{\Delta u}
+\Longrightarrow R > \frac{\tau}{\epsilon}\times\frac{u + (h-1)\Delta u}{\Delta u}.
 \end{equation}
@@
 When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
-only one full leak repair for one VM scheduled for every 12 days. Each repairs uses at most  90MB memory on average
+only one full leak repair for one physical machine scheduled for every 12 days. 
+Each repairs uses at most  90MB memory on average
 as discussed earlier and takes a short period of time.

### 2013-09-19 snapshot_system/fast14_architecture.tex
revise

@@
 As shown in Figure~\ref{fig:as_arch}, we explain the data structure of snapshot stores as follows.
-\end{itemize}
 \begin{figure}[htbp]
@@
 A periodic cleanup is conducted  to remove unused PDS chunks (e.g. in every few months). 
+\end{itemize}
 
@@
 If a chunk's reference is not found in the merged summary vector, we are sure that
-this chunk is not used by any live snapshots, thus it's safe delete it. 
+this chunk is not used by any live snapshots, thus can be deleted safely.
 However, among all the chunks to be deleted, 

### 2013-09-20 snapshot_system/fast14_architecture.tex
revise

@@
 Our system runs on a cluster of Linux machines with Xen-based VMs and
-an open-source package for the distributed file system  called QFS~\cite{QFS} to 
-manages  the physical disk storage. 
+an open-source package for the distributed file system  called QFS~\cite{QFS}. 
+%to %manage  the physical disk storage. 
 All data needed for VM services, such as virtual disk images used by runtime VMs,
@@
 By limiting the size of a container, we can effectively control the length of each round of compaction.
-The compaction  routine can work on one container at a time and move used data chunks to another container.
+The compaction  routine can work on one container at a time and move the used data chunks to another container.
 
@@
 Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
-There is an option to use the data structure similar to the non-PDS store. We opt to this simple format because
+There is an option to use the data structure similar to the non-PDS store. We opt for this simple format because
 PDS chunks have less spatial locality in data access and it is not so effective to group a large number of chunks
@@
 \begin{itemize}
-\item {\em Append()}. For non-PDS data, this call places a chunk into 
+\item {\em Append()}. 
+For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
+For non-PDS data, this call places a chunk into 
 the snapshot store and returns a reference to be stored in 
@@
 
-For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
 \item{\em Get()}.
@@
 is as efficient as before. Maintaining the stability of chunk IDs also ensures that recipes do not
-depend directly on physical storage locations and thus simplifies data migration.
+depend directly on physical storage locations, which simplifies data migration.
 \end{itemize}
@@
 to efficiently identify unused chunks.
-
 The algorithm contains three aspects.
@@
 Leakage repair is conducted periodically to fix the above approximation error.
-This procedure compares the live chunks for each VM with what are truly used in the VM snapshot metadata recipe.
+This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipe.
 That requires a scanning of all chunks in a VM. Since it is a VM-specific procedure 
@@
 $(1- \frac{1}{z}) ^{j U}$. 
-Then the misjudgment rate of being in use $\epsilon$ is: 
+Then the misjudgment rate of being in use  is: 
 \begin{equation}

### 2013-09-20 snapshot_system/fast14_deduplication.tex
revise

@@
 
-\subsection{Key VM-centric  Strategies}
+\subsection{Key VC  Strategies}
 \label{sect:vc-strategies}
@@
 parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
-which contain chunk fingerpints which can  potentially be duplicates.
-To limit the search scope, we set a limit on the the number of  similar segments to be  searched. 
+which contain chunk fingerpints to be compared.
+To control the time cost of search, we set a limit on the the number of  similar segments to be  fetched. 
 % Then,
@@
 
-\item \textbf{Cross-VM deduplication with popular chunks and replication support}
+\item \textbf{Cross-VM deduplication with popular chunks and replication support.}
 This step accomplishes the standard global fingerprint comparison as conducted
@@
 $N_o$ & the average number  of file system blocks  in a VM for VO\\
+\hline
+A(r) & the availability of a file system block with replication degree $r$\\
 \hline
@@
 A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of VM snapshot blocks.
-
 We use file system blocks rather than a deduplication
@@
 V *p*N_1 *s  \approx c_u (1-\sigma)\; \mbox{ and } \; 
-V *p*N_2 *s  \approx c_u \sigma *V_c
+V *p*N_2 *s  \approx c_u \sigma V_c.
 \]
-For the VO approach, 
+
 For VO, each VM has an average of $N_o$ file system blocks
@@
 one VM.
-From data, 
-we have observed that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
-This is likely because the PDS FSBs tightly pack data used by many VMs, 
-which decreases the overall number of FSBs required to backup a VM.
-Also if  the backup for multiple VMs were conducted concurrently, there would be more
+Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
+Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
+%From data, 
+%we have observed that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
+%This is likely because the PDS FSBs tightly pack data used by many VMs, 
+%which decreases the overall number of FSBs required to backup a VM.
+Noted that  if  the backup for multiple VMs were conducted concurrently, there would be more
 VMs shared  by each file block on average in VO. 
@@
 \end{equation}
-Figure~\ref{fig:fsb-availability} illustrates that the availability of an individual file system block
-with different replication degree. This demonstrates inequality 
+Figure~\ref{fig:fsb-availability} illustrates the $A(r)$ values with
+%that the availability of an individual file system block
+with different replication degrees. This demonstrates inequality 
 % $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
-$A(r) < A(r_c)$
-.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
+$A(r) < A(r_c)$.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
 these two conditions support that VC has a  higher availability. 

### 2013-09-20 snapshot_system/fast14_evaluation.tex
updates to paper
paper revisions

@@
 \subsection{Impact on Fault Tolerance}
-Figure~\ref{fig:vm-availability} shows the availability of VM snapshots when 
-there are up to 25 storage nodes failed in a 1000-node cluster. 
-Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
-$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
-The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
+Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
+as storage nodes fail. We assume a random distirbution of 64MB filesystem
+blocks (FSBs). where FSBs are not randomly distributed availability might
+be improved by limiting the number of storage nodes a particualr VM depends
+on but we take the conservative approach. We compare VO, the expected case for
+VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
+based on measured values in our dataset.
 To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
 count the number of dependencies from a file system block to VM.
-In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
+In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
 case for VO approach. 
-Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
-For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
-while VC with 99.9\% loses snapshots of 2.5 VMs.
-The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
-and packs  data blocks for one VM as much as possible.  The extra replication
-for PDS blocks also significantly increases the snapshot availability even when
-a PDS file block is shared by every VM.
+Our results show that even the worst case for VC has a higher availability than VO.
+By having extra replicas for the PDS data, we reduce the failure rate of PDS
+FSBs enough that the failure rate for the VM approaches the failure rate of the
+Non-PDS blocks. This minimizes the drop in availability between the expected
+and worst case for VC.
 
-Figure~\ref{fig:pds-replication}
-shows the snapshot availability when increasing the replication degree for PDS blocks. 
-It can be seen that increasing the replication of 
-the PDS blocks can have a good impact on the overall availability of the VM backups. 
-PDS with more replication  makes up a small percent of the
-stored data; however, the benefit to the snapshot availability is significant.
+Our VM-centric approach shows significant improvements
+in VM availability.
+For example, with 5/100 machines failed, VO with 93.3\% availability would lose data in 169 VMs 
+while VC with 99.9\% loses data for 2 VMs.
+The key reason is that for most data in VC ($1-\sigma$), only a single
+VM can be affected by the loss of a single FSB, because our VM-centric approach
+localizes deduplication.  Although the loss of a PDS block affects many VMs,
+by increasing replication for those blocks we minimize the affect on VM
+availability.
+
+One of the advantages of VC is that there is a division between
+popular and non-popular data to facilitate improved reliability. An important
+consideration then is how much to increase PDS data replication. The additional
+cost is relatively small, but based on our model we evaulated several
+difference PDS replication factors (see Figure~\ref{fig:pds-replication}),
+and found that beyond 6 replicas there is minimal improvement in data reliability.
+This is because, as described before, the availability of the VM approaches the
+availiability of the Non-PDS data as the failure rate of PDS data gets very small.
+In the graph, the lines for $r_c=6$ and $r_c=9$ overlap because of this effect.
 
@@
 \end{figure}
+\begin{table}
+    \footnotesize
+    \tabcolsep=0.11cm
+    \begin{tabular}{|l|l|l|l|l|l|l|}
+        \hline
+        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{VM Availability} \\
+                                    %\cline{2-7}
+                                    & \multicolumn{3}{c|}{$p=100$} & \multicolumn{3}{c|}{$p=1000$} \\
+                                    %\cline{2-7}
+                                    & VO & VC & VC(WC) & VO & VC & VC(WC) \\
+        \hline
+        3 & 99.304 & 99.891 & 99.891 & 99.999 & 99.999 & 99.999\\
+        5 & 93.256 & 98.919 & 98.919 & 99.993 & 99.999 & 99.999\\
+        10 & 43.251 & 87.707 & 87.638 & 99.919 & 99.987 & 99.987\\
+        20 & 0.034 & 24.953 & 21.571 & 99.228 & 99.879 & 99.879\\
+        \hline
+    \end{tabular}
+    \caption{Availability of VM backups for VO and VC models. VC is shown
+    for the expected and worst case (WC) values for $V_c$}
+    \label{tab:vm-availability}
+\end{table}
 
@@
 of duplicate detection.
-Our VC approach delivers slightly worse deduplication efficiency compare to SRB, which is totally acceptable
-because we are rewarded by architecture-wise benefits such as fault-tolerant and fast approximate deletion.
+SRB provides slightly better deduplication efficiency than our VC approach, which we accept
+because we are rewarded by architecture-wise benefits such as fault-tolerance and fast approximate deletion.
 
-This result shows VC can remove  a competitive amount of duplicates.
+Though not our primary goal, this result does show that VC can remove a competitive amount of duplicates.
 In general, our experiments show that
@@
 delivers additional 6.4\% reduction.
+
+Figure~\ref{fig:exbin-efficiency-graph2} also shows the benefits of our minhash
+similar segment search in the parent snapshot. Without this, when an entire
+segment is moved to another location on disk (e.g. when a file is rewritten
+rather than modified in place), searching only the segment in the same location
+in the parent will miss the deduplication opportunity. We have found that in
+approximately 1/3 of the VMs in our dataset this movement happens frequently,
+so the similarity search becomes important for those VMs.
 

### 2013-09-20 snapshot_system/fast14_evaluation.tex
revise

--- 2013-09-19 snapshot_system/fast14_evaluation.tex
@@
 Our evaluation objective is to
-study the benefit in fault tolerance and   deduplication efficiency of the VC approach and compare it
+study the benefit in fault tolerance and   deduplication efficiency of VC and compare it
 with an alternative VO design. We also and assess backup throughput and  resource usage for a large number of VMs.
 
-We will compare our VC approach with
-a VO approach  using stateless routing with binning (SRB) 
-based on~\cite{Dong2011,extreme_binning09}
-SRB executes a distributed deduplication by routing a data chunk to a machine~\cite{Dong2011}
+We will compare VC with a VO approach  using stateless routing with binning (SRB) 
+based on~\cite{Dong2011,extreme_binning09}.
+SRB executes a distributed deduplication by routing a data chunk to one of cluster machines~\cite{Dong2011}
 using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
-a machine, this chunk is compared with the fingerprint index of this machine locally.
+a machine, this chunk is compared with the fingerprint index within this machine locally.
 
@@
 Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
-The backup of VM snapshots is completed within a few  hours every night.
+The backup of VM snapshots is required to complete within few  hours every night.
 Based on our study of production  data,  each VM has about 40GB of storage  data  on average
 including OS and user data disk.
-All data are divided into 2 MB fix-sized segments and each segment is divided into 
-variable-sized content chunks ~\cite{similar94,rabin81} with an average size of 4KB.
-The signature for variable-sized blocks is computed using their SHA-1 hash. 
-Popularity of data blocks are collected through global counting and 
-and top popular ones ($\delta=1-2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.
+%All data are divided into 2 MB fix-sized segments and 
+The signature for variable-sized blocks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
+%Each segment is divided into 
+%variable-sized content chunks with an average size of 4KB.
+%Popularity of data blocks are collected through global counting and 
+%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.
 
@@
 Figure~\ref{fig:vm-availability} shows the availability of VM snapshots when 
-there are up to 25 storage nodes failed in a 1000-node cluster. 
-Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
-$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
-The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
-To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
-count the number of dependencies from a file system block to VM.
-In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
-case for VO approach. 
+there are up to 25 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
+We show three snapshot  availability curves as the number of machines failed increases.
+%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
+Curve ``VC(worst-case)" represents the situation that each PDS file system block is shared by all VMs.
+%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
+%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
+%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
+%count the number of dependencies from a file system block to VM.
+%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
+%case for VO approach. 
 Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
@@
 \end{figure}
+
+%\begin{table}
+%    \begin{tabular}{|l|l|l|l|l|l|l|}
+%        \multirow{2}{c}{Nodes Failed & \multicolumn{2}{c}{p=100} & \multicolumn{2}{c}{p=1000} \\
+%        1 & ~ & ~ & ~\\
+%        5 & ~ & ~ & ~\\
+%        10 & ~ & ~ & ~\\
+%        20 & ~ & ~ & ~\\
+%    \end{tabular}
+%    \label{tab:vm-availability}
+%\end{table}
 

### 2013-09-20 snapshot_system/fast14_evaluation.tex

--- 2013-09-20 snapshot_system/fast14_evaluation.tex
@@
 Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
-The backup of VM snapshots is completed within a few  hours every night.
+The backup of VM snapshots is required to complete within few  hours every night.
 Based on our study of production  data,  each VM has about 40GB of storage  data  on average
 including OS and user data disk.
-All data are divided into 2 MB fix-sized segments and each segment is divided into 
-variable-sized content chunks ~\cite{similar94,rabin81} with an average size of 4KB.
-The signature for variable-sized blocks is computed using their SHA-1 hash. 
-Popularity of data blocks are collected through global counting and 
-and top popular ones ($\delta=1-2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.
+%All data are divided into 2 MB fix-sized segments and 
+The signature for variable-sized blocks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
+%Each segment is divided into 
+%variable-sized content chunks with an average size of 4KB.
+%Popularity of data blocks are collected through global counting and 
+%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.
 
 \subsection{Impact on Fault Tolerance}
-Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
-as storage nodes fail. We assume a random distirbution of 64MB filesystem
-blocks (FSBs). where FSBs are not randomly distributed availability might
-be improved by limiting the number of storage nodes a particualr VM depends
-on but we take the conservative approach. We compare VO, the expected case for
-VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
-based on measured values in our dataset.
-To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
-count the number of dependencies from a file system block to VM.
-In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
-case for VO approach. 
+
+Figure~\ref{fig:vm-availability} shows the availability of VM snapshots when 
+there are up to 25 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
+We show three snapshot  availability curves as the number of machines failed increases.
+%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
+Curve ``VC(worst-case)" represents the situation that each PDS file system block is shared by all VMs.
+%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
+%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
+%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
+%count the number of dependencies from a file system block to VM.
+%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
+%case for VO approach. 
+%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
+%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
+%while VC with 99.9\% loses snapshots of 2.5 VMs.
+%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
+%and packs  data blocks for one VM as much as possible.  The extra replication
+%for PDS blocks also significantly increases the snapshot availability even when
+%a PDS file block is shared by every VM.
+%=======
+%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
+%as storage nodes fail. 
+%We assume a random distirbution of 64MB filesystem
+%blocks (FSBs). where FSBs are not randomly distributed availability might
+%be improved by limiting the number of storage nodes a particualr VM depends
+%on but we take the conservative approach. We compare VO, the expected case for
+%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
+%based on measured values in our dataset.
+%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
+%count the number of dependencies from a file system block to VM.
+%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
+%case for VO approach. 
 Our results show that even the worst case for VC has a higher availability than VO.

### 2013-09-20 snapshot_system/fast14_conclusion.tex
revised evaluation

@@
 The design places a special consideration for low-resource usages as a collocated cloud service.
-Evaluation using  VM backup data shows that
-our solution can accomplish 92\% of what complete global
+Evaluation using  VM backup data shows that VC strikes a tradeoff and 
+can accomplish close to 97\% of what complete global
 deduplication can do while the availability of snapshots increases substantially with this VM-centric

### 2013-09-20 snapshot_system/fast14_evaluation.tex
revised evaluation

@@
 
-Figure~\ref{fig:vm-availability} shows the availability of VM snapshots when 
+ Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
 there are up to 25 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
@@
 %based on measured values in our dataset.
-%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
-%count the number of dependencies from a file system block to VM.
+To obtain VM sharing of file blocs, we perform perfect deduplication over 105 VMs, 
+append unique chunks to a DFS file and
+count the number of dependencies from a file system block to VM.
 %In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
@@
 Our results show that even the worst case for VC has a higher availability than VO.
-By having extra replicas for the PDS data, we reduce the failure rate of PDS
-FSBs enough that the failure rate for the VM approaches the failure rate of the
-Non-PDS blocks. This minimizes the drop in availability between the expected
-and worst case for VC.
-
-Our VM-centric approach shows significant improvements
-in VM availability.
+%Our VM-centric approach shows significant improvements
+%in VM availability.
 For example, with 5/100 machines failed, VO with 93.3\% availability would lose data in 169 VMs 
 while VC with 99.9\% loses data for 2 VMs.
-The key reason is that for most data in VC ($1-\sigma$), only a single
-VM can be affected by the loss of a single FSB, because our VM-centric approach
-localizes deduplication.  Although the loss of a PDS block affects many VMs,
-by increasing replication for those blocks we minimize the affect on VM
-availability.
+The key reason is that for most data in VC, only a single
+VM can be affected by the loss of a single FSB.
+% because our VM-centric approach
+%localizes deduplication.
 
-One of the advantages of VC is that there is a division between
-popular and non-popular data to facilitate improved reliability. An important
-consideration then is how much to increase PDS data replication. The additional
-cost is relatively small, but based on our model we evaulated several
-difference PDS replication factors (see Figure~\ref{fig:pds-replication}),
-and found that beyond 6 replicas there is minimal improvement in data reliability.
-This is because, as described before, the availability of the VM approaches the
-availiability of the Non-PDS data as the failure rate of PDS data gets very small.
-In the graph, the lines for $r_c=6$ and $r_c=9$ overlap because of this effect.
+Although the loss of a PDS block affects many VMs,
+by increasing replication for those blocks we minimize the affect on VM availability.
+%By having extra replicas for the PDS data, we reduce the failure rate of PDS
+%FSBs enough that the failure rate for the VM approaches the failure rate of the
+%Non-PDS blocks. This minimizes the drop in availability between the expected
+%and worst case for VC.
+%
+%One of the advantages of VC is that there is a division between
+%popular and non-popular data to facilitate improved reliability. 
+Figure~\ref{fig:pds-replication}) shows
+the impact of  to increasing PDS data replication. 
+While the impact on replication storage cost is small, 
+the replication degree 6  has a significant improvement over 4, but  the availability is about
+the same for $r_c=6$ and $r_c=9$.
 
+%This is because, as described before, the availability of the VM approaches the
+%availiability of the Non-PDS data as the failure rate of PDS data gets very small.
+
+\comments{
 \begin{figure}[ht]
@@
     \pgfplotslegendfromname{legend:vm-availability}
-      \caption{Availability of VM backup snapshots for VO and VC when failed machines vary
+      \caption{Availability of VM snapshots for VO and VC when failed machines vary
 from 1 to 40.  Non-PDS replication is fixed
@@
 \end{figure}
+}
 \begin{table}
@@
         \hline
-        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{VM Availability} \\
+        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{Snapshot Availability} \\
                                     %\cline{2-7}
@@
     \end{tabular}
-    \caption{Availability of VM backups for VO and VC models. VC is shown
-    for the expected and worst case (WC) values for $V_c$}
+    \caption{Availability of VM snapshots for VO and VC. VC(WC) stands for the case that a 
+PDS file block is shared by all VMs.}
     \label{tab:vm-availability}
@@
 	\end{tikzpicture}
-  \caption{Theoretical Availability of VM backup snapshots as nodes fail in VC
- (Non-PDS replication fixed at 3, and average PDS block links set to 1250 for 100 node cluster)}
+  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
   \label{fig:pds-replication}
@@
 which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
- We also compare several PDS sizes chosen for VC
-(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
+ We also compare several PDS sizes chosen for VC.
+%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
 %we allocate the space of distributed shared memory  to accommodate 2\%
 %of data chunks shared among VMs, as defined in 
-With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
-and  the deduplication efficiency can reach over 96\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 97\%. 
-The loss of efficiency in VC is caused by the restriction of the total physical memory available
-in the cluster to support PDS index. 
-In the extreme case if we put all the fingerprint into PDS 
-index ($\sigma=100\%$) then VC will have 100\% efficiency.
-The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
-of duplicate detection.
-SRB provides slightly better deduplication efficiency than our VC approach, which we accept
-because we are rewarded by architecture-wise benefits such as fault-tolerance and fast approximate deletion.
+With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
+and  the deduplication efficiency can reach over 96.??\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 97.??\% while space consumption increases to 200MB per machine. 
+The loss of efficiency in VC is caused by the restriction of the physical memory available
+in the cluster to support fast in-memory PDS index lookup. 
+%In the extreme case if we put all the fingerprint into PDS 
+%index ($\sigma=100\%$) then VC will have 100\% efficiency.
+SRB can deliver up to 97.6??\% deduplication efficiency which is slightly better than VC.
+Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
+with a competitive deduplication efficiency.
+%its loss of efficiency is caused by the routing of data chunks which restricts the search scope
+%of duplicate detection.
+%SRB provides slightly better deduplication efficiency than our VC approach, which we accept
+%because we are rewarded by architecture-wise benefits such as fault-tolerance and fast 
+%Though not our primary goal, this result does show that VC can remove a competitive amount of duplicates.
 
-Though not our primary goal, this result does show that VC can remove a competitive amount of duplicates.
+Figure~\ref{fig:exbin-efficiency-graph2} also shows the effectiveness of VC without local similarity-based search.
+Without this, when an entire
+segment is moved to another location on disk (e.g. when a file is rewritten
+rather than modified in place), searching only the segment in the same location
+in the parent will miss the deduplication opportunity. We have found that in
+approximately 1/3 of the VMs in our dataset this movement happens frequently,
+so the similarity search becomes important for those VMs.
 In general, our experiments show that
@@
 
-Figure~\ref{fig:exbin-efficiency-graph2} also shows the benefits of our minhash
-similar segment search in the parent snapshot. Without this, when an entire
-segment is moved to another location on disk (e.g. when a file is rewritten
-rather than modified in place), searching only the segment in the same location
-in the parent will miss the deduplication opportunity. We have found that in
-approximately 1/3 of the VMs in our dataset this movement happens frequently,
-so the similarity search becomes important for those VMs.
+%Figure~\ref{fig:exbin-efficiency-graph2} also shows the benefits of our minhash
+%similar segment search in the parent snapshot.
 
 \subsection{Resource Usage and Processing Time}
+
+\comments{
 \begin{table}
@@
 \end{table}
+}
 
-{\bf Storage cost of replication.} Table ~\ref{tab:replication_cost} shows the total storage space required by 
-VC as the PDS replication degree changes. The increase in storage cost is minimal because the PDS makes up a 
-small percent of the total storage space, while increasing replication degree has a  more significant benefit for
-availability as shown in Figure~\ref{fig:pds-replication}.
+{\bf Storage cost of replication.} 
+%Table ~\ref{tab:replication_cost} shows the total storage space required by 
+%VC as the PDS replication degree changes while non-PDS replication degree is fixed as 3. 
+The total storage  for all VM snapshots in each physical machine takes about 3.065TB on aveage when
+the replication degree of both PDS and non-PDS data is 3. 
+Allocating  one extra  copy for PDS data only adds  7GB in total per machine.
+Thus PDS replication degree 6 only adds the total space by 0.685\% while PDS replication degree 9 adds 1.37\% 
+space overhead, which is still small.
+%The increase in storage cost is minimal because the PDS makes up a 
+%small percent of the total storage space, while increasing replication degree has a  more significant benefit for
+%availability as shown in Figure~\ref{fig:pds-replication}.
 
 \begin{table}
-    \begin{tabular}{|c|c|c|c|c|}
+    \begin{tabular}{|c|c|c|c|c|c|}
     \hline
-    Tasks & CPU & Mem (MB) & Write (MB/s) & Time (hrs) \\ \hline
-    1     & 19\% & 18.1 & 8.37 & 1.314\\ \hline
-    2     & 35\% & 31.8 & 8.97 & 1.226\\ \hline
-    4     & 63\% & 54.1 & 9.33 & 1.179\\ \hline
-    6     & 77\% & 71.9 & 9.46 & 1.162\\ \hline
+    Tasks & CPU & Mem &Read &  Write  & Time  \\ \hline
+    & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline
+%    1     & 19\% & 118.1 & 50MB/s 8.37 & 1.314\\ \hline
+    1     & 19\% & 118 & 50 & 8.4 & 1.31\\ \hline
+%    2     & 35\% & 131.8 & 9.0 & 1.226\\ \hline
+    2     & 35\% & 132 &50  & 9.0 & 1.23\\ \hline
+    %4     & 63\% & 154.1 & 9.3 & 1.179\\ \hline
+    4     & 63\% & 154&50   & 9.3 & 1.18\\ \hline
+%    6     & 77\% & 171.9 & 9.46 & 1.162\\ \hline
 %    8     & 82\% & 90.5 & 89.2 & \\ \hline
@@
     \end{tabular}
-\caption{Resource usage of concurrent backup tasks in each node}
+\caption{Resource usage of concurrent backup tasks at each machine}
 \label{tab:resource_usage}
@@
 We have further studied the memory and disk bandwidth usage 
-when running concurrent VM snapshot backup on each node. 
-Table ~\ref{tab:resource_usage} gives the CPU, memory and disk write workload of backing up multiple VMs 
-at the same time on each physical machine. 
+when running concurrent VM snapshot backup on each machine with $\delta=2\%$. 
+Table ~\ref{tab:resource_usage} gives the CPU, memory and disk read/write  workload when
+running 1 or multiple  backing tasks at the same time on each physical machine. 
+Disk read is controled as 50MB/s bandwidth usage so that other cloud services are not impacted a lot.
 % [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
 % the cloud infrastructure services and are shared among many applications.]
-We see our hybrid deduplication scheme only occupies a small amount of system resources. 
-The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
-memory during duplicate detection.
+The memory usage includes 100MB of PDS index and other space cost for executing deduplication tasks such as 
+receipt metadata and cache. 
+%We see our hybrid deduplication scheme only occupies a small amount of system resources. 
+%The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
+%memory during duplicate detection.
 
-Based on the observed performance numbers, even with a single backup task per node and enforcing the disk read speed to
-50 MB/s,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
-at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.
+Table ~\ref{tab:resource_usage} shows that  a single backup task per node can complete the backup of the entire
+VM cluster in about 1.58 hours. Since there are about 25 VMs per machine, we could execute
+more tasks in parallel at each machine. But adding more bakcup concurrency does not shorten the overall time
+a lot because of the controlled  disk read time.
+%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
+%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.
 
@@
   \epsfig{file=figures/vc_srb_combined, width=3in}
-  \caption{Time to backup a dirty VM segment under SRB and VC appraoches}
+  \caption{Average time to backup a dirty VM segment under SRB and VC}
   \label{fig:vc_srb_combined}

### 2013-09-21 snapshot_system/fast14_deduplication.tex
paper revisions
revised evaluation
revised evaluation etc

@@
 
-\subsection{Storage Space and Impact on Fault Tolerance}
+\subsection{Storage Space and Impact on Fault Isolation}
 
@@
 \[
-\sigma \frac{r_c}{r} + 1-\sigma
+\sigma \frac{r_c}{r} + 1-\sigma.
 \]
@@
 the VC approach has a much lower chance to lose a snapshot than VO. 
-Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
-our test dataset.
-%which shows how many VMs the failure of a single block can affect. 
-For VC, we only show
-the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
-one VM.
-Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
+%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
+%our test dataset.
+%For VC, we only show
+%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
+%one VM.
+%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
 Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
-%From data, 
-%we have observed that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
-%This is likely because the PDS FSBs tightly pack data used by many VMs, 
-%which decreases the overall number of FSBs required to backup a VM.
+From data, we have observed that $N_1 +N_2 < N_o$ in practice. 
+This is likely because the PDS FSBs tightly pack data used by many VMs, 
+which decreases the overall number of FSBs required to backup a VM.
 Noted that  if  the backup for multiple VMs were conducted concurrently, there would be more
 VMs shared  by each file block on average in VO.
+
 %Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.
 
+\comments{
 \begin{figure}[htbp]
@@
 \end{equation}
-Figure~\ref{fig:fsb-availability} illustrates the $A(r)$ values with
+Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
 %that the availability of an individual file system block
@@
 \end{figure}
+}
+
+\begin{table}
+    \footnotesize
+    \tabcolsep=0.11cm
+    \begin{tabular}{|l|l|l|l|}
+        \hline
+        \multirow{2}{*}{Failures}   & \multicolumn{3}{c|}{FSB Availability} \\
+                                    %\cline{2-4}
+                                    & $R_c=3$ & $R_c=6$ & $R_c=9$ \\
+        \hline
+        3 & 99.999 & 100 & 100\\
+        5 & 99.994 & 100 & 100\\
+        10 & 99.925 & 99.999 & 99.999\\
+        20 & 99.295 & 99.997 & 99.999 \\
+        \hline
+    \end{tabular}
+    \caption{Availability of individual 64MB Filesystem blocks (FSBs) as storage
+    nodes fail in a 100 node cluster.}
+    \label{tab:fsb-availability}
+\end{table}

### 2013-09-21 snapshot_system/fast14_evaluation.tex
figure changes
revised evaluation etc

@@
 
-\subsection{Impact on Fault Tolerance}
+\subsection{Impact on Fault Isolation}
 
@@
 %Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
-Curve ``VC(worst-case)" represents the situation that each PDS file system block is shared by all VMs.
+Curve ``VC(WC)" represents a worst-case  situation that each PDS file system block is shared by all VMs.
 %$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
@@
     \end{tabular}
-    \caption{Availability of VM snapshots for VO and VC. VC(WC) stands for the case that a 
-PDS file block is shared by all VMs.}
+    \caption{Availability of VM snapshots for VO and VC.}
     \label{tab:vm-availability}
@@
                 xmin=0,
-                xmax=10,
+                xmax=20,
 		%extra y ticks={99.9}, %if important numbers are missing
@@
 %VC as the PDS replication degree changes while non-PDS replication degree is fixed as 3. 
-The total storage  for all VM snapshots in each physical machine takes about 3.065TB on aveage when
+The total storage  for all VM snapshots in each physical machine takes about 3.065TB on average when
 the replication degree of both PDS and non-PDS data is 3. 
@@
 when running concurrent VM snapshot backup on each machine with $\delta=2\%$. 
-Table ~\ref{tab:resource_usage} gives the CPU, memory and disk read/write  workload when
-running 1 or multiple  backing tasks at the same time on each physical machine. 
-Disk read is controled as 50MB/s bandwidth usage so that other cloud services are not impacted a lot.
+Table ~\ref{tab:resource_usage} gives the resource usage  when
+running 1 or multiple  VM backup tasks at the same time on each physical machine. 
+CPU column is the percentage of a core usage. 
+The memory usage includes 100MB of PDS index and other space cost for executing deduplication tasks such as 
+receipt metadata and cache. 
+Disk read is controlled as 50MB/s bandwidth usage so that other cloud services are not impacted a lot.
+Disk write is the write usage of QFS and notice that each QFS write leads writes in multiple machines due to
+data replication.     
 % [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
 % the cloud infrastructure services and are shared among many applications.]
-The memory usage includes 100MB of PDS index and other space cost for executing deduplication tasks such as 
-receipt metadata and cache. 
 %We see our hybrid deduplication scheme only occupies a small amount of system resources. 
@@
 VM cluster in about 1.58 hours. Since there are about 25 VMs per machine, we could execute
-more tasks in parallel at each machine. But adding more bakcup concurrency does not shorten the overall time
+more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
 a lot because of the controlled  disk read time.
@@
 the  average  processing  time of  a VM segment under VC and SRB. 
+VC uses $\sigma=2\%$ and $4\%$.
 It has a breakdown of time for reading data, updating the metadata, network latency to visit
 a remote machine, and index access for fingerprint comparison.
+The change of $\sigma$ does not significantly affect the overall backup speed as
+PDS lookup takes only a small amount of time.
 SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
@@
 Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.
+%Figure~\ref{fig:vc_srb_combined} also reports the average backup time for a VM in VC when
+%varying the PDS size.  It lists the time distribution for data reading,
+%similarity-guided local search, cross-VM PDS lookup, and non-duplicate data writing. 
+%While data reading dominates the backup process, PDS lookup spends about a similar amount
+%of time as local search.
 
@@
 % \end{figure}
-
-Figure~\ref{fig:vc_srb_combined} also reports the average backup time for a VM in VC when
-varying the PDS size.  It lists the time distribution for data reading,
-similarity-guided local search, cross-VM PDS lookup, and non-duplicate data writing. 
-While data reading dominates the backup process, PDS lookup spends about a similar amount
-of time as local search.
-The change of $\sigma$ does not significantly affect the overall backup speed as
-PDS lookup takes only a small amount of time.
 
@@
     \end{tabular}
-\caption{Backup throughput under different concurrency}
+\caption{Throughput of software layers under different concurrency}
 \label{tab:throughput}
 \end{table*}
-{\bf Throughput.}
-Table~\ref{tab:throughput} shows the  backup throughput per each machine when all machine nodes 
-handle  several VMs in parallel.
-To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
-increase number of VMs to 12 to saturate our system capability. We observed 
-the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
-which is far beyond our QFS file system capability. The reason behind it is our efficient
-deduplication architecture and compression which greatly reduce the amount of data that needs to be written to
-the file system. The main bottleneck here is that our QFS installation only
-manages one disk per node, which prevents it from fully utilizing the the
-benefits of parallel disk access. We expect our architecture can
-perform even better in production clusters, which often have ten or more disks on each node.
+{\bf Throughput of software layers.}
+Table~\ref{tab:throughput} shows the  average throughput of software layer
+when I/O is throttled under 50MB/second and when there is no restriction.
+%machine when all machine nodes execute one or multiple MV backup tasks.
+``Raw'' column is the throughput  of the backup service  per machine.
+``Snapshot store" is the  write throughput of the snapshot store layer and the gap between this
+column and  ``Raw" column is caused by significant data reduction by dirty bit and duplication
+detection. Only non-duplicate chunks trigger a snapshot store write.
+``QFS'' column is the write request traffic to the underlying file system after compression.
+The underlying disk storage traffic will be three times or more because of replication.
+The result shows that the backup service can deliver up to 5.46GB/second without I/O restriction
+per machine with 6 concurrent backup tasks.
+With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine under 1.31 hours.
+
+%To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
+%increase number of VMs to 12 to saturate our system capability. 
+%We observed 
+%the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
+%which is far beyond our QFS file system capability. The reason behind it is our efficient
+%deduplication architecture and compression which greatly reduce the amount of data that needs to be written to
+%the file system. The main bottleneck here is that our QFS installation only
+%manages one disk per node, which prevents it from fully utilizing the the
+%benefits of parallel disk access. We expect our architecture can
+%perform even better in production clusters, which often have ten or more disks on each node.
 
@@
 
-% \subsection{Effectiveness of Approximate Deletion}
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=3in]{figures/leakage}
-%     \caption{Accumulated storage leakage by approximate snapshot deletions}
-%     \label{fig:leakage}
-% \end{figure}
+ \subsection{Effectiveness of Approximate Deletion}
+ \begin{figure}
+     \centering
+     \includegraphics[width=3in]{figures/leakage}
+     \caption{Accumulated storage leakage by approximate snapshot deletions}
+     \label{fig:leakage}
+ \end{figure}
 

### 2013-09-21 snapshot_system/fast14_evaluation.tex
revise

@@
 running 1 or multiple  VM backup tasks at the same time on each physical machine. 
-CPU column is the percentage of a core usage. 
-The memory usage includes 100MB of PDS index and other space cost for executing deduplication tasks such as 
+``CPU'' column is the percentage of a core usage. 
+``Mem'' column includes 100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
 receipt metadata and cache. 
-Disk read is controlled as 50MB/s bandwidth usage so that other cloud services are not impacted a lot.
-Disk write is the write usage of QFS and notice that each QFS write leads writes in multiple machines due to
+``Read'' column is controlled as 50MB/s bandwidth usage so that other cloud services are not impacted a lot.
+``Write'' column is the I/O write usage of QFS and notice that each QFS write leads writes in multiple machines due to
 data replication.     

### 2013-09-23 snapshot_system/fast14_evaluation.tex
revise
Updated to adjusted model

@@
 %in VM availability.
-For example, with 5/100 machines failed, VO with 93.3\% availability would lose data in 169 VMs 
-while VC with 99.9\% loses data for 2 VMs.
+For example, with 5/100 machines failed, VO with 93.256\% availability would lose data in 169 VMs 
+while VC with 97.763\% loses data for 56 VMs.
 The key reason is that for most data in VC, only a single
@@
                     \addlegendentry{VC}
-                    \addplot table[x=NodesFailed,y=VCWC1]{figures/node_failures_100.txt};
-                    \addlegendentry{VC (worst-case)}
+                    %\addplot table[x=NodesFailed,y=VCOpt1]{figures/node_failures_100.txt};
+                    %\addlegendentry{VC (CDS ordering)}
                     \end{axis}
@@
                                     %\cline{2-7}
-                                    & VO & VC & VC(WC) & VO & VC & VC(WC) \\
+                                    & VO & VC & VC(Opt) & VO & VC & VC(Opt) \\
         \hline
-        3 & 99.304 & 99.891 & 99.891 & 99.999 & 99.999 & 99.999\\
-        5 & 93.256 & 98.919 & 98.919 & 99.993 & 99.999 & 99.999\\
-        10 & 43.251 & 87.707 & 87.638 & 99.919 & 99.987 & 99.987\\
-        20 & 0.034 & 24.953 & 21.571 & 99.228 & 99.879 & 99.879\\
+        3 & 99.304 & 99.774 & 99.774 & 99.999 & 99.999 & 99.999 \\
+        5 & 93.256 & 97.763  & 97.763 & 99.993 & 99.998 & 99.998 \\
+        10 & 43.252 & 76.094 & 76.214 & 99.919 & 99.974 & 99.974 \\
+        20 & 0.034 & 5.614 & 7.507 & 99.228 & 99.749 & 99.749 \\
         \hline
@@
     \hline
-    Tasks & CPU & Mem &Read &  Write  & Time  \\ \hline
+    Tasks & CPU & Mem &Read &  Write  & Time  \\ 
     & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline

### 2013-09-23 snapshot_system/fast14_abstract.tex
revisions

@@
 A cloud environment that hosts a large number of virtual machines (VMs) has
-a high storage demand for frequent backup of system image snapshots and
-signature-based deduplication of data blocks is necessary to eliminate excessive 
-redundant blocks. Collocating a cluster-based duplicate service with other cloud services
+a high storage demand for frequent backup of system image snapshots. 
+Deduplication of data blocks is necessary to eliminate
+redundant blocks and reduce cost. Collocating a cluster-based duplicate service with other cloud services
 reduces network traffic;
-however it is resource expensive and less fault-resilient to perform global deduplication
-and let a data block be shared by many virtual machines. 
+however, performng global deduplication and letting a data block be shared
+by many virtual machines is resource expensive and less fault-resilient. 
 This paper proposes a VM-centric collocated backup service that  

### 2013-09-23 snapshot_system/fast14_architecture.tex
revised evaluation etc
revisions

@@
 We use the virtual device driver in Xen that employs a bitmap to track the changes 
-that have been made to virtual disk.
+that have been made to the virtual disk.
 Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicating whether the segment
@@
     \centering
-    \includegraphics[width=6in]{images/socc_arch_cluster}
+    \includegraphics[width=4.5in]{images/socc_arch_cluster}
     \caption{System Architecture}
@@
 \begin{itemize}
-\item Data of each VM snapshot store excluding PDS is divided into a set of containers and 
+\item Data of each VM snapshot store, excluding the PDS store, are divided into a set of containers and 
 each container is approximately 1GB. 
@@
 By limiting the size of a container, we can effectively control the length of each round of compaction.
-The compaction  routine can work on one container at a time and move the used data chunks to another container.
+The compaction  routine can work on one container at a time and move the in-use data chunks to another container.
 

### 2013-09-23 snapshot_system/fast14_background.tex
revised evaluation
revisions

@@
 which  occurs frequently when snapshots expire regularly. 
-The mark-sweep approach~\cite{Guo2011} is effective for deletion, and its main cost
+The mark-and-sweep approach~\cite{Guo2011} is effective for deletion, but has a high cost, and its main cost
 is to count if a data chunk is still shared by other snapshots.
 Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
-deduplication efficiency, and  can faciltate parallel execition of snaptshot operations.
+deduplication efficiency, and  can faciltate parallel execution of snaptshot operations.
 \item{\em  Management of file system blocks.}
 The file block size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
- a data chunk in a typical deduplication system is of a nonuniform size with 4KB or 8KB on average.
-Packaging data chunks to a file system block can create more data dependence among VMs
-since a file block can be shared with even more VMs.
+while the data chunk in a typical deduplication system is of a nonuniform size with 4KB or 8KB on average.
+Packaging data chunks to a file system block can create more data dependencies among VMs
+since a file block can be shared by even more VMs.
 Thus we need to consider a minimum association of a fie system block to VMs in the packaging process.
@@
 The key resource for signature comparison  is memory for storing the fingerprints. 
-We will consider the approximation techniques with less memory consumption along 
-with the fault isolation consideration discussed below.
+We will consider the approximation techniques with reduced memory consumption along 
+with the fault isolation considerations discussed below.
 
 We call the traditional deduplication approach as   VM-oblivious (VO)
-because they compare fingerprints of snapshots without consideration of VM.
+because they compare fingerprints of snapshots without consideration of VMs.
 With the above  considerations in mind, we study a 
@@
 to the existing applications.
+
 In designing a VC duplication algorithm, we have considered and adopted some of
 the following previously-developed techniques.
-\begin{itemize}
-\item {\bf Version-based change detection}.
+1)
+{\em Version-based change detection}.
 VM snapshots can be  backed up  incrementally by identifying file  blocks that have
@@
 cross-VM  signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
-\item {\bf Stateless  Data Routing}.
+2) {\em Stateless  data Routing}.
 One approach for scalable duplicate comparison is to use a content-based hash
@@
 VM-specific local search.
-\item {\bf Sampled Index}.
+3) {\em Sampled Index}.
 One effective approach that reduces memory usage is 
@@
 can be significant.
-\end{itemize}
 

### 2013-09-23 snapshot_system/fast14_deduplication.tex
revisions

@@
 segments to search, the amount of memory for maintaining those fingerprints in similar segments is small.
+As part of our local duplicate search we also compare the current segment
+against the parent segment at the same offset.
 
@@
 data chunks is limited and  on average the number of consecutive data chunks is 7 among popular chunks.
-This is not sufficient to enable prefetching which is required  for index sampling.
+This is not sufficient to enable effective prefetching which is required  for index sampling.
 
@@
 studied from  application datasets.
-Our previous study shows that the popularity of data chunks after inner VM deduplication follows 
+A previous study shows that the popularity of data chunks after inner VM deduplication follows 
 a Zipf-like distribution\cite{Breslau1999a} and its
@@
 Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
-We will use a number of parameters in our analysis below and they are defined in
+The parameters we will use in our analysis below are defined in
 Table~\ref{tab:symbol}.
@@
 0.65 and measured PDS coverage in our test dataset.
-$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for top $k$ PDS.
+$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
 While the predicted value remains flat, the  real coverage actually increases as the data size
@@
 to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
-if this block is used by this VM.
+if this block is used by the VM.
 
@@
 which decreases the overall number of FSBs required to backup a VM.
-Noted that  if  the backup for multiple VMs were conducted concurrently, there would be more
-VMs shared  by each file block on average in VO.
+Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
+VMs sharing each file block on average in VO.
 
@@
                                     %\cline{2-4}
-                                    & $R_c=3$ & $R_c=6$ & $R_c=9$ \\
+                                    & $R=3$ & $R=6$ & $R=9$ \\
         \hline
-        3 & 99.999 & 100 & 100\\
-        5 & 99.994 & 100 & 100\\
-        10 & 99.925 & 99.999 & 99.999\\
-        20 & 99.295 & 99.997 & 99.999 \\
+        3 & 99.9994 & 100 & 100\\
+        5 & 99.9939 & 100 & 100\\
+        10 & 99.9258 & 99.9999 & 99.9999 \\
+        20 & 99.2950 & 99.9967 & 99.9999 \\
         \hline

### 2013-09-23 snapshot_system/fast14_introduction.tex
revisions

@@
 deduplication, most data chunks are shared by several to many virtual machines.
-Failure of few shared data chunks can have a 
+Failure of a few shared data chunks can have a 
 broad effect and many
@@
 Another issue considered is that
-that deletion of old snapshots competes for computing resource as well. 
+that deletion of old snapshots also competes for computing resources. 
 Sharing of data chunks among by multiple VMs needs to be detected during

### 2013-09-24 snapshot_system/fast14_deduplication.tex
now generates availability tables from data files

@@
                 \addplot[blue,mark=none] table[x=VMs,y=N_O] {figures/vm_links_all.txt};
-                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
+                %\addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
                 \addplot[red,dashdotted] table[x=VMs,y=N_1] {figures/vm_links_all.txt};
                 \addplot[red,densely dashed,mark=none] table[x=VMs,y=N_2] {figures/vm_links_all.txt};
-                \legend{$N_o$, $N_1+N_2$, $N_1$, $N_2$};
+                \legend{$N_o$,
+                    %$N_1+N_2$,
+                    $N_1$,
+                    $N_2$};
 		\end{axis}
@@
     \tabcolsep=0.11cm
+    \comments{%table data is obsolete, now uses pgfplotstable
         \begin{tabular}{|l|l|l|l|}
         \hline
-        \multirow{2}{*}{Failures}   & \multicolumn{3}{c|}{FSB Availability} \\
+        \multirow{2}{*}{Failuresi ($d$)}   & \multicolumn{3}{c|}{$A(r_c)$} \\
                                     %\cline{2-4}
-                                    & $R=3$ & $R=6$ & $R=9$ \\
+                                    & $r_c=3$ & $r_c=6$ & $r_c=9$ \\
         \hline
@@
     \end{tabular}
-    \caption{Availability of individual 64MB Filesystem blocks (FSBs) as storage
-    nodes fail in a 100 node cluster.}
+    }
+    \pgfplotstabletypeset[
+        columns={NodesFailed,Availability3,Availability6,Availability9},
+        columns/NodesFailed/.style={
+            column name={\multirow{2}{*}{Failures ($d$)}}
+        },
+        columns/Availability3/.style={
+            column name={\multicolumn{3}{c|}{$A(r_c)$}\\&$r_c=3$},
+            fixed, precision=9
+        },
+        columns/Availability6/.style={
+            column name={$r_c=6$},
+            fixed, precision=9},
+        columns/Availability9/.style={
+            column name={$r_c=9$},
+            fixed, precision=9},
+        every head row/.style={
+            before row={\hline},
+            after row={\hline},
+        },
+        every last row/.style={after row=\hline},
+        column type/.add={}{|},
+        every first column/.style={column type/.add={|}{}},
+    ]{figures/fsb_availability.txt}
+    \caption{$A(r_c)$ as storage nodes fail in a 100 node cluster.}
     \label{tab:fsb-availability}

### 2013-09-24 snapshot_system/fast14_evaluation.tex
revisions
now generates availability tables from data files

@@
     \tabcolsep=0.11cm
+    \comments{%table here is obsolete, now uses pgfpltostable to generate latex
         \begin{tabular}{|l|l|l|l|l|l|l|}
@@
         \hline
-        3 & 99.304 & 99.774 & 99.774 & 99.999 & 99.999 & 99.999 \\
-        5 & 93.256 & 97.763  & 97.763 & 99.993 & 99.998 & 99.998 \\
-        10 & 43.252 & 76.094 & 76.214 & 99.919 & 99.974 & 99.974 \\
-        20 & 0.034 & 5.614 & 7.507 & 99.228 & 99.749 & 99.749 \\
+        3 & 99.3042 & 99.7740 & 99.7740 & 99.9993 & 99.9998 & 99.9998 \\
+        5 & 93.2561 & 97.7627  & 97.7627 & 99.9932 & 99.9978 & 99.9978 \\
+        10 & 43.2519 & 76.0940 & 76.1541 & 99.9185 & 99.9736 & 99.9736 \\
+        20 & 0.0340 & 5.6139 & 6.4942 & 99.2285 & 99.7490 & 99.7491 \\
         \hline
     \end{tabular}
+    }
+    \pgfplotstabletypeset[
+        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
+        columns/NodesFailed/.style={
+            column name={\multirow{3}{*}{Failures ($d$)}}
+        },
+        columns/VO100/.style={
+            column name={
+                \multicolumn{4}{c|}{VM Availability(\%)}\\&
+                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
+            VO},
+            fixed, precision=6
+        },
+        columns/VC100/.style={
+            column name={VC},
+            fixed, precision=6},
+        columns/VO1000/.style={
+            column name={VO},
+            fixed, precision=6},
+        columns/VC1000/.style={
+            column name={VC},
+            fixed, precision=6},
+        every head row/.style={
+            before row={\hline},
+            after row={\hline},
+        },
+        every last row/.style={after row=\hline},
+        column type/.add={}{|},
+        every first column/.style={column type/.add={|}{}},
+        %skip rows between index={0}{3},
+        %skip rows between index={4}{5},
+        %skip rows between index={6}{10},
+        %skip rows between index={11}{20},
+        %skip rows between index={21}{41}
+    ]{figures/availability_table.txt}
     \caption{Availability of VM snapshots for VO and VC.}

### 2013-09-24 snapshot_system/fast14_deduplication.tex
revise

@@
 \item \textbf{Cross-VM deduplication with popular chunks and replication support.}
-This step accomplishes the standard global fingerprint comparison as conducted
-in the previous work~\cite{WeiZhangIEEE}.
-One key observation is that the inner-VM deduplication has removed many of the duplicates.
+This step accomplishes the standard global fingerprint comparison using standard fingerprint 
+comparison (e.g. ~\cite{bottleneck08}).
+Our key observation is that the inner-VM deduplication has removed many of the duplicates.
 There are fewer deduplication opportunities across VMs while the memory and network
@@
 most popular chunk signatures in a distributed shared memory.  
+Our previous work~\cite{WeiZhangIEEE} studies a preliminary solution using data popularity and this
+paper improves this with a more comprehensive scheme with  similarity-guided search and fault isolation.
 
@@
 
-We store the popular index using a distributed shared memory hashtable such as MemCacheD
+We store the popular index using a distributed shared memory hashtable such as Memcached
 and allocate a fixed percentage of memory space   per physical machine for top $k$ popular items.
@@
 
-\subsection{Storage Space and Impact on Fault Isolation}
+\subsection{ Impact on Storage Space and Fault Isolation}
 

### 2013-09-24 snapshot_system/fast14_deduplication.tex
update

@@
 \label{sect:vc-strategies}
-\begin{itemize}
-\item \textbf{VM-specific local duplicate search within similar segments.}
-We start with the standard dirty bit approach in a coarse grain segment level.
+%\begin{itemize}
+%\item 
+\textbf{VM-specific local duplicate search within similar segments.}
+We start with the changed block tracking approach in a coarse grain segment level.
 In our implementation with Xen on an Alibaba platform, the segment size is 2MB
-and  the device driver is extended to support  changed block tracking. 
+and the device driver is extended to support tracking changed segments using a dirty bitmap. 
 Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
@@
 The Microsoft SDK provides an API that allows external applications to monitor 
-the VM's I/O traffic and implement  the changed block tracking feature.
+the VM's I/O traffic and implement such changed block tracking feature.
 
@@
 which contain chunk fingerpints to be compared.
-To control the time cost of search, we set a limit on the the number of  similar segments to be  fetched. 
+To control the time cost of search, we set a limit on the the number of  similar segments recipes to be fetched. 
 % Then,
@@
 %with those in similar segments.  
-For example, a 2MB segment contains about 500 fingerprints and by limiting at most 10 similar
-segments to search, the amount of memory for maintaining those fingerprints in similar segments is small.
+For a 2MB segment, its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
+by limiting at most 10 similar segments to search, the amount of memory for maintaining those similar segment recipes is small.
 As part of our local duplicate search we also compare the current segment
@@
 
-\item \textbf{Cross-VM deduplication with popular chunks and replication support.}
-This step accomplishes the standard global fingerprint comparison using standard fingerprint 
-comparison (e.g. ~\cite{bottleneck08}).
-Our key observation is that the inner-VM deduplication has removed many of the duplicates.
+%\item 
+\textbf{Global deduplication with popular chunks and replication support.}
+This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
+Our key observation is that the local deduplication has removed most of the duplicates.
 There are fewer deduplication opportunities across VMs while the memory and network
@@
 Thus our approximation is that the global fingerprint comparison only searches for the top $k$
-most popular items. This dataset is called the PDS (popular data set). 
-The popularity of a chunk is the number  of data chunks  from different VMs
-that are duplicates of this chunk after the inner VM deduplication.
+most popular items. This dataset is called the \textbf{PDS} (popular data set). 
+\textbf{The popularity of a chunk is the number  of data chunks  from different VMs
+that are duplicates of this chunk after the inner VM deduplication.}
 This number can be computed periodically (e.g., on a weekly basis).
 Once the popularity of all data chunks is collected, the system only maintains the top $k$
-most popular chunk signatures in a distributed shared memory.  
+most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
 Our previous work~\cite{WeiZhangIEEE} studies a preliminary solution using data popularity and this
@@
 Since $k$ is relatively small and these top $k$ chunks are shared among multiple VMs, 
-we can afford to provide extra replicas for these popular chunks to enhance the fault resilience.
+we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
 
-\item \textbf{VM-centric file system block management.}
+%\item 
+\textbf{VM-centric file system block management.}
 When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
 to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
-accumulate small local chunks. We manage this accumulation process using an append-store  scheme built
+accumulate small local chunks. We manage this accumulation process using an log-structured storage scheme built
 on a distributed file system discussed in Section~\ref{sect:architecture}.
@@
 A file system block for non-PDS chunks is associated with one VM and does not contain
-any PDS chunks, to maintain our goal of fault isolation.
-PDS chunks are stored in a separate append-store instance with special replication handling. 
-The system allows all machines conduct the backup in parallel, and each machine
-conducts the backup of one VM at a time, and thus only requires a write  buffer for one VM.
-\end{itemize}
+any PDS chunks, such that our goal of fault isolation is maintained.
+In addition, storing PDS chunks separately allows special replication handling for those popular shared data. 
+%%% talk something about snapshot store advantage here? %%%
+
+%The system allows all machines conduct backups in parallel, and each machine
+%conducts the backup of one VM at a time, and thus only requires a write buffer for one VM.
+%\end{itemize}
 
@@
 \end{figure}
-We have not  adopted the  sampled index~\cite{Guo2011} 
-for  detecting duplicates from popular chunks.
-For the data sets we have tested, the spatial locality 
-among popular
-data chunks is limited and  on average the number of consecutive data chunks is 7 among popular chunks.
-This is not sufficient to enable effective prefetching which is required  for index sampling.
+We decide not to take the sampled index appraoch~\cite{Guo2011} 
+for detecting duplicates from PDS.
+This is because for the data sets we have tested, we only observed very limited spatial locality 
+among popular data chunks. On average the number of consecutive PDS index hits is lower than 7,
+which is not sufficient to enable effective prefetching which is required for index sampling.
 

### 2013-09-24 snapshot_system/fast14_architecture.tex
update

@@
 Our system runs on a cluster of Linux machines with Xen-based VMs and
-an open-source package for the distributed file system  called QFS~\cite{QFS}. 
+an open-source package for the distributed file system  called QFS~\cite{michael2013}. 
 %to %manage  the physical disk storage. 
@@
 
-\begin{figure*}[t]
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width=4.5in]{images/socc_arch_cluster}
-    \caption{System Architecture}
+    \includegraphics[width=3in]{images/socc_arch_cluster}
+    \caption{System architecture and data flow during snapshot write}
     \label{fig:arch_vm}
-\end{figure*}
+\end{figure}
 

### 2013-09-24 snapshot_system/fast14_evaluation.tex
update
paper revisions

@@
  Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
-there are up to 25 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
-We show three snapshot  availability curves as the number of machines failed increases.
+there are up to 20 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
 %Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
-Curve ``VC(WC)" represents a worst-case  situation that each PDS file system block is shared by all VMs.
+We assume that every VM points to every filesystem block in the PDS ($V_c=p*V$), which is to be expected when PDS
+blocks are sorted by hash, as their order is randomized.
 %$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
@@
 %based on measured values in our dataset.
-To obtain VM sharing of file blocs, we perform perfect deduplication over 105 VMs, 
+To obtain VO sharing of file blocks, we perform perfect deduplication over 105 VMs, 
 append unique chunks to a DFS file and
@@
 %case for VO approach. 
-Our results show that even the worst case for VC has a higher availability than VO.
+Our results show that even the worst case for VC (where $v_c=p*V$) has a higher availability than VO.
 %Our VM-centric approach shows significant improvements
 %in VM availability.
-For example, with 5/100 machines failed, VO with 93.256\% availability would lose data in 169 VMs 
+For example, with 5/100 machines failed and 25 VMs per machine, VO with 93.256\% availability would lose data in 169 VMs 
 while VC with 97.763\% loses data for 56 VMs.
 The key reason is that for most data in VC, only a single
-VM can be affected by the loss of a single FSB.
+VM can be affected by the loss of a single FSB. Since most FSBs contain blocks for a single VM, VMs can point to a smaller number of FSBs.
 % because our VM-centric approach
@@
 \begin{table}
+  \centering
     \footnotesize
     \tabcolsep=0.11cm
-    \comments{%table here is obsolete, now uses pgfpltostable to generate latex
-        \begin{tabular}{|l|l|l|l|l|l|l|}
-        \hline
-        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{Snapshot Availability} \\
-                                    %\cline{2-7}
-                                    & \multicolumn{3}{c|}{$p=100$} & \multicolumn{3}{c|}{$p=1000$} \\
-                                    %\cline{2-7}
-                                    & VO & VC & VC(Opt) & VO & VC & VC(Opt) \\
-        \hline
-        3 & 99.3042 & 99.7740 & 99.7740 & 99.9993 & 99.9998 & 99.9998 \\
-        5 & 93.2561 & 97.7627  & 97.7627 & 99.9932 & 99.9978 & 99.9978 \\
-        10 & 43.2519 & 76.0940 & 76.1541 & 99.9185 & 99.9736 & 99.9736 \\
-        20 & 0.0340 & 5.6139 & 6.4942 & 99.2285 & 99.7490 & 99.7491 \\
-        \hline
-    \end{tabular}
-    }
     \pgfplotstabletypeset[
@@
         every first column/.style={column type/.add={|}{}},
+        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
         %skip rows between index={0}{3},
@@
                 \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
-                \legend{$R_C=4$,$R_C=5$,$R_C=6$, $R_C=9$}
+                \legend{$r_c=4$,$r_c=5$,$r_c=6$, $r_c=9$}
 		\end{axis}
@@
 
-Figure~\ref{fig:exbin-efficiency-graph2} also shows the effectiveness of VC without local similarity-based search.
-Without this, when an entire
-segment is moved to another location on disk (e.g. when a file is rewritten
-rather than modified in place), searching only the segment in the same location
-in the parent will miss the deduplication opportunity. We have found that in
+Figure~\ref{fig:exbin-efficiency-graph2} also shows the effectiveness of the local similarity-based search in VC.
+Without this (i.e. when we only check the parent segment at the same offset), when an entire
+segment is moved to another location on disk, for example when a file is rewritten
+rather than modified in place, the deduplication opportunity is missed. We have found that in
 approximately 1/3 of the VMs in our dataset this movement happens frequently,

### 2013-09-24 snapshot_system/fast14_evaluation.tex
revisions

@@
 With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
-and  the deduplication efficiency can reach over 96.??\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 97.??\% while space consumption increases to 200MB per machine. 
+and  the deduplication efficiency can reach 96.489\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
 The loss of efficiency in VC is caused by the restriction of the physical memory available
@@
 %index ($\sigma=100\%$) then VC will have 100\% efficiency.
-SRB can deliver up to 97.6??\% deduplication efficiency which is slightly better than VC.
-Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
-with a competitive deduplication efficiency.
+SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
+Thus this represents a tradeoff: VC provides better fault tolerance and fast
+approximate deletion with a competitive (but slightly lower) deduplication
+efficiency.
 %its loss of efficiency is caused by the routing of data chunks which restricts the search scope

### 2013-09-24 snapshot_system/fast14_evaluation.tex
update

--- 2013-09-24 snapshot_system/fast14_evaluation.tex
@@
 \begin{table}
+  \centering
     \footnotesize
@@
 With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
-and  the deduplication efficiency can reach over 96.??\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 97.??\% while space consumption increases to 200MB per machine. 
+and  the deduplication efficiency can reach over 96.33\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 96.9\% while space consumption increases to 200MB per machine. 
 The loss of efficiency in VC is caused by the restriction of the physical memory available
@@
 %index ($\sigma=100\%$) then VC will have 100\% efficiency.
-SRB can deliver up to 97.6??\% deduplication efficiency which is slightly better than VC.
+SRB can deliver up to 97.79\% deduplication efficiency which is slightly better than VC.
 Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
@@
 In general, our experiments show that
-dirty-bit detection at the segment level can reduce the data size to about 24\% of original data, 
-which leads  about 76\% reduction.
+dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
+which leads about 75.86\% reduction.
 Similarity-guided local search can further reduce the data size
-to about 12\% of original size, namely it delivers additional 12\% reduction.
+to about 12.05\% of original size, namely it delivers additional 12.09\% reduction.
 The PDS-based cross-VM detection with $\sigma=2\% $
-can reduce the  size further to 5.6\% of original size, namely it 
-delivers additional 6.4\% reduction.
+can reduce the size further to 8.6\% of original size, namely it 
+delivers additional 3.45\% reduction.
 

### 2013-09-24 snapshot_system/fast14_architecture.tex
revisions

@@
 Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
-There is an option to use the data structure similar to the non-PDS store. We opt for this simple format because
-PDS chunks have less spatial locality in data access and it is not so effective to group a large number of chunks
+There is an option to use a data structure similar to the non-PDS store. We opt
+for the simpler format because
+PDS chunks have less spatial locality in data access and it is not so effective
+to group a large number of chunks
 as a compression and data fetch unit.
@@
 The old data is not removed because they can still be referenced by the existing snapshots. 
-A periodic cleanup is conducted  to remove unused PDS chunks (e.g. in every few months). 
+A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months). 
 \end{itemize}
@@
 The fetch operation for the PDS data chunk is straightforward since each reference contains 
-the file offset and the size of a PDS chunk is available from a segment receipt.
+the file offset and the size of a PDS chunk is available from a segment recipe.
 We also maintain a small data cache for the PDS data service to speedup common data fetching.
@@
 While we can use the mark-and-sweep technique~\cite{Guo2011}, 
-it still takes significant resources to conduct this process every time there is a snapshot deletion.
+it takes significant resources to conduct this process every time there is a snapshot deletion.
 In the case of Alibaba, snapshot backup is conducted automatically and there are 
@@
 a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
-a balanced storage use.
+balanced storage use.
 
@@
 reference of deleted chunks  with
-the merged Bloom-filter reference summary in other live snapshots.
-The merging of live snapshot Bloom-filter bits uses the logical OR operator 
+the merged Bloom-filter reference summary of other live snapshots.
+The merging of live snapshot Bloom-filter bits uses the bitwise OR operator 
 and the merged vector still takes $z$ bits.
@@
 there is a small percentage of unused chunks  which
-are misjudged as  being in use, resulting in a storage leakage.
+are misjudged as  being in use, resulting in storage leakage.
 
@@
 Leakage repair is conducted periodically to fix the above approximation error.
-This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipe.
+This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
 That requires a scanning of all chunks in a VM. Since it is a VM-specific procedure 

### 2013-09-24 snapshot_system/fast14_evaluation.tex
revisions

--- 2013-09-24 snapshot_system/fast14_evaluation.tex
@@
 %popular and non-popular data to facilitate improved reliability. 
-Figure~\ref{fig:pds-replication}) shows
-the impact of  to increasing PDS data replication. 
-While the impact on replication storage cost is small, 
-the replication degree 6  has a significant improvement over 4, but  the availability is about
-the same for $r_c=6$ and $r_c=9$.
+Figure~\ref{fig:pds-replication} shows
+the impact of increasing PDS data replication. 
+While the impact on storage cost is small, 
+a replication degree of 6  has a significant improvement over 4, but the availability is about
+the same for $r_c=6$ and $r_c=9$ (beyond $r_c=6$ improvements are minimal).
 
@@
 		]
+                \addplot table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                 \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
@@
                 \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
-                \legend{$r_c=4$,$r_c=5$,$r_c=6$, $r_c=9$}
+                \legend{
+                    VO,
+                    $r_c=4$,
+                    $r_c=5$,
+                    $r_c=6$,
+                    $r_c=9$
+                }
 		\end{axis}
@@
 ``Snapshot store" is the  write throughput of the snapshot store layer and the gap between this
-column and  ``Raw" column is caused by significant data reduction by dirty bit and duplication
+column and  ``Raw" column is caused by significant data reduction by dirty bit and duplicate
 detection. Only non-duplicate chunks trigger a snapshot store write.
 ``QFS'' column is the write request traffic to the underlying file system after compression.
-The underlying disk storage traffic will be three times or more because of replication.
+The underlying disk storage traffic will be three times greater because of replication.
 The result shows that the backup service can deliver up to 5.46GB/second without I/O restriction

### 2013-09-24 snapshot_system/fast14_evaluation.tex

--- 2013-09-24 snapshot_system/fast14_evaluation.tex
@@
 With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
-and  the deduplication efficiency can reach 96.489\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
+and  the deduplication efficiency can reach over 96.33\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 96.9\% while space consumption increases to 200MB per machine. 
+%and  the deduplication efficiency can reach 96.489\%.
+%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
 The loss of efficiency in VC is caused by the restriction of the physical memory available
@@
 %index ($\sigma=100\%$) then VC will have 100\% efficiency.
-SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
-Thus this represents a tradeoff: VC provides better fault tolerance and fast
-approximate deletion with a competitive (but slightly lower) deduplication
-efficiency.
+SRB can deliver up to 97.79\% deduplication efficiency which is slightly better than VC.
+Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
+with a competitive deduplication efficiency.
+
+% SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
+% Thus this represents a tradeoff: VC provides better fault tolerance and fast
+% approximate deletion with a competitive (but slightly lower) deduplication
+% efficiency.
+% >>>>>>> 4dcd68612b052c0f890ed30361a9ed03771b5df1
 %its loss of efficiency is caused by the routing of data chunks which restricts the search scope

### 2013-09-24 snapshot_system/fast14_evaluation.tex
update

@@
 so the similarity search becomes important for those VMs.
+% In general, our experiments show that
+% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
+% which leads about 75.86\% reduction.
+% Similarity-guided local search can further reduce the data size
+% to about 12.05\% of original size, namely it delivers additional 12.09\% reduction.
+% The PDS-based cross-VM detection with $\sigma=2\% $
+% can reduce the size further to 8.6\% of original size, namely it 
+% delivers additional 3.45\% reduction.
 In general, our experiments show that
 dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
-which leads about 75.86\% reduction.
+which leads to about 75.86\% reduction.
 Similarity-guided local search can further reduce the data size
-to about 12.05\% of original size, namely it delivers additional 12.09\% reduction.
-The PDS-based cross-VM detection with $\sigma=2\% $
-can reduce the size further to 8.6\% of original size, namely it 
-delivers additional 3.45\% reduction.
+to about 12.05\% of original, namely it delivers 50.08\% reduction to the dirty segments.
+The popularity-guided global deduplication with $\sigma=2\% $
+can reduce the data further to 8.6\% of its original size, 
+it provides additional 28.63\% reduction to the remaining data.
 

### 2013-09-24 snapshot_system/fast14_architecture.tex
revisions

@@
 the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
+This is ensured because we only dedup against the direct parent of a snapshot, so the deleted snapshot's blocks
+will only be used if they also exist in other snapshots.
 Periodically, the snapshot  store picks those containers with an excessive
@@
 consider each reference consumes 8 bytes plus  1 mark bit, a VM that has 40GB backup data with about
-10 million chunks will need less than 90MB of memory to complete a VM-specific mark-sweep process.
+10 million chunks will need less than 85MB of memory to complete a VM-specific mark-sweep process.
 \end{itemize}

### 2013-09-24 snapshot_system/fast14_evaluation.tex
revisions

--- 2013-09-24 snapshot_system/fast14_evaluation.tex
@@
 With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
-and  the deduplication efficiency can reach over 96.33\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 96.9\% while space consumption increases to 200MB per machine. 
-%and  the deduplication efficiency can reach 96.489\%.
-%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
+and  the deduplication efficiency can reach 96.489\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
 The loss of efficiency in VC is caused by the restriction of the physical memory available
@@
 %index ($\sigma=100\%$) then VC will have 100\% efficiency.
-SRB can deliver up to 97.79\% deduplication efficiency which is slightly better than VC.
-Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
-with a competitive deduplication efficiency.
-
-% SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
-% Thus this represents a tradeoff: VC provides better fault tolerance and fast
-% approximate deletion with a competitive (but slightly lower) deduplication
-% efficiency.
-% >>>>>>> 4dcd68612b052c0f890ed30361a9ed03771b5df1
+SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
+Thus this represents a tradeoff: VC provides better fault tolerance and fast
+approximate deletion with a competitive (but slightly lower) deduplication
+efficiency.
 %its loss of efficiency is caused by the routing of data chunks which restricts the search scope
@@
 In general, our experiments show that
-dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
-which leads about 75.86\% reduction.
+dirty-bit detection at the segment level can reduce the data size to about 24\% of original data, 
+which leads  about 76\% reduction.
 Similarity-guided local search can further reduce the data size
-to about 12.05\% of original size, namely it delivers additional 12.09\% reduction.
+to about 12\% of original size, namely it delivers additional 12\% reduction.
 The PDS-based cross-VM detection with $\sigma=2\% $
-can reduce the size further to 8.6\% of original size, namely it 
-delivers additional 3.45\% reduction.
+can reduce the  size further to 5.6\% of original size, namely it 
+delivers additional 6.4\% reduction.
 
@@
 running 1 or multiple  VM backup tasks at the same time on each physical machine. 
-``CPU'' column is the percentage of a core usage. 
+``CPU'' column is the percentage of a single core used. 
 ``Mem'' column includes 100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
@@
 PDS lookup takes only a small amount of time.
-SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
-it relies on this local machine to access its index (often on the disk, supported by a Bloom filter) 
+SRB has higher index access and fingerprint comparison costs because all chunk signatures for whom the current
+machine does not control the index must be sent over the network, and then rely
+on the index holding machine to access its index (often on the disk, supported by a Bloom filter) 
 and perform comparison.
 VC is faster for index access because it conducts in-memory local search first and then
-accesses  the PDS on distributed shared memory.  
+accesses  the PDS on distributed shared memory, so most chunks can be dealt with locally.  
 SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
-local meta data index.
+local meta data index in addition to partition indices.
 Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.

### 2013-09-25 snapshot_system/fast14_conclusion.tex
revisions. moved from inner/cross-VM to local/global dedup

@@
 maximize fault isolation while delivering competitive deduplication efficiency.
-Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
-while cross-VM deduplication with a small common data set.
-VM-specific file block packing also reduces inter-VM dependence and enhances fault tolerance.
+Similarity guided local search reduces cross-VM data dependency and exposes more parallelism  
+while global deduplication with a small common data set eliminates popular duplicates.
+VM-specific file block packing also enhances fault tolerance by reducing data dependencies.
 The design places a special consideration for low-resource usages as a collocated cloud service.

### 2013-09-25 snapshot_system/fast14_deduplication.tex
update
revisions. moved from inner/cross-VM to local/global dedup

@@
 in the average of 4K or 8K~\cite{Jin2009},
-we conduct additional local inner-VM deduplication on a snapshot by comparing
+we conduct additional local similary guided deduplication on a snapshot by comparing
 chunk fingerprints of a dirty segment 
@@
 most popular items. This dataset is called the \textbf{PDS} (popular data set). 
-\textbf{The popularity of a chunk is the number  of data chunks  from different VMs
-that are duplicates of this chunk after the inner VM deduplication.}
+We define chunk popularity as the number of unique copies of the chunk in the data-store,
+that is the number of copies of the chunk after local deduplication.
 This number can be computed periodically (e.g., on a weekly basis).
@@
  \includegraphics[width=3in]{figures/log-log-disk}
-\caption{Duplicate frequency versus  chunk ranking in a log scale after inner-VM deduplication.}
+\caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
 \label{fig:Datazipf}
@@
 \hline
-$\delta$ &  the percentage of duplicates detected in inner VM deduplication\\
+$\delta$ &  the percentage of duplicates detected in local deduplication\\
 \hline
@@
 studied from  application datasets.
-A previous study shows that the popularity of data chunks after inner VM deduplication follows 
+A previous study shows that the popularity of data chunks after local deduplication follows 
 a Zipf-like distribution\cite{Breslau1999a} and its
@@
 
-The  $k$ most popular fingerprints can cover the following number of chunks after inner VM 
+The  $k$ most popular fingerprints can cover the following number of chunks after local 
 deduplication:
@@
 Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
-chunks detected as duplicates in global cross-VM deduplication due to PDS.
+chunks detected as duplicates in global deduplication due to PDS.
 We call this PDS coverage.

### 2013-09-25 snapshot_system/fast14_introduction.tex
revisions. moved from inner/cross-VM to local/global dedup

@@
 The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
-based on  version  detection, inner VM duplicate search,
-and controlled cross-VM comparison. 
+based on  version  detection, similarity guided local deduplication,
+and popularity guided global deduplication. 
 This approach is VM centric by localizing duplicate detection within each VM  

### 2013-09-25 snapshot_system/fast14_main.tex
revised
update
commented out authors

@@
 \usepackage{pgfplots}
+\usepackage{pgfplotstable}
 \usepackage{sansmath}
+\usepackage{booktabs}
 \pgfplotsset{compat=1.5}
@@
 
-\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]}
-
-\author{
-  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, and Hong Tang$^\dagger$ \\
-  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
-  \{wei, tyang, dagun\}@cs.ucsb.edu, hongtang@alibaba-inc.com
-}
+%\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]}
+\title{
+Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
+%\author{
+%  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, and Hong Tang$^\dagger$ \\
+%  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
+%  \{wei, tyang, dagun\}@cs.ucsb.edu, hongtang@alibaba-inc.com
+%}
 

### 2013-09-25 snapshot_system/fast14_evaluation.tex
revisions. moved from inner/cross-VM to local/global dedup
redability improvements to graphs
shrink the last table

@@
 		]
-                \addplot table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
+                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                 \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
@@
                 %{blue,solid,mark=pentagon*,mark size=1.4},
-                {red,draw=red,densely dotted,mark=square},
+                {red,draw=red,dotted,mark=square},
                 %{red,densely dotted,mark=triangle,mark size=1.5},
                 %{red,densely dotted,mark=diamond,mark size=1.5},
-                {brown,densely dashed,mark=*},
+                {brown,dashed,mark=*},
                 %{red,densely dotted,mark=o},
@@
 % to about 12.05\% of original size, namely it delivers additional 12.09\% reduction.
-% The PDS-based cross-VM detection with $\sigma=2\% $
+% The PDS-based global duplicate detection with $\sigma=2\% $
 % can reduce the size further to 8.6\% of original size, namely it 
@@
 %varying the PDS size.  It lists the time distribution for data reading,
-%similarity-guided local search, cross-VM PDS lookup, and non-duplicate data writing. 
+%similarity-guided local search, global PDS lookup, and non-duplicate data writing. 
 %While data reading dominates the backup process, PDS lookup spends about a similar amount
@@
 
-\begin{table*}[t]
+% \begin{table*}[t]
+%     \centering
+%     \begin{tabular}{c|ccc|ccc}
+%     Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
+%     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
+%     per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
+%     1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
+%     2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
+%     4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
+%     6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
+%     \end{tabular}
+% \caption{Throughput of software layers under different concurrency}
+% \label{tab:throughput}
+% \end{table*}
+\begin{table}[htbp]
     \centering
-    \begin{tabular}{c|ccc|ccc}
-    Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
-    backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
-    per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
-    1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
-    2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
-    4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
-    6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
+    \begin{tabular}{c|ccc}
+    Num. of concurrent      & \multicolumn{3}{c}{Throughput without}    \\
+    backup tasks            & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-4}
+    per node                & Raw                                        & Snapshot Store & QFS  \\ \hline
+    1                       & 1369.6                                     & 148.0          & 18.0 \\
+    2                       & 2408.5                                     & 260.2          & 31.7 \\
+    4                       & 4101.8                                     & 443.3          & 54.1 \\
+    6                       & 5456.5                                     & 589.7          & 72.0 \\
     \end{tabular}
@@
 \label{tab:throughput}
-\end{table*}
+\end{table}
+
 {\bf Throughput of software layers.}

### 2013-09-25 snapshot_system/fast14_architecture.tex
update

@@
 A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months).
+
+We decide not to take the sampled index appraoch~\cite{Guo2011} 
+for detecting duplicates from PDS.
+This is because for the data sets we have tested, we only observed very limited spatial locality 
+among popular data chunks. On average the number of consecutive PDS index hits is lower than 7,
+which is not sufficient to enable effective prefetching which is required for index sampling.
 \end{itemize}

### 2013-09-25 snapshot_system/fast14_background.tex
revisions. moved from inner/cross-VM to local/global dedup
update

@@
 to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
-Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}
+Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
 and a parallel batch solution for cluster-based deduplication is 
-studied in ~\cite{WeiZhangHotStorage13}. 
+studied in ~\cite{wei2013}. 
 All of the above approaches have focused on optimization of deduplication
@@
 We are seeking for a tradeoff since 
-cross-VM  signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
+global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
 2) {\em Stateless  data Routing}.

### 2013-09-25 snapshot_system/fast14_deduplication.tex
update

@@
 computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
-content similarity is  an approximation~\cite{AdnriBroader}.  When processing a dirty segment,
+content similarity is an approximation~\cite{resemblance97}.  When processing a dirty segment,
 its  similar segments can be found easily from the
@@
 \end{figure}
-We decide not to take the sampled index appraoch~\cite{Guo2011} 
-for detecting duplicates from PDS.
-This is because for the data sets we have tested, we only observed very limited spatial locality 
-among popular data chunks. On average the number of consecutive PDS index hits is lower than 7,
-which is not sufficient to enable effective prefetching which is required for index sampling.
+
+% {\it [Need to find a place to put these numbers in: Total number of chunks 
+% in 350 snapshots: 1,546,635,485. 
+% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
+\subsection{Impact on deduplication efficiency}
+Choosing the value $k$ for the most popular chunks affects the deduplication efficiency.
+We analyze this impact based on the characteristics  of the VM snapshot traces
+studied from  application datasets.
+A previous study shows that the popularity of data chunks after local deduplication follows 
+a Zipf-like distribution\cite{Breslau1999a} and its
+exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
+Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
+The parameters we will use in our analysis below are defined in
+Table~\ref{tab:symbol}.
 
@@
 $p$ & the number of machines in the cluster\\
+% \hline
+% $V$ & the average number of VMs hosted on each machine\\
 \hline
-$V$ & the average number of VMs hosted on each machine\\
+$E$ & the deduplication efficiency of VC approach\\
 %\hline
@@
 
-% {\it [Need to find a place to put these numbers in: Total number of chunks 
-% in 350 snapshots: 1,546,635,485. 
-% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
-\subsection{Impact on deduplication efficiency}
-Choosing the value  $k$ for the most popular chunks affects the deduplication efficiency.
-We analyze this impact based on the characteristics  of the VM snapshot traces
-studied from  application datasets.
-A previous study shows that the popularity of data chunks after local deduplication follows 
-a Zipf-like distribution\cite{Breslau1999a} and its
-exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
-Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
-The parameters we will use in our analysis below are defined in
-Table~\ref{tab:symbol}.
-
 %Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
@@
 %$f_i$ be the frequency for the $i$th most popular fingerprint. 
-By Zipf-like distribution, $f_i = \frac{f_1}{i^\alpha}.$
-Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
+By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
+The total amount of chunks reside in our backup storage which
+has local duplicates excluded is $c (1-\delta)$, this can be represented
+as the sum of each unique fingerprint times its frequency:
+%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
 \[
@@
 
-The  $k$ most popular fingerprints can cover the following number of chunks after local 
+Thus putting the $k$ most popular fingerprints into PDS index can remove the following number of chunks during global 
 deduplication:
@@
 %e_k &= 
-\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
+E=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
 {c  - c_u }.\\
@@
 
-We store the popular index using a distributed shared memory hashtable such as Memcached
+% After the global deduplication, the number of remaining chunks is:
+% \[
+% c-E(c-c_u)
+% \]
+
+We store the PDS index using a distributed shared memory hashtable such as Memcached
 and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
@@
 increases, which indicates that $\alpha$ increases with the data size. 
-Thus in practice, the coverage of the PDS increases as more VMs are involved.
+Therefore in practice, the coverage of the PDS increases as more VMs are involved.
 
@@
 file systems~\cite{googlefs03,hdfs10}.
-In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
+In the VC approach, a special replication degree $r_c$ is used for PDS data where $r_c>r$. 
 The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
-$ k*r_c  + (c_u-k)*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
+$ k*r_c  + (c-E(c-c_u))*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
 \[
-\sigma \frac{r_c}{r} + 1-\sigma.
+\sigma \frac{r_c}{r} + \frac{c-e(c-c_u)}{c_u}.
 \]
@@
 term $\sigma \frac{r_c}{r}$ is small in the above expression.  
-Thus the impact on storage increase is very small even when we choose a large $\frac{r_c}{r}$ ratio. 
-For example, $\frac{r_c}{r}=2$ or 3.
+Thus the impact on storage increase is very small even when we choose a large $r_c/r$ ratio. 
+For example, $r_c/r=2$ or 3.
 
@@
 to the the VC and VO approaches.  
-A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of VM snapshot blocks.
+A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
 We use file system blocks rather than a deduplication
@@
  and  we denote that PDS file system blocks are
-shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block. Then, 
+shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block, 
+$V$ be the average number of VMs hosted on each machine. Then, 
 \[
-V *p*N_1 *s  \approx c_u (1-\sigma)\; \mbox{ and } \; 
+V *p*N_1 *s  \approx c-E(c-c_u)\; \mbox{ and } \; 
 V *p*N_2 *s  \approx c_u \sigma V_c.
@@
 \[
-\frac{N_1}{N_o} \approx  \frac{1-\sigma}{V_o}.
+\frac{N_1}{N_o} \approx  \frac{c-E(c-c_u)}{c_uV_o}.
 \]
 
-Thus $N_1$ is much smaller than $N_o$. 
+If we achieve very high deduplication efficiecny, then $N_1$ would be much smaller than $N_o$. 
 When there is a failure in file blocks with replication degree $r$

### 2013-09-25 snapshot_system/fast14_deduplication.tex
adjusted figures
revision

@@
 To compute the full availability of all snapshots of a VM, we derive
-the probablity of losing a snapshot file block of a VM by
+the probability of losing a snapshot file block of a VM by
 estimating the number of file system blocks per VM in each approach.
@@
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		legend pos=south west
+		%legend pos=north east,
+                legend style={
+                    at={(1,0.825)},
+                    anchor=north east
+                },
+                %legend columns=3
 		]

### 2013-09-25 snapshot_system/fast14_evaluation.tex
update

@@
     backup tasks            & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-4}
-    per node                & Raw                                        & Snapshot Store & QFS  \\ \hline
-    1                       & 1369.6                                     & 148.0          & 18.0 \\
-    2                       & 2408.5                                     & 260.2          & 31.7 \\
-    4                       & 4101.8                                     & 443.3          & 54.1 \\
-    6                       & 5456.5                                     & 589.7          & 72.0 \\
+    per node                & Backup                                     & Snapshot Store & QFS  \\ \hline
+    1                       & 1369.6                                     & 148.0          & 35.3 \\
+    2                       & 2408.5                                     & 260.2          & 61.7 \\
+    4                       & 4101.8                                     & 443.3          & 103.1 \\
+    6                       & 5456.5                                     & 589.7          & 143.8 \\
     \end{tabular}
@@
 %machine when all machine nodes execute one or multiple MV backup tasks.
-``Raw'' column is the throughput  of the backup service  per machine.
+``Backup'' column is the throughput  of the backup service  per machine.
 ``Snapshot store" is the  write throughput of the snapshot store layer and the gap between this

### 2013-09-25 snapshot_system/fast14_deduplication.tex

@@
 most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
-Our previous work~\cite{WeiZhangIEEE} studies a preliminary solution using data popularity and this
+previous work~\cite{WeiZhangIEEE} has studied a solution taking advantage of data popularity. This
 paper improves this with a more comprehensive scheme with similarity-guided search and fault isolation.

### 2013-09-25 snapshot_system/fast14_deduplication.tex

@@
 in the average of 4K or 8K~\cite{Jin2009},
-we conduct additional local similary guided deduplication on a snapshot by comparing
+we conduct additional local similarity guided deduplication on a snapshot by comparing
 chunk fingerprints of a dirty segment 
@@
 parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
-which contain chunk fingerpints to be compared.
+which contain chunk fingerprints to be compared.
 To control the time cost of search, we set a limit on the the number of  similar segments recipes to be fetched. 
@@
 most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
-previous work~\cite{WeiZhangIEEE} has studied a solution taking advantage of data popularity. This
-paper improves this with a more comprehensive scheme with similarity-guided search and fault isolation.
+Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
+this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
+analytic design guidance.
 
@@
 \hline
-$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belong to  PDS\\
+$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belonging to  PDS\\
 \hline
@@
 \hline
-$E$ & the deduplication efficiency of VC approach\\
+$E_c, E_o$ & deduplication efficiency of VC and VO \\
 %\hline
@@
 %e_k &= 
-E=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
+E_c=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
 {c  - c_u }.\\
@@
 $\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
-While the predicted value remains flat, the  real coverage actually increases as the data size
-increases, which indicates that $\alpha$ increases with the data size. 
-Therefore in practice, the coverage of the PDS increases as more VMs are involved.
+While the predicted value remains flat, PDS  coverage actually increases as more VMs are involved.
+increases. This is because actual $\alpha$ value increases with the data size.
+%Then  PDS coverage PDS increases as more VMs are involved.
 
-\subsection{ Impact on Storage Space and Fault Isolation}
+\subsection{ Impact Fault Isolation}
 
@@
 file systems~\cite{googlefs03,hdfs10}.
-In the VC approach, a special replication degree $r_c$ is used for PDS data where $r_c>r$. 
-The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
-$ k*r_c  + (c-E(c-c_u))*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
-\[
-\sigma \frac{r_c}{r} + \frac{c-e(c-c_u)}{c_u}.
-\]
 Since $\sigma$ is small (it is 2\% in our experiments),  
-term $\sigma \frac{r_c}{r}$ is small in the above expression.  
-Thus the impact on storage increase is very small even when we choose a large $r_c/r$ ratio. 
-For example, $r_c/r=2$ or 3.
+the impact of replication on storage increase is very small even 
+when we choose a large $r_c/r$ ratio.  For example, $r_c/r=2$ or 3.
 
-Next we  assess  the impact of losing $d$ machines 
+%In the VC approach, a special replication degree $r_c$ is used for PDS data where $r_c>r$. 
+%The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
+%$ k*r_c  + (c-E(c-c_u))*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
+%\[
+%\sigma \frac{r_c}{r} + \frac{c-e(c-c_u)}{c_u}.
+%\]
+%Since $\sigma$ is small (it is 2\% in our experiments),  
+%term $\sigma \frac{r_c}{r}$ is small in the above expression.  
+%Thus the impact on storage increase is very small even when we choose a large $r_c/r$ ratio. 
+%For example, $r_c/r=2$ or 3.
+
+Now we  assess  the impact of losing $d$ machines 
 to the the VC and VO approaches.  
@@
 \[
-V *p*N_1 *s  \approx c-E(c-c_u)\; \mbox{ and } \; 
+V *p*N_1 *s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
 V *p*N_2 *s  \approx c_u \sigma V_c.
@@
 \[
-V *p*N_o *s  = c_u  V_o.
+V *p*N_o *s  = (c- E_o(c-c_u) ) V_o.
 \]
@@
 each file block contains the hot low-level chunks shared by many VMs, and it also contains
-rare chunks which are not shared.  From the above equations:
+rare chunks which are not shared.  Since $c>> c_u$, from the above equations:
 \[
-\frac{N_1}{N_o} \approx  \frac{c-E(c-c_u)}{c_uV_o}.
+\frac{N_1}{N_o} \approx  \frac{1-E_o}{(1-E_c) V_o}.
 \] 
-
-If we achieve very high deduplication efficiecny, then $N_1$ would be much smaller than $N_o$. 
+When $E_c\approx E_o$ as we demonstrate in Section~\ref{sect:evaldedup}, $N_1$ would be much smaller than $N_o$. 
 When there is a failure in file blocks with replication degree $r$
@@
 Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
-From data, we have observed that $N_1 +N_2 < N_o$ in practice. 
-This is likely because the PDS FSBs tightly pack data used by many VMs, 
-which decreases the overall number of FSBs required to backup a VM.
-Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
-VMs sharing each file block on average in VO.
+From data, we have observed that $N_1$ is much smaller than $N_o$.  
+In the evaluation discussed in Section~\ref{ref:evaldedup}, we have considered a worst case scenario that
+every PDS file block is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
+Even with that, the availability of VC snapshots is much higher than VO and we analyze  this below.
+%In fact, $N_1 +N_2 < N_o$. 
+%This is likely because the PDS FSBs tightly pack data used by many VMs, 
+%which decreases the overall number of FSBs required to backup a VM.
+%Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
+%VMs sharing each file block on average in VO.
 
@@
 % $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
-$A(r) < A(r_c)$.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
+$A(r) < A(r_c)$ because of  $r < r_c$.  
+Since $N_1$ is much smaller than $N_o$ as discussed previously, 
 these two conditions support that VC has a  higher availability. 

### 2013-09-25 snapshot_system/fast14_architecture.tex
revisions

@@
 In snapshot and segment recipes, 
-the data structures  includes reference to the actual data location to eliminate the need for additional indirection.
+the data structures  include reference to the actual data location to eliminate the need for additional indirection.
 
@@
 
-We decide not to take the sampled index appraoch~\cite{Guo2011} 
+We decide not to take the sampled index approach~\cite{Guo2011} 
 for detecting duplicates from PDS.
@@
 about 10 snapshot stored for every VM customer. When there is
-a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
+a new snapshot created every day,  there will be  a snapshot expired every day to maintain
 balanced storage use.
@@
 However, among all the chunks to be deleted, 
-there is a small percentage of unused chunks  which
+there are a small percentage of unused chunks  which
 are misjudged as  being in use, resulting in storage leakage.
@@
 Assume that  a VM keeps $h$ snapshots in the backup storage, creates and deletes one snapshot
-everyday. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
+every day. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
 number of additional unique chunks added from one snapshot to the next snapshot version. Then the total number of unique
@@
 increase the probability of being a 0 bit in all $h$ summary vectors.
-Thus the probablity that a particular bit is 0  in all $h$ summary vectors is  
+Thus the probability that a particular bit is 0  in all $h$ summary vectors is  
 $(1- \frac{1}{z}) ^{j U}$. 
@@
 each VM keeps $h=10$ snapshots and each snapshot has
-about 1-5\% of new data. Thus $\frac{\Delta u}{u} \leq 0.05$. For a 40GB snapshot, $u\approx  10$ millions.
-Then $U=10.45$ millions.
+about 1-5\% of new data. Thus $\frac{\Delta u}{u} \leq 0.05$. For a 40GB snapshot, $u\approx  10$ million.
+Then $U=10.45$ million.
 We choose  $\epsilon = 0.01$ and $\tau=0.1$.  From Equation~\ref{eq:falserate}, 
@@
 only one full leak repair for one physical machine scheduled for every 12 days. 
-Each repairs uses at most  90MB memory on average
+Each repair uses at most  90MB memory on average
 as discussed earlier and takes a short period of time.

### 2013-09-25 snapshot_system/fast14_background.tex
revisions

@@
 
-Our key design consideration is VM dependence minimization during deduplication and file block management.
+Our key design consideration is VM dependence minimization during deduplication and file system block management.
 \begin{itemize}
@@
 Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
-deduplication efficiency, and  can faciltate parallel execution of snaptshot operations.
+deduplication efficiency, and  can facilitate parallel execution of snapshot operations.
 \item{\em  Management of file system blocks.}
-The file block size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
-while the data chunk in a typical deduplication system is of a nonuniform size with 4KB or 8KB on average.
-Packaging data chunks to a file system block can create more data dependencies among VMs
-since a file block can be shared by even more VMs.
-Thus we need to consider a minimum association of a fie system block to VMs in the packaging process.
+The file system block (FSB) size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
+while the data chunk in a typical deduplication system is of a non-uniform size with 4KB or 8KB on average.
+Packaging data chunks to a FSB can create more data dependencies among VMs
+since a file system block can be shared by even more VMs.
+Thus we need to consider a minimum association of FSBs to VMs in the packaging process.
 \end{itemize}
@@
 {\em Version-based change detection}.
-VM snapshots can be  backed up  incrementally by identifying file  blocks that have
+VM snapshots can be  backed up  incrementally by identifying file segments that have
 changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
@@
 partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011} 
-that divides the deduplication work with a similarity approximation. This work 
+Stateless data routing divides the deduplication work with a similarity approximation. This work 
 is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 

### 2013-09-25 snapshot_system/fast14_evaluation.tex
rvise formula
revisions

--- 2013-09-25 snapshot_system/fast14_evaluation.tex
@@
 Alibaba Aliyun's cloud platform with about 100 machines. 
-Each machine hosts upto 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage system while
+Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage system while
 a user may instruct extra snapshots to be saved.
@@
 %Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
-We assume that every VM points to every filesystem block in the PDS ($V_c=p*V$), which is to be expected when PDS
+We assume that every VM points to every file system block in the PDS ($V_c=p*V$), which is to be expected when PDS
 blocks are sorted by hash, as their order is randomized.
@@
 %as storage nodes fail. 
-%We assume a random distirbution of 64MB filesystem
+%We assume a random distirbution of 64MB file system
 %blocks (FSBs). where FSBs are not randomly distributed availability might
@@
 Although the loss of a PDS block affects many VMs,
-by increasing replication for those blocks we minimize the affect on VM availability.
+by increasing replication for those blocks we minimize the effect on VM availability.
 %By having extra replicas for the PDS data, we reduce the failure rate of PDS
@@
 \subsection{Deduplication Efficiency}
+\label{sect:evaldedup}
+
 %this version combines the old and the minhash alg. to compare against srb
@@
 Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
-with a competitive deduplication efficiency.
+with competitive deduplication efficiency.
 
@@
 % Thus this represents a tradeoff: VC provides better fault tolerance and fast
-% approximate deletion with a competitive (but slightly lower) deduplication
+% approximate deletion with competitive (but slightly lower) deduplication
 % efficiency.
@@
 %because we are rewarded by architecture-wise benefits such as fault-tolerance and fast 
-%Though not our primary goal, this result does show that VC can remove a competitive amount of duplicates.
+%Though not our primary goal, this result does show that VC can remove competitive amount of duplicates.
 
@@
 % dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
-% which leads about 75.86\% reduction.
+% which leads about a 75.86\% reduction.
 % Similarity-guided local search can further reduce the data size
-% to about 12.05\% of original size, namely it delivers additional 12.09\% reduction.
+% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
 % The PDS-based global duplicate detection with $\sigma=2\% $
 % can reduce the size further to 8.6\% of original size, namely it 
-% delivers additional 3.45\% reduction.
+% delivers an additional 3.45\% reduction.
 In general, our experiments show that
 dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
-which leads to about 75.86\% reduction.
+which leads to about a 75.86\% reduction.
 Similarity-guided local search can further reduce the data size
-to about 12.05\% of original, namely it delivers 50.08\% reduction to the dirty segments.
+to about 12.05\% of original, namely it delivers a 50.08\% reduction to the dirty segments.
 The popularity-guided global deduplication with $\sigma=2\% $
-can reduce the data further to 8.6\% of its original size, 
+can reduce the data further to 8.6\% of its original size, so
 it provides additional 28.63\% reduction to the remaining data.
@@
 Allocating  one extra  copy for PDS data only adds  7GB in total per machine.
-Thus PDS replication degree 6 only adds the total space by 0.685\% while PDS replication degree 9 adds 1.37\% 
+Thus PDS replication degree 6 only increases the total space by 0.685\% while PDS replication degree 9 adds 1.37\% 
 space overhead, which is still small.
@@
 per machine with 6 concurrent backup tasks.
-With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine under 1.31 hours.
+With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.
 
@@
 %the file system. The main bottleneck here is that our QFS installation only
-%manages one disk per node, which prevents it from fully utilizing the the
+%manages one disk per node, which prevents it from fully utilizing the
 %benefits of parallel disk access. We expect our architecture can

### 2013-09-26 snapshot_system/fast14_abstract.tex
revisions. moved from inner/cross-VM to local/global dedup

@@
 reduces network traffic;
-however, performng global deduplication and letting a data block be shared
+however, performing global deduplication and letting a data block be shared
 by many virtual machines is resource expensive and less fault-resilient. 
@@
 search and associates  underlying file blocks with one VM for most cases.
-It restricts cross-VM deduplication to popular blocks with extra replication support.
+It restricts global deduplication to popular blocks with extra replication support.
 Our analysis shows that  this VM centric scheme 
 can  provide  better fault tolerance while using a small amount of computing and storage resources. 
-This  paper  describes a comparative evaluation of this scheme in  accomplishing a competitive deduplication 
+This  paper  describes a comparative evaluation of this scheme in  accomplishing competitive deduplication 
 efficiency while sustaining a good backup throughput. 

### 2013-09-26 snapshot_system/fast14_deduplication.tex

@@
 and cannot afford a small segment size.
-It should be noted that dirtybit tracking is supported or can be easily implemented in 
+It should be noted that dirty bit tracking is supported or can be easily implemented in 
 major virtualization solution vendors. For example,
@@
 
-Since the best deduplication uses a nonuniform chunk size 
-in the average of 4K or 8K~\cite{Jin2009},
+Since the best deduplication uses a non-uniform chunk size 
+in the average of 4KB or 8KB~\cite{Jin2009},
 we conduct additional local similarity guided deduplication on a snapshot by comparing
@@
 which contain chunk fingerprints to be compared.
-To control the time cost of search, we set a limit on the the number of  similar segments recipes to be fetched. 
+To control the time cost of search, we set a limit on the number of  similar segments recipes to be fetched. 
 % Then,
@@
 We define chunk popularity as the number of unique copies of the chunk in the data-store,
-that is the number of copies of the chunk after local deduplication.
-This number can be computed periodically (e.g., on a weekly basis).
+i.e., the number of copies of the chunk after local deduplication.
+This number can be computed periodically, e.g., on a weekly basis.
 Once the popularity of all data chunks is collected, the system only maintains the top $k$
@@
 to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
-accumulate small local chunks. We manage this accumulation process using an log-structured storage scheme built
+accumulate small local chunks. We manage this accumulation process using a log-structured storage scheme built
 on a distributed file system discussed in Section~\ref{sect:architecture}.
@@
 \hline
-$N_1$ & the average number  of non-PDS file system blocks  in a VM for VC\\
+$N_1$ & the average number  of non-PDS FSBs in a VM for VC\\
 \hline
-$N_2$ & the average number  of PDS file system blocks  in a VM for VC\\
+$N_2$ & the average number  of PDS FSBs in a VM for VC\\
 \hline
-$N_o$ & the average number  of file system blocks  in a VM for VO\\
+$N_o$ & the average number  of FSBs  in a VM for VO\\
 \hline
-A(r) & the availability of a file system block with replication degree $r$\\
+A(r) & the availability of an FSB with replication degree $r$\\
 \hline
@@
 By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
-The total amount of chunks reside in our backup storage which
+The total number of chunks in our backup storage which
 has local duplicates excluded is $c (1-\delta)$, this can be represented
@@
 
-We store the PDS index using a distributed shared memory hashtable such as Memcached
+We store the PDS index using a distributed shared memory hash table such as Memcached
 and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
@@
 $\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
-While the predicted value remains flat, PDS  coverage actually increases as more VMs are involved.
-increases. This is because actual $\alpha$ value increases with the data size.
+While the predicted value remains flat, measured PDS coverage increases as more VMs are involved.
+This is because the actual $\alpha$ value increases with the data size.
 %Then  PDS coverage PDS increases as more VMs are involved.
 
-\subsection{ Impact Fault Isolation}
+\subsection{ Impact on Fault Isolation}
 
@@
     \centering
-    \subfigure[Sharing of file blocks under VC]
+    \subfigure[Sharing of file system blocks under VC]
     {
@@
     \\
-    \subfigure[Sharing of file blocks under VO]
+    \subfigure[Sharing of file system blocks under VO]
     {
@@
     }
-    \caption{Bipartite association of VMs and file blocks under (a) VC and (b) VO. }
+    \caption{Bipartite association of VMs and file system blocks under (a) VC and (b) VO. }
     \label{fig:share}
@@
 The replication degree of the backup storage 
-is $r$ for regular file blocks and $r=3$ is a typical setting in distributed
+is $r$ for regular file system blocks and $r=3$ is a typical setting in distributed
 file systems~\cite{googlefs03,hdfs10}.
@@
 Now we  assess  the impact of losing $d$ machines 
-to the the VC and VO approaches.  
+to the VC and VO approaches.  
 A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
-We use file system blocks rather than a deduplication
+We use FSBs rather than a deduplication
 data chunk as our unit of failure because the DFS keeps
-filesystem blocks as its base unit of storage.
+file system blocks as its base unit of storage.
 To compute the full availability of all snapshots of a VM, we derive
-the probability of losing a snapshot file block of a VM by
+the probability of losing a snapshot FSB of a VM by
 estimating the number of file system blocks per VM in each approach.
@@
 we build a bipartite graph representing the association from unique file system blocks
-to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
+to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
 if this block is used by the VM.
 
-For VC, each VM has an average number of $N_1$ non-PDS file system blocks
-and  has  an average of  $N_2$ PDS file system blocks. 
-Each non-PDS file system block is associated with one VM
- and  we denote that PDS file system blocks are
-shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block, 
+For VC, each VM has an average number of $N_1$ non-PDS FSBs
+and  has  an average of  $N_2$ PDS FSBs. 
+Each non-PDS FSB is associated with one VM
+ and  we denote that PDS FSBs are
+shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file system block, 
 $V$ be the average number of VMs hosted on each machine. Then, 
@@
 
-For VO, each VM has an average of $N_o$ file system blocks
-and let $V_o$ be the average number of VMs shared by each file system block.
+For VO, each VM has an average of $N_o$ FSBs
+and let $V_o$ be the average number of VMs shared by each FSB.
 \[
@@
 
-Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
-each file block contains the hot low-level chunks shared by many VMs, and it also contains
+Since each FSB (with default size $64MB$) contains many chunks (on average 4KB),
+each FSB contains the hot low-level chunks shared by many VMs, and it also contains
 rare chunks which are not shared.  Since $c>> c_u$, from the above equations:
@@
 When $E_c\approx E_o$ as we demonstrate in Section~\ref{sect:evaldedup}, $N_1$ would be much smaller than $N_o$. 
-When there is a failure in file blocks with replication degree $r$
+When there is a failure in FSBs with replication degree $r$
 and there is no failure for PDS data with more replicas,   a VM in
@@
 In the evaluation discussed in Section~\ref{ref:evaldedup}, we have considered a worst case scenario that
-every PDS file block is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
+every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
 Even with that, the availability of VC snapshots is much higher than VO and we analyze  this below.
@@
 Then the availability of one VM's snapshot data under VO approach is the probability that
- all its file system blocks are unaffected during the system failure:
+ all its FSBs are unaffected during the system failure:
 \begin{equation}
@@
 \item
-When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
+When $r_c \leq d$, both non-PDS and PDS file system blocks in VC can have a loss.
 The full snapshot availability of  a VM in the VC approach is
@@
 %that the availability of an individual file system block
-with different replication degrees. This demonstrates inequality 
+different replication degrees. This demonstrates inequality 
 % $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$

### 2013-09-26 snapshot_system/fast14_architecture.tex
update

@@
 In snapshot and segment recipes, 
-the data structures  include reference to the actual data location to eliminate the need for additional indirection.
+the data structures  include references to the actual data location to eliminate the need for additional indirection.
 
@@
     \centering
-    \includegraphics[width=3in]{images/socc_arch_cluster}
+    \includegraphics[width=2.75in]{images/socc_arch_cluster}
     \caption{System architecture and data flow during snapshot write}
@@
   \centering
-  \epsfig{file=images/sstore_arch, width=3in}
+  \includegraphics[width=2.75in]{images/sstore_arch}
   \caption{Data structure of a VM snapshot store.}
@@
 
-\begin{itemize}
-\item Data of each VM snapshot store, excluding the PDS store, are divided into a set of containers and 
+%\begin{itemize}
+%\item
+Data of each VM snapshot store, excluding the PDS store, are divided into a set of containers and 
 each container is approximately 1GB. 
@@
 
-\item Each data container is represented by three files in the DFS:
+%\item
+Each data container is represented by three files in the DFS:
 1) the container data file holds the actual content, 
@@
 
-\item A data chunk reference stored in the index of snapshot recipes
+%\item
+A data chunk reference stored in the index of snapshot recipes
 is composed of two parts: a container ID with 2 bytes and a local chunk ID with 6 bytes.
@@
 
-\item The PDS chunks are stored in one PDS file. 
+%\item
+The PDS chunks are stored in one PDS file. 
 Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
@@
 which is not sufficient to enable effective prefetching which is required for index sampling.
-\end{itemize}
+%\end{itemize}
 
-The snapshot  store supports three API calls.
-\begin{itemize}
-\item {\em Append()}. 
+The snapshot  store supports three API calls:
+%\begin{itemize}
+
+%\item
+\noindent\textbf{Append()}. 
 For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
@@
 
-\item{\em Get()}.
+%\item
+\noindent\textbf{Get()}.
 The fetch operation for the PDS data chunk is straightforward since each reference contains 
-the file offset and the size of a PDS chunk is available from a segment recipe.
+the file offset, and the size of a PDS chunk is available from a segment recipe.
 We also maintain a small data cache for the PDS data service to speedup common data fetching.
@@
 anticipate future sequential reads.
-\item {\em Delete()}.
+
+%\item
+\noindent\textbf{Delete()}.
 Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user
@@
 depend directly on physical storage locations, which simplifies data migration.
-\end{itemize}
+%\end{itemize}
 

### 2013-09-26 snapshot_system/fast14_abstract.tex
revise

@@
 Our analysis shows that  this VM centric scheme 
-can  provide  better fault tolerance while using a small amount of computing and storage resources. 
+can  strike a balance for better fault isolation with competitive  deduplication efficiency
+while using a small amount of computing and storage resources. 
 This  paper  describes a comparative evaluation of this scheme in  accomplishing competitive deduplication 

### 2013-09-26 snapshot_system/fast14_deduplication.tex
revise

@@
 \hline
-$N_1$ & the average number  of non-PDS FSBs in a VM for VC\\
+$N_1$ & the average number  of non-PDS FSBs blocks in a VM for VC\\
 \hline
@@
 the impact of replication on storage increase is very small even 
-when we choose a large $r_c/r$ ratio.  For example, $r_c/r=2$ or 3.
+when choosing  $r_c/r$ ratio as 2 or 3.
 
@@
 A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
-We use FSBs rather than a deduplication
+We use an FSB rather than a deduplication
 data chunk as our unit of failure because the DFS keeps
@@
 \[
-V *p*N_1 *s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
-V *p*N_2 *s  \approx c_u \sigma V_c.
+V pN_1 s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
+V pN_2 s  \approx c_u \sigma V_c.
 \]
@@
 \[
-V *p*N_o *s  = (c- E_o(c-c_u) ) V_o.
+V pN_o s  = (c- E_o(c-c_u) ) V_o.
 \]
@@
 \] 
-When $E_c\approx E_o$ as we demonstrate in Section~\ref{sect:evaldedup}, $N_1$ would be much smaller than $N_o$. 
-When there is a failure in FSBs with replication degree $r$
-and there is no failure for PDS data with more replicas,   a VM in
-the VC approach has a much lower chance to lose a snapshot than VO. 
+When $E_c$ is close to $E_o$ as demonstrated in Section~\ref{sect:evaldedup}, $N_1$ is 
+much smaller than $N_o$. 
+%When there is a failure in FSBs with replication degree $r$
+%and there is no failure for PDS data with more replicas,   a VM in
+%the VC approach has a much lower chance to lose a snapshot than VO. 
 %Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
@@
 %Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
-Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
-From data, we have observed that $N_1$ is much smaller than $N_o$.  
-In the evaluation discussed in Section~\ref{ref:evaldedup}, we have considered a worst case scenario that
-every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
-Even with that, the availability of VC snapshots is much higher than VO and we analyze  this below.
+Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO
+and  $N_1$ is indeed  much smaller than $N_o$ in our tested dataset.  
 %In fact, $N_1 +N_2 < N_o$. 
@@
 the VC approach has a higher availability of VM snapshots than VO.
+In the evaluation discussed in Section~\ref{sect:evaldedup}, we have considered a worst case scenario that
+every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
+Even with that, the availability of VC snapshots is much higher than VO and we analyze  this below.
 
@@
 \end{equation}
+%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
+\end{itemize} 
+In the evaluation discussed in Section~\ref{sect:evaldedup}, we have considered a worst case scenario that
+every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
+Even with that, the availability of VC snapshots is still much higher than VO and  
+there are two reasons.  1) $N_1$ is much smaller than $N_o$ as discussed previously.
+2)  $A(r) < A(r_c)$ because of  $r < r_c$.  
 Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
 %that the availability of an individual file system block
-different replication degrees. This demonstrates inequality 
+different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.
+
 % $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
-$A(r) < A(r_c)$ because of  $r < r_c$.  
-Since $N_1$ is much smaller than $N_o$ as discussed previously, 
-these two conditions support that VC has a  higher availability. 
-%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
-\end{itemize}
 
@@
         \hline
-        \multirow{2}{*}{Failuresi ($d$)}   & \multicolumn{3}{c|}{$A(r_c)$} \\
+        \multirow{2}{*}{Failures ($d$)}   & \multicolumn{3}{c|}{$A(r_c)\times 100\%$} \\
                                     %\cline{2-4}

### 2013-09-26 snapshot_system/fast14_evaluation.tex
revise

@@
 %Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
-We assume that every VM points to every file system block in the PDS ($V_c=p*V$), which is to be expected when PDS
-blocks are sorted by hash, as their order is randomized.
+We have assumed a worst-case scenario that  a PDS block is shared by every VM. 
+%($V_c=p*V$), which is to be expected when PDS
+%blocks are sorted by hash, as their order is randomized.
 %$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
@@
 %based on measured values in our dataset.
-To obtain VO sharing of file blocks, we perform perfect deduplication over 105 VMs, 
-append unique chunks to a DFS file and
-count the number of dependencies from a file system block to VM.
+%To obtain VO sharing of file blocks, we perform perfect deduplication over 105 VMs, 
+%append unique chunks to a DFS file and
+%count the number of dependencies from a file system block to VM.
 %In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
 %case for VO approach. 
-Our results show that even the worst case for VC (where $v_c=p*V$) has a higher availability than VO.
+Our results show that even the worst case,  VC  still has a significantly  higher availability than VO as the number of
+failed machines increases.
 %Our VM-centric approach shows significant improvements
@@
 
-Figure~\ref{fig:exbin-efficiency-graph2} also shows the effectiveness of the local similarity-based search in VC.
-Without this (i.e. when we only check the parent segment at the same offset), when an entire
-segment is moved to another location on disk, for example when a file is rewritten
-rather than modified in place, the deduplication opportunity is missed. We have found that in
+Figure~\ref{fig:exbin-efficiency-graph2} also shows the curve  of VC without local similarity search.
+Adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
+That is one significant improvement compared to the work in ~\cite{WeiZhangIEEEClound}.
+The reason is that  
+%Without this (i.e. when we only check the parent segment at the same offset), 
+when a data  segment is moved to another location on disk, for example when a file is rewritten
+rather than modified in place,  dirty-bit based detection would not be able to detect such a movement.
+ We have found that in
 approximately 1/3 of the VMs in our dataset this movement happens frequently,
@@
 receipt metadata and cache. 
-``Read'' column is controlled as 50MB/s bandwidth usage so that other cloud services are not impacted a lot.
+``Read'' column is controlled as 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted a lot.
 ``Write'' column is the I/O write usage of QFS and notice that each QFS write leads writes in multiple machines due to
@@
     \end{tabular}
-\caption{Throughput of software layers under different concurrency}
+\caption{Throughput of software layers per machine under different concurrency}
 \label{tab:throughput}
@@
 Table~\ref{tab:throughput} shows the  average throughput of software layer
-when I/O is throttled under 50MB/second and when there is no restriction.
+when when I/O throttling is not applied to control the usage.
 %machine when all machine nodes execute one or multiple MV backup tasks.
 ``Backup'' column is the throughput  of the backup service  per machine.
-``Snapshot store" is the  write throughput of the snapshot store layer and the gap between this
-column and  ``Raw" column is caused by significant data reduction by dirty bit and duplicate
+``Snapshot store" is the  write throughput of the snapshot store layer. The gap between this
+column and  ``Backup" column is caused by significant data reduction by dirty bit and duplicate
 detection. Only non-duplicate chunks trigger a snapshot store write.

### 2013-09-26 snapshot_system/fast14_introduction.tex
revise

@@
 backup operations can run simultaneously without a central  bottleneck.
-This  VM-centric solution uses  a small amount of  memory while delivering a reasonable deduplication efficiency.
+This  VM-centric solution uses  a small amount of  memory while delivering reasonable deduplication efficiency.
 
@@
 with a VM-centric approach. 
-Section~\ref{sect:deduplication}  analyzes the tradeoffs and benefits of our approach. 
+Section~\ref{sect:deduplication}  analyzes the tradeoff and benefits of our approach. 
 Section~\ref{sect:architecture}  describes our system architecture and implementation details.

### 2013-09-26 snapshot_system/fast14_evaluation.tex
revise

@@
 Adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
-That is one significant improvement compared to the work in ~\cite{WeiZhangIEEEClound}.
+That is one significant improvement compared to the work in ~\cite{WeiZhangIEEEClound}
+which uses the parent segment at the same offset to detect duplicates locally.
 The reason is that  
-%Without this (i.e. when we only check the parent segment at the same offset), 
+%Without this (i.e. when we only 
 when a data  segment is moved to another location on disk, for example when a file is rewritten
@@
 \begin{table}[htbp]
+\begin{small}
     \centering
@@
     backup tasks            & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-4}
-    per node                & Backup                                     & Snapshot Store & QFS  \\ \hline
+    per machine                & Backup                                     & Snapshot Store & QFS  \\ \hline
     1                       & 1369.6                                     & 148.0          & 35.3 \\
@@
     \end{tabular}
+\end{small}
 \caption{Throughput of software layers per machine under different concurrency}

### 2013-09-26 snapshot_system/fast14_abstract.tex

--- 2013-09-26 snapshot_system/fast14_abstract.tex
@@
 search and associates  underlying file blocks with one VM for most cases.
-It restricts global deduplication to popular blocks with extra replication support.
+It restricts global deduplication to popular chunks with extra replication support.
 Our analysis shows that  this VM centric scheme 
-can  provide  better fault tolerance while using a small amount of computing and storage resources. 
-This  paper  describes a comparative evaluation of this scheme in  accomplishing competitive deduplication 
-efficiency while sustaining a good backup throughput. 
+can  strike a balance for better fault isolation with competitive  deduplication efficiency
+while using a small amount of computing resources. 
+This  paper  describes a comparative evaluation of this scheme to assess  its deduplication 
+efficiency and backup throughput. 
 \end{abstract}

### 2013-09-26 snapshot_system/fast14_conclusion.tex

@@
 Evaluation using  VM backup data shows that VC strikes a tradeoff and 
-can accomplish close to 97\% of what complete global
+can accomplish 96.33\% or 96.9\% of what complete global
 deduplication can do while the availability of snapshots increases substantially with this VM-centric

### 2013-09-26 snapshot_system/fast14_deduplication.tex

@@
 most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
-Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
-this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
-analytic design guidance.
+%Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
+%this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
+%analytic design guidance.
 
@@
 file systems~\cite{googlefs03,hdfs10}.
-Since $\sigma$ is small (it is 2\% in our experiments),  
+Since $\sigma$ is small (e.g.  2\% in our experiments),  
 the impact of replication on storage increase is very small even 
@@
         columns/Availability3/.style={
-            column name={\multicolumn{3}{c|}{$A(r_c)$}\\&$r_c=3$},
+            column name={\multicolumn{3}{c|}{$A(r_c) \times 100\%$}\\&$r_c=3$},
             fixed, precision=9

### 2013-09-26 snapshot_system/fast14_architecture.tex
update

@@
   \centering
-  \epsfig{file=images/deletion.png, width=3in}
+  \epsfig{file=images/deletion.pdf, width=3in}
   \caption{Approximate deletion}
@@
 We seek a fast solution with low resource usage to delete snapshots and
-the VM-centric design simplifies the deletion process. 
+our VM-centric design simplifies the deletion process. 
 Since PDS is small and separated, we can focus on  unreferenced non-PDS chunks within each VM. 
@@
 \begin{itemize}
-\item {\bf Computation for snapshot fingerprint summary.}
+\item {\bf Computation for snapshot reference summary.}
 Every time there is a new snapshot created,
-we compute a Bloom-filter with $z$ bits as the reference summary for all non-PDS chunks used 
-in this snapshot. Given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
+we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
+in this snapshot,
+the items we put into summary vector are all the references that are used in its snapshot and segment recipes.
+Foe each VM we preset the vector size according to  estimation of VM image size,
+given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
 
@@
 we need to identify if  chunks to be deleted from that snapshot
-are still used by other snapshots. 
+are still referenced by other snapshots. 
 This is done approximately and quickly by comparing the 
@@
 This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
-That requires a scanning of all chunks in a VM. Since it is a VM-specific procedure 
+That requires a scan of all the metadata in a single VM backup. Since it is a VM-specific procedure 
 the space and time cost is relatively small compared to the traditional mark-sweep procedure~\cite{Guo2011} which scans snapshot 
@@
 every day. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
-number of additional unique chunks added from one snapshot to the next snapshot version. Then the total number of unique
-chunks used in a VM is about:
+number of additional chunks added from one snapshot to the next snapshot version. Then the total number of 
+chunks stored in a VM's snapshot store is about:
 \[
@@
 \[
-L = R \Delta u \epsilon.
+L = R \epsilon \Delta u.
 \]
@@
 For example in our tested dataset,  
-each VM keeps $h=10$ snapshots and each snapshot has
-about 1-5\% of new data. Thus $\frac{\Delta u}{u} \leq 0.05$. For a 40GB snapshot, $u\approx  10$ million.
-Then $U=10.45$ million.
+each VM keeps $h=10$ snapshots and each snapshot adds
+about 0.1-4\% of new data. Thus we take ${\Delta u}/{u} \approx 0.02$. For a 40GB snapshot, $u\approx  10$ million.
+Then $U=11.8$ million.
 We choose  $\epsilon = 0.01$ and $\tau=0.1$.  From Equation~\ref{eq:falserate}, 
-$z=10U=100.45$ million bits. From Equation~\ref{eq:leakrepair}, 
-leak repair should be triggered once for every R=290 runs of approximate deletion. 
+each summary vector requires $z=10U=118$ million bits. From Equation~\ref{eq:leakrepair}, 
+leak repair should be triggered once for every R=590 runs of approximate deletion. 
 When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
-only one full leak repair for one physical machine scheduled for every 12 days. 
+only one full leak repair for one physical machine scheduled for every 23.6 days. 
 Each repair uses at most  90MB memory on average

### 2013-09-26 snapshot_system/fast14_evaluation.tex
update

@@
 Adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
-That is one significant improvement compared to the work in ~\cite{WeiZhangIEEEClound}
+That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
 which uses the parent segment at the same offset to detect duplicates locally.
@@
     \centering
-    \begin{tabular}{c|ccc}
-    Num. of concurrent      & \multicolumn{3}{c}{Throughput without}    \\
-    backup tasks            & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-4}
+    \begin{tabular}{|c|ccc|}
+\hline
+    Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    \\
+    backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} \\ \cline{2-4}
     per machine                & Backup                                     & Snapshot Store & QFS  \\ \hline
@@
     4                       & 4101.8                                     & 443.3          & 103.1 \\
-    6                       & 5456.5                                     & 589.7          & 143.8 \\
+    6                       & 5456.5                                     & 589.7          & 143.8 \\ \hline
     \end{tabular}
@@
 storage space per VM caused  by approximate deletions.
-The solid line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
-while the dashed line is the actual leakage measured during the experiment.
-% [OTHER PARAMETERS USED]
-After 9 snapshot deletions, the actual leakage reaches 0.01\% and this means that
-there is only 1MB space leaked for every 10GB of stored data.
+The dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
+given $\Delta u/u=0.02$,
+while the top solid line represents the actual leakage measured during the experiment 
+with the same $\Delta u/u=0.02$ setting for summary vectors.
+After 9 snapshot deletions, the actual leakage reaches 0.0018\% and this means that
+there is only 1.8MB space leaked for every 1GB of stored data. 
+We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.
+As this value increases, larger summary vectors are generated thus results in a decrease on the
+false-positive ratio, therefore less amount of unused chunks are misjudged.

### 2013-09-26 snapshot_system/fast14_evaluation.tex
revisions

@@
 using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
-a machine, this chunk is compared with the fingerprint index within this machine locally.
+a machine, the chunk is compared with the fingerprint index within this machine locally.
 
@@
 approximately 1/3 of the VMs in our dataset this movement happens frequently,
-so the similarity search becomes important for those VMs.
+so the similarity search becomes especially important for those VMs.
 % In general, our experiments show that
@@
 We have further studied the memory and disk bandwidth usage 
-when running concurrent VM snapshot backup on each machine with $\delta=2\%$. 
+when running concurrent VM snapshot backup on each machine with $\sigma=2\%$. 
 Table ~\ref{tab:resource_usage} gives the resource usage  when
@@
 receipt metadata and cache. 
-``Read'' column is controlled as 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted a lot.
+``Read'' column is controlled as 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted too much.
 ``Write'' column is the I/O write usage of QFS and notice that each QFS write leads writes in multiple machines due to
@@
 more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
-a lot because of the controlled  disk read time.
+significantly because of the controlled  disk read time.
 %,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
@@
 VC uses $\sigma=2\%$ and $4\%$.
-It has a breakdown of time for reading data, updating the metadata, network latency to visit
+It has a breakdown of time for reading data and updating the metadata, network latency to visit
 a remote machine, and index access for fingerprint comparison.
@@
 and perform comparison.
-VC is faster for index access because it conducts in-memory local search first and then
+VC is faster in this regard because it conducts in-memory local search first and then
 accesses  the PDS on distributed shared memory, so most chunks can be dealt with locally.  

### 2013-09-26 snapshot_system/fast14_architecture.tex

@@
 that have been made to the virtual disk.
-Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicating whether the segment
+Every bit in the bitmap represents a fixed-sized (2MB) region called a \textit{segment}, indicating whether the segment
 has been modified since last backup. 
@@
 After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
-For data modification during backup, a copy-on-write protection is set so that backup can continue to
+For data modification during backup, copy-on-write protection is set so that backup can continue to
 copy  a specific version while new changes are still recorded.
@@
 There is also a special store containing all PDS chunks shared among different VMs.
-As shown in Figure~\ref{fig:as_arch}, we explain the data structure of snapshot stores as follows.
+As shown in Figure~\ref{fig:as_arch}, we explain the data structure of the snapshot stores as follows.
 \begin{figure}[htbp]
@@
 In writing a chunk during backup, the system accumulates data chunks and stores the entire
-group as a unit after a compression.
+group as a unit after compression.
 When accessing a particular chunk, its chunk group is retrieved from the storage
-and uncompressed. Given the high spatial locality and usefulness of prefetching  in 
+and decompressed. Given the high spatial locality and usefulness of prefetching  in 
 snapshot chunk accessing~\cite{Guo2011,foundation08},
@@
 Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user
-and we will discuss the snapshot deletion in detail in the following subsection.
+(we will discuss the snapshot deletion in detail in the following subsection).
 When deletion requests are issued for a specific container,
@@
 Deduplication complicates the deletion process because space saving relies on the sharing of data
-and it requires the global reference of deleted chunks to be identified before  they can be safely removed.
+and it requires the global references to deleted chunks to be identified before  they can be safely removed.
 While we can use the mark-and-sweep technique~\cite{Guo2011}, 
@@
 That requires a scan of all the metadata in a single VM backup. Since it is a VM-specific procedure 
-the space and time cost is relatively small compared to the traditional mark-sweep procedure~\cite{Guo2011} which scans snapshot 
+the space and time cost is relatively small compared to the traditional mark-and-sweep procedure~\cite{Guo2011} which scans snapshot 
 chunks from all VMs.
@@
 consider each reference consumes 8 bytes plus  1 mark bit, a VM that has 40GB backup data with about
-10 million chunks will need less than 85MB of memory to complete a VM-specific mark-sweep process.
+10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process.
 \end{itemize}
@@
 Each repair uses at most  90MB memory on average
-as discussed earlier and takes a short period of time.
+%as discussed earlier
+and takes a short period of time.

### 2013-09-26 snapshot_system/fast14_architecture.tex
revise
update

@@
 each VM keeps $h=10$ snapshots and each snapshot adds
-about 0.1-4\% of new data. Thus we take ${\Delta u}/{u} \approx 0.02$. For a 40GB snapshot, $u\approx  10$ million.
-Then $U=11.8$ million.
+about 0.1-5\% of new data. Thus we take ${\Delta u}/{u} \approx 0.025$. For a 40GB snapshot, $u\approx  10$ million.
+Then $U=12.25$ million.
 We choose  $\epsilon = 0.01$ and $\tau=0.1$.  From Equation~\ref{eq:falserate}, 
-each summary vector requires $z=10U=118$ million bits. From Equation~\ref{eq:leakrepair}, 
-leak repair should be triggered once for every R=590 runs of approximate deletion. 
+each summary vector requires $z=10U=122.5$ million bits or 15MB. From Equation~\ref{eq:leakrepair}, 
+leak repair should be triggered once for every R=490 runs of approximate deletion. 
 When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
-only one full leak repair for one physical machine scheduled for every 23.6 days. 
+only one full leak repair for one physical machine scheduled for every 19.6 days. 
 Each repair uses at most  90MB memory on average

### 2013-09-26 snapshot_system/fast14_evaluation.tex
update
revise

@@
 %    1     & 19\% & 118.1 & 50MB/s 8.37 & 1.314\\ \hline
-    1     & 19\% & 118 & 50 & 8.4 & 1.31\\ \hline
+    1     & 19\% & 118 & 50 & 16.4 & 1.31\\ \hline
 %    2     & 35\% & 131.8 & 9.0 & 1.226\\ \hline
-    2     & 35\% & 132 &50  & 9.0 & 1.23\\ \hline
+    2     & 35\% & 132 &50  & 17.6 & 1.23\\ \hline
     %4     & 63\% & 154.1 & 9.3 & 1.179\\ \hline
-    4     & 63\% & 154&50   & 9.3 & 1.18\\ \hline
+    4     & 63\% & 154&50   & 18.3 & 1.18\\ \hline
 %    6     & 77\% & 171.9 & 9.46 & 1.162\\ \hline
@@
 storage space per VM caused  by approximate deletions.
-The dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
-given $\Delta u/u=0.02$,
+The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
+given $\Delta u/u=0.025$,
 while the top solid line represents the actual leakage measured during the experiment 
-with the same $\Delta u/u=0.02$ setting for summary vectors.
-After 9 snapshot deletions, the actual leakage reaches 0.0018\% and this means that
-there is only 1.8MB space leaked for every 1GB of stored data. 
+with the same $\Delta u/u=0.025$ setting for summary vectors.
+After 9 snapshot deletions, the actual leakage ratio reaches 0.0018 and this means that
+there is only 1.8MB space leaked for every 1GB of stored data, it is also obvious that
+the leakage grows linearly as we expect. 
 We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.

### 2013-09-26 snapshot_system/fast14_evaluation.tex
upate

@@
  \subsection{Effectiveness of Approximate Deletion}
+
  \begin{figure}
@@
      \includegraphics[width=3in]{figures/leakage}
-     \caption{Accumulated storage leakage by approximate snapshot deletions}
+     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
      \label{fig:leakage}
@@
 the leakage grows linearly as we expect. 
-We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.
-As this value increases, larger summary vectors are generated thus results in a decrease on the
-false-positive ratio, therefore less amount of unused chunks are misjudged.
+% We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.
+% As this value increases, larger summary vectors are generated thus results in a decrease on the
+% false-positive ratio, therefore less amount of unused chunks are misjudged.

### 2013-09-26 snapshot_system/fast14_architecture.tex
update

@@
 Then $U=12.25$ million.
-We choose  $\epsilon = 0.01$ and $\tau=0.1$.  From Equation~\ref{eq:falserate}, 
+We choose  $\epsilon = 0.01$ and $\tau=0.05$.  From Equation~\ref{eq:falserate}, 
 each summary vector requires $z=10U=122.5$ million bits or 15MB. From Equation~\ref{eq:leakrepair}, 
-leak repair should be triggered once for every R=490 runs of approximate deletion. 
+leak repair should be triggered once for every R=245 runs of approximate deletion. 
 When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
-only one full leak repair for one physical machine scheduled for every 19.6 days. 
+only one full leak repair for one physical machine scheduled for every 9.8 days. 
+If $\tau = 0.1$ then leakage repair only occurs every 19.6 days.
 Each repair uses at most 90MB memory on average

### 2013-09-26 snapshot_system/fast14_architecture.tex

@@
 %to %manage  the physical disk storage. 
-All data needed for VM services, such as virtual disk images used by runtime VMs,
-and snapshot data for backup purposes, reside in this distributed file system. 
+All data needed for the backup service including snapshot and  metadata data
+%and snapshot data for backup purposes, 
+resides in this distributed file system. 
 One physical node hosts tens of VMs, each of which accesses its virtual machine disk image through the
@@
 For data modification during backup, copy-on-write protection is set so that backup can continue to
-copy  a specific version while new changes are still recorded.
+copy  a specific version while new changes are recorded.
 %copies a frozen version while the modification can still carry on.
@@
     \includegraphics[width=2.75in]{images/socc_arch_cluster}
-    \caption{System architecture and data flow during snapshot write}
+    \caption{System architecture and data flow during snapshot backup}
     \label{fig:arch_vm}
@@
 %\item
-Data of each VM snapshot store, excluding the PDS store, are divided into a set of containers and 
+PDS chunks are stored in one PDS file. 
+Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
+%There is an option to use a data structure similar to the non-PDS store. We opt
+%for the simpler format because
+Additional compression is not applied because PDS chunks have less spatial locality in data access. 
+For the data sets we have tested, we only observed very limited spatial locality 
+among popular data chunks. On average the number of consecutive PDS index hits is lower than 7.
+Thus it is not so effective to group a large number of chunks as a compression and data fetch unit. 
+For the same reason, we decide not to take the sampled index approach~\cite{Guo2011} 
+for detecting duplicates from PDS as limited spatial locality is not sufficient to enable
+effective prefetching for sampled indexing.
+
+PDS data is re-calculated periodically, but 
+the total data size is small.  When
+a new PDS data  set is computed, in-memory PDS index is replaced, but 
+the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
+The old data is not removed because they can still be referenced by the existing snapshots. 
+A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months).
+
+%\end{itemize}
+
+For non PDS data, the snapshot store of a VM is  divided into a set of containers and 
 each container is approximately 1GB. 
@@
 
-Each container is further divided into a set of chunk data groups. Each chunk group is composed of
+Each non-PDS data container is further divided into a set of chunk data groups. Each chunk group is composed of
 a set of data chunks and is the basic unit in data access and retrieval. 
 In writing a chunk during backup, the system accumulates data chunks and stores the entire
-group as a unit after compression.
+group as a unit after compression. This  compression can reduce data by several times  in our tested applications.
 When accessing a particular chunk, its chunk group is retrieved from the storage
@@
 retrieval of  a data chunk  group naturally works well with prefetching. 
-A  typical chunk group contains 100 to 1000 chunks, with an average size of 
-200-600 chunks.
+A  typical chunk group contains 1000 chunks in our experiment.
+% with an average size of 200-600 chunks.
 
@@
 %\item
-A data chunk reference stored in the index of snapshot recipes
+A non-PDS data chunk reference stored in the index of snapshot recipes
 is composed of two parts: a container ID with 2 bytes and a local chunk ID with 6 bytes.
@@
 %\item
-The PDS chunks are stored in one PDS file. 
-Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
-There is an option to use a data structure similar to the non-PDS store. We opt
-for the simpler format because
-PDS chunks have less spatial locality in data access and it is not so effective
-to group a large number of chunks
-as a compression and data fetch unit.
-
-PDS data is re-calculated periodically, but 
-the total data size is small.  When
-a new PDS data  set is computed, in-memory PDS index is replaced, but 
-the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
-The old data is not removed because they can still be referenced by the existing snapshots. 
-A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months).
-
-We decide not to take the sampled index approach~\cite{Guo2011} 
-for detecting duplicates from PDS.
-This is because for the data sets we have tested, we only observed very limited spatial locality 
-among popular data chunks. On average the number of consecutive PDS index hits is lower than 7,
-which is not sufficient to enable effective prefetching which is required for index sampling.
-%\end{itemize}
 
@@
 \noindent\textbf{Delete()}.
-Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user
-(we will discuss the snapshot deletion in detail in the following subsection).
+Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user and we discuss this in more details in next
+subsection.
+%(we will discuss the snapshot deletion in detail in the following subsection).
 When deletion requests are issued for a specific container,
@@
 only one full leak repair for one physical machine scheduled for every 9.8 days. 
-If $\tau = 0.1$ then leakage repair only occurs every 19.6 days.
-Each repair uses at most 90MB memory on average
+If $\tau = 0.1$ then leakage repair would occur every 19.6 days.
+Each repair uses less than 90MB memory on average
 %as discussed earlier

### 2013-09-26 snapshot_system/fast14_evaluation.tex
revise
figure updates

@@
 Our evaluation objective is to
-study the benefit in fault tolerance and   deduplication efficiency of VC and compare it
-with an alternative VO design. We also and assess backup throughput and  resource usage for a large number of VMs.
+study the benefit in fault tolerance and   deduplication efficiency of VC,  
+and assess its backup throughput and  resource usage.
 
@@
 Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
-The backup of VM snapshots is required to complete within few  hours every night.
+%The backup of VM snapshots is required to complete within few  hours every night.
 Based on our study of production  data,  each VM has about 40GB of storage  data  on average
@@
 %All data are divided into 2 MB fix-sized segments and 
-The signature for variable-sized blocks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
+The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
 %Each segment is divided into 
@@
 
-\subsection{Impact on Fault Isolation}
+\subsection{Fault Isolation and Snapshot Availability}
 
@@
 Although the loss of a PDS block affects many VMs,
-by increasing replication for those blocks we minimize the effect on VM availability.
+by increasing replication for those blocks we minimize the effect on snapshot availability.
 %By having extra replicas for the PDS data, we reduce the failure rate of PDS
@@
                     xlabel={\tiny Failed nodes},
-                    ylabel={\tiny VM Availability (\%)},
+                    ylabel={\tiny Snapshot Availability (\%)},
                     %extra y ticks={99.9}, %if important numbers are missing
@@
 		xlabel={\tiny Failed nodes},
-		ylabel={\tiny VM Availability (\%)},
+		ylabel={\tiny Snapshot Availability (\%)},
 		%extra y ticks={99.99}, %if important numbers are missing
@@
             column name={
-                \multicolumn{4}{c|}{VM Availability(\%)}\\&
+                \multicolumn{4}{c|}{Snapshot Availability(\%)}\\&
                 \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
@@
 
-Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
+Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC,
 % <<<<<<< HEAD
@@
 % =======
-Deduplication efficiency is defined as the percent of duplicate chunks
-which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
- We also compare several PDS sizes chosen for VC.
+namely the percent of duplicate chunks
+which are detected and removed.
+% so only global perfect deduplication can have 100\% efficiency.
+% We also compare several PDS sizes chosen for VC.
 %(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
@@
 The loss of efficiency in VC is caused by the restriction of the physical memory available
-in the cluster to support fast in-memory PDS index lookup. 
+in the cluster for fast in-memory PDS index lookup. 
 %In the extreme case if we put all the fingerprint into PDS 
@@
 Figure~\ref{fig:exbin-efficiency-graph2} also shows the curve  of VC without local similarity search.
-Adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
-That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
-which uses the parent segment at the same offset to detect duplicates locally.
+There is a big efficiency drop in this curve when the number of VMs is about 30.
 The reason is that  
@@
 when a data  segment is moved to another location on disk, for example when a file is rewritten
-rather than modified in place,  dirty-bit based detection would not be able to detect such a movement.
- We have found that in
-approximately 1/3 of the VMs in our dataset this movement happens frequently,
-so the similarity search becomes especially important for those VMs.
+rather than modified in place,  
+a dirty-bit or offset based detection would not be able to detect such a movement and 
+similarity search becomes especially important.  We have found that in
+approximately 1/3 of the VMs in our dataset this movement happens frequently.
+In general, adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
+That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
+which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
 % In general, our experiments show that
@@
 % delivers an additional 3.45\% reduction.
+
 In general, our experiments show that
@@
 %VC as the PDS replication degree changes while non-PDS replication degree is fixed as 3. 
-The total storage  for all VM snapshots in each physical machine takes about 3.065TB on average when
-the replication degree of both PDS and non-PDS data is 3. 
-Allocating  one extra  copy for PDS data only adds  7GB in total per machine.
+When the replication degree of both PDS and non-PDS data is 3, 
+the total storage  for all VM snapshots in each physical machine takes about 3.065TB on average before compression
+and 0.75TB after compression.  Allocating  one extra  copy for PDS data only adds  7GB in total per machine.
 Thus PDS replication degree 6 only increases the total space by 0.685\% while PDS replication degree 9 adds 1.37\% 
@@
     4     & 63\% & 154&50   & 18.3 & 1.18\\ \hline
-%    6     & 77\% & 171.9 & 9.46 & 1.162\\ \hline
+    6     & 77\% & 171.9 & 9.46 & 1.162\\ \hline
 %    8     & 82\% & 90.5 & 89.2 & \\ \hline
@@
 ``Read'' column is controlled as 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted too much.
+The peak read performance is about 300MB and we only use 16.7\% with this collocation consideration.
 ``Write'' column is the I/O write usage of QFS and notice that each QFS write leads writes in multiple machines due to
-data replication.     
+data replication.     50MB dirty segment read speed triggers about 16.4MB/second disk write for non duplicates with one backup task.
 % [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
@@
 Table ~\ref{tab:resource_usage} shows that  a single backup task per node can complete the backup of the entire
-VM cluster in about 1.58 hours. Since there are about 25 VMs per machine, we could execute
+VM cluster in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
 more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
@@
 VC uses $\sigma=2\%$ and $4\%$.
-It has a breakdown of time for reading data and updating the metadata, network latency to visit
+It has a breakdown of processing time.
+``Data read/write'' includes disk reading and writing, and 
+updating of the metadata.
+`` Network cost" includes the cost of transferring snapshot and meta data from one machine to another during backup.
+``Index access/lookup'' includes the time for 
+latency to visit
 a remote machine, and index access for fingerprint comparison.

### 2013-09-26 snapshot_system/fast14_abstract.tex
revisions

@@
 This paper proposes a VM-centric collocated backup service that  
-localizes deduplication as much as possible within each virtual machine using similarity-guided
-search and associates  underlying file blocks with one VM for most cases.
+localizes deduplication as much as possible within each virtual machine. Our approach uses similarity-guided
+search and associate  underlying file blocks with one VM for most cases.
 It restricts global deduplication to popular chunks with extra replication support.

### 2013-09-26 snapshot_system/fast14_deduplication.tex
update figures
revisions

@@
 Given $\alpha <1$, $f_1$ can be approximated with integration:
-\begin{equation}
+%\begin{equation}
+\[
 f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
-\end{equation}
+\]
+%\end{equation}
 
@@
 
-For VC, each VM has an average number of $N_1$ non-PDS FSBs
+For VC, each VM has an average number $N_1$ of non-PDS FSBs
 and  has  an average of  $N_2$ PDS FSBs. 
@@
 \] 
-When $E_c$ is close to $E_o$ as demonstrated in Section~\ref{sect:evaldedup}, $N_1$ is 
-much smaller than $N_o$. 
+When $E_c$ is close to $E_o$,
+%as demonstrated in Section~\ref{sect:evaldedup},
+$N_1$ is much smaller than $N_o$. 
 %When there is a failure in FSBs with replication degree $r$
@@
  all its FSBs are unaffected during the system failure:
-\begin{equation}
-\label{eq:VO}
+%\begin{equation}
+%\label{eq:VO}
 %(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
+\[
 A(r)^{N_o}. 
-\end{equation}
+\]
+%\end{equation}
 
@@
 the full snapshot availability of a VM in the VC approach is 
-\begin{equation}
-\label{eq:VC1}
+%\begin{equation}
+%\label{eq:VC1}
 %(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
+\[
 A(r)^{N_1}.
-\end{equation}
+\]
+%\end{equation}
 Since $N_1$ is typically much smaller than $N_o$, 
 the VC approach has a higher availability of VM snapshots than VO.
-In the evaluation discussed in Section~\ref{sect:evaldedup}, we have considered a worst case scenario that
+%In the evaluation discussed in Section~\ref{sect:evaldedup}, 
+We have considered a worst case scenario where
 every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
@@
 The full snapshot availability of  a VM in the VC approach is
-\begin{equation}
-\label{eq:VC2}
+%\begin{equation}
+%\label{eq:VC2}
 % (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
@@
 % (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
+\[
 A(r)^{N_1} * A(r_c)^{N_2}
-\end{equation}
+\]
+%\end{equation}
 %comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
 \end{itemize} 
-In the evaluation discussed in Section~\ref{sect:evaldedup}, we have considered a worst case scenario that
+%In the evaluation discussed in Section~\ref{sect:evaldedup},
+We have considered a worst case scenario that
 every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
 Even with that, the availability of VC snapshots is still much higher than VO and  
-there are two reasons.  1) $N_1$ is much smaller than $N_o$ as discussed previously.
+there are two reasons for.  1) $N_1$ is much smaller than $N_o$ as discussed previously.
 2)  $A(r) < A(r_c)$ because of  $r < r_c$.  

### 2013-09-26 snapshot_system/fast14_introduction.tex
revisions

@@
 Another issue considered is that
-that deletion of old snapshots also competes for computing resources. 
+that garbage collection after deletion of old snapshots also competes for computing resources. 
 Sharing of data chunks among by multiple VMs needs to be detected during
-snapshot   deletion and such dependencies complicate deletion operations.
+garbage collection and such dependencies complicate deletion operations.
 
 The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
-based on  version  detection, similarity guided local deduplication,
+based on  changed block tracking, similarity guided local deduplication,
 and popularity guided global deduplication. 

### 2013-09-26 snapshot_system/fast14_architecture.tex
update figures
architecture and snapshot store revisions

@@
 %to %manage  the physical disk storage. 
-All data needed for the backup service including snapshot and  metadata data
+All data needed for the backup service including snapshot data and  metadata
 %and snapshot data for backup purposes, 
@@
 node  for supporting backup and deduplication: 
-1) a virtual block device driver, 2) a snapshot deduplication component,
-3) an append store client to store  and access snapshot data,
+1) a virtual block device driver, 2) a snapshot deduplication agent,
+3) a snapshot store client to store  and access snapshot data,
 and 4)  a PDS client to support PDS metadata access.
@@
 We use the virtual device driver in Xen that employs a bitmap to track the changes 
-that have been made to the virtual disk.
+that have been made to the virtual disk (CBT).
 Every bit in the bitmap represents a fixed-sized (2MB) region called a \textit{segment}, indicating whether the segment
@@
 among popular data chunks. On average the number of consecutive PDS index hits is lower than 7.
-Thus it is not so effective to group a large number of chunks as a compression and data fetch unit. 
+Thus it is not very effective to group a large number of chunks as a compression and data fetch unit. 
 For the same reason, we decide not to take the sampled index approach~\cite{Guo2011} 
@@
 the total data size is small.  When
-a new PDS data  set is computed, in-memory PDS index is replaced, but 
+a new PDS data  set is computed, the in-memory PDS index is replaced, but 
 the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
@@
 %\item
-Each data container is represented by three files in the DFS:
+Each non-PDS data container is represented by three files in the DFS:
 1) the container data file holds the actual content, 
@@
 Each repair uses less than 90MB memory on average
-%as discussed earlier
 and takes a short period of time.

### 2013-09-26 snapshot_system/fast14_deduplication.tex
architecture and snapshot store revisions

@@
   \centering
-  \epsfig{file=images/mh_local_dedup.png, width=3in}
+  \epsfig{file=images/mh_local_dedup.pdf, width=3in}
   \caption{Similarity-guided local duplicate detection}
@@
 Since $N_1$ is typically much smaller than $N_o$, 
-the VC approach has a higher availability of VM snapshots than VO.
+the VC approach has a higher availability of VM snapshots than VO in this case.
 %In the evaluation discussed in Section~\ref{sect:evaldedup}, 
-We have considered a worst case scenario where
-every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
-Even with that, the availability of VC snapshots is much higher than VO and we analyze  this below.
+%We have considered a worst case scenario where
+%every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
+%Even with $N_2$ being much higher than $N_o$ (as discussed below),
+%the availability of VC snapshots is much higher than VO.
 
@@
 Even with that, the availability of VC snapshots is still much higher than VO and  
-there are two reasons for.  1) $N_1$ is much smaller than $N_o$ as discussed previously.
-2)  $A(r) < A(r_c)$ because of  $r < r_c$.  
+there are two reasons for this:  1) $N_1$ is much smaller than $N_o$ as discussed previously.
+2)  $A(r) < A(r_c)$ because $r < r_c$.  
 Table~\ref{tab:fsb-availability} lists the $A(r)$ values with

### 2013-09-26 snapshot_system/fast14_background.tex
revise
revisions
update

@@
 \item {\em Deduplication localization.}
-Because a data chunk is compared with signatures collected from all VMs during
+Because a data chunk is compared with fingerprints collected from all VMs during
 the deduplication process, only one copy of duplicates is stored in the storage,
@@
 while the data chunk in a typical deduplication system is of a non-uniform size with 4KB or 8KB on average.
-Packaging data chunks to a FSB can create more data dependencies among VMs
+Packaging data chunks to an FSB can create more data dependencies among VMs
 since a file system block can be shared by even more VMs.
@@
 1)
-{\em Version-based change detection}.
-VM snapshots can be  backed up  incrementally by identifying file segments that have
+{\em Changed block Tracking}.
+VM snapshots can be  backed up  incrementally by identifying data segments that have
 changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
@@
 global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
-2) {\em Stateless  data Routing}.
+2) {\em Stateless  Data Routing}.
 One approach for scalable duplicate comparison is to use a content-based hash

### 2013-09-26 snapshot_system/fast14_evaluation.tex
revise

@@
 Although the loss of a PDS block affects many VMs,
-by increasing replication for those blocks we minimize the effect on snapshot availability.
+by increasing replication for those blocks we minimize the effect on VM snapshot availability.
 %By having extra replicas for the PDS data, we reduce the failure rate of PDS
@@
             column name={
-                \multicolumn{4}{c|}{Snapshot Availability(\%)}\\&
+                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
                 \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
@@
                 font={\tiny\sffamily},
+                nodes={right}
                 %at={(0.5,-0.2)},
@@
                 %VC($\sigma=4\%$),
-                VC(No MH\,$\sigma=2\%$),
+                VC($\sigma=2\%$\, No similarity guidance),
                 %VC($\sigma=1\%$),
@@
 It has a breakdown of processing time.
-``Data read/write'' includes disk reading and writing, and 
+``Snapshot read/write'' includes snapshot reading and writing from disk, and 
 updating of the metadata.
-`` Network cost" includes the cost of transferring snapshot and meta data from one machine to another during backup.
-``Index access/lookup'' includes the time for 
-latency to visit
-a remote machine, and index access for fingerprint comparison.
-The change of $\sigma$ does not significantly affect the overall backup speed as
+`` Network transfer" includes the cost of transferring raw and meta data from one machine to another during 
+snapshot read and write.
+``Index access/comparison'' includes the disk, network and CPU time during fingerprint comparison.
+This includes PDS data lookup for VC and index lookup from disk in VO after Bloom filter lookup.
+For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
 PDS lookup takes only a small amount of time.
-SRB has higher index access and fingerprint comparison costs because all chunk signatures for whom the current
-machine does not control the index must be sent over the network, and then rely
-on the index holding machine to access its index (often on the disk, supported by a Bloom filter) 
-and perform comparison.
-VC is faster in this regard because it conducts in-memory local search first and then
-accesses  the PDS on distributed shared memory, so most chunks can be dealt with locally.  
-SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
-local meta data index in addition to partition indices.
-Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.
+While the amount raw data transferred in network is about the same for VC and SRB, 
+SRB spends slightly more time for snapshot read/write because each snapshot  backup, more smaller bins are involved
+ in  SRB while VC only involves fewer containers with a bigger size. Thus I/O aggregation is more effective in VC.
+SRB has a higher cost for index access and fingerprint comparison because most of  chunk fingerprints are routed
+to remote machines for comparison while   VC handles most of chunk fingerprints locally.
+
+%on the index holding machine to access its index (often on the disk, supported by a Bloom filter) 
+%and perform comparison.
+%VC is faster in this regard because it conducts in-memory local search first and then
+%accesses  the PDS on distributed shared memory, so most chunks can be dealt with locally.  
+%SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
+%local meta data index in addition to partition indices.
+%As a result Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.
 %Figure~\ref{fig:vc_srb_combined} also reports the average backup time for a VM in VC when
@@
 \hline
-    Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    \\
+    Concurrent      & \multicolumn{3}{c|}{Throughput without}    \\
     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} \\ \cline{2-4}
     per machine                & Backup                                     & Snapshot Store & QFS  \\ \hline
+    		&                                      & (write) & (write)  \\ \hline
     1                       & 1369.6                                     & 148.0          & 35.3 \\
@@
 ``QFS'' column is the write request traffic to the underlying file system after compression.
-The underlying disk storage traffic will be three times greater because of replication.
+For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
+after compression.  The underlying disk storage traffic will be three times greater with replication.
 The result shows that the backup service can deliver up to 5.46GB/second without I/O restriction
-per machine with 6 concurrent backup tasks.
-With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.
+per machine with 6 concurrent backup tasks. With a higher disk storage bandwidth available, the above backup
+ throughput would be higher. 
+%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.
 
@@
 given $\Delta u/u=0.025$,
-while the top solid line represents the actual leakage measured during the experiment 
-with the same $\Delta u/u=0.025$ setting for summary vectors.
-After 9 snapshot deletions, the actual leakage ratio reaches 0.0018 and this means that
-there is only 1.8MB space leaked for every 1GB of stored data, it is also obvious that
-the leakage grows linearly as we expect. 
+while the solid line represents the actual leakage measured during the experiment. 
+The Bloom filter setting is based on $\Delta u/u=0.025$.
+After 9 snapshot deletions, the actual leakage ratio reaches 0.0015 and this means that
+there is only 1.8MB space leaked for every 1GB of stored data.
+The actual leakage can reach to 4.1\% after  245 deletions.
 % We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.

### 2013-09-26 snapshot_system/fast14_conclusion.tex
re

--- 2013-09-25 snapshot_system/fast14_conclusion.tex
@@
 Evaluation using  VM backup data shows that VC strikes a tradeoff and 
-can accomplish close to 97\% of what complete global
-deduplication can do while the availability of snapshots increases substantially with this VM-centric
-and a small replication overhead for popular inter-VM chunks.
+can accomplish 96.33\% or 96.9\% of what complete global
+deduplication can do.  The availability of snapshots increases substantially with 
+a small replication overhead for popular inter-VM chunks.

### 2013-09-26 snapshot_system/fast14_architecture.tex
update

@@
 local chunk IDs are monotonically increasing.
-When a snapshot chunk is to be accessed, the snapshot recipe contains a reference pointing to  a data chunk
+When a chunk is to be accessed, the segment recipe contains a reference pointing to  a data chunk
 in the PDS store or in a non-PDS VM snapshot  store. 

### 2013-09-26 snapshot_system/fast14_evaluation.tex

@@
     4     & 63\% & 154&50   & 18.3 & 1.18\\ \hline
-    6     & 77\% & 171.9 & 9.46 & 1.162\\ \hline
+    6     & 77\% & 171.9 & 50 &  9.46 & 1.162\\ \hline
 %    8     & 82\% & 90.5 & 89.2 & \\ \hline
@@
     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} \\ \cline{2-4}
-    per machine                & Backup                                     & Snapshot Store & QFS  \\ \hline
+    per machine                & Backup                                     & Snapshot Store & QFS  \\ 
     		&                                      & (write) & (write)  \\ \hline

### 2013-09-26 snapshot_system/fast14_architecture.tex
revi

--- 2013-09-26 snapshot_system/fast14_architecture.tex
@@
 %\item
-PDS chunks are stored in one PDS file. 
+All PDS chunks are stored in one PDS file. 
 Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
@@
 %for the simpler format because
-Additional compression is not applied because PDS chunks have less spatial locality in data access. 
-For the data sets we have tested, we only observed very limited spatial locality 
+Additional compression is not applied because 
+for the data sets we have tested, we only observed very limited spatial locality 
 among popular data chunks. On average the number of consecutive PDS index hits is lower than 7.
@@
 Every local chunk ID however is directly copied rather than re-generated. This
-process leaves holes in the CID values, but preserves the order and IDs of chunks.
+process leaves holes in the chunk ID values, but preserves the order and IDs of chunks.
 As a result, all data references stored 

### 2013-09-26 snapshot_system/fast14_architecture.tex
update

--- 2013-09-26 snapshot_system/fast14_architecture.tex
@@
 
-\subsection{ Components of a cluster node } 
+\subsection{ Components of a Cluster Node } 
 As depicted in Figure~\ref{fig:arch_vm}, 
@@
 
-\subsection{A VM-centric snapshot store for backup data}
+\subsection{A VM-centric Snapshot Store for Backup Data}
 \label{sect:store}

### 2013-09-27 snapshot_system/fast14_architecture.tex
revision

--- 2013-09-26 snapshot_system/fast14_architecture.tex
@@
 
-PDS data is re-calculated periodically, but 
+PDS data are re-calculated periodically, but 
 the total data size is small.  When
@@
 the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
-The old data is not removed because they can still be referenced by the existing snapshots. 
+The old data are not removed because they can still be referenced by the existing snapshots. 
 A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months).

### 2013-09-27 snapshot_system/fast14_deduplication.tex
update

@@
 % Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
-\subsection{Impact on deduplication efficiency}
+\subsection{Impact on Deduplication Efficiency}
 Choosing the value $k$ for the most popular chunks affects the deduplication efficiency.
@@
 \centering
-\begin{tabular}{|p{1.25cm}|p{5.5cm}|}
+\tabcolsep=0.11cm
+\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
 \hline
@@
 $p$ & the number of machines in the cluster\\
-% \hline
-% $V$ & the average number of VMs hosted on each machine\\
+\hline
+$V$ & the average number of VMs hosted on each machine\\
 \hline
@@
 %\hline
-%$C$ & the average data chunk size. Our setting is  4K.\\
-%\hline
-%$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
+%$s$ & the average data chunk size. Our setting is  4K.\\
+\hline
+$s$ & the average number of chunks per FSB\\
 %\hline
@@
  and  we denote that PDS FSBs are
-shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file system block, 
-$V$ be the average number of VMs hosted on each machine. Then, 
+shared by an average of $V_c$ VMs. 
+%Let $s$ be the average number of chunks per file system block, 
+%$V$ be the average number of VMs hosted on each machine. 
+Then, 
 \[

### 2013-09-27 snapshot_system/fast14_evaluation.tex
update
revision

@@
 The key reason is that for most data in VC, only a single
-VM can be affected by the loss of a single FSB. Since most FSBs contain blocks for a single VM, VMs can point to a smaller number of FSBs.
+VM can be affected by the loss of a single FSB. Since most FSBs contain chunks for a single VM, VMs can depend on a smaller number of FSBs.
 % because our VM-centric approach
@@
     4     & 63\% & 154&50   & 18.3 & 1.18\\ \hline
-    6     & 77\% & 171.9 & 50 &  9.46 & 1.162\\ \hline
+    6     & 77\% & 171.9 & 50 &  18.8 & 1.162\\ \hline
 %    8     & 82\% & 90.5 & 89.2 & \\ \hline
@@
 PDS lookup takes only a small amount of time.
-While the amount raw data transferred in network is about the same for VC and SRB, 
+While the amount of raw data transferred in network is about the same for VC and SRB, 
 SRB spends slightly more time for snapshot read/write because each snapshot  backup, more smaller bins are involved
@@
 After 9 snapshot deletions, the actual leakage ratio reaches 0.0015 and this means that
-there is only 1.8MB space leaked for every 1GB of stored data.
-The actual leakage can reach to 4.1\% after  245 deletions.
+there is only 1.5MB space leaked for every 1GB of stored data.
+The actual leakage can reach  4.1\% after  245 deletions.
 % We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.

### 2013-09-27 snapshot_system/fast14_introduction.tex
update

@@
 
-The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
+The key contribution is the development and analysis of a VM-centric approach which integrates  multiple duplicate detection strategies
 based on changed block tracking, similarity guided local deduplication,
 and popularity guided global deduplication. 
-This approach is VM centric by localizing duplicate detection within each VM  
-and by packaging only data chunks from the same VM into a file system block as much as possible.
+This approach localizes duplicate detection within each VM  
+and packages only data chunks from the same VM into a file system block as much as possible.
 By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
@@
 fault resilience while sustaining competitive deduplication efficiency.
+In addition, our VM-centric design allows garbage collection to be performed in a localized
+scope and we propose an approximate deletion scheme to reduce this cost further.
 Localization also brings the benefits of greater ability to exploit parallelism so

### 2013-09-27 snapshot_system/fast14_architecture.tex
revised contributions
revisions

@@
 that have been made to the virtual disk (CBT).
-Every bit in the bitmap represents a fixed-sized (2MB) region called a \textit{segment}, indicating whether the segment
+Every bit in the bitmap represents a fixed-sized (2MB) segment, indicating whether the segment
 has been modified since last backup. 
@@
 to be non-duplicates.
-There is also a special store containing all PDS chunks shared among different VMs.
 As shown in Figure~\ref{fig:as_arch}, we explain the data structure of the snapshot stores as follows.
@@
 %\item
-All PDS chunks are stored in one PDS file. 
+There is also an independent store containing all PDS chunks shared among different VMs as
+a single file.
+%All PDS chunks are stored in one PDS file. 
 Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
@@
 Additional compression is not applied because 
-for the data sets we have tested, we only observed very limited spatial locality 
+for the data sets we have tested, we only observed limited spatial locality 
 among popular data chunks. On average the number of consecutive PDS index hits is lower than 7.
@@
 each container is approximately 1GB. 
-The reason for dividing the snapshot into containers is to simplify the compaction process
+The reason for dividing the snapshot store into containers is to simplify the compaction process
 conducted periodically. As discussed later, data chunks are deleted from old snapshots
@@
 In writing a chunk during backup, the system accumulates data chunks and stores the entire
-group as a unit after compression. This  compression can reduce data by several times  in our tested applications.
+group as a unit after compression. This  compression can reduce data by several times  in our tested data.
 When accessing a particular chunk, its chunk group is retrieved from the storage
@@
 
-The snapshot  store supports three API calls:
+Three API calls are supported for data backup:
 %\begin{itemize}
@@
 For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
+Note that PDS append may only be used during PDS recalculation.
 For non-PDS data, this call places a chunk into 
@@
 it takes significant resources to conduct this process every time there is a snapshot deletion.
-In the case of Alibaba, snapshot backup is conducted automatically and there are 
-about 10 snapshot stored for every VM customer. When there is
-a new snapshot created every day,  there will be a snapshot expired every day to maintain
+%In the case of Alibaba, snapshot backup is conducted automatically and there are 
+%about 10 snapshot stored for every VM customer.
+Snapshot deletion can occur frequently, for example when there is
+a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
 balanced storage use.
@@
 we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
-in this snapshot,
-the items we put into summary vector are all the references that are used in its snapshot and segment recipes.
-Foe each VM we preset the vector size according to  estimation of VM image size,
+in this snapshot.
+The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
+For each VM we preset the vector size according to  estimation of VM image size,
 given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
@@
 This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
-That requires a scan of all the metadata in a single VM backup. Since it is a VM-specific procedure 
+This requires a scan of the entire snapshot store. Since it is a VM-specific procedure 
 the space and time cost is relatively small compared to the traditional mark-and-sweep procedure~\cite{Guo2011} which scans snapshot 
@@
 For example,
-consider each reference consumes 8 bytes plus  1 mark bit, a VM that has 40GB backup data with about
-10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process.
+consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
+10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process
+in less than half an hour, assuming 50MB/s disk bandwidth is allocated.
 \end{itemize}
@@
 
-When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we derive the condition to execute a leak repair as:
+When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$ we trigger a leak repair. Namely,
 
@@
 For example in our tested dataset,  
-each VM keeps $h=10$ snapshots and each snapshot adds
+$h=10$ and each snapshot adds
 about 0.1-5\% of new data. Thus we take ${\Delta u}/{u} \approx 0.025$. For a 40GB snapshot, $u\approx  10$ million.
@@
 If $\tau = 0.1$ then leakage repair would occur every 19.6 days.
-Each repair uses less than 90MB memory on average
-and takes a short period of time.

### 2013-09-27 snapshot_system/fast14_evaluation.tex
revisions

@@
 %index ($\sigma=100\%$) then VC will have 100\% efficiency.
-SRB can deliver up to 97.79\% deduplication efficiency which is slightly better than VC.
+SRB can deliver up to 97.79\% deduplication efficiency, which is slightly better than VC.
 Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
@@
 %Without this (i.e. when we only 
-when a data  segment is moved to another location on disk, for example when a file is rewritten
+there are VMs in which
+data  segments are moved to another location on disk, for example when a file is rewritten
 rather than modified in place,  
@@
 ``Read'' column is controlled as 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted too much.
-The peak read performance is about 300MB and we only use 16.7\% with this collocation consideration.
-``Write'' column is the I/O write usage of QFS and notice that each QFS write leads writes in multiple machines due to
-data replication.     50MB dirty segment read speed triggers about 16.4MB/second disk write for non duplicates with one backup task.
+The peak raw storage read performance is about 300MB/s and we only use 16.7\% with this collocation consideration.
+``Write'' column is the I/O write usage of QFS and notice that each QFS write triggers disk writes in multiple machines due to
+data replication.     50MB/s dirty segment read speed triggers about 16.4MB/s disk write for non duplicates with one backup task.
 % [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
@@
 snapshot read and write.
-``Index access/comparison'' includes the disk, network and CPU time during fingerprint comparison.
+``Index access/comparison'' is the disk, network and CPU time during fingerprint comparison.
 This includes PDS data lookup for VC and index lookup from disk in VO after Bloom filter lookup.
 For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
-PDS lookup takes only a small amount of time.
-While the amount of raw data transferred in network is about the same for VC and SRB, 
-SRB spends slightly more time for snapshot read/write because each snapshot  backup, more smaller bins are involved
- in  SRB while VC only involves fewer containers with a bigger size. Thus I/O aggregation is more effective in VC.
+PDS lookup takes only a small amount of time. The network transfer time for VC and SRB is about the same, because the 
+amount of raw data they transfer is comparable.
+SRB spends slightly more time for snapshot read/write because during each snapshot  backup, SRB involves many small bins,
+ while VC only involves few containers with a bigger size. Thus I/O aggregation is more effective in VC.
 SRB has a higher cost for index access and fingerprint comparison because most of  chunk fingerprints are routed

### 2013-09-27 snapshot_system/fast14_introduction.tex
revisions

@@
 
-The key contribution is the development and analysis of a VM-centric approach which integrates  multiple duplicate detection strategies
-based on changed block tracking, similarity guided local deduplication,
+The key contribution is the development and analysis of a VM-centric approach
+which considers fault isolation and integrates  multiple duplicate detection strategies
+supported by similarity guided local deduplication
 and popularity guided global deduplication. 

### 2013-09-27 snapshot_system/fast14_architecture.tex
revisions

@@
 %\item
-There is also an independent store containing all PDS chunks shared among different VMs as
+There is an independent store containing all PDS chunks shared among different VMs as
 a single file.
@@
 will only be used if they also exist in other snapshots.
-Periodically, the snapshot  store picks those containers with an excessive
+Periodically, the snapshot  store identifies those containers with an excessive
 number of deletion requests to  compact and  reclaim the corresponding disk space. 
@@
 given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
+We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
+This can be done during the periodic leakage repair stage described below.
 
@@
 reference of deleted chunks  with
-the merged Bloom-filter reference summary of other live snapshots.
-The merging of live snapshot Bloom-filter bits uses the bitwise OR operator 
+the merged reference summary vectors of other live snapshots.
+The merging of live snapshot Bloom-filter vectors uses the bitwise OR operator 
 and the merged vector still takes $z$ bits.
@@
 If a chunk's reference is not found in the merged summary vector, we are sure that
-this chunk is not used by any live snapshots, thus can be deleted safely.
+this chunk is not used by any live snapshots, thus it can be deleted safely.
 However, among all the chunks to be deleted, 
@@
 
-When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$ we trigger a leak repair. Namely,
+When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we trigger a leak repair. Namely,
 

### 2013-09-27 snapshot_system/fast14_introduction.tex
revisions

--- 2013-09-27 snapshot_system/fast14_introduction.tex
@@
 
-The key contribution is the development and analysis of a VM-centric approach which integrates  multiple duplicate detection strategies
-based on changed block tracking, similarity guided local deduplication,
+The key contribution of this work is the development and analysis of a VM-centric approach
+which considers fault isolation and integrates  multiple duplicate detection strategies
+supported by similarity guided local deduplication
 and popularity guided global deduplication. 

### 2013-09-27 snapshot_system/fast14_architecture.tex
final update, bye!

@@
 and it requires the global references to deleted chunks to be identified before they can be safely removed.
-While we can use the mark-and-sweep technique~\cite{Guo2011}, 
+The complexity of our distributed environment obviates reference counting as an option,
+and while we can use the mark-and-sweep, 
 it takes significant resources to conduct this process every time there is a snapshot deletion.
+%
 %In the case of Alibaba, snapshot backup is conducted automatically and there are 
 %about 10 snapshot stored for every VM customer.
-Snapshot deletion can occur frequently, for example when there is
-a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
-balanced storage use.
+% Snapshot deletion can occur frequently, for example when there is
+% a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
+% balanced storage use. 
+In addition, cloud users expect the reduced storage usage to be reflected
+instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.
 
@@
 This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
-This requires a scan of the entire snapshot store. Since it is a VM-specific procedure 
-the space and time cost is relatively small compared to the traditional mark-and-sweep procedure~\cite{Guo2011} which scans snapshot 
-chunks from all VMs.
-For example,
-consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
+Our VM-centric mark-and-sweep procedure is similar to Guo\cite{Guo2011} 
+in a way that the data dependency is clearly known.
+This generally requires a scan of almost the entire snapshot store which is much more expensive than approximate deletion,
+although certain optimized algorithms may apply\cite{Przemyslaw2013}. But since it is a VM-specific procedure, 
+the space and time cost is relatively small compared to the tranditional mark-and-sweep
+which scans snapshot chunks from all VMs.
+For example, consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
 10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process

### 2013-09-27 snapshot_system/fast14_architecture.tex
revise on mark-sweep

--- 2013-09-27 snapshot_system/fast14_architecture.tex
@@
 and it requires the global references to deleted chunks to be identified before they can be safely removed.
-While we can use the mark-and-sweep technique~\cite{Guo2011}, 
-it takes significant resources to conduct this process every time there is a snapshot deletion.
+%The complexity of our distributed environment obviates reference counting as an option,
+%and While we can use the mark-and-sweep, 
+%While the mark-and-sweep techniques can be used and optimization can be considered~\cite{Fabiano2013},
+%it still takes significant resources to conduct reference counting every time there is a snapshot deletion.
+%
 %In the case of Alibaba, snapshot backup is conducted automatically and there are 
 %about 10 snapshot stored for every VM customer.
-Snapshot deletion can occur frequently, for example when there is
-a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
-balanced storage use.
+% Snapshot deletion can occur frequently, for example when there is
+% a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
+% balanced storage use. 
+%In addition, cloud users expect the reduced storage usage to be reflected
+%instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.
 
@@
 This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
-This requires a scan of the entire snapshot store. Since it is a VM-specific procedure 
-the space and time cost is relatively small compared to the traditional mark-and-sweep procedure~\cite{Guo2011} which scans snapshot 
-chunks from all VMs.
-For example,
-consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
+A mark-and-sweep process  requires a scan of the entire snapshot store.
+%Our VM-centric mark-and-sweep procedure is similar to Guo\cite{Guo2011} 
+%in a way that the data dependency is clearly known.
+%This generally requires a scan of almost the entire snapshot store which is much more expensive than approximate deletion,
+%although certain optimized algorithms may apply\cite{Przemyslaw2013}. But 
+Since it is a VM-specific procedure, 
+the space and time cost is relatively small compared to the tranditional mark-and-sweep
+which scans snapshot chunks from all VMs.
+For example, consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
 10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process

### 2013-09-27 snapshot_system/fast14_background.tex
update
revise on mark-sweep

@@
 which  occurs frequently when snapshots expire regularly. 
-The mark-and-sweep approach~\cite{Guo2011} is effective for deletion, but has a high cost, and its main cost
-is to count if a data chunk is still shared by other snapshots.
+The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for deletion, but still carries a significant cost
+to count if a data chunk is still shared by other snapshots. 
 Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
@@
 
-In designing a VC duplication algorithm, we have considered and adopted some of
+In designing a VC duplication solution, we have considered and adopted some of
 the following previously-developed techniques.

### 2013-10-22 batchdedup/arch.tex
arch graph

@@
 \centering
-\includegraphics[width=0.5\textwidth]{snapshotdata.pdf}
-\caption{ Metadata structure of a VM snapshot.}
+\includegraphics[width=0.5\textwidth]{images/batch_arch.pdf}
+\caption{Overall architecture of parallel VM snapshot deduplication}
 \label{fig:snapshot}
@@
 has a two-level index structure in the form of a hierarchical
-directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
+directed acyclic graph.% as shown in Figure~\ref{fig:snapshot}.
 A VM image is divided into a set of segments and each  segment contains 

### 2013-10-22 batchdedup/main.tex
revised

@@
 \usepackage{epsfig}
+\usepackage{listings}
+%\lstset{language=C}
 %\usepackage{breakurl}
@@
 \usepackage{pgfplots}
-\pgfplotsset{compat=1.7}
+\pgfplotsset{compat=1.5}
 \DeclareGraphicsExtensions{.pdf}
@@
 }
+%this is my preferred default cycle list for pgfplots.
 \pgfplotscreateplotcyclelist{mcolor}{%
@@
 \newcommand{\comments}[1]{}
+\newcommand{\todo}[1]{\textit{\color{red}#1}}
 
@@
 \author{
-Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, and Hong Tang$^\dagger$ \\
-{\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
+Daniel Agun$^{\star}$,  
+Wei Zhang$^{\star}$, and Tao Yang$^\star$ \\
+{\normalsize$^\star$  University of California at Santa Barbara}, 
+%{\normalsize$^\dagger$Alibaba Inc.}
 %Wei Zhang, Tao Yang, Gautham Narayanasamy\\
@@
 \input{arch} %, design considerations, architecture
-%\input{analysis} %, design considerations, architecture
+\input{analysis} %, design considerations, architecture
+\input{scheduling} % CoW cost considerations and round scheduling
 \input{eval} %data study, zipf, model of cds size and dedup efficiency

### 2013-10-24 batchdedup/arch.tex
differentiated stage 4a and 4b in architecture

@@
 including dup-with-new blocks, are returned to the requesters from the index
-holders and the snapshot
-recipes are updated with those pointers.
+holders in 4a, And in 4b the snapshot recipes are updated with those pointers.
 

### 2013-10-30 thesis/Dissertation.tex
thesis template

% Root File for a UCSB Dissertation
%
%

\documentclass[12pt,twoside,draft]{ucthesis}
% todo: final options: [12pt,oneside,final]

\usepackage{graphics,epsfig}
%\usepackage{amssymb, amsmath, amsfonts, epsfig, graphicx, graphics, latexsym, makeidx, psfig, subeqn, verbatim, xspace,textcomp}

%% Document Parts

% run latex with only these files; it's faster without all eps figures etc.
%\includeonly{Title,Front,Intro}
%\includeonly{Title,Front,Intro,Literature,Chapter1,Chapter2,Conclusions}

%%% Document Portion:

\begin{document}

%% Front Matter:
\input{Title}          % First Page
\maketitle             % Make Title Page

\begin{frontmatter}
\approvalpage
\copyrightpage
\input{Dedicate}
\input{Acknowledgements}
\input{Vitae}
%\input{Preface}
\input{Abstract}
\tableofcontents
\listoffigures
\listoftables
\end{frontmatter}

% the chapters

% spacing in figures and tables and their captions can be
% changed here (\ssp for single-space, empty for same as surrounding 
% text); for this to work, the command \figsp has to be included
% in every figure and table right after the \begin{figure}
\def\figsp{\ssp}
%\def\figsp{}

\include{Intro}

%\include{Literature}

%\include{Chapter1}

%\include{Chapter2}

%\include{Conclusions}

\ssp   % bibliography can be single-spaced for UC thesis format
\bibliography{mybibfile}
\bibliographystyle{abbrv}%{unsrt}%{alpha}{siam}{apalike}{ieeetr}{plain}{acm}{abbrv}
%\bibliographystyle{IEEE-Alpha}

\part*{\addcontentsline{toc}{part}{Appendices}Appendices}
\appendix

\include{Appendix}

\end{document}

### 2013-10-30 thesis/uctest.tex
thesis template

\documentclass[11pt]{ucthesis}
\def\dsp{\def\baselinestretch{2.0}\large\normalsize}
\dsp
\begin{document}

% Declarations for Front Matter

\title{The Elements of Theses}
\author{Perry H. Disdainful}
\degreeyear{1994}
\degreesemester{Spring}
\degree{Doctor of Philosophy}
\chair{Professor Ignatius Arrogant}
\othermembers{Professor Ivory Insular\\
Professor General Reference}
\numberofmembers{3}
\prevdegrees{B.A. (University of Northern South Dakota at Hoople) 1978\\
M.S. (Ed's School of Quantum Mechanics and Muffler Repair Shop) 1989}
\field{Aboriginal Basketry}
\campus{Berkeley}

\maketitle
\approvalpage
\copyrightpage

\begin{abstract}
Theses have elements.  Isn't that nice?

\abstractsignature
\end{abstract}

\begin{frontmatter}

\begin{dedication}
\null\vfil
{\large
\begin{center}
To myself,\\\vspace{12pt}
Perry H. Disdainful,\\\vspace{12pt}
the only person worthy of my company.
\end{center}}
\vfil\null
\end{dedication}

\tableofcontents
\listoffigures
\listoftables
\begin{acknowledgements}
I want to ``thank'' my committee, without whose ridiculous demands, I
would have graduated so, so, very much faster.
\end{acknowledgements}

\end{frontmatter}

\part{First Part}

\chapter{Introduction}

Every dissertation should have an introduction.  You might not realize
it, but the introduction should introduce the concepts, backgrouand,
and goals of the dissertation.

\begin{table}
\begin{tabular}{|l|r|}
  \hline 
Title & Author \\
\hline
War And Peace & Leo Tolstoy \\
The Great Gatsby & F. Scott Fitzgerald \\ \hline
\end{tabular}
\caption{A normalsize table.  There has been a complaint that table
captions are not single-spaced.  This is odd because the code
indicates that they should be.}
\end{table}

\begin{table}
\caption{A small table.}
\begin{scriptsizetabular}{|l|r|}
  \hline 
Title & Author \\
\hline
War And Peace & Leo Tolstoy \\
The Great Gatsby & F. Scott Fitzgerald \\ \hline
\end{scriptsizetabular}
\end{table}

\chapter{Previous Work}

Some other research was once performed.

\begin{figure}
\caption{A first figure.}
\end{figure}

\begin{figure}
\caption{A second figure.}
\end{figure}

\chapter{Conclusion}

\nocite{*}
\bibliographystyle{plain}
\bibliography{uctest}

\appendix
\chapter{Some Ancillary Stuff}

Ancillary material should be put in appendices, which appear after the
bibliography.

\end{document}

### 2013-11-01 batchdedup/scheduling.tex
update coe analysis

@@
 \label{sect:scheduling}
-The simplest way to take advantage of the efficiency of batch processing is to
-schedule all the work to be done in one round.  This works well if all of the
-data being backed up are only copies, e.g. a separate backup system which data
-is sent to over the network. However, in our case we are backing up the
-original virtual disk, so a single round backup presents several problems.
-The first is that the average turnaround time for a VM is the time it takes to
-backup all the VMs. The second, which is related to the first, is that a single
-round backup has the highest cost to maintain a consistent view of the virtual
-disks. We use Copy on Write (CoW) for this, and the consistent view must be
-maintained between stage 1a and stage 2b, which can have sisgnificant cost if
-the system must wait for every single VM before unlocking any of the VMs.
-Other studies have
-shown that as much as 8\% or even more of total capacity must be reserved for
-CoW \cite{EMCIncrementalDataChanges}. The actual cost of CoW is a factor of the
-data size, the write rate, and duration CoW is taking place. The data size
-isn't something we can change, nor the write rate, but we can minimize the
-duration that a given VM is undergoing CoW. By minimizing the backup time for
-individual VMs we also improve CoW cost. To evaulate our
-CoW cost improvement, we assume a poisson distribution of
-writes (which closely fits the meaured results from
-\cite{EMCIncrementalDataChanges}).
+The naive way to take advantage of the efficiency of batch processing is to
+schedule all the work to be done in one round.  
+% This works well if all of the
+% data being backed up are only copies, e.g. a separate backup system which data
+% is sent to over the network. 
+However, in our case we are backing up the
+live virtual disks, thus such single round backup presents several problems
+in our synchronous approach.
+This first is that in order to preserve a consistent view of VM images, we apply
+Copy-on-Write (CoW) to protect the dirty segments against incoming disk writes during 
+the backup period of stage 1 and 2.
+Previous studies have shown that as much as 8\% or even more of total capacity must be reserved for
+CoW \cite{EMCIncrementalDataChanges}, while the actual cost of CoW is a factor of the
+data size, the write rate, and duration of CoW protection.
+The second problem is that a single round backup brings the highest cost of CoW
+because of the workload in stage 1a is imbalanced,
+causing machines with small VMs to wait while CoW protection is turned on.
+Thus we must minimize the duration that a given VM is undergoing CoW protection.
+
+% The first is that the average turnaround time for a VM is the time it takes to
+% backup all the VMs. The second, which is related to the first, is that a single
+% round backup has the highest cost to maintain a consistent view of the virtual
+% disks. We use Copy on Write (CoW) for this, and the consistent view must be
+% maintained between stage 1a and stage 2b, which can have significant cost if
+% the system must wait for every single VM before unlocking any of the VMs.
+% Other studies have shown that as much as 8\% or even more of total capacity must be reserved for
+% CoW \cite{EMCIncrementalDataChanges}. The actual cost of CoW is a factor of the
+% data size, the write rate, and duration CoW is taking place. The data size
+% isn't something we can change, nor the write rate, but we can minimize the
+% duration that a given VM is undergoing CoW. By minimizing the backup time for
+% individual VMs we also improve CoW cost. 
+To evaulate our CoW cost, we assume the incoming writes point to random disk locations, 
+which would incur a CoW operation over a segment if the write location fall into a dirty segment
+for the first time (consequential writes to that segment will be re-directed 
+to the new copy so there's no extra cost). Therefore the number of dirty segments needs to be copied represents
+the CoW cost of a VM, which follows a poisson distribution (similar results are meaured from \cite{EMCIncrementalDataChanges}).
 
@@
 In the above model, $n$ is the number of dirty segments, $t$ is the time under
-CoW, $w$ is the
+CoW protection, $w$ is the
 write rate during CoW, $d_1$ is the \% of clean data (which doesn't go under

### 2013-11-01 batchdedup/eval.tex
added scheduling simulation results to eval

@@
 		\begin{axis}[
-		%title={Read Buffer Size},
-		xlabel={Read Buffer Size (MB)},
-		ylabel={Backup Time},
+		%title={Network Buffer Size},
+		xlabel={Rounds},
+		ylabel={Throughput (GB/s)},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		]
-                \addplot table[x=rbufmem,y=totaltime] {figures/rbufmem.txt};
+                \addplot table[x=rounds,y=throughput] {figures/sim_full.txt};
                 %\legend{Total Backup Time};
@@
 	\end{tikzpicture}
-  \caption{Backup time for verying amounts of memory allocated to disk read buffering. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffers 2.5MB, write buffer 6.25MB}
+  \caption{simulated results for average throughput for individual VMs in 100 node cluster.}
   \label{fig:mpibuf-mem}
 \end{figure}
-
 \begin{figure}[ht]
@@
 		\begin{axis}[
-		%title={Write Buffer Size},
-		xlabel={Total Write Buffer Memory (MB)},
-		ylabel={Backup Time},
+		%title={Network Buffer Size},
+		xlabel={Rounds},
+		ylabel={Average Backup Time (min)},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		]
-                \addplot table[x=wbufmem,y=totaltime] {figures/wbufmem.txt};
+                \addplot table[x=rounds,y expr=(\thisrow{avgbackuptime})/60] {figures/sim_full.txt};
                 %\legend{Total Backup Time};
@@
 	\end{tikzpicture}
-  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffer memory 2.5MB, Read Buffer 128KB}
+  \caption{simulated results for average vm backup time for individual VMs in 100 node cluster.}
   \label{fig:mpibuf-mem}
 \end{figure}
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Network Buffer Size},
+		xlabel={Rounds},
+		ylabel={Average Turnaround Time (min)},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+		%legend pos=north west
+		]
+                \addplot table[x=rounds,y expr=(\thisrow{turnaround})/60] {figures/sim_full.txt};
+                %\legend{Total Backup Time};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{simulated results for average vm turnaround time for individual VMs in 100 node cluster.}
+  \label{fig:mpibuf-mem}
+\end{figure}
+
+%\begin{figure}[ht]
+%  \centering
+%	\begin{tikzpicture}
+%		\begin{axis}[
+%		%title={Read Buffer Size},
+%		xlabel={Read Buffer Size (MB)},
+%		ylabel={Backup Time},
+%		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+%		%legend pos=north west
+%		]
+%                \addplot table[x=rbufmem,y=totaltime] {figures/rbufmem.txt};
+%                %\legend{Total Backup Time};
+%		\end{axis}
+%	\end{tikzpicture}
+%  \caption{Backup time for verying amounts of memory allocated to disk read buffering. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffers 2.5MB, write buffer 6.25MB}
+%  \label{fig:mpibuf-mem}
+%\end{figure}
+%
+%\begin{figure}[ht]
+%  \centering
+%	\begin{tikzpicture}
+%		\begin{axis}[
+%		%title={Write Buffer Size},
+%		xlabel={Total Write Buffer Memory (MB)},
+%		ylabel={Backup Time},
+%		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+%		%legend pos=north west
+%		]
+%                \addplot table[x=wbufmem,y=totaltime] {figures/wbufmem.txt};
+%                %\legend{Total Backup Time};
+%		\end{axis}
+%	\end{tikzpicture}
+%  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffer memory 2.5MB, Read Buffer 128KB}
+%  \label{fig:mpibuf-mem}
+%\end{figure}
 

### 2013-11-01 batchdedup/scheduling.tex
update formula

@@
 to the new copy so there's no extra cost). Therefore the number of dirty segments needs to be copied represents
-the CoW cost of a VM, which follows a poisson distribution (similar results are meaured from \cite{EMCIncrementalDataChanges}).
+the CoW cost of a VM.
 
-Our basic CoW cost model is:
+Let $t$ be the time that a VM is under Cow protection, $w$ be the write rate
+during that period, $n$ be the total number of segments and $d_1$ 
+be the percentage of clean segments that don't need to
+be protected, then the total number of dirty segments is
 \[
-    CoW=n(1-e^{-m/n})
+n_d=n(1-d_1)
 \]
-    where
+and the total number of writes fall into dirty segments is
 \[
-    m=tw(1-d_1)c
+w_d=tw(1-d_1)
 \]
+Then the total number of dirty segments that need to be copied is:
+\[
+Cost = n_d(1-e^{-w_d/n_d}) = n(1-d_1)(1-e^{-tw/n})
+\]
+From the above formula it is clear that decreasing CoW time $t$ will
+reduce the CoW protection cost, 
+the model we derive is similar to the results meaured by \cite{EMCIncrementalDataChanges}.
+% Our basic CoW cost model is:
+% \[
+%     CoW=n(1-e^{-m/n})
+% \]
+%     where
+% \[
+%     m=tw(1-d_1)c
+% \]
 
-In the above model, $n$ is the number of dirty segments, $t$ is the time under
-CoW protection, $w$ is the
-write rate during CoW, $d_1$ is the \% of clean data (which doesn't go under
-CoW), and $c$ is a constant determining how likely writes are to touch dirty
-segments which haven't yet been copied vs. dirty segments which have already
-been copied during the current backup. With this CoW cost model and the earlier
-performance model, we can estimate the CoW cost of a given backup schedule.
-Note that CoW ends in Stage 2b, so only the time up to the end of 2b counts
-towards CoW. \todo{we still need to pick a value for $c$}
+% In the above model, $n$ is the number of dirty segments, $t$ is the time under
+% CoW protection, $w$ is the
+% write rate during CoW, $d_1$ is the \% of clean data (which doesn't go under
+% CoW), and $c$ is a constant determining how likely writes are to touch dirty
+% segments which haven't yet been copied vs. dirty segments which have already
+% been copied during the current backup. With this CoW cost model and the earlier
+% performance model, we can estimate the CoW cost of a given backup schedule.
+% Note that CoW ends in Stage 2b, so only the time up to the end of 2b counts
+% towards CoW. \todo{we still need to pick a value for $c$}
 

### 2013-11-07 batchdedup/scheduling.tex
fixed round variable to k in scheduling algorithms

@@
 the number of bins, using binary search to arrive at the best number of
-bins. A(I,N) is defined to return the optimality of packing set I into N bins
+bins. A(I,k) is defined to return the optimality of packing set I into k bins
 using A. We take this basic idea and look at several VM packing heuristics to
@@
 while UB>LB
-  set N = (UB+LB+1)/2
-  if A(machines,N) > T, set UB=N-1
-  else set LB=N
+  set k = (UB+LB+1)/2
+  if A(machines,k) > T, set UB=k-1
+  else set LB=k
 Halt
@@
 
-where A(machines,N) returns the total backup time of the schedule for N rounds\\
+where A(machines,k) returns the total backup time of the schedule for k rounds\\
 This algorithm returns the packing generated by A(machines,UB) after loop finishes

### 2013-11-08 batchdedup/scheduling.tex
added proof for basic round packing algorithm

@@
 focuses on the deduplication and so doesn't make use of CoW, but we can see
-that our simulated times closely match measured runtimes (hopefully). \todo{I
-haven't actually implemented the schedulers into the dedup yet to test this}
+that our simulated times closely match measured runtimes (hopefully).
+
+\subsection{Standard Bin Packing Heuristic}
+\todo{this section might need to be moved around and/or broken up. also, notation might still need to be adjusted. }
+\begin{figure}
+\begin{lstlisting}[frame=single]
+bpl:
+for each Machine m
+  sort VMs in descending order by size
+  while there is an unscheduled VM
+    pick the first unscheduled VM a
+    pick the round b with the least
+      amount of VM data for m
+    schedule VM a to round b
+Halt
+\end{lstlisting}
+\caption{Round packing heuristic}
+\end{figure}
+
+Using the above algorithm we can show that for any round $r$, the amount of
+data scheduled to $r$ across all VMs has the upper bound of twice the optimal
+amount of data for a perfectly balanced schedule (i.e. the worst case for any
+round is bounded by twice the best case).
+
+Proof:
+first we define $load(m,r)$ to be the amount of data from VMs on Machine $m$
+to round $r$, $Machines$ to be the set of all machines, and $Rounds$ to be
+the set of all rounds.
+now define $2b_m$ to be the upper bound for data backuped up in a single round, 
+where 
+%$b_m = min(\frac{\sum \left\{ {x \mid x \in {VMS}_m} \right\}}{\left\vert\ {Rounds} \right\vert}, largest~VM~on~m)$,
+$b_m = min(\frac{\sum \left\{ {VMs~on~m} \right\}}{\left\vert {Rounds} \right\vert}, largest~VM~on~m)$,
+and $2b$ to be the global upper bound for each round, where
+$b = \sum \left\{ b_m | m \in Machines \right\}$. We would like to prove the
+actual global load is less than $2b$. we will do this by proving that for
+each machine $2b_m$ is the upper bound, which from the definition of $b$ can be
+extended to a global uppoer bound of $2b$. More formally, we would like to show:
+
+\[
+    (\forall m \in Machines, \forall r \in Rounds) load(m,r) < 2b_m
+\]
+
+Now let $x$ be a VM from Machine $m$ to be scheduled.
+For each round $r$ there are two possibilities:
+\begin{itemize}
+    \item $load(m,r) < b_m \Longrightarrow$
+        $load(m,r)+x < b_m+x$
+    \item $load(m,r) \ge b_m \Longrightarrow$
+
+        $(\exists k \in Rounds) load(m,k) < b_m$
+\end{itemize}
+
+since we never schedule to a round where $load(m,r) \ge b_m$, $load(m,r)$ must
+be less than $b_m+x$, where $x$ is the largest VM on $m$. By Definition
+$b_m > x$, so
+$load(m,r) < 2b_m$ for each machine, and therefore the global load for each
+round is less than $2b$.
+The expected case can be improved though by
+packing the largest VMs first and always scheduling to the round with the least
+data.

### 2013-11-14 batchdedup/scheduling.tex
rewrote round scheduling analysis for batchdedup paper

@@
 
-From our requirements a model that closely fits our goals is the dual version
-of the
-bin packing problem. In standard bin packing the goal is to fit all of the
-items into as few bins as possible, without overfilling any bins. In the dual
-version of the problem however as many bins as possible are to filled to at
-least some minimum level. This fits our purpose because we want to maximize the
-number of rounds to minimize VM backup times, with some constraint to keep the
-efficiency benefits of batch processing and keep the total backup time low.
-In our dual-bin-packing solution the constraint is to keep the total
-cost of the schedule under a time limit rather than mandating a minimum bin
-level. We have adapted
-an algorithm for dual bin packing\cite{DualBinPacking} to fit our VM
-scheduling problem. The algorithm adapted is called iterated A and works by
-iteratively callng a bin packing heuristic A with the items to be scheduled and
-the number of bins, using binary search to arrive at the best number of
-bins. A(I,k) is defined to return the optimality of packing set I into k bins
-using A. We take this basic idea and look at several VM packing heuristics to
-arrive at an efficient packing algorithm. More formally, our adaptation of the
-iterated A algorithm is defined as:
+%From our requirements a model that closely fits our goals is the dual version
+%of the
+%bin packing problem. In standard bin packing the goal is to fit all of the
+%items into as few bins as possible, without overfilling any bins. In the dual
+%version of the problem however as many bins as possible are to filled to at
+%least some minimum level. This fits our purpose because we want to maximize the
+%number of rounds to minimize VM backup times, with some constraint to keep the
+%efficiency benefits of batch processing and keep the total backup time low.
+%In our dual-bin-packing solution the constraint is to keep the total
+%cost of the schedule under a time limit rather than mandating a minimum bin
+%level. We have adapted
+%an algorithm for dual bin packing\cite{DualBinPacking} to fit our VM
+%scheduling problem. The algorithm adapted is called iterated A and works by
+%iteratively callng a bin packing heuristic A with the items to be scheduled and
+%the number of bins, using binary search to arrive at the best number of
+%bins. A(I,k) is defined to return the optimality of packing set I into k bins
+%using A. We take this basic idea and look at several VM packing heuristics to
+%arrive at an efficient packing algorithm. More formally, our adaptation of the
+%iterated A algorithm is defined as:
+%
+%
+%%lstset{basicstyle=\ttfamily\tiny
+%%}
+%\todo{justify choice of initial UB (right now it is mostly arbitrary)}
+%\begin{figure}
+%\begin{lstlisting}[frame=single]
+%Iterated A:
+%Set UB=min(n,2*v)
+%Set LB=1
+%while UB>LB
+%  set k = (UB+LB+1)/2
+%  if A(machines,k) > T, set UB=k-1
+%  else set LB=k
+%Halt
+%\end{lstlisting}
+%\caption{Iterated A scheduling algorithm, requires good choice of A to be effective}
+%\end{figure}
+%
+%where A(machines,k) returns the total backup time of the schedule for k rounds\\
+%This algorithm returns the packing generated by A(machines,UB) after loop finishes
+%
+%The general algorithm relies on a good choice of A to arrive at an efficent
+%packing. Our first VM packing heuristic, A0, is a na\"\i{}ve approach very
+%close to the un-adapted algorithm from the dual bin packing paper. For both
+%algorithms we develop, in case of ties, choose the left-most item.
+%
+%\begin{figure}
+%\begin{lstlisting}[frame=single]
+%A0:
+%sort VMs in descending order by size
+%while there is an unscheduled VM
+%  pick the first unscheduled VM a
+%    pick the round with the current
+%    lowest runtime b
+%  schedule VM a to round b
+%Halt
+%\end{lstlisting}
+%\caption{Na\"{\i}ve round packing heuristic based on VM size and current round runtime}
+%\end{figure}
+%
+%\begin{figure}[thb]
+%\centering
+%\includegraphics[width=0.5\textwidth]{images/VMRound.pdf}
+%\caption{Choosing a round to schedule a VM to. Though the rounds look
+%identical in terms of total/average load, Round 1 is a much better choice.}
+%\label{fig:VMRound}
+%\end{figure}
+%
+%A0 does provide for shorter rounds (see Table~\ref{tab:schedule-costs}), but
+%the efficiency of the packing is poor due to several issues
+%The first issue is that the round with the current lowest runtime
+%is chosen. Because backup time is dependent on a combination of the highest
+%machine load and average machine load, if we add a VM to the currently most
+%loaded machine in a round it will increase runtime much more than if we add the
+%VM to a different round where that machine is currently empty. You can see this
+%in Figure~\ref{fig:VMRound}, where VM1D must be scheduled to one of two rounds
+%which currently have the same average/total load. The effect of VM1D on round 1
+%would be much less than the effect on round 2 because we wouldn't be increasing
+%the maximum machine load of the round, so we should schedule to round 1.
+%Therefore a better
+%scheduling heuristic is one based on predicted runtime after adding the VM, and
+%picking the round with the lowest runtime after adding the VM to that round.
+%This new round picking heuristic
+%takes into account that the same VM might have different affects on different
+%rounds. This aspect of round picking must be considered because we assume a VM
+%must be backed
+%up by the machine that hosts it. If the VMs are located on a DFS such that they
+%can be
+%backed up by any machine in the cluster then the problem of load balancing
+%becomes a simpler but much different problem, but isn't considered here. We
+%also pick the most heavily loaded (i.e. most data remaing) machine in case of
+%ties so we can make the most backup progress in a round, given equivalent
+%equivalent options.
+%
+%Another improvement we can make to A0 is to the VM picking heuristic. For the
+%same reason as given above, the largest VM may not always have the greatest
+%impact on time (e.g. picking a slightly smaller VM on the most heavily loaded
+%machine has a greater impact than selecting the largest VM on a lightly loaded
+%machine). Our improved hueristic to pick VMs is to predict the one-round
+%runtime after removing that VM, and pick the VM whose removal most
+%decreases the single round time (i.e. the VM that has the greatest impact on
+%overall backup time). By picking VMs this way we take into account
+%the machine load in picking which VM to schedule next, and minimize the time
+%the remaining VMs will take to backup
+%
+%After making the two above changes we arrive at VM packing heuristic A1.
+%
+%\begin{figure}
+%\begin{lstlisting}[frame=single]
+%A1:
+%while there is an unscheduled VM
+%  pick the VM a whose removal will
+%    most decrease single round time
+%    tie-breaker:VM on most heavily
+%    loaded round
+%  pick the round b whose runtime will
+%    be lowest after adding VM a
+%  schedule VM a to round b
+%Halt
+%\end{lstlisting}
+%\caption{More effective round packing heuristic based on minimizing remaining work and predicted round time}
+%\end{figure}
+%
+%A1 significantly improves our simulated results, also bringing our CoW costs
+%much closer to the best case than the worst case, as can be seen in
+%Figure~\ref{tab:schedule-costs}.  Our current implementation of the algorithm
+%focuses on the deduplication and so doesn't make use of CoW, but we can see
+%that our simulated times closely match measured runtimes (hopefully).
 
-%lstset{basicstyle=\ttfamily\tiny
-%}
-\todo{justify choice of initial UB (right now it is mostly arbitrary)}
+The problem of scheduling VM backup tasks to specific rounds is a variant of
+bin packing, with some additional constraints. We want to efficiently schedule
+VMs to rounds, minimizing average VM backup time (and thereby minimizing CoW),
+while also taking into account resource usage and total jobspan (which are
+minimized in the single round schedule). We solve the problem with a 2-part
+algorithm. First, we have a round packing heuristic which takes a number of
+rounds and a set of VMs, and returns a schedule for the backup process. Second,
+we have a higher level algorithm that determines the optimal number of rounds,
+given the constraints.
+
+Our round packing heuristic uses a descending sorted order worst fit packing, 
+Scheduling VMs machine by machine, and is described in Fig~\ref{fig-bpl}.
+For our higher-level scheduling algorithm, we minimize Resource usage and average
+backup time, while ensuring that the jobspan constaint is met (if possible). The
+overall scheduling algorithm is described in Fig~\ref{fig-scheduler}, where T is
+the alotted time for backup. our cost function is defined as
+$cost(s) = \alpha\times Resource~Usage(s) + (1-\alpha)\times Avg~Backup~Time(s)$.
+
+%\todo{this section might need to be moved around and/or broken up. also, notation might still need to be adjusted. }
 \begin{figure}
 \begin{lstlisting}[frame=single]
-Iterated A:
-Set UB=min(n,2*v)
-Set LB=1
-while UB>LB
-  set k = (UB+LB+1)/2
-  if A(machines,k) > T, set UB=k-1
-  else set LB=k
-Halt
-\end{lstlisting}
-\caption{Iterated A scheduling algorithm, requires good choice of A to be effective}
-\end{figure}
-
-where A(machines,k) returns the total backup time of the schedule for k rounds\\
-This algorithm returns the packing generated by A(machines,UB) after loop finishes
-
-The general algorithm relies on a good choice of A to arrive at an efficent
-packing. Our first VM packing heuristic, A0, is a na\"\i{}ve approach very
-close to the un-adapted algorithm from the dual bin packing paper. For both
-algorithms we develop, in case of ties, choose the left-most item.
-
-\begin{figure}
-\begin{lstlisting}[frame=single]
-A0:
-sort VMs in descending order by size
-while there is an unscheduled VM
-  pick the first unscheduled VM a
-    pick the round with the current
-    lowest runtime b
-  schedule VM a to round b
-Halt
-\end{lstlisting}
-\caption{Na\"{\i}ve round packing heuristic based on VM size and current round runtime}
-\end{figure}
-
-\begin{figure}[thb]
-\centering
-\includegraphics[width=0.5\textwidth]{images/VMRound.pdf}
-\caption{Choosing a round to schedule a VM to. Though the rounds look
-identical in terms of total/average load, Round 1 is a much better choice.}
-\label{fig:VMRound}
-\end{figure}
-
-A0 does provide for shorter rounds (see Table~\ref{tab:schedule-costs}), but
-the efficiency of the packing is poor due to several issues
-The first issue is that the round with the current lowest runtime
-is chosen. Because backup time is dependent on a combination of the highest
-machine load and average machine load, if we add a VM to the currently most
-loaded machine in a round it will increase runtime much more than if we add the
-VM to a different round where that machine is currently empty. You can see this
-in Figure~\ref{fig:VMRound}, where VM1D must be scheduled to one of two rounds
-which currently have the same average/total load. The effect of VM1D on round 1
-would be much less than the effect on round 2 because we wouldn't be increasing
-the maximum machine load of the round, so we should schedule to round 1.
-Therefore a better
-scheduling heuristic is one based on predicted runtime after adding the VM, and
-picking the round with the lowest runtime after adding the VM to that round.
-This new round picking heuristic
-takes into account that the same VM might have different affects on different
-rounds. This aspect of round picking must be considered because we assume a VM
-must be backed
-up by the machine that hosts it. If the VMs are located on a DFS such that they
-can be
-backed up by any machine in the cluster then the problem of load balancing
-becomes a simpler but much different problem, but isn't considered here. We
-also pick the most heavily loaded (i.e. most data remaing) machine in case of
-ties so we can make the most backup progress in a round, given equivalent
-equivalent options.
-
-Another improvement we can make to A0 is to the VM picking heuristic. For the
-same reason as given above, the largest VM may not always have the greatest
-impact on time (e.g. picking a slightly smaller VM on the most heavily loaded
-machine has a greater impact than selecting the largest VM on a lightly loaded
-machine). Our improved hueristic to pick VMs is to predict the one-round
-runtime after removing that VM, and pick the VM whose removal most
-decreases the single round time (i.e. the VM that has the greatest impact on
-overall backup time). By picking VMs this way we take into account
-the machine load in picking which VM to schedule next, and minimize the time
-the remaining VMs will take to backup
-
-After making the two above changes we arrive at VM packing heuristic A1.
-
-\begin{figure}
-\begin{lstlisting}[frame=single]
-A1:
-while there is an unscheduled VM
-  pick the VM a whose removal will
-    most decrease single round time
-    tie-breaker:VM on most heavily
-    loaded round
-  pick the round b whose runtime will
-    be lowest after adding VM a
-  schedule VM a to round b
-Halt
-\end{lstlisting}
-\caption{More effective round packing heuristic based on minimizing remaining work and predicted round time}
-\end{figure}
-
-A1 significantly improves our simulated results, also bringing our CoW costs
-much closer to the best case than the worst case, as can be seen in
-Figure~\ref{tab:schedule-costs}.  Our current implementation of the algorithm
-focuses on the deduplication and so doesn't make use of CoW, but we can see
-that our simulated times closely match measured runtimes (hopefully).
-
-\subsection{Standard Bin Packing Heuristic}
-\todo{this section might need to be moved around and/or broken up. also, notation might still need to be adjusted. }
-\begin{figure}
-\begin{lstlisting}[frame=single]
-bpl:
 for each Machine m
@@
 \end{lstlisting}
-\caption{Round packing heuristic}
+\caption{Round packing heuristic A}
+\label{fig-bpl}
+\end{figure}
+
+\begin{figure}
+\begin{lstlisting}[frame=single]
+Set UB=min(n,2*v)
+set k=1
+while k < UB
+  sch = A(machines,k)
+  if jobspan(sch) > T
+    return A(machines,min(1,k-1))
+  cost = cost(sch);
+  if k=1 OR cost < min_cost
+    min_cost = cost;
+    min_sch = sch;
+return min_sch;
+\end{lstlisting}
+\caption{Scheduling Algorithm}
+\label{fig-scheduler}
 \end{figure}
@@
 data scheduled to $r$ across all VMs has the upper bound of twice the optimal
-amount of data for a perfectly balanced schedule (i.e. the worst case for any
-round is bounded by twice the best case).
+amount of data for a perfectly balanced schedule.
 
@@
 the set of all rounds.
-now define $2b_m$ to be the upper bound for data backuped up in a single round, 
+now define $2b_m$ to be the upper bound for data backed up in a single round, 
 where 

### 2013-11-25 batchdedup/eval.tex
added dual bin packing text back into paper. Added figures comparing jobspan and avg backup time

@@
   \label{fig:mpibuf-mem}
+\end{figure}
+
+\todo{The names of the algorithms are just the temporary names I've been using for coding, DBP2 is the relative of the dual bin packing algorithm, BPL is the machine by machine largest VM to shortest round algorithm}
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Network Buffer Size},
+		xlabel={Rounds},
+		ylabel={Total Jobspan (s)},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+                %legend pos=north west
+		]
+                \addplot table[x=Rounds,y=DBP2jobspan] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y=BPLjobspan] {figures/packing_comparison.txt};
+                \legend{DBP2, BPL};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Jobspan for DBP2 and BPL}
+  \label{fig:jobspan-comparison}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Network Buffer Size},
+		xlabel={Rounds},
+		ylabel={Average Backup Time (s)},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+                %legend pos=north west
+		]
+                \addplot table[x=Rounds,y=DBP2avgbackup] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y=BPLavgbackup] {figures/packing_comparison.txt};
+                \legend{DBP2, BPL};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Average Backup Time for DBP2 and BPL}
+  \label{fig:avgbackup-comparison}
 \end{figure}

### 2013-12-10 thesis/Abstract.tex
Thesis, first draft.

%
%  Abstract
%

\begin{abstract}

\addcontentsline{toc}{chapter}{Abstract}
A cloud platform that hosts a large number of virtual machines (VMs) has high storage demand for frequent backup of VM snapshots. Content signature based deduplication is necessary to eliminate excessive redundant blocks.  While dedicated backup storage systems can be used to reduce data  redundancy,  such an architecture is expensive and introduces huge network  traffic in a large cluster.   This thesis research is focused on a low-cost backup and deduplication service collocated with other cloud services to reduce infrastructure and network cost.

The previous research for cluster-based data deduplication has concentrated on various inline solutions. The first part of the thesis work is a  highly parallel and offline solution with synchronized backup scalable for a large number of virtual machines. The key idea is to separate duplicate detection from the actual storage backup, and partition global index and detection requests among machines using fingerprint values. Then each machine conducts duplicate detection partition by partition independently with minimal memory consumption. Another optimization is to allocate and control buffer space for exchanging detection requests and duplicate summaries among machines. The memory requirement and disk usage for the proposed solution is very small while the overall throughput and backup process timing is not compromised. Our evaluation validates this and shows a satisfactory backup throughput in a large cloud setting.

The second part of the thesis work is a VM-centric collocated backup service with inline deduplication. The key difference compared to the previous work is its novelty in fault resilience and low resource usage. We propose a multi-level selective deduplication scheme which integrates similarity-guided and popularity-guided duplicate elimination under a stringent resource requirement. This scheme uses popular common data to facilitate fingerprint comparison, localizes deduplication as much as possible within each VM, and associates underlying file blocks with one VM for most of cases. The main advantage of this scheme is that it strikes a balance between inner and inter VM  deduplication to increase parallelism and  improve reliability.  Our analysis shows that this VM-centric scheme can provide better fault tolerance while using a small amount of computing and storage resource. We have conducted a comparative evaluation of this scheme on its competitiveness in terms of deduplication efficiency and backup throughput.

\abstractsignature

\end{abstract}

%\begin{germanabstract}

%\addcontentsline{toc}{chapter}{Zusammenfassung}

%\end{germanabstract}

### 2013-12-10 thesis/Acknowledgements.tex
Thesis, first draft.

\begin{acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
I want to take this opportunity to thank my advisor Professor Tao Yang for 
his invaluable advice and instructions to me on selecting interesting and challenging
research topics, identifying specific problems for each research phase, 
as well as preparing for my future career.

I also want to thank members and ex-members of my research group, Michael Agun, and 
Hong Tang, for their incessant support in the forms of technical discussion, 
system co-development, cluster administration, and other research activities.

Finally, I want to thank my dissertation committee members, Professor 
Jianwen Su, Professor Richard Wolski 
for their insightful comments over my dissertation.

This dissertation study was supported in part by NSF xxx.
\end{acknowledgements}

### 2013-12-10 thesis/Background.tex
Thesis, first draft.

\chapter{Background}
\label{chap:back}
At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which
means no fine-grained file system metadata can be used to determine the changed data. 
Backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.

Many deduplication systems have been built for VM backup purposes. 
In this chapter we will investigate several system design options at high-level.
Section~\ref{back:coll} discusses the comparison of collocated solution vesus dedicated appliance.
Section~\ref{back:trade} talks the tradeoffs in designing a deduplication storage system.
Section~\ref{back:algo} introduces deduplication optimizations.

\section{Architecture Options - Collocated vesus Dedicated} 
\label{back:coll}
Dedicated deduplication is a great way to augment existing tape based backup infrastructures due to its simple integration with existing backup applications. So if an end user is happy with their current backup application, a Dedicated approach may be very compelling as it does not necessitate a significant change of the backup infrastructure or the relearning of a new backup application.

One of the strongest use cases for Dedicated deduplication is protecting large Oracle or SQL database (in excess of 2TBs) environments. Since each of these applications can natively backup their data to a Dedicated appliance, from an integration standpoint, there is low/no barrier to entry to begin protecting these environments rapidly. Some deduplication appliance manufacturers even offer direct integration with database backup tools like Oracle RMAN. This helps drive out some of the inefficiencies in the data center as both backup administrators and DBAs can share a common pool of backup resources and achieve reductions where there may be an overlap in backup processes.

Another benefit to database target deduplication is a reduction in the consumption of primary storage resources. Many DBAs utilize a disk to disk to tape backup scheme to protect log files, table spaces etc. on primary storage that has no deduplication capability. Between periodic snapshots and direct dumps to disk, there tends to be an over consumption of expensive disk resources when protecting database environments. By migrating database backups to a deduplication appliance, scarce primary storage resources can be reclaimed for production applications. Whats more, the deduplication effect for database environments can range from a 5-1 to a 20-1 reduction in the physical disk or tape space required to perform normal backup operations - potentially generating a return on investment.

In short, Dedicated deduplication provides an easy entry point for customers interested in leveraging the efficiencies of deduplication to reduce backup windows, enhance data protection and improve overall operational efficiencies in the data center without making major changes to their environment.

Collocated deduplication generally consists of backup application software with embedded deduplication at the client layer and some form of disk storage to serve as the repository for backup data. As the name implies, Collocated data deduplication takes place at the source or where data originates - at the server or application layer. Collocated deduplication offerings consist of placing a lightweight backup agent at the virtual or physical server and then only backing up the unique data segments that have changed since the prior backup job. The data segments are then sent over the LAN and/or WAN to a disk based storage grid for protection.

The advantages of Collocated deduplication are rapid backup windows and a large reduction in the volume of LAN/WAN traffic generated during the backup window. Instead of pushing a full backup over the wire from a media server each night, unique deduplicated backup segments trickle between the application hosts and the backend deduplication storage grid. The data transfers are extremely efficient - equivalent to a meta-data handshake. Think speed of source side deduplication as an incremental (only more efficient) forever with the benefit of producing a full backup each night.

In general, Collocated deduplication is a great solution for environments with a low daily data change rate. Great use cases for Collocated deduplication solutions include data on the edge  remote offices and laptops in the field (great for C level execs) and file heavy environments (NAS, VMware). In the case of remote offices, often the investment in Collocated deduplication can be justified by the cost avoidance attained by eliminating the legacy remote office backup infrastructure  backup server hardware, software, tape libraries, tape media, courier expenses, etc.

In the VM snapshot backup case that we study, there is hardly any value for deploying dedicated backup
solution because it's not affordable to VM users. Therefore we seek for low-cost collocated deduplication options
to reduce the VM snapshot storage cost.
Collocating a backup service on the existing
cloud cluster avoids the extra cost to acquire a dedicated backup facility
and reduces the network bandwidth consumption in transferring the
raw data for backup.

\section{Tradeoff in Design Goals}
\label{back:trade}
Given we are designing scalable low-cost collocated deduplication solutions,
the effectiveness of a deduplication system is determined 
by the extent to which it can achieve three mutually competing goals: 
deduplication efficiency, throughput, and job turnaround time. 
Deduplication efficiency refers to
how well the system can detect and share duplicate data
units which is its primary compression goal. Throughput refers
to the rate at which data can be transferred in and out of
the system, and constitutes the main performance metric.
Job turnaround time is the total time for a backup job from submit to finish.
All three metrics are important. Good dedupe efficiency 
reduces the storage cost. High throughput
is particularly important because it can enable fast backups, 
minimizing the length of a backup window. 
Job turnaround time reflects how fast primary storage 
can be released from backup related I/O activity.
Among the three goals, it is easy to optimize any two of them,
but not all. To get good deduplication efficiency, 
it is necessary to perform data indexing for duplicate detection.
The indexing metadata size grows linearly with the capacity of the system. 
Keeping this metadata in memory,
would yield good throughput. 
But the amount of available RAM would set a hard limit to the scalability of the
system. Partition indexing metadata man remove
the scalability limit, but significantly hurt job turnaround time.
Finally, we can optimize for both throughput and turnaround time, 
, but then we lose deduplication as there's no cheap solution to search all metadata quickly. 
Achieving all three goals is a non-trivial task.

Another less obvious but equally important problem is
duplicate reference management: duplicate data sharing
introduces the need to determine who is using a particular data unit, and when it can be reclaimed. 
The computational and space complexity of these reference management mechanisms grows 
with the amount of supported capacity. Real world experience has shown that the
cost of reference management for garbage collection (upon addition and deletion of data) 
has become one of the biggest 
bottlenecks.

This dissertation studies two low-cost deduplication design options with different tradeoffs. 
Chapter~\ref{chap:offline} gives a synchronous parallel deduplication design that
sacrifices the job turnaround time to achieve high throughput and deduplication efficiency.
Chapter~\ref{chap:inline} describes an multi-level selective deduplication solution
that comprises deduplication efficiency to improve throughput and job turnaround time.

\section{Deduplication Optimizations}
\label{back:algo}
Since it is expensive to compare a large number of chunk signatures for deduplication,
several techniques have been proposed to speedup searching of duplicate
fingerprints. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
and a parallel batch solution for cluster-based deduplication is 
studied in ~\cite{wei2013}. 
All of the above approaches have focused on optimization of deduplication
efficiency, and none of them have considered the impact
of deduplication on fault tolerance in the cluster-based environment that we have considered
in this dissertation.

### 2013-12-10 thesis/Conclusion.tex
Thesis, first draft.

\chapter{Conclusion and Future Works}
\label{chap:concl}
Building deduplication in backup storage with the ever-increasing demand on 
scalability and throughput is a challenging  task.  This dissertation investigates 
techniques in building a VM snapshot storage system, that provides low-cost
deduplication support for scale out VM clouds.  In particular, our work focuses on 
three specific  aspects  of VM snapshot deduplication: synchronous solution for offline duplicate detection,
multi-level selective approach for inline deduplication, and data management on top of
cloud file system with emphysis on fault tolerancy and garbage collection.
Our system  has  been  implemented on Xen based Linux VM clusters.

This dissertation begins with studying a low-cost multi-stage
parallel deduplication solution for automatically synchronous backup use case. 
We split the original inline deduplication process into different stages to
facilitate parallel batch processing.
We first performing parallel duplicate detection for VM content blocks among all
machines before performing actual data backup. Each
machine accumulates detection requests and then performs 
detection partition by partition with minimal resource usage. 
Fingerprint based partitioning allows
highly parallel duplicate detection and also simplifies
reference counting management
Because the design of separation
of duplicate detection and actual backup, we are able
to evenly distribute fingerprint comparison among clustered machine nodes, 
and only load one partition at time
at each machine for in-memory comparison.
which makes the proposed scheme very resource-friendly 
to the existing cloud services.

In the next we present a multi-level selective deduplication scheme for 
on-demand snapshot service in VM cloud. Our approach utilitizes similarity guided inner-VM
deduplication to localize backup data dependency and exposes
more parallelism, while depending on popularity guided cross-VM deduplication 
with a small
popular data set effectively covers a large amount of duplicated data. 
Our solution accomplishes the majority of potential
global deduplication saving while still meets stringent cloud
resources requirement. Compare to todays widelyused snapshot technique, 
our scheme reduces almost two-third
of snapshot storage cost. Finally, our scheme uses a very
small amount of memory on each node, and leaves room for
additional optimization we are further studying.

Finally this dissertation proposes a collocated VM-centric backup architecture
built on the top of a cloud cluster with emphysis on fault tolerancy and garbage collection. 
Benefited from our multi-level selective deduplication scheme, 
we can reduce cross-VM data dependency and exposes more parallelism. 
VM-specific file
block packing also enhances fault tolerance by reducing
data dependencies.
The key contribution is a VM-centric data management scheme 
to maximize data localization (reduce cross VM sharing) while delivering 
competitive deduplication efficiency. In addition,
such design allows garbage collection to be performed in a 
localized scope and we propose an approximate deletion
scheme to reduce this cost further.
As supported by theoretical analysis and study on real VMs, 
the availability of snapshots increases substantially with a small
replication overhead for popular inter-VM chunks.
Most importantly, our design places a special consideration for 
low-resource usages as a collocated cloud service.

The design of our VM-centric deduplication approach exposes the potential of
envolving into a general purpose cloud backup system or file caching service. The idea of collecting
popular data becomes more interesting as to how much data in common in people's personal usages.
However, the access to popular data could be a bottleneck in the I/O path if not designed carefully,
these issues remain to be solved.

### 2013-12-10 thesis/DataManagement.tex
Thesis, first draft.

\chapter{VM-centric Storage Management with Approximate Deletion}
\label{chap:data}
\section{Introduction}
\label{data:intro}
In this chapter, we discuss a low-cost architecture option that collocates
a backup service with other cloud services and uses a minimum amount of resources. 
We also consider the fact that after
deduplication, most data chunks are shared by several to many virtual machines.
Failure of a few shared data chunks can have a 
broad effect and many
snapshots of virtual machines could be affected.
The previous work in deduplication focuses on the efficiency and approximation of
fingerprint comparison, and has not addressed fault tolerance issues  together with deduplication.
Thus we also seek deduplication options that yield better fault isolation.
Another issue considered is that
that garbage collection after deletion of old snapshots also competes for computing resources. 
Sharing of data chunks among by multiple VMs needs to be detected during
garbage collection and such dependencies complicate deletion operations.

The key contribution of this work is the development and analysis of a VM-centric approach
which considers fault isolation and integrates multiple duplicate detection strategies
supported by similarity guided local deduplication
and popularity guided global deduplication. 
This approach localizes duplicate detection within each VM  
and packages only data chunks from the same VM into a file system block as much as possible.
By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
this scheme can afford to allocate extra replicas of these shared chunks for better
fault resilience while sustaining competitive deduplication efficiency.
In addition, our VM-centric design allows garbage collection to be performed in a localized
scope and we propose an approximate deletion scheme to reduce this cost further.
Localization also brings the benefits of greater ability to exploit parallelism so
backup operations can run simultaneously without a central  bottleneck.
This VM-centric solution uses a small amount of  memory while delivering reasonable deduplication efficiency.

The rest of this chapter is organized as follows.
Section~\ref{data:options} reviews the background and discusses the design options for snapshot backup 
with a VM-centric approach. 
Section~\ref{data:arch} describes our system architecture and implementation details.
Section~\ref{data:analysis} analyzes the tradeoff and benefits of our approach. 
Section~\ref{data:deletion} describes out approximate deletion algorithm.
%   the benefit of our approach for fault isolation. 
Section~\ref{data:impl} is our experimental evaluation that compares with other approaches.
Section~\ref{data:related} reviews the related works.
Section~\ref{data:concl} concludes this chapter.

\section{Background and Design Considerations}
\label{data:options}
Our key design consideration is VM dependence minimization during deduplication 
and file system block management.
\begin{itemize}
\item {\em Deduplication localization.}
Because a data chunk is compared with fingerprints collected from all VMs during
the deduplication process, only one copy of duplicates is stored in the storage,
this artificially creates data dependencies among different VM users. 
Content sharing via deduplication affects fault isolation since machine failures happen periodically 
in a large-scale cloud and
loss of a small number of shared data chunks can 
cause the unavailability of snapshots for a large number of virtual machines.
Localizing the impact of deduplication can increase fault isolation and resilience.
Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
discouraged. 
Another disadvantage of sharing is that it complicates snapshot deletion, 
which  occurs frequently when snapshots expire regularly. 
The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for deletion, but still carries a significant cost
to count if a data chunk is still shared by other snapshots. 
Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
deduplication efficiency, and  can facilitate parallel execution of snapshot operations.
\item{\em  Management of file system blocks.}
The file system block (FSB) size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
while the data chunk in a typical deduplication system is of a non-uniform size with 4KB or 8KB on average.
Packaging data chunks to an FSB can create more data dependencies among VMs
since a file system block can be shared by even more VMs.
Thus we need to consider a minimum association of FSBs to VMs in the packaging process.
\end{itemize}

Another consideration is the computing cost of deduplication.
Because of collocation of this snapshot service with other existing cloud services, 
cloud providers will want the backup service to only consume small resources
with a minimal impact to the existing cloud services.
The key resource for signature comparison  is memory for storing the fingerprints. 
We will consider the approximation techniques with reduced memory consumption along 
with the fault isolation considerations discussed below.

We call the traditional deduplication approach as VM-oblivious (VO)
because they compare fingerprints of snapshots without consideration of VMs.
With the above  considerations in mind, we study a 
VM-centric approach (called VC)
for a collocated backup service with resource usage friendly
to the existing applications.

We will first present an VM-centric architecture and implementation design with deletion support 
that can be integrated with our multi-level selective deduplication scheme, then
discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation.

\section{Snapshot Storage Architecture}
\label{data:arch}
\subsection{Components of a Cluster Node}
\label{data:node}
Our VM cloud runs on a cluster of Linux machines with Xen-based VMs and
an open-source package for the distributed file system  called QFS~\cite{michael2013}. 
All data needed for the backup service including snapshot data and metadata
resides in this distributed file system. 
One physical node hosts tens of VMs, each of which accesses its virtual machine disk image through the
virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).

As depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication agent,
3) a snapshot store client to store  and access snapshot data,
and 4)  a PDS client to support PDS metadata access.

We use the virtual device driver in Xen that employs a bitmap to track the changes 
that have been made to the virtual disk (CBT).
Every bit in the bitmap represents a fixed-sized (2MB) segment, indicating whether the segment
has been modified since last backup. 
Segments are further divided into variable-sized chunks (average 4KB) 
using a content-based chunking algorithm~\cite{frame05}, 
which brings the opportunity of fine-grained deduplication.
When the VM issues a disk write, the dirty bit for the corresponding segment is set
and this indicates such a segments needs to be checked during snapshot backup. 
After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
For data modification during backup, copy-on-write protection is set so that backup can continue to
copy  a specific version while new changes are recorded.
%copies a frozen version while the modification can still carry on.

The representation of each snapshot has  a two-level index data structure.
The snapshot meta data (called snapshot recipe) contains a list of segments, each of which contains segment
metadata of its chunks (called segment recipe).
In snapshot and segment recipes, 
the data structures  include references to the actual data location to eliminate the need for additional indirection.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=4in]{images/socc_arch_cluster}
    \caption{System architecture and data flow during snapshot backup}
    \label{fig:arch_vm}
\end{figure}

\subsection{A VM-centric Snapshot Store for Backup Data}
\label{data:store}
We build the snapshot storage on the top of a distributed file system.
Following the VM-centric idea for the purpose of fault isolation,
each VM has its own snapshot store, containing new data chunks which are considered
to be non-duplicates.
As shown in Figure~\ref{fig:as_arch}, we explain the data structure of the snapshot stores as follows.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=4in]{images/sstore_arch}
  \caption{Data structure of a VM snapshot store.}
  \label{fig:as_arch}
\end{figure}

%\begin{itemize}
%\item
There is an independent store containing all PDS chunks shared among different VMs as
a single file.
%All PDS chunks are stored in one PDS file. 
Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
%There is an option to use a data structure similar to the non-PDS store. We opt
%for the simpler format because
Additional compression is not applied because 
for the data sets we have tested, we only observed limited spatial locality 
among popular data chunks. On average the number of consecutive PDS index hits is lower than 7.
Thus it is not very effective to group a large number of chunks as a compression and data fetch unit. 
For the same reason, we decide not to take the sampled index approach~\cite{Guo2011} 
for detecting duplicates from PDS as limited spatial locality is not sufficient to enable
effective prefetching for sampled indexing.

PDS data are re-calculated periodically, but 
the total data size is small.  When
a new PDS data  set is computed, the in-memory PDS index is replaced, but 
the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
The old data are not removed because they can still be referenced by the existing snapshots. 
A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months).

%\end{itemize}

For non PDS data, the snapshot store of a VM is  divided into a set of containers and 
each container is approximately 1GB. 
The reason for dividing the snapshot store into containers is to simplify the compaction process
conducted periodically. As discussed later, data chunks are deleted from old snapshots
and chunks without any reference from other snapshots can be removed by this compaction process.
By limiting the size of a container, we can effectively control the length of each round of compaction.
The compaction  routine can work on one container at a time and move the in-use data chunks to another container.

Each non-PDS data container is further divided into a set of chunk data groups. Each chunk group is composed of
a set of data chunks and is the basic unit in data access and retrieval. 
In writing a chunk during backup, the system accumulates data chunks and stores the entire
group as a unit after compression. This  compression can reduce data by several times  in our tested data.
When accessing a particular chunk, its chunk group is retrieved from the storage
and decompressed. Given the high spatial locality and usefulness of prefetching  in 
snapshot chunk accessing~\cite{Guo2011,foundation08},
retrieval of  a data chunk  group naturally works well with prefetching. 
A  typical chunk group contains 1000 chunks in our experiment.
% with an average size of 200-600 chunks.

%\item
Each non-PDS data container is represented by three files in the DFS:
1) the container data file holds the actual content, 
2) the container index file is responsible for translating a data reference
into its location within a container, and 
3) a chunk deletion log file records all the deletion requests within  the container.

%\item
A non-PDS data chunk reference stored in the index of snapshot recipes
is composed of two parts: a container ID with 2 bytes and a local chunk ID with 6 bytes.
Each container maintains a local  chunk counter and assigns the current number 
as a chunk ID  when  a new chunk is added to this  container. 
Since data chunks are always appended to a snapshot store during backup, 
local chunk IDs are monotonically increasing.
When a chunk is to be accessed, the segment recipe contains a reference pointing to  a data chunk
in the PDS store or in a non-PDS VM snapshot  store. 
Using  a container ID, the corresponding container index file of this VM is accessed and 
the chunk group is identified using a simple chunk ID range search. Once the chunk group is loaded to memory, 
its header contains the exact offset of the corresponding chunk ID and the content is then accessed from the memory buffer.

Three API calls are supported for data backup:
%\begin{itemize}

%\item
\noindent\textbf{Append()}. 
For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
Note that PDS append may only be used during PDS recalculation.
For non-PDS data, this call places a chunk into 
the snapshot store and returns a reference to be stored in 
the recipe metadata of a snapshot. 
The write requests to append data chunks to a VM store are accumulated at the client side. 
When the number of write requests reaches a fixed group size, the snapshot store client compresses
the accumulated   chunk group, adds a chunk group index  to the beginning of the group, and then
appends the header and data  to the corresponding VM file.
A new container  index entry is also created for each chunk group and is written to the corresponding
container index file.

%\item
\noindent\textbf{Get()}.
The fetch operation for the PDS data chunk is straightforward since each reference contains 
the file offset, and the size of a PDS chunk is available from a segment recipe.
We also maintain a small data cache for the PDS data service to speedup common data fetching.

To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client first loads the
corresponding VM's container index file specified by the container ID, then searches the chunk
groups  using their  chunk ID coverage.
After that, it reads the identified chunk group from DFS, decompresses it, and seeks to the exact chunk data 
specified by the chunk ID. 
Finally, the client updates its internal chunk data cache with the newly loaded content to 
anticipate future sequential reads.

%\item
\noindent\textbf{Delete()}.
Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user and we discuss this in more details in next
subsection.
%(we will discuss the snapshot deletion in detail in the following subsection).
When deletion requests are issued for a specific container,
those requests are simply recorded into the  container's deletion log initially and thus  a lazy
deletion strategy is exercised.
Once local chunk IDs appear in
the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
This is ensured because we only dedup against the direct parent of a snapshot, so the deleted snapshot's blocks
will only be used if they also exist in other snapshots.
Periodically, the snapshot  store identifies those containers with an excessive
number of deletion requests to  compact and  reclaim the corresponding disk space. 
During compaction, the snapshot store creates a new container (with the same container ID) to replace the 
existing one. This is done by sequentially scanning the old container, copying all the chunks that are not 
found in the deletion log to the new container, and creating new chunk groups and indices. 
Every local chunk ID however is directly copied rather than re-generated. This
process leaves holes in the chunk ID values, but preserves the order and IDs of chunks.
As a result, all data references stored 
in recipes are permanent and stable, and the data reading process
is as efficient as before. Maintaining the stability of chunk IDs also ensures that recipes do not
depend directly on physical storage locations, which simplifies data migration.
%\end{itemize}

\section{Analysis of VM-centric Approach}
\label{data:analysis}
In this section we give out analysis of the impacts of our VM-centric deduplication scheme. 
As introduced in chapter~\ref{inline:dedup}, our VM-centric approach put the cluster wide 
popular data into PDS which prevent each VM from keeping their own copies. We will show that by adding
extra replication to PDS data, this strategy brings advantages to both fault tolerancy and deduplication efficiency.
The parameters we will use in our analysis below are defined in Table~\ref{tab:symbol}.

\begin{table}[htbp]
\centering
\tabcolsep=0.11cm
\begin{tabular}{|p{1.5cm}|p{11cm}|}
\hline
$k$ &  the number of top most popular chunks selected for deduplication\\ 
\hline
$c$ &  the total amount of data chunks in a cluster of VMs\\ 
\hline
$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
\hline
$f_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in local deduplication\\
\hline
$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belonging to  PDS\\
\hline
$p$ & the number of machines in the cluster\\
\hline
$V$ & the average number of VMs per machine\\
\hline
$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
\hline
$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$ & the average number  of non-PDS FSBs blocks in a VM for VC\\
\hline
$N_2$ & the average number  of PDS FSBs in a VM for VC\\
\hline
$N_o$ & the average number  of FSBs  in a VM for VO\\
\hline
A(r) & the availability of an FSB  with replication degree $r$\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

\subsection{Impact on Deduplication Efficiency}
Choosing the value $k$ for the most popular chunks affects the deduplication efficiency.
We analyze this impact based on the characteristics  of the VM snapshot traces
studied from  application datasets.
A previous study shows that the popularity of data chunks after local deduplication follows 
a Zipf-like distribution\cite{Breslau1999a} and its
exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
Figure~\ref{fig:zipf-data} illustrates the Zipf-like distribution of chunk popularity.

%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
%let $c$ be the total number of data chunks. 
%$c_u$ be the total number of fingerprints 
%in the global index after complete deduplication, and
%$f_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
The total number of chunks in our backup storage which
has local duplicates excluded is $c (1-\delta)$, this can be represented
as the sum of each unique fingerprint times its frequency:
%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
\[
f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
\]
Given $\alpha <1$, $f_1$ can be approximated with integration:
%\begin{equation}
\[
f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
\]
%\end{equation}

Thus putting the $k$ most popular fingerprints into PDS index can remove the following number of chunks during global 
deduplication:
\[
f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}
=c(1-\delta) \sigma^{1-\alpha}.
\]

Deduplication efficiency of the VC approach using top $k$ popular chunks
is the percentage of duplicates that can be detected:  
\begin{equation}
\label{eq:dedupeff}
%\begin{split}
%e_k &= 
E_c=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
{c  - c_u }.\\
%\end{split}
\end{equation}

% After the global deduplication, the number of remaining chunks is:
% \[
% c-E(c-c_u)
% \]

We store the PDS index using a distributed shared memory hash table such as Memcached
and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
As the number of physical machines ($p$) increases,
the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
a constant because each physical machine on average still hosts a fixed constant number of 
VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
remains constant.
Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={PDS Coverage},
            width=0.7\linewidth,
            height=0.5\linewidth,
            cycle multi list={
                mline\nextlist
                [3 of]mmark*\nextlist
            },
            %cycle list name=mcolor,
            xlabel={Total num. chunks stored (in billions)},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.30)},
            anchor=north},
            ]
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {data/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {data/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {data/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {data/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {data/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {data/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{Predicted vs. actual PDS coverage as data size increases.}
  \label{fig:cds-coverage}
\end{figure}
Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global deduplication due to PDS.
We call this PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
While the predicted value remains flat, measured PDS coverage increases as more VMs are involved.
This is because the actual $\alpha$ value increases with the data size.
%Then  PDS coverage PDS increases as more VMs are involved.

\subsection{ Impact on Fault Isolation}

\begin{figure}
    \centering
    \subfigure[Sharing of file system blocks under VC]
    {
        \includegraphics[width=4in]{images/share_vc}
        \label{fig:share_vc}
    }
    \\
    \subfigure[Sharing of file system blocks under VO]
    {
        \includegraphics[width=4in]{images/share_vo}
        \label{fig:share_vo}
    }
    \caption{Bipartite association of VMs and file system blocks under (a) VC and (b) VO. }
    \label{fig:share}
\end{figure}

The replication degree of the backup storage 
is $r$ for regular file system blocks and $r=3$ is a typical setting in distributed
file systems~\cite{googlefs03,hdfs10}.
Since $\sigma$ is small (e.g.  2\% in our experiments),  
the impact of replication on storage increase is very small even 
when choosing  $r_c/r$ ratio as 2 or 3.

%In the VC approach, a special replication degree $r_c$ is used for PDS data where $r_c>r$. 
%The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
%$ k*r_c  + (c-E(c-c_u))*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
%\[
%\sigma \frac{r_c}{r} + \frac{c-e(c-c_u)}{c_u}.
%\]
%Since $\sigma$ is small (it is 2\% in our experiments),  
%term $\sigma \frac{r_c}{r}$ is small in the above expression.  
%Thus the impact on storage increase is very small even when we choose a large $r_c/r$ ratio. 
%For example, $r_c/r=2$ or 3.

Now we  assess  the impact of losing $d$ machines 
to the VC and VO approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use an FSB rather than a deduplication
data chunk as our unit of failure because the DFS keeps
file system blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probability of losing a snapshot FSB of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
if this block is used by the VM.

For VC, each VM has an average number $N_1$ of non-PDS FSBs
and  has  an average of  $N_2$ PDS FSBs. 
Each non-PDS FSB is associated with one VM
 and  we denote that PDS FSBs are
shared by an average of $V_c$ VMs. 
%Let $s$ be the average number of chunks per file system block, 
%$V$ be the average number of VMs hosted on each machine. 
Then, 
\[
V pN_1 s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
V pN_2 s  \approx c_u \sigma V_c.
\]

For VO, each VM has an average of $N_o$ FSBs
and let $V_o$ be the average number of VMs shared by each FSB.
\[
V pN_o s  = (c- E_o(c-c_u) ) V_o.
\]

Since each FSB (with default size $64MB$) contains many chunks (on average 4KB),
each FSB contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  Since $c>> c_u$, from the above equations:
\[
\frac{N_1}{N_o} \approx  \frac{1-E_o}{(1-E_c) V_o}.
\] 
When $E_c$ is close to $E_o$,
%as demonstrated in Section~\ref{sect:evaldedup},
$N_1$ is much smaller than $N_o$. 
%When there is a failure in FSBs with replication degree $r$
%and there is no failure for PDS data with more replicas,   a VM in
%the VC approach has a much lower chance to lose a snapshot than VO. 
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
%our test dataset.
%For VC, we only show
%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
%one VM.
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO
and  $N_1$ is indeed  much smaller than $N_o$ in our tested dataset.  
%In fact, $N_1 +N_2 < N_o$. 
%This is likely because the PDS FSBs tightly pack data used by many VMs, 
%which decreases the overall number of FSBs required to backup a VM.
%Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
%VMs sharing each file block on average in VO.

%Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
                width=0.7\linewidth,
                height=0.5\linewidth,
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north east,
                legend style={
                    at={(1,0.825)},
                    anchor=north east
                },
                %legend columns=3
		]
                \addplot[blue,mark=none] table[x=VMs,y=N_O] {data/vm_links_all.txt};
                %\addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N_1] {data/vm_links_all.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N_2] {data/vm_links_all.txt};
                \legend{$N_o$,
                    %$N_1+N_2$,
                    $N_1$,
                    $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}

The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
 $N_2$ for VC and $N_o$ for VO.
Given normal data replication degree $r$, PDS data replication degree $r_c$, 
the availability of a file system block is the probability that  
all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
Namely, we define it as
\[
A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
\]
Then the availability of one VM's snapshot data under VO approach is the probability that
 all its FSBs are unaffected during the system failure:
%\begin{equation}
%\label{eq:VO}
%(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
\[
A(r)^{N_o}. 
\]
%\end{equation}

For VC, there are two cases for $d$ failed machines.
\begin{itemize}
\item
When $r \le d<r_c$,  there is no PDS data loss and  
the full snapshot availability of a VM in the VC approach is 
%\begin{equation}
%\label{eq:VC1}
%(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
\[
A(r)^{N_1}.
\]
%\end{equation}
Since $N_1$ is typically much smaller than $N_o$, 
the VC approach has a higher availability of VM snapshots than VO in this case.
%In the evaluation discussed in Section~\ref{sect:evaldedup}, 
%We have considered a worst case scenario where
%every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
%Even with $N_2$ being much higher than $N_o$ (as discussed below),
%the availability of VC snapshots is much higher than VO.

\item
When $r_c \leq d$, both non-PDS and PDS file system blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
%\begin{equation}
%\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\[
A(r)^{N_1} * A(r_c)^{N_2}.
\]
%\end{equation}
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize} 
%In the evaluation discussed in Section~\ref{sect:evaldedup},
We have considered a worst case scenario that
every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
Even with that, the availability of VC snapshots is still much higher than VO and  
there are two reasons for this:  1) $N_1$ is much smaller than $N_o$ as discussed previously.
2)  $A(r) < A(r_c)$ because $r < r_c$.  
Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
%that the availability of an individual file system block
different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.

% $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$

\comments{
\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            %extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {data/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {data/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {data/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of a file system block in a 100 machine cluster with different replication 
and failure settings.THIS PLOT WILL BE REPLACED BY TABLE}
  \label{fig:fsb-availability}
\end{figure}
}

\begin{table}
  \centering
    \footnotesize
    \tabcolsep=0.11cm
    \comments{%table data is obsolete, now uses pgfplotstable
        \begin{tabular}{|l|l|l|l|}
        \hline
        \multirow{2}{*}{Failures ($d$)}   & \multicolumn{3}{c|}{$A(r_c)\times 100\%$} \\
                                    %\cline{2-4}
                                    & $r_c=3$ & $r_c=6$ & $r_c=9$ \\
        \hline
        3 & 99.9994 & 100 & 100\\
        5 & 99.9939 & 100 & 100\\
        10 & 99.9258 & 99.9999 & 99.9999 \\
        20 & 99.2950 & 99.9967 & 99.9999 \\
        \hline
    \end{tabular}
    }
    \pgfplotstabletypeset[
        columns={NodesFailed,Availability3,Availability6,Availability9},
        columns/NodesFailed/.style={
            column name={\multirow{2}{*}{Failures ($d$)}}
        },
        columns/Availability3/.style={
            column name={\multicolumn{3}{c|}{$A(r_c) \times 100\%$}\\&$r_c=3$},
            fixed, precision=9
        },
        columns/Availability6/.style={
            column name={$r_c=6$},
            fixed, precision=9},
        columns/Availability9/.style={
            column name={$r_c=9$},
            fixed, precision=9},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
    ]{data/fsb_availability.txt}
    \caption{$A(r_c)$ as storage nodes fail in a 100 node cluster.}
    \label{tab:fsb-availability}
\end{table}

\section{Approximate Snapshot Deletion with Leak Repair}
\label{data:deletion}

In a busy VM cluster, snapshot deletions can occur frequently.
Deduplication complicates the deletion process because space saving relies on the sharing of data
and it requires the global references to deleted chunks to be identified before they can be safely removed.
The complexity of our distributed environment obviates reference counting as an option,
and while the mark-and-sweep techniques can be used and optimization can be considered~\cite{Fabiano2013},
it still takes significant resources to conduct reference counting every time there is a snapshot deletion.
%
%In the case of Alibaba, snapshot backup is conducted automatically and there are 
%about 10 snapshot stored for every VM customer.
% Snapshot deletion can occur frequently, for example when there is
% a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
% balanced storage use. 
%In addition, cloud users expect the reduced storage usage to be reflected
%instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.
We seek a fast solution with low resource usage to delete snapshots and
our VM-centric design simplifies the deletion process. 
Since PDS is small and separated, we can focus on unreferenced non-PDS chunks within each VM. 
%The PDS data chunks are commonly shared among all VMs and we do not consider them
%during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
Another resource-saving strategy we propose is
an {\em approximate} deletion strategy to trade deletion accuracy for
speed and resource usage. Our method sacrifices a small percent of storage leakage
to efficiently identify unused chunks.

\begin{figure}
  \centering
  \includegraphics{images/deletion.pdf}
  \caption{Approximate deletion merges existing snapshot summaries to check block reference validity contained by a deleted snapshot}
  \label{fig:deletion_flow}
\end{figure}

We depict our approximate deletion process in Fig.\ref{fig:deletion_flow}, this procedure contains three aspects.
\begin{itemize}
\item {\bf Computation for snapshot reference summary.}
Every time there is a new snapshot created,
we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
in this snapshot.
The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
For each VM we preset the vector size according to  estimation of VM image size,
given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
This can be done during the periodic leakage repair stage described below.

\item {\bf Approximate deletion with fast summary comparison.}
When there is a snapshot deletion,  
we need to identify if chunks to be deleted from that snapshot
are still referenced by other snapshots. 
This is done approximately and quickly by comparing the 
reference of deleted chunks  with
the merged reference summary vectors of other live snapshots.
The merging of live snapshot Bloom-filter vectors uses the bitwise OR operator 
and the merged vector still takes $z$ bits.
Since the number of live snapshots $h$ is limited for
each VM, 
the time and memory cost of this comparison is small, linear to the number of chunks to be deleted.

If a chunk's reference is not found in the merged summary vector, we are sure that
this chunk is not used by any live snapshots, thus it can be deleted safely.
However, among all the chunks to be deleted, 
there are a small percentage of unused chunks  which
are misjudged as  being in use, resulting in storage leakage.

\item {\bf Periodic repair of leakage}.
%[exlpain why second Bloom filter, why scan append store]
Leakage repair is conducted periodically to fix the above approximation error.
This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
A mark-and-sweep process  requires a scan of the entire snapshot store.
%Our VM-centric mark-and-sweep procedure is similar to Guo\cite{Guo2011} 
%in a way that the data dependency is clearly known.
%This generally requires a scan of almost the entire snapshot store which is much more expensive than approximate deletion,
%although certain optimized algorithms may apply\cite{Przemyslaw2013}. But 
Since it is a VM-specific procedure, 
the space and time cost is relatively small compared to the tranditional mark-and-sweep
which scans snapshot chunks from all VMs.
For example, consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process
in less than half an hour, assuming 50MB/s disk bandwidth is allocated.
\end{itemize}

%{\bf Discussion}
We now estimate the size of storage leakage and how often leak repair needs to be conducted.
Assume that  a VM keeps $h$ snapshots in the backup storage, creates and deletes one snapshot
every day. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
number of additional chunks added from one snapshot to the next snapshot version. Then the total number of 
chunks stored in a VM's snapshot store is about:
\[
U = u + (h-1)\Delta u.
\]

Each Bloom filter vector has  $z$ bits for each snapshot and let $j$ be the number of hash functions used by the
Bloom filter.  Notice that a chunk may appear multiple times in these summary vectors; however, this should not 
increase the probability of being a 0 bit in all $h$ summary vectors.
Thus the probability that a particular bit is 0  in all $h$ summary vectors is  
$(1- \frac{1}{z}) ^{j U}$. 
Then the misjudgment rate of being in use  is: 
\begin{equation}
\label{eq:falserate}
\epsilon = (1-(1-\frac{1}{z})^{jU})^j.
\end{equation}

For each snapshot deletion, the number of chunks to be deleted is nearly identical to the number of
newly added chunks $\Delta u$. 
Let $R$ be the total number of runs of approximate deletion between two consecutive 
repairs. We estimate  the total leakage $L$ after $R$ runs as:
\[
L = R \epsilon \Delta u.
\]

When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we trigger a leak repair. Namely,

\begin{equation}
\label{eq:leakrepair}
\frac{L}{U} = \frac{R \Delta u \epsilon}{u+(h-1)\Delta u } > \tau 
\Longrightarrow R > \frac{\tau}{\epsilon}\times\frac{u + (h-1)\Delta u}{\Delta u}.
\end{equation}

For example in our tested dataset,  
$h=10$ and each snapshot adds
about 0.1-5\% of new data. Thus we take ${\Delta u}/{u} \approx 0.025$. For a 40GB snapshot, $u\approx  10$ million.
Then $U=12.25$ million.
We choose  $\epsilon = 0.01$ and $\tau=0.05$.  From Equation~\ref{eq:falserate}, 
each summary vector requires $z=10U=122.5$ million bits or 15MB. From Equation~\ref{eq:leakrepair}, 
leak repair should be triggered once for every R=245 runs of approximate deletion. 
When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
only one full leak repair for one physical machine scheduled for every 9.8 days. 
If $\tau = 0.1$ then leakage repair would occur every 19.6 days.

\section{System Implementation and Experimental Evaluations}
\label{data:impl}
We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
8-core 3.1Ghz AMD FX-8120 and 16 GB RAM. 
Our implementation is based on Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 6.
Our evaluation objective is to
study the benefit in fault tolerance and   deduplication efficiency of VC,  
and assess its backup throughput and  resource usage.

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes a distributed deduplication by routing a data chunk to one of cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally.

\subsection{Settings}
We have performed a trace-driven study using a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 100 machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage system while
a user may instruct extra snapshots to be saved.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
Based on our study of production  data,  each VM has about 40GB of storage  data  on average
including OS and user data disk.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

\subsection{Fault Isolation and Snapshot Availability}

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
We have assumed a worst-case scenario that  a PDS block is shared by every VM. 
%($V_c=p*V$), which is to be expected when PDS
%blocks are sorted by hash, as their order is randomized.
%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
%count the number of dependencies from a file system block to VM.
%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
%while VC with 99.9\% loses snapshots of 2.5 VMs.
%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
%and packs  data blocks for one VM as much as possible.  The extra replication
%for PDS blocks also significantly increases the snapshot availability even when
%a PDS file block is shared by every VM.
%=======
%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
%as storage nodes fail. 
%We assume a random distirbution of 64MB file system
%blocks (FSBs). where FSBs are not randomly distributed availability might
%be improved by limiting the number of storage nodes a particualr VM depends
%on but we take the conservative approach. We compare VO, the expected case for
%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
%based on measured values in our dataset.
%To obtain VO sharing of file blocks, we perform perfect deduplication over 105 VMs, 
%append unique chunks to a DFS file and
%count the number of dependencies from a file system block to VM.
%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
Our results show that even the worst case,  VC  still has a significantly  higher availability than VO as the number of
failed machines increases.
%Our VM-centric approach shows significant improvements
%in VM availability.
For example, with 5/100 machines failed and 25 VMs per machine, VO with 93.256\% availability would lose data in 169 VMs 
while VC with 97.763\% loses data for 56 VMs.
The key reason is that for most data in VC, only a single
VM can be affected by the loss of a single FSB. Since most FSBs contain chunks for a single VM, VMs can depend on a smaller number of FSBs.
% because our VM-centric approach
%localizes deduplication.

Although the loss of a PDS block affects many VMs,
by increasing replication for those blocks we minimize the effect on VM snapshot availability.
%By having extra replicas for the PDS data, we reduce the failure rate of PDS
%FSBs enough that the failure rate for the VM approaches the failure rate of the
%Non-PDS blocks. This minimizes the drop in availability between the expected
%and worst case for VC.
%
%One of the advantages of VC is that there is a division between
%popular and non-popular data to facilitate improved reliability. 
Figure~\ref{fig:pds-replication} shows
the impact of increasing PDS data replication. 
While the impact on storage cost is small, 
a replication degree of 6  has a significant improvement over 4, but the availability is about
the same for $r_c=6$ and $r_c=9$ (beyond $r_c=6$ improvements are minimal).

\begin{table}
  \centering
    \footnotesize
    \tabcolsep=0.11cm
    \pgfplotstabletypeset[
        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
        columns/NodesFailed/.style={
            column name={\multirow{3}{*}{Failures ($d$)}}
        },
        columns/VO100/.style={
            column name={
                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
            VO},
            fixed, precision=6
        },
        columns/VC100/.style={
            column name={VC},
            fixed, precision=6},
        columns/VO1000/.style={
            column name={VO},
            fixed, precision=6},
        columns/VC1000/.style={
            column name={VC},
            fixed, precision=6},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
        %skip rows between index={0}{3},
        %skip rows between index={4}{5},
        %skip rows between index={6}{10},
        %skip rows between index={11}{20},
        %skip rows between index={21}{41}
    ]{data/availability_table.txt}
    \caption{Availability of VM snapshots for VO and VC.}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=20,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{data/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{data/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{data/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{data/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{data/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
  \label{fig:pds-replication}
\end{figure}

\subsection{Deduplication Efficiency}
\label{sect:evaldedup}

%this version combines the old and the minhash alg. to compare against srb
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            width=\linewidth,
            height=0.75\linewidth,
            cycle list={%
                {blue,solid,mark=square*},
                {blue,solid,mark=triangle*,mark size=1.5},
                {blue,solid,mark=diamond*,mark size=1.5},
                %{blue,solid,mark=pentagon*,mark size=1.4},
                {red,draw=red,dotted,mark=square},
                %{red,densely dotted,mark=triangle,mark size=1.5},
                %{red,densely dotted,mark=diamond,mark size=1.5},
                {brown,dashed,mark=*},
                %{red,densely dotted,mark=o},
                %{red,densely dotted,mark=pentagon,mark size=1.4},
            },
            mark repeat={10},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            xmin=0,
            ymin=85,
            ymax=100,
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            legend columns=2,
            legend style={
                font={\tiny\sffamily},
                nodes={right}
                %at={(0.5,-0.2)},
                %anchor=north
            },
            ]
            \addplot table[x=VMs,y=MHcds4] {data/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds2] {data/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=MHcds1] {data/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHNocds] {data/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=cds4] {data/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=cds2] {data/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=cds1] {data/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=exbin] {data/exbin_efficiency_comparison2.txt};
            \legend{VC( $\sigma=4\%$),
                VC($\sigma=2\%$),
                %VC MH($\sigma=1\%$),
                VC(No PDS),
                %VC($\sigma=4\%$),
                VC($\sigma=2\%$\, No similarity guidance),
                %VC($\sigma=1\%$),
                SRB
            };
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication efficiency of VC and SRB.}
  \label{fig:exbin-efficiency-graph2}
\end{figure}

Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC,
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
namely the percent of duplicate chunks
which are detected and removed.
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
and  the deduplication efficiency can reach over 96.33\%.
When $\sigma=4\%$, the deduplication efficiency can reach 96.9\% while space consumption increases to 200MB per machine. 
%and  the deduplication efficiency can reach 96.489\%.
%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB can deliver up to 97.79\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with competitive deduplication efficiency.

% SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
% Thus this represents a tradeoff: VC provides better fault tolerance and fast
% approximate deletion with competitive (but slightly lower) deduplication
% efficiency.
% >>>>>>> 4dcd68612b052c0f890ed30361a9ed03771b5df1
%its loss of efficiency is caused by the routing of data chunks which restricts the search scope
%of duplicate detection.
%SRB provides slightly better deduplication efficiency than our VC approach, which we accept
%because we are rewarded by architecture-wise benefits such as fault-tolerance and fast 
%Though not our primary goal, this result does show that VC can remove competitive amount of duplicates.

Figure~\ref{fig:exbin-efficiency-graph2} also shows the curve  of VC without local similarity search.
There is a big efficiency drop in this curve when the number of VMs is about 30.
The reason is that  
%Without this (i.e. when we only 
there are VMs in which
data  segments are moved to another location on disk, for example when a file is rewritten
rather than modified in place,  
a dirty-bit or offset based detection would not be able to detect such a movement and 
similarity search becomes especially important.  We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently.
In general, adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about a 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
% The PDS-based global duplicate detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers an additional 3.45\% reduction.

In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about a 75.86\% reduction.
Similarity-guided local search can further reduce the data size
to about 12.05\% of original, namely it delivers a 50.08\% reduction to the dirty segments.
The popularity-guided global deduplication with $\sigma=2\% $
can reduce the data further to 8.6\% of its original size, so
it provides additional 28.63\% reduction to the remaining data.

%Figure~\ref{fig:exbin-efficiency-graph2} also shows the benefits of our minhash
%similar segment search in the parent snapshot.

\subsection{Resource Usage and Processing Time}

\comments{
\begin{table}
    \begin{tabular}{|c|c|}
    \hline
    PDS replication degree & Disk usage per machine  \\ \hline
    3                      & 3065GB             \\ \hline
    4                      & 3072GB             \\ \hline
    5                      & 3079GB             \\ \hline
    6                      & 3086GB             \\ \hline
    7                      & 3093GB             \\ \hline
    \end{tabular}
\caption{Storage space cost per machine for DFS under different PDS replication degree}
\label{tab:replication_cost}
\end{table}
}

{\bf Storage cost of replication.} 
%Table ~\ref{tab:replication_cost} shows the total storage space required by 
%VC as the PDS replication degree changes while non-PDS replication degree is fixed as 3. 
When the replication degree of both PDS and non-PDS data is 3, 
the total storage  for all VM snapshots in each physical machine takes about 3.065TB on average before compression
and 0.75TB after compression.  Allocating  one extra  copy for PDS data only adds  7GB in total per machine.
Thus PDS replication degree 6 only increases the total space by 0.685\% while PDS replication degree 9 adds 1.37\% 
space overhead, which is still small.
%The increase in storage cost is minimal because the PDS makes up a 
%small percent of the total storage space, while increasing replication degree has a  more significant benefit for
%availability as shown in Figure~\ref{fig:pds-replication}.

\begin{table}
  \centering
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Tasks & CPU & Mem &Read &  Write  & Time  \\ 
    & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline
%    1     & 19\% & 118.1 & 50MB/s 8.37 & 1.314\\ \hline
    1     & 19\% & 118 & 50 & 16.4 & 1.31\\ \hline
%    2     & 35\% & 131.8 & 9.0 & 1.226\\ \hline
    2     & 35\% & 132 &50  & 17.6 & 1.23\\ \hline
    %4     & 63\% & 154.1 & 9.3 & 1.179\\ \hline
    4     & 63\% & 154&50   & 18.3 & 1.18\\ \hline
    6     & 77\% & 171.9 & 50 &  18.8 & 1.162\\ \hline
%    8     & 82\% & 90.5 & 89.2 & \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\caption{Resource usage of concurrent backup tasks at each machine}
\label{tab:resource_usage}
\end{table}

{\bf Memory and disk bandwidth usage with multi-VM processing}. 
We have further studied the memory and disk bandwidth usage 
when running concurrent VM snapshot backup on each machine with $\sigma=2\%$. 
Table ~\ref{tab:resource_usage} gives the resource usage  when
running 1 or multiple  VM backup tasks at the same time on each physical machine. 
``CPU'' column is the percentage of a single core used. 
``Mem'' column includes 100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
receipt metadata and cache. 
``Read'' column is controlled as 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted too much.
The peak raw storage read performance is about 300MB/s and we only use 16.7\% with this collocation consideration.
``Write'' column is the I/O write usage of QFS and notice that each QFS write triggers disk writes in multiple machines due to
data replication.     50MB/s dirty segment read speed triggers about 16.4MB/s disk write for non duplicates with one backup task.
% [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
% the cloud infrastructure services and are shared among many applications.]
%We see our hybrid deduplication scheme only occupies a small amount of system resources. 
%The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
%memory during duplicate detection.

Table ~\ref{tab:resource_usage} shows that  a single backup task per node can complete the backup of the entire
VM cluster in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
significantly because of the controlled  disk read time.
%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.

{\bf Processing Time breakdown}.
Figure~\ref{fig:vc_srb_combined} shows
the  average  processing  time of  a VM segment under VC and SRB. 
VC uses $\sigma=2\%$ and $4\%$.
It has a breakdown of processing time.
``Snapshot read/write'' includes snapshot reading and writing from disk, and 
updating of the metadata.
`` Network transfer" includes the cost of transferring raw and meta data from one machine to another during 
snapshot read and write.
``Index access/comparison'' is the disk, network and CPU time during fingerprint comparison.
This includes PDS data lookup for VC and index lookup from disk in VO after Bloom filter lookup.
For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time. The network transfer time for VC and SRB is about the same, because the 
amount of raw data they transfer is comparable.
SRB spends slightly more time for snapshot read/write because during each snapshot  backup, SRB involves many small bins,
 while VC only involves few containers with a bigger size. Thus, there are more opportunities for I/O aggregation in VC to reduce seek time.
SRB has a higher cost for index access and fingerprint comparison because most of  chunk fingerprints are routed
to remote machines for comparison while   VC handles most of chunk fingerprints locally.

%on the index holding machine to access its index (often on the disk, supported by a Bloom filter) 
%and perform comparison.
%VC is faster in this regard because it conducts in-memory local search first and then
%accesses  the PDS on distributed shared memory, so most chunks can be dealt with locally.  
%SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
%local meta data index in addition to partition indices.
%As a result Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.
%Figure~\ref{fig:vc_srb_combined} also reports the average backup time for a VM in VC when
%varying the PDS size.  It lists the time distribution for data reading,
%similarity-guided local search, global PDS lookup, and non-duplicate data writing. 
%While data reading dominates the backup process, PDS lookup spends about a similar amount
%of time as local search.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=4in]{figures/vc_srb_combined}
  \caption{Average time to backup a dirty VM segment under SRB and VC}
  \label{fig:vc_srb_combined}
\end{figure}

% \begin{figure}[htbp]
%   \centering
%   \epsfig{file=figures/srb_vs_vc, width=3in}
%   \caption{Time to backup a dirty VM segment under SRB and VC}
%   \label{fig:srb_vs_vc}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=3in]{figures/single_backup_time}
%     \caption{Average time to backup a VM in VC with varying PDS sizes}
%     \label{fig:single_vm_backup}
% \end{figure}

% \begin{table*}[t]
%     \centering
%     \begin{tabular}{c|ccc|ccc}
%     Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
%     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
%     per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
%     1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
%     2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
%     4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
%     6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
%     \end{tabular}
% \caption{Throughput of software layers under different concurrency}
% \label{tab:throughput}
% \end{table*}
\begin{table}[htbp]
\centering
\begin{small}
    \begin{tabular}{|c|ccc|}
\hline
    Concurrent      & \multicolumn{3}{c|}{Throughput without}    \\
    backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} \\ \cline{2-4}
    per machine                & Backup                                     & Snapshot Store & QFS  \\ 
    		&                                      & (write) & (write)  \\ \hline
    1                       & 1369.6                                     & 148.0          & 35.3 \\
    2                       & 2408.5                                     & 260.2          & 61.7 \\
    4                       & 4101.8                                     & 443.3          & 103.1 \\
    6                       & 5456.5                                     & 589.7          & 143.8 \\ \hline
    \end{tabular}
\end{small}
\caption{Throughput of software layers per machine under different concurrency}
\label{tab:throughput}
\end{table}

{\bf Throughput of software layers.}
Table~\ref{tab:throughput} shows the  average throughput of software layer
when when I/O throttling is not applied to control the usage.
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer. The gap between this
column and  ``Backup" column is caused by significant data reduction by dirty bit and duplicate
detection. Only non-duplicate chunks trigger a snapshot store write.
``QFS'' column is the write request traffic to the underlying file system after compression.
For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
after compression.  The underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46GB/second without I/O restriction
per machine with 6 concurrent backup tasks. With a higher disk storage bandwidth available, the above backup
 throughput would be higher. 
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

%To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
%increase number of VMs to 12 to saturate our system capability. 
%We observed 
%the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
%which is far beyond our QFS file system capability. The reason behind it is our efficient
%deduplication architecture and compression which greatly reduce the amount of data that needs to be written to
%the file system. The main bottleneck here is that our QFS installation only
%manages one disk per node, which prevents it from fully utilizing the
%benefits of parallel disk access. We expect our architecture can
%perform even better in production clusters, which often have ten or more disks on each node.

% \begin{figure}
%     \centering
%     \subfigure[Backup throughput per node under controlled I/O bandwidth usage]
%     {
%         \includegraphics[width=3in]{figures/parallel_backup_with_read}
%         \label{fig:withread}
%     }
%     \\
%     \subfigure[Deduplication and storage system performance]
%     {
%         \includegraphics[width=3in]{figures/parallel_backup_no_read}
%         \label{fig:noread}
%     }
%     \caption{Throughput per-node with concurrent snapshot backup tasks}
%     \label{fig:parallel_backup}
% \end{figure}

 \subsection{Effectiveness of Approximate Deletion}

 \begin{figure}
     \centering
     \includegraphics[width=4in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}

Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{data:deletion}
given $\Delta u/u=0.025$,
while the solid line represents the actual leakage measured during the experiment. 
The Bloom filter setting is based on $\Delta u/u=0.025$.
After 9 snapshot deletions, the actual leakage ratio reaches 0.0015 and this means that
there is only 1.5MB space leaked for every 1GB of stored data.
The actual leakage can reach  4.1\% after  245 deletions.

\section{Related Work}
\label{data:related}
Since it is expensive to compare a large number of chunk signatures for deduplication,
several techniques have been proposed to speedup searching of duplicate
fingerprints. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
and a parallel batch solution for cluster-based deduplication is 
studied in ~\cite{wei2013}. 
All of the above approaches have focused on optimization of deduplication
efficiency, and none of them have considered the impact
of deduplication on fault tolerance in the cluster-based environment that we have considered
in this work.

In designing a VC duplication solution, we have considered and adopted some of
the following previously-developed techniques.
1)
{\em Changed block Tracking}.
VM snapshots can be  backed up  incrementally by identifying data segments that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Such a scheme  is  VM-centric since deduplication is localized. 
We are seeking for a tradeoff since 
global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
2) {\em Stateless Data Routing}.
One approach for scalable duplicate comparison is to use a content-based hash
partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011} 
Stateless data routing divides the deduplication work with a similarity approximation. This work 
is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 
each request is routed  to a machine which holds
a Bloom filter  or can fetch on-disk index for additional comparison.
While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
VM-specific local search.
3) {\em Sampled Index}.
One effective approach that reduces memory usage is 
to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
To use a distributed memory version of the sampled index, every deduplication request
may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.

\section{Concluding Remarks}
\label{data:concl}
In this chapter we propose a collocated backup service built on
the top of a cloud cluster to reduce network traffic and infrastructure requirements.
The key contribution is a VM-centric data management architecture that
integrate with multi-level deduplication to 
maximize fault isolation while delivering competitive deduplication efficiency.
Similarity guided local search reduces cross-VM data dependency and exposes more parallelism  
while global deduplication with a small common data set eliminates popular duplicates.
VM-specific file block packing also enhances fault tolerance by reducing data dependencies.
The design places a special consideration for low-resource usages as a collocated cloud service.
Evaluation using  VM backup data shows that VC strikes a tradeoff and 
can accomplish 96.33\% or 96.9\% of what complete global
deduplication can do.  The availability of snapshots increases substantially with 
a small replication overhead for popular inter-VM chunks.

We consider our approach has the potential to become a general purpose storage backend build
into the cloud to serve dropbox-like general file system backups.

### 2013-12-10 thesis/Dissertation.tex
Thesis, first draft.

@@
 %
-
-\documentclass[12pt,twoside,draft]{ucthesis}
-% todo: final options: [12pt,oneside,final]
+% draft options
+%\documentclass[12pt,twoside,draft]{ucthesis}
+% final options: 
+\documentclass[12pt,oneside,final]{ucthesis}
 
 \usepackage{graphics,epsfig}
-%\usepackage{amssymb, amsmath, amsfonts, epsfig, graphicx, graphics, latexsym, makeidx, psfig, subeqn, verbatim, xspace,textcomp}
+\usepackage{pgfplots}
+\usepackage{pgfplotstable}
+\usepackage{sansmath}
+\usepackage{mathptmx}
+\usepackage{subfigure}
+\usepackage{multirow}
+\usepackage{breqn}
+\usepackage{rotating}
+%\usepackage{amssymb, amsmath, amsfonts, epsfig, graphicx, graphics, latexsym, makeidx, psfig, subeqn, verbatim, xspace,textco
+%mp}
+\pgfplotsset{
+    %You are supposed to use append style rather than just setting
+    %parameters globally so they are easier to override to special cases
+    %thickness options:thin,ultra thin,very thin,semithick,thick,very thick
+    every axis/.append style={
+        thick,
+        tick style={thick},
+        tick label style={font=\small\mathversion{sans}\sffamily},
+        label style={font=\small\sffamily},
+        font={\small\sffamily},
+        mark size=1.0
+    },
+    every legend/.append style={font={\small\mathversion{sans}\sffamily}}
+}
+\pgfplotsset{
+    every mark/.append style={solid}
+}
+\pgfplotscreateplotcyclelist{mcolor}{%
+    {blue,every mark/.append style={fill=blue},mark=*},
+    {red,every mark/.append style={fill=red},mark=square*},
+    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=1.5},
+    {black,every mark/.append style={fill=black},mark=diamond*,mark size=1.5},
+    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=1.4},
+    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=1.5},
+    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
+    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
+    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=1.5},
+    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=1.5},
+    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=1.4},
+    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=1.5}}
 
+\pgfplotscreateplotcyclelist{mmark*}{
+    {mark=*},
+    {mark=square*},
+    {mark=triangle*,mark size=1.5},
+    {mark=diamond*,mark size=1.5},
+    {mark=pentagon*,mark size=1.4},
+    {mark=star,mark size=1.5},
+    {mark=asterisk,mark size=1.5},
+    {mark=+,mark size=1.5},
+    {mark=Mercedes star,mark size=1.5}}
+
+\pgfplotscreateplotcyclelist{mline}{
+    {solid,blue,every mark/.append style={fill=blue}},
+    {densely dashed,red,every mark/.append style={fill=red}},
+    {densely dotted,brown,every mark/.append style={fill=brown}},
+    {loosely dotted,black,every mark/.append style={fill=black}},
+    {loosely dashed,green!60!black,every mark/.append style={fill=green!60!black}},
+    {densely dashdotted,magenta!90!black,every mark/.append style={fill=magenta!90!black}},
+    {densely dashdotdotted,teal,every mark/.append style={fill=teal}},
+    {loosely dashdotted,orange,every mark/.append style={fill=orange}},
+    {loosely dashdotdotted,violet,every mark/.append style={fill=violet}}}
+
+    \pgfplotsset{cycle list name=mcolor}
+
+\newcommand{\comments}[1]{}
 %% Document Parts
@@
 
-\include{Intro}
-
-%\include{Literature}
-
-%\include{Chapter1}
-
-%\include{Chapter2}
-
-%\include{Conclusions}
+\include{Introduction}
+\include{Background}
+\include{Overview}
+\include{OfflineDedup}
+\include{InlineDedup}
+\include{DataManagement}
+\include{Conclusion}
 
 \ssp   % bibliography can be single-spaced for UC thesis format
-\bibliography{mybibfile}
+\bibliography{Dissertation}
 \bibliographystyle{abbrv}%{unsrt}%{alpha}{siam}{apalike}{ieeetr}{plain}{acm}{abbrv}
@@
 
-\part*{\addcontentsline{toc}{part}{Appendices}Appendices}
-\appendix
-
-\include{Appendix}
+% \part*{\addcontentsline{toc}{part}{Appendices}Appendices}
+% \appendix
+% \include{Appendix}
 

### 2013-12-10 thesis/InlineDedup.tex
Thesis, first draft.

\chapter{Multi-level Selective Approach for Inline Deduplication}
\label{chap:inline}

\section{Introduction}
\label{inline:intro}
In a public virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
VM snapshots are created on user's requests. Because the snapshot captures 
the virtual disk state at a specific point of time,
virtual disk under snapshot backup operation must be protected by copy-on-write until the 
operation finishes. However, copy-on-write introduces additional disk I/O and space overheads, 
users are typically advised to reduce their disk I/O activities to the minimum before making
a snapshot backup operation, such activities typically include their web and database services. 
As a result,
it is critical to perform the backup operation in the shortest amount of time 
to make the VM back to work.

Our synchronous batched deduplication introduced in chapter~\ref{chap:offline} does not apply 
to such situation which requests fast inline deduplication.
Based on the requirement that we are now pursuing low-cost solution with short job turnaround time,
we choose to design a deduplication solution which will sacrifice the deduplication efficiency to 
satisfy the cost and time constraints.
By observations on the VM snapshot data from production cloud, we found snapshot data duplication 
can be easily classified into two categories: \emph{inner-VM} and \emph{cross-VM}. Inner-VM duplication
exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL.
As the result, different VMs tend to backup large amount of highly similar data.

With these in mind, we have developed a distributed multi-level solution to conduct 
segment-level  and block-level inner-VM  deduplication to localize the deduplication effort when possible.
It then makes cross-VM deduplication by excluding a small number of
popular popular data blocks from being backed up. Our study shows that popular data blocks
occupy significant amount of storage space while they only take
a small amount of resources to deduplicate.
Separating deduplication into multi levels effectively accomplish the major space saving goal
compare the global complete deduplication scheme, at the same time it makes
the backup of different VMs to be independent for better fault tolerance, 
which we will discuss more in chapter~\ref{chap:data}.

%Restricting the scope of global deduplication reduces
%the inter-component  data dependenc during machine failure.

%Several operations are provided for creating and managing snapshots and snapshot trees,
%such as create snapshots, revert to any snapshot, and remove snapshots.
%VM snapshots is different from traditional file system backup from a few aspects:
%\begin{enumerate}
%\item The backup loads are heavy but resources are limited. The whole VM cluster have PBs of data and need to be backuped at daily basis, if not more frequently. But at the same time snapshot tasks must not affect the normal VM operations, which means only a tiny slice of CPU and memory can be used for this purpose.
%\item No file system semantics are provided. Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided.
%\item Snapshots can be shared between users. This does not only complicates the parent-child relationship between snapshots, but also require all snapshots be managed in a global namespace.
%\end{enumerate}

%In this paper we intorduce the deduplication scheme of snapshot storage in Aliyun's VM cloud. We exploit the 
The rest of the paper is arranged as follows. 
Section~\ref{inline:options} discusses the requirements and  design options,
Section ~\ref{inline:dedup} presents our multi-level selective deduplication scheme,
Section ~\ref{inline:impl} presents our evaluation results on the effectiveness
of multi-level deduplication for snapshot backup. 
Section ~\ref{inline:related}
discusses on some background and related work.
Section ~\ref{inline:concl} concludes this chapter.

\section{Requirements and Design Options}
\label{inline:options}
We discuss the characteristics and 
main requirements for VM snapshot backup in a cloud environment.
which are different from a traditional data backup. 
% That arises mainly in Alibaba's Aliyun cloud service.
%concerns
%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
\begin{enumerate}
\item {\em Cost consciousness.}
There are tens of thousands of VMs running on a large-scale cluster. 
The amount of data is so huge such that backup cost must be controlled carefully.
On the other hand, the computing resources allocated for snapshot service is very limited
because VM performance has higher priority.  
At Aliyun, it is required that while CPU and disk usage should be small or modest during backup time,
the memory footprint of snapshot service should not exceed 500MB at each node.

%snapshot service shall not compete cpu, memory, or I/O bandwidth with VMs. Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
\item {\em Fast backup speed.}
Often a cloud has a few hours of light workload each day (e.g. midnight),  which creates an small window for automatic backup.
%But a  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with the existing cloud,
%which is not preferred for cloud production system operation. 
Thus it is desirable that backup for all nodes
can be conducted in parallel and any centralized or  cross-machine communication for
deduplication should not become a bottleneck.
%As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
%to be processed is huge. 
%For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, The aggreated amount of data 
 % the system must finish saving daily snapshots of all VMs in 2 hours. In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.

% the system must finish saving daily snapshots of all VMs in 2 hours. In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.
\item {\em Fault tolerance.}
The addition of data deduplication should not decrease the degree of
fault tolerance. It's not desirable that small scale of data failure affects the backup of many VMs.
%when users access snapshots in a recovery process. 
\end{enumerate}

There are multiple choices in designing a backup architecture  for VM snapshots.
We discuss the following design options with a consideration on their strengths and weakness.
\begin{enumerate}
\item  {\em An external and dedicated backup storage system.} 
In this architecture setting, a separate backup storage system using
the standard backup and deduplication techniques can be deployed~\cite{bottleneck08,extreme_binning09,sparseindex09}. 
This system is attached to the cloud network and every machine can periodically transfer snapshot data to 
the attached backup system. 
A key weakness of this approach is communication bottleneck between a large number of machines
in a cloud to this centralized  service.
Another weakness is that the cost of allocating separate resource for dedicated backup  can be expensive.
Since most of backup data is not used eventually, CPU and memory resource in such a backup cluster may not be fully utilized.
\item {\em A decentralized and co-hosted backup system with full deduplication.}
In this option, the backup system runs on an existing set of cluster machines.
% and a distributed storage architecture for backup allows a possible exploitation of  data locality between
%the source of data and storage location of backup data. 
The disadvantage is that 
%the backup service would compete CPU, memory, and disk resources with the other cloud services.
even such a  backup service may only use  a fraction of the existing disk storage, 
fingerprint-based search does require a significant amount of memory for fingerprint lookup of searching duplicates.
This competes memory resource  with the existing VMs.
%Decentralized deduplication is studied in ~\cite{Clements2009} and the focus is on
%block-level copy-on-write and compare-by-value techniques.

Even approximation~\cite{extreme_binning09,sparseindex09} can be used to reduce memory requirement,
one key weakness the hasn't been addressed by previous solutions is that global content sharing affects
fault isolation.
Because a content chunk is compared with a content signature collected from other users,
this artificially creates data dependency among different VM users.
% since storage for shared identical content chunks can become a failure point.
In large scale cloud, node failures happen at daily basis,
the loss of a shared block can affect many users whose snapshots share this 
data block. 
Without any control of such data sharing, we can only increase  
replication for global dataset to enhance the availability,
but this incurs significantly more cost.

%we want to isolate 
%each VM's snapshot backup as much as possible while still enjoy the benefit of deduplication.
%In large scale cloud, node faiures happen at daily basis, we don't want a problem at small scale
%to affect large amount of VMs due to data sharing.
%a key weakness of global content fingerprint comparison is that it affects fault isolation.

%2) data sharing among users for accessing popular signagutes causes the system less resilient to storage failures.
%any loss of one piece of  shared data content hash and actualcontent will damange many VM snapshots, which can cause massive impacts
%on reliability of many users.

%Another point is that the previous work in signature-based comparison does not address
%load balancing for a distributed environment during parallel access.  
%Some content signatures can be extremely hot, but the machines  that  handle such signatures can become
% a bottleneck. Uncoordinated signature assignment could lead to imbalanced access workload.
\end{enumerate}

%There are multiple choices of snapshot backup design for VM images and our considerations are described
%as follows. 
%Our design considerations
%\begin{enumerate}
%\item {\bf Centralized vs. decenalized} 
%
%It is desirable to have  a decentralized architecture.
%Given a large amount of snapshot data communicated from each machine to the backup storage,
%with a distributed storage architecture for backup, one could exploit  exploit data locality between
%the source of data and storage location of data to reduce cross-platform bandwidth requirement for backup.

%execute in parallel and easy to coordinate. In fact, we want to avoid cross-node dependency at scheduling VM snapshot operations, such that no global coordinator is necessary.
%\item {Load balancing in resource consumption}: the cost of snapshot service shall be evenly distributed onto every node. We don't have a super powerful
%or stable node that can accept extra responsibility.
%\item {minimization of inter-user data dependency for fault tolerance}: we want to minimize the data dependency to a controllable level. Data deduplication means sharing of data, thus one failure at a single point may affect the snapshot service of hundreds of VMs, which is absolutely unacceptable.
%\item {Resource usage modeling and control}.
%\end{enumerate}

With these considerations in mind, we propose a decentralized backup architecture with multi-level and selective 
deduplication. This service is hosted   in the existing set of machines and resource usage is controlled
with a minimal impact to the existing applications.
The deduplication process is first conducted among snapshots within each VM
and then is conducted across VMs.  
Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
and complicate failure management,
we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance.

\section{Multi-level Selective Deduplication Scheme}
\label{inline:dedup}
\subsection{Similarity Guided Inner-VM Deduplication}
\label{sect:innerVM}
The first-level deduplication is logically localized within each VM.
%There are several reasons that we let each MS have  its own block store for localized duplication rather than sharing. 
%First, all data written to block store are already being processed by deduplication
%process, thus no sharing is necessary unless we want to perform additional deduplication
%inside the block store. Second, 
Such localization increases data independency between different  VM backups,
simplifies  snapshot  management and statistics collection during VM migration and termination,
and facilitates parallel execution of snapshot operations.
%Finally, this reduces the complexity of concurrent snapshot operations.

%\begin{figure}[htbp]
%  \centering
%  %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
%  \epsfig{file=images/dedup_process.eps,  width=3.2in}
%  \caption{An example  of multi-level deduplication process.}
%  \label{fig:arch}
%\end{figure}

The inner VM deduplication contains two levels of duplicate detection efforts and the representation of
each snapshot is correspondingly designed as a two-level level index data structure in the form of a hierarchical
directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
An image file is divided into a set of segments and each  segment contains hundreds of content blocks from the bottom level.
These blocks are of variable-size, partitioned using
the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
%To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
Segment metadata (called segment recipe) records its  content block hashes and data pointers. 
The snapshot recipe contains a list of segments and other meta data information.
\begin{itemize}
\item {\em Level 1 Changed segment tracking}.
% If a segment is not changed, indicated by a dirty bit embedded in the virtual disk driver, its content blocks are not changed as well, thus its segment recipe can be simply reused. Operations at this level have almost no cost and most of unmodified data are filtered here. 
We start with the changed block tracking approach in a coarse grain segment level.
In our implementation with Xen on an Alibaba platform, the segment size is 2MB
and the device driver is extended to support tracking changed segments using a dirty bitmap. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment size.
It should be noted that dirty bit tracking is supported or can be easily implemented in 
major virtualization solution vendors. For example,
the VMWare hypervisor has an API to let external backup applications know 
the changed areas since last backup. 
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic and implement such changed block tracking feature.

\item {\em Level 2  Similarity guided segment comparison.}
% If a segment is modified, we perform fine-grained deduplication using content blocks of this segment to compared with 
% the same segment in
% the previous snapshot (also called parent snapshot). Partial duplication
% within the segment can be detected and eliminated. 
Since the best deduplication uses a non-uniform chunk size 
in the average of 4KB or 8KB~\cite{Jin2009},
we conduct additional local similarity guided deduplication on a snapshot by comparing
chunk fingerprints of a dirty segment 
with those in  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their content signature is the same.
This segment content signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
content similarity is an approximation~\cite{resemblance97}.  When processing a dirty segment,
its  similar segments can be found easily from the
parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
which contain chunk fingerprints to be compared.
To control the time cost of search, we set a limit on the number of  similar segments recipes to be fetched. 
For a 2MB segment, its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
by limiting at most 10 similar segments to search, the amount of memory for maintaining those similar segment recipes is small.
As part of our local duplicate search we also compare the current segment
against the parent segment at the same offset.

\end{itemize}

We choose this two-level structure because in practice we observe that during each backup period only a small amount
of VM data are added or modified. As the result, even the metadata of two snapshots can be highly similar,
thus aggregating a large number of content blocks as one segment can significantly
reduce the space cost of snapshot meta data. 
%Namely the  snapshort metadata starts with
%the representation of segment-level meta data. Each segment receipe can be further represented by
%a set of content block receipes.

How can we choose the length of a segment?
Instead of using variables-sized segments, we take a simple approach
to let every segment being aligned to the page boundary of each virtual image file.
For Aliyun, each VM image file is represented as a virtual disk file format
(called \emph{vhd} at Xen) and we use a dirty bit to capture if a page (or segment) of a virtual disk file 
has been modified or not to ease the segment-level deduplication.
%This is effective because  
%a vhd   file keeps the allocated inner blocks at the same positions until deletion,
%which means the locality of snapshot data is almost natively aligned. 
A dirty bit array is used to indicate which segments have been modified or not. 
Each page (segment) size in our implementation uses 2MB, which contains a large number of content blocks.
%Enforcing a boundary at every 2MB will 
%only break 0.2\% of total data blocks which is tiny.
% dirty bits array. This is because
%Inside the TapDisk driver, we maintain an array of \emph{dirty bits} to record the dirty area
%of runtime VM image file since the last snapshot, each bit represent a 2MB fix-sized
%data segment. During a snapshot operation, we only need to look at the dirty region
%rather than scan over the whold image file, which would be extremely slow.

%We let each virtual disk has its own block store rather than sharing for several reasons:
%first, all data written to block store are already being processed by deduplication
%process, thus no sharing is necessary unless we want to perform additional deduplication
%inside the block store. Second, such seperation will facilitate VM data stastics, 
%deletion and migration. Finally, this reduces the complexity of concurrent snapshot operations.

Once level-2 deduplication is activated for those segments that have been modified,
it requires memory to load  block fingerprints from the corresponding
parent snapshot's segment.
This scheme processes one segment at time and each segment of 2MB contains about 
500 content blocks on average given 4KB is the average block size.
That only takes a tiny amount of space to hold their fingerprints.
%Given  1-2 hours of window to backup snapshots and every VM has  on average about 40GB, there is enough
%time to search all segments sequentially~\cite{NOT-CLEAR-HERE}

\subsection{Popularity guided Cross-VM Deduplication with PDS}
\label{sect:crossVM}

The level-3 deduplication is to identify duplicated data blocks among multiple VMs through the index cache
of popular data set (PDS).  PDS is the most popular content blocks 
among snapshots across all VMs. 
Each index entry contains  the block fingerprint and a reference pointer to the location of its real content
in the snapshot content block store.
%The structure of PDS meta is not different from the segment recipe we discussed above, 
%except that it is partitioned into many small slices so that each node is easy to load its own slice.

At the runtime, the PDS index resides in a distributed  memory lookup table  
implemented using Memcached~\cite{memcached} to leverage the aggregated memory in a cluster.
The usage of memory at each machine is small and thus  this scheme  does not
lead to  a memory resource contention with the existing cloud services.
PDS raw data stored  in the distributed file system
has multiple copies in different machines for the purpose of fault tolerance and 
while providing high read throughput.

To control the size of searchable popular data in this global setting, we focus on those items that 
are most popular based on the historical snapshot data and the popular analysis is conducted periodically to ensure 
meta data freshness to match the latest data access trend.
There are two advantages to exploit this.
First, a smaller PDS reduces overall resource requirement while covering most of data duplication.
Second, knowing this small set of data is shared heavily makes the fault tolerance management 
easier because we can replicate more copies to mitigate the failure.

\begin{figure}[htbp]
\centering
\includegraphics[width=5in]{images/vector.pdf}
\caption{Number of duplicates vesus ranking}
\label{fig:zipf-data}
\end{figure}

In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus one or more data disks.
During VM's creation, its OS disk is directly copied from user's chosen base image.
Given the separation of OS disks and data disks, we study  their characteristics separately.
We expect that data related to OS and popular software installations are not frequently
modified or deleted, to facilitate analysis we call them \emph{OS-related} data, 
and the rest of data, either from OS or data disks, are called \emph{user-related} data.
%base image data as a hint.Through users may change configurations, install software, or write user data into OS disk,
%Thus most of content blocks for the OS related snapshots  shall keep unchanged.
%This is verified in  Section~\ref{sect:exper}.

We have studied the popularity of popular blocks in the OS and data disks from a dataset
containing over 1,000 VMs, taking their first snapshots to watch the cross-VM duplication pattern 
(scale of OS disk sampling is smaller due to performance impact to user VMs).
Figure \ref{fig:zipf-data} shows the duplicate count for unique data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number 1 is the block with the highest number of duplicates.
These two curves exhibit that the popularity of popular blocks partially follows a Zipf-like distribution.
%$Y$ axis is the popularity of an OS block in a log scale 
%measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
%sorted by their duplicate rank.  
%For the top ranked blocks, there is a flat line in terms of duplicate counts. That
%is because there are a large number of OS blocks which have appeared in all copies of such OS releases.

%\epsfig{file=images/log-log.disk.eps, width=3in}

%\begin{tabular}{cc}
%\epsfig{file=images/datadisk.count_rank.eps, width=1.5in} &
%\epsfig{file=images/35vmos.count-rank.eps,width=1.5in}
%\end{tabular}

%\begin{figure}
%\centering
%\epsfig{file=images/35vmos.count-rank.eps,width=3in}
%\caption{ Duplicate count of  popular OS blocks in a log scale.}
%\label{fig:OSpopular}
%\end{figure}

Base on the Zipf-like distribution pattern, many previous analysis and results on web caching\cite{Adamic2002,Breslau1999b} may apply.
In general this indicates a small set of popular data dominates data duplication.
Although we already know OS-related data are heavily duplicated among OS disks, 
it still surprises us that user-related data follow a similar pattern.
Therefore, we collect the PDS by performing global reference counting through map-reduce for all
blocks in snapshot store, and select the most popular ones base on the memory limitation of
PDS hash index.

The PDS collected from user-related data is generally proportional to the data size.
As discussed in Section~\ref{inline:impl}, selecting about 1\% of data (after level 1 and level 2 deduplication)
can cover about 38\% of data blocks. Consider we allow maximum 25 VMs per machine, each VM has
about 30GB of user-related data, having 10 snapshots in its snapshot store and the data change ratio during
each backup is 10\%, this translates to 15GB PDS data per machine. 
Consider each PDS hash index entry cost about 40 bytes and the average block size is 4KB, this leads to
a 1:100 ratio so the 
memory cost by PDS hash index is about 150MB per machine.
On the other hand, the PDS from OS-related data is only relevant to the number of OS releases.
Our experiment on 7 major OS releases shows that about 100GB of data is never modified, and we expect
it won't grow over 200GB in the near future. So it would cost the entire cluster 2GB of memory to
store its hash index, or 20MB per machine on a 100 node cluster. On average each OS disk has about 10GB
of data that can be completely eliminated in this way.
Thus in total the PDS index size per node takes less than 170MB in a large cluster bigger than 100 nodes, 
covering over 47\% of blocks in OS and data disks after inner-VM deduplication.
This memory usage is well below the limit required by our VM services.

\subsection{Illustration of multi-level deduplication process}

%%Our deduplication process is divided into three levels, at each level, we eliminate the most of duplicate data with available knowledge, preventing them from going further because deduplication at deeper level is more expensive.
%
\begin{figure}
  \centering
  \includegraphics[width=5in]{images/dedup_flow2.pdf}
  \caption{Illustration of snapshot deduplication dataflow.}
  \label{fig:dedupflow}
\end{figure}

We illustrate the steps of 3-level deduplication in Figure~\ref{fig:dedupflow}, which can be summarized as 5 steps:
\begin{enumerate}
\item {\em Segment level checkup.}
As shown in Figure~\ref{fig:dedupflow} (a),
when  a snapshot of a plain virtual disk file is being created, we first check the dirty bitmap 
to see which segments are modified. If a segment is not modified since last snapshot, 
it's data pointer in the recipe of the  parent snapshot  can be directly copied into 
current snapshot recipe (shown as the shadow area in Figure~\ref{fig:dedupflow} (b)).

\item {\em Block level checkup.}
As shown in Figure~\ref{fig:dedupflow} (b),
for each dirty segment, we divide it into variable-sized blocks,
and compare their signatures with  the similar segment recipes in the previous snapshot (called parent
snapshot). 
For any duplicated block, we copy the data pointer directly from the parent segment recipe. 
\item {\em PDS checkup.} For the remaining  content blocks whose duplicate status is unknown,
Figure~\ref{fig:dedupflow} (d)
shows  a further check to compare  them with  the cached signatures in the PDS by querying
the PDS hash index. If there is a match, the corresponding data pointer from the PDS index is
copied into the segment recipe. 
\item {\em Write new snapshot blocks :}
If a data block cannot be found in the PDS index, this block is considered to be a new block
and such a block is to be saved in the snapshot store, the returned data pointer is
saved in the  segment recipe.
\item {\em Save recipes.} Finally the  segment recipes are saved in the  snapshot block store also.
 After all segment recipes are saved, the snapshot recipe is complete and can be saved.
\end{enumerate}

If there is no parent snapshot available, which happens when a VM creates its first snapshot, 
only PDS-based checkup will be conducted. 
Most of the cross-VM duplication, such as OS-related data, is eliminated
at this stage.

\section{System Implementation and Experimental Evaluations}
\label{inline:impl}
We have implemented the snapshot deduplication scheme on the Aliyun's cloud platform.
Objectives of our experimental evaluation are:
1) Analyze the popularality of content data blocks and the popularity  of hot items. 
2) Assess the effectiveness  of 3-level deduplication for reducing the storage cost of snapshot 
backup. 
3) Examine the impacts of PDS size on deduplication ratio.

\subsection{Experimental setup}

At Aliyun our target is to backup cluster up to 1000 nodes
with 25 VMs on each.
%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
Based on the data studied,  each VM has about  40GB of storage  data usage on average,
OS disk and data disk each takes about 50\% of storage space.
The backup of VM snapshots is completed within two hours every day,
and that translates to a backup throughput of 139GB per second, or 500TB per hour.
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.

% the system must finish saving daily snapshots of all VMs in 2 hours. In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 500TB/hour.

%In our snapshot deduplication architecture, PDS is the key to achieve greater deduplication than
%incremental backup solutions. Our basic assumption of PDS us that VM disks, especially OS disks,
%have huge amount of data in popular, and such popular data can be represented by a relatively smaller data set
%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
%the effectiveness of PDS using real user VM disks from our production VM cluster.

Since it's impossible to perform large scale analysis without affecting the VM performance,
we sampled two data sets from real user VMs to measure the effectiveness of our deduplication scheme.
Dataset1 is used study the detail impact of 3-level deduplication process,
it compose of 35 VMs from 7 popular OSes: 
Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
The overall data size for this 700 full snapshots is 17.6 TB.

Dataset2 contains the first snapshots of 1323 VMs' data disks from a small cluster with 100 nodes. 
Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
study the PDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.

All data are divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks ~\cite{similar94,rabin81} with an average size of 4KB.
The signature for variable-sized blocks is computed using their SHA-1 hash. 
Popularity of data blocks are collected through global counting 
and the top 1\% will fall into PDS, as discussed in Section~\ref{sect:crossVM}.

%To compare the effectiveness with a full deduplication approach with an approximation,
%we use  extreme binning and perfect deduplication~\cite{extreme_binning09}. 
%For perfect deduplication and extreme binning, each snapshot is also divided into chunk blocks
%using TTTD with an average size of 4KB. The original extreme binning work uses the whole file
%as the input unit and  this size is too big in our system. 
%Thus we split each image snapshot file into variable-sized segments base on the block hash list, 
%using TTTD with average size of 2MB.

\subsection{Effectiveness of Multi-level Deduplication}

\begin{figure}
  \centering
  \includegraphics[width=5in]{images/overall_effect.pdf}
  \caption{Impacts of 3-level deduplication. The height of each bar is the data size after 
deduplication divided by the original data size and the unit is percentage. }
  \label{fig:overall}
\end{figure}

Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication on dataset1.
The X axis shows the overall impact in (a),  impact on OS disks in (b), and impact on data disks in (c).
Each bar in the Y axis shows the data size after deduplication divided by the original data size.
Level-1 elimination can reduce the data size to about 23\% of original data, namely it delivers close 77\% reduction.
Level-2 elimination is applied to data that could pass level-1, it
reduces the size further to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
Level-3 elimination together with level 1 and 2
reduces the size further to 8\% of original size, namely it delivers additional 10.5\% reduction.
Level 2 elimination is more visible in OS disk than data disk, because data change frequency is really small
when we sample last 10 snapshots of each user in 10 days. Nevertheless, the overall impact of level 2 is still significant.
A 4.5\% of reduction from the original data represents about 450TB space saving for a 1000-node cluster.

\begin{figure}
  \centering
 %\epsfig{file=images/os_cds_sim.eps, width=3in}
  \includegraphics[width=5in]{images/3level_os.pdf}
  \caption{Impact of 3-level deduplication for OS releases.}
  \label{fig:oscds}
\end{figure}

%To see the impact of multi-level deduplication on different OS releases,
%Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
Figure~\ref{fig:oscds} shows the impact of different levels of deduplication for different OS releases.
In this experiment, we tag each block in 350 OS disk snapshots from dataset1 as  ``new''
if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot store;
``PDS''  if this block can be found  in PDS;
``Parent segment'' if  this block is marked unchanged in parent's segment recipe.
``Parent block'' if  this block is marked unchanged in parent's block recipe.
With this tagging, we compute the percentage of deduplication accomplished by each level.
As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination,
this is because the time interval between two snapshots in our dataset
is quite short and the Aliyun cloud service makes a snapshot  everyday  for each VM.
On the other hand,  PDS still finds lots of duplicates that inner VM deduplication can't find,
contributing about 10\% of reduction on average.

It is noticeable that level-1 deduplication doesn't work well for CentOS, a significant percentage of data is not
eliminated until they reach level-3. It shows that even user upgrade his VM system heavily and frequently
such that data locality is totally lost, those OS-related data can still be identified at level-3.

In general we see a stable data reduction ratio for all OS varieties, ranging from 92\% to 97\%, that means
the storage cost of 10 full snapshots combined is still smaller than the original disk size. And compare to 
today's widely used copy-on-write snapshot technique, which is similar to our level-1 deduplication, our
solution cut the snapshot storage cost by 64\%.

%Combining OS disks in all the VMs, we see the overall 7.4TB of data is reduced to 512GB. 
%The extreme binning approach can reduce this data set to 542GB, which is slightly worse. As a reference, 
%perfect deduplication achieves 364GB in this experiment.

%Overall speaking, inner   VM deduplication or  PDS-based deduplication
%can work well alone, but by combining them together we get a fairly good and stable deduplication ratio to 
%all kind of OSes. 
%Compared to a traditional dirty bit approach based on pages of
%each file (e.g. segment in our scheme),
%our PDS-based level 3 approach  can save additional 50\% storage space because many of level 2 block
%content can be eliminated using the PDS also.

\subsection{Coverage of popular data blocks}

%We study characteristics of popular data blocks among snapshots of VM users
%and examine the impacts if we only store a relative small amount of popular data blocks to be sored in the PDS server.
%There are two advantages to exploit this.
%First, a smaller PDS reduces overall resource requirement while covering  most of data blocks in snapshots.
%Second a smaller PDS makes the fault tolerance management  easier because we can replicate  more copies
%to mitigate the failure.

%We consider each virtual disk contains two parts: OS partition and regular user data partition
%and study their characteristics seperately.
%In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus  one or more data disks.
%During VM's creation, its OS disk is directly copied from user's choosen base image.
%Since  they dare brought by the operating system and popular 
%software installations,  they are rarely modified or deleted.
%base image data as a hint.
%Through users may change configurations, install software, or write user data into OS disk,
%but most of the OS related data shall keep unchanged.

%Previous study has also supported this\cite{vmimage}. Therefore, we can let all OS disks share these
%popular data in their snapshot backups.
%We choose user's data disks rather than OS disks in thie experiment for several reasons: First, the data in OS disks are 
%instinctively highly similar, because most of the VM users only make some popular or unique but tiny changes to their OSes,
%so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
%Second, the data disks are way more important in terms of data safty and backup because they are 
%what users really care about.

%Furthermore, our study on user's data disks has shown that the duplication pattern of
%variable-sized data blocks follows \emph{Zipf-like} distribution. As a result, the major portion of 
%deduplication effect will emerge from eliminating the duplication of frequently seen data.
%define PDS

\begin{figure}
\centering
\includegraphics[width=5in]{images/ay41a_big_data_disk_cdf.pdf}
\caption{Cumulative  coverage of popular popular user data blocks.}
\label{fig:userdatacoverage}
\end{figure}

One of our biggest advantage is small memory footprint for deduplication, because we only
eliminate a small amount of highly popular data.
we use dataset2 to demonstrate the coverage of popular data blocks on user-related data, 
as shown in Figure \ref{fig:userdatacoverage}.
%content blocks used in image files using 90\% of
%the collected dataset.
%Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular popular user data blocks. 
The $X$ axis is the rank of popular user data blocks, and $Y$ shows how much raw data can be covered given
the size of PDS.
Let $S_i$ and $F_I$ be the size and duplicate count 
of the $i$-th block ranked by its duplicate rank.  Then $Y$ axis is the coverage of
the popular dataset covering data items from rank 1 to rank $i$. Namely  
\[
\frac{ \sum_{i=1}^{i} S_i * F_i} {\mbox{Total data size}}.
\]

Thus with about 1\% of blocks on data disks, PDS can cover about 38\% of total data blocks
appeared in all data snapshots. The corresponding PDS index uses no more than 150MB memory per machine,
which can be easily co-located with other cloud services.

%Figure~\ref{fig:OSdatacoverage} shows the cumulative coverage  ratio of  popular popular OS blocks. 
%From both graphs, a small number of most popular popular blocks can coverage a large percentage of 
%snapshot blocks and thus the size of PDS can be chosen to be small while still having a large
%coverage.

%\begin{figure}
%\centering
%\epsfig{file=images/ay41a_small.os_incremental.cdf.eps, width=3in}
%\caption{ Cumulative  coverage of popular popular OS disk blocks.}
%\label{fig:OSdatacoverage}
%\end{figure}

%We define \emph{OS PDS} to be the unchanged data across the base VM image and the snapshots of all
%OS disks which are derived from it. Such data are brought by the operating system and popular 
%software installations, they are rarely modified or deleted, and can be easily extracted using 
%base image data as a hint.

Because there are a limited number of OS releases, we study popular blocks among
OS disks loaded with  the same OS release. 
%The selection of PDS is completed by separating OS disk and data disk.
%While block popularality among data disks may be affected in some degree
% when we scale up the number of total VMs  to be supported,
%we expect that  the block popularality among OS disks still remains to be high and  
%%can be well covered by a fixed PDS because users still adopt popular OS releases.
%we choose 7 major OSes in Aliyun's
%VM cloud platform and they are: 
%Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
%distributions are 64 bits).
%we examine 5 VM user disks from each OS, and 10 snapshots for each VM. These VMs have been actively used by their
%owners. Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
%their OS disks. 
%For example, some Ubuntu OS disks have only 2GB of data while some have 50GB.
%For each OS, the base image and all OS
%disk snapshots are divided into variable-sized blocks. Then 
In  Figure~\ref{fig:OSunchanged},  we list a conservative  popularality study in 7 major OS versions  supported
in Aliyun.
%We consider the earlier snapshot for each OS disk as the base image.
For every block in the base image, we classify this block as ``unchanged''
if this block has appeared in all snapshots of the same OS release even they are used by different VMs.
Figure \ref{fig:OSunchanged} shows that for each
OS,  at least 70\% of OS blocks are completely unchanged among all snapshots of the same OS. 
Some latest release  of OS tends to have a higher percentage of content change
while  old release tends to have more variations of content versions.
That can be interpreted as that users with very old  version of operating systems
have a lower tendency to update their OS versions and this causes a larger discrepancy
among OS snapshots of these users.

%into the unchanged category of OS data.

\begin{figure}
\centering
\includegraphics[width=5in]{images/os_subset.pdf}
\caption{Percentage of completely popular blocks among different VMs for the same OS release.}
\label{fig:OSunchanged}
\end{figure}

Based on the above analysis, we have selected a small set of most popular
OS blocks, which is about 100GB OS data and its corresponding PDS index takes about 1GB memory space in total.
They can cover sufficiently over 70\% of OS-related data.

%Then we use this PDS to run the deduplication process again.
%That correspond to about  80GB of OS blocks and its corresponding PDS meta occupies 800MB in the cache.
%  data from 350 OS disk snapshots,

%The above analysis is only an estimation of OS and software related popular data, 
%some user installed software may not be discovered by this method because they are not 
%included in the base image. However, as we can see in the next section, 
%the overall duplication of user generated data
%follows the Zipf-like distribution, thus all popular data can be discovered by statistic analysis.

%Zipf's law has been shown to characterize use of words in a natural language, city populations, 
%popularity of website visits and other internet traffic data.

%Here we present the first fully consistent empirical study showing that data duplication
%pattern in very large scale storage follows Zipf-like distribution. More specifically,
%we show that the duplication count of any unique data block is inversely proportional to its rank
%in the frequency table, with $\alpha$ smaller than unity. 
%As far as we know, this is the first study of large scale real user data to disclose
%the Zipf-like distribution pattern in data storage area.

%\subsubsection{The model}
%Consider a general storage system that holds user's files without any deduplication. 
%Let $N$ be the total number of unique data blocks after 
%content-defined chunking and deduplication, 
%$C_N(i)$ be the number of duplicate copies that the $i$th data block being
%stored in storage, given all the unique data blocks be ranked in order of their number of duplicate copies.
%Let $S_i$ be the size of $i$th block,
%then the actual ranking of the $i$th block is reflected by $\sum_{1}^{i-1}S_i$.

%\subsubsection{Methodology}
%1323 users' virtual data disks were scanned using TTTD content-defined chunking, and we performed global perfect deduplication 
%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
%and maximum block size, all variable-sized blocks are compared by their SHA-1 hash arther than real data.
%
%We choose user's data disks rather than OS disks in thie experiment for several reasons: First, the data in OS disks are 
%instinctively highly similar, because most of the VM users only make some popular or unique but tiny changes to their OSes,
%so the data duplication pattern in OS disks cannot reflect the real distribution of general user data.
%Second, the data disks are way more important in terms of data safty and backup because they are 
%what users really care about.

%In our snapshot deduplication architecture, PDS is the key to achieve greater deduplication than
%incremental backup solutions. Our basic assumption of PDS us that VM disks, especially OS disks,
%have huge amount of data in popular, and such popular data can be represented by a relatively smaller data set
%because of their high appearence frequency. As a result, the major portion of snapshot deduplication effect shall 
%emerge from eliminating the duplication of such a small data set. In this section, we evaluate
%the effectiveness of PDS using real user VM disks from our production VM cluster.

\subsection{A comparison of perfect and PDS-based deduplication }
%Figure~\ref{fig:pd} shows the compression ratio of perfect deduplication at different dataset sizes
%as we vary the data size from about 4 terabytes to about 23.5 terabytes.
After level-1 and level 2 elimination, we find that 
the complete deduplication would reduce the storage cost further by 50\%. 
If we put all these unique data into PDS, 
we could achieve complete deduplication,
but fingerprint lookup in such huge PDS hash index would become a bottleneck as discussed in many pervious works. 
So we use dataset2 to evaluate how much space saving of 
deduplication can be achieved when varying the PDS size.
%\begin{figure}
%  \centering
%  \epsfig{file=images/dedup_ratio.eps, height=2in, width=2.66in}
%  \caption{Perfect deduplication on data disks}
%  \label{fig:pd}
%\end{figure}

%We rank unique data blocks by their duplication count, and choose the hottest blocks as PDS. 
Figure \ref{fig:datacdssize} shows the relationship between PDS cache size and relative space saving ratio
compared to the full deduplication.  The unit of PDS size is gigabytes.
We define \emph{space saving ratio} as the space saving of PDS method divided by 
full deduplication space reduction. 
With a 100GB PDS data (namely 1GB PDS index) can still  accomplish about 75\% 
of what perfect deduplication can do.
%But this effect decreases when more data are added to PDS. 
%The lower bound of PDS space saving ratio is 50\%, which is very easy to accomplish.

\begin{figure}
  \centering
  \includegraphics[width=5in]{images/uniquedata-saving1.pdf}
  \caption{Relative ratio of space size compared to full deduplication when PDS size changes.}
  \label{fig:datacdssize}
\end{figure}

%PDS size is restricted by system memory resource.
With dataset2, Figure \ref{fig:datacds} shows how PDS space saving ratio
compared to the full deduplication is affected by the dataset size. 
%The calculation is done after level 1 and level 2 deduplication.
In this experiment we first set out a goal of space saving ratio completed, 
then watch how much data needs to be placed in PDS cache to achieve this goal.
From the graph we can see a 75\% saving ratio lead to a stable ratio between 
PDS size and data size, which requires 1\% of data to be placed in PDS.

When we deal with a large cluster of 1,000 nodes, we expect that using
1\% of data disks can cover more than what we have seen from this
1323 VM dataset, assuming that the average behavior of every subcluster with 100 machines
exhibits a similar popularality. 
In addition to this, PDS for OS disks will become even more effective when
there are more VMs sharing the same collection of OS releases. 
%Base on above data we can estimate the size of data PDS and its effect. 
%Currently we prepared 500MB memory per machine to store PDS meta, then it can represent 50GB of data. 
%If we assume each VM has 30GB of user data at runtime, and we host 25 VMs per machine, 
% maintain 10 snapshots per VM, each brings 10\% additional modified data. 
%Thus the user data in snapshot system is 1.5TB per machine. So the upper bound of 
%$PDS size/ Data size = 0.033$, which is sufficient for the 75\% saving goal.

\begin{figure}
  \centering
  \includegraphics[width=5in]{images/cds_scale_07.pdf}
  \caption{The relative size ratio of  PDS over the data size. }
  \label{fig:datacds}
\end{figure}

\section{Related Work}
\label{inline:related}
In a VM cloud, several operations are provided for creating and managing snapshots and snapshot trees,
such as creating snapshots, reverting to any snapshot, and removing snapshots.
For VM snapshot backup, file-level semantics are normally not provided. 
Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided.
%Snapshots may be shared among VMs when a user runs the same binary image on different  VMs.
% This feature complicates the snapshot management, 
%but also require all snapshots be managed in a global namespace.

%While snapshot backup loads are heavy but computing and storage  resources available 
%can be limited to reduce the overall operation cost of a cloud. The whole VM cluster have petabytes of data and need to 
%be backed up at daily basis, if not more frequently. But at the same time snapshot tasks must not affect the normal VM operations
%in a cloud service, which means only a tiny slice of CPU and memory can be used for this purpose.

VM snapshots can be  backed up  incrementally by identifying file  blocks that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
%Even though the snapshots are saved incrementally,
%when deleting a snapshot, only the data not needed for any other snapshot is removed.
%So regardless of which prior snapshots have been deleted, all active snapshots will contain
%all the information needed to restore the virtual disk.
%One widely used snapshot strategy is copy-on-write (CoW).
%The earlier use of COW is to improve memory usage and reduce copying overhead in process 
%management~\cite{OSbook,Waldspurger2002} and it can be extended for snapshot 
%storage management~\cite{vmware_kb1015180}. 
%C. Waldspurger. Memory Resource Management in VMware ESX Server in Proceedings of the 5th Symposium 
%on Operating Systems Design and Implementation, 2002
%Upon VM image storage system receives a save snapshot request,
%it freezes the state of that image file, then all consequent write request will result in the write region being copied
%to an incremental snapshot data file. 
%Such a strategy exploits version difference between consecutive snapshots
%of the same image.
The main weakness
is that it does not reveal content redundancy among data blocks from different snapshots or
different VMs.
%has several disadvantages:
%first, CoW may affect the general I/O performance due to defered data coping. 
%Second, CoW does not seperate backup data and runtime image data,
%which have distinct access requirements: runtime image data is directly used by the running VM, 
%thus need high throughput, and is very sensitive to latency,
%such data must be served with hig cost hardware, but backup data generally only need fair aggregate throughput, 
%is not sensitive to latency, thus can be stored in secondary storage devices.
%Finally, VM snapshots contain tremendous amount of data duplication, which is nearly impossible to tackle 
%if these two kinds of data are tightly coupled together.

Data deduplication techniques can eliminate redundancy globally among different files from different users. 
Backup systems have been developed to use content hash (finger prints) to identify duplicate 
content~\cite{venti02,Rhea2008}.
%,NGmiddleware2011}. 
Today's commercial data backup systems (e.g. from EMC and NetApp)
%\cite{emc_avamar}\cite{datadomain_whitepaper} 
use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
%Chunking divides a data stream into variable length chunks, it has been used to conserve bandwidth\cite{lbfs01}, 
%search and index documents in large repositories\cite{bhag07}, scalable storage systems\cite{hydrastor09}, 
%store and transfer large directory trees efficiently and with high reliability\cite{jumbo07}.
As data grows to be big, fingerprint lookup in such schemes
becomes too slow to be scalable.
%and searching such disk
%However, unless some form of locality or similarity is exploited, inline, chunk-based deduplication, 
%when done at a large scale faces what has been termed the disk bottleneck problem: to facilitate fast chunk ID lookup, 
%a single index containing the chunk IDs of all the backed up chunks must be maintained. 
%As the backed up data grows, the index overflows the amount of RAM available and must be paged to disk. 
%Without locality, the index cannot be cached effectively, and it is popular for nearly 
%every index access to require a random disk access. This disk bottleneck severely limits deduplication throughput.
Several techniques have been proposed to speedup searching of duplicate 
content. For example,  
Zhu et al.~\cite{bottleneck08} tackle it 
by using an in-memory Bloom filter and prefetch groups of chunk IDs that are likely to be 
accessed together with high probability. It takes significant memory resource for filtering and caching.
NG et al.~\cite{ NGmiddleware2011}  use  
a related filtering technique for integrating deduplication in Linux  file system and the memory
consumed is up to 2GB for a single machine. That is still too big in our context discussed below. 
%Lillibridge et al.~\cite{sparseindex09} break list of chunks 
%into large segments, the chunk IDs in each incoming segment are sampled and the segment is 
%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments. 
%These are segments that share many chunk IDs with the incoming segment with high probability.
%Deepavali et al.~\cite{extreme_binning09}  use signature-based file similarity  and group similar files
%into the same physical location (bins) to deduplicate against each other.

Duplicate  search approximation~\cite{extreme_binning09,sparseindex09,Xia2011}  has been proposed 
%in extreme bining and other sparse indexing 
to package similar content in one location, and duplicate lookup  only searches
for chunks within files which have a similar file-level or segment-level  content fingerprints.
That leads  to a smaller amount of memory usage for storing meta data in signature
lookup with a tradeoff of the reduced recall ratio.

\section{Concluding Remarks}
\label{inline:concl}
In this chapter we propose a multi-level selective deduplication scheme for 
snapshot service in VM cloud. 
Similarity based inner-VM deduplication localizes backup data dependency and exposes more parallelism  
while popularity based cross-VM deduplication with a small popular data set
effectively  covers a large amount of duplicated data.
Our solution accomplishes the majority of
potential global deduplication saving while still meets stringent cloud resources requirement. 
Evaluation using real user's VM data shows
our solution can accomplish 75\% of what complete global
deduplication can do. 
Compare to today's widely-used snapshot technique, our scheme reduces almost
two-third of snapshot storage cost.
Finally, our scheme uses a very small amount of memory on each node, and leaves
room for additional optimization we are further studying.
In future we may conduct more field study on large VM clusters to better study the 
VM data duplication patterns.

### 2013-12-10 thesis/Introduction.tex
Thesis, first draft.

\chapter{Introduction}
\label{chap:intro}
\section{Problem Statement and Motivation}
\label{intro:prob}
The  ubiquity  of the cloud computing  has  resulted  in  the 
widespread availability of cloud based services and applications accessible through 
the network. Examples include online storage services, big data analysis, and various websites.
In such a cluster-based cloud environment,
each physical machine runs a number of virtual machines as  instances of a guest operating system 
to contain different kind of user applications,
and their data are stored in virtual hard disks which are represented 
as virtual disk image files in the host operating system.
Frequent snapshot backup of virtual disk images is critical to increase  the service reliability
and protect data safty.
For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.

The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand. 
If such VM snapshot data are plainly backuped without any duplicate detection, the storage waste would be 
extreme. For example, a fresh Windows server 2008 installation costs 25 GB on the virtual  disk,
and they are almost certianly duplicated with other Windows VM instances.
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
can effectively identify and remove content duplicates among snapshots, 
but such a solution can be expensive. There is also a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

Unlike the previous work dealing with general file-level
backup and deduplication, our problem is focused on virtual
disk image backup. Although we treat each virtual disk as a
file logically, its size is very large. On the other hand, we need
to support parallel backup of a large number of virtual disks
in a cloud every day. One key requirement we face at busy clouds
 is that VM snapshot backup should only use a minimal
amount of system resources so that most of resources is kept
for regular cloud system services or applications. Thus our
objective is to exploit the characteristics of VM snapshot data
and pursue a cost-effective deduplication solution. Another
goal is to decentralize VM snapshot backup and localize
deduplication as much as possible, which brings the benefits
for increased parallelism and fault isolation.

Despite its importance, storage deduplication remains a challenging task for cloud storage providers. 
And this is especially true for resource constrained large scale public VM cloud. 
In recognizing this importance and
the associated challenges,  my thesis is that

\textit{It  is  possible  to  build  an efficient, scalable, and fault tolerant backup storage
supporting highly accurate deduplication and easy management of deduplicated data
with sustainable high throughput.}

In  other  words,  the  main  goal  of this  study  is  to  answer  the  following 
question.  Given a large scale VM cluster running tens of thousand of VMs, 
how can such a snapshot backup service identify whether a piece of data in VM disk
really needs to backup? And how to manage backup data under complex sharing relationship?
This dissertation investigates 
techniques  in  building  a snapshot storage architecture that provides 
low-cost deduplication support for large VM clouds.  In particular,  it 
contains the following contributions to establish my thesis:

\begin{itemize}
\item A design of low-cost multi-stage parallel deduplication solution for automically batched deduplication.
\item An inline multi-level deduplication scheme with similarity guided local detection and popularity guided global detection.
\item The development and analysis of a VM-centric storage approach which considers fault isolation and integrates multiple duplicate detection strategies.
\item Fast and efficient garbage collection with approximate snapshot deletion and leak repair.
\end{itemize}

In general, this  dissertation  study  is  built  upon  a  large  body  of previous  research 
in storage deduplication and distributed storage systems.  The goal 
of this work is to provide low-cost deduplication support and storage management for 
large scale resource-constrained VM cloud. This solution should be collocated with existing
cloud infrastructure services and require no dedicated hardware support. It also needs to
accomplish good deduplication efficiency and does comprise the data reliability due to the
inherent volatility of commodity hardware.
Under the  above consideration, our system is designed to support multiple levels of deduplication
depending on backup requirements. The objective is to provide satisfactory deduplication efficiency
and high throughput with the emphasis on low resource usage and fault tolerancy.

\section{Dissertation Organization}
\label{intro:organ}
The rest of this dissertation is organized as follows.  
Chapter~\ref{chap:back} gives an introduction to the history and background of thesis problems.
Chapter~\ref{chap:overview} presents the overall VM snapshot storage architecture.
Chapter~\ref{chap:offline}  describes a synchronous and parallel deduplication scheme for offline batched complete deduplication.
Chapter~\ref{chap:inline} studies a multi-level selective deduplication solution for inline deduplication.
Chapter~\ref{chap:data}  describes a VM-centric storage management with approximate deletion.
Chapter~\ref{chap:concl}  concludes this  dissertation  and  briefly discusses some potential future work.

### 2013-12-10 thesis/OfflineDedup.tex
Thesis, first draft.

--- 2013-05-14 hotstorage13/arch.tex
@@
-\section{System Design}
-\label{sect:arch}
+\chapter{Synchronous and Parallel Approach for Offline Deduplication}
+\label{chap:offline}
+\section{Introduction}
+\label{offline:intro}
+This chapter introduces a low-cost architecture option and considers that
+a backup service uses the existing cloud computing resource.
+%Since most of backup data is not used in practice, system resource in such a service is not fully utilized. 
+Performing deduplication adds significant  memory cost for comparison of content fingerprints. 
+Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently. 
+Cloud providers often wish that the backup service only consumes  small or modest resources 
+%with a minimal impact to the existing cloud services.  Another challenge for backup with deduplication is 
+with a minimal impact to the existing cloud services.  Another challenge is 
+%that deletion of old snapshots compete for computing resource as well. That is because data dependence created 
+that deletion of old snapshots compete for computing resource as well, because data dependence created 
+by duplicate relationship among snapshots  adds processing complexity.
 
-%\begin{figure}[htbp]
-%  \centering
-  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
-%  \epsfig{file=images/arch.eps, width=3.9in}
-%  \caption{Snapshot backup architecture of each node.}
-%  \label{fig:arch}
-%\end{figure}
+The traditional approach to deduplication is an inline approach which follows
+a sequence of block reading, duplicate detection,  and non-duplicate  block write to the 
+backup storage. In this chapter we introduce an synchronous and parallel approach
+for offline batched deduplication. This solution is suitable for cloud which typically conduct
+automatic backup of all the VMs during system's spare time.
+Our key idea  is to  first perform parallel duplicate detection for VM content blocks 
+among all machines before performing actual data backup. Each machine
+accumulates detection requests and  then performs detection   partition by partition 
+with minimal resource usage.
+Fingerprint based partitioning allows highly parallel duplicate detection  and also simplifies 
+reference counting management.  
+% as the entire process can also be divided into a
+%parition-wise  deletion.
 
+While our synchronous offline solution accomplishes perfect deduplication efficiency while maintaining
+low resource usage,
+the tradeoff of this approach is that the job turnaround time for each individual
+VM backup task becomes longer. In addition,
+every machine has to read dirty segments twice
+and that some deduplication requests are delayed for staged parallel processing.
+However, with our careful parallelism and buffer management,
+this multi-stage detection scheme can provide a sufficient throughput for VM backup.
+
+The rest of this chapter is organized as follows.
+Section~\ref{offline:design} describes our synchronous processing steps.
+Section~\ref{offline:eval} is our experimental evaluation that compares with other approaches.
+Section~\ref{offline:related} reviews the related works.
+Section~\ref{offline:concl} concludes this chapter.
+
+\section{Multi-stage Synchronous Deduplication Design}
+\label{offline:design}
 We consider deduplication in two levels. The first level
@@
 %our scheme uses a single-thread procedure on each machine to minimize the use of CPU, network bandwidth, and disk bandwidth.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{snapshotdata.pdf}
-\caption{ Metadata structure of a VM snapshot.}
-\label{fig:snapshot}
-\end{figure}
-%\subsection{Snapshot Representation}
-
-The representation of each snapshot in the backup storage
-has a two-level index structure in the form of a hierarchical
-directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
-A VM image is divided into a set of segments and each  segment contains 
-content blocks of variable-size, partitioned using
-the standard chunking technique with 4KB as the average block size. 
-%the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
-%To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
+We use the two level metadata hierachy as discussed in section~\ref{overview:meta}.
 The snapshot metadata  contains a list of segments and other meta data information.
@@
 
-\begin{figure*}[tbhp]
+\begin{sidewaysfigure*}[tbhp]
 \centering
-
-\includegraphics[width=0.95\textwidth]{steps.pdf}
+\includegraphics[height=0.45\textwidth]{images/steps.pdf}
 \caption{Processing flow of Stage  1 (dirty segment scan and request accumulation), Stage 2 
@@
 \label{fig:flow}
-\end{figure*}
+\end{sidewaysfigure*}
 
@@
 its deletion log is too big.
-%Due to the paper constraint, we will not discuss the deletion operations in details.
 
-%The above method requires the counter information to be consistently maintained in the global index.
-%Finally the deleteion summary.
-it will adjust the corresponding reference counts.
-At the end of bucket worker's operation, it outputs the unused blocks information to each VM data repository's deletion log.
+\section{System Implementation and Experimental Evaluations}
+\label{offline:eval}
+We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a cluster
+of dual quad-core Intel Nehalem 2.4GHz E5530 machines with 24GB memory.  
+Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
+Objectives of our evaluation are:
+1) Analyze the deduplication throughput and effectiveness for a large number of VMs.
+%Compare with the data domain approach~\cite{bottleneck08}.
+2) Examine the impacts of buffering during metadata exchange.
 
-%This compaction will make a copy of all the data in use, and remove the obsoleted blocks.
-However, after such a compaction, many block offsets will be changed, as a result, such changes are sent to the bucket job queue so that changes will be reflected upon the next bucket update.
+%\subsection{Experimental setup}
 
-%Since we maintain a single copy of each block information in the bucket index, and there is at most one bucket worker operating the bucket index at one time, it it safe to do the simple referencec ounting rather than mark-and-sweep.
+%We are running our deduplication/backup  service on 100 nodes.
+%Memory usage is about 150MB space per node during backup and
+%the CPU usage is very small during the experiments. 
+We have performed a trace-driven study using  a 1323 VM dataset  collected from 
+%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
+a cloud cluster at Alibaba's Aliyun.
+% ~\cite{WeiZhangIEEE}.
+% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
+For each VM, the system keeps 10 automatically-backed snapshots in the storage while
+a user may instruct extra snapshots to be saved.
+The backup of VM snapshots is completed within a few  hours every night.
+Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
+including OS and user data disk.
+Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
+variable-sized content blocks  with an average size of 4KB.
+%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
+The signature for variable-sized blocks is computed using their SHA-1 hash.
+
+The seek cost of each random IO request in our test machines is about  10 milliseconds.
+The average I/O usage of local storage is controlled about 50MB/second for backup 
+in the presence of other I/O jobs. Noted that a typical 1U server can host
+6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
+of local storage bandwidth. 
+The final snapshots are stored in a distributed file system built on the same 
+cluster.
+
+The total local disk usage on each machine is about 8GB for the duplicate detection purpose,
+mainly for global index. 
+Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
+block-wise full deduplication removes about additional 74.5\% of duplicates.
+The final content copied to the backup storage is reduced by 94.4\% in total.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.6\textwidth]{figures/mem_time.pdf}
+\caption{Parallel processing time when memory limit varies.}
+\label{fig:memory}
+\end{figure}
+
+Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
+ a 100-node cluster a  when 
+limit $M$ imposed on each node varies.
+%  from 20MB to 200MB.
+This figure also depicts the time breakdown for Stages 1, 2, and 3. 
+%The parallel time includes the first scanning time, 
+%of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
+%fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
+The time in Stages 1 and 3  is  dominated by  the two scans of dirty segments,
+and final data copying to the backup storage is overlapped with VM scanning.
+During dirty segment reading, the average number of consecutive dirty segments is 2.92. 
+%Each scan takes about 1.4 hours.
+The overall processing time does not have a significant reduction as $M$ increases to 190MB.
+The aggregated deduplication throughput is  about 8.76GB per second,
+which is the size of 2500 VM images divided by the parallel time. 
+The system runs with  a single thread and  its CPU resource usage is 10-13\% of one core. 
+The result shows the backup with multi-stage deduplication  for all VM images can be 
+completed in about 3.1 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
+As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
+scales up linearly since the number of VMs is  $25p$.
+
+Table~\ref{tab:overall} shows performance change when limit $M$=35MB is imposed and
+the number of partitions per machine ($q$) varies.
+% varies from 100 to 1000.
+Row 2 is memory space required to load a partition of global index and detection requests.
+When $q=100$, the required memory is 83.6 MB and this exceeds the limit $M=$35MB.  
+Row 3 is the parallel time and Row 4 is  the aggregated throughput of  100 nodes.
+%The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
+%with the very small resource usage.
+Row 5 is  the parallel time for using Option 1 with $p\times q$ send buffers 
+described in Section~\ref{offline:design}. 
+When $q$ increases, the available space per buffer reduces and there is a big increase of seek cost.  
+The main network usage before performing the final data write is for request accumulation and
+summary output. It lasts about 20 minutes and each machine exchanges 
+about   8MB of metadata per second with others during that period, which is 6.25\% of the network bandwidth.
+
+\begin{table}[hbt]
+\caption{ Performance when $M$=35MB and $q$ varies.}
+\begin{center}
+\begin{tabular} {|c|c|c|c|c|c|}
+\hline \#Partitions ($q$)  & 100 & 250  & 500 &  750 &  1000 \\
+\hline Index+request (MB) & 83.6 &  33.5 & 16.8 & 11.2 & 8.45 \\
+\hline Total Time (Hours) & N/A&  3.12 & 3.15 & 3.22 & 3.29 \\
+\hline Throughput (GB/s) & N/A &  8.76 & 8.67 & 8.48 & 8.30 \\
+\hline Total time (Option 1) & N/A&  7.8& 11.7 & 14.8 & 26 \\
+\hline
+\end{tabular}
+\end{center}
+\label{tab:overall}
+\end{table}
+
+\section{Related Work}
+\label{offline:related}
+%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
+At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
+represented as virtual disk image files in the host operating system.
+For VM snapshot backup, file-level semantics are normally not provided.
+Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. 
+%Only raw access information at disk block level are provided. 
+%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
+%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
+%only a very small slice of cluster resource can be used for the backup purpose.
+
+%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
+Backup systems have been developed to use content fingerprints to identify duplicate
+content~\cite{venti02,Rhea2008}.
+Offline deduplication is 
+used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
+%,NGmiddleware2011}.
+%Today's commercial data backup systems (e.g. from EMC and NetApp)
+%\cite{emc_avamar}\cite{datadomain_whitepaper}
+%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
+Several techniques have been proposed to speedup searching of duplicate
+fingerprints. For example, the data domain method ~\cite{bottleneck08} 
+uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
+accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
+As discussed in Section~\ref{offline:intro},
+there is no dedicated resource for deduplication in our targeted setting and low memory usage
+ is required so that the resource impact to other cloud services is minimized.
+%NG et al.~\cite{ NGmiddleware2011}  use
+%a related filtering technique for integrating deduplication in Linux  file system and the memory
+%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
+%Lillibridge et al.~\cite{sparseindex09} break list of chunks
+%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
+%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
+%These are segments that share many chunk IDs with the incoming segment with high probability.
+The approximation techniques are studied in~\cite{extreme_binning09,Guo2011}  
+%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
+to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
+%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
+%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
+%lookup  
+In comparison, this paper focuses on  full deduplication without approximation.
+%We also take advantages of the fact that in a VM cloud environment,
+%the virtual device driver can easily keep track if  large data
+%segments have been modified using dirty bits and such information can avoid sending
+%unmodified data segments for deduplication, which significantly saves cost.
+
+Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}. 
+All of the above approaches have focused on
+such inline duplicate detection in which  deduplication of an individual block  is on the critical write path.
+In our work, this constraint is relaxed and 
+there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
+in our context, finishing the backup of required VM images within a reasonable time window is more
+important than optimizing individual VM block  backup requests.
+
+\section{Concluding Remarks}
+\label{offline:concl}
+The contribution  of this work is a low-cost multi-stage parallel deduplication solution.
+Because of separation  of duplicate detection and actual backup,
+we are able to evenly distribute  fingerprint comparison among clustered machine
+nodes, and only load one partition at time at each machine for in-memory comparison.
+%The tradeoff is that every machine has to read dirty segments twice 
+%and that some deduplication requests are delayed for staged processing.
+
+The proposed  scheme is resource-friendly to the existing cloud services.
+The evaluation shows that the overall 
+deduplication time and throughput of 100 machines  are satisfactory with 
+about 8.76GB per second for 2500 VMs. During processing, each machine uses 
+35MB memory, 8GB disk space, and 10-13\% of one CPU core with a single thread  execution.
+Our future work is to conduct more experiments with production workloads.
+%and a modest use of IO and network resource.
+%Thus the proposed  scheme does not take a significant  amount of the resource away
+%to compete with the existing cloud services.
+%While using an insignificant system resource,
+%When the cluster size changes, our experiment also shows a linear speedup of overall throughputs
+%because highly parallel fingerprint comparisons.  
+%The cluster  of 100 nodes and 2500 VMs can deliver about 
+%8.8GB per second deduplication performance.  We expect the system performs well in a larger cloud 
+%setting and
+
+The major limitation of our synchronous approach is that all VM snapshots must be processed together
+in order to achieve maximum aggregated throughput, as a result, small VMs need to wait big VMs during
+the duplicate detection phase until all VMs finishes stage 2. Since the small VM disks 
+need to be put under copy-on-write protection longer, their disk I/O performance will be slow down
+and  additional disk space are needed to store the modified segments during backup. Another limitation
+is that VM user cannot choose the time of taking snapshot freely. Therefore, our synchronous approach 
+is ideal for private cloud in which the IT admin needs to backup all the VMs together, but it may not
+be suitable 
+for public cloud which demands real-time snapshot backup operation. We will discuss our solution
+for on demand inline deduplication in the next chapter.

### 2013-12-10 thesis/Overview.tex
Thesis, first draft.

--- 2012-05-06 vm_snapshot_sim/2012arch.tex
@@
-\section{Multi-level Selective Deduplication}
-\label{sect:arch}
+\chapter{System Overview}
+\label{chap:overview}
+At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
+represented as virtual disk image files in the host operating system.
+For VM snapshot backup, file-level semantics are normally not provided.
+Snapshot operations take place at the virtual device driver level, which
+means no fine-grained file system metadata can be used to determine the changed data. 
+Backup systems have been developed to use content fingerprints to identify duplicate
+content~\cite{venti02,Rhea2008}.  
+As discussed earlier, collocating a backup service on the existing
+cloud cluster avoids the extra cost to acquire a dedicated backup facility
+and reduces the network bandwidth consumption in transferring the
+raw data for backup. 
+Figure~\ref{fig:collocated} illustrates the cluster architecture where
+each physical machine runs a backup service and a distributed file system (DFS)~\cite{googlefs03,hdfs10} 
+serves a backup store  for the snapshots.
 
-\subsection{Snapshot Service Architecture}
-%\subsection{Aliyun's VM Cloud and 
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=5in]{images/colocated-arch}
+    \caption{Collocated VM Backup System.}
+    \label{fig:collocated}
+\end{figure}
+
+\section{Snapshot Service Overview}
+\label{overview:ss}
+We will briefly introduce the abstraction of our storage architecture here 
+and discuss the implementation details in chapter~\ref{chap:data}.
 Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China 
@@
 The cross-VM deduplication is conducted by the broker to access 
-a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
+a popular data set (PDS) (will discuss in Section~\ref{sect:crossVM},
 whose block hash index is stored in a distributed memory cache.
@@
   %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
-  \epsfig{file=images/arch.eps, width=3.9in}
-  \caption{Snapshot backup architecture of each node.}
+  \includegraphics[width=5in]{images/arch1.pdf}
+  \caption{Snapshot backup architecture abstraction}
   \label{fig:arch}
@@
 The snapshot store 
-supports data access operations such as \emph{get}, \emph{put} and \emph{delete}.
+supports data access operations such as \emph{Get}, \emph{Append} and \emph{Delete}.
 Other operations include data block traverse and resource usage report.
@@
 
-\subsection{Inner-VM Deduplication}
-\label{sect:innerVM}
+\section{Two Level Hierarchical Design of VM Metadata}
+\label{overview:meta}
 
-The first-level deduplication is logically localized within each VM.
-%There are several reasons that we let each MS have  its own block store for localized duplication rather than sharing. 
-%First, all data written to block store are already being processed by deduplication
-%process, thus no sharing is necessary unless we want to perform additional deduplication
-%inside the block store. Second, 
-Such localization increases data independency between different  VM backups,
-simplifies  snapshot  management and statistics collection during VM migration and termination,
-and facilitates parallel execution of snapshot operations.
-%Finally, this reduces the complexity of concurrent snapshot operations.
-
-%\begin{figure}[htbp]
-%  \centering
-%  %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
-%  \epsfig{file=images/dedup_process.eps,  width=3.2in}
-%  \caption{An example  of multi-level deduplication process.}
-%  \label{fig:arch}
-%\end{figure}
 \begin{figure}[htbp]
@@
   %\epsfig{file=images/dedup_process.eps, height=2in, width=2.66in}
-  \epsfig{file=images/snapshot_representation.eps,  width=3.7in}
+  \includegraphics[width=5in]{images/snapshot_representation.pdf}
   \caption{An example of snapshot representation.}
@@
 
-The inner VM deduplication contains two levels of duplicate detection efforts and the representation of
-each snapshot is correspondingly designed as a two-level level index data structure in the form of a hierarchical
-directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
-An image file is divided into a set of segments and each  segment contains hundreds of content blocks from the bottom level.
-These blocks are of variable-size, partitioned using
-the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
-%To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
-Segment metadata (called segment recipe) records its  content block hashes and data pointers. 
-The snapshot recipe contains a list of segments and other meta data information.
-\begin{itemize}
-\item {\em Level 1 Segment modification  detection}.
-If a segment is not changed, indicated by a dirty bit embedded in the virtual disk driver, its content blocks are not changed as well, thus its segment recipe can be simply reused.
-Operations at this level have almost no cost and most of unmodified data are filtered here.
-
-\item {\em Level 2  Block fingerprint comparison.}
-If a segment is modified, we perform fine-grained deduplication using content blocks of this segment to compared with 
-the same segment in
-the previous snapshot (also called parent snapshot). Partial duplication
-within the segment can be detected and eliminated. 
-\end{itemize}
-
-\begin{figure*}[htbp]
-\centering
-\epsfig{file=images/vector.eps, width=7in}
-\caption{Number of duplicates vesus ranking}
-\label{fig:zipf-data}
-\end{figure*}
-
-We choose this two-level structure because in practice we observe that during each backup period only a small amount
-of VM data are added or modified. As the result, even the meat data of two snapshots can be highly similar,
-thus aggregating a large number of content blocks as one segment can significantly
-reduce the space cost of snapshot meta data. 
-%Namely the  snapshort metadata starts with
-%the representation of segment-level meta data. Each segment receipe can be further represented by
-%a set of content block receipes.
-
-How can we choose the length of a segment?
-Instead of using variables-sized segments, we take a simple approach
-to let every segment being aligned to the page boundary of each virtual image file.
-For Aliyun, each VM image file is represented as a virtual disk file format
-(called \emph{vhd} at Xen) and we use a dirty bit to capture if a page (or segment) of a virtual disk file 
-has been modified or not to ease the segment-level deduplication.
-%This is effective because  
-%a vhd   file keeps the allocated inner blocks at the same positions until deletion,
-%which means the locality of snapshot data is almost natively aligned. 
-A dirty bit array is used to indicate which segments have been modified or not. 
-Each page (segment) size in our implementation uses 2MB, which contains a large number of content blocks.
-%Enforcing a boundary at every 2MB will 
-%only break 0.2\% of total data blocks which is tiny.
-% dirty bits array. This is because
-%Inside the TapDisk driver, we maintain an array of \emph{dirty bits} to record the dirty area
-%of runtime VM image file since the last snapshot, each bit represent a 2MB fix-sized
-%data segment. During a snapshot operation, we only need to look at the dirty region
-%rather than scan over the whold image file, which would be extremely slow.
-
-%We let each virtual disk has its own block store rather than sharing for several reasons:
-%first, all data written to block store are already being processed by deduplication
-%process, thus no sharing is necessary unless we want to perform additional deduplication
-%inside the block store. Second, such seperation will facilitate VM data stastics, 
-%deletion and migration. Finally, this reduces the complexity of concurrent snapshot operations.
-
-Once level-2 deduplication is activated for those segments that have been modified,
-it requires memory to load  block fingerprints from the corresponding
-parent snapshot's segment.
-This scheme processes one segment at time and each segment of 2MB contains about 
-500 content blocks on average given 4KB is the average block size.
-That only takes a tiny amount of space to hold their fingerprints.
-%Given  1-2 hours of window to backup snapshots and every VM has  on average about 40GB, there is enough
-%time to search all segments sequentially~\cite{NOT-CLEAR-HERE}
-
-\subsection{Cross-VM Deduplication with CDS}
-\label{sect:crossVM}
-
-The level-3 deduplication is to identify duplicated data blocks among multiple VMs through the index cache
-of common data set (CDS).  CDS is the most popular content blocks 
-among snapshots across all VMs. 
-Each index entry contains  the block fingerprint and a reference pointer to the location of its real content
-in the snapshot content block store.
-%The structure of CDS meta is not different from the segment recipe we discussed above, 
-%except that it is partitioned into many small slices so that each node is easy to load its own slice.
-
-At the runtime, the CDS index resides in a distributed  memory lookup table  
-implemented using Memcached~\cite{memcached} to leverage the aggregated memory in a cluster.
-The usage of memory at each machine is small and thus  this scheme  does not
-lead to  a memory resource contention with the existing cloud services.
-%For example, in our current implementation setting at Aliyun, we use up to  150MB memory per node during night backup
-%including CDS and other metadata for all levels of deduplication. Most of memory resource (48GB per node 
-%in our experiment) is used for existing  applications.
-CDS raw data stored  in the distributed file system
-has multiple copies in different machines for the purpose of fault tolerance and 
-while providing high read throughput.  
-%The data of CDS is stored in a special block store in the distribued file system.
-
-% which doesn't belong to any VM disk.
-
-%CDS meta assignment is done statically, each slice of CDS meta has one primary and two backup nodes.
-%During the system bootup, snapshot storage controller will read the assignment, 
-%load its primary portion of CDS meta from distributed file system. Loading the backup portion
-%of CDS is due upon a query arrives for it. Everyday the CDS assignment and CDS data will be checked
-% for updates and reloaded if necessary.
-
-%Behind the scene there is a offline map-reduce job, which will periodically scan the block stores
-%in the entire cluster and perform a ``word counting''. High frequency blocks are then added to the CDS if its count 
-% is greater than threshold, which is pre-defined by the system memory restrictions.
-To control the size of searchable common data in this global setting, we focus on those items that 
-are most popular based on the historical snapshot data and the popular analysis is conducted periodically to ensure 
-meta data freshness to match the latest data access trend.
-There are two advantages to exploit this.
-First, a smaller CDS reduces overall resource requirement while covering most of data duplication.
-Second, knowing this small set of data is shared heavily makes the fault tolerance management 
-easier because we can replicate more copies to mitigate the failure.
-
-In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus one or more data disks.
-During VM's creation, its OS disk is directly copied from user's chosen base image.
-Given the separation of OS disks and data disks, we study  their characteristics separately.
-We expect that data related to OS and popular software installations are not frequently
-modified or deleted, to facilitate analysis we call them \emph{OS-related} data, 
-and the rest of data, either from OS or data disks, are called \emph{user-related} data.
-%base image data as a hint.Through users may change configurations, install software, or write user data into OS disk,
-%Thus most of content blocks for the OS related snapshots  shall keep unchanged.
-%This is verified in  Section~\ref{sect:exper}.
-
-We have studied the popularity of common blocks in the OS and data disks from a dataset
-containing over 1,000 VMs, taking their first snapshots to watch the cross-VM duplication pattern 
-(scale of OS disk sampling is smaller due to performance impact to user VMs).
-Figure \ref{fig:zipf-data} shows the duplicate count for unique data blocks sorted by their ranking in 
-terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
-measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
-sorted by their duplicate rank.  The rank number 1 is the block with the highest number of duplicates.
-These two curves exhibit that the popularity of common blocks partially follows a Zipf-like distribution.
-%$Y$ axis is the popularity of an OS block in a log scale 
-%measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
-%sorted by their duplicate rank.  
-%For the top ranked blocks, there is a flat line in terms of duplicate counts. That
-%is because there are a large number of OS blocks which have appeared in all copies of such OS releases.
-
-%\epsfig{file=images/log-log.disk.eps, width=3in}
-
-%\begin{tabular}{cc}
-%\epsfig{file=images/datadisk.count_rank.eps, width=1.5in} &
-%\epsfig{file=images/35vmos.count-rank.eps,width=1.5in}
-%\end{tabular}
-
-%\begin{figure}
-%\centering
-%\epsfig{file=images/35vmos.count-rank.eps,width=3in}
-%\caption{ Duplicate count of  common OS blocks in a log scale.}
-%\label{fig:OSpopular}
-%\end{figure}
-
-Base on the Zipf-like distribution pattern, many previous analysis and results on web caching may apply.
-In general this indicates a small set of popular data dominates data duplication.
-Although we already know OS-related data are heavily duplicated among OS disks, 
-it still surprises us that user-related data follow a similar pattern.
-Therefore, we collect the CDS by performing global reference counting through map-reduce for all
-blocks in snapshot store, and select the most popular ones base on the memory limitation of
-CDS hash index.
-
-The CDS collected from user-related data is generally proportional to the data size.
-As discussed in Section~\ref{sect:exper}, selecting about 1\% of data (after level 1 and level 2 deduplication)
-can cover about 38\% of data blocks. Consider we allow maximum 25 VMs per machine, each VM has
-about 30GB of user-related data, having 10 snapshots in its snapshot store and the data change ratio during
-each backup is 10\%, this translates to 15GB CDS data per machine. 
-Consider each CDS hash index entry cost about 40 bytes and the average block size is 4KB, this leads to
-a 1:100 ratio so the 
-memory cost by CDS hash index is about 150MB per machine.
-On the other hand, the CDS from OS-related data is only relevant to the number of OS releases.
-Our experiment on 7 major OS releases shows that about 100GB of data is never modified, and we expect
-it won't grow over 200GB in the near future. So it would cost the entire cluster 2GB of memory to
-store its hash index, or 20MB per machine on a 100 node cluster. On average each OS disk has about 10GB
-of data that can be completely eliminated in this way.
-\comments{
-As the number of VMs increases, the popularity of common blocks for data disks changes.
-But this increase has a small impact on OS block popularity because 
-there are a limited number of OS releases used by VMs. We let CDS cover the common OS blocks first and
-our CDS selection strategy is designed as follows.
-
-\begin{itemize}
-\item First, most popular items from OS disks are selected as the initial CDS.
-Our experiment data shows that about 
-100GB data from 7 most popular OS releases
-can at least cover over 70\% of OS snapshots and the index of these 100GB OS blocks
-only takes about total 1GB in the CDS index and then memory requirement per node 
-for duplicate search a large cluster is tiny.
-We expect that the OS CDS index may grow up to 2GB in order to cover large varieties  of commonly deployed
-OS releases in practice.
-\item Second, the degree of duplication is computed for the rest of blocks in snapshot store, and
-% and also snapshot 
-%blocks of user data items stored in the OS disk (some users store data in their OS disks).
-the  most popular items are selected. As discussed in Section~\ref{sect:exper}, 
-that about 1\% of data blocks are selected based on their duplicate counts and these popular blocks
-can cover about 38\% of data  blocks appeared in various snapshots after level 1 and level deduplication.  
-The memory size per node used for CDS is within 150MB.
-\end{itemize}}
-Thus in total the CDS index size per node takes less than 170MB in a large cluster bigger than 100 nodes, 
-covering over 47\% of blocks in OS and data disks after inner-VM deduplication.
-This memory usage is well below the limit required by our VM services.
-
-\subsection{Illustration  of multi-level deduplication process}
-
-\comments{
-\begin{figure*}
-  \centering
-  %\epsfig{file=images/dedup_flow1.eps, height=2in, width=3.5in}
-  \epsfig{file=images/dedup_flow1.eps,  width=6in}
-  \caption{Flow of deduplication.}
-  \label{fig:tapdisk}
-\end{figure*}
-
-The 3-level deduplication process can be summarized as four steps:
-\begin{list}{Dedup}{}
-\item {Dirty bits: Copy the unchanged portion of snapshot recipe from parent snapshot, base on dirty bits.}
-\item {Locality: Divide dirty segments into blocks, compare to the corresponding segment recipe at the same position of parent snapshot, if duplicate, copy the data reference into segment recipe.}
-\item {CDS: Check if this data exist in the CDS, if yes, copy the returned data reference. Otherwise, write data block to block store, save the returned reference into segment recipe.}
-\item {Save meta: write down the segment recipes and snapshot recipe when finish.}
-\end{list}
-
-}
-
-%%Our deduplication process is divided into three levels, at each level, we eliminate the most of duplicate data with available knowledge, preventing them from going further because deduplication at deeper level is more expensive.
-%
-\begin{figure}
-  \centering
-  \epsfig{file=images/dedup_flow1.eps, width=3.8in}
-  \caption{Illustration of snapshot deduplication dataflow.}
-  \label{fig:dedupflow}
-\end{figure}
-
-We illustrate the steps of 3-level deduplication in Figure~\ref{fig:dedupflow}, which can be summarized as 5 steps:
-\begin{enumerate}
-\item {\em Segment level checkup.}
-As shown in Figure~\ref{fig:dedupflow} (a),
-when  a snapshot of a plain virtual disk file is being created, we first check the dirty bitmap 
-to see which segments are modified. If a segment is not modified since last snapshot, 
-it's data pointer in the recipe of the  parent snapshot  can be directly copied into 
-current snapshot recipe (shown as the shadow area in Figure~\ref{fig:dedupflow} (b)).
-
-\item {\em Block level checkup.}
-As shown in Figure~\ref{fig:dedupflow} (b),
-for each dirty segment, we divide it into variable-sized blocks,
-and compare their signatures with  the corresponding segment recipe in the previous snapshot (called parent
-snapshot). 
-For any duplicated block, we copy the data pointer directly from the parent segment recipe. 
-\item {\em CDS checkup.} For the remaining  content blocks whose duplicate status is unknown,
-Figure~\ref{fig:dedupflow} (d)
-shows  a further check to compare  them with  the cached signatures in the CDS by querying
-the CDS hash index. If there is a match, the corresponding data pointer from the CDS index is
-copied into the segment recipe. 
-\item {\em Write new snapshot blocks :}
-If a data block cannot be found in the CDS index, this block is considered to be a new block
-and such a block is to be saved in the snapshot store, the returned data pointer is
-saved in the  segment recipe.
-\item {\em Save recipes.} Finally the  segment recipes are saved in the  snapshot block store also.
- After all segment recipes are saved, the snapshot recipe is complete and can be saved.
-\end{enumerate}
-
-If there is no parent snapshot available, which happens when a VM creates its first snapshot, 
-only CDS-based checkup will be conducted. 
-Most of the cross-VM duplication, such as OS-related data, is eliminated
-at this stage. 
-%Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.
-%This is important because most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
-%at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.
+The representation of each snapshot in the backup
+storage has a two-level index structure in the form of a
+hierarchical directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
+A VM image is divided into a set of segments and each
+segment contains content blocks of variable-size, partitioned using the standard chunking technique with 4KB
+as the average block size. The snapshot metadata contains a list of segments and other meta data information.
+Segment metadata contains its content block fingerprints
+and reference pointers. If a segment is not changed from
+one snapshot to another, indicated by a dirty bit embedded in the virtual disk driver, its segment metadata contains a reference pointer to an earlier segment. For a
+dirty segment, if one of its blocks is duplicate to another
+block in the system, the block metadata contains a reference pointer to the earlier block.

### 2013-12-10 thesis/Vitae.tex
Thesis, first draft.

\begin{vitae}
\addcontentsline{toc}{chapter}{Curriculum Vit\ae}
{\small

\begin{vitaesection}{Education}
\vspace{-0.1cm}
   \item [2002 -- 2005] Master of Science in Computer Science, Tsinghua University, Beijing, China.

   \item [1997 -- 2001] Bachelor of Science in Electrical Engineering, Wuhan University, Wuhan, China.

\end{vitaesection}

% \begin{vitaesection}{Experience}
% \vspace{-0.1cm}
%    \item [1999 -- 2000] Graduate Research Assistant, University of California,
%     Santa Barbara.

% \end{vitaesection}

%{\bf Selected Publications}
\begin{vitaesection}{Publications}
%\vspace{-0.5cm}
\item Michael Daniel Agun, Wei Zhang, Tao Yang, ``Optimized Synchronous Data Deduplication for Virtual Machine Backup in Cloud Storage''. {\it To be submitted for publication}.

\item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang. ``Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud''. {\it Submitted to the 12th USENIX Conference on File and Storage Technologies (FAST '14)}.

\item Wei Zhang, Tao Yang, Gautham Narayanasamy, Hong Tang. ``Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage''. {\it In Proceedings of the 5th USENIX Workshop on Hot Topics in File and Storage Technologies (HotStorage'13)}, July 2013.

\item Wei Zhang, Hong Tang, Hao Jiang, Tao Yang, Xiaogang Li, Yue Zeng. ``Multi-level Selective Deduplication for VM Snapshots in Cloud Storage''. {\it In Proceedings of the 5th IEEE International Conference on Cloud Computing (CLOUD'12)}, June 2012.

\item Wen Ye, Wei Zhang, Rich Wolski. ``Simulation-Based Augmented Reality for Sensor Network Development''. {\it In Proceedings of the 5th ACM Conference on Embedded Networked Sensor Systems (SenSys'07)}, November 2007.

\item Wei Zhang, Haoxiang Lin. ``A Versatile Cryptographic File System for Linux''. {\it In Journal of Micro Computer Systems, China}, 2006.

\item Wei Zhang, Fuchun Sun. ``An Improved FCM Algorithm Based On Search Space Smoothing''. {\it In Proceedings of the 1st IASTED International Conference on Computational Intelligence (CI'05)}, July 2005.

   % \item Me Myself, S. Mart, and A. Nother Advisor:
   % ``Cool Paper Title,'' In
   % {\it Proc.\ IEEE Intl.\ Conference Cool Papers 
   %      (ICCP)}, August 2000.
\vspace{0.3cm}

\end{vitaesection}

}

\end{vitae}

### 2013-12-10 batchdedup/scheduling.tex

--- 2013-11-08 batchdedup/scheduling.tex
@@
 
+\todo{START OF DUAL BIN PACKING BASED ALGORITHM}
 From our requirements a model that closely fits our goals is the dual version
@@
 
-\subsection{Standard Bin Packing Heuristic}
-\todo{this section might need to be moved around and/or broken up. also, notation might still need to be adjusted. }
+\todo{END OF DUAL BIN PACKING BASED ALGORITHM}
+
+The problem of scheduling VM backup tasks to specific rounds is a variant of
+bin packing, with some additional constraints. We want to efficiently schedule
+VMs to rounds, minimizing average VM backup time (and thereby minimizing CoW),
+while also taking into account resource usage and total jobspan (which are
+minimized in the single round schedule). We solve the problem with a 2-part
+algorithm. First, we have a round packing heuristic which takes a number of
+rounds and a set of VMs, and returns a schedule for the backup process. Second,
+we have a higher level algorithm that determines the optimal number of rounds,
+given the constraints.
+
+Our round packing heuristic uses a descending sorted order worst fit packing, 
+Scheduling VMs machine by machine, and is described in Fig~\ref{fig-bpl}.
+For our higher-level scheduling algorithm, we minimize Resource usage and average
+backup time, while ensuring that the jobspan constaint is met (if possible). The
+overall scheduling algorithm is described in Fig~\ref{fig-scheduler}, where T is
+the alotted time for backup. our cost function is defined as
+$cost(s) = \alpha\times Resource~Usage(s) + (1-\alpha)\times Avg~Backup~Time(s)$.
+
+%\todo{this section might need to be moved around and/or broken up. also, notation might still need to be adjusted. }
 \begin{figure}
 \begin{lstlisting}[frame=single]
-bpl:
 for each Machine m

### 2013-12-10 batchdedup/eval.tex
added metrics section.

@@
 \end{figure}
-\begin{figure}[ht]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={Network Buffer Size},
-		xlabel={Rounds},
-		ylabel={Average Turnaround Time (min)},
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		%legend pos=north west
-		]
-                \addplot table[x=rounds,y expr=(\thisrow{turnaround})/60] {figures/sim_full.txt};
-                %\legend{Total Backup Time};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{simulated results for average vm turnaround time for individual VMs in 100 node cluster.}
-  \label{fig:mpibuf-mem}
-\end{figure}
+
+%TODO: make this figure
+%\begin{figure}[ht]
+%  \centering
+%	\begin{tikzpicture}
+%		\begin{axis}[
+%		%title={Network Buffer Size},
+%		xlabel={Rounds},
+%		ylabel={Backup Cost},
+%		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+%		%legend pos=north west
+%		]
+%                \addplot table[x=rounds,y=DBP2Cost] {figures/cost.txt};
+%                %\legend{Total Backup Time};
+%		\end{axis}
+%	\end{tikzpicture}
+%  \caption{simulated results for backup cost based on real 120 node cluster.}
+%  \label{fig:mpibuf-mem}
+%\end{figure}
 
@@
 		xlabel={Rounds},
-		ylabel={Total Jobspan (s)},
+		ylabel={Total Jobspan (m)},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		]
-                \addplot table[x=Rounds,y=DBP2jobspan] {figures/packing_comparison.txt};
-                \addplot table[x=Rounds,y=BPLjobspan] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{DBP2jobspan})/60] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{BPLjobspan})/60] {figures/packing_comparison.txt};
                 \legend{DBP2, BPL};

### 2013-12-10 batchdedup/eval.tex
added backup cost

--- 2013-11-25 batchdedup/eval.tex
@@
 
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Network Buffer Size},
+		xlabel={Rounds},
+		ylabel={Backup Cost},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+                legend pos=north west
+		]
+                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}*0.5+\thisrow{DBP2jobspan}*0.5)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}*0.7+\thisrow{DBP2jobspan}*0.3)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}*0.9+\thisrow{DBP2jobspan}*0.1)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}*0.5+\thisrow{BPLjobspan}*0.5)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}*0.7+\thisrow{BPLjobspan}*0.3)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}*0.9+\thisrow{BPLjobspan}*0.1)] {figures/packing_comparison.txt};
+                \legend{DBP2 $\alpha=.5$, DBP2 $\alpha=.7$, DBP2 $\alpha=.9$, BPL $\alpha=.5$, BPL $\alpha=.7$, BPL $\alpha=.9$};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Backup Cost for DBP2 and BPL}
+  \label{fig:jobspan-comparison}
+\end{figure}
+
 %\begin{figure}[ht]

### 2013-12-10 batchdedup/eval.tex

--- 2013-12-10 batchdedup/eval.tex
@@
 
+\begin{figure}[ht]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		%title={Network Buffer Size},
+		xlabel={Rounds},
+		ylabel={Backup Cost},
+		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
+                legend pos=north west
+		]
+                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}*0.5+\thisrow{DBP2jobspan}*0.5)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}*0.7+\thisrow{DBP2jobspan}*0.3)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}*0.9+\thisrow{DBP2jobspan}*0.1)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}*0.5+\thisrow{BPLjobspan}*0.5)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}*0.7+\thisrow{BPLjobspan}*0.3)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}*0.9+\thisrow{BPLjobspan}*0.1)] {figures/packing_comparison.txt};
+                \legend{DBP2 $\alpha=.5$, DBP2 $\alpha=.7$, DBP2 $\alpha=.9$, BPL $\alpha=.5$, BPL $\alpha=.7$, BPL $\alpha=.9$};
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Backup Cost for DBP2 and BPL. TODO:reformat this graph}
+  \label{fig:cost-comparison}
+\end{figure}
+
 %\begin{figure}[ht]

### 2013-12-10 batchdedup/scheduling.tex
added a representative histogram for one of the clusters

@@
 The second problem is that a single round backup brings the highest cost of CoW
-because of the workload in stage 1a is imbalanced,
+because of the workload in stage 1a is imbalanced (see Fig.~\ref{fig:hist-1}),
 causing machines with small VMs to wait while CoW protection is turned on.
-Thus we must minimize the duration that a given VM is undergoing CoW protection.
+Thus we must minimize the duration that a given VM is undergoing CoW protection.r
+
+To determine how evenly distributed VM sizes are, we obtained statistical data
+for 22 Aliyun clusters. The clusters in our dataset all have a very long tail distribution,
+Though local minima exist in the histogram and the range of VM sizes varies. Other production clusters
+may have different distributions, but our findings justify our architecture for a multi-round algorithm.
+A representative histogram for one of the clusters is shown in Fig.~\ref{fig:hist-1}.
+
+\begin{figure}[ht]
+  \centering
+  \begin{tikzpicture}
+      \begin{axis}[
+              ybar interval,
+      ]
+          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
+      \end{axis}
+  \end{tikzpicture}
+  \caption{Histogram of average data sizes for a real cluster. TODO:reformat graph, I just wanted to get the data into the paper}
+  \label{fig:hist-1}
+\end{figure}
 

### 2013-12-12 batchdedup/main.tex
revise round scheduling

@@
 %\title{Selective Deduplication for VM Snapshots in Cloud Storage}
-\title{ Low-Cost Data Deduplication  for  Virtual Machine Backup in Cloud Storage}
+%\title{ Low-Cost Data Deduplication  for  Virtual Machine Backup in Cloud Storage}
+\title{Parallel Deduplication with Batch  Scheduling for  Collocated Virtual Machine Backup in the Cloud}
 %\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
@@
 Wei Zhang$^{\star}$, and Tao Yang$^\star$ \\
-{\normalsize$^\star$  University of California at Santa Barbara}, 
+{\normalsize$^\star$  University of California at Santa Barbara} 
 %{\normalsize$^\dagger$Alibaba Inc.}
@@
 \input{arch} %, design considerations, architecture
-\input{analysis} %, design considerations, architecture
+%\input{analysis} %, design considerations, architecture
 \input{scheduling} % CoW cost considerations and round scheduling
@@
 
-{\bf Acknowledgment.} We thank Michael Agun, Renu Tewari, and
-the anonymous referees for their valuable comments.
+{\bf Acknowledgment.} We thank Hong Tong for his help and support.
+%Renu Tewari, and anonymous referees in for their valuable comments.
 This work is supported in part by NSF IIS-1118106. 

### 2013-12-12 batchdedup/scheduling.tex
revise round scheduling

--- 2013-12-10 batchdedup/scheduling.tex
@@
-\section{Round Scheduling}
+\section{Multi-round Batch Scheduling}
 \label{sect:scheduling}
-The naive way to take advantage of the efficiency of batch processing is to
-schedule all the work to be done in one round.  
+The naive way for synchronized backup is   to schedule all of the backup tasks in one round.
+Since parallel backup of these tasks goes through several stages,
+that results in the backup time of each VM is approximately equal to the total execution of all backup tasks.
+Given VM sizes are highly skewed in a large cluster, some big VMs will take a long time and other
+small VM backup tasks synchronized in one round will have to wait.
+Thus the average backup time for small VMs is fairly large.
+
+Figure~\ref{sizeDistribution} shows the size distribution of VMs for a dataset from Alibaba containing
+about 3000VMs. The largest VM size is to a few terabytes while  the smallest VMs only have a few gigabytes of data.
+The percentage of changes from last backup is also show in the graph and 
+it shows that the change is fairly uniform for large VMs also. Namely when scheduling all VM backup tasks
+in one round in a synchronized manner, and the average backup time per VM is fairly large.
+
+There is another disadvantage with a single-round scheduling. 
+During backup period, new data modification requests can lead a inconsistency between data signature 
+read previously and actual data on the disk.
 % This works well if all of the
@@
 % is sent to over the network. 
-However, in our case we are backing up the
-live virtual disks, thus such single round backup presents several problems
-in our synchronous approach.
-This first is that in order to preserve a consistent view of VM images, we apply
-Copy-on-Write (CoW) to protect the dirty segments against incoming disk writes during 
-the backup period of stage 1 and 2.
-Previous studies have shown that as much as 8\% or even more of total capacity must be reserved for
-CoW \cite{EMCIncrementalDataChanges}, while the actual cost of CoW is a factor of the
-data size, the write rate, and duration of CoW protection.
-The second problem is that a single round backup brings the highest cost of CoW
-because of the workload in stage 1a is imbalanced,
-causing machines with small VMs to wait while CoW protection is turned on.
-Thus we must minimize the duration that a given VM is undergoing CoW protection.
+%However, in our case we are backing up the
+%live virtual disks, thus such single round backup presents several problems
+%in our synchronous approach.
+In order to preserve a consistent view of VM images, we employ
+the Copy-on-Write (CoW) technique to protect the dirty segments against incoming disk writes during 
+the backup period~\cite{VMare2013}. 
+The cost of CoW is a factor of the data size, the write rate, and duration of CoW protection.
+Previous studies have shown that as much as 8\% or even more of total disk capacity may have to be 
+reserved for CoW~\cite{EMCIncrementalDataChanges}.
+Prolonging the backup time of individual VM backup  caused by skewed VM size distribution
+and single-round operation synchronization significantly increases COW overhead.
+%The second problem is that a single round backup brings the highest cost of CoW
+%because of the workload in stage 1a is imbalanced,
+%causing machines with small VMs to wait while CoW protection is turned on.
+%Thus we must minimize the duration that a given VM is undergoing CoW protection.
 
@@
 % individual VMs we also improve CoW cost.
-To evaulate our CoW cost, we assume the incoming writes point to random disk locations, 
+
+\comments{
+To evaluate our CoW cost, we assume the incoming writes point to random disk locations, 
 which would incur a CoW operation over a segment if the write location fall into a dirty segment
@@
 reduce the CoW protection cost, 
-the model we derive is similar to the results meaured by \cite{EMCIncrementalDataChanges}.
+the model we derive is similar to the results measured by \cite{EMCIncrementalDataChanges}.
 % Our basic CoW cost model is:
@@
 % towards CoW. \todo{we still need to pick a value for $c$}
+}
 
-In addition to backup time for individual VMs, another cost consideration is
-total backup time for the system. It is generally preferred to run backups
-during low demand hours to make use of otherwise unused time and minimize the
-impact on users. This leaves a window of several hours (e.g. from 1am to 4am)
-to complete the backup. The more rounds there
-are the shorter each round can be and therefore the smaller the VM backup times
-and the total CoW costs. The
-more rounds there are however the greater the overheads and some of the
-efficiency gained from batch processing is lessened. We balance these costs by
-developing an algorithm to schedule VMs into rounds.
+\subsection{Cost Functions and Optimization Objectives}
 
+When a multi-round schedule is deployed, the backup of a  VM can be executed in one of these rounds.
+Tasks at each round go through the processing stages discussed in Section~\ref{processingStage}.
+\begin{figure}[thb]
+\centering
+\includegraphics[width=0.5\textwidth]{images/VMRound.pdf}
+\caption{Choosing a round to schedule a VM (marked as VM1D in a two-round schedule.  }
+\label{fig:VMRound}
+\end{figure}
+
+The question is which round a VM backup task should be scheduled?
+Figure~\ref{fig:VMRound} illustrates an intermediate step of scheduling in which
+some of VMs have been assigned to a round, and they are marked with the gray boxes. 
+VM named  VM1D is to be scheduled and  can be assigned  to Round 1 or Round 2.
+Scheduling VM1D on Round 1 would not significantly increase the execution time of round 1
+because machine M1 does not have any VM scheduled.
+
+The disadvantage of having many rounds of backup is that the time for  the entire
+backup job for all VMs is stretched for many iterations.
+We call this time as the backup job span.
+In practice, we would like the job span to be controlled within few hours during
+night time. Thus there is a tradeoff to strike in the design of scheduling and
+the optimization  metrics are listed as follow.
+\begin{itemize}
+\item {\em Average backup time T}.
+This is to measure the average number of the backup time time. 
+A smaller number will also shorten the COW cost as discussed above.
+The average backup time also reflects the average computing resource required.
+A shorter backup time means that the computer system devotes less resource in the backup of each VM. 
+\item {\em The job span: J}.
+This is to measure the total time needed to complete all backup tasks.
+Longer the job span is, the more burden is imposed to the cluster management.
+While a short span is better, the  constraint is not high as long as the job can be completed
+in a short period of time (e.g. a few hours during night time).
+
+%It is generally preferred to run backups
+%during low demand hours to make use of otherwise unused time and minimize the
+%impact on users. This leaves a window of several hours (e.g. from 1am to 4am)
+%to complete the backup. The more 
+%are the shorter each round can be and therefore the smaller the VM backup times
+%and the total CoW costs. The
+%more rounds there are however the greater the overheads and some of the
+%efficiency gained from batch processing is lessened. We balance these costs by
+%developing an algorithm to schedule VMs into rounds.
+\item {\em Aggregated optimization}.
+We will use the following combined cost function to set the optimization objective.
+\[
+\alpha T + (1-\alpha) J
+\]
+where $\alpha$ varying between 0 and 1 represents the importance of the average backup time.
+\end{itemize}
+
+%Our round packing heuristic uses a descending sorted order worst fit packing, 
+%Scheduling VMs machine by machine, and is described in Fig~\ref{fig-bpl}.
+%For our higher-level scheduling algorithm, we minimize Resource usage and average
+%backup time, while ensuring that the jobspan constaint is met (if possible). The
+%overall scheduling algorithm is described in Fig~\ref{fig-scheduler}, where T is
+%the alotted time for backup. our cost function is defined as
+%$cost(s) = \alpha\times Resource~Usage(s) + (1-\alpha)\times Avg~Backup~Time(s)$.
+
+There are two cost functions involved.
+\begin{itemize}
+\item Function $Load(m, r)$  is
+the summation of all VMs  processed by each physical machine $m$ at each round $r$.
+\item The execution of time of each round in completing the back up of the assigned VMs.
+We can show that the execution time of each round is proportional to the maximum
+data load of all physical machines.
+\end{itemize}
+
+%Therefore a better scheduling heuristic is one based on predicted runtime after adding the VM, and
+%picking the round with the lowest runtime after adding the VM to that round.
+%This new round picking heuristic
+%takes into account that the same VM might have different affects on different
+%rounds. This aspect of round picking must be considered because we assume a VM
+%must be backed
+%up by the machine that hosts it. If the VMs are located on a DFS such that they
+%can be
+%backed up by any machine in the cluster then the problem of load balancing
+%becomes a simpler but much different problem, but isn't considered here. We
+%also pick the most heavily loaded (i.e. most data remaing) machine in case of
+%ties so we can make the most backup progress in a round, given equivalent
+%equivalent options.
+
+\subsection{Heuristic Algorithms}
+
+Since the physical machine location of each VM is preassigned,
+a scheduling algorithm is to decide the number of rounds to be used
+and the round number that each VM is processed.
+Our algorithm mapping each VM to a round number is outlined as follows.
+% and there are two options in selecting the tasks.
+\begin{itemize}
+\item Repeat following steps for all possible $k$ numbers and choose the schedule
+with the smallest objective function.
+\item For given round number $k$, derive  a schedule as follows.
+	\begin{itemize}
+	\item Select an unscheduled VM. The default option is to select this VM with the maximum VM size.
+Another option is to consider the maximum-sized VM in a physical machine which has the highest 
+unscheduled work load.
+	\item Try all $k$ rounds and find a round number  to assign the selected VM. 
+There are two options to select such a round.
+		\begin{itemize}
+		\item Select the round which has the smallest value $Load(m,r)$.
+		\item Select the round that  gives the minimum increase of the total execution time.
+		\end{itemize}
+	\end{itemize}
+\end{itemize}
+
+\comments{
 \todo{START OF DUAL BIN PACKING BASED ALGORITHM}
@@
 scheduling problem. The algorithm adapted is called iterated A and works by
-iteratively callng a bin packing heuristic A with the items to be scheduled and
+iteratively calling a bin packing heuristic A with the items to be scheduled and
 the number of bins, using binary search to arrive at the best number of
@@
 
-The general algorithm relies on a good choice of A to arrive at an efficent
+The general algorithm relies on a good choice of A to arrive at an efficient
 packing. Our first VM packing heuristic, A0, is a na\"\i{}ve approach very
@@
 
-\begin{figure}[thb]
-\centering
-\includegraphics[width=0.5\textwidth]{images/VMRound.pdf}
-\caption{Choosing a round to schedule a VM to. Though the rounds look
-identical in terms of total/average load, Round 1 is a much better choice.}
-\label{fig:VMRound}
-\end{figure}
-
 A0 does provide for shorter rounds (see Table~\ref{tab:schedule-costs}), but
@@
 loaded machine in a round it will increase runtime much more than if we add the
-VM to a different round where that machine is currently empty. You can see this
-in Figure~\ref{fig:VMRound}, where VM1D must be scheduled to one of two rounds
-which currently have the same average/total load. The effect of VM1D on round 1
-would be much less than the effect on round 2 because we wouldn't be increasing
-the maximum machine load of the round, so we should schedule to round 1.
-Therefore a better
-scheduling heuristic is one based on predicted runtime after adding the VM, and
-picking the round with the lowest runtime after adding the VM to that round.
-This new round picking heuristic
-takes into account that the same VM might have different affects on different
-rounds. This aspect of round picking must be considered because we assume a VM
-must be backed
-up by the machine that hosts it. If the VMs are located on a DFS such that they
-can be
-backed up by any machine in the cluster then the problem of load balancing
-becomes a simpler but much different problem, but isn't considered here. We
-also pick the most heavily loaded (i.e. most data remaing) machine in case of
-ties so we can make the most backup progress in a round, given equivalent
-equivalent options.
+VM to a different round where that machine is currently empty.
 
@@
 machine has a greater impact than selecting the largest VM on a lightly loaded
-machine). Our improved hueristic to pick VMs is to predict the one-round
+machine). Our improved heuristic to pick VMs is to predict the one-round
 runtime after removing that VM, and pick the VM whose removal most
@@
 VMs to rounds, minimizing average VM backup time (and thereby minimizing CoW),
-while also taking into account resource usage and total jobspan (which are
+while also taking into account resource usage and total job span (which are
 minimized in the single round schedule). We solve the problem with a 2-part
@@
 given the constraints.
-
-Our round packing heuristic uses a descending sorted order worst fit packing, 
-Scheduling VMs machine by machine, and is described in Fig~\ref{fig-bpl}.
-For our higher-level scheduling algorithm, we minimize Resource usage and average
-backup time, while ensuring that the jobspan constaint is met (if possible). The
-overall scheduling algorithm is described in Fig~\ref{fig-scheduler}, where T is
-the alotted time for backup. our cost function is defined as
-$cost(s) = \alpha\times Resource~Usage(s) + (1-\alpha)\times Avg~Backup~Time(s)$.
 
@@
 
-Using the above algorithm we can show that for any round $r$, the amount of
-data scheduled to $r$ across all VMs has the upper bound of twice the optimal
-amount of data for a perfectly balanced schedule.
+}
 
-Proof:
-first we define $load(m,r)$ to be the amount of data from VMs on Machine $m$
-to round $r$, $Machines$ to be the set of all machines, and $Rounds$ to be
-the set of all rounds.
-now define $2b_m$ to be the upper bound for data backed up in a single round, 
+\subsection{Properties and Discussions}
+
+The round scheduling algorithm, which chooses a round number that has the smallest
+workload for the corresponding physical machine of a VM, can be competitive to
+the optimum schedule that minimizes the average backup time.
+The competitive factor is 2 and we list the analysis as follows.
+
+%Using the above algorithm we can show that for any round $r$, the amount of
+%data scheduled to $r$ across all VMs has the upper bound of twice the optimal
+%amount of data for a perfectly balanced schedule.
+
+{\bf Property.}
+{\it
+The RS2 algorithm delivers a schedule with average backup time $T$ and
+it satisfies $T \leq 2 T_{opt}$.
+}
+
+\comments{
+%First we define $load(m,r)$ to be the amount of data from VMs on Machine $m$
+%to round $r$, $Machines$ to be the set of all machines, and $Rounds$ to be
+%the set of all rounds.
+Let $m(v)$ be the physical machine location and $d(v)$ be the dirty data size
+of virtual machine $v$.
+
+Let $w(m)$ be the average workload per round and its value is defined as
+\[
+w(m) = \frac{\sum_{v in V(m)} d(v)}{k}
+\]
+When  scheduling a VM $v$ to a round $r$ under Algorithm  RS2, there are two cases.
+\begin{itemize}
+\item Case 1: $Load(m(v),r) > w(m)$.
+Since RS2 selects the round without the minimum $Load(m(v),r)$,
+this implies that
+$\sum{r=1}^k Load(m(v),r) > k*w(m)$.  This case is impossible.
+
+\item Case 2: $Load(m(v),r) \leq w(m)$.
+
+Then the updated workload for machine $m(v)$ satisfies 
+\[
+Load(m(v),r) + d(v) \leq w(m) + d(v) 
+\]
+
+\end{itemize}
+
 where 
@@
 each machine $2b_m$ is the upper bound, which from the definition of $b$ can be
-extended to a global uppoer bound of $2b$. More formally, we would like to show:
+extended to a global upper bound of $2b$. More formally, we would like to show:
 
@@
         $load(m,r)+x < b_m+x$
-    \item $load(m,r) \ge b_m \Longrightarrow$
 
@@
 data.
+
+}
+%$\blacksquare$

### 2014-01-07 batchdedup/scheduling.tex

@@
 % is sent to over the network.
+
 %However, in our case we are backing up the
@@
 %Thus we must minimize the duration that a given VM is undergoing CoW protection.
+
+To determine how evenly distributed VM sizes are, we obtained statistical data
+for 22 Aliyun clusters. The clusters in our dataset all have a very long tail distribution,
+Though local minima exist in the histogram and the range of VM sizes varies. Other production clusters
+may have different distributions, but our findings justify our architecture for a multi-round algorithm.
+A representative histogram for one of the clusters is shown in Fig.~\ref{fig:hist-1}.
+
+\begin{figure}[ht]
+  \centering
+  \begin{tikzpicture}
+      \begin{axis}[
+              ybar interval,
+      ]
+          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
+      \end{axis}
+  \end{tikzpicture}
+  \caption{Histogram of average data sizes for a real cluster. TODO:reformat graph, I just wanted to get the data into the paper}
+  \label{fig:hist-1}
+\end{figure}
 

### 2014-01-07 batchdedup/background.tex
added support for our general purpose approach to backround. added initial simulation approach description to eval.

@@
 determine the changed data.
+
+Further, System admistrators may wish to adjust the balance between resource 
+usage for backup and the time spent performing backups. There may be a small
+backup window (e.g. 2 hours) to complete the backups each night, but the backup
+should also minimize impact on VMs running during that time. Other studies have
+shown, for example, that the cost of Copy on Write (CoW) during daily backups
+can be as much as 8\% of the total data size \cite{EMCIncrementalDataChanges}.
 

### 2014-01-07 batchdedup/eval.tex
added support for our general purpose approach to backround. added initial simulation approach description to eval.

@@
 		xlabel={Total Network Memory Buffer (MB)},
-		ylabel={Backup Time},
+		ylabel={Backup Time (hrs)},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		]
-                \addplot table[x=mpibufmem,y=totaltime] {figures/mpibufmem.txt};
+                \addplot table[x=mpibufmem,y expr=(\thisrow{totaltime}/3600)] {figures/mpibufmem.txt};
                 %\legend{Total Backup Time};
@@
   \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, write buffer 6.25MB, Read Buffer 128KB}
-  \label{fig:mpibuf-mem}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={Network Buffer Size},
-		xlabel={Rounds},
-		ylabel={Throughput (GB/s)},
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		%legend pos=north west
-		]
-                \addplot table[x=rounds,y=throughput] {figures/sim_full.txt};
-                %\legend{Total Backup Time};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{simulated results for average throughput for individual VMs in 100 node cluster.}
-  \label{fig:mpibuf-mem}
-\end{figure}
-\begin{figure}[ht]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={Network Buffer Size},
-		xlabel={Rounds},
-		ylabel={Average Backup Time (min)},
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		%legend pos=north west
-		]
-                \addplot table[x=rounds,y expr=(\thisrow{avgbackuptime})/60] {figures/sim_full.txt};
-                %\legend{Total Backup Time};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{simulated results for average vm backup time for individual VMs in 100 node cluster.}
   \label{fig:mpibuf-mem}
@@
 %\end{figure}
+
+\subsection{Simulated Algorithm Comparison}
+
+Based on results from out trace-driven study, we also compare algorithms using
+the amount of data transferred over the network, written to disk, and read from
+disk in each stage. From this simple performance model, we can compare
+different scheduling heuristics and weights and choose the most appropriate
+algorithm for a set of requirements. Our simulation uses VM size distributions
+from production clusters to evaluate the scheduling algorithms across several
+clusters. we discuss the size distributions in section \ref{??}.
 
@@
 		xlabel={Rounds},
-		ylabel={Average Backup Time (s)},
+		ylabel={Average Backup Time (hrs)},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		]
-                \addplot table[x=Rounds,y=DBP2avgbackup] {figures/packing_comparison.txt};
-                \addplot table[x=Rounds,y=BPLavgbackup] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}/3600)] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}/3600)] {figures/packing_comparison.txt};
                 \legend{DBP2, BPL};

### 2014-01-07 batchdedup/scheduling.tex
updates to histogram

@@
 
-Figure~\ref{sizeDistribution} shows the size distribution of VMs for a dataset from Alibaba containing
-about 3000VMs. The largest VM size is to a few terabytes while  the smallest VMs only have a few gigabytes of data.
-The percentage of changes from last backup is also show in the graph and 
-it shows that the change is fairly uniform for large VMs also. Namely when scheduling all VM backup tasks
-in one round in a synchronized manner, and the average backup time per VM is fairly large.
+%Figure~\ref{sizeDistribution} shows the size distribution of VMs for a dataset from Alibaba containing
+%about 3000VMs. The largest VM size is to a few terabytes while  the smallest VMs only have a few gigabytes of data.
+%The percentage of changes from last backup is also show in the graph and 
+%it shows that the change is fairly uniform for large VMs also. Namely when scheduling all VM backup tasks
+%in one round in a synchronized manner, and the average backup time per VM is fairly large.
 
@@
 A representative histogram for one of the clusters is shown in Fig.~\ref{fig:hist-1}.
+You can see that the range of sizes is very large (the smallest group of 100 VMs has an average size of ~15GB, while the largest has an average size of over 700GB).
+It is that fact that VM sizes vary greatly that makes the scheduling of VMs to rounds important.
 
@@
               ybar interval,
+              xlabel=Avg VM Size in Group (GB),
+              ylabel=Number of Groups,
+              xticklabel={\pgfmathparse{(\tick*1)}\num[round-mode=places, round-precision=0]{\pgfmathresult}}
       ]
@@
   \end{tikzpicture}
-  \caption{Histogram of average data sizes for a real cluster. TODO:reformat graph, I just wanted to get the data into the paper}
+  \caption{Histogram of average data sizes for a real cluster. TODO:adjust this using the new spreadsheets}
   \label{fig:hist-1}

### 2014-01-15 thesis/Acknowledgements.tex
final thesis

@@
 \addcontentsline{toc}{chapter}{Acknowledgements}
-I want to take this opportunity to thank my advisor Professor Tao Yang for 
+
+First of all, I want to take this opportunity to thank my advisor Professor Tao Yang for 
 his invaluable advice and instructions to me on selecting interesting and challenging
 research topics, identifying specific problems for each research phase, 
-as well as preparing for my future career.
+as well as preparing for my future career. I would also like to thank my committee
+members, Professor Rich Wolski and Professor Jianwen Su, for their pertinent and helpful
+instructions on my research work.
 
-I also want to thank members and ex-members of my research group, Michael Agun, and 
-Hong Tang, for their incessant support in the forms of technical discussion, 
+I also want to thank members and ex-members of my research group, Michael Agun, Gautham Narayanasamy,
+Prakash Chandrasekaran, Xiaofei Du, and Hong Tang, 
+for their incessant support in the forms of technical discussion, 
 system co-development, cluster administration, and other research activities.
 
-Finally, I want to thank my dissertation committee members, Professor 
-Jianwen Su, Professor Richard Wolski 
-for their insightful comments over my dissertation.
+I owe my deepest gratitude to my parents, for their love and support, which give 
+me the confidence and energy to overcome all past, current, and future difficulties.
 
-This dissertation study was supported in part by NSF xxx.
+Finally and most importantly, I would like to express my gratitude beyond 
+words to my wife, Jiayin, who has been encouraging and inspiring me 
+since we met in love. We went through all the difficlut times together,
+and depended on each other in this foreign place one Pacific Ocean away from our homeland.
+Every step forward I have made is unimaginable without Jiayin's support.
+
+This dissertation study was supported in part by NSF IIS-1118106.
 \end{acknowledgements}

### 2014-01-15 batchdedup/analysis.tex

@@
 
+\subsection{Metrics}
+We have chosen two primary metrics to evaluate our approach and the efficiency
+of our scheduling (discussed in the next section). The first metric is total
+jobspan. This metric is used to determine how long of a backup window is
+required for each round of backups, and also can show throughput of the entire
+system.
+
+Our system uses a multi-round batch approach, so we need another metric to
+evaluate how the rounds affect time.  The second metric we have chosen is
+average VM backup time. This metric helps us to compare different schedules,
+and evaluate the tradeoff between batch efficiency and the time that VMs are
+spent in backup (which affects CoW). Within a round, we assign all VMs the backup time
+for that round, and then compute the mean backup time across all VMs.
+
 \subsection{A Comparison with Other Approaches}

### 2014-01-15 batchdedup/eval.tex
updated scales on graphs

@@
 		xlabel={Rounds},
-		ylabel={Total Jobspan (m)},
+		ylabel={Total Jobspan (hrs)},
 		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
@@
 		]
-                \addplot table[x=Rounds,y expr=(\thisrow{DBP2jobspan})/60] {figures/packing_comparison.txt};
-                \addplot table[x=Rounds,y expr=(\thisrow{BPLjobspan})/60] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{DBP2jobspan})/3600] {figures/packing_comparison.txt};
+                \addplot table[x=Rounds,y expr=(\thisrow{BPLjobspan})/3600] {figures/packing_comparison.txt};
                 \legend{DBP2, BPL};

### 2014-01-17 batchdedup/scheduling.tex
update size distribution chart with density function to compute bins

@@
 
+%\begin{figure}[ht]
+%  \centering
+%  \begin{tikzpicture}
+%      \begin{axis}[
+%              ybar interval,
+%              xlabel=Avg VM Size in Group (GB),
+%              ylabel=Number of Groups,
+%              xticklabel={\pgfmathparse{(\tick*1)}\num[round-mode=places, round-precision=0]{\pgfmathresult}}
+%      ]
+%          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
+%      \end{axis}
+%  \end{tikzpicture}
+%  \caption{Histogram of average data sizes for a real cluster. TODO:adjust this using the new spreadsheets}
+%  \label{fig:hist-1}
+%\end{figure}
+
 \begin{figure}[ht]
@@
               ybar interval,
-              xlabel=Avg VM Size in Group (GB),
-              ylabel=Number of Groups,
-              xticklabel={\pgfmathparse{(\tick*1)}\num[round-mode=places, round-precision=0]{\pgfmathresult}}
+              xlabel=VM Size (GB),
+              ylabel=Probability Distribution,
+              xtick={50,100,200,300,400,500,600,700,800,900,1000},
       ]
-          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
+          \addplot+[fill=blue] table[x=MinSize,y=Prob] {figures/AY41A_PD.txt};
       \end{axis}
@@
 \end{figure}
+
+%xticklabel={\pgfmathparse{(\tick*1)}\num[round-mode=places, round-precision=0]{\pgfmathresult}}
 

### 2014-01-22 snapshot_system/fast14_conclusion.tex
added tradeoffs to intro and conclusion, added VO with extra replication approach

@@
 In this paper we propose a collocated backup service built on
-the top of a cloud cluster to reduce network traffic and infrastructure.
+the top of a cloud cluster to reduce network traffic and infrastructure requirements.
 The key contribution is a VM-centric deduplication scheme to 
-maximize fault isolation while delivering competitive deduplication efficiency.
+maximize fault isolation with only a slight tradeoff in deduplication efficiency.
 Similarity guided local search reduces cross-VM data dependency and exposes more parallelism  

### 2014-01-22 snapshot_system/fast14_deduplication.tex
re
revisions
added tradeoffs to intro and conclusion, added VO with extra replication approach

@@
 the VM's I/O traffic and implement such changed block tracking feature.
+%The dirty bit tracking is valuable because it immediately cuts down the number of blocks
+%which must be processed, and reduces memory, network, and cpu resource requirements.
 
@@
 % Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
-\subsection{Impact on Deduplication Efficiency}
-Choosing the value $k$ for the most popular chunks affects the deduplication efficiency.
-We analyze this impact based on the characteristics  of the VM snapshot traces
-studied from  application datasets.
-A previous study shows that the popularity of data chunks after local deduplication follows 
-a Zipf-like distribution\cite{Breslau1999a} and its
-exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
-Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
-The parameters we will use in our analysis below are defined in
-Table~\ref{tab:symbol}.
 
@@
 \hline
-$V$ & the average number of VMs hosted on each machine\\
+$V$ & the average number of VMs per machine\\
 \hline
@@
 \end{table}
+
+\subsection{Impact on Deduplication Efficiency}
+Choosing the value $k$ for the most popular chunks affects the deduplication efficiency.
+We analyze this impact based on the characteristics  of the VM snapshot traces
+studied from  application datasets.
+A previous study shows that the popularity of data chunks after local deduplication follows 
+a Zipf-like distribution\cite{Breslau1999a} and its
+exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
+Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
+The parameters we will use in our analysis below are defined in
+Table~\ref{tab:symbol}.
 
@@
 
+In Figure~\ref{fig:share} we build a bipartite graph representing the
+association from unique file system blocks to their corresponding VMs in the VC
+and VO approaches. We use an FSB rather than data chunk as our unit of failure
+because the DFS keeps file system blocks as its base unit of storage, and in
+the case of 64MB FSBs and 4KB chunks, there are 16K chunks per block. In VC
+we assign extra replication to the PDS blocks, while in VO the replication
+degree is fixed.
+
+We could consider a third approach (call it VO+), adopting the VO approach, and
+then relying on filesystem features to provide extra replication to popular
+blocks, without the extra complexity of separating popular and non-popular
+data. The problem with this VO+ approach is that without separating the
+popular chunks from the less-popular, the popular chunks are dispersed across
+all of the filesystem blocks in the storage system. Because the popular blocks
+are dispersed, there are very few popular FSBs. The end result is that we
+either have to add extra replication on unpopular chunks to ensure the popular
+chunks have sufficient replication, or we have to accept a reduced replication
+factor on popular chunks. This explains why we must separate the PDS and
+non-PDS data in our system to acheive the desired $r_c/r$ ratio (though both can be stored on the same DFS).
+
 %In the VC approach, a special replication degree $r_c$ is used for PDS data where $r_c>r$. 
@@
 A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
-We use an FSB rather than a deduplication
-data chunk as our unit of failure because the DFS keeps
-file system blocks as its base unit of storage.
 To compute the full availability of all snapshots of a VM, we derive
@@
 estimating the number of file system blocks per VM in each approach.
-As illustrated in Figure~\ref{fig:share},
-we build a bipartite graph representing the association from unique file system blocks
-to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
+An association edge is  drawn  from an FSB to a VM 
 if this block is used by the VM.
@@
 \[
-A(r)^{N_1} * A(r_c)^{N_2}
+A(r)^{N_1} * A(r_c)^{N_2}.
 \]

### 2014-01-22 batchdedup/scheduling.tex
Additional cluster histogram added

@@
 To determine how evenly distributed VM sizes are, we obtained statistical data
-for 22 Aliyun clusters. The clusters in our dataset all have a very long tail distribution,
-Though local minima exist in the histogram and the range of VM sizes varies. Other production clusters
-may have different distributions, but our findings justify our architecture for a multi-round algorithm.
-A representative histogram for one of the clusters is shown in Fig.~\ref{fig:hist-1}.
-You can see that the range of sizes is very large (the smallest group of 100 VMs has an average size of ~15GB, while the largest has an average size of over 700GB).
-It is that fact that VM sizes vary greatly that makes the scheduling of VMs to rounds important.
+for 22 Aliyun clusters. The clusters in our dataset all have a very long tail
+distribution, though local minima exist in the histogram and the range of VM
+sizes varies. Other production clusters may have different distributions, but
+all of the clusters we have looked at have similarly shaped distributions. Size
+distribution histograms for two of the clusters are shown in
+Fig.~\ref{fig:hist}. There is a long tail on both histrograms which has been
+cut (out to 100GB for the first, and out to 2000GB for the second). The
+important thing to get from this data is that in none of the productions
+clusters we evaluated was the VM Size distribution flat, which motivates the
+importance of round scheduling.
 
@@
 \begin{figure}[ht]
+%\centering
+\begin{subfigure}%{.5\textwidth}
   \centering
@@
               ybar interval,
-              xlabel=VM Size (GB),
-              ylabel=Probability Distribution,
-              xtick={50,100,200,300,400,500,600,700,800,900,1000},
+              width=0.55\linewidth,
+                    tick label style={font=\scriptsize},
+                    tick style=thin,
+              xmax=150,
+              xlabel={\tiny VM Size (GB)},
+              ylabel={\tiny Percent of VMs},
+              xtick={0,50,100,150,200,250,300,400,500,600},
       ]
-          \addplot+[fill=blue] table[x=MinSize,y=Prob] {figures/AY41A_PD.txt};
+          \addplot+[fill=blue] table[x=MinSize,y expr=\thisrow{Prob}*100] {figures/AY41A_PD.txt};
       \end{axis}
   \end{tikzpicture}
-  \caption{Histogram of average data sizes for a real cluster. TODO:adjust this using the new spreadsheets}
-  \label{fig:hist-1}
+  %\caption{Histogram of average data sizes for a real cluster.}
+  \label{fig:hist-AY41A}
+\end{subfigure}
+%
+%
+\begin{subfigure}%{.5\textwidth}
+  \centering
+  \begin{tikzpicture}
+      \begin{axis}[
+              ybar interval,
+              width=0.55\linewidth,
+                    tick label style={font=\scriptsize},
+                    tick style=thin,
+              xmax=150,
+              xlabel={\tiny VM Size (GB)},
+              ylabel={\tiny Percent of VMs},
+              xtick={0,50,100,150,200,250,300,400,500,600},
+      ]
+          \addplot+[fill=blue] table[x=MinSize,y expr=\thisrow{Prob}*100] {figures/AY41H_PD.txt};
+      \end{axis}
+  \end{tikzpicture}
+  %\caption{Histogram of average data sizes for a real cluster.}
+  \label{fig:hist-AY41H}
+\end{subfigure}
+\caption{Histograms of average VM sizes for several production clusters}
+\label{fig:hist}
 \end{figure}

### 2014-01-22 batchdedup/scheduling.tex
algorithm updates

@@
 
-Since the physical machine location of each VM is preassigned,
-a scheduling algorithm is to decide the number of rounds to be used
-and the round number that each VM is processed.
-Our algorithm mapping each VM to a round number is outlined as follows.
+We assume the physical machine location of each VM is preassigned, and that the
+VM should be backed up from the machine hosting it.  This may not be a
+requirement of the system (e.g. if the virtual disks are stored on a DFS any
+machine could theoretically backup the VM), but in a converged storage
+architecture it should be the case that at least one replica of the VM disk is
+on/near the hosting machine, so we maximize data locality by taking advantage
+of this. A scheduling algorithm is developed to decide the number of rounds to
+be used and the round number that each VM is processed.  Our algorithm mapping
+each VM to a round number is outlined as follows.
 % and there are two options in selecting the tasks.
 \begin{itemize}
-\item Repeat following steps for all possible $k$ numbers and choose the schedule
+\item Repeat following steps for all possible $k$ values (numbers of rounds) and choose the schedule
 with the smallest objective function.
@@
 	\begin{itemize}
-	\item Select an unscheduled VM. The default option is to select this VM with the maximum VM size.
+	\item Select an unscheduled VM. The default option is to select the VM with the maximum VM size.
 Another option is to consider the maximum-sized VM in a physical machine which has the highest 
@@
 \end{itemize}
+
+\begin{algorithm}
+\ForEach{k in (1..Num VMs)}{
+  Sort VMs in descending size order\;
+  \ForEach{VM}{
+    schedule VM to round with smallest load\;
+  }
+  Compute the cost of this schedule (using objective function)\;
+}
+Select the k which had the lowest schedule cost\;
+\caption{VM round scheduling algorithm}
+\end{algorithm}
+
+\begin{algorithm}
+\ForEach{k in (1..Num VMs)}{
+  \ForEach{x in (1..Num VMs}{
+    Choose the largest VM from the machine with the highest unscheduled workload\;
+    Schedule VM to round with smallest load\;
+  }
+  Compute the cost of this schedule (using objective function)\;
+}
+Select the k which had the lowest schedule cost\;
+\caption{Alternate VM round scheduling algorithm}
+\end{algorithm}
 

### 2014-01-23 snapshot_system/paper_abs.tex
add paper files

\begin{abstract}
Data deduplication has been widely used for cloud data backup
because of excessive redundant content blocks. Common techniques use dirty bits to detect
the version  change and  perform global fingerprint comparison to remove duplicates
across virtual machines. However, letting a duplicate data block be shared
by many virtual machines creates data dependence and is less fault-resilient. 
%This paper studies the impact of deduplication on 
%fault resilidence  of virtual machine snapshots, created by data dependence  among duplicates
%and proposes a VM-centric approach that strikes a balance between deduplication efficiency
%and fault isolation 
This paper proposes a VM-centric backup service on a converged  storage cluster architecture
and  strikes a balance for better fault isolation with competitive  deduplication efficiency.
It localizes deduplication as much as possible within each 
virtual machine, guided by similarity
search and associates  underlying file blocks with one VM for most cases.
It restricts global deduplication to popular chunks with extra replication support.
This VM-centric scheme also has  an advantage of   using less  computing resources for fingerprint comparison and simplifies snapshot deletion, suitable for a collocated backup service 
on a non-dedicated cluster architecture.
This  paper  describes an evaluation of this scheme to assess  its deduplication 
efficiency and fault resilience.

% Collocating a cluster-based duplicate service with other cloud services
%   necessary to eliminate
%redundant blocks and reduce cost. Collocating a cluster-based duplicate service with other cloud services

%A cloud environment that hosts a large number of virtual machines (VMs) has
%a high storage demand for frequent backup of system image snapshots. 
%Deduplication of data blocks is necessary to eliminate
%redundant blocks and reduce cost. Collocating a cluster-based duplicate service with other cloud services
%reduces network traffic;
%however, 
\end{abstract}

### 2014-01-23 snapshot_system/paper_analysis.tex
add paper files

--- 2013-09-27 snapshot_system/fast14_deduplication.tex
@@
-\section{VM-centric Snapshot Deduplication}
-\label{sect:deduplication}
-
-\subsection{Key VC  Strategies}
-\label{sect:vc-strategies}
-%\begin{itemize}
-%\item 
-\textbf{VM-specific local duplicate search within similar segments.}
-We start with the changed block tracking approach in a coarse grain segment level.
-In our implementation with Xen on an Alibaba platform, the segment size is 2MB
-and the device driver is extended to support tracking changed segments using a dirty bitmap. 
-Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
-and cannot afford a small segment size.
-It should be noted that dirty bit tracking is supported or can be easily implemented in 
-major virtualization solution vendors. For example,
-the VMWare hypervisor has an API to let external backup applications know 
-the changed areas since last backup. 
-The Microsoft SDK provides an API that allows external applications to monitor 
-the VM's I/O traffic and implement such changed block tracking feature.
-
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=images/mh_local_dedup.pdf, width=3in}
-  \caption{Similarity-guided local duplicate detection}
-  \label{fig:local_dedup}
-\end{figure}
-
-Since the best deduplication uses a non-uniform chunk size 
-in the average of 4KB or 8KB~\cite{Jin2009},
-we conduct additional local similarity guided deduplication on a snapshot by comparing
-chunk fingerprints of a dirty segment 
-with those in  {\em similar} segments from its parent snapshot. 
-We define two segments are similar if their content signature is the same.
-This segment content signature value is defined as the minimum value of all its chunk fingerprints 
-computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
-content similarity is an approximation~\cite{resemblance97}.  When processing a dirty segment,
-its  similar segments can be found easily from the
-parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
-which contain chunk fingerprints to be compared.
-To control the time cost of search, we set a limit on the number of  similar segments recipes to be fetched. 
-% Then,
-%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
-%with those in similar segments.  
-For a 2MB segment, its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
-by limiting at most 10 similar segments to search, the amount of memory for maintaining those similar segment recipes is small.
-As part of our local duplicate search we also compare the current segment
-against the parent segment at the same offset.
-
-%\item 
-\textbf{Global deduplication with popular chunks and replication support.}
-This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
-Our key observation is that the local deduplication has removed most of the duplicates.
-There are fewer deduplication opportunities across VMs while the memory and network
-consumption for global comparison is more expensive.
-Thus our approximation is that the global fingerprint comparison only searches for the top $k$
-most popular items. This dataset is called the \textbf{PDS} (popular data set). 
-We define chunk popularity as the number of unique copies of the chunk in the data-store,
-i.e., the number of copies of the chunk after local deduplication.
-This number can be computed periodically, e.g., on a weekly basis.
-Once the popularity of all data chunks is collected, the system only maintains the top $k$
-most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
-%Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
-%this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
-%analytic design guidance.
-
-Since $k$ is relatively small and these top $k$ chunks are shared among multiple VMs, 
-we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
-
-%\item 
-\textbf{VM-centric file system block management.}
-When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
-to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
-accumulate small local chunks. We manage this accumulation process using a log-structured storage scheme built
-on a distributed file system discussed in Section~\ref{sect:architecture}.
-%Non-PDS chunks from the same VM are stored in one append store. 
-Each file system block is either dedicated to non-PDS chunks, or PDS-chunks.
-A file system block for non-PDS chunks is associated with one VM and does not contain
-any PDS chunks, such that our goal of fault isolation is maintained.
-In addition, storing PDS chunks separately allows special replication handling for those popular shared data. 
-%%% talk something about snapshot store advantage here? %%%
-
-%The system allows all machines conduct backups in parallel, and each machine
-%conducts the backup of one VM at a time, and thus only requires a write buffer for one VM.
-%\end{itemize}
-
-\begin{figure}
-\centering
-%\epsfig{file=log-log.disk,width=3in}
-%source ../vm_snapshot_sim/images/log-log.disk.eps
- \includegraphics[width=3in]{figures/log-log-disk}
-\caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
-\label{fig:Datazipf}
-\end{figure}
-
-% {\it [Need to find a place to put these numbers in: Total number of chunks 
-% in 350 snapshots: 1,546,635,485. 
-% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
-\subsection{Impact on Deduplication Efficiency}
-Choosing the value $k$ for the most popular chunks affects the deduplication efficiency.
-We analyze this impact based on the characteristics  of the VM snapshot traces
-studied from  application datasets.
-A previous study shows that the popularity of data chunks after local deduplication follows 
-a Zipf-like distribution\cite{Breslau1999a} and its
-exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
-Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
-The parameters we will use in our analysis below are defined in
-Table~\ref{tab:symbol}.
-
 \begin{table}[htbp]
@@
 
-%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
-%let $c$ be the total number of data chunks. 
-%$c_u$ be the total number of fingerprints 
-%in the global index after complete deduplication, and
-%$f_i$ be the frequency for the $i$th most popular fingerprint. 
-By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
-The total number of chunks in our backup storage which
-has local duplicates excluded is $c (1-\delta)$, this can be represented
-as the sum of each unique fingerprint times its frequency:
-%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
-\[
-f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
-\]
-Given $\alpha <1$, $f_1$ can be approximated with integration:
-%\begin{equation}
-\[
-f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
-\]
-%\end{equation}
-
-Thus putting the $k$ most popular fingerprints into PDS index can remove the following number of chunks during global 
-deduplication:
-\[
-f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
-f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}
-=c(1-\delta) \sigma^{1-\alpha}.
-\]
-
-Deduplication efficiency of the VC approach using top $k$ popular chunks
-is the percentage of duplicates that can be detected:  
-\begin{equation}
-\label{eq:dedupeff}
-%\begin{split}
-%e_k &= 
-E_c=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
-{c  - c_u }.\\
-%\end{split}
-\end{equation}
-
-% After the global deduplication, the number of remaining chunks is:
-% \[
-% c-E(c-c_u)
-% \]
-
-We store the PDS index using a distributed shared memory hash table such as Memcached
-and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
-As the number of physical machines ($p$) increases,
-the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
-a constant because each physical machine on average still hosts a fixed constant number of 
-VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
-remains constant.
-Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.
-
-\begin{figure}[htbp]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={PDS Coverage},
-            width=\linewidth,
-            height=0.6\linewidth,
-            cycle multi list={
-                mline\nextlist
-                [3 of]mmark*\nextlist
-            },
-            %cycle list name=mcolor,
-            xlabel={Total num. chunks stored (in billions)},
-            ylabel={PDS Coverage (\%)},
-            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
-            mark options=solid,
-            %legend pos=outer north east,
-            legend columns=2,
-            legend style={
-                at={(0.5,-0.30)},
-            anchor=north},
-            ]
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
-            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
-            \end{axis}
-    \end{tikzpicture}
-  \caption{Predicted vs. actual PDS coverage as data size increases.}
-  \label{fig:cds-coverage}
-\end{figure}
-Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
-chunks detected as duplicates in global deduplication due to PDS.
-We call this PDS coverage.
-Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
-0.65 and measured PDS coverage in our test dataset.
-$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
-While the predicted value remains flat, measured PDS coverage increases as more VMs are involved.
-This is because the actual $\alpha$ value increases with the data size.
-%Then  PDS coverage PDS increases as more VMs are involved.
-
 \subsection{ Impact on Fault Isolation}
@@
 
+We analyze the impact of replication degree for PDS and non-PDS data items.
+The parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
 The replication degree of the backup storage 
@@
 \end{table}
+
+\comments{
+\subsection{Impact on Deduplication Efficiency}
+Choosing the value $k$ for the most popular chunks affects the deduplication efficiency.
+We analyze this impact based on the characteristics  of the VM snapshot traces
+studied from  application datasets.
+A previous study shows that the popularity of data chunks after local deduplication follows 
+a Zipf-like distribution\cite{Breslau1999a} and its
+exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
+Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
+The parameters we will use in our analysis below are defined in
+Table~\ref{tab:symbol}.
+
+%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
+%let $c$ be the total number of data chunks. 
+%$c_u$ be the total number of fingerprints 
+%in the global index after complete deduplication, and
+%$f_i$ be the frequency for the $i$th most popular fingerprint. 
+By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
+The total number of chunks in our backup storage which
+has local duplicates excluded is $c (1-\delta)$, this can be represented
+as the sum of each unique fingerprint times its frequency:
+%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
+\[
+f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
+\]
+Given $\alpha <1$, $f_1$ can be approximated with integration:
+%\begin{equation}
+\[
+f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
+\]
+%\end{equation}
+
+Thus putting the $k$ most popular fingerprints into PDS index can remove the following number of chunks during global 
+deduplication:
+\[
+f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
+f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}
+=c(1-\delta) \sigma^{1-\alpha}.
+\]
+
+Deduplication efficiency of the VC approach using top $k$ popular chunks
+is the percentage of duplicates that can be detected:  
+\begin{equation}
+\label{eq:dedupeff}
+%\begin{split}
+%e_k &= 
+E_c=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
+{c  - c_u }.\\
+%\end{split}
+\end{equation}
+
+% After the global deduplication, the number of remaining chunks is:
+% \[
+% c-E(c-c_u)
+% \]
+
+We store the PDS index using a distributed shared memory hash table such as Memcached
+and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
+As the number of physical machines ($p$) increases,
+the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
+a constant because each physical machine on average still hosts a fixed constant number of 
+VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
+remains constant.
+Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.
+
+\begin{figure}[htbp]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={PDS Coverage},
+            width=\linewidth,
+            height=0.6\linewidth,
+            cycle multi list={
+                mline\nextlist
+                [3 of]mmark*\nextlist
+            },
+            %cycle list name=mcolor,
+            xlabel={Total num. chunks stored (in billions)},
+            ylabel={PDS Coverage (\%)},
+            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
+            mark options=solid,
+            %legend pos=outer north east,
+            legend columns=2,
+            legend style={
+                at={(0.5,-0.30)},
+            anchor=north},
+            ]
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
+            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
+            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
+            \end{axis}
+    \end{tikzpicture}
+  \caption{Predicted vs. actual PDS coverage as data size increases.}
+  \label{fig:cds-coverage}
+\end{figure}
+Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
+chunks detected as duplicates in global deduplication due to PDS.
+We call this PDS coverage.
+Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
+0.65 and measured PDS coverage in our test dataset.
+$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
+While the predicted value remains flat, measured PDS coverage increases as more VMs are involved.
+This is because the actual $\alpha$ value increases with the data size.
+%Then  PDS coverage PDS increases as more VMs are involved.
+}

### 2014-01-23 snapshot_system/paper_arch.tex
add paper files

--- 2013-09-27 snapshot_system/fast14_architecture.tex
@@
 %\end{itemize}
-
-\subsection{ VM-centric Approximate Snapshot Deletion with Leak Repair}
-\label{sect:delete}
-
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=images/deletion.pdf, width=3in}
-  \caption{Approximate deletion}
-  \label{fig:deletion_flow}
-\end{figure}
-
-In a busy VM cluster, snapshot deletions can occur frequently.
-Deduplication complicates the deletion process because space saving relies on the sharing of data
-and it requires the global references to deleted chunks to be identified before  they can be safely removed.
-While we can use the mark-and-sweep technique~\cite{Guo2011}, 
-it takes significant resources to conduct this process every time there is a snapshot deletion.
-%In the case of Alibaba, snapshot backup is conducted automatically and there are 
-%about 10 snapshot stored for every VM customer.
-Snapshot deletion can occur frequently, for example when there is
-a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
-balanced storage use.
-
-We seek a fast solution with low resource usage to delete snapshots and
-our VM-centric design simplifies the deletion process. 
-Since PDS is small and separated, we can focus on  unreferenced non-PDS chunks within each VM. 
-%The PDS data chunks are commonly shared among all VMs and we do not consider them
-%during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
-Another resource-saving strategy we propose is
-an {\em approximate} deletion strategy to trade deletion accuracy for
-speed and resource usage. Our method sacrifices a small percent of storage leakage
-to efficiently identify unused chunks.
-The algorithm contains three aspects.
-
-\begin{itemize}
-\item {\bf Computation for snapshot reference summary.}
-Every time there is a new snapshot created,
-we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
-in this snapshot.
-The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
-For each VM we preset the vector size according to  estimation of VM image size,
-given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
-We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
-This can be done during the periodic leakage repair stage described below.
-
-\item {\bf Approximate deletion with fast summary comparison.}
-When there is a snapshot deletion,  
-we need to identify if  chunks to be deleted from that snapshot
-are still referenced by other snapshots. 
-This is done approximately and quickly by comparing the 
-reference of deleted chunks  with
-the merged reference summary vectors of other live snapshots.
-The merging of live snapshot Bloom-filter vectors uses the bitwise OR operator 
-and the merged vector still takes $z$ bits.
-Since the number of live snapshots $h$ is limited for
-each VM, 
-the time and memory cost of this comparison is small, linear to the number of chunks to be deleted.
-
-If a chunk's reference is not found in the merged summary vector, we are sure that
-this chunk is not used by any live snapshots, thus it can be deleted safely.
-However, among all the chunks to be deleted, 
-there are a small percentage of unused chunks  which
-are misjudged as  being in use, resulting in storage leakage.
-
-\item {\bf Periodic repair of leakage}.
-%[exlpain why second Bloom filter, why scan append store]
-Leakage repair is conducted periodically to fix the above approximation error.
-This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
-This requires a scan of the entire snapshot store. Since it is a VM-specific procedure 
-the space and time cost is relatively small compared to the traditional mark-and-sweep procedure~\cite{Guo2011} which scans snapshot 
-chunks from all VMs.
-For example,
-consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
-10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process
-in less than half an hour, assuming 50MB/s disk bandwidth is allocated.
-\end{itemize}
-
-%{\bf Discussion}
-We now estimate the size of storage leakage and how often leak repair needs to be conducted.
-Assume that  a VM keeps $h$ snapshots in the backup storage, creates and deletes one snapshot
-every day. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
-number of additional chunks added from one snapshot to the next snapshot version. Then the total number of 
-chunks stored in a VM's snapshot store is about:
-\[
-U = u + (h-1)\Delta u.
-\]
-
-Each Bloom filter vector has  $z$ bits for each snapshot and let $j$ be the number of hash functions used by the
-Bloom filter.  Notice that a chunk may appear multiple times in these summary vectors; however, this should not 
-increase the probability of being a 0 bit in all $h$ summary vectors.
-Thus the probability that a particular bit is 0  in all $h$ summary vectors is  
-$(1- \frac{1}{z}) ^{j U}$. 
-Then the misjudgment rate of being in use  is: 
-\begin{equation}
-\label{eq:falserate}
-\epsilon = (1-(1-\frac{1}{z})^{jU})^j.
-\end{equation}
-
-For each snapshot deletion, the number of chunks to be deleted is nearly identical to the number of
-newly added chunks $\Delta u$. 
-Let $R$ be the total number of runs of approximate deletion between two consecutive 
-repairs. We estimate  the total leakage $L$ after $R$ runs as:
-\[
-L = R \epsilon \Delta u.
-\]
-
-When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we trigger a leak repair. Namely,
-
-\begin{equation}
-\label{eq:leakrepair}
-\frac{L}{U} = \frac{R \Delta u \epsilon}{u+(h-1)\Delta u } > \tau 
-\Longrightarrow R > \frac{\tau}{\epsilon}\times\frac{u + (h-1)\Delta u}{\Delta u}.
-\end{equation}
-
-For example in our tested dataset,  
-$h=10$ and each snapshot adds
-about 0.1-5\% of new data. Thus we take ${\Delta u}/{u} \approx 0.025$. For a 40GB snapshot, $u\approx  10$ million.
-Then $U=12.25$ million.
-We choose  $\epsilon = 0.01$ and $\tau=0.05$.  From Equation~\ref{eq:falserate}, 
-each summary vector requires $z=10U=122.5$ million bits or 15MB. From Equation~\ref{eq:leakrepair}, 
-leak repair should be triggered once for every R=245 runs of approximate deletion. 
-When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
-only one full leak repair for one physical machine scheduled for every 9.8 days. 
-If $\tau = 0.1$ then leakage repair would occur every 19.6 days.

### 2014-01-23 snapshot_system/paper_background.tex
add paper files

--- 2013-09-27 snapshot_system/fast14_background.tex
@@
 \label{sect:background}
-At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
+
+Figure~\ref{fig:collocated} illustrates a converged cloud architecture where
+each commodity server hosts a number of virtual machines and storage of these servers
+is clustered using a distributed file system (DFS)~\cite{googlefs03,hdfs10}.
+Each physical machine 
+each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
 represented as virtual disk image files in the host operating system.
@@
 means no fine-grained file system metadata can be used to determine the changed data. 
-Backup systems have been developed to use content fingerprints to identify duplicate
-content~\cite{venti02,Rhea2008}.  
-As discussed earlier, collocating a backup service on the existing
-cloud cluster avoids the extra cost to acquire a dedicated backup facility
-and reduces the network bandwidth consumption in transferring the
-raw data for backup. 
-Figure~\ref{fig:collocated} illustrates the cluster architecture where
-each physical machine runs a backup service and a distributed file system (DFS)~\cite{googlefs03,hdfs10} 
-serves a backup store  for the snapshots.
+This architecture does not use a seperate  backup facility for a lower cost and 
+reduces the network bandwidth consumption in transferring the raw data for backup. 
+A backup sevice runs on these commodity servers and stores deduplicated data  in  the storage in this cluster or in
+a seperate storage cluster.
+
+%runs a backup service and
+
+%As discussed earlier, collocating a backup service on the existing
+%cloud cluster avoids the extra cost to acquire a dedicated backup facility
 
@@
 
-Since it is expensive to compare a large number of chunk signatures for deduplication,
-several techniques have been proposed to speedup searching of duplicate
-fingerprints. For example, the data domain method ~\cite{bottleneck08} 
+Backup systems have been developed to use content fingerprints to identify duplicate
+content~\cite{venti02,Rhea2008}.  It is expensive to compare a large number of chunk fingerprints
+and several techniques have been proposed to speedup. For example, the data domain method ~\cite{bottleneck08} 
 uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
-accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
+accessed.  
+%An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
 The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
@@
 efficiency, and none of them have considered the impact
-of deduplication on fault tolerance in the cluster-based environment that we have considered
-in this paper.
-
-Our key design consideration is VM dependence minimization during deduplication and file system block management.
+of deduplication on fault tolerance in a cloud  cluster environment considered in this paper.
+Our consideration is discussed below.
+%VM dependence minimization during deduplication and file system block management.
 \begin{itemize}
@@
 Thus we need to consider a minimum association of FSBs to VMs in the packaging process.
+
+\item {\em Low resource usage in a nondedicated cloud cluster.}
+Since the cluster we consider is shared by many cloud services,
+low resource usage of deduplication is desired so that
+there is  a minimal impact to the other existing cloud services.
+The key resource for global comparison  is memory for storing the fingerprints. 
+We will consider the approximation techniques with reduced memory consumption. 
 \end{itemize}
-
-Another consideration is the computing cost of deduplication.
-Because of collocation of this snapshot service with other existing cloud services, 
-cloud providers will want the backup service to only consume small resources
-with a minimal impact to the existing cloud services.
-The key resource for signature comparison  is memory for storing the fingerprints. 
-We will consider the approximation techniques with reduced memory consumption along 
-with the fault isolation considerations discussed below.
 
@@
 We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, 
-and then present
-an architecture and implementation design with deletion support.
+and discuss snapshot deletion support, then present an implementation design.

### 2014-01-23 snapshot_system/paper_dedup.tex
add paper files

--- 2013-09-27 snapshot_system/fast14_deduplication.tex
@@
 
+Figure~\ref{fig:Datazipf} illustrates the distribution of chunk popularity based on a data trace from Alibaba with over 2500 VMs.
+The distribution is zipf like and popular chunks are dominating the large portion of data chunks.
+We denote $\sigma$ as the percentage of unique data chunks beloning to PDS and from the evaluation we find that
+$\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.
+
 %\item 
@@
 % Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
-\subsection{Impact on Deduplication Efficiency}
-Choosing the value $k$ for the most popular chunks affects the deduplication efficiency.
-We analyze this impact based on the characteristics  of the VM snapshot traces
-studied from  application datasets.
-A previous study shows that the popularity of data chunks after local deduplication follows 
-a Zipf-like distribution\cite{Breslau1999a} and its
-exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
-Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
-The parameters we will use in our analysis below are defined in
-Table~\ref{tab:symbol}.
-
-\begin{table}[htbp]
-\centering
-\tabcolsep=0.11cm
-\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
-\hline
-$k$ &  the number of top most popular chunks selected for deduplication\\ 
-\hline
-$c$ &  the total amount of data chunks in a cluster of VMs\\ 
-\hline
-$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
-\hline
-$f_i$ &  the frequency for the $i$th most popular fingerprint\\
-\hline
-$\delta$ &  the percentage of duplicates detected in local deduplication\\
-\hline
-$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belonging to  PDS\\
-\hline
-$p$ & the number of machines in the cluster\\
-\hline
-$V$ & the average number of VMs hosted on each machine\\
-\hline
-$E_c, E_o$ & deduplication efficiency of VC and VO \\
-%\hline
-%$D$ & the amount of unique data on each machine\\
-%\hline
-%$s$ & the average data chunk size. Our setting is  4K.\\
-\hline
-$s$ & the average number of chunks per FSB\\
-%\hline
-%$m$ & memory size on each node used by VC\\ 
-%\hline
-%$E$ & the size of an popular data index entry\\
-\hline
-$N_1$ & the average number  of non-PDS FSBs blocks in a VM for VC\\
-\hline
-$N_2$ & the average number  of PDS FSBs in a VM for VC\\
-\hline
-$N_o$ & the average number  of FSBs  in a VM for VO\\
-\hline
-A(r) & the availability of an FSB  with replication degree $r$\\
-\hline
-\end{tabular}
-\caption{Modeling  parameters}
-\label{tab:symbol}
-\end{table}
-
-%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
-%let $c$ be the total number of data chunks. 
-%$c_u$ be the total number of fingerprints 
-%in the global index after complete deduplication, and
-%$f_i$ be the frequency for the $i$th most popular fingerprint. 
-By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
-The total number of chunks in our backup storage which
-has local duplicates excluded is $c (1-\delta)$, this can be represented
-as the sum of each unique fingerprint times its frequency:
-%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
-\[
-f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
-\]
-Given $\alpha <1$, $f_1$ can be approximated with integration:
-%\begin{equation}
-\[
-f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
-\]
-%\end{equation}
-
-Thus putting the $k$ most popular fingerprints into PDS index can remove the following number of chunks during global 
-deduplication:
-\[
-f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
-f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}
-=c(1-\delta) \sigma^{1-\alpha}.
-\]
-
-Deduplication efficiency of the VC approach using top $k$ popular chunks
-is the percentage of duplicates that can be detected:  
-\begin{equation}
-\label{eq:dedupeff}
-%\begin{split}
-%e_k &= 
-E_c=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
-{c  - c_u }.\\
-%\end{split}
-\end{equation}
-
-% After the global deduplication, the number of remaining chunks is:
-% \[
-% c-E(c-c_u)
-% \]
-
-We store the PDS index using a distributed shared memory hash table such as Memcached
-and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
-As the number of physical machines ($p$) increases,
-the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
-a constant because each physical machine on average still hosts a fixed constant number of 
-VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
-remains constant.
-Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.
-
-\begin{figure}[htbp]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={PDS Coverage},
-            width=\linewidth,
-            height=0.6\linewidth,
-            cycle multi list={
-                mline\nextlist
-                [3 of]mmark*\nextlist
-            },
-            %cycle list name=mcolor,
-            xlabel={Total num. chunks stored (in billions)},
-            ylabel={PDS Coverage (\%)},
-            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
-            mark options=solid,
-            %legend pos=outer north east,
-            legend columns=2,
-            legend style={
-                at={(0.5,-0.30)},
-            anchor=north},
-            ]
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
-            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
-            \end{axis}
-    \end{tikzpicture}
-  \caption{Predicted vs. actual PDS coverage as data size increases.}
-  \label{fig:cds-coverage}
-\end{figure}
-Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
-chunks detected as duplicates in global deduplication due to PDS.
-We call this PDS coverage.
-Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
-0.65 and measured PDS coverage in our test dataset.
-$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
-While the predicted value remains flat, measured PDS coverage increases as more VMs are involved.
-This is because the actual $\alpha$ value increases with the data size.
-%Then  PDS coverage PDS increases as more VMs are involved.
-
-\subsection{ Impact on Fault Isolation}
-
-\begin{figure}
-    \centering
-    \subfigure[Sharing of file system blocks under VC]
-    {
-        \includegraphics[width=3in]{images/share_vc}
-        \label{fig:share_vc}
-    }
-    \\
-    \subfigure[Sharing of file system blocks under VO]
-    {
-        \includegraphics[width=3in]{images/share_vo}
-        \label{fig:share_vo}
-    }
-    \caption{Bipartite association of VMs and file system blocks under (a) VC and (b) VO. }
-    \label{fig:share}
-\end{figure}
-
-The replication degree of the backup storage 
-is $r$ for regular file system blocks and $r=3$ is a typical setting in distributed
-file systems~\cite{googlefs03,hdfs10}.
-Since $\sigma$ is small (e.g.  2\% in our experiments),  
-the impact of replication on storage increase is very small even 
-when choosing  $r_c/r$ ratio as 2 or 3.
-
-%In the VC approach, a special replication degree $r_c$ is used for PDS data where $r_c>r$. 
-%The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
-%$ k*r_c  + (c-E(c-c_u))*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
-%\[
-%\sigma \frac{r_c}{r} + \frac{c-e(c-c_u)}{c_u}.
-%\]
-%Since $\sigma$ is small (it is 2\% in our experiments),  
-%term $\sigma \frac{r_c}{r}$ is small in the above expression.  
-%Thus the impact on storage increase is very small even when we choose a large $r_c/r$ ratio. 
-%For example, $r_c/r=2$ or 3.
-
-Now we  assess  the impact of losing $d$ machines 
-to the VC and VO approaches.  
-A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
-We use an FSB rather than a deduplication
-data chunk as our unit of failure because the DFS keeps
-file system blocks as its base unit of storage.
-To compute the full availability of all snapshots of a VM, we derive
-the probability of losing a snapshot FSB of a VM by
-estimating the number of file system blocks per VM in each approach.
-As illustrated in Figure~\ref{fig:share},
-we build a bipartite graph representing the association from unique file system blocks
-to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
-if this block is used by the VM.
-
-For VC, each VM has an average number $N_1$ of non-PDS FSBs
-and  has  an average of  $N_2$ PDS FSBs. 
-Each non-PDS FSB is associated with one VM
- and  we denote that PDS FSBs are
-shared by an average of $V_c$ VMs. 
-%Let $s$ be the average number of chunks per file system block, 
-%$V$ be the average number of VMs hosted on each machine. 
-Then, 
-\[
-V pN_1 s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
-V pN_2 s  \approx c_u \sigma V_c.
-\]
-
-For VO, each VM has an average of $N_o$ FSBs
-and let $V_o$ be the average number of VMs shared by each FSB.
-\[
-V pN_o s  = (c- E_o(c-c_u) ) V_o.
-\]
-
-Since each FSB (with default size $64MB$) contains many chunks (on average 4KB),
-each FSB contains the hot low-level chunks shared by many VMs, and it also contains
-rare chunks which are not shared.  Since $c>> c_u$, from the above equations:
-\[
-\frac{N_1}{N_o} \approx  \frac{1-E_o}{(1-E_c) V_o}.
-\] 
-When $E_c$ is close to $E_o$,
-%as demonstrated in Section~\ref{sect:evaldedup},
-$N_1$ is much smaller than $N_o$. 
-%When there is a failure in FSBs with replication degree $r$
-%and there is no failure for PDS data with more replicas,   a VM in
-%the VC approach has a much lower chance to lose a snapshot than VO. 
-%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
-%our test dataset.
-%For VC, we only show
-%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
-%one VM.
-%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
-Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO
-and  $N_1$ is indeed  much smaller than $N_o$ in our tested dataset.  
-%In fact, $N_1 +N_2 < N_o$. 
-%This is likely because the PDS FSBs tightly pack data used by many VMs, 
-%which decreases the overall number of FSBs required to backup a VM.
-%Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
-%VMs sharing each file block on average in VO.
-
-%Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.
-
-\comments{
-\begin{figure}[htbp]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-                width=\linewidth,
-                height=0.6\linewidth,
-		%title={VO FSB links},
-		xlabel={Number of VMs},
-		ylabel={Avg. Num. VMs sharing FSB},
-                cycle list name=mline,
-                xmin=0,
-                ymin=0,
-                xmax=106,
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		legend pos=north west
-		]
-                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
-		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
-                \legend{VO, PDS in VC};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Measured average number of VMs sharing a 64MB FSB in VO and in VC.}
-  \label{fig:fsb-links}
-\end{figure}
-
-}
-
-\begin{figure}[htbp]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={VO VM links},
-                width=\linewidth,
-                height=0.6\linewidth,
-		xlabel={Number of VMs},
-		ylabel={Avg. Num. FSBs used by VM},
-                xmin=0,
-                ymin=0,
-                xmax=106,
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		%legend pos=north east,
-                legend style={
-                    at={(1,0.825)},
-                    anchor=north east
-                },
-                %legend columns=3
-		]
-                \addplot[blue,mark=none] table[x=VMs,y=N_O] {figures/vm_links_all.txt};
-                %\addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
-                \addplot[red,dashdotted] table[x=VMs,y=N_1] {figures/vm_links_all.txt};
-                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N_2] {figures/vm_links_all.txt};
-                \legend{$N_o$,
-                    %$N_1+N_2$,
-                    $N_1$,
-                    $N_2$};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Measured average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
-  \label{fig:vm-links}
-\end{figure}
-
-The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
- $N_2$ for VC and $N_o$ for VO.
-Given normal data replication degree $r$, PDS data replication degree $r_c$, 
-the availability of a file system block is the probability that  
-all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
-Namely, we define it as
-\[
-A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
-\]
-Then the availability of one VM's snapshot data under VO approach is the probability that
- all its FSBs are unaffected during the system failure:
-%\begin{equation}
-%\label{eq:VO}
-%(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
-\[
-A(r)^{N_o}. 
-\]
-%\end{equation}
-
-For VC, there are two cases for $d$ failed machines.
-\begin{itemize}
-\item
-When $r \le d<r_c$,  there is no PDS data loss and  
-the full snapshot availability of a VM in the VC approach is 
-%\begin{equation}
-%\label{eq:VC1}
-%(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
-\[
-A(r)^{N_1}.
-\]
-%\end{equation}
-Since $N_1$ is typically much smaller than $N_o$, 
-the VC approach has a higher availability of VM snapshots than VO in this case.
-%In the evaluation discussed in Section~\ref{sect:evaldedup}, 
-%We have considered a worst case scenario where
-%every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
-%Even with $N_2$ being much higher than $N_o$ (as discussed below),
-%the availability of VC snapshots is much higher than VO.
-
-\item
-When $r_c \leq d$, both non-PDS and PDS file system blocks in VC can have a loss.
-The full snapshot availability of  a VM in the VC approach is
-%\begin{equation}
-%\label{eq:VC2}
-% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
-% *
-% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
-\[
-A(r)^{N_1} * A(r_c)^{N_2}
-\]
-%\end{equation}
-%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
-\end{itemize} 
-%In the evaluation discussed in Section~\ref{sect:evaldedup},
-We have considered a worst case scenario that
-every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
-Even with that, the availability of VC snapshots is still much higher than VO and  
-there are two reasons for this:  1) $N_1$ is much smaller than $N_o$ as discussed previously.
-2)  $A(r) < A(r_c)$ because $r < r_c$.  
-Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
-%that the availability of an individual file system block
-different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.
-
-% $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
-
-\comments{
-\begin{figure}[htbp]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-                width=\linewidth,
-                height=0.6\linewidth,
-            %title={FSB Availability},
-            cycle list name=mline,
-            xlabel={Number of Machines Failed},
-            ylabel={Availability of Single FSB (\%)},
-            %extra y ticks={99.9}, %to add extra ticks
-            mark options=solid,
-            legend pos=south west,
-            %legend columns=2,
-            %legend style={
-            %    at={(0.5,-0.2)},
-            %anchor=north}
-            ]
-            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
-            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
-            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
-            \legend{$R=5$,$R=4$,$R=3$};
-            \end{axis}
-    \end{tikzpicture}
-    \caption{Availability of a file system block in a 100 machine cluster with different replication 
-and failure settings.THIS PLOT WILL BE REPLACED BY TABLE}
-  \label{fig:fsb-availability}
-\end{figure}
-}
-
-\begin{table}
-  \centering
-    \footnotesize
-    \tabcolsep=0.11cm
-    \comments{%table data is obsolete, now uses pgfplotstable
-        \begin{tabular}{|l|l|l|l|}
-        \hline
-        \multirow{2}{*}{Failures ($d$)}   & \multicolumn{3}{c|}{$A(r_c)\times 100\%$} \\
-                                    %\cline{2-4}
-                                    & $r_c=3$ & $r_c=6$ & $r_c=9$ \\
-        \hline
-        3 & 99.9994 & 100 & 100\\
-        5 & 99.9939 & 100 & 100\\
-        10 & 99.9258 & 99.9999 & 99.9999 \\
-        20 & 99.2950 & 99.9967 & 99.9999 \\
-        \hline
-    \end{tabular}
-    }
-    \pgfplotstabletypeset[
-        columns={NodesFailed,Availability3,Availability6,Availability9},
-        columns/NodesFailed/.style={
-            column name={\multirow{2}{*}{Failures ($d$)}}
-        },
-        columns/Availability3/.style={
-            column name={\multicolumn{3}{c|}{$A(r_c) \times 100\%$}\\&$r_c=3$},
-            fixed, precision=9
-        },
-        columns/Availability6/.style={
-            column name={$r_c=6$},
-            fixed, precision=9},
-        columns/Availability9/.style={
-            column name={$r_c=9$},
-            fixed, precision=9},
-        every head row/.style={
-            before row={\hline},
-            after row={\hline},
-        },
-        every last row/.style={after row=\hline},
-        column type/.add={}{|},
-        every first column/.style={column type/.add={|}{}},
-    ]{figures/fsb_availability.txt}
-    \caption{$A(r_c)$ as storage nodes fail in a 100 node cluster.}
-    \label{tab:fsb-availability}
-\end{table}

### 2014-01-23 snapshot_system/paper_del.tex
add paper files

--- 2013-09-27 snapshot_system/fast14_architecture.tex
@@
-\section{Architecture and Implementation Details}
-\label{sect:architecture}
-
-Our system runs on a cluster of Linux machines with Xen-based VMs and
-an open-source package for the distributed file system  called QFS~\cite{michael2013}. 
-%to %manage  the physical disk storage. 
-All data needed for the backup service including snapshot data and metadata
-%and snapshot data for backup purposes, 
-resides in this distributed file system. 
-One physical node hosts tens of VMs, each of which accesses its virtual machine disk image through the
-virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
-
-\subsection{ Components of a Cluster Node } 
-As depicted in Figure~\ref{fig:arch_vm}, 
-there are four key service components running on each cluster
-node  for supporting backup and deduplication: 
-1) a virtual block device driver, 2) a snapshot deduplication agent,
-3) a snapshot store client to store  and access snapshot data,
-and 4)  a PDS client to support PDS metadata access.
-
-We use the virtual device driver in Xen that employs a bitmap to track the changes 
-that have been made to the virtual disk (CBT).
-Every bit in the bitmap represents a fixed-sized (2MB) segment, indicating whether the segment
-has been modified since last backup. 
-Segments are further divided into variable-sized chunks (average 4KB) 
-using a content-based chunking algorithm~\cite{frame05}, 
-which brings the opportunity of fine-grained deduplication.
-When the VM issues a disk write, the dirty bit for the corresponding segment is set
-and this indicates such a segments needs to be checked during snapshot backup. 
-After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
-For data modification during backup, copy-on-write protection is set so that backup can continue to
-copy  a specific version while new changes are recorded.
-%copies a frozen version while the modification can still carry on.
-
-The representation of each snapshot has  a two-level index data structure.
-The snapshot meta data (called snapshot recipe) contains a list of segments, each of which contains segment
-metadata of its chunks (called segment recipe).
-In snapshot and segment recipes, 
-the data structures  include references to the actual data location to eliminate the need for additional indirection.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=2.75in]{images/socc_arch_cluster}
-    \caption{System architecture and data flow during snapshot backup}
-    \label{fig:arch_vm}
-\end{figure}
-
-\subsection{A VM-centric Snapshot Store for Backup Data}
-\label{sect:store}
-We build the snapshot storage on the top of a distributed file system.
-Following the VM-centric idea for the purpose of fault isolation,
-each VM has its own snapshot store, containing new data chunks which are considered
-to be non-duplicates.
-As shown in Figure~\ref{fig:as_arch}, we explain the data structure of the snapshot stores as follows.
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=2.75in]{images/sstore_arch}
-  \caption{Data structure of a VM snapshot store.}
-  \label{fig:as_arch}
-\end{figure}
-
-%\begin{itemize}
-%\item
-There is an independent store containing all PDS chunks shared among different VMs as
-a single file.
-%All PDS chunks are stored in one PDS file. 
-Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
-%There is an option to use a data structure similar to the non-PDS store. We opt
-%for the simpler format because
-Additional compression is not applied because 
-for the data sets we have tested, we only observed limited spatial locality 
-among popular data chunks. On average the number of consecutive PDS index hits is lower than 7.
-Thus it is not very effective to group a large number of chunks as a compression and data fetch unit. 
-For the same reason, we decide not to take the sampled index approach~\cite{Guo2011} 
-for detecting duplicates from PDS as limited spatial locality is not sufficient to enable
-effective prefetching for sampled indexing.
-
-PDS data are re-calculated periodically, but 
-the total data size is small.  When
-a new PDS data  set is computed, the in-memory PDS index is replaced, but 
-the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
-The old data are not removed because they can still be referenced by the existing snapshots. 
-A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months).
-
-%\end{itemize}
-
-For non PDS data, the snapshot store of a VM is  divided into a set of containers and 
-each container is approximately 1GB. 
-The reason for dividing the snapshot store into containers is to simplify the compaction process
-conducted periodically. As discussed later, data chunks are deleted from old snapshots
-and chunks without any reference from other snapshots can be removed by this compaction process.
-By limiting the size of a container, we can effectively control the length of each round of compaction.
-The compaction  routine can work on one container at a time and move the in-use data chunks to another container.
-
-Each non-PDS data container is further divided into a set of chunk data groups. Each chunk group is composed of
-a set of data chunks and is the basic unit in data access and retrieval. 
-In writing a chunk during backup, the system accumulates data chunks and stores the entire
-group as a unit after compression. This  compression can reduce data by several times  in our tested data.
-When accessing a particular chunk, its chunk group is retrieved from the storage
-and decompressed. Given the high spatial locality and usefulness of prefetching  in 
-snapshot chunk accessing~\cite{Guo2011,foundation08},
-retrieval of  a data chunk  group naturally works well with prefetching. 
-A  typical chunk group contains 1000 chunks in our experiment.
-% with an average size of 200-600 chunks.
-
-%\item
-Each non-PDS data container is represented by three files in the DFS:
-1) the container data file holds the actual content, 
-2) the container index file is responsible for translating a data reference
-into its location within a container, and 
-3) a chunk deletion log file records all the deletion requests within  the container.
-
-%\item
-A non-PDS data chunk reference stored in the index of snapshot recipes
-is composed of two parts: a container ID with 2 bytes and a local chunk ID with 6 bytes.
-Each container maintains a local  chunk counter and assigns the current number 
-as a chunk ID  when  a new chunk is added to this  container. 
-Since data chunks are always appended to a snapshot store during backup, 
-local chunk IDs are monotonically increasing.
-When a chunk is to be accessed, the segment recipe contains a reference pointing to  a data chunk
-in the PDS store or in a non-PDS VM snapshot  store. 
-Using  a container ID, the corresponding container index file of this VM is accessed and 
-the chunk group is identified using a simple chunk ID range search. Once the chunk group is loaded to memory, 
-its header contains the exact offset of the corresponding chunk ID and the content is then accessed from the memory buffer.
-
-%\item
-
-Three API calls are supported for data backup:
-%\begin{itemize}
-
-%\item
-\noindent\textbf{Append()}. 
-For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
-Note that PDS append may only be used during PDS recalculation.
-For non-PDS data, this call places a chunk into 
-the snapshot store and returns a reference to be stored in 
-the recipe metadata of a snapshot. 
-The write requests to append data chunks to a VM store are accumulated at the client side. 
-When the number of write requests reaches a fixed group size, the snapshot store client compresses
-the accumulated   chunk group, adds a chunk group index  to the beginning of the group, and then
-appends the header and data  to the corresponding VM file.
-A new container  index entry is also created for each chunk group and is written to the corresponding
-container index file.
-
-%\item
-\noindent\textbf{Get()}.
-The fetch operation for the PDS data chunk is straightforward since each reference contains 
-the file offset, and the size of a PDS chunk is available from a segment recipe.
-We also maintain a small data cache for the PDS data service to speedup common data fetching.
-
-To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client first loads the
-corresponding VM's container index file specified by the container ID, then searches the chunk
-groups  using their  chunk ID coverage.
-After that, it reads the identified chunk group from DFS, decompresses it, and seeks to the exact chunk data 
-specified by the chunk ID. 
-Finally, the client updates its internal chunk data cache with the newly loaded content to 
-anticipate future sequential reads.
-
-%\item
-\noindent\textbf{Delete()}.
-Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user and we discuss this in more details in next
-subsection.
-%(we will discuss the snapshot deletion in detail in the following subsection).
-When deletion requests are issued for a specific container,
-those requests are simply recorded into the  container's deletion log initially and thus  a lazy
-deletion strategy is exercised.
-Once local chunk IDs appear in
-the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
-This is ensured because we only dedup against the direct parent of a snapshot, so the deleted snapshot's blocks
-will only be used if they also exist in other snapshots.
-Periodically, the snapshot  store identifies those containers with an excessive
-number of deletion requests to  compact and  reclaim the corresponding disk space. 
-During compaction, the snapshot store creates a new container (with the same container ID) to replace the 
-existing one. This is done by sequentially scanning the old container, copying all the chunks that are not 
-found in the deletion log to the new container, and creating new chunk groups and indices. 
-Every local chunk ID however is directly copied rather than re-generated. This
-process leaves holes in the chunk ID values, but preserves the order and IDs of chunks.
-As a result, all data references stored 
-in recipes are permanent and stable, and the data reading process
-is as efficient as before. Maintaining the stability of chunk IDs also ensures that recipes do not
-depend directly on physical storage locations, which simplifies data migration.
-%\end{itemize}
-
-\subsection{ VM-centric Approximate Snapshot Deletion with Leak Repair}
+\section{ VM-centric Approximate Snapshot Deletion with Leak Repair}
 \label{sect:delete}

### 2014-01-23 snapshot_system/paper_intro.tex
add paper files

\section{Introduction}

One of popular architectures for building cloud services
is a converged architecture that leverages commodity servers with software clustered storage and network, without 
requiring network storage (e.g. SAN or NAS)~\cite{NutanixPaper}. 
Leading cloud platform companies such as Google, Amazon, Alibaba,
Microsoft Azure  have built a converged compute and storage infrastructure and used
a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
to glue a large number of commodity servers with local storage into a single cluster.
In such an environment,
%That  allows the use of scalable compute and storage, without incurring the costs and
%performance limitations associated with network storage.
each physical machine runs a number  of virtual machines as  instances of a guest operating system 
and their  virtual hard disks are represented as virtual disk image files in the host operating system.
Frequent  snapshot backup of virtual disk images  can increase  the service reliability
and deduplication of redundant content blocks~\cite{venti02,bottleneck08}
 is necessary to substantially reduce the storage demand.
%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
%automatically conducts  the backup of virtual disk images to all active users every day.
%The cost of supporting a large number of concurrent backup streams is high
%because of the huge storage demand and the use of deduplication

%Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
%can effectively identify and remove content duplicates among snapshots, 
%but such a solution can be expensive. There is also a large amount of 
%network traffic to transfer  data from the host machines to the backup facility
%before duplicates are removed.

A common technique for VM snapshot deduplication is    version-based detection that identifies file  blocks that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Another popular technique is to conduct global fingerprint  comparison to identify duplicates that exist
among all files~\cite{Guo2011,Dong2011,extreme_binning09}.
Because of highly repetitive content in snapshot backup,
most data chunks are shared by many virtual machines.  Failure of a few shared data chunks can have a 
broad effect and many snapshots of virtual machines could be affected.
The previous work in deduplication focuses on the efficiency and approximation of
fingerprint comparison, and has not addressed fault tolerance issues  together with deduplication.
Thus we also seek deduplication options that yield better fault isolation.

The key contribution of this work is to evaluate the fault tolerance  impact of popular data blocks shared by many
virtual machines, and   propose a VM-centric approach that localizes deduplication as much as possible 
and restrict global deduplication only to a limited set of most popular blocks.
Local deduplication also uses similarity-guided elimination to improve the deduplication coverage.
Since the file system block size is normally bigger than the average data chunk size used for deduplication,
we also package data chunks from the same VM into a file system block as much as possible to improve fault isolation.
Because data sharing is restricted, 
this VM-centric approach can also simplify the snapshot deletion process and reduce the overall resource usage, which
is suitable when the backup service with deduplication is collocated with other services running on a shared compute and storage
cluster.
We have evaluated this VM-centric approach using  a prototype system that runs a cluster of Linux machines with Xen and 
a standard distributed file system for the backup storage. 
%This approach localizes duplicate detection within each VM  
%By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
%this scheme can afford to allocate extra replicas of these shared chunks for better
%fault resilience while sustaining competitive deduplication efficiency.

%In addition, our VM-centric design allows garbage collection to be performed in a localized
%scope and we propose an approximate deletion scheme to reduce this cost further.
%Localization also brings the benefits of greater ability to exploit parallelism so
%backup operations can run simultaneously without a central  bottleneck.
%This VM-centric solution uses a small amount of  memory while delivering reasonable deduplication efficiency.

%Another issue considered is that
%that garbage collection after deletion of old snapshots also competes for computing resources. 
%Sharing of data chunks among by multiple VMs needs to be detected during
%garbage collection and such dependencies complicate deletion operations.

%************** Paper sections summary
%THIS NEEDS MODIFICATION
The rest of this paper is organized as follows.
Section~\ref{sect:background} reviews the background and discusses the  design options for snapshot backup 
with a VM-centric approach. 
Section~\ref{sect:deduplication}  analyzes the tradeoff and benefits of the VM-centric approach. 
Section~\ref{sect:architecture}  describes a system implementation that evaluates the proposed techniques.
%   the benefit of our approach for fault isolation. 
Section~\ref{sect:evaluation} is our experimental evaluation that compares with other approaches.
Section~\ref{sect:conclusion}  concludes this paper.

### 2014-01-23 thesis/Background.tex

@@
 \label{chap:back}
-At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
+% what is the problem
+Storage is the biggest challenge in virtualized cloud today.
+At a cloud cluster node, each instance of a guest operating 
+system runs on a virtual machine, accessing virtual hard disks 
 represented as virtual disk image files in the host operating system.
-For VM snapshot backup, file-level semantics are normally not provided.
+Backing up virtual machines is typically done through taking snapshots,
+which is a copy of the virtual machine's disk file at a given point in time.
+Performing such VM snapshot backup tasks for the entire cluster is a difficult task
+for several reasons: 
+\begin{itemize}
+\item \textbf{Huge storage demand.} Each VM contains from tens of GBs to multiple TBs of data,
+the snapshots size of an entire cloud often exceeds one PB, and they need to be backed up from daily to weekly.
+\item \textbf{Big network bandwidth cost.} Sending such amount of backup data requires
+a lot of network bandwidth and may impede normal application activity.
+\end{itemize}
+
+As a result, data deduplication is mandatory in order to reduce the storage and bandwidth
+costs of backup in cloud. But adding deduplication at cloud scale brings new
+challenges against previous developed techniques:
+\begin{itemize}
+\item \textbf{Limited resources.} Without dedicated hardware support in backup appliances, 
+VM backup and data deduplication in cloud must not race for CPU and memory resources with
+existing VM activities. Compare to dedicated backup appliances which are typically equipped with
+tens of GBs of memory and  multiple processors, backup service in the cloud are only allowed to use
+no more than a few hundred MBs of memory, and its CPU usage must always stay low.
+\item \textbf{Garbage collection for shared data.} Data management for deduplicated storage
+is complicated due to the need of tracking use of every shared data block. In order to reclaim
+disk space, the reference counts of
+shared data blocks will need to be updated whenever a snapshot is added or deleted.
+Managing reference counting for data blocks at KB level in a PB level storage is extreme difficult.
+\item \textbf{Little semantic information.} For VM snapshot backup, file-level semantics are normally not provided.
 Snapshot operations take place at the virtual device driver level, which
 means no fine-grained file system metadata can be used to determine the changed data. 
-Backup systems have been developed to use content fingerprints to identify duplicate
-content~\cite{venti02,Rhea2008}.
+\end{itemize}
 
-Many deduplication systems have been built for VM backup purposes. 
-In this chapter we will investigate several system design options at high-level.
-Section~\ref{back:coll} discusses the comparison of collocated solution vesus dedicated appliance.
-Section~\ref{back:trade} talks the tradeoffs in designing a deduplication storage system.
-Section~\ref{back:algo} introduces deduplication optimizations.
+% summary
+In sum, deduplication systems designed for legacy network storage that are attached to
+physical servers are too expensive and complex for virtual machines. 
+Both cloud users and providers are seeking low-cost solutions to effectively backup
+their data, otherwise they will be forced to backup less amount of data or less frequently,
+which in return will compromise the data safty and recovery time. For example, Electronic Arts, which deploys
+its data analytics platform in Amazon's AWS using several hundreds of VMs, 
+avoids using Amazon's built-in snapshot storage and chooses to backup hand-picked data manuallyv for cost reasons.
 
-\section{Architecture Options - Collocated vesus Dedicated} 
-\label{back:coll}
-Dedicated deduplication is a great way to augment existing tape based backup infrastructures due to its simple integration with existing backup applications.
-So if an end user is happy with their current backup application, a Dedicated approach may be very compelling as it does not necessitate a significant change of the backup infrastructure or the relearning of a new backup application.
+To that end, this dissertation proposes low-cost deduplication storage architecture that is
+collocated with other cloud services. We have learned a lot from 
+% The network storage architecture designed fifteen years ago for physical
+% servers 
+% Backup systems have been developed to use content fingerprints to identify duplicate
+% content~\cite{venti02,Rhea2008}.  
+% Without an enterprise-class
+% alternative, organizations are forced to use traditional solutions, which cannot
+% keep up with virtual machines that are dynamic, grow rapidly in number and
+% continue to demand new levels of performance and capacity.
+various deduplication systems built in the past for different backup scenarios. 
+In this chapter we will review the literature and discuss several system design options at high-level.
+Section~\ref{back:dedup} introduces the origin and applications of data deduplication.
+Section~\ref{back:optm} talks the optimization and tradeoffs in designing a deduplication storage system.
+Section~\ref{back:arch} discusses design options of backup storage architecture.
 
-One of the strongest use cases for Dedicated deduplication is protecting large Oracle or SQL database (in excess of 2TBs) environments.
-Since each of these applications can natively backup their data to a Dedicated appliance, from an integration standpoint, there is low/no barrier to entry to begin protecting these environments rapidly.
-Some deduplication appliance manufacturers even offer direct integration with database backup tools like Oracle RMAN.
-This helps drive out some of the inefficiencies in the data center as both backup administrators and DBAs can share a common pool of backup resources and achieve reductions where there may be an overlap in backup processes.
+\section{Deduplication}
+\label{back:dedup}
+Backup storage for VM snapshots in the cloud contains PBs of data from many VMs,
+the data redundancy in such a data set is very high\cite{Jayaram2011, agrawal07}.
+If we treat each snapshot as a single data object, the similarities between snapshots
+can not be utilized. Therefore we need better method to break files into data blocks.
+In the recent decad, data deduplication techniques are emerged to solve this data
+redundancy problem in backup systems.
+Most of data de-duplication methods can be categorized by their granularities:
 
-Another benefit to database target deduplication is a reduction in the consumption of primary storage resources.
-Many DBAs utilize a disk to disk to tape backup scheme to protect log files, table spaces etc.
-on primary storage that has no deduplication capability.
-Between periodic snapshots and direct dumps to disk, there tends to be an over consumption of expensive disk resources when protecting database environments.
-By migrating database backups to a deduplication appliance, scarce primary storage resources can be reclaimed for production applications.
-Whats more, the deduplication effect for database environments can range from a 5-1 to a 20-1 reduction in the physical disk or tape space required to perform normal backup operations - potentially generating a return on investment.
+\begin{itemize}
+\item \textbf{By file:} Old storage systems detect the duplicated files by compare their hash value
+or byte-by-byte. If two files are the same, then only one copy of data is saved, duplicated
+copies will be saved as metadata plus a pointer to the data. Thus this method can not detect any redundant data
+between different files.
 
-In short, Dedicated deduplication provides an easy entry point for customers interested in leveraging the efficiencies of deduplication to reduce backup windows, enhance data protection and improve overall operational efficiencies in the data center without making major changes to their environment.
+\item \textbf{By fixed size block:} Many popular file systems or tools can catch data redundancy at block level.
+It breaks files into many small fixed size blocks, and such block is the basic unit 
+for comparison. Typical applications based on this method are Windows shadow copy, ZFS\cite{zfs} snapshot, and Rsync\cite{rsync}. 
+While this method does better than simple file comparison, it can only be used in pair-wise comparison
+between different versions of
+the same logical data object, and any insertion/deletion will completely destroy the block similarity after the position
+where modifications are taken place.
 
-Collocated deduplication generally consists of backup application software with embedded deduplication at the client layer and some form of disk storage to serve as the repository for backup data.
-As the name implies, Collocated data deduplication takes place at the source or where data originates - at the server or application layer.
-Collocated deduplication offerings consist of placing a lightweight backup agent at the virtual or physical server and then only backing up the unique data segments that have changed since the prior backup job.
-The data segments are then sent over the LAN and/or WAN to a disk based storage grid for protection.
+\item \textbf{By variable size block:} This method breaks data into variable size blocks, and the block boundary
+is only decided by local data content, so it is also called content-based chunking. 
+Because of the chunk boundaries are only decided by local data content,
+this method is modification-resistant. It resolves the
+limitations in the previous two methods, and provides
+best de-duplication efficiency. 
+\end{itemize}
 
-The advantages of Collocated deduplication are rapid backup windows and a large reduction in the volume of LAN/WAN traffic generated during the backup window.
-Instead of pushing a full backup over the wire from a media server each night, unique deduplicated backup segments trickle between the application hosts and the backend deduplication storage grid.
-The data transfers are extremely efficient - equivalent to a meta-data handshake.
-Think speed of source side deduplication as an incremental (only more efficient) forever with the benefit of producing a full backup each night.
+Content-based chunking is first proposed by Manber\cite{similar94}.
+He uses Rabin's fingerprints\cite{rabin81, identify00} to sample
+data in order to find similar files. This technique computes
+fingerprints of all possible substrings of a certain
+length in a file and chooses a subset of these fingerprints
+based on their values,  e.g., if $(fingerprint(s)\ mod\ a) = b$, where
+$s$ is a substring,
+$a$ and $b$ are pre-defined values, then the position of substring $s$
+is considered as a breakpoint. 
+These breakpoints provide 
+modification-resistant boundaries that seperate the file
+into many small chunks. A sequence of hash values of such chunks
+is a compact representation of a file, that is then used to compare
+against other fingerprinted files.
 
-In general, Collocated deduplication is a great solution for environments with a low daily data change rate.
-Great use cases for Collocated deduplication solutions include data on the edge  remote offices and laptops in the field (great for C level execs) and file heavy environments (NAS, VMware).
-In the case of remote offices, often the investment in Collocated deduplication can be justified by the cost avoidance attained by eliminating the legacy remote office backup infrastructure  backup server hardware, software, tape libraries, tape media, courier expenses, etc.
+There are pathological cases in finding breakpoints, for example,
+a long extent of zeros may never contain a breakpoint. Thus, LBFS\cite{lbfs01}
+introduces min and max thresholds to the chunk size: when scanning the file
+sequentially for breakpoints, if the distance between current substring 
+and previous breakpoint is less than the minimum threshold, then it is skipped;
+if the distance reaches the maximum threshold, then a breakpoint
+is enforced. This method also reduces the computation because less substrings
+are checked. In order to increase the chance of finding a breakpoint between
+two thresholds, Kave\cite{frame05}
+proposes the two divisors idea, in addition to have a standard breaking condition,
+a weaker breaking condition is used to find backup breakpoints.
 
-In the VM snapshot backup case that we study, there is hardly any value for deploying dedicated backup
-solution because it's not affordable to VM users. Therefore we seek for low-cost collocated deduplication options
-to reduce the VM snapshot storage cost.
-Collocating a backup service on the existing
-cloud cluster avoids the extra cost to acquire a dedicated backup facility
-and reduces the network bandwidth consumption in transferring the
-raw data for backup.
+Policroniades\cite{poli04} gives out
+experimental results and present a comparative analysis
+to three de-duplication methods: First, the content based chunking
+is always the best strategy to discover redundancy in any data sets.
+Second, the fixed size block method can sometimes provides
+close results compare to content based chunking, and it has smalleris less
+computation intensive. Finally, if only for local file system,
+file compression is still the
+best strategy to save disk space, combining the content based chunking
+with compression does not justify the computation it costs.
 
-\section{Tradeoff in Design Goals}
-\label{back:trade}
+Data de-duplication is extensively used in saving bandwidth for data synchronization.
+The popular rsync\cite{rsync} protocol exploits the similarity of two directory trees
+using fixed size blocks de-duplication. 
+LBFS uses content-based chunking to improve the NFS protocol, 
+it avoids transmitting redundant chunks which already exist at the other side.
+But data du-duplication has its cost. Content-based chunking algorithm needs to
+scan the whole file looking for breakpoints, which is very slow (about 20MB/s using a single 2GHz core). 
+StoreGPU\cite{storegpu08}
+exploits the possibility of using GPU to chunk the file,
+their results are exciting. Another option is to use parallel
+chunking algorithm to improve the chunking speed,
+so that future's many-core chips will be helpful. 
+Meanwhile, stripping files is not a quite big issue in cloud storage scenario,
+because it is expected to be done at the client side before files are
+sent to the cloud.
+
+Since content-based chunking strips files into data blocks 
+and identify them by content hash,
+it is very natrual to build CAS system base on it.
+Jumbo Store and others\cite{jumbo07,efficient_dedup05,you06} encodes directory tree snapshots
+into a graph whose nodes are data blocks and edges
+are hash value pointers.
+Directory metadata, file metadata and data chunk are all
+represented in the form of variable-size data blocks that indetified by content hash.
+A object which encapsulate metadata also has a list of hash indentifiers 
+that point to other blocks it contains.
+Such a de-duplication storage system has some great advantages 
+in terms of space efficiency, file transmission efficiency (through a LBFS-like protocol), 
+and data integrity checking (by verifying the hash).
+
+Cumulus\cite{cumulus09} is a client side backup tool to store 
+file system snapshots in exist cloud storage such as S3.
+To create a snapshot, Cumulus uses content-based chunking to break files into data blocks,
+then compare (by hash) them to the list of stored blocks (in local logs).
+New blocks will be packed and compressed into a segment file, and sent to server.
+The advantage of Cumulus is portability, because it makes 
+the de-duplication backup totoally opaque to the server.
+However, without the de-duplication support from protocol and server side, 
+it's hard to have efficent storage management, and from server's perspective,
+snapshots from many users still contain much redundant data.
+
+\section{Optimizations and Tradeoffs}
+\label{back:optm}
+Many previous studies on data deduplication focus on the disk bottleneck problem,
+which refers to the key performance challenge in finding duplicate blocks. 
+Let's consider a single machine in cluster which hosts many VMs and has 10 TB of virtual disks in total,
+if it needs to be backed up daily, then the performance target would be 115 MB/sec on each machine.
+Given a block size of 4 KB, a deduplication system must process approximately 28,900 blocks per second.
+An in-memory index of all block fingerprints could easily achieve this performance, but the size of the index would limit system size and increase system cost. 
+If we use 20 bytes as block fingerprint size, then supporting 10 TB worth of unique blocks, would require 50 GB just to store the fingerprints.
+An alternative approach is to maintain an on-disk index of block fingerprints and use a cache to accelerate block index accesses.
+Unfortunately, a traditional cache would not be effective for this workload.
+Since fingerprint values are random, there is no spatial locality in the block index accesses.
+With low cache hit ratios, most index lookups require disk operations.
+If each index lookup requires a disk access which may take 10 msec and 8 disks are used for index lookups in parallel, the write throughput will be about 6.4MB/sec, which is far from the throughput goal of deduplicating at 115 MB/sec for our cloud backup scenario, and don't forget that this goal
+is conservative since VM users generally want the backup task to finish in tens of minutes without affecting their normal
+application activities.
+
+Massive efforts have been put into the optimization of searching duplicate
+fingerprints in large index. They can be summarized into three categories:
+
+\begin{itemize}
+\item \textbf{Reduce disk index access.} The data domain method ~\cite{bottleneck08} 
+uses an in-memory Bloom filter and a locality-based prefetching cache to intercept fingerprint lookup which may
+access the on-disk index. Bloom filter\cite{Bonomi2006} helps to tell if a fingerprint is new, and prefetching cache
+helps to quickly find consequential duplicates. Improvements to this work with parallelization can be found
+ in ~\cite{MAD210,DEBAR,nath08}.
+\item \textbf{Index sampling.} A sampled index can be 
+put into memory\cite{sparseindex09} or NAND flash\cite{Guo2011} to accelerate fingerprint lookup. 
+This sampled index is 100 times or more smaller than the full index so that 
+they can be accessed quickly and easily.
+Once there's a hit in the sampled index, system loads the fingerprints that are next to the hitted one on disk,
+so that it can efficiently catches duplicates based on spatial locality.
+\item \textbf{Similarity based sharding.} Several similarity based techniques\cite{shingling97} such like 
+Extremely Binning\cite{extreme_binning09, Dong2011, Srinivasan2012, chord01} group big files by similarity metrics
+such that similar files are likely to fall into the same group. Then block level deduplication is performed
+within the group. While all the group indices are still on the disk, it can deduplicate an entire file
+by only load one group index into memory. This approach can easily scale-out, but it misses small amount of duplicates 
+because the similarity algorithm does not guarantee always mapping a file to the most similar group.
+\end{itemize}
+
+Most of approaches discussed above focus on optimization of inline deduplication
+performance by sacraficing a small percent of deduplication efficiency.
+In our cloud backup scenario, we must always satisfy the low resource usage constraints while 
+providing sustainable good throughput. As a result, we consider to sacrifice other performance metrics 
+to achieve our design goals, which we descibe as below:
+% In addition, none of them have considered the impact
+% of deduplication on fault tolerance in the cluster-based environment that we have considered
+% in this dissertation.
+
+% \section{Tradeoff in Design Goals}
+% \label{back:trade}
 Given we are designing scalable low-cost collocated deduplication solutions,
@@
 
-\section{Deduplication Optimizations}
-\label{back:algo}
-Since it is expensive to compare a large number of chunk signatures for deduplication,
-several techniques have been proposed to speedup searching of duplicate
-fingerprints. For example, the data domain method ~\cite{bottleneck08} 
-uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
-accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
-to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
-Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
-and a parallel batch solution for cluster-based deduplication is 
-studied in ~\cite{wei2013}. 
-All of the above approaches have focused on optimization of deduplication
-efficiency, and none of them have considered the impact
-of deduplication on fault tolerance in the cluster-based environment that we have considered
-in this dissertation.
+\section{Architecture Options} 
+\label{back:arch}
+The way that backup storage architecture envolves has been following the pace of
+primary storage, so we will give a glimpse on primary storage's evolution first.
+Organizations start with ﻿building ﻿their ﻿virtualization ﻿infrastructure ﻿using ﻿the﻿
+traditional ﻿servers-connected-to-storage-over-a-network ﻿architecture, ﻿which﻿
+can’t ﻿adapt ﻿to ﻿the ﻿ever-changing ﻿demands ﻿of ﻿virtualization. ﻿In ﻿addition ﻿to ﻿slow﻿
+performance,﻿ network ﻿storage ﻿has ﻿become﻿ the﻿ single﻿ biggest﻿ source ﻿of ﻿cost ﻿and﻿
+complexity ﻿in ﻿virtualized ﻿environments.﻿ The ﻿network﻿ storage-based ﻿architecture﻿
+worked﻿ well ﻿for ﻿physical﻿ servers ﻿that ﻿served﻿ relatively﻿ static ﻿workloads.﻿
+Virtualization,﻿ and﻿ now﻿ Cloud﻿ Computing,﻿ has﻿ made﻿ data﻿ centers﻿ extremely﻿
+dynamic\cite{berkeleycloud09};﻿ virtual﻿ machines﻿ are﻿ created﻿ on﻿ the﻿ fly,﻿ move﻿ from﻿ server﻿ to﻿ server﻿ and﻿﻿
+depend﻿ heavily﻿ on﻿ shared﻿ resources.﻿ These ﻿characteristics ﻿make ﻿the ﻿management﻿
+of ﻿virtual ﻿machines ﻿and ﻿their﻿ underlying ﻿physical﻿ infrastructure ﻿extremely﻿
+complex: Data ﻿volumes ﻿are﻿ growing﻿ at ﻿a ﻿rapid ﻿pace﻿ in﻿ the ﻿data ﻿center, ﻿thanks﻿ to ﻿the ﻿ease﻿
+of﻿ creating ﻿new﻿ VMs.﻿ In ﻿the﻿ enterprise,﻿ new﻿ initiatives ﻿like ﻿desktop﻿ virtualization﻿
+contribute﻿ to ﻿this﻿ trend.﻿ Service﻿ providers﻿ deal﻿ with﻿ an﻿ even﻿ larger﻿ number﻿ of﻿
+VMs﻿ as﻿ they﻿ build﻿ data﻿ centers﻿ to﻿ serve﻿ customers﻿ who﻿ can’t﻿ afford﻿ the﻿ cost﻿
+and﻿ management﻿ overhead﻿ that﻿ virtualization ﻿requires. ﻿This﻿ growing ﻿pool ﻿of﻿
+VMs﻿ is ﻿exerting ﻿tremendous ﻿cost, ﻿performance﻿ and ﻿manageability ﻿pressure﻿ on﻿
+the ﻿traditional ﻿architecture ﻿that ﻿connects﻿ compute﻿ to ﻿storage﻿ over ﻿a ﻿multi-hop﻿
+network.﻿
+
+Google﻿\cite{googlefs03} and﻿ other﻿ leading ﻿cloud-generation﻿ companies ﻿such﻿ as ﻿Amazon,﻿ Yahoo﻿
+and﻿ Microsoft﻿(Azure)﻿\cite{azure} realized ﻿that ﻿a ﻿network-storage﻿ based﻿ approach﻿ would﻿
+not ﻿work﻿ for﻿ their﻿ data ﻿centers.﻿ They﻿ built﻿ software﻿ technology﻿ (such ﻿as ﻿Google﻿
+File ﻿System)﻿ that﻿ could ﻿glue﻿ a﻿ large﻿ number﻿ of ﻿commodity﻿ servers﻿ with﻿ local﻿
+storage ﻿into ﻿a ﻿single﻿ cluster.﻿ This﻿ approach﻿ allowed﻿ Google﻿ to ﻿build ﻿a ﻿converged﻿
+compute﻿ and﻿ storage ﻿infrastructure﻿ that﻿ used﻿ commodity﻿ servers﻿ with﻿ local﻿
+storage﻿ as ﻿its ﻿building ﻿block\cite{deconstructing05}.﻿ Google﻿ File﻿ System﻿ runs﻿ across﻿ a ﻿cluster ﻿of ﻿servers﻿
+and﻿ creates ﻿a ﻿single ﻿pool﻿ of﻿ local﻿ storage﻿ that﻿ can ﻿be﻿ seamlessly﻿ accessed﻿ by﻿
+applications﻿ running﻿ on ﻿any ﻿server﻿ in﻿ the ﻿cluster.﻿ It ﻿provides﻿ high﻿ availability﻿
+to ﻿applications ﻿by ﻿masking﻿ failures ﻿of ﻿hard﻿ disks ﻿and ﻿even﻿ complete ﻿servers.﻿
+Google﻿ File﻿ System ﻿allowed ﻿Google﻿ to﻿ build﻿ data﻿ centers ﻿with﻿ massively ﻿scalable﻿
+compute﻿ and﻿ storage,﻿ without ﻿incurring ﻿the ﻿costs﻿ and﻿ performance﻿ limitations﻿
+associated ﻿with﻿ network ﻿storage.﻿
+
+In cooperate with the changes of primary storage in cloud, backup storage architecture
+has to envolve as well. A dedicated backup storage appliance sits aside the cloud does provide some good properties,
+such like it deduplicates all the backup data together so it provides good deduplication efficiency,
+ and because it uses dedicated hardware to fingerprint lookups, it leaves very small resource footprint on the client side.
+However, its weakness on high-cost and bandwidth demand make it unsuitable for large scale cloud
+backup scenario. This is especially true for public clouds whose users are very sensitive
+to the storage pricing.
+
+To make VM snapshot backup efficient and economy for large scale cloud, 
+we must seek for a low-cost architecture that can be collocated with existing
+storage and other cloud services. To avoid excessive bandwidth usage on transmitting 
+backup data, it must process fingerprint lookups at the client side and provides
+good deduplication efficiency. In addition, the resource footprint of deduplication must stay
+very low in order to minimize the influence to normal VM activities. Finally, it must provides
+efficient mechanism to manage the complicated data sharing relationship on deduplicated data.
+
+% Dedicated deduplication is a great way to augment existing tape based backup infrastructures due to its simple integration with existing backup applications.
+So if an end user is happy with their current backup application, a Dedicated approach may be very compelling as it does not necessitate a significant change of the backup infrastructure or the relearning of a new backup application.
+
+% One of the strongest use cases for Dedicated deduplication is protecting large Oracle or SQL database (in excess of 2TBs) environments.
+Since each of these applications can natively backup their data to a Dedicated appliance, from an integration standpoint, there is low/no barrier to entry to begin protecting these environments rapidly.
+Some deduplication appliance manufacturers even offer direct integration with database backup tools like Oracle RMAN.
+This helps drive out some of the inefficiencies in the data center as both backup administrators and DBAs can share a common pool of backup resources and achieve reductions where there may be an overlap in backup processes.
+
+% Another benefit to database target deduplication is a reduction in the consumption of primary storage resources.
+Many DBAs utilize a disk to disk to tape backup scheme to protect log files, table spaces etc.
+on primary storage that has no deduplication capability.
+Between periodic snapshots and direct dumps to disk, there tends to be an over consumption of expensive disk resources when protecting database environments.
+By migrating database backups to a deduplication appliance, scarce primary storage resources can be reclaimed for production applications.
+Whats more, the deduplication effect for database environments can range from a 5-1 to a 20-1 reduction in the physical disk or tape space required to perform normal backup operations - potentially generating a return on investment.
+
+% In short, Dedicated deduplication provides an easy entry point for customers interested in leveraging the efficiencies of deduplication to reduce backup windows, enhance data protection and improve overall operational efficiencies in the data center without making major changes to their environment.
+
+% Collocated deduplication generally consists of backup application software with embedded deduplication at the client layer and some form of disk storage to serve as the repository for backup data.
+As the name implies, Collocated data deduplication takes place at the source or where data originates - at the server or application layer.
+Collocated deduplication offerings consist of placing a lightweight backup agent at the virtual or physical server and then only backing up the unique data segments that have changed since the prior backup job.
+The data segments are then sent over the LAN and/or WAN to a disk based storage grid for protection.
+
+% The advantages of Collocated deduplication are rapid backup windows and a large reduction in the volume of LAN/WAN traffic generated during the backup window.
+Instead of pushing a full backup over the wire from a media server each night, unique deduplicated backup segments trickle between the application hosts and the backend deduplication storage grid.
+The data transfers are extremely efficient - equivalent to a meta-data handshake.
+Think speed of source side deduplication as an incremental (only more efficient) forever with the benefit of producing a full backup each night.
+
+% In general, Collocated deduplication is a great solution for environments with a low daily data change rate.
+Great use cases for Collocated deduplication solutions include data on the edge  remote offices and laptops in the field (great for C level execs) and file heavy environments (NAS, VMware).
+In the case of remote offices, often the investment in Collocated deduplication can be justified by the cost avoidance attained by eliminating the legacy remote office backup infrastructure  backup server hardware, software, tape libraries, tape media, courier expenses, etc.
+
+% In the VM snapshot backup case that we study, there is hardly any value for deploying dedicated backup
+% solution because it's not affordable to VM users. Therefore we seek for low-cost collocated deduplication options
+% to reduce the VM snapshot storage cost.
+% Collocating a backup service on the existing
+% cloud cluster avoids the extra cost to acquire a dedicated backup facility
+% and reduces the network bandwidth consumption in transferring the
+% raw data for backup.

### 2014-01-23 thesis/DataManagement.tex

@@
 \label{data:intro}
-In this chapter, we discuss a low-cost architecture option that collocates
+In this chapter, we discuss a low-cost storage and management architecture that collocates
 a backup service with other cloud services and uses a minimum amount of resources. 
@@
 
-\section{Background and Design Considerations}
+\section{Design Considerations}
 \label{data:options}
@@
 
-Three API calls are supported for data backup:
+Our snapshot store supports three API calls for block data operations:
 %\begin{itemize}
@@
 We also maintain a small data cache for the PDS data service to speedup common data fetching.
-
 To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client first loads the
@@
 
+Additional APIs such as \textbf{Scan()}, \textbf{Compact()}, \textbf{Create()} and \textit{Remove()} are provided for 
+higher level operations. Scan() is used by the map-reduce procedure to collect the most popular blocks among all snapshot stores.
+Compact() is called when the system determines a container has too much unclaimed space and needs to be reclaimed.
+Create() and Remove() initialize and delete a container respectively.
+
 \section{Analysis of VM-centric Approach}
@@
 A previous study shows that the popularity of data chunks after local deduplication follows 
-a Zipf-like distribution\cite{Breslau1999a} and its
+a Zipf-like distribution\cite{Breslau1999a, Baek2011} and its
 exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
@@
 uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
-accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
+accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR,arrow08}.
 The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
@@
 VM snapshots can be  backed up  incrementally by identifying data segments that have
-changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
+changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011,cvfs03}.
 Such a scheme  is  VM-centric since deduplication is localized. 

### 2014-01-23 thesis/InlineDedup.tex

@@
 Our synchronous batched deduplication introduced in chapter~\ref{chap:offline} does not apply 
-to such situation which requests fast inline deduplication.
+to such situation which requires fast inline deduplication.
 Based on the requirement that we are now pursuing low-cost solution with short job turnaround time,
@@
 At Aliyun, it is required that while CPU and disk usage should be small or modest during backup time,
-the memory footprint of snapshot service should not exceed 500MB at each node.
+the memory footprint of snapshot service should not exceed 500 MB at each node.
 
@@
 We start with the changed block tracking approach in a coarse grain segment level.
-In our implementation with Xen on an Alibaba platform, the segment size is 2MB
+In our implementation with Xen on an Alibaba platform, the segment size is 2 MB
 and the device driver is extended to support tracking changed segments using a dirty bitmap. 
@@
 A dirty bit array is used to indicate which segments have been modified or not. 
-Each page (segment) size in our implementation uses 2MB, which contains a large number of content blocks.
+Each page (segment) size in our implementation uses 2 MB, which contains a large number of content blocks.
 %Enforcing a boundary at every 2MB will 
@@
 parent snapshot's segment.
-This scheme processes one segment at time and each segment of 2MB contains about 
+This scheme processes one segment at time and each segment of 2 MB contains about 
 500 content blocks on average given 4KB is the average block size.
@@
 can cover about 38\% of data blocks. Consider we allow maximum 25 VMs per machine, each VM has
-about 30GB of user-related data, having 10 snapshots in its snapshot store and the data change ratio during
-each backup is 10\%, this translates to 15GB PDS data per machine. 
+about 30 GB of user-related data, having 10 snapshots in its snapshot store and the data change ratio during
+each backup is 10\%, this translates to 15 GB PDS data per machine. 
 Consider each PDS hash index entry cost about 40 bytes and the average block size is 4KB, this leads to
 a 1:100 ratio so the 
-memory cost by PDS hash index is about 150MB per machine.
+memory cost by PDS hash index is about 150 MB per machine.
 On the other hand, the PDS from OS-related data is only relevant to the number of OS releases.
-Our experiment on 7 major OS releases shows that about 100GB of data is never modified, and we expect
-it won't grow over 200GB in the near future. So it would cost the entire cluster 2GB of memory to
-store its hash index, or 20MB per machine on a 100 node cluster. On average each OS disk has about 10GB
+Our experiment on 7 major OS releases shows that about 100 GB of data is never modified, and we expect
+it won't grow over 200 GB in the near future. So it would cost the entire cluster 2 GB of memory to
+store its hash index, or 20 MB per machine on a 100 node cluster. On average each OS disk has about 10 GB
 of data that can be completely eliminated in this way.
-Thus in total the PDS index size per node takes less than 170MB in a large cluster bigger than 100 nodes, 
+Thus in total the PDS index size per node takes less than 170 MB in a large cluster bigger than 100 nodes, 
 covering over 47\% of blocks in OS and data disks after inner-VM deduplication.
@@
 %the CPU usage is very small during the experiments. 
-Based on the data studied,  each VM has about  40GB of storage  data usage on average,
+Based on the data studied,  each VM has about  40 GB of storage  data usage on average,
 OS disk and data disk each takes about 50\% of storage space.
 The backup of VM snapshots is completed within two hours every day,
-and that translates to a backup throughput of 139GB per second, or 500TB per hour.
+and that translates to a backup throughput of 139 GB per second, or 500TB per hour.
 For each VM, the system keeps 10 automatically-backed snapshots in the storage while
@@
 it compose of 35 VMs from 7 popular OSes: 
-Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
+Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, Win2003 64 bit and Win2008 64 bit. For each OS, 
 5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
@@
 Thus with about 1\% of blocks on data disks, PDS can cover about 38\% of total data blocks
-appeared in all data snapshots. The corresponding PDS index uses no more than 150MB memory per machine,
+appeared in all data snapshots. The corresponding PDS index uses no more than 150 MB memory per machine,
 which can be easily co-located with other cloud services.
@@
 Based on the above analysis, we have selected a small set of most popular
-OS blocks, which is about 100GB OS data and its corresponding PDS index takes about 1GB memory space in total.
+OS blocks, which is about 100 GB OS data and its corresponding PDS index takes about 1 GB memory space in total.
 They can cover sufficiently over 70\% of OS-related data.
@@
 full deduplication space reduction. 
-With a 100GB PDS data (namely 1GB PDS index) can still  accomplish about 75\% 
+With a 100 GB PDS data (namely 1 GB PDS index) can still  accomplish about 75\% 
 of what perfect deduplication can do.
@@
 a related filtering technique for integrating deduplication in Linux  file system and the memory
-consumed is up to 2GB for a single machine. That is still too big in our context discussed below. 
+consumed is up to 2 GB for a single machine. That is still too big in our context discussed below. 
 %Lillibridge et al.~\cite{sparseindex09} break list of chunks 

### 2014-01-23 thesis/Introduction.tex

@@
 because of the huge storage demand. 
-If such VM snapshot data are plainly backuped without any duplicate detection, the storage waste would be 
-extreme. For example, a fresh Windows server 2008 installation costs 25 GB on the virtual  disk,
-and they are almost certianly duplicated with other Windows VM instances.
+If such VM snapshot data are plainly backed up without any duplicate reduction, storage waste would be 
+extreme high. For example, a fresh Windows server 2008 installation costs 25 GB on the virtual disk,
+and they are almost certianly duplicated with other Windows VM instances\cite{common07, pedal96}.
 Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
@@
 Unlike the previous work dealing with general file-level
-backup and deduplication, our problem is focused on virtual
-disk image backup. Although we treat each virtual disk as a
+backup and deduplication inside a centralized storage appliance, our problem is focused on virtual
+disk image backup in a cluster of machines. Although we treat each virtual disk as a
 file logically, its size is very large. On the other hand, we need
@@
 \textit{It  is  possible  to  build  an efficient, scalable, and fault tolerant backup storage
-supporting highly accurate deduplication and easy management of deduplicated data
-with sustainable high throughput.}
+supporting highly accurate deduplication with sustainable high throughput
+and easy management on deduplicated data.}
 

### 2014-01-24 snapshot_system/paper_analysis.tex
added VO+ approach to explain why we can't rely on DFS features for extra replication

@@
 A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
-We use an FSB rather than a deduplication
-data chunk as our unit of failure because the DFS keeps
-file system blocks as its base unit of storage.
+%We use an FSB rather than a deduplication
+%data chunk as our unit of failure because the DFS keeps
+%file system blocks as its base unit of storage.
 To compute the full availability of all snapshots of a VM, we derive
@@
 estimating the number of file system blocks per VM in each approach.
-As illustrated in Figure~\ref{fig:share},
-we build a bipartite graph representing the association from unique file system blocks
-to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
-if this block is used by the VM.
+%As illustrated in Figure~\ref{fig:share},
+%we build a bipartite graph representing the association from unique file system blocks
+%to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
+%if this block is used by the VM.
+
+As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
+association from unique file system blocks to their corresponding VMs in the VC
+and VO approaches. We use an FSB rather than data chunk as our unit of failure
+because the DFS keeps file system blocks as its base unit of storage, and in
+the case of 64MB FSBs and 4KB chunks, there are 16K chunks per block. In VC
+we assign extra replication to the PDS blocks, while in VO the replication
+degree is fixed.
+
+We could consider a third approach (call it VO+), adopting the VO approach, and
+then relying on filesystem features to provide extra replication to popular
+blocks, without the extra complexity of separating popular and non-popular
+data. The problem with this VO+ approach is that without separating the
+popular chunks from the less-popular, the popular chunks are dispersed across
+all of the filesystem blocks in the storage system. Because the popular blocks
+are dispersed, there are very few popular FSBs. The end result is that we
+either have to add extra replication on unpopular chunks to ensure the popular
+chunks have sufficient replication, or we have to accept a reduced replication
+factor on popular chunks. This explains why we must separate the PDS and
+non-PDS data in our system to acheive the desired $r_c/r$ ratio (though both
+can be stored on the same DFS).
 

### 2014-01-24 snapshot_system/paper_abs.tex
revised

@@
 Data deduplication has been widely used for cloud data backup
-because of excessive redundant content blocks. Common techniques use dirty bits to detect
-the version  change and  perform global fingerprint comparison to remove duplicates
+because of excessive redundant content blocks. Common techniques 
+%use dirty bits to detect
+%the version  change and  
+perform fingerprint comparison to remove duplicates
 across virtual machines. However, letting a duplicate data block be shared
@@
 This paper proposes a VM-centric backup service on a converged  storage cluster architecture
-and  strikes a balance for better fault isolation with competitive  deduplication efficiency.
+and  strikes a tradeoff for better fault isolation with competitive  deduplication efficiency.
 It localizes deduplication as much as possible within each 
 virtual machine, guided by similarity
-search and associates  underlying file blocks with one VM for most cases.
-It restricts global deduplication to popular chunks with extra replication support.
-This VM-centric scheme also has  an advantage of   using less  computing resources for fingerprint comparison and simplifies snapshot deletion, suitable for a collocated backup service 
-on a non-dedicated cluster architecture.
+search, and it restricts global deduplication under popular chunks with extra replication support.
+It associates  underlying file blocks with one VM for most cases
+and proposes an approximate method for fast and simplified snapshot deletion.
+This VM-centric scheme also has  an advantage of   using less  computing resources, suitable for a collocated 
+backup service on a non-dedicated cluster architecture.
 This  paper  describes an evaluation of this scheme to assess  its deduplication 

### 2014-01-24 snapshot_system/paper_analysis.tex
revised

@@
 
-We analyze the impact of replication degree for PDS and non-PDS data items.
-The parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
-The replication degree of the backup storage 
-is $r$ for regular file system blocks and $r=3$ is a typical setting in distributed
-file systems~\cite{googlefs03,hdfs10}.
-Since $\sigma$ is small (e.g.  2\% in our experiments),  
-the impact of replication on storage increase is very small even 
-when choosing  $r_c/r$ ratio as 2 or 3.
+We analyze the impact of the above VM centric design on fault isolation and compare it
+with a VM oblivious design.
+Let $r$ be the replication degree of standard file blocks in the underlying backup storage. 
+$r=3$ is a typical setting in distributed file systems~\cite{googlefs03,hdfs10}.
+Let $r_c$ be the replication degree of file blocks for PDS. 
+Additional parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
+%The replication degree of the backup storage 
+%is $r$ for regular file system blocks and 
+%Since $\sigma$ is small (e.g.  2\% in our experiments),  
+%the impact of replication on storage increase is very small even 
+%when choosing  $r_c/r$ ratio as 2 or 3.
 
@@
 Now we  assess  the impact of losing $d$ machines 
-to the VC and VO approaches.  
+to the VM centric and oblivious approaches.  
 A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
@@
 %file system blocks as its base unit of storage.
-To compute the full availability of all snapshots of a VM, we derive
-the probability of losing a snapshot FSB of a VM by
-estimating the number of file system blocks per VM in each approach.
+To compute the full availability of all snapshots of a VM, we estimate
+the number of file system blocks per VM and the probability of losing a snapshot file system 
+block of a VM in each approach as follows.
 %As illustrated in Figure~\ref{fig:share},
@@
 As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
-association from unique file system blocks to their corresponding VMs in the VC
-and VO approaches. We use an FSB rather than data chunk as our unit of failure
-because the DFS keeps file system blocks as its base unit of storage, and in
-the case of 64MB FSBs and 4KB chunks, there are 16K chunks per block. In VC
-we assign extra replication to the PDS blocks, while in VO the replication
+association from unique file system blocks to their corresponding VMs in two 
+approaches. We use a file system block rather than data chunk as our unit of failure
+because the underlying file system keeps file system blocks as its base unit of storage, and in
+the case of 64MB file system blocks  and 4KB chunks, there are 16K chunks per file block. For VM centric,
+we assign extra replication to the PDS blocks, while for VM oblivious, the replication
 degree is fixed.
 
+\comments{
+%Moved up in the strategy subsection
 We could consider a third approach (call it VO+), adopting the VO approach, and
@@
 factor on popular chunks. This explains why we must separate the PDS and
-non-PDS data in our system to acheive the desired $r_c/r$ ratio (though both
+non-PDS data in our system to achieve the desired $r_c/r$ ratio (though both
 can be stored on the same DFS).
-
+}
 For VC, each VM has an average number $N_1$ of non-PDS FSBs

### 2014-01-24 snapshot_system/paper_background.tex
revised

@@
 each commodity server hosts a number of virtual machines and storage of these servers
-is clustered using a distributed file system (DFS)~\cite{googlefs03,hdfs10}.
+is clustered using a distributed file system~\cite{googlefs03,hdfs10}.
 Each physical machine 
@@
 means no fine-grained file system metadata can be used to determine the changed data. 
-This architecture does not use a seperate  backup facility for a lower cost and 
-reduces the network bandwidth consumption in transferring the raw data for backup. 
-A backup sevice runs on these commodity servers and stores deduplicated data  in  the storage in this cluster or in
+%This architecture does not use a seperate  backup facility for a lower cost and 
+%reduces the network bandwidth consumption in transferring the raw data for backup. 
+A backup sevice may collocate with other cloud services on these commodity servers and 
+stores deduplicated data  in  the storage in this cluster or in
 a seperate storage cluster.
@@
     \includegraphics[width=3in]{images/colocated-arch}
-    \caption{Collocated VM Backup System.}
+    \caption{VM snapshot backup running on a converged cloud cluster.}
     \label{fig:collocated}
@@
 
-Backup systems have been developed to use content fingerprints to identify duplicate
+File backup systems have been developed to use content fingerprints to identify duplicate
 content~\cite{venti02,Rhea2008}.  It is expensive to compare a large number of chunk fingerprints
@@
 \item{\em  Management of file system blocks.}
-The file system block (FSB) size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
+The file system block (FSB) size in a distributed file system such as  Hadoop and Google file system
+ is uniform and large (e.g.  64MB),
 while the data chunk in a typical deduplication system is of a non-uniform size with 4KB or 8KB on average.
@@
 \item {\em Low resource usage in a nondedicated cloud cluster.}
-Since the cluster we consider is shared by many cloud services,
+When a backup service collocates with other cloud services as illustrated in Figure~\ref{fig:collocated},
 low resource usage of deduplication is desired so that
@@
 The key resource for global comparison  is memory for storing the fingerprints.
-We will consider the approximation techniques with reduced memory consumption. 
+During snapshot deltion, reference counting for all unique blocks used in all VMs requires a significant resource usage
+too.  Thus we seek for the low-profile techniques with approximation and low resource consumption. 
 \end{itemize}
@@
 for a collocated backup service with resource usage friendly
-to the existing applications.
+to the existing applications in a converged clustr architecture.
 

### 2014-01-24 snapshot_system/paper_conc.tex
add paper files
revised

--- 2013-09-26 snapshot_system/fast14_conclusion.tex
@@
 \label{sect:conclusion}
-In this paper we propose a collocated backup service built on
-the top of a cloud cluster to reduce network traffic and infrastructure.
-The key contribution is a VM-centric deduplication scheme to 
-maximize fault isolation while delivering competitive deduplication efficiency.
-Similarity guided local search reduces cross-VM data dependency and exposes more parallelism  
-while global deduplication with a small common data set eliminates popular duplicates.
-VM-specific file block packing also enhances fault tolerance by reducing data dependencies.
-The design places a special consideration for low-resource usages as a collocated cloud service.
-Evaluation using  VM backup data shows that VC strikes a tradeoff and 
+%In this paper we propose a collocated backup service built on
+%the top of a cloud cluster to reduce network traffic and infrastructure requirements.
+The main contribution of this paper is a low-profile and VM-centric deduplication scheme to 
+maximize fault isolation while delivering competitive deduplication efficiency using
+a small amount of system resource.
+Evaluation using  this scheme strikes a tradeoff and restricted cross-VM duplicate detection
 can accomplish 96.33\% or 96.9\% of what complete global
-deduplication can do.  The availability of snapshots increases substantially with 
-a small replication overhead for popular inter-VM chunks.
+deduplication can do, and the approximate snapshot deletion effectively manages deleted chunks with a 
+low-resource usage.  The availability of snapshots increases substantially when
+adding more replication for popular cross-VM chunks and packaging chunks from the same 
+VM in one file system block.
+%Currently we are studying how the
+
+%Similarity guided local search reduces cross-VM data dependency and exposes more parallelism  
+%while global deduplication with a small common data set eliminates popular duplicates.
+%VM-specific file block packing also enhances fault tolerance by reducing data dependencies.
+%The design places a special consideration for low-resource usages as a collocated cloud service
+%and

### 2014-01-24 snapshot_system/paper_dedup.tex
revised

@@
 
-\subsection{Key VC  Strategies}
+\subsection{VM centric  strategies}
 \label{sect:vc-strategies}
@@
 
+It should not be noted that one could consider 
+to rely on filesystem features to provide more replication to popular
+blocks, without the extra complexity of separating popular and non-popular
+data. The main problem with this  approach is that without separating the
+popular chunks from the less-popular, the popular chunks are dispersed across
+all of the filesystem blocks in the storage system.  We would
+have to add extra replication to each file block as long as it contains a popular chunk.
+
+%factor on popular chunks. This explains why we must separate the PDS and
+%non-PDS data in our system to acheive the desired $r_c/r$ ratio (though both
+%can be stored on the same DFS).
+
 %The system allows all machines conduct backups in parallel, and each machine

### 2014-01-24 snapshot_system/paper_del.tex
revised

@@
 
-In a busy VM cluster, snapshot deletions can occur frequently.
-Deduplication complicates the deletion process because space saving relies on the sharing of data
-and it requires the global references to deleted chunks to be identified before they can be safely removed.
+Snapshot deletions can occur frequently since old snapshots become less useful.
+General deduplication complicates the deletion process because sharing of duplicates
+requires a global refence counting to identify if  a chunk can be  safely removed without any reference.
 %The complexity of our distributed environment obviates reference counting as an option,
@@
 %instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.
-
-We seek a fast solution with low resource usage to delete snapshots and
-our VM-centric design simplifies the deletion process. 
-Since PDS is small and separated, we can focus on  unreferenced non-PDS chunks within each VM. 
+Since our VM-centric design restricts sharing of data chunks only to a small dataset,
+we can greatly simplify the deletion process by 
+focusing on  unreferenced non-PDS chunks within each VM. 
+This process can be conducted by independent among VMs, and thus results in  a simpler flow control and 
+lower resource usage. 
 %The PDS data chunks are commonly shared among all VMs and we do not consider them
 %during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
-Another resource-saving strategy we propose is
-an {\em approximate} deletion strategy to trade deletion accuracy for
+
+We further propose an {\em approximate} deletion strategy to trade deletion accuracy for
 speed and resource usage. Our method sacrifices a small percent of storage leakage
@@
 The algorithm contains three aspects.
-
 \begin{itemize}

### 2014-01-24 snapshot_system/paper_intro.tex
revised

@@
 
-One of popular architectures for building cloud services
-is a converged architecture that leverages commodity servers with software clustered storage and network, without 
-requiring network storage (e.g. SAN or NAS)~\cite{NutanixPaper}. 
+One of emerging architectures for building cloud services
+is a converged architecture that leverages commodity servers with software clustered storage, without 
+requiring network storage (e.g. ~\cite{NutanixPaper}). 
 Leading cloud platform companies such as Google, Amazon, Alibaba,
@@
 a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
-to glue a large number of commodity servers with local storage into a single cluster.
+to glue a large number of commodity servers.
+% with local storage into a single cluster.
 In such an environment,
@@
 %performance limitations associated with network storage.
-each physical machine runs a number  of virtual machines as  instances of a guest operating system 
-and their  virtual hard disks are represented as virtual disk image files in the host operating system.
+each physical machine runs a number  of virtual machines 
+%as  instances of a guest operating system 
+and their  virtual disks are represented as virtual disk image files in the host operating system.
 Frequent  snapshot backup of virtual disk images  can increase  the service reliability
@@
 
-A common technique for VM snapshot deduplication is    version-based detection that identifies file  blocks that have
-changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
-Another popular technique is to conduct global fingerprint  comparison to identify duplicates that exist
+While version-based detection  has been used to  identify file  blocks that have not 
+changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011},
+a popular technique for deduplicatioon is to 
+conduct fingerprint  comparison and identify duplicates that exist
 among all files~\cite{Guo2011,Dong2011,extreme_binning09}. 
-Because of highly repetitive content in snapshot backup,
-most data chunks are shared by many virtual machines.  Failure of a few shared data chunks can have a 
-broad effect and many snapshots of virtual machines could be affected.
+Because of highly repetitive content in snapshots from different VMs,
+many data chunks are shared by virtual machines.  
+Failure of a few shared data chunks can have a 
+broad effect and snapshots of these virtual machines could be affected.
 The previous work in deduplication focuses on the efficiency and approximation of
 fingerprint comparison, and has not addressed fault tolerance issues  together with deduplication.
-Thus we also seek deduplication options that yield better fault isolation.
+Thus we seek a method that strikes a balance between fault isolation and deduplication efficiency.
 
-The key contribution of this work is to evaluate the fault tolerance  impact of popular data blocks shared by many
+The main contribution of this work is to evaluate the fault tolerance  impact of popular data blocks shared by many
 virtual machines, and   propose a VM-centric approach that localizes deduplication as much as possible 
-and restrict global deduplication only to a limited set of most popular blocks.
+and restricts global deduplication only to a limited set of most popular blocks.
 Local deduplication also uses similarity-guided elimination to improve the deduplication coverage.
 Since the file system block size is normally bigger than the average data chunk size used for deduplication,
-we also package data chunks from the same VM into a file system block as much as possible to improve fault isolation.
+we package data chunks from the same VM into a file system block as much as possible to improve fault isolation.
 Because data sharing is restricted, 
-this VM-centric approach can also simplify the snapshot deletion process and reduce the overall resource usage, which
+this VM-centric approach reduces the overall resource usage significantly during backup and
+simplifies the snapshot deletion process. This low-resource design
 is suitable when the backup service with deduplication is collocated with other services running on a shared compute and storage
-cluster.
-We have evaluated this VM-centric approach using  a prototype system that runs a cluster of Linux machines with Xen and 
-a standard distributed file system for the backup storage. 
+cluster.  We have evaluated this VM-centric approach using  a prototype system.
+% that runs a cluster of Linux machines with Xen and a standard distributed file system for the backup storage. 
 %This approach localizes duplicate detection within each VM  

### 2014-01-24 snapshot_system/paper_eval.tex
deleted old main.pdf, adjusted failures to 10 for figures

--- 2013-09-27 snapshot_system/fast14_evaluation.tex
@@
     \pgfplotstabletypeset[
+        comment chars=!,
         columns={NodesFailed,VO100,VC100,VO1000,VC1000},
@@
 
-\begin{figure}[htbp]
+\begin{figure}[htb]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+                        width=\linewidth,
+                        height=0.6\linewidth,
+		%title={PDS Replication affect on availability},
+		xlabel={Failed storage nodes},
+		ylabel={VM Snapshot Availability (\%)},
+                xmin=0,
+                xmax=10,
+		%extra y ticks={99.9}, %if important numbers are missing
+                mark options=solid,
+                legend style={
+                    cells={anchor=west}, %legend entry alignment
+                    legend pos=south west %legend position
+                },
+                reverse legend,
+		]
+                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
+                \legend{
+                    VO,
+                    $r_c=4$,
+                    $r_c=5$,
+                    $r_c=6$,
+                    $r_c=9$
+                }
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
+  \label{fig:pds-replication}
+\end{figure}
+
+\begin{figure}[htb]
   \centering
@@
 	\end{tikzpicture}
-  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
-  \label{fig:pds-replication}
+  \caption{Availability of VM snapshots in VC with different PDS replication degrees \todo{decide which one}}
+  \label{fig:pds-replication-old}
 \end{figure}
@@
 SRB spends slightly more time for snapshot read/write because during each snapshot  backup, SRB involves many small bins,
- while VC only involves few containers with a bigger size. Thus I/O aggregation is more effective in VC.
+ while VC only involves few containers with a bigger size. Thus, there are more opportunities for I/O aggregation in VC to reduce seek time.
 SRB has a higher cost for index access and fingerprint comparison because most of  chunk fingerprints are routed

### 2014-01-26 snapshot_system/paper_intro.tex
update on converged model

@@
 One of emerging architectures for building cloud services
-is a converged architecture that leverages commodity servers with software clustered storage, without 
-requiring network storage (e.g. ~\cite{NutanixPaper}). 
+is a converged storage architecture that leverages commodity servers with software clustered storage.
+The converged architecture (server plus compute in same tier) grew out of the Google model.
+What Google recognized is that they could leverage their software to meld multiple direct attached low-cost disks together across servers and avoid paying high margins for traditional network attached storage systems.
+%This(e.g.
+~\cite{NutanixPaper}).
 Leading cloud platform companies such as Google, Amazon, Alibaba,

### 2014-01-27 snapshot_system/paper_intro.tex
update intro to converged arch

@@
 is a converged storage architecture that leverages commodity servers with software clustered storage.
-The converged architecture (server plus compute in same tier) grew out of the Google model.
-What Google recognized is that they could leverage their software to meld multiple direct attached low-cost disks together across servers and avoid paying high margins for traditional network attached storage systems.
-%This(e.g.
-~\cite{NutanixPaper}).
-Leading cloud platform companies such as Google, Amazon, Alibaba,
-Microsoft Azure  have built a converged compute and storage infrastructure and used
+This converged architecture (server plus compute in same tier) grew out of the Google model. 
+What Google recognized is that they could leverage their software to 
+meld multiple direct attached low-cost disks together across servers, 
+such approach allow Google to avoid paying high margins to traditional network attached storage vendors,
+as well as ditching their scalability limitations.
+
+Server virtualization is one of the most benefited area of adopting converged storage architecture.
+Leading cloud platform providers such as Google AppEngine, Amazon AWS, 
+Microsoft Azure and Alibaba have built such a converged compute and storage infrastructure and used
 a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
 to glue a large number of commodity servers.
+Many VDI environment in private clouds are also adopting this converged architecture 
+provided by Nutanix~\cite{NutanixPaper}, Simplivity and others. 
 % with local storage into a single cluster.

### 2014-01-28 snapshot_system/paper_intro.tex
update more on converged arch

@@
 to glue a large number of commodity servers.
-Many VDI environment in private clouds are also adopting this converged architecture 
+And such converged storage architecture also becomes increasingly popular 
+in VDI environment in private clouds
 provided by Nutanix~\cite{NutanixPaper}, Simplivity and others. 
@@
 and their virtual disks are represented as virtual disk image files in the host operating system.
+
+As more and more production 
+applications are running in virtualized environments in the cloud,
+the need to protect these virtual machines against data loss is urgent.
 Frequent snapshot backup of virtual disk images  can increase  the service reliability
@@
  is necessary to substantially reduce the storage demand.
+This is typically done through offloading backup workload from production 
+server hosts and consolidating it on dedicated backup proxy servers (e.g. EMC Data Domain) or
+backup services (e.g. Amazon S3). This approach simplifies the cluster architecture and 
+avoids potential performance hits to the production applications when backup is in progress,
+but it also brings its own problems:
+From VM users' perspective, the cost of a dedicated backup storage is very high.
+From cloud architecture's perspective, sending out pre-deduplication backup data wastes huge amount
+of bandwidth. Finally and most importantly, such dedicated backup storage is either difficult to scale out
+which would comprise the overall scalability of the converged architecture, 
+or has to give up global deduplication in order to gain scalability which would then increase the backup cost.
+
+Contrary to using dedicated backup storage for VM snapshots, 
+in this paper we propose a collocated backup storage sitting on top of 
+the existing distributed file system in a converged storage architecture,
+and provide methodologies to address associated challenges: 
+First, it must achieves good global deduplication 
+while the computing resources are very limited and spread over every node. 
+Second, it has to provide augmented fault isolation for the sharing of deduplicated data,
+given that node failures in converged architecture are the norm rather than exception.
+Finally, it needs to provide easily managable garbage collection so that user immediately
+sees storage charge changes after he deletes a snapshot.
+
+% low-cost VM-centric snapshot backup approach that is collocated within 
+% the existing converged storage architecture. Our solution leverages the scalability of the underlying
+% distributed file system and provides global data deduplication in a resource friendly manner.
+
 %For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 

### 2014-01-28 snapshot_system/paper_background.tex
merged in final changes from fast14_*, update makefile for paper_*
Rich is making a pass

@@
 
-Figure~\ref{fig:collocated} illustrates a converged cloud architecture where
+Figure~\ref{fig:collocated} illustrates a converged IaaS cloud architecture 
+where
 each commodity server hosts a number of virtual machines and storage of these servers
 is clustered using a distributed file system~\cite{googlefs03,hdfs10}.
-Each physical machine 
-each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
-represented as virtual disk image files in the host operating system.
+Each physical machine hosts multiple virtual machines.  Every virtual machine
+runs its own guest operating system (typically one of only a few
+installed on the system) and accesses virtual hard disks 
+stored as image files maintained by the operating system running on the
+physical host.
 For VM snapshot backup, file-level semantics are normally not provided.
@@
 %reduces the network bandwidth consumption in transferring the raw data for backup. 
-A backup sevice may collocate with other cloud services on these commodity servers and 
-stores deduplicated data  in  the storage in this cluster or in
-a seperate storage cluster.
+%A backup sevice may collocate with other cloud services on these commodity servers and 
+%stores deduplicated data  in  the storage in this cluster or in
+%a seperate storage cluster.
 
@@
 
-File backup systems have been developed to use content fingerprints to identify duplicate
-content~\cite{venti02,Rhea2008}.  It is expensive to compare a large number of chunk fingerprints
-and several techniques have been proposed to speedup. For example, the data domain method ~\cite{bottleneck08} 
-uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
+File backup systems have been developed to use fingerprints generated for
+data ``chunks''  to identify duplicate
+content~\cite{venti02,Rhea2008}.  In its simple implementation,
+it is expensive to compare a large number of 
+fingerprints
+so several techniques have been proposed to improve duplicate identification. 
+For example, the data domain method ~\cite{bottleneck08} 
+uses  an in-memory Bloom filter and a prefetching cache for data chunks 
+which may be
 accessed.  
 %An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
-to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
+Approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
+to reduce memory requirements at the cost of some loss of deduplication
+eficiency.
 Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
@@
 efficiency, and none of them have considered the impact
-of deduplication on fault tolerance in a cloud  cluster environment considered in this paper.
-Our consideration is discussed below.
+of deduplication on fault resilience in a cloud environment.  To do so, we
+examine the following properties of VM snapshot deduplication for converged
+IaaS architectures.
+%considered in this paper.
+%Our consideration is discussed below.
 %VM dependence minimization during deduplication and file system block management.
-\begin{itemize}
-\item {\em Deduplication localization.}
-Because a data chunk is compared with fingerprints collected from all VMs during
-the deduplication process, only one copy of duplicates is stored in the storage,
-this artificially creates data dependencies among different VM users. 
-Content sharing via deduplication affects fault isolation since machine failures happen periodically 
-in a large-scale cloud and
-loss of a small number of shared data chunks can 
-cause the unavailability of snapshots for a large number of virtual machines.
-Localizing the impact of deduplication can increase fault isolation and resilience.
-Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
-discouraged. 
-Another disadvantage of sharing is that it complicates snapshot deletion, 
+\paragraph*{Local versus Global Deduplication} --
+If deduplication is implemented strictly in the storage system,
+a data chunk is compared with fingerprints collected from all VMs during
+the deduplication process, and only a small number of
+copies of duplicates are stored in the storage.  This sharing
+artificially creates hidden data dependencies among different VMs owned by
+different 
+who
+contract for isolation 
+by the IaaS cloud platform.  That is, the unit of failure visible to the cloud
+user is the VM, but the unit of sharing in a deduplicated data store is the
+data chunk.
+
+%Further, 
+%this artificial dependence affects fault isolation since 
+%the loss of all replicas of a data chunk can affect the otherwise unrelated
+%VMs that share it.
+
+Indeed, the greater the deduplication efficiency, the less
+the data redundancy that is maintained, and the greater the ``hidden'' data
+dependence between VMs that must be hosted as if they were physically isolated.
+%machine failures happen periodically 
+%in a large-scale cloud and
+%loss of a small number of shared data chunks can 
+%cause the unavailability of snapshots for a large number of virtual machines.
+Thus,
+restricting deduplication to be local to each VM (but across snapshots) 
+aligns the units of storage with the isolation properties guaranteed by the
+cloud at the possible expense of storage efficiency.
+%Localizing the impact of deduplication can increase fault isolation and resilience.
+%Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
+%discouraged.
+
+Additionally, storage efficient deduplication can be computationally expensive
+to implement in a distributed setting.  In particular, duplicate detection is
+logically a ``global'' operation with respect to the population of data chunks
+under consideration.
+By localizing duplicate search, the computational requirements
+for deduplication can be reduced, because fewer chunks must be compared.
+Further, deduplication of otherwise unrelated VMs can be implemented in
+parallel.
+
+Another disadvantage of cross-VM sharing is that it complicates 
+snapshot deletion, 
 which occurs frequently when snapshots expire regularly. 
-The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for deletion, but still carries a significant cost
-to count if a data chunk is still shared by other snapshots. 
-Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
-deduplication efficiency, and  can facilitate parallel execution of snapshot operations.
-\item{\em  Management of file system blocks.}
-The file system block (FSB) size in a distributed file system such as  Hadoop and Google file system
- is uniform and large (e.g.  64MB),
-while the data chunk in a typical deduplication system is of a non-uniform size with 4KB or 8KB on average.
-Packaging data chunks to an FSB can create more data dependencies among VMs
-since a file system block can be shared by even more VMs.
-Thus we need to consider a minimum association of FSBs to VMs in the packaging process.
+The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
+deletion, but still carries a significant cost, again in the distributed cloud
+setting.
+%to count if a data chunk is still shared by other snapshots.
 
-\item {\em Low resource usage in a nondedicated cloud cluster.}
-When a backup service collocates with other cloud services as illustrated in Figure~\ref{fig:collocated},
-low resource usage of deduplication is desired so that
-there is  a minimal impact to the other existing cloud services.
-The key resource for global comparison  is memory for storing the fingerprints.
-During snapshot deltion, reference counting for all unique blocks used in all VMs requires a significant resource usage
-too.  Thus we seek for the low-profile techniques with approximation and low resource consumption. 
-\end{itemize}
+Thus,
+localizing deduplication to the VM can align fault isolation properties and
+guarantees, improve the computational efficiency of snapshot maintenance, and
+simplyfy snapshot deletion over non-localized approaches at the possible
+expense of storage efficiency.
 
-We call the traditional deduplication approach as   VM-oblivious (VO)
-because they compare fingerprints of snapshots without consideration of VMs.
-With the above  considerations in mind, we study a 
+%minimize data sharing and simplify deletion while sacrificing 
+%deduplication efficiency, and  can facilitate parallel execution of snapshot operations.
+\paragraph*{Units of Storage versus Units of Sharing} --
+The file system block (FSB) size in a distributed file system such as  
+the Hadoop file system and the Google file system
+is uniform and large (e.g.  64MB) so as to optimize file system performance
+for bandwidth usage.
+Typically, deduplication implementations use smaller block sizes (4K bytes to
+8K bytes on average).
+In addition to the failure correlation that cross-VM data deduplication can
+introduce, disk block sharing of data chunks is another potential source of
+hidden data dependence.
+Thus a VM-centric solution should consider how data chunks from VMs are
+distriuted among large file system blocks when a large-scale distributed file
+system is used for disk image files.
+
+%a minimum association of FSBs to VMs in the packaging
+%process. By minimizing this association we can improve fault tolerance by
+%reducing the number of VMs affected when storage nodes are lost.
+
+\paragraph*{Moderating Resource Usage} --
+In a converged setting, the resources that are used to implement snapshot
+backup and deduplication are the same resources that must support cloud-hosted
+VMs.  Thus the backup service must share the resources available to
+other cloud services as illustrated in Figure~\ref{fig:collocated},
+and thus miniomize its impact on user-deliverable performance.
+%The key resource for global comparison  is memory for storing the fingerprints.
+%During snapshot deltion, reference counting for all unique blocks used in all VMs requires a significant resource usage
+%too.  Thus we seek for the low-profile techniques with approximation and low resource consumption.
+
+For the remainder of this paper, 
+we term the traditional deduplication approach {\em VM-oblivious} (VO)
+because it manages duplicate data chunks without consideration of VMs.
+With the above  considerations in mind, we propose a 
 VM-centric approach (called VC)
-for a collocated backup service with resource usage friendly
-to the existing applications in a converged clustr architecture.
+for a co-located backup service that has a resource usage profile
+suitable for use with converged cloud architecture.
 
@@
 the following previously-developed techniques.
-1)
-{\em Changed block Tracking}.
+\begin{itemize}
+\item {\em Changed Block Tracking} --
 VM snapshots can be  backed up  incrementally by identifying data segments that have
 changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
-Such a scheme  is  VM-centric since deduplication is localized. 
-We are seeking for a tradeoff since 
-global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
-2) {\em Stateless  Data Routing}.
-One approach for scalable duplicate comparison is to use a content-based hash
+Such a scheme  is  VM-centric since deduplication is localized to the snapshot
+history for each VM.
+%We are seeking for a tradeoff since 
+%global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
+\item {\em Stateless  Data Routing} --
+One approach to scalable duplicate comparison is to use a content-based hash
 partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011} 
@@
 VM-specific local search.
-3) {\em Sampled Index}.
+\item {\em Sampled Index for Memory Parsimony} -- 
 One effective approach that reduces memory usage is 
@@
 can be significant.  
+\end{itemize}
 

### 2014-01-28 snapshot_system/paper_intro.tex
Rich is making a pass

--- 2014-01-26 snapshot_system/paper_intro.tex
@@
 
-One of emerging architectures for building cloud services
-is a converged storage architecture that leverages commodity servers with software clustered storage.
-The converged architecture (server plus compute in same tier) grew out of the Google model.
-What Google recognized is that they could leverage their software to meld multiple direct attached low-cost disks together across servers and avoid paying high margins for traditional network attached storage systems.
-%This(e.g.
-~\cite{NutanixPaper}).
-Leading cloud platform companies such as Google, Amazon, Alibaba,
-Microsoft Azure  have built a converged compute and storage infrastructure and used
-a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
-to glue a large number of commodity servers.
+Commercial ``Infrastructure as a Service'' clouds (i.e. {\em public
+clouds}) often make use of commodity data center components to achieve the
+best possible economies of scale.  In particular, large-scale e-commerce cloud
+providers such as Google and Alibaba deploy ``converged'' components that
+co-locate computing and storage in each hardware module (as opposed to having
+separate computing and storage ``tiers.'')
+%One of emerging architectures for building cloud services is a converged
+%storage architecture that leverages commodity servers with software clustered
+%storage.
+%The converged architecture (server plus compute in same tier) grew out of the
+%Google model. 
+These providers use software to
+aggregate multiple direct attached low-cost disks together across
+servers as a way of avoiding the relatively high cost of network attached 
+storage~\cite{googlefs03,hdfs10}.
+%systems. %This(e.g. ~\cite{NutanixPaper}).  Leading cloud platform companies
+%such as Google, Amazon, Alibaba, Microsoft Azure  have built a converged
+%compute and storage infrastructure and used a distributed file system such as
+%Google file system~\cite{googlefs03,hdfs10} to glue a large number of
+%commodity servers.
 % with local storage into a single cluster.
 In such an environment,
-%That  allows the use of scalable compute and storage, without incurring the costs and
-%performance limitations associated with network storage.
-each physical machine runs a number  of virtual machines 
+%That  allows the use of scalable compute and storage, without incurring the
+%costs and performance limitations associated with network storage.
+each physical machine runs a number of virtual machines (VMs)
 %as  instances of a guest operating system 
-and their  virtual disks are represented as virtual disk image files in the host operating system.
-Frequent  snapshot backup of virtual disk images  can increase  the service reliability
-and deduplication of redundant content blocks~\cite{venti02,bottleneck08}
- is necessary to substantially reduce the storage demand.
-%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
-%automatically conducts  the backup of virtual disk images to all active users every day.
-%The cost of supporting a large number of concurrent backup streams is high
-%because of the huge storage demand and the use of deduplication
+and their virtual disks are stored as disk image files, typically
+using a local (possibly shared) file system.
+Frequent snapshot backup of virtual disk images can
+increase the service reliability by allowing VMs to restart from their latest
+snapshot in the event of a server failure.  However, because the disk
+blocks that make up the VMs are often the same from snapshot to snapshot,  
+deduplication of redundant content
+blocks~\cite{venti02,bottleneck08} is necessary to substantially reduce the
+storage demand.
+%For example, the Aliyun cloud, which is  the largest cloud service provider
+%by Alibaba in China, automatically conducts  the backup of virtual disk
+%images to all active users every day.  The cost of supporting a large number
+%of concurrent backup streams is high because of the huge storage demand and
+%the use of deduplication
 
@@
 
-While version-based detection  has been used to  identify file  blocks that have not 
-changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011},
-a popular technique for deduplicatioon is to 
-conduct fingerprint  comparison and identify duplicates that exist
-among all files~\cite{Guo2011,Dong2011,extreme_binning09}. 
-Because of highly repetitive content in snapshots from different VMs,
-many data chunks are shared by virtual machines.  
-Failure of a few shared data chunks can have a 
-broad effect and snapshots of these virtual machines could be affected.
-The previous work in deduplication focuses on the efficiency and approximation of
-fingerprint comparison, and has not addressed fault tolerance issues  together with deduplication.
-Thus we seek a method that strikes a balance between fault isolation and deduplication efficiency.
+Version-based detection has been used to identify file blocks that have not
+changed across snapshots so their redundant storage can be
+avoided~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
+%the previous version of the
+%snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}, 
+Alternatively, techniques that compare block ``fingerprints'' to
+identify duplicates
+that exist among all files regardless of their 
+origin~\cite{Guo2011,Dong2011,extreme_binning09} have
+also gained in popularity.
 
-The main contribution of this work is to evaluate the fault tolerance  impact of popular data blocks shared by many
-virtual machines, and   propose a VM-centric approach that localizes deduplication as much as possible 
-and restricts global deduplication only to a limited set of most popular blocks.
-Local deduplication also uses similarity-guided elimination to improve the deduplication coverage.
-Since the file system block size is normally bigger than the average data chunk size used for deduplication,
-we package data chunks from the same VM into a file system block as much as possible to improve fault isolation.
-Because data sharing is restricted, 
-this VM-centric approach reduces the overall resource usage significantly during backup and
-simplifies the snapshot deletion process. This low-resource design
-is suitable when the backup service with deduplication is collocated with other services running on a shared compute and storage
-cluster.  We have evaluated this VM-centric approach using  a prototype system.
-% that runs a cluster of Linux machines with Xen and a standard distributed file system for the backup storage. 
-%This approach localizes duplicate detection within each VM  
-%By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
-%this scheme can afford to allocate extra replicas of these shared chunks for better
-%fault resilience while sustaining competitive deduplication efficiency.
+One consequence of aggressive deduplication is the possible loss of failure
+resilience.  Separate files share the same physical copies of blocks that are
+logically duplicated among them.  If a shared block is lost, all files that
+share that block are affected.  The problem is particularly accute for VM
+snapshots where the purpose of the snapshot is precisely to create redundant
+data copies so that VMs are more fault resilient.  Thus, there exists a
+tension between the additional redundancy that snapshot creation is intended
+to provide, and the storage efficiencies that deduplication makes possible.
+
+%Because
+%of highly repetitive content in snapshots from different VMs, many data chunks
+%are shared by virtual machines.  Failure of a few shared data chunks can have
+%a broad effect and snapshots of these virtual machines could be affected.  The
+%previous work in deduplication focuses on the efficiency and approximation of
+%fingerprint comparison, and has not addressed fault tolerance issues  together
+%with deduplication.
+
+In this paper {\em we explore a method for deduplicating VM snapshots in
+converged architecture IaaS systems that strikes a balance between fault
+isolation and storage efficiency}.  The main contribution of this work is to
+evaluate the impact of sharing only ``popular'' data blocks 
+(through deduplication and limited replication)
+across 
+virtual machines while using localized deduplication within each VM
+to achieve both storage savings and fault isolation.
+%, and to propose a VM-centric approach that localizes
+%deduplication as much as possible and restricts global deduplication only to a
+%limited set of most popular blocks.  
+%In our method, local deduplication uses
+%similarity-guided elimination to improve the deduplication coverage.  
+Since
+the file system block size is normally bigger than the average data chunk size
+used for deduplication, 
+our approach uses a deduplication data chunk size that is smaller than a
+single file block and
+packages data chunks from the same VM into a file
+system block as much as possible to improve fault isolation.  Deduplicating
+data locally within a VM also reduces the need to maintain a global index of
+chunks that are shared among VMs, thereby increasing the scaling efficiency of
+the snapshot system.  The cost associated with localization, however, is in 
+the lost
+storage efficiency that cross-VM deduplication makes possible.  To recover
+some of this efficiency we allow a small number of the most popular data
+blocks to be deduplicated (and then replicated) across VMs.
+
+This work explores the storage and
+performance efficiencies that such a {\em VM-centric} 
+combination of local and global
+techniques can achieve.  We term it VM-centric because the deduplication
+algorithm considers VM boundaries in making its decisions as opposed to
+treating all blocks as being equivalent within the storage system.
+We detail the storage, performance,
+and fault isolation properties
+of our method and verify these properties empirically using a prototype
+system that we have developed to run as a co-located back-up service in
+converged IaaS cloud enviornments.
+
+%Because data
+%sharing is restricted, this VM-centric approach reduces the overall resource
+%usage significantly during backup and simplifies the snapshot deletion
+%process. This low-resource design is suitable when the backup service with
+%deduplication is collocated with other services running on a shared compute
+%and storage cluster.  We have evaluated this VM-centric approach using  a
+%prototype system.
+% that runs a cluster of Linux machines with Xen and a standard distributed
+% file system for the backup storage. 
+%This approach localizes duplicate detection within each VM  By narrowing
+%duplicate sharing within a small percent of common data chunks and exploiting
+%their popularity, this scheme can afford to allocate extra replicas of these
+%shared chunks for better fault resilience while sustaining competitive
+%deduplication efficiency.
 

### 2014-01-28 snapshot_system/paper_intro.tex

@@
 
+Without deduplication,
+the cloud typically offloads backup workload from production 
+server hosts to dedicated backup proxy servers (e.g. EMC Data Domain) or
+backup services (e.g. Amazon S3). This approach simplifies the cluster 
+architecture and 
+avoids potential performance degredation to production applications when 
+backups are in progress.
+However, sending out pre-deduplication backup data wastes huge amount
+of network bandwidth that would otherwise be available to user VMs. 
+Even when the storage system implements deduplication internally
+such dedicated backup storage is either difficult to scale out
+(which can comprise the overall scalability of the converged architecture) 
+or it must forego global deduplication in order to gain scalability 
+(which increases backup cost).
+
+In this paper we propose a backup service for converged cloud architectures
+that is co-located with user VMs, sharing the cloud computer, network, and
+storage resource swith them.
+We describe methodologies to address the following challenges: 
+\begin{itemize}
+\item good global deduplication efficiency using a distributed implementation
+that limits its resource usage, 
+\item augmented fault isolation for the sharing of deduplicated data,
+given that node failures in converged architecture are the norm rather than
+exception, and
+\item efficient garbage collection so that users stop incurring 
+storage charges immediately after snapshot deletion.
+\end{itemize}
+
+% low-cost VM-centric snapshot backup approach that is collocated within 
+% the existing converged storage architecture. Our solution leverages the scalability of the underlying
+% distributed file system and provides global data deduplication in a resource friendly manner.
+
+%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
+%automatically conducts  the backup of virtual disk images to all active users every day.
+%The cost of supporting a large number of concurrent backup streams is high
+%because of the huge storage demand and the use of deduplication
+
 %Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
@@
 
-In this paper {\em we explore a method for deduplicating VM snapshots in
-converged architecture IaaS systems that strikes a balance between fault
-isolation and storage efficiency}.  The main contribution of this work is to
-evaluate the impact of sharing only ``popular'' data blocks 
+The main technical approach of our work focuses on
+sharing only ``popular'' data blocks 
 (through deduplication and limited replication)
@@
 
-This work explores the storage and
+This paper explores the storage and
 performance efficiencies that such a {\em VM-centric} 

### 2014-01-28 snapshot_system/paper_background.tex
update converged arch
Rich makes it through paper_dedup

@@
 means no fine-grained file system metadata can be used to determine the changed data. 
-%This architecture does not use a seperate  backup facility for a lower cost and 
+%This architecture does not use a separate  backup facility for a lower cost and 
 %reduces the network bandwidth consumption in transferring the raw data for backup. 
-%A backup sevice may collocate with other cloud services on these commodity servers and 
+%A backup service may co-locate with other cloud services on these commodity servers and 
 %stores deduplicated data  in  the storage in this cluster or in
-%a seperate storage cluster.
+%a separate storage cluster.
 
@@
 
-%As discussed earlier, collocating a backup service on the existing
+%As discussed earlier, co-locating a backup service on the existing
 %cloud cluster avoids the extra cost to acquire a dedicated backup facility
@@
 to reduce memory requirements at the cost of some loss of deduplication
-eficiency.
+efficiency.
 Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
@@
 guarantees, improve the computational efficiency of snapshot maintenance, and
-simplyfy snapshot deletion over non-localized approaches at the possible
+simplify snapshot deletion over non-localized approaches at the possible
 expense of storage efficiency.
@@
 Thus a VM-centric solution should consider how data chunks from VMs are
-distriuted among large file system blocks when a large-scale distributed file
+distributed among large file system blocks when a large-scale distributed file
 system is used for disk image files.
@@
 other cloud services as illustrated in Figure~\ref{fig:collocated},
-and thus miniomize its impact on user-deliverable performance.
+and thus minimize its impact on user-deliverable performance.
 %The key resource for global comparison  is memory for storing the fingerprints.
-%During snapshot deltion, reference counting for all unique blocks used in all VMs requires a significant resource usage
+%During snapshot deletion, reference counting for all unique blocks used in all VMs requires a significant resource usage
 %too.  Thus we seek for the low-profile techniques with approximation and low resource consumption.

### 2014-01-28 snapshot_system/paper_dedup.tex
Rich makes it through paper_dedup

@@
 \label{sect:vc-strategies}
+
+We describe our overall deduplication approach as consisting of three
+complementary strategies: VM-local
+duplicate search optimization, global deduplication using popular chunks, and 
+VM-centric file system block management. 
 %\begin{itemize}
 %\item 
-\textbf{VM-specific local duplicate search within similar segments.}
+\paragraph*{VM-local duplicate search optimization} --
 We start with the changed block tracking approach in a coarse grain segment level.
-In our implementation with Xen on an Alibaba platform, the segment size is 2MB
+In our implementation 
+%with Xen on an Alibaba platform, 
+the segment size is 2MB
 and the device driver is extended to support tracking changed segments using a dirty bitmap. 
@@
 %\item 
-\textbf{Global deduplication with popular chunks and replication support.}
+\paragraph*{Global deduplication using popular chunks} --
 This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
@@
 The distribution is zipf like and popular chunks are dominating the large portion of data chunks.
-We denote $\sigma$ as the percentage of unique data chunks beloning to PDS and from the evaluation we find that
+We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
 $\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.
@@
 %\item 
-\textbf{VM-centric file system block management.}
+\paragraph*{VM-centric file system block management} --
 When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
@@
 %factor on popular chunks. This explains why we must separate the PDS and
-%non-PDS data in our system to acheive the desired $r_c/r$ ratio (though both
+%non-PDS data in our system to achieve the desired $r_c/r$ ratio (though both
 %can be stored on the same DFS).

### 2014-01-28 snapshot_system/paper_intro.tex
Rich makes it through paper_dedup

@@
 architecture and 
-avoids potential performance degredation to production applications when 
+avoids potential performance degradation to production applications when 
 backups are in progress.
@@
 that is co-located with user VMs, sharing the cloud computer, network, and
-storage resource swith them.
+storage resource with them.
 We describe methodologies to address the following challenges: 
@@
 
-% low-cost VM-centric snapshot backup approach that is collocated within 
+% low-cost VM-centric snapshot backup approach that is co-located within 
 % the existing converged storage architecture. Our solution leverages the scalability of the underlying
@@
 logically duplicated among them.  If a shared block is lost, all files that
-share that block are affected.  The problem is particularly accute for VM
+share that block are affected.  The problem is particularly acute for VM
 snapshots where the purpose of the snapshot is precisely to create redundant
@@
 system that we have developed to run as a co-located back-up service in
-converged IaaS cloud enviornments.
+converged IaaS cloud environments.
 
@@
 %process. This low-resource design is suitable when the backup service with
-%deduplication is collocated with other services running on a shared compute
+%deduplication is co-located with other services running on a shared compute
 %and storage cluster.  We have evaluated this VM-centric approach using  a

### 2014-01-28 snapshot_system/paper_intro.tex
tightening it up a bit

@@
 co-locate computing and storage in each hardware module (as opposed to having
-separate computing and storage ``tiers.'')
+separate computing and storage ``tiers.'')  The advantage of such an approach
+is that all infrastructure components are used to support paying customers --
+there are no resources specifically dedicated to cloud services.
 %One of emerging architectures for building cloud services is a converged
@@
 %Google model. 
-These providers use software to
+In particular, these providers use software to
 aggregate multiple direct attached low-cost disks together across

### 2014-01-29 snapshot_system/paper_analysis.tex
shortened

@@
 \begin{tabular}{|p{1.0cm}|p{5.75cm}|}
+%\hline
+%$k$ &  the number of top most popular chunks selected for deduplication\\ 
+%\hline
+%$c$ &  the total amount of data chunks in a cluster of VMs\\ 
+%\hline
+%$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
+%\hline
+%$f_i$ &  the frequency for the $i$th most popular fingerprint\\
+%\hline
+%$\delta$ &  the percentage of duplicates detected in local deduplication\\
+%\hline
+%$\sigma$ & = percentage of unique data  belonging to  PDS\\
 \hline
-$k$ &  the number of top most popular chunks selected for deduplication\\ 
+$r$, $r_c$ & replication degree of non-PDS, and PDS file blocks\\
 \hline
-$c$ &  the total amount of data chunks in a cluster of VMs\\ 
-\hline
-$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
-\hline
-$f_i$ &  the frequency for the $i$th most popular fingerprint\\
-\hline
-$\delta$ &  the percentage of duplicates detected in local deduplication\\
-\hline
-$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belonging to  PDS\\
-\hline
-$p$ & the number of machines in the cluster\\
-\hline
-$V$ & the average number of VMs per machine\\
-\hline
-$E_c, E_o$ & deduplication efficiency of VC and VO \\
+$n$, $p$ & no. of virtual and physical machines in the cluster\\
+%\hline
+%$V$ & the average number of VMs per machine\\
+%\hline
+%$E_c, E_o$ & deduplication efficiency of VC and VO \\
 %\hline
@@
 %$s$ & the average data chunk size. Our setting is  4K.\\
-\hline
-$s$ & the average number of chunks per FSB\\
+%\hline
+%$s$ & the average number of chunks per FSB\\
 %\hline
@@
 \hline
-$N_1$ & the average number  of non-PDS FSBs blocks in a VM for VC\\
+$N_1$, $N_2$ & the average number  of non-PDS and PDS file blocks in a VM for VC\\
 \hline
-$N_2$ & the average number  of PDS FSBs in a VM for VC\\
+$N_o$ & the average number  of file blocks  in a VM for VO\\
 \hline
-$N_o$ & the average number  of FSBs  in a VM for VO\\
-\hline
-A(r) & the availability of an FSB  with replication degree $r$\\
+A(r) & the availability of a file block with replication degree $r$\\
 \hline
@@
 with a VM oblivious design.
-Let $r$ be the replication degree of standard file blocks in the underlying backup storage. 
-$r=3$ is a typical setting in distributed file systems~\cite{googlefs03,hdfs10}.
-Let $r_c$ be the replication degree of file blocks for PDS. 
-Additional parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
+%Let $r$ be the replication degree of standard file blocks in the underlying backup storage. 
+%$r=3$ is a typical setting in distributed file systems~\cite{googlefs03,hdfs10}.
+%Let $r_c$ be the replication degree of file blocks for PDS. 
+Parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
 %The replication degree of the backup storage 
@@
 to the VM centric and oblivious approaches.  
-A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
+%A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
 %We use an FSB rather than a deduplication
@@
 
-\comments{
-%Moved up in the strategy subsection
-We could consider a third approach (call it VO+), adopting the VO approach, and
-then relying on filesystem features to provide extra replication to popular
-blocks, without the extra complexity of separating popular and non-popular
-data. The problem with this VO+ approach is that without separating the
-popular chunks from the less-popular, the popular chunks are dispersed across
-all of the filesystem blocks in the storage system. Because the popular blocks
-are dispersed, there are very few popular FSBs. The end result is that we
-either have to add extra replication on unpopular chunks to ensure the popular
-chunks have sufficient replication, or we have to accept a reduced replication
-factor on popular chunks. This explains why we must separate the PDS and
-non-PDS data in our system to achieve the desired $r_c/r$ ratio (though both
-can be stored on the same DFS).
-}
 For VC, each VM has an average number $N_1$ of non-PDS FSBs
@@
 shared by an average of $V_c$ VMs. 
-%Let $s$ be the average number of chunks per file system block, 
-%$V$ be the average number of VMs hosted on each machine. 
 Then, 
 \[
-V pN_1 s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
-V pN_2 s  \approx c_u \sigma V_c.
+n* N_1   \approx \mbox{ No of non-PDS file system blocks} 
 \]
 
-For VO, each VM has an average of $N_o$ FSBs
+For VO, each VM has an average of $N_o$ file system blocks
 and let $V_o$ be the average number of VMs shared by each FSB.
 \[
-V pN_o s  = (c- E_o(c-c_u) ) V_o.
+n *N_o   =  V_o *\mbox{ No of file system blocks} 
 \]
 
-Since each FSB (with default size $64MB$) contains many chunks (on average 4KB),
-each FSB contains the hot low-level chunks shared by many VMs, and it also contains
-rare chunks which are not shared.  Since $c>> c_u$, from the above equations:
+Since the number of PDS file system blocks is small, 
+and the deduplication efficiency of VC is very close to that of VO,
+the number of non-PDS file blocks in VC is close to the number of file blocks in VO.
+Then
 \[
-\frac{N_1}{N_o} \approx  \frac{1-E_o}{(1-E_c) V_o}.
+\frac{N_o}{N_1} \approx  V_o.
 \]
-When $E_c$ is close to $E_o$,
-%as demonstrated in Section~\ref{sect:evaldedup},
-$N_1$ is much smaller than $N_o$. 
-%When there is a failure in FSBs with replication degree $r$
-%and there is no failure for PDS data with more replicas,   a VM in
-%the VC approach has a much lower chance to lose a snapshot than VO. 
-%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
-%our test dataset.
-%For VC, we only show
-%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
-%one VM.
-%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
+Thus $N_o >> N_1$.
 Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO
 and  $N_1$ is indeed  much smaller than $N_o$ in our tested dataset.
+
 %In fact, $N_1 +N_2 < N_o$. 
@@
 %Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.
-
-\comments{
-\begin{figure}[htbp]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-                width=\linewidth,
-                height=0.6\linewidth,
-		%title={VO FSB links},
-		xlabel={Number of VMs},
-		ylabel={Avg. Num. VMs sharing FSB},
-                cycle list name=mline,
-                xmin=0,
-                ymin=0,
-                xmax=106,
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		legend pos=north west
-		]
-                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
-		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
-                \legend{VO, PDS in VC};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Measured average number of VMs sharing a 64MB FSB in VO and in VC.}
-  \label{fig:fsb-links}
-\end{figure}
-
-}
 

### 2014-01-29 snapshot_system/paper_analysis.tex
revised

@@
 \hline
-A(r) & the availability of a file block with replication degree $r$\\
+A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
 \hline
@@
 and the deduplication efficiency of VC is very close to that of VO,
+Section~\ref{sect:evaluation} shows that
 the number of non-PDS file blocks in VC is close to the number of file blocks in VO.
@@
 \]
-Thus $N_o >> N_1$.
-Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO
-and  $N_1$ is indeed  much smaller than $N_o$ in our tested dataset.
+%Thus $N_o >> N_1$.
+
+Figure~\ref{fig:vm-links} shows $N_1$, $N_2$, and $N_o$ values in our tested dataset when increasing the number of VMs.  
+%the average number of file system blocks for each VM in VC and in VO
+$N_1$ is much smaller than $N_o$ as the formula shows above.
 
@@
 
-The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
- $N_2$ for VC and $N_o$ for VO.
-Given normal data replication degree $r$, PDS data replication degree $r_c$, 
-the availability of a file system block is the probability that  
+%The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
+% $N_2$ for VC and $N_o$ for VO.
+Given $d$ failed physical machines and $r$ replicas fr each block,
+%normal data replication degree $r$, PDS data replication degree $r_c$, 
+the availability of a file block is the probability that  
 all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
-Namely, we define it as
+Namely, 
 \[
@@
 Then the availability of one VM's snapshot data under VO approach is the probability that
- all its FSBs are unaffected during the system failure:
+ all its file blocks  are unaffected during the system failure:
 %\begin{equation}
@@
 
-For VC, there are two cases for $d$ failed machines.
+For VC, there are two cases: 
 \begin{itemize}
 \item
-When $r \le d<r_c$,  there is no PDS data loss and  
-the full snapshot availability of a VM in the VC approach is 
+When $r \le d<r_c$,  there is no PDS data loss and we need to look at the non-PDS data loss. 
+The full snapshot availability of a VM is: 
 %\begin{equation}
@@
 \]
+That is still smaller than that of $V_O$ based on the observation with our data. There are two reasons for this:  
+1) $N_1$ is much smaller than $N_o$ and we are observing that $N_1+N_2<N_o$. 
+2)  $A(r) < A(r_c)$ because $r < r_c$.  
+Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
+%that the availability of an individual file system block
+different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.
 %\end{equation}
@@
 %In the evaluation discussed in Section~\ref{sect:evaldedup},
-We have considered a worst case scenario that
-every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
-Even with that, the availability of VC snapshots is still much higher than VO and  
-there are two reasons for this:  1) $N_1$ is much smaller than $N_o$ as discussed previously.
-2)  $A(r) < A(r_c)$ because $r < r_c$.  
-Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
-%that the availability of an individual file system block
-different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.
+%We have considered a worst case scenario that
+%every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
+%Even with that, the availability of VC snapshots is still much higher than VO and
 
@@
     ]{figures/fsb_availability.txt}
-    \caption{$A(r_c)$ as storage nodes fail in a 100 node cluster.}
+    \caption{$A(r_c)$ values in a cluster with p=100 nodes.}
     \label{tab:fsb-availability}

### 2014-01-29 snapshot_system/paper_dedup.tex
revised

@@
 \paragraph*{VM-local duplicate search optimization} --
-We start with the changed block tracking approach in a coarse grain segment level.
-In our implementation 
-%with Xen on an Alibaba platform, 
-the segment size is 2MB
-and the device driver is extended to support tracking changed segments using a dirty bitmap. 
-Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
-and cannot afford a small segment size.
+
+We use the standard version-based detection~\cite{Clements2009,Vrable2009}
+to identify changed content with dirty bits in a coarse grain segment level.
+%In our implementation 
+%the segment size is 2MB
+%and the device driver is extended to support tracking changed segments using a dirty bitmap. 
+The reason to choose a coarse grain level is that 
+since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in 
+memory and cannot afford a small segment size.
 It should be noted that dirty bit tracking is supported or can be easily implemented in 
@@
 %with those in similar segments.  
-For a 2MB segment, its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
-by limiting at most 10 similar segments to search, the amount of memory for maintaining those similar segment recipes is small.
+For example, assume that  a segment is of size  2MB, 
+its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
+by limiting at most 10 similar segments to search, the amount of memory for maintaining those 
+similar segment recipes is small.
 As part of our local duplicate search we also compare the current segment

### 2014-01-29 snapshot_system/paper_del.tex
rv

@@
 General deduplication complicates the deletion process because sharing of duplicates
-requires a global refence counting to identify if  a chunk can be  safely removed without any reference.
+requires a global refence counting~\cite{Guo2011,Fabiano2013} 
+ to identify if  a chunk can be  safely removed without any reference.
 %The complexity of our distributed environment obviates reference counting as an option,

### 2014-01-29 snapshot_system/paper_analysis.tex
revise

@@
 \hline
-$r$, $r_c$ & replication degree of non-PDS, and PDS file blocks\\
+$r$, $r_c$ & replication degree of non-PDS, and PDS file blocks in VC\\
 \hline
@@
 
-For VC, each VM has an average number $N_1$ of non-PDS FSBs
-and  has  an average of  $N_2$ PDS FSBs. 
-Each non-PDS FSB is associated with one VM
- and  we denote that PDS FSBs are
+For VC, each VM has an average number $N_1$ of non-PDS file system blocks
+and  has  an average of  $N_2$ PDS file system blocks. 
+Each non-PDS block is associated with one VM
+ and  we denote that PDS blocks are
 shared by an average of $V_c$ VMs. 
@@
 For VO, each VM has an average of $N_o$ file system blocks
-and let $V_o$ be the average number of VMs shared by each FSB.
+and let $V_o$ be the average number of VMs shared by each file block.
 \[
@@
 		xlabel={Number of VMs},
-		ylabel={Avg. Num. FSBs used by VM},
+		ylabel={Avg. no file system blocks  used by VM},
                 xmin=0,
@@
 	\end{tikzpicture}
-  \caption{Measured average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
+  \caption{Measured average number of 64MB file system blocks used by a single VM in
+VC and VO. }
   \label{fig:vm-links}

### 2014-01-29 snapshot_system/paper_background.tex
revise

@@
 \paragraph*{Units of Storage versus Units of Sharing} --
-The file system block (FSB) size in a distributed file system such as  
-the Hadoop file system and the Google file system
-is uniform and large (e.g.  64MB) so as to optimize file system performance
-for bandwidth usage.
+The file system block  size in a distributed file system such as  
+the Hadoop file system and the Google file system~\cite{googlefs03}
+is large (e.g.  64MB) so as to optimize file system performance
+for big data.
 Typically, deduplication implementations use smaller block sizes (4K bytes to
-8K bytes on average).
+8K bytes on average~\cite{Jin2009}).
 In addition to the failure correlation that cross-VM data deduplication can

### 2014-01-29 snapshot_system/paper_intro.tex
revise

@@
 snapshot in the event of a server failure.  However, because the disk
-blocks that make up the VMs are often the same from snapshot to snapshot,  
+blocks that make up the VMs are often the same from snapshot to snapshot
+and are shared among VMs,  
 deduplication of redundant content
@@
 
-Without deduplication,
-the cloud typically offloads backup workload from production 
+%Without deduplication,
+A cloud may offload backup workload from production 
 server hosts to dedicated backup proxy servers (e.g. EMC Data Domain) or
@@
 backups are in progress.
-However, sending out pre-deduplication backup data wastes huge amount
+However, sending out undeduplicated backup data wastes huge amount
 of network bandwidth that would otherwise be available to user VMs. 
-Even when the storage system implements deduplication internally
-such dedicated backup storage is either difficult to scale out
-(which can comprise the overall scalability of the converged architecture) 
-or it must forego global deduplication in order to gain scalability 
-(which increases backup cost).
+%Even when the storage system implements deduplication internally
+%such dedicated backup storage is either difficult to scale out
+%(which can comprise the overall scalability of the converged architecture) 
+%or it must forego global deduplication in order to gain scalability 
+%(which increases backup cost).
 
-In this paper we propose a backup service for converged cloud architectures
+In this paper we consider a backup service for converged cloud architectures
 that is co-located with user VMs, sharing the cloud computer, network, and
 storage resource with them.
-We describe methodologies to address the following challenges: 
+We describe methodologies to address the following two challenges: 
 \begin{itemize}
-\item good global deduplication efficiency using a distributed implementation
-that limits its resource usage, 
+\item simple deduplication and snapshot deletion with competitive efficiency and 
+a small resource usage without affecting other collocated cloud services.
 \item augmented fault isolation for the sharing of deduplicated data,
 given that node failures in converged architecture are the norm rather than
-exception, and
-\item efficient garbage collection so that users stop incurring 
-storage charges immediately after snapshot deletion.
+exception. 
+% so that users stop incurring storage charges immediately after snapshot deletion.
 \end{itemize}
@@
 also gained in popularity.  
-
 One consequence of aggressive deduplication is the possible loss of failure
@@
 logically duplicated among them.  If a shared block is lost, all files that
-share that block are affected.  The problem is particularly acute for VM
-snapshots where the purpose of the snapshot is precisely to create redundant
-data copies so that VMs are more fault resilient.  Thus, there exists a
+share that block are affected.  
+%The problem is particularly acute for VM
+%snapshots where the purpose of the snapshot is precisely to create redundant
+%data copies so that VMs are more fault resilient.  
+Thus, there exists a
 tension between the additional redundancy that snapshot creation is intended
-to provide, and the storage efficiencies that deduplication makes possible.
-
+to provide, and the storage efficiency that deduplication makes possible.
+The previous work on deduplication has not considered the impact of 
+duplicate sharing on  fault tolerance.
 %Because
@@
 
-The main technical approach of our work focuses on
-sharing only ``popular'' data blocks 
+%This paper explores the storage and
+%performance efficiencies that such a {\em VM-centric} 
+%combination of local and global
+%techniques can achieve.  
+We term our approach {\em VM-centric} because the deduplication
+algorithm considers VM boundaries in making its decisions as opposed to
+treating all blocks as being equivalent within the storage system.
+We detail the storage, performance,
+and fault isolation properties
+of our method and verify these properties empirically using a prototype
+system that we have developed to run as a co-located back-up service in
+converged IaaS cloud environments.
+Our work focuses on sharing only ``popular'' data blocks 
 (through deduplication and limited replication)
@@
 the file system block size is normally bigger than the average data chunk size
-used for deduplication, 
-our approach uses a deduplication data chunk size that is smaller than a
-single file block and
-packages data chunks from the same VM into a file
-system block as much as possible to improve fault isolation.  Deduplicating
-data locally within a VM also reduces the need to maintain a global index of
-chunks that are shared among VMs, thereby increasing the scaling efficiency of
-the snapshot system.  The cost associated with localization, however, is in 
+used for deduplication,  packaging
+content from different VMs into the same file block  creates a ``false'' sharing that 
+affects fault isolation. Thus we avoid such VM-oblivious packaging.
+%our approach uses a deduplication data chunk size that is smaller than a
+%single file block and
+%Thus our strategy is to packages data chunks from the same VM into a file
+%system block as much as possible to improve fault isolation.  
+%Deduplicating
+%data locally within a VM also reduces the need to maintain a global index of
+%chunks that are shared among VMs, thereby increasing the scaling efficiency of
+%the snapshot system.  
+The cost associated with localization, however, is in 
 the lost
@@
 blocks to be deduplicated (and then replicated) across VMs.
-
-This paper explores the storage and
-performance efficiencies that such a {\em VM-centric} 
-combination of local and global
-techniques can achieve.  We term it VM-centric because the deduplication
-algorithm considers VM boundaries in making its decisions as opposed to
-treating all blocks as being equivalent within the storage system.
-We detail the storage, performance,
-and fault isolation properties
-of our method and verify these properties empirically using a prototype
-system that we have developed to run as a co-located back-up service in
-converged IaaS cloud environments.
 

### 2014-01-30 snapshot_system/paper_eval.tex
lots of figure updates, new modeling data

@@
     \pgfplotstabletypeset[
-        comment chars=!,
+        comment chars=!,%use ! before a row in the data table to exclude it
         columns={NodesFailed,VO100,VC100,VO1000,VC1000},
@@
     ]{figures/availability_table.txt}
-    \caption{Availability of VM snapshots for VO and VC.}
+    \caption{Availability of VM snapshots for VO and VC ($r_c=6$).}
     \label{tab:vm-availability}
@@
                 xmin=0,
-                xmax=10,
+                xmax=6,
 		%extra y ticks={99.9}, %if important numbers are missing
@@
   \label{fig:exbin-efficiency-graph2}
+\end{figure}
+
+\begin{figure}[]
+    \centering
+    \begin{tikzpicture}
+        \begin{axis}[
+                ybar,
+                xtick=data,
+                %symbolic x coords={VC(No PDS), VC($\sigma=2\%$\, No similarity guidance), VC($\sigma=2\%$), VC( $\sigma=4\%$), SRB},
+                symbolic x coords={VC0, VC2N, VC2, VC4, SRB},
+                %xticklabels from table={figures/efficiency_comparison_bars.txt}{alg}
+            ]
+            \addplot[fill=blue] coordinates {(VC0,93.02) (VC2N,94.31) (VC2,96.01) (VC4,96.58) (SRB,97.86)};
+        \end{axis}
+    \end{tikzpicture}
+    \caption{Efficiency Comparison between different VC settings and SRB}
+    \label{tab:efficiency-comparison}
 \end{figure}

### 2014-01-30 snapshot_system/paper_eval.tex
took out VO from availability plot
rev

--- 2014-01-24 snapshot_system/paper_eval.tex
@@
 \subsection{Settings}
-We have performed a trace-driven study using a production dataset~\cite{WeiZhangIEEE} from 
-Alibaba Aliyun's cloud platform with about 100 machines. 
+We have performed a trace-driven study based on a dataset~\cite{WeiZhangIEEE} from 
+Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
 Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage system while
@@
  Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
-there are up to 20 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
+there are up to 20 machine nodes failed in a cluster with $p=100$ physical machines.
+The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
+and thus calculate the average availability of VM snapshots.
+The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
+the same from $p=100$ setting to $p=1000$. With differnet $p$ values, how the availability varies when 
+the number of failures in the cluster changes.
+
 %Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
-We have assumed a worst-case scenario that  a PDS block is shared by every VM. 
+%We have assumed a worst-case scenario that  a PDS block is shared by every VM. 
 %($V_c=p*V$), which is to be expected when PDS
@@
 %case for VO approach. 
-Our results show that even the worst case,  VC  still has a significantly  higher availability than VO as the number of
-failed machines increases.
+Our results show that VC  has a significantly  higher availability than VO as the number of failed machines increases.
 %Our VM-centric approach shows significant improvements

### 2014-01-30 snapshot_system/paper_eval.tex

@@
                 xmin=0,
-                xmax=20,
+                xmax=10,
 		%extra y ticks={99.9}, %if important numbers are missing
@@
 		]
-                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
+                %\addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                 \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
@@
                 \legend{
-                    VO,
+                    %VO,
                     $r_c=4$,

### 2014-01-30 snapshot_system/paper_eval.tex
various figure changes. Reworded fault isolation and dedup efficiency sections to emphasize our contribution to deduplication.

--- 2014-01-30 snapshot_system/paper_eval.tex
@@
 %Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
-We have assumed a worst-case scenario that  a PDS block is shared by every VM. 
+%We have assumed a worst-case scenario that  a PDS block is shared by every VM. 
 %($V_c=p*V$), which is to be expected when PDS
@@
 %case for VO approach. 
-Our results show that even the worst case,  VC  still has a significantly  higher availability than VO as the number of
+Our results show that VC has a significantly  higher availability than VO as the number of
 failed machines increases.
@@
 %in VM availability.
-For example, with 5/100 machines failed and 25 VMs per machine, VO with 93.256\% availability would lose data in 169 VMs 
-while VC with 97.763\% loses data for 56 VMs.
-The key reason is that for most data in VC, only a single
-VM can be affected by the loss of a single FSB. Since most FSBs contain chunks for a single VM, VMs can depend on a smaller number of FSBs.
+For example, with 3/100 machines failed and 25 VMs per machine, VO with 69.5\% availability could lose data in 763 VMs 
+while VC with 99.7\% loses data for 8 VMs.
+The key reason is that for most data in VC, only a single VM can be affected by
+the loss of a single file block. Since most blocks contain chunks for a single
+VM, VMs can depend on a smaller number of blocks, while in VO, the loss of a
+single block tends to affect many VMs.
 % because our VM-centric approach
@@
 Although the loss of a PDS block affects many VMs,
-by increasing replication for those blocks we minimize the effect on VM snapshot availability.
+by increasing replication for those blocks we minimize the effect on VM
+snapshot availability, and this is one of the key contributions of our
+approach, the clear separation of highly popular data from less popular data.
 %By having extra replicas for the PDS data, we reduce the failure rate of PDS
@@
 the impact of increasing PDS data replication. 
-While the impact on storage cost is small, 
-a replication degree of 6  has a significant improvement over 4, but the availability is about
-the same for $r_c=6$ and $r_c=9$ (beyond $r_c=6$ improvements are minimal).
+While the impact on storage cost is small (because we have separated out only
+the most popular blocks),
+a replication degree of 6  has a significant improvement over 4. The
+availability is very similar
+for $r_c=6$ and $r_c=9$, and beyond $r_c=6$ improvements are minimal.
 
@@
                 xmin=0,
-                xmax=6,
+                xmax=10,
 		%extra y ticks={99.9}, %if important numbers are missing
@@
 
+\comments{
 \begin{figure}[htb]
@@
 		]
-                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
-                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
+                %\addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
+                %\addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                 \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
@@
                 \legend{
-                    VO,
-                    $r_c=4$,
+                    %VO,
+                    %$r_c=4$,
                     $r_c=5$,
@@
 
+}
+
 \subsection{Deduplication Efficiency}
@@
 
+\comments{
 %this version combines the old and the minhash alg. to compare against srb
@@
 
+}
+
 \begin{figure}[]
@@
                 ybar,
-                xtick=data,
-                %symbolic x coords={VC(No PDS), VC($\sigma=2\%$\, No similarity guidance), VC($\sigma=2\%$), VC( $\sigma=4\%$), SRB},
-                symbolic x coords={VC0, VC2N, VC2, VC4, SRB},
+                ylabel={Dedup. Efficiency (\%)},
+                xtick=\empty,
+                %symbolic x coords={VC-No PDS, VC-2\%PDS w/o similarity, VC-2\%PDS, VC-4\%PDS, SRB},
+                %symbolic x coords={VC0, VC2N, VC2, VC4, SRB},
                 %xticklabels from table={figures/efficiency_comparison_bars.txt}{alg}
+                nodes near coords,
+                every node near coord/.append style={
+                anchor=-145+\coordindex*10}
             ]
-            \addplot[fill=blue] coordinates {(VC0,93.02) (VC2N,94.31) (VC2,96.01) (VC4,96.58) (SRB,97.86)};
+            %\addplot[fill=blue] coordinates {(VC0,93.02) (VC2N,94.31) (VC2,96.01) (VC4,96.58) (SRB,97.86)};
+            %\addplot[fill=blue] coordinates { (VC-No PDS,93.02) (VC-2\%PDS w/o similarity,94.31) (VC-2\%PDS,96.01) (VC-4\%PDS,96.58) (SRB,97.86) };
+            \addplot [%
+                point meta=explicit symbolic,
+                fill=blue
+            ] table [x expr=\coordindex, y=efficiency,meta=alg] {figures/efficiency_comparison_bars.txt};
         \end{axis}
@@
     \caption{Efficiency Comparison between different VC settings and SRB}
-    \label{tab:efficiency-comparison}
+    \label{fig:efficiency-comparison}
 \end{figure}
 
-Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC,
+Figure~\ref{fig:efficiency-comparison} shows the deduplication efficiency for SRB and VC using different settings,
 % <<<<<<< HEAD
@@
 % =======
-namely the percent of duplicate chunks
+that is the percent of duplicate chunks
 which are detected and removed.
@@
 With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
-and  the deduplication efficiency can reach over 96.33\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 96.9\% while space consumption increases to 200MB per machine. 
+and  the deduplication efficiency can reach over 96\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 96.6\% while space consumption increases to 200MB per machine. 
 %and  the deduplication efficiency can reach 96.489\%.
@@
 %index ($\sigma=100\%$) then VC will have 100\% efficiency.
-SRB can deliver up to 97.79\% deduplication efficiency, which is slightly better than VC.
+SRB can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
 Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
-with competitive deduplication efficiency.
+with a slight reduction in deduplication efficiency.
 
@@
 
-Figure~\ref{fig:exbin-efficiency-graph2} also shows the curve  of VC without local similarity search.
-There is a big efficiency drop in this curve when the number of VMs is about 30.
-The reason is that  
+Figure~\ref{fig:efficiency-comparison} also shows the efficiency of VC without local similarity search.
+%There is a big efficiency drop in this curve when the number of VMs is about 30.
+The reason similarity search provides such an improvement is that
 %Without this (i.e. when we only 
@@
 rather than modified in place,  
-a dirty-bit or offset based detection would not be able to detect such a movement and 
-similarity search becomes especially important.  We have found that in
+and a dirty-bit or offset-only based detection would not be able to detect such a movement.
+We have found that in
 approximately 1/3 of the VMs in our dataset this movement happens frequently.
-In general, adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
+In general, adding local similarity-guided search increases deduplication efficiency from 94\% to over 96\%.
 That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}

### 2014-01-30 snapshot_system/paper_eval.tex
figure updates. Compressed and improved fig:efficiency-comparison. Created tab:vc_srb_combined as a possible compact replacement for the bar chart.

@@
         \begin{axis}[
+                width=\linewidth,
+                height=0.6\linewidth,
                 ybar,
+                bar width=0.5cm,
+                ymax=98.7,
+                enlarge x limits=0.15,
+                style=thin,
                 ylabel={Dedup. Efficiency (\%)},
+                ytick={93,94,95,96,97,98},
                 xtick=\empty,
+                ymajorgrids,
+                grid style=densely dotted,
                 %symbolic x coords={VC-No PDS, VC-2\%PDS w/o similarity, VC-2\%PDS, VC-4\%PDS, SRB},
@@
                 every node near coord/.append style={
-                anchor=-145+\coordindex*10}
+                    anchor=-145+\coordindex*10
+                }
             ]
@@
 
+\begin{table}
+  \centering
+    \footnotesize
+    %\tabcolsep=0.11cm
+    \pgfplotstabletypeset[
+        comment chars=!,%use ! before a row in the data table to exclude it
+        col sep=tab,
+        %columns={Algorithm,Snapshot Read/Write,Network Transfer,Index access and comparison},
+        columns={Algorithm,ReadWrite,Network,Index},
+        columns/Algorithm/.style={
+            string type,
+            column name={\multirow{2}{*}{Algorithm}}
+        },
+        columns/ReadWrite/.style={
+            column name={
+                \multicolumn{3}{c|}{Time Spent in Task (ms)}\\&
+                Read/Write
+            },
+            multiply by={1000},
+            %preproc cell content/.code={1#1 1},
+            fixed, precision=3
+        },
+        columns/Network/.style={
+            column name={Network},
+            multiply by={1000},
+            fixed, precision=3
+        },
+        columns/Index/.style={
+            column name={Index Lookup},
+            multiply by={1000},
+            fixed, precision=3
+        },
+        every head row/.style={
+            before row={\hline},
+            after row={\hline},
+        },
+        every last row/.style={after row=\hline},
+        column type/.add={}{|},
+        every first column/.style={column type/.add={|}{}},
+    ]{figures/vc_srb_combined_pgfplots.txt}
+    \caption{Average time to backup a dirty VM segment under SRB and VC
+        \todo{Decide between this and bar plot with the same caption}
+    }
+    \label{tab:vc_srb_combined}
+\end{table}
+
 \begin{figure}[htbp]

### 2014-01-30 snapshot_system/paper_background.tex
update deletion eval

@@
 other cloud services as illustrated in Figure~\ref{fig:collocated},
-and thus minimize its impact on user-deliverable performance.
+and has to minimize its impact on user-deliverable performance.
 %The key resource for global comparison  is memory for storing the fingerprints.
@@
 
-In designing a VC duplication solution, we have considered and adopted some of
+In designing a VC deduplication solution, we have considered and adopted some of
 the following previously-developed techniques.
@@
 One approach to scalable duplicate comparison is to use a content-based hash
-partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011} 
+partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011}.
 Stateless data routing divides the deduplication work with a similarity approximation. This work 

### 2014-01-30 snapshot_system/paper_eval.tex
update deletion eval

@@
 storage space per VM caused  by approximate deletions.
+We choose 35 VMs, first let all the VMs accumulate to 10 snapshots, then start to delete snapshots
+in reverse order from the latest to the second using approximate deletion.
+As we already know the actual storage needs after each snapshot creation,
+thus the storage leakage can be verified by
+comparing the size of remain data in use after deletion to what it should be.
 The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
 given $\Delta u/u=0.025$,
-while the solid line represents the actual leakage measured during the experiment. 
+while the solid line represents the actual average leakage measured during the experiment for all the VMs. 
 The Bloom filter setting is based on $\Delta u/u=0.025$.

### 2014-01-30 snapshot_system/paper_arch.tex
revised
Rich tightens a bit

@@
-\section{Architecture and Implementation Details}
+\section{Prototype Implementation}
 \label{sect:architecture}
 
-Our system runs on a cluster of Linux machines with Xen-based VMs and
-an open-source package for the distributed file system  called QFS~\cite{michael2013}. 
+Our prototype system runs on a cluster of Linux machines with Xen-based VMs 
+and the QFS~\cite{michael2013} distributd file system. 
 %to %manage  the physical disk storage. 
@@
 
-\subsection{ Components of a Cluster Node } 
+\subsection{Per Node Software Components} 
 As depicted in Figure~\ref{fig:arch_vm}, 
@@
 We use the virtual device driver in Xen that employs a bitmap to track the changes 
-that have been made to the virtual disk (CBT).
+that have been made to the virtual disk.
 Every bit in the bitmap represents a fixed-sized (2MB) segment, indicating whether the segment
@@
     \includegraphics[width=2.75in]{images/socc_arch_cluster}
-    \caption{System architecture and data flow during snapshot backup}
+    \caption{Per node architecture and data flow during snapshot backup}
     \label{fig:arch_vm}
@@
 \label{sect:store}
-We build the snapshot storage on the top of a distributed file system.
+We use the QFS distributed file system to hold snapshot backups.
 Following the VM-centric idea for the purpose of fault isolation,
@@
   \includegraphics[width=2.75in]{images/sstore_arch}
-  \caption{Data structure of a VM snapshot store.}
+  \caption{VM snapshot store data structures}
   \label{fig:as_arch}

### 2014-01-30 snapshot_system/paper_dedup.tex
update deletion eval
Rich tightens a bit

@@
 
-\subsection{VM centric  strategies}
-\label{sect:vc-strategies}
+%\subsection{VM centric  strategies}
+%\label{sect:vc-strategies}
 
@@
 %\item
-\paragraph*{VM-local duplicate search optimization} --
 
+\textbf{VM-local duplicate search optimization} --
 We use the standard version-based detection~\cite{Clements2009,Vrable2009}
@@
 It should be noted that dirty bit tracking is supported or can be easily implemented in 
-major virtualization solution vendors. For example,
-the VMWare hypervisor has an API to let external backup applications know 
-the changed areas since last backup. 
-The Microsoft SDK provides an API that allows external applications to monitor 
-the VM's I/O traffic and implement such changed block tracking feature.
+major virtualization solution vendors. 
+%% this method is so widely-used and easy to understand, everyone include Pure Storage has it, I feel no need to explain further.
+%{
+%For example,
+%the VMWare hypervisor has an API to let external backup applications know 
+%the changed areas since last backup. 
+%The Microsoft SDK provides an API that allows external applications to monitor 
+%the VM's I/O traffic and implement such changed block tracking feature.
+%}
 
@@
 %\item 
-\paragraph*{Global deduplication using popular chunks} --
+\textbf{Global deduplication using popular chunks} --
 This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
@@
 %\item 
-\paragraph*{VM-centric file system block management} --
+\textbf{VM-centric file system block management} --
 When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written

### 2014-01-30 snapshot_system/paper_eval.tex
Rich tightens a bit

@@
 {\bf Processing Time breakdown}.
-Figure~\ref{fig:vc_srb_combined} shows
+Table~\ref{tab:vc_srb_combined} shows
 the  average  processing  time of  a VM segment under VC and SRB. 
@@
 
-\begin{table}
+\begin{table}[t]
   \centering
@@
     \caption{Average time to backup a dirty VM segment under SRB and VC
-        \todo{Decide between this and bar plot with the same caption}
+%        \todo{Decide between this and bar plot with the same caption}
     }
@@
 
-\begin{figure}[htbp]
-  \centering
-  \epsfig{file=figures/vc_srb_combined, width=3in}
-  \caption{Average time to backup a dirty VM segment under SRB and VC}
-  \label{fig:vc_srb_combined}
-\end{figure}
+%\begin{figure}[htbp]
+%  \centering
+%  \epsfig{file=figures/vc_srb_combined, width=3in}
+%  \caption{Average time to backup a dirty VM segment under SRB and VC}
+%  \label{fig:vc_srb_combined}
+%\end{figure}
 
@@
 % \end{table*}
-\begin{table}[htbp]
+%\begin{table}[htbp]
+\begin{table}[t]
 \begin{small}
@@
  \begin{figure}
+\vspace{-0.1in}
      \centering

### 2014-01-30 snapshot_system/paper_analysis.tex
updated VO/VC VM->FSB mapping figure with N0/1/2.
Rich tightens a bit
as dense as I could make it

@@
-\begin{table}[htbp]
+%\begin{table}[htbp]
+\begin{table}[t]
 \centering
@@
 
-\subsection{ Impact on Fault Isolation}
+\subsection{Fault Isolation}
 
@@
 \[
-n* N_1   \approx \mbox{ No of non-PDS file system blocks} 
+n* N_1   \approx \mbox{ Number of non-PDS file system blocks} 
 \]
@@
 \[
-n *N_o   =  V_o *\mbox{ No of file system blocks} 
+n *N_o   =  V_o *\mbox{ Number of file system blocks} 
 \]
@@
 
-For VC, there are two cases: 
-\begin{itemize}
-\item
-When $r \le d<r_c$,  there is no PDS data loss and we need to look at the non-PDS data loss. 
+For VC, there are two cases: $r \le d<r_c$ and $r_c \leq d$.
+
+\noindent $r \le d<r_c$:  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
 The full snapshot availability of a VM is: 
@@
 
-\item
-When $r_c \leq d$, both non-PDS and PDS file system blocks in VC can have a loss.
+\noindent $r_c \leq d$: Both non-PDS and PDS file system blocks in VC can have a loss.
 The full snapshot availability of  a VM in the VC approach is
@@
 %comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
-\end{itemize} 
 %In the evaluation discussed in Section~\ref{sect:evaldedup},

### 2014-01-30 snapshot_system/paper_eval.tex
revise

--- 2014-01-30 snapshot_system/paper_eval.tex
@@
  Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
-there are up to 20 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
+there are up to 20 machine nodes failed in a cluster with $p=100$ physical machines.
+The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
+and thus calculate the average availability of VM snapshots.
+The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
+the same from $p=100$ setting to $p=1000$. With differnet $p$ values, how the availability varies when 
+the number of failures in the cluster changes.
+
 %Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
@@
 %case for VO approach. 
-Our results show that VC has a significantly  higher availability than VO as the number of
-failed machines increases.
+Our results show that VC  has a significantly  higher availability than VO as the number of failed machines increases.
 %Our VM-centric approach shows significant improvements
 %in VM availability.
-For example, with 3/100 machines failed and 25 VMs per machine, VO with 69.5\% availability could lose data in 763 VMs 
-while VC with 99.7\% loses data for 8 VMs.
-The key reason is that for most data in VC, only a single VM can be affected by
-the loss of a single file block. Since most blocks contain chunks for a single
-VM, VMs can depend on a smaller number of blocks, while in VO, the loss of a
-single block tends to affect many VMs.
+For example, with 5/100 machines failed and 25 VMs per machine, VO with 93.256\% availability would lose data in 169 VMs 
+while VC with 97.763\% loses data for 56 VMs.
+The key reason is that for most data in VC, only a single
+VM can be affected by the loss of a single FSB. Since most FSBs contain chunks for a single VM, VMs can depend on a smaller number of FSBs.
 % because our VM-centric approach
@@
 Although the loss of a PDS block affects many VMs,
-by increasing replication for those blocks we minimize the effect on VM
-snapshot availability, and this is one of the key contributions of our
-approach, the clear separation of highly popular data from less popular data.
+by increasing replication for those blocks we minimize the effect on VM snapshot availability.
 %By having extra replicas for the PDS data, we reduce the failure rate of PDS
@@
 the impact of increasing PDS data replication. 
-While the impact on storage cost is small (because we have separated out only
-the most popular blocks),
-a replication degree of 6  has a significant improvement over 4. The
-availability is very similar
-for $r_c=6$ and $r_c=9$, and beyond $r_c=6$ improvements are minimal.
+While the impact on storage cost is small, 
+a replication degree of 6  has a significant improvement over 4, but the availability is about
+the same for $r_c=6$ and $r_c=9$ (beyond $r_c=6$ improvements are minimal).
 
@@
 
-\comments{
 \begin{figure}[htb]
@@
                 %\addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
-                %\addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                 \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
@@
                     %VO,
-                    %$r_c=4$,
+                    $r_c=4$,
                     $r_c=5$,
@@
 
-}
-
 \subsection{Deduplication Efficiency}
@@
 
-\comments{
 %this version combines the old and the minhash alg. to compare against srb
@@
 
-}
-
 \begin{figure}[]
@@
         \begin{axis}[
-                width=\linewidth,
-                height=0.6\linewidth,
                 ybar,
-                bar width=0.5cm,
-                ymax=98.7,
-                enlarge x limits=0.15,
-                style=thin,
-                ylabel={Dedup. Efficiency (\%)},
-                ytick={93,94,95,96,97,98},
-                xtick=\empty,
-                ymajorgrids,
-                grid style=densely dotted,
-                %symbolic x coords={VC-No PDS, VC-2\%PDS w/o similarity, VC-2\%PDS, VC-4\%PDS, SRB},
-                %symbolic x coords={VC0, VC2N, VC2, VC4, SRB},
+                xtick=data,
+                %symbolic x coords={VC(No PDS), VC($\sigma=2\%$\, No similarity guidance), VC($\sigma=2\%$), VC( $\sigma=4\%$), SRB},
+                symbolic x coords={VC0, VC2N, VC2, VC4, SRB},
                 %xticklabels from table={figures/efficiency_comparison_bars.txt}{alg}
-                nodes near coords,
-                every node near coord/.append style={
-                    anchor=-145+\coordindex*10
-                }
             ]
-            %\addplot[fill=blue] coordinates {(VC0,93.02) (VC2N,94.31) (VC2,96.01) (VC4,96.58) (SRB,97.86)};
-            %\addplot[fill=blue] coordinates { (VC-No PDS,93.02) (VC-2\%PDS w/o similarity,94.31) (VC-2\%PDS,96.01) (VC-4\%PDS,96.58) (SRB,97.86) };
-            \addplot [%
-                point meta=explicit symbolic,
-                fill=blue
-            ] table [x expr=\coordindex, y=efficiency,meta=alg] {figures/efficiency_comparison_bars.txt};
+            \addplot[fill=blue] coordinates {(VC0,93.02) (VC2N,94.31) (VC2,96.01) (VC4,96.58) (SRB,97.86)};
         \end{axis}
@@
     \caption{Efficiency Comparison between different VC settings and SRB}
-    \label{fig:efficiency-comparison}
+    \label{tab:efficiency-comparison}
 \end{figure}
 
-Figure~\ref{fig:efficiency-comparison} shows the deduplication efficiency for SRB and VC using different settings,
+Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC,
 % <<<<<<< HEAD
@@
 % =======
-that is the percent of duplicate chunks
+namely the percent of duplicate chunks
 which are detected and removed.
@@
 With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
-and  the deduplication efficiency can reach over 96\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 96.6\% while space consumption increases to 200MB per machine. 
+and  the deduplication efficiency can reach over 96.33\%.
+When $\sigma=4\%$, the deduplication efficiency can reach 96.9\% while space consumption increases to 200MB per machine. 
 %and  the deduplication efficiency can reach 96.489\%.
@@
 %index ($\sigma=100\%$) then VC will have 100\% efficiency.
-SRB can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
+SRB can deliver up to 97.79\% deduplication efficiency, which is slightly better than VC.
 Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
-with a slight reduction in deduplication efficiency.
+with competitive deduplication efficiency.
 
@@
 
-Figure~\ref{fig:efficiency-comparison} also shows the efficiency of VC without local similarity search.
-%There is a big efficiency drop in this curve when the number of VMs is about 30.
-The reason similarity search provides such an improvement is that
+Figure~\ref{fig:exbin-efficiency-graph2} also shows the curve  of VC without local similarity search.
+There is a big efficiency drop in this curve when the number of VMs is about 30.
+The reason is that  
 %Without this (i.e. when we only 
@@
 rather than modified in place,  
-and a dirty-bit or offset-only based detection would not be able to detect such a movement.
-We have found that in
+a dirty-bit or offset based detection would not be able to detect such a movement and 
+similarity search becomes especially important.  We have found that in
 approximately 1/3 of the VMs in our dataset this movement happens frequently.
-In general, adding local similarity-guided search increases deduplication efficiency from 94\% to over 96\%.
+In general, adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
 That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
@@
 
-\begin{table}
-  \centering
-    \footnotesize
-    %\tabcolsep=0.11cm
-    \pgfplotstabletypeset[
-        comment chars=!,%use ! before a row in the data table to exclude it
-        col sep=tab,
-        %columns={Algorithm,Snapshot Read/Write,Network Transfer,Index access and comparison},
-        columns={Algorithm,ReadWrite,Network,Index},
-        columns/Algorithm/.style={
-            string type,
-            column name={\multirow{2}{*}{Algorithm}}
-        },
-        columns/ReadWrite/.style={
-            column name={
-                \multicolumn{3}{c|}{Time Spent in Task (ms)}\\&
-                Read/Write
-            },
-            multiply by={1000},
-            %preproc cell content/.code={1#1 1},
-            fixed, precision=3
-        },
-        columns/Network/.style={
-            column name={Network},
-            multiply by={1000},
-            fixed, precision=3
-        },
-        columns/Index/.style={
-            column name={Index Lookup},
-            multiply by={1000},
-            fixed, precision=3
-        },
-        every head row/.style={
-            before row={\hline},
-            after row={\hline},
-        },
-        every last row/.style={after row=\hline},
-        column type/.add={}{|},
-        every first column/.style={column type/.add={|}{}},
-    ]{figures/vc_srb_combined_pgfplots.txt}
-    \caption{Average time to backup a dirty VM segment under SRB and VC
-        \todo{Decide between this and bar plot with the same caption}
-    }
-    \label{tab:vc_srb_combined}
-\end{table}
-
 \begin{figure}[htbp]
@@
 
+%In this experiment, we start with the incremetnal backup of 10 versions of 100 VMs with a total of 1,000 snapshots.
 Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of

### 2014-01-30 batchdedup/intro.tex

@@
 identifies redundant content duplicates among snapshots.  
-One architectural approach is to attach  a separate backup system with deduplication
-support to the cloud cluster, and  every machine periodically transfers snapshots to
+One architectural approach is to attach  a separate backup system with deduplication support such as ones
+from  EMC~\cite{EMC} or NetApp{NetApp}
+to the cloud cluster, and  the snaphosts of every virtual machine is   periodically transferred to
 the attached backup system.  Such a dedicated backup  configuration can be expensive, 
-considering that significant networking  and computing resource  is required to transfer 
-raw data and conduct signature comparison.
+considering that significant networking  and computing resource  is required 
+to transfer undeduplicatd data and conduct signature comparison. 
+Our work is targeted applications where data processing and archiving  can be conducted
+in an inexpensive commodity storage cluster using the  Google file system or Hadoop~\cite{googlefs03}
+and such a storage cluster is non-dedicated, shared with other services running in the entire cluster.
+Resource sharing is common especially in the cloud where many computing and storage
+services are collocated in the same physical machines.
 
-This paper seeks for a low-cost architecture option and considers a backup
-service that uses the existing cloud computing resource.
+With  resource sharing with other services as an assumption, we are motivated to develop a 
+low-profile backup solution with deduplication. 
+Deduplication is a major
+
+%This paper seeks for a low-cost architecture option and considers a backup
+%service that uses the existing cloud computing resource.
 %Since most of backup data is not used in practice, system resource in such a service is not fully utilized. 

### 2014-01-30 snapshot_system/paper_dedup.tex

@@
 we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
-
-Figure~\ref{fig:Datazipf} illustrates the distribution of chunk popularity based on a data trace from Alibaba with over 2500 VMs.
-The distribution is zipf like and popular chunks are dominating the large portion of data chunks.
+We have studied the distribution of chunk popularity~\cite{WeiZhangIEEE} 
+based on a data trace from Alibaba with over 2500 VMs.
+The distribution is zipf-like and popular chunks are dominating the large portion of data chunks.
 We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
 $\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.
+
+% Figure~\ref{fig:Datazipf} illustrates the distribution of chunk popularity based on a data trace from Alibaba with over 2500 VMs.
+% The distribution is zipf like and popular chunks are dominating the large portion of data chunks.
+% We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
+% $\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.
 
@@
 
-\begin{figure}
-\centering
-%\epsfig{file=log-log.disk,width=3in}
-%source ../vm_snapshot_sim/images/log-log.disk.eps
- \includegraphics[width=3in]{figures/log-log-disk}
-\caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
-\label{fig:Datazipf}
-\end{figure}
+% \begin{figure}
+% \centering
+%  \includegraphics[width=3in]{figures/log-log-disk}
+% \caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
+% \label{fig:Datazipf}
+% \end{figure}
 

### 2014-01-30 snapshot_system/paper_abs.tex
revised

@@
 %and fault isolation 
-This paper proposes a VM-centric backup service on a converged  storage cluster architecture
+This paper proposes a VM-centric backup service on a converged  cloud cluster architecture
 and  strikes a tradeoff for better fault isolation with competitive  deduplication efficiency.
@@
 and proposes an approximate method for fast and simplified snapshot deletion.
-This VM-centric scheme also has  an advantage of   using less  computing resources, suitable for a collocated 
-backup service on a non-dedicated cluster architecture.
+This VM-centric scheme also has  an advantage of   using less  computing resources, suitable for running
+the backup service on a converged cloud architecture that cohosts  many other services.
 This  paper  describes an evaluation of this scheme to assess  its deduplication 

### 2014-01-30 snapshot_system/paper_analysis.tex
fixed various warnings, made other minor formatting adjustments
revised

@@
 \hline
-$r$, $r_c$ & replication degree of non-PDS, and PDS file blocks in VC\\
+$r$, $r_c$ & replication degree of non-PDS and PDS file blocks in VC. $r$ is also replication degree in VO.\\
 \hline
@@
 \hline
-$N_1$, $N_2$ & the average number  of non-PDS and PDS file blocks in a VM for VC\\
+$N_1$, $N_2$ & the average no.  of non-PDS and PDS file blocks in a VM in VC\\
 \hline
-$N_o$ & the average number  of file blocks  in a VM for VO\\
+$N_o$, $V_o$ & the average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
 \hline
@@
 
-We analyze the impact of the above VM centric design on fault isolation and compare it
-with a VM oblivious design.
+%We analyze the impact of the above VM centric design on fault isolation and compare it
+%with a VM oblivious design.
 %Let $r$ be the replication degree of standard file blocks in the underlying backup storage. 
@@
 %Let $r_c$ be the replication degree of file blocks for PDS. 
-Parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
 %The replication degree of the backup storage 
@@
 
-Now we  assess  the impact of losing $d$ machines 
+Now we  analyze  the impact of losing $d$ physical machines 
 to the VM centric and oblivious approaches.  
+Parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
 %A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
@@
 association from unique file system blocks to their corresponding VMs in two 
-approaches. We use a file system block rather than data chunk as our unit of failure
-because the underlying file system keeps file system blocks as its base unit of storage, and in
-the case of 64MB file system blocks  and 4KB chunks, there are 16K chunks per file block. For VM centric,
-we assign extra replication to the PDS blocks, while for VM oblivious, the replication
-degree is fixed.
-
+approaches. 
+%We use a file system block rather than data chunk as our unit of failure
+%because the underlying file system keeps file system blocks as its base unit of storage, and in
+%the case of 64MB file system blocks  and 4KB chunks, there are 16K chunks per file block. For VM centric,
+%we assign extra replication to the PDS blocks, while for VM oblivious, the replication
+%degree is fixed.
 For VC, each VM has an average number $N_1$ of non-PDS file system blocks
 and  has  an average of  $N_2$ PDS file system blocks. 
-Each non-PDS block is associated with one VM
- and  we denote that PDS blocks are
-shared by an average of $V_c$ VMs. 
-Then, 
+Each non-PDS block is associated with only one VM.
+% and  we denote that PDS blocks are shared by an average of $V_c$ VMs. 
+Then by counting outgoing edges from VMs in Figure~\ref{fig:share}(a),
 \[
-n* N_1   \approx \mbox{ Number of non-PDS file system blocks} 
+n* N_1   = \mbox{ Number of non-PDS file system blocks in VC.} 
 \]
 
-For VO, each VM has an average of $N_o$ file system blocks
-and let $V_o$ be the average number of VMs shared by each file block.
+For VO, 
+%each VM has an average of $N_o$ file system blocks
+%and let $V_o$ be the average number of VMs shared by each file block.
+by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
+Table~\ref{tab:symbol}: 
 \[
-n *N_o   =  V_o *\mbox{ Number of file system blocks} 
+n *N_o   =  V_o *\mbox{ Number of file system blocks in VO.} 
 \]
 
-Since the number of PDS file system blocks is small, 
-and the deduplication efficiency of VC is very close to that of VO,
-Section~\ref{sect:evaluation} shows that
-the number of non-PDS file blocks in VC is close to the number of file blocks in VO.
+Since we choose 2-4\% of unique chunks for PDS
+and Section~\ref{sect:evaldedup} 
+shows that the deduplication efficiency of VC is very close to that of VO,
+the number of non-PDS file blocks in VC is approximately close to the number of file blocks in VO.
 Then
@@
 		xlabel={Number of VMs},
-		ylabel={Avg. no file system blocks  used by VM},
+		ylabel={file system blocks},
                 xmin=0,
@@
 % $N_2$ for VC and $N_o$ for VO.
-Given $d$ failed physical machines and $r$ replicas fr each block,
+Given $d$ failed physical machines and $r$ replicas for each file block,
 %normal data replication degree $r$, PDS data replication degree $r_c$, 

### 2014-01-30 snapshot_system/paper_background.tex
revised

@@
 each commodity server hosts a number of virtual machines and storage of these servers
-is clustered using a distributed file system~\cite{googlefs03,hdfs10}.
+is clustered using a distributed file system~\cite{googlefs03,hdfs10,NutanixPaper}.
 Each physical machine hosts multiple virtual machines.  Every virtual machine

### 2014-01-30 snapshot_system/paper_dedup.tex
revised

@@
 
+\comments{
 It should not be noted that one could consider 
 to rely on filesystem features to provide more replication to popular
-blocks, without the extra complexity of separating popular and non-popular
-data. The main problem with this  approach is that without separating the
+chunks.
+%, without the extra complexity of separating popular and non-popular
+%data. 
+The main problem with this  approach is that without separating the
 popular chunks from the less-popular, the popular chunks are dispersed across
@@
 have to add extra replication to each file block as long as it contains a popular chunk.
-
+}
 %factor on popular chunks. This explains why we must separate the PDS and

### 2014-01-30 snapshot_system/paper_eval.tex
fixed various warnings, made other minor formatting adjustments
revised

--- 2014-01-30 snapshot_system/paper_eval.tex
@@
 \subsection{Settings}
-We have performed a trace-driven study using a production dataset~\cite{WeiZhangIEEE} from 
-Alibaba Aliyun's cloud platform with about 100 machines. 
+We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
+Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
 Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage system while
@@
 %The backup of VM snapshots is required to complete within few  hours every night.
-Based on our study of production  data,  each VM has about 40GB of storage  data  on average
+Each VM has about 40GB of storage  data  on average
 including OS and user data disk.
+The daily snapshot change rate is about 2-3\% on average.
 %All data are divided into 2 MB fix-sized segments and 
@@
 %case for VO approach.
+
 Our results show that VC has a significantly  higher availability than VO as the number of

### 2014-01-30 snapshot_system/paper_intro.tex
update deletion eval
revised

@@
 servers as a way of avoiding the relatively high cost of network attached 
-storage~\cite{googlefs03,hdfs10}.
+storage~\cite{googlefs03,hdfs10,NutanixPaper}.
 %systems. %This(e.g. ~\cite{NutanixPaper}).  Leading cloud platform companies
@@
 We describe methodologies to address the following two challenges: 
-\begin{itemize}
-\item simple deduplication and snapshot deletion with competitive efficiency and 
-a small resource usage without affecting other collocated cloud services.
-\item augmented fault isolation for the sharing of deduplicated data,
+1) simple deduplication and snapshot deletion with competitive efficiency and 
+a small resource usage without affecting other collocated cloud services;
+2) augmented fault isolation for the sharing of deduplicated data,
 given that node failures in converged architecture are the norm rather than
@@
 % so that users stop incurring storage charges immediately after snapshot deletion.
-\end{itemize}
+%\end{itemize}
 
@@
 %similarity-guided elimination to improve the deduplication coverage.  
-Since
-the file system block size is normally bigger than the average data chunk size
+Since the underlying storage file system block size is typically bigger than the average data chunk size
 used for deduplication,  packaging
 content from different VMs into the same file block  creates a ``false'' sharing that 
-affects fault isolation. Thus we avoid such VM-oblivious packaging.
+affects fault isolation. Thus we choose to avoid such VM-oblivious packaging.
 %our approach uses a deduplication data chunk size that is smaller than a

### 2014-01-30 snapshot_system/paper_eval.tex

@@
 
-\comments{
+\comments{ %replaced by table below to recuce space requirements
 \begin{figure}[ht]
@@
 
-\begin{figure}[]
+\begin{figure}[htb]
     \centering
@@
     \end{tikzpicture}
-    \caption{Efficiency Comparison between different VC settings and SRB}
+    \caption{Efficiency comparison between different VC settings and
+        Stateless Routing with Binning}
     \label{fig:efficiency-comparison}
@@
 Table~\ref{tab:vc_srb_combined} shows
-the  average  processing  time of  a VM segment under VC and SRB. 
+the  average  processing  time of  a VM segment under VC and Stateless Routing with Binning (SRB). 
 VC uses $\sigma=2\%$ and $4\%$.
 It has a breakdown of processing time.
-``Snapshot read/write'' includes snapshot reading and writing from disk, and 
+``Read/Write'' includes snapshot reading and writing from disk, and 
 updating of the metadata.
-`` Network transfer" includes the cost of transferring raw and meta data from one machine to another during 
+``Network'' includes the cost of transferring raw and meta data from one machine to another during 
 snapshot read and write.
-``Index access/comparison'' is the disk, network and CPU time during fingerprint comparison.
-This includes PDS data lookup for VC and index lookup from disk in VO after Bloom filter lookup.
+``Index Lookup'' is the disk, network and CPU time during fingerprint comparison.
+This includes PDS data lookup for VC and index lookup from disk in SRB after Bloom filter lookup.
 For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
@@
  while VC only involves few containers with a bigger size. Thus, there are more opportunities for I/O aggregation in VC to reduce seek time.
-SRB has a higher cost for index access and fingerprint comparison because most of  chunk fingerprints are routed
-to remote machines for comparison while   VC handles most of chunk fingerprints locally.
+SRB also has a higher cost for index access and fingerprint comparison because most chunk fingerprints are routed
+to remote machines for comparison while   VC handles most chunk fingerprints locally.
 

### 2014-01-31 snapshot_system/paper_dedup.tex
revise

--- 2014-01-30 snapshot_system/paper_dedup.tex
@@
 
-It should not be noted that one could consider 
-to rely on filesystem features to provide more replication to popular
-blocks, without the extra complexity of separating popular and non-popular
-data. The main problem with this  approach is that without separating the
+%One could try to rely on filesystem features to 
+If we do not separate the
 popular chunks from the less-popular, the popular chunks are dispersed across
-all of the filesystem blocks in the storage system.  We would
-have to add extra replication to each file block as long as it contains a popular chunk.
+all of the filesystem blocks in the storage system.  Then we cannot leverage the file system features to 
+provide extra replication to popular and shared chunks because  
+we have to add extra replication to each file block as long as it contains a popular chunk.
 

### 2014-01-31 snapshot_system/paper_eval.tex
revise

@@
 Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
-Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage system while
-a user may instruct extra snapshots to be saved.
+Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
+system while a user may instruct extra snapshots to be saved.
+Each VM has about 40GB of storage  data  on average
+including OS and user data disk.
+Each physical machine deals with about 10TB of snapshot data.
 The VMs of the sampled data set use popular operating systems such as 
@@
 %The backup of VM snapshots is required to complete within few  hours every night.
-Each VM has about 40GB of storage  data  on average
-including OS and user data disk.
 The daily snapshot change rate is about 2-3\% on average.
@@
 Our results show that VC has a significantly  higher availability than VO as the number of
-failed machines increases.
+failed machines increases from 3 to 20
+in this table.
 %Our VM-centric approach shows significant improvements
 %in VM availability.
-For example, with 3/100 machines failed and 25 VMs per machine, VO with 69.5\% availability could lose data in 763 VMs 
+With $p=100$ and 3 machine failures,
+there are 2500 VMs in total. VO with 69.5\% availability could lose data in 763 VMs 
 while VC with 99.7\% loses data for 8 VMs.
@@
 single block tends to affect many VMs.
+When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
+and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
+loses most of non-PDS blocks given the replication degree for non PDS is 3.
+On the other hand, when $p=1000$, the pecetnage of machine failure is then 2\% and
+ VC outperforms VO significantly in availabilty in this case by delivering a meaningful avaiability with 99.62\%.
+
 % because our VM-centric approach
@@
 
-Although the loss of a PDS block affects many VMs,
-by increasing replication for those blocks we minimize the effect on VM
-snapshot availability, and this is one of the key contributions of our
-approach, the clear separation of highly popular data from less popular data.
+%Although the loss of a PDS block affects many VMs,
+%by increasing replication for those blocks we minimize the effect on VM
+%snapshot availability, and this is one of the key contributions of our
+%approach, the clear separation of highly popular data from less popular data.
+
 %By having extra replicas for the PDS data, we reduce the failure rate of PDS
@@
 Figure~\ref{fig:pds-replication} shows
-the impact of increasing PDS data replication. 
+the impact of increasing PDS data replication degree. 
 While the impact on storage cost is small (because we have separated out only
@@
 a replication degree of 6  has a significant improvement over 4. The
-availability is very similar
-for $r_c=6$ and $r_c=9$, and beyond $r_c=6$ improvements are minimal.
+availability does not increase much  when increasing
+$r_c$ from 6 to 9 and the benefit is not so visible after $r_c>9$. 
+That is because when the number of failed machines increases beyond 6, 
+the non-PDS data availability starts to deteroriate significantly given its replication degree
+$r$ is fixed as 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.
 
@@
 
-\comments{ %replaced by table below to recuce space requirements
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}%{.5\textwidth}
-      \centering
-      %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
-            \begin{tikzpicture}
-                    \begin{axis}[
-                    tick label style={font=\scriptsize},
-                    tick style=thin,
-                    width=0.5\linewidth,
-                    title={\small $p=100$},
-                    cycle list={
-                        {blue,thin,solid,mark=none},
-                        {red,thin,densely dashed,mark=none},
-                        {red,thin,densely dotted,mark=none}
-                    },
-                    xlabel={\tiny Failed nodes},
-                    ylabel={\tiny Snapshot Availability (\%)},
-                    %extra y ticks={99.9}, %if important numbers are missing
-                    mark options=solid,
-                    legend columns=-1,
-                    legend style={
-                        font=\small\sffamily,
-                        cells={anchor=west}, %legend entry alignment
-                        legend pos=south west %legend position
-                    },
-                    legend to name=legend:vm-availability,
-                    %reverse legend,
-                    ]
-                    \addplot table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
-                    \addlegendentry{VO}
-                    \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
-                    \addlegendentry{VC}
-                    %\addplot table[x=NodesFailed,y=VCOpt1]{figures/node_failures_100.txt};
-                    %\addlegendentry{VC (CDS ordering)}
-                    \end{axis}
-            \end{tikzpicture}
-      %\caption{100 machine cluster.}
-      \label{fig:vm-availability-100}
-    \end{subfigure}%
-    \begin{subfigure}%{.5\textwidth}
-  \centering
-  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
-	\begin{tikzpicture}
-            %the expressions in this plot are simply to trick pgfplots into not expanding the y range, and don't actually change the data
-            % expression used: (99.999+((y-99.999)*1000)/1000)
-            \pgfplotsset{/pgf/number format/.cd,
-                fixed,precision=4}
-		\begin{axis}[
-                    width=0.5\linewidth,
-                    tick label style={font=\scriptsize},
-                    tick style=thin,
-		title={\small $p=1000$},
-                %ymin=099.9991,
-                %ymax=100.0002,
-                %ytick=data,
-                %yticklabels from table={figures/vm_availability_1000.txt}{[index]1},
-                yticklabel={%this is a hack to get around the small yrange
-                    \pgfmathfloatparse{99.999+\tick/1000}
-                    \pgfmathprintnumber{\pgfmathresult}
-                },
-                cycle list={
-                    {blue,thin,solid,mark=none},
-                    {red,thin,densely dashed,mark=none},
-                    {red,thin,densely dotted,mark=none}
-                },
-		xlabel={\tiny Failed nodes},
-		ylabel={\tiny Snapshot Availability (\%)},
-		%extra y ticks={99.99}, %if important numbers are missing
-                mark options=solid,
-                legend style={
-                    cells={anchor=west}, %legend entry alignment
-                    legend pos=south west %legend position
-                },
-                %reverse legend,
-		]
-                %\addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
-                \addplot table[x=NodesFailed,y expr=(\thisrow{VO}-99.999)*1000]{figures/node_failures_1000.txt};
-                %\addlegendentry{$VO\,6.3$ (optimistic)}
-                %\addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
-                \addplot table[x=NodesFailed,y expr=(\thisrow{VC3}-99.999)*1000]{figures/node_failures_1000.txt};
-                %\addlegendentry{$VC\,1250$ (estimated)}
-                %\addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
-                \addplot table[x=NodesFailed,y expr=(\thisrow{VCWC1}-99.999)*1000]{figures/node_failures_1000.txt};
-                %\addlegendentry{$VC\,2500000$ (worst-case)}
-                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
-                %\addlegendentry{$VO\,20$ (optimistic)}
-		\end{axis}
-	\end{tikzpicture}
-        %\caption{1000 machine cluster.}
-  \label{fig:vm-availability-1000}
-\end{subfigure}
-    \pgfplotslegendfromname{legend:vm-availability}
-      \caption{Availability of VM snapshots for VO and VC when failed machines vary
-from 1 to 40.  Non-PDS replication is fixed
-at 3 and PDS replication is 6 \emph{THIS PLOT IS BEING REPLACED BY A TABLE} 
-      }
-      \label{fig:vm-availability}
-
-\end{figure}
-}
 \begin{table}
@@
     ]{figures/availability_table.txt}
-    \caption{Availability of VM snapshots for VO and VC ($r_c=6$).}
+    \caption{Availability of VM snapshots for VO ($r=3$) and VC ($r_c=6$, $r=3$).}
     \label{tab:vm-availability}
@@
 	\end{tikzpicture}
-  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
+  \caption{Availability of VM snapshots in VC with different PDS replication degrees on a $p=100$-node cluster.}
   \label{fig:pds-replication}
@@
 
-\comments{
-\begin{figure}[htb]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-                        width=\linewidth,
-                        height=0.6\linewidth,
-		%title={PDS Replication affect on availability},
-		xlabel={Failed storage nodes},
-		ylabel={VM Snapshot Availability (\%)},
-                xmin=0,
-                xmax=20,
-		%extra y ticks={99.9}, %if important numbers are missing
-                mark options=solid,
-                legend style={
-                    cells={anchor=west}, %legend entry alignment
-                    legend pos=south west %legend position
-                },
-                reverse legend,
-		]
-                %\addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
-                %\addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
-                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
-                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
-                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
-                \legend{
-                    %VO,
-                    %$r_c=4$,
-                    $r_c=5$,
-                    $r_c=6$,
-                    $r_c=9$
-                }
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Availability of VM snapshots in VC with different PDS replication degrees \todo{decide which one}}
-  \label{fig:pds-replication-old}
-\end{figure}
-
-}
-
-\subsection{Deduplication Efficiency}
+\subsection{Competitiveness of Deduplication Efficiency}
 \label{sect:evaldedup}
@@
 \comments{
-%this version combines the old and the minhash alg. to compare against srb
-\begin{figure}[ht]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={Ex-Binning Efficiency},
-            width=\linewidth,
-            height=0.75\linewidth,
-            cycle list={%
-                {blue,solid,mark=square*},
-                {blue,solid,mark=triangle*,mark size=1.5},
-                {blue,solid,mark=diamond*,mark size=1.5},
-                %{blue,solid,mark=pentagon*,mark size=1.4},
-                {red,draw=red,dotted,mark=square},
-                %{red,densely dotted,mark=triangle,mark size=1.5},
-                %{red,densely dotted,mark=diamond,mark size=1.5},
-                {brown,dashed,mark=*},
-                %{red,densely dotted,mark=o},
-                %{red,densely dotted,mark=pentagon,mark size=1.4},
-            },
-            mark repeat={10},
-            xlabel={Number of VMs added},
-            ylabel={Dedup. Efficiency (\%)},
-            xmin=0,
-            ymin=85,
-            ymax=100,
-            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
-            mark options=solid,
-            legend pos=south west,
-            legend columns=2,
-            legend style={
-                font={\tiny\sffamily},
-                nodes={right}
-                %at={(0.5,-0.2)},
-                %anchor=north
-            },
-            ]
-            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
-            %\addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
-            %\addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison2.txt};
-            %\addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison2.txt};
-            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
-            \legend{VC( $\sigma=4\%$),
-                VC($\sigma=2\%$),
-                %VC MH($\sigma=1\%$),
-                VC(No PDS),
-                %VC($\sigma=4\%$),
-                VC($\sigma=2\%$\, No similarity guidance),
-                %VC($\sigma=1\%$),
-                SRB
-            };
-            \end{axis}
-    \end{tikzpicture}
-    \caption{Deduplication efficiency of VC and SRB.}
-  \label{fig:exbin-efficiency-graph2}
-\end{figure}
-
-}
-
 \begin{figure}[htb]
@@
 \end{figure}
+}
 
-Figure~\ref{fig:efficiency-comparison} shows the deduplication efficiency for SRB and VC using different settings,
+\comments{
+alg     efficiency
+\scriptsize{}VC-2\%\tiny{}No\ Similarity        94.3132243792193
+\scriptsize{}VC-NoPDS   93.0202119345744
+\scriptsize{}VC-2\%PDS  96.0127647380588
+\scriptsize{}VC-4\%PDS  96.5784837160482
+\scriptsize{}SRB        97.8625610883421
+}
+\begin{table}
+\begin{small}
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline
+     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
+     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
+     no-simi&   &&  &    \\ \hline
+     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
+    \end{tabular}
+\end{small}
+    \caption{Deduplication efficiency for different VC settings and
+        Stateless Routing with Binning (SRB).}
+    \label{tab:efficiency-comparison}
+\end{table}
+
+Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
+settings
+and
 % <<<<<<< HEAD
@@
 % =======
-that is the percent of duplicate chunks
-which are detected and removed.
+duplication efficiency is defined as the percent of duplicate chunks which are removed
+compared to a perfect scheme which detects and removes  all deduplicates. 
 % so only global perfect deduplication can have 100\% efficiency.
@@
 %of data chunks shared among VMs, as defined in 
-With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
-and  the deduplication efficiency can reach over 96\%.
-When $\sigma=4\%$, the deduplication efficiency can reach 96.6\% while space consumption increases to 200MB per machine. 
+Notice $\sigma$ is the percentage of unique chunks selected in PDS.
+With $\sigma =2\%$, Column 3 shows its 
+%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
+deduplication efficiency can 
+reach over 96\%.
+When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
+more index space is allocated  per machine for  PDS fingerprint lookup.
+% increases from 100MB to 200MB per physical machine as discussed later. 
 %and  the deduplication efficiency can reach 96.489\%.
@@
 %index ($\sigma=100\%$) then VC will have 100\% efficiency.
-SRB can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
+SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
 Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
@@
 
-Figure~\ref{fig:efficiency-comparison} also shows the efficiency of VC without local similarity search.
+Column 2 of Table~\ref{fig:efficiency-comparison} shows deduplication efficiency of VC without 
+using PDS and it achieves 93.02\%, missing about 3-3.56\% of the original data. That is losing upto
+356GB per physical machine because every machine deals with about 10TB data of snapshots. 
+Column 1 of Table~\ref{fig:efficiency-comparison} shows deduplication efficiency of VC without 
+local similarity search.
 %There is a big efficiency drop in this curve when the number of VMs is about 30.
@@
 In general, our experiments show that
-dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
-which leads to about a 75.86\% reduction.
+version detection at the segment level can reduce the data size to about 24.14\% of original data, 
+which leads to about a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
 Similarity-guided local search can further reduce the data size
@@
 The popularity-guided global deduplication with $\sigma=2\% $
-can reduce the data further to 8.6\% of its original size, so
-it provides additional 28.63\% reduction to the remaining data.
+can reduce the data further to 8.6\% of its original size and namely the final snapshot data size per machine
+is reduced to 860GB, so it provides additional 28.63\% reduction to the remaining data.
 
@@
 \begin{table}
+\begin{small}
     \begin{tabular}{|c|c|c|c|c|c|}
     \hline
-    Tasks & CPU & Mem &Read &  Write  & Time  \\ 
+    Tasks & CPU & Mem &Read &  Write  & Backup Time  \\ 
     & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline
@@
     \end{tabular}
-\caption{Resource usage of concurrent backup tasks at each machine}
+\end{small}
+\caption{Resource usage of concurrent backup tasks at each physical machine with $\sigma=2\%$.}
 \label{tab:resource_usage}

### 2014-01-31 snapshot_system/paper_arch.tex
as dense as I could make it
revised
whole paper revisions

@@
 
+%\begin{figure}[htbp]
 \begin{figure}[htbp]
     \centering
-    \includegraphics[width=2.75in]{images/socc_arch_cluster}
+    %\includegraphics[width=2.75in]{images/socc_arch_cluster}
+    \includegraphics[width=2.3in]{images/socc_arch_cluster}
     \caption{Per node architecture and data flow during snapshot backup}
@@
 As shown in Figure~\ref{fig:as_arch}, we explain the data structure of the snapshot stores as follows.
+%\begin{figure}[htbp]
 \begin{figure}[htbp]
   \centering
-  \includegraphics[width=2.75in]{images/sstore_arch}
+%  \includegraphics[width=2.75in]{images/sstore_arch}
+  \includegraphics[width=2.3in]{images/sstore_arch}
   \caption{VM snapshot store data structures}
@@
 for the data sets we have tested, we only observed limited spatial locality 
-among popular data chunks. On average the number of consecutive PDS index hits is lower than 7.
-Thus it is not very effective to group a large number of chunks as a compression and data fetch unit. 
+among popular data chunks. On average the number of consecutive PDS index hits is lower than 7,
+thus it is not very effective to group a large number of chunks as a compression and data fetch unit. 
 For the same reason, we decide not to take the sampled index approach~\cite{Guo2011} 
@@
 local chunk IDs are monotonically increasing.
-When a chunk is to be accessed, the segment recipe contains a reference pointing to  a data chunk
-in the PDS store or in a non-PDS VM snapshot  store. 
-Using  a container ID, the corresponding container index file of this VM is accessed and 
-the chunk group is identified using a simple chunk ID range search. Once the chunk group is loaded to memory, 
-its header contains the exact offset of the corresponding chunk ID and the content is then accessed from the memory buffer.
+When a chunk is to be accessed, the segment recipe contains a reference pointing to  a data chunk, which is used to lookup up the chunk data as described shortly.
 
@@
 \noindent\textbf{Delete()}.
-Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user and we discuss this in more details in next
-subsection.
-%(we will discuss the snapshot deletion in detail in the following subsection).
+Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user (the overall deletion strategy was discussed in detail in Section~\ref{sect:delete}).
 When deletion requests are issued for a specific container,

### 2014-01-31 snapshot_system/paper_conc.tex
whole paper revisions

@@
 Evaluation using  this scheme strikes a tradeoff and restricted cross-VM duplicate detection
-can accomplish 96.33\% or 96.9\% of what complete global
+can accomplish as much as 96.58\% of what complete global
 deduplication can do, and the approximate snapshot deletion effectively manages deleted chunks with a 

### 2014-01-31 snapshot_system/paper_del.tex
Rich tightens a bit
whole paper revisions

@@
-\section{ VM-centric Approximate Snapshot Deletion with Leak Repair}
+\subsection{Snapshot Deletion with Leak Repair}
 \label{sect:delete}
@@
 focusing on  unreferenced non-PDS chunks within each VM. 
-This process can be conducted by independent among VMs, and thus results in  a simpler flow control and 
+This process can be conducted independently per VM, and thus results in  a simpler flow control and 
 lower resource usage. 
@@
 The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
-For each VM we preset the vector size according to  estimation of VM image size,
+For each VM we preset the vector size according to estimated VM image size;
 given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
@@
 This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
-A mark-and-sweep process  requires a scan of the entire snapshot store.
+A mark-and-sweep process  requires a scan of all the metadata for a snapshot store.
 %Our VM-centric mark-and-sweep procedure is similar to Guo\cite{Guo2011} 

### 2014-01-31 snapshot_system/paper_eval.tex
whole paper revisions

@@
 8-core 3.1Ghz AMD FX-8120 and 16 GB RAM. 
-Our implementation is based on Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
+Our implementation is based on the Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
 and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 6.
@@
 based on~\cite{Dong2011,extreme_binning09}.
-SRB executes a distributed deduplication by routing a data chunk to one of cluster machines~\cite{Dong2011}
+SRB executes distributed deduplication by routing a data chunks to cluster machines~\cite{Dong2011}
 using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
@@
 As we already know the actual storage needs after each snapshot creation,
-thus the storage leakage can be verified by
+the storage leakage can be verified by
 comparing the size of remain data in use after deletion to what it should be.

### 2014-01-31 snapshot_system/paper_conc.tex
re

--- 2014-01-24 snapshot_system/paper_conc.tex
@@
 can accomplish 96.33\% or 96.9\% of what complete global
-deduplication can do, and the approximate snapshot deletion effectively manages deleted chunks with a 
+deduplication can do, and the VM-centric
+approximate snapshot deletion effectively manages deleted chunks with a 
 low-resource usage.  The availability of snapshots increases substantially when
 adding more replication for popular cross-VM chunks and packaging chunks from the same 
-VM in one file system block.
+VM in one file system block. The analysis shows that the replication degree
+for the popular data set between 6 and 9 is good enough when the replication degree
+for other data blocks is 3.
 %Currently we are studying how the

### 2014-01-31 snapshot_system/paper_eval.tex
re

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
 
-{\bf Memory and disk bandwidth usage with multi-VM processing}. 
+{\bf Memory usage with multi-VM processing and disk bandwidth with  I/O throttling}. 
 We have further studied the memory and disk bandwidth usage 
@@
 more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
-significantly because of the controlled  disk read time.
+significantly because of the controlled  disk read bandwidth usage.
 %,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
 %at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.
+
+It should be noted that global fingerprint  space requirement of VC is about 2\% of SRB 
+(with $\sigma$=2\%) since we only deal with popular items. 
+\comments{
+The total memory space would cost over 6GB per machine.
+We have implemented a bloomfilter for SRB which uses a comparable in-memory
+index space size per machine compared VC, but SRB also needs extra space for caching hot index.
+The total space used in SRB is about 1GB per machine. 
+}
 
@@
 VC uses $\sigma=2\%$ and $4\%$.
+For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
+PDS lookup takes only a small amount of time. 
 It has a breakdown of processing time.
@@
 This includes PDS data lookup for VC and index lookup from disk in SRB after Bloom filter lookup.
-For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
-PDS lookup takes only a small amount of time. The network transfer time for VC and SRB is about the same, because the 
+The network transfer time for VC and SRB is about the same, because the 
 amount of raw data they transfer is comparable.
@@
     ]{figures/vc_srb_combined_pgfplots.txt}
-    \caption{Average time to backup a dirty VM segment under SRB and VC
+    \caption{Average time in microsecond to backup a dirty 2MB VM segment under SRB and VC with I/O throttling.
 %        \todo{Decide between this and bar plot with the same caption}
@@
 \end{small}
-\caption{Throughput of software layers per machine under different concurrency}
+\caption{Throughput of software layers per machine under different concurrency and without I/O throttling.}
 \label{tab:throughput}
@@
 
-{\bf Throughput of software layers.}
+{\bf Throughput of software layers without I/O throttling.}
 Table~\ref{tab:throughput} shows the  average throughput of software layer
@@
 ``Backup'' column is the throughput  of the backup service  per machine.
-``Snapshot store" is the  write throughput of the snapshot store layer. The gap between this
-column and  ``Backup" column is caused by significant data reduction by dirty bit and duplicate
-detection. Only non-duplicate chunks trigger a snapshot store write.
+``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
+column to  ``Backup" column is caused by deduplication.
+Only non-duplicate chunks trigger a snapshot store write.
 ``QFS'' column is the write request traffic to the underlying file system after compression.
@@
 after compression.  The underlying disk storage traffic will be three times greater with replication.
-The result shows that the backup service can deliver up to 5.46GB/second without I/O restriction
-per machine with 6 concurrent backup tasks. With a higher disk storage bandwidth available, the above backup
+The result shows that the backup service can deliver up to 5.46GB/second 
+per machine without I/O restriction
+under 6 concurrent backup tasks. 
+For our dataset with 1TB per machine to backup snapshots of 25 VMs, each machine
+would complete the backup in about 3.05 minutes.
+With a higher disk storage bandwidth available, the above backup
 throughput would be higher. 
@@
 
-%In this experiment, we start with the incremetnal backup of 10 versions of 100 VMs with a total of 1,000 snapshots.
+In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
+then start to delete those snapshots one by one.
+As we know the actual storage needs after each snapshot creation,
+the storage leakage can be detected by
+comparing the size of remaining data in use after deletion to the correct number.
 Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
 storage space per VM caused  by approximate deletions.
-We choose 35 VMs, first let all the VMs accumulate to 10 snapshots, then start to delete snapshots
-in reverse order from the latest to the second using approximate deletion.
-As we already know the actual storage needs after each snapshot creation,
-thus the storage leakage can be verified by
-comparing the size of remain data in use after deletion to what it should be.
 The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
@@
 The actual leakage can reach  4.1\% after  245 deletions.
+This experiment shows that the leakge of our approximate snapshot deletion is very small, 
+below the estimated number.
+
 % We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.

### 2014-01-31 snapshot_system/paper_analysis.tex

@@
 
-\begin{figure}
+\begin{figure}[htb]
     \centering
@@
 % and  we denote that PDS blocks are shared by an average of $V_c$ VMs. 
-Then by counting outgoing edges from VMs in Figure~\ref{fig:share}(a),
+Then by counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
 \[
@@
 shows that the deduplication efficiency of VC is very close to that of VO,
-the number of non-PDS file blocks in VC is approximately close to the number of file blocks in VO.
+the number of non-PDS file blocks in VC is similar to the number of file blocks in VO.
 Then
@@
 
-\noindent $r \le d<r_c$:  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
+\noindent {\bf $r \le d<r_c$:}  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
 The full snapshot availability of a VM is: 
@@
 
-\noindent $r_c \leq d$: Both non-PDS and PDS file system blocks in VC can have a loss.
+\noindent {\bf $r_c \leq d$:} Both non-PDS and PDS file system blocks in VC can have a loss.
 The full snapshot availability of  a VM in the VC approach is
@@
 \]
-That is still smaller than that of $V_O$ based on the observation with our data. There are two reasons for this:  
+That is still smaller than that of $V_O$ based on the observations of our data. There are two reasons for this:  
 1) $N_1$ is much smaller than $N_o$ and we are observing that $N_1+N_2<N_o$. 

### 2014-01-31 snapshot_system/paper_background.tex

@@
 Each physical machine hosts multiple virtual machines.  Every virtual machine
-runs its own guest operating system (typically one of only a few
-installed on the system) and accesses virtual hard disks 
+runs its own guest operating system and accesses virtual hard disks 
 stored as image files maintained by the operating system running on the
@@
 data ``chunks''  to identify duplicate
-content~\cite{venti02,Rhea2008}.  In its simple implementation,
+content~\cite{venti02,Rhea2008}.  In a simple implementation,
 it is expensive to compare a large number of 
@@
 All of the above approaches have focused on optimization of deduplication
-efficiency, and none of them have considered the impact
+efficiency or speed, and none of them have considered the impact
 of deduplication on fault resilience in a cloud environment.  To do so, we
@@
 Indeed, the greater the deduplication efficiency, the less
-the data redundancy that is maintained, and the greater the ``hidden'' data
+the data redundancy is maintained, and the greater the ``hidden'' data
 dependence between VMs that must be hosted as if they were physically isolated.
@@
 to implement in a distributed setting.  In particular, duplicate detection is
-logically a ``global'' operation with respect to the population of data chunks
+logically a ``global'' operation over all data chunks
 under consideration.
@@
 for deduplication can be reduced, because fewer chunks must be compared.
-Further, deduplication of otherwise unrelated VMs can be implemented in
+Further, deduplication of VMs can easily be implemented in
 parallel.
@@
 The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
-deletion, but still carries a significant cost, again in the distributed cloud
+deletion, but still carries a significant cost, especially in the distributed cloud
 setting.
@@
 distributed among large file system blocks when a large-scale distributed file
-system is used for disk image files.
+system is used for snapshot storage.
 
@@
 for a co-located backup service that has a resource usage profile
-suitable for use with converged cloud architecture.
+suitable for use with converged cloud architectures.
 
@@
 
-We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, 
+We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation 
 and discuss snapshot deletion support, then present an implementation design.

### 2014-01-31 snapshot_system/paper_dedup.tex

@@
 Since the best deduplication uses a non-uniform chunk size 
-in the average of 4KB or 8KB~\cite{Jin2009},
+with an average of 4KB or 8KB~\cite{Jin2009},
 we conduct additional local similarity guided deduplication on a snapshot by comparing
@@
 which contain chunk fingerprints to be compared.
-To control the time cost of search, we set a limit on the number of  similar segments recipes to be fetched. 
+To control the time cost of search, we set a limit on the number of  similar segment recipes to be fetched. 
 % Then,
@@
 For example, assume that  a segment is of size  2MB, 
-its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
-by limiting at most 10 similar segments to search, the amount of memory for maintaining those 
+its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata.
+By limiting at most 10 similar segments to search, the amount of memory for maintaining those 
 similar segment recipes is small.
@@
 based on a data trace from Alibaba with over 2500 VMs.
-The distribution is zipf-like and popular chunks are dominating the large portion of data chunks.
+The distribution is zipf-like and popular chunks dominate the distribution.
 We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that

### 2014-01-31 snapshot_system/paper_analysis.tex
updates

@@
 
-\noindent {\bf $r \le d<r_c$:}  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
+\noindent $r \le d<r_c$:  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
 The full snapshot availability of a VM is: 
@@
 
-\noindent {\bf $r_c \leq d$:} Both non-PDS and PDS file system blocks in VC can have a loss.
+\noindent $r_c \leq d$: Both non-PDS and PDS file system blocks in VC can have a loss.
 The full snapshot availability of  a VM in the VC approach is

### 2014-01-31 snapshot_system/paper_eval.tex
updates

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
 based on~\cite{Dong2011,extreme_binning09}.
-SRB executes distributed deduplication by routing a data chunks to cluster machines~\cite{Dong2011}
+SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
 using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to

### 2014-01-31 snapshot_system/paper_conc.tex

@@
 Evaluation using  this scheme strikes a tradeoff and restricted cross-VM duplicate detection
-can accomplish 96.33\% or 96.9\% of what complete global
-deduplication can do, and the VM-centric
-approximate snapshot deletion effectively manages deleted chunks with a 
+can accomplish up to 96.58\% of what complete global
+deduplication can do, and the approximate snapshot deletion effectively manages deleted chunks with a 
 low-resource usage.  The availability of snapshots increases substantially when

### 2014-01-31 snapshot_system/paper_eval.tex
updated eval section. Expanded all USENIX bib entries to use proper conference name

@@
  Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
-there are up to 20 machine nodes failed in a cluster with $p=100$ physical machines.
+there are up to 20 machines failed in a cluster with $p=100$ physical machines.
 The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
@@
 Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
-settings
-and
+settings.
 % <<<<<<< HEAD
@@
 % =======
-duplication efficiency is defined as the percent of duplicate chunks which are removed
+Deduplication efficiency is defined as the percent of duplicate chunks which are removed
 compared to a perfect scheme which detects and removes  all deduplicates. 
@@
 
-Column 2 of Table~\ref{fig:efficiency-comparison} shows deduplication efficiency of VC without 
+Column 2 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
 using PDS and it achieves 93.02\%, missing about 3-3.56\% of the original data. That is losing upto
 356GB per physical machine because every machine deals with about 10TB data of snapshots. 
-Column 1 of Table~\ref{fig:efficiency-comparison} shows deduplication efficiency of VC without 
+Column 1 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
 local similarity search.
@@
 ``Mem'' column includes 100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
-receipt metadata and cache. 
-``Read'' column is controlled as 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted too much.
+recipe metadata and cache. 
+The ``Read'' column is controlled to 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted too much.
 The peak raw storage read performance is about 300MB/s and we only use 16.7\% with this collocation consideration.
-``Write'' column is the I/O write usage of QFS and notice that each QFS write triggers disk writes in multiple machines due to
+``Write'' is the I/O write usage of QFS; note that each QFS write triggers disk writes in multiple machines due to
 data replication.     50MB/s dirty segment read speed triggers about 16.4MB/s disk write for non duplicates with one backup task.
@@
 Table~\ref{tab:vc_srb_combined} shows
-the  average  processing  time of  a VM segment under VC and Stateless Routing with Binning (SRB). 
+the  average processing  time breakdown of  a VM segment under VC and Stateless Routing with Binning (SRB). 
 VC uses $\sigma=2\%$ and $4\%$.
@@
 {\bf Throughput of software layers without I/O throttling.}
-Table~\ref{tab:throughput} shows the  average throughput of software layer
-when when I/O throttling is not applied to control the usage.
+Table~\ref{tab:throughput} shows the  average throughput of the software layer
+when when I/O throttling is not applied to control usage. The
 %machine when all machine nodes execute one or multiple MV backup tasks.
@@
 Only non-duplicate chunks trigger a snapshot store write.
-``QFS'' column is the write request traffic to the underlying file system after compression.
+``QFS'' is the write request traffic to the underlying file system after compression.
 For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second

### 2014-01-31 snapshot_system/paper_eval.tex
deletion update

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
 8-core 3.1Ghz AMD FX-8120 and 16 GB RAM. 
-Our implementation is based on the Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
+Our implementation is based on Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
 and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 6.
@@
 based on~\cite{Dong2011,extreme_binning09}.
-SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
+SRB executes a distributed deduplication by routing a data chunk to one of cluster machines~\cite{Dong2011}
 using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
@@
 storage space per VM caused  by approximate deletions.
-We choose 35 VMs, first let all the VMs accumulate to 10 snapshots, then start to delete snapshots
-in reverse order from the latest to the second using approximate deletion.
+We choose 35 VMs, first let all of them create 10 daily snapshots, then start to delete snapshots
+in a reverse order from the latest to the second using approximate deletion.
 As we already know the actual storage needs after each snapshot creation,
-the storage leakage can be verified by
-comparing the size of remain data in use after deletion to what it should be.
+thus the storage leakage can be verified by
+comparing the size of remaining data after deletion to what it should be.
 The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
@@
 there is only 1.5MB space leaked for every 1GB of stored data.
-The actual leakage can reach  4.1\% after  245 deletions.
+The actual leakage can reach  4.1\% after 245 deletions and will be repaired at that time.
 % We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.

### 2014-01-31 snapshot_system/paper.tex
add paper files
deleted old main.pdf, adjusted failures to 10 for figures
update deletion eval
as dense as I could make it
revise
revised
rev

--- 2013-09-13 snapshot_system/fast14_main.tex
@@
 \usepackage{pgfplots}
+\usepackage{pgfplotstable}
 \usepackage{sansmath}
+\usepackage{booktabs}
+\usepackage{soul}
 \pgfplotsset{compat=1.5}
@@
 
-\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]}
-
+%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
+%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
+\title{
+VM-Centric  Snapshot Deduplication  with Fault Isolation 
+for Converged Cloud Architectures} 
+%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
 \author{
-  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, and Hong Tang$^\dagger$ \\
+  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
   {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
-  \{wei, tyang, dagun\}@cs.ucsb.edu, hongtang@alibaba-inc.com
+%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
 }
@@
 
-\input{fast14_abstract}
-\input{fast14_introduction}
-\input{fast14_background}
-\input{fast14_deduplication}
-\input{fast14_architecture}
-\input{fast14_evaluation}
-\input{fast14_conclusion}
+\input{paper_abs}
+\input{paper_intro}
+\input{paper_background}
+\input{paper_dedup}
+\input{paper_analysis}
+\input{paper_del}
+\input{paper_arch}
+\input{paper_eval}
+\input{paper_conc}
 
+\begin{small}
 \bibliographystyle{abbrv}
 \bibliography{library,dedup1}
+\end{small}
 \end{document}

### 2014-01-31 snapshot_system/paper_del.tex
rev

@@
 Since it is a VM-specific procedure, 
-the space and time cost is relatively small compared to the tranditional mark-and-sweep
-which scans snapshot chunks from all VMs.
-For example, consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
-10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process
-in less than half an hour, assuming 50MB/s disk bandwidth is allocated.
+the space cost for processing each VM is proportional to the number of chunks
+within each VM. For example, it is about 85MB space requirement for a VM of size 40GB in our tested dataset.
+ This is  much smaller compared to the tranditional mark-and-sweep
+which scans snapshot chunks from all VMs. Given $n$ VMs in a cluster, the space cost
+is $n$ times larger.
+%For example, consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
+%10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process
+%in less than half an hour, assuming 50MB/s disk bandwidth is allocated.
 \end{itemize}

### 2014-01-31 snapshot_system/paper_eval.tex
rev

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
 based on~\cite{Dong2011,extreme_binning09}.
-SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
+SRB executes distributed deduplication by routing a data chunks to cluster machines~\cite{Dong2011}
 using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
-a machine, the chunk is compared with the fingerprint index within this machine locally.
-
+a machine, the chunk is compared with the fingerprint index within this machine locally based 
+on~\cite{extreme_binning09}.
 \subsection{Settings}
@@
 The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
-the same from $p=100$ setting to $p=1000$. With differnet $p$ values, how the availability varies when 
+the same from $p=100$ setting to $p=1000$. With different $p$ values, how the availability varies when 
 the number of failures in the cluster changes.
@@
 loses most of non-PDS blocks given the replication degree for non PDS is 3.
-On the other hand, when $p=1000$, the pecetnage of machine failure is then 2\% and
- VC outperforms VO significantly in availabilty in this case by delivering a meaningful avaiability with 99.62\%.
+On the other hand, when $p=1000$, the percentage of machine failure is then 2\% and
+ VC outperforms VO significantly in availability in this case by delivering a meaningful availability with 99.62\%.
 
@@
 That is because when the number of failed machines increases beyond 6, 
-the non-PDS data availability starts to deteroriate significantly given its replication degree
+the non-PDS data availability starts to deteriorate significantly given its replication degree
 $r$ is fixed as 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.
@@
 duplication efficiency is defined as the percent of duplicate chunks which are removed
-compared to a perfect scheme which detects and removes  all deduplicates. 
+compared to a perfect scheme which detects and removes  all duplicates. 
 % so only global perfect deduplication can have 100\% efficiency.
@@
 
-Table ~\ref{tab:resource_usage} shows that  a single backup task per node can complete the backup of the entire
-VM cluster in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
+Table ~\ref{tab:resource_usage} shows that when  each machine conducts
+backup one VM at a time, the backup of the entire
+VM cluster completes in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
 more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
-significantly because of the controlled  disk read bandwidth usage.
+significantly in this case because of the controlled  disk read bandwidth usage.
 %,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
@@
 
-It should be noted that global fingerprint  space requirement of VC is about 2\% of SRB 
-(with $\sigma$=2\%) since we only deal with popular items. 
+It should be noted that global fingerprint  space requirement of VC is about 2\% of all unique fingerprints 
+with $\sigma$=2\%. SRB uses an approximated method to look for a match within a bin and
+its memory space usage is about 190MB per machine. That is compared with 118MB used in VC with $\sigma=2\%$.
+Using a bloom filter with an index cache would require more memory space~\cite{Dong2011}.
+
 \comments{
 The total memory space would cost over 6GB per machine.
-We have implemented a bloomfilter for SRB which uses a comparable in-memory
+We have implemented a bloom-filter for SRB which uses a comparable in-memory
 index space size per machine compared VC, but SRB also needs extra space for caching hot index.
@@
 
-{\bf Processing Time breakdown}.
+{\bf Processing Time breakdown without I/O throttling}.
 Table~\ref{tab:vc_srb_combined} shows
-the  average  processing  time of  a VM segment under VC and Stateless Routing with Binning (SRB). 
+the  average  processing  time of  a dirty VM segment in milliseconds
+under VC and Stateless Routing with Binning (SRB). 
 VC uses $\sigma=2\%$ and $4\%$.
+The overall processing latency of SRB is about 23.9\% slower than VC.
 For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
@@
 ``Index Lookup'' is the disk, network and CPU time during fingerprint comparison.
-This includes PDS data lookup for VC and index lookup from disk in SRB after Bloom filter lookup.
+This includes PDS data lookup for VC and index lookup from disk in SRB. 
 The network transfer time for VC and SRB is about the same, because the 
@@
     ]{figures/vc_srb_combined_pgfplots.txt}
-    \caption{Average time in microsecond to backup a dirty 2MB VM segment under SRB and VC with I/O throttling.
+    \caption{Average time in milliseconds  to backup a dirty 2MB VM segment under SRB and VC with I/O throttling.
 %        \todo{Decide between this and bar plot with the same caption}
@@
 under 6 concurrent backup tasks. 
-For our dataset with 1TB per machine to backup snapshots of 25 VMs, each machine
+For our dataset, each version of total snapshots  has abut  1TB per machine for 25 VMs and  thus  each machine
 would complete the backup in about 3.05 minutes.
@@
 
+\comments{
  \begin{figure}
@@
  \end{figure}
+}
+\begin{table}
+\begin{small}
+    \begin{tabular}{|c|c|c|c|c|c|}
+    \hline
+   &     1 &  3  & 5 & 7  & 9 \\ 
+\hline   
+     Estimated& .02\% & .06\% & .10\%& .14\% & .18\%\\ 
+\hline   
+     Measured & .01\% & .055\% & .09\% & .12\% & .15\% \\
+\hline   
+    \end{tabular}
+\end{small}
+     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
+     \label{tab:leakage}
+\end{table}
 
+Table~\ref{tab:leakage} shows the average accumulated storage leakage in terms of percentage of
+storage space per VM caused  by approximate deletions.
 In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
@@
 comparing the size of remaining data in use after deletion to the correct number.
-Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
-storage space per VM caused  by approximate deletions.
 The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
@@
 there is only 1.5MB space leaked for every 1GB of stored data.
-The actual leakage can reach  4.1\% after  245 deletions.
-This experiment shows that the leakge of our approximate snapshot deletion is very small, 
+The actual leakage can reach  4.1\% after  245 deletions and such a repair is needed every 12 days
+to the  leakage under 5\%. 
+This experiment shows that the leakage of our approximate snapshot deletion is very small, 
 below the estimated number.
+
+The space cost for deletion and leakage repair is very small.
+Consider each reference consumes 8 bytes plus  1 mark bit. 
+A VM that has 40GB backup data with about 10 million chunks will need less than 85MB of memory.
+A VM-specific mark-and-sweep process takes  less than half an hour, when disk bandwidth is controlled as 50MB/s.
+
+When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, a total of 212GB memory
+space on 100 node is accessed for processing each VM and each machine quires 2.12GB.
+Assuming snapshot deletion happens daily,
+such a  mark-and-sweep deletion needs to be conducted every two days to control garbage space under 5\%
+since there is 2.5\% data change for each snapshot.
 

### 2014-01-31 snapshot_system/paper_eval.tex

@@
 % =======
-duplication efficiency is defined as the percent of duplicate chunks which are removed
+Deduplication efficiency is defined as the percent of duplicate chunks which are removed
 compared to a perfect scheme which detects and removes  all duplicates. 
@@
 Table~\ref{tab:vc_srb_combined} shows
-the  average  processing  time of  a dirty VM segment in milliseconds
+
+the  average  time breakdown for processing a dirty VM segment in milliseconds
 under VC and Stateless Routing with Binning (SRB). 

### 2014-01-31 snapshot_system/paper_conc.tex
rev

@@
 can accomplish up to 96.58\% of what complete global
-deduplication can do, and the approximate snapshot deletion effectively manages deleted chunks with a 
-low-resource usage.  The availability of snapshots increases substantially when
+deduplication can do, and the simple and approximate snapshot deletion 
+effectively manages deleted chunks with a 
+much lower resource usage.  The availability of snapshots increases substantially when
 adding more replication for popular cross-VM chunks and packaging chunks from the same 

### 2014-01-31 snapshot_system/paper_eval.tex
rev

@@
 
-The space cost for deletion and leakage repair is very small.
-Consider each reference consumes 8 bytes plus  1 mark bit. 
-A VM that has 40GB backup data with about 10 million chunks will need less than 85MB of memory.
-A VM-specific mark-and-sweep process takes  less than half an hour, when disk bandwidth is controlled as 50MB/s.
-
-When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, a total of 212GB memory
-space on 100 node is accessed for processing each VM and each machine quires 2.12GB.
-Assuming snapshot deletion happens daily,
-such a  mark-and-sweep deletion needs to be conducted every two days to control garbage space under 5\%
-since there is 2.5\% data change for each snapshot.
+The space cost for deletion is insignificant.
+Leakage repair need less than 85MB of memory
+considering each reference consumes 8 bytes plus  1 mark bit and  
+each VM snapshot has 40GB backup data with about 10 million chunks. 
+Our VM-specific mark-and-sweep process in VC takes  less than half an hour, when disk bandwidth is controlled as 50MB/s. 
+When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
+a total of 212GB memory
+space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
+To control the garbage growth, such a process needs to be conducted much more frequently than our
+VM-centric leakage repair. 
+%Assuming snapshot deletion happens daily,
+%such a  mark-and-sweep deletion needs to be conducted every two days to control garbage space under 5\%
+%since there is 2.5\% data change for each snapshot.
 

### 2014-01-31 snapshot_system/paper_del.tex
re

@@
 General deduplication complicates the deletion process because sharing of duplicates
-requires a global refence counting~\cite{Guo2011,Fabiano2013} 
+requires a global reference counting~\cite{Guo2011,Fabiano2013} 
  to identify if  a chunk can be  safely removed without any reference.
@@
 
-\item {\bf Approximate deletion with fast summary comparison.}
+\item {\bf Fast approximate deletion with summary comparison.}
 When there is a snapshot deletion,  
@@
 
+One advantage of the above fast method is that it can finish  and free storage 
+usage immediately, while other offline methods (e.g. ~\cite{Guo2011,Fabiano2013})
+can't. That is important for storage accounting as users pay what are used and delayed deletion
+affects the accounting.
+
 \item {\bf Periodic repair of leakage}.
@@
 within each VM. For example, it is about 85MB space requirement for a VM of size 40GB in our tested dataset.
- This is  much smaller compared to the tranditional mark-and-sweep
-which scans snapshot chunks from all VMs. Given $n$ VMs in a cluster, the space cost
-is $n$ times larger.
+ This is  much less expensive  than  the VM-oblivious mark-and-sweep
+which scans snapshot chunks from all VMs, even with optimization~\cite{Guo2011}
+
+%Given $n$ VMs in a cluster, the space cost is $n$ times larger.
 %For example, consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about

### 2014-01-31 snapshot_system/paper_eval.tex
re

@@
 Table~\ref{tab:vc_srb_combined} shows
-
 the  average  time breakdown for processing a dirty VM segment in milliseconds
@@
 each VM snapshot has 40GB backup data with about 10 million chunks. 
-Our VM-specific mark-and-sweep process in VC takes  less than half an hour, when disk bandwidth is controlled as 50MB/s. 
-When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
-a total of 212GB memory
-space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
-To control the garbage growth, such a process needs to be conducted much more frequently than our
-VM-centric leakage repair. 
+This VM-specific leakage  repair takes  less than half an hour for each VM, 
+when disk bandwidth is controlled as 50MB/s. 
+%When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
+%a total of 212GB memory
+%space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
+%To control the garbage growth, such a process needs to be conducted much more frequently than our
+%VM-centric leakage repair.
+
 %Assuming snapshot deletion happens daily,

### 2014-01-31 snapshot_system/paper_intro.tex
re

@@
 of network bandwidth that would otherwise be available to user VMs. 
-%Even when the storage system implements deduplication internally
-%such dedicated backup storage is either difficult to scale out
-%(which can comprise the overall scalability of the converged architecture) 
-%or it must forego global deduplication in order to gain scalability 
-%(which increases backup cost).
+Even when the storage system implements deduplication internally
+such dedicated backup storage is either difficult to scale out
+(which can comprise the overall scalability of the converged architecture) 
+or it must forego global deduplication in order to gain scalability 
+(which increases backup cost).
 
@@
 a small resource usage without affecting other collocated cloud services;
-2) augmented fault isolation for the sharing of deduplicated data,
+2) improved fault isolation for the sharing of deduplicated data,
 given that node failures in converged architecture are the norm rather than

### 2014-01-31 snapshot_system/paper_del.tex
wording revisions

@@
 the space cost for processing each VM is proportional to the number of chunks
-within each VM. For example, it is about 85MB space requirement for a VM of size 40GB in our tested dataset.
+within each VM. For example, the space requirement is about 85MB for a VM of size 40GB in our tested dataset.
  This is  much less expensive  than  the VM-oblivious mark-and-sweep
-which scans snapshot chunks from all VMs, even with optimization~\cite{Guo2011}
+which scans snapshot chunks from all VMs, even with optimization~\cite{Guo2011}.
 

### 2014-01-31 snapshot_system/paper_eval.tex
wording revisions

@@
 The space cost for deletion is insignificant.
-Leakage repair need less than 85MB of memory
+Leakage repair needs less than 85MB of memory
 considering each reference consumes 8 bytes plus  1 mark bit and  
@@
 This VM-specific leakage  repair takes  less than half an hour for each VM, 
-when disk bandwidth is controlled as 50MB/s. 
+when disk bandwidth is controlled to 50MB/s. 
 %When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 

### 2014-01-31 snapshot_system/paper.tex
r

@@
 
+\linespread{.98} % to squeeeze lines and put figures in same page
 \begin{document}
@@
   Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
-  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
+  {\normalsize$^\star$  University of California at Santa Barbara} {\normalsize$^\dagger$Alibaba Inc.} \\
 %  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
@@
 \begin{small}
+\linespread{.90} % to squeeeze lines and put figures in same page
 \bibliographystyle{abbrv}

### 2014-01-31 snapshot_system/paper_eval.tex
r

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
 on~\cite{extreme_binning09}.
-\subsection{Settings}
+
+{\bf Settings}.
 We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
@@
 
-\subsection{Fault Isolation and Snapshot Availability}
+%\subsection{Fault Isolation and Snapshot Availability}
+\subsection{Snapshot Availability}
 
@@
 
-\begin{table}
+\begin{table}[htbp]
   \centering
@@
 
-\begin{figure}[htb]
+\begin{figure}[htbp]
   \centering
@@
 
-\subsection{Competitiveness of Deduplication Efficiency}
+\subsection{Deduplication Efficiency}
 \label{sect:evaldedup}
@@
 }
-\begin{table}
+\begin{table}[htbp]
 \begin{small}

### 2014-01-31 snapshot_system/paper_eval.tex

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
 using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
-a machine, the chunk is compared with the fingerprint index within this machine locally based 
-on~\cite{extreme_binning09}.
+a machine, the chunk is compared with the fingerprint index within this machine locally.
+
 \subsection{Settings}
@@
 The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
-the same from $p=100$ setting to $p=1000$. With different $p$ values, how the availability varies when 
+the same from $p=100$ setting to $p=1000$. With differnet $p$ values, how the availability varies when 
 the number of failures in the cluster changes.
@@
 loses most of non-PDS blocks given the replication degree for non PDS is 3.
-On the other hand, when $p=1000$, the percentage of machine failure is then 2\% and
- VC outperforms VO significantly in availability in this case by delivering a meaningful availability with 99.62\%.
+On the other hand, when $p=1000$, the pecetnage of machine failure is then 2\% and
+ VC outperforms VO significantly in availabilty in this case by delivering a meaningful avaiability with 99.62\%.
 
@@
 That is because when the number of failed machines increases beyond 6, 
-the non-PDS data availability starts to deteriorate significantly given its replication degree
+the non-PDS data availability starts to deteroriate significantly given its replication degree
 $r$ is fixed as 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.
@@
 Deduplication efficiency is defined as the percent of duplicate chunks which are removed
-compared to a perfect scheme which detects and removes  all duplicates. 
+compared to a perfect scheme which detects and removes  all deduplicates. 
 % so only global perfect deduplication can have 100\% efficiency.
@@
 
-Table ~\ref{tab:resource_usage} shows that when  each machine conducts
-backup one VM at a time, the backup of the entire
-VM cluster completes in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
+Table ~\ref{tab:resource_usage} shows that  a single backup task per node can complete the backup of the entire
+VM cluster in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
 more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
-significantly in this case because of the controlled  disk read bandwidth usage.
+significantly because of the controlled  disk read bandwidth usage.
 %,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
@@
 
-It should be noted that global fingerprint  space requirement of VC is about 2\% of all unique fingerprints 
-with $\sigma$=2\%. SRB uses an approximated method to look for a match within a bin and
-its memory space usage is about 190MB per machine. That is compared with 118MB used in VC with $\sigma=2\%$.
-Using a bloom filter with an index cache would require more memory space~\cite{Dong2011}.
-
+It should be noted that global fingerprint  space requirement of VC is about 2\% of SRB 
+(with $\sigma$=2\%) since we only deal with popular items. 
 \comments{
 The total memory space would cost over 6GB per machine.
-We have implemented a bloom-filter for SRB which uses a comparable in-memory
+We have implemented a bloomfilter for SRB which uses a comparable in-memory
 index space size per machine compared VC, but SRB also needs extra space for caching hot index.
@@
 
-{\bf Processing Time breakdown without I/O throttling}.
+{\bf Processing Time breakdown}.
 Table~\ref{tab:vc_srb_combined} shows
-the  average  time breakdown for processing a dirty VM segment in milliseconds
-under VC and Stateless Routing with Binning (SRB). 
+the  average processing  time breakdown of  a VM segment under VC and Stateless Routing with Binning (SRB). 
 VC uses $\sigma=2\%$ and $4\%$.
-The overall processing latency of SRB is about 23.9\% slower than VC.
 For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
@@
 ``Index Lookup'' is the disk, network and CPU time during fingerprint comparison.
-This includes PDS data lookup for VC and index lookup from disk in SRB. 
+This includes PDS data lookup for VC and index lookup from disk in SRB after Bloom filter lookup.
 The network transfer time for VC and SRB is about the same, because the 
@@
     ]{figures/vc_srb_combined_pgfplots.txt}
-    \caption{Average time in milliseconds  to backup a dirty 2MB VM segment under SRB and VC with I/O throttling.
+    \caption{Average time in microsecond to backup a dirty 2MB VM segment under SRB and VC with I/O throttling.
 %        \todo{Decide between this and bar plot with the same caption}
@@
 under 6 concurrent backup tasks. 
-For our dataset, each version of total snapshots  has abut  1TB per machine for 25 VMs and  thus  each machine
+For our dataset with 1TB per machine to backup snapshots of 25 VMs, each machine
 would complete the backup in about 3.05 minutes.
@@
 
-\comments{
  \begin{figure}
@@
  \end{figure}
-}
-\begin{table}
-\begin{small}
-    \begin{tabular}{|c|c|c|c|c|c|}
-    \hline
-   &     1 &  3  & 5 & 7  & 9 \\ 
-\hline   
-     Estimated& .02\% & .06\% & .10\%& .14\% & .18\%\\ 
-\hline   
-     Measured & .01\% & .055\% & .09\% & .12\% & .15\% \\
-\hline   
-    \end{tabular}
-\end{small}
-     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
-     \label{tab:leakage}
-\end{table}
 
-Table~\ref{tab:leakage} shows the average accumulated storage leakage in terms of percentage of
-storage space per VM caused  by approximate deletions.
-In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
-then start to delete those snapshots one by one.
+In this experiment, we select 105 VMs and let all the VMs accumulate 10 snapshots, 
+then start to delete those snapshots one by one in reverse order.
 As we know the actual storage needs after each snapshot creation,
@@
 comparing the size of remaining data in use after deletion to the correct number.
+Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
+storage space per VM caused  by approximate deletions.
 The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
@@
 there is only 1.5MB space leaked for every 1GB of stored data.
-The actual leakage can reach  4.1\% after  245 deletions and such a repair is needed every 12 days
-to the  leakage under 5\%. 
-This experiment shows that the leakage of our approximate snapshot deletion is very small, 
+The actual leakage can reach  4.1\% after  245 deletions.
+This experiment shows that the leakge of our approximate snapshot deletion is very small, 
 below the estimated number.
-
-The space cost for deletion is insignificant.
-Leakage repair needs less than 85MB of memory
-considering each reference consumes 8 bytes plus  1 mark bit and  
-each VM snapshot has 40GB backup data with about 10 million chunks. 
-This VM-specific leakage  repair takes  less than half an hour for each VM, 
-when disk bandwidth is controlled to 50MB/s. 
-%When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
-%a total of 212GB memory
-%space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
-%To control the garbage growth, such a process needs to be conducted much more frequently than our
-%VM-centric leakage repair.
-
-%Assuming snapshot deletion happens daily,
-%such a  mark-and-sweep deletion needs to be conducted every two days to control garbage space under 5\%
-%since there is 2.5\% data change for each snapshot.
-
-% We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.
-% As this value increases, larger summary vectors are generated thus results in a decrease on the
-% false-positive ratio, therefore less amount of unused chunks are misjudged.

### 2014-01-31 snapshot_system/paper_intro.tex

@@
 of network bandwidth that would otherwise be available to user VMs. 
-Even when the storage system implements deduplication internally
-such dedicated backup storage is either difficult to scale out
-(which can comprise the overall scalability of the converged architecture) 
-or it must forego global deduplication in order to gain scalability 
-(which increases backup cost).
+%Even when the storage system implements deduplication internally
+%such dedicated backup storage is either difficult to scale out
+%(which can comprise the overall scalability of the converged architecture) 
+%or it must forego global deduplication in order to gain scalability 
+%(which increases backup cost).
 

### 2014-01-31 snapshot_system/paper_eval.tex
revise

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
     \hline
-   &     1 &  3  & 5 & 7  & 9 \\ 
+Del. step   &     1 &  3  & 5 & 7  & 9 \\ 
 \hline   
@@
 In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
-then start to delete those snapshots one by one.
+then start to delete 9 snapshots one by one.
 As we know the actual storage needs after each snapshot creation,
@@
 comparing the size of remaining data in use after deletion to the correct number.
-The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
+Row 1 in  Table~\ref{tab:leakage} 
+is the deletion step. 3 means that version 3 is deleted. 
+Row  2 is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
 given $\Delta u/u=0.025$,
-while the solid line represents the actual average leakage measured during the experiment for all the VMs. 
+while Row 3 lists the actual average leakage measured during the experiment for all the VMs. 
 The Bloom filter setting is based on $\Delta u/u=0.025$.
@@
 
-The space cost for deletion is insignificant.
-Leakage repair needs less than 85MB of memory
+The space cost for each snapshot deletion is insignificant.
+Leakage repair for each VM needs less than 85MB of memory
 considering each reference consumes 8 bytes plus  1 mark bit and  

### 2014-01-31 snapshot_system/paper_arch.tex
re

@@
 Our prototype system runs on a cluster of Linux machines with Xen-based VMs 
-and the QFS~\cite{michael2013} distributd file system. 
+and the QFS~\cite{michael2013} distributed file system. 
 %to %manage  the physical disk storage. 
@@
 \subsection{Per Node Software Components} 
+%\begin{figure}[htbp]
+\begin{figure}[htbp]
+    \centering
+    %\includegraphics[width=2.75in]{images/socc_arch_cluster}
+    \includegraphics[width=2.2in]{images/socc_arch_cluster}
+    \caption{Data flow during snapshot backup}
+    \label{fig:arch_vm}
+\end{figure}
 As depicted in Figure~\ref{fig:arch_vm}, 
@@
 
+\subsection{A VM-centric Snapshot Store for Backup Data}
+\label{sect:store}
 %\begin{figure}[htbp]
@@
   \centering
-    %\includegraphics[width=2.75in]{images/socc_arch_cluster}
-    \includegraphics[width=2.3in]{images/socc_arch_cluster}
-    \caption{Per node architecture and data flow during snapshot backup}
-    \label{fig:arch_vm}
+%  \includegraphics[width=2.75in]{images/sstore_arch}
+  \includegraphics[width=2.2in]{images/sstore_arch}
+  \caption{VM snapshot store data structures}
+  \label{fig:as_arch}
 \end{figure}
 
-\subsection{A VM-centric Snapshot Store for Backup Data}
-\label{sect:store}
 We use the QFS distributed file system to hold snapshot backups.
@@
 As shown in Figure~\ref{fig:as_arch}, we explain the data structure of the snapshot stores as follows.
-%\begin{figure}[htbp]
-\begin{figure}[htbp]
-  \centering
-%  \includegraphics[width=2.75in]{images/sstore_arch}
-  \includegraphics[width=2.3in]{images/sstore_arch}
-  \caption{VM snapshot store data structures}
-  \label{fig:as_arch}
-\end{figure}
-
 %\begin{itemize}

### 2014-01-31 snapshot_system/paper_eval.tex

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
 storage space per VM caused  by approximate deletions.
-In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
-then start to delete those snapshots one by one.
+In this experiment, we select 105 VMs and let all the VMs accumulate 10 snapshots, 
+then start to delete those snapshots one by one in reverse order.
 As we know the actual storage needs after each snapshot creation,
@@
 below the estimated number.
-
-The space cost for deletion is insignificant.
-Leakage repair needs less than 85MB of memory
-considering each reference consumes 8 bytes plus  1 mark bit and  
-each VM snapshot has 40GB backup data with about 10 million chunks. 
-This VM-specific leakage  repair takes  less than half an hour for each VM, 
-when disk bandwidth is controlled to 50MB/s. 
-%When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
-%a total of 212GB memory
-%space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
-%To control the garbage growth, such a process needs to be conducted much more frequently than our
-%VM-centric leakage repair.
-
-%Assuming snapshot deletion happens daily,
-%such a  mark-and-sweep deletion needs to be conducted every two days to control garbage space under 5\%
-%since there is 2.5\% data change for each snapshot.
-
-% We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.
-% As this value increases, larger summary vectors are generated thus results in a decrease on the
-% false-positive ratio, therefore less amount of unused chunks are misjudged.

### 2014-01-31 snapshot_system/paper.tex

@@
   Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
-  {\normalsize$^\star$  University of California at Santa Barbara} {\normalsize$^\dagger$Alibaba Inc.} \\
+  {\normalsize$^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\
 %  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com

### 2014-01-31 snapshot_system/paper_analysis.tex
r
figure revisions, shrunk modeling parameters table
s

@@
     {
-        \includegraphics[width=3in]{images/share_vc}
+        \includegraphics[width=2.9in]{images/share_vc}
         \label{fig:share_vc}
@@
     {
-        \includegraphics[width=3in]{images/share_vo}
+        \includegraphics[width=2.9in]{images/share_vo}
         \label{fig:share_vo}
     }
-    \caption{Bipartite association of VMs and file system blocks under (a) VC and (b) VO. }
+    \caption{Bipartite association of VMs and file blocks. }
     \label{fig:share}
@@
 to the VM centric and oblivious approaches.  
-Parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
+There are two impacts to VC. 
+1) Some PDS fingerprint lookup services do not respond.  As  a result, some duplicates
+are not detected and deduplication efficiency suffers, but the overall systems can still
+function well and fault tolerance is not affected.  As discussed in Section ~\ref{sect:architecture}, 
+PDS index is distributed
+among all machines in our implementation and thus a percentage of failed nodes
+causes an increase in missed duplicates proportionally.
+2) Some storage nodes do not  respond and file blocks on those machines are lost. The availability of
+VM snapshots is affected and we analyze this impact as follows.
+
 %A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
@@
 block of a VM in each approach as follows.
+Parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
 %As illustrated in Figure~\ref{fig:share},
@@
 shows that the deduplication efficiency of VC is very close to that of VO,
-the number of non-PDS file blocks in VC is similar to the number of file blocks in VO.
+the number of non-PDS file blocks in VC is fairly close to the number of file blocks in VO.
 Then
@@
 
-Figure~\ref{fig:vm-links} shows $N_1$, $N_2$, and $N_o$ values in our tested dataset when increasing the number of VMs.  
+Figure~\ref{fig:vm-links} shows $N_1$, $N_2$, and $N_o$ values of 105 VMs from a  test dataset 
+discussed in Section~\ref{sect:evaluation} when increasing the number of VMs.  
 %the average number of file system blocks for each VM in VC and in VO

### 2014-01-31 snapshot_system/paper_dedup.tex
explain top k
s

@@
   \centering
-  \epsfig{file=images/mh_local_dedup.pdf, width=3in}
+  \epsfig{file=images/mh_local_dedup.pdf, width=2.7in}
   \caption{Similarity-guided local duplicate detection}
@@
 
+We have studied the distribution of chunk popularity~\cite{WeiZhangIEEE} 
+based on a production data trace from Alibaba with over 2500 VMs.
+The distribution is Zipf-like and popular chunks dominate the distribution.
+We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
+$\sigma$ with a range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
+
 Since $k$ is relatively small and these top $k$ chunks are shared among multiple VMs, 
 we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
-We have studied the distribution of chunk popularity~\cite{WeiZhangIEEE} 
-based on a data trace from Alibaba with over 2500 VMs.
-The distribution is zipf-like and popular chunks dominate the distribution.
-We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
-$\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.
 

### 2014-01-31 snapshot_system/paper_eval.tex
figure revisions, shrunk modeling parameters table
changes
s

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
 including OS and user data disk.
-Each physical machine deals with about 10TB of snapshot data.
-The VMs of the sampled data set use popular operating systems such as 
+Each physical machine deals with about 10TB of snapshot data and each 1TB data represents one snapshot version
+of 25 VMs.  The VMs of the sampled data set use popular operating systems such as 
 Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
@@
 The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
-and thus calculate the average availability of VM snapshots.
+and then calculate the average availability of VM snapshots.
 The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
@@
 the non-PDS data availability starts to deteriorate significantly given its replication degree
-$r$ is fixed as 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.
+$r$ is set to 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.
 
@@
 Column 2 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
-using PDS and it achieves 93.02\%, missing about 3-3.56\% of the original data. That is losing upto
-356GB per physical machine because every machine deals with about 10TB data of snapshots. 
+using PDS and it achieves 93.02\% and  missed duplicates take  up-to  3.56\% of the original space, which
+is about 356GB per physical machine. 
 Column 1 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
@@
 Similarity-guided local search can further reduce the data size
-to about 12.05\% of original, namely it delivers a 50.08\% reduction to the dirty segments.
+to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction to the dirty segments.
 The popularity-guided global deduplication with $\sigma=2\% $
-can reduce the data further to 8.6\% of its original size and namely the final snapshot data size per machine
-is reduced to 860GB, so it provides additional 28.63\% reduction to the remaining data.
+reduces the data further to 860GB, namely 8.6\% of the original size. 
+So it provides additional 28.63\% reduction.
 
@@
 \end{small}
-\caption{Resource usage of concurrent backup tasks at each physical machine with $\sigma=2\%$.}
+\caption{Resource usage of concurrent backup tasks at each physical machine with $\sigma=2\%$ and I/O throttling.}
 \label{tab:resource_usage}
@@
 {\bf Throughput of software layers without I/O throttling.}
-Table~\ref{tab:throughput} shows the  average throughput of the software layer
-when when I/O throttling is not applied to control usage. The
+Table~\ref{tab:throughput} shows the  average throughput of software layers
+when I/O throttling is not applied to control usage. The
 %machine when all machine nodes execute one or multiple MV backup tasks.
@@
 Only non-duplicate chunks trigger a snapshot store write.
-``QFS'' is the write request traffic to the underlying file system after compression.
+Column ``QFS'' is the write request traffic to the underlying file system after compression.
 For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
@@
 storage space per VM caused  by approximate deletions.
-In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
-then start to delete 9 snapshots one by one.
+In this experiment, we select 105 VMs and let all the VMs accumulate 10 snapshots, 
+then start to delete those snapshots one by one in reverse order.
 As we know the actual storage needs after each snapshot creation,

### 2014-01-31 snapshot_system/paper_background.tex
re

@@
 The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
-deletion, but still carries a significant cost, especially in the distributed cloud
+deletion, but still carries a significant cost, especially in a distributed 
 setting.
@@
 \item {\em Stateless  Data Routing} --
-One approach to scalable duplicate comparison is to use a content-based hash
-partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011}.
+One approach to scalable duplicate comparison is to use content-based hash
+partitioning called stateless data routing by Dong et al.~\cite{Dong2011}.
 Stateless data routing divides the deduplication work with a similarity approximation. This work 

### 2014-01-31 snapshot_system/paper_dedup.tex
re

@@
 complementary strategies: VM-local
-duplicate search optimization, global deduplication using popular chunks, and 
+duplicate search, global deduplication using popular chunks, and 
 VM-centric file system block management. 
@@
 $\sigma$ with a range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
+For example,
+with top 2\% of the most popular chunks stored in PDS, up-to 40\% of the raw backup 
+data can be eliminated by fingerprint lookup in PDS index.
 
-Since $k$ is relatively small and these top $k$ chunks are shared among multiple VMs, 
+Since $\sigma$ is relatively small and these top chunks are shared among multiple VMs, 
 we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.

### 2014-01-31 snapshot_system/paper_del.tex
r
re

@@
   \centering
-  \epsfig{file=images/deletion.pdf, width=3in}
-  \caption{Approximate deletion}
+  \epsfig{file=images/deletion.pdf, width=2.7in}
+  \caption{Fast approximate deletion}
   \label{fig:deletion_flow}
@@
 We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
-This can be done during the periodic leakage repair stage described below.
+This can be done during periodic leakage repair described below.
 
@@
 Since it is a VM-specific procedure, 
-the space cost for processing each VM is proportional to the number of chunks
+the space cost is proportional to the number of chunks
 within each VM. For example, the space requirement is about 85MB for a VM of size 40GB in our tested dataset.
@@
 every day. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
-number of additional chunks added from one snapshot to the next snapshot version. Then the total number of 
-chunks stored in a VM's snapshot store is about:
+number of additional chunks added from one version to next snapshot version. Then the total number of 
+chunks in a VM's snapshot store is about:
 \[

### 2014-01-31 snapshot_system/paper_intro.tex
re

--- 2014-01-31 snapshot_system/paper_intro.tex
@@
 
-In this paper we consider a backup service for converged cloud architectures
+This paper considers a backup service for converged cloud architectures
 that is co-located with user VMs, sharing the cloud computer, network, and

### 2014-01-31 snapshot_system/paper_background.tex
fixed

@@
 each commodity server hosts a number of virtual machines and storage of these servers
-is clustered using a distributed file system~\cite{googlefs03,hdfs10,NutanixPaper}.
+is clustered using a distributed file system~\cite{googlefs03,hdfs10}.
 Each physical machine hosts multiple virtual machines.  Every virtual machine
@@
 the following previously-developed techniques.
-\begin{itemize}
-\item {\em Changed Block Tracking} --
+1) {\em Changed Block Tracking}. 
 VM snapshots can be  backed up  incrementally by identifying data segments that have
@@
 %global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
-\item {\em Stateless  Data Routing} --
+1) {\em Stateless  Data Routing}.
 One approach to scalable duplicate comparison is to use content-based hash
@@
 VM-specific local search.
-\item {\em Sampled Index for Memory Parsimony} -- 
+3) {\em Sampled Index for Memory Parsimony}. 
 One effective approach that reduces memory usage is 

### 2014-01-31 snapshot_system/paper_dedup.tex
fixed

@@
 
-We have studied the distribution of chunk popularity~\cite{WeiZhangIEEE} 
-based on a production data trace from Alibaba with over 2500 VMs.
+ Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 
+from Alibaba with 2500 VMs discussed in Section ~\ref{sect:evaluation}.
+%the distribution of chunk popularity~\cite{WeiZhangIEEE} 
+%based on a production data trace from Alibaba with over 2500 VMs.
 The distribution is Zipf-like and popular chunks dominate the distribution.
-We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
+We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and 
+from the evaluation in Section~\ref{sect:evaluation}, we find that
 $\sigma$ with a range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
-For example,
-with top 2\% of the most popular chunks stored in PDS, up-to 40\% of the raw backup 
-data can be eliminated by fingerprint lookup in PDS index.
+%For example,
+%with top 2\% of the most popular chunks stored in PDS, up-to 40\% of the raw backup 
+%data can be eliminated by fingerprint lookup in PDS index.
 
@@
 to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
-accumulate small local chunks. We manage this accumulation process using a log-structured storage scheme built
-on a distributed file system discussed in Section~\ref{sect:architecture}.
+accumulate small local chunks. 
+%We manage this accumulation process using a log-structured storage scheme built
+%on a distributed file system discussed in Section~\ref{sect:architecture}.
 %Non-PDS chunks from the same VM are stored in one append store. 
@@
 
-% \begin{figure}
-% \centering
-%  \includegraphics[width=3in]{figures/log-log-disk}
-% \caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
-% \label{fig:Datazipf}
-% \end{figure}
+ \begin{figure}
+ \centering
+  \includegraphics[width=2.5in]{figures/log-log-disk}
+ \caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
+ \label{fig:Datazipf}
+ \end{figure}
 

### 2014-01-31 snapshot_system/paper_intro.tex
fixed

@@
 servers as a way of avoiding the relatively high cost of network attached 
-storage~\cite{googlefs03,hdfs10,NutanixPaper}.
+storage~\cite{googlefs03,hdfs10}.
 %systems. %This(e.g. ~\cite{NutanixPaper}).  Leading cloud platform companies

### 2014-01-31 snapshot_system/paper_analysis.tex
re
fixed

@@
 %\begin{table}[htbp]
-\begin{table}[t]
+\begin{table}[t]\small
 \centering
@@
     {
-        \includegraphics[width=2.9in]{images/share_vc}
+        \includegraphics[width=2.7in]{images/share_vc}
         \label{fig:share_vc}
@@
     {
-        \includegraphics[width=2.9in]{images/share_vo}
+        \includegraphics[width=2.7in]{images/share_vo}
         \label{fig:share_vo}
@@
 Then by counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
-\[
+$
 n* N_1   = \mbox{ Number of non-PDS file system blocks in VC.} 
-\]
+$
 
@@
 by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
-Table~\ref{tab:symbol}: 
-\[
+Table~\ref{tab:symbol},  we have
+$
 n *N_o   =  V_o *\mbox{ Number of file system blocks in VO.} 
-\]
+$
 
@@
 Then
-\[
+$
 \frac{N_o}{N_1} \approx  V_o.
-\]
+$
 %Thus $N_o >> N_1$.
@@
 		%title={VO VM links},
-                width=\linewidth,
+                width=0.7*\linewidth,
                 height=0.6\linewidth,
@@
 % $N_2$ for VC and $N_o$ for VO.
-Given $d$ failed physical machines and $r$ replicas for each file block,
+Given $d$ failed machines and $r$ replicas for each file block,
 %normal data replication degree $r$, PDS data replication degree $r_c$, 
 the availability of a file block is the probability that  
-all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
+all of its replicas do not appear in any group of $d$ failed machines among $p$ nodes. 
 Namely, 
-\[
+$
 A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
-\]
+$
 Then the availability of one VM's snapshot data under VO approach is the probability that

### 2014-01-31 snapshot_system/paper_arch.tex
re

@@
 
-\subsection{A VM-centric Snapshot Store for Backup Data}
+\subsection{A VM-centric Snapshot Store}
 \label{sect:store}
@@
 For non PDS data, the snapshot store of a VM is  divided into a set of containers and 
-each container is approximately 1GB. 
-The reason for dividing the snapshot store into containers is to simplify the compaction process
-conducted periodically. As discussed later, data chunks are deleted from old snapshots
-and chunks without any reference from other snapshots can be removed by this compaction process.
-By limiting the size of a container, we can effectively control the length of each round of compaction.
-The compaction  routine can work on one container at a time and move the in-use data chunks to another container.
+each container is approximately 1GB.  The reason for this  divison is to simplify the compaction process
+conducted periodically. When  chunks are deleted from old snapshots,
+chunks without any reference from other snapshots can be removed by this compaction process.
+By limiting the size of a container, we can control the length of each round of compaction.
+The compaction  can work on one container at a time and move the in-use data chunks to another container.
 
@@
 For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
-Note that PDS append may only be used during PDS recalculation.
+This operation  may only be used during PDS recalculation.
 For non-PDS data, this call places a chunk into 
-the snapshot store and returns a reference to be stored in 
-the recipe metadata of a snapshot. 
-The write requests to append data chunks to a VM store are accumulated at the client side. 
-When the number of write requests reaches a fixed group size, the snapshot store client compresses
+the snapshot store and returns a reference to be stored in the recipe of a snapshot. 
+The write requests to append chunks to a VM store are accumulated at the client side. 
+When the number of write requests reaches a fixed group size, the client compresses
 the accumulated   chunk group, adds a chunk group index  to the beginning of the group, and then
@@
 \noindent\textbf{Get()}.
-The fetch operation for the PDS data chunk is straightforward since each reference contains 
+Fetching PDS data is straightforward since each reference contains 
 the file offset, and the size of a PDS chunk is available from a segment recipe.
 We also maintain a small data cache for the PDS data service to speedup common data fetching.
-
-To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client first loads the
+To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client 
+first loads the
 corresponding VM's container index file specified by the container ID, then searches the chunk
@@
 specified by the chunk ID. 
-Finally, the client updates its internal chunk data cache with the newly loaded content to 
+Finally, the client updates its internal chunk cache with the newly loaded content to 
 anticipate future sequential reads.

### 2014-01-31 snapshot_system/paper_del.tex
re

@@
 When there is a snapshot deletion,  
-we need to identify if chunks to be deleted from that snapshot
+we identify if chunks to be deleted from that snapshot
 are still referenced by other snapshots. 
@@
 the time and memory cost of this comparison is small, linear to the number of chunks to be deleted.
-
-If a chunk's reference is not found in the merged summary vector, we are sure that
-this chunk is not used by any live snapshots, thus it can be deleted safely.
+If a chunk's reference is not found in the merged summary vector, 
+this chunk is not used by any live snapshots. Thus it can be deleted safely.
 However, among all the chunks to be deleted, 
@@
 %{\bf Discussion}
-We now estimate the size of storage leakage and how often leak repair needs to be conducted.
-Assume that  a VM keeps $h$ snapshots in the backup storage, creates and deletes one snapshot
-every day. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
+We estimate storage leakage size and how often leak repair should be conducted.
+Assume that  a VM keeps $h$ snapshots in backup storage, creates and deletes one snapshot
+every day. Let $u$ be the number of chunks brought by initial backup for a VM, $\Delta u$ be the average
 number of additional chunks added from one version to next snapshot version. Then the total number of 
 chunks in a VM's snapshot store is about:
-\[
+$
 U = u + (h-1)\Delta u.
-\]
+$
 
@@
 repairs. We estimate  the total leakage $L$ after $R$ runs as:
-\[
+$
 L = R \epsilon \Delta u.
-\]
+$
 
@@
 
-For example in our tested dataset,  
+For example for our test data in Section~\ref{sect:evaluation},  
 $h=10$ and each snapshot adds
-about 0.1-5\% of new data. Thus we take ${\Delta u}/{u} \approx 0.025$. For a 40GB snapshot, $u\approx  10$ million.
+about 0.1-5\% of new data. Thus ${\Delta u}/{u} \approx 0.025$. For a 40GB snapshot, $u\approx  10$ million.
 Then $U=12.25$ million.

### 2014-01-31 snapshot_system/paper_eval.tex
shrunk ylabel on figure 9 to reclaim space
re

@@
  Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
-there are up to 20 machines failed in a cluster with $p=100$ physical machines.
+there are up to 20 machines failed in a cluster. 
 The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
 and then calculate the average availability of VM snapshots.
-The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
-the same from $p=100$ setting to $p=1000$. With different $p$ values, how the availability varies when 
-the number of failures in the cluster changes.
+The case for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
+the same from $p=100$ setting to $p=1000$. Each machine hosts about 25 VMs in both cases
+and with different $p$ values, the availability varies when the number of failures in the cluster changes.
 
@@
 
-Our results show that VC has a significantly  higher availability than VO as the number of
-failed machines increases from 3 to 20
-in this table.
+ Table~\ref{tab:vm-availability} shows 
+that VC has a significantly  higher availability than VO.
+% as the number of failed machines increases from 3 to 20.
 %Our VM-centric approach shows significant improvements
 %in VM availability.
-With $p=100$ and 3 machine failures,
-there are 2500 VMs in total. VO with 69.5\% availability could lose data in 763 VMs 
-while VC with 99.7\% loses data for 8 VMs.
+With $p=100$ and 3 failures,
+VO with 69.5\% availability could lose data in 763 VMs 
+while VC with 99.7\% only loses data for 8 VMs out of 2500 VMs.
 The key reason is that for most data in VC, only a single VM can be affected by
-the loss of a single file block. Since most blocks contain chunks for a single
-VM, VMs can depend on a smaller number of blocks, while in VO, the loss of a
+the loss of a single file block
+%Since most blocks contain chunks for a single
+%VM, VMs can depend on a smaller number of blocks, 
+while in VO, the loss of a
 single block tends to affect many VMs.
@@
 loses most of non-PDS blocks given the replication degree for non PDS is 3.
-On the other hand, when $p=1000$, the percentage of machine failure is then 2\% and
- VC outperforms VO significantly in availability in this case by delivering a meaningful availability with 99.62\%.
+When $p=1000$, the percentage of failures is then 2\% and VC delivers a meaningful availability 
+with 99.62\%, outperforming VO significantly.
 
@@
 }
-\begin{table}[htbp]
+\begin{table}[htb]
 \begin{small}
@@
 \begin{table}[t]
+  \centering
 \begin{small}
-    \centering
     \begin{tabular}{|c|ccc|}
@@
 \begin{table}
+\centering
 \begin{small}

### 2014-01-31 snapshot_system/paper_eval.tex
re
chagne

@@
 		xlabel={Failed storage nodes},
-		ylabel={VM Snapshot Availability (\%)},
+		ylabel={Availability (\%)},
                 xmin=0,
@@
 
-In general, our experiments show that
+In summary, our experiments show that
 version detection at the segment level can reduce the data size to about 24.14\% of original data, 
@@
 Similarity-guided local search can further reduce the data size
-to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction to the dirty segments.
+to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction after the version-based
+ deduplication.
 The popularity-guided global deduplication with $\sigma=2\% $

### 2014-01-31 snapshot_system/paper_eval.tex
centering table
re

@@
 {\bf Settings}.
-We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
-Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
+We have performed a trace-driven study based on a production dataset
+from Alibaba Aliyun's cloud platform~\cite{Aliyun} 
+with about 2500 VMs, running on 100 physical machines. 
 Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
@@
 each VM snapshot has 40GB backup data with about 10 million chunks. 
-This VM-specific leakage  repair takes  less than half an hour for each VM, 
-when disk bandwidth is controlled to 50MB/s. 
+This VM-specific leakage  repair takes  less than half an hour for each VM. 
+%when disk bandwidth is controlled to 50MB/s. 
 %When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 

### 2014-01-31 snapshot_system/paper.tex
fixed

--- 2014-01-31 snapshot_system/paper.tex
@@
 
+%\linespread{.98} % to squeeeze lines and put figures in same page
 \begin{document}
@@
 \author{
-  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
-  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
+  Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
+  {\normalsize$^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\
 %  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
@@
 \begin{small}
+%\linespread{.97} % to squeeeze lines and put figures in same page
 \bibliographystyle{abbrv}

### 2014-01-31 snapshot_system/paper_eval.tex
updateminors

--- 2014-01-31 snapshot_system/paper_eval.tex
@@
 \begin{table}[htb]
+\centering
 \begin{small}
@@
 Column ``QFS'' is the write request traffic to the underlying file system after compression.
-For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
-after compression.  The underlying disk storage traffic will be three times greater with replication.
-The result shows that the backup service can deliver up to 5.46GB/second 
+For example, with 148 MB/s write traffic to the snapshot store, QFS write traffic is about 35.3 MB/s
+after compression.  However, the underlying disk storage traffic will be three times greater with replication.
+The result shows that the backup service can deliver up to 5.46 GB/s 
 per machine without I/O restriction

### 2014-02-05 batchdedup/arch.tex
revised batchdedup paper

@@
 % unless its owner explicitly asks for its retention.
-We adopt the idea of mark-and-sweep~\cite{Guo2011}. 
+To perform compaction of unused blocks, We adopt the idea of mark-and-sweep~\cite{Guo2011}. 
 A block or a segment can be deleted if its reference count is zero.
 %As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
-To delete useless  blocks or segments periodically, we read the meta data  of all
-snapshots and compute the reference count of all blocks and segments  in parallel.
+To delete unreferenced blocks or segments periodically, we read the meta data  of all
+snapshots and determine which blocks and segments are referenced  in parallel.
 %while following the fingerprint-based partitioning.
-Similar to the multi-stage duplicate detection process, reference counting is conducted in multi-stages. 
+Similar to the multi-stage duplicate detection process, marking is conducted in multiple stages. 
 Stage  1 is to read  the segment and block  metadata 
-to accumulate  reference count requests in different machines  in the fingerprint based distribution.
-Stage   2 is to count references within each partition and detect those records with zero 
-reference. 
+to accumulate  references in different machines  based on the fingerprint based distribution.
+Stage   2 is to mark blocks/segments within each partition and detect those records which are unmarked (and therefore can be deleted).
 %Stage 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.

### 2014-02-05 batchdedup/eval.tex
revised batchdedup paper

@@
 %100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
-a cloud cluster at Alibaba's Aliyun.
+a cloud cluster at Alibaba's Aliyun. based on the data distribution from the
+trace data, we have also simulated the VM size distribution of several much
+larger clusters by generating synthetic traces (e.g. the two clusters in
+Fig~\ref{fig:hist} have 4224 and 8046 VMs).
 % ~\cite{WeiZhangIEEE}.
 % and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
-For each VM, the system keeps 10 automatically-backed snapshots in the storage while
-a user may instruct extra snapshots to be saved.
-The backup of VM snapshots is completed within a few  hours every night.
-Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
-including OS and user data disk.
+For each VM, the system keeps 10 automatically-backed snapshots in the storage
+while a user may instruct extra snapshots to be saved.  The backup of VM
+snapshots is completed within a few  hours every night.  Based on our study of
+its production  data,  each VM has an average of 40GB of storage  data usage on
+including OS and user data disk (though the exact size of a VM varies with a
+long-tail distribution).
+
 Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 

### 2014-02-05 batchdedup/scheduling.tex
revised batchdedup paper

@@
 \label{sect:scheduling}
-The naive way for synchronized backup is   to schedule all of the backup tasks in one round.
-Since parallel backup of these tasks goes through several stages,
-that results in the backup time of each VM is approximately equal to the total execution of all backup tasks.
-Given VM sizes are highly skewed in a large cluster, some big VMs will take a long time and other
+The na\"{\i}ve way for synchronized backup is to schedule all of the backup tasks in one round.
+Since parallel backup of these tasks goes through several synchronized stages,
+the backup time of each VM is approximately equal to the total execution of all backup tasks.
+Given VM sizes are highly skewed in a large cluster (see Fig.~\ref{fig:hist} for a plot of the distribution in several real clusters), some big VMs will take a long time and other
 small VM backup tasks synchronized in one round will have to wait.
@@
 distribution, though local minima exist in the histogram and the range of VM
-sizes varies. Other production clusters may have different distributions, but
-all of the clusters we have looked at have similarly shaped distributions. Size
+sizes varies.
+All of the clusters we have looked at have similarly shaped distributions. Size
 distribution histograms for two of the clusters are shown in

### 2014-02-12 batchdedup/arch.tex
paper revision. also major figure refactoring.

@@
 %We use a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
-Our experiment with Alibaba's production dataset shows that over 70 percentage of 
+Our experiments with Alibaba's production dataset shows that over 70 percent of 
 duplicates can be detected using segment dirty bits when the segment size is 2M bytes.  
@@
 Our approach is to perform duplicate detection first before actual data backup.
-That requires a prescanning of  dirty VM segments, which
+This requires a prescanning of  dirty VM segments, which
 %  and after that, real backup  for those non-duplicates is conducted. 
@@
 Since each partition corresponds to a small portion of global index, 
-memory cost to process detection requests within a partition is small.
+memory cost to process detection requests within a partition is small and can
+be handled in memory.
 %the cost to process detection requests within a partition is significantly smaller than processing all 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/batch_arch.pdf}
+%\includegraphics[width=0.5\textwidth]{batch_arch}
+%this is an alternate version of the figure done completely in latex
+\input{figures/batch_arch}
 \caption{Overall architecture of parallel VM snapshot deduplication}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/Stage1.pdf}
+\includegraphics[width=0.5\textwidth]{Stage1}
 \caption{Processing flow of Stage 1.}
@@
 and outputs each request buffer to one of the request partitions on the disk
-when this request buffer becomes full.  Option 2, which is  depicted in Figure~\ref{fig:flow},
+when this request buffer becomes full.  Option 2, which is  depicted in Figure~\ref{fig:stage1},
 is much more efficient than Option 1 because $2p+q$ is much smaller than
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/Stage2.pdf}
+\includegraphics[width=0.5\textwidth]{Stage2}
 \caption{Processing flow of Stage 2.}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/Stage3.pdf}
+\includegraphics[width=0.5\textwidth]{Stage3}
 \caption{Processing flow of Stage 3.}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/Stage4.pdf}
+\includegraphics[width=0.5\textwidth]{Stage4}
 \caption{Processing flow of Stage 4.}

### 2014-02-12 batchdedup/background.tex
paper revision. also major figure refactoring.

@@
 not provided, and snapshot operations take place at the virtual device driver
-level.  This meands no fine-grained file system metadata can be used to
+level.  This means no fine-grained file system metadata can be used to
 determine the changed data.
@@
 studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}.  In comparison, this
-paper focuses on full deduplication without approximation
+paper focuses on full deduplication without approximation.
 

### 2014-02-12 batchdedup/eval.tex
paper revision. also major figure refactoring.

@@
 \centering
-\includegraphics[width=0.4\textwidth]{mem_time.pdf}
+\includegraphics[width=0.4\textwidth]{mem_time}
 \caption{ Parallel time when memory limit varies.}
@@
 \end{figure}
+
+\comments{
+alternate version of fig:memory done all in pgfplots
+\begin{figure}[ht]
+  \centering
+    \begin{tikzpicture}
+            \begin{axis}[
+            %title={Extreme-Binning Efficiency},
+            ybar stacked,
+            width=0.85\columnwidth,
+            cycle list name=mfill,
+            bar width=0.70cm,
+            style=very thin,
+            symbolic x coords={35M,45M,55M,65M,95M,190M},
+            %xlabel={Memory Usage},
+            ylabel={Time (hours)},
+            %extra y ticks={4.5,5.5,6.5}, %to add extra ticks
+            xtick=data, %without this the symbolic coords may be repeated as filler
+            enlarge x limits=0.15, %used to push plots towards center
+            ymin=0,
+            %ymax=4.,
+            ytick={0,0.5,1,...,4},
+            %{/pgf/number format/.cd,fixed,precision=2},
+            ymajorgrids,
+            grid style=densely dotted,
+            major x tick style=transparent,
+            tick label style={font=\scriptsize\mathversion{sans}\sffamily},
+            label style={font=\footnotesize\sf},
+            legend pos=south east,
+            reverse legend,
+            area legend,
+            legend cell align=right,
+            legend style={
+                %    at={(0.5,-0.2)},
+                %anchor=north,
+                font=\scriptsize\sf,
+                %draw=none,
+            },
+            ]
+            \addplot table[header=false,x index=0,y index=2] {figures/mem_time_new.data};
+            \addlegendentry{Stage 1}
+            \addplot table[header=false,x index=0,y index=3] {figures/mem_time_new.data};
+            \addlegendentry{Stage 2}
+            \addplot table[header=false,x index=0,y index=4] {figures/mem_time_new.data};
+            \addlegendentry{Stage 3}
+            %\legend{Data read/write,Network cost, Index access/lookup}
+            \end{axis}
+    \end{tikzpicture}
+    \caption{Parallel time when memory limit varies}
+  \label{fig:memory}
+\end{figure}
+}
 

### 2014-02-12 batchdedup/intro.tex
paper revision. also major figure refactoring.

@@
 Our work is targeted applications where data processing and archiving  can be conducted
-in an inexpensive commodity storage cluster using the  Google file system or Hadoop~\cite{googlefs03}
-and such a storage cluster is non-dedicated, shared with other services running in the entire cluster.
-Resource sharing is common especially in the cloud where many computing and storage
-services are collocated in the same physical machines.
+in an inexpensive commodity storage cluster using a distributed file system
+such as the Google file system or Hadoop~\cite{googlefs03,hdfs10}.
+Resource sharing is common, especially in the cloud where many computing and storage
+services are collocated in the same physical machines, so we 
+expect the storage cluster to be non-dedicated.
 
@@
 low-profile backup solution with deduplication. 
-Deduplication is a major
+%Deduplication is a major
 
@@
 
-Among the three factors - time, cost and deduplication efficiency, one of them has to be compromised for the other two.
-For instance, if we were building a deduplication system that has a high rate of duplication detection and has a very fast response time,
-it would need a lot of memory to hold fingerprint index and cache.  This leads to a compromise on cost. 
-Our objective is to lower the cost incurred while sustaining the highest de-duplication ratio
-and  a sufficient throughput in dealing with a large number of VM images.% This business model partially  resembles that of Amazon Glacier.
+%Among the three factors - time, cost and deduplication efficiency, one of them
+%has to be compromised for the other two. For instance, if we were building a
+%deduplication system that has a high rate of duplication detection and has a
+%very fast response time, 
+%it would need a lot of memory to hold fingerprint index and cache.  This leads to a compromise on cost. 
+%Our objective is to lower the cost incurred while sustaining the highest de-duplication ratio
+%and  a sufficient throughput in dealing with a large number of VM images.% This business model partially  resembles that of Amazon Glacier.
+
+Among the three factors - time, cost, and deduplication efficiency, our main
+objective is low cost, so as to not significantly impact primary services. By
+sacrificing memory a faster deduplication system
+can be built, but then machines must be dedicated to backup, which goes
+against the converged architecture model that we are supporting. For daily
+backup jobs, it is ok if the job takes 2-3 hours, as long as the resource
+usage is minimal and it can be finished during lower usage hours of the day.
 

### 2014-02-12 batchdedup/main.tex
Additional cluster histogram added
paper revision. also major figure refactoring.

@@
 %\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
+\usepackage[usenames]{xcolor}
 \usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
 \usepackage{epsfig}
-\usepackage{listings}
+\usepackage{sansmath}
+%\usepackage{listings}
+\usepackage[]{algorithm2e}
 %\lstset{language=C}
@@
 
+\usepackage{subfigure}
+%\usepackage{graphicx}
+\usepackage{siunitx}
+\usepackage{tikz}
+\usetikzlibrary{calc}
 \usepackage{pgfplots}
-\pgfplotsset{compat=1.5}
+\pgfplotsset{compat=1.8}
 \DeclareGraphicsExtensions{.pdf}
+\graphicspath{ {./images/}{./figures/} }
 
 %pgfplots setup
-\pgfplotsset{every axis/.append style={
+\usetikzlibrary{patterns}
+\tikzset{ %I believe this sets the defaults, but I am not sure
+    hatch distance/.store in=\hatchdistance,
+    hatch distance=10pt,
+    hatch thickness/.store in=\hatchthickness,
+    hatch thickness=2pt
+}
+\pgfplotsset{
+    %You are supposed to use append style rather than just setting
+    %parameters globally so they are easier to override to special cases
+    %thickness options:thin,ultra thin,very thin,semithick,thick,very thick
+    every axis/.append style={
         very thick,
-	tick style={thick}}}
+        tick style={thick},
+        tick label style={font=\small\mathversion{sans}\sffamily},
+        label style={font=\small\sffamily},
+        font={\small\sffamily},
+        %mark size=1.0
+    },
+    every legend/.append style={font={\small\mathversion{sans}\sffamily}}
+}
 \pgfplotsset{
@@
 }
+
 %this is my preferred default cycle list for pgfplots.
@@
 
-\pgfplotscreateplotcyclelist{mmark*}{
-    {mark=*},
-    {mark=square*},
-    {mark=triangle*,mark size=2.7},
-    {mark=diamond*,mark size=2.7},
-    {mark=pentagon*,mark size=2.5},
-    {mark=star,mark size=3},
-    {mark=asterisk,mark size=3},
-    {mark=+,mark size=3},
-    {mark=Mercedes star,mark size=3}}
-
+%uses just line styles instead of marks to differentiate
 \pgfplotscreateplotcyclelist{mline}{
@@
     {loosely dashdotdotted,violet,every mark/.append style={fill=violet}}}
+
+%fill pattern for bar charts similar to the gnuplot one used previously
+\pgfplotscreateplotcyclelist{mfill}{
+    {fill=white,postaction={pattern=crosshatch,pattern color=red}},
+    {fill=white,postaction={pattern=north east lines,pattern color=green}},
+    {fill=white,postaction={pattern=north west lines,pattern color=blue}}}
 

### 2014-02-12 batchdedup/scheduling.tex
paper revision. also major figure refactoring.

@@
 distribution histograms for two of the clusters are shown in
-Fig.~\ref{fig:hist}. There is a long tail on both histrograms which has been
+Fig.~\ref{fig:hist}. Note that there is a long tail on both histrograms which has been
 cut (out to 100GB for the first, and out to 2000GB for the second). The
-important thing to get from this data is that in none of the productions
-clusters we evaluated was the VM Size distribution flat, which motivates the
-importance of round scheduling.
+key insight from these size distributions is that in all of the productions
+clusters we evaluated, the VM Size distribution is highly skewed, which
+motivates the importance of round scheduling.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/VMRound.pdf}
-\caption{Choosing a round to schedule a VM (marked as VM1D in a two-round schedule.  }
+%\includegraphics[width=0.5\textwidth]{VMRound}
+%implementation of the above figure in pure latex
+\input{figures/VMRound}
+\caption{Choosing a round to schedule a VM. New VM marked as VM1A.}
 \label{fig:VMRound}

### 2014-05-12 snapshot_system/paper_del.tex
updates to contributions

@@
  to identify if  a chunk can be  safely removed without any reference.
-%The complexity of our distributed environment obviates reference counting as an option,
-%and While we can use the mark-and-sweep, 
-%While the mark-and-sweep techniques can be used and optimization can be considered~\cite{Fabiano2013},
-%it still takes significant resources to conduct reference counting every time there is a snapshot deletion.
-%
-%In the case of Alibaba, snapshot backup is conducted automatically and there are 
-%about 10 snapshot stored for every VM customer.
-% Snapshot deletion can occur frequently, for example when there is
-% a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
-% balanced storage use. 
-%In addition, cloud users expect the reduced storage usage to be reflected
-%instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.
-Since our VM-centric design restricts sharing of data chunks only to a small dataset,
-we can greatly simplify the deletion process by 
-focusing on  unreferenced non-PDS chunks within each VM. 
-This process can be conducted independently per VM, and thus results in  a simpler flow control and 
-lower resource usage. 
-%The PDS data chunks are commonly shared among all VMs and we do not consider them
-%during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
+%Since our VM-centric design restricts sharing of data chunks only to a small dataset,
+%we can greatly simplify the deletion process by 
+%focusing on  unreferenced non-PDS chunks within each VM. 
+%This process can be conducted independently per VM, and thus results in  a simpler flow control and 
+%lower resource usage. 
+One of the key benefits of our VM-centric design is that it allows for faster and simpler deletion. First, since
+sharing in our approach is limited to only a small dataset, we can greatly simplify deletion by focusing
+on intra-VM sharing rather than inter-VM sharing. Our deletion can therefore be conducted independently per VM.
+Second, we propose an {\em approximate} deletion stragegy to trade deletion accuracy for speed and
+resource usage.
 
-We further propose an {\em approximate} deletion strategy to trade deletion accuracy for
-speed and resource usage. Our method sacrifices a small percent of storage leakage
-to efficiently identify unused chunks.
+Our approximate deletion method sacrifices a small percent of storage leakage
+to efficiently identify unused chunks using a per-snapshot bloomfilter.
 The algorithm contains three aspects.

### 2014-05-12 snapshot_system/paper_intro.tex
updates to contributions

@@
 This paper considers a backup service for converged cloud architectures
-that is co-located with user VMs, sharing the cloud computer, network, and
-storage resource with them.
-We describe methodologies to address the following two challenges: 
+that is co-located with user VMs, sharing the cloud compute, network, and
+storage resources with them.
+%We describe methodologies to address the following two challenges: 
+The key contribution of this work is a set of methodologies to address the following two challenges:
 1) simple deduplication and snapshot deletion with competitive efficiency and 

### 2014-06-27 snapshot_system/paper_background.tex
revise for ACM cloud

@@
 means no fine-grained file system metadata can be used to determine the changed data. 
+In a converged setting with source-side deduplication, the resources that are used to implement snapshot
+backup and deduplication are the same resources that must support cloud-hosted
+VMs.  Thus the backup service colocated with 
+other cloud services has to minimize its resource impact.  
 %This architecture does not use a separate  backup facility for a lower cost and 
@@
 studied in ~\cite{wei2013}.
+
+\comments{
 All of the above approaches have focused on optimization of deduplication
@@
 IaaS architectures.
+}
 %considered in this paper.
@@
 %VM dependence minimization during deduplication and file system block management.
+
+Even with these optimization and approximation techniques, resource usage for deduplication
+is still extensive for a shared cloud cluster.  For example, the
+sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011},
+uses 5GB memory space for 100TB of raw data even the compressed data size
+is about 5TB. It is fairly typical for
+a physical machine with terabytes of disk storage and tens of gigabytes of memory
+to support  more than 20 VMs and 10 snapshots per VM and can require  over 100TB of raw space
+even the actual storage space need is about 5TB assuming 20:1 compression ratio with deduplication.
+It is not easy  to adopt the sampled index method  for a distributed architecture
+and every deduplication request may access a remote machine for index lookup and the overall overhead of access latency 
+for all requests can be significant.  In general
+with a cluster of machines in a cloiud cluster, there will be more memory requirement per machine such as a 
+fingerprint cache, for cross-machine fingerprint comparison~\cite{bottleneck08,Dong2011} and a deduplication
+task often needs several gigabytpes of memory, which impacts other cloud services sharing the omputing resource.
+
+Whiel deduplication reduces storage cost, it creates an artitical data dependence among VMs: when a shared data chunk
+is lost in the storage, all VMs that refer such chunks after deduplication face a data loss.
+This issue is identified in ~\cite{Baghat2006} which proposes to use more replication for data shared by more files.
+It is complex to implement this idea in VM snapshot backup. 
+This is because the file system block  size in a distributed file system such as  
+the Hadoop file system and the Google file system~\cite{googlefs03}
+is large (e.g.  64MB) so as to optimize file system performance
+for big data. Since  deduplication implementations~\cite{Guo2011,extreme_binning09,bottleneck08,Jin2009,Dong2011}
+ typically use smaller chunk sizes (e.g. 4K bytes),  a large file block contains many small chunks with different 
+degree of sharing and  these file blocks would have to be replicated.
+
+Cross-VM chunk sharing also complicates snapshot deletion which occurs frequently when snapshots expire regularly
+and reference counting is required to identify chunks that are no longer used. 
+The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
+deletion, but still carries a significant cost, especially in a distributed 
+setting.  
+%to count if a data chunk is still shared by other snapshots.
+
+%still significant
+%especailly for a distributed setting.
+
+\comments{
 \paragraph*{Local versus Global Deduplication} --
@@
 
-%Further, 
-%this artificial dependence affects fault isolation since 
-%the loss of all replicas of a data chunk can affect the otherwise unrelated
-%VMs that share it.
-
 Indeed, the greater the deduplication efficiency, the less
@@
 dependence between VMs that must be hosted as if they were physically isolated.
-%machine failures happen periodically 
-%in a large-scale cloud and
-%loss of a small number of shared data chunks can 
-%cause the unavailability of snapshots for a large number of virtual machines.
 Thus,
@@
 
-For the remainder of this paper, 
-we term the traditional deduplication approach {\em VM-oblivious} (VO)
-because it manages duplicate data chunks without consideration of VMs.
+}
+
+\comments{
 With the above  considerations in mind, we propose a 
@@
 suitable for use with converged cloud architectures.  
-
+This compares the traditional deduplication approach {\em VM-oblivious} (VO)
+which manages duplicate data chunks without consideration of VMs.
+We discuss our key ideas and design in the next section.
+%Our key idea is to simplify deduplication management and 
+}
+\comments{
 In designing a VC deduplication solution, we have considered and adopted some of
@@
 and discuss snapshot deletion support, then present an implementation design. 
+}

### 2014-06-27 snapshot_system/paper_dedup.tex
update graph
revise for ACM cloud

@@
 
-%\subsection{VM centric  strategies}
-%\label{sect:vc-strategies}
+With the considerations discussed in the previous section, we propose a
+VM-centric approach (called VC)
+for a co-located backup service that has a resource usage profile
+suitable for use with converged cloud architectures.
+This compares the traditional deduplication approach {\em VM-oblivious} (VO)
+which manages duplicate data chunks without consideration of VMs.
+Section~\ref{sect:vc-strategies} discusses  our key ideas and design for duplicate detection.
+Section~\ref{sect:delete} presents  a simplified snapshot deletion with  the VM-centric approach.
+
+\subsection{VM centric  strategies}
+\label{sect:vc-strategies}
 
@@
 VM-centric file system block management. 
-%\begin{itemize}
-%\item
+\begin{itemize}
+\item 
+\textbf{Cross-VM global deduplication using popular chunks} --
+We seperate the deduplication within a VM and cross VMs.
+This is because global deduplication that detects the apperance of a chunk 
+in any VM requires a substantial resource for fingerprint comparison.
+%This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
+Our key observation is for those chunks that appear in different VMs, top $k$ most popular items
+dominate the apperance. 
+ \begin{figure}
+ \centering
+  \includegraphics[width=2.5in]{figures/zipf_count_rank.pdf}
+ \caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
+ \label{fig:Datazipf}
+ \end{figure}
 
-\textbf{VM-local duplicate search optimization} --
-We use the standard version-based detection~\cite{Clements2009,Vrable2009}
+% {\it [Need to find a place to put these numbers in: Total number of chunks 
+% in 350 snapshots: 1,546,635,485. 
+% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
+
+ Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 
+from Alibaba with 2500 VMs discussed in Section ~\ref{sect:evaluation}.
+%the distribution of chunk popularity~\cite{WeiZhangIEEE} 
+%based on a production data trace from Alibaba with over 2500 VMs.
+The distribution is Zipf-like and popular chunks dominate the distribution.
+We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and 
+from the evaluation in Section~\ref{sect:evaluation}, we find that
+$\sigma$ with a range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
+%For example,
+%with top 2\% of the most popular chunks stored in PDS, up-to 40\% of the raw backup 
+%data can be eliminated by fingerprint lookup in PDS index.
+
+Since $\sigma$ is relatively small and these top chunks are shared among multiple VMs, 
+we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
+
+%when restricting fingerprint comparison within a VM uses
+%only a small amount of resource. 
+%ehat the local deduplication has removed most of the duplicates.
+%There are fewer deduplication opportunities across VMs while the memory and network
+%consumption for global comparison is more expensive.
+Thus our approximation is that the global cross-VM fingerprint comparison only searches for the top $k$
+most popular items. This dataset is called the \textbf{PDS} (popular data set). 
+We define chunk popularity as the number of unique copies of the chunk in the data-store,
+i.e., the number of copies of the chunk after local deduplication.
+This number can be computed periodically, e.g., on a weekly basis.
+Once the popularity of all data chunks is collected, the system only maintains the top $k$
+most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
+%Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
+%this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
+%analytic design guidance.
+
+% Figure~\ref{fig:Datazipf} illustrates the distribution of chunk popularity based on a data trace from Alibaba with over 2500 VMs.
+% The distribution is zipf like and popular chunks are dominating the large portion of data chunks.
+% We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
+% $\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.
+
+\item 
+\textbf{VM-specific duplicate search optimization} --
+Fingerprint lookup within a VM does not require a signficant  amount of memory resource.
+While cross-VM deduplication is simplified, we intend to optimize the VM-sepcific deduplication 
+as much as possible.
+
+We start with the standard version-based detection~\cite{Clements2009,Vrable2009}
 to identify changed content with dirty bits in a coarse grain segment level.
@@
 
-Since the best deduplication uses a non-uniform chunk size 
-with an average of 4KB or 8KB~\cite{Jin2009},
+Since the previous work typically uses a non-uniform chunk size 
+with an average of 4KB or 8KB for the best deduplication 
+effectiveness~\cite{Guo2011,extreme_binning09,bottleneck08,Dong2011},
 we conduct additional local similarity guided deduplication on a snapshot by comparing
@@
 
-%\item 
-\textbf{Global deduplication using popular chunks} --
-This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
-Our key observation is that the local deduplication has removed most of the duplicates.
-There are fewer deduplication opportunities across VMs while the memory and network
-consumption for global comparison is more expensive.
-Thus our approximation is that the global fingerprint comparison only searches for the top $k$
-most popular items. This dataset is called the \textbf{PDS} (popular data set). 
-We define chunk popularity as the number of unique copies of the chunk in the data-store,
-i.e., the number of copies of the chunk after local deduplication.
-This number can be computed periodically, e.g., on a weekly basis.
-Once the popularity of all data chunks is collected, the system only maintains the top $k$
-most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
-%Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
-%this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
-%analytic design guidance.
-
- Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 
-from Alibaba with 2500 VMs discussed in Section ~\ref{sect:evaluation}.
-%the distribution of chunk popularity~\cite{WeiZhangIEEE} 
-%based on a production data trace from Alibaba with over 2500 VMs.
-The distribution is Zipf-like and popular chunks dominate the distribution.
-We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and 
-from the evaluation in Section~\ref{sect:evaluation}, we find that
-$\sigma$ with a range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
-%For example,
-%with top 2\% of the most popular chunks stored in PDS, up-to 40\% of the raw backup 
-%data can be eliminated by fingerprint lookup in PDS index.
-
-Since $\sigma$ is relatively small and these top chunks are shared among multiple VMs, 
-we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
-
-% Figure~\ref{fig:Datazipf} illustrates the distribution of chunk popularity based on a data trace from Alibaba with over 2500 VMs.
-% The distribution is zipf like and popular chunks are dominating the large portion of data chunks.
-% We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
-% $\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.
-
-%\item 
+\item 
 \textbf{VM-centric file system block management} --
@@
 %conducts the backup of one VM at a time, and thus only requires a write buffer for one VM.
-%\end{itemize}
-
- \begin{figure}
- \centering
-  \includegraphics[width=2.5in]{figures/log-log-disk}
- \caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
- \label{fig:Datazipf}
- \end{figure}
-
-% {\it [Need to find a place to put these numbers in: Total number of chunks 
-% in 350 snapshots: 1,546,635,485. 
-% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
+\end{itemize}

### 2014-06-27 snapshot_system/paper_intro.tex
revise for ACM cloud

--- 2014-01-31 snapshot_system/paper_intro.tex
@@
 storage demand.
+
 %For example, the Aliyun cloud, which is  the largest cloud service provider
@@
 %Without deduplication,
+Source-side deduplication (e.g. ~\cite{Symantic Netbean})
+ eliminates duplicates before backup data is transmitted
+to a secondary storage, which saves network bandwidth significantly; however its resource
+usage can impact other co-located cloud services. 
+But it is memory-intensive to compare a large number of fingerprints and identify
+duplicates, even optimization or approximation techniques are developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
+When deleting unused snapshots, a mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  
+is effective while it still carries a significant cost, especially in a distributed
+setting.  Another side effect of deduplication is the possible loss of failure
+resilience~\cite{Bhagwat2006}.  Separate files share the same physical copies of blocks that are
+logically duplicated among them.  If a shared block is lost, all files that
+share that block are affected.  
 A cloud may offload backup workload from production 
@@
 of network bandwidth that would otherwise be available to user VMs. 
+\comments{
 Even when the storage system implements deduplication internally
@@
 (which increases backup cost).
+}
 
@@
 that is co-located with user VMs, sharing the cloud computer, network, and
-storage resource with them.
-We describe methodologies to address the following two challenges: 
-1) simple deduplication and snapshot deletion with competitive efficiency and 
-a small resource usage without affecting other collocated cloud services;
+storage resource with them.  We propose a VM-centric approach that
+simplifies deduplication and snapshot deletion.
+The key benefit is that while maintaining  a competitive deduplication efficiency,
+the scheme uses a small resource usage without affecting other collocated cloud services.
+\comments{
 2) improved fault isolation for the sharing of deduplicated data,
@@
 exception.
-% so that users stop incurring storage charges immediately after snapshot deletion.
-%\end{itemize}
-
-% low-cost VM-centric snapshot backup approach that is co-located within 
-% the existing converged storage architecture. Our solution leverages the scalability of the underlying
-% distributed file system and provides global data deduplication in a resource friendly manner.
-
-%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
-%automatically conducts  the backup of virtual disk images to all active users every day.
-%The cost of supporting a large number of concurrent backup streams is high
-%because of the huge storage demand and the use of deduplication
-
-%Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
-%can effectively identify and remove content duplicates among snapshots, 
-%but such a solution can be expensive. There is also a large amount of 
-%network traffic to transfer  data from the host machines to the backup facility
-%before duplicates are removed.
 
@@
 share that block are affected.  
-%The problem is particularly acute for VM
-%snapshots where the purpose of the snapshot is precisely to create redundant
-%data copies so that VMs are more fault resilient.  
 Thus, there exists a
@@
 duplicate sharing on  fault tolerance.
-%Because
-%of highly repetitive content in snapshots from different VMs, many data chunks
-%are shared by virtual machines.  Failure of a few shared data chunks can have
-%a broad effect and snapshots of these virtual machines could be affected.  The
-%previous work in deduplication focuses on the efficiency and approximation of
-%fingerprint comparison, and has not addressed fault tolerance issues  together
-%with deduplication.
-
-%This paper explores the storage and
-%performance efficiencies that such a {\em VM-centric} 
-%combination of local and global
-%techniques can achieve.  
+} 
 We term our approach {\em VM-centric} because the deduplication
@@
 treating all blocks as being equivalent within the storage system.
-We detail the storage, performance,
-and fault isolation properties
+Our work focuses on a tradeoff that allows the sharing of only ``popular'' data blocks 
+across virtual machines while using localized deduplication within each VM
+to achieve both storage savings and fault isolation.
+\comments{
+We detail the storage, performance, and fault isolation properties
 of our method and verify these properties empirically using a prototype
@@
 converged IaaS cloud environments.
-Our work focuses on sharing only ``popular'' data blocks 
-(through deduplication and limited replication)
-across 
-virtual machines while using localized deduplication within each VM
-to achieve both storage savings and fault isolation.
+
 %, and to propose a VM-centric approach that localizes
@@
 blocks to be deduplicated (and then replicated) across VMs.  
+}
 

### 2014-06-27 snapshot_system/paper_abs.tex

@@
 because of excessive redundant content blocks. Common techniques 
-%use dirty bits to detect
-%the version  change and  
 perform fingerprint comparison to remove duplicates
-across virtual machines. However, letting a duplicate data block be shared
-by many virtual machines creates data dependence and is less fault-resilient. 
-%This paper studies the impact of deduplication on 
-%fault resilidence  of virtual machine snapshots, created by data dependence  among duplicates
-%and proposes a VM-centric approach that strikes a balance between deduplication efficiency
-%and fault isolation 
+across virtual machines.
+However, letting a duplicate data block be shared
+by many virtual machines represents a tradeoff between
+storage efficiency and data availability.
+%by many virtual machines creates data dependence and is less fault-resilient. 
+%%This paper studies the impact of deduplication on 
+%%fault resilidence  of virtual machine snapshots, created by data dependence  among duplicates
+%%and proposes a VM-centric approach that strikes a balance between deduplication efficiency
+%%and fault isolation 
 This paper proposes a VM-centric backup service on a converged  cloud cluster architecture

### 2014-06-27 snapshot_system/paper_intro.tex

@@
 simplifies deduplication and snapshot deletion.
-The key benefit is that while maintaining  a competitive deduplication efficiency,
+The key advantage of this approach  is that while maintaining  a competitive deduplication efficiency,
 the scheme uses a small resource usage without affecting other collocated cloud services.
 \comments{
+The key contribution of this work is a set of methodologies to address the following two challenges:
+1) simple deduplication and snapshot deletion with competitive efficiency and 
+a small resource usage without affecting other collocated cloud services;
 2) improved fault isolation for the sharing of deduplicated data,

### 2014-07-17 snapshot_system/paper_background.tex
revis

@@
 and a parallel batch solution for cluster-based deduplication is 
-studied in ~\cite{wei2013}.
+studied in ~\cite{WeiZhangIEEE}.
 
@@
 is lost in the storage, all VMs that refer such chunks after deduplication face a data loss.
-This issue is identified in ~\cite{Baghat2006} which proposes to use more replication for data shared by more files.
+This issue is identified in ~\cite{Reliability06} which proposes to use more replication for data shared by more files.
 It is complex to implement this idea in VM snapshot backup. 

### 2014-07-17 snapshot_system/paper_dedup.tex
revis

@@
 
-Since $\sigma$ is relatively small and these top chunks are shared among multiple VMs, 
-we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
-
 %when restricting fingerprint comparison within a VM uses
@@
 most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
+These top chunks are shared among multiple VMs and  since $\sigma$ is relatively small, 
+we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
 %Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
@@
 
+It should be noted that the fingerprint-guided mapping used in ~\cite{extreme_binning09,Dong2011} narrows
+the search scope of each data chunk, but it does not reduce th total amount of searchable fingerprints
+used for the entire deduplication. In comparison we only focus on top popular chunks among VMs and this
+significantly reduces the total amount of  searchable fingerprints.
+
 \item 
 \textbf{VM-specific duplicate search optimization} --
-Fingerprint lookup within a VM does not require a signficant  amount of memory resource.
 While cross-VM deduplication is simplified, we intend to optimize the VM-sepcific deduplication 
-as much as possible.
+as much as possible under a reasonable memory consumption
+ to make up the loss of deduplication opportunites due to the cross-VM popularity constraint.
+
+%Fingerprint lookup within a VM does not require a signficant  amount of memory resource.
 
@@
 chunk fingerprints of a dirty segment 
-with those in  {\em similar} segments from its parent snapshot. 
-We define two segments are similar if their content signature is the same.
+with those in  {\em potentially similar} segments from its parent snapshot. 
+We define a parent  segment is  potentially similar to the currnet segment if 1) the paranet segment
+at the same offset as the current segment.
+2) the signature of these segments is the same.
 This segment content signature value is defined as the minimum value of all its chunk fingerprints 
@@
 By limiting at most 10 similar segments to search, the amount of memory for maintaining those 
-similar segment recipes is small.
-As part of our local duplicate search we also compare the current segment
-against the parent segment at the same offset.
+similar segment recipes is 190K, which is small.
+
+%As part of our local duplicate search we also compare the current segment
+%against the parent segment at the same offset.
 

### 2014-07-17 snapshot_system/paper_intro.tex
revis

@@
 %Without deduplication,
-Source-side deduplication (e.g. ~\cite{Symantic Netbean})
+Source-side deduplication (e.g. ~\cite{Symantec2009})
  eliminates duplicates before backup data is transmitted
@@
 setting.  Another side effect of deduplication is the possible loss of failure
-resilience~\cite{Bhagwat2006}.  Separate files share the same physical copies of blocks that are
+resilience~\cite{Reliability06}.  Separate files share the same physical copies of blocks that are
 logically duplicated among them.  If a shared block is lost, all files that

### 2014-07-17 snapshot_system/paper_background.tex
re
rev

--- 2014-06-27 snapshot_system/paper_background.tex
@@
     \centering
-    \includegraphics[width=3in]{images/colocated-arch}
+    %\includegraphics[width=3in]{images/colocated-arch}
+    \includegraphics[width=3in]{images/converged_arch}
     \caption{VM snapshot backup running on a converged cloud cluster.}
@@
 uses  an in-memory Bloom filter and a prefetching cache for data chunks 
-which may be
-accessed.  
+which may be accessed.  
 %An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
-Approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
-to reduce memory requirements at the cost of some loss of deduplication
-efficiency.
-Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
-and a parallel batch solution for cluster-based deduplication is 
-studied in ~\cite{wei2013}.
-
+%Approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
+%to reduce memory requirements at the cost of some loss of deduplication
+%efficiency.
+Additional inline deduplication and  approximation techniques
+are studied in ~\cite{extreme_binning09,Guo2011,sparseindex09,Guo2011,Srinivasan2012,WeiZhangIEEE}.  
+%and a parallel batch solution for cluster-based deduplication is 
+%studied in ~\cite{WeiZhangIEEE}. 
 \comments{
@@
 %VM dependence minimization during deduplication and file system block management.
-
-Even with these optimization and approximation techniques, resource usage for deduplication
-is still extensive for a shared cloud cluster.  For example, the
+Even with these optimization and approximation techniques, resource usage such as memory  for deduplication
+is still extensive for a shared cloud cluster.  
+\comments{
+For example, the
 sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011},
@@
 and every deduplication request may access a remote machine for index lookup and the overall overhead of access latency 
-for all requests can be significant.  In general
-with a cluster of machines in a cloiud cluster, there will be more memory requirement per machine such as a 
+for all requests can be significant. 
+ In general
+with a cluster of machines in a cloud cluster, there will be more memory requirement per machine such as a 
 fingerprint cache, for cross-machine fingerprint comparison~\cite{bottleneck08,Dong2011} and a deduplication
-task often needs several gigabytpes of memory, which impacts other cloud services sharing the omputing resource.
+task often needs several gigabytpes of memory, which impacts other cloud services sharing the computing resource.
+}
 
-Whiel deduplication reduces storage cost, it creates an artitical data dependence among VMs: when a shared data chunk
+While deduplication reduces storage cost, it creates an artificial data dependence among VMs: when a shared data chunk
 is lost in the storage, all VMs that refer such chunks after deduplication face a data loss.
-This issue is identified in ~\cite{Baghat2006} which proposes to use more replication for data shared by more files.
-It is complex to implement this idea in VM snapshot backup. 
-This is because the file system block  size in a distributed file system such as  
-the Hadoop file system and the Google file system~\cite{googlefs03}
-is large (e.g.  64MB) so as to optimize file system performance
-for big data. Since  deduplication implementations~\cite{Guo2011,extreme_binning09,bottleneck08,Jin2009,Dong2011}
- typically use smaller chunk sizes (e.g. 4K bytes),  a large file block contains many small chunks with different 
-degree of sharing and  these file blocks would have to be replicated.
+This issue is identified in ~\cite{Reliability06} which proposes to use more replication for data shared by more files,
+and we will adopt this idea.
+When the backup storage is implemented using a distributed file system such as Hadoop and Google file system~\cite{googlefs03},  
+the file system block  size is often chosen to be large. On the other hand, 
+deduplication implementations~\cite{Guo2011,extreme_binning09,bottleneck08,Jin2009,Dong2011}
+ typically use smaller chunk sizes (e.g. 4K bytes).
+Thus we need to consider the size gap between file system blocks and chunks  in adding more replications for popular chunks.
 

### 2014-07-17 snapshot_system/paper_dedup.tex
rev

@@
 \textbf{Cross-VM global deduplication using popular chunks} --
-We seperate the deduplication within a VM and cross VMs.
-This is because global deduplication that detects the apperance of a chunk 
+We separate the deduplication within a VM and cross VMs
+and simplify the cross-VM deduplication while maximizing the inter-VM deduplication efficiency  as much as possible.
+This is because global deduplication that detects the appearance of a chunk 
 in any VM requires a substantial resource for fingerprint comparison.
+To simplify cross-VM deduplication, we restrict the search scope of deduplication within the top $k$ most popular items.
 %This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
-Our key observation is for those chunks that appear in different VMs, top $k$ most popular items
-dominate the apperance. 
  \begin{figure}
@@
 % Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
-
+Our key observation is for those chunks that appear in different VMs, top $k$ most popular items
+dominate the distribution.  This popular data set is called the \textbf{PDS}. 
 Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 
 from Alibaba with 2500 VMs discussed in Section ~\ref{sect:evaluation}.
+We define chunk popularity as the number of unique copies of the chunk in the data-store,
+i.e., the number of copies of the chunk after local deduplication.
 %the distribution of chunk popularity~\cite{WeiZhangIEEE} 
 %based on a production data trace from Alibaba with over 2500 VMs.
-The distribution is Zipf-like and popular chunks dominate the distribution.
-We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and 
+The distribution from this figure is Zipf-like. 
+Let  $\sigma$ denote as the percentage of unique data chunks belonging to PDS and 
 from the evaluation in Section~\ref{sect:evaluation}, we find that
@@
 %consumption for global comparison is more expensive.
-Thus our approximation is that the global cross-VM fingerprint comparison only searches for the top $k$
-most popular items. This dataset is called the \textbf{PDS} (popular data set). 
-We define chunk popularity as the number of unique copies of the chunk in the data-store,
-i.e., the number of copies of the chunk after local deduplication.
-This number can be computed periodically, e.g., on a weekly basis.
-Once the popularity of all data chunks is collected, the system only maintains the top $k$
-most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
-These top chunks are shared among multiple VMs and  since $\sigma$ is relatively small, 
-we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
+%Thus our approximation is that the global cross-VM fingerprint comparison only searches for the top $k$
+%most popular items. 
+PDS  can be computed periodically, e.g., on a monthly basis.
+%Once the popularity of all data chunks is collected, the system only maintains the top $k$
+%most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
+%These top chunks are shared among multiple VMs and  since $\sigma$ is relatively small, 
+%we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
 %Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
@@
 
-It should be noted that the fingerprint-guided mapping used in ~\cite{extreme_binning09,Dong2011} narrows
+Compared to ~\cite{bottleneck08}, the fingerprint index  size is reduced by $1-\sigma$
+and the searchable fingerprint space  becomes very small under the popularity constraint.  
+The fingerprint-guided distributed mapping in ~\cite{extreme_binning09,Dong2011} narrows
 the search scope of each data chunk, but it does not reduce th total amount of searchable fingerprints
-used for the entire deduplication. In comparison we only focus on top popular chunks among VMs and this
-significantly reduces the total amount of  searchable fingerprints.
+used for the entire deduplication. 
+%In comparison we only focus on top popular chunks among VMs and this
+%significantly reduces the total amount of  searchable fingerprints.
 
@@
 \textbf{VM-specific duplicate search optimization} --
-While cross-VM deduplication is simplified, we intend to optimize the VM-sepcific deduplication 
+While cross-VM deduplication is simplified, we intend to optimize the VM-specific deduplication 
 as much as possible under a reasonable memory consumption
- to make up the loss of deduplication opportunites due to the cross-VM popularity constraint.
+ to make up the loss of deduplication opportunities due to the cross-VM popularity constraint.
 
@@
 %and the device driver is extended to support tracking changed segments using a dirty bitmap. 
-The reason to choose a coarse grain level is that 
+The reason to choose a coarse grain segment level is that 
 since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in 
@@
 with those in  {\em potentially similar} segments from its parent snapshot. 
-We define a parent  segment is  potentially similar to the currnet segment if 1) the paranet segment
+We define a parent  segment is  potentially similar to the current segment if 1) the parent segment
 at the same offset as the current segment.
@@
 This segment content signature value is defined as the minimum value of all its chunk fingerprints 
-computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
-content similarity is an approximation~\cite{resemblance97}.  When processing a dirty segment,
+computed during backup and is recorded in the snapshot metadata (called recipe). 
+%Note that this definition of content similarity is an approximation~\cite{resemblance97}.  
+When processing a dirty segment,
 its  similar segments can be found easily from the
@@
 When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
-to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
-accumulate small local chunks. 
+into a file system block.  A  backend file system block can contain a number of chunks,
+there are   two reasons. In addition to the reason that a file system block is often
+configured to be large, there is another reason that a number of chunks can be combined together
+and compressed further using a standard data compression method. 
 %We manage this accumulation process using a log-structured storage scheme built
@@
 %Non-PDS chunks from the same VM are stored in one append store. 
-Each file system block is either dedicated to non-PDS chunks, or PDS-chunks.
-A file system block for non-PDS chunks is associated with one VM and does not contain
-any PDS chunks, such that our goal of fault isolation is maintained.
+We set two constraints in composing chunks for a file system block as follows:
+1) Each file system block is either dedicated to non-PDS chunks, or PDS-chunks.
+2) A non-PDS file system block is only associated with one VM.
+
+Restricting the association with one VM improves fault isolation when some file blocks are lost during failure. 
 In addition, storing PDS chunks separately allows special replication handling for those popular shared data. 
 %%% talk something about snapshot store advantage here? %%%
-
 %One could try to rely on filesystem features to 
@@
 popular chunks from the less-popular, the popular chunks are dispersed across
-all of the filesystem blocks in the storage system.  Then we cannot leverage the file system features to 
-provide extra replication to popular and shared chunks because  
-we have to add extra replication to each file block as long as it contains a popular chunk.
+all of the filesystem blocks in the storage system and we would have
+to add extra replications for {\em all} file blocks in order to   follow the popularity-driven replication idea 
+from ~\cite{Reliability06}. That reduces the storage efficiency.
+%Then we cannot leverage the file system features to 
+%provide extra replication to popular and shared chunks because  
+%we have to add extra replication to each file block as long as it contains a popular chunk.
 

### 2014-07-17 snapshot_system/paper_dedup.tex
r

@@
 %significantly reduces the total amount of  searchable fingerprints. 
+We have not adopted the index sampling in \cite{Guo2011} because its extension for
+for a distributed architecture is difficult.  To use a distributed memory version of the sampled index, every deduplication 
+request may access a remote machine for index lookup and the overall overhead of access latency for all requests
+can be significant.
 

### 2014-07-17 snapshot_system/paper_eval.tex
re

@@
 %and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.
-
-%\subsection{Fault Isolation and Snapshot Availability}
-\subsection{Snapshot Availability}
-
- Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
-there are up to 20 machines failed in a cluster. 
-The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
-and then calculate the average availability of VM snapshots.
-The case for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
-the same from $p=100$ setting to $p=1000$. Each machine hosts about 25 VMs in both cases
-and with different $p$ values, the availability varies when the number of failures in the cluster changes.
-
-%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
-%We have assumed a worst-case scenario that  a PDS block is shared by every VM. 
-%($V_c=p*V$), which is to be expected when PDS
-%blocks are sorted by hash, as their order is randomized.
-%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
-%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
-%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
-%count the number of dependencies from a file system block to VM.
-%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
-%case for VO approach. 
-%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
-%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
-%while VC with 99.9\% loses snapshots of 2.5 VMs.
-%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
-%and packs  data blocks for one VM as much as possible.  The extra replication
-%for PDS blocks also significantly increases the snapshot availability even when
-%a PDS file block is shared by every VM.
-%=======
-%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
-%as storage nodes fail. 
-%We assume a random distirbution of 64MB file system
-%blocks (FSBs). where FSBs are not randomly distributed availability might
-%be improved by limiting the number of storage nodes a particualr VM depends
-%on but we take the conservative approach. We compare VO, the expected case for
-%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
-%based on measured values in our dataset.
-%To obtain VO sharing of file blocks, we perform perfect deduplication over 105 VMs, 
-%append unique chunks to a DFS file and
-%count the number of dependencies from a file system block to VM.
-%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
-%case for VO approach.
-
- Table~\ref{tab:vm-availability} shows 
-that VC has a significantly  higher availability than VO.
-% as the number of failed machines increases from 3 to 20.
-%Our VM-centric approach shows significant improvements
-%in VM availability.
-With $p=100$ and 3 failures,
-VO with 69.5\% availability could lose data in 763 VMs 
-while VC with 99.7\% only loses data for 8 VMs out of 2500 VMs.
-The key reason is that for most data in VC, only a single VM can be affected by
-the loss of a single file block
-%Since most blocks contain chunks for a single
-%VM, VMs can depend on a smaller number of blocks, 
-while in VO, the loss of a
-single block tends to affect many VMs.
-When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
-and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
-loses most of non-PDS blocks given the replication degree for non PDS is 3.
-When $p=1000$, the percentage of failures is then 2\% and VC delivers a meaningful availability 
-with 99.62\%, outperforming VO significantly.
-
-% because our VM-centric approach
-%localizes deduplication.
-
-%Although the loss of a PDS block affects many VMs,
-%by increasing replication for those blocks we minimize the effect on VM
-%snapshot availability, and this is one of the key contributions of our
-%approach, the clear separation of highly popular data from less popular data.
-
-%By having extra replicas for the PDS data, we reduce the failure rate of PDS
-%FSBs enough that the failure rate for the VM approaches the failure rate of the
-%Non-PDS blocks. This minimizes the drop in availability between the expected
-%and worst case for VC.
-%
-%One of the advantages of VC is that there is a division between
-%popular and non-popular data to facilitate improved reliability. 
-Figure~\ref{fig:pds-replication} shows
-the impact of increasing PDS data replication degree. 
-While the impact on storage cost is small (because we have separated out only
-the most popular blocks),
-a replication degree of 6  has a significant improvement over 4. The
-availability does not increase much  when increasing
-$r_c$ from 6 to 9 and the benefit is not so visible after $r_c>9$. 
-That is because when the number of failed machines increases beyond 6, 
-the non-PDS data availability starts to deteriorate significantly given its replication degree
-$r$ is set to 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.
-
-%This is because, as described before, the availability of the VM approaches the
-%availiability of the Non-PDS data as the failure rate of PDS data gets very small.
-
-\begin{table}[htbp]
-  \centering
-    \footnotesize
-    \tabcolsep=0.11cm
-    \pgfplotstabletypeset[
-        comment chars=!,%use ! before a row in the data table to exclude it
-        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
-        columns/NodesFailed/.style={
-            column name={\multirow{3}{*}{Failures ($d$)}}
-        },
-        columns/VO100/.style={
-            column name={
-                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
-                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
-            VO},
-            fixed, precision=6
-        },
-        columns/VC100/.style={
-            column name={VC},
-            fixed, precision=6},
-        columns/VO1000/.style={
-            column name={VO},
-            fixed, precision=6},
-        columns/VC1000/.style={
-            column name={VC},
-            fixed, precision=6},
-        every head row/.style={
-            before row={\hline},
-            after row={\hline},
-        },
-        every last row/.style={after row=\hline},
-        column type/.add={}{|},
-        every first column/.style={column type/.add={|}{}},
-        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
-        %skip rows between index={0}{3},
-        %skip rows between index={4}{5},
-        %skip rows between index={6}{10},
-        %skip rows between index={11}{20},
-        %skip rows between index={21}{41}
-    ]{figures/availability_table.txt}
-    \caption{Availability of VM snapshots for VO ($r=3$) and VC ($r_c=6$, $r=3$).}
-    \label{tab:vm-availability}
-\end{table}
-
-\begin{figure}[htbp]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-                        width=\linewidth,
-                        height=0.6\linewidth,
-		%title={PDS Replication affect on availability},
-		xlabel={Failed storage nodes},
-		ylabel={Availability (\%)},
-                xmin=0,
-                xmax=10,
-		%extra y ticks={99.9}, %if important numbers are missing
-                mark options=solid,
-                legend style={
-                    cells={anchor=west}, %legend entry alignment
-                    legend pos=south west %legend position
-                },
-                reverse legend,
-		]
-                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
-                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
-                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
-                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
-                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
-                \legend{
-                    VO,
-                    $r_c=4$,
-                    $r_c=5$,
-                    $r_c=6$,
-                    $r_c=9$
-                }
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Availability of VM snapshots in VC with different PDS replication degrees on a $p=100$-node cluster.}
-  \label{fig:pds-replication}
-\end{figure}
 
@@
 \begin{small}
-    \begin{tabular}{|c|c|c|c|c|}
+    \begin{tabular}{|c|c|c|c|c|c|}
     \hline 
+&
      \multicolumn{4}{|c|}{VC}  & VO \\ \hline
+&
      2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
-     no-simi&   &&  &    \\ \hline
-     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
+&     no-simi&   &&  &    \\ \hline
+Dedup &     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
+Mem(MB) &     108&  46 & 118  & 190 & 2400 \\ \hline
     \end{tabular}
 \end{small}
-    \caption{Deduplication efficiency for different VC settings and
+    \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
         Stateless Routing with Binning (SRB).}
@@
 % false-positive ratio, therefore less amount of unused chunks are misjudged.
+
+%\subsection{Fault Isolation and Snapshot Availability}
+\subsection{Snapshot Availability}
+
+ Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
+there are up to 20 machines failed in a cluster. 
+The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
+and then calculate the average availability of VM snapshots.
+The case for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
+the same from $p=100$ setting to $p=1000$. Each machine hosts about 25 VMs in both cases
+and with different $p$ values, the availability varies when the number of failures in the cluster changes.
+
+%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
+%We have assumed a worst-case scenario that  a PDS block is shared by every VM. 
+%($V_c=p*V$), which is to be expected when PDS
+%blocks are sorted by hash, as their order is randomized.
+%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
+%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
+%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
+%count the number of dependencies from a file system block to VM.
+%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
+%case for VO approach. 
+%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
+%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
+%while VC with 99.9\% loses snapshots of 2.5 VMs.
+%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
+%and packs  data blocks for one VM as much as possible.  The extra replication
+%for PDS blocks also significantly increases the snapshot availability even when
+%a PDS file block is shared by every VM.
+%=======
+%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
+%as storage nodes fail. 
+%We assume a random distirbution of 64MB file system
+%blocks (FSBs). where FSBs are not randomly distributed availability might
+%be improved by limiting the number of storage nodes a particualr VM depends
+%on but we take the conservative approach. We compare VO, the expected case for
+%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
+%based on measured values in our dataset.
+%To obtain VO sharing of file blocks, we perform perfect deduplication over 105 VMs, 
+%append unique chunks to a DFS file and
+%count the number of dependencies from a file system block to VM.
+%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
+%case for VO approach.
+
+ Table~\ref{tab:vm-availability} shows 
+that VC has a significantly  higher availability than VO.
+% as the number of failed machines increases from 3 to 20.
+%Our VM-centric approach shows significant improvements
+%in VM availability.
+With $p=100$ and 3 failures,
+VO with 69.5\% availability could lose data in 763 VMs 
+while VC with 99.7\% only loses data for 8 VMs out of 2500 VMs.
+The key reason is that for most data in VC, only a single VM can be affected by
+the loss of a single file block
+%Since most blocks contain chunks for a single
+%VM, VMs can depend on a smaller number of blocks, 
+while in VO, the loss of a
+single block tends to affect many VMs.
+When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
+and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
+loses most of non-PDS blocks given the replication degree for non PDS is 3.
+When $p=1000$, the percentage of failures is then 2\% and VC delivers a meaningful availability 
+with 99.62\%, outperforming VO significantly.
+
+% because our VM-centric approach
+%localizes deduplication.
+
+%Although the loss of a PDS block affects many VMs,
+%by increasing replication for those blocks we minimize the effect on VM
+%snapshot availability, and this is one of the key contributions of our
+%approach, the clear separation of highly popular data from less popular data.
+
+%By having extra replicas for the PDS data, we reduce the failure rate of PDS
+%FSBs enough that the failure rate for the VM approaches the failure rate of the
+%Non-PDS blocks. This minimizes the drop in availability between the expected
+%and worst case for VC.
+%
+%One of the advantages of VC is that there is a division between
+%popular and non-popular data to facilitate improved reliability. 
+Figure~\ref{fig:pds-replication} shows
+the impact of increasing PDS data replication degree. 
+While the impact on storage cost is small (because we have separated out only
+the most popular blocks),
+a replication degree of 6  has a significant improvement over 4. The
+availability does not increase much  when increasing
+$r_c$ from 6 to 9 and the benefit is not so visible after $r_c>9$. 
+That is because when the number of failed machines increases beyond 6, 
+the non-PDS data availability starts to deteriorate significantly given its replication degree
+$r$ is set to 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.
+
+%This is because, as described before, the availability of the VM approaches the
+%availiability of the Non-PDS data as the failure rate of PDS data gets very small.
+
+\begin{table}[htbp]
+  \centering
+    \footnotesize
+    \tabcolsep=0.11cm
+    \pgfplotstabletypeset[
+        comment chars=!,%use ! before a row in the data table to exclude it
+        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
+        columns/NodesFailed/.style={
+            column name={\multirow{3}{*}{Failures ($d$)}}
+        },
+        columns/VO100/.style={
+            column name={
+                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
+                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
+            VO},
+            fixed, precision=6
+        },
+        columns/VC100/.style={
+            column name={VC},
+            fixed, precision=6},
+        columns/VO1000/.style={
+            column name={VO},
+            fixed, precision=6},
+        columns/VC1000/.style={
+            column name={VC},
+            fixed, precision=6},
+        every head row/.style={
+            before row={\hline},
+            after row={\hline},
+        },
+        every last row/.style={after row=\hline},
+        column type/.add={}{|},
+        every first column/.style={column type/.add={|}{}},
+        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
+        %skip rows between index={0}{3},
+        %skip rows between index={4}{5},
+        %skip rows between index={6}{10},
+        %skip rows between index={11}{20},
+        %skip rows between index={21}{41}
+    ]{figures/availability_table.txt}
+    \caption{Availability of VM snapshots for VO ($r=3$) and VC ($r_c=6$, $r=3$).}
+    \label{tab:vm-availability}
+\end{table}
+
+\begin{figure}[htbp]
+  \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+                        width=\linewidth,
+                        height=0.6\linewidth,
+		%title={PDS Replication affect on availability},
+		xlabel={Failed storage nodes},
+		ylabel={Availability (\%)},
+                xmin=0,
+                xmax=10,
+		%extra y ticks={99.9}, %if important numbers are missing
+                mark options=solid,
+                legend style={
+                    cells={anchor=west}, %legend entry alignment
+                    legend pos=south west %legend position
+                },
+                reverse legend,
+		]
+                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
+                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
+                \legend{
+                    VO,
+                    $r_c=4$,
+                    $r_c=5$,
+                    $r_c=6$,
+                    $r_c=9$
+                }
+		\end{axis}
+	\end{tikzpicture}
+  \caption{Availability of VM snapshots in VC with different PDS replication degrees on a $p=100$-node cluster.}
+  \label{fig:pds-replication}
+\end{figure}

### 2014-07-17 snapshot_system/paper_eval_del.tex
revise deletion experiments

\begin{table}[htb]
\centering
\begin{small}
\begin{tabular}{|c|c|c|c|}
    \hline 
%& \multicolumn{4}{|c|}{VC}  & VO \\ \hline
	    &Time p=50 & Time p=100 & Memory \\
	    &(hours)  & (hours) & (GB) \\
\hline
Mark-sweep  & 35.9  &  84.3  & 1.2--3 \\
\hline
Grouped &     18.6    & 43.6   & 1.2--3 \\
mark-sweep &        &    &  \\
\hline
VC w/o sum &  0.7     & 0.82   & 0.05 -- 1.96 \\
\hline
VC  &  0.012      & 0.014   & 0.015  \\
\hline
VC Repair  &  0.7      & 0.82   & 0.05 -- 1.96 \\
\hline
    \end{tabular}
\end{small}
    \caption{ Processing time and memory usage  for
deletion}  
    \label{tab:deletion-cmp}
\end{table}

Table~\ref{tab:deletion-cmp}   lists a comparison of processing time and memory usage
using the four deletion approaches when $p=100$ and $p=50$. These four 
methods are 1) the standard mark-sweep method. 2) Grouped mark-sweep~\cite{Guo2011}. 
3)   VC summary vectors. 4) VC with summary vectors.
The I/O speed for the backend distributed file system is about 50MB/second
and the speed drops to about 25MB/second when
when 100 machines read the backend file system concurrently due to the network
contention. We explain the results for $p=100$ below and notice each physical machine hosts 25VMs on average. The explanation for $p=50$ is similar.

For the mark-sweep approach on $p=100$, a physical machine is responsible of 
reading the metadata of non-deduplicated chunks used in the hosted 
virtual machines and keeping the usage index table in the memory.
Then all machines read the meta data 
of snapshots in parallel and mark the usage of referenced chunks
in the usage table.
This process is repeated 100 times for all physical machines.
The memory allocated at each physical machine is for the 
chunk usage table of 25 VMs. The average size is 1.2GB and the maximum is
3GB. If we reduce the size of  the usage table at each machine, 
then there are more iterations to mark all data and it 
will take longer time.    
For the grouped mark-sweep, about 50\% of snapshot meta reading can be 
avoided in assessing the reference usage of non-duplicate chunks. 
Thus it takes 50\% less time, which is about 43 hours, but the 
memory requirement does not decrease.

For VC without summary vectors, all physical machines conduct the mark-sweep process in parallel, 
but each machine only handles one VM at time and 
the scope of meta data comparison is controlled within the single VM.
Popular chunks are excluded. The average memory usage is the index size of 
non-deduplicated VM chunks, which is about 50MB on average and the largest
size is 1.96GB. 
For VC with summary vectors, each physical machine loads
the VM snapshots and only needs to compare with the summary vectors.
The memory usage is controlled within 15MB for hosting the summary vectors
and small buffers. The deletion time is reduced to less than 1 minute.
The periodic leakage repair still takes about 0.83 hours while using
an average of 50MB memory. For  few big VMs in a skewed data distribution,
the repair uses upto 1.9GB memory.
Such a repair does not occur often (e.g. occurs every 19.6 days as discussed in Section~\ref{sect:delete}).

### 2014-07-17 snapshot_system/paper_dedup.tex
rev

@@
 from the evaluation in Section~\ref{sect:evaluation}, we find that
-$\sigma$ with a range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
+$\sigma$ with about  2\% can deliver a fairly competitive deduplication efficiency.
+%$\sigma$ with about  range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
 %For example,

### 2014-07-17 snapshot_system/paper_eval.tex
add deletion
rev

@@
 
-\subsection{Deduplication Efficiency}
+\subsection{Deduplication Efficiency and Memory Usage}
 \label{sect:evaldedup}
@@
 }
-\begin{table}[htb]
-\centering
-\begin{small}
+
+\comments{
+old table, delete 4%
     \begin{tabular}{|c|c|c|c|c|c|}
@@
     \end{tabular}
+
+}
+\begin{table}[htb]
+\centering
+\begin{small}
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline 
+&
+     \multicolumn{3}{|c|}{VC}  & VO \\ \hline
+&
+     2\%No PDS &2\%PDS     & 2\%PDS & SRB  \\ 
+&        &&     no-simi & \\ \hline
+Dedup &      93.02\%  & 96.01\% & 94.31\% & 97.86\% \\ 
+efficiency &          &       &           &      \\    \hline 
+Memory(MB) &      46 & 118  & 108 & 2400 \\ \hline
+    \end{tabular}
 \end{small}
@@
 
-Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
+Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency and per-machine memory usage for SRB and VC with different 
 settings.
@@
 reach over 96\%. 
-When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
-more index space is allocated  per machine for  PDS fingerprint lookup.
-% increases from 100MB to 200MB per physical machine as discussed later. 
-%and  the deduplication efficiency can reach 96.489\%.
-%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
+%When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
+%more index space is allocated  per machine for  PDS fingerprint lookup.
 The loss of efficiency in VC is caused by the restriction of the physical memory available
 in the cluster for fast in-memory PDS index lookup. 
+Memory usage per machine is low because each machine only hosts $1/p$  of  index for PDS plus some buffer space. 
 %In the extreme case if we put all the fingerprint into PDS 
@@
 with a slight reduction in deduplication efficiency.
-
+Memory usage per machine in SRB includes the Bloom filter space to access the on-disk index
+and  cache for frequently or recently accessed chunk index.  
 % SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
@@
 is about 356GB per physical machine. 
-Column 1 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
-local similarity search.
+Column 4 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC which only uses
+the same offset in the parent segment to look for duplicates  but does not use 
+the fingerprint-guided similarity search. 
 %There is a big efficiency drop in this curve when the number of VMs is about 30.
@@
 
+The overall memory usage of VC for each physical machine is very small, which is not visible to other hosted cloud services.
+The 2.4GB memory usage of SRB is very visible to other services even each physical machine has 32GB memory.
+
 %Figure~\ref{fig:exbin-efficiency-graph2} also shows the benefits of our minhash
@@
 
-\subsection{Resource Usage and Processing Time}
+\subsection{More on Resource Usage and Processing Time}
 
+We show  more experimental results on resource usage and processing time with SRB.
 \comments{
@@
 under VC and Stateless Routing with Binning (SRB). 
-VC uses $\sigma=2\%$ and $4\%$.
+%VC uses $\sigma=2\%$ and $4\%$.
+VC uses $\sigma=2\%$. 
 The overall processing latency of SRB is about 23.9\% slower than VC.
@@
 
+\input{paper_eval_del}
 \comments{

### 2014-07-17 snapshot_system/paper_background.tex
ref

@@
 is still extensive for a shared cloud cluster.  
+For example, in the experiment discussed in Section~\ref{sect:dedup}, 
+cross-machine fingerprint comparison using Bloom filter and approximated routing~\cite{bottleneck08,Dong2011} 
+still needs several gigabytes of memory per machine, which impacts other cloud services sharing the same
+computing resource while our objective is to have an approximation scheme 
+which uses about 100 or few hundred megabytes of memory.
+
 \comments{

### 2014-07-17 snapshot_system/paper_background.tex
revi

--- 2014-07-17 snapshot_system/paper_background.tex
@@
 is still extensive for a shared cloud cluster.  
+For example, in the experiment discussed in Section~\ref{sect:evaldedup}, 
+cross-machine fingerprint comparison using Bloom filter and approximated routing~\cite{bottleneck08,Dong2011} 
+still needs several gigabytes of memory per machine, which impacts other cloud services sharing the same
+computing resource while our objective is to have an approximation scheme 
+which uses about 100 or few hundred megabytes of memory.
+
 \comments{

### 2014-07-18 snapshot_system/paper_intro.tex
full revision sweep

@@
 backups are in progress.
-However, sending out undeduplicated backup data wastes huge amount
+However, sending out undeduplicated backup data wastes a huge amount
 of network bandwidth that would otherwise be available to user VMs. 
@@
 This paper considers a backup service for converged cloud architectures
-that is co-located with user VMs, sharing the cloud computer, network, and
+that is co-located with user VMs, sharing the cloud compute, network, and
 storage resource with them.  We propose a VM-centric approach that
@@
 The key advantage of this approach  is that while maintaining  a competitive deduplication efficiency,
-the scheme uses a small resource usage without affecting other collocated cloud services.
+the scheme requires little resource usage to minimize the impact on other collocated cloud services.
 \comments{

### 2014-07-18 snapshot_system/paper.tex
revise for ACM cloud
change to acm format
remove all small tables
re

@@
-\documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix}
+\documentclass{acm_proc_article-sp}
 \usepackage{mathptmx}
@@
 %Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
+
+%with Fault Isolation 
 \title{
-VM-Centric  Snapshot Deduplication  with Fault Isolation 
-for Converged Cloud Architectures} 
+VM-Centric  Snapshot Deduplication  for Converged Cloud Architectures} 
 %VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
@@
 \input{paper_abs}
+
+\category{D.2.8}{Information Systems}{Information Storage Systems}
+%\terms{System}
+
+\keywords{Virtual machine images, snapshot backup and deletion, source-side deduplication, 
+cloud clusters and distributed architectures} % NOT required for Proceedings
+
 \input{paper_intro}
@@
 \input{paper_dedup}
-\input{paper_analysis}
 \input{paper_del}
@@
 \input{paper_conc}
+\appendix
+\input{paper_analysis}
 
-\begin{small}
 %\linespread{.97} % to squeeeze lines and put figures in same page
@@
 \bibliography{library,dedup1}
-\end{small}
 \end{document}

### 2014-07-18 snapshot_system/paper_abs.tex
re

@@
 Data deduplication has been widely used for cloud data backup
-because of excessive redundant content blocks. Common techniques 
+because of excessive redundant content. Common techniques 
 perform fingerprint comparison to remove duplicates
 across virtual machines.
-However, letting a duplicate data block be shared
-by many virtual machines represents a tradeoff between
-storage efficiency and data availability.
+However, fingerprint search for source-side duplicate detection is resource
+intensive when the backup service is co-located with  other cloud services.
+%letting a duplicate data block be shared
+%by many virtual machines represents a tradeoff between
+%storage efficiency and data availability.
 %by many virtual machines creates data dependence and is less fault-resilient. 
@@
 %%and fault isolation 
-This paper proposes a VM-centric backup service on a converged  cloud cluster architecture
-and  strikes a tradeoff for better fault isolation with competitive  deduplication efficiency.
-It localizes deduplication as much as possible within each 
+This paper proposes a VM-centric backup service 
+which  strikes a tradeoff for a competitive  deduplication efficiency while
+has  an advantage of   using less  computing resources, suitable for running
+on a converged cloud architecture that cohosts  many other services.
+This VM-centric scheme also leads to  better fault isolation and simplifies snapshot deletion.  
+The key techniques used are to
+localize deduplication as much as possible within each 
 virtual machine, guided by similarity
-search, and it restricts global deduplication under popular chunks with extra replication support.
-It associates  underlying file blocks with one VM for most cases
+search, and to restrict global deduplication under popular chunks with extra replication support.
+This scheme associates  underlying file blocks with one VM for most cases
 and proposes an approximate method for fast and simplified snapshot deletion.
-This VM-centric scheme also has  an advantage of   using less  computing resources, suitable for running
-the backup service on a converged cloud architecture that cohosts  many other services.
 This  paper  describes an evaluation of this scheme to assess  its deduplication 
-efficiency and fault resilience.
+efficiency, resource usage,  and fault resilience.
 

### 2014-07-18 snapshot_system/paper_background.tex
rev

--- 2014-07-17 snapshot_system/paper_background.tex
@@
 fingerprints
-so several techniques have been proposed to improve duplicate identification. 
+so a number of techniques have been proposed to improve duplicate identification. 
 For example, the data domain method ~\cite{bottleneck08} 
@@
 %VM dependence minimization during deduplication and file system block management.
+
 Even with these optimization and approximation techniques, resource usage such as memory  for deduplication
 is still extensive for a shared cloud cluster.  
+For example, in the experiment discussed in Section~\ref{sect:evaldedup}, 
+cross-machine fingerprint comparison using Bloom filter and approximated routing~\cite{bottleneck08,Dong2011} 
+still needs several gigabytes of memory per machine. This can impact other primary cloud services sharing the same
+computing resource while our objective is to have an approximation scheme 
+which uses no more than a few hundred megabytes of memory during normal operation.
+We have not adopted the index sampling in \cite{Guo2011} because its extension for
+for a distributed architecture is difficult.  To use a distributed memory version of the sampled index, every deduplication
+request may access a remote machine for index lookup and the overall overhead of access latency for all requests
+can be significant.
+
 \comments{

### 2014-07-18 snapshot_system/paper_conc.tex

--- 2014-01-31 snapshot_system/paper_conc.tex
@@
 a small amount of system resource.
-Evaluation using  this scheme strikes a tradeoff and restricted cross-VM duplicate detection
+Evaluation using  this scheme shows it strikes a tradeoff and restricted cross-VM duplicate detection
 can accomplish up to 96.58\% of what complete global
-deduplication can do, and the approximate snapshot deletion effectively manages deleted chunks with a 
-low-resource usage.  The availability of snapshots increases substantially when
+deduplication can do, and the simple and approximate snapshot deletion 
+effectively manages deleted chunks with
+much lower resource usage.  The availability of snapshots increases substantially when
 adding more replication for popular cross-VM chunks and packaging chunks from the same 
@@
 for the popular data set between 6 and 9 is good enough when the replication degree
-for other data blocks is 3.
+for other data blocks is 3, and adds only a small cost to storage.
 %Currently we are studying how the

### 2014-07-18 snapshot_system/paper_dedup.tex
rev

@@
 % Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
-Our key observation is for those chunks that appear in different VMs, top $k$ most popular items
+Our key observation is for those chunks that appear in different VMs, the top $k$ most popular items
 dominate the distribution.  This popular data set is called the \textbf{PDS}. 
@@
 %significantly reduces the total amount of  searchable fingerprints.
+
+\comments{
 We have not adopted the index sampling in \cite{Guo2011} because its extension for
@@
 can be significant.
-
+}
 \item 
@@
 We define a parent  segment is  potentially similar to the current segment if 1) the parent segment
-at the same offset as the current segment.
+is at the same offset as the current segment.
 2) the signature of these segments is the same.
@@
 By limiting at most 10 similar segments to search, the amount of memory for maintaining those 
-similar segment recipes is 190K, which is small.
+similar segment recipes is 190K, which is tiny compared to other memory requirements.
 
@@
 When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
-into a file system block.  A  backend file system block can contain a number of chunks,
-there are   two reasons. In addition to the reason that a file system block is often
-configured to be large, there is another reason that a number of chunks can be combined together
+into a file system block.  A  backend file system block can contain a large number of chunks.
+In addition to the fact that a distributed file system block is often
+configured to be large (e.g. 64MB), a number of chunks can be combined together
 and compressed further using a standard data compression method. 

### 2014-07-18 snapshot_system/paper_eval.tex
remove all small tables

@@
 \centering
-\begin{small}
     \begin{tabular}{|c|c|c|c|c|}
@@
     \end{tabular}
-\end{small}
     \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
@@
 \begin{table}
-\begin{small}
     \begin{tabular}{|c|c|c|c|c|c|}
@@
     \end{tabular}
-\end{small}
 \caption{Resource usage of concurrent backup tasks at each physical machine with $\sigma=2\%$ and I/O throttling.}
@@
 ``CPU'' column is the percentage of a single core used. 
-``Mem'' column includes 100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
+``Mem'' column includes $\sim$100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
 recipe metadata and cache. 
-The ``Read'' column is controlled to 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted too much.
+The ``Read'' column is controlled to 50MB/s bandwidth usage with I/O throttling so that other cloud services are not significantly impacted.
 The peak raw storage read performance is about 300MB/s and we only use 16.7\% with this collocation consideration.
@@
 
-It should be noted that global fingerprint  space requirement of VC is about 2\% of all unique fingerprints 
+It should be noted that global fingerprint  space requirement of VC is 2\% of all unique fingerprints 
 with $\sigma$=2\%. SRB uses an approximated method to look for a match within a bin and
@@
   \centering
-\begin{small}
     \begin{tabular}{|c|ccc|}
@@
     \end{tabular}
-\end{small}
 \caption{Throughput of software layers per machine under different concurrency and without I/O throttling.}
@@
 \centering
-\begin{small}
     \begin{tabular}{|c|c|c|c|c|c|}
@@
     \end{tabular}
-\end{small}
      \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}

### 2014-07-18 snapshot_system/paper_eval_del.tex
remove all small tables

@@
 \centering
-\begin{small}
 \begin{tabular}{|c|c|c|c|}
@@
     \end{tabular}
-\end{small}
     \caption{ Processing time and memory usage  for
@@
 
-For the mark-sweep approach on $p=100$, a physical machine is responsible of 
+For the mark-sweep approach on $p=100$, a physical machine is responsible for
 reading the metadata of non-deduplicated chunks used in the hosted 
@@
 in the usage table.
-This process is repeated 100 times for all physical machines.
+This process is repeated 100 times (once for for each physical machine).
 The memory allocated at each physical machine is for the 
 chunk usage table of 25 VMs. The average size is 1.2GB and the maximum is
-3GB. If we reduce the size of  the usage table at each machine, 
+3GB in our dataset. If we reduce the size of  the usage table at each machine, 
 then there are more iterations to mark all data and it 
-will take longer time.    
-For the grouped mark-sweep, about 50\% of snapshot meta reading can be 
+will take more time.    
+For the grouped mark-sweep, about 50\% of snapshot metadata reading can be 
 avoided in assessing the reference usage of non-duplicate chunks. 

### 2014-07-18 snapshot_system/paper.tex
re

@@
   Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
-  {\normalsize$^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\
+  $^\star$University of California at Santa Barbara \\
+  $^\dagger$Alibaba Inc. \\
 %  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
 }
+  %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\
 
@@
 \category{D.2.8}{Information Systems}{Information Storage Systems}
-%\terms{System}
+\terms{Design, Experimentation, Performance, Reliability}
 

### 2014-07-18 snapshot_system/paper_intro.tex
re

@@
 %as  instances of a guest operating system 
-and their virtual disks are stored as disk image files, typically
-using a local (possibly shared) file system.
-Frequent snapshot backup of virtual disk images can
+and their virtual disks are stored as disk image files.
+% typically using a local (possibly shared) file system.
+Frequent snapshot backup of virtual machine images can
 increase the service reliability by allowing VMs to restart from their latest
-snapshot in the event of a server failure.  However, because the disk
-blocks that make up the VMs are often the same from snapshot to snapshot
-and are shared among VMs,  
-deduplication of redundant content
-blocks~\cite{venti02,bottleneck08} is necessary to substantially reduce the
+snapshot in the event of a server failure. Snapshots contain highly redundant content chunks and 
+%  However, because the disk
+%blocks that make up the VMs are often the same from snapshot to snapshot
+%and are shared among VMs,  
+deduplication of redundant 
+content~\cite{venti02,bottleneck08} is necessary to substantially reduce the
 storage demand.
@@
 usage can impact other co-located cloud services. 
-But it is memory-intensive to compare a large number of fingerprints and identify
+It is memory-intensive to compare a large number of fingerprints and identify
 duplicates, even optimization or approximation techniques are developed~\cite{Guo2011,Dong2011,extreme_binning09}. 

### 2014-07-18 snapshot_system/paper_intro.tex
a

@@
 is that all infrastructure components are used to support paying customers --
-there are no resources specifically dedicated to cloud services.
+there are no resources specifically dedicated to cloud services~\cite{NutanixPaper}.
 %One of emerging architectures for building cloud services is a converged

### 2014-07-18 snapshot_system/paper_analysis.tex
revise for ACM cloud
remove mbox

@@
 
-\subsection{Fault Isolation}
+\section{Impact on Fault Isolation}
 
@@
 by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
-Table~\ref{tab:symbol},  we have
-$
-n *N_o   =  V_o *\mbox{ Number of file system blocks in VO.} 
-$
+Table~\ref{tab:symbol},  we have $n *N_o   =  V_o * $Number of file system blocks in VO.
 

### 2014-07-18 snapshot_system/paper_background.tex
rev

@@
 backup and deduplication are the same resources that must support cloud-hosted
-VMs.  Thus the backup service colocated with 
+VMs.  Thus the backup service collocated with 
 other cloud services has to minimize its resource impact.  
@@
 Additional inline deduplication and  approximation techniques
-are studied in ~\cite{extreme_binning09,Guo2011,sparseindex09,Guo2011,Srinivasan2012,WeiZhangIEEE}.  
+are studied in ~\cite{extreme_binning09,sparseindex09,Srinivasan2012,WeiZhangIEEE}.  
 %and a parallel batch solution for cluster-based deduplication is 
@@
 For example, in the experiment discussed in Section~\ref{sect:evaldedup}, 
+the raw snapshot data has a size of 1,000TB on 100 physical machines that host VMs,
 cross-machine fingerprint comparison using Bloom filter and approximated routing~\cite{bottleneck08,Dong2011} 
 still needs several gigabytes of memory per machine. This can impact other primary cloud services sharing the same
-computing resource while our objective is to have an approximation scheme 
+computing resource. Our objective is to have an approximation scheme 
 which uses no more than a few hundred megabytes of memory during normal operation.
-We have not adopted the index sampling in \cite{Guo2011} because its extension for
-for a distributed architecture is difficult.  To use a distributed memory version of the sampled index, every deduplication
-request may access a remote machine for index lookup and the overall overhead of access latency for all requests
-can be significant.
+The desired ratio of raw data to memory ratio is from 100K:1 to 30K:1 
+and this ratio remains to be a constant as the number of machines increases.
+Our proposed scheme achieves 86K:1.
+
+Index sampling with a prefetch cache  is proposed in
+in~\cite{Guo2011} for efficient single-machine deduplication. 
+This scheme uses 25GB memory per 500TB of raw data
+and thus the ratio is 20K:1. Our scheme proposed in this paper 
+uses 4 times less memory and we have not incorporated this index 
+sampling technique because its extension for
+for a distributed architecture is difficult.  To use a distributed memory version 
+of the sampled index, every deduplication
+request may access a remote machine for index lookup and the overall overhead 
+of access latency for all requests can be significant.
 
@@
 When the backup storage is implemented using a distributed file system such as Hadoop and Google file system~\cite{googlefs03},  
-the file system block  size is often chosen to be large. On the other hand, 
+the file system block  size is often chosen to be large (e.g. 64MB). On the other hand, 
 deduplication implementations~\cite{Guo2011,extreme_binning09,bottleneck08,Jin2009,Dong2011}
@@
 
-Cross-VM chunk sharing also complicates snapshot deletion which occurs frequently when snapshots expire regularly
+%Cross-VM chunk sharing also complicates 
+Snapshot deletion occurs frequently since  snapshots expire regularly
 and reference counting is required to identify chunks that are no longer used.
-The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
-deletion, but still carries a significant cost, especially in a distributed 
-setting.  
+The grouped mark-and-sweep approach~\cite{Guo2011}
+is effective for deletion, but still carries a significant cost, especially in a distributed 
+setting.   This is because any data chunk can be used by any snapshot
+of virtual machines in a large cloud cluster and there are multiple rounds of  extensive I/O involved
+to scan through the metadata of snapshots to determine if a chunk has been used or not.
+As the number of virtual  machines increases, the cost becomes even worse.
+%~\cite{Guo2011,Fabiano2013}  
 %to count if a data chunk is still shared by other snapshots.

### 2014-07-18 snapshot_system/paper_dedup.tex
re

@@
 in any VM requires a substantial resource for fingerprint comparison.
-To simplify cross-VM deduplication, we restrict the search scope of deduplication within the top $k$ most popular items.
+To simplify cross-VM deduplication, we restrict the search scope of deduplication within the top $k$ 
+most popular items. This popular data set is called the \textbf{PDS}. 
 %This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
@@
  \centering
-  \includegraphics[width=2.5in]{figures/zipf_count_rank.pdf}
+  \includegraphics[width=3.25in]{figures/zipf_count_rank.pdf}
  \caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
@@
 % Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
-Our key observation is for those chunks that appear in different VMs, the top $k$ most popular items
-dominate the distribution.  This popular data set is called the \textbf{PDS}. 
+The observation that motivates us to use the PDS
+is that for those chunks that appear in different VMs, the top $k$ most popular items
+dominate the distribution.  
 Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 
@@
 %analytic design guidance. 
-
 % Figure~\ref{fig:Datazipf} illustrates the distribution of chunk popularity based on a data trace from Alibaba with over 2500 VMs.
@@
 
-Compared to ~\cite{bottleneck08}, the fingerprint index  size is reduced by $1-\sigma$
+Compared to ~\cite{bottleneck08}, the fingerprint index  size is reduced by $100-\sigma$ percentage
+(e.g. 98\% with $\sigma=2\%$)
 and the searchable fingerprint space  becomes very small under the popularity constraint.  
@@
   \centering
-  \epsfig{file=images/mh_local_dedup.pdf, width=2.7in}
+  \epsfig{file=images/mh_local_dedup.pdf, width=3.25in}
   \caption{Similarity-guided local duplicate detection}
@@
 effectiveness~\cite{Guo2011,extreme_binning09,bottleneck08,Dong2011},
-we conduct additional local similarity guided deduplication on a snapshot by comparing
-chunk fingerprints of a dirty segment 
+we conduct additional local similarity guided deduplication 
+by comparing chunk fingerprints of a dirty segment on a snapshot 
 with those in  {\em potentially similar} segments from its parent snapshot. 
-We define a parent  segment is  potentially similar to the current segment if 1) the parent segment
+We consider a parent  segment is  potentially similar to the current dirty segment if 1) the parent segment
 is at the same offset as the current segment.
 2) the signature of these segments is the same.
-This segment content signature value is defined as the minimum value of all its chunk fingerprints 
+The signature of a segment is defined as the minimum value of all its chunk fingerprints 
 computed during backup and is recorded in the snapshot metadata (called recipe). 
 %Note that this definition of content similarity is an approximation~\cite{resemblance97}.  
+This signature definition is motivated by the previous work for similarity-based routing in parallel
+deduplication~\cite{extreme_binning09,Dong2011} and near duplicate detection~\cite{shingling97}.
+
 When processing a dirty segment,
@@
 When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
-into a file system block.  A  backend file system block can contain a large number of chunks.
+into a file system block.  
 In addition to the fact that a distributed file system block is often
-configured to be large (e.g. 64MB), a number of chunks can be combined together
-and compressed further using a standard data compression method. 
+configured to be much  larger than a chunk, a number of chunks can be combined together
+and compressed further using a standard compression method such as LZO. 
+Thus a  backend file system block contains a large number of compressed chunks.
 %We manage this accumulation process using a log-structured storage scheme built
@@
 %Non-PDS chunks from the same VM are stored in one append store. 
-We set two constraints in composing chunks for a file system block as follows:
-1) Each file system block is either dedicated to non-PDS chunks, or PDS-chunks.
+We set the following two constraints in composing chunks for a file system block as follows:
+1) Each file system block is either dedicated to non-PDS chunks, or to PDS-chunks.
 2) A non-PDS file system block is only associated with one VM.
 
-Restricting the association with one VM improves fault isolation when some file blocks are lost during failure. 
-In addition, storing PDS chunks separately allows special replication handling for those popular shared data. 
+Restricting the association with one VM improves fault isolation when some file blocks are lost during 
+storage failure. 
+In addition, storing PDS chunks separately from non-PDS chunks
+allows special replication handling for those popular shared data. 
 %%% talk something about snapshot store advantage here? %%%

### 2014-07-18 snapshot_system/paper_del.tex
revise for ACM cloud
re

@@
-\subsection{Snapshot Deletion with Leak Repair}
+\subsection{VM-Centric Snapshot Deletion with Periodic Leak Repair}
 \label{sect:delete}
@@
   \centering
-  \epsfig{file=images/deletion.pdf, width=2.7in}
+  \epsfig{file=images/deletion.pdf, width=3.25in}
   \caption{Fast approximate deletion}
@@
 %lower resource usage. 
-One of the key benefits of our VM-centric design is that it allows for faster and simpler deletion. First, since
+One of the key benefits of our VM-centric design is that it allows for faster and simpler deletion. 
+We propose the following strategies to speedup the deletion process and reduce its resource usage.
+\begin{itemize}
+\item First, since
 sharing in our approach is limited to only a small dataset, we can greatly simplify deletion by focusing
-on intra-VM sharing rather than inter-VM sharing. Our deletion can therefore be conducted independently per VM.
-Second, we propose an {\em approximate} deletion stragegy to trade deletion accuracy for speed and
-resource usage.
-
+on intra-VM sharing rather than inter-VM sharing. Then the snapshot
+ deletion can therefore be conducted independently among VMs.
+\item Second,  we propose an {\em approximate} deletion strategy to trade deletion accuracy for speed and
+resource usage. Since the VM size is highly skewed in practice,  a large VM may still require
+a substantial amount of memory  to facilitate the mark-sweep process of data chunks used within all snapshots
+of this VM. 
 Our approximate deletion method sacrifices a small percent of storage leakage
-to efficiently identify unused chunks using a per-snapshot bloomfilter.
-The algorithm contains three aspects.
+to efficiently identify unused chunks using a per-snapshot bloom-filter.
+\end{itemize}
+The simplified deletion algorithm contains three aspects.
 \begin{itemize}
@@
 the merged reference summary vectors of other live snapshots.
-The merging of live snapshot Bloom-filter vectors uses the bitwise OR operator 
+The merging of live snapshot Bloom-filter vectors uses the bit-wise OR operator 
 and the merged vector still takes $z$ bits.
@@
 usage immediately, while other offline methods (e.g. ~\cite{Guo2011,Fabiano2013})
-can't. That is important for storage accounting as users pay what are used and delayed deletion
+can't. That is important for storage accounting as users pay for used storage and delayed deletion
 affects the accounting.
@@
 the space cost is proportional to the number of chunks
-within each VM. For example, the space requirement is about 85MB for a VM of size 40GB in our tested dataset.
+within each VM. 
+%For example, the space requirement is about 85MB for a VM of size 40GB in our tested dataset.
  This is  much less expensive  than  the VM-oblivious mark-and-sweep
@@
 Thus the probability that a particular bit is 0  in all $h$ summary vectors is  
-$(1- \frac{1}{z}) ^{j U}$. 
+\[
+(1- \frac{1}{z}) ^{j U}.
+\] 
 Then the misjudgment rate of being in use  is: 
@@
 repairs. We estimate  the total leakage $L$ after $R$ runs as:
-$
+\[
 L = R \epsilon \Delta u.
-$
+\]
 

### 2014-07-18 snapshot_system/paper_background.tex
re

@@
     %\includegraphics[width=3in]{images/colocated-arch}
-    \includegraphics[width=3in]{images/converged_arch}
+    \includegraphics[width=3.25in]{images/converged_arch}
     \caption{VM snapshot backup running on a converged cloud cluster.}
@@
 This scheme uses 25GB memory per 500TB of raw data
-and thus the ratio is 20K:1. Our scheme proposed in this paper 
-uses 4 times less memory and we have not incorporated this index 
+and thus the raw data to memory ratio is 20K:1. Our scheme proposed in this paper 
+uses three times less memory and we have not incorporated this index 
 sampling technique because its extension for

### 2014-07-18 snapshot_system/paper_eval.tex
re

@@
 with about 2500 VMs, running on 100 physical machines. 
+Each machine in the production environment is more powerful than our evaluation cluster
+and has 16 cores with 48GB memory.
 Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
@@
 Each VM has about 40GB of storage  data  on average
-including OS and user data disk.
+including OS and user data disk while the size distribution is highly skewed and the maximum to
+the average ratio is close to 40.
 Each physical machine deals with about 10TB of snapshot data and each 1TB data represents one snapshot version
-of 25 VMs.  The VMs of the sampled data set use popular operating systems such as 
+of 25 VMs.  Thus the total amount of raw snapshot shot in 100 physical machines
+is about 1,000TB.
+The VMs of the sampled data set use popular operating systems such as 
 Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
@@
 Dedup &      93.02\%  & 96.01\% & 94.31\% & 97.86\% \\ 
-efficiency &          &       &           &      \\    \hline 
-Memory(MB) &      46 & 118  & 108 & 2400 \\ \hline
+Efficiency &          &       &           &      \\    \hline 
+Memory &      46MB & 118MB  & 108MB & 2.4GB \\ 
+per-machine &      &   &  &  \\ \hline
     \end{tabular}

### 2014-07-18 snapshot_system/paper_background.tex
re

@@
 which uses no more than a few hundred megabytes of memory during normal operation.
-The desired ratio of raw data to memory ratio is from 100K:1 to 30K:1 
-and this ratio remains to be a constant as the number of machines increases.
-Our proposed scheme achieves 86K:1.
+The desired ratio of raw data to memory ratio is from 100K:1 to 30K:1.
+Our proposed scheme achieves 86K:1
+and this ratio is about the same as the number of machines increases.
 

### 2014-07-18 snapshot_system/paper_eval.tex
re

@@
 
-{\bf Settings}.
+%{\bf Settings}.
 We have performed a trace-driven study based on a production dataset
@@
 in the cluster for fast in-memory PDS index lookup. 
-Memory usage per machine is low because each machine only hosts $1/p$  of  index for PDS plus some buffer space. 
+Memory usage per machine is low because each machine only hosts $1/p$  of  index for PDS 
+plus some buffer space where $p$ is the number of physical machines. 
 %In the extreme case if we put all the fingerprint into PDS 
@@
 Column 4 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC which only uses
-the same offset in the parent segment to look for duplicates  but does not use 
-the fingerprint-guided similarity search. 
+the same offset in the parent segment to look for duplicates  but does not look for other potentially
+similar segments. 
 %There is a big efficiency drop in this curve when the number of VMs is about 30.
-The reason similarity search provides such an improvement is that
+We explain why similarity-guided local search provides such an improvement as follows.
 %Without this (i.e. when we only 
-there are VMs in which
-data  segments are moved to another location on disk, for example when a file is rewritten
+There are VMs in which data  segments are moved to another location on disk, for example 
+when a file is rewritten
 rather than modified in place,  
@@
 
-The overall memory usage of VC for each physical machine is very small, which is not visible to other hosted cloud services.
-The 2.4GB memory usage of SRB is very visible to other services even each physical machine has 32GB memory.
+The overall memory usage of VC for each physical machine is very small, which is insignificant to other 
+hosted cloud services.  In comparison, the 2.4GB per-machine memory usage of SRB is very visible 
+to other services.
+% even each physical machine in the production environment has 48GB memory.
 
@@
 
-\subsection{More on Resource Usage and Processing Time}
+Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
+our scheme achives a 86K:1 ratio between raw snapshot data and memory usage 
+with 96\% deduplication efficiency
+while the sampled index method achives 20K:1 (10GB memory per 500TB raw data)
+with 97\% deduplication efficiency.
+Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
+If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
+memory usage per machine increses to about 220MB. 
+Notice that the sampled index method is designed for single-machine deduplication
+and it is not easy to extend to a distributed cluster architecture.
 
-We show  more experimental results on resource usage and processing time with SRB.
+\subsection{More on Resource Usage and Processing Speed}
+
+We show  additional experimental results on resource usage, processing time and throughput of VC.
 \comments{
@@
 running 1 or multiple  VM backup tasks at the same time on each physical machine. 
+Each task handles the backup of one VM snapshop including deduplication.
 ``CPU'' column is the percentage of a single core used. 
@@
 recipe metadata and cache. 
-The ``Read'' column is controlled to 50MB/s bandwidth usage with I/O throttling so that other cloud services are not significantly impacted.
+The ``Read'' column is controlled to 50MB/s local disk bandwidth usage with I/O throttling so that other 
+cloud services are not significantly impacted.
 The peak raw storage read performance is about 300MB/s and we only use 16.7\% with this collocation consideration.
@@
 VM cluster completes in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
-more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
+more tasks in parallel at each machine. But adding more backup concurrency does 
+not shorten the overall time
 significantly in this case because of the controlled  disk read bandwidth usage.
+When I/O throttling is not used, we will show later that processing multiple VMs concurrently 
+does improve the throughput of backup.
 %,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
@@
 
+\comments{
 It should be noted that global fingerprint  space requirement of VC is 2\% of all unique fingerprints 
@@
 Using a bloom filter with an index cache would require more memory space~\cite{Dong2011}.
+}
 
@@
 
-{\bf Processing Time breakdown without I/O throttling}.
+{\bf Processing time breakdown without I/O throttling}.
 Table~\ref{tab:vc_srb_combined} shows
@@
 throughput would be higher. 
+In comparison, the sampled index method in~\cite{Guo2011} achives about 5.5GB per second
+with 16 concurrent backup tasks and 6GB per second with
+more tasks.  The per-machine throughput of our scheme is reasonable.
 %With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

### 2014-07-18 snapshot_system/paper_eval_del.tex
re

--- 2014-07-17 snapshot_system/paper_eval_del.tex
@@
 \hline
+\hline
 VC Repair  &  0.7      & 0.82   & 0.05 -- 1.96 \\
@@
     \end{tabular}
-\end{small}
-    \caption{ Processing time and memory usage  for
+    \caption{ Processing time and per-machine memory usage  for
 deletion}  
@@
 Table~\ref{tab:deletion-cmp}   lists a comparison of processing time and memory usage
-using the four deletion approaches when $p=100$ and $p=50$. These four 
+using the four deletion methods when the number of physical machines
+$p=100$ and $p=50$. These four 
 methods are 1) the standard mark-sweep method. 2) Grouped mark-sweep~\cite{Guo2011}. 
-3)   VC summary vectors. 4) VC with summary vectors.
-The I/O speed for the backend distributed file system is about 50MB/second
-and the speed drops to about 25MB/second when
-when 100 machines read the backend file system concurrently due to the network
-contention. We explain the results for $p=100$ below and notice each physical machine hosts 25VMs on average. The explanation for $p=50$ is similar.
+3)   VC without using summary vectors (Row 4). 4) VC with summary vectors.
+Last row of Table~\ref{tab:deletion-cmp} 
+is the cost of the leakage  repair for VC with summary vectors.
+The mark-sweep process requires all machines read snapshot metadata for usage comparison.
+The I/O read speed for the backend distributed file system is about 50MB/second
+and there is some throughout contention when all machines read data simultaneously:
+the speed drops to about 30MB/second when $p=50$ and 25 with $p=100$.
+We explain the results for $p=100$ below and notice each physical machine hosts 25VMs on average. 
+The explanation for $p=50$ is similar and the result difference for $p=100$ and $p=50$ shows
+our deletion method scales well when the number of machines increases.
 
-For the mark-sweep approach on $p=100$, a physical machine is responsible of 
-reading the metadata of non-deduplicated chunks used in the hosted 
-virtual machines and keeping the usage index table in the memory.
+For the mark-sweep method (Row 2 of Table~\ref{tab:deletion-cmp}) 
+on $p=100$, we contact $p$ phases of the mark-sweep process.
+At each phase, a physical machine 
+reads $1/p$ of the non-deduplicated chunk metadata
+and keeps a reference table in the memory.
 Then all machines read the meta data 
-of snapshots in parallel and mark the usage of referenced chunks
-in the usage table.
-This process is repeated 100 times for all physical machines.
+of snapshots in parallel and mark the used chunks
+in the above reference table.
+The above phase is repeated 100 times (one for for each physical machine).
 The memory allocated at each physical machine is for the 
-chunk usage table of 25 VMs. The average size is 1.2GB and the maximum is
-3GB. If we reduce the size of  the usage table at each machine, 
-then there are more iterations to mark all data and it 
-will take longer time.    
-For the grouped mark-sweep, about 50\% of snapshot meta reading can be 
+chunk reference table at each phase. The average size is 1.2GB and the maximum is
+3GB due to data skewness.  
+There is a tradeoff between memory usage of a reference table in terms of the size
+and the total processing time. If we reduce the size of  the reference table at each phase, 
+then there are more phases to mark all data and the whole process  will take more time.
+For the grouped mark-sweep (Row 3), about 50\% of snapshot metadata reading can be 
 avoided in assessing the reference usage of non-duplicate chunks. 
@@
 
-For VC without summary vectors, all physical machines conduct the mark-sweep process in parallel, 
+For VC without summary vectors (Row 4 of Table~\ref{tab:deletion-cmp}), 
+all physical machines conduct the mark-sweep process in parallel, 
 but each machine only handles one VM at time and 
@@
 size is 1.96GB. 
-For VC with summary vectors, each physical machine loads
+For VC with summary vectors (Row 5), each physical machine loads
 the VM snapshots and only needs to compare with the summary vectors.

### 2014-07-18 snapshot_system/paper_background.tex
change data domain

--- 2014-07-18 snapshot_system/paper_background.tex
@@
 backup and deduplication are the same resources that must support cloud-hosted
-VMs.  Thus the backup service collocated with 
+VMs.  Thus the backup service colocated with 
 other cloud services has to minimize its resource impact.  
@@
 For example, the data domain method ~\cite{bottleneck08} 
-uses  an in-memory Bloom filter and a prefetching cache for data chunks 
-which may be accessed.  
+uses an in-memory Bloom filter to identify non-duplicates and a prefetching cache for potential
+duplicates that might hit in the future.
 %An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
@@
 Additional inline deduplication and  approximation techniques
-are studied in ~\cite{extreme_binning09,sparseindex09,Srinivasan2012,WeiZhangIEEE}.  
+are studied in ~\cite{extreme_binning09,Guo2011,sparseindex09,Guo2011,Srinivasan2012,WeiZhangIEEE}.  
 %and a parallel batch solution for cluster-based deduplication is 
@@
 For example, in the experiment discussed in Section~\ref{sect:evaldedup}, 
-the raw snapshot data has a size of 1,000TB on 100 physical machines that host VMs,
 cross-machine fingerprint comparison using Bloom filter and approximated routing~\cite{bottleneck08,Dong2011} 
 still needs several gigabytes of memory per machine. This can impact other primary cloud services sharing the same
-computing resource. Our objective is to have an approximation scheme 
+computing resource while our objective is to have an approximation scheme 
 which uses no more than a few hundred megabytes of memory during normal operation.
-The desired ratio of raw data to memory ratio is from 100K:1 to 30K:1 
-and this ratio remains to be a constant as the number of machines increases.
-Our proposed scheme achieves 86K:1.
-
-Index sampling with a prefetch cache  is proposed in
-in~\cite{Guo2011} for efficient single-machine deduplication. 
-This scheme uses 25GB memory per 500TB of raw data
-and thus the ratio is 20K:1. Our scheme proposed in this paper 
-uses 4 times less memory and we have not incorporated this index 
-sampling technique because its extension for
-for a distributed architecture is difficult.  To use a distributed memory version 
-of the sampled index, every deduplication
-request may access a remote machine for index lookup and the overall overhead 
-of access latency for all requests can be significant.
+We have not adopted the index sampling in \cite{Guo2011} because its extension for
+for a distributed architecture is difficult.  To use a distributed memory version of the sampled index, every deduplication
+request may access a remote machine for index lookup and the overall overhead of access latency for all requests
+can be significant.
 
@@
 When the backup storage is implemented using a distributed file system such as Hadoop and Google file system~\cite{googlefs03},  
-the file system block  size is often chosen to be large (e.g. 64MB). On the other hand, 
+the file system block  size is often chosen to be large. On the other hand, 
 deduplication implementations~\cite{Guo2011,extreme_binning09,bottleneck08,Jin2009,Dong2011}
@@
 
-%Cross-VM chunk sharing also complicates 
-Snapshot deletion occurs frequently since  snapshots expire regularly
+Cross-VM chunk sharing also complicates snapshot deletion which occurs frequently when snapshots expire regularly
 and reference counting is required to identify chunks that are no longer used. 
-The grouped mark-and-sweep approach~\cite{Guo2011}
-is effective for deletion, but still carries a significant cost, especially in a distributed 
-setting.   This is because any data chunk can be used by any snapshot
-of virtual machines in a large cloud cluster and there are multiple rounds of  extensive I/O involved
-to scan through the metadata of snapshots to determine if a chunk has been used or not.
-As the number of virtual  machines increases, the cost becomes even worse.
-%~\cite{Guo2011,Fabiano2013}  
+The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
+deletion, but still carries a significant cost, especially in a distributed 
+setting.  
 %to count if a data chunk is still shared by other snapshots.

### 2014-07-18 snapshot_system/paper_del.tex

@@
 \begin{figure}[htbp]
+\vspace{2em}
   \centering
-  \epsfig{file=images/deletion.pdf, width=3.25in}
+  \epsfig{file=images/deletion.pdf, width=3.35in}
   \caption{Fast approximate deletion}
@@
 chunks in a VM's snapshot store is about:
-$
+\[
 U = u + (h-1)\Delta u.
-$
+\]
 
@@
 \]
-
 When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we trigger a leak repair. Namely,

### 2014-07-18 snapshot_system/paper_eval.tex

@@
 Row 1 in  Table~\ref{tab:leakage} 
-is the deletion step. 3 means that version 3 is deleted. 
+is the deletion step. Entry value 3 in this row   means that Version 3 is deleted. 
 Row  2 is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
@@
 there is only 1.5MB space leaked for every 1GB of stored data.
-The actual leakage can reach  4.1\% after  245 deletions and such a repair is needed every 12 days
-to the  leakage under 5\%. 
+The actual leakage can reach  4.1\% after  245 deletions.
+% and such a repair is needed every 12 days to the  leakage under 5\%. 
 This experiment shows that the leakage of our approximate snapshot deletion is very small, 
@@
 
+\comments{
 The space cost for each snapshot deletion is insignificant.
@@
 This VM-specific leakage  repair takes  less than half an hour for each VM. 
+}
 %when disk bandwidth is controlled to 50MB/s. 

### 2014-07-18 snapshot_system/paper_analysis.tex
re

--- 2014-01-31 snapshot_system/paper_analysis.tex
@@
 
-\subsection{Fault Isolation}
+\section{Impact on Fault Isolation}
+\label{sect:fault}
 
@@
     {
-        \includegraphics[width=2.9in]{images/share_vc}
+        \includegraphics[width=3.25in]{images/share_vc}
         \label{fig:share_vc}
@@
     {
-        \includegraphics[width=2.9in]{images/share_vo}
+        \includegraphics[width=3.25in]{images/share_vo}
         \label{fig:share_vo}
@@
 
-Now we  analyze  the impact of losing $d$ physical machines 
+We  analyze  the impact of losing $d$ physical machines 
 to the VM centric and oblivious approaches.  
@@
 by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
-Table~\ref{tab:symbol}: 
+Table~\ref{tab:symbol},  we have 
 \[
-n *N_o   =  V_o *\mbox{ Number of file system blocks in VO.} 
+n *N_o   =  V_o * \mbox{Number of file system blocks in VO}.
 \]
@@
                 width=\linewidth,
-                height=0.6\linewidth,
+                %height=0.6\linewidth,
+                %width=0.7*\linewidth,
+                %height=0.6\linewidth,
 		xlabel={Number of VMs},
@@
 % $N_2$ for VC and $N_o$ for VO.
-Given $d$ failed physical machines and $r$ replicas for each file block,
+Given $d$ failed machines and $r$ replicas for each file block,
 %normal data replication degree $r$, PDS data replication degree $r_c$, 
 the availability of a file block is the probability that  
-all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
+all of its replicas do not appear in any group of $d$ failed machines among $p$ nodes~\cite{CoHadoop2011}. 
 Namely, 
@@
 \begin{figure}[htbp]
+\vspace{2em}
+
   \centering

### 2014-07-18 snapshot_system/paper_conc.tex
re

@@
 %the top of a cloud cluster to reduce network traffic and infrastructure requirements.
-The main contribution of this paper is a low-profile and VM-centric deduplication scheme to 
-maximize fault isolation while delivering competitive deduplication efficiency using
-a small amount of system resource.
-Evaluation using  this scheme shows it strikes a tradeoff and restricted cross-VM duplicate detection
-can accomplish up to 96.58\% of what complete global
-deduplication can do, and the simple and approximate snapshot deletion 
-effectively manages deleted chunks with
-much lower resource usage.  The availability of snapshots increases substantially when
+The main contribution of this paper is a low-profile and VM-centric deduplication scheme that
+uses  a small amount of system resource in both snapshot deduplication and deletion
+while delivering competitive deduplication efficiency.
+The VM-centric design also allows an optimization for  fast snapshot fault isolation.
+
+Our evaluation with an Alibaba dataset has the following results.
+\begin{itemize}
+\item {\em Competitive deduplication efficiency with a tradeoff}. 
+The proposed VC scheme 
+can accomplish over  96\% of what complete global
+deduplication can do. In comparison, the SRB and sampled index~\cite{Dong2011,extreme_binning09,Guo2011}
+can accomplish 97\% to 97.86\%.
+\item {\em Low resource usage in deduplication}. 
+The VC scheme achieves a 85K:1 ratio between raw snapshot data and memory usage
+and is much more memory-efficient than 
+SRB  with 4K:1 ratio and sampled index with 20K:1.
+Both VC and SRB are designed for a distributed cluster architecture while
+the sampled index method is for a single-machine architecture.
+\item {\em Low cost in snapshot deletion}. 
+\item {\em Higher availability}. 
+The availability of snapshots increases substantially when
 adding more replication for popular cross-VM chunks and packaging chunks from the same 
@@
 for other data blocks is 3, and adds only a small cost to storage.
+\end{itemize}
 %Currently we are studying how the

### 2014-07-18 snapshot_system/paper_background.tex
re
change bk

@@
 which occurs frequently when snapshots expire regularly. 
-The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
-deletion, but still carries a significant cost, especially in a distributed 
-setting.
+Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
+the dependencies from data containers to metadata groups, such that only a subset of
+metadata needs to be scanned in order to reclaim the garbage in a given data container.
+However, data in VM environment tend to be highly dedupable which means
+such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost.
+
+% especially in a distributed setting.
 %to count if a data chunk is still shared by other snapshots.

### 2014-07-18 snapshot_system/concl.tex

@@
 \label{sect:final}
-In this paper we propose a collocated backup service built on
-the top of a cloud cluster to reduce network traffic and infrastructure.
-The key contribution is a VM-centric deduplication scheme to 
-maximize fault isolation while delivering competitive deduplication efficiency.
-Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
-while cross-VM deduplication with a small common data set.
-VM-specific file block packing also reduces inter-VM dependence and enhances fault tolerance.
+In this paper we propose a collocated backup service with source-side deduplication built on
+the top of a cloud cluster to reduce network traffic and infrastructure cost.
 The design places a special consideration for low-resource usages as a collocated cloud service.
-Evaluation using  VM backup data shows that
-our solution can accomplish 92\% of what complete global
+The main contribution is a VM-centric deduplication scheme to play
+a tradeoff for low resurce usages and competitive deduplication efficiency. 
+%It also maximizes fault isolation by seperating popular and non-
+Inner-VM deduplication with similarity-guided local search
+maximizes the deduplication efficiency while
+localizing backup data dependency and exposing more parallelism during deduplication.  
+Cross-VM deduplication with a small popular data set leverages the zipf characteristics
+of popular items. 
+VM-specific file block packing reduces inter-VM dependence and enhances fault tolerance.
+
+The evaluation based on  an  Alibaba  production dataset 
+shows that our solution can accomplish 92\% of what complete global
 deduplication can do while the availability of snapshots increases substantially with this VM-centric
@@
 
+Comparing the experiment results of the sampled index method reported in~\cite{Guo2011},
+our scheme achives a 86K:1 ratio between raw snapshot data and memory usage
+with 96\% deduplication efficiency
+while the sampled index method achives 20K:1 (10GB memory per 500TB raw data)
+with 97\% deduplication efficiency.
+Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
+If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
+memory usage per machine increses to about 220MB.
+Notice that the sampled index method is designed for single-machine deduplication
+and it is not easy to extend to a distributed cluster architecture.
 % effectively  covers a large percent of duplicate data.

### 2014-07-18 snapshot_system/paper_eval.tex

@@
 Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
-our scheme achives a 86K:1 ratio between raw snapshot data and memory usage 
+our scheme achives a 85K:1 ratio between raw snapshot data and memory usage 
 with 96\% deduplication efficiency
@@
 
- Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
+We demonstrate  the impact of adding extra replication for PDS in VC
+and compare the snapshot availability of VC and VO. 
+Appendix~\ref{sect:fault} provides a detailed analysis of 
+snapshot availablility and the estimated result depends on how frequent a duplicate chunk
+is shared among snapshots of VMs.
+The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO 
+and VC approaches
+and then calculate the average availability of VM snapshots.
+
+Table~\ref{tab:vm-availability} shows the estimated availability of VM snapshots when 
 there are up to 20 machines failed in a cluster. 
-The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
-and then calculate the average availability of VM snapshots.
 The case for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain

### 2014-07-18 snapshot_system/paper_background.tex
add bg

--- 2014-07-18 snapshot_system/paper_background.tex
@@
 The desired ratio of raw data to memory ratio is from 100K:1 to 30K:1.
-Our proposed scheme achieves 86K:1
+Our proposed scheme achieves 85K:1
 and this ratio is about the same as the number of machines increases.
@@
 Another disadvantage of cross-VM sharing is that it complicates 
-snapshot deletion, 
-which occurs frequently when snapshots expire regularly. 
-The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
-deletion, but still carries a significant cost, especially in a distributed 
-setting.
+snapshot deletion, which occurs frequently because snapshots expire regularly.
+Several well developed garbage collection methods do not apply to the
+converged virtualized architecture due to various environment and resource limitations:
+Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
+the dependencies from data containers to metadata groups, such that only a subset of
+metadata needs to be scanned in order to reclaim the garbage in any given data container.
+However, data in VM environment tend to be highly dedupable which means
+such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
+ especially in a distributed setting.
+Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
+hashes in a compact form, however, it still requires the scan of all data hashes before any garbage could begin,
+which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
+to store the hashing result which couldn't be hold anywhere in our converged architecture.
 %to count if a data chunk is still shared by other snapshots.

### 2014-07-18 snapshot_system/paper_conc.tex
re

@@
 can accomplish over  96\% of what complete global
-deduplication can do. In comparison, the SRB and sampled index~\cite{Dong2011,extreme_binning09,Guo2011}
-can accomplish 97\% to 97.86\%.
+deduplication can do. In comparison, SRB~\cite{Dong2011,extreme_binning09}
+can accomplish 97.86 while 
+the sampled index~\cite{Guo2011} can deliver 97\% for a different test dataset. 
 \item {\em Low resource usage in deduplication}. 
@@
 \item {\em Low cost in snapshot deletion}. 
+The VC deletion takes less than a minute for snapshot deletion 
 \item {\em Higher availability}. 

### 2014-07-18 snapshot_system/paper_eval.tex
re

@@
 Efficiency &          &       &           &      \\    \hline 
-Memory &      46MB & 118MB  & 108MB & 2.4GB \\ 
+Memory &      10MB & 118MB  & 108MB & 2.4GB \\ 
 per-machine &      &   &  &  \\ \hline

### 2014-07-18 snapshot_system/paper_conc.tex
rev

@@
 while delivering competitive deduplication efficiency.
-The VM-centric design also allows an optimization for  fast snapshot fault isolation.
+The VM-centric design also allows an optimization for  better fault isolation and tolerance.
 
@@
 the sampled index~\cite{Guo2011} can deliver 97\% for a different test dataset. 
-\item {\em Low resource usage in deduplication}. 
+\item {\em Lower resource usage in deduplication}. 
 The VC scheme achieves a 85K:1 ratio between raw snapshot data and memory usage
@@
 SRB  with 4K:1 ratio and sampled index with 20K:1.
-Both VC and SRB are designed for a distributed cluster architecture while
+VC with 100 machines takes 1.31 hours to complete the backup of 2,500 VMs
+using 19\% of a single core and 16.7\% of IO bandwidth per machine. 
+Processing time of VC is 23.9\% faster  than SRB in our tested cases
+and the per-machine throughput of VC is reasonable based on the result 
+from~\cite{Guo2011}. 
+Noted that both VC and SRB are designed for a distributed cluster architecture while
 the sampled index method is for a single-machine architecture.
-\item {\em Low cost in snapshot deletion}. 
-The VC deletion takes less than a minute for snapshot deletion 
+\item {\em Lower cost in snapshot deletion}. 
+The deletion in VC with summary vectors
+takes less than a minute for snapshot deletion using 15MB memory per machine
+and all machines run this operation in parallel without data dependence. 
+The grouped mark-sweep method can take 43 hours using
+1.2 to 3GB memory per machine in our tested cases.
+The leak repair in VC takes 0.82 hours using 50MB on average while processing
+some VMs may use upto 1.96GB. Such a repair is conducted infrequently (e.g. every 19.6 days) 
 \item {\em Higher availability}. 
-The availability of snapshots increases substantially when
-adding more replication for popular cross-VM chunks and packaging chunks from the same 
-VM in one file system block. The analysis shows that the replication degree
+%The availability of snapshots increases substantially when
+%adding more replication for popular cross-VM file blocks and packaging chunks from the same 
+%VM in one file system block. 
+The snapshot availability of VC is 99.66\% with 3 failed machines in a 100-machine cluster
+while it is 69.54\% for  a VM oblivious approach.
+The analysis shows that the replication degree
 for the popular data set between 6 and 9 is good enough when the replication degree

### 2014-07-18 snapshot_system/paper.tex
re
add bg

@@
-\documentclass{acm_proc_article-sp}
+\documentclass[10pt,reprint]{socc14}
 \usepackage{mathptmx}
@@
 \begin{document}
-
+\special{papersize=8.5in,11in}
+\setlength{\pdfpageheight}{\paperheight}
+\setlength{\pdfpagewidth}{\paperwidth}
+\conferenceinfo{Submission to SoCC '14}{October, 2014, Seattle, WA, USA}
+\copyrightyear{2014}
+\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
+\doi{nnnnnnn.nnnnnnn}
 %\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
@@
 %VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
-\author{
+\authorinfo{
   Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
@@
 \category{D.2.8}{Information Systems}{Information Storage Systems}
-\terms{Design, Experimentation, Performance, Reliability}
+\terms
+Design, Experimentation, Performance, Analysis
 
-\keywords{Virtual machine images, snapshot backup and deletion, source-side deduplication, 
-cloud clusters and distributed architectures} % NOT required for Proceedings
+\keywords
+Virtual machine images, snapshot backup and deletion, source-side deduplication, cloud clusters and distributed architectures
 
@@
 \input{paper_conc}
+
+%\linespread{.97} % to squeeeze lines and put figures in same page
 \appendix
 \input{paper_analysis}
-
-%\linespread{.97} % to squeeeze lines and put figures in same page
-\bibliographystyle{abbrv}
+\bibliographystyle{abbrvnat}
 \bibliography{library,dedup1}

### 2014-07-18 snapshot_system/paper_background.tex
add bg
change bg

@@
 
+Another disadvantage of cross-VM sharing is that it complicates
+snapshot deletion, which is the garbage collection in VM environment
+that occurs frequently because snapshots expire regularly.
+Several well developed garbage collection methods do not apply to the
+converged virtualized architecture due to various environment and resource limitations:
+Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
+the dependencies from data containers to metadata groups, such that only a subset of
+metadata needs to be scanned in order to reclaim the garbage in any given data container.
+However, data in VM environment tend to be highly dedupable which means
+such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
+ especially in a distributed setting.
+Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
+hashes in a compact form, however, it still requires the scan of all data hashes before any garbage collection could begin,
+which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
+to store the hashing result which is still too big to be hold anywhere in a converged architecture.
+
 %Cross-VM chunk sharing also complicates 
-Snapshot deletion occurs frequently since  snapshots expire regularly
-and reference counting is required to identify chunks that are no longer used.
-The grouped mark-and-sweep approach~\cite{Guo2011}
-is effective for deletion, but still carries a significant cost, especially in a distributed 
-setting.   This is because any data chunk can be used by any snapshot
-of virtual machines in a large cloud cluster and there are multiple rounds of  extensive I/O involved
-to scan through the metadata of snapshots to determine if a chunk has been used or not.
-As the number of virtual  machines increases, the cost becomes even worse.
+% Snapshot deletion occurs frequently since  snapshots expire regularly
+% and reference counting is required to identify chunks that are no longer used.
+% The grouped mark-and-sweep approach~\cite{Guo2011}
+% is effective for deletion, but still carries a significant cost, especially in a distributed
+% setting.   This is because any data chunk can be used by any snapshot
+% of virtual machines in a large cloud cluster and there are multiple rounds of  extensive I/O involved
+% to scan through the metadata of snapshots to determine if a chunk has been used or not.
+% As the number of virtual  machines increases, the cost becomes even worse.
 %~\cite{Guo2011,Fabiano2013}  
@@
 which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
-to store the hashing result which couldn't be hold anywhere in our converged architecture.
+to store the hashing result which is still too big to be hold anywhere in a converged architecture.
+
 %to count if a data chunk is still shared by other snapshots.

### 2014-07-18 snapshot_system/template.tex

%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------

\documentclass[10pt,reprint]{socc14}

\usepackage{amsmath}
\usepackage{mathptmx}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\conferenceinfo{Submission to SoCC '14}{October, 2014, Seattle, WA, USA} 
\copyrightyear{2014} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\doi{nnnnnnn.nnnnnnn}

% Uncomment one of the following two, if you are not going for the 
% traditional copyright transfer agreement.

%\exclusivelicense                % ACM gets exclusive license to publish, 
                                  % you retain copyright

%\permissiontopublish             % ACM gets nonexclusive license to publish
                                  % (paid open-access papers, 
                                  % short abstracts)

%\titlebanner{banner above paper title}        % These are ignored unless
%\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Title Text}
\subtitle{Subtitle text, if any}

\authorinfo{Name1}
           {Affiliation1}
           {Email1}
\authorinfo{Name2\and Name3}
           {Affiliation2/3}
           {Email2/3}

\maketitle

\begin{abstract}
This is the text of the abstract.
\end{abstract}

\category{CR-number}{subcategory}{third-level}

% general terms are not compulsory anymore, 
% you may leave them out
\terms
term1, term2

\keywords
keyword1, keyword2

\section{Introduction}

A paragraph of text goes here.  Lots of text. More text.  Plenty of interesting
text.

\section{This section has subsections}

\subsection{New subsection}

Sometimes you want to really call attention to a piece of text.  You
can center it in the column like this:
\begin{center}
{\tt \_1008e614\_Vector\_p}
\end{center}
and people will really notice it.\\

\noindent
The noindent at the start of this paragraph makes it clear that it's
a continuation of the preceding text, not a new para in its own right.

Now this is an ingenious way to get a forced space.
{\tt Real~$*$} and {\tt double~$*$} are equivalent.

Now here is another way to call attention to a line of code, but instead
of centering it, we noindent and bold it.\\

\noindent
{\bf \tt size\_t : fread ptr size nobj stream } \\

And here we have made an indented para like a definition tag (dt)
in HTML.  You don't need a surrounding list macro pair.
\begin{itemize}
\item[]  {\tt fread} reads from {\tt stream} into the array {\tt ptr} at
most {\tt nobj} objects of size {\tt size}.   {\tt fread} returns
the number of objects read. 
\end{itemize}
This concludes the definitions tag.

\section{This is another section}

This is an example of unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
followed by another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}

Now we're going to cite somebody~\cite{smith02}.  Watch for the cite tag.  The tilde character (\~{}) in the source means a non-breaking space.  This way, your reference will always be attached to the word that preceded it, instead of going to the next line.

\section{Conclusions}

Well, it's getting boring isn't it.  This is the last section
where we wrap it up.

\appendix
\section{Appendix title}

This is the text of the appendix, if you need one.

\acks

Acknowledgments, if needed.

% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{}
\softraggedright

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
P. Q. Smith, and X. Y. Jones. ...reference text...

\end{thebibliography}

\end{document}

### 2014-07-18 snapshot_system/paper.tex
re
author

@@
 %with Fault Isolation 
-\title{
-VM-Centric  Snapshot Deduplication  for Converged Cloud Architectures} 
+\title{VM-Centric Snapshot Deduplication for Converged Cloud Architectures}
 %VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
-\authorinfo{
-  Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
-  $^\star$University of California at Santa Barbara \\
-  $^\dagger$Alibaba Inc. \\
-%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
-}
+\authorinfo{Wei Zhang\and Daniel Agun\and Tao Yang}
+           {UC Santa Barbara}
+           {\{wei,dagun,tyang\}@cs.ucsb.edu}
+\authorinfo{Hong Tang}
+           {Alibaba Inc.}
+           {hongtang@alibaba-inc.com}
+\authorinfo{Rich Wolski}
+           {UC Santa Barbara}
+           {rich@cs.ucsb.edu}
+
+% \authorinfo{
+%   Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
+%   $^\star$University of California at Santa Barbara \\
+%   $^\dagger$Alibaba Inc. \\
+% %  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
+% }
   %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\

### 2014-07-18 snapshot_system/paper.tex
re

@@
 %VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
+\comments{
 \authorinfo{Wei Zhang\and Daniel Agun\and Tao Yang}
@@
            {rich@cs.ucsb.edu}
+}
+ \authorinfo{
+   Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
+Hong Tang$^\dagger$}
+   {$^\star$University of California at Santa Barbara} 
+{$^\dagger$Alibaba Inc. }
+%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
 
-% \authorinfo{
-%   Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
-%   $^\star$University of California at Santa Barbara \\
-%   $^\dagger$Alibaba Inc. \\
-% %  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
-% }
   %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\
@@
 
-\category{D.2.8}{Information Systems}{Information Storage Systems}
-\terms
-Design, Experimentation, Performance, Analysis
+\category{}{Information Systems}{Information Storage Systems}
+\category{}{Distributed Architectures}{Cloud Computing}
+%\category{D.2.8}{Information Systems}{Information Storage Systems}
+\terms{Design, Experimentation, Performance}
 

### 2014-07-19 snapshot_system/paper_arch.tex
re

@@
 \begin{figure}[htbp]
+\vspace{1em}
     \centering
     %\includegraphics[width=2.75in]{images/socc_arch_cluster}
-    \includegraphics[width=2.2in]{images/socc_arch_cluster}
+    \includegraphics[width=3in]{images/socc_arch_cluster}
+%\vspace{1em}
     \caption{Data flow during snapshot backup}
@@
 \label{sect:store}
+
 %\begin{figure}[htbp]
 \begin{figure}[htbp]
+\vspace{1em}
   \centering
 %  \includegraphics[width=2.75in]{images/sstore_arch}
-  \includegraphics[width=2.2in]{images/sstore_arch}
+  \includegraphics[width=3in]{images/sstore_arch}
+%\vspace{1em}
+  \centering
   \caption{VM snapshot store data structures}
@@
 
-PDS data are re-calculated periodically, but 
+PDS data are re-calculated periodically in an offline manner, but 
 the total data size is small.  When
@@
 Three API calls are supported for data backup:
-%\begin{itemize}
+\begin{itemize}
 
-%\item
+\item
 \noindent\textbf{Append()}. 
@@
 
-%\item
+\item
 \noindent\textbf{Get()}.
@@
 
-%\item
+\item
 \noindent\textbf{Delete()}.
-Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user (the overall deletion strategy was discussed in detail in Section~\ref{sect:delete}).
+Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user. 
+%(the overall deletion strategy was discussed in detail in Section~\ref{sect:delete}).
 When deletion requests are issued for a specific container,
@@
 depend directly on physical storage locations, which simplifies data migration.
-%\end{itemize}
+\end{itemize}

### 2014-07-19 snapshot_system/paper_background.tex
re

@@
 is still extensive for a shared cloud cluster.  
-For example, in the experiment discussed in Section~\ref{sect:evaldedup}, 
+For example, in the experiments discussed in Section~\ref{sect:evaldedup}, 
 the raw snapshot data has a size of 1,000TB on 100 physical machines that host VMs,
@@
 which uses no more than a few hundred megabytes of memory during normal operation.
-The desired ratio of raw data to memory ratio is from 100K:1 to 30K:1.
+Thus the  desired ratio of raw data to memory ratio is from 100K:1 to 30K:1.
 Our proposed scheme achieves 85K:1
@@
 
-Index sampling with a prefetch cache  is proposed in
+Index sampling with a prefetch cache  is proposed 
 in~\cite{Guo2011} for efficient single-machine deduplication. 
 This scheme uses 25GB memory per 500TB of raw data
-and thus the raw data to memory ratio is 20K:1. Our scheme proposed in this paper 
-uses three times less memory and we have not incorporated this index 
-sampling technique because its extension for
-for a distributed architecture is difficult.  To use a distributed memory version 
+and thus the raw data to memory ratio is 20K:1. The scheme proposed in this paper 
+uses three times less memory. We have not incorporated this index 
+sampling technique because it is difficult to extend 
+for a distributed architecture.  To use a distributed memory version 
 of the sampled index, every deduplication
 request may access a remote machine for index lookup and the overall overhead 
-of access latency for all requests can be significant.
+of access latency for all requests is significant.
 
@@
 is lost in the storage, all VMs that refer such chunks after deduplication face a data loss.
-This issue is identified in ~\cite{Reliability06} which proposes to use more replication for data shared by more files,
+The work in ~\cite{Reliability06} identifies such an issue in file systems 
+and uses more replication for data shared by more files,
 and we will adopt this idea.
@@
  typically use smaller chunk sizes (e.g. 4K bytes).
-Thus we need to consider the size gap between file system blocks and chunks  in adding more replications for popular chunks.
+Thus we need to address  the size gap between file system blocks and chunks.  
+%in adding more replications for popular chunks.
 
-Another disadvantage of cross-VM sharing is that it complicates
-snapshot deletion, which is the garbage collection in VM environment
-that occurs frequently because snapshots expire regularly.
-Several well developed garbage collection methods do not apply to the
-converged virtualized architecture due to various environment and resource limitations:
-Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
-the dependencies from data containers to metadata groups, such that only a subset of
-metadata needs to be scanned in order to reclaim the garbage in any given data container.
-However, data in VM environment tend to be highly dedupable which means
-such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
- especially in a distributed setting.
-Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
-hashes in a compact form, however, it still requires the scan of all data hashes before any garbage collection could begin,
-which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
-to store the hashing result which is still too big to be hold anywhere in a converged architecture.
+%Another disadvantage of cross-VM sharing is that it complicates
+Snapshot deletion 
+%which is the garbage collection in VM environment
+occurs frequently because snapshots expire regularly
+and reference counting is required to identify chunks that are no loner used.
+%Several well developed garbage collection methods do not apply to the
+%converged virtualized architecture due to various environment and resource limitations:
+Grouped mark-and-sweep~\cite{Guo2011} is effective for deletion by tracking
+the dependencies from data containers to metadata groups, but still it carries
+a significant cost in a cloud cluster. This is because any data chunk can still be
+used by a large number of VMs, and there are multiple rounds of extensive I/O involved
+to scan through the meta data of snapshots to check if a chunk is referenced or not.
+As the number of machines increases, the I/O cost becomes more expensive.
+% and  we show  such that only a subset of
+%metadata needs to be scanned in order to reclaim the garbage in any given data container.
+%However, data in VM environment tend to be highly dedupable which means
+%such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
+% especially in a distributed setting.
+Perfect hashing~\cite{Fabiano2013} provides a memory efficient way to represent a large set of
+hashes in a compact form, however, it still requires the scanning of all data hashes before any 
+garbage collection could begin, which limits its application to an offline batch process. 
+In addition, it requires a centralized location
+to store the hashing result which is still too big to hold in a converged architecture.
 
@@
 metadata needs to be scanned in order to reclaim the garbage in any given data container.
-However, data in VM environment tend to be highly dedupable which means
+However, data in VM environment tend to be highly redundant which means
 such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,

### 2014-07-19 snapshot_system/paper_dedup.tex
re

@@
 is that for those chunks that appear in different VMs, the top $k$ most popular items
-dominate the distribution.  
+dominate the appearance distribution.  
 Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 
@@
 %most popular items. 
-PDS  can be computed periodically, e.g., on a monthly basis.
+PDS  can be computed in an offline manner periodically, e.g., on a monthly basis.
 %Once the popularity of all data chunks is collected, the system only maintains the top $k$
@@
 % $\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.
-
 Compared to ~\cite{bottleneck08}, the fingerprint index  size is reduced by $100-\sigma$ percentage
@@
 While cross-VM deduplication is simplified, we intend to optimize the VM-specific deduplication 
-as much as possible under a reasonable memory consumption
+under a reasonable memory consumption
  to make up the loss of deduplication opportunities due to the cross-VM popularity constraint.
-
 %Fingerprint lookup within a VM does not require a signficant  amount of memory resource.
-
 We start with the standard version-based detection~\cite{Clements2009,Vrable2009}
@@
 its  similar segments can be found easily from the
-parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
+parent snapshot metadata.  Then metadata of the similar segments is loaded to memory,
 which contain chunk fingerprints to be compared.
@@
 By limiting at most 10 similar segments to search, the amount of memory for maintaining those 
-similar segment recipes is 190K, which is tiny compared to other memory requirements.
+similar segment recipes is 190K, which is insignificant. 
+%compared to other memory requirements.
 
@@
 %Non-PDS chunks from the same VM are stored in one append store. 
-We set the following two constraints in composing chunks for a file system block as follows:
+We set the following two constraints in composing chunks for a file system block:
 1) Each file system block is either dedicated to non-PDS chunks, or to PDS-chunks.
@@
 Restricting the association with one VM improves fault isolation when some file blocks are lost during 
-storage failure. 
+storage failures. 
 In addition, storing PDS chunks separately from non-PDS chunks

### 2014-07-19 snapshot_system/paper_background.tex
change del

--- 2014-07-18 snapshot_system/paper_background.tex
@@
 %studied in ~\cite{WeiZhangIEEE}. 
-\comments{
-All of the above approaches have focused on optimization of deduplication
-efficiency or speed, and none of them have considered the impact
-of deduplication on fault resilience in a cloud environment.  To do so, we
-examine the following properties of VM snapshot deduplication for converged
-IaaS architectures.
-}
+% \comments{
+% All of the above approaches have focused on optimization of deduplication
+% efficiency or speed, and none of them have considered the impact
+% of deduplication on fault resilience in a cloud environment.  To do so, we
+% examine the following properties of VM snapshot deduplication for converged
+% IaaS architectures.
+% }
 %considered in this paper.
@@
 
-\comments{
-For example, the
-sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011},
-uses 5GB memory space for 100TB of raw data even the compressed data size
-is about 5TB. It is fairly typical for
-a physical machine with terabytes of disk storage and tens of gigabytes of memory
-to support  more than 20 VMs and 10 snapshots per VM and can require  over 100TB of raw space
-even the actual storage space need is about 5TB assuming 20:1 compression ratio with deduplication.
-It is not easy  to adopt the sampled index method  for a distributed architecture
-and every deduplication request may access a remote machine for index lookup and the overall overhead of access latency 
-for all requests can be significant. 
- In general
-with a cluster of machines in a cloud cluster, there will be more memory requirement per machine such as a 
-fingerprint cache, for cross-machine fingerprint comparison~\cite{bottleneck08,Dong2011} and a deduplication
-task often needs several gigabytpes of memory, which impacts other cloud services sharing the computing resource.
-}
+% \comments{
+% For example, the
+% sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011},
+% uses 5GB memory space for 100TB of raw data even the compressed data size
+% is about 5TB. It is fairly typical for
+% a physical machine with terabytes of disk storage and tens of gigabytes of memory
+% to support  more than 20 VMs and 10 snapshots per VM and can require  over 100TB of raw space
+% even the actual storage space need is about 5TB assuming 20:1 compression ratio with deduplication.
+% It is not easy  to adopt the sampled index method  for a distributed architecture
+% and every deduplication request may access a remote machine for index lookup and the overall overhead of access latency
+% for all requests can be significant.
+%  In general
+% with a cluster of machines in a cloud cluster, there will be more memory requirement per machine such as a
+% fingerprint cache, for cross-machine fingerprint comparison~\cite{bottleneck08,Dong2011} and a deduplication
+% task often needs several gigabytpes of memory, which impacts other cloud services sharing the computing resource.
+% }
 
@@
 
-\comments{
-\paragraph*{Local versus Global Deduplication} --
-If deduplication is implemented strictly in the storage system,
-a data chunk is compared with fingerprints collected from all VMs during
-the deduplication process, and only a small number of
-copies of duplicates are stored in the storage.  This sharing
-artificially creates hidden data dependencies among different VMs owned by
-different 
-who
-contract for isolation 
-by the IaaS cloud platform.  That is, the unit of failure visible to the cloud
-user is the VM, but the unit of sharing in a deduplicated data store is the
-data chunk.
+% \comments{
+% \paragraph*{Local versus Global Deduplication} --
+% If deduplication is implemented strictly in the storage system,
+% a data chunk is compared with fingerprints collected from all VMs during
+% the deduplication process, and only a small number of
+% copies of duplicates are stored in the storage.  This sharing
+% artificially creates hidden data dependencies among different VMs owned by
+% different
+% who
+% contract for isolation
+% by the IaaS cloud platform.  That is, the unit of failure visible to the cloud
+% user is the VM, but the unit of sharing in a deduplicated data store is the
+% data chunk.
 
-Indeed, the greater the deduplication efficiency, the less
-the data redundancy is maintained, and the greater the ``hidden'' data
-dependence between VMs that must be hosted as if they were physically isolated.
-Thus,
-restricting deduplication to be local to each VM (but across snapshots) 
-aligns the units of storage with the isolation properties guaranteed by the
-cloud at the possible expense of storage efficiency.
-%Localizing the impact of deduplication can increase fault isolation and resilience.
-%Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
-%discouraged.
+% Indeed, the greater the deduplication efficiency, the less
+% the data redundancy is maintained, and the greater the ``hidden'' data
+% dependence between VMs that must be hosted as if they were physically isolated.
+% Thus,
+% restricting deduplication to be local to each VM (but across snapshots)
+% aligns the units of storage with the isolation properties guaranteed by the
+% cloud at the possible expense of storage efficiency.
+% %Localizing the impact of deduplication can increase fault isolation and resilience.
+% %Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is
+% %discouraged.
 
-Additionally, storage efficient deduplication can be computationally expensive
-to implement in a distributed setting.  In particular, duplicate detection is
-logically a ``global'' operation over all data chunks
-under consideration.
-By localizing duplicate search, the computational requirements
-for deduplication can be reduced, because fewer chunks must be compared.
-Further, deduplication of VMs can easily be implemented in
-parallel.
+% Additionally, storage efficient deduplication can be computationally expensive
+% to implement in a distributed setting.  In particular, duplicate detection is
+% logically a ``global'' operation over all data chunks
+% under consideration.
+% By localizing duplicate search, the computational requirements
+% for deduplication can be reduced, because fewer chunks must be compared.
+% Further, deduplication of VMs can easily be implemented in
+% parallel.
 
-Another disadvantage of cross-VM sharing is that it complicates 
-snapshot deletion, which occurs frequently because snapshots expire regularly.
-Several well developed garbage collection methods do not apply to the
-converged virtualized architecture due to various environment and resource limitations:
-Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
-the dependencies from data containers to metadata groups, such that only a subset of
-metadata needs to be scanned in order to reclaim the garbage in any given data container.
-However, data in VM environment tend to be highly dedupable which means
-such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
- especially in a distributed setting.
-Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
-hashes in a compact form, however, it still requires the scan of all data hashes before any garbage could begin,
-which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
-to store the hashing result which is still too big to be hold anywhere in a converged architecture.
+% Another disadvantage of cross-VM sharing is that it complicates
+% snapshot deletion, which occurs frequently because snapshots expire regularly.
+% Several well developed garbage collection methods do not apply to the
+% converged virtualized architecture due to various environment and resource limitations:
+% Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
+% the dependencies from data containers to metadata groups, such that only a subset of
+% metadata needs to be scanned in order to reclaim the garbage in any given data container.
+% However, data in VM environment tend to be highly dedupable which means
+% such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
+%  especially in a distributed setting.
+% Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
+% hashes in a compact form, however, it still requires the scan of all data hashes before any garbage could begin,
+% which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
+% to store the hashing result which is still too big to be hold anywhere in a converged architecture.
 
-%to count if a data chunk is still shared by other snapshots.
+% %to count if a data chunk is still shared by other snapshots.
 
-Thus,
-localizing deduplication to the VM can align fault isolation properties and
-guarantees, improve the computational efficiency of snapshot maintenance, and
-simplify snapshot deletion over non-localized approaches at the possible
-expense of storage efficiency.
+% Thus,
+% localizing deduplication to the VM can align fault isolation properties and
+% guarantees, improve the computational efficiency of snapshot maintenance, and
+% simplify snapshot deletion over non-localized approaches at the possible
+% expense of storage efficiency.
 
-%minimize data sharing and simplify deletion while sacrificing 
-%deduplication efficiency, and  can facilitate parallel execution of snapshot operations.
-\paragraph*{Units of Storage versus Units of Sharing} --
-The file system block  size in a distributed file system such as  
-the Hadoop file system and the Google file system~\cite{googlefs03}
-is large (e.g.  64MB) so as to optimize file system performance
-for big data.
-Typically, deduplication implementations use smaller block sizes (4K bytes to
-8K bytes on average~\cite{Jin2009}).
-In addition to the failure correlation that cross-VM data deduplication can
-introduce, disk block sharing of data chunks is another potential source of
-hidden data dependence.
-Thus a VM-centric solution should consider how data chunks from VMs are
-distributed among large file system blocks when a large-scale distributed file
-system is used for snapshot storage.
+% %minimize data sharing and simplify deletion while sacrificing
+% %deduplication efficiency, and  can facilitate parallel execution of snapshot operations.
+% \paragraph*{Units of Storage versus Units of Sharing} --
+% The file system block  size in a distributed file system such as
+% the Hadoop file system and the Google file system~\cite{googlefs03}
+% is large (e.g.  64MB) so as to optimize file system performance
+% for big data.
+% Typically, deduplication implementations use smaller block sizes (4K bytes to
+% 8K bytes on average~\cite{Jin2009}).
+% In addition to the failure correlation that cross-VM data deduplication can
+% introduce, disk block sharing of data chunks is another potential source of
+% hidden data dependence.
+% Thus a VM-centric solution should consider how data chunks from VMs are
+% distributed among large file system blocks when a large-scale distributed file
+% system is used for snapshot storage.
 
-%a minimum association of FSBs to VMs in the packaging
-%process. By minimizing this association we can improve fault tolerance by
-%reducing the number of VMs affected when storage nodes are lost.
+% %a minimum association of FSBs to VMs in the packaging
+% %process. By minimizing this association we can improve fault tolerance by
+% %reducing the number of VMs affected when storage nodes are lost.
 
-\paragraph*{Moderating Resource Usage} --
-In a converged setting, the resources that are used to implement snapshot
-backup and deduplication are the same resources that must support cloud-hosted
-VMs.  Thus the backup service must share the resources available to
-other cloud services as illustrated in Figure~\ref{fig:collocated},
-and has to minimize its impact on user-deliverable performance.
-%The key resource for global comparison  is memory for storing the fingerprints.
-%During snapshot deletion, reference counting for all unique blocks used in all VMs requires a significant resource usage
-%too.  Thus we seek for the low-profile techniques with approximation and low resource consumption.
+% \paragraph*{Moderating Resource Usage} --
+% In a converged setting, the resources that are used to implement snapshot
+% backup and deduplication are the same resources that must support cloud-hosted
+% VMs.  Thus the backup service must share the resources available to
+% other cloud services as illustrated in Figure~\ref{fig:collocated},
+% and has to minimize its impact on user-deliverable performance.
+% %The key resource for global comparison  is memory for storing the fingerprints.
+% %During snapshot deletion, reference counting for all unique blocks used in all VMs requires a significant resource usage
+% %too.  Thus we seek for the low-profile techniques with approximation and low resource consumption.
 
-}
+% }
 
-\comments{
-With the above  considerations in mind, we propose a 
-VM-centric approach (called VC)
-for a co-located backup service that has a resource usage profile
-suitable for use with converged cloud architectures.  
-This compares the traditional deduplication approach {\em VM-oblivious} (VO)
-which manages duplicate data chunks without consideration of VMs.
-We discuss our key ideas and design in the next section.
-%Our key idea is to simplify deduplication management and 
-}
-\comments{
-In designing a VC deduplication solution, we have considered and adopted some of
-the following previously-developed techniques.
-1) {\em Changed Block Tracking}. 
-VM snapshots can be  backed up  incrementally by identifying data segments that have
-changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
-Such a scheme  is  VM-centric since deduplication is localized to the snapshot
-history for each VM.
-%We are seeking for a tradeoff since 
-%global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
-1) {\em Stateless  Data Routing}.
-One approach to scalable duplicate comparison is to use content-based hash
-partitioning called stateless data routing by Dong et al.~\cite{Dong2011}.
-Stateless data routing divides the deduplication work with a similarity approximation. This work 
-is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 
-each request is routed  to a machine which holds
-a Bloom filter  or can fetch on-disk index for additional comparison.
-While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
-VM-specific local search.
-3) {\em Sampled Index for Memory Parsimony}. 
-One effective approach that reduces memory usage is 
-to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
-The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
-To use a distributed memory version of the sampled index, every deduplication request
-may access a remote machine for index lookup and the overall overhead of access latency for all requests
-can be significant.
+% \comments{
+% With the above  considerations in mind, we propose a
+% VM-centric approach (called VC)
+% for a co-located backup service that has a resource usage profile
+% suitable for use with converged cloud architectures.
+% This compares the traditional deduplication approach {\em VM-oblivious} (VO)
+% which manages duplicate data chunks without consideration of VMs.
+% We discuss our key ideas and design in the next section.
+% %Our key idea is to simplify deduplication management and
+% }
+% \comments{
+% In designing a VC deduplication solution, we have considered and adopted some of
+% the following previously-developed techniques.
+% 1) {\em Changed Block Tracking}.
+% VM snapshots can be  backed up  incrementally by identifying data segments that have
+% changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
+% Such a scheme  is  VM-centric since deduplication is localized to the snapshot
+% history for each VM.
+% %We are seeking for a tradeoff since
+% %global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
+% 1) {\em Stateless  Data Routing}.
+% One approach to scalable duplicate comparison is to use content-based hash
+% partitioning called stateless data routing by Dong et al.~\cite{Dong2011}.
+% Stateless data routing divides the deduplication work with a similarity approximation. This work
+% is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and
+% each request is routed  to a machine which holds
+% a Bloom filter  or can fetch on-disk index for additional comparison.
+% While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
+% VM-specific local search.
+% 3) {\em Sampled Index for Memory Parsimony}.
+% One effective approach that reduces memory usage is
+% to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}.
+% The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture.
+% To use a distributed memory version of the sampled index, every deduplication request
+% may access a remote machine for index lookup and the overall overhead of access latency for all requests
+% can be significant.
 
-We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation 
-and discuss snapshot deletion support, then present an implementation design. 
-}
+% We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation
+% and discuss snapshot deletion support, then present an implementation design.
+% }

### 2014-07-19 snapshot_system/paper_del.tex
re
change del

@@
 Snapshot deletions can occur frequently since old snapshots become less useful.
-General deduplication complicates the deletion process because sharing of duplicates
-requires a global reference counting~\cite{Guo2011,Fabiano2013} 
- to identify if  a chunk can be  safely removed without any reference.
+Both space accounting and reclaimation are difficult because deduplication
+greatly complicates how we identify unused data when deletion occurs.
+To filter out un-referenced data from shared duplicates,
+it would require to either maintain expensive live schemas and operations
+such as global reference counting,
+or use some advanced mark-and-sweep methodologies~\cite{Guo2011,Fabiano2013},
+which are all unsuitable for converged architecture as discussed in section~\ref{sect:background}.
+% to identify if a chunk can be safely removed without any reference.
 %Since our VM-centric design restricts sharing of data chunks only to a small dataset,

### 2014-07-19 snapshot_system/paper.tex

@@
 Hong Tang$^\dagger$}
-   {$^\star$University of California at Santa Barbara} 
-{$^\dagger$Alibaba Inc. }
+   {$^\star$University of California at Santa Barbara \ \ \  
+   $^\dagger$Alibaba Inc. }
 %  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com

### 2014-07-19 snapshot_system/paper_abs.tex

@@
 However, fingerprint search for source-side duplicate detection is resource
-intensive when the backup service is co-located with  other cloud services.
+intensive when the backup service for virtual machines (VMs)  is co-located with  other cloud services.
 %letting a duplicate data block be shared
@@
 which  strikes a tradeoff for a competitive  deduplication efficiency while
-has  an advantage of   using less  computing resources, suitable for running
+using small  computing resources, suitable for running
 on a converged cloud architecture that cohosts  many other services.
-This VM-centric scheme also leads to  better fault isolation and simplifies snapshot deletion.  
-The key techniques used are to
+This VM-centric design also improves the snapshot availability  during machine failures  
+and simplifies snapshot deletion.  The key techniques used are to
 localize deduplication as much as possible within each 

### 2014-07-19 snapshot_system/paper_arch.tex
re

@@
 \begin{figure}[htbp]
-\vspace{1em}
+%\vspace{1em}
     \centering
@@
 \begin{figure}[htbp]
-\vspace{1em}
+%\vspace{1em}
   \centering
@@
 and decompressed. Given the high spatial locality and usefulness of prefetching  in 
-snapshot chunk accessing~\cite{Guo2011,foundation08},
+snapshot chunk accessing~\cite{Guo2011,Rhea2008},
 retrieval of  a data chunk  group naturally works well with prefetching. 

### 2014-07-19 snapshot_system/paper_background.tex

@@
 % parallel.
+
+% Another disadvantage of cross-VM sharing is that it complicates
+% snapshot deletion, which occurs frequently because snapshots expire regularly.
+% Several well developed garbage collection methods do not apply to the
+% converged virtualized architecture due to various environment and resource limitations:
+% Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
+% the dependencies from data containers to metadata groups, such that only a subset of
+% metadata needs to be scanned in order to reclaim the garbage in any given data container.
+% However, data in VM environment tend to be highly redundant which means
+% such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
+%  especially in a distributed setting.
+% Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
+% hashes in a compact form, however, it still requires the scan of all data hashes before any garbage could begin,
+% which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
+% to store the hashing result which is still too big to be hold anywhere in a converged architecture.
 

### 2014-07-19 snapshot_system/paper_eval.tex
re

@@
 Our evaluation objective is to
-study the benefit in fault tolerance and   deduplication efficiency of VC,  
-and assess its backup throughput and  resource usage.
-
+study deduplication efficiency and resource usage of VC,  
+and assess its processing time and backup throughput, and  
+the benefit in fault tolerance. 
 We will compare VC with a VO approach  using stateless routing with binning (SRB) 
@@
 SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
-Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
-with a slight reduction in deduplication efficiency.
+Thus this represents a tradeoff as VC uses much less resource  and faster deletion.
+%with a slight reduction in deduplication efficiency.
 Memory usage per machine in SRB includes the Bloom filter space to access the on-disk index
@@
 So it provides additional 28.63\% reduction. 
-
 The overall memory usage of VC for each physical machine is very small, which is insignificant to other 
@@
 memory usage per machine increses to about 220MB. 
-Notice that the sampled index method is designed for single-machine deduplication
-and it is not easy to extend to a distributed cluster architecture.
+Notice that the sampled index method is designed for single-machine deduplication.
+%and it is not easy to extend to a distributed cluster architecture.
 
@@
 significantly in this case because of the controlled  disk read bandwidth usage.
-When I/O throttling is not used, we will show later that processing multiple VMs concurrently 
+When I/O throttling is not used, we will show below that processing multiple VMs concurrently 
 does improve the throughput of backup.
@@
 with 16 concurrent backup tasks and 6GB per second with
-more tasks.  The per-machine throughput of our scheme is reasonable.
+more tasks.  Thus the per-machine throughput of our scheme is reasonable.
 %With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

### 2014-07-19 snapshot_system/paper_eval.tex
re

@@
 Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
-our scheme achives a 85K:1 ratio between raw snapshot data and memory usage 
+our scheme achieves a 85K:1 ratio between raw snapshot data and memory usage 
 with 96\% deduplication efficiency
-while the sampled index method achives 20K:1 (10GB memory per 500TB raw data)
+while the sampled index method achieves 20K:1 (10GB memory per 500TB raw data)
 with 97\% deduplication efficiency.
@@
 If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
-memory usage per machine increses to about 220MB. 
+memory usage per machine increases to about 220MB. 
 Notice that the sampled index method is designed for single-machine deduplication.
@@
 running 1 or multiple  VM backup tasks at the same time on each physical machine. 
-Each task handles the backup of one VM snapshop including deduplication.
+Each task handles the backup of one VM snapshot including deduplication.
 ``CPU'' column is the percentage of a single core used. 
@@
 throughput would be higher. 
-In comparison, the sampled index method in~\cite{Guo2011} achives about 5.5GB per second
+In comparison, the sampled index method in~\cite{Guo2011} achieves about 5.5GB per second
 with 16 concurrent backup tasks and 6GB per second with
@@
 
-We demonstrate  the impact of adding extra replication for PDS in VC
-and compare the snapshot availability of VC and VO. 
+We demonstrate  
+%the impact of adding extra replication for PDS in VC
+%and compare 
+the snapshot availability of VC and SRB-based VO  when there are failed machines. 
 Appendix~\ref{sect:fault} provides a detailed analysis of 
-snapshot availablility and the estimated result depends on how frequent a duplicate chunk
+snapshot availability and the estimated result depends on how frequent a duplicate chunk
 is shared among snapshots of VMs.

### 2014-07-19 snapshot_system/paper_analysis.tex
rev

@@
-%\begin{table}[htbp]
-\begin{table}[t]\small
+\section{Impact on Fault Isolation}
+\label{sect:fault}
+We  analyze  the impact of losing $d$ physical machines 
+to the VM centric and oblivious approaches.  
+There are two impacts to VC. 
+1) Some PDS fingerprint lookup services do not respond.  As  a result, some duplicates
+are not detected and deduplication efficiency suffers, but the overall systems can still
+function well and fault tolerance is not affected.  As discussed in Section ~\ref{sect:architecture}, 
+PDS index is distributed
+among all machines in our implementation and thus a percentage of failed nodes
+causes an increase in missed duplicates proportionally.
+2) Some storage nodes do not  respond and file blocks on those machines are lost. The availability of
+VM snapshots is affected and we analyze this impact as follows.
+
+%A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
+%We use an FSB rather than a deduplication
+%data chunk as our unit of failure because the DFS keeps
+%file system blocks as its base unit of storage.
+To compute the full availability of all snapshots of a VM, we estimate
+the number of file system blocks per VM and the probability of losing a snapshot file system 
+block of a VM in each approach as follows.
+Parameters used in our analysis below are defined in Table~\ref{tab:symbol}.
+
+\begin{table}[htbp]
+%\begin{table}[t]
+\small
 \centering
-\tabcolsep=0.11cm
+%\tabcolsep=0.11cm
 \begin{tabular}{|p{1.0cm}|p{5.75cm}|}
@@
 
-\section{Impact on Fault Isolation}
-\label{sect:fault}
-
 \begin{figure}[htb]
@@
     {
-        \includegraphics[width=3.25in]{images/share_vc}
+        \includegraphics[width=3in]{images/share_vc}
         \label{fig:share_vc}
@@
     {
-        \includegraphics[width=3.25in]{images/share_vo}
+        \includegraphics[width=3in]{images/share_vo}
         \label{fig:share_vo}
@@
 
-We  analyze  the impact of losing $d$ physical machines 
-to the VM centric and oblivious approaches.  
-There are two impacts to VC. 
-1) Some PDS fingerprint lookup services do not respond.  As  a result, some duplicates
-are not detected and deduplication efficiency suffers, but the overall systems can still
-function well and fault tolerance is not affected.  As discussed in Section ~\ref{sect:architecture}, 
-PDS index is distributed
-among all machines in our implementation and thus a percentage of failed nodes
-causes an increase in missed duplicates proportionally.
-2) Some storage nodes do not  respond and file blocks on those machines are lost. The availability of
-VM snapshots is affected and we analyze this impact as follows.
-
-%A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
-%We use an FSB rather than a deduplication
-%data chunk as our unit of failure because the DFS keeps
-%file system blocks as its base unit of storage.
-To compute the full availability of all snapshots of a VM, we estimate
-the number of file system blocks per VM and the probability of losing a snapshot file system 
-block of a VM in each approach as follows.
-Parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
 %As illustrated in Figure~\ref{fig:share},
@@
 % and  we denote that PDS blocks are shared by an average of $V_c$ VMs. 
-Then by counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
+By counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
 \[
@@
 		%title={VO VM links},
-                width=\linewidth,
-                %height=0.6\linewidth,
-                %width=0.7*\linewidth,
-                %height=0.6\linewidth,
+               % width=\linewidth,
+                width=0.7*\linewidth,
+                height=0.6\linewidth,
 		xlabel={Number of VMs},
@@
 Namely, 
-\[
+$
 A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
-\]
+$
 Then the availability of one VM's snapshot data under VO approach is the probability that

### 2014-07-19 snapshot_system/paper_conc.tex
re

@@
 The VM-centric design also allows an optimization for  better fault isolation and tolerance.
-
-Our evaluation with an Alibaba dataset has the following results.
+Our evaluation has the following results.
 \begin{itemize}
@@
 deduplication can do. In comparison, SRB~\cite{Dong2011,extreme_binning09}
-can accomplish 97.86 while 
+can accomplish 97.86\% while 
 the sampled index~\cite{Guo2011} can deliver 97\% for a different test dataset. 
@@
 VC with 100 machines takes 1.31 hours to complete the backup of 2,500 VMs
-using 19\% of a single core and 16.7\% of IO bandwidth per machine. 
+using 19\% of one core and 16.7\% of IO bandwidth per machine. 
 Processing time of VC is 23.9\% faster  than SRB in our tested cases
@@
 takes less than a minute for snapshot deletion using 15MB memory per machine
-and all machines run this operation in parallel without data dependence. 
+and all machines can run this operation in parallel without data dependence. 
 The grouped mark-sweep method can take 43 hours using
@@
 \end{itemize}
+The offline PDS recomputation does require some modest I/O and memory resource and 
+since the recomputing frequency is relatively low (e.g. on a monthly basis), we expect such resource
+consumption is acceptable in practice.
+
 %Currently we are studying how the

### 2014-07-19 snapshot_system/paper_eval_del.tex

@@
 \hline
-Mark-sweep  & 35.9  &  84.3  & 1.2--3 \\
+Mark\&sweep  & 35.9  &  84.3  & 1.2--3 \\
 \hline
 Grouped &     18.6    & 43.6   & 1.2--3 \\
-mark-sweep &        &    &  \\
+mark\&sweep &        &    &  \\
 \hline
@@
 $p=100$ and $p=50$. These four 
-methods are 1) the standard mark-sweep method. 2) Grouped mark-sweep~\cite{Guo2011}. 
+methods are 1) the standard mark-and-sweep method. 2) Grouped mark-and-sweep~\cite{Guo2011}. 
 3)   VC without using summary vectors (Row 4). 4) VC with summary vectors.
@@
 is the cost of the leakage  repair for VC with summary vectors.
-The mark-sweep process requires all machines read snapshot metadata for usage comparison.
+The mark-and-sweep process requires all machines read snapshot metadata for usage comparison.
 The I/O read speed for the backend distributed file system is about 50MB/second
 and there is some throughout contention when all machines read data simultaneously:
-the speed drops to about 30MB/second when $p=50$ and 25 with $p=100$.
-We explain the results for $p=100$ below and notice each physical machine hosts 25VMs on average. 
+the speed drops to about 30MB/second when $p=50$ and 25MB/s with $p=100$.
+We explain the results for $p=100$ below.
+% and notice each physical machine hosts 25VMs on average. 
 The explanation for $p=50$ is similar and the result difference for $p=100$ and $p=50$ shows
@@
 
-For the mark-sweep method (Row 2 of Table~\ref{tab:deletion-cmp}) 
-on $p=100$, we contact $p$ phases of the mark-sweep process.
+For the mark-and-sweep method (Row 2 of Table~\ref{tab:deletion-cmp}) 
+on $p=100$, we conduct $p$ phases of the mark-and-sweep process.
 At each phase, a physical machine 
@@
 then there are more phases to mark all data and the whole process  will take more time.
-For the grouped mark-sweep (Row 3), about 50\% of snapshot metadata reading can be 
-avoided in assessing the reference usage of non-duplicate chunks. 
+For the grouped mark-and-sweep (Row 3), about 50\% of snapshot metadata reading can be 
+avoided by actively tracking the reference usage of non-duplicate chunks. 
 Thus it takes 50\% less time, which is about 43 hours, but the 
@@
 For VC without summary vectors (Row 4 of Table~\ref{tab:deletion-cmp}), 
-all physical machines conduct the mark-sweep process in parallel, 
+all physical machines conduct the mark-and-sweep process in parallel, 
 but each machine only handles one VM at time and 
@@
 the VM snapshots and only needs to compare with the summary vectors.
-The memory usage is controlled within 15MB for hosting the summary vectors
+The memory usage is controlled around 15MB for hosting the summary vectors
 and small buffers. The deletion time is reduced to less than 1 minute.
-The periodic leakage repair still takes about 0.83 hours while using
-an average of 50MB memory. For  few big VMs in a skewed data distribution,
-the repair uses upto 1.9GB memory.
-Such a repair does not occur often (e.g. occurs every 19.6 days as discussed in Section~\ref{sect:delete}).
+The periodic leakage repair (Row 6) still takes about 0.83 hours while using
+an average of 50MB memory. For  few big VMs due to data skewness, the repair uses upto 1.9GB memory.
+Such a repair does not occur often (e.g. every 19.6 days as discussed in Section~\ref{sect:delete}).

### 2014-07-19 snapshot_system/paper_intro.tex
re

--- 2014-07-18 snapshot_system/paper_intro.tex
@@
 increase the service reliability by allowing VMs to restart from their latest
-snapshot in the event of a server failure. Snapshots contain highly redundant content chunks and 
+snapshot in the event of a server failure. Snapshots contain highly redundant 
+data chunks and 
 %  However, because the disk
@@
 duplicates, even optimization or approximation techniques are developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
-When deleting unused snapshots, a mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  
+When deleting unused snapshots, a grouped mark-and-sweep approach~\cite{Guo2011}  
 is effective while it still carries a significant cost, especially in a distributed
 setting.  Another side effect of deduplication is the possible loss of failure
-resilience~\cite{Reliability06}.  Separate files share the same physical copies of blocks that are
-logically duplicated among them.  If a shared block is lost, all files that
+resilience~\cite{Reliability06}.  
+%Separate files share the same physical copies of blocks that are
+%logically duplicated among them.  
+If a shared block is lost, all files that
 share that block are affected.  
@@
 with a VM-centric approach. 
-Section~\ref{sect:deduplication}  analyzes the tradeoff and benefits of the VM-centric approach. 
+%Section~\ref{sect:deduplication}  analyzes the tradeoff and benefits of the VM-centric approach. 
+Section~\ref{sect:deduplication}  presents our scheme for  snapshot deduplication and deletion.
 Section~\ref{sect:architecture}  describes a system implementation that evaluates the proposed techniques.
@@
 Section~\ref{sect:conclusion}  concludes this paper.
+The appendix describes an analysis on the snapshot availability of our scheme during storage failures.

### 2014-07-19 snapshot_system/paper_eval.tex
re

@@
     \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
-        Stateless Routing with Binning (SRB).}
+        SRB.}
     \label{tab:efficiency-comparison}
@@
 the  average  time breakdown for processing a dirty VM segment in milliseconds
-under VC and Stateless Routing with Binning (SRB). 
+under VC and SRB.
 %VC uses $\sigma=2\%$ and $4\%$.

### 2014-07-19 snapshot_system/paper_dedup.tex
re

@@
  \centering
-  \includegraphics[width=3.25in]{figures/zipf_count_rank.pdf}
+  \includegraphics[width=3in]{figures/zipf_count_rank.pdf}
  \caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
@@
 % Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
-The observation that motivates us to use the PDS
+What  motivates us to use PDS
 is that for those chunks that appear in different VMs, the top $k$ most popular items
@@
 we conduct additional local similarity guided deduplication 
-by comparing chunk fingerprints of a dirty segment on a snapshot 
+by comparing chunk fingerprints of a dirty segment in a snapshot 
 with those in  {\em potentially similar} segments from its parent snapshot. 
@@
 parent snapshot metadata.  Then metadata of the similar segments is loaded to memory,
-which contain chunk fingerprints to be compared.
+containing chunk fingerprints to be compared.
 To control the time cost of search, we set a limit on the number of  similar segment recipes to be fetched. 

### 2014-07-19 snapshot_system/paper_del.tex
re

--- 2014-07-18 snapshot_system/paper_del.tex
@@
 \begin{figure}[htbp]
-\vspace{2em}
+%\vspace{2em}
   \centering
@@
 Snapshot deletions can occur frequently since old snapshots become less useful.
-General deduplication complicates the deletion process because sharing of duplicates
-requires a global reference counting~\cite{Guo2011,Fabiano2013} 
- to identify if  a chunk can be  safely removed without any reference.
+Both space accounting and reclamation are difficult because deduplication
+greatly complicates how we identify unused data when deletion occurs.
+To filter out un-referenced data from shared duplicates,
+it would require to either maintain expensive live schemas or conduct
+global reference counting~\cite{Guo2011}.
+%or use some advanced mark-and-sweep methodologies
+%which are all unsuitable for converged architecture as discussed in section~\ref{sect:background}.
+% to identify if a chunk can be safely removed without any reference.
 %Since our VM-centric design restricts sharing of data chunks only to a small dataset,
@@
 chunks in a VM's snapshot store is about:
-\[
+$
 U = u + (h-1)\Delta u.
-\]
+$
 

### 2014-07-19 snapshot_system/paper_eval.tex
revise

@@
 with 96\% deduplication efficiency
-while the sampled index method achieves 20K:1 (10GB memory per 500TB raw data)
+while the sampled index method achieves 20K:1 (25GB memory per 500TB raw data)
 with 97\% deduplication efficiency.

### 2014-07-19 snapshot_system/paper_eval.tex
revise
wording

@@
 memory usage per machine increases to about 220MB. 
-Notice that the sampled index method is designed for single-machine deduplication.
+Notice also that the sampled index method is designed for single-machine deduplication.
 %and it is not easy to extend to a distributed cluster architecture.
@@
 When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
-and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
-loses most of non-PDS blocks given the replication degree for non PDS is 3.
+and VC also drops to 1.13\%. This is because even though availability for PDS data remains good, VC still
+loses many of the non-PDS blocks given the replication degree for non-PDS is 3.
 When $p=1000$, the percentage of failures is then 2\% and VC delivers a meaningful availability 

### 2014-07-19 snapshot_system/paper_del.tex
re

@@
 Both space accounting and reclamation are difficult because deduplication
-greatly complicates how we identify unused data when deletion occurs.
+greatly complicates the  identification of unused data when deletion occurs.
 To filter out un-referenced data from shared duplicates,
@@
 %lower resource usage. 
+For example, the experiment in Section~\ref{sect:evaldel} shows that
+ the grouped mark-and-sweep process takes 43 hours for a 2500 VM cluster using upto 3GB memory per machine.
+
 One of the key benefits of our VM-centric design is that it allows for faster and simpler deletion. 
@@
 \begin{itemize}
-\item First, since
-sharing in our approach is limited to only a small dataset, we can greatly simplify deletion by focusing
-on intra-VM sharing rather than inter-VM sharing. Then the snapshot
- deletion can therefore be conducted independently among VMs.
+\item First, reference counting is focused on non-PDS chunks which are not shared among VMs,
+and the mark-and-sweep process is applied within each VM. 
+Therefore,  the snapshot deletion can be conducted independently among VMs.
+%sharing in our approach is limited to only a small dataset, we can greatly 
+%on intra-VM sharing rather than inter-VM sharing. Then
+
 \item Second,  we propose an {\em approximate} deletion strategy to trade deletion accuracy for speed and
 resource usage. Since the VM size is highly skewed in practice,  a large VM may still require
-a substantial amount of memory  to facilitate the mark-sweep process of data chunks used within all snapshots
+a substantial amount of memory  to facilitate the mark-and-sweep process of data chunks used within all snapshots
 of this VM. 

### 2014-07-19 snapshot_system/paper_eval.tex
revised replication degree wording
re

@@
 backup one VM at a time, the backup of the entire
-VM cluster completes in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
+VM cluster completes in about 1.31 hours. Since there are about 25 VMs per physical machine, we could execute
 more tasks in parallel at each machine. But adding more backup concurrency does 
@@
  \subsection{Effectiveness of Approximate Deletion}
-
+\label{sect:evaldel}
 \input{paper_eval_del}
@@
 availability does not increase much  when increasing
-$r_c$ from 6 to 9 and the benefit is not so visible after $r_c>9$. 
+$r_c$ from 6 to 9 and the benefit is minimal after $r_c>9$. 
 That is because when the number of failed machines increases beyond 6, 

### 2014-07-19 snapshot_system/paper_abs.tex
re

--- 2014-06-27 snapshot_system/paper_abs.tex
@@
 \begin{abstract}
-Data deduplication has been widely used for cloud data backup
-because of excessive redundant content blocks. Common techniques 
-perform fingerprint comparison to remove duplicates
-across virtual machines.
-However, letting a duplicate data block be shared
-by many virtual machines represents a tradeoff between
-storage efficiency and data availability.
-%by many virtual machines creates data dependence and is less fault-resilient. 
-%%This paper studies the impact of deduplication on 
-%%fault resilidence  of virtual machine snapshots, created by data dependence  among duplicates
-%%and proposes a VM-centric approach that strikes a balance between deduplication efficiency
-%%and fault isolation 
-This paper proposes a VM-centric backup service on a converged  cloud cluster architecture
-and  strikes a tradeoff for better fault isolation with competitive  deduplication efficiency.
-It localizes deduplication as much as possible within each 
-virtual machine, guided by similarity
-search, and it restricts global deduplication under popular chunks with extra replication support.
-It associates  underlying file blocks with one VM for most cases
-and proposes an approximate method for fast and simplified snapshot deletion.
-This VM-centric scheme also has  an advantage of   using less  computing resources, suitable for running
-the backup service on a converged cloud architecture that cohosts  many other services.
-This  paper  describes an evaluation of this scheme to assess  its deduplication 
-efficiency and fault resilience.
+Data deduplication is important  for snapshot backup of virtual machines (VMs)
+because of excessive redundant content.  Fingerprint search for source-side duplicate 
+detection is resource intensive when the backup service for VMs  is co-located with  other 
+cloud services.  This paper proposes a VM-centric backup service with  a tradeoff 
+for a competitive  deduplication efficiency while using small computing resources, 
+suitable for running on a converged cloud architecture that cohosts  many other services.
+The key techniques in the proposed scheme are to localize deduplication as much as 
+possible within each VM guided by similarity search, restrict global 
+deduplication under popular chunks with extra replication support,
+and use an approximate method for fast and simplified snapshot deletion.
+This VM-centric design also improves the snapshot availability  during machine failures  
+by separating popular chunks and associating  file system blocks with one VM for non-popular chunks.
+This  paper  describes an evaluation of this VM-centric scheme to assess  its deduplication 
+efficiency, resource usage,  and fault tolerance.
 

### 2014-07-19 snapshot_system/paper_abs.tex
re

@@
 detection is resource intensive when the backup service for VMs  is co-located with  other 
-cloud services.  This paper proposes a VM-centric backup service with  a tradeoff 
+cloud services.  This paper proposes a low-profile VM-centric backup service with  a tradeoff 
 for a competitive  deduplication efficiency while using small computing resources, 

### 2014-07-19 snapshot_system/paper_dedup.tex
re

@@
 into a file system block.  
-In addition to the fact that a distributed file system block is often
+In addition to the fact that a distributed file system block~\cite{googlefs03,hdfs10} is often
 configured to be much  larger than a chunk, a number of chunks can be combined together
@@
 from ~\cite{Reliability06}. That reduces the storage efficiency.
+
+%and compare
+
 %Then we cannot leverage the file system features to 
@@
 \end{itemize}
+The underlying distributed  file system has  a fixed replication degree for 
+all file system blocks~\cite{googlefs03,hdfs10}.
+We add extra replicas for file blocks containing PDS chunks  
+and this brings additional  failure protection for these chunks shared by many VMs.
+Appendix~\ref{sect:fault} provides a detailed analysis of snapshot availability
+under this VC scheme and compares it with VO.

### 2014-07-19 snapshot_system/paper_arch.tex
re

@@
     %\includegraphics[width=2.75in]{images/socc_arch_cluster}
-    \includegraphics[width=3in]{images/socc_arch_cluster}
+    \includegraphics[width=2.8in]{images/socc_arch_cluster}
 %\vspace{1em}
@@
 %  \includegraphics[width=2.75in]{images/sstore_arch}
-  \includegraphics[width=3in]{images/sstore_arch}
+  \includegraphics[width=2.8in]{images/sstore_arch}
 %\vspace{1em}
@@
 For non PDS data, the snapshot store of a VM is  divided into a set of containers and 
-each container is approximately 1GB.  The reason for this  divison is to simplify the compaction process
+each container is approximately 1GB.  The reason for this  division is to simplify the compaction process
 conducted periodically. When  chunks are deleted from old snapshots,
@@
 
-Each non-PDS data container is further divided into a set of chunk data groups. Each chunk group is composed of
+Each non-PDS container is further divided into a set of chunk data groups. Each chunk group is composed of
 a set of data chunks and is the basic unit in data access and retrieval. 
@@
 %\item
-Each non-PDS data container is represented by three files in the DFS:
+Each non-PDS data container is represented by three files:
+%in the DFS
 1) the container data file holds the actual content, 

### 2014-07-19 snapshot_system/paper_background.tex
re
figure update

@@
 physical host. 
+%The secondary storage can be cluster-based and implemented with a distributed file system~\cite{googlefs03}.   
 For VM snapshot backup, file-level semantics are normally not provided.
@@
     %\includegraphics[width=3in]{images/colocated-arch}
-    \includegraphics[width=3.25in]{images/converged_arch}
+    %\includegraphics[width=3in]{images/converged_arch}
+    \resizebox{0.85\linewidth}{!}{
+        \input{images/converged_arch}
+        %\includegraphics{figures/converged_arch}
+    }
     \caption{VM snapshot backup running on a converged cloud cluster.}
@@
 and we will adopt this idea.
-When the backup storage is implemented using a distributed file system such as Hadoop and Google file system~\cite{googlefs03},  
+When the backup storage is implemented using a distributed file system such as Hadoop and 
+Google file system~\cite{googlefs03},  
 the file system block  size is often chosen to be large (e.g. 64MB). On the other hand, 
@@
 In addition, it requires a centralized location
-to store the hashing result which is still too big to hold in a converged architecture.
+to store the hashing result which is still too big to be held in a converged architecture.
+
+Our previous work on parallel deduplication~\cite{zhangusenix13} is a low-cost
+solution, but it is not an inline solution and th backup for all VMs needs to be conducted
+around the same time. It does not address  snapshot deletion and file system block 
+packaging for fault tolerance.
 

### 2014-07-19 snapshot_system/paper_eval.tex
re

@@
 In summary, our experiments show that
-version detection at the segment level can reduce the data size to about 24.14\% of original data, 
-which leads to about a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
+segment-level version detection 
+reduces the data size to about 24.14\% of original data, 
+which is a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
 Similarity-guided local search can further reduce the data size

### 2014-07-19 snapshot_system/paper_background.tex
re

@@
 
+\comments{
 Our previous work on parallel deduplication~\cite{zhangusenix13} is a low-cost
 solution, but it is not an inline solution and th backup for all VMs needs to be conducted
-around the same time. It does not address  snapshot deletion and file system block 
-packaging for fault tolerance.
+around the same time. 
+It does not address  snapshot deletion and file system block packaging for fault tolerance. 
+}
+
+Our previous work on parallel deduplication~\cite{zhangusenix13,WeiZhangIEEE} 
+is not a comprehensive VM-centric solution and does not address  snapshot deletion and file system block 
+packaging for fault tolerance.  The work in ~\cite{zhangusenix13} a low-cost
+solution, but requires all backups for each day to occur at the same time and is less flexible than the approach presented here.
+
+% a low cost solution, but it not an inline solution and 
+%the backup for all VMs needs to be conducted
+%around the same time.
 

### 2014-07-19 snapshot_system/paper_conc.tex
re

@@
-\section{Conclusion}
+\section{Conclusions}
 \label{sect:conclusion}
@@
 %the top of a cloud cluster to reduce network traffic and infrastructure requirements.
-The main contribution of this paper is a low-profile and VM-centric deduplication scheme that
+The main contribution of this paper is the development and comparative study of a low-profile and VM-centric deduplication scheme that
 uses  a small amount of system resource in both snapshot deduplication and deletion
@@
 The snapshot availability of VC is 99.66\% with 3 failed machines in a 100-machine cluster
-while it is 69.54\% for  a VM oblivious approach.
+while it is 69.54\% for  SRB or a VM-oblivious approach.
 The analysis shows that the replication degree

### 2014-07-19 snapshot_system/paper_dedup.tex
re

@@
 is that for those chunks that appear in different VMs, the top $k$ most popular items
-dominate the appearance distribution.  
+dominate the appearance distribution~\cite{WeiZhangIEEE}.  
 Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 

### 2014-07-19 snapshot_system/paper_intro.tex
re

@@
 backups are in progress.
-However, sending out undeduplicated backup data wastes a huge amount
+However, sending out raw and undeduplicated backup data wastes a huge amount
 of network bandwidth that would otherwise be available to user VMs. 
@@
 that is co-located with user VMs, sharing the cloud compute, network, and
-storage resource with them.  We propose a VM-centric approach that
-simplifies deduplication and snapshot deletion.
+storage resource with them.  The main contribution of this paper is
+the development and comparative study of  a VM-centric approach that
+simplifies deduplication and snapshot deletion and improves snapshot availability.
 The key advantage of this approach  is that while maintaining  a competitive deduplication efficiency,

### 2014-07-19 snapshot_system/paper_analysis.tex
re

@@
-\section{Impact on Fault Isolation}
+\section{Fault Tolerance and Snapshot Availability}
 \label{sect:fault}
@@
 By counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
-\[
+$
 n* N_1   = \mbox{ Number of non-PDS file system blocks in VC.} 
-\]
+$
 
@@
 Table~\ref{tab:symbol},  we have 
-\[
+$
 n *N_o   =  V_o * \mbox{Number of file system blocks in VO}.
-\]
+$
 

### 2014-07-19 snapshot_system/paper_eval.tex
re

@@
 % =======
-Deduplication efficiency is defined as the percent of duplicate chunks which are removed
-compared to a perfect scheme which detects and removes  all duplicates. 
+Deduplication efficiency is defined as the percent of duplicate 
+chunks removed, comparing to a perfect scheme which detects and removes  all duplicates. 
 % so only global perfect deduplication can have 100\% efficiency.
@@
 Table ~\ref{tab:resource_usage} shows that when  each machine conducts
-backup one VM at a time, the backup of the entire
-VM cluster completes in about 1.31 hours. Since there are about 25 VMs per physical machine, we could execute
+backup one VM at a time, the entire cluster backup 
+completes in 1.31 hours. Since there are about 25 VMs per physical machine, we could execute
 more tasks in parallel at each machine. But adding more backup concurrency does 

### 2014-07-19 snapshot_system/paper_background.tex
re

@@
 is not a comprehensive VM-centric solution and does not address  snapshot deletion and file system block 
-packaging for fault tolerance.  The work in ~\cite{zhangusenix13} a low-cost
+packaging for fault tolerance.  The work in ~\cite{zhangusenix13} is a low-cost
 solution, but requires all backups for each day to occur at the same time and is less flexible than the approach presented here.

### 2014-08-25 thesis/Overview.tex
update to thesis

@@
 raw data for backup. 
-Figure~\ref{fig:collocated} illustrates the cluster architecture where
-each physical machine runs a backup service and a distributed file system (DFS)~\cite{googlefs03,hdfs10} 
-serves a backup store  for the snapshots.
+% Figure~\ref{fig:collocated} illustrates the cluster architecture where
+% each physical machine runs a backup service and a distributed file system (DFS)~\cite{googlefs03,hdfs10}
+% serves a backup store  for the snapshots.
+Figure~\ref{fig:collocated} illustrates a converged IaaS cloud architecture
+where each commodity server hosts a number of virtual machines and storage of these servers
+is clustered using a distributed file system~\cite{googlefs03,hdfs10}.
+Each physical machine hosts multiple virtual machines.  Every virtual machine
+runs its own guest operating system and accesses virtual hard disks
+stored as image files maintained by the operating system running on the
+physical host.
 
@@
     \includegraphics[width=5in]{images/colocated-arch}
-    \caption{Collocated VM Backup System.}
+    \caption{VM snapshot backup running on a converged cloud cluster.}
     \label{fig:collocated}
@@
 
-\section{Two Level Hierarchical Design of VM Metadata}
+\section{VM Snapshot Metadata Hierarchy}
 \label{overview:meta}

### 2014-08-25 thesis/Vitae.tex
update to thesis

@@
 %\vspace{-0.5cm}
-\item Michael Daniel Agun, Wei Zhang, Tao Yang, ``Optimized Synchronous Data Deduplication for Virtual Machine Backup in Cloud Storage''. {\it To be submitted for publication}.
+\item Michael Daniel Agun, Tao Yang, Wei Zhang. ``Asynchronous Source-side Deduplication for Cloud Data Backup''. {\it To be submitted for publication}.
 
-\item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang.
-``Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud''.
-{\it Submitted to the 12th USENIX Conference on File and Storage Technologies (FAST '14)}.
+\item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang. ``VM-Centric Snapshot Deduplication for Converged Cloud Architectures''. {\it Submitted to 2014 ACM Symposium on Cloud Computing (SoCC'14)}.
 
@@
 
-   % \item Me Myself, S. Mart, and A. Nother Advisor:
-   % ``Cool Paper Title,'' In
-   % {\it Proc.\ IEEE Intl.\ Conference Cool Papers 
-   %      (ICCP)}, August 2000.
 \vspace{0.3cm}

### 2014-08-29 thesis/Abstract.tex
final thesis
update to thesis
some changes

@@
 \addcontentsline{toc}{chapter}{Abstract}
-A cloud platform that hosts a large number of virtual machines (VMs) has high storage demand for frequent backup of VM snapshots.
+A cloud platform that hosts a large number of virtual machines (VMs) has high storage demand for frequent backup 
+of VM snapshots. 
 Content signature based deduplication is necessary to eliminate excessive redundant blocks. 
@@
 Then each machine conducts duplicate detection partition by partition independently with minimal memory consumption.
-Another optimization is to allocate and control buffer space for exchanging detection requests and duplicate summaries among machines.
-The memory requirement and disk usage for the proposed solution is very small while the overall throughput and backup process timing is not compromised.
+Another optimization is to allocate and control buffer space for exchanging detection requests and duplicate summaries
+among machines. The resource requirement in terms of memory and disk usage for the proposed solution is 
+very small while the backup efficiency in terms of overall throughput and time is not compromised. 
 Our evaluation validates this and shows a satisfactory backup throughput in a large cloud setting.
@@
 \end{abstract}
-
-%\begin{germanabstract}
-
-%\addcontentsline{toc}{chapter}{Zusammenfassung}
-
-%\end{germanabstract}

### 2014-08-29 thesis/Background.tex
some changes

@@
 % what is the problem
-Storage is the biggest challenge in virtualized cloud today.
+
+%Storage is the biggest challenge in virtualized cloud today.
 At a cloud cluster node, each instance of a guest operating 
@@
 represented as virtual disk image files in the host operating system.
-Backing up virtual machines is typically done through taking snapshots,
-which is a copy of the virtual machine's disk file at a given point in time.
-Performing such VM snapshot backup tasks for the entire cluster is a difficult task
+Virtual machine backup is typically conducted through a snapshot,
+which is a copy of the virtual machine's disk files at a given time.
+Performing VM snapshot backup for the entire cluster is difficult 
 for several reasons: 
 \begin{itemize}
-\item \textbf{Huge storage demand.} Each VM contains from tens of GBs to multiple TBs of data,
-the snapshots size of an entire cloud often exceeds one PB, and they need to be backed up from daily to weekly.
-\item \textbf{Big network bandwidth cost.} Sending such amount of backup data requires
-a lot of network bandwidth and may impede normal application activity.
+\item \textbf{Huge storage demand.} The size of each VM snapshot varies from tens of gigabytes to multiple 
+terabytes while the total snapshot size of an entire cloud cluster is often  in a petabyte level.
+Such data needs to be backed up daily or weekly.
+\item \textbf{Big network bandwidth cost.} Sending such a large amount of snapshot data requires
+a large network bandwidth and may impede normal application activities.
 \end{itemize}
 
-As a result, data deduplication is mandatory in order to reduce the storage and bandwidth
-costs of backup in cloud. But adding deduplication at cloud scale brings new
+As a result, data deduplication is necessary in order to reduce the storage and bandwidth
+costs of backup in a cloud cluster. But adding deduplication at a cloud scale brings new
 challenges against previous developed techniques:
@@
 % summary
-In sum, deduplication systems designed for legacy network storage that are attached to
+In summary, deduplication systems designed for legacy network storage that are attached to
 physical servers are too expensive and complex for virtual machines. 
@@
 their data, otherwise they will be forced to backup less amount of data or less frequently,
-which in return will compromise the data safty and recovery time. For example, Electronic Arts, which deploys
+which in return will compromise the data safety and recovery time. For example, Electronic Arts, which deploys
 its data analytics platform in Amazon's AWS using several hundreds of VMs, 
-avoids using Amazon's built-in snapshot storage and chooses to backup hand-picked data manuallyv for cost reasons.
+avoids using Amazon's built-in snapshot storage and chooses to backup hand-picked data manually for cost reasons.
 
@@
 Section~\ref{back:dedup} introduces the origin and applications of data deduplication.
-Section~\ref{back:optm} talks the optimization and tradeoffs in designing a deduplication storage system.
+Section~\ref{back:optm} talks the optimization and tradeoff in designing a deduplication storage system.
 Section~\ref{back:arch} discusses design options of backup storage architecture.
@@
 can not be utilized. Therefore we need better method to break files into data blocks.
-In the recent decad, data deduplication techniques are emerged to solve this data
+In the recent decade, data deduplication techniques are emerged to solve this data
 redundancy problem in backup systems.
@@
 These breakpoints provide 
-modification-resistant boundaries that seperate the file
+modification-resistant boundaries that separate the file
 into many small chunks. A sequence of hash values of such chunks
@@
 There are pathological cases in finding breakpoints, for example,
-a long extent of zeros may never contain a breakpoint. Thus, LBFS\cite{lbfs01}
+a long extent of zeros may never contain a break point. Thus, LBFS\cite{lbfs01}
 introduces min and max thresholds to the chunk size: when scanning the file
@@
 and identify them by content hash,
-it is very natrual to build CAS system base on it.
+it is very natural to build CAS system base on it.
 Jumbo Store and others\cite{jumbo07,efficient_dedup05,you06} encodes directory tree snapshots
@@
 Directory metadata, file metadata and data chunk are all
-represented in the form of variable-size data blocks that indetified by content hash.
-A object which encapsulate metadata also has a list of hash indentifiers 
+represented in the form of variable-size data blocks that identified by content hash.
+A object which encapsulate metadata also has a list of hash identifiers 
 that point to other blocks it contains.
@@
 The advantage of Cumulus is portability, because it makes 
-the de-duplication backup totoally opaque to the server.
+the de-duplication backup totally opaque to the server.
 However, without the de-duplication support from protocol and server side, 
-it's hard to have efficent storage management, and from server's perspective,
+it's hard to have efficient storage management, and from server's perspective,
 snapshots from many users still contain much redundant data.
 
-\section{Optimizations and Tradeoffs}
+\section{Optimization and Tradeoff}
 \label{back:optm}
@@
 Most of approaches discussed above focus on optimization of inline deduplication
-performance by sacraficing a small percent of deduplication efficiency.
+performance by sacrificing a small percent of deduplication efficiency.
 In our cloud backup scenario, we must always satisfy the low resource usage constraints while 
 providing sustainable good throughput. As a result, we consider to sacrifice other performance metrics 
-to achieve our design goals, which we descibe as below:
+to achieve our design goals, which we describe as below:
 % In addition, none of them have considered the impact
@@
 Job turnaround time is the total time for a backup job from submit to finish.
-All three metrics are important. Good dedupe efficiency 
+All three metrics are important. Good deduplication efficiency 
 reduces the storage cost. High throughput
@@
 
-This dissertation studies two low-cost deduplication design options with different tradeoffs. 
+This dissertation studies two low-cost deduplication design options with different tradeoff. 
 Chapter~\ref{chap:offline} gives a synchronous parallel deduplication design that

### 2014-08-29 thesis/Introduction.tex
update to thesis
some changes

@@
 The ubiquity of the cloud computing has resulted in the 
-widespread availability of cloud based services and applications accessible through 
-the network. Examples include online storage services, big data analysis, and various websites.
+widespread availability of cluster-based services and applications accessible through 
+the Internet. Examples include online storage services, big data analytics, and e-commerce websites.
 In such a cluster-based cloud environment,
@@
 to contain different kind of user applications,
-and their data are stored in virtual hard disks which are represented 
+and their data is stored in virtual hard disks which are represented 
 as virtual disk image files in the host operating system.
@@
 because of the huge storage demand. 
-If such VM snapshot data are plainly backed up without any duplicate reduction, storage waste would be 
+If such VM snapshot data is plainly backed up without any duplicate reduction, storage waste would be 
 extreme high. For example, a fresh Windows server 2008 installation costs 25 GB on the virtual disk,
@@
 Unlike the previous work dealing with general file-level
-backup and deduplication inside a centralized storage appliance, our problem is focused on virtual
+backup and deduplication inside a centralized storage appliance, our research is focused on virtual
 disk image backup in a cluster of machines. Although we treat each virtual disk as a
@@
 to support parallel backup of a large number of virtual disks
-in a cloud every day. One key requirement we face at busy clouds
+in a cloud every day. One key requirement we face at a busy cloud cluster
  is that VM snapshot backup should only use a minimal
@@
 
-Despite its importance, storage deduplication remains a challenging task for cloud storage providers. 
-And this is especially true for resource constrained large scale public VM cloud. 
+Despite its importance, storage deduplication remains a challenging task for cloud storage providers,
+especially for resource-constrained large-scale public VM clouds. 
 In recognizing this importance and
@@
 
-\textit{It  is  possible  to  build  an efficient, scalable, and fault tolerant backup storage
-supporting highly accurate deduplication with sustainable high throughput
-and easy management on deduplicated data.}
+\textit{It  is  possible  to  build  an efficient, scalable, and fault-tolerant backup service
+supporting highly accurate deduplication with sustainable high throughput.}
 
@@
 how can such a snapshot backup service identify whether a piece of data in VM disk
-really needs to backup? And how to manage backup data under complex sharing relationship?
+really needs a backup? And how to manage backup data under complex sharing relationship?
 This dissertation investigates 
@@
 \begin{itemize}
-\item A design of low-cost multi-stage parallel deduplication solution for automically batched deduplication.
-\item An inline multi-level deduplication scheme with similarity guided local detection and popularity guided global detection.
+\item The design of a low-cost multi-stage parallel deduplication solution for automically batched deduplication.
+\item An inline multi-level deduplication scheme with similarity-guided local detection and 
+popularity-guided global detection.
 \item The development and analysis of a VM-centric storage approach which considers fault isolation and integrates multiple duplicate detection strategies.
@@
 of this work is to provide low-cost deduplication support and storage management for 
-large scale resource-constrained VM cloud. This solution should be collocated with existing
+large-scale resource-constrained VM clouds. This solution should be collocated with existing
 cloud infrastructure services and require no dedicated hardware support. It also needs to
-accomplish good deduplication efficiency and does comprise the data reliability due to the
+accomplish good deduplication efficiency and does not comprise the data reliability due to the
 inherent volatility of commodity hardware.
@@
 depending on backup requirements. The objective is to provide satisfactory deduplication efficiency
-and high throughput with the emphasis on low resource usage and fault tolerancy.
+and high throughput with the emphasis on low resource usage and fault tolerance.
 
@@
 The rest of this dissertation is organized as follows.  
-Chapter~\ref{chap:back} gives an introduction to the history and background of thesis problems.
+Chapter~\ref{chap:back} gives the background of thesis problems.
 Chapter~\ref{chap:overview} presents the overall VM snapshot storage architecture.
-Chapter~\ref{chap:offline}  describes a synchronous and parallel deduplication scheme for offline batched complete deduplication.
+Chapter~\ref{chap:offline}  describes a synchronous and parallel deduplication scheme for batched complete deduplication.
 Chapter~\ref{chap:inline} studies a multi-level selective deduplication solution for inline deduplication.

### 2014-08-29 thesis/Conclusion.tex
re

@@
 \label{chap:concl}
-Building deduplication in backup storage with the ever-increasing demand on 
-scalability and throughput is a challenging  task.  This dissertation investigates 
-techniques in building a VM snapshot storage system, that provides low-cost
-deduplication support for scale out VM clouds.  In particular, our work focuses on 
-three specific  aspects  of VM snapshot deduplication: synchronous solution for offline duplicate detection,
-multi-level selective approach for inline deduplication, and data management on top of
-cloud file system with emphysis on fault tolerancy and garbage collection.
-Our system  has  been  implemented on Xen based Linux VM clusters.
+Deduplication in storage backup with an ever-increasing demand faces 
+scalability and throughput challenges.  This dissertation investigates 
+scalable techniques in building a VM snapshot storage system that provides low-cost
+deduplication support for large VM clouds.  In particular, our work focuses on 
+three specific  aspects  of VM snapshot deduplication: a synchronous solution for offline duplicate detection,
+a multi-level selective approach for inline deduplication, and data management on the top of
+cloud file system with an emphasis on fault tolerance and garbage collection.
+Our system  has  been  implemented on Xen-based Linux VM clusters.
 
 This dissertation begins with studying a low-cost multi-stage
-parallel deduplication solution for automatically synchronous backup use case. 
+parallel deduplication solution for synchronous backup. 
 We split the original inline deduplication process into different stages to
@@
 machine accumulates detection requests and then performs 
-detection partition by partition with minimal resource usage. 
+detection partition by partition with a minimal resource usage. 
 Fingerprint based partitioning allows
 highly parallel duplicate detection and also simplifies
-reference counting management
-Because the design of separation
+reference counting management.
+Because the design separation
 of duplicate detection and actual backup, we are able
-to evenly distribute fingerprint comparison among clustered machine nodes, 
+to conduct distributed fingerprint comparison in parallel among clustered machine nodes, 
 and only load one partition at time
 at each machine for in-memory comparison.
-which makes the proposed scheme very resource-friendly 
+This makes the proposed scheme very resource-friendly 
 to the existing cloud services.
 
-In the next we present a multi-level selective deduplication scheme for 
-on-demand snapshot service in VM cloud. Our approach utilitizes similarity guided inner-VM
-deduplication to localize backup data dependency and exposes
-more parallelism, while depending on popularity guided cross-VM deduplication 
-with a small
-popular data set effectively covers a large amount of duplicated data. 
-Our solution accomplishes the majority of potential
-global deduplication saving while still meets stringent cloud
-resources requirement. Compare to todays widelyused snapshot technique, 
-our scheme reduces almost two-third
+We have also presented a multi-level selective deduplication scheme for 
+on-demand snapshot backup service. Our approach utilizes similarity guided inner-VM
+deduplication to localize backup data dependence and exposes
+more parallelism. Meanwhile cross-VM deduplication uses
+a small popular data set to effectively cover a large amount of  content blocks. 
+Our solution achieves the majority of what perfect
+global deduplication can accomplish while meeting stringent 
+resource requirements. Compared to the existing snapshot techniques, 
+our scheme reduces about two-third
 of snapshot storage cost. Finally, our scheme uses a very
-small amount of memory on each node, and leaves room for
-additional optimization we are further studying.
+small amount of memory on each node, and leaves room for employing other
+optimization techniques.
 
-Finally this dissertation proposes a collocated VM-centric backup architecture
-built on the top of a cloud cluster with emphysis on fault tolerancy and garbage collection. 
-Benefited from our multi-level selective deduplication scheme, 
-we can reduce cross-VM data dependency and exposes more parallelism. 
-VM-specific file
-block packing also enhances fault tolerance by reducing
-data dependencies.
-The key contribution is a VM-centric data management scheme 
-to maximize data localization (reduce cross VM sharing) while delivering 
-competitive deduplication efficiency. In addition,
-such design allows garbage collection to be performed in a 
+%The VM-centric backup service is collocated with other cloud servies.
+%built on the top of a cloud cluster with emphasis on fault tolerance and garbage collection. 
+%Benefited from our multi-level selective deduplication scheme, 
+%we can reduce cross-VM data dependency and exposes more parallelism. 
+The key contribution of our VM-centric data management is 
+VM-specific file block packing that enhances fault tolerance by 
+maximizing data localization and reducing cross VM sharing.
+In addition, such a design allows garbage collection to be performed in a 
 localized scope and we propose an approximate deletion
-scheme to reduce this cost further.
-As supported by theoretical analysis and study on real VMs, 
-the availability of snapshots increases substantially with a small
+scheme to further reduce the cost.
+As supported by theoretical analysis and experimental studies, 
+the availability of VM snapshots increases substantially with a small
 replication overhead for popular inter-VM chunks.
-Most importantly, our design places a special consideration for 
-low-resource usages as a collocated cloud service.
+%Most importantly, our design places a special consideration for 
+%low-resource usages as a collocated cloud service.
 
-The design of our VM-centric deduplication approach exposes the potential of
-envolving into a general purpose cloud backup system or file caching service. The idea of collecting
-popular data becomes more interesting as to how much data in common in people's personal usages.
+The design of our VM-centric deduplication approach has a potential of being applied
+to general purpose cloud backup. The idea of collecting
+popular data becomes more interesting based on in data commonality among users.
 However, the access to popular data could be a bottleneck in the I/O path if not designed carefully,

### 2014-08-29 thesis/Acknowledgements.tex
re

@@
 \begin{acknowledgements}
-\addcontentsline{toc}{chapter}{Acknowledgements}
+\addcontentsline{toc}{chapter}{Acknowledgments}
 
@@
 words to my wife, Jiayin, who has been encouraging and inspiring me 
-since we met in love. We went through all the difficlut times together,
+since we met in love. We went through all the difficult times together,
 and depended on each other in this foreign place one Pacific Ocean away from our homeland.
@@
 This dissertation study was supported in part by NSF IIS-1118106.
+Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
+do not necessarily reflect the views of Alibaba or the National Science Foundation.
 \end{acknowledgements}

### 2014-09-01 thesis/Background.tex
remove invalide chars

@@
 existing VM activities. Compare to dedicated backup appliances which are typically equipped with
-tens of GBs of memory and  multiple processors, backup service in the cloud are only allowed to use
-no more than a few hundred MBs of memory, and its CPU usage must always stay low.
+tens of GB of memory and  multiple processors, backup service in the cloud are only allowed to use
+no more than a few hundred MB of memory, and its CPU usage must always stay low.
 \item \textbf{Garbage collection for shared data.} Data management for deduplicated storage
@@
 Section~\ref{back:dedup} introduces the origin and applications of data deduplication.
-Section~\ref{back:optm} talks the optimization and tradeoff in designing a deduplication storage system.
+Section~\ref{back:optm} talks the optimization and trade-off in designing a deduplication storage system.
 Section~\ref{back:arch} discusses design options of backup storage architecture.
@@
 redundancy problem in backup systems.
-Most of data de-duplication methods can be categorized by their granularities:
+Most of data de-duplication methods can be categorized by their granularity:
 
@@
 data in order to find similar files. This technique computes
-fingerprints of all possible substrings of a certain
+fingerprints of all possible sub-strings of a certain
 length in a file and chooses a subset of these fingerprints
 based on their values,  e.g., if $(fingerprint(s)\ mod\ a) = b$, where
-$s$ is a substring,
-$a$ and $b$ are pre-defined values, then the position of substring $s$
+$s$ is a sub-string,
+$a$ and $b$ are pre-defined values, then the position of sub-string $s$
 is considered as a breakpoint. 
@@
 introduces min and max thresholds to the chunk size: when scanning the file
-sequentially for breakpoints, if the distance between current substring 
+sequentially for breakpoints, if the distance between current sub-string 
 and previous breakpoint is less than the minimum threshold, then it is skipped;
 if the distance reaches the maximum threshold, then a breakpoint
-is enforced. This method also reduces the computation because less substrings
+is enforced. This method also reduces the computation because less sub-strings
 are checked. In order to increase the chance of finding a breakpoint between
@@
 
-\section{Optimization and Tradeoff}
+\section{Optimization and Trade-off}
 \label{back:optm}
@@
 With low cache hit ratios, most index lookups require disk operations.
-If each index lookup requires a disk access which may take 10 msec and 8 disks are used for index lookups in parallel, the write throughput will be about 6.4MB/sec, which is far from the throughput goal of deduplicating at 115 MB/sec for our cloud backup scenario, and don't forget that this goal
+If each index lookup requires a disk access which may take 10 ms and 8 disks are used for index lookups in parallel, the write throughput will be about 6.4MB/sec, which is far from the throughput goal of deduplicating at 115 MB/sec for our cloud backup scenario, and don't forget that this goal
 is conservative since VM users generally want the backup task to finish in tens of minutes without affecting their normal
@@
 they can be accessed quickly and easily.
-Once there's a hit in the sampled index, system loads the fingerprints that are next to the hitted one on disk,
+Once there's a hit in the sampled index, system loads the fingerprints that are next to the hit one on disk,
 so that it can efficiently catches duplicates based on spatial locality.
@@
 
-This dissertation studies two low-cost deduplication design options with different tradeoff. 
+This dissertation studies two low-cost deduplication design options with different trade-off. 
 Chapter~\ref{chap:offline} gives a synchronous parallel deduplication design that
@@
 primary storage, so we will give a glimpse on primary storage's evolution first.
-Organizations start with ﻿building ﻿their ﻿virtualization ﻿infrastructure ﻿using ﻿the﻿
-traditional ﻿servers-connected-to-storage-over-a-network ﻿architecture, ﻿which﻿
-can’t ﻿adapt ﻿to ﻿the ﻿ever-changing ﻿demands ﻿of ﻿virtualization. ﻿In ﻿addition ﻿to ﻿slow﻿
-performance,﻿ network ﻿storage ﻿has ﻿become﻿ the﻿ single﻿ biggest﻿ source ﻿of ﻿cost ﻿and﻿
-complexity ﻿in ﻿virtualized ﻿environments.﻿ The ﻿network﻿ storage-based ﻿architecture﻿
-worked﻿ well ﻿for ﻿physical﻿ servers ﻿that ﻿served﻿ relatively﻿ static ﻿workloads.﻿
-Virtualization,﻿ and﻿ now﻿ Cloud﻿ Computing,﻿ has﻿ made﻿ data﻿ centers﻿ extremely﻿
-dynamic\cite{berkeleycloud09};﻿ virtual﻿ machines﻿ are﻿ created﻿ on﻿ the﻿ fly,﻿ move﻿ from﻿ server﻿ to﻿ server﻿ and﻿﻿
-depend﻿ heavily﻿ on﻿ shared﻿ resources.﻿ These ﻿characteristics ﻿make ﻿the ﻿management﻿
-of ﻿virtual ﻿machines ﻿and ﻿their﻿ underlying ﻿physical﻿ infrastructure ﻿extremely﻿
-complex: Data ﻿volumes ﻿are﻿ growing﻿ at ﻿a ﻿rapid ﻿pace﻿ in﻿ the ﻿data ﻿center, ﻿thanks﻿ to ﻿the ﻿ease﻿
-of﻿ creating ﻿new﻿ VMs.﻿ In ﻿the﻿ enterprise,﻿ new﻿ initiatives ﻿like ﻿desktop﻿ virtualization﻿
-contribute﻿ to ﻿this﻿ trend.﻿ Service﻿ providers﻿ deal﻿ with﻿ an﻿ even﻿ larger﻿ number﻿ of﻿
-VMs﻿ as﻿ they﻿ build﻿ data﻿ centers﻿ to﻿ serve﻿ customers﻿ who﻿ can’t﻿ afford﻿ the﻿ cost﻿
-and﻿ management﻿ overhead﻿ that﻿ virtualization ﻿requires. ﻿This﻿ growing ﻿pool ﻿of﻿
-VMs﻿ is ﻿exerting ﻿tremendous ﻿cost, ﻿performance﻿ and ﻿manageability ﻿pressure﻿ on﻿
-the ﻿traditional ﻿architecture ﻿that ﻿connects﻿ compute﻿ to ﻿storage﻿ over ﻿a ﻿multi-hop﻿
-network.﻿
+Organizations start with building their virtualization infrastructure using the
+traditional servers-connected-to-storage-over-a-network architecture, which
+can’t adapt to the ever-changing demands of virtualization. In addition to slow
+performance, network storage has become the single biggest source of cost and
+complexity in virtualized environments. The network storage-based architecture
+worked well for physical servers that served relatively static workloads.
+Virtualization, and now Cloud Computing, has made data centers extremely
+dynamic\cite{berkeleycloud09}; virtual machines are created on the fly, move from server to server and
+depend heavily on shared resources. These characteristics make the management
+of virtual machines and their underlying physical infrastructure extremely
+complex: Data volumes are growing at a rapid pace in the data center, thanks to the ease
+of creating new VMs. In the enterprise, new initiatives like desktop virtualization
+contribute to this trend. Service providers deal with an even larger number of
+VMs as they build data centers to serve customers who can’t afford the cost
+and management overhead that virtualization requires. This growing pool of
+VMs is exerting tremendous cost, performance and manageability pressure on
+the traditional architecture that connects compute to storage over a multi-hop
+network.
 
-Google﻿\cite{googlefs03} and﻿ other﻿ leading ﻿cloud-generation﻿ companies ﻿such﻿ as ﻿Amazon,﻿ Yahoo﻿
-and﻿ Microsoft﻿(Azure)﻿\cite{azure} realized ﻿that ﻿a ﻿network-storage﻿ based﻿ approach﻿ would﻿
-not ﻿work﻿ for﻿ their﻿ data ﻿centers.﻿ They﻿ built﻿ software﻿ technology﻿ (such ﻿as ﻿Google﻿
-File ﻿System)﻿ that﻿ could ﻿glue﻿ a﻿ large﻿ number﻿ of ﻿commodity﻿ servers﻿ with﻿ local﻿
-storage ﻿into ﻿a ﻿single﻿ cluster.﻿ This﻿ approach﻿ allowed﻿ Google﻿ to ﻿build ﻿a ﻿converged﻿
-compute﻿ and﻿ storage ﻿infrastructure﻿ that﻿ used﻿ commodity﻿ servers﻿ with﻿ local﻿
-storage﻿ as ﻿its ﻿building ﻿block\cite{deconstructing05}.﻿ Google﻿ File﻿ System﻿ runs﻿ across﻿ a ﻿cluster ﻿of ﻿servers﻿
-and﻿ creates ﻿a ﻿single ﻿pool﻿ of﻿ local﻿ storage﻿ that﻿ can ﻿be﻿ seamlessly﻿ accessed﻿ by﻿
-applications﻿ running﻿ on ﻿any ﻿server﻿ in﻿ the ﻿cluster.﻿ It ﻿provides﻿ high﻿ availability﻿
-to ﻿applications ﻿by ﻿masking﻿ failures ﻿of ﻿hard﻿ disks ﻿and ﻿even﻿ complete ﻿servers.﻿
-Google﻿ File﻿ System ﻿allowed ﻿Google﻿ to﻿ build﻿ data﻿ centers ﻿with﻿ massively ﻿scalable﻿
-compute﻿ and﻿ storage,﻿ without ﻿incurring ﻿the ﻿costs﻿ and﻿ performance﻿ limitations﻿
-associated ﻿with﻿ network ﻿storage.﻿
+Google\cite{googlefs03} and other leading cloud-generation companies such as Amazon, Yahoo
+and Microsoft(Azure)\cite{azure} realized that a network-storage based approach would
+not work for their data centers. They built software technology (such as Google
+File System) that could glue a large number of commodity servers with local
+storage into a single cluster. This approach allowed Google to build a converged
+compute and storage infrastructure that used commodity servers with local
+storage as its building block\cite{deconstructing05}. Google File System runs across a cluster of servers
+and creates a single pool of local storage that can be seamlessly accessed by
+applications running on any server in the cluster. It provides high availability
+to applications by masking failures of hard disks and even complete servers.
+Google File System allowed Google to build data centers with massively scalable
+compute and storage, without incurring the costs and performance limitations
+associated with network storage.
 

### 2014-09-01 thesis/Abstract.tex
grammar fixes

@@
 \addcontentsline{toc}{chapter}{Abstract}
-A cloud platform that hosts a large number of virtual machines (VMs) has high storage demand for frequent backup 
-of VM snapshots. 
-Content signature based deduplication is necessary to eliminate excessive redundant blocks. 
-While dedicated backup storage systems can be used to reduce data  redundancy,  such an architecture is expensive and introduces huge network  traffic in a large cluster. 
-This thesis research is focused on a low-cost backup and deduplication service collocated with other cloud services to reduce infrastructure and network cost.
+Cloud platforms that host a large number of virtual machines (VMs) have high storage demand for frequent backups
+of VM snapshots. Content signature based deduplication is necessary to eliminate excessive redundant blocks.
+While dedicated backup storage systems can be used to reduce data  redundancy,
+such an architecture is expensive and introduces huge network  traffic in a large cluster.
+This thesis research is focused on a low-cost backup and deduplication service collocated with
+other cloud services to reduce infrastructure and network cost.
 
 The previous research for cluster-based data deduplication has concentrated on various inline solutions.
-The first part of the thesis work is a  highly parallel and offline solution with synchronized backup scalable for a large number of virtual machines.
-The key idea is to separate duplicate detection from the actual storage backup, and partition global index and detection requests among machines using fingerprint values.
+The first part of the thesis work is a  highly parallel and offline solution with synchronized backup scalable
+for a large number of virtual machines. The key idea is to separate duplicate detection from the actual storage backup,
+and to partition global index and detection requests among machines using fingerprint values.
 Then each machine conducts duplicate detection partition by partition independently with minimal memory consumption.
@@
 The key difference compared to the previous work is its novelty in fault resilience and low resource usage.
-We propose a multi-level selective deduplication scheme which integrates similarity-guided and popularity-guided duplicate elimination under a stringent resource requirement.
-This scheme uses popular common data to facilitate fingerprint comparison, localizes deduplication as much as possible within each VM, and associates underlying file blocks with one VM for most of cases.
-The main advantage of this scheme is that it strikes a balance between inner and inter VM  deduplication to increase parallelism and  improve reliability.
-Our analysis shows that this VM-centric scheme can provide better fault tolerance while using a small amount of computing and storage resource.
+We propose a multi-level selective deduplication scheme which integrates similarity-guided and
+popularity-guided duplicate elimination under a stringent resource requirement.
+This scheme uses popular common data to facilitate fingerprint comparison, localizes deduplication
+as much as possible within each VM, and associates underlying file blocks with one VM for most of cases.
+The main advantage of this scheme is that it strikes a balance between inner and inter VM deduplication,
+increasing parallelism and  improving reliability.  Our analysis shows that this VM-centric scheme can provide
+better fault tolerance while using a small amount of computing and storage resource.
 We have conducted a comparative evaluation of this scheme on its competitiveness in terms of deduplication efficiency and backup throughput.

### 2014-09-07 thesis/Background.tex
grammar changes

@@
 \label{back:dedup}
-Backup storage for VM snapshots in the cloud contains PBs of data from many VMs,
+Backup storage for VM snapshots in the cloud contains petabytes of data from many VMs,
 the data redundancy in such a data set is very high\cite{Jayaram2011, agrawal07}.
@@
 redundancy problem in backup systems.
-Most of data de-duplication methods can be categorized by their granularity:
+Most of data deduplication methods can be categorized by their granularity:
 
@@
 limitations in the previous two methods, and provides
-best de-duplication efficiency. 
+best deduplication efficiency.
 \end{itemize}
@@
 experimental results and present a comparative analysis
-to three de-duplication methods: First, the content based chunking
+to three deduplication methods: First, the content based chunking
 is always the best strategy to discover redundancy in any data sets.
 Second, the fixed size block method can sometimes provides
-close results compare to content based chunking, and it has smalleris less
-computation intensive. Finally, if only for local file system,
-file compression is still the
-best strategy to save disk space, combining the content based chunking
-with compression does not justify the computation it costs.
+close results compare to content based chunking, and it brings significant less
+overhead to computation and data management. Finally, for I/O intensive primary storage system,
+data compression is still the most efficient approach to save disk space,
+inline data reduction through deduplication has too much random I/O overhead, making it difficult to
+justify the limited space savings in a primary storage system.
 
-Data de-duplication is extensively used in saving bandwidth for data synchronization.
+Data deduplication is extensively used in saving bandwidth for data synchronization.
 The popular rsync\cite{rsync} protocol exploits the similarity of two directory trees
-using fixed size blocks de-duplication. 
+using fixed size blocks deduplication.
 LBFS uses content-based chunking to improve the NFS protocol,
 it avoids transmitting redundant chunks which already exist at the other side.
-But data du-duplication has its cost. Content-based chunking algorithm needs to
+But data deduplication has its cost. Content-based chunking algorithm needs to
 scan the whole file looking for breakpoints, which is very slow (about 20MB/s using a single 2GHz core). 
@@
 that point to other blocks it contains.
-Such a de-duplication storage system has some great advantages 
+Such a deduplication storage system has some great advantages
 in terms of space efficiency, file transmission efficiency (through a LBFS-like protocol), 
@@
 The advantage of Cumulus is portability, because it makes 
-the de-duplication backup totally opaque to the server.
-However, without the de-duplication support from protocol and server side, 
+the deduplication backup totally opaque to the server.
+However, without the deduplication support from protocol and server side,
 it's hard to have efficient storage management, and from server's perspective,
@@
 \label{back:arch}
-The way that backup storage architecture envolves has been following the pace of
+The way that backup storage architecture evolves has been following the pace of
 primary storage, so we will give a glimpse on primary storage's evolution first.
@@
 In cooperate with the changes of primary storage in cloud, backup storage architecture
-has to envolve as well. A dedicated backup storage appliance sits aside the cloud does provide some good properties,
+has to evolve as well. A dedicated backup storage appliance sits aside the cloud does provide some good properties,
 such like it deduplicates all the backup data together so it provides good deduplication efficiency,
@@
 % raw data for backup.
+
+% ption in transferring the
+% % raw data for backup.

### 2014-09-08 thesis/DataManagement.tex
update to thesis
fix typos

@@
 Section~\ref{data:arch} describes our system architecture and implementation details.
-Section~\ref{data:analysis} analyzes the tradeoff and benefits of our approach. 
+Section~\ref{data:analysis} analyzes the trade-off and benefits of our approach.
 Section~\ref{data:deletion} describes out approximate deletion algorithm.
@@
 
-Additional APIs such as \textbf{Scan()}, \textbf{Compact()}, \textbf{Create()} and \textit{Remove()} are provided for 
+Additional APIs such as \textbf{Scan()}, \textbf{Compact()}, \textbf{Create()} and \textbf{Remove()} are provided for 
 higher level operations. Scan() is used by the map-reduce procedure to collect the most popular blocks among all snapshot stores.
@@
 popular data into PDS which prevent each VM from keeping their own copies. We will show that by adding
-extra replication to PDS data, this strategy brings advantages to both fault tolerancy and deduplication efficiency.
+extra replication to PDS data, this strategy brings advantages to both fault tolerance and deduplication efficiency.
 The parameters we will use in our analysis below are defined in Table~\ref{tab:symbol}.
@@
 Since it is a VM-specific procedure,
-the space and time cost is relatively small compared to the tranditional mark-and-sweep
+the space and time cost is relatively small compared to the transitional mark-and-sweep
 which scans snapshot chunks from all VMs.
@@
 SRB can deliver up to 97.79\% deduplication efficiency, which is slightly better than VC.
-Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
+Thus this represents a trade-off that VC provides better fault tolerance and fast approximate deletion
 with competitive deduplication efficiency.
@@
 % SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
-% Thus this represents a tradeoff: VC provides better fault tolerance and fast
+% Thus this represents a trade-off: VC provides better fault tolerance and fast
 % approximate deletion with competitive (but slightly lower) deduplication
@@
 The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}
-to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
+to reduce memory requirements with the trade-off of a reduced deduplication ratio.
 Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
@@
 Such a scheme  is  VM-centric since deduplication is localized.
-We are seeking for a tradeoff since 
+We are seeking for a trade-off since
 global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
@@
 The design places a special consideration for low-resource usages as a collocated cloud service.
-Evaluation using  VM backup data shows that VC strikes a tradeoff and 
+Evaluation using  VM backup data shows that VC strikes a trade-off and
 can accomplish 96.33\% or 96.9\% of what complete global

### 2014-09-08 thesis/OfflineDedup.tex
fix typos

@@
 low resource usage,
-the tradeoff of this approach is that the job turnaround time for each individual
+the trade-off of this approach is that the job turnaround time for each individual
 VM backup task becomes longer. In addition,
@@
 %our scheme uses a single-thread procedure on each machine to minimize the use of CPU, network bandwidth, and disk bandwidth.
-We use the two level metadata hierachy as discussed in section~\ref{overview:meta}.
+We use the two level metadata hierarchy as discussed in section~\ref{overview:meta}.
 The snapshot metadata  contains a list of segments and other meta data information.
@@
 %Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}
-to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
+to reduce memory requirement with a trade-off of the reduced deduplication ratio.
 %use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
@@
 nodes, and only load one partition at time at each machine for in-memory comparison.
-%The tradeoff is that every machine has to read dirty segments twice 
+%The trade-off is that every machine has to read dirty segments twice
 %and that some deduplication requests are delayed for staged processing.

### 2014-09-08 thesis/Vitae.tex
remove unpublished

@@
 %\vspace{-0.5cm}
-\item Michael Daniel Agun, Tao Yang, Wei Zhang. ``Asynchronous Source-side Deduplication for Cloud Data Backup''. {\it To be submitted for publication}.
+% \item Michael Daniel Agun, Tao Yang, Wei Zhang. ``Asynchronous Source-side Deduplication for Cloud Data Backup''. {\it To be submitted for publication}.
 
-\item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang. ``VM-Centric Snapshot Deduplication for Converged Cloud Architectures''. {\it Submitted to 2014 ACM Symposium on Cloud Computing (SoCC'14)}.
+% \item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang.
+``VM-Centric Snapshot Deduplication for Converged Cloud Architectures''.
+{\it Submitted to 2014 ACM Symposium on Cloud Computing (SoCC'14)}.
 

### 2014-09-09 thesis/Conclusion.tex
offline -> batched

@@
 deduplication support for large VM clouds.  In particular, our work focuses on
-three specific  aspects  of VM snapshot deduplication: a synchronous solution for offline duplicate detection,
+three specific  aspects  of VM snapshot deduplication: a synchronous solution for batched duplicate detection,
 a multi-level selective approach for inline deduplication, and data management on the top of

### 2015-03-06 snapshot_system/mass.tex
prepare for mass conference

--- 2014-07-19 snapshot_system/paper.tex
@@
 \usepackage{breqn}
+\usepackage{tikz}
+\usetikzlibrary{calc,shapes,positioning,decorations.pathmorphing}
 \usepackage{pgfplots}
@@
 %with Fault Isolation 
-\title{VM-Centric Snapshot Deduplication for Converged Cloud Architectures}
+\title{VM-Centric Snapshot Deduplication for Cluster-based Cloud Backup}
 %VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
@@
 \keywords
-Virtual machine images, snapshot backup and deletion, source-side deduplication, cloud clusters and distributed architectures
+Virtual machine images, snapshot backup and deletion, source-side deduplication, cluster-based architectures
 
-\input{paper_intro}
-\input{paper_background}
-\input{paper_dedup}
-\input{paper_del}
-\input{paper_arch}
-\input{paper_eval}
-\input{paper_conc}
+\input{mass_intro}
+\input{mass_background}
+\input{mass_dedup}
+\input{mass_analysis}
+%\input{mass_del}
+\input{mass_arch}
+\input{mass_eval}
+\input{mass_conc}
 
 %\linespread{.97} % to squeeeze lines and put figures in same page
-\appendix
-\input{paper_analysis}
+%\appendix
 \bibliographystyle{abbrvnat}

### 2015-03-06 snapshot_system/mass_abs.tex
prepare for mass conference

--- 2014-07-19 snapshot_system/paper_abs.tex
@@
 suitable for running on a converged cloud architecture that cohosts  many other services.
-The key techniques in the proposed scheme are to localize deduplication as much as 
-possible within each VM guided by similarity search, restrict global 
-deduplication under popular chunks with extra replication support,
-and use an approximate method for fast and simplified snapshot deletion.
-This VM-centric design also improves the snapshot availability  during machine failures  
-by separating popular chunks and associating  file system blocks with one VM for non-popular chunks.
+We follow  a  VM-centric design that restricts global deduplication and 
+separates popular chunks with non-popular ones.   
+The  proposed techniques  are  similarity-guided local search 
+for  improving the effectiveness of  this VM-centric deduplication
+an  VM-centric file system block management to increase  the VM snapshot availability.  
+%deduplication under popular chunks with extra replication support.
+%and use an approximate method for fast and simplified snapshot deletion.
+%by separating popular chunks and associating  file system blocks with one VM for non-popular chunks.
 This  paper  describes an evaluation of this VM-centric scheme to assess  its deduplication 

### 2015-03-06 snapshot_system/mass_intro.tex
prepare for mass conference

--- 2014-07-19 snapshot_system/paper_intro.tex
@@
 the development and comparative study of  a VM-centric approach that
-simplifies deduplication and snapshot deletion and improves snapshot availability.
+simplifies deduplication improves snapshot availability.
 The key advantage of this approach  is that while maintaining  a competitive deduplication efficiency,

### 2015-03-06 thesis/InlineDedup.tex

@@
 Objectives of our experimental evaluation are:
-1) Analyze the popularality of content data blocks and the popularity  of hot items. 
+1) Analyze the popularity of content data blocks and the popularity  of hot items.
 2) Assess the effectiveness  of 3-level deduplication for reducing the storage cost of snapshot
@@
 %disk snapshots are divided into variable-sized blocks. Then
-In  Figure~\ref{fig:OSunchanged},  we list a conservative  popularality study in 7 major OS versions  supported
+In  Figure~\ref{fig:OSunchanged},  we list a conservative  popularity study in 7 major OS versions  supported
 in Aliyun.
@@
 1323 VM dataset, assuming that the average behavior of every subcluster with 100 machines
-exhibits a similar popularality. 
+exhibits a similar popularity.
 In addition to this, PDS for OS disks will become even more effective when
@@
 That leads  to a smaller amount of memory usage for storing meta data in signature
-lookup with a tradeoff of the reduced recall ratio.
+lookup with a trade-off of the reduced recall ratio.
 

### 2015-03-06 thesis/Introduction.tex

@@
 Frequent snapshot backup of virtual disk images is critical to increase  the service reliability
-and protect data safty.
+and protect data safety.
 For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China,
@@
 extreme high. For example, a fresh Windows server 2008 installation costs 25 GB on the virtual disk,
-and they are almost certianly duplicated with other Windows VM instances\cite{common07, pedal96}.
+and they are almost certainly duplicated with other Windows VM instances\cite{common07, pedal96}.
 Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
@@
 \begin{itemize}
-\item The design of a low-cost multi-stage parallel deduplication solution for automically batched deduplication.
+\item The design of a low-cost multi-stage parallel deduplication solution for automatically batched deduplication.
 \item An inline multi-level deduplication scheme with similarity-guided local detection and

### 2015-03-06 thesis/OfflineDedup.tex

@@
-\chapter{Synchronous and Parallel Approach for Offline Deduplication}
+\chapter{Synchronous and Parallel Approach for Batched Deduplication}
 \label{chap:offline}
@@
 backup storage. In this chapter we introduce an synchronous and parallel approach
-for offline batched deduplication. This solution is suitable for cloud which typically conduct
+for batched deduplication. This solution is suitable for cloud which typically conduct
 automatic backup of all the VMs during system's spare time.
@@
 
-While our synchronous offline solution accomplishes perfect deduplication efficiency while maintaining
+While our synchronous batched solution accomplishes perfect deduplication efficiency while maintaining
 low resource usage,
@@
 Offline deduplication is
-used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
+used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during system's idle time.
 %,NGmiddleware2011}.

### 2015-03-06 snapshot_system/mass_abs.tex
re

@@
 for  improving the effectiveness of  this VM-centric deduplication
-an  VM-centric file system block management to increase  the VM snapshot availability.  
+and  VM-centric file system block management for increasing  the VM snapshot availability.  
 %deduplication under popular chunks with extra replication support.

### 2015-03-06 snapshot_system/mass_abs.tex
re

--- 2015-03-06 snapshot_system/mass_abs.tex
@@
 detection is resource intensive when the backup service for VMs  is co-located with  other 
-cloud services.  This paper proposes a low-profile VM-centric backup service with  a tradeoff 
+cloud services.  This paper presents the design and implementation of
+a low-profile VM-centric backup service with  a tradeoff 
 for a competitive deduplication efficiency while using small computing resources, 
 suitable for running on a converged cloud architecture that cohosts  many other services.
-We follow  a  VM-centric design that restricts global deduplication and 
+This cluster-based service restricts global deduplication and 
 separates popular chunks with non-popular ones.   
-The  proposed techniques  are  similarity-guided local search 
-for  improving the effectiveness of  this VM-centric deduplication
-an  VM-centric file system block management to increase  the VM snapshot availability.  
+The  developed optimization includes similarity-guided local search 
+for  the improved overall deduplication effectiveness 
+and  VM-centric file system block management for the increased VM snapshot availability.  
 %deduplication under popular chunks with extra replication support.

### 2015-03-06 snapshot_system/mass_intro.tex
re

@@
 duplicates, even optimization or approximation techniques are developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
+\comments{
 When deleting unused snapshots, a grouped mark-and-sweep approach~\cite{Guo2011}  
 is effective while it still carries a significant cost, especially in a distributed
-setting.  Another side effect of deduplication is the possible loss of failure
+setting. 
+} Another side effect of deduplication is the possible loss of failure
 resilience~\cite{Reliability06}.  
@@
 
-This paper considers a backup service for converged cloud architectures
+Our work  considers a backup service for converged cloud architectures
 that is co-located with user VMs, sharing the cloud compute, network, and
-storage resource with them.  The main contribution of this paper is
-the development and comparative study of  a VM-centric approach that
-simplifies deduplication improves snapshot availability.
-The key advantage of this approach  is that while maintaining  a competitive deduplication efficiency,
-the scheme requires little resource usage to minimize the impact on other collocated cloud services.
+storage resource with them.  
+This paper follows our preliminary simulation study  in ~\cite{WeiZhangIEEE} to 
+restrict the scope of cross-VM deduplication and simplify the deduplication process
+by separating popular data chunks and presents the design and implementation of 
+a VM-centric scheme.  
+We term this approach {\em VM-centric} because the deduplication
+algorithm considers VM boundaries in making its decisions as opposed to
+treating all blocks as being equivalent within the storage system.
+Our work focuses on a tradeoff that allows the sharing of only ``popular'' data blocks 
+across virtual machines while using localized deduplication within each VM
+to achieve both storage savings and fault isolation.
+Another issue addressed is fault  isolation in a content sharing environment caused by deduplication.
+One consequence of aggressive deduplication is the possible loss of failure
+resilience.  If a shared block is lost, all files that
+share that block are affected.  Our work is motivated by \cite{Reliability06} that provides more
+replication for shared file system blocks and proposes VM-centric techniques.
+to 
+\comments{
+Since the underlying storage file system block size is typically bigger than the average data chunk size
+used for deduplication,  packaging
+content from different VMs into the same file block  creates a ``false'' sharing that 
+affects fault isolation;
+}
+
+The main contribution of this paper is
+1) a similarity-guided local deduplication for
+each VM to make the overall deduplication efficiency more competitive 
+to a transitional deduplication scheme;
+2) a VM-centric file block management to improve snapshot availability by
+separating popular chunk replication and
+packaging data chunks from the same VM into a file system block as much as possible; 
+3) a design and implementation of a VM-centric  backup service to integrate and validate
+the proposed techniques while imposing  little resource usage and  minimizing the impact on other collocated cloud services.
+Our  experimental study compares  the VM-centric approach with the previous 
+VM-oblivious approaches in terms of deduplication efficiency, resource usage,  and snapshot availability.
+%Thus we improve  to avoid such VM-oblivious packaging.
+%our approach uses a deduplication data chunk size that is smaller than a
+%single file block and
+
+%Deduplicating
+%data locally within a VM also reduces the need to maintain a global index of
+%chunks that are shared among VMs, thereby increasing the scaling efficiency of
+%the snapshot system.
+
 \comments{
@@
 } 
-We term our approach {\em VM-centric} because the deduplication
-algorithm considers VM boundaries in making its decisions as opposed to
-treating all blocks as being equivalent within the storage system.
-Our work focuses on a tradeoff that allows the sharing of only ``popular'' data blocks 
-across virtual machines while using localized deduplication within each VM
-to achieve both storage savings and fault isolation.
 \comments{
@@
 %THIS NEEDS MODIFICATION
+
 The rest of this paper is organized as follows.
@@
 %Section~\ref{sect:deduplication}  analyzes the tradeoff and benefits of the VM-centric approach. 
-Section~\ref{sect:deduplication}  presents our scheme for  snapshot deduplication and deletion.
+Section~\ref{sect:deduplication}  presents our scheme for  snapshot deduplication. 
+%and deletion.
 Section~\ref{sect:architecture}  describes a system implementation that evaluates the proposed techniques.

### 2015-03-07 snapshot_system/mass_arch.tex
prepare for mass conference
re

--- 2014-07-19 snapshot_system/paper_arch.tex
@@
-\section{Prototype Implementation}
+\section{System Design and Implementation}
 \label{sect:architecture}
 
-Our prototype system runs on a cluster of Linux machines with Xen-based VMs 
+We describe the design and implementation of a VM-centric backup system that
+runs on a cluster of Linux machines with Xen-based VMs 
 and the QFS~\cite{michael2013} distributed file system. 
@@
     %\includegraphics[width=2.75in]{images/socc_arch_cluster}
-    \includegraphics[width=2.8in]{images/socc_arch_cluster}
+    \includegraphics[width=2.7in]{images/socc_arch_cluster}
 %\vspace{1em}
@@
 %  \includegraphics[width=2.75in]{images/sstore_arch}
-  \includegraphics[width=2.8in]{images/sstore_arch}
+  \includegraphics[width=2.7in]{images/sstore_arch}
 %\vspace{1em}

### 2015-03-07 snapshot_system/mass_background.tex
re

--- 2014-07-19 snapshot_system/paper_background.tex
@@
 %Another disadvantage of cross-VM sharing is that it complicates
+\comments{
 Snapshot deletion 
@@
 
+Our previous work on parallel deduplication~\cite{WeiZhangIEEE}
+demonstrates the simulation results for  
+is not a comprehensive VM-centric solution and does not address  snapshot deletion and file system block 
+packaging for fault tolerance.
+
+Our previous work on popularity distribution of  deduplication~\cite{WeiZhangIEEE}
+demonstrates the simulation results for  
+The work in ~\cite{zhangusenix13} is a low-cost
+solution, but requires all backups for each day to occur at the same time and is less flexible than the approach presented here.
+}
+
 \comments{
@@
 It does not address  snapshot deletion and file system block packaging for fault tolerance.
+
 }
-
-Our previous work on parallel deduplication~\cite{zhangusenix13,WeiZhangIEEE} 
-is not a comprehensive VM-centric solution and does not address  snapshot deletion and file system block 
-packaging for fault tolerance.  The work in ~\cite{zhangusenix13} a low-cost
-solution, but requires all backups for each day to occur at the same time and is less flexible than the approach presented here.
 

### 2015-03-07 snapshot_system/mass_dedup.tex
prepare for mass conference
re

--- 2014-07-19 snapshot_system/paper_dedup.tex
@@
 Section~\ref{sect:vc-strategies} discusses  our key ideas and design for duplicate detection.
-Section~\ref{sect:delete} presents  a simplified snapshot deletion with  the VM-centric approach.
+%Section~\ref{sect:delete} presents  a simplified snapshot deletion with  the VM-centric approach.
 
@@
 
-We describe our overall deduplication approach as consisting of three
-complementary strategies: VM-local
-duplicate search, global deduplication using popular chunks, and 
-VM-centric file system block management. 
-\begin{itemize}
-\item 
-\textbf{Cross-VM global deduplication using popular chunks} --
+%We describe our overall deduplication approach as consisting of three
+%complementary strategies: VM-local
+%duplicate search, 
+%and %VM-centric file system block management. 
+%\textbf{Cross-VM global deduplication using popular chunks} --
+%global deduplication using popular chunks, 
 We separate the deduplication within a VM and cross VMs
@@
 is that for those chunks that appear in different VMs, the top $k$ most popular items
-dominate the appearance distribution.  
+dominate the appearance distribution following our previous evaluation~\cite{WeiZhangIEEE}.  
 Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 
@@
 }
+
+We describe two  complementary strategies below for the above  VM-centric design.
+%duplicate search, 
+%and %VM-centric file system block management. 
+%\textbf{Cross-VM global deduplication using popular chunks} --
+\begin{itemize}
 \item 
@@
 and this brings additional  failure protection for these chunks shared by many VMs.
-Appendix~\ref{sect:fault} provides a detailed analysis of snapshot availability
-under this VC scheme and compares it with VO.
+%Appendix~\ref{sect:fault} provides a detailed analysis of snapshot availability
+%under this VC scheme and compares it with VO.

### 2015-03-07 snapshot_system/mass_intro.tex
re

@@
 storage resource with them.  
-This paper follows our preliminary simulation study  in ~\cite{WeiZhangIEEE} to 
+This paper extends our preliminary simulation study  in ~\cite{WeiZhangIEEE} to 
 restrict the scope of cross-VM deduplication and simplify the deduplication process
 by separating popular data chunks and presents the design and implementation of 
-a VM-centric scheme.  
+a VM-centric backup scheme.  
 We term this approach {\em VM-centric} because the deduplication

### 2015-03-07 snapshot_system/mass.tex
re

@@
 %with Fault Isolation 
-\title{VM-Centric Snapshot Deduplication for Cluster-based Cloud Backup}
+\title{VM-Centric Snapshot Deduplication for Cloud Data Backup}
 %VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
@@
  \authorinfo{
-   Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
-Hong Tang$^\dagger$}
-   {$^\star$University of California at Santa Barbara \ \ \  
-   $^\dagger$Alibaba Inc. }
+   Wei Zhang$^{\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
+Hong Tang$^\dagger$\\
+   $^\star$University of California at Santa Barbara \ \ \  \\
+   $^\ast$Pure Storage Inc.\ \ \  $^\dagger$Alibaba Inc. }
 %  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
@@
 
-\input{paper_abs}
+\input{mass_abs}
 

### 2015-03-07 snapshot_system/mass.tex
re

@@
 \documentclass[10pt,reprint]{socc14}
+
+%\documentclass[conference]{IEEEtran}
+
 \usepackage{mathptmx}
@@
 \setlength{\pdfpagewidth}{\paperwidth}
-\conferenceinfo{Submission to SoCC '14}{October, 2014, Seattle, WA, USA}
-\copyrightyear{2014}
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
-\doi{nnnnnnn.nnnnnnn}
+%\conferenceinfo{Submission to SoCC '14}{October, 2014, Seattle, WA, USA}
+%\copyrightyear{2014}
+%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
+%\doi{nnnnnnn.nnnnnnn}
 %\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
@@
 }
+
  \authorinfo{
-   Wei Zhang$^{\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
+   Wei Zhang$^{\star,\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
 Hong Tang$^\dagger$\\
@@
 
+\comments{
+\author{
+\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1,2}, Daniel Agun\IEEEauthorrefmark{2}, 
+Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
+Hong Tan\IEEEauthorrefmark{3}}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}
+\IEEEauthorblockA{\IEEEauthorrefmark{2}Pure Storage Inc.}
+\IEEEauthorblockA{\IEEEauthorrefmark{3}Alibaba Inc.}
+%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$,
+%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
+%   {\normalsize $^\star$UC Santa Barbara}\\
+%   {\normalsize$^\dagger$Alibaba.com}
+}
+}
 \maketitle
@@
 
-\category{}{Information Systems}{Information Storage Systems}
-\category{}{Distributed Architectures}{Cloud Computing}
+%\category{}{Information Systems}{Information Storage Systems}
+%\category{}{Distributed Architectures}{Cloud Computing}
 %\category{D.2.8}{Information Systems}{Information Storage Systems}
-\terms{Design, Experimentation, Performance}
+%\terms{Design, Experimentation, Performance}
 
-\keywords
-Virtual machine images, snapshot backup and deletion, source-side deduplication, cluster-based architectures
+%\keywords
+%Virtual machine images, snapshot backup and deletion, source-side deduplication, cluster-based architectures
 

### 2015-03-07 snapshot_system/mass.tex
re

@@
-\documentclass[10pt,reprint]{socc14}
+%\documentclass[10pt,reprint]{socc14}
 
-%\documentclass[conference]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 
@@
 
+\comments{
  \authorinfo{
-   Wei Zhang$^{\star,\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
+   Wei Zhang$^{\star\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
 Hong Tang$^\dagger$\\
@@
   %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\
+}
 
-\comments{
 \author{
-\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1,2}, Daniel Agun\IEEEauthorrefmark{2}, 
+\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Daniel Agun\IEEEauthorrefmark{2}, 
 Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
@@
 %   {\normalsize$^\dagger$Alibaba.com}
-}
+
 }
@@
 %\appendix
-\bibliographystyle{abbrvnat}
+%\bibliographystyle{abbrvnat}
+\bibliographystyle{abbrv}
 \bibliography{library,dedup1}

### 2015-03-09 snapshot_system/mass_analysis.tex
prepare for mass conference
re

--- 2014-07-19 snapshot_system/paper_analysis.tex
@@
-\section{Impact on Fault Isolation}
+\subsection{Fault Tolerance and Snapshot Availability}
 \label{sect:fault}
@@
 Namely, 
-$
+\[
 A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
-$
+\]
 Then the availability of one VM's snapshot data under VO approach is the probability that
@@
 For VC, there are two cases: $r \le d<r_c$ and $r_c \leq d$.  
-
-\noindent $r \le d<r_c$:  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
+\begin{itemize}
+%\noindent 
+\item
+$r \le d<r_c$:  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
 The full snapshot availability of a VM is: 
@@
 
-\noindent $r_c \leq d$: Both non-PDS and PDS file system blocks in VC can have a loss.
+\item
+%\noindent 
+$r_c \leq d$: Both non-PDS and PDS file system blocks in VC can have a loss.
 The full snapshot availability of  a VM in the VC approach is
@@
 2)  $A(r) < A(r_c)$ because $r < r_c$.  
+\end{itemize}
+
 Table~\ref{tab:fsb-availability} lists the $A(r)$ values with

### 2015-03-09 snapshot_system/mass_dedupanalysis.tex
re

--- 2014-07-19 snapshot_system/paper_analysis.tex
@@
-\section{Impact on Fault Isolation}
-\label{sect:fault}
-We  analyze  the impact of losing $d$ physical machines 
-to the VM centric and oblivious approaches.  
-There are two impacts to VC. 
-1) Some PDS fingerprint lookup services do not respond.  As  a result, some duplicates
-are not detected and deduplication efficiency suffers, but the overall systems can still
-function well and fault tolerance is not affected.  As discussed in Section ~\ref{sect:architecture}, 
-PDS index is distributed
-among all machines in our implementation and thus a percentage of failed nodes
-causes an increase in missed duplicates proportionally.
-2) Some storage nodes do not  respond and file blocks on those machines are lost. The availability of
-VM snapshots is affected and we analyze this impact as follows.
-
-%A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
-%We use an FSB rather than a deduplication
-%data chunk as our unit of failure because the DFS keeps
-%file system blocks as its base unit of storage.
-To compute the full availability of all snapshots of a VM, we estimate
-the number of file system blocks per VM and the probability of losing a snapshot file system 
-block of a VM in each approach as follows.
-Parameters used in our analysis below are defined in Table~\ref{tab:symbol}.
-
-\begin{table}[htbp]
-%\begin{table}[t]
-\small
-\centering
-%\tabcolsep=0.11cm
-\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
-%\hline
-%$k$ &  the number of top most popular chunks selected for deduplication\\ 
-%\hline
-%$c$ &  the total amount of data chunks in a cluster of VMs\\ 
-%\hline
-%$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
-%\hline
-%$f_i$ &  the frequency for the $i$th most popular fingerprint\\
-%\hline
-%$\delta$ &  the percentage of duplicates detected in local deduplication\\
-%\hline
-%$\sigma$ & = percentage of unique data  belonging to  PDS\\
-\hline
-$r$, $r_c$ & replication degree of non-PDS and PDS file blocks in VC. $r$ is also replication degree in VO.\\
-\hline
-$n$, $p$ & no. of virtual and physical machines in the cluster\\
-%\hline
-%$V$ & the average number of VMs per machine\\
-%\hline
-%$E_c, E_o$ & deduplication efficiency of VC and VO \\
-%\hline
-%$D$ & the amount of unique data on each machine\\
-%\hline
-%$s$ & the average data chunk size. Our setting is  4K.\\
-%\hline
-%$s$ & the average number of chunks per FSB\\
-%\hline
-%$m$ & memory size on each node used by VC\\ 
-%\hline
-%$E$ & the size of an popular data index entry\\
-\hline
-$N_1$, $N_2$ & the average no.  of non-PDS and PDS file blocks in a VM in VC\\
-\hline
-$N_o$, $V_o$ & the average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
-\hline
-A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
-\hline
-\end{tabular}
-\caption{Modeling  parameters}
-\label{tab:symbol}
-\end{table}
-
-\begin{figure}[htb]
-    \centering
-    \subfigure[Sharing of file system blocks under VC]
-    {
-        \includegraphics[width=3in]{images/share_vc}
-        \label{fig:share_vc}
-    }
-    \\
-    \subfigure[Sharing of file system blocks under VO]
-    {
-        \includegraphics[width=3in]{images/share_vo}
-        \label{fig:share_vo}
-    }
-    \caption{Bipartite association of VMs and file blocks. }
-    \label{fig:share}
-\end{figure}
-
-%We analyze the impact of the above VM centric design on fault isolation and compare it
-%with a VM oblivious design.
-%Let $r$ be the replication degree of standard file blocks in the underlying backup storage. 
-%$r=3$ is a typical setting in distributed file systems~\cite{googlefs03,hdfs10}.
-%Let $r_c$ be the replication degree of file blocks for PDS. 
-%The replication degree of the backup storage 
-%is $r$ for regular file system blocks and 
-%Since $\sigma$ is small (e.g.  2\% in our experiments),  
-%the impact of replication on storage increase is very small even 
-%when choosing  $r_c/r$ ratio as 2 or 3.
-
-%In the VC approach, a special replication degree $r_c$ is used for PDS data where $r_c>r$. 
-%The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
-%$ k*r_c  + (c-E(c-c_u))*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
-%\[
-%\sigma \frac{r_c}{r} + \frac{c-e(c-c_u)}{c_u}.
-%\]
-%Since $\sigma$ is small (it is 2\% in our experiments),  
-%term $\sigma \frac{r_c}{r}$ is small in the above expression.  
-%Thus the impact on storage increase is very small even when we choose a large $r_c/r$ ratio. 
-%For example, $r_c/r=2$ or 3.
-
-%As illustrated in Figure~\ref{fig:share},
-%we build a bipartite graph representing the association from unique file system blocks
-%to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
-%if this block is used by the VM.
-
-As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
-association from unique file system blocks to their corresponding VMs in two 
-approaches. 
-%We use a file system block rather than data chunk as our unit of failure
-%because the underlying file system keeps file system blocks as its base unit of storage, and in
-%the case of 64MB file system blocks  and 4KB chunks, there are 16K chunks per file block. For VM centric,
-%we assign extra replication to the PDS blocks, while for VM oblivious, the replication
-%degree is fixed.
-For VC, each VM has an average number $N_1$ of non-PDS file system blocks
-and  has  an average of  $N_2$ PDS file system blocks. 
-Each non-PDS block is associated with only one VM.
-% and  we denote that PDS blocks are shared by an average of $V_c$ VMs. 
-By counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
-\[
-n* N_1   = \mbox{ Number of non-PDS file system blocks in VC.} 
-\]
-
-For VO, 
-%each VM has an average of $N_o$ file system blocks
-%and let $V_o$ be the average number of VMs shared by each file block.
-by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
-Table~\ref{tab:symbol},  we have 
-\[
-n *N_o   =  V_o * \mbox{Number of file system blocks in VO}.
-\]
-
-Since we choose 2-4\% of unique chunks for PDS
-and Section~\ref{sect:evaldedup} 
-shows that the deduplication efficiency of VC is very close to that of VO,
-the number of non-PDS file blocks in VC is fairly close to the number of file blocks in VO.
-Then
-\[
-\frac{N_o}{N_1} \approx  V_o.
-\]
-%Thus $N_o >> N_1$.
-
-Figure~\ref{fig:vm-links} shows $N_1$, $N_2$, and $N_o$ values of 105 VMs from a  test dataset 
-discussed in Section~\ref{sect:evaluation} when increasing the number of VMs.  
-%the average number of file system blocks for each VM in VC and in VO
-$N_1$ is much smaller than $N_o$ as the formula shows above.
-
-%In fact, $N_1 +N_2 < N_o$. 
-%This is likely because the PDS FSBs tightly pack data used by many VMs, 
-%which decreases the overall number of FSBs required to backup a VM.
-%Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
-%VMs sharing each file block on average in VO.
-
-%Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.
-
-\begin{figure}[htbp]
-  \centering
-	\begin{tikzpicture}
-		\begin{axis}[
-		%title={VO VM links},
-               % width=\linewidth,
-                width=0.7*\linewidth,
-                height=0.6\linewidth,
-		xlabel={Number of VMs},
-		ylabel={file system blocks},
-                xmin=0,
-                ymin=0,
-                xmax=106,
-		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
-		%legend pos=north east,
-                legend style={
-                    at={(1,0.825)},
-                    anchor=north east
-                },
-                %legend columns=3
-		]
-                \addplot[blue,mark=none] table[x=VMs,y=N_O] {figures/vm_links_all.txt};
-                %\addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
-                \addplot[red,dashdotted] table[x=VMs,y=N_1] {figures/vm_links_all.txt};
-                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N_2] {figures/vm_links_all.txt};
-                \legend{$N_o$,
-                    %$N_1+N_2$,
-                    $N_1$,
-                    $N_2$};
-		\end{axis}
-	\end{tikzpicture}
-  \caption{Measured average number of 64MB file system blocks used by a single VM in
-VC and VO. }
-  \label{fig:vm-links}
-\end{figure}
-
-%The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
-% $N_2$ for VC and $N_o$ for VO.
-Given $d$ failed machines and $r$ replicas for each file block,
-%normal data replication degree $r$, PDS data replication degree $r_c$, 
-the availability of a file block is the probability that  
-all of its replicas do not appear in any group of $d$ failed machines among $p$ nodes~\cite{CoHadoop2011}. 
-Namely, 
-$
-A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
-$
-Then the availability of one VM's snapshot data under VO approach is the probability that
- all its file blocks  are unaffected during the system failure:
-%\begin{equation}
-%\label{eq:VO}
-%(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
-\[
-A(r)^{N_o}. 
-\]
-%\end{equation}
-
-For VC, there are two cases: $r \le d<r_c$ and $r_c \leq d$.
-
-\noindent $r \le d<r_c$:  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
-The full snapshot availability of a VM is: 
-%\begin{equation}
-%\label{eq:VC1}
-%(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
-\[
-A(r)^{N_1}.
-\]
-%\end{equation}
-Since $N_1$ is typically much smaller than $N_o$, 
-the VC approach has a higher availability of VM snapshots than VO in this case.
-%In the evaluation discussed in Section~\ref{sect:evaldedup}, 
-%We have considered a worst case scenario where
-%every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
-%Even with $N_2$ being much higher than $N_o$ (as discussed below),
-%the availability of VC snapshots is much higher than VO.
-
-\noindent $r_c \leq d$: Both non-PDS and PDS file system blocks in VC can have a loss.
-The full snapshot availability of  a VM in the VC approach is
-%\begin{equation}
-%\label{eq:VC2}
-% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
-% *
-% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
-\[
-A(r)^{N_1} * A(r_c)^{N_2}.
-\]
-That is still smaller than that of $V_O$ based on the observations of our data. There are two reasons for this:  
-1) $N_1$ is much smaller than $N_o$ and we are observing that $N_1+N_2<N_o$. 
-2)  $A(r) < A(r_c)$ because $r < r_c$.  
-Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
-%that the availability of an individual file system block
-different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.
-%\end{equation}
-%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
-%In the evaluation discussed in Section~\ref{sect:evaldedup},
-%We have considered a worst case scenario that
-%every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
-%Even with that, the availability of VC snapshots is still much higher than VO and
-
-% $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
-
-\comments{
-\begin{figure}[htbp]
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-                width=\linewidth,
-                height=0.6\linewidth,
-            %title={FSB Availability},
-            cycle list name=mline,
-            xlabel={Number of Machines Failed},
-            ylabel={Availability of Single FSB (\%)},
-            %extra y ticks={99.9}, %to add extra ticks
-            mark options=solid,
-            legend pos=south west,
-            %legend columns=2,
-            %legend style={
-            %    at={(0.5,-0.2)},
-            %anchor=north}
-            ]
-            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
-            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
-            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
-            \legend{$R=5$,$R=4$,$R=3$};
-            \end{axis}
-    \end{tikzpicture}
-    \caption{Availability of a file system block in a 100 machine cluster with different replication 
-and failure settings.THIS PLOT WILL BE REPLACED BY TABLE}
-  \label{fig:fsb-availability}
-\end{figure}
-}
-
-\begin{table}
-  \centering
-    \footnotesize
-    \tabcolsep=0.11cm
-    \comments{%table data is obsolete, now uses pgfplotstable
-        \begin{tabular}{|l|l|l|l|}
-        \hline
-        \multirow{2}{*}{Failures ($d$)}   & \multicolumn{3}{c|}{$A(r_c)\times 100\%$} \\
-                                    %\cline{2-4}
-                                    & $r_c=3$ & $r_c=6$ & $r_c=9$ \\
-        \hline
-        3 & 99.9994 & 100 & 100\\
-        5 & 99.9939 & 100 & 100\\
-        10 & 99.9258 & 99.9999 & 99.9999 \\
-        20 & 99.2950 & 99.9967 & 99.9999 \\
-        \hline
-    \end{tabular}
-    }
-    \pgfplotstabletypeset[
-        columns={NodesFailed,Availability3,Availability6,Availability9},
-        columns/NodesFailed/.style={
-            column name={\multirow{2}{*}{Failures ($d$)}}
-        },
-        columns/Availability3/.style={
-            column name={\multicolumn{3}{c|}{$A(r_c) \times 100\%$}\\&$r_c=3$},
-            fixed, precision=9
-        },
-        columns/Availability6/.style={
-            column name={$r_c=6$},
-            fixed, precision=9},
-        columns/Availability9/.style={
-            column name={$r_c=9$},
-            fixed, precision=9},
-        every head row/.style={
-            before row={\hline},
-            after row={\hline},
-        },
-        every last row/.style={after row=\hline},
-        column type/.add={}{|},
-        every first column/.style={column type/.add={|}{}},
-    ]{figures/fsb_availability.txt}
-    \caption{$A(r_c)$ values in a cluster with p=100 nodes.}
-    \label{tab:fsb-availability}
-\end{table}
-
-\comments{
-\subsection{Impact on Deduplication Efficiency}
-Choosing the value $k$ for the most popular chunks affects the deduplication efficiency.
+\section{Impact on Deduplication Efficiency}
+Choosing the top $k$ value  for the most popular chunks affects the deduplication efficiency.
 We analyze this impact based on the characteristics  of the VM snapshot traces
@@
 exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
-Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
+%Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
 The parameters we will use in our analysis below are defined in
@@
 %Then  PDS coverage PDS increases as more VMs are involved.
-}

### 2015-03-10 snapshot_system/mass_background.tex
re

@@
 and uses more replication for data shared by more files,
-and we will adopt this idea.
+and we follow this idea and study VM-centric strategies.
 When the backup storage is implemented using a distributed file system such as Hadoop and 

### 2015-03-10 snapshot_system/mass_dedupanalysis.tex
re

@@
-\section{Impact on Deduplication Efficiency}
+\section{Impact of Top $k$ Value on Deduplication Efficiency}
+\label{sect:dedupanalysis}
+
 Choosing the top $k$ value  for the most popular chunks affects the deduplication efficiency.
@@
 %Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
-The parameters we will use in our analysis below are defined in
-Table~\ref{tab:symbol}.
+Additional parameters used in this analysis are defined in Table~\ref{tab:symbol2}.
+
+\begin{table}[htbp]
+%\begin{table}[t]
+\small
+\centering
+%\tabcolsep=0.11cm
+\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
+\hline
+$k$ &  the number of top most popular chunks selected for deduplication\\ 
+\hline
+$c$ &  the total amount of data chunks in a cluster of VMs\\ 
+\hline
+$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
+\hline
+$f_i$ &  the frequency for the $i$th most popular fingerprint\\
+\hline
+$\delta$ &  the percentage of duplicates detected in local deduplication\\
+\hline
+$\sigma$ & = percentage of unique data  belonging to  PDS\\
+%\hline
+%$V$ & the average number of VMs per machine\\
+\hline
+%$E_c, E_o$ & deduplication efficiency of VC and VO \\
+%\hline
+%$D$ & the amount of unique data on each machine\\
+%\hline
+%$s$ & the average data chunk size. Our setting is  4K.\\
+%\hline
+%$s$ & the average number of chunks per FSB\\
+%\hline
+%$m$ & memory size on each node used by VC\\ 
+%\hline
+%$E$ & the size of an popular data index entry\\
+%\hline
+%$N_1$, $N_2$ & the average no.  of non-PDS and PDS file blocks in a VM in VC\\
+%\hline
+%$N_o$, $V_o$ & the average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
+%\hline
+%A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
+%\hline
+\end{tabular}
+\caption{Parameters for modeling deduplication.}
+%\caption{Parameters for modeling deduplication with top $k$ popular chunks.}
+\label{tab:symbol2}
+\end{table}
 

### 2015-03-10 snapshot_system/mass_eval.tex
prepare for mass conference
re

--- 2014-07-19 snapshot_system/paper_eval.tex
@@
 \comments{
-old table, delete 4%
+%old table, delete 4%
     \begin{tabular}{|c|c|c|c|c|c|}
@@
     \end{tabular}
-
 }
@@
      \multicolumn{3}{|c|}{VC}  & VO \\ \hline
-&
-     2\%No PDS &2\%PDS     & 2\%PDS & SRB  \\ 
-&        &&     no-simi & \\ \hline
-Dedup &      93.02\%  & 96.01\% & 94.31\% & 97.86\% \\ 
+&       No PDS & No PDS &  2\%PDS     &   SRB  \\ 
+&       no simi &simi   &  simi    &\\ \hline
+Dedup & 75.86\%    &87.91\%  & 96.01\%   & 97.86\% \\ 
 Efficiency & &           &       &                 \\    \hline 
-Memory &      10MB & 118MB  & 108MB & 2.4GB \\ 
+Memory &     N/A&   10MB & 118MB  & 2.4GB \\ 
 per-machine & &     &   &    \\ \hline
@@
 Notice $\sigma$ is the percentage of unique chunks selected in PDS.
-With $\sigma =2\%$, Column 3 shows its 
+With $\sigma =2\%$, Column 4 shows its 
 %memory usage for PDS index lookup per machine is about 100MB per machine and  the 
@@
 Column 2 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
-using PDS and it achieves 93.02\% and  missed duplicates take  up-to  3.56\% of the original space, which
-is about 356GB per physical machine. 
-Column 4 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC which only uses
-the same offset in the parent segment to look for duplicates  but does not look for other potentially
-similar segments. 
+using PDS and local similarity search.
+It just relies on the file segment dirty bits maintained in the Alibaba  virtual machine platform.
+Thus there is no memory cost (marked as N/A).
+Thus segment-level version detection 
+reduces the data size to about 24.14\% of original data, 
+which is a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
+%Column 3 shows that with local similarity search,
+%deduplication efficiency achieves 93\%.
+% and  missed duplicates take  up-to  3.56\% of the original space, which
+%is about 356GB per physical machine. 
+Column 3 shows the deduplication result with similarity-guided local.
+It  can further reduce the data size
+to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction after the version-based
+deduplication.
+The popularity-guided global deduplication with $\sigma=2\% $
+reduces the data further to 860GB, namely 8.6\% of the original size. 
+So it provides additional 28.63\% reduction. 
+The overall memory usage of VC for each physical machine is very small, which is insignificant to other 
+hosted cloud services.  In comparison, the 2.4GB per-machine memory usage of SRB is very visible 
+to other services.
+
 %There is a big efficiency drop in this curve when the number of VMs is about 30.
+
 We explain why similarity-guided local search provides such an improvement as follows.
@@
 approximately 1/3 of the VMs in our dataset this movement happens frequently.
-In general, adding local similarity-guided search increases deduplication efficiency from 94\% to over 96\%.
-That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
-which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
+%Column 4 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC which only uses
+%the same offset in the parent segment to look for duplicates  but does not look for other potentially
+%similar segments. 
+Compared an approach in ~\cite{WeiZhangIEEE} which maintains additional offset dirty bits within each segment,
+ local similarity-guided search adds additional  deduplication efficiency about 3\%,
+which is a saving of 300GB per machine.
+%from 94\% to over 96\%.
+%That is one significant improvement compared to the work in 
+%which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
 % In general, our experiments show that
@@
 
-In summary, our experiments show that
-segment-level version detection 
-reduces the data size to about 24.14\% of original data, 
-which is a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
-Similarity-guided local search can further reduce the data size
-to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction after the version-based
- deduplication.
-The popularity-guided global deduplication with $\sigma=2\% $
-reduces the data further to 860GB, namely 8.6\% of the original size. 
-So it provides additional 28.63\% reduction. 
-The overall memory usage of VC for each physical machine is very small, which is insignificant to other 
-hosted cloud services.  In comparison, the 2.4GB per-machine memory usage of SRB is very visible 
-to other services.
 % even each physical machine in the production environment has 48GB memory.
@@
 
+\comments{
  \subsection{Effectiveness of Approximate Deletion}
@@
 
+}
 \comments{

### 2015-03-10 snapshot_system/mass_intro.tex
re

@@
 
-Our work  considers a backup service for converged cloud architectures
+Our work  considers a backup service with source-side deduplication for converged cloud architectures
 that is co-located with user VMs, sharing the cloud compute, network, and
@@
 resilience.  If a shared block is lost, all files that
-share that block are affected.  Our work is motivated by \cite{Reliability06} that provides more
-replication for shared file system blocks and proposes VM-centric techniques.
-to 
+share that block are affected~\cite{Reliability06} and  our work is motivated by this
+and develops VM-centric fault isolation techniques.
 \comments{
@@
 3) a design and implementation of a VM-centric  backup service to integrate and validate
-the proposed techniques while imposing  little resource usage and  minimizing the impact on other collocated cloud services.
+the proposed techniques while imposing  little resource usage and  minimizing the impact on other 
+collocated cloud services.We provide an analysis on the deduplication efficiency by using popular items
+and also on fault isolation.
 Our  experimental study compares  the VM-centric approach with the previous 

### 2015-03-10 snapshot_system/temp.tex
re

--- 2015-03-10 snapshot_system/mass_dedupanalysis.tex
@@
-\section{Impact of Top $k$ Value on Deduplication Efficiency}
-\label{sect:dedupanalysis}
-
-Choosing the top $k$ value  for the most popular chunks affects the deduplication efficiency.
-We analyze this impact based on the characteristics  of the VM snapshot traces
-studied from  application datasets.
-A previous study shows that the popularity of data chunks after local deduplication follows 
-a Zipf-like distribution\cite{Breslau1999a} and its
-exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
-%Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
 Additional parameters used in this analysis are defined in Table~\ref{tab:symbol2}.
@@
 %A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
-%\hline
+\hline
 \end{tabular}
-\caption{Parameters for modeling deduplication.}
-%\caption{Parameters for modeling deduplication with top $k$ popular chunks.}
-\label{tab:symbol2}
+\caption{Parameters for modeling deduplication with top $k$ popular chunks.}
+\label{tab:symbol}
 \end{table}
-
-%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
-%let $c$ be the total number of data chunks. 
-%$c_u$ be the total number of fingerprints 
-%in the global index after complete deduplication, and
-%$f_i$ be the frequency for the $i$th most popular fingerprint. 
-By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
-The total number of chunks in our backup storage which
-has local duplicates excluded is $c (1-\delta)$, this can be represented
-as the sum of each unique fingerprint times its frequency:
-%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
-\[
-f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
-\]
-Given $\alpha <1$, $f_1$ can be approximated with integration:
-%\begin{equation}
-\[
-f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
-\]
-%\end{equation}
-
-Thus putting the $k$ most popular fingerprints into PDS index can remove the following number of chunks during global 
-deduplication:
-\[
-f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
-f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}
-=c(1-\delta) \sigma^{1-\alpha}.
-\]
-
-Deduplication efficiency of the VC approach using top $k$ popular chunks
-is the percentage of duplicates that can be detected:  
-\begin{equation}
-\label{eq:dedupeff}
-%\begin{split}
-%e_k &= 
-E_c=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
-{c  - c_u }.\\
-%\end{split}
-\end{equation}
-
-% After the global deduplication, the number of remaining chunks is:
-% \[
-% c-E(c-c_u)
-% \]
-
-We store the PDS index using a distributed shared memory hash table such as Memcached
-and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
-As the number of physical machines ($p$) increases,
-the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
-a constant because each physical machine on average still hosts a fixed constant number of 
-VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
-remains constant.
-Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.
-
-\begin{figure}[htbp]
-\vspace{2em}
-
-  \centering
-    \begin{tikzpicture}
-            \begin{axis}[
-            %title={PDS Coverage},
-            width=\linewidth,
-            height=0.6\linewidth,
-            cycle multi list={
-                mline\nextlist
-                [3 of]mmark*\nextlist
-            },
-            %cycle list name=mcolor,
-            xlabel={Total num. chunks stored (in billions)},
-            ylabel={PDS Coverage (\%)},
-            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
-            mark options=solid,
-            %legend pos=outer north east,
-            legend columns=2,
-            legend style={
-                at={(0.5,-0.30)},
-            anchor=north},
-            ]
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
-            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
-            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
-            \end{axis}
-    \end{tikzpicture}
-  \caption{Predicted vs. actual PDS coverage as data size increases.}
-  \label{fig:cds-coverage}
-\end{figure}
-Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
-chunks detected as duplicates in global deduplication due to PDS.
-We call this PDS coverage.
-Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
-0.65 and measured PDS coverage in our test dataset.
-$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
-While the predicted value remains flat, measured PDS coverage increases as more VMs are involved.
-This is because the actual $\alpha$ value increases with the data size.
-%Then  PDS coverage PDS increases as more VMs are involved.

### 2015-03-10 snapshot_system/mass.tex
re

@@
 \usepackage{mathptmx}
-\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
+%\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
 \usepackage{subfigure}
@@
 %with Fault Isolation 
-\title{VM-Centric Snapshot Deduplication for Cloud Data Backup}
+\title{VM-Centric Snapshot Deduplication\\ for Cloud Data Backup}
 %VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
@@
 \author{
-\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Daniel Agun\IEEEauthorrefmark{2}, 
+\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{2}\IEEEauthorrefmark{1}, Daniel Agun\IEEEauthorrefmark{1}, 
 Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
@@
 %\appendix
+\appendices
+
+\input{mass_dedupanalysis}
 %\bibliographystyle{abbrvnat}
+%\bibliographystyle{ieeetr}
 \bibliographystyle{abbrv}
 \bibliography{library,dedup1}
+
 \end{document}

### 2015-03-12 snapshot_system/mass.tex
re

@@
 Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
-Hong Tan\IEEEauthorrefmark{3}}
+Hong Tang\IEEEauthorrefmark{3}}
 \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}

### 2015-03-12 snapshot_system/mass_analysis.tex
re

@@
 %\begin{table}[t]
-\small
+%\small
 \centering
@@
 \hline
-$r$, $r_c$ & replication degree of non-PDS and PDS file blocks in VC. $r$ is also replication degree in VO.\\
+$r$, $r_c$ & Replication degree of non-PDS and PDS file blocks in VC. $r$ is also replication degree in VO.\\
 \hline
-$n$, $p$ & no. of virtual and physical machines in the cluster\\
+$n$, $p$ & Number of virtual and physical machines in the cluster\\
 %\hline
@@
 \hline
-$N_1$, $N_2$ & the average no.  of non-PDS and PDS file blocks in a VM in VC\\
+$N_1$, $N_2$ & The average no.  of non-PDS and PDS file blocks in a VM in VC\\
 \hline
-$N_o$, $V_o$ & the average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
+$N_o$, $V_o$ & The average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
 \hline
-A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
+A(r) & Availability of a file block with $r$ replicas and $d$ failed physical machines\\
 \hline

### 2015-03-12 snapshot_system/mass_dedupanalysis.tex
re

@@
 studied from  application datasets.
-A previous study shows that the popularity of data chunks after local deduplication follows 
+Additional parameters used in this analysis are defined in Table~\ref{tab:symbol2}. 
+%A previous study shows that 
+The popularity of data chunks after local deduplication follows 
 a Zipf-like distribution\cite{Breslau1999a} and its
-exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
+exponent $\alpha$ is ranged between 0.65  and  0.7.
 %Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
-Additional parameters used in this analysis are defined in Table~\ref{tab:symbol2}.
 
@@
 \hline
-$k$ &  the number of top most popular chunks selected for deduplication\\ 
+$k$ &  The number of top most popular chunks selected for deduplication\\ 
 \hline
-$c$ &  the total amount of data chunks in a cluster of VMs\\ 
+$c$ &  The total amount of data chunks in a cluster of VMs\\ 
 \hline
-$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
+$c_u$ &  The total amount of unique fingerprints after perfect  deduplication\\
 \hline
-$f_i$ &  the frequency for the $i$th most popular fingerprint\\
+$f_i$ &  The frequency for the $i$th most popular fingerprint\\
 \hline
-$\delta$ &  the percentage of duplicates detected in local deduplication\\
+$\delta$ &  The percentage of duplicates detected in local deduplication\\
 \hline
-$\sigma$ & = percentage of unique data  belonging to  PDS\\
+$\sigma$ & The percentage of unique data  belonging to  PDS\\
 %\hline

### 2015-03-13 snapshot_system/mass_intro.tex
re
revise

@@
 It is memory-intensive to compare a large number of fingerprints and identify
-duplicates, even optimization or approximation techniques are developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
+duplicates, even with optimization or approximation techniques developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
 \comments{
@@
 share that block are affected~\cite{Reliability06} and  our work is motivated by this
-and develops VM-centric fault isolation techniques.
+to develop VM-centric fault isolation techniques.
 \comments{
@@
 Section~\ref{sect:conclusion}  concludes this paper.
-The appendix describes an analysis on the snapshot availability of our scheme during storage failures.
+The appendix describes an analysis on the deduplication  efficiency with top $k$ popular chunks.

### 2015-03-14 snapshot_system/mass.tex
added flushend
re

--- 2015-03-10 snapshot_system/mass.tex
@@
 \usepackage{soul}
+\usepackage{flushend} %automatically balance columns of last page
 \pgfplotsset{compat=1.5}
@@
 \author{
-\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{2}\IEEEauthorrefmark{1}, Daniel Agun\IEEEauthorrefmark{1}, 
+\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{2}, Daniel Agun\IEEEauthorrefmark{1}, 
 Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
-Hong Tan\IEEEauthorrefmark{3}}
+Hong Tang\IEEEauthorrefmark{3}}
 \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}

### 2015-03-14 snapshot_system/mass_abs.tex
re

@@
 cloud services.  This paper presents the design and implementation of
-a low-profile VM-centric backup service with  a tradeoff 
+a fast VM-centric backup service with  a tradeoff 
 for a competitive deduplication efficiency while using small computing resources, 
 suitable for running on a converged cloud architecture that cohosts  many other services.
-This cluster-based service restricts global deduplication and 
-separates popular chunks with non-popular ones.   
 The  developed optimization includes similarity-guided local search 

### 2015-03-14 snapshot_system/abs.tex
re

@@
 It restricts cross-VM deduplication under common blocks with extra replication support.
-Our analysis shows that  this VM centric scheme 
-can  provide  better fault tolerance while using a small amount of computing and storage resources. 
-This  paper  describes a comparative evaluation of this scheme in  accomplishing a competitive deduplication 
-efficiency while sustaining a good backup throughput.
+This  paper  describes an analytical and experimental evaluation of this scheme 
+in providing  better fault tolerance and competitive deduplication efficiency
+while using a small amount of computing and storage resources. 
+%for  accomplishing a competitive deduplication 
+%efficiency while sustaining a good backup throughput.
 

### 2015-03-14 snapshot_system/mass_abs.tex
re

@@
 detection is resource intensive when the backup service for VMs  is co-located with  other 
-cloud services.  This paper presents the design and implementation of
+cloud services.  This paper presents the design and analysis of
 a fast VM-centric backup service with  a tradeoff 
@@
 suitable for running on a converged cloud architecture that cohosts  many other services.
-The  developed optimization includes similarity-guided local search 
-for  the improved overall deduplication effectiveness 
-and  VM-centric file system block management for the increased VM snapshot availability.  
+The  design consideration includes 
+VM-centric file system block management for the increased VM snapshot availability.
+%and  similarity-guided local search for  the improved overall deduplication effectiveness. 
 %deduplication under popular chunks with extra replication support.
@@
 %by separating popular chunks and associating  file system blocks with one VM for non-popular chunks.
-This  paper  describes an evaluation of this VM-centric scheme to assess  its deduplication 
-efficiency, resource usage,  and fault tolerance.
+This  paper  describes an evaluation of this VM-centric scheme 
+to assess  its deduplication efficiency, resource usage,  and fault tolerance.
 

### 2015-03-14 snapshot_system/mass_conc.tex
re

--- 2014-07-19 snapshot_system/paper_conc.tex
@@
-\section{Conclusions}
+\section{Discussions and Conclusions}
 \label{sect:conclusion}
@@
 %the top of a cloud cluster to reduce network traffic and infrastructure requirements.
-The main contribution of this paper is the development and comparative study of a low-profile and VM-centric deduplication scheme that
+The main contribution of this paper is the development and analysis of a low-profile and VM-centric deduplication scheme that
 uses  a small amount of system resource in both snapshot deduplication and deletion
@@
 the sampled index~\cite{Guo2011} can deliver 97\% for a different test dataset. 
+Local similarity search removes 12.05\% of the original data after using a segment-based
+ dirty bit method and among them, 3\% is contributed by the increased similarity search compared to
+a simple dirty offset method in ~\cite{WeiZhangIEEE}.
 \item {\em Lower resource usage in deduplication}. 
@@
 the sampled index method is for a single-machine architecture.
-\item {\em Lower cost in snapshot deletion}. 
-The deletion in VC with summary vectors
-takes less than a minute for snapshot deletion using 15MB memory per machine
-and all machines can run this operation in parallel without data dependence. 
-The grouped mark-sweep method can take 43 hours using
-1.2 to 3GB memory per machine in our tested cases.
-The leak repair in VC takes 0.82 hours using 50MB on average while processing
-some VMs may use upto 1.96GB. Such a repair is conducted infrequently (e.g. every 19.6 days) 
 \item {\em Higher availability}. 
@@
 
+%We have also developed a VM-centric strategy for snapshot deletion and the VM-centric design
+%allows the deletion be localized for each VM, which greatly simplifies the reference counting
+%process. That is beyond  the scope of this paper.
+
+\comments{
+\item {\em Lower cost in snapshot deletion}. 
+The deletion in VC with summary vectors
+takes less than a minute for snapshot deletion using 15MB memory per machine
+and all machines can run this operation in parallel without data dependence. 
+The grouped mark-sweep method can take 43 hours using
+1.2 to 3GB memory per machine in our tested cases.
+The leak repair in VC takes 0.82 hours using 50MB on average while processing
+some VMs may use upto 1.96GB. Such a repair is conducted infrequently (e.g. every 19.6 days) 
+}
+
 %Currently we are studying how the

### 2015-03-14 snapshot_system/mass_dedup.tex
re

@@
 %significantly reduces the total amount of  searchable fingerprints. 
+Appendix~\ref{sect:dedupanalysis} provides an analysis of the $k$ value selection and
+PDS effectiveness.
+
+%under this VC scheme and compares it with VO.
 
@@
 %Note that this definition of content similarity is an approximation~\cite{resemblance97}.  
-This signature definition is motivated by the previous work for similarity-based routing in parallel
-deduplication~\cite{extreme_binning09,Dong2011} and near duplicate detection~\cite{shingling97}.
+This above approach is motivated by the previous work for similarity-based 
+deduplication~\cite{shingling97,extreme_binning09,Dong2011,Aronovich2009} while our focus is local search.
 

### 2015-03-14 snapshot_system/mass_intro.tex
re

@@
 It is memory-intensive to compare a large number of fingerprints and identify
-duplicates, even with optimization or approximation techniques developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
+duplicates, even with optimization or approximation techniques developed~\cite{Guo2011,Dong2011,extreme_binning09,FuFast2015}. 
 \comments{
@@
 The main contribution of this paper is
-1) a similarity-guided local deduplication for
-each VM to make the overall deduplication efficiency more competitive 
-to a transitional deduplication scheme;
+1) a design and implementation of a backup service 
+to integrate the VM-centric techniques while minimizing the resource impact on other 
+collocated cloud services;
 2) a VM-centric file block management to improve snapshot availability by
@@
 packaging data chunks from the same VM into a file system block as much as possible; 
-3) a design and implementation of a VM-centric  backup service to integrate and validate
-the proposed techniques while imposing  little resource usage and  minimizing the impact on other 
-collocated cloud services.We provide an analysis on the deduplication efficiency by using popular items
-and also on fault isolation.
+3) an analysis on the deduplication efficiency by using popular items
+and also on the impact of above fault isolation design on snapshot availability.
+The integrated optimization includes  similarity-guided local deduplication for
+each VM to make the overall deduplication efficiency more competitive 
+to a traditional deduplication scheme.
 Our  experimental study compares  the VM-centric approach with the previous 

### 2015-03-14 snapshot_system/mass_intro.tex
re

@@
 3) an analysis on the deduplication efficiency by using popular items
-and also on the impact of above fault isolation design on snapshot availability.
+and also on snapshot availability improved by the above fault isolation design. 
 The integrated optimization includes  similarity-guided local deduplication for

### 2015-03-14 snapshot_system/mass_conc.tex
re

@@
 Local similarity search removes 12.05\% of the original data after using a segment-based
- dirty bit method and among them, 3\% is contributed by the increased similarity search compared to
-a simple dirty offset method in ~\cite{WeiZhangIEEE}.
+ dirty bit method and among them, 3\% is contributed by the increased similarity search.
+Notice that our earlier study~\cite{WeiZhangIEEE} reaches 92\% of what global deduplication can do
+with a relatively simplier strategy and thus the new design in this paper makes a
+VM-centric scheme much more competitive to a traditional VM-oblivious approach.
 \item {\em Lower resource usage in deduplication}. 

### 2015-03-14 snapshot_system/mass_conc.tex
re

@@
 Notice that our earlier study~\cite{WeiZhangIEEE} reaches 92\% of what global deduplication can do
-with a relatively simplier strategy and thus the new design in this paper makes a
+with a relatively simpler strategy and thus the new design in this paper makes a
 VM-centric scheme much more competitive to a traditional VM-oblivious approach.

### 2015-05-07 snapshot_system/mass_arch.tex
change for msst

@@
 has been modified since last backup. 
-Segments are further divided into variable-sized chunks (average 4KB) 
+Segments are further divided into chunks 
+%(average 4KB) 
 using a content-based chunking algorithm~\cite{frame05}, 
@@
 In snapshot and segment recipes, 
-the data structures  include references to the actual data location to eliminate the need for additional indirection.
+the data structures  include reference IDs to the actual data location to eliminate the need for additional indirection.
 
@@
 %All PDS chunks are stored in one PDS file. 
-Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
+Each reference ID to a PDS data chunk in the PDS index is the offset within the PDS file.
 %There is an option to use a data structure similar to the non-PDS store. We opt
@@
 effective prefetching for sampled indexing.
+%MSST-CHANGE-BEGIN
+It should be noted that the above spatial locality number for PDS data 
+is subject to application characteristics and we plan to study further on this issue in the future.
+%MSST-CHANGE-END
 
@@
 The compaction  can work on one container at a time and move the in-use data chunks to another container. 
+%MSST-CHANGE-BEGIN
+The 1GB setting is based on our experience that compaction 
+performs well and can  complete  in a reasonable amount time.
+%MSST-CHANGE-END
 
@@
 group as a unit after compression. This  compression can reduce data by several times  in our tested data.
+%MSST-CHANGE-BEGIN
+For the experiments, we use LZO2 which is a lossless compression libary and does not affect snapshot
+data availability. 
+%MSST-CHANGE-END
 When accessing a particular chunk, its chunk group is retrieved from the storage
@@
 retrieval of  a data chunk  group naturally works well with prefetching. 
-A  typical chunk group contains 1000 chunks in our experiment.
+%MSST-CHANGE-BEGIN
+A  typical chunk group contains 1000 chunks in our experiment and this setting is effective
+for VM snapshot backup we are studying here.
 % with an average size of 200-600 chunks.
-
+%MSST-CHANGE-END
 %\item
@@
 %\item
-A non-PDS data chunk reference stored in the index of snapshot recipes
+A non-PDS data chunk reference ID stored in the index of snapshot recipes
 is composed of two parts: a container ID with 2 bytes and a local chunk ID with 6 bytes.
@@
 local chunk IDs are monotonically increasing.
-When a chunk is to be accessed, the segment recipe contains a reference pointing to  a data chunk, which is used to lookup up the chunk data as described shortly.
+When a chunk is to be accessed, the segment recipe contains a reference ID pointing to  
+a data chunk, which is used to lookup up the chunk data as described shortly.
 
@@
 For non-PDS data, this call places a chunk into 
-the snapshot store and returns a reference to be stored in the recipe of a snapshot. 
+the snapshot store and returns a reference ID to be stored in the recipe of a snapshot. 
 The write requests to append chunks to a VM store are accumulated at the client side. 
@@
 \noindent\textbf{Get()}.
-Fetching PDS data is straightforward since each reference contains 
+Fetching PDS data is straightforward since each reference ID contains 
 the file offset, and the size of a PDS chunk is available from a segment recipe.
 We also maintain a small data cache for the PDS data service to speedup common data fetching.
-To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client 
+To read a non-PDS chunk using its reference ID with container ID and local chunk ID,  the snapshot store client 
 first loads the
@@
 process leaves holes in the chunk ID values, but preserves the order and IDs of chunks.
-As a result, all data references stored 
+As a result, all data reference IDs stored 
 in recipes are permanent and stable, and the data reading process
@@
 depend directly on physical storage locations, which simplifies data migration.
+
+%MSST-CHANGE-BEGIN
+It should be emphasized that the deleted chunks are marked in the log but do not get deleted until compaction
+time.  Only compaction process will read and use this information.  
+New snapshots should not refer a chunk marked as deletion
+and referenced data will never enter the delete log. This is guaranteed 
+by the no-false-negative property of the bloom filter.
+%MSST-CHANGE-END
 \end{itemize}

### 2015-05-07 snapshot_system/mass_background.tex
change for msst

--- 2015-03-07 snapshot_system/mass_background.tex
@@
 data ``chunks''  to identify duplicate
-content~\cite{venti02,Rhea2008}.  In a simple implementation,
-it is expensive to compare a large number of 
-fingerprints
+content~\cite{venti02,Rhea2008}.  
+%MSST-CHANGE-BEGIN
+Source-side deduplication is studied at a chunk or file
+level~\cite{Vrable2009,Tan2010} for data backup and can be
+integrated  with global deduplication among multiple clients~\cite{Fu2014}.
+In this context, the client side deduplication is considered as the source-side
+and the client-side computing resource  restriction is not a primary concern.
+Our work considers the source-side deduplication in a cloud cluster environment before data is transferred
+to a backup storage and the computing resource constraint at the cluster side is a major concern.
+%MSST-CHANGE-END
+
+It is expensive to compare a large number of fingerprints
 so a number of techniques have been proposed to improve duplicate identification. 
-For example, the data domain method ~\cite{bottleneck08} 
+For example, the Data Domain method~\cite{bottleneck08} 
 uses an in-memory Bloom filter to identify non-duplicates and a prefetching cache for potential
@@
 Additional inline deduplication and  approximation techniques
-are studied in ~\cite{extreme_binning09,sparseindex09,Srinivasan2012,WeiZhangIEEE}.  
+are studied in the previous work~\cite{extreme_binning09,sparseindex09,Srinivasan2012,WeiZhangIEEE}.  
 %and a parallel batch solution for cluster-based deduplication is 
@@
 
-Index sampling with a prefetch cache  is proposed 
-in~\cite{Guo2011} for efficient single-machine deduplication. 
+Index sampling with a prefetch cache~\cite{Guo2011} 
+is proposed 
+for efficient single-machine deduplication. 
 This scheme uses 25GB memory per 500TB of raw data
@@
 is lost in the storage, all VMs that refer such chunks after deduplication face a data loss.
-The work in ~\cite{Reliability06} identifies such an issue in file systems 
-and uses more replication for data shared by more files,
-and we will adopt this idea.
+Such an issue has been identified in file systems~\cite{Reliability06}
+and more replication is used for shared data. we follow this idea and study VM-centric strategies.
 When the backup storage is implemented using a distributed file system such as Hadoop and 

### 2015-05-07 snapshot_system/mass_dedup.tex
change for msst

@@
 with those in  {\em potentially similar} segments from its parent snapshot.
+
+%MSST-CHANGE-BEGIN
+Similarity-guided search is effective for cases that  data chunks are deduplicated irregularly.
+For example, we found from the Alibaba's cloud cluster dataset that 
+data segment movement happens frequently and  files are  often rewritten rather than being
+modified in place.  A dirty-bit or offset-based detection is not able to detect such a movement.
+%MSST-CHANGE-END
+
 We consider a parent  segment is  potentially similar to the current dirty segment if 1) the parent segment

### 2015-05-07 snapshot_system/mass_eval.tex
change for msst

@@
 We will compare VC with a VO approach  using stateless routing with binning (SRB) 
-based on~\cite{Dong2011,extreme_binning09}.
+based on the previous work~\cite{Dong2011,extreme_binning09}.
 SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
-using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
-a machine, the chunk is compared with the fingerprint index within this machine locally based 
-on~\cite{extreme_binning09}.
+using  a min-hash function~\cite{extreme_binning09}. Once a data chunk is routed to
+a machine, the chunk is compared with the fingerprint index within this machine 
+locally~\cite{extreme_binning09}.
+%MSST-CHANGE-BEGIN
+While this VO approach is designed for general deduplication and data backup,
+we choose this VO approach as a baseline to compare because the other
+approaches would have  a similar level of computing resource usage.
+%MSST-CHANGE-END
 
@@
 Each physical machine deals with about 10TB of snapshot data and each 1TB data represents one snapshot version
-of 25 VMs.  Thus the total amount of raw snapshot shot in 100 physical machines
+of 25 VMs.  Thus the total amount of raw snapshot in 100 physical machines
 is about 1,000TB.
@@
 %The backup of VM snapshots is required to complete within few  hours every night.
-The daily snapshot change rate is about 2-3\% on average.
+%MSST-CHANGE-BEGIN
+Each machine hosts a variety of applications running these operating systems including web services and 
+database management. The amount of daily data update is not significant and
+the daily snapshot change rate is about 1-3\% on average.
+%MSST-CHANGE-END
 %All data are divided into 2 MB fix-sized segments and 
 The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
+Note that variable sizing is not required in our scheme and we just follow the setting in the previous work.
 %Each segment is divided into 
@@
      2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
-&     no-simi&   &&  &    \\ \hline
+&     no-simil&   &&  &    \\ \hline
 Dedup &     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
@@
 &       No PDS & No PDS &  2\%PDS     &   SRB  \\ 
-&       no simi &simi   &  simi    &\\ \hline
+&       no simil &simil   &  simil    &\\ \hline
 Dedup & 75.86\%    &87.91\%  & 96.01\%   & 97.86\% \\ 
@@
 %similar segments. 
-Compared an approach in ~\cite{WeiZhangIEEE} which maintains additional offset dirty bits within each segment,
+Compared a previous  approach~\cite{WeiZhangIEEE} which maintains additional offset dirty bits within each segment,
  local similarity-guided search adds additional  deduplication efficiency about 3\%,
@@
 
-Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
+Comparing the experiment results of the sampled index method~\cite{Guo2011}, 
 our scheme achieves a 85K:1 ratio between raw snapshot data and memory usage 
@@
 throughput would be higher. 
-In comparison, the sampled index method in~\cite{Guo2011} achieves about 5.5GB per second
+In comparison, the sampled index method~\cite{Guo2011} achieves about 5.5GB per second
 with 16 concurrent backup tasks and 6GB per second with

### 2015-05-07 snapshot_system/mass_intro.tex
re
change for msst

@@
 %Without deduplication,
-Source-side deduplication (e.g. ~\cite{Symantec2009})
+Source-side deduplication~\cite{Vrable2009,Tan2010,Fu2014,Symantec2009}
 eliminates duplicates before backup data is transmitted
@@
 storage resource with them.  
-This paper extends our preliminary simulation study  in ~\cite{WeiZhangIEEE} to 
+This paper extends our preliminary simulation study~\cite{WeiZhangIEEE} to 
 restrict the scope of cross-VM deduplication and simplify the deduplication process
@@
 and also on snapshot availability improved by the above fault isolation design. 
+The analysis provides insights and justification on the proposed VM-centric strategies.
 The integrated optimization includes  similarity-guided local deduplication for
@@
 VM-oblivious approaches in terms of deduplication efficiency, resource usage,  and snapshot availability.
+Compared to our earlier study~\cite{WeiZhangIEEE} which achieves 92\% of what the full deduplication
+can do, our integrated system delivers over  96\% in a tested dataset from Alibaba cloud. 
 %Thus we improve  to avoid such VM-oblivious packaging.

### 2015-05-07 snapshot_system/mass_arch.tex
re

@@
 has been modified since last backup. 
-Segments are further divided into chunks 
+Segments as super-chunks are further divided into chunks 
 %(average 4KB) 
@@
 
-Each non-PDS container is further divided into a set of chunk data groups. Each chunk group is composed of
-a set of data chunks and is the basic unit in data access and retrieval. 
+Each non-PDS container is further divided into a set of chunk groups for compression. Each chunk compression group is composed of
+a set of data chunks and is the basic unit for compression and for data access and retrieval. 
 In writing a chunk during backup, the system accumulates data chunks and stores the entire
@@
 %MSST-CHANGE-BEGIN
-For the experiments, we use LZO2 which is a lossless compression libary and does not affect snapshot
+For the experiments, we use LZO2 which is a lossless compression library and does not affect snapshot
 data availability. 
 %MSST-CHANGE-END
-When accessing a particular chunk, its chunk group is retrieved from the storage
+When accessing a particular chunk, its chunk compression group is retrieved from the storage
 and decompressed. Given the high spatial locality and usefulness of prefetching  in 
@@
 %MSST-CHANGE-BEGIN
-A  typical chunk group contains 1000 chunks in our experiment and this setting is effective
-for VM snapshot backup we are studying here.
+A  typical chunk compression group contains 1000 chunks in our experiment and this setting is effective
+for the VM snapshot dataset  experienced at Alibaba.
 % with an average size of 200-600 chunks.
@@
 %MSST-CHANGE-BEGIN
-It should be emphasized that the deleted chunks are marked in the log but do not get deleted until compaction
+It should be emphasized that the deleted chunks are marked in the log, but they do not get deleted until compaction
 time.  Only compaction process will read and use this information.  
 New snapshots should not refer a chunk marked as deletion
-and referenced data will never enter the delete log. This is guaranteed 
-by the no-false-negative property of the bloom filter.
+and referenced data will never enter the delete log. 
+%This is guaranteed by the no-false-negative property of the bloom filter.
 %MSST-CHANGE-END

### 2015-05-07 snapshot_system/mass_background.tex
re

@@
 Source-side deduplication is studied at a chunk or file
-level~\cite{Vrable2009,Tan2010} for data backup and can be
+level~\cite{Vrable2009,Tan2010} for client data backup and can be
 integrated  with global deduplication among multiple clients~\cite{Fu2014}.
-In this context, the client side deduplication is considered as the source-side
+In this context, the client side is the source-side
 and the client-side computing resource  restriction is not a primary concern.

### 2015-05-07 snapshot_system/mass_conc.tex
change for msst
re

@@
 consumption is acceptable in practice.
+%MSST-CHANGE-BEGIN
+The erasure code has been shown to be effective  to improve reliability on duplicated data 
+storage~\cite{Li2011} and such a technique can be incorporated.
+Other interesting future work includes
+studying the physical layout of backup images~\cite{SmaldoneWH13} and 
+further assessing the benefit of PDS separation.
+
+% and comparing with related work~\cite{Vrable2009,Tan2010,Fu2014}. 
+%MSST-CHANGE-END
 
@@
 
+\section*{Acknowledgments}
+{
+We would like to thank Yujuan Tan and the anonymous referees for their valuable comments,
+Hao Jiang, Xiaogang Li, Yue Zeng, Weicai Chen, and Shikun Tian from Alibaba for their kind support and feedback. 
+Wei Zhang has received internship support from Alibaba  for VM backup system development.
+This work was supported in part by NSF IIS-1118106.
+Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
+do not necessarily reflect the views of the National Science Foundation or Alibaba.
+}
+
 %Currently we are studying how the

### 2015-05-07 snapshot_system/mass_eval.tex
re

@@
 The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
-Note that variable sizing is not required in our scheme and we just follow the setting in the previous work.
+Note that variable sizing is not required in our scheme. 
 %Each segment is divided into 
@@
 single block tends to affect many VMs.
+The availability of PDS data is very high as seen in  Table~\ref{tab:fsb-availability} 
+with more  failures. On the other hand, the increasing of failures  gradually affects the availability of non-PDS data. 
+Overall speaking,  VC can  tolerate more failures compared to VO. 
 When the number of physical machines failed reaches 20, the availability of VO reaches 0\%

### 2015-05-08 snapshot_system/mass_eval.tex
minor changes

@@
 While this VO approach is designed for general deduplication and data backup,
-we choose this VO approach as a baseline to compare because the other
+we choose it as a baseline for comparison because the other
 approaches would have  a similar level of computing resource usage.

### 2015-05-22 snapshot_system/mass.tex
change for msst
add copyright info

@@
-%\documentclass[10pt,reprint]{socc14}
-
 \documentclass[conference]{IEEEtran}
@@
 \author{
-\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{2}, Daniel Agun\IEEEauthorrefmark{1}, 
+\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Daniel Agun\IEEEauthorrefmark{1}, 
 Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
@@
 \IEEEauthorblockA{\IEEEauthorrefmark{3}Alibaba Inc.}
-%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$,
-%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
-%   {\normalsize $^\star$UC Santa Barbara}\\
-%   {\normalsize$^\dagger$Alibaba.com}
+\IEEEauthorblockA{Email: wei@purestorage.com, \{dagun, tyang, rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com}
+}
 
-}
+\IEEEoverridecommandlockouts
+\IEEEpubid{978-1-4673-7619-8/15/\$31.00~\copyright~2015 IEEE}
 \maketitle
@@
 \bibliographystyle{abbrv}
-\bibliography{library,dedup1}
+\bibliography{library,dedup1,dedup15}
 

### 2015-05-22 snapshot_system/mass_intro.tex
add copyright info

@@
 
+\IEEEpubidadjcol
 Our work  considers a backup service with source-side deduplication for converged cloud architectures
